### 2019-11-21 Literature Review/Literature Review - Informal/sample.tex
Updated Literature Review, source file only

\documentclass[preprint,8pt]{report}

\usepackage{matlab-prettifier}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=0.5in,letterpaper]{geometry}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
\usepackage{listings}
\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\title{Literature Review - Informal}

\author{Aamal Hussain}

\date{\today}

\begin{document}

\maketitle
\tableofcontents

\chapter*{Introduction}

\textbf{Note: This review is a work in progress. Please expect an update on the Game Theoretic, Hard Coded and Multi Agent Dynamics sections of this review within the week. Verification in swarms may take a little more time for me to catch up with.} \newline

The areas of interest regarding Multi Agent Systems fall into two distinct categories (which have some slight overlap). The first is denoted as 'Decision Making', though the terms 'Planning' and 'Distributed Control' may sometimes be used as substitutes. It is important to note that, in my case, I do not include Planning Formalisation techniques such as PDDL. Instead, I focus on the particular methods which involve interaction in the world. The second, I will refer to as 'Multi Agent Dynamics', though sometimes I will refer to this as 'Stability Analysis'.

\subsection*{Scope}

Both of the aforementioned topics have been applied to all variants of multi agent systems and have sufficient room for further exploration. The typical variants of multi agent systems that I will consider are

\begin{itemize}
    \item Swarms
    \item Multi Agent Reinforcement Learning (MARL)
    \item Decentralised Partially Observed Markov Decision Processes (Dec-POMDP)
    \item Game Theoretic Approaches
    \item Hard Coded
\end{itemize}

In the above, 'Game Theoretic Approaches' cover a wide spectrum, including zero-sum (minimax) games, bayesian games, and many more. The final category, 'Hard Coded', refers to any approach which does not fit neatly into any of these categories. The name is chosen since they often refer to methods which revolve around a series of if-else statements.

I will first consider Decision Making as this is most closely related to the research proposal, before I consider Multi Agent Dynamics, which has strong implications for Safe and Trusted Multi Agent Systems.

\subsection*{Objectives}

The aim of the following sections is not to provide an exhaustive list of all work done in the aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With these directions, we may be able to narrow down the remaining literature review and hone in on particular problems and, in fact, we may find that we address multiple of these over the next four years (while we, of course add more). As such, the end of each chapter will provide a list of research directions which I have identified from the preceding review.

\chapter{Decision Making}

Decision making refers to the generalised problem of considering how a multi-agent system should interact in the world to achieve their goals. This subsumes both the cases where the agents' goals are aligned (cooperative) or in conflict with one another (competitive).

The following sections will provide an overview of the literature aimed towards coordinating such systems as followed by interesting sub-fields in each approach which present avenues for research related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added as the review progresses.

\section{Swarms}

Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves through a formation using a series of simple local interactions with their neighbours \cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour may exhibit complex phenomena emulating systems observed in biological organisations such as bee or ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated performance in reaching globally optimal solutions in search-based tasks. The advantage of many swarm algorithms is that they are based on local interactions and so are incredibly scalable \cite{Rizk2018}.

The reduction of the complexity in interactions between agents also allows for the robots to perform other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).

Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly adapt to the loss of agents or separation of groups throughout the task. However, the assumptions made regarding the homogeneity of individual agents and the simplicity of their local interactions result in significant limitations placed on the complexity of the tasks that swarm systems can accomplish.

\subsection{Co-evolution and Self-Healing}

Recently, there has been an increased interest in introducing heterogeneity into the swarm systems to improve their real world applicability. An example of this which have been shown strong real world success can be found in \cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two swarm teams, referred to as 'foot bots' and 'eye bots' who work in unison to explore an environment and solve a navigation task.

This area of research is sparsely populated and warrants further exploration. This is since the use of co-evolutionary teams can improve the robustness of the swarm optimisation. This is since it will be possible for a team to automatically determine when robots in the other team are not exhibiting expected behaviour and ensure that the other team self corrects. This process is referred to as 'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a user to define the goals of a swarm system. From this, a 'trust' metric can be defined which measures the deviation of each agent from the expected behaviour. The self-healing process occurs by limiting communication of all agents with 'untrusted' agents and encouraging communication with 'trusted' agents. The unison of self-healing with co-evolution may present the opportunity for heterogenous swarms to maintain their evolutionary stability, even in the face of environmental disturbances.

\subsection{Fault Detection}

The above sections have considered the fact that swarm systems are robust to losses in the group. However, any MAS system must first be able to recognise that an agent has undergone some failure.

To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop a robust fault detection approach in which the swarm itself, in a decentralised manner, is capable of assessing deviation from 'normal' behaviour, even when the behaviour of the swarm itself is altered (perhaps by a remote operator). The authors achieve this by requiring that the agents themselves sense and characterise their own behaviour. This characterisation is formulated as a binary feature vector which is then communicated to the agent's neighbours. These neighbours will reach a consensus over whether the agent should be treated as faulty based on their collective behaviour. The results presented in \cite{Tarapore2019FaultDetection} show extremely promising results and suggest that their method is, in fact, able to determine faults with high accuracy in the presence of various fault types (including sensor and actuator failures), although poor performance is seen in actuation failures in some instances. It should be noted that this method requires that each robot transmit their feature vector to the nearest neighbours. In environments where communication may be severely limited, this may present further errors. Furthermore, it is unlikely that, when a robot is damaged, only one of its components will be affected. Therefore, it is important to determine the effect on performance in the face of multiple agent failures and in communication losses. This exploration may open the possibility of improving the state of the art in terms of failure detection in swarm systems. (Of course, this conclusion is based off two papers so further review is required).

\subsection{Verification}

Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they require further reading

\subsection{Directions}

From the above consideration of swarms, the following research directions have been identified which, in my view, concern themselves with STAI.

\begin{itemize}
    \item Healing through co-evolution: The application of heterogenous robot swarms towards ensuring that emergent phenomenon and swarm behaviour are as expected by the user.
    \item Fault Detection in limited communication: Considering the ability of a swarm to, in a decentralised approach, consider which robots in the team have failed, even in cases of no communication or multiple failures.
\end{itemize}

\section{Dec-POMDPs}

The use of POMDPs in multi-agent settings is formalised as decentralised POMDP (Dec-POMDP) which aims for a team of agents to maximise a common utility. However, it has been found that determining the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and so is intractable for all but toy problems. A number of methods have been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such as brute force) are intractable for all but toy problems.

Approximate solutions to Dec-POMDP have been proposed, perhaps most notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by Amato et al. Here, macro actions (actions which extend over multiple time steps) are used, as opposed to low-level actions which are re-evaluated at each time step. This allows an exact solution to be found as it does not need to be evaluated at each time step. This method assumes that, once macro-actions are distributed, the policies (sequence of state-action pairs) are known. Since this is not the case, Amato also proposes the use of a Dec-POSMDP \cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to 'Semi-Markov Decision Process, in which a high level model is defined without the underlying Dec-POMDP's actions and observations.

However, this is largely applicable in passive settings where common payoffs can be determined by an offline planner. They also require a significant amount of data with which to allow the system to learn the underlying models and payoff structures. This limits the applicability of the system when communication is limited and the system is presented with environments that it has not seen before. Recent work in MDPs \cite{Klima2019RobustDomains} has considered learning in the face of Significant Rare Events (SREs) which the system has not yet observed. Currently, it is required that a model of such SREs is known and so it would be interesting to consider the application of Dec-POMDPs in situations where the SRE model is incomplete or erroneous and assess the robustness of the Dec-POMDP framework against such events.

\subsection{Directions}

The area of Dec-POMDPs still requires more review from me, especially for solutions which are not developed by Amato as he seems to largely dominate the field. Based on this initial review of the area, a potential direction for research is

\begin{itemize}
    \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to SREs which have a limited or erroneous model.
    \item Agent Failures: The Dec-POMDP model uses a centralised planner which acts offline. It therefore assumes that the agents will be able to carry out their assigned tasks. It would be interesting to examine the possibility of, either adaptive planning, or planning with contingencies in the Dec-POMDP framework.
\end{itemize}

\section{Game Theoretic Approaches}

Game theoretic models are generally the go-to method for understanding multi-agent systems. As such they fit into all of the categories in this chapter (except, perhaps, swarms) since Dec-POMDP and MARL methods have both used game theory to support their frameworks. In fact, Dec-POMDP is a subset of Partially Observed Stochastic Games (POSG), in which all agents use the same payoff. Game theory can, therefore, be used in an applied capacity to direct task allocation across heterogenous teams.

\subsection{Market Based Methods}

Garapati et al. \cite{Garapati2018AMissions} define a market based method as the setting where agents "follow their own interests and establish the mechanism of a market for distributing the tasks". Auctioning is the most widely used sub-field of market approaches and so I will use them interchangeably.

Whilst there are different variants to autioning, the general procedure is that an auctioneer who has knowledge of a task (or multiple tasks) will set up an auction for said task. Agents can then make bids on these tasks and, once the auction is complete, the highest bid will win the task. In the specific application to robotics, a robot's bid will often reflect the costs, suitability or utility their undertaking the task \cite{BernardineDias2006Market-basedAnalysis}. This immediately highlights a few points. The first is that the method is not too heavily reliant upon a single processor to determine some joint policy. Tasks are allocated on a case-by-case basis and the utilities are calculated by the agent themselves. The only centralised process is the auctioneer's assessment of the winner which then relays this information back to them. The downside of this is that the system is heavily reliant upon strong communication channels, without which tasks may not be assigned, incorrect utilities may be communicated and, in general, sub-optimal solutions reached. Furthermore, the requirement that the agents themselves determine the cost of their actions assumes that they have the computational capability to do so. Furthermore, the bids placed by each agent need to be a strong representation of their capability to perform a task which may be hard to estimate without expert knowledge. However, market based methods are well suited to explanation through argumentation (similar to \cite{Jung2001DistributedArgumentation}.

With well chosen payoffs, market based approaches work extremely well. For instance, in \cite{Dias2000ASystem}, the authors show that a free market approach (where agents try to maximise their own profits) can lead to a strong collaborative effort across teams. Similarly, in \cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the auctioning scheme presented in \cite{Gerkey2002Sold:Coordination} towards a robot construction team. However, it is important to note that these are both passive settings; tasks were assigned before the team were in the field and, in the case of \cite{Gerkey2002Sold:Coordination}, the system would repeat the bidding process if a robot failed. While both show strong performance, it cannot be said that either would be applicable in dangerous environments in which dynamic reassignment must happen within strict time constraints. Stancliff et al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust method to planning would be to account for failures a priori, a philosophy which is exemplified in \cite{Chen2010ACollaboration} who consider the robot's reliability and relevance to a task as well as 'history relevance' which considers the relationship between pairs of robots with the aim of producing more effective teams.

There has also been some interesting work in probabilistic verification of market based approaches. Most notable to me is \cite{Pallottino2007ProbabilisticAvoidance} which considers the case of conflict avoidance. Though their method focuses on collision avoidance, it highlights the need for verification of conflict resolution and goal achievement in market based approaches with different payoff structures. Sirigineedi et al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this direction by considering the verification of cooperative surveillance along a route network. From my understanding, this means that they were able to verify that their agents were able to traverse along the network without interference. However, this, as always, requires further analysis to truly understand.

\subsection{Directions}

The particular considerations which have jumped out to me from the above analysis are as follows:

\begin{itemize}
    \item Verification of goal achievement under different payoffs: can we ensure that self-interested agents will, in fact, show cooperative emergent properties? A similar question arises in terms of valuations (how much cost each agent incurs).
    \item A priori consideration of reliability: Can we learn and take into account the fact that robots may fail throughout the progress of a mission when we assign tasks?
\end{itemize}

\subsection*{Stochastic Games}

\section{Hard Coded}

\section{MARL}

Reinforcement learning extends the Markov Decision Process problem by considering the case where the payoff model is not known. This, of course, is the case for most real world environments. As such, MARL algorithms can perhaps be considered to be more applicable than Dec-POMDP models. Fortunately, MARL has picked up a lot of traction in research recently, with a large body dedicated towards solving the many problems it presents.

The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted in the Multi Agent setting since other agents in the environment will be learning concurrently. This learning will be based on their own history of interactions which extend beyond the previous state. As such, we must now consider that the policy for any one agent will depend on the policy of all other agents. As such, a big concern in this area is regarding convergence guarantees and the stability of the learner system. Approaches to this will be discussed in the next chapter.

\subsection*{Agent Modelling}

Returning to the problem of non-stationarity, solutions have been presented in which the agent models the learning of other agents. A noteworthy example of this is found in \cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other agents' learning and optimises with respect to this expected return. They show that this leads to stable learning and can even lead to emergent cooperation from competition. However, the method requires that both agents have exact knowledge of the others' value functions in order to perform the one step lookahead. Furthermore, it has only been considered for the case of a two agent adversarial game and so the scalability of the system to multiple agents is not yet understood. Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect the actions and observations of all agents and allows it to model the joint policy of teammates. This is shown to generate cooperative behaviour across four agents and so is more applicable to real world settings. However, its disadvantage over the method presented in \cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this requires the presence of an agent (perhaps a laptop) which is able to handle the computational load of determining a joint policy across all agents and must then communicate the Q-values of all agents back to them. This is both a taxing both in terms of computation and time.

Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by tasking a CNN with determining the policy features of other agents and then embedding these as features in its own DQN. This shows strong performance in settings where other agents dynamically change their policies. The concerns with this, however, are that, as the number of agents in the field increase, the CNN in each agent must perform another approximation. This places strong requirements on the performance of the CNN since errors in estimation will accumulate as the number of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are added.

Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent modelling is an important one to ensure stable learning and to understand the evolution of the system. It also presents a strong challenge and is open to exploration. To put it in context the methods described in this section are all from 2018-19, so its all very new.

\subsection{Directions}

I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions. However, on initial assessment I put forward

\begin{itemize}
    \item Modelling evolving teammates: The purpose of this is to more strictly ensure the stability of the learning process. However, the particular problem I suggest is to consider the modelling in a decentralised manner and with the consideration of evolving numbers of agents in teams.
\end{itemize}

\section{Dec-POMDPs and MARL}

As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in \cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs. The methods which I feel may be applicable are 
\begin{itemize}
    \item Alternating Maximisation: This is effectively coordinate ascent for determining a joint policy.
    \item Approximation as Bayesian Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does, however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games 
    \item Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In order to make this work, we would also need to consider how to select the feature space of sub-trees and how to collect this information.
\end{itemize}

\chapter{Multi Agent Control}

Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent Systems (MAS). This model then serves to be able to predict the evolution of a learning system as well as to understand the trajectory of learning. Typically, this looks at considering whether or not the method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this applicability into real world settings requires the study of stable equilbrium points; \cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE) are not necessarily the same and, in fact, argue that stable points are more informative than NEs. Stability provides some guarantees against the stochastic nature of the environment since a stable equilibrium will always be returned to even after perturbations. This extremely important in Safe and Trusted AI as it provides guarantees against undesired behaviour in real world learning environments.

\section{Stability of Learning Agents}

Stability may be looked at from the view point of two perspectives. The first is from an optimisation point of view. This considers the dynamics of the learning model, allowing us to better choose our parameters and design our models so that they may converge to a stable result. The second is from the view point of the state-action space of a learnt model. This allows us to determine, before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability analysis allows us to build multi agent systems which will learn and act in the way that we expect them to.

In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is one in which the loss function is twice differentiable. Using this formulation, they are able to analyse the system from new perspectives by considering the current state-of-the-art understanding of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical exercise, they go on to show that the insights gained allow them to develop a new multi-objective optimisation technique for GANs which shows stronger convergence properties, most notably of which is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the two players' loss functions.

Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement learning agent as a non-linear, time varying feedback controller. Using this notion, they then consider the bounded-input-bounded-output stability of the system. They do this by analysing the ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains finite then the system may be considered to be stable. They then apply these considerations on real-world applications including multi-agent flight formation and obtain stability certificates (essentially confirming that the system will remain stable under certain conditions) for the learned controller.

Berkenkamp et al. \cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different definition of stability. Specifically, they look at stability from the point of view of Lyapunov functions. A system is said to be stable if the applying the policy will result in stricly lower evaluations of the function. In other words, a system is stable if its corresponding Lyapunov function is decreasing towards a minimum point. The authors use this idea to define a 'region of attraction' in which the system is stable in the sense of Lyapunov. The goal of Safe Lyapunov Learning, a method which they develop from these insights, is to learn a policy without leaving this region of attraction. They do this by taking measurements within the set and using this to learn about the system dynamics, thereby increasing the safe set. With this, we now have a guarantee that policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and exploration.

As we can see from the discussion thus far, there are many definitions and perpectives of stability, each lending to a new understanding of learning systems. To add another to the mix, Milchtaich in \cite{Milchtaich2007StaticGames}, presents a notion of static stability. This means that it is based solely on the incentives of the players and does not require a consideration of the dynamics of the system. Milchtaich's definition of a stable system is one in which, when perturbed, it is more beneficial for an agent to move back towards the equilibrium than it is for them to move away. This is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows that it is applicable to all strategic games, within certain assumptions (finite set of player and continuous strategy space) and considers probabilistic perturbations from the original state. This is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy spaces) since these systems require random exploration of the strategy space and the dynamics are not known a priori. However, the lack of dynamics means that we do not consider the evolution of learning.

\subsection{Directions}

The above discussion has illustrated a few points. The first, and perhaps most important, is that stability is extremely applicable to Multi Agent Reinforcement Learning. This is because of the fact that learning agents, especially in real world environments, are subject to uncertainty and perturbations as well as epsilon-random exploration. As such, it is important that the system is able to return to a stable state after such perturbations. This leads to the need to develop learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge to stable fixed points.

The second point is that the notion of stability has multiple definitions. Each one is appropriate in different conditions and, as such, it is important to explore stability from various viewpoints to consider how to best understand the evolution of a learning system.

Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open question and is well worth consideration. This would help guide the choice of loss functions and strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a dramatic impact on the safety certification of MARL systems.

The problem of finding stable solutions through multi agent dynamics also opens the door for a large degree of application domains which are currently quite sparse. I would recommend looking at the contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems control and economic modelling. My particular interest, as always, lies within robotic control problems. This appears to be the most direct and relevant application of stable MAS systems; we can, for instance, use MARL to determine control rules which will lead to stable performance of the system. An example of this might be the problem of Cooperative Moving Path Following Control considered by \cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a pre-defined path without interfering with one another. It is clear then that each player's control is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to determine control rules which lead to stable coordination across the team. Similarly, we can model consider modelling a controller and an adversarial environment as a zero-sum game as examined in \cite{Marden2018AnnualControl}. Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that of Generative adversarial networks (GANs) which can be considered as a two player minimax game with differentiable loss functions.

The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem, Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees, Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found particularly relevant to this study. However, they will require some further analysis before I write about them here.

\bibliographystyle{IEEEtran}
\bibliography{IEEEfull,references}

\end{document}

### 2019-11-26 Literature Review/Literature Review - Informal/sample.tex
Updated Literature review with MARL algorithms

@@
 \chapter*{Introduction}
-
-\textbf{Note: This review is a work in progress.
-Please expect an update on the Game Theoretic, Hard Coded and Multi Agent Dynamics sections of this review within the week.
-Verification in swarms may take a little more time for me to catch up with.} \newline
 
@@
 
-\section{Dec-POMDPs and MARL}
+\section{MARL Approaches}
+
+The task of MARL is to determine an optimal joint policy for all agents across the game.
+This joint policy may be the concatenation of all the individual policy or it may just be options for each agent to take.
+In either case, optimality is defined through the standard notions of Nash equilibria and so, in this section, I will try to consider the broad spectrum of methods which attempt to achieve this Nash equilibria.
+I will start with the more foundational methods which are, thankfully, all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}.
+I will use the chapters of the book to help guide this review.
+I am not referencing the individual papers immediately, though the references can be found in the book.
+
+\subsubsection*{Learning in Two Player Matrix Games}
+
+The most fundamental method to learning in Matrix games is the simplex algorithm.
+This is a popular method of linear programming (in which constraints are linear).
+This will be important in considering more current methods.
+A similar consideration is given to the infinitesimal gradient ascent algorithm, in which the step size converges to zero.
+This method guarantees that, in the infite horizon limit, the payoffs will converge to the Nash equilibrium payoff.
+Note that this does not necessarily mean that both agents will converge to a single Nash equilibrium.
+This is a particular problem in games where there are multiple Nash equilibria.
+However, in practice it is difficult to choose a convergence rate of the step size and, without an appropriate choice the strategy may oscillate as shown in the book.
+To address this, a modified approach is presented by Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
+WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always to a NE.
+The concern with WoLF methods, however, is that it requires explicit knowledge of the payoff matrix (which is not so much of a problem for model based methods) and the opponent's strategy (which is more of a problem in real-world methods).
+Finally, the Policy Hill Climbing method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary (i.e.
+are not learning).
+However, it is shown that, when this is not the case, the algorithm again oscillates.
+The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both players with minimal oscillation.
+
+The above methods are all centralised techniques, in which a controller determines the optimal joint policy for both agents.
+However, in real scenarios it is often preferable that each agent learns their own strategy, a task which must be completed without information of the other agent's strategy.
+The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$) which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$ lagging anchor algorithm which can converge to both pure and mixed NEs.
+
+\subsubsection*{Learning in Multiplayer Stochastic Games}
+
+Stochastic Games (or Markov Games) form a basis for MARL settings.
+However, in this case the agents must learn about the equilibrium strategies by playing the game, which means they do not have a priori knowledge of the reward or transition functions.
+Schwarz considers two properties which should be used for evaluating MARL algorithm: rationality and convergence.
+The latter simply states that the method should converge to some equilibrium whereas the former suggests that the method should learn the best response to stationary opponents.
+A similar set of conditions is considered by Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly.
+Schwarz then presents a review of MARL methods (as of September 2014)
+
+\subsection*{Dec-POMDP and MARL}
 
@@
 
+\section{Learning Stable Agents}
+
+The above discussion has considered how notions of stability and control are important to Multi-Agent Learning.
+It stands to reason, therefore, that Multi-Agent Learning and, more specifically, game theory, can be used to develop controllers which drive systems to stable states.
+This idea is explored in \cite{Marden2018AnnualControl}.
+Here, a zero-sum game is considered in which the players are a controller and an adversarial environment.
+The design of the controller must be such that it is able to drive the system to zero error.
+To illustrate, consider the problem of designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which vortices seek to destabilise the agent.
+This will allow us to build stable agents in a much more efficient manner since we can simulate the adversarial environment and hypothetical scenarios the agent may encounter without actually encountering them.
+The same notion is explored by Bardi et al \cite{Bardi1991DifferentialDisturbances}.
+
+ Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision avoidance problem, similarly from the point of view of differential game theory.
+They develop a robust feedback system for the robots which they show to be able to drive the system towards predefined targets without interference from other agents.
+In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent systems
+
 \subsection{Directions}

### 2019-11-26 Literature Review/Literature Review - Informal/sample.tex
Updated Control section of Literature Review

@@
-\documentclass[preprint,8pt]{report}
+\documentclass[preprint,11pt]{report}
 
@@
 
-\maketitle
-\tableofcontents
+\maketitle tableofcontents
 
@@
 
-The areas of interest regarding Multi Agent Systems fall into two distinct categories (which have some slight overlap).
-The first is denoted as 'Decision Making', though the terms 'Planning' and 'Distributed Control' may sometimes be used as substitutes.
-It is important to note that, in my case, I do not include Planning Formalisation techniques such as PDDL.
-Instead, I focus on the particular methods which involve interaction in the world.
-The second, I will refer to as 'Multi Agent Dynamics', though sometimes I will refer to this as 'Stability Analysis'.
+The areas of interest regarding Multi Agent Systems fall into two distinct categories (which have
+some slight overlap). The first is denoted as 'Decision Making', though the terms 'Planning' and
+'Distributed Control' may sometimes be used as substitutes. It is important to note that, in my
+case, I do not include Planning Formalisation techniques such as PDDL. Instead, I focus on the
+particular methods which involve interaction in the world. The second, I will refer to as 'Multi
+Agent Dynamics', though sometimes I will refer to this as 'Stability Analysis'.
 
@@
 
-Both of the aforementioned topics have been applied to all variants of multi agent systems and have sufficient room for further exploration.
-The typical variants of multi agent systems that I will consider are
+Both of the aforementioned topics have been applied to all variants of multi agent systems and have
+sufficient room for further exploration. The typical variants of multi agent systems that I will
+consider are
 
-\begin{itemize}
-    \item Swarms
-    \item Multi Agent Reinforcement Learning (MARL)
-    \item Decentralised Partially Observed Markov Decision Processes (Dec-POMDP)
-    \item Game Theoretic Approaches
-    \item Hard Coded
-\end{itemize}
+\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
+Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
+Coded \end{itemize}
 
-In the above, 'Game Theoretic Approaches' cover a wide spectrum, including zero-sum (minimax) games, bayesian games, and many more.
-The final category, 'Hard Coded', refers to any approach which does not fit neatly into any of these categories.
-The name is chosen since they often refer to methods which revolve around a series of if-else statements.
+In the above, 'Game Theoretic Approaches' cover a wide spectrum, including zero-sum (minimax) games,
+bayesian games, and many more. The final category, 'Hard Coded', refers to any approach which does
+not fit neatly into any of these categories. The name is chosen since they often refer to methods
+which revolve around a series of if-else statements.
 
-I will first consider Decision Making as this is most closely related to the research proposal, before I consider Multi Agent Dynamics, which has strong implications for Safe and Trusted Multi Agent Systems.
+I will first consider Decision Making as this is most closely related to the research proposal,
+before I consider Multi Agent Dynamics, which has strong implications for Safe and Trusted Multi
+Agent Systems.
 
@@
 
-The aim of the following sections is not to provide an exhaustive list of all work done in the aforementioned areas.
-To attempt to do this would be an exercise in futility.
-Instead, it is to identify research directions which lie within the broad scope of Multi-Agent Systems (MAS).
-With these directions, we may be able to narrow down the remaining literature review and hone in on particular problems and, in fact, we may find that we address multiple of these over the next four years (while we, of course add more).
-As such, the end of each chapter will provide a list of research directions which I have identified from the preceding review.
+The aim of the following sections is not to provide an exhaustive list of all work done in the
+aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
+identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
+these directions, we may be able to narrow down the remaining literature review and hone in on
+particular problems and, in fact, we may find that we address multiple of these over the next four
+years (while we, of course add more). As such, the end of each chapter will provide a list of
+research directions which I have identified from the preceding review.
 
@@
 
-Decision making refers to the generalised problem of considering how a multi-agent system should interact in the world to achieve their goals.
-This subsumes both the cases where the agents' goals are aligned (cooperative) or in conflict with one another (competitive).
+Decision making refers to the generalised problem of considering how a multi-agent system should
+interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
+are aligned (cooperative) or in conflict with one another (competitive).
 
-The following sections will provide an overview of the literature aimed towards coordinating such systems as followed by interesting sub-fields in each approach which present avenues for research related to Safe and Trusted AI (STAI).
-These, of course, are not exhaustive and more will be added as the review progresses.
+The following sections will provide an overview of the literature aimed towards coordinating such
+systems as followed by interesting sub-fields in each approach which present avenues for research
+related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
+as the review progresses.
 
@@
 
-Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves through a formation using a series of simple local interactions with their neighbours \cite{Couceiro2015}.
-Whilst the individual agents are generally simplistic, the collective behaviour may exhibit complex phenomena emulating systems observed in biological organisations such as bee or ant colonies \cite{Sethi2017}.
-Hybrid algorithms such as in \cite{Gao2018} show an accelerated performance in reaching globally optimal solutions in search-based tasks.
-The advantage of many swarm algorithms is that they are based on local interactions and so are incredibly scalable \cite{Rizk2018}.
+Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
+through a formation using a series of simple local interactions with their neighbours
+\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
+may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
+ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
+performance in reaching globally optimal solutions in search-based tasks. The advantage of many
+swarm algorithms is that they are based on local interactions and so are incredibly scalable
+\cite{Rizk2018}.
 
-The reduction of the complexity in interactions between agents also allows for the robots to perform other calculations on board.
-In \cite{Pini2011TaskSelection}, Pini et al.
-leverage this by considering adaptive task partitioning across swarms.
-This allows a swarm, in a decentralised manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its whole.
-As of now (to the best of my knowledge) the problem of partitioning general tasks into its N sub-tasks is unexplored.
-This, however, highlights another advantage of swarm systems; they are readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
+The reduction of the complexity in interactions between agents also allows for the robots to perform
+other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
+considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
+manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
+whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
+sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
+readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
+divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
 
-Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a central controller \cite{Couceiro2015}.
-This presents the advantage that the system can rapidly adapt to the loss of agents or separation of groups throughout the task.
-However, the assumptions made regarding the homogeneity of individual agents and the simplicity of their local interactions result in significant limitations placed on the complexity of the tasks that swarm systems can accomplish.
+Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
+central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
+adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
+made regarding the homogeneity of individual agents and the simplicity of their local interactions
+result in significant limitations placed on the complexity of the tasks that swarm systems can
+accomplish.
 
@@
 
-Recently, there has been an increased interest in introducing heterogeneity into the swarm systems to improve their real world applicability.
-An example of this which have been shown strong real world success can be found in \cite{DucatelleSelf-organizedSwarms}.
-Here, the authors consider two swarm teams, referred to as 'foot bots' and 'eye bots' who work in unison to explore an environment and solve a navigation task.
+Recently, there has been an increased interest in introducing heterogeneity into the swarm systems
+to improve their real world applicability. An example of this which have been shown strong real
+world success can be found in \cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
+swarm teams, referred to as 'foot bots' and 'eye bots' who work in unison to explore an environment
+and solve a navigation task.
 
-This area of research is sparsely populated and warrants further exploration.
-This is since the use of co-evolutionary teams can improve the robustness of the swarm optimisation.
-This is since it will be possible for a team to automatically determine when robots in the other team are not exhibiting expected behaviour and ensure that the other team self corrects.
-This process is referred to as 'Self-Healing' in \cite{LiuTrust-Aware}.
-Here, the authors allow a user to define the goals of a swarm system.
-From this, a 'trust' metric can be defined which measures the deviation of each agent from the expected behaviour.
-The self-healing process occurs by limiting communication of all agents with 'untrusted' agents and encouraging communication with 'trusted' agents.
-The unison of self-healing with co-evolution may present the opportunity for heterogenous swarms to maintain their evolutionary stability, even in the face of environmental disturbances.
+This area of research is sparsely populated and warrants further exploration. This is since the use
+of co-evolutionary teams can improve the robustness of the swarm optimisation. This is since it will
+be possible for a team to automatically determine when robots in the other team are not exhibiting
+expected behaviour and ensure that the other team self corrects. This process is referred to as
+'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a user to define the goals of a
+swarm system. From this, a 'trust' metric can be defined which measures the deviation of each agent
+from the expected behaviour. The self-healing process occurs by limiting communication of all agents
+with 'untrusted' agents and encouraging communication with 'trusted' agents. The unison of
+self-healing with co-evolution may present the opportunity for heterogenous swarms to maintain their
+evolutionary stability, even in the face of environmental disturbances.
 
@@
 
-The above sections have considered the fact that swarm systems are robust to losses in the group. However, any MAS system must first be able to recognise that an agent has undergone some failure.
+The above sections have considered the fact that swarm systems are robust to losses in the group.
+However, any MAS system must first be able to recognise that an agent has undergone some failure.
 
-To this end, Tarapore et al.
-\cite{Tarapore2019FaultDetection} develop a robust fault detection approach in which the swarm itself, in a decentralised manner, is capable of assessing deviation from 'normal' behaviour, even when the behaviour of the swarm itself is altered (perhaps by a remote operator).
-The authors achieve this by requiring that the agents themselves sense and characterise their own behaviour.
-This characterisation is formulated as a binary feature vector which is then communicated to the agent's neighbours.
-These neighbours will reach a consensus over whether the agent should be treated as faulty based on their collective behaviour.
-The results presented in \cite{Tarapore2019FaultDetection} show extremely promising results and suggest that their method is, in fact, able to determine faults with high accuracy in the presence of various fault types (including sensor and actuator failures), although poor performance is seen in actuation failures in some instances.
-It should be noted that this method requires that each robot transmit their feature vector to the nearest neighbours.
-In environments where communication may be severely limited, this may present further errors.
-Furthermore, it is unlikely that, when a robot is damaged, only one of its components will be affected.
-Therefore, it is important to determine the effect on performance in the face of multiple agent failures and in communication losses.
-This exploration may open the possibility of improving the state of the art in terms of failure detection in swarm systems.
-(Of course, this conclusion is based off two papers so further review is required).
+To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop a robust fault detection
+approach in which the swarm itself, in a decentralised manner, is capable of assessing deviation
+from 'normal' behaviour, even when the behaviour of the swarm itself is altered (perhaps by a remote
+operator). The authors achieve this by requiring that the agents themselves sense and characterise
+their own behaviour. This characterisation is formulated as a binary feature vector which is then
+communicated to the agent's neighbours. These neighbours will reach a consensus over whether the
+agent should be treated as faulty based on their collective behaviour. The results presented in
+\cite{Tarapore2019FaultDetection} show extremely promising results and suggest that their method is,
+in fact, able to determine faults with high accuracy in the presence of various fault types
+(including sensor and actuator failures), although poor performance is seen in actuation failures in
+some instances. It should be noted that this method requires that each robot transmit their feature
+vector to the nearest neighbours. In environments where communication may be severely limited, this
+may present further errors. Furthermore, it is unlikely that, when a robot is damaged, only one of
+its components will be affected. Therefore, it is important to determine the effect on performance
+in the face of multiple agent failures and in communication losses. This exploration may open the
+possibility of improving the state of the art in terms of failure detection in swarm systems. (Of
+course, this conclusion is based off two papers so further review is required).
 
@@
 
-Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they require further reading
+Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
+require further reading
 
@@
 
-From the above consideration of swarms, the following research directions have been identified which, in my view, concern themselves with STAI.
+From the above consideration of swarms, the following research directions have been identified
+which, in my view, concern themselves with STAI.
 
-\begin{itemize}
-    \item Healing through co-evolution: The application of heterogenous robot swarms towards ensuring that emergent phenomenon and swarm behaviour are as expected by the user.
-    \item Fault Detection in limited communication: Considering the ability of a swarm to, in a decentralised approach, consider which robots in the team have failed, even in cases of no communication or multiple failures.
-\end{itemize}
+\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
+towards ensuring that emergent phenomenon and swarm behaviour are as expected by the user. \item
+Fault Detection in limited communication: Considering the ability of a swarm to, in a decentralised
+approach, consider which robots in the team have failed, even in cases of no communication or
+multiple failures. \end{itemize}
 
@@
 
-The use of POMDPs in multi-agent settings is formalised as decentralised POMDP (Dec-POMDP) which aims for a team of agents to maximise a common utility.
-However, it has been found that determining the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and so is intractable for all but toy problems.
-A number of methods have been presented to attempt to solve Dec-POMDPs.
-Oliehoek gives a review of these in \cite{OliehoekDecentralizedPOMDPs}.
-Most solutions (such as brute force) are intractable for all but toy problems.
+The use of POMDPs in multi-agent settings is formalised as decentralised POMDP (Dec-POMDP) which
+aims for a team of agents to maximise a common utility. However, it has been found that determining
+the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and so is intractable for all but
+toy problems. A number of methods have been presented to attempt to solve Dec-POMDPs. Oliehoek gives
+a review of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such as brute force) are
+intractable for all but toy problems.
 
-Approximate solutions to Dec-POMDP have been proposed, perhaps most notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by Amato et al.
-Here, macro actions (actions which extend over multiple time steps) are used, as opposed to low-level actions which are re-evaluated at each time step.
-This allows an exact solution to be found as it does not need to be evaluated at each time step.
-This method assumes that, once macro-actions are distributed, the policies (sequence of state-action pairs) are known.
-Since this is not the case, Amato also proposes the use of a Dec-POSMDP \cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to 'Semi-Markov Decision Process, in which a high level model is defined without the underlying Dec-POMDP's actions and observations.
+Approximate solutions to Dec-POMDP have been proposed, perhaps most notable of which is the proposal
+of MacDec-POMDP \cite{Amato2015} by Amato et al. Here, macro actions (actions which extend over
+multiple time steps) are used, as opposed to low-level actions which are re-evaluated at each time
+step. This allows an exact solution to be found as it does not need to be evaluated at each time
+step. This method assumes that, once macro-actions are distributed, the policies (sequence of
+state-action pairs) are known. Since this is not the case, Amato also proposes the use of a
+Dec-POSMDP \cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to 'Semi-Markov Decision
+Process, in which a high level model is defined without the underlying Dec-POMDP's actions and
+observations.
 
-However, this is largely applicable in passive settings where common payoffs can be determined by an offline planner.
-They also require a significant amount of data with which to allow the system to learn the underlying models and payoff structures.
-This limits the applicability of the system when communication is limited and the system is presented with environments that it has not seen before.
-Recent work in MDPs \cite{Klima2019RobustDomains} has considered learning in the face of Significant Rare Events (SREs) which the system has not yet observed.
-Currently, it is required that a model of such SREs is known and so it would be interesting to consider the application of Dec-POMDPs in situations where the SRE model is incomplete or erroneous and assess the robustness of the Dec-POMDP framework against such events.
+However, this is largely applicable in passive settings where common payoffs can be determined by an
+offline planner. They also require a significant amount of data with which to allow the system to
+learn the underlying models and payoff structures. This limits the applicability of the system when
+communication is limited and the system is presented with environments that it has not seen before.
+Recent work in MDPs \cite{Klima2019RobustDomains} has considered learning in the face of Significant
+Rare Events (SREs) which the system has not yet observed. Currently, it is required that a model of
+such SREs is known and so it would be interesting to consider the application of Dec-POMDPs in
+situations where the SRE model is incomplete or erroneous and assess the robustness of the Dec-POMDP
+framework against such events.
 
@@
 
-The area of Dec-POMDPs still requires more review from me, especially for solutions which are not developed by Amato as he seems to largely dominate the field.
-Based on this initial review of the area, a potential direction for research is
+The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
+developed by Amato as he seems to largely dominate the field. Based on this initial review of the
+area, a potential direction for research is
 
-\begin{itemize}
-    \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to SREs which have a limited or erroneous model.
-    \item Agent Failures: The Dec-POMDP model uses a centralised planner which acts offline.
-It therefore assumes that the agents will be able to carry out their assigned tasks.
-It would be interesting to examine the possibility of, either adaptive planning, or planning with contingencies in the Dec-POMDP framework.
-\end{itemize}
+\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
+SREs which have a limited or erroneous model. \item Agent Failures: The Dec-POMDP model uses a
+centralised planner which acts offline. It therefore assumes that the agents will be able to carry
+out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
+planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
 
@@
 
-Game theoretic models are generally the go-to method for understanding multi-agent systems.
-As such they fit into all of the categories in this chapter (except, perhaps, swarms) since Dec-POMDP and MARL methods have both used game theory to support their frameworks.
-In fact, Dec-POMDP is a subset of Partially Observed Stochastic Games (POSG), in which all agents use the same payoff.
-Game theory can, therefore, be used in an applied capacity to direct task allocation across heterogenous teams.
+Game theoretic models are generally the go-to method for understanding multi-agent systems. As such
+they fit into all of the categories in this chapter (except, perhaps, swarms) since Dec-POMDP and
+MARL methods have both used game theory to support their frameworks. In fact, Dec-POMDP is a subset
+of Partially Observed Stochastic Games (POSG), in which all agents use the same payoff. Game theory
+can, therefore, be used in an applied capacity to direct task allocation across heterogenous teams.
 
@@
 
-Garapati et al.
-\cite{Garapati2018AMissions} define a market based method as the setting where agents "follow their own interests and establish the mechanism of a market for distributing the tasks".
-Auctioning is the most widely used sub-field of market approaches and so I will use them interchangeably.
+Garapati et al. \cite{Garapati2018AMissions} define a market based method as the setting where
+agents "follow their own interests and establish the mechanism of a market for distributing the
+tasks". Auctioning is the most widely used sub-field of market approaches and so I will use them
+interchangeably.
 
-Whilst there are different variants to autioning, the general procedure is that an auctioneer who has knowledge of a task (or multiple tasks) will set up an auction for said task.
-Agents can then make bids on these tasks and, once the auction is complete, the highest bid will win the task.
-In the specific application to robotics, a robot's bid will often reflect the costs, suitability or utility their undertaking the task \cite{BernardineDias2006Market-basedAnalysis}.
-This immediately highlights a few points.
-The first is that the method is not too heavily reliant upon a single processor to determine some joint policy.
-Tasks are allocated on a case-by-case basis and the utilities are calculated by the agent themselves.
-The only centralised process is the auctioneer's assessment of the winner which then relays this information back to them.
-The downside of this is that the system is heavily reliant upon strong communication channels, without which tasks may not be assigned, incorrect utilities may be communicated and, in general, sub-optimal solutions reached.
-Furthermore, the requirement that the agents themselves determine the cost of their actions assumes that they have the computational capability to do so.
-Furthermore, the bids placed by each agent need to be a strong representation of their capability to perform a task which may be hard to estimate without expert knowledge.
-However, market based methods are well suited to explanation through argumentation (similar to \cite{Jung2001DistributedArgumentation}.
+Whilst there are different variants to autioning, the general procedure is that an auctioneer who
+has knowledge of a task (or multiple tasks) will set up an auction for said task. Agents can then
+make bids on these tasks and, once the auction is complete, the highest bid will win the task. In
+the specific application to robotics, a robot's bid will often reflect the costs, suitability or
+utility their undertaking the task \cite{BernardineDias2006Market-basedAnalysis}. This immediately
+highlights a few points. The first is that the method is not too heavily reliant upon a single
+processor to determine some joint policy. Tasks are allocated on a case-by-case basis and the
+utilities are calculated by the agent themselves. The only centralised process is the auctioneer's
+assessment of the winner which then relays this information back to them. The downside of this is
+that the system is heavily reliant upon strong communication channels, without which tasks may not
+be assigned, incorrect utilities may be communicated and, in general, sub-optimal solutions reached.
+Furthermore, the requirement that the agents themselves determine the cost of their actions assumes
+that they have the computational capability to do so. Furthermore, the bids placed by each agent
+need to be a strong representation of their capability to perform a task which may be hard to
+estimate without expert knowledge. However, market based methods are well suited to explanation
+through argumentation (similar to \cite{Jung2001DistributedArgumentation}.
 
-With well chosen payoffs, market based approaches work extremely well.
-For instance, in \cite{Dias2000ASystem}, the authors show that a free market approach (where agents try to maximise their own profits) can lead to a strong collaborative effort across teams.
-Similarly, in \cite{Thomas2005Multi-robotScenarios}, Thomas et al.
-apply the auctioning scheme presented in \cite{Gerkey2002Sold:Coordination} towards a robot construction team.
-However, it is important to note that these are both passive settings; tasks were assigned before the team were in the field and, in the case of \cite{Gerkey2002Sold:Coordination}, the system would repeat the bidding process if a robot failed.
-While both show strong performance, it cannot be said that either would be applicable in dangerous environments in which dynamic reassignment must happen within strict time constraints.
-Stancliff et al.
-\cite{Stancliff2009PlanningAllocation} suggest that a more robust method to planning would be to account for failures a priori, a philosophy which is exemplified in \cite{Chen2010ACollaboration} who consider the robot's reliability and relevance to a task as well as 'history relevance' which considers the relationship between pairs of robots with the aim of producing more effective teams.
+With well chosen payoffs, market based approaches work extremely well. For instance, in
+\cite{Dias2000ASystem}, the authors show that a free market approach (where agents try to maximise
+their own profits) can lead to a strong collaborative effort across teams. Similarly, in
+\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the auctioning scheme presented in
+\cite{Gerkey2002Sold:Coordination} towards a robot construction team. However, it is important to
+note that these are both passive settings; tasks were assigned before the team were in the field
+and, in the case of \cite{Gerkey2002Sold:Coordination}, the system would repeat the bidding process
+if a robot failed. While both show strong performance, it cannot be said that either would be
+applicable in dangerous environments in which dynamic reassignment must happen within strict time
+constraints. Stancliff et al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
+method to planning would be to account for failures a priori, a philosophy which is exemplified in
+\cite{Chen2010ACollaboration} who consider the robot's reliability and relevance to a task as well
+as 'history relevance' which considers the relationship between pairs of robots with the aim of
+producing more effective teams.
 
 There has also been some interesting work in probabilistic verification of market based approaches.
-Most notable to me is \cite{Pallottino2007ProbabilisticAvoidance} which considers the case of conflict avoidance.
-Though their method focuses on collision avoidance, it highlights the need for verification of conflict resolution and goal achievement in market based approaches with different payoff structures.
-Sirigineedi et al.
-\cite{Sirigineedi2010DecentralisedApproach} make a step in this direction by considering the verification of cooperative surveillance along a route network.
-From my understanding, this means that they were able to verify that their agents were able to traverse along the network without interference.
-However, this, as always, requires further analysis to truly understand.
+Most notable to me is \cite{Pallottino2007ProbabilisticAvoidance} which considers the case of
+conflict avoidance. Though their method focuses on collision avoidance, it highlights the need for
+verification of conflict resolution and goal achievement in market based approaches with different
+payoff structures. Sirigineedi et al. \cite{Sirigineedi2010DecentralisedApproach} make a step in
+this direction by considering the verification of cooperative surveillance along a route network.
+From my understanding, this means that they were able to verify that their agents were able to
+traverse along the network without interference. However, this, as always, requires further analysis
+to truly understand.
 
@@
 
-\begin{itemize}
-    \item Verification of goal achievement under different payoffs: can we ensure that self-interested agents will, in fact, show cooperative emergent properties?
-A similar question arises in terms of valuations (how much cost each agent incurs).
-    \item A priori consideration of reliability: Can we learn and take into account the fact that robots may fail throughout the progress of a mission when we assign tasks?
-\end{itemize}
+\begin{itemize} \item Verification of goal achievement under different payoffs: can we ensure that
+self-interested agents will, in fact, show cooperative emergent properties? A similar question
+arises in terms of valuations (how much cost each agent incurs). \item A priori consideration of
+reliability: Can we learn and take into account the fact that robots may fail throughout the
+progress of a mission when we assign tasks? \end{itemize}
 
@@
 
-Reinforcement learning extends the Markov Decision Process problem by considering the case where the payoff model is not known.
-This, of course, is the case for most real world environments.
-As such, MARL algorithms can perhaps be considered to be more applicable than Dec-POMDP models.
-Fortunately, MARL has picked up a lot of traction in research recently, with a large body dedicated towards solving the many problems it presents.
+Reinforcement learning extends the Markov Decision Process problem by considering the case where the
+payoff model is not known. This, of course, is the case for most real world environments. As such,
+MARL algorithms can perhaps be considered to be more applicable than Dec-POMDP models. Fortunately,
+MARL has picked up a lot of traction in research recently, with a large body dedicated towards
+solving the many problems it presents.
 
-The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}.
-In single-agent settings, it is assumed that the environment is Markovian.
-However, this must be lifted in the Multi Agent setting since other agents in the environment will be learning concurrently.
-This learning will be based on their own history of interactions which extend beyond the previous state.
-As such, we must now consider that the policy for any one agent will depend on the policy of all other agents.
-As such, a big concern in this area is regarding convergence guarantees and the stability of the learner system.
-Approaches to this will be discussed in the next chapter.
+The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
+single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
+in the Multi Agent setting since other agents in the environment will be learning concurrently. This
+learning will be based on their own history of interactions which extend beyond the previous state.
+As such, we must now consider that the policy for any one agent will depend on the policy of all
+other agents. As such, a big concern in this area is regarding convergence guarantees and the
+stability of the learner system. Approaches to this will be discussed in the next chapter.
 
@@
 
-Returning to the problem of non-stationarity, solutions have been presented in which the agent models the learning of other agents.
-A noteworthy example of this is found in \cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other agents' learning and optimises with respect to this expected return.
-They show that this leads to stable learning and can even lead to emergent cooperation from competition.
-However, the method requires that both agents have exact knowledge of the others' value functions in order to perform the one step lookahead.
-Furthermore, it has only been considered for the case of a two agent adversarial game and so the scalability of the system to multiple agents is not yet understood.
-Another method presented by Mao et al.
-\cite{MaoModellingDDPG} uses a centralised critic to collect the actions and observations of all agents and allows it to model the joint policy of teammates.
-This is shown to generate cooperative behaviour across four agents and so is more applicable to real world settings.
-However, its disadvantage over the method presented in \cite{Foerster2018LearningAwareness} is that the critic is centralised.
-In real world settings, this requires the presence of an agent (perhaps a laptop) which is able to handle the computational load of determining a joint policy across all agents and must then communicate the Q-values of all agents back to them.
-This is both a taxing both in terms of computation and time.
+Returning to the problem of non-stationarity, solutions have been presented in which the agent
+models the learning of other agents. A noteworthy example of this is found in
+\cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other
+agents' learning and optimises with respect to this expected return. They show that this leads to
+stable learning and can even lead to emergent cooperation from competition. However, the method
+requires that both agents have exact knowledge of the others' value functions in order to perform
+the one step lookahead. Furthermore, it has only been considered for the case of a two agent
+adversarial game and so the scalability of the system to multiple agents is not yet understood.
+Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect
+the actions and observations of all agents and allows it to model the joint policy of teammates.
+This is shown to generate cooperative behaviour across four agents and so is more applicable to real
+world settings. However, its disadvantage over the method presented in
+\cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this
+requires the presence of an agent (perhaps a laptop) which is able to handle the computational load
+of determining a joint policy across all agents and must then communicate the Q-values of all agents
+back to them. This is both a taxing both in terms of computation and time.
 
-Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by tasking a CNN with determining the policy features of other agents and then embedding these as features in its own DQN.
-This shows strong performance in settings where other agents dynamically change their policies.
-The concerns with this, however, are that, as the number of agents in the field increase, the CNN in each agent must perform another approximation.
-This places strong requirements on the performance of the CNN since errors in estimation will accumulate as the number of agents increases.
-Similarly, the complexity of the DQN will increase as more feature vectors are added.
+Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by
+tasking a CNN with determining the policy features of other agents and then embedding these as
+features in its own DQN. This shows strong performance in settings where other agents dynamically
+change their policies. The concerns with this, however, are that, as the number of agents in the
+field increase, the CNN in each agent must perform another approximation. This places strong
+requirements on the performance of the CNN since errors in estimation will accumulate as the number
+of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are
+added.
 
-Finally, all of the above methods are not robust to evolving numbers of agents.
-The problem of agent modelling is an important one to ensure stable learning and to understand the evolution of the system.
-It also presents a strong challenge and is open to exploration.
-To put it in context the methods described in this section are all from 2018-19, so its all very new.
+Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent
+modelling is an important one to ensure stable learning and to understand the evolution of the
+system. It also presents a strong challenge and is open to exploration. To put it in context the
+methods described in this section are all from 2018-19, so its all very new.
 
@@
 
-I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions. However, on initial assessment I put forward
+I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
+However, on initial assessment I put forward
 
-\begin{itemize}
-    \item Modelling evolving teammates: The purpose of this is to more strictly ensure the stability of the learning process.
-However, the particular problem I suggest is to consider the modelling in a decentralised manner and with the consideration of evolving numbers of agents in teams.
-\end{itemize}
+\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
+the stability of the learning process. However, the particular problem I suggest is to consider the
+modelling in a decentralised manner and with the consideration of evolving numbers of agents in
+teams. \end{itemize}
 
-\section{MARL Approaches}
+\section{MARL Approaches} \label{sec::MARL Approaches}
 
-The task of MARL is to determine an optimal joint policy for all agents across the game.
-This joint policy may be the concatenation of all the individual policy or it may just be options for each agent to take.
-In either case, optimality is defined through the standard notions of Nash equilibria and so, in this section, I will try to consider the broad spectrum of methods which attempt to achieve this Nash equilibria.
-I will start with the more foundational methods which are, thankfully, all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}.
-I will use the chapters of the book to help guide this review.
-I am not referencing the individual papers immediately, though the references can be found in the book.
+The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
+policy may be the concatenation of all the individual policy or it may just be options for each
+agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
+and so, in this section, I will try to consider the broad spectrum of methods which attempt to
+achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
+all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
+to help guide this review. I am not referencing the individual papers immediately, though the
+references can be found in the book.
 
@@
 
-The most fundamental method to learning in Matrix games is the simplex algorithm.
-This is a popular method of linear programming (in which constraints are linear).
-This will be important in considering more current methods.
-A similar consideration is given to the infinitesimal gradient ascent algorithm, in which the step size converges to zero.
-This method guarantees that, in the infite horizon limit, the payoffs will converge to the Nash equilibrium payoff.
-Note that this does not necessarily mean that both agents will converge to a single Nash equilibrium.
-This is a particular problem in games where there are multiple Nash equilibria.
-However, in practice it is difficult to choose a convergence rate of the step size and, without an appropriate choice the strategy may oscillate as shown in the book.
-To address this, a modified approach is presented by Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always to a NE.
-The concern with WoLF methods, however, is that it requires explicit knowledge of the payoff matrix (which is not so much of a problem for model based methods) and the opponent's strategy (which is more of a problem in real-world methods).
-Finally, the Policy Hill Climbing method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary (i.e.
-are not learning).
-However, it is shown that, when this is not the case, the algorithm again oscillates.
-The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both players with minimal oscillation.
+The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
+method of linear programming (in which constraints are linear). This will be important in
+considering more current methods. A similar consideration is given to the infinitesimal gradient
+ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
+infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
+not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
+particular problem in games where there are multiple Nash equilibria. However, in practice it is
+difficult to choose a convergence rate of the step size and, without an appropriate choice the
+strategy may oscillate as shown in the book. To address this, a modified approach is presented by
+Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
+WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
+to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
+payoff matrix (which is not so much of a problem for model based methods) and the opponent's
+strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
+method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
+(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
+oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
+players with minimal oscillation.
 
-The above methods are all centralised techniques, in which a controller determines the optimal joint policy for both agents.
-However, in real scenarios it is often preferable that each agent learns their own strategy, a task which must be completed without information of the other agent's strategy.
-The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$) which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$ lagging anchor algorithm which can converge to both pure and mixed NEs.
+The above methods are all centralised techniques, in which a controller determines the optimal joint
+policy for both agents. However, in real scenarios it is often preferable that each agent learns
+their own strategy, a task which must be completed without information of the other agent's
+strategy. The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which
+guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$)
+which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor
+algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$
+lagging anchor algorithm which can converge to both pure and mixed NEs.
 
@@
 
-Stochastic Games (or Markov Games) form a basis for MARL settings.
-However, in this case the agents must learn about the equilibrium strategies by playing the game, which means they do not have a priori knowledge of the reward or transition functions.
-Schwarz considers two properties which should be used for evaluating MARL algorithm: rationality and convergence.
-The latter simply states that the method should converge to some equilibrium whereas the former suggests that the method should learn the best response to stationary opponents.
-A similar set of conditions is considered by Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly.
-Schwarz then presents a review of MARL methods (as of September 2014)
+Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
+must learn about the equilibrium strategies by playing the game, which means they do not have a
+priori knowledge of the reward or transition functions. Schwarz considers two properties which
+should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
+that the method should converge to some equilibrium whereas the former suggests that the method
+should learn the best response to stationary opponents. A similar set of conditions is considered by
+Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
+then presents a review of MARL methods (as of September 2014)
 
@@
 
-As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other methods for solving Dec-POMDPs should provide insights into improving MARL.
-Fortunately Oliehock in \cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are
-\begin{itemize}
-    \item Alternating Maximisation: This is effectively coordinate ascent for determining a joint policy.
-    \item Approximation as Bayesian Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient.
-It does, however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games
-    \item Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal?
-In order to make this work, we would also need to consider how to select the feature space of sub-trees and how to collect this information.
-\end{itemize}
+As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
+methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
+\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
+The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
+is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
+Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
+however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
+Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
+order to make this work, we would also need to consider how to select the feature space of sub-trees
+and how to collect this information. \end{itemize}
 
@@
 
-Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent Systems (MAS).
-This model then serves to be able to predict the evolution of a learning system as well as to understand the trajectory of learning.
-Typically, this looks at considering whether or not the method is likely to converge towards a Nash equilibrium.
-This is generally a difficult problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems.
-To extend this applicability into real world settings requires the study of stable equilbrium points; \cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE) are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable equilibrium will always be returned to even after perturbations.
-This extremely important in Safe and Trusted AI as it provides guarantees against undesired behaviour in real world learning environments.
+Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
+Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
+well as to understand the trajectory of learning. Typically, this looks at considering whether or
+not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
+problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
+applicability into real world settings requires the study of stable equilbrium points;
+\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
+are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of the environment since a stable
+equilibrium will always be returned to even after perturbations. This extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour in real world learning
+environments.
 
@@
 
-Stability may be looked at from the view point of two perspectives.
-The first is from an optimisation point of view.
-This considers the dynamics of the learning model, allowing us to better choose our parameters and design our models so that they may converge to a stable result.
-The second is from the view point of the state-action space of a learnt model.
-This allows us to determine, before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour.
-This knowledge allows us to consider which state-action pairs should be avoided.
-In both cases, stability analysis allows us to build multi agent systems which will learn and act in the way that we expect them to.
+Stability may be looked at from the view point of two perspectives. The first is from an
+optimisation point of view. This considers the dynamics of the learning model, allowing us to better
+choose our parameters and design our models so that they may converge to a stable result. The second
+is from the view point of the state-action space of a learnt model. This allows us to determine,
+before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This
+knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability
+analysis allows us to build multi agent systems which will learn and act in the way that we expect
+them to.
 
-In \cite{Letcher2019DifferentiableMechanics}, Letcher et al.
-model gradient descent learning of generative-adversarial-networks (GANs) as a two-player differentiable game.
-A differentiable game is one in which the loss function is twice differentiable.
-Using this formulation, they are able to analyse the system from new perspectives by considering the current state-of-the-art understanding of differentiable game theory.
-Whilst, at first glance, this may seem like a purely theoretical exercise, they go on to show that the insights gained allow them to develop a new multi-objective optimisation technique for GANs which shows stronger convergence properties, most notably of which is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the two players' loss functions.
+In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of
+generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is
+one in which the loss function is twice differentiable. Using this formulation, they are able to
+analyse the system from new perspectives by considering the current state-of-the-art understanding
+of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical
+exercise, they go on to show that the insights gained allow them to develop a new multi-objective
+optimisation technique for GANs which shows stronger convergence properties, most notably of which
+is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the
+two players' loss functions.
 
-Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement learning agent as a non-linear, time varying feedback controller.
-Using this notion, they then consider the bounded-input-bounded-output stability of the system.
-They do this by analysing the ratio between the total output and total input energy (called the L2 gain).
-If the L2 gain remains finite then the system may be considered to be stable.
-They then apply these considerations on real-world applications including multi-agent flight formation and obtain stability certificates (essentially confirming that the system will remain stable under certain conditions) for the learned controller.
+Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement
+learning agent as a non-linear, time varying feedback controller. Using this notion, they then
+consider the bounded-input-bounded-output stability of the system. They do this by analysing the
+ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains
+finite then the system may be considered to be stable. They then apply these considerations on
+real-world applications including multi-agent flight formation and obtain stability certificates
+(essentially confirming that the system will remain stable under certain conditions) for the learned
+controller.
 
-Berkenkamp et al.
-\cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different definition of stability.
-Specifically, they look at stability from the point of view of Lyapunov functions.
-A system is said to be stable if the applying the policy will result in stricly lower evaluations of the function.
-In other words, a system is stable if its corresponding Lyapunov function is decreasing towards a minimum point.
-The authors use this idea to define a 'region of attraction' in which the system is stable in the sense of Lyapunov.
-The goal of Safe Lyapunov Learning, a method which they develop from these insights, is to learn a policy without leaving this region of attraction.
-They do this by taking measurements within the set and using this to learn about the system dynamics, thereby increasing the safe set.
-With this, we now have a guarantee that policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and exploration.
+Berkenkamp et al. \cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different
+definition of stability. Specifically, they look at stability from the point of view of Lyapunov
+functions. A system is said to be stable if the applying the policy will result in stricly lower
+evaluations of the function. In other words, a system is stable if its corresponding Lyapunov
+function is decreasing towards a minimum point. The authors use this idea to define a 'region of
+attraction' in which the system is stable in the sense of Lyapunov. The goal of Safe Lyapunov
+Learning, a method which they develop from these insights, is to learn a policy without leaving this
+region of attraction. They do this by taking measurements within the set and using this to learn
+about the system dynamics, thereby increasing the safe set. With this, we now have a guarantee that
+policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and
+exploration.
 
-As we can see from the discussion thus far, there are many definitions and perpectives of stability, each lending to a new understanding of learning systems.
-To add another to the mix, Milchtaich in \cite{Milchtaich2007StaticGames}, presents a notion of static stability.
-This means that it is based solely on the incentives of the players and does not require a consideration of the dynamics of the system.
-Milchtaich's definition of a stable system is one in which, when perturbed, it is more beneficial for an agent to move back towards the equilibrium than it is for them to move away.
-This is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows that it is applicable to all strategic games, within certain assumptions (finite set of player and continuous strategy space) and considers probabilistic perturbations from the original state.
-This is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy spaces) since these systems require random exploration of the strategy space and the dynamics are not known a priori.
-However, the lack of dynamics means that we do not consider the evolution of learning.
+As we can see from the discussion thus far, there are many definitions and perpectives of stability,
+each lending to a new understanding of learning systems. To add another to the mix, Milchtaich in
+\cite{Milchtaich2007StaticGames}, presents a notion of static stability. This means that it is based
+solely on the incentives of the players and does not require a consideration of the dynamics of the
+system. Milchtaich's definition of a stable system is one in which, when perturbed, it is more
+beneficial for an agent to move back towards the equilibrium than it is for them to move away. This
+is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows
+that it is applicable to all strategic games, within certain assumptions (finite set of player and
+continuous strategy space) and considers probabilistic perturbations from the original state. This
+is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy
+spaces) since these systems require random exploration of the strategy space and the dynamics are
+not known a priori. However, the lack of dynamics means that we do not consider the evolution of
+learning.
 
@@
 
-The above discussion has considered how notions of stability and control are important to Multi-Agent Learning.
-It stands to reason, therefore, that Multi-Agent Learning and, more specifically, game theory, can be used to develop controllers which drive systems to stable states.
-This idea is explored in \cite{Marden2018AnnualControl}.
-Here, a zero-sum game is considered in which the players are a controller and an adversarial environment.
-The design of the controller must be such that it is able to drive the system to zero error.
-To illustrate, consider the problem of designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which vortices seek to destabilise the agent.
-This will allow us to build stable agents in a much more efficient manner since we can simulate the adversarial environment and hypothetical scenarios the agent may encounter without actually encountering them.
-The same notion is explored by Bardi et al \cite{Bardi1991DifferentialDisturbances}.
+The above discussion has considered how notions of stability and control are important to
+Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
+specifically, game theory, can be used to develop controllers which drive systems to stable states.
+This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
+which the players are a controller and an adversarial environment. The design of the controller must
+be such that it is able to drive the system to zero error. To illustrate, consider the problem of
+designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
+vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
+efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
+agent may encounter without actually encountering them. The same notion is explored by Bardi et al
+\cite{Bardi1991DifferentialDisturbances}.
 
- Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision avoidance problem, similarly from the point of view of differential game theory.
-They develop a robust feedback system for the robots which they show to be able to drive the system towards predefined targets without interference from other agents.
-In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent systems
+ Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
+ avoidance problem, similarly from the point of view of differential game theory. They develop a
+ robust feedback system for the robots which they show to be able to drive the system towards
+ predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
+ In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
+ systems in a distributed manner. Here, agents only consider their own payoff structure and have
+ limited communication with one another. The author shows that the an approximate equilibrium can be
+ found using algebraic methods and illustrate the capabilities of the technique using a collision
+ avoidance example. For the sake of brevity, I will not include all of the numerous strides that
+ Mylvaganam has introduced to the area. However, I must conclude with those presented in
+ \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
+ games, including linear-quadratic differential games (in which system dynamics are linear functions
+ whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
+ induced across the players (a notion was suggested in the research proposal) and mean-field games,
+ which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
+ differential game is the stability of the solution; solutions for the Nash equilibria are
+ admissable iff they are locally exponentially stable (which the author often shows with the aid of
+ Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
+ calculate online. The author then shows that this is not simply a theoretical exercise by applying
+ the novel methods towards multi-agent collision problems and designs dynamic control laws which
+ guarantee that each agent will reach their desired state whilst avoiding collision with the other
+ agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
+ robot system.
 
@@
 
-The above discussion has illustrated a few points.
-The first, and perhaps most important, is that stability is extremely applicable to Multi Agent Reinforcement Learning.
-This is because of the fact that learning agents, especially in real world environments, are subject to uncertainty and perturbations as well as epsilon-random exploration.
-As such, it is important that the system is able to return to a stable state after such perturbations.
-This leads to the need to develop learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable equilibria.
-Similarly, it allows us to consider existing algorithms and whether they lead to stable equilibria.
-For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge to stable fixed points.
+I will briefly summarise the research directions which I develop in this section, to save ourselves
+some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}
 
-The second point is that the notion of stability has multiple definitions.
-Each one is appropriate in different conditions and, as such, it is important to explore stability from various viewpoints to consider how to best understand the evolution of a learning system.
+The above discussion has illustrated a few points. The first, and perhaps most important, is that
+stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
+that learning agents, especially in real world environments, are subject to uncertainty and
+perturbations as well as epsilon-random exploration. As such, it is important that the system is
+able to return to a stable state after such perturbations. This leads to the need to develop
+learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
+equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
+equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
+Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
+to stable fixed points.
 
-Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do not necessarily contain stable fixed points.
-The existence of stable equilibria is therefore an open question and is well worth consideration.
-This would help guide the choice of loss functions and strategy spaces.
-This is likely to be an extremely difficult problem to generalise but would have a dramatic impact on the safety certification of MARL systems.
+The second point is that the notion of stability has multiple definitions. Each one is appropriate
+in different conditions and, as such, it is important to explore stability from various viewpoints
+to consider how to best understand the evolution of a learning system.
 
-The problem of finding stable solutions through multi agent dynamics also opens the door for a large degree of application domains which are currently quite sparse.
-I would recommend looking at the contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems control and economic modelling.
-My particular interest, as always, lies within robotic control problems.
-This appears to be the most direct and relevant application of stable MAS systems; we can, for instance, use MARL to determine control rules which will lead to stable performance of the system.
-An example of this might be the problem of Cooperative Moving Path Following Control considered by \cite{Reis2019RobustVehicles}.
-Here, multiple agents must track moving targets according to a pre-defined path without interfering with one another.
-It is clear then that each player's control is dependent on the other and so can be modelled as a game theoretic problem.
-Our task, then, is to determine control rules which lead to stable coordination across the team.
-Similarly, we can model consider modelling a controller and an adversarial environment as a zero-sum game as examined in \cite{Marden2018AnnualControl}.
-Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that of Generative adversarial networks (GANs) which can be considered as a two player minimax game with differentiable loss functions.
+Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
+not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
+question and is well worth consideration. This would help guide the choice of loss functions and
+strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
+dramatic impact on the safety certification of MARL systems.
 
-The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem, Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees, Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found particularly relevant to this study.
-However, they will require some further analysis before I write about them here.
+The problem of finding stable solutions through multi agent dynamics also opens the door for a large
+degree of application domains which are currently quite sparse. I would recommend looking at the
+contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
+of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
+control and economic modelling. My particular interest, as always, lies within robotic control
+problems. This appears to be the most direct and relevant application of stable MAS systems. An
+example of this might be the problem of Cooperative Moving Path Following Control considered by
+\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
+pre-defined path without interfering with one another. It is clear then that each player's control
+is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
+determine control rules which lead to stable coordination across the team. Similarly, we can model
+consider modelling a controller and an adversarial environment as a zero-sum game as examined in
+\cite{Marden2018AnnualControl}.
+
+Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
+of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
+differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
+the differential game problem from the point of view of different information structures. In
+real-world systems, it is unlikely that all agents will have access to the information of other
+agent' cost functions and current positions. It could, however, be interesting to explore the use of
+localisation methods to determine and track this information through observation (e.g. through
+Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
+considers the case where system dynamics are linear. A whole new set of problems arise in the more
+realistic case where we must consider the non-linearity of system dynamics. Such a consideration
+would also allow us to extend these technique to the more difficult (and important) problems in
+control.
+
+The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
+Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
+Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
+particularly relevant to this study. However, they will require some further analysis before I write
+about them here.
 
 \bibliographystyle{IEEEtran}
+
 \bibliography{IEEEfull,references}

### 2019-11-28 Literature Review/Literature Review - Informal/sample.tex
Included MPC section - must read

@@
 \usepackage{subcaption}
+\usepackage{csquotes}
 \usepackage{algpseudocode}
@@
 
-\maketitle tableofcontents
+\maketitle
+
+\tableofcontents
 
@@
 
+\section{Stochastic and Robust Model Predictive Control}
+
+\textbf{Francesco: I've moved this to the top for your attention - it seems to be the most
+interesting problem with the scope to improve the theoretical results as well as applications in
+complex domains which are of significant interest these days.}
+
+The idea of Stochastic Control is best described in the research statement of the Control and
+Analysis of Stochastic Systems (CASS) group at Penn State:
+
+\begin{displayquote}
+	"...to model, predict and control uncertain engineering systems where the interplay between
+	dynamics and uncertainty (stochasticity) is important."
+\end{displayquote}
+
+When operating in the real world, systems are subject to uncertainty and environment perturbations.
+Despite this, for their safe operation, they must provide certain guarantees (such as collision
+avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
+system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
+control have found their way into controlling power distribution, chemical processes and (of course)
+robotics.
+
+Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
+of operating real-world agents safely in the face of environmental disturbances. The overarching
+idea begins with the assumpion that we have a model of the environment. As an example, in
+the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
+affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
+environment state for a few time steps ahead, and generate a policy for this horizon. The agent
+performs the immediate action generated by the policy, and then we repeat the process, after taking
+measurements of the environment to determine the error in the system. Throughout this process, the
+controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
+example, a likely constraint would be that the controller will never result in the car going on the
+pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
+the requirement of stability that the system is required to remain safe throughout operation. To
+that end, mathematical proofs of these properties are provided in the literature ensuring that we
+can trust in the system's performance.
+
+Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
+knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
+computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
+provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
+of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
+we no longer assume the exact nature of the environment and can guard against worst case scenarios.
+This is extremely effective in closed environments or for simple tasks, but falters in more complex
+environments.
+
+Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
+perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
+define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
+optimality is defined in terms of the minimisation of the expectation of a probabilistic
+cost function. This formulation brings about controllers which are more applicable and robust when
+deployed. However, the field is in its infancy and presents a number of theoretical challenges.
+These are best described by Mesbah in \cite{Mesbah2016}
+
+\begin{itemize}
+	\item The arbitrary form of the feedback control laws
+	\item The non-convexity and intractability of the chance constraints
+	\item The complexity of the uncertainty propagations
+	\item Establishing stability of the control problem
+\end{itemize}
+
+Since the review was written in 2016, there have been a number of approaches towards solving some of
+these problems, most notably the intractability of the chance contraints. For instance, in 
+\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
+time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
+suited to non-linear systems, which itself is an open problem in the MPC sphere.
+
+\subsection{Directions}
+
+The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
+and applied problems. Control in autonomous systems is also one of the more applicable problems
+related to STAI since it requires that we place mathematical guarantees on the performance and
+stability of the system as well as guarantees on the satisfaction of constraints. This is, of
+course, an ever present problem in autonomous systems which operate in the real world. I begin by
+listing the more theoretical areas for exploration in MPC before then considering their application
+domains.
+
+\begin{itemize}
+	\item Significant exploration is required with regards to the optimisation problem. Especially
+	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
+	approximate methods (such as sampling) should be explored and their effect on the system
+	guarantees presented.
+	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
+	determine the uncertainty in the environment model in order to generate control laws. We should
+	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
+	particle filters, against modern deep learning methods for propagation.
+	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
+	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
+	together whilst maintaining a specified distance from one another). Consider, then, the case
+	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
+	and hence requires adaptation. It would again be interesting to consider the use of neural
+	networks in this manner. However, specifically we should consider whether the use of a function
+	approximator in the form of an NN might result in a violation of the constraints.
+	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
+	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
+	effect that each agent has on the other, the effect of the environment on all agents, estimating the
+	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
+	here that I believe game-theoretic notions (especially differential games) will come to our
+	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
+	in the case of multiple disturbances, but I will elaborate on this in the applied problems
+	section.
+\end{itemize}
+
+\section*{Multi Agent Dynamics}
+
 Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
@@
 equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world learning
+and Trusted AI as it provides guarantees against undesired behaviour in real world
 environments.

### 2019-11-28 Literature Review/Literature Review - Informal/sample.tex
Updated MPC research section

@@
 interesting problem with the scope to improve the theoretical results as well as applications in
-complex domains which are of significant interest these days.}
+complex domains which are of significant interest these days. I will be adding in the
+state-of-the-art review as we go along, but for now the general overview and research directions
+are provided.}
 
@@
 robotics.
+
+\subsection*{Model Predictive Control}
 
@@
 
-Since the review was written in 2016, there have been a number of approaches towards solving some of
+Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
+some of
 these problems, most notably the intractability of the chance contraints. For instance, in 
@@
 	section.
+\end{itemize}
+
+the following presents a consideration of the applied end of MPC problems. I have tried to focus on
+the domain independent suggestions, since the domain specific ones are virtually limitless.
+
+\begin{itemize}
+	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
+	interact with each other. In addition, we may consider that there are multiple known disturbances
+	acting on the system. This, at first seems like an impossible problem to solve due to the many
+	interactions between all elements of the system. However, we can consider this as a game
+	theoretic problem in which the components and the disturbances are players. The relatively new
+	class of 'mean-field games' is a method which allows the many body problem to be approximated as
+	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
+	predictive control' remain, this may prove to be a valuable area of applied research.
+	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
+	which emerge into more complex results. It would be interesting to consider the application of
+	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
+	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
+	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
+	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
+	adaptive stochastic model would be interesting to examine here to remain robust to agent
+	failures in the group.
 \end{itemize}

### 2019-12-19 Literature Review/Literature Review - Informal/sample.tex
Nothing important changed

@@
 
-\begin{itemize} \item Verification of goal achievement under different payoffs: can we ensure that
+\begin{itemize} 
+	\item Verification of goal achievement under different payoffs: can we ensure that
 	self-interested agents will, in fact, show cooperative emergent properties? A similar question
-arises in terms of valuations (how much cost each agent incurs). \item A priori consideration of
+	arises in terms of valuations (how much cost each agent incurs). 
+	\item A priori consideration of
 	reliability: Can we learn and take into account the fact that robots may fail throughout the
-progress of a mission when we assign tasks? \end{itemize}
+	progress of a mission when we assign tasks? 
+\end{itemize}
 
@@
 
-\textbf{Francesco: I've moved this to the top for your attention - it seems to be the most
-interesting problem with the scope to improve the theoretical results as well as applications in
-complex domains which are of significant interest these days. I will be adding in the
-state-of-the-art review as we go along, but for now the general overview and research directions
-are provided.}
-
 The idea of Stochastic Control is best described in the research statement of the Control and
@@
 
+The research in using Distributed Predictive Control is quite sparse as compared with, for example,
+single agent predictive control. The added complexity of stochastic environments has meant that this
+area of research is still very open for looking into. With this said, the main works that I have
+found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
+\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
+Usually these are some combination of the following:
+
+\begin{itemize}
+	\item The agents act in a deterministic environment. This suggests that predicted futures will
+	be close enough to the ground truth.
+	\item The agents are uncoupled from one another. This is a strong assumption to make and
+	essentially allows us to consider the agents as completely independent of one another. 
+	\item The agents can easily communicate with one another. This allows for longer pieces of
+	communication (most often predicted trajectories) to be communicated between agents.
+\end{itemize}
+
 \subsection{Directions}
@@
 	failures in the group.
+	\item Modular Robotics?
 \end{itemize}
@@
 particularly relevant to this study. However, they will require some further analysis before I write
-about them here.
+about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
+entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
+document out.)
+
+\chapter{Research Directions}
+
+\section{Stochastic Model Predictive Control for Distributed Systems}
+
+The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
+that end, I propose the following techniques towards improving DSMPC.
+
+\begin{itemize}
+	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
+	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
+	distribution of the action that will likely be selected by $j$, effectively performing a
+	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
+	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
+	this may seem computationally expensive, its advantage lies in the fact that it requires little
+	communication across the agents. An immediate disadvantage of this is that, as the number of
+	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
+	not yet confident on the feasibility or the usefulness of this technique, but looking further
+	into the literature (which seems to add new things every day) may provide insights which could
+	help refine the technique. This method is, in many ways, similar to that presented in 
+	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
+	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
+	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
+	all systems to update at each time step.
+
+	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
+	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
+	public belief based on the observed actions of all agents. This joint belief will likely provide
+	some representation of the trajectories that each agent will carry out or an understanding of
+	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
+	will be chosen from a family of existing models using a recursive Bayesian update. The idea
+	would be for this update to be conditioned on the history of observations as is done in 
+	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
+	state and use this, in combination with their own system models to determine a feasible
+	trajectory. The challenge here would be proving the stability and controllability of the system
+	and that it requires communication with a central controller. However, it would appear to be a
+	feasible area of exploration.
+\end{itemize}
+
+\section{Stochastic Control of Swarms}
+
+Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
+when considering its application in stochastic environments. In particular, the ideas presented
+below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
+desired distribution.
+
+\begin{itemize}
+	\item Consideration of state constraints or boundary conditions (terms which I will use
+interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
+particular stochastic difference equation (the Ito equation). However, this does not account for any
+boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
+obstacle avoidance. However, in environments where there are human operators, or in general areas
+where we do not want swarms to enter, it is important to have a guarantee of constraint
+satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
+conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
+confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
+Furthermore, it may present an opportunity for us to consider the decentralised control of the
+agents which can ensure state constraint satisfaction. The resources which are most relevant to this
+study (and from which the ideas are derived) are
+\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
+
+\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
+the diffusion models, as mentioned above, do not take into consideration the interactions between
+agents, since it adds a large degree of complexity to the model. However, it would be important from
+a safety perspective to take these into account by looking at the attractive and repulsive
+potentials across agents. This would allow us to provide a guarantee of inter-agent collision
+avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
+mention that they are already looking into this problem and have proposed a similar manner of
+tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
+they publish?
+
+\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
+By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
+number of their nearest neighbours. However, this may not always be the case. It will often be that
+in different environmental conditions, the observation or communication capabilities of the robots
+may increase or decrease. To better accomodate for this fact, I propose the extension of the model
+with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
+'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
+success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
+way into swarm dynamics. It will, however, become particularly important in cases where we can no
+longer take the consistency of agent communication for granted. 
+\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
+not seem like the connection of MJD and swarm dynamics has been made yet.
+\end{itemize}
+
+\section{Multi Agent Reinforcement Learning}
+
+The ideas I have down here are a little more sparsely populated, but further reading may provide
+some insights into potential directions.
+
+\begin{itemize}
+	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
+	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
+	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
+	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
+	required that we determine a safe manner in which MARL agents may explore without leading to
+	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
+	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
+	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
+	independent learners who do not consider the effect that they have on the other agent(s). The
+	particular extension that I propose is to consider the coupled effect between agents as part of
+	the determination of a safe set for exploration.
+
+	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
+	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
+	problems. Although it makes strong assumptions about the nature of the system, in practice it
+	has shown strong results. Particular examples of this are found in 
+	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
+	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
+	systems by considering sub-groups within the population. Each of these may be updated
+	individually. It would be interesting to examine how this might increase the complexity, and
+	also the generalisability of the mean-field method.
+	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
+	part but the potential directions are largely summarised in Section 2.3.1.
+\end{itemize}
 

### 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
added comments

@@
 
+\newcommand\fr[1]{\textcolor{red}{FR: #1}}
+
 \author{Aamal Hussain}
@@
 
-The areas of interest regarding Multi Agent Systems fall into two distinct categories (which have
-some slight overlap). The first is denoted as 'Decision Making', though the terms 'Planning' and
-'Distributed Control' may sometimes be used as substitutes. It is important to note that, in my
-case, I do not include Planning Formalisation techniques such as PDDL. Instead, I focus on the
-particular methods which involve interaction in the world. The second, I will refer to as 'Multi
-Agent Dynamics', though sometimes I will refer to this as 'Stability Analysis'.
+The areas of interest regarding Multi Agent Systems fall into two
+distinct categories (which have some slight overlap). The first is
+denoted as 'Decision Making', though the terms 'Planning' and
+'Distributed Control' may sometimes be used as substitutes. It is
+important to note that, in my case, I do not include Planning
+Formalisation techniques such as PDDL. Instead, I focus on the
+particular methods which involve interaction in the world. The second,
+I will refer to as 'Multi Agent Dynamics', though sometimes I will
+refer to this as 'Stability Analysis'.
 
@@
 
-Both of the aforementioned topics have been applied to all variants of multi agent systems and have
-sufficient room for further exploration. The typical variants of multi agent systems that I will
+Both of the aforementioned topics have been applied to all variants of
+multi agent systems and have sufficient room for further
+exploration. The typical variants of multi agent systems that I will
 consider are
@@
 
-In the above, 'Game Theoretic Approaches' cover a wide spectrum, including zero-sum (minimax) games,
-bayesian games, and many more. The final category, 'Hard Coded', refers to any approach which does
-not fit neatly into any of these categories. The name is chosen since they often refer to methods
-which revolve around a series of if-else statements.
+In the above, 'Game Theoretic Approaches' cover a wide spectrum,
+including zero-sum (minimax) games, bayesian games, and many more. The
+final category, 'Hard Coded', refers to any approach which does not
+fit neatly into any of these categories. The name is chosen since they
+often refer to methods which revolve around a series of if-else
+statements.
 
-I will first consider Decision Making as this is most closely related to the research proposal,
-before I consider Multi Agent Dynamics, which has strong implications for Safe and Trusted Multi
-Agent Systems.
+\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}
+
+I will first consider Decision Making as this is most closely related
+to the research proposal, before I consider Multi Agent Dynamics,
+which has strong implications for Safe and Trusted Multi Agent
+Systems.
 
@@
 
+\fr{What are the standard techniques used in swarms?
+that is, how are swarms and their interactions modelled?
+how are solutions computed?
+what kind of algorithms are used in this area?
+most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
+
 \subsection{Co-evolution and Self-Healing}
 
-Recently, there has been an increased interest in introducing heterogeneity into the swarm systems
-to improve their real world applicability. An example of this which have been shown strong real
-world success can be found in \cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
-swarm teams, referred to as 'foot bots' and 'eye bots' who work in unison to explore an environment
-and solve a navigation task.
+Recently, there has been an increased interest in introducing
+heterogeneity into the swarm systems to improve their real world
+applicability. An example of this which have been shown strong real
+world success can be found in
+\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
+swarm teams, referred to as 'foot bots' and 'eye bots' who work in
+unison to explore an environment and solve a navigation task.
 
-This area of research is sparsely populated and warrants further exploration. This is since the use
-of co-evolutionary teams can improve the robustness of the swarm optimisation. This is since it will
-be possible for a team to automatically determine when robots in the other team are not exhibiting
-expected behaviour and ensure that the other team self corrects. This process is referred to as
-'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a user to define the goals of a
-swarm system. From this, a 'trust' metric can be defined which measures the deviation of each agent
-from the expected behaviour. The self-healing process occurs by limiting communication of all agents
-with 'untrusted' agents and encouraging communication with 'trusted' agents. The unison of
-self-healing with co-evolution may present the opportunity for heterogenous swarms to maintain their
-evolutionary stability, even in the face of environmental disturbances.
+This area of research is sparsely populated and warrants further
+exploration. This is since the use of co-evolutionary teams can
+improve the robustness of the swarm optimisation. This is since it
+will be possible for a team to automatically determine when robots in
+the other team are not exhibiting expected behaviour and ensure that
+the other team self corrects. This process is referred to as
+'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
+user to define the goals of a swarm system. From this, a 'trust'
+metric can be defined which measures the deviation of each agent from
+the expected behaviour. The self-healing process occurs by limiting
+communication of all agents with 'untrusted' agents and encouraging
+communication with 'trusted' agents. The unison of self-healing with
+co-evolution may present the opportunity for heterogenous swarms to
+maintain their evolutionary stability, even in the face of
+environmental disturbances.
 
@@
 
-The above sections have considered the fact that swarm systems are robust to losses in the group.
-However, any MAS system must first be able to recognise that an agent has undergone some failure.
+The above sections have considered the fact that swarm systems are
+robust to losses in the group.  However, any MAS system must first be
+able to recognise that an agent has undergone some failure.
 
-To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop a robust fault detection
-approach in which the swarm itself, in a decentralised manner, is capable of assessing deviation
-from 'normal' behaviour, even when the behaviour of the swarm itself is altered (perhaps by a remote
-operator). The authors achieve this by requiring that the agents themselves sense and characterise
-their own behaviour. This characterisation is formulated as a binary feature vector which is then
-communicated to the agent's neighbours. These neighbours will reach a consensus over whether the
-agent should be treated as faulty based on their collective behaviour. The results presented in
-\cite{Tarapore2019FaultDetection} show extremely promising results and suggest that their method is,
-in fact, able to determine faults with high accuracy in the presence of various fault types
-(including sensor and actuator failures), although poor performance is seen in actuation failures in
-some instances. It should be noted that this method requires that each robot transmit their feature
-vector to the nearest neighbours. In environments where communication may be severely limited, this
-may present further errors. Furthermore, it is unlikely that, when a robot is damaged, only one of
-its components will be affected. Therefore, it is important to determine the effect on performance
-in the face of multiple agent failures and in communication losses. This exploration may open the
-possibility of improving the state of the art in terms of failure detection in swarm systems. (Of
-course, this conclusion is based off two papers so further review is required).
+To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
+a robust fault detection approach in which the swarm itself, in a
+decentralised manner, is capable of assessing deviation from 'normal'
+behaviour, even when the behaviour of the swarm itself is altered
+(perhaps by a remote operator). The authors achieve this by requiring
+that the agents themselves sense and characterise their own
+behaviour. This characterisation is formulated as a binary feature
+vector which is then communicated to the agent's neighbours. These
+neighbours will reach a consensus over whether the agent should be
+treated as faulty based on their collective behaviour. The results
+presented in \cite{Tarapore2019FaultDetection} show extremely
+promising results and suggest that their method is, in fact, able to
+determine faults with high accuracy in the presence of various fault
+types (including sensor and actuator failures), although poor
+performance is seen in actuation failures in some instances. It should
+be noted that this method requires that each robot transmit their
+feature vector to the nearest neighbours. In environments where
+communication may be severely limited, this may present further
+errors. Furthermore, it is unlikely that, when a robot is damaged,
+only one of its components will be affected. Therefore, it is
+important to determine the effect on performance in the face of
+multiple agent failures and in communication losses. This exploration
+may open the possibility of improving the state of the art in terms of
+failure detection in swarm systems. (Of course, this conclusion is
+based off two papers so further review is required).
+
+\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas.
+As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another.
+However, this depends essentially on the different modelling assumptions.}
 
@@
 
-From the above consideration of swarms, the following research directions have been identified
-which, in my view, concern themselves with STAI.
+From the above consideration of swarms, the following research
+directions have been identified which, in my view, concern themselves
+with STAI.
 
 \begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
-towards ensuring that emergent phenomenon and swarm behaviour are as expected by the user. \item
-Fault Detection in limited communication: Considering the ability of a swarm to, in a decentralised
-approach, consider which robots in the team have failed, even in cases of no communication or
-multiple failures. \end{itemize}
+towards ensuring that emergent phenomenon and swarm behaviour are as
+expected by the user.
+
+\item Fault Detection in limited communication:
+Considering the ability of a swarm to, in a decentralised approach,
+consider which robots in the team have failed, even in cases of no
+communication or multiple failures.
+
+\fr{The second item looks promising, possibly in combinations with
+  techniques from Game Theory and MARL. Let's keep Fault R\&D in
+  mind.}
+
+\end{itemize}
 
@@
 
-The use of POMDPs in multi-agent settings is formalised as decentralised POMDP (Dec-POMDP) which
-aims for a team of agents to maximise a common utility. However, it has been found that determining
-the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and so is intractable for all but
-toy problems. A number of methods have been presented to attempt to solve Dec-POMDPs. Oliehoek gives
-a review of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such as brute force) are
-intractable for all but toy problems.
+The use of POMDPs in multi-agent settings is formalised as
+decentralised POMDP (Dec-POMDP) which aims for a team of agents to
+maximise a common utility. However, it has been found that determining
+the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
+so is intractable for all but toy problems. A number of methods have
+been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
+of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
+as brute force) are intractable for all but toy problems.
 
-Approximate solutions to Dec-POMDP have been proposed, perhaps most notable of which is the proposal
-of MacDec-POMDP \cite{Amato2015} by Amato et al. Here, macro actions (actions which extend over
-multiple time steps) are used, as opposed to low-level actions which are re-evaluated at each time
-step. This allows an exact solution to be found as it does not need to be evaluated at each time
-step. This method assumes that, once macro-actions are distributed, the policies (sequence of
-state-action pairs) are known. Since this is not the case, Amato also proposes the use of a
-Dec-POSMDP \cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to 'Semi-Markov Decision
-Process, in which a high level model is defined without the underlying Dec-POMDP's actions and
-observations.
+Approximate solutions to Dec-POMDP have been proposed, perhaps most
+notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
+Amato et al. Here, macro actions (actions which extend over multiple
+time steps) are used, as opposed to low-level actions which are
+re-evaluated at each time step. This allows an exact solution to be
+found as it does not need to be evaluated at each time step. This
+method assumes that, once macro-actions are distributed, the policies
+(sequence of state-action pairs) are known. Since this is not the
+case, Amato also proposes the use of a Dec-POSMDP
+\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
+'Semi-Markov Decision Process, in which a high level model is defined
+without the underlying Dec-POMDP's actions and observations.
 
-However, this is largely applicable in passive settings where common payoffs can be determined by an
-offline planner. They also require a significant amount of data with which to allow the system to
-learn the underlying models and payoff structures. This limits the applicability of the system when
-communication is limited and the system is presented with environments that it has not seen before.
-Recent work in MDPs \cite{Klima2019RobustDomains} has considered learning in the face of Significant
-Rare Events (SREs) which the system has not yet observed. Currently, it is required that a model of
-such SREs is known and so it would be interesting to consider the application of Dec-POMDPs in
-situations where the SRE model is incomplete or erroneous and assess the robustness of the Dec-POMDP
-framework against such events.
+However, this is largely applicable in passive settings where common
+payoffs can be determined by an offline planner. They also require a
+significant amount of data with which to allow the system to learn the
+underlying models and payoff structures. This limits the applicability
+of the system when communication is limited and the system is
+presented with environments that it has not seen before.  Recent work
+in MDPs \cite{Klima2019RobustDomains} has considered learning in the
+face of Significant Rare Events (SREs) which the system has not yet
+observed. Currently, it is required that a model of such SREs is known
+and so it would be interesting to consider the application of
+Dec-POMDPs in situations where the SRE model is incomplete or
+erroneous and assess the robustness of the Dec-POMDP framework against
+such events.
 
@@
 \begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
-SREs which have a limited or erroneous model. \item Agent Failures: The Dec-POMDP model uses a
+  SREs which have a limited or erroneous model.
+
+\item Agent Failures: The Dec-POMDP model uses a
 centralised planner which acts offline. It therefore assumes that the agents will be able to carry
@@
 planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
+
+\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
+Also, it might be interesting to understand why swarms scale up better
+than MDPs, and in general why the former have better computational
+properties than the latter: is it a matter of
+``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
+some other swarm-like restriction? It might be interesting to combine
+the two approaches in order to get the ``best of both worlds''.}
 

### 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
added comments

@@
 
-Game theoretic models are generally the go-to method for understanding multi-agent systems. As such
-they fit into all of the categories in this chapter (except, perhaps, swarms) since Dec-POMDP and
-MARL methods have both used game theory to support their frameworks. In fact, Dec-POMDP is a subset
-of Partially Observed Stochastic Games (POSG), in which all agents use the same payoff. Game theory
-can, therefore, be used in an applied capacity to direct task allocation across heterogenous teams.
+Game theoretic models are generally the go-to method for understanding
+multi-agent systems. As such they fit into all of the categories in
+this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
+methods have both used game theory to support their frameworks. In
+fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
+(POSG), in which all agents use the same payoff. \fr{That's an
+  interesting remark. It might be worth to check whether we can
+  leverage on this and similar observations.} Game theory can,
+therefore, be used in an applied capacity to direct task allocation
+across heterogenous teams.
 
@@
 
-Garapati et al. \cite{Garapati2018AMissions} define a market based method as the setting where
-agents "follow their own interests and establish the mechanism of a market for distributing the
-tasks". Auctioning is the most widely used sub-field of market approaches and so I will use them
-interchangeably.
+Garapati et al. \cite{Garapati2018AMissions} define a market based
+method as the setting where agents "follow their own interests and
+establish the mechanism of a market for distributing the
+tasks". Auctioning is the most widely used sub-field of market
+approaches and so I will use them interchangeably.
 
-Whilst there are different variants to autioning, the general procedure is that an auctioneer who
-has knowledge of a task (or multiple tasks) will set up an auction for said task. Agents can then
-make bids on these tasks and, once the auction is complete, the highest bid will win the task. In
-the specific application to robotics, a robot's bid will often reflect the costs, suitability or
-utility their undertaking the task \cite{BernardineDias2006Market-basedAnalysis}. This immediately
-highlights a few points. The first is that the method is not too heavily reliant upon a single
-processor to determine some joint policy. Tasks are allocated on a case-by-case basis and the
-utilities are calculated by the agent themselves. The only centralised process is the auctioneer's
-assessment of the winner which then relays this information back to them. The downside of this is
-that the system is heavily reliant upon strong communication channels, without which tasks may not
-be assigned, incorrect utilities may be communicated and, in general, sub-optimal solutions reached.
-Furthermore, the requirement that the agents themselves determine the cost of their actions assumes
-that they have the computational capability to do so. Furthermore, the bids placed by each agent
-need to be a strong representation of their capability to perform a task which may be hard to
-estimate without expert knowledge. However, market based methods are well suited to explanation
-through argumentation (similar to \cite{Jung2001DistributedArgumentation}.
+Whilst there are different variants to autioning, the general
+procedure is that an auctioneer who has knowledge of a task (or
+multiple tasks) will set up an auction for said task. Agents can then
+make bids on these tasks and, once the auction is complete, the
+highest bid will win the task. In the specific application to
+robotics, a robot's bid will often reflect the costs, suitability or
+utility their undertaking the task
+\cite{BernardineDias2006Market-basedAnalysis}. This immediately
+highlights a few points. The first is that the method is not too
+heavily reliant upon a single processor to determine some joint
+policy. Tasks are allocated on a case-by-case basis and the utilities
+are calculated by the agent themselves. The only centralised process
+is the auctioneer's assessment of the winner which then relays this
+information back to them. The downside of this is that the system is
+heavily reliant upon strong communication channels, without which
+tasks may not be assigned, incorrect utilities may be communicated
+and, in general, sub-optimal solutions reached.  Furthermore, the
+requirement that the agents themselves determine the cost of their
+actions assumes that they have the computational capability to do
+so. Furthermore, the bids placed by each agent need to be a strong
+representation of their capability to perform a task which may be hard
+to estimate without expert knowledge. However, market based methods
+are well suited to explanation through argumentation (similar to
+\cite{Jung2001DistributedArgumentation}.
 
-With well chosen payoffs, market based approaches work extremely well. For instance, in
-\cite{Dias2000ASystem}, the authors show that a free market approach (where agents try to maximise
-their own profits) can lead to a strong collaborative effort across teams. Similarly, in
-\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the auctioning scheme presented in
-\cite{Gerkey2002Sold:Coordination} towards a robot construction team. However, it is important to
-note that these are both passive settings; tasks were assigned before the team were in the field
-and, in the case of \cite{Gerkey2002Sold:Coordination}, the system would repeat the bidding process
-if a robot failed. While both show strong performance, it cannot be said that either would be
-applicable in dangerous environments in which dynamic reassignment must happen within strict time
-constraints. Stancliff et al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
-method to planning would be to account for failures a priori, a philosophy which is exemplified in
-\cite{Chen2010ACollaboration} who consider the robot's reliability and relevance to a task as well
-as 'history relevance' which considers the relationship between pairs of robots with the aim of
-producing more effective teams.
+\fr{The game-theoretic approaches described above might suffer from the
+  same drawbacks identified above for fault detection, namely reliance
+  on communication and on a single central authority. I'd rather
+  favour distributed approaches. Also, market-based mechanisms and
+  negotiation might lead us to a completely different direction.}
 
-There has also been some interesting work in probabilistic verification of market based approaches.
-Most notable to me is \cite{Pallottino2007ProbabilisticAvoidance} which considers the case of
-conflict avoidance. Though their method focuses on collision avoidance, it highlights the need for
-verification of conflict resolution and goal achievement in market based approaches with different
-payoff structures. Sirigineedi et al. \cite{Sirigineedi2010DecentralisedApproach} make a step in
-this direction by considering the verification of cooperative surveillance along a route network.
-From my understanding, this means that they were able to verify that their agents were able to
-traverse along the network without interference. However, this, as always, requires further analysis
-to truly understand.
+With well chosen payoffs, market based approaches work extremely
+well. For instance, in \cite{Dias2000ASystem}, the authors show that a
+free market approach (where agents try to maximise their own profits)
+can lead to a strong collaborative effort across teams. Similarly, in
+\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
+auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
+towards a robot construction team. However, it is important to note
+that these are both passive settings; tasks were assigned before the
+team were in the field and, in the case of
+\cite{Gerkey2002Sold:Coordination}, the system would repeat the
+bidding process if a robot failed. While both show strong performance,
+it cannot be said that either would be applicable in dangerous
+environments in which dynamic reassignment must happen within strict
+time constraints. Stancliff et
+al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
+method to planning would be to account for failures a priori, a
+philosophy which is exemplified in \cite{Chen2010ACollaboration} who
+consider the robot's reliability and relevance to a task as well as
+'history relevance' which considers the relationship between pairs of
+robots with the aim of producing more effective teams.
+
+There has also been some interesting work in probabilistic
+verification of market based approaches.  Most notable to me is
+\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
+of conflict avoidance. Though their method focuses on collision
+avoidance, it highlights the need for verification of conflict
+resolution and goal achievement in market based approaches with
+different payoff structures. Sirigineedi et
+al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
+direction by considering the verification of cooperative surveillance
+along a route network.  From my understanding, this means that they
+were able to verify that their agents were able to traverse along the
+network without interference. However, this, as always, requires
+further analysis to truly understand.
 
@@
 
-Reinforcement learning extends the Markov Decision Process problem by considering the case where the
-payoff model is not known. This, of course, is the case for most real world environments. As such,
-MARL algorithms can perhaps be considered to be more applicable than Dec-POMDP models. Fortunately,
-MARL has picked up a lot of traction in research recently, with a large body dedicated towards
-solving the many problems it presents.
+Reinforcement learning extends the Markov Decision Process problem by
+considering the case where the payoff model is not known. This, of
+course, is the case for most real world environments. As such, MARL
+algorithms can perhaps be considered to be more applicable than
+Dec-POMDP models.
+\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}
+
+Fortunately, MARL has picked up a lot of traction in
+research recently, with a large body dedicated towards solving the
+many problems it presents.
 
@@
 
+\fr{This looks like an interesting, non-trivial problem: how can we
+  represent the other agents within the agent model itself, in order
+  to improve learning in MARL? Shall we have a closer look at this problem?}
+
 \section{MARL Approaches} \label{sec::MARL Approaches}
@@
 
-Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
-must learn about the equilibrium strategies by playing the game, which means they do not have a
-priori knowledge of the reward or transition functions. Schwarz considers two properties which
-should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
-that the method should converge to some equilibrium whereas the former suggests that the method
-should learn the best response to stationary opponents. A similar set of conditions is considered by
-Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
-then presents a review of MARL methods (as of September 2014)
+Stochastic Games (or Markov Games) form a basis for MARL
+settings. However, in this case the agents must learn about the
+equilibrium strategies by playing the game, which means they do not
+have a priori knowledge of the reward or transition functions. Schwarz
+considers two properties which should be used for evaluating MARL
+algorithm: rationality and convergence. The latter simply states that
+the method should converge to some equilibrium whereas the former
+suggests that the method should learn the best response to stationary
+opponents. A similar set of conditions is considered by Conitzer and
+Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
+shortly. Schwarz then presents a review of MARL methods (as of
+September 2014)
+
+\fr{All the above looks extremely interesting. I would explore the
+  above for decentralized and partially observable settings. What
+  results are mentioned \cite{SchwartzMulti-agentApproach} under such
+  assumptions?}
 

### 2019-12-23 Literature Review/Literature Review - Informal/sample.tex
added comments

@@
 
-\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
+\begin{enumerate} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
 Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
-Coded \end{itemize}
+Coded \end{enumerate}
 
@@
 what kind of algorithms are used in this area?
-most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
+most importantly, does any of these overlap with any of the areas below, for example (PO)MDPs?}
 
@@
 
-\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
+\begin{enumerate} \item Healing through co-evolution: The application of heterogenous robot swarms
 towards ensuring that emergent phenomenon and swarm behaviour are as
@@
 
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
+\begin{enumerate} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
   SREs which have a limited or erroneous model.
@@
 out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
-planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
+planning, or planning with contingencies in the Dec-POMDP framework. \end{enumerate}
 
@@
 
-\begin{itemize} 
+\begin{enumerate} 
 	\item Verification of goal achievement under different payoffs: can we ensure that
@@
 	progress of a mission when we assign tasks? 
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
+\begin{enumerate} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
 the stability of the learning process. However, the particular problem I suggest is to consider the
 modelling in a decentralised manner and with the consideration of evolving numbers of agents in
-teams. \end{itemize}
+teams. \end{enumerate}
 
@@
 \cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
+The methods which I feel may be applicable are  \begin{enumerate} \item Alternating Maximisation: This
 is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
@@
 order to make this work, we would also need to consider how to select the feature space of sub-trees
-and how to collect this information. \end{itemize}
+and how to collect this information. \end{enumerate}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item The arbitrary form of the feedback control laws
@@
 	\item Establishing stability of the control problem
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item The agents act in a deterministic environment. This suggests that predicted futures will
@@
 	communication (most often predicted trajectories) to be communicated between agents.
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item Significant exploration is required with regards to the optimisation problem. Especially
@@
 	section.
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
@@
 	\item Modular Robotics?
-\end{itemize}
+\end{enumerate}
+
+\fr{All the above looks interesting. However, we need to understand
+  how much the scalability issue is going to affect the strength of
+  the results we can expect. Is a multi-agent extension of MPC
+  completely hopeless? or can we find ``islands of tractability'',
+  perhaps in combination with some of the other methods that you
+  mention?}
 
@@
 
+\fr{The above sounds a bit technical, but the interest for MARL is apparent.
+It might be worth to understand what are the limits of applicability of these resutls, that is, what assumptions are they based on.}
+
 \section{Learning Stable Agents}
@@
 
+\fr{I agree that we first need to understand what is exactly meant by
+  stabililty across all these different works, and possibly use a
+  notion that is relevant and interesting, especially in a multi-agent
+  contex as you point you hereafter.}
+
 Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
@@
 
-\begin{itemize}
-	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
-	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
-	distribution of the action that will likely be selected by $j$, effectively performing a
-	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
-	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
-	this may seem computationally expensive, its advantage lies in the fact that it requires little
-	communication across the agents. An immediate disadvantage of this is that, as the number of
-	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
-	not yet confident on the feasibility or the usefulness of this technique, but looking further
-	into the literature (which seems to add new things every day) may provide insights which could
-	help refine the technique. This method is, in many ways, similar to that presented in 
-	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
-	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
-	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
-	all systems to update at each time step.
+\begin{enumerate}
+	\item Each agent $i$ takes into consideration their
+          observations of the past N measurements of the actions
+          selected by another agent $j$. Using this, a Gaussian
+          Process (GP) regression informs the distribution of the
+          action that will likely be selected by $j$, effectively
+          performing a one-step lookahead of $j$'s actions. By
+          propagating the effects of this predicted input $i$ can then
+          determine a likely trajectory for $j$ and then perform its
+          own update accordingly. Whilst this may seem computationally
+          expensive, its advantage lies in the fact that it requires
+          little communication across the agents. An immediate
+          disadvantage of this is that, as the number of agents
+          increases, $i$ would need to perform all of these
+          calculations for each $j \neq i$. I'm not yet confident on
+          the feasibility or the usefulness of this technique, but
+          looking further into the literature (which seems to add new
+          things every day) may provide insights which could help
+          refine the technique. This method is, in many ways, similar
+          to that presented in \cite{Conte2014} and
+          \cite{Dai2017}. The advantage of this proposal over that in
+          \cite{Conte2014} is that it does not assume that the
+          uncertainties from the predictions of other agents are
+          bounded. Likewise, the advantage over \cite{Dai2017} is that
+          our proposal allows for all systems to update at each time
+          step.
+
+          \fr{It sounds interesting, might warrant further
+            investigation.}
 
@@
 	feasible area of exploration.
-\end{itemize}
+\end{enumerate}
 
@@
 when considering its application in stochastic environments. In particular, the ideas presented
-below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
+below concern the transport problem of swarms, i.e., moving a swarm from an initial distribution to a
 desired distribution.
 
-\begin{itemize}
-	\item Consideration of state constraints or boundary conditions (terms which I will use
-interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
-particular stochastic difference equation (the Ito equation). However, this does not account for any
-boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
-obstacle avoidance. However, in environments where there are human operators, or in general areas
-where we do not want swarms to enter, it is important to have a guarantee of constraint
-satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
-conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
-confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
-Furthermore, it may present an opportunity for us to consider the decentralised control of the
-agents which can ensure state constraint satisfaction. The resources which are most relevant to this
-study (and from which the ideas are derived) are
+\begin{enumerate}
+	\item Consideration of state constraints or boundary
+          conditions (terms which I will use interchangeably) in the
+          diffusion process. In general, stochastic swarm systems are
+          modelled using a particular stochastic difference equation
+          (the Ito equation). However, this does not account for any
+          boundary conditions on the diffusion. Indeed most swarms use
+          simple 'stop-and-turn' notions of obstacle
+          avoidance. However, in environments where there are human
+          operators, or in general areas where we do not want swarms
+          to enter, it is important to have a guarantee of constraint
+          satisfaction. To accomplish this, I propose extending the
+          Ito equation to incorporate boundary conditions. This will,
+          firstly, provide a more suitable model for the evolution of
+          a swarm system in confined spaces, allowing for a more
+          intuitive understanding of the future behaviour of the
+          swarm.  Furthermore, it may present an opportunity for us to
+          consider the decentralised control of the agents which can
+          ensure state constraint satisfaction. The resources which
+          are most relevant to this study (and from which the ideas
+          are derived) are
           \cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
 
-\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
-the diffusion models, as mentioned above, do not take into consideration the interactions between
-agents, since it adds a large degree of complexity to the model. However, it would be important from
-a safety perspective to take these into account by looking at the attractive and repulsive
-potentials across agents. This would allow us to provide a guarantee of inter-agent collision
-avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
-mention that they are already looking into this problem and have proposed a similar manner of
-tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
-they publish?
+          \fr{I have basic knowledge of Ito equation from unrelated past experience and must say that it is not trivial to work with them.}
+
+\item Consideration of pairwise interactions between agents to ensure
+  collision avoidance. Most of the diffusion models, as mentioned
+  above, do not take into consideration the interactions between
+  agents, since it adds a large degree of complexity to the
+  model. However, it would be important from a safety perspective to
+  take these into account by looking at the attractive and repulsive
+  potentials across agents. This would allow us to provide a guarantee
+  of inter-agent collision avoidance whilst maintaining the diffusive
+  progress of the swarm. In \cite{Inoue2019}, the authors mention that
+  they are already looking into this problem and have proposed a
+  similar manner of tackling it as I have. Perhaps we may be able to
+  build upon or improve their results if and when they publish?
 
@@
 not seem like the connection of MJD and swarm dynamics has been made yet.
-\end{itemize}
+\end{enumerate}
+
+\fr{Please refer also to the items in my email.}
 
@@
 
-\begin{itemize}
-	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
-	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
-	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
-	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
-	required that we determine a safe manner in which MARL agents may explore without leading to
-	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
-	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
-	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
-	independent learners who do not consider the effect that they have on the other agent(s). The
-	particular extension that I propose is to consider the coupled effect between agents as part of
-	the determination of a safe set for exploration.
+\begin{enumerate}
+	\item Stable exploration in MARL. This builds on the ideas of
+          \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective}
+          and an important point mentioned in \cite{Marinescu2014}
+          that 'the dynamics implied by multi-agent systems lead to
+          stochastic behaviour resulting sometimes in undesired
+          effects'. In particular, most RL methods require some
+          trade-off between exploration and exploitation. It is,
+          therefore, required that we determine a safe manner in which
+          MARL agents may explore without leading to unstable
+          behaviour. This would require extending the work of
+          \cite{Berkenkamp2017} and/or
+          \cite{Jin2018Stability-certifiedPerspective} to the
+          multi-agent case. Note that
+          \cite{Jin2018Stability-certifiedPerspective} does actually
+          consider a multi-agent case, but with independent learners
+          who do not consider the effect that they have on the other
+          agent(s). The particular extension that I propose is to
+          consider the coupled effect between agents as part of the
+          determination of a safe set for exploration.
+
+        \fr{That's interesting. Can we leverage on results in Model
+          Predictive Control?}
 
@@
 	also the generalisability of the mean-field method.
-	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
-	part but the potential directions are largely summarised in Section 2.3.1.
-\end{itemize}
+	\item A Dynamical Systems analysis on Games. The ideas here
+          still require further reading on my part but the potential
+          directions are largely summarised in Section 2.3.1.
+
+          \fr{Interesting direction, but in my opinion the game-theoretic analysis should be grounded in some already well-developed theory (MPC?)}
+\end{enumerate}
 

### 2020-01-02 Literature Review/Literature Review - Informal/sample.tex
Added Revised Literature Review

@@
 
-Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
-some of
-these problems, most notably the intractability of the chance contraints. For instance, in 
-\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
-time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
-suited to non-linear systems, which itself is an open problem in the MPC sphere.
+Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches
+towards solving some of these problems, most notably the intractability of the chance contraints.
+For instance, in  \cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints
+in considering time varying stochastic disturbances as well as model uncertainty. This is shown to
+be strongly suited to non-linear systems, which itself is an open problem in the MPC sphere.
 

### 2020-01-02 Literature Review/Literature Review - Revised/sections/ControlTheory.tex
Added Revised Literature Review

\documentclass[../sample.tex]{subfiles}

\begin{document}

The control theoretic perspective considers generating a set of control laws for the system. These
are chosen with the aim to satisfy certain properties. The main properties are

\begin{itemize}
	\item Stability, that a system will return to the desired setpoint (or within a neighbourhood) if
	perturbed.

	\item Robustness, that a system will perform its function in the presence of uncertainty and
	noise

	\item Optimality, that the system will achieve some defined function

	\item Feasibility, that the controller will always be able to generate a control law which
	satisfies the desired properties.
\end{itemize}

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The particular methodology that this chapter focuses largely on
is Model Predictive Control (MPC) as STAI is particularly interested in model-based techniques for
autonomous systems.

\section{Model Predictive Control}

Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
of operating real-world agents safely in the face of environmental disturbances. The overarching
idea begins with the assumpion that we have a model of the environment. As an example, in
the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
environment state for a few time steps ahead, and generate a policy for this horizon. The agent
performs the immediate action generated by the policy, and then we repeat the process, after taking
measurements of the environment to determine the error in the system. Throughout this process, the
controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
example, a likely constraint would be that the controller will never result in the car going on the
pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
the requirement of stability that the system is required to remain safe throughout operation. To
that end, mathematical proofs of these properties are provided in the literature ensuring that we
can trust in the system's performance.

Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
we no longer assume the exact nature of the environment and can guard against worst case scenarios.
This is extremely effective in closed environments or for simple tasks, but falters in more complex
environments.

Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
optimality is defined in terms of the minimisation of the expectation of a probabilistic
cost function. This formulation brings about controllers which are more applicable and robust when
deployed. However, the field is in its infancy and presents a number of theoretical challenges.
These are best described by Mesbah in \cite{Mesbah2016}

\begin{enumerate}
	\item The arbitrary form of the feedback control laws
	\item The non-convexity and intractability of the chance constraints
	\item The complexity of the uncertainty propagations
	\item Establishing stability of the control problem
\end{enumerate}

Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches
towards solving some of these problems, most notably the intractability of the chance contraints.
For instance, in  \cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints
in considering time varying stochastic disturbances as well as model uncertainty. This is shown to
be strongly suited to non-linear systems, which itself is an open problem in the MPC sphere.

\subsection{Distributed MPC}

Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once.

Decentralised control is the scheme in which agents do not have information about the actions of
other agents and can only optimise for their own objective. This has the advantage of requiring no
communication, but can often lead to poor performance when the agents are strongly coupled as each
agent’s model is incomplete. In the non-cooperative setting, each agent optimises their own loss
function whilst treating the others’ actions as a known disturbance. In this setting, each agent has
knowledge of the others’ control laws and their effect. In this case, the agents must communicate
their intended actions to one another and iterate to achieve a consensus (or Nash equilibrium). This
is the same for cooperative control, except that the loss function is now shared across the team.

Of all of these systems, cooperative control has found greatest applicability in autonomous systems
\cite{Negenborn2014}, perhaps due to the favourable stability properties \cite{Venkat2006}. One
particularly strong application of this system is in vehicle platooning. Here, self-driving cars or
unmanned aerial vehicles (UAVs) must move in a certain formation without colliding into one another.
A number of examples can be found such as in \cite{Liu2019, VanParys2017, Zheng2017}. Distributed
MPC provides the advantage that guarantees can be placed regarding coupled constraint satisfaction and
feasibility.

The advances in stochastic and robust MPC, however, do lend themselves towards revisiting the
capabilities of decentralised control. Recall that, in this scheme, the agents cannot communicate
with one another. However, advances in MARL show us that this disadvantage can be made less
prevalent if each agent has a model of the other \cite{Foerster}. To this end, a methodology such as
presented in \cite{Heirung2019} may prove beneficial in the decentralised scheme. Here, the system
chooses amongst a family of system models when choosing its control laws. Similarly, agents who
determine (or perhaps learn) models of the other agents may be able to leverage this information,
minimising the model error when optimising.

\subsection{Hybrid Control}

Hybrid control considers agents whose behaviour is governed not only by continuous time dynamics but
also according to discrete switches \cite{Lygeros2004}. This is particularly useful in systems
which may have different modes of operations (such as autonomous vehicles with gear shifts or
mechanical systems which undergo collisions). It is particularly useful for the case of systems
which undergo discrete failures (e.g. burst tire in an self-driving car). It is important,
therefore, that control systems be designed with the aim to account for such switching behaviour.

Mendes et al \cite{Mendes2017} present one of the first practical implementations of MPC for
distributed hybrid systems. Here, a Mixed Integer Quadratic Program (MIQP) is transformed into a set
of QPs by generating a controller for each of the feasible combinations of binary variables. An
iterative search is then used to determine the best solution out of this family of distributed
control laws. The method is shown to reduce optimality slightly in favour of efficient computation.
It would perhaps be interesting to consider distributed control from the perspective of fault
detection and recovery, and consider how a system similar to that of Tarapore et al may be used in
place of generating all possible controllers. Since Tarapore’s method is developed for swarms, it
maintains the advantages of low communication overheads but may prove advantageous in terms of
communication.

Mendes’ method, however, considers deterministic switching control. When considering faults,
however, this can no longer be the case, since faults occur stochastically. To this end, it is
important to consider stochastic switching dynamics. One proposed method is that of Jump Markovian
Linear Systems (JMLS). In this, discrete ‘jumps’ can occur in a system which, otherwise is governed
by continuous time dynamics \cite{Ma2017}. To this end, Blackmore et al \cite{Blackmore2007} develop
a method towards predictive control of such systems using a particle filtering approach. The aim of
this method is for the resultant system to remain within a safe set with a defined maximum
probability which takes into account the discrete changes (which they consider as brake failures in
an autonomous vehicle), as well as the usual continuous stochasticity which occurs due to noise and
uncertainty. Their method is seen to remain robust to both of these and allows for safe operation
(by constraint satisfaction) of an autonomous vehicle. Yin et al \cite{Yin2014}, similarly
considering this problem, but for the specific case in which the transition probability of the MJLS
is partially unknown. To this end, they similarly develop a controller which is independent of the
mode of operation (and so can operate safely in any of those modes) but supplement it with a
mode-dependent controller which drives the system initially. This allows for a better implementation
than in \cite{Blackmore2007} in terms of optimality, but at the expense of robustness and
computation.

Stochastic Hybrid systems have yet to find their way into distributed predictive control settings
but may prove critical for developing multi-agent systems which are robust to agent failures.
Consider, for instance, the case of the platooning problem but with the added complexity that agents
within the platoon may undergo failures in their braking system. Similarly, communication failures
may occur when driving which may result in an agent having to operate with reduced communication
capacity. Developing Stochastic Hybrid Distributed Systems may present the opportunity for
autonomous systems to remain robust to known failures.

\end{document}

### 2020-01-02 Literature Review/Literature Review - Revised/sections/Dec-POMDPs.tex
Added Revised Literature Review

--- 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
@@
-\documentclass[preprint,11pt]{report}
-
-\usepackage{matlab-prettifier}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{float}
-\usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{csquotes}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[margin=0.5in,letterpaper]{geometry}
-\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
-\let\endchangemargin=\endlist 
-\usepackage{listings}
-\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
-\let\endchangemargin=\endlist
-\title{Literature Review - Informal}
-
-\newcommand\fr[1]{\textcolor{red}{FR: #1}}
-
-\author{Aamal Hussain}
-
-\date{\today}
+\documentclass[../sample.tex]{subfiles}
 
@@
 
-\maketitle
+The use of POMDPs in multi-agent settings is formalised as decentralised POMDP (Dec-POMDP) which
+aims for a team of agents to maximise a common utility. However, it has been found that determining
+the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and so is intractable for all but
+toy problems. A number of methods have been presented to attempt to solve Dec-POMDPs. Oliehoek gives
+a review of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such as brute force) are
+intractable for all but toy problems. Solutions which have found some tractability are
 
-\tableofcontents
-
-\chapter*{Introduction}
-
-The areas of interest regarding Multi Agent Systems fall into two
-distinct categories (which have some slight overlap). The first is
-denoted as 'Decision Making', though the terms 'Planning' and
-'Distributed Control' may sometimes be used as substitutes. It is
-important to note that, in my case, I do not include Planning
-Formalisation techniques such as PDDL. Instead, I focus on the
-particular methods which involve interaction in the world. The second,
-I will refer to as 'Multi Agent Dynamics', though sometimes I will
-refer to this as 'Stability Analysis'.
-
-\subsection*{Scope}
-
-Both of the aforementioned topics have been applied to all variants of
-multi agent systems and have sufficient room for further
-exploration. The typical variants of multi agent systems that I will
-consider are
-
-\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
-Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
-Coded \end{itemize}
-
-In the above, 'Game Theoretic Approaches' cover a wide spectrum,
-including zero-sum (minimax) games, bayesian games, and many more. The
-final category, 'Hard Coded', refers to any approach which does not
-fit neatly into any of these categories. The name is chosen since they
-often refer to methods which revolve around a series of if-else
-statements.
-
-\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}
-
-I will first consider Decision Making as this is most closely related
-to the research proposal, before I consider Multi Agent Dynamics,
-which has strong implications for Safe and Trusted Multi Agent
-Systems.
-
-\subsection*{Objectives}
-
-The aim of the following sections is not to provide an exhaustive list of all work done in the
-aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
-identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
-these directions, we may be able to narrow down the remaining literature review and hone in on
-particular problems and, in fact, we may find that we address multiple of these over the next four
-years (while we, of course add more). As such, the end of each chapter will provide a list of
-research directions which I have identified from the preceding review.
-
-\chapter{Decision Making}
-
-Decision making refers to the generalised problem of considering how a multi-agent system should
-interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
-are aligned (cooperative) or in conflict with one another (competitive).
-
-The following sections will provide an overview of the literature aimed towards coordinating such
-systems as followed by interesting sub-fields in each approach which present avenues for research
-related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
-as the review progresses.
-
-\section{Swarms}
-
-Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
-through a formation using a series of simple local interactions with their neighbours
-\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
-may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
-ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
-performance in reaching globally optimal solutions in search-based tasks. The advantage of many
-swarm algorithms is that they are based on local interactions and so are incredibly scalable
-\cite{Rizk2018}.
-
-The reduction of the complexity in interactions between agents also allows for the robots to perform
-other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
-considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
-manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
-whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
-sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
-readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
-divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
-
-Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
-central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
-adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
-made regarding the homogeneity of individual agents and the simplicity of their local interactions
-result in significant limitations placed on the complexity of the tasks that swarm systems can
-accomplish.
-
-\fr{What are the standard techniques used in swarms?
-that is, how are swarms and their interactions modelled?
-how are solutions computed?
-what kind of algorithms are used in this area?
-most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
-
-\subsection{Co-evolution and Self-Healing}
-
-Recently, there has been an increased interest in introducing
-heterogeneity into the swarm systems to improve their real world
-applicability. An example of this which have been shown strong real
-world success can be found in
-\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
-swarm teams, referred to as 'foot bots' and 'eye bots' who work in
-unison to explore an environment and solve a navigation task.
-
-This area of research is sparsely populated and warrants further
-exploration. This is since the use of co-evolutionary teams can
-improve the robustness of the swarm optimisation. This is since it
-will be possible for a team to automatically determine when robots in
-the other team are not exhibiting expected behaviour and ensure that
-the other team self corrects. This process is referred to as
-'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
-user to define the goals of a swarm system. From this, a 'trust'
-metric can be defined which measures the deviation of each agent from
-the expected behaviour. The self-healing process occurs by limiting
-communication of all agents with 'untrusted' agents and encouraging
-communication with 'trusted' agents. The unison of self-healing with
-co-evolution may present the opportunity for heterogenous swarms to
-maintain their evolutionary stability, even in the face of
-environmental disturbances.
-
-\subsection{Fault Detection}
-
-The above sections have considered the fact that swarm systems are
-robust to losses in the group.  However, any MAS system must first be
-able to recognise that an agent has undergone some failure.
-
-To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
-a robust fault detection approach in which the swarm itself, in a
-decentralised manner, is capable of assessing deviation from 'normal'
-behaviour, even when the behaviour of the swarm itself is altered
-(perhaps by a remote operator). The authors achieve this by requiring
-that the agents themselves sense and characterise their own
-behaviour. This characterisation is formulated as a binary feature
-vector which is then communicated to the agent's neighbours. These
-neighbours will reach a consensus over whether the agent should be
-treated as faulty based on their collective behaviour. The results
-presented in \cite{Tarapore2019FaultDetection} show extremely
-promising results and suggest that their method is, in fact, able to
-determine faults with high accuracy in the presence of various fault
-types (including sensor and actuator failures), although poor
-performance is seen in actuation failures in some instances. It should
-be noted that this method requires that each robot transmit their
-feature vector to the nearest neighbours. In environments where
-communication may be severely limited, this may present further
-errors. Furthermore, it is unlikely that, when a robot is damaged,
-only one of its components will be affected. Therefore, it is
-important to determine the effect on performance in the face of
-multiple agent failures and in communication losses. This exploration
-may open the possibility of improving the state of the art in terms of
-failure detection in swarm systems. (Of course, this conclusion is
-based off two papers so further review is required).
-
-\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas.
-As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another.
-However, this depends essentially on the different modelling assumptions.}
-
-\subsection{Verification}
-
-Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
-require further reading
-
-\subsection{Directions}
-
-From the above consideration of swarms, the following research
-directions have been identified which, in my view, concern themselves
-with STAI.
-
-\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
-towards ensuring that emergent phenomenon and swarm behaviour are as
-expected by the user.
-
-\item Fault Detection in limited communication:
-Considering the ability of a swarm to, in a decentralised approach,
-consider which robots in the team have failed, even in cases of no
-communication or multiple failures.
-
-\fr{The second item looks promising, possibly in combinations with
-  techniques from Game Theory and MARL. Let's keep Fault R\&D in
-  mind.}
-
+\begin{itemize} 
+\item Alternating Maximisation: This is effectively coordinate ascent for determining a joint
+policy; the optimal policy for one agent is found by keeping the others' actions fixed. This process
+is iterated across the entire team.
+\item Approximation as Bayesian Games: A Dec-POMDP can be approximated as a series of Bayesian (or
+Markov) Games. This is accomplished by giving each agent the same payoff in each game and allowing
+the payoff vector to transform Markovially at each time-step. By determining the solution to each of
+the games in turn, an approximate solution to the Dec-POMDP
+\item Selecting sub-tree policies: This considers standard tree search methods such as breadth
+first search or depth first search. This is used with the aim to reduce the number of possible
+policies which are searched over. 
 \end{itemize}
 
-\section{Dec-POMDPs}
+Whilst the above solutions are show lower complexity than the brute force approach, they
+are still limited in their tractability to large scale problems, perhaps with many agents
+or larger (even continuous) action spaces. This intractability largely occurs due to the
+fact that Dec-POMDP methods attempt to find optimal actions across the entire team at
+each time-step. This is in contrast to, for instance, swarm methods in which actions are chosen on a
+local basis and so computation is not affected by the size of the team.
 
-The use of POMDPs in multi-agent settings is formalised as
-decentralised POMDP (Dec-POMDP) which aims for a team of agents to
-maximise a common utility. However, it has been found that determining
-the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
-so is intractable for all but toy problems. A number of methods have
-been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
-of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
-as brute force) are intractable for all but toy problems.
+Approximate solutions to Dec-POMDP have been proposed, perhaps most notable of which is the proposal
+of MacDec-POMDP \cite{Amato2015} by Amato et al. Here, macro actions (actions which extend over
+multiple time steps) are used, as opposed to low-level actions which are re-evaluated at each time
+step. This allows an exact solution to be found as it does not need to be evaluated at each time
+step. This method assumes that, once macro-actions are distributed, the policies (sequence of
+state-action pairs) are known. Since this is not the case, Amato also proposes the use of a
+Dec-POSMDP \cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to 'Semi-Markov Decision
+Process, in which a high level model is defined without the underlying Dec-POMDP's actions and
+observations.
 
-Approximate solutions to Dec-POMDP have been proposed, perhaps most
-notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
-Amato et al. Here, macro actions (actions which extend over multiple
-time steps) are used, as opposed to low-level actions which are
-re-evaluated at each time step. This allows an exact solution to be
-found as it does not need to be evaluated at each time step. This
-method assumes that, once macro-actions are distributed, the policies
-(sequence of state-action pairs) are known. Since this is not the
-case, Amato also proposes the use of a Dec-POSMDP
-\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
-'Semi-Markov Decision Process, in which a high level model is defined
-without the underlying Dec-POMDP's actions and observations.
-
-However, this is largely applicable in passive settings where common
-payoffs can be determined by an offline planner. They also require a
-significant amount of data with which to allow the system to learn the
-underlying models and payoff structures. This limits the applicability
-of the system when communication is limited and the system is
-presented with environments that it has not seen before.  Recent work
-in MDPs \cite{Klima2019RobustDomains} has considered learning in the
-face of Significant Rare Events (SREs) which the system has not yet
-observed. Currently, it is required that a model of such SREs is known
-and so it would be interesting to consider the application of
-Dec-POMDPs in situations where the SRE model is incomplete or
-erroneous and assess the robustness of the Dec-POMDP framework against
-such events.
-
-\subsection{Directions}
-
-The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
-developed by Amato as he seems to largely dominate the field. Based on this initial review of the
-area, a potential direction for research is
-
-\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
-  SREs which have a limited or erroneous model.
-
-\item Agent Failures: The Dec-POMDP model uses a
-centralised planner which acts offline. It therefore assumes that the agents will be able to carry
-out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
-planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
-
-\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
-Also, it might be interesting to understand why swarms scale up better
-than MDPs, and in general why the former have better computational
-properties than the latter: is it a matter of
-``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
-some other swarm-like restriction? It might be interesting to combine
-the two approaches in order to get the ``best of both worlds''.}
-
-\section{Game Theoretic Approaches}
-
-Game theoretic models are generally the go-to method for understanding
-multi-agent systems. As such they fit into all of the categories in
-this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
-methods have both used game theory to support their frameworks. In
-fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
-(POSG), in which all agents use the same payoff. \fr{That's an
-  interesting remark. It might be worth to check whether we can
-  leverage on this and similar observations.} Game theory can,
-therefore, be used in an applied capacity to direct task allocation
-across heterogenous teams.
-
-\subsection{Market Based Methods}
-
-Garapati et al. \cite{Garapati2018AMissions} define a market based
-method as the setting where agents "follow their own interests and
-establish the mechanism of a market for distributing the
-tasks". Auctioning is the most widely used sub-field of market
-approaches and so I will use them interchangeably.
-
-Whilst there are different variants to autioning, the general
-procedure is that an auctioneer who has knowledge of a task (or
-multiple tasks) will set up an auction for said task. Agents can then
-make bids on these tasks and, once the auction is complete, the
-highest bid will win the task. In the specific application to
-robotics, a robot's bid will often reflect the costs, suitability or
-utility their undertaking the task
-\cite{BernardineDias2006Market-basedAnalysis}. This immediately
-highlights a few points. The first is that the method is not too
-heavily reliant upon a single processor to determine some joint
-policy. Tasks are allocated on a case-by-case basis and the utilities
-are calculated by the agent themselves. The only centralised process
-is the auctioneer's assessment of the winner which then relays this
-information back to them. The downside of this is that the system is
-heavily reliant upon strong communication channels, without which
-tasks may not be assigned, incorrect utilities may be communicated
-and, in general, sub-optimal solutions reached.  Furthermore, the
-requirement that the agents themselves determine the cost of their
-actions assumes that they have the computational capability to do
-so. Furthermore, the bids placed by each agent need to be a strong
-representation of their capability to perform a task which may be hard
-to estimate without expert knowledge. However, market based methods
-are well suited to explanation through argumentation (similar to
-\cite{Jung2001DistributedArgumentation}.
-
-\fr{The game-theoretic approaches described above might suffer from the
-  same drawbacks identified above for fault detection, namely reliance
-  on communication and on a single central authority. I'd rather
-  favour distributed approaches. Also, market-based mechanisms and
-  negotiation might lead us to a completely different direction.}
-
-With well chosen payoffs, market based approaches work extremely
-well. For instance, in \cite{Dias2000ASystem}, the authors show that a
-free market approach (where agents try to maximise their own profits)
-can lead to a strong collaborative effort across teams. Similarly, in
-\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
-auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
-towards a robot construction team. However, it is important to note
-that these are both passive settings; tasks were assigned before the
-team were in the field and, in the case of
-\cite{Gerkey2002Sold:Coordination}, the system would repeat the
-bidding process if a robot failed. While both show strong performance,
-it cannot be said that either would be applicable in dangerous
-environments in which dynamic reassignment must happen within strict
-time constraints. Stancliff et
-al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
-method to planning would be to account for failures a priori, a
-philosophy which is exemplified in \cite{Chen2010ACollaboration} who
-consider the robot's reliability and relevance to a task as well as
-'history relevance' which considers the relationship between pairs of
-robots with the aim of producing more effective teams.
-
-There has also been some interesting work in probabilistic
-verification of market based approaches.  Most notable to me is
-\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
-of conflict avoidance. Though their method focuses on collision
-avoidance, it highlights the need for verification of conflict
-resolution and goal achievement in market based approaches with
-different payoff structures. Sirigineedi et
-al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
-direction by considering the verification of cooperative surveillance
-along a route network.  From my understanding, this means that they
-were able to verify that their agents were able to traverse along the
-network without interference. However, this, as always, requires
-further analysis to truly understand.
-
-\subsection{Directions}
-
-The particular considerations which have jumped out to me from the above analysis are as follows:
-
-\begin{itemize} 
-	\item Verification of goal achievement under different payoffs: can we ensure that
-	self-interested agents will, in fact, show cooperative emergent properties? A similar question
-	arises in terms of valuations (how much cost each agent incurs). 
-	\item A priori consideration of
-	reliability: Can we learn and take into account the fact that robots may fail throughout the
-	progress of a mission when we assign tasks? 
-\end{itemize}
-
-\subsection*{Stochastic Games}
-
-\section{Hard Coded}
-
-\section{MARL}
-
-Reinforcement learning extends the Markov Decision Process problem by
-considering the case where the payoff model is not known. This, of
-course, is the case for most real world environments. As such, MARL
-algorithms can perhaps be considered to be more applicable than
-Dec-POMDP models.
-\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}
-
-Fortunately, MARL has picked up a lot of traction in
-research recently, with a large body dedicated towards solving the
-many problems it presents.
-
-The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
-single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
-in the Multi Agent setting since other agents in the environment will be learning concurrently. This
-learning will be based on their own history of interactions which extend beyond the previous state.
-As such, we must now consider that the policy for any one agent will depend on the policy of all
-other agents. As such, a big concern in this area is regarding convergence guarantees and the
-stability of the learner system. Approaches to this will be discussed in the next chapter.
-
-\subsection*{Agent Modelling}
-
-Returning to the problem of non-stationarity, solutions have been presented in which the agent
-models the learning of other agents. A noteworthy example of this is found in
-\cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other
-agents' learning and optimises with respect to this expected return. They show that this leads to
-stable learning and can even lead to emergent cooperation from competition. However, the method
-requires that both agents have exact knowledge of the others' value functions in order to perform
-the one step lookahead. Furthermore, it has only been considered for the case of a two agent
-adversarial game and so the scalability of the system to multiple agents is not yet understood.
-Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect
-the actions and observations of all agents and allows it to model the joint policy of teammates.
-This is shown to generate cooperative behaviour across four agents and so is more applicable to real
-world settings. However, its disadvantage over the method presented in
-\cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this
-requires the presence of an agent (perhaps a laptop) which is able to handle the computational load
-of determining a joint policy across all agents and must then communicate the Q-values of all agents
-back to them. This is both a taxing both in terms of computation and time.
-
-Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by
-tasking a CNN with determining the policy features of other agents and then embedding these as
-features in its own DQN. This shows strong performance in settings where other agents dynamically
-change their policies. The concerns with this, however, are that, as the number of agents in the
-field increase, the CNN in each agent must perform another approximation. This places strong
-requirements on the performance of the CNN since errors in estimation will accumulate as the number
-of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are
-added.
-
-Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent
-modelling is an important one to ensure stable learning and to understand the evolution of the
-system. It also presents a strong challenge and is open to exploration. To put it in context the
-methods described in this section are all from 2018-19, so its all very new.
-
-\subsection{Directions}
-
-I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
-However, on initial assessment I put forward
-
-\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
-the stability of the learning process. However, the particular problem I suggest is to consider the
-modelling in a decentralised manner and with the consideration of evolving numbers of agents in
-teams. \end{itemize}
-
-\fr{This looks like an interesting, non-trivial problem: how can we
-  represent the other agents within the agent model itself, in order
-  to improve learning in MARL? Shall we have a closer look at this problem?}
-
-\section{MARL Approaches} \label{sec::MARL Approaches}
-
-The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
-policy may be the concatenation of all the individual policy or it may just be options for each
-agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
-and so, in this section, I will try to consider the broad spectrum of methods which attempt to
-achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
-all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
-to help guide this review. I am not referencing the individual papers immediately, though the
-references can be found in the book.
-
-\subsubsection*{Learning in Two Player Matrix Games}
-
-The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
-method of linear programming (in which constraints are linear). This will be important in
-considering more current methods. A similar consideration is given to the infinitesimal gradient
-ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
-infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
-not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
-particular problem in games where there are multiple Nash equilibria. However, in practice it is
-difficult to choose a convergence rate of the step size and, without an appropriate choice the
-strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
-to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
-payoff matrix (which is not so much of a problem for model based methods) and the opponent's
-strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
-method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
-(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
-oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
-players with minimal oscillation.
-
-The above methods are all centralised techniques, in which a controller determines the optimal joint
-policy for both agents. However, in real scenarios it is often preferable that each agent learns
-their own strategy, a task which must be completed without information of the other agent's
-strategy. The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which
-guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$)
-which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor
-algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$
-lagging anchor algorithm which can converge to both pure and mixed NEs.
-
-\subsubsection*{Learning in Multiplayer Stochastic Games}
-
-Stochastic Games (or Markov Games) form a basis for MARL
-settings. However, in this case the agents must learn about the
-equilibrium strategies by playing the game, which means they do not
-have a priori knowledge of the reward or transition functions. Schwarz
-considers two properties which should be used for evaluating MARL
-algorithm: rationality and convergence. The latter simply states that
-the method should converge to some equilibrium whereas the former
-suggests that the method should learn the best response to stationary
-opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
-shortly. Schwarz then presents a review of MARL methods (as of
-September 2014)
-
-\fr{All the above looks extremely interesting. I would explore the
-  above for decentralized and partially observable settings. What
-  results are mentioned \cite{SchwartzMulti-agentApproach} under such
-  assumptions?}
-
-\subsection*{Dec-POMDP and MARL}
-
-As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
-methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
-\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
-is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
-Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
-however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
-Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
-order to make this work, we would also need to consider how to select the feature space of sub-trees
-and how to collect this information. \end{itemize}
-
-\chapter{Multi Agent Control}
-
-\section{Stochastic and Robust Model Predictive Control}
-
-The idea of Stochastic Control is best described in the research statement of the Control and
-Analysis of Stochastic Systems (CASS) group at Penn State:
-
-\begin{displayquote}
-	"...to model, predict and control uncertain engineering systems where the interplay between
-	dynamics and uncertainty (stochasticity) is important."
-\end{displayquote}
-
-When operating in the real world, systems are subject to uncertainty and environment perturbations.
-Despite this, for their safe operation, they must provide certain guarantees (such as collision
-avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
-system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
-control have found their way into controlling power distribution, chemical processes and (of course)
-robotics.
-
-\subsection*{Model Predictive Control}
-
-Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
-of operating real-world agents safely in the face of environmental disturbances. The overarching
-idea begins with the assumpion that we have a model of the environment. As an example, in
-the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
-affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
-environment state for a few time steps ahead, and generate a policy for this horizon. The agent
-performs the immediate action generated by the policy, and then we repeat the process, after taking
-measurements of the environment to determine the error in the system. Throughout this process, the
-controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
-example, a likely constraint would be that the controller will never result in the car going on the
-pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
-the requirement of stability that the system is required to remain safe throughout operation. To
-that end, mathematical proofs of these properties are provided in the literature ensuring that we
-can trust in the system's performance.
-
-Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
-knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
-computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
-provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
-of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
-we no longer assume the exact nature of the environment and can guard against worst case scenarios.
-This is extremely effective in closed environments or for simple tasks, but falters in more complex
-environments.
-
-Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
-perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
-define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
-optimality is defined in terms of the minimisation of the expectation of a probabilistic
-cost function. This formulation brings about controllers which are more applicable and robust when
-deployed. However, the field is in its infancy and presents a number of theoretical challenges.
-These are best described by Mesbah in \cite{Mesbah2016}
-
-\begin{itemize}
-	\item The arbitrary form of the feedback control laws
-	\item The non-convexity and intractability of the chance constraints
-	\item The complexity of the uncertainty propagations
-	\item Establishing stability of the control problem
-\end{itemize}
-
-Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
-some of
-these problems, most notably the intractability of the chance contraints. For instance, in 
-\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
-time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
-suited to non-linear systems, which itself is an open problem in the MPC sphere.
-
-The research in using Distributed Predictive Control is quite sparse as compared with, for example,
-single agent predictive control. The added complexity of stochastic environments has meant that this
-area of research is still very open for looking into. With this said, the main works that I have
-found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
-\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
-Usually these are some combination of the following:
-
-\begin{itemize}
-	\item The agents act in a deterministic environment. This suggests that predicted futures will
-	be close enough to the ground truth.
-	\item The agents are uncoupled from one another. This is a strong assumption to make and
-	essentially allows us to consider the agents as completely independent of one another. 
-	\item The agents can easily communicate with one another. This allows for longer pieces of
-	communication (most often predicted trajectories) to be communicated between agents.
-\end{itemize}
-
-\subsection{Directions}
-
-The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
-and applied problems. Control in autonomous systems is also one of the more applicable problems
-related to STAI since it requires that we place mathematical guarantees on the performance and
-stability of the system as well as guarantees on the satisfaction of constraints. This is, of
-course, an ever present problem in autonomous systems which operate in the real world. I begin by
-listing the more theoretical areas for exploration in MPC before then considering their application
-domains.
-
-\begin{itemize}
-	\item Significant exploration is required with regards to the optimisation problem. Especially
-	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
-	approximate methods (such as sampling) should be explored and their effect on the system
-	guarantees presented.
-	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
-	determine the uncertainty in the environment model in order to generate control laws. We should
-	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
-	particle filters, against modern deep learning methods for propagation.
-	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
-	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
-	together whilst maintaining a specified distance from one another). Consider, then, the case
-	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
-	and hence requires adaptation. It would again be interesting to consider the use of neural
-	networks in this manner. However, specifically we should consider whether the use of a function
-	approximator in the form of an NN might result in a violation of the constraints.
-	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
-	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
-	effect that each agent has on the other, the effect of the environment on all agents, estimating the
-	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
-	here that I believe game-theoretic notions (especially differential games) will come to our
-	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
-	in the case of multiple disturbances, but I will elaborate on this in the applied problems
-	section.
-\end{itemize}
-
-the following presents a consideration of the applied end of MPC problems. I have tried to focus on
-the domain independent suggestions, since the domain specific ones are virtually limitless.
-
-\begin{itemize}
-	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
-	interact with each other. In addition, we may consider that there are multiple known disturbances
-	acting on the system. This, at first seems like an impossible problem to solve due to the many
-	interactions between all elements of the system. However, we can consider this as a game
-	theoretic problem in which the components and the disturbances are players. The relatively new
-	class of 'mean-field games' is a method which allows the many body problem to be approximated as
-	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
-	predictive control' remain, this may prove to be a valuable area of applied research.
-	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
-	which emerge into more complex results. It would be interesting to consider the application of
-	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
-	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
-	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
-	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
-	adaptive stochastic model would be interesting to examine here to remain robust to agent
-	failures in the group.
-	\item Modular Robotics?
-\end{itemize}
-
-\section*{Multi Agent Dynamics}
-
-Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
-Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
-well as to understand the trajectory of learning. Typically, this looks at considering whether or
-not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
-problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
-applicability into real world settings requires the study of stable equilbrium points;
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world
-environments.
-
-\section{Stability of Learning Agents}
-
-Stability may be looked at from the view point of two perspectives. The first is from an
-optimisation point of view. This considers the dynamics of the learning model, allowing us to better
-choose our parameters and design our models so that they may converge to a stable result. The second
-is from the view point of the state-action space of a learnt model. This allows us to determine,
-before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This
-knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability
-analysis allows us to build multi agent systems which will learn and act in the way that we expect
-them to.
-
-In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of
-generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is
-one in which the loss function is twice differentiable. Using this formulation, they are able to
-analyse the system from new perspectives by considering the current state-of-the-art understanding
-of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical
-exercise, they go on to show that the insights gained allow them to develop a new multi-objective
-optimisation technique for GANs which shows stronger convergence properties, most notably of which
-is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the
-two players' loss functions.
-
-Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement
-learning agent as a non-linear, time varying feedback controller. Using this notion, they then
-consider the bounded-input-bounded-output stability of the system. They do this by analysing the
-ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains
-finite then the system may be considered to be stable. They then apply these considerations on
-real-world applications including multi-agent flight formation and obtain stability certificates
-(essentially confirming that the system will remain stable under certain conditions) for the learned
-controller.
-
-Berkenkamp et al. \cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different
-definition of stability. Specifically, they look at stability from the point of view of Lyapunov
-functions. A system is said to be stable if the applying the policy will result in stricly lower
-evaluations of the function. In other words, a system is stable if its corresponding Lyapunov
-function is decreasing towards a minimum point. The authors use this idea to define a 'region of
-attraction' in which the system is stable in the sense of Lyapunov. The goal of Safe Lyapunov
-Learning, a method which they develop from these insights, is to learn a policy without leaving this
-region of attraction. They do this by taking measurements within the set and using this to learn
-about the system dynamics, thereby increasing the safe set. With this, we now have a guarantee that
-policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and
-exploration.
-
-As we can see from the discussion thus far, there are many definitions and perpectives of stability,
-each lending to a new understanding of learning systems. To add another to the mix, Milchtaich in
-\cite{Milchtaich2007StaticGames}, presents a notion of static stability. This means that it is based
-solely on the incentives of the players and does not require a consideration of the dynamics of the
-system. Milchtaich's definition of a stable system is one in which, when perturbed, it is more
-beneficial for an agent to move back towards the equilibrium than it is for them to move away. This
-is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows
-that it is applicable to all strategic games, within certain assumptions (finite set of player and
-continuous strategy space) and considers probabilistic perturbations from the original state. This
-is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy
-spaces) since these systems require random exploration of the strategy space and the dynamics are
-not known a priori. However, the lack of dynamics means that we do not consider the evolution of
-learning.
-
-\section{Learning Stable Agents}
-
-The above discussion has considered how notions of stability and control are important to
-Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
-specifically, game theory, can be used to develop controllers which drive systems to stable states.
-This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
-which the players are a controller and an adversarial environment. The design of the controller must
-be such that it is able to drive the system to zero error. To illustrate, consider the problem of
-designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
-vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
-efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
-agent may encounter without actually encountering them. The same notion is explored by Bardi et al
-\cite{Bardi1991DifferentialDisturbances}.
-
- Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
- avoidance problem, similarly from the point of view of differential game theory. They develop a
- robust feedback system for the robots which they show to be able to drive the system towards
- predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
- In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
- systems in a distributed manner. Here, agents only consider their own payoff structure and have
- limited communication with one another. The author shows that the an approximate equilibrium can be
- found using algebraic methods and illustrate the capabilities of the technique using a collision
- avoidance example. For the sake of brevity, I will not include all of the numerous strides that
- Mylvaganam has introduced to the area. However, I must conclude with those presented in
- \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
- games, including linear-quadratic differential games (in which system dynamics are linear functions
- whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
- induced across the players (a notion was suggested in the research proposal) and mean-field games,
- which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
- differential game is the stability of the solution; solutions for the Nash equilibria are
- admissable iff they are locally exponentially stable (which the author often shows with the aid of
- Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
- calculate online. The author then shows that this is not simply a theoretical exercise by applying
- the novel methods towards multi-agent collision problems and designs dynamic control laws which
- guarantee that each agent will reach their desired state whilst avoiding collision with the other
- agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
- robot system.
-
-\subsection{Directions}
-
-I will briefly summarise the research directions which I develop in this section, to save ourselves
-some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}
-
-The above discussion has illustrated a few points. The first, and perhaps most important, is that
-stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
-that learning agents, especially in real world environments, are subject to uncertainty and
-perturbations as well as epsilon-random exploration. As such, it is important that the system is
-able to return to a stable state after such perturbations. This leads to the need to develop
-learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
-equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
-equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
-Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
-to stable fixed points.
-
-The second point is that the notion of stability has multiple definitions. Each one is appropriate
-in different conditions and, as such, it is important to explore stability from various viewpoints
-to consider how to best understand the evolution of a learning system.
-
-Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
-not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
-question and is well worth consideration. This would help guide the choice of loss functions and
-strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
-dramatic impact on the safety certification of MARL systems.
-
-The problem of finding stable solutions through multi agent dynamics also opens the door for a large
-degree of application domains which are currently quite sparse. I would recommend looking at the
-contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
-of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
-control and economic modelling. My particular interest, as always, lies within robotic control
-problems. This appears to be the most direct and relevant application of stable MAS systems. An
-example of this might be the problem of Cooperative Moving Path Following Control considered by
-\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
-pre-defined path without interfering with one another. It is clear then that each player's control
-is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
-determine control rules which lead to stable coordination across the team. Similarly, we can model
-consider modelling a controller and an adversarial environment as a zero-sum game as examined in
-\cite{Marden2018AnnualControl}.
-
-Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
-of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
-differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
-the differential game problem from the point of view of different information structures. In
-real-world systems, it is unlikely that all agents will have access to the information of other
-agent' cost functions and current positions. It could, however, be interesting to explore the use of
-localisation methods to determine and track this information through observation (e.g. through
-Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
-considers the case where system dynamics are linear. A whole new set of problems arise in the more
-realistic case where we must consider the non-linearity of system dynamics. Such a consideration
-would also allow us to extend these technique to the more difficult (and important) problems in
-control.
-
-The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
-Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
-Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
-particularly relevant to this study. However, they will require some further analysis before I write
-about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
-entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
-document out.)
-
-\chapter{Research Directions}
-
-\section{Stochastic Model Predictive Control for Distributed Systems}
-
-The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
-that end, I propose the following techniques towards improving DSMPC.
-
-\begin{itemize}
-	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
-	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
-	distribution of the action that will likely be selected by $j$, effectively performing a
-	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
-	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
-	this may seem computationally expensive, its advantage lies in the fact that it requires little
-	communication across the agents. An immediate disadvantage of this is that, as the number of
-	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
-	not yet confident on the feasibility or the usefulness of this technique, but looking further
-	into the literature (which seems to add new things every day) may provide insights which could
-	help refine the technique. This method is, in many ways, similar to that presented in 
-	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
-	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
-	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
-	all systems to update at each time step.
-
-	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
-	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
-	public belief based on the observed actions of all agents. This joint belief will likely provide
-	some representation of the trajectories that each agent will carry out or an understanding of
-	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
-	will be chosen from a family of existing models using a recursive Bayesian update. The idea
-	would be for this update to be conditioned on the history of observations as is done in 
-	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
-	state and use this, in combination with their own system models to determine a feasible
-	trajectory. The challenge here would be proving the stability and controllability of the system
-	and that it requires communication with a central controller. However, it would appear to be a
-	feasible area of exploration.
-\end{itemize}
-
-\section{Stochastic Control of Swarms}
-
-Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
-when considering its application in stochastic environments. In particular, the ideas presented
-below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
-desired distribution.
-
-\begin{itemize}
-	\item Consideration of state constraints or boundary conditions (terms which I will use
-interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
-particular stochastic difference equation (the Ito equation). However, this does not account for any
-boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
-obstacle avoidance. However, in environments where there are human operators, or in general areas
-where we do not want swarms to enter, it is important to have a guarantee of constraint
-satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
-conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
-confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
-Furthermore, it may present an opportunity for us to consider the decentralised control of the
-agents which can ensure state constraint satisfaction. The resources which are most relevant to this
-study (and from which the ideas are derived) are
-\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
-
-\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
-the diffusion models, as mentioned above, do not take into consideration the interactions between
-agents, since it adds a large degree of complexity to the model. However, it would be important from
-a safety perspective to take these into account by looking at the attractive and repulsive
-potentials across agents. This would allow us to provide a guarantee of inter-agent collision
-avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
-mention that they are already looking into this problem and have proposed a similar manner of
-tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
-they publish?
-
-\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
-By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
-number of their nearest neighbours. However, this may not always be the case. It will often be that
-in different environmental conditions, the observation or communication capabilities of the robots
-may increase or decrease. To better accomodate for this fact, I propose the extension of the model
-with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
-'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
-success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
-way into swarm dynamics. It will, however, become particularly important in cases where we can no
-longer take the consistency of agent communication for granted. 
-\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
-not seem like the connection of MJD and swarm dynamics has been made yet.
-\end{itemize}
-
-\section{Multi Agent Reinforcement Learning}
-
-The ideas I have down here are a little more sparsely populated, but further reading may provide
-some insights into potential directions.
-
-\begin{itemize}
-	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
-	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
-	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
-	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
-	required that we determine a safe manner in which MARL agents may explore without leading to
-	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
-	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
-	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
-	independent learners who do not consider the effect that they have on the other agent(s). The
-	particular extension that I propose is to consider the coupled effect between agents as part of
-	the determination of a safe set for exploration.
-
-	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
-	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
-	problems. Although it makes strong assumptions about the nature of the system, in practice it
-	has shown strong results. Particular examples of this are found in 
-	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
-	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
-	systems by considering sub-groups within the population. Each of these may be updated
-	individually. It would be interesting to examine how this might increase the complexity, and
-	also the generalisability of the mean-field method.
-	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
-	part but the potential directions are largely summarised in Section 2.3.1.
-\end{itemize}
-
-\bibliographystyle{IEEEtran}
-
-\bibliography{IEEEfull,references}
+However, this is largely applicable in passive settings where common payoffs can be determined by an
+offline planner. They also require a significant amount of data with which to allow the system to
+learn the underlying models and payoff structures. This limits the applicability of the system when
+communication is limited and the system is presented with environments that it has not seen before. 
+Recent work in MDPs \cite{Klima2019RobustDomains} has considered learning in the face of Significant
+Rare Events (SREs) which the system has not yet observed. Currently, it is required that a model of
+such SREs is known and so it would be interesting to consider the application of Dec-POMDPs in
+situations where the SRE model is incomplete or erroneous and assess the robustness of the Dec-POMDP
+framework against such events.
 

### 2020-01-02 Literature Review/Literature Review - Revised/sections/Intro.tex
Added Revised Literature Review

\documentclass[../sample.tex]{subfiles}

\begin{document}

This review attempts to present the current state-of-the-art in regard to solving the ‘Multi-Agent
Problem’, which considers a scenario of multiple agents (such as robots, AI systems etc) must
interact, whether cooperatively or competitively, to achieve defined goals. To this end, this review
categorises work based on the approach towards solving this problem. Each approach often places
assumptions on the type of agents present within the system and so each is appropriate in different
settings. Briefly, these categories are

\begin{itemize} 
\item Swarms, in which the agents are often assumed to be homogeneous and with limited sensing and
communication capabilities.

\item Decentralised-Partially Observable Markov Decision Processes (Dec-POMDPs), in which agents
must choose actions with the aim to optimise a known loss function which is applied to the entire
team.

\item Game Theory, which allows for each agent to have an individual payoff function which they
must optimise with respect to the actions of the other agents.

\item Multi-Agent Reinforcement Learning, in which agents do not immediately have access to the
payoff function and so must determine it through iterations of exploration.

\item Control Theory, which considers the low-level operation of each agent and mathematically
defines control laws for each agent which satisfy properties such as stability and controllability.

	\item Hard Coded, a term of the author’s devising to categorise systems which do not fit in any of
the formal methods above. These systems are built on a series of if-then statements, allowing agents
to reason about their current state and future tasks.

\end{itemize}

\section{Objective}

The aim of the following sections is not to provide an exhaustive list of all work done in the
aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
identify research directions which lie within the broad scope of Multi-Agent Systems (MAS).  Once
identified, these directions will form the basis for the remainder of this review, allowing for
particular problems to emerge. It will likely be the case that a medley of these problems will be
addressed throughout the course of the PhD and, of course, more will likely be added.

\end{document}

### 2020-01-02 Literature Review/Literature Review - Revised/sections/MARL.tex
Added Revised Literature Review

--- 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
@@
 
-\maketitle
+Reinforcement learning extends the Markov Decision Process problem by considering the case where the
+reward model is not initially known to the agent. In a similar manner, Multi Agent Reinforcement
+Learning (MARL) extends the Markov Game setting to one where the payoff structure is not a priori
+knowledge.
 
-\tableofcontents
+The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
+policy may be the concatenation of all the individual policy or it may just be options for each
+agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
+and so, in this section, I will try to consider the broad spectrum of methods which attempt to
+achieve this Nash equilibria. The largest problem in MARL is the non-stationarity of the environment
+\cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian.
+However, this must be lifted in the Multi Agent setting since other agents in the environment will
+be learning concurrently. As such, we must now consider that the policy for any one agent will
+depend on the policy of all other agents.
 
-\chapter*{Introduction}
+This chapter begins with a selection of the foundational methods which were developed towards
+solving the MARL problem. The interested reader may find a stronger review and analysis in
+\cite{SchwartzMulti-agentApproach}. I then go on to consider more contemporary approaches, most
+notably that of agent modelling.
 
-The areas of interest regarding Multi Agent Systems fall into two
-distinct categories (which have some slight overlap). The first is
-denoted as 'Decision Making', though the terms 'Planning' and
-'Distributed Control' may sometimes be used as substitutes. It is
-important to note that, in my case, I do not include Planning
-Formalisation techniques such as PDDL. Instead, I focus on the
-particular methods which involve interaction in the world. The second,
-I will refer to as 'Multi Agent Dynamics', though sometimes I will
-refer to this as 'Stability Analysis'.
+\section{Learning in Two Player Matrix Games}
 
-\subsection*{Scope}
+The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
+method of linear programming (in which constraints are linear). This will be important in
+considering more current methods. A similar consideration is given to the infinitesimal gradient
+ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
+infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
+not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
+particular problem in games where there are multiple Nash equilibria. However, in practice it is
+difficult to choose a convergence rate of the step size and, without an appropriate choice the
+strategy may oscillate as shown in the book. To address this, a modified approach is presented by
+Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
+WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
+to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
+payoff matrix (which is not so much of a problem for model based methods) and the opponent's
+strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
+method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
+(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
+oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
+players with minimal oscillation.
 
-Both of the aforementioned topics have been applied to all variants of
-multi agent systems and have sufficient room for further
-exploration. The typical variants of multi agent systems that I will
-consider are
+\section{Learning in Multiplayer Stochastic Games}
 
-\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
-Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
-Coded \end{itemize}
+Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
+must learn about the equilibrium strategies by playing the game, which means they do not have a
+priori knowledge of the reward or transition functions. Schwarz considers two properties which
+should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
+that the method should converge to some equilibrium whereas the former suggests that the method
+should learn the best response to stationary opponents. A similar set of conditions is considered by
+Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
+then presents a review of MARL methods (as of September 2014)
 
-In the above, 'Game Theoretic Approaches' cover a wide spectrum,
-including zero-sum (minimax) games, bayesian games, and many more. The
-final category, 'Hard Coded', refers to any approach which does not
-fit neatly into any of these categories. The name is chosen since they
-often refer to methods which revolve around a series of if-else
-statements.
-
-\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}
-
-I will first consider Decision Making as this is most closely related
-to the research proposal, before I consider Multi Agent Dynamics,
-which has strong implications for Safe and Trusted Multi Agent
-Systems.
-
-\subsection*{Objectives}
-
-The aim of the following sections is not to provide an exhaustive list of all work done in the
-aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
-identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
-these directions, we may be able to narrow down the remaining literature review and hone in on
-particular problems and, in fact, we may find that we address multiple of these over the next four
-years (while we, of course add more). As such, the end of each chapter will provide a list of
-research directions which I have identified from the preceding review.
-
-\chapter{Decision Making}
-
-Decision making refers to the generalised problem of considering how a multi-agent system should
-interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
-are aligned (cooperative) or in conflict with one another (competitive).
-
-The following sections will provide an overview of the literature aimed towards coordinating such
-systems as followed by interesting sub-fields in each approach which present avenues for research
-related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
-as the review progresses.
-
-\section{Swarms}
-
-Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
-through a formation using a series of simple local interactions with their neighbours
-\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
-may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
-ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
-performance in reaching globally optimal solutions in search-based tasks. The advantage of many
-swarm algorithms is that they are based on local interactions and so are incredibly scalable
-\cite{Rizk2018}.
-
-The reduction of the complexity in interactions between agents also allows for the robots to perform
-other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
-considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
-manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
-whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
-sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
-readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
-divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
-
-Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
-central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
-adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
-made regarding the homogeneity of individual agents and the simplicity of their local interactions
-result in significant limitations placed on the complexity of the tasks that swarm systems can
-accomplish.
-
-\fr{What are the standard techniques used in swarms?
-that is, how are swarms and their interactions modelled?
-how are solutions computed?
-what kind of algorithms are used in this area?
-most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
-
-\subsection{Co-evolution and Self-Healing}
-
-Recently, there has been an increased interest in introducing
-heterogeneity into the swarm systems to improve their real world
-applicability. An example of this which have been shown strong real
-world success can be found in
-\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
-swarm teams, referred to as 'foot bots' and 'eye bots' who work in
-unison to explore an environment and solve a navigation task.
-
-This area of research is sparsely populated and warrants further
-exploration. This is since the use of co-evolutionary teams can
-improve the robustness of the swarm optimisation. This is since it
-will be possible for a team to automatically determine when robots in
-the other team are not exhibiting expected behaviour and ensure that
-the other team self corrects. This process is referred to as
-'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
-user to define the goals of a swarm system. From this, a 'trust'
-metric can be defined which measures the deviation of each agent from
-the expected behaviour. The self-healing process occurs by limiting
-communication of all agents with 'untrusted' agents and encouraging
-communication with 'trusted' agents. The unison of self-healing with
-co-evolution may present the opportunity for heterogenous swarms to
-maintain their evolutionary stability, even in the face of
-environmental disturbances.
-
-\subsection{Fault Detection}
-
-The above sections have considered the fact that swarm systems are
-robust to losses in the group.  However, any MAS system must first be
-able to recognise that an agent has undergone some failure.
-
-To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
-a robust fault detection approach in which the swarm itself, in a
-decentralised manner, is capable of assessing deviation from 'normal'
-behaviour, even when the behaviour of the swarm itself is altered
-(perhaps by a remote operator). The authors achieve this by requiring
-that the agents themselves sense and characterise their own
-behaviour. This characterisation is formulated as a binary feature
-vector which is then communicated to the agent's neighbours. These
-neighbours will reach a consensus over whether the agent should be
-treated as faulty based on their collective behaviour. The results
-presented in \cite{Tarapore2019FaultDetection} show extremely
-promising results and suggest that their method is, in fact, able to
-determine faults with high accuracy in the presence of various fault
-types (including sensor and actuator failures), although poor
-performance is seen in actuation failures in some instances. It should
-be noted that this method requires that each robot transmit their
-feature vector to the nearest neighbours. In environments where
-communication may be severely limited, this may present further
-errors. Furthermore, it is unlikely that, when a robot is damaged,
-only one of its components will be affected. Therefore, it is
-important to determine the effect on performance in the face of
-multiple agent failures and in communication losses. This exploration
-may open the possibility of improving the state of the art in terms of
-failure detection in swarm systems. (Of course, this conclusion is
-based off two papers so further review is required).
-
-\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas.
-As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another.
-However, this depends essentially on the different modelling assumptions.}
-
-\subsection{Verification}
-
-Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
-require further reading
-
-\subsection{Directions}
-
-From the above consideration of swarms, the following research
-directions have been identified which, in my view, concern themselves
-with STAI.
-
-\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
-towards ensuring that emergent phenomenon and swarm behaviour are as
-expected by the user.
-
-\item Fault Detection in limited communication:
-Considering the ability of a swarm to, in a decentralised approach,
-consider which robots in the team have failed, even in cases of no
-communication or multiple failures.
-
-\fr{The second item looks promising, possibly in combinations with
-  techniques from Game Theory and MARL. Let's keep Fault R\&D in
-  mind.}
-
-\end{itemize}
-
-\section{Dec-POMDPs}
-
-The use of POMDPs in multi-agent settings is formalised as
-decentralised POMDP (Dec-POMDP) which aims for a team of agents to
-maximise a common utility. However, it has been found that determining
-the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
-so is intractable for all but toy problems. A number of methods have
-been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
-of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
-as brute force) are intractable for all but toy problems.
-
-Approximate solutions to Dec-POMDP have been proposed, perhaps most
-notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
-Amato et al. Here, macro actions (actions which extend over multiple
-time steps) are used, as opposed to low-level actions which are
-re-evaluated at each time step. This allows an exact solution to be
-found as it does not need to be evaluated at each time step. This
-method assumes that, once macro-actions are distributed, the policies
-(sequence of state-action pairs) are known. Since this is not the
-case, Amato also proposes the use of a Dec-POSMDP
-\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
-'Semi-Markov Decision Process, in which a high level model is defined
-without the underlying Dec-POMDP's actions and observations.
-
-However, this is largely applicable in passive settings where common
-payoffs can be determined by an offline planner. They also require a
-significant amount of data with which to allow the system to learn the
-underlying models and payoff structures. This limits the applicability
-of the system when communication is limited and the system is
-presented with environments that it has not seen before.  Recent work
-in MDPs \cite{Klima2019RobustDomains} has considered learning in the
-face of Significant Rare Events (SREs) which the system has not yet
-observed. Currently, it is required that a model of such SREs is known
-and so it would be interesting to consider the application of
-Dec-POMDPs in situations where the SRE model is incomplete or
-erroneous and assess the robustness of the Dec-POMDP framework against
-such events.
-
-\subsection{Directions}
-
-The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
-developed by Amato as he seems to largely dominate the field. Based on this initial review of the
-area, a potential direction for research is
-
-\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
-  SREs which have a limited or erroneous model.
-
-\item Agent Failures: The Dec-POMDP model uses a
-centralised planner which acts offline. It therefore assumes that the agents will be able to carry
-out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
-planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
-
-\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
-Also, it might be interesting to understand why swarms scale up better
-than MDPs, and in general why the former have better computational
-properties than the latter: is it a matter of
-``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
-some other swarm-like restriction? It might be interesting to combine
-the two approaches in order to get the ``best of both worlds''.}
-
-\section{Game Theoretic Approaches}
-
-Game theoretic models are generally the go-to method for understanding
-multi-agent systems. As such they fit into all of the categories in
-this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
-methods have both used game theory to support their frameworks. In
-fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
-(POSG), in which all agents use the same payoff. \fr{That's an
-  interesting remark. It might be worth to check whether we can
-  leverage on this and similar observations.} Game theory can,
-therefore, be used in an applied capacity to direct task allocation
-across heterogenous teams.
-
-\subsection{Market Based Methods}
-
-Garapati et al. \cite{Garapati2018AMissions} define a market based
-method as the setting where agents "follow their own interests and
-establish the mechanism of a market for distributing the
-tasks". Auctioning is the most widely used sub-field of market
-approaches and so I will use them interchangeably.
-
-Whilst there are different variants to autioning, the general
-procedure is that an auctioneer who has knowledge of a task (or
-multiple tasks) will set up an auction for said task. Agents can then
-make bids on these tasks and, once the auction is complete, the
-highest bid will win the task. In the specific application to
-robotics, a robot's bid will often reflect the costs, suitability or
-utility their undertaking the task
-\cite{BernardineDias2006Market-basedAnalysis}. This immediately
-highlights a few points. The first is that the method is not too
-heavily reliant upon a single processor to determine some joint
-policy. Tasks are allocated on a case-by-case basis and the utilities
-are calculated by the agent themselves. The only centralised process
-is the auctioneer's assessment of the winner which then relays this
-information back to them. The downside of this is that the system is
-heavily reliant upon strong communication channels, without which
-tasks may not be assigned, incorrect utilities may be communicated
-and, in general, sub-optimal solutions reached.  Furthermore, the
-requirement that the agents themselves determine the cost of their
-actions assumes that they have the computational capability to do
-so. Furthermore, the bids placed by each agent need to be a strong
-representation of their capability to perform a task which may be hard
-to estimate without expert knowledge. However, market based methods
-are well suited to explanation through argumentation (similar to
-\cite{Jung2001DistributedArgumentation}.
-
-\fr{The game-theoretic approaches described above might suffer from the
-  same drawbacks identified above for fault detection, namely reliance
-  on communication and on a single central authority. I'd rather
-  favour distributed approaches. Also, market-based mechanisms and
-  negotiation might lead us to a completely different direction.}
-
-With well chosen payoffs, market based approaches work extremely
-well. For instance, in \cite{Dias2000ASystem}, the authors show that a
-free market approach (where agents try to maximise their own profits)
-can lead to a strong collaborative effort across teams. Similarly, in
-\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
-auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
-towards a robot construction team. However, it is important to note
-that these are both passive settings; tasks were assigned before the
-team were in the field and, in the case of
-\cite{Gerkey2002Sold:Coordination}, the system would repeat the
-bidding process if a robot failed. While both show strong performance,
-it cannot be said that either would be applicable in dangerous
-environments in which dynamic reassignment must happen within strict
-time constraints. Stancliff et
-al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
-method to planning would be to account for failures a priori, a
-philosophy which is exemplified in \cite{Chen2010ACollaboration} who
-consider the robot's reliability and relevance to a task as well as
-'history relevance' which considers the relationship between pairs of
-robots with the aim of producing more effective teams.
-
-There has also been some interesting work in probabilistic
-verification of market based approaches.  Most notable to me is
-\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
-of conflict avoidance. Though their method focuses on collision
-avoidance, it highlights the need for verification of conflict
-resolution and goal achievement in market based approaches with
-different payoff structures. Sirigineedi et
-al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
-direction by considering the verification of cooperative surveillance
-along a route network.  From my understanding, this means that they
-were able to verify that their agents were able to traverse along the
-network without interference. However, this, as always, requires
-further analysis to truly understand.
-
-\subsection{Directions}
-
-The particular considerations which have jumped out to me from the above analysis are as follows:
-
-\begin{itemize} 
-	\item Verification of goal achievement under different payoffs: can we ensure that
-	self-interested agents will, in fact, show cooperative emergent properties? A similar question
-	arises in terms of valuations (how much cost each agent incurs). 
-	\item A priori consideration of
-	reliability: Can we learn and take into account the fact that robots may fail throughout the
-	progress of a mission when we assign tasks? 
-\end{itemize}
-
-\subsection*{Stochastic Games}
-
-\section{Hard Coded}
-
-\section{MARL}
-
-Reinforcement learning extends the Markov Decision Process problem by
-considering the case where the payoff model is not known. This, of
-course, is the case for most real world environments. As such, MARL
-algorithms can perhaps be considered to be more applicable than
-Dec-POMDP models.
-\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}
-
-Fortunately, MARL has picked up a lot of traction in
-research recently, with a large body dedicated towards solving the
-many problems it presents.
-
-The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
-single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
-in the Multi Agent setting since other agents in the environment will be learning concurrently. This
-learning will be based on their own history of interactions which extend beyond the previous state.
-As such, we must now consider that the policy for any one agent will depend on the policy of all
-other agents. As such, a big concern in this area is regarding convergence guarantees and the
-stability of the learner system. Approaches to this will be discussed in the next chapter.
+\TODO{Consider the case for partially observed/decentralised settings. Find the relevant material
+within \cite{SchwartzMulti-agentApproach} which addresses this issue.}
 
@@
 
-\subsection{Directions}
-
-I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
-However, on initial assessment I put forward
-
-\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
-the stability of the learning process. However, the particular problem I suggest is to consider the
-modelling in a decentralised manner and with the consideration of evolving numbers of agents in
-teams. \end{itemize}
-
-\fr{This looks like an interesting, non-trivial problem: how can we
-  represent the other agents within the agent model itself, in order
-  to improve learning in MARL? Shall we have a closer look at this problem?}
-
-\section{MARL Approaches} \label{sec::MARL Approaches}
-
-The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
-policy may be the concatenation of all the individual policy or it may just be options for each
-agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
-and so, in this section, I will try to consider the broad spectrum of methods which attempt to
-achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
-all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
-to help guide this review. I am not referencing the individual papers immediately, though the
-references can be found in the book.
-
-\subsubsection*{Learning in Two Player Matrix Games}
-
-The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
-method of linear programming (in which constraints are linear). This will be important in
-considering more current methods. A similar consideration is given to the infinitesimal gradient
-ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
-infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
-not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
-particular problem in games where there are multiple Nash equilibria. However, in practice it is
-difficult to choose a convergence rate of the step size and, without an appropriate choice the
-strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
-to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
-payoff matrix (which is not so much of a problem for model based methods) and the opponent's
-strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
-method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
-(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
-oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
-players with minimal oscillation.
-
 The above methods are all centralised techniques, in which a controller determines the optimal joint
@@
 
-\subsubsection*{Learning in Multiplayer Stochastic Games}
+\section{Stable Learning}
 
-Stochastic Games (or Markov Games) form a basis for MARL
-settings. However, in this case the agents must learn about the
-equilibrium strategies by playing the game, which means they do not
-have a priori knowledge of the reward or transition functions. Schwarz
-considers two properties which should be used for evaluating MARL
-algorithm: rationality and convergence. The latter simply states that
-the method should converge to some equilibrium whereas the former
-suggests that the method should learn the best response to stationary
-opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
-shortly. Schwarz then presents a review of MARL methods (as of
-September 2014)
-
-\fr{All the above looks extremely interesting. I would explore the
-  above for decentralized and partially observable settings. What
-  results are mentioned \cite{SchwartzMulti-agentApproach} under such
-  assumptions?}
-
-\subsection*{Dec-POMDP and MARL}
-
-As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
-methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
-\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
-is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
-Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
-however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
-Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
-order to make this work, we would also need to consider how to select the feature space of sub-trees
-and how to collect this information. \end{itemize}
-
-\chapter{Multi Agent Control}
-
-\section{Stochastic and Robust Model Predictive Control}
-
-The idea of Stochastic Control is best described in the research statement of the Control and
-Analysis of Stochastic Systems (CASS) group at Penn State:
-
-\begin{displayquote}
-	"...to model, predict and control uncertain engineering systems where the interplay between
-	dynamics and uncertainty (stochasticity) is important."
-\end{displayquote}
-
-When operating in the real world, systems are subject to uncertainty and environment perturbations.
-Despite this, for their safe operation, they must provide certain guarantees (such as collision
-avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
-system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
-control have found their way into controlling power distribution, chemical processes and (of course)
-robotics.
-
-\subsection*{Model Predictive Control}
-
-Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
-of operating real-world agents safely in the face of environmental disturbances. The overarching
-idea begins with the assumpion that we have a model of the environment. As an example, in
-the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
-affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
-environment state for a few time steps ahead, and generate a policy for this horizon. The agent
-performs the immediate action generated by the policy, and then we repeat the process, after taking
-measurements of the environment to determine the error in the system. Throughout this process, the
-controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
-example, a likely constraint would be that the controller will never result in the car going on the
-pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
-the requirement of stability that the system is required to remain safe throughout operation. To
-that end, mathematical proofs of these properties are provided in the literature ensuring that we
-can trust in the system's performance.
-
-Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
-knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
-computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
-provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
-of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
-we no longer assume the exact nature of the environment and can guard against worst case scenarios.
-This is extremely effective in closed environments or for simple tasks, but falters in more complex
-environments.
-
-Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
-perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
-define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
-optimality is defined in terms of the minimisation of the expectation of a probabilistic
-cost function. This formulation brings about controllers which are more applicable and robust when
-deployed. However, the field is in its infancy and presents a number of theoretical challenges.
-These are best described by Mesbah in \cite{Mesbah2016}
-
-\begin{itemize}
-	\item The arbitrary form of the feedback control laws
-	\item The non-convexity and intractability of the chance constraints
-	\item The complexity of the uncertainty propagations
-	\item Establishing stability of the control problem
-\end{itemize}
-
-Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
-some of
-these problems, most notably the intractability of the chance contraints. For instance, in 
-\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
-time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
-suited to non-linear systems, which itself is an open problem in the MPC sphere.
-
-The research in using Distributed Predictive Control is quite sparse as compared with, for example,
-single agent predictive control. The added complexity of stochastic environments has meant that this
-area of research is still very open for looking into. With this said, the main works that I have
-found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
-\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
-Usually these are some combination of the following:
-
-\begin{itemize}
-	\item The agents act in a deterministic environment. This suggests that predicted futures will
-	be close enough to the ground truth.
-	\item The agents are uncoupled from one another. This is a strong assumption to make and
-	essentially allows us to consider the agents as completely independent of one another. 
-	\item The agents can easily communicate with one another. This allows for longer pieces of
-	communication (most often predicted trajectories) to be communicated between agents.
-\end{itemize}
-
-\subsection{Directions}
-
-The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
-and applied problems. Control in autonomous systems is also one of the more applicable problems
-related to STAI since it requires that we place mathematical guarantees on the performance and
-stability of the system as well as guarantees on the satisfaction of constraints. This is, of
-course, an ever present problem in autonomous systems which operate in the real world. I begin by
-listing the more theoretical areas for exploration in MPC before then considering their application
-domains.
-
-\begin{itemize}
-	\item Significant exploration is required with regards to the optimisation problem. Especially
-	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
-	approximate methods (such as sampling) should be explored and their effect on the system
-	guarantees presented.
-	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
-	determine the uncertainty in the environment model in order to generate control laws. We should
-	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
-	particle filters, against modern deep learning methods for propagation.
-	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
-	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
-	together whilst maintaining a specified distance from one another). Consider, then, the case
-	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
-	and hence requires adaptation. It would again be interesting to consider the use of neural
-	networks in this manner. However, specifically we should consider whether the use of a function
-	approximator in the form of an NN might result in a violation of the constraints.
-	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
-	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
-	effect that each agent has on the other, the effect of the environment on all agents, estimating the
-	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
-	here that I believe game-theoretic notions (especially differential games) will come to our
-	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
-	in the case of multiple disturbances, but I will elaborate on this in the applied problems
-	section.
-\end{itemize}
-
-the following presents a consideration of the applied end of MPC problems. I have tried to focus on
-the domain independent suggestions, since the domain specific ones are virtually limitless.
-
-\begin{itemize}
-	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
-	interact with each other. In addition, we may consider that there are multiple known disturbances
-	acting on the system. This, at first seems like an impossible problem to solve due to the many
-	interactions between all elements of the system. However, we can consider this as a game
-	theoretic problem in which the components and the disturbances are players. The relatively new
-	class of 'mean-field games' is a method which allows the many body problem to be approximated as
-	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
-	predictive control' remain, this may prove to be a valuable area of applied research.
-	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
-	which emerge into more complex results. It would be interesting to consider the application of
-	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
-	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
-	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
-	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
-	adaptive stochastic model would be interesting to examine here to remain robust to agent
-	failures in the group.
-	\item Modular Robotics?
-\end{itemize}
-
-\section*{Multi Agent Dynamics}
-
-Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
-Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
-well as to understand the trajectory of learning. Typically, this looks at considering whether or
-not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
-problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
-applicability into real world settings requires the study of stable equilbrium points;
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world
-environments.
-
-\section{Stability of Learning Agents}
+This section considers a dynamical systems approach towards learning agents. Its aim is to develop learning systems which prioritise stability.
 
@@
 
-\section{Learning Stable Agents}
-
-The above discussion has considered how notions of stability and control are important to
-Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
-specifically, game theory, can be used to develop controllers which drive systems to stable states.
-This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
-which the players are a controller and an adversarial environment. The design of the controller must
-be such that it is able to drive the system to zero error. To illustrate, consider the problem of
-designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
-vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
-efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
-agent may encounter without actually encountering them. The same notion is explored by Bardi et al
-\cite{Bardi1991DifferentialDisturbances}.
-
- Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
- avoidance problem, similarly from the point of view of differential game theory. They develop a
- robust feedback system for the robots which they show to be able to drive the system towards
- predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
- In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
- systems in a distributed manner. Here, agents only consider their own payoff structure and have
- limited communication with one another. The author shows that the an approximate equilibrium can be
- found using algebraic methods and illustrate the capabilities of the technique using a collision
- avoidance example. For the sake of brevity, I will not include all of the numerous strides that
- Mylvaganam has introduced to the area. However, I must conclude with those presented in
- \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
- games, including linear-quadratic differential games (in which system dynamics are linear functions
- whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
- induced across the players (a notion was suggested in the research proposal) and mean-field games,
- which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
- differential game is the stability of the solution; solutions for the Nash equilibria are
- admissable iff they are locally exponentially stable (which the author often shows with the aid of
- Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
- calculate online. The author then shows that this is not simply a theoretical exercise by applying
- the novel methods towards multi-agent collision problems and designs dynamic control laws which
- guarantee that each agent will reach their desired state whilst avoiding collision with the other
- agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
- robot system.
-
-\subsection{Directions}
-
-I will briefly summarise the research directions which I develop in this section, to save ourselves
-some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}
-
-The above discussion has illustrated a few points. The first, and perhaps most important, is that
-stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
-that learning agents, especially in real world environments, are subject to uncertainty and
-perturbations as well as epsilon-random exploration. As such, it is important that the system is
-able to return to a stable state after such perturbations. This leads to the need to develop
-learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
-equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
-equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
-Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
-to stable fixed points.
-
-The second point is that the notion of stability has multiple definitions. Each one is appropriate
-in different conditions and, as such, it is important to explore stability from various viewpoints
-to consider how to best understand the evolution of a learning system.
-
-Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
-not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
-question and is well worth consideration. This would help guide the choice of loss functions and
-strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
-dramatic impact on the safety certification of MARL systems.
-
-The problem of finding stable solutions through multi agent dynamics also opens the door for a large
-degree of application domains which are currently quite sparse. I would recommend looking at the
-contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
-of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
-control and economic modelling. My particular interest, as always, lies within robotic control
-problems. This appears to be the most direct and relevant application of stable MAS systems. An
-example of this might be the problem of Cooperative Moving Path Following Control considered by
-\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
-pre-defined path without interfering with one another. It is clear then that each player's control
-is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
-determine control rules which lead to stable coordination across the team. Similarly, we can model
-consider modelling a controller and an adversarial environment as a zero-sum game as examined in
-\cite{Marden2018AnnualControl}.
-
-Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
-of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
-differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
-the differential game problem from the point of view of different information structures. In
-real-world systems, it is unlikely that all agents will have access to the information of other
-agent' cost functions and current positions. It could, however, be interesting to explore the use of
-localisation methods to determine and track this information through observation (e.g. through
-Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
-considers the case where system dynamics are linear. A whole new set of problems arise in the more
-realistic case where we must consider the non-linearity of system dynamics. Such a consideration
-would also allow us to extend these technique to the more difficult (and important) problems in
-control.
-
-The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
-Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
-Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
-particularly relevant to this study. However, they will require some further analysis before I write
-about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
-entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
-document out.)
-
-\chapter{Research Directions}
-
-\section{Stochastic Model Predictive Control for Distributed Systems}
-
-The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
-that end, I propose the following techniques towards improving DSMPC.
-
-\begin{itemize}
-	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
-	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
-	distribution of the action that will likely be selected by $j$, effectively performing a
-	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
-	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
-	this may seem computationally expensive, its advantage lies in the fact that it requires little
-	communication across the agents. An immediate disadvantage of this is that, as the number of
-	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
-	not yet confident on the feasibility or the usefulness of this technique, but looking further
-	into the literature (which seems to add new things every day) may provide insights which could
-	help refine the technique. This method is, in many ways, similar to that presented in 
-	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
-	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
-	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
-	all systems to update at each time step.
-
-	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
-	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
-	public belief based on the observed actions of all agents. This joint belief will likely provide
-	some representation of the trajectories that each agent will carry out or an understanding of
-	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
-	will be chosen from a family of existing models using a recursive Bayesian update. The idea
-	would be for this update to be conditioned on the history of observations as is done in 
-	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
-	state and use this, in combination with their own system models to determine a feasible
-	trajectory. The challenge here would be proving the stability and controllability of the system
-	and that it requires communication with a central controller. However, it would appear to be a
-	feasible area of exploration.
-\end{itemize}
-
-\section{Stochastic Control of Swarms}
-
-Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
-when considering its application in stochastic environments. In particular, the ideas presented
-below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
-desired distribution.
-
-\begin{itemize}
-	\item Consideration of state constraints or boundary conditions (terms which I will use
-interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
-particular stochastic difference equation (the Ito equation). However, this does not account for any
-boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
-obstacle avoidance. However, in environments where there are human operators, or in general areas
-where we do not want swarms to enter, it is important to have a guarantee of constraint
-satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
-conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
-confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
-Furthermore, it may present an opportunity for us to consider the decentralised control of the
-agents which can ensure state constraint satisfaction. The resources which are most relevant to this
-study (and from which the ideas are derived) are
-\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
-
-\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
-the diffusion models, as mentioned above, do not take into consideration the interactions between
-agents, since it adds a large degree of complexity to the model. However, it would be important from
-a safety perspective to take these into account by looking at the attractive and repulsive
-potentials across agents. This would allow us to provide a guarantee of inter-agent collision
-avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
-mention that they are already looking into this problem and have proposed a similar manner of
-tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
-they publish?
-
-\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
-By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
-number of their nearest neighbours. However, this may not always be the case. It will often be that
-in different environmental conditions, the observation or communication capabilities of the robots
-may increase or decrease. To better accomodate for this fact, I propose the extension of the model
-with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
-'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
-success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
-way into swarm dynamics. It will, however, become particularly important in cases where we can no
-longer take the consistency of agent communication for granted. 
-\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
-not seem like the connection of MJD and swarm dynamics has been made yet.
-\end{itemize}
-
-\section{Multi Agent Reinforcement Learning}
-
-The ideas I have down here are a little more sparsely populated, but further reading may provide
-some insights into potential directions.
-
-\begin{itemize}
-	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
-	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
-	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
-	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
-	required that we determine a safe manner in which MARL agents may explore without leading to
-	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
-	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
-	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
-	independent learners who do not consider the effect that they have on the other agent(s). The
-	particular extension that I propose is to consider the coupled effect between agents as part of
-	the determination of a safe set for exploration.
-
-	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
-	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
-	problems. Although it makes strong assumptions about the nature of the system, in practice it
-	has shown strong results. Particular examples of this are found in 
-	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
-	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
-	systems by considering sub-groups within the population. Each of these may be updated
-	individually. It would be interesting to examine how this might increase the complexity, and
-	also the generalisability of the mean-field method.
-	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
-	part but the potential directions are largely summarised in Section 2.3.1.
-\end{itemize}
-
-\bibliographystyle{IEEEtran}
-
-\bibliography{IEEEfull,references}
+\TODO{In the above, look specifically at the assumptions made within the papers. In the multi-agent
+case, the biggest assumption is that of independent learning. Perhaps consider how advances in
+coupled dynamical systems may be used to consider learning agents whose actions affect one another.}
 

### 2020-01-02 Literature Review/Literature Review - Revised/sections/Proposals.tex
Added Revised Literature Review

\documentclass[../sample.tex]{subfiles}

\begin{document}

\section{Considering Intelligence in Swarm Dynamics}

Most of the diffusion models, as mentioned in ‘Swarms’, do not take into consideration the
interactions between agents, since it adds a large degree of complexity to the model. However, it
would be important from a safety perspective to take these into account by looking at the attractive
and repulsive potentials across agents. This would allow us to provide a guarantee of inter-agent
collision avoidance whilst maintaining the progression of the swarm towards desired tasks. As
mentioned in ‘Swarms’, advances have been made towards considering the pairwise interactions between
swarm agents \cite{Bellomo2017}. Importantly, this addition presents the first step towards
considering the intelligence of the individual within the swarm.

By expanding the control perspective of stochastic swarms, predictive control methodologies can be
developed, similar to that of \cite{Borzi2015} which allow swarms to produce more complex phenomena
such as constraint satisfaction. As an example of where this might be important, consider the
problem of swarm systems in urban search and rescue, where one swarm sub-group is required to carry
a victim away from the scene, whilst another is required to search the area. This can be viewed as
from a control perspective where it is required that the latter group’s macroscopic model ensures
that agents do not enter within a safe region of the former group.

Stochasticity can then be considered from a hybrid perspective through JMLS (see Hybrid Control),
allowing the control laws to take into account agent and communication failures.
\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
not seem like the connection of MJD and swarm dynamics has been made yet.

Finally, it may be appropriate to consider stochastic control of heterogenous swarms to allow for a
‘marriage’ between swarm dynamics and game dynamics. This presents the possibility for swarms
sub-groups to adapt to each other’s behaviour through repeatedly play and perhaps display elements
of cooperative (or non-cooperative) behaviour, all while maintaining the required properties of
stability and controllability.

\section{Stochastic Predictive Control for Decentralised Hybrid Systems}

The purpose of this method is to leverage the ideas presented in \cite{Foerster} and
\cite{Heirung2019}. Here, agents must maintain (and perhaps learn) a model of the other agents
within the system. This model provides some representation of the trajectories that the other agents
will carry out or an understanding of their future actions. Using their own system models in tandem
with these belief models, agents must then determine their trajectory. The challenge here would be
proving the stability and controllability of the system whilst maintaining minimal communication
requirements. However, it would appear to be a feasible area of exploration.

This system can then be expanded by considering the case of stochastic hybrid systems. This draws on
the ideas presented in ‘Hybrid Control’ where we argue that agents in the system may be subject to
stochastic failures. It is, therefore, required that we develop control methodologies which are
robust to these switching dynamics to ensure their safe operation.

Similarly, it would be important to consider the learning aspect of these systems. The method so far
assumes that each agent knows all possible modes of operation of other agents and their transition
probability. However, this is unlikely to be the case. As such, it would be important to consider
the ability of agents to learn these models through iterative interaction and learning. This may
improve the robustness and optimality of the system, whilst maintaining its desired properties.

On a similar topic of learning, it would be vital, from a failure perspective, to consider fault
detection in a decentralised hybrid system. The above considers learning the system model of other
agents who have undergone a faiure. However, it is equally interesting to consider learning 
\textit{that} they have failed in the first place. The results suggested in 'Swarms' may be
applicable here, in an effort to maintain the decentralisation of the system.

Finally, these methods could be extended towards settings where the resultant behaviour is not best
described by a Nash Equilibrium. The control theory literature, thus far, has shown a strong
assumption that the system will always converge to a Nash Equilibrium. However, in games of repeated
play, the resultant dynamics of the game may be best described through cyclic or recurrent behaviour
\cite{Boone2019FromTheory}. Taking this into consideration would allow distributed control to be applied in a
wider array of settings, particularly in those where agent interests are conflicting with one
another.

\section{Stable Exploration in Multi Agent Reinforcement Learning}

This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and an
important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent systems
lead to stochastic behaviour resulting sometimes in undesired effects'. In particular, most RL
methods require some trade-off between exploration and exploitation. It is, therefore, required that
we determine a safe manner in which MARL agents may explore without leading to unstable behaviour.
This would require extending the work of \cite{Berkenkamp2017} and/or
\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that
\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
independent learners who do not consider the effect that they have on the other agent(s). The
particular extension that I propose is to consider the coupled effect between agents as part of the
determination of a safe set for exploration.

\end{document}

### 2020-01-06 Literature Review/Literature Review - Revised/.history/sections/GameTheory_20200106140400.tex
Updated Game Dynamics

--- 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
@@
 
-\maketitle
+Game Theory has a rich history when considering an understanding of multi-agent systems. These begin
+in economics but have found a strong application in computation due to the rising need for
+distributed systems. Game Theory, therefore, branches across all of the categories in this section
+(although its synergy with swarms is requires significant development) since Dec-POMDP and MARL
+methods have both used game theory to support their frameworks. In fact, Dec-POMDP is a subset of
+Partially Observed Stochastic Games (POSG), in which all agents use the same payoff.
 
-\tableofcontents
+\section{Market Based Methods}
 
-\chapter*{Introduction}
+Garapati et al. \cite{Garapati2018AMissions} define a market based method as the setting where
+agents "follow their own interests and establish the mechanism of a market for distributing the
+tasks". Auctioning is the most widely used sub-field of market approaches and so I will use them
+interchangeably.
 
-The areas of interest regarding Multi Agent Systems fall into two
-distinct categories (which have some slight overlap). The first is
-denoted as 'Decision Making', though the terms 'Planning' and
-'Distributed Control' may sometimes be used as substitutes. It is
-important to note that, in my case, I do not include Planning
-Formalisation techniques such as PDDL. Instead, I focus on the
-particular methods which involve interaction in the world. The second,
-I will refer to as 'Multi Agent Dynamics', though sometimes I will
-refer to this as 'Stability Analysis'.
+Whilst there are different variants to auctioning, the general procedure is that an auctioneer who
+has knowledge of a task (or multiple tasks) will set up an auction for said task. Agents can then
+make bids on these tasks and, once the auction is complete, the highest bid will win the task. In
+the specific application to robotics, a robot's bid will often reflect the costs, suitability or
+utility their undertaking the task \cite{BernardineDias2006Market-basedAnalysis}. This immediately
+highlights a few points. The first is that the method is not too heavily reliant upon a single
+processor to determine some joint policy. Tasks are allocated on a case-by-case basis and the
+utilities are calculated by the agent themselves. The only centralised process is the auctioneer's
+assessment of the winner which then relays this information back to them. The downside of this is
+that the system is heavily reliant upon strong communication channels, without which tasks may not
+be assigned, incorrect utilities may be communicated and, in general, sub-optimal solutions reached.
+ Furthermore, the requirement that the agents themselves determine the cost of their actions assumes
+that they have the computational capability to do so. Furthermore, the bids placed by each agent
+need to be a strong representation of their capability to perform a task which may be hard to
+estimate without expert knowledge. However, market based methods are well suited to explanation
+through argumentation (similar to \cite{Jung2001DistributedArgumentation}.
 
-\subsection*{Scope}
+With well chosen payoffs, market based approaches work extremely well. For instance, in
+\cite{Dias2000ASystem}, the authors show that a free market approach (where agents try to maximise
+their own profits) can lead to a strong collaborative effort across teams. Similarly, in
+\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the auctioning scheme presented in
+\cite{Gerkey2002Sold:Coordination} towards a robot construction team. However, it is important to
+note that these are both passive settings; tasks were assigned before the team were in the field
+and, in the case of \cite{Gerkey2002Sold:Coordination}, the system would repeat the bidding process
+if a robot failed. While both show strong performance, it cannot be said that either would be
+applicable in dangerous environments in which dynamic reassignment must happen within strict time
+constraints. Stancliff et al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
+method to planning would be to account for failures a priori, a philosophy which is exemplified in
+\cite{Chen2010ACollaboration} who consider the robot's reliability and relevance to a task as well
+as 'history relevance' which considers the relationship between pairs of robots with the aim of
+producing more effective teams.
 
-Both of the aforementioned topics have been applied to all variants of
-multi agent systems and have sufficient room for further
-exploration. The typical variants of multi agent systems that I will
-consider are
+There has also been some interesting work in probabilistic verification of market based approaches. 
+Most notable to me is \cite{Pallottino2007ProbabilisticAvoidance} which considers the case of
+conflict avoidance. Though their method focuses on collision avoidance, it highlights the need for
+verification of conflict resolution and goal achievement in market based approaches with different
+payoff structures. Sirigineedi et al. \cite{Sirigineedi2010DecentralisedApproach} make a step in
+this direction by considering the verification of cooperative surveillance along a route network. 
+From my understanding, this means that they were able to verify that their agents were able to
+traverse along the network without interference.
 
-\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
-Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
-Coded \end{itemize}
+\section{Stochastic Games}
 
-In the above, 'Game Theoretic Approaches' cover a wide spectrum,
-including zero-sum (minimax) games, bayesian games, and many more. The
-final category, 'Hard Coded', refers to any approach which does not
-fit neatly into any of these categories. The name is chosen since they
-often refer to methods which revolve around a series of if-else
-statements.
+\TODO{For the love of God do this already}
 
-\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}
+\section{Game Theoretic Control}
 
-I will first consider Decision Making as this is most closely related
-to the research proposal, before I consider Multi Agent Dynamics,
-which has strong implications for Safe and Trusted Multi Agent
-Systems.
+Game theory can often be applied to problems of control theory (particularly where there are
+multiple agents) to develop robust controllers which guarantee properties of stability and
+constraint satisfaction.
 
-\subsection*{Objectives}
-
-The aim of the following sections is not to provide an exhaustive list of all work done in the
-aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
-identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
-these directions, we may be able to narrow down the remaining literature review and hone in on
-particular problems and, in fact, we may find that we address multiple of these over the next four
-years (while we, of course add more). As such, the end of each chapter will provide a list of
-research directions which I have identified from the preceding review.
-
-\chapter{Decision Making}
-
-Decision making refers to the generalised problem of considering how a multi-agent system should
-interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
-are aligned (cooperative) or in conflict with one another (competitive).
-
-The following sections will provide an overview of the literature aimed towards coordinating such
-systems as followed by interesting sub-fields in each approach which present avenues for research
-related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
-as the review progresses.
-
-\section{Swarms}
-
-Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
-through a formation using a series of simple local interactions with their neighbours
-\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
-may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
-ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
-performance in reaching globally optimal solutions in search-based tasks. The advantage of many
-swarm algorithms is that they are based on local interactions and so are incredibly scalable
-\cite{Rizk2018}.
-
-The reduction of the complexity in interactions between agents also allows for the robots to perform
-other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
-considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
-manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
-whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
-sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
-readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
-divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
-
-Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
-central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
-adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
-made regarding the homogeneity of individual agents and the simplicity of their local interactions
-result in significant limitations placed on the complexity of the tasks that swarm systems can
-accomplish.
-
-\fr{What are the standard techniques used in swarms?
-that is, how are swarms and their interactions modelled?
-how are solutions computed?
-what kind of algorithms are used in this area?
-most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
-
-\subsection{Co-evolution and Self-Healing}
-
-Recently, there has been an increased interest in introducing
-heterogeneity into the swarm systems to improve their real world
-applicability. An example of this which have been shown strong real
-world success can be found in
-\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
-swarm teams, referred to as 'foot bots' and 'eye bots' who work in
-unison to explore an environment and solve a navigation task.
-
-This area of research is sparsely populated and warrants further
-exploration. This is since the use of co-evolutionary teams can
-improve the robustness of the swarm optimisation. This is since it
-will be possible for a team to automatically determine when robots in
-the other team are not exhibiting expected behaviour and ensure that
-the other team self corrects. This process is referred to as
-'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
-user to define the goals of a swarm system. From this, a 'trust'
-metric can be defined which measures the deviation of each agent from
-the expected behaviour. The self-healing process occurs by limiting
-communication of all agents with 'untrusted' agents and encouraging
-communication with 'trusted' agents. The unison of self-healing with
-co-evolution may present the opportunity for heterogenous swarms to
-maintain their evolutionary stability, even in the face of
-environmental disturbances.
-
-\subsection{Fault Detection}
-
-The above sections have considered the fact that swarm systems are
-robust to losses in the group.  However, any MAS system must first be
-able to recognise that an agent has undergone some failure.
-
-To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
-a robust fault detection approach in which the swarm itself, in a
-decentralised manner, is capable of assessing deviation from 'normal'
-behaviour, even when the behaviour of the swarm itself is altered
-(perhaps by a remote operator). The authors achieve this by requiring
-that the agents themselves sense and characterise their own
-behaviour. This characterisation is formulated as a binary feature
-vector which is then communicated to the agent's neighbours. These
-neighbours will reach a consensus over whether the agent should be
-treated as faulty based on their collective behaviour. The results
-presented in \cite{Tarapore2019FaultDetection} show extremely
-promising results and suggest that their method is, in fact, able to
-determine faults with high accuracy in the presence of various fault
-types (including sensor and actuator failures), although poor
-performance is seen in actuation failures in some instances. It should
-be noted that this method requires that each robot transmit their
-feature vector to the nearest neighbours. In environments where
-communication may be severely limited, this may present further
-errors. Furthermore, it is unlikely that, when a robot is damaged,
-only one of its components will be affected. Therefore, it is
-important to determine the effect on performance in the face of
-multiple agent failures and in communication losses. This exploration
-may open the possibility of improving the state of the art in terms of
-failure detection in swarm systems. (Of course, this conclusion is
-based off two papers so further review is required).
-
-\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas.
-As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another.
-However, this depends essentially on the different modelling assumptions.}
-
-\subsection{Verification}
-
-Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
-require further reading
-
-\subsection{Directions}
-
-From the above consideration of swarms, the following research
-directions have been identified which, in my view, concern themselves
-with STAI.
-
-\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
-towards ensuring that emergent phenomenon and swarm behaviour are as
-expected by the user.
-
-\item Fault Detection in limited communication:
-Considering the ability of a swarm to, in a decentralised approach,
-consider which robots in the team have failed, even in cases of no
-communication or multiple failures.
-
-\fr{The second item looks promising, possibly in combinations with
-  techniques from Game Theory and MARL. Let's keep Fault R\&D in
-  mind.}
-
-\end{itemize}
-
-\section{Dec-POMDPs}
-
-The use of POMDPs in multi-agent settings is formalised as
-decentralised POMDP (Dec-POMDP) which aims for a team of agents to
-maximise a common utility. However, it has been found that determining
-the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
-so is intractable for all but toy problems. A number of methods have
-been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
-of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
-as brute force) are intractable for all but toy problems.
-
-Approximate solutions to Dec-POMDP have been proposed, perhaps most
-notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
-Amato et al. Here, macro actions (actions which extend over multiple
-time steps) are used, as opposed to low-level actions which are
-re-evaluated at each time step. This allows an exact solution to be
-found as it does not need to be evaluated at each time step. This
-method assumes that, once macro-actions are distributed, the policies
-(sequence of state-action pairs) are known. Since this is not the
-case, Amato also proposes the use of a Dec-POSMDP
-\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
-'Semi-Markov Decision Process, in which a high level model is defined
-without the underlying Dec-POMDP's actions and observations.
-
-However, this is largely applicable in passive settings where common
-payoffs can be determined by an offline planner. They also require a
-significant amount of data with which to allow the system to learn the
-underlying models and payoff structures. This limits the applicability
-of the system when communication is limited and the system is
-presented with environments that it has not seen before.  Recent work
-in MDPs \cite{Klima2019RobustDomains} has considered learning in the
-face of Significant Rare Events (SREs) which the system has not yet
-observed. Currently, it is required that a model of such SREs is known
-and so it would be interesting to consider the application of
-Dec-POMDPs in situations where the SRE model is incomplete or
-erroneous and assess the robustness of the Dec-POMDP framework against
-such events.
-
-\subsection{Directions}
-
-The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
-developed by Amato as he seems to largely dominate the field. Based on this initial review of the
-area, a potential direction for research is
-
-\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
-  SREs which have a limited or erroneous model.
-
-\item Agent Failures: The Dec-POMDP model uses a
-centralised planner which acts offline. It therefore assumes that the agents will be able to carry
-out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
-planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
-
-\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
-Also, it might be interesting to understand why swarms scale up better
-than MDPs, and in general why the former have better computational
-properties than the latter: is it a matter of
-``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
-some other swarm-like restriction? It might be interesting to combine
-the two approaches in order to get the ``best of both worlds''.}
-
-\section{Game Theoretic Approaches}
-
-Game theoretic models are generally the go-to method for understanding
-multi-agent systems. As such they fit into all of the categories in
-this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
-methods have both used game theory to support their frameworks. In
-fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
-(POSG), in which all agents use the same payoff. \fr{That's an
-  interesting remark. It might be worth to check whether we can
-  leverage on this and similar observations.} Game theory can,
-therefore, be used in an applied capacity to direct task allocation
-across heterogenous teams.
-
-\subsection{Market Based Methods}
-
-Garapati et al. \cite{Garapati2018AMissions} define a market based
-method as the setting where agents "follow their own interests and
-establish the mechanism of a market for distributing the
-tasks". Auctioning is the most widely used sub-field of market
-approaches and so I will use them interchangeably.
-
-Whilst there are different variants to autioning, the general
-procedure is that an auctioneer who has knowledge of a task (or
-multiple tasks) will set up an auction for said task. Agents can then
-make bids on these tasks and, once the auction is complete, the
-highest bid will win the task. In the specific application to
-robotics, a robot's bid will often reflect the costs, suitability or
-utility their undertaking the task
-\cite{BernardineDias2006Market-basedAnalysis}. This immediately
-highlights a few points. The first is that the method is not too
-heavily reliant upon a single processor to determine some joint
-policy. Tasks are allocated on a case-by-case basis and the utilities
-are calculated by the agent themselves. The only centralised process
-is the auctioneer's assessment of the winner which then relays this
-information back to them. The downside of this is that the system is
-heavily reliant upon strong communication channels, without which
-tasks may not be assigned, incorrect utilities may be communicated
-and, in general, sub-optimal solutions reached.  Furthermore, the
-requirement that the agents themselves determine the cost of their
-actions assumes that they have the computational capability to do
-so. Furthermore, the bids placed by each agent need to be a strong
-representation of their capability to perform a task which may be hard
-to estimate without expert knowledge. However, market based methods
-are well suited to explanation through argumentation (similar to
-\cite{Jung2001DistributedArgumentation}.
-
-\fr{The game-theoretic approaches described above might suffer from the
-  same drawbacks identified above for fault detection, namely reliance
-  on communication and on a single central authority. I'd rather
-  favour distributed approaches. Also, market-based mechanisms and
-  negotiation might lead us to a completely different direction.}
-
-With well chosen payoffs, market based approaches work extremely
-well. For instance, in \cite{Dias2000ASystem}, the authors show that a
-free market approach (where agents try to maximise their own profits)
-can lead to a strong collaborative effort across teams. Similarly, in
-\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
-auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
-towards a robot construction team. However, it is important to note
-that these are both passive settings; tasks were assigned before the
-team were in the field and, in the case of
-\cite{Gerkey2002Sold:Coordination}, the system would repeat the
-bidding process if a robot failed. While both show strong performance,
-it cannot be said that either would be applicable in dangerous
-environments in which dynamic reassignment must happen within strict
-time constraints. Stancliff et
-al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
-method to planning would be to account for failures a priori, a
-philosophy which is exemplified in \cite{Chen2010ACollaboration} who
-consider the robot's reliability and relevance to a task as well as
-'history relevance' which considers the relationship between pairs of
-robots with the aim of producing more effective teams.
-
-There has also been some interesting work in probabilistic
-verification of market based approaches.  Most notable to me is
-\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
-of conflict avoidance. Though their method focuses on collision
-avoidance, it highlights the need for verification of conflict
-resolution and goal achievement in market based approaches with
-different payoff structures. Sirigineedi et
-al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
-direction by considering the verification of cooperative surveillance
-along a route network.  From my understanding, this means that they
-were able to verify that their agents were able to traverse along the
-network without interference. However, this, as always, requires
-further analysis to truly understand.
-
-\subsection{Directions}
-
-The particular considerations which have jumped out to me from the above analysis are as follows:
-
-\begin{itemize} 
-	\item Verification of goal achievement under different payoffs: can we ensure that
-	self-interested agents will, in fact, show cooperative emergent properties? A similar question
-	arises in terms of valuations (how much cost each agent incurs). 
-	\item A priori consideration of
-	reliability: Can we learn and take into account the fact that robots may fail throughout the
-	progress of a mission when we assign tasks? 
-\end{itemize}
-
-\subsection*{Stochastic Games}
-
-\section{Hard Coded}
-
-\section{MARL}
-
-Reinforcement learning extends the Markov Decision Process problem by
-considering the case where the payoff model is not known. This, of
-course, is the case for most real world environments. As such, MARL
-algorithms can perhaps be considered to be more applicable than
-Dec-POMDP models.
-\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}
-
-Fortunately, MARL has picked up a lot of traction in
-research recently, with a large body dedicated towards solving the
-many problems it presents.
-
-The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
-single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
-in the Multi Agent setting since other agents in the environment will be learning concurrently. This
-learning will be based on their own history of interactions which extend beyond the previous state.
-As such, we must now consider that the policy for any one agent will depend on the policy of all
-other agents. As such, a big concern in this area is regarding convergence guarantees and the
-stability of the learner system. Approaches to this will be discussed in the next chapter.
-
-\subsection*{Agent Modelling}
-
-Returning to the problem of non-stationarity, solutions have been presented in which the agent
-models the learning of other agents. A noteworthy example of this is found in
-\cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other
-agents' learning and optimises with respect to this expected return. They show that this leads to
-stable learning and can even lead to emergent cooperation from competition. However, the method
-requires that both agents have exact knowledge of the others' value functions in order to perform
-the one step lookahead. Furthermore, it has only been considered for the case of a two agent
-adversarial game and so the scalability of the system to multiple agents is not yet understood.
-Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect
-the actions and observations of all agents and allows it to model the joint policy of teammates.
-This is shown to generate cooperative behaviour across four agents and so is more applicable to real
-world settings. However, its disadvantage over the method presented in
-\cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this
-requires the presence of an agent (perhaps a laptop) which is able to handle the computational load
-of determining a joint policy across all agents and must then communicate the Q-values of all agents
-back to them. This is both a taxing both in terms of computation and time.
-
-Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by
-tasking a CNN with determining the policy features of other agents and then embedding these as
-features in its own DQN. This shows strong performance in settings where other agents dynamically
-change their policies. The concerns with this, however, are that, as the number of agents in the
-field increase, the CNN in each agent must perform another approximation. This places strong
-requirements on the performance of the CNN since errors in estimation will accumulate as the number
-of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are
-added.
-
-Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent
-modelling is an important one to ensure stable learning and to understand the evolution of the
-system. It also presents a strong challenge and is open to exploration. To put it in context the
-methods described in this section are all from 2018-19, so its all very new.
-
-\subsection{Directions}
-
-I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
-However, on initial assessment I put forward
-
-\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
-the stability of the learning process. However, the particular problem I suggest is to consider the
-modelling in a decentralised manner and with the consideration of evolving numbers of agents in
-teams. \end{itemize}
-
-\fr{This looks like an interesting, non-trivial problem: how can we
-  represent the other agents within the agent model itself, in order
-  to improve learning in MARL? Shall we have a closer look at this problem?}
-
-\section{MARL Approaches} \label{sec::MARL Approaches}
-
-The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
-policy may be the concatenation of all the individual policy or it may just be options for each
-agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
-and so, in this section, I will try to consider the broad spectrum of methods which attempt to
-achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
-all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
-to help guide this review. I am not referencing the individual papers immediately, though the
-references can be found in the book.
-
-\subsubsection*{Learning in Two Player Matrix Games}
-
-The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
-method of linear programming (in which constraints are linear). This will be important in
-considering more current methods. A similar consideration is given to the infinitesimal gradient
-ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
-infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
-not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
-particular problem in games where there are multiple Nash equilibria. However, in practice it is
-difficult to choose a convergence rate of the step size and, without an appropriate choice the
-strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
-to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
-payoff matrix (which is not so much of a problem for model based methods) and the opponent's
-strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
-method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
-(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
-oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
-players with minimal oscillation.
-
-The above methods are all centralised techniques, in which a controller determines the optimal joint
-policy for both agents. However, in real scenarios it is often preferable that each agent learns
-their own strategy, a task which must be completed without information of the other agent's
-strategy. The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which
-guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$)
-which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor
-algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$
-lagging anchor algorithm which can converge to both pure and mixed NEs.
-
-\subsubsection*{Learning in Multiplayer Stochastic Games}
-
-Stochastic Games (or Markov Games) form a basis for MARL
-settings. However, in this case the agents must learn about the
-equilibrium strategies by playing the game, which means they do not
-have a priori knowledge of the reward or transition functions. Schwarz
-considers two properties which should be used for evaluating MARL
-algorithm: rationality and convergence. The latter simply states that
-the method should converge to some equilibrium whereas the former
-suggests that the method should learn the best response to stationary
-opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
-shortly. Schwarz then presents a review of MARL methods (as of
-September 2014)
-
-\fr{All the above looks extremely interesting. I would explore the
-  above for decentralized and partially observable settings. What
-  results are mentioned \cite{SchwartzMulti-agentApproach} under such
-  assumptions?}
-
-\subsection*{Dec-POMDP and MARL}
-
-As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
-methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
-\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
-is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
-Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
-however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
-Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
-order to make this work, we would also need to consider how to select the feature space of sub-trees
-and how to collect this information. \end{itemize}
-
-\chapter{Multi Agent Control}
-
-\section{Stochastic and Robust Model Predictive Control}
-
-The idea of Stochastic Control is best described in the research statement of the Control and
-Analysis of Stochastic Systems (CASS) group at Penn State:
-
-\begin{displayquote}
-	"...to model, predict and control uncertain engineering systems where the interplay between
-	dynamics and uncertainty (stochasticity) is important."
-\end{displayquote}
-
-When operating in the real world, systems are subject to uncertainty and environment perturbations.
-Despite this, for their safe operation, they must provide certain guarantees (such as collision
-avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
-system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
-control have found their way into controlling power distribution, chemical processes and (of course)
-robotics.
-
-\subsection*{Model Predictive Control}
-
-Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
-of operating real-world agents safely in the face of environmental disturbances. The overarching
-idea begins with the assumpion that we have a model of the environment. As an example, in
-the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
-affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
-environment state for a few time steps ahead, and generate a policy for this horizon. The agent
-performs the immediate action generated by the policy, and then we repeat the process, after taking
-measurements of the environment to determine the error in the system. Throughout this process, the
-controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
-example, a likely constraint would be that the controller will never result in the car going on the
-pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
-the requirement of stability that the system is required to remain safe throughout operation. To
-that end, mathematical proofs of these properties are provided in the literature ensuring that we
-can trust in the system's performance.
-
-Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
-knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
-computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
-provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
-of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
-we no longer assume the exact nature of the environment and can guard against worst case scenarios.
-This is extremely effective in closed environments or for simple tasks, but falters in more complex
-environments.
-
-Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
-perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
-define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
-optimality is defined in terms of the minimisation of the expectation of a probabilistic
-cost function. This formulation brings about controllers which are more applicable and robust when
-deployed. However, the field is in its infancy and presents a number of theoretical challenges.
-These are best described by Mesbah in \cite{Mesbah2016}
-
-\begin{itemize}
-	\item The arbitrary form of the feedback control laws
-	\item The non-convexity and intractability of the chance constraints
-	\item The complexity of the uncertainty propagations
-	\item Establishing stability of the control problem
-\end{itemize}
-
-Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
-some of
-these problems, most notably the intractability of the chance contraints. For instance, in 
-\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
-time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
-suited to non-linear systems, which itself is an open problem in the MPC sphere.
-
-The research in using Distributed Predictive Control is quite sparse as compared with, for example,
-single agent predictive control. The added complexity of stochastic environments has meant that this
-area of research is still very open for looking into. With this said, the main works that I have
-found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
-\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
-Usually these are some combination of the following:
-
-\begin{itemize}
-	\item The agents act in a deterministic environment. This suggests that predicted futures will
-	be close enough to the ground truth.
-	\item The agents are uncoupled from one another. This is a strong assumption to make and
-	essentially allows us to consider the agents as completely independent of one another. 
-	\item The agents can easily communicate with one another. This allows for longer pieces of
-	communication (most often predicted trajectories) to be communicated between agents.
-\end{itemize}
-
-\subsection{Directions}
-
-The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
-and applied problems. Control in autonomous systems is also one of the more applicable problems
-related to STAI since it requires that we place mathematical guarantees on the performance and
-stability of the system as well as guarantees on the satisfaction of constraints. This is, of
-course, an ever present problem in autonomous systems which operate in the real world. I begin by
-listing the more theoretical areas for exploration in MPC before then considering their application
-domains.
-
-\begin{itemize}
-	\item Significant exploration is required with regards to the optimisation problem. Especially
-	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
-	approximate methods (such as sampling) should be explored and their effect on the system
-	guarantees presented.
-	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
-	determine the uncertainty in the environment model in order to generate control laws. We should
-	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
-	particle filters, against modern deep learning methods for propagation.
-	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
-	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
-	together whilst maintaining a specified distance from one another). Consider, then, the case
-	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
-	and hence requires adaptation. It would again be interesting to consider the use of neural
-	networks in this manner. However, specifically we should consider whether the use of a function
-	approximator in the form of an NN might result in a violation of the constraints.
-	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
-	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
-	effect that each agent has on the other, the effect of the environment on all agents, estimating the
-	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
-	here that I believe game-theoretic notions (especially differential games) will come to our
-	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
-	in the case of multiple disturbances, but I will elaborate on this in the applied problems
-	section.
-\end{itemize}
-
-the following presents a consideration of the applied end of MPC problems. I have tried to focus on
-the domain independent suggestions, since the domain specific ones are virtually limitless.
-
-\begin{itemize}
-	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
-	interact with each other. In addition, we may consider that there are multiple known disturbances
-	acting on the system. This, at first seems like an impossible problem to solve due to the many
-	interactions between all elements of the system. However, we can consider this as a game
-	theoretic problem in which the components and the disturbances are players. The relatively new
-	class of 'mean-field games' is a method which allows the many body problem to be approximated as
-	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
-	predictive control' remain, this may prove to be a valuable area of applied research.
-	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
-	which emerge into more complex results. It would be interesting to consider the application of
-	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
-	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
-	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
-	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
-	adaptive stochastic model would be interesting to examine here to remain robust to agent
-	failures in the group.
-	\item Modular Robotics?
-\end{itemize}
-
-\section*{Multi Agent Dynamics}
-
-Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
-Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
-well as to understand the trajectory of learning. Typically, this looks at considering whether or
-not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
-problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
-applicability into real world settings requires the study of stable equilbrium points;
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world
-environments.
-
-\section{Stability of Learning Agents}
-
-Stability may be looked at from the view point of two perspectives. The first is from an
-optimisation point of view. This considers the dynamics of the learning model, allowing us to better
-choose our parameters and design our models so that they may converge to a stable result. The second
-is from the view point of the state-action space of a learnt model. This allows us to determine,
-before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This
-knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability
-analysis allows us to build multi agent systems which will learn and act in the way that we expect
-them to.
-
-In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of
-generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is
-one in which the loss function is twice differentiable. Using this formulation, they are able to
-analyse the system from new perspectives by considering the current state-of-the-art understanding
-of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical
-exercise, they go on to show that the insights gained allow them to develop a new multi-objective
-optimisation technique for GANs which shows stronger convergence properties, most notably of which
-is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the
-two players' loss functions.
-
-Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement
-learning agent as a non-linear, time varying feedback controller. Using this notion, they then
-consider the bounded-input-bounded-output stability of the system. They do this by analysing the
-ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains
-finite then the system may be considered to be stable. They then apply these considerations on
-real-world applications including multi-agent flight formation and obtain stability certificates
-(essentially confirming that the system will remain stable under certain conditions) for the learned
-controller.
-
-Berkenkamp et al. \cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different
-definition of stability. Specifically, they look at stability from the point of view of Lyapunov
-functions. A system is said to be stable if the applying the policy will result in stricly lower
-evaluations of the function. In other words, a system is stable if its corresponding Lyapunov
-function is decreasing towards a minimum point. The authors use this idea to define a 'region of
-attraction' in which the system is stable in the sense of Lyapunov. The goal of Safe Lyapunov
-Learning, a method which they develop from these insights, is to learn a policy without leaving this
-region of attraction. They do this by taking measurements within the set and using this to learn
-about the system dynamics, thereby increasing the safe set. With this, we now have a guarantee that
-policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and
-exploration.
-
-As we can see from the discussion thus far, there are many definitions and perpectives of stability,
-each lending to a new understanding of learning systems. To add another to the mix, Milchtaich in
-\cite{Milchtaich2007StaticGames}, presents a notion of static stability. This means that it is based
-solely on the incentives of the players and does not require a consideration of the dynamics of the
-system. Milchtaich's definition of a stable system is one in which, when perturbed, it is more
-beneficial for an agent to move back towards the equilibrium than it is for them to move away. This
-is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows
-that it is applicable to all strategic games, within certain assumptions (finite set of player and
-continuous strategy space) and considers probabilistic perturbations from the original state. This
-is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy
-spaces) since these systems require random exploration of the strategy space and the dynamics are
-not known a priori. However, the lack of dynamics means that we do not consider the evolution of
-learning.
-
-\section{Learning Stable Agents}
-
-The above discussion has considered how notions of stability and control are important to
-Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
-specifically, game theory, can be used to develop controllers which drive systems to stable states.
 This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
@@
 systems in a distributed manner. Here, agents only consider their own payoff structure and have
- limited communication with one another. The author shows that the an approximate equilibrium can be
+limited communication with one another. The author shows that an approximate equilibrium can be
 found using algebraic methods and illustrate the capabilities of the technique using a collision
@@
 induced across the players (a notion was suggested in the research proposal) and mean-field games,
- which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
+which is discussed in 'MARL'. The importance of the linear-quadratic
 differential game is the stability of the solution; solutions for the Nash equilibria are
@@
 
-\subsection{Directions}
-
-I will briefly summarise the research directions which I develop in this section, to save ourselves
-some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}
-
-The above discussion has illustrated a few points. The first, and perhaps most important, is that
-stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
-that learning agents, especially in real world environments, are subject to uncertainty and
-perturbations as well as epsilon-random exploration. As such, it is important that the system is
-able to return to a stable state after such perturbations. This leads to the need to develop
-learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
-equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
-equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
-Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
-to stable fixed points.
-
-The second point is that the notion of stability has multiple definitions. Each one is appropriate
-in different conditions and, as such, it is important to explore stability from various viewpoints
-to consider how to best understand the evolution of a learning system.
-
-Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
-not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
-question and is well worth consideration. This would help guide the choice of loss functions and
-strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
-dramatic impact on the safety certification of MARL systems.
-
-The problem of finding stable solutions through multi agent dynamics also opens the door for a large
-degree of application domains which are currently quite sparse. I would recommend looking at the
-contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
-of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
-control and economic modelling. My particular interest, as always, lies within robotic control
-problems. This appears to be the most direct and relevant application of stable MAS systems. An
-example of this might be the problem of Cooperative Moving Path Following Control considered by
-\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
-pre-defined path without interfering with one another. It is clear then that each player's control
-is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
-determine control rules which lead to stable coordination across the team. Similarly, we can model
-consider modelling a controller and an adversarial environment as a zero-sum game as examined in
-\cite{Marden2018AnnualControl}.
-
-Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
-of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
-differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
-the differential game problem from the point of view of different information structures. In
-real-world systems, it is unlikely that all agents will have access to the information of other
-agent' cost functions and current positions. It could, however, be interesting to explore the use of
-localisation methods to determine and track this information through observation (e.g. through
-Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
-considers the case where system dynamics are linear. A whole new set of problems arise in the more
-realistic case where we must consider the non-linearity of system dynamics. Such a consideration
-would also allow us to extend these technique to the more difficult (and important) problems in
-control.
-
-The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
-Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
-Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
-particularly relevant to this study. However, they will require some further analysis before I write
-about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
-entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
-document out.)
-
-\chapter{Research Directions}
-
-\section{Stochastic Model Predictive Control for Distributed Systems}
-
-The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
-that end, I propose the following techniques towards improving DSMPC.
-
-\begin{itemize}
-	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
-	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
-	distribution of the action that will likely be selected by $j$, effectively performing a
-	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
-	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
-	this may seem computationally expensive, its advantage lies in the fact that it requires little
-	communication across the agents. An immediate disadvantage of this is that, as the number of
-	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
-	not yet confident on the feasibility or the usefulness of this technique, but looking further
-	into the literature (which seems to add new things every day) may provide insights which could
-	help refine the technique. This method is, in many ways, similar to that presented in 
-	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
-	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
-	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
-	all systems to update at each time step.
-
-	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
-	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
-	public belief based on the observed actions of all agents. This joint belief will likely provide
-	some representation of the trajectories that each agent will carry out or an understanding of
-	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
-	will be chosen from a family of existing models using a recursive Bayesian update. The idea
-	would be for this update to be conditioned on the history of observations as is done in 
-	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
-	state and use this, in combination with their own system models to determine a feasible
-	trajectory. The challenge here would be proving the stability and controllability of the system
-	and that it requires communication with a central controller. However, it would appear to be a
-	feasible area of exploration.
-\end{itemize}
-
-\section{Stochastic Control of Swarms}
-
-Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
-when considering its application in stochastic environments. In particular, the ideas presented
-below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
-desired distribution.
-
-\begin{itemize}
-	\item Consideration of state constraints or boundary conditions (terms which I will use
-interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
-particular stochastic difference equation (the Ito equation). However, this does not account for any
-boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
-obstacle avoidance. However, in environments where there are human operators, or in general areas
-where we do not want swarms to enter, it is important to have a guarantee of constraint
-satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
-conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
-confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
-Furthermore, it may present an opportunity for us to consider the decentralised control of the
-agents which can ensure state constraint satisfaction. The resources which are most relevant to this
-study (and from which the ideas are derived) are
-\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
-
-\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
-the diffusion models, as mentioned above, do not take into consideration the interactions between
-agents, since it adds a large degree of complexity to the model. However, it would be important from
-a safety perspective to take these into account by looking at the attractive and repulsive
-potentials across agents. This would allow us to provide a guarantee of inter-agent collision
-avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
-mention that they are already looking into this problem and have proposed a similar manner of
-tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
-they publish?
-
-\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
-By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
-number of their nearest neighbours. However, this may not always be the case. It will often be that
-in different environmental conditions, the observation or communication capabilities of the robots
-may increase or decrease. To better accomodate for this fact, I propose the extension of the model
-with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
-'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
-success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
-way into swarm dynamics. It will, however, become particularly important in cases where we can no
-longer take the consistency of agent communication for granted. 
-\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
-not seem like the connection of MJD and swarm dynamics has been made yet.
-\end{itemize}
-
-\section{Multi Agent Reinforcement Learning}
-
-The ideas I have down here are a little more sparsely populated, but further reading may provide
-some insights into potential directions.
-
-\begin{itemize}
-	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
-	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
-	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
-	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
-	required that we determine a safe manner in which MARL agents may explore without leading to
-	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
-	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
-	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
-	independent learners who do not consider the effect that they have on the other agent(s). The
-	particular extension that I propose is to consider the coupled effect between agents as part of
-	the determination of a safe set for exploration.
-
-	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
-	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
-	problems. Although it makes strong assumptions about the nature of the system, in practice it
-	has shown strong results. Particular examples of this are found in 
-	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
-	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
-	systems by considering sub-groups within the population. Each of these may be updated
-	individually. It would be interesting to examine how this might increase the complexity, and
-	also the generalisability of the mean-field method.
-	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
-	part but the potential directions are largely summarised in Section 2.3.1.
-\end{itemize}
-
-\bibliographystyle{IEEEtran}
-
-\bibliography{IEEEfull,references}
-
 \end{document}

### 2020-01-06 Literature Review/Literature Review - Revised/.history/sections/MARL_20200106140400.tex
Updated Game Dynamics

--- 2020-01-02 Literature Review/Literature Review - Revised/sections/MARL.tex
@@
 
+\section{Game Dynamics}
+
+Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
+problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
+another. This model then serves to be able to predict the evolution of the system as well as to
+understand the trajectory of learning. Typically, this looks at considering whether or not the
+method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
+solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this applicability into
+real world settings requires the study of stable equilbrium points;
+\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
+are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of the environment since a stable
+equilibrium will always be returned to even after perturbations. This extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
+
+\TODO{Add in the papers from Mendeley which are useful to this part of the study}
+
 \section{Stable Learning}

### 2020-01-07 Literature Review/Literature Review - Revised/sections/MARL.tex
Added Proposal 7.3

@@
 
+\section{Learning Dynamics}
+
+Game Dynamics (which I often refer to as Multi Agent Dynamics or Game Dynamics) considers the
+problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
+another. This model then serves to be able to predict the evolution of the system as well as to
+understand the trajectory of learning. Typically, this looks at considering whether or not the
+method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
+solve \cite{ShohamMultiagentFoundations} for all but toy problems.
+\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
+are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of the environment since a stable
+equilibrium will always be returned to even after perturbations. This extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
+
+The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
+evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
+considers similar assumptions to that of MARL: agents are no longer required to be rational and play
+the game optimise their expected return through repeated play. Importantly, players have no
+knowledge of the others' payoffs \cite{Tuyls2006AnGames}. The first major breakthrough in this field
+is in \cite{Borgers1997} where Boergers and Sarin determine the relation between the replicator
+dynamics concept of EGT (a differential equation defining the evolution of the proportion of a
+subgroup in an evolving population) and the 'Cross' learning method for multi agent reinforcement
+learning. This idea is advanced in \cite{Tuyls2006AnGames} where Tuyls et al. determine  a similar
+relation for Q-Learning using Boltzmann probabilities as Q-values. The result was a dynamics
+equation which describes, for each action, the evolution of its selection probability which could
+even account for random exploration. There have since been a number of works which apply the same
+insight into different game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken
+into the following categories
+
+\begin{itemize}
+	\item Stateless games with discrete actions. Here, stateless refers to the idea that the game is
+	static and so the environment has no impact on the result. The aforementioned result 
+	\cite{Tuyls2006AnGames} fits into this category.
+	\item Stateless games with continuous actions. These consider more realistic MARL than the
+	previous category by replacing each agent's strategy vector with a probability density function 
+	(pdf) over a continuous action space.
+	\item Stateful games with discrete actions. This mostly considers stochastic games, where there
+	are multiple states with probabilistic (usually Markovian) transitions between them. However,
+	extensive form games, which considers more complex phenomena such as sequential moves and
+	imperfect information, are also briefly mentioned.
+	\item Stateful games with continuous actions. This is one of the more realistic assumptions
+	considered. However, the authors point out that this area is yet to see results, leaving it open
+	for possible research.
+\end{itemize}
+
+Though the above have seen success through experimental validation, most work is applied to bimatrix
+games (games of two to three players with finite action spaces). An example of this can be found in
+\cite{Hofbauer1996} in which Hofbauer shows that learning a zero-sum bimatrix game follows
+Hamiltonian dynamics and results in stable equilibria. Recent work has begun the consideration of
+improving the models towards more complex scenarios with larger agent populations. For instance,
+Bailey and Piliouras show in \cite{Bailey2019Multi-AgentSystem} that the results of
+\cite{Hofbauer1996} can be extended to the n-agent case, even with different network structures.
+They show that the result generalises to any zero-sum network game where agents use a
+Follow-The-Regularised-Leader learning approach. Another, more recent example of this is 
+\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
+Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
+its strategy based on the mean effect of the population. The result is a system of three equations
+which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
+presents an important first step in modelling the learning dynamics of large agent populations and
+has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
+n-agent games.
+
+An advantage of determining the evolutionary dynamics of learning is that it can describe the
+expected behaviour using different learning methodologies for various game settings. This is
+particularly important to understand the convergence of the applied learning method; certain games
+will often show cyclic behaviour even with the existence of a strict NE. For instance, Imhof et al.
+show in \cite{Imhof2005} that a repeated prisoner's dilemma game results in cyclic behaviour when
+considering the options of cooperation or defection. In an interesting twist, Galla shows in
+\cite{Galla2011} that this result is dependent on the memory of the agent. Therefore, by using a
+method of batch learning, in which agents may discount observations from the distant past, the
+agents will move their convergent result from a stict NE (to always defect) to a mixed, stable
+equilibrium which promotes cooperation. In \cite{Sanders2018}, Sanders et al. extend this approach
+to a general n-player game which is learnt through an experience-weighted attraction method. They
+show that the method will display different dynamical behaviour including: convergence to stable
+equilibria, limit cycles and chaos. They determine a parameter which describes the likelihood of
+complex dynamics and show that, as the number of players increase, the likelihood of complex
+dynamics (which will not converge to fixed points) will increase. A similarly interesting result is
+that of chaotic dynamics in certain game types and learning algorithms. Sato et al show in
+\cite{Sato2002} that Cross learning in two person games result in choatic behaviour and use the
+simple rock-paper-scissors game to illustrate this point. In \cite{Foster2001}, Foster and Young
+show that in these games, agents cannot learn the future behaviour of their opponents, regardless of
+the learning technique. This therefore means that the game does not converge to a NE.
+
+The above discussion highlights just some of the growing body of work regarding the dynamics of
+multi-agent learning. It is clear that these studies provide strong insights into the prevalent
+problem of multi agent systems, particularly those using reinforcement learning. It allows for an
+analysis of the conditions under which learning is possible as well as a method to evaluate
+different learning algorithms. However, this field still requires significant work in terms of
+generality. A proposal to expand this research is presented in 'Proposed Research'.
+
 \section{Stable Learning}

### 2020-01-07 Literature Review/Literature Review - Revised/sections/Proposals.tex
Added Proposal 7.3

@@
 
-\section{Stable Exploration in Multi Agent Reinforcement Learning}
+\section{Dynamical Study of Multi Agent Learning}
 
-This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and an
-important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent systems
-lead to stochastic behaviour resulting sometimes in undesired effects'. In particular, most RL
-methods require some trade-off between exploration and exploitation. It is, therefore, required that
-we determine a safe manner in which MARL agents may explore without leading to unstable behaviour.
-This would require extending the work of \cite{Berkenkamp2017} and/or
+This builds on the methods and studies presented in 'Learning Dynamics' and an important point
+mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent systems lead to
+stochastic behaviour resulting sometimes in undesired effects'. It is clear from the discussion that
+this study has important implications for MARL. Specifically, it allows us to consider under which
+conditions convergence to an equilibrium is possible. It also allows for directed parameter tuning
+to ensure that the resultant game yields desired effects. However, this study is still in its
+infancy and there are areas yet unexplored. For instance, it would be important to consider the
+challenge presented by Bloembergen et al. in \cite{Bloembergen2015} - stateful games with a
+continuous action space. This will by no means be trivial and will require strong assumptions
+regarding the learning method used and the structure of the game (two-player, symmetric etc). The
+analysis presented in \cite{Letcher2019DifferentiableMechanics} regarding Differential Game
+Mechanics would prove as a valuable starting point.
+
+Extending to the large n-player case considers the other end of the spectrum which builds on the
+work of Hu in \cite{Hu2019} by extending the dynamical study of the mean-field MARL approach which
+is gaining popularity. The models may be extended to the consideration of multiple populations,
+asymmetric games and continuous action spaces. Perhaps the results presented in \cite{Bellomo2017}
+may prove useful in the consideration of the inter-agent effect on the larger population.
+
+Important questions must be considered in this study, such as the ability of agents to predict the
+behaviour of other agents. Chaotic dynamics means that this there are limitations to the degree of
+predictability that agents show whilst playing a game. These limitations should be explored so that
+algorithms which require predictive behaviour may be benchmarked.
+
+As shown in \cite{Bloembergen2015}, these studies are not only useful as a modality for study but
+can also be reverse-engineered to develop learning methods which exhibit desired behaviours. To this
+end, I propose considering a control theoretic approach towards multi-agent learning. This would
+require extending the work of \cite{Berkenkamp2017} and/or
 \cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that
@@
 independent learners who do not consider the effect that they have on the other agent(s). The
-particular extension that I propose is to consider the coupled effect between agents as part of the
-determination of a safe set for exploration.
+particular extension that I propose is to consider the coupled effect between agents using
+replicator dynamics.
 

### 2020-02-04 Literature Review/Literature Review - Revised/.history/sample_20200203092523.tex
Added Chapter 8

--- 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
@@
-\documentclass[preprint,11pt]{report}
+\documentclass[11pt]{report}
 
@@
 \let\endchangemargin=\endlist
-\title{Literature Review - Informal}
+
+\usepackage{subfiles}
+
+\title{Literature Review - Revised}
 
 \newcommand\fr[1]{\textcolor{red}{FR: #1}}
+\newcommand\TODO[1]{\textcolor{purple}{TODO: #1}}
 
@@
 
-\chapter*{Introduction}
+\chapter{Introduction} \subfile{sections/Intro} \label{ch::Intro}
 
-The areas of interest regarding Multi Agent Systems fall into two
-distinct categories (which have some slight overlap). The first is
-denoted as 'Decision Making', though the terms 'Planning' and
-'Distributed Control' may sometimes be used as substitutes. It is
-important to note that, in my case, I do not include Planning
-Formalisation techniques such as PDDL. Instead, I focus on the
-particular methods which involve interaction in the world. The second,
-I will refer to as 'Multi Agent Dynamics', though sometimes I will
-refer to this as 'Stability Analysis'.
+\chapter{Swarms} \subfile{sections/Swarms.tex} \label{ch::Swarms}
 
-\subsection*{Scope}
+\chapter{Dec-POMDPs} \subfile{sections/Dec-POMDPs} \label{ch::Dec-POMDPs}
 
-Both of the aforementioned topics have been applied to all variants of
-multi agent systems and have sufficient room for further
-exploration. The typical variants of multi agent systems that I will
-consider are
+\chapter{Game Theory} \subfile{sections/GameTheory} \label{ch::GameTheory}
 
-\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
-Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
-Coded \end{itemize}
+\chapter{Multi Agent Reinforcement Learning} \subfile{sections/MARL} \label{ch::MARL}
 
-In the above, 'Game Theoretic Approaches' cover a wide spectrum,
-including zero-sum (minimax) games, bayesian games, and many more. The
-final category, 'Hard Coded', refers to any approach which does not
-fit neatly into any of these categories. The name is chosen since they
-often refer to methods which revolve around a series of if-else
-statements.
+\chapter{Control Theory} \subfile{sections/ControlTheory} \label{ch::ControlTheory}
 
-\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}
-
-I will first consider Decision Making as this is most closely related
-to the research proposal, before I consider Multi Agent Dynamics,
-which has strong implications for Safe and Trusted Multi Agent
-Systems.
-
-\subsection*{Objectives}
-
-The aim of the following sections is not to provide an exhaustive list of all work done in the
-aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
-identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
-these directions, we may be able to narrow down the remaining literature review and hone in on
-particular problems and, in fact, we may find that we address multiple of these over the next four
-years (while we, of course add more). As such, the end of each chapter will provide a list of
-research directions which I have identified from the preceding review.
-
-\chapter{Decision Making}
-
-Decision making refers to the generalised problem of considering how a multi-agent system should
-interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
-are aligned (cooperative) or in conflict with one another (competitive).
-
-The following sections will provide an overview of the literature aimed towards coordinating such
-systems as followed by interesting sub-fields in each approach which present avenues for research
-related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
-as the review progresses.
-
-\section{Swarms}
-
-Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
-through a formation using a series of simple local interactions with their neighbours
-\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
-may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
-ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
-performance in reaching globally optimal solutions in search-based tasks. The advantage of many
-swarm algorithms is that they are based on local interactions and so are incredibly scalable
-\cite{Rizk2018}.
-
-The reduction of the complexity in interactions between agents also allows for the robots to perform
-other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
-considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
-manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
-whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
-sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
-readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
-divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
-
-Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
-central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
-adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
-made regarding the homogeneity of individual agents and the simplicity of their local interactions
-result in significant limitations placed on the complexity of the tasks that swarm systems can
-accomplish.
-
-\fr{What are the standard techniques used in swarms?
-that is, how are swarms and their interactions modelled?
-how are solutions computed?
-what kind of algorithms are used in this area?
-most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
-
-\subsection{Co-evolution and Self-Healing}
-
-Recently, there has been an increased interest in introducing
-heterogeneity into the swarm systems to improve their real world
-applicability. An example of this which have been shown strong real
-world success can be found in
-\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
-swarm teams, referred to as 'foot bots' and 'eye bots' who work in
-unison to explore an environment and solve a navigation task.
-
-This area of research is sparsely populated and warrants further
-exploration. This is since the use of co-evolutionary teams can
-improve the robustness of the swarm optimisation. This is since it
-will be possible for a team to automatically determine when robots in
-the other team are not exhibiting expected behaviour and ensure that
-the other team self corrects. This process is referred to as
-'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
-user to define the goals of a swarm system. From this, a 'trust'
-metric can be defined which measures the deviation of each agent from
-the expected behaviour. The self-healing process occurs by limiting
-communication of all agents with 'untrusted' agents and encouraging
-communication with 'trusted' agents. The unison of self-healing with
-co-evolution may present the opportunity for heterogenous swarms to
-maintain their evolutionary stability, even in the face of
-environmental disturbances.
-
-\subsection{Fault Detection}
-
-The above sections have considered the fact that swarm systems are
-robust to losses in the group.  However, any MAS system must first be
-able to recognise that an agent has undergone some failure.
-
-To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
-a robust fault detection approach in which the swarm itself, in a
-decentralised manner, is capable of assessing deviation from 'normal'
-behaviour, even when the behaviour of the swarm itself is altered
-(perhaps by a remote operator). The authors achieve this by requiring
-that the agents themselves sense and characterise their own
-behaviour. This characterisation is formulated as a binary feature
-vector which is then communicated to the agent's neighbours. These
-neighbours will reach a consensus over whether the agent should be
-treated as faulty based on their collective behaviour. The results
-presented in \cite{Tarapore2019FaultDetection} show extremely
-promising results and suggest that their method is, in fact, able to
-determine faults with high accuracy in the presence of various fault
-types (including sensor and actuator failures), although poor
-performance is seen in actuation failures in some instances. It should
-be noted that this method requires that each robot transmit their
-feature vector to the nearest neighbours. In environments where
-communication may be severely limited, this may present further
-errors. Furthermore, it is unlikely that, when a robot is damaged,
-only one of its components will be affected. Therefore, it is
-important to determine the effect on performance in the face of
-multiple agent failures and in communication losses. This exploration
-may open the possibility of improving the state of the art in terms of
-failure detection in swarm systems. (Of course, this conclusion is
-based off two papers so further review is required).
-
-\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas.
-As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another.
-However, this depends essentially on the different modelling assumptions.}
-
-\subsection{Verification}
-
-Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
-require further reading
-
-\subsection{Directions}
-
-From the above consideration of swarms, the following research
-directions have been identified which, in my view, concern themselves
-with STAI.
-
-\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
-towards ensuring that emergent phenomenon and swarm behaviour are as
-expected by the user.
-
-\item Fault Detection in limited communication:
-Considering the ability of a swarm to, in a decentralised approach,
-consider which robots in the team have failed, even in cases of no
-communication or multiple failures.
-
-\fr{The second item looks promising, possibly in combinations with
-  techniques from Game Theory and MARL. Let's keep Fault R\&D in
-  mind.}
-
-\end{itemize}
-
-\section{Dec-POMDPs}
-
-The use of POMDPs in multi-agent settings is formalised as
-decentralised POMDP (Dec-POMDP) which aims for a team of agents to
-maximise a common utility. However, it has been found that determining
-the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
-so is intractable for all but toy problems. A number of methods have
-been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
-of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
-as brute force) are intractable for all but toy problems.
-
-Approximate solutions to Dec-POMDP have been proposed, perhaps most
-notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
-Amato et al. Here, macro actions (actions which extend over multiple
-time steps) are used, as opposed to low-level actions which are
-re-evaluated at each time step. This allows an exact solution to be
-found as it does not need to be evaluated at each time step. This
-method assumes that, once macro-actions are distributed, the policies
-(sequence of state-action pairs) are known. Since this is not the
-case, Amato also proposes the use of a Dec-POSMDP
-\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
-'Semi-Markov Decision Process, in which a high level model is defined
-without the underlying Dec-POMDP's actions and observations.
-
-However, this is largely applicable in passive settings where common
-payoffs can be determined by an offline planner. They also require a
-significant amount of data with which to allow the system to learn the
-underlying models and payoff structures. This limits the applicability
-of the system when communication is limited and the system is
-presented with environments that it has not seen before.  Recent work
-in MDPs \cite{Klima2019RobustDomains} has considered learning in the
-face of Significant Rare Events (SREs) which the system has not yet
-observed. Currently, it is required that a model of such SREs is known
-and so it would be interesting to consider the application of
-Dec-POMDPs in situations where the SRE model is incomplete or
-erroneous and assess the robustness of the Dec-POMDP framework against
-such events.
-
-\subsection{Directions}
-
-The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
-developed by Amato as he seems to largely dominate the field. Based on this initial review of the
-area, a potential direction for research is
-
-\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
-  SREs which have a limited or erroneous model.
-
-\item Agent Failures: The Dec-POMDP model uses a
-centralised planner which acts offline. It therefore assumes that the agents will be able to carry
-out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
-planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
-
-\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
-Also, it might be interesting to understand why swarms scale up better
-than MDPs, and in general why the former have better computational
-properties than the latter: is it a matter of
-``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
-some other swarm-like restriction? It might be interesting to combine
-the two approaches in order to get the ``best of both worlds''.}
-
-\section{Game Theoretic Approaches}
-
-Game theoretic models are generally the go-to method for understanding
-multi-agent systems. As such they fit into all of the categories in
-this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
-methods have both used game theory to support their frameworks. In
-fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
-(POSG), in which all agents use the same payoff. \fr{That's an
-  interesting remark. It might be worth to check whether we can
-  leverage on this and similar observations.} Game theory can,
-therefore, be used in an applied capacity to direct task allocation
-across heterogenous teams.
-
-\subsection{Market Based Methods}
-
-Garapati et al. \cite{Garapati2018AMissions} define a market based
-method as the setting where agents "follow their own interests and
-establish the mechanism of a market for distributing the
-tasks". Auctioning is the most widely used sub-field of market
-approaches and so I will use them interchangeably.
-
-Whilst there are different variants to autioning, the general
-procedure is that an auctioneer who has knowledge of a task (or
-multiple tasks) will set up an auction for said task. Agents can then
-make bids on these tasks and, once the auction is complete, the
-highest bid will win the task. In the specific application to
-robotics, a robot's bid will often reflect the costs, suitability or
-utility their undertaking the task
-\cite{BernardineDias2006Market-basedAnalysis}. This immediately
-highlights a few points. The first is that the method is not too
-heavily reliant upon a single processor to determine some joint
-policy. Tasks are allocated on a case-by-case basis and the utilities
-are calculated by the agent themselves. The only centralised process
-is the auctioneer's assessment of the winner which then relays this
-information back to them. The downside of this is that the system is
-heavily reliant upon strong communication channels, without which
-tasks may not be assigned, incorrect utilities may be communicated
-and, in general, sub-optimal solutions reached.  Furthermore, the
-requirement that the agents themselves determine the cost of their
-actions assumes that they have the computational capability to do
-so. Furthermore, the bids placed by each agent need to be a strong
-representation of their capability to perform a task which may be hard
-to estimate without expert knowledge. However, market based methods
-are well suited to explanation through argumentation (similar to
-\cite{Jung2001DistributedArgumentation}.
-
-\fr{The game-theoretic approaches described above might suffer from the
-  same drawbacks identified above for fault detection, namely reliance
-  on communication and on a single central authority. I'd rather
-  favour distributed approaches. Also, market-based mechanisms and
-  negotiation might lead us to a completely different direction.}
-
-With well chosen payoffs, market based approaches work extremely
-well. For instance, in \cite{Dias2000ASystem}, the authors show that a
-free market approach (where agents try to maximise their own profits)
-can lead to a strong collaborative effort across teams. Similarly, in
-\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
-auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
-towards a robot construction team. However, it is important to note
-that these are both passive settings; tasks were assigned before the
-team were in the field and, in the case of
-\cite{Gerkey2002Sold:Coordination}, the system would repeat the
-bidding process if a robot failed. While both show strong performance,
-it cannot be said that either would be applicable in dangerous
-environments in which dynamic reassignment must happen within strict
-time constraints. Stancliff et
-al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
-method to planning would be to account for failures a priori, a
-philosophy which is exemplified in \cite{Chen2010ACollaboration} who
-consider the robot's reliability and relevance to a task as well as
-'history relevance' which considers the relationship between pairs of
-robots with the aim of producing more effective teams.
-
-There has also been some interesting work in probabilistic
-verification of market based approaches.  Most notable to me is
-\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
-of conflict avoidance. Though their method focuses on collision
-avoidance, it highlights the need for verification of conflict
-resolution and goal achievement in market based approaches with
-different payoff structures. Sirigineedi et
-al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
-direction by considering the verification of cooperative surveillance
-along a route network.  From my understanding, this means that they
-were able to verify that their agents were able to traverse along the
-network without interference. However, this, as always, requires
-further analysis to truly understand.
-
-\subsection{Directions}
-
-The particular considerations which have jumped out to me from the above analysis are as follows:
-
-\begin{itemize} 
-	\item Verification of goal achievement under different payoffs: can we ensure that
-	self-interested agents will, in fact, show cooperative emergent properties? A similar question
-	arises in terms of valuations (how much cost each agent incurs). 
-	\item A priori consideration of
-	reliability: Can we learn and take into account the fact that robots may fail throughout the
-	progress of a mission when we assign tasks? 
-\end{itemize}
-
-\subsection*{Stochastic Games}
-
-\section{Hard Coded}
-
-\section{MARL}
-
-Reinforcement learning extends the Markov Decision Process problem by
-considering the case where the payoff model is not known. This, of
-course, is the case for most real world environments. As such, MARL
-algorithms can perhaps be considered to be more applicable than
-Dec-POMDP models.
-\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}
-
-Fortunately, MARL has picked up a lot of traction in
-research recently, with a large body dedicated towards solving the
-many problems it presents.
-
-The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
-single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
-in the Multi Agent setting since other agents in the environment will be learning concurrently. This
-learning will be based on their own history of interactions which extend beyond the previous state.
-As such, we must now consider that the policy for any one agent will depend on the policy of all
-other agents. As such, a big concern in this area is regarding convergence guarantees and the
-stability of the learner system. Approaches to this will be discussed in the next chapter.
-
-\subsection*{Agent Modelling}
-
-Returning to the problem of non-stationarity, solutions have been presented in which the agent
-models the learning of other agents. A noteworthy example of this is found in
-\cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other
-agents' learning and optimises with respect to this expected return. They show that this leads to
-stable learning and can even lead to emergent cooperation from competition. However, the method
-requires that both agents have exact knowledge of the others' value functions in order to perform
-the one step lookahead. Furthermore, it has only been considered for the case of a two agent
-adversarial game and so the scalability of the system to multiple agents is not yet understood.
-Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect
-the actions and observations of all agents and allows it to model the joint policy of teammates.
-This is shown to generate cooperative behaviour across four agents and so is more applicable to real
-world settings. However, its disadvantage over the method presented in
-\cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this
-requires the presence of an agent (perhaps a laptop) which is able to handle the computational load
-of determining a joint policy across all agents and must then communicate the Q-values of all agents
-back to them. This is both a taxing both in terms of computation and time.
-
-Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by
-tasking a CNN with determining the policy features of other agents and then embedding these as
-features in its own DQN. This shows strong performance in settings where other agents dynamically
-change their policies. The concerns with this, however, are that, as the number of agents in the
-field increase, the CNN in each agent must perform another approximation. This places strong
-requirements on the performance of the CNN since errors in estimation will accumulate as the number
-of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are
-added.
-
-Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent
-modelling is an important one to ensure stable learning and to understand the evolution of the
-system. It also presents a strong challenge and is open to exploration. To put it in context the
-methods described in this section are all from 2018-19, so its all very new.
-
-\subsection{Directions}
-
-I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
-However, on initial assessment I put forward
-
-\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
-the stability of the learning process. However, the particular problem I suggest is to consider the
-modelling in a decentralised manner and with the consideration of evolving numbers of agents in
-teams. \end{itemize}
-
-\fr{This looks like an interesting, non-trivial problem: how can we
-  represent the other agents within the agent model itself, in order
-  to improve learning in MARL? Shall we have a closer look at this problem?}
-
-\section{MARL Approaches} \label{sec::MARL Approaches}
-
-The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
-policy may be the concatenation of all the individual policy or it may just be options for each
-agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
-and so, in this section, I will try to consider the broad spectrum of methods which attempt to
-achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
-all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
-to help guide this review. I am not referencing the individual papers immediately, though the
-references can be found in the book.
-
-\subsubsection*{Learning in Two Player Matrix Games}
-
-The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
-method of linear programming (in which constraints are linear). This will be important in
-considering more current methods. A similar consideration is given to the infinitesimal gradient
-ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
-infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
-not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
-particular problem in games where there are multiple Nash equilibria. However, in practice it is
-difficult to choose a convergence rate of the step size and, without an appropriate choice the
-strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
-to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
-payoff matrix (which is not so much of a problem for model based methods) and the opponent's
-strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
-method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
-(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
-oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
-players with minimal oscillation.
-
-The above methods are all centralised techniques, in which a controller determines the optimal joint
-policy for both agents. However, in real scenarios it is often preferable that each agent learns
-their own strategy, a task which must be completed without information of the other agent's
-strategy. The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which
-guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$)
-which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor
-algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$
-lagging anchor algorithm which can converge to both pure and mixed NEs.
-
-\subsubsection*{Learning in Multiplayer Stochastic Games}
-
-Stochastic Games (or Markov Games) form a basis for MARL
-settings. However, in this case the agents must learn about the
-equilibrium strategies by playing the game, which means they do not
-have a priori knowledge of the reward or transition functions. Schwarz
-considers two properties which should be used for evaluating MARL
-algorithm: rationality and convergence. The latter simply states that
-the method should converge to some equilibrium whereas the former
-suggests that the method should learn the best response to stationary
-opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
-shortly. Schwarz then presents a review of MARL methods (as of
-September 2014)
-
-\fr{All the above looks extremely interesting. I would explore the
-  above for decentralized and partially observable settings. What
-  results are mentioned \cite{SchwartzMulti-agentApproach} under such
-  assumptions?}
-
-\subsection*{Dec-POMDP and MARL}
-
-As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
-methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
-\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
-is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
-Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
-however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
-Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
-order to make this work, we would also need to consider how to select the feature space of sub-trees
-and how to collect this information. \end{itemize}
-
-\chapter{Multi Agent Control}
-
-\section{Stochastic and Robust Model Predictive Control}
-
-The idea of Stochastic Control is best described in the research statement of the Control and
-Analysis of Stochastic Systems (CASS) group at Penn State:
-
-\begin{displayquote}
-	"...to model, predict and control uncertain engineering systems where the interplay between
-	dynamics and uncertainty (stochasticity) is important."
-\end{displayquote}
-
-When operating in the real world, systems are subject to uncertainty and environment perturbations.
-Despite this, for their safe operation, they must provide certain guarantees (such as collision
-avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
-system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
-control have found their way into controlling power distribution, chemical processes and (of course)
-robotics.
-
-\subsection*{Model Predictive Control}
-
-Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
-of operating real-world agents safely in the face of environmental disturbances. The overarching
-idea begins with the assumpion that we have a model of the environment. As an example, in
-the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
-affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
-environment state for a few time steps ahead, and generate a policy for this horizon. The agent
-performs the immediate action generated by the policy, and then we repeat the process, after taking
-measurements of the environment to determine the error in the system. Throughout this process, the
-controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
-example, a likely constraint would be that the controller will never result in the car going on the
-pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
-the requirement of stability that the system is required to remain safe throughout operation. To
-that end, mathematical proofs of these properties are provided in the literature ensuring that we
-can trust in the system's performance.
-
-Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
-knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
-computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
-provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
-of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
-we no longer assume the exact nature of the environment and can guard against worst case scenarios.
-This is extremely effective in closed environments or for simple tasks, but falters in more complex
-environments.
-
-Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
-perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
-define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
-optimality is defined in terms of the minimisation of the expectation of a probabilistic
-cost function. This formulation brings about controllers which are more applicable and robust when
-deployed. However, the field is in its infancy and presents a number of theoretical challenges.
-These are best described by Mesbah in \cite{Mesbah2016}
-
-\begin{itemize}
-	\item The arbitrary form of the feedback control laws
-	\item The non-convexity and intractability of the chance constraints
-	\item The complexity of the uncertainty propagations
-	\item Establishing stability of the control problem
-\end{itemize}
-
-Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
-some of
-these problems, most notably the intractability of the chance contraints. For instance, in 
-\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
-time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
-suited to non-linear systems, which itself is an open problem in the MPC sphere.
-
-The research in using Distributed Predictive Control is quite sparse as compared with, for example,
-single agent predictive control. The added complexity of stochastic environments has meant that this
-area of research is still very open for looking into. With this said, the main works that I have
-found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
-\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
-Usually these are some combination of the following:
-
-\begin{itemize}
-	\item The agents act in a deterministic environment. This suggests that predicted futures will
-	be close enough to the ground truth.
-	\item The agents are uncoupled from one another. This is a strong assumption to make and
-	essentially allows us to consider the agents as completely independent of one another. 
-	\item The agents can easily communicate with one another. This allows for longer pieces of
-	communication (most often predicted trajectories) to be communicated between agents.
-\end{itemize}
-
-\subsection{Directions}
-
-The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
-and applied problems. Control in autonomous systems is also one of the more applicable problems
-related to STAI since it requires that we place mathematical guarantees on the performance and
-stability of the system as well as guarantees on the satisfaction of constraints. This is, of
-course, an ever present problem in autonomous systems which operate in the real world. I begin by
-listing the more theoretical areas for exploration in MPC before then considering their application
-domains.
-
-\begin{itemize}
-	\item Significant exploration is required with regards to the optimisation problem. Especially
-	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
-	approximate methods (such as sampling) should be explored and their effect on the system
-	guarantees presented.
-	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
-	determine the uncertainty in the environment model in order to generate control laws. We should
-	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
-	particle filters, against modern deep learning methods for propagation.
-	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
-	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
-	together whilst maintaining a specified distance from one another). Consider, then, the case
-	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
-	and hence requires adaptation. It would again be interesting to consider the use of neural
-	networks in this manner. However, specifically we should consider whether the use of a function
-	approximator in the form of an NN might result in a violation of the constraints.
-	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
-	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
-	effect that each agent has on the other, the effect of the environment on all agents, estimating the
-	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
-	here that I believe game-theoretic notions (especially differential games) will come to our
-	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
-	in the case of multiple disturbances, but I will elaborate on this in the applied problems
-	section.
-\end{itemize}
-
-the following presents a consideration of the applied end of MPC problems. I have tried to focus on
-the domain independent suggestions, since the domain specific ones are virtually limitless.
-
-\begin{itemize}
-	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
-	interact with each other. In addition, we may consider that there are multiple known disturbances
-	acting on the system. This, at first seems like an impossible problem to solve due to the many
-	interactions between all elements of the system. However, we can consider this as a game
-	theoretic problem in which the components and the disturbances are players. The relatively new
-	class of 'mean-field games' is a method which allows the many body problem to be approximated as
-	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
-	predictive control' remain, this may prove to be a valuable area of applied research.
-	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
-	which emerge into more complex results. It would be interesting to consider the application of
-	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
-	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
-	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
-	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
-	adaptive stochastic model would be interesting to examine here to remain robust to agent
-	failures in the group.
-	\item Modular Robotics?
-\end{itemize}
-
-\section*{Multi Agent Dynamics}
-
-Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
-Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
-well as to understand the trajectory of learning. Typically, this looks at considering whether or
-not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
-problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
-applicability into real world settings requires the study of stable equilbrium points;
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world
-environments.
-
-\section{Stability of Learning Agents}
-
-Stability may be looked at from the view point of two perspectives. The first is from an
-optimisation point of view. This considers the dynamics of the learning model, allowing us to better
-choose our parameters and design our models so that they may converge to a stable result. The second
-is from the view point of the state-action space of a learnt model. This allows us to determine,
-before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This
-knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability
-analysis allows us to build multi agent systems which will learn and act in the way that we expect
-them to.
-
-In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of
-generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is
-one in which the loss function is twice differentiable. Using this formulation, they are able to
-analyse the system from new perspectives by considering the current state-of-the-art understanding
-of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical
-exercise, they go on to show that the insights gained allow them to develop a new multi-objective
-optimisation technique for GANs which shows stronger convergence properties, most notably of which
-is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the
-two players' loss functions.
-
-Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement
-learning agent as a non-linear, time varying feedback controller. Using this notion, they then
-consider the bounded-input-bounded-output stability of the system. They do this by analysing the
-ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains
-finite then the system may be considered to be stable. They then apply these considerations on
-real-world applications including multi-agent flight formation and obtain stability certificates
-(essentially confirming that the system will remain stable under certain conditions) for the learned
-controller.
-
-Berkenkamp et al. \cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different
-definition of stability. Specifically, they look at stability from the point of view of Lyapunov
-functions. A system is said to be stable if the applying the policy will result in stricly lower
-evaluations of the function. In other words, a system is stable if its corresponding Lyapunov
-function is decreasing towards a minimum point. The authors use this idea to define a 'region of
-attraction' in which the system is stable in the sense of Lyapunov. The goal of Safe Lyapunov
-Learning, a method which they develop from these insights, is to learn a policy without leaving this
-region of attraction. They do this by taking measurements within the set and using this to learn
-about the system dynamics, thereby increasing the safe set. With this, we now have a guarantee that
-policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and
-exploration.
-
-As we can see from the discussion thus far, there are many definitions and perpectives of stability,
-each lending to a new understanding of learning systems. To add another to the mix, Milchtaich in
-\cite{Milchtaich2007StaticGames}, presents a notion of static stability. This means that it is based
-solely on the incentives of the players and does not require a consideration of the dynamics of the
-system. Milchtaich's definition of a stable system is one in which, when perturbed, it is more
-beneficial for an agent to move back towards the equilibrium than it is for them to move away. This
-is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows
-that it is applicable to all strategic games, within certain assumptions (finite set of player and
-continuous strategy space) and considers probabilistic perturbations from the original state. This
-is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy
-spaces) since these systems require random exploration of the strategy space and the dynamics are
-not known a priori. However, the lack of dynamics means that we do not consider the evolution of
-learning.
-
-\section{Learning Stable Agents}
-
-The above discussion has considered how notions of stability and control are important to
-Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
-specifically, game theory, can be used to develop controllers which drive systems to stable states.
-This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
-which the players are a controller and an adversarial environment. The design of the controller must
-be such that it is able to drive the system to zero error. To illustrate, consider the problem of
-designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
-vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
-efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
-agent may encounter without actually encountering them. The same notion is explored by Bardi et al
-\cite{Bardi1991DifferentialDisturbances}.
-
- Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
- avoidance problem, similarly from the point of view of differential game theory. They develop a
- robust feedback system for the robots which they show to be able to drive the system towards
- predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
- In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
- systems in a distributed manner. Here, agents only consider their own payoff structure and have
- limited communication with one another. The author shows that the an approximate equilibrium can be
- found using algebraic methods and illustrate the capabilities of the technique using a collision
- avoidance example. For the sake of brevity, I will not include all of the numerous strides that
- Mylvaganam has introduced to the area. However, I must conclude with those presented in
- \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
- games, including linear-quadratic differential games (in which system dynamics are linear functions
- whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
- induced across the players (a notion was suggested in the research proposal) and mean-field games,
- which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
- differential game is the stability of the solution; solutions for the Nash equilibria are
- admissable iff they are locally exponentially stable (which the author often shows with the aid of
- Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
- calculate online. The author then shows that this is not simply a theoretical exercise by applying
- the novel methods towards multi-agent collision problems and designs dynamic control laws which
- guarantee that each agent will reach their desired state whilst avoiding collision with the other
- agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
- robot system.
-
-\subsection{Directions}
-
-I will briefly summarise the research directions which I develop in this section, to save ourselves
-some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}
-
-The above discussion has illustrated a few points. The first, and perhaps most important, is that
-stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
-that learning agents, especially in real world environments, are subject to uncertainty and
-perturbations as well as epsilon-random exploration. As such, it is important that the system is
-able to return to a stable state after such perturbations. This leads to the need to develop
-learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
-equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
-equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
-Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
-to stable fixed points.
-
-The second point is that the notion of stability has multiple definitions. Each one is appropriate
-in different conditions and, as such, it is important to explore stability from various viewpoints
-to consider how to best understand the evolution of a learning system.
-
-Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
-not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
-question and is well worth consideration. This would help guide the choice of loss functions and
-strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
-dramatic impact on the safety certification of MARL systems.
-
-The problem of finding stable solutions through multi agent dynamics also opens the door for a large
-degree of application domains which are currently quite sparse. I would recommend looking at the
-contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
-of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
-control and economic modelling. My particular interest, as always, lies within robotic control
-problems. This appears to be the most direct and relevant application of stable MAS systems. An
-example of this might be the problem of Cooperative Moving Path Following Control considered by
-\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
-pre-defined path without interfering with one another. It is clear then that each player's control
-is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
-determine control rules which lead to stable coordination across the team. Similarly, we can model
-consider modelling a controller and an adversarial environment as a zero-sum game as examined in
-\cite{Marden2018AnnualControl}.
-
-Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
-of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
-differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
-the differential game problem from the point of view of different information structures. In
-real-world systems, it is unlikely that all agents will have access to the information of other
-agent' cost functions and current positions. It could, however, be interesting to explore the use of
-localisation methods to determine and track this information through observation (e.g. through
-Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
-considers the case where system dynamics are linear. A whole new set of problems arise in the more
-realistic case where we must consider the non-linearity of system dynamics. Such a consideration
-would also allow us to extend these technique to the more difficult (and important) problems in
-control.
-
-The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
-Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
-Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
-particularly relevant to this study. However, they will require some further analysis before I write
-about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
-entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
-document out.)
-
-\chapter{Research Directions}
-
-\section{Stochastic Model Predictive Control for Distributed Systems}
-
-The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
-that end, I propose the following techniques towards improving DSMPC.
-
-\begin{itemize}
-	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
-	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
-	distribution of the action that will likely be selected by $j$, effectively performing a
-	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
-	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
-	this may seem computationally expensive, its advantage lies in the fact that it requires little
-	communication across the agents. An immediate disadvantage of this is that, as the number of
-	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
-	not yet confident on the feasibility or the usefulness of this technique, but looking further
-	into the literature (which seems to add new things every day) may provide insights which could
-	help refine the technique. This method is, in many ways, similar to that presented in 
-	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
-	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
-	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
-	all systems to update at each time step.
-
-	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
-	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
-	public belief based on the observed actions of all agents. This joint belief will likely provide
-	some representation of the trajectories that each agent will carry out or an understanding of
-	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
-	will be chosen from a family of existing models using a recursive Bayesian update. The idea
-	would be for this update to be conditioned on the history of observations as is done in 
-	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
-	state and use this, in combination with their own system models to determine a feasible
-	trajectory. The challenge here would be proving the stability and controllability of the system
-	and that it requires communication with a central controller. However, it would appear to be a
-	feasible area of exploration.
-\end{itemize}
-
-\section{Stochastic Control of Swarms}
-
-Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
-when considering its application in stochastic environments. In particular, the ideas presented
-below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
-desired distribution.
-
-\begin{itemize}
-	\item Consideration of state constraints or boundary conditions (terms which I will use
-interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
-particular stochastic difference equation (the Ito equation). However, this does not account for any
-boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
-obstacle avoidance. However, in environments where there are human operators, or in general areas
-where we do not want swarms to enter, it is important to have a guarantee of constraint
-satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
-conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
-confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
-Furthermore, it may present an opportunity for us to consider the decentralised control of the
-agents which can ensure state constraint satisfaction. The resources which are most relevant to this
-study (and from which the ideas are derived) are
-\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
-
-\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
-the diffusion models, as mentioned above, do not take into consideration the interactions between
-agents, since it adds a large degree of complexity to the model. However, it would be important from
-a safety perspective to take these into account by looking at the attractive and repulsive
-potentials across agents. This would allow us to provide a guarantee of inter-agent collision
-avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
-mention that they are already looking into this problem and have proposed a similar manner of
-tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
-they publish?
-
-\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
-By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
-number of their nearest neighbours. However, this may not always be the case. It will often be that
-in different environmental conditions, the observation or communication capabilities of the robots
-may increase or decrease. To better accomodate for this fact, I propose the extension of the model
-with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
-'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
-success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
-way into swarm dynamics. It will, however, become particularly important in cases where we can no
-longer take the consistency of agent communication for granted. 
-\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
-not seem like the connection of MJD and swarm dynamics has been made yet.
-\end{itemize}
-
-\section{Multi Agent Reinforcement Learning}
-
-The ideas I have down here are a little more sparsely populated, but further reading may provide
-some insights into potential directions.
-
-\begin{itemize}
-	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
-	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
-	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
-	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
-	required that we determine a safe manner in which MARL agents may explore without leading to
-	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
-	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
-	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
-	independent learners who do not consider the effect that they have on the other agent(s). The
-	particular extension that I propose is to consider the coupled effect between agents as part of
-	the determination of a safe set for exploration.
-
-	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
-	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
-	problems. Although it makes strong assumptions about the nature of the system, in practice it
-	has shown strong results. Particular examples of this are found in 
-	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
-	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
-	systems by considering sub-groups within the population. Each of these may be updated
-	individually. It would be interesting to examine how this might increase the complexity, and
-	also the generalisability of the mean-field method.
-	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
-	part but the potential directions are largely summarised in Section 2.3.1.
-\end{itemize}
+\chapter{Proposed Research} \subfile{sections/Proposals} \label{ch::Proposals}
 

### 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203155017.tex
Added Chapter 8

\documentclass[../sample.tex]{subfiles}

\begin{document}
    The purpose of this chapter is to further develop the ideas presented in Chapter
    \ref{ch::Proposals}. As mentioned, there are four main areas which have been identified for
    development in this field. These all aim to better apply the study to cases which are more
    relevant for real world Reinforcement Learning problems. To this end, the following studies are
    proposed.

    \begin{itemize}
        \item Dynamics of large agent populations with heterogenous agents.
        \item Dynamics of Reinforcement Learning in continuous action spaces.
        \item Dynamics of Learning in 'stateful' environments.
        \item Characterisation of complex dynamics using Reinforcement Learning Algorithms
    \end{itemize}

    In the above, the term 'stateful' is borrowed from Bloembergen et al. \cite{Bloembergen2015} and
   refers to the consideration of state transitions in the game. The remainder of this chapter will
   address current research in the above topics and avenues for attempting new results.

   \section{Large Agent Dynamics}

    This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
    point is made that the vast majority of the work done in this area considers games with a finite
    (usually two) number of agents. This limits the capability of the analysis to generalise to much
    larger agent populations, such as swarms. To allieviate this concern, the authors present an
    anaysis of the learning dynamics for a large agent population (which they approximate as
    containing infinite agents) where each agent is an independent Q-Learning using Boltzmann
    exploration. The emergent dynamics is given by a Fokker-Planck equation which is numerical shown
    to be a strong approximation of the true learning dynamics. However, as the authors point out,
    this is the first attempt at considering such a problem, and relies on heavy assumptions.
    Possible extensions therefore require a consideration of asymmetic games, stateful games (which
    ties in to Section \ref{sec::Stateful}) and heterogenous populations.

    \section{Continuous Action Spaces}

    Here lies the opportunity to extend the work of Tuyls' et al. \cite{Tuyls2006AnGames} towards
    continuous action spaces. This would be particularly useful for most robotic applications, which
    operate in continuous spaces.

    Work has commenced in this area, but is still in its infancy. Notable examples are: 
    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et al. consider the dynamics of
    Differentiable Games, though their focus is on its application to gradient descent in GANs as
    opposed to reinforcement learning, and \cite{Galstyan2013}, in which the dynamics of Q-Learning,
    with a Boltzmann action selection is considered. To achieve the result, the author replaces the
    strategy vector with a probability density function (pdf) over the strategy space, which leads
    to an integro-differential equation which describes the evolution of the pdf with time. Due to
    its complexity, the dynamics cannot be analysed as easily as those in \cite{Tuyls2006AnGames},
    and so Galstyan restricts the analysis to the steady-state solution (i.e. the fixed point) of
    the dynamics. Their analysis shows strong agreement with the designed experiments, under varying
    payoff conditions (note that the payoffs are now a function, rather than a discrete matrix).

    Galstyan goes on to present avenues for further work. These are summarised below:

    \begin{itemize}
        \item  An analysis of the steady state equations, considering the existence and uniqueness
        of solutions under varying payoff structures. How do these compare with the underlying Nash
        Equilibrium. Tuyls and Westra also suggest the consideration of stability analysis in this regard.
        \item A consideration of larger agent populations. No attempt towards this has yet been made
        as far as I am aware.
        \item A consideration of these dynamics under state transitions. Tuyls and Westra suggest
        that an analysis using switching dynamics (Chapter \ref{ch::ControlTheory}) may be useful
        here, but no attempt has yet been made as far as I am aware.
    \end{itemize}

    Tuyls and Westra \cite{TuylesWestra} also consider continuous action spaces from the same
    perspective as Ruijgrok and Ruijgrok \cite{Ruijgrok}, namely that of the replicator dynamics.
    The former extend the analysis of the latter by considering the case where mutations are
    deterministic (e.g. through epsilon-greedy exploration) and these mutations only allow for small
    changes within the strategy space. From an EGT perspective, this analysis provides a strong
    characterisation of learning dynamics in continous action spaces and generalises the results of
    Galstyan to generic update rules (rather than the traditional Q-Learning approach).

    \section{Stateful environments} \label{sec::Stateful}

    This is potentially the most relevant of the sections in regards to applicability to
    reinforcement learning as it extends the typical consideration of stateless normal-form games,
    in which the payoffs and strategies of each player is well defined, to stochastic games, in
    which games have probabilistic transitions across them. I have yet to explore this section in
    depth.

    \section{Characterisation of Complex Dynamics}

    The intention of this area of study is to consider the ideas presented in works such as 
    \cite{Sanders2018} and \cite{Galla2011} which consider complex behaviour, including cycles and
    chaos, in certain games using simple reinforcement learning algorithms. These provide a great
    deal of insight into whether or not the game will converge and, if so, to what equilibrium.
    Galla, for instance, shows that adjusting a memory parameter when learning to solve an Iterated
    Prisoner's Dilemma game can shift the equilibrium from one showing purely defective behaviour to
    one showing cycles of cooperations and defection. Sanders et al. generalise this result by
    showing that, for a particular learning algorithm known as Experience Weighted Attraction,
    learning dynamics varies dependent on the mutual effect of two parameters.

    This determination of where RL algorithms will show complex dynamics is important, not only for
    a priori understanding of resultant behaviour, but is particularly important for algorithms in
    which agents aim to predict the behaviour of other agents. For this to be feasible, the learning
    dynamics must not exhibit chaos, otherwise it would be impossible for an agent to make any
    reasonable predictions about the future behaviour of its opponents.

\end{document}

### 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200204152650.tex
Added Chapter 8

--- 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203155017.tex
@@
     this is the first attempt at considering such a problem, and relies on heavy assumptions.
-    Possible extensions therefore require a consideration of asymmetic games, stateful games (which
-    ties in to Section \ref{sec::Stateful}) and heterogenous populations.
+    Possible extensions therefore require a consideration of:
+
+    \begin{itemize}
+        \item Asymmetric games, in which agents have different payoffs, introducing heterogeneity
+        and competition into the system.
+        \item Stateful Games.
+        \item Heterogeneous populations, in which there are p different populations of agents.
+    \end{itemize}
+
+    To the best of my knowledge, in the particular case of $N >> 1$ agent populations, none of the
+    above have yet been attempted.
 
@@
 
+    \cite{Amato2015PlanningUncertainty}
+
 \end{document}

### 2020-02-04 Literature Review/Literature Review - Revised/sections/DynMARL.tex
Added Chapter 8

--- 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200204152650.tex
@@
 
-    This is potentially the most relevant of the sections in regards to applicability to
+    This is potentially the most relevant of the sections in regards to direct applicability to
     reinforcement learning as it extends the typical consideration of stateless normal-form games,
     in which the payoffs and strategies of each player is well defined, to stochastic games, in
-    which games have probabilistic transitions across them. I have yet to explore this section in
-    depth.
+    which games have probabilistic transitions across them. To the best of my knowledge, the
+    existing work in this area is sparse. The earliest example is proposed by Vrancx et al 
+    \cite{Vrancx2008} in which the authors extend the concept of replicator dynamics to 'piecewise
+    replicator dynamics', which allows them to consider multi-state games with discrete transitions
+    between them. However, this analysis places strong assumptions on the nature of the learning, in
+    particular that, at each state, the strategies in all other states may be considered as fixed.
+    Whilst the authors attempt to add corrections to mitigate this effect, it is clear from the
+    results that the lack of state-coupling produces deficiencies in the accuracy of the model.
+    Hennes et al \cite{Hennes2009} improve upon this result by incorporating state-coupling into the
+    model, leading to 'state-coupled replicator dynamics'. This is proven to be a stronger indicator
+    of the behaviour of their chosen learning algorithm (the Linear Reward Inaction Penalty put
+    forward by Bowling and Veloso \cite{LRI}). Hennes et al. \cite{Hennes2010} go on to use the
+    state-coupled replicator dynamics to reverse-engineer a learning automata algorithm, known as
+    RESQ-Learning, which is shown to arrive at desired pure or Nash equilibria.
+
+    The state-coupled replicator dynamics provides an important step into the advancement of
+    Dynamical Studies of Multi Agent Learning. However, the above appear to be the only works
+    presented in this area and so its improvement is an open area of study. Potential directions for
+    this include:
+
+    \begin{itemize}
+        \item The consideration of larger state spaces (the above studies only consider two).
+        \item Lifting the assumption of ergodicity on the state space
+        \item Extending the results to extensive form games. The closest attempt to this is
+        considered by Panozzo et al. \cite{Panozzo} who consider Q-Learning in a sequence form game.
+    \end{itemize}
 
@@
 
-    \cite{Amato2015PlanningUncertainty}
+    To this end, the potential avenue for research in this regard is to extend the ideas of Sanders
+    et al. and Galla et al. towards games learnt using classical reinforcement learning algorithms 
+    (such as Q-Learning with Boltzmann exploration, which seems to be a common choice). The work may
+    then be able to extend beyond this, and towards continuous spaces, stateful games and large
+    agent populations. This would allow for an understanding of the important parameters which
+    define the behaviour of reinforcement learning algorithms and allow for a characterisation of
+    the expected resultant behaviour when applying a particular algorithm to a particular game. It
+    would also allow for a characterisation of the conditions under which MARL algorithms may
+    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
+    payoff matrices and parameters accordingly.
 

### 2020-02-04 Literature Review/Literature Review - Revised/sections/MARL.tex

@@
 
-Game Dynamics (which I often refer to as Multi Agent Dynamics or Game Dynamics) considers the
+Learning Dynamics (which I often refer to as Multi Agent Dynamics or Game Dynamics) considers the
 problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one

### 2020-02-06 Literature Review/Literature Review - Revised/sections/DynMARL.tex
minor edits

@@
 
-    This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
-    point is made that the vast majority of the work done in this area considers games with a finite
-    (usually two) number of agents. This limits the capability of the analysis to generalise to much
-    larger agent populations, such as swarms. To allieviate this concern, the authors present an
-    anaysis of the learning dynamics for a large agent population (which they approximate as
-    containing infinite agents) where each agent is an independent Q-Learning using Boltzmann
-    exploration. The emergent dynamics is given by a Fokker-Planck equation which is numerical shown
-    to be a strong approximation of the true learning dynamics. However, as the authors point out,
-    this is the first attempt at considering such a problem, and relies on heavy assumptions.
-    Possible extensions therefore require a consideration of:
+    This suggestion aims to build upon the work presented by Hu et
+    al. \cite{Hu2019} in which the point is made that the vast
+    majority of the work done in this area considers games with a
+    finite (usually two) number of agents. This limits the capability
+    of the analysis to generalise to much larger agent populations,
+    such as swarms. To allieviate this concern, the authors present an
+    anaysis of the learning dynamics for a large agent population
+    (which they approximate as containing infinite agents) where each
+    agent is an independent Q-Learning using Boltzmann
+    exploration. The emergent dynamics is given by a Fokker-Planck
+    equation which is numerical shown to be a strong approximation of
+    the true learning dynamics. However, as the authors point out,
+    this is the first attempt at considering such a problem, and
+    relies on heavy assumptions.  Possible extensions therefore
+    require a consideration of:
 
     \begin{itemize}
-        \item Asymmetric games, in which agents have different payoffs, introducing heterogeneity
-        and competition into the system.
-        \item Stateful Games.
+        \item Asymmetric games, in which agents have different
+          payoffs, introducing heterogeneity and competition into the
+          system. \fr{this is not really a problem  in relation with swarms, is it?}
+        \item Stateful Games. \fr{what is the interest of stateful games?}
         \item Heterogeneous populations, in which there are p different populations of agents.
@@
 
-    Here lies the opportunity to extend the work of Tuyls' et al. \cite{Tuyls2006AnGames} towards
-    continuous action spaces. This would be particularly useful for most robotic applications, which
-    operate in continuous spaces.
+    Here lies the opportunity to extend the work of Tuyls' et
+    al. \cite{Tuyls2006AnGames} towards continuous action spaces. This
+    would be particularly useful for most robotic applications, which
+    operate in continuous spaces. \fr{do we have other examples?}
 
-    Work has commenced in this area, but is still in its infancy. Notable examples are: 
-    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et al. consider the dynamics of
-    Differentiable Games, though their focus is on its application to gradient descent in GANs as
-    opposed to reinforcement learning, and \cite{Galstyan2013}, in which the dynamics of Q-Learning,
-    with a Boltzmann action selection is considered. To achieve the result, the author replaces the
-    strategy vector with a probability density function (pdf) over the strategy space, which leads
-    to an integro-differential equation which describes the evolution of the pdf with time. Due to
-    its complexity, the dynamics cannot be analysed as easily as those in \cite{Tuyls2006AnGames},
-    and so Galstyan restricts the analysis to the steady-state solution (i.e. the fixed point) of
-    the dynamics. Their analysis shows strong agreement with the designed experiments, under varying
-    payoff conditions (note that the payoffs are now a function, rather than a discrete matrix).
+    Work has commenced in this area, but is still in its
+    infancy. Notable examples are:
+    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et
+    al. consider the dynamics of Differentiable Games, though their
+    focus is on its application to gradient descent in GANs as opposed
+    to reinforcement learning, and \cite{Galstyan2013}, in which the
+    dynamics of Q-Learning, with a Boltzmann action selection is
+    considered. To achieve the result, the author replaces the
+    strategy vector with a probability density function (pdf) over the
+    strategy space, which leads to an integro-differential equation
+    which describes the evolution of the pdf with time. Due to its
+    complexity, the dynamics cannot be analysed as easily as those in
+    \cite{Tuyls2006AnGames}, and so Galstyan restricts the analysis to
+    the steady-state solution (i.e.~the fixed point) of the
+    dynamics. Their analysis shows strong agreement with the designed
+    experiments, under varying payoff conditions (note that the
+    payoffs are now a function, rather than a discrete matrix).
 
@@
 
+    \fr{application of the above?}
+
     \section{Characterisation of Complex Dynamics}
@@
 
+    \fr{this last line might possibly be the most relevant for the CDT.}
+
 \end{document}

### 2020-02-24 EGT-RL/.conda/lib/python3.7/_sysconfigdata_m_darwin_darwin.py
Fokker Planck Model added

@@ -1,702 +1,0 @@
-# system configuration generated and used by the sysconfig module
-build_time_vars = {'ABIFLAGS': 'm',
- 'AC_APPLE_UNIVERSAL_BUILD': 0,
- 'AIX_GENUINE_CPLUSPLUS': 0,
- 'ANDROID_API_LEVEL': 0,
- 'AR': 'ar',
- 'ARFLAGS': 'rc',
- 'BASECFLAGS': '-Wno-unused-result -Wsign-compare -Wunreachable-code',
- 'BASECPPFLAGS': '',
- 'BASEMODLIBS': '',
- 'BINDIR': '/Users/aamalh/Desktop/EGT-RL/.conda/bin',
- 'BINLIBDEST': '/Users/aamalh/Desktop/EGT-RL/.conda/lib/python3.7',
- 'BLDLIBRARY': '-L. -lpython3.7m',
- 'BLDSHARED': 'gcc -bundle -undefined dynamic_lookup '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib  '
-              '-arch x86_64 '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib  '
-              '-arch x86_64',
- 'BUILDEXE': '.exe',
- 'BUILDPYTHON': 'python.exe',
- 'BUILD_GNU_TYPE': 'x86_64-apple-darwin13.4.0',
- 'BYTESTR_DEPS': '\\',
- 'CC': 'gcc',
- 'CCSHARED': '',
- 'CFLAGS': '-Wno-unused-result -Wsign-compare -Wunreachable-code -DNDEBUG -g '
-           '-fwrapv -O3 -Wall -Wstrict-prototypes '
-           '-I/Users/aamalh/Desktop/EGT-RL/.conda/include  '
-           '-arch x86_64 '
-           '-I/Users/aamalh/Desktop/EGT-RL/.conda/include  '
[…]

### 2020-02-24 EGT-RL/.conda/lib/python3.7/_sysconfigdata_powerpc64le_conda_cos7_linux_gnu.py

@@ -1,788 +1,0 @@
-# system configuration generated and used by the sysconfig module
-build_time_vars = {'ABIFLAGS': 'm',
- 'AC_APPLE_UNIVERSAL_BUILD': 0,
- 'AIX_GENUINE_CPLUSPLUS': 0,
- 'ANDROID_API_LEVEL': 0,
- 'AR': 'powerpc64le-conda_cos7-linux-gnu-ar',
- 'ARFLAGS': 'rc',
- 'BASECFLAGS': '-Wno-unused-result -Wsign-compare',
- 'BASECPPFLAGS': '-IObjects -IInclude -IPython',
- 'BASEMODLIBS': '',
- 'BINDIR': '/Users/aamalh/Desktop/EGT-RL/.conda/bin',
- 'BINLIBDEST': '/Users/aamalh/Desktop/EGT-RL/.conda/lib/python3.7',
- 'BLDLIBRARY': 'libpython3.7m.a',
- 'BLDSHARED': 'powerpc64le-conda_cos7-linux-gnu-gcc -pthread -shared -Wl,-O2 '
-              '-Wl,--sort-common -Wl,--as-needed -Wl,-z,relro -Wl,-z,now '
-              '-Wl,-rpath,/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-Wl,-O2 -Wl,--sort-common -Wl,--as-needed -Wl,-z,relro '
-              '-Wl,-z,now '
-              '-Wl,-rpath,/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '   '
-              '',
- 'BUILDEXE': '',
- 'BUILDPYTHON': 'python',
- 'BUILD_GNU_TYPE': 'powerpc64le-conda_cos7-linux-gnu',
- 'BYTESTR_DEPS': '\\',
- 'CC': 'powerpc64le-conda_cos7-linux-gnu-gcc -pthread',
- 'CCSHARED': '-fPIC',
[…]

### 2020-02-24 EGT-RL/.conda/lib/python3.7/_sysconfigdata_x86_64_apple_darwin13_4_0.py

@@ -1,801 +1,0 @@
-# system configuration generated and used by the sysconfig module
-build_time_vars = {'ABIFLAGS': 'm',
- 'AC_APPLE_UNIVERSAL_BUILD': 0,
- 'AIX_GENUINE_CPLUSPLUS': 0,
- 'ANDROID_API_LEVEL': 0,
- 'AR': 'x86_64-apple-darwin13.4.0-ar',
- 'ARFLAGS': 'rcs',
- 'BASECFLAGS': '-fno-strict-aliasing -Wsign-compare -Wunreachable-code',
- 'BASECPPFLAGS': '-IObjects -IInclude -IPython',
- 'BASEMODLIBS': '',
- 'BINDIR': '/Users/aamalh/Desktop/EGT-RL/.conda/bin',
- 'BINLIBDEST': '/Users/aamalh/Desktop/EGT-RL/.conda/lib/python3.7',
- 'BLDLIBRARY': 'libpython3.7m.a',
- 'BLDSHARED': 'x86_64-apple-darwin13.4.0-clang -bundle -undefined '
-              'dynamic_lookup -Wl,-pie -Wl,-headerpad_max_install_names '
-              '-Wl,-dead_strip_dylibs '
-              '-Wl,-rpath,/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-flto -Wl,-export_dynamic -Wl,-pie '
-              '-Wl,-headerpad_max_install_names -Wl,-dead_strip_dylibs '
-              '-Wl,-rpath,/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib',
- 'BUILDEXE': '.exe',
- 'BUILDPYTHON': 'python.exe',
- 'BUILD_GNU_TYPE': 'x86_64-apple-darwin13.4.0',
- 'BYTESTR_DEPS': '\\',
- 'CC': 'x86_64-apple-darwin13.4.0-clang',
- 'CCSHARED': '',
[…]

### 2020-02-24 EGT-RL/.conda/lib/python3.7/_sysconfigdata_x86_64_conda_cos6_linux_gnu.py

@@ -1,773 +1,0 @@
-# system configuration generated and used by the sysconfig module
-build_time_vars = {'ABIFLAGS': 'm',
- 'AC_APPLE_UNIVERSAL_BUILD': 0,
- 'AIX_GENUINE_CPLUSPLUS': 0,
- 'ANDROID_API_LEVEL': 0,
- 'AR': 'x86_64-conda_cos6-linux-gnu-ar',
- 'ARFLAGS': 'rc',
- 'BASECFLAGS': '-Wno-unused-result -Wsign-compare',
- 'BASECPPFLAGS': '-IObjects -IInclude -IPython',
- 'BASEMODLIBS': '',
- 'BINDIR': '/Users/aamalh/Desktop/EGT-RL/.conda/bin',
- 'BINLIBDEST': '/Users/aamalh/Desktop/EGT-RL/.conda/lib/python3.7',
- 'BLDLIBRARY': 'libpython3.7m.a',
- 'BLDSHARED': 'x86_64-conda_cos6-linux-gnu-gcc -pthread -shared -Wl,-O2 '
-              '-Wl,--sort-common -Wl,--as-needed -Wl,-z,relro -Wl,-z,now '
-              '-Wl,-rpath,/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-Wl,-O2 -Wl,--sort-common -Wl,--as-needed -Wl,-z,relro '
-              '-Wl,-z,now '
-              '-Wl,-rpath,/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '-L/Users/aamalh/Desktop/EGT-RL/.conda/lib '
-              '   '
-              '',
- 'BUILDEXE': '',
- 'BUILDPYTHON': 'python',
- 'BUILD_GNU_TYPE': 'x86_64-conda_cos6-linux-gnu',
- 'BYTESTR_DEPS': '\\',
- 'CC': 'x86_64-conda_cos6-linux-gnu-gcc -pthread',
- 'CCSHARED': '-fPIC',
[…]

### 2020-02-24 EGT-RL/.conda/lib/python3.7/config-3.7m-darwin/python-config.py

@@ -1,67 +1,0 @@
-#!/Users/aamalh/Desktop/EGT-RL/.conda/bin/python3.7m
-# -*- python -*-
-
-# Keep this script in sync with python-config.sh.in
-
-import getopt
-import os
-import sys
-import sysconfig
-
-valid_opts = ['prefix', 'exec-prefix', 'includes', 'libs', 'cflags',
-              'ldflags', 'extension-suffix', 'help', 'abiflags', 'configdir']
-
-def exit_with_usage(code=1):
-    print("Usage: {0} [{1}]".format(
-        sys.argv[0], '|'.join('--'+opt for opt in valid_opts)), file=sys.stderr)
-    sys.exit(code)
-
-try:
-    opts, args = getopt.getopt(sys.argv[1:], '', valid_opts)
-except getopt.error:
-    exit_with_usage()
-
-if not opts:
-    exit_with_usage()
-
-pyver = sysconfig.get_config_var('VERSION')
-getvar = sysconfig.get_config_var
-
-opt_flags = [flag for (flag, val) in opts]
-
-if '--help' in opt_flags:
-    exit_with_usage(code=0)
-
-for opt in opt_flags:
-    if opt == '--prefix':
-        print(sysconfig.get_config_var('prefix'))
-
-    elif opt == '--exec-prefix':
-        print(sysconfig.get_config_var('exec_prefix'))
-
-    elif opt in ('--includes', '--cflags'):
-        flags = ['-I' + sysconfig.get_path('include'),
-                 '-I' + sysconfig.get_path('platinclude')]
-        if opt == '--cflags':
-            flags.extend(getvar('CFLAGS').split())
-        print(' '.join(flags))
-
-    elif opt in ('--libs', '--ldflags'):
-        libs = ['-lpython' + pyver + sys.abiflags]
-        libs += getvar('LIBS').split()
-        libs += getvar('SYSLIBS').split()
-        # add the prefix/lib/pythonX.Y/config dir, but only if there is no
-        # shared library in prefix/lib/.
-        if opt == '--ldflags':
-            if not getvar('Py_ENABLE_SHARED'):
-                libs.insert(0, '-L' + getvar('LIBPL'))
-        print(' '.join(libs))
-
-    elif opt == '--extension-suffix':
-        print(sysconfig.get_config_var('EXT_SUFFIX'))
-
-    elif opt == '--abiflags':
-        print(sys.abiflags)
-
-    elif opt == '--configdir':
-        print(sysconfig.get_config_var('LIBPL'))

### 2020-02-24 EGT-RL/.conda/lib/tclConfig.sh

@@ -1,169 +1,0 @@
-# tclConfig.sh --
-#
-# This shell script (for sh) is generated automatically by Tcl's
-# configure script.  It will create shell variables for most of
-# the configuration options discovered by the configure script.
-# This script is intended to be included by the configure scripts
-# for Tcl extensions so that they don't have to figure this all
-# out for themselves.
-#
-# The information in this file is specific to a single platform.
-
-# Tcl's version number.
-TCL_VERSION='8.6'
-TCL_MAJOR_VERSION='8'
-TCL_MINOR_VERSION='6'
-TCL_PATCH_LEVEL='.8'
-
-# C compiler to use for compilation.
-TCL_CC='x86_64-apple-darwin13.4.0-clang'
-
-# -D flags for use with the C compiler.
-TCL_DEFS='-DPACKAGE_NAME=\"tcl\" -DPACKAGE_TARNAME=\"tcl\" -DPACKAGE_VERSION=\"8.6\" -DPACKAGE_STRING=\"tcl\ 8.6\" -DPACKAGE_BUGREPORT=\"\" -DSTDC_HEADERS=1 -DHAVE_SYS_TYPES_H=1 -DHAVE_SYS_STAT_H=1 -DHAVE_STDLIB_H=1 -DHAVE_STRING_H=1 -DHAVE_MEMORY_H=1 -DHAVE_STRINGS_H=1 -DHAVE_INTTYPES_H=1 -DHAVE_STDINT_H=1 -DHAVE_UNISTD_H=1 -DNO_VALUES_H=1 -DHAVE_SYS_PARAM_H=1 -DUSE_THREAD_ALLOC=1 -D_REENTRANT=1 -D_THREAD_SAFE=1 -DHAVE_PTHREAD_ATTR_SETSTACKSIZE=1 -DHAVE_PTHREAD_ATFORK=1 -DTCL_THREADS=1 -DTCL_CFGVAL_ENCODING=\"iso8859-1\" -DHAVE_ZLIB=1 -DMODULE_SCOPE=extern\ __attribute__\(\(__visibility__\(\"hidden\"\)\)\) -DHAVE_HIDDEN=1 -DMAC_OSX_TCL=1 -DHAVE_COREFOUNDATION=1 -DTCL_CFG_DO64BIT=1 -DHAVE_CAST
[…]

### 2020-02-24 EGT-RL/.conda/lib/tkConfig.sh

@@ -1,97 +1,0 @@
-# tkConfig.sh --
-#
-# This shell script (for sh) is generated automatically by Tk's
-# configure script.  It will create shell variables for most of
-# the configuration options discovered by the configure script.
-# This script is intended to be included by the configure scripts
-# for Tk extensions so that they don't have to figure this all
-# out for themselves.  This file does not duplicate information
-# already provided by tclConfig.sh, so you may need to use that
-# file in addition to this one.
-#
-# The information in this file is specific to a single platform.
-
-# Tk's version number.
-TK_VERSION='8.6'
-TK_MAJOR_VERSION='8'
-TK_MINOR_VERSION='6'
-TK_PATCH_LEVEL='.8'
-
-# -D flags for use with the C compiler.
[…]

### 2020-02-24 EGT-RL/.conda/ssl/misc/CA.pl

@@ -1,215 +1,0 @@
-#!/Users/aamalh/Desktop/EGT-RL/.conda/bin/perl
-# Copyright 2000-2018 The OpenSSL Project Authors. All Rights Reserved.
-#
-# Licensed under the OpenSSL license (the "License").  You may not use
-# this file except in compliance with the License.  You can obtain a copy
-# in the file LICENSE in the source distribution or at
-# https://www.openssl.org/source/license.html
-
-#
-# Wrapper around the ca to make it easier to use
-#
-# WARNING: do not edit!
-# Generated by Makefile from apps/CA.pl.in
-
-use strict;
-use warnings;
-
-my $openssl = "openssl";
-if(defined $ENV{'OPENSSL'}) {
-    $openssl = $ENV{'OPENSSL'};
-} else {
-    $ENV{'OPENSSL'} = $openssl;
-}
-
-my $verbose = 1;
-
-my $OPENSSL_CONFIG = $ENV{"OPENSSL_CONFIG"} || "";
-my $DAYS = "-days 365";
-my $CADAYS = "-days 1095";	# 3 years
-my $REQ = "$openssl req $OPENSSL_CONFIG";
-my $CA = "$openssl ca $OPENSSL_CONFIG";
-my $VERIFY = "$openssl verify";
-my $X509 = "$openssl x509";
-my $PKCS12 = "$openssl pkcs12";
-
-# default openssl.cnf file has setup as per the following
-my $CATOP = "./demoCA";
-my $CAKEY = "cakey.pem";
-my $CAREQ = "careq.pem";
-my $CACERT = "cacert.pem";
-my $CACRL = "crl.pem";
-my $DIRMODE = 0777;
-
-my $NEWKEY = "newkey.pem";
-my $NEWREQ = "newreq.pem";
-my $NEWCERT = "newcert.pem";
-my $NEWP12 = "newcert.p12";
-my $RET = 0;
-my $WHAT = shift @ARGV || "";
-my @OPENSSL_CMDS = ("req", "ca", "pkcs12", "x509", "verify");
-my %EXTRA = extra_args(\@ARGV, "-extra-");
-my $FILE;
-
-sub extra_args {
-    my ($args_ref, $arg_prefix) = @_;
-    my %eargs = map {
-	if ($_ < $#$args_ref) {
-	    my ($arg, $value) = splice(@$args_ref, $_, 2);
-	    $arg =~ s/$arg_prefix//;
-	    ($arg, $value);
-	} else {
-	    ();
-	}
[…]

### 2020-02-24 EGT-RL/.conda/ssl/misc/tsget.pl

@@ -1,200 +1,0 @@
-#!/Users/aamalh/Desktop/EGT-RL/.conda/bin/perl
-# Copyright 2002-2018 The OpenSSL Project Authors. All Rights Reserved.
-# Copyright (c) 2002 The OpenTSA Project. All rights reserved.
-#
-# Licensed under the OpenSSL license (the "License").  You may not use
-# this file except in compliance with the License.  You can obtain a copy
-# in the file LICENSE in the source distribution or at
-# https://www.openssl.org/source/license.html
-
-use strict;
-use IO::Handle;
-use Getopt::Std;
-use File::Basename;
-use WWW::Curl::Easy;
-
-use vars qw(%options);
-
-# Callback for reading the body.
-sub read_body {
-    my ($maxlength, $state) = @_;
-    my $return_data = "";
-    my $data_len = length ${$state->{data}};
-    if ($state->{bytes} < $data_len) {
-	$data_len = $data_len - $state->{bytes};
-	$data_len = $maxlength if $data_len > $maxlength;
-	$return_data = substr ${$state->{data}}, $state->{bytes}, $data_len;
-	$state->{bytes} += $data_len;
-    }
-    return $return_data;
-}
-
-# Callback for writing the body into a variable.
-sub write_body {
-    my ($data, $pointer) = @_;
-    ${$pointer} .= $data;
-    return length($data);
-}
-
-# Initialise a new Curl object.
-sub create_curl {
-    my $url = shift;
-
-    # Create Curl object.
-    my $curl = WWW::Curl::Easy::new();
-
-    # Error-handling related options.
-    $curl->setopt(CURLOPT_VERBOSE, 1) if $options{d};
-    $curl->setopt(CURLOPT_FAILONERROR, 1);
-    $curl->setopt(CURLOPT_USERAGENT,
-        "OpenTSA tsget.pl/openssl-1.1.1d");
-
-    # Options for POST method.
-    $curl->setopt(CURLOPT_UPLOAD, 1);
-    $curl->setopt(CURLOPT_CUSTOMREQUEST, "POST");
-    $curl->setopt(CURLOPT_HTTPHEADER,
-		["Content-Type: application/timestamp-query",
-		"Accept: application/timestamp-reply,application/timestamp-response"]);
-    $curl->setopt(CURLOPT_READFUNCTION, \&read_body);
-    $curl->setopt(CURLOPT_HEADERFUNCTION, sub { return length($_[0]); });
-
-    # Options for getting the result.
[…]

### 2020-02-24 EGT-RL/.history/MeanFieldSim_20200217134524.py

@@ -1,34 +1,0 @@
-import numpy as np
-from QLearner import QLearner
-from tqdm import tqdm
-
-nIter = 100
-numberOfAgents = 500
-numberofActions = 2
-numberofOpponents = int(0.5 * numberOfAgents)
-
-game = np.zeros((2, 2, 2))
-
-game[:, :, 0] = np.array([[3, 0], [0, 1]])
-game[:, :, 1] = np.array([[3, 5], [5, 1]])
-
-agentPopulation = [QLearner(r=1) for i in range(numberOfAgents)]
-
-for cIter in tqdm(range(nIter)):
-
-    for i in range(numberOfAgents):
-        agentPopulation[i].selectAction()
-
-    for i in range(numberOfAgents):
-        while agentPopulation[i].gamesPlayed < numberofOpponents:
-            for m in range(numberofOpponents):
-                o = i
-                while o == i:
-                    o = np.random.choice(list(range(10)))
-
-                agentPopulation[i].playGame(agentPopulation[o], game)
-
-    [agent.qUpdate() for agent in agentPopulation]
-
-if __name__ == "__main__":
-    rationality = np.linspace(0, 10, 0.1)

### 2020-02-24 EGT-RL/.history/Tuyls_20200110155212.py

@@ -1,11 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-alpha = 1
-A = np.array([[1, 1], [1, 1]])
-tau = 1
-
-
-# pure strategies look like 1) (1, 0) and (1, 0) or 2) (1, 0) and (0, 1) or 3) (0, 1) and (1, 0) or 4) (0, 1) and (0, 1)
-
-# Then, the population will look like a mixture of all of these pure strategies. If we take the expectation on each of these

### 2020-02-24 EGT-RL/.history/Tuyls_20200110160241.py

@@ -1,25 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-alpha = 1
-A = np.array([[1, 1], [1, 1]])
-tau = 1
-
-
-# pure strategies look like 1) (1, 0) and (1, 0) or 2) (1, 0) and (0, 1) or 3) (0, 1) and (1, 0) or 
-# 4) (0, 1) and (0, 1)
-
-# Then, the population will look like a mixture of all of these pure strategies. If we take the
-# expectation on each of these, then that might end up looking like the mixed strategies that we're
-# going for
-
-# We will also need to define a population x to begin with so I'm not entirely sure where they got
-# that from
-
-
-
-x = np.array([[1, 0], [0, 1]])
-y = np.array([[1, 0], [0, 1]])
-
-A = np.array([[1, 5], [0, 3]])
-B = np.array([[1, 0], [5, 3]])

### 2020-02-24 EGT-RL/.history/Tuyls_20200110180534.py

@@ -1,26 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-alpha = 1
-A = np.array([1, 5])
-tau = 1
-
-
-# pure strategies look like 1) (1, 0) and (1, 0) or 2) (1, 0) and (0, 1) or 3) (0, 1) and (1, 0) or 
-# 4) (0, 1) and (0, 1)
-
-# Then, the population will look like a mixture of all of these pure strategies. If we take the
-# expectation on each of these, then that might end up looking like the mixed strategies that we're
-# going for
-
-# We will also need to define a population x to begin with so I'm not entirely sure where they got
-# that from
-
-x = np.linspace(0, 1, 50)
-
-x_dot = lambda a: ((A[0] * a) - np.dot([a, 1-a], A@[a, 1-a])) * a
-
-X_DOT = [x_dot(a) for a in x]
-
-plt.plot(x, X_DOT, 'r-')
-plt.show()

### 2020-02-24 EGT-RL/.history/Tuyls_20200110180543.py

@@ -1,25 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-alpha = 1
-A = np.array([1, 5])
-tau = 1
-
-# pure strategies look like 1) (1, 0) and (1, 0) or 2) (1, 0) and (0, 1) or 3) (0, 1) and (1, 0) or 
-# 4) (0, 1) and (0, 1)
-
-# Then, the population will look like a mixture of all of these pure strategies. If we take the
-# expectation on each of these, then that might end up looking like the mixed strategies that we're
-# going for
-
-# We will also need to define a population x to begin with so I'm not entirely sure where they got
-# that from
-
-x = np.linspace(0, 1, 50)
-
-x_dot = lambda a: ((A[0] * a) - np.dot([a, 1-a], A@[a, 1-a])) * a
-
-X_DOT = [x_dot(a) for a in x]
-
-plt.plot(x, X_DOT, 'r-')
-plt.show()

### 2020-02-24 EGT-RL/.history/Tuyls_20200110181116.py

@@ -1,25 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-alpha = 1
-A = np.array([1, 5])
-tau = 1
-
-# pure strategies look like 1) (1, 0) and (1, 0) or 2) (1, 0) and (0, 1) or 3) (0, 1) and (1, 0) or 
-# 4) (0, 1) and (0, 1)
-
-# Then, the population will look like a mixture of all of these pure strategies. If we take the
-# expectation on each of these, then that might end up looking like the mixed strategies that we're
-# going for
-
-# We will also need to define a population x to begin with so I'm not entirely sure where they got
-# that from
-
-x = np.linspace(0, 1, 50)
-
-x_dot = lambda a: ((A[0] * a) - np.dot([a, 1-a], A*[a, 1-a])) * a
-
-X_DOT = [x_dot(a) for a in x]
-
-plt.plot(x, X_DOT, 'r-')
-plt.show()

### 2020-02-24 EGT-RL/MeanFieldDyn.py

@@ -1,0 +1,31 @@
+import numpy as np
+from pClass import p
+from tqdm import tqdm
+
+## Set up code parameters
+tau = 10
+
+## Set up game
+game = np.zeros((2, 2, 2))
+game[:, :, 0] = np.array([[3, 0], [5, 1]])
+game[:, :, 1] = np.array([[3, 5], [0, 1]])
+
+nAgents = 1e3
+qValues = np.random.rand(2, int(nAgents))
+meanStrategy = [np.mean([np.exp(tau * qValues[0, i])/(np.exp(tau * qValues[0, i]) + np.exp(tau * qValues[1, i])) for i in range(int(nAgents))]), np.mean([np.exp(tau * qValues[1, i])/(np.exp(tau * qValues[0, i]) + np.exp(tau * qValues[1, i])) for i in range(int(nAgents))])]
+
+## Generate pInit
+
+P = p(game, meanStrategy=meanStrategy, initP=True, initQ=qValues)
+
+for t in tqdm(np.arange(0, 0.5, P.deltaT)):
+
+    meanStrategy = np.zeros(2)
+    for q1 in np.arange(0, 1, P.deltaQ):
+        for q2 in np.arange(0, 1, P.deltaQ):
+            meanStrategy[0] += np.exp(P.tau * (q1 + P.deltaQ/2))/(np.exp(P.tau * (q1 + P.deltaQ/2)) + np.exp(P.tau * (q2 + P.deltaQ/2))) * P([q1, q2])
+
+            meanStrategy[1] += np.exp(P.tau * (q2 + P.deltaQ/2))/(np.exp(P.tau * (q1 + P.deltaQ/2)) + np.exp(P.tau * (q2 + P.deltaQ/2))) * P([q1, q2])
+    print(sum(meanStrategy))
+
+    P = p(game, oldP=P, meanStrategy=meanStrategy)

### 2020-02-24 EGT-RL/pClass.py

@@ -1,0 +1,37 @@
+import numpy as np
+
+
+class p():
+    def __init__(self, game, oldP = None,  meanStrategy=None, initP = False, initQ = None):
+        self.tau = 10
+        self.eta = 1
+        self.game = game
+
+        self.deltaT = 1e-2
+        self.deltaQ = 1e-2
+
+        self.oldP = oldP
+        self.initP = initP
+        self.initQ = initQ
+        self.x = meanStrategy
+        if self.initP:
+            self.v = lambda j, Q, x: 0
+        else:
+            self.v = lambda j, Q, x: self.eta * np.exp(self.tau * Q[j])/(np.exp(self.tau * Q[j]) + np.exp(self.tau * Q[1 - j])) * ((self.game[:, :, 0] @ x)[j] - Q[j])
+
+    def __call__(self, Q):
+        if (self.initP):
+            return len(np.where((self.initQ[0, :] < Q[0] + self.deltaQ) & (self.initQ[0, :] > Q[0]) & (self.initQ[1, :] < Q[1] + self.deltaQ) & (self.initQ[1, :] > Q[1]))[0])/self.initQ.shape[1]
+            
+        else:
+            return self.oldP(Q) + self.oldP.pDot(Q) * self.deltaT
+
+    def pDot(self, Q):
+        if self.initP:
+            return 0
+        else:
+            return -1 * (self.oldP([Q[0] + self.deltaQ, Q[1]]) * self.oldP.v(0, [Q[0] + self.deltaQ, Q[1]], self.oldP.x) -
+                     self.oldP(Q) * self.oldP.v(0, Q, self.oldP.x))/self.deltaQ - \
+                    (self.oldP([Q[0], Q[1] + self.deltaQ]) * self.oldP.v(1, [Q[0], Q[1] + self.deltaQ], self.oldP.x) -
+                     self.oldP(Q) * self.oldP.v(1, Q, self.oldP.x))/self.deltaQ
+

### 2020-02-24 MeanFieldDyn.m
Added MeanField Simulation

@@ -1,28 +1,55 @@
 %%
 clear
+
+global deltaQ;
+global deltaT;
+global tau;
+global eta;
+
+deltaQ = 1e-2;
+deltaT = 1e-2;
 %% Set up game
+
 tau = 10;
 eta = 1;
 
 game = zeros(2, 2, 3);
 game(:, :, 1) = [3, 0; 0, 1];
 game(:, :, 2) = [3, 5; 5, 1];
-nAgents = 1e4;
+nAgents = 1e3;
 qValues = rand(2, nAgents);
 
-%% Determine x(t)
+%% Determine p_init
 
-x = [0; 0];
-for q1 = 0:deltaQ:(1 - deltaQ)
-for q2 = 0:deltaQ:(1 - deltaQ)
-p = nnz(find(((qValues(1, :) > q1) & (qValues(1, :) < (q1 + deltaQ)) & (qValues(2, :) > q2) & (qValues(2, :) < (q2 + deltaQ)))))/nAgents;
-x(1) = x(1) + ((exp(tau * (q1 + deltaQ/2))/(exp(tau * (q1 + deltaQ/2)) + exp(tau * (q2 + deltaQ/2)))) * p);
-x(2) = x(2) + ((exp(tau * (q2 + deltaQ/2))/(exp(tau * (q1 + deltaQ/2)) + exp(tau * (q2 + deltaQ/2)))) * p);
-end
-end
+p = @(Q)  nnz(find(((qValues(1, :) > Q(1)) & (qValues(1, :) < (Q(1) + deltaQ)) & (qValues(2, :) > Q(2)) & (qValues(2, :) < (Q(2) + deltaQ)))))/nAgents;
 
 %% Determine v(t)
 
-v= [0;0];
+v = @(Q, X) eta/(exp(tau * (Q(1))) + exp(tau * (Q(2)))) * [exp(tau * (Q(1))); exp(tau * (Q(2)))] .* (game(:, :, 2) * X - Q);
 
-v(1) = eta * (exp(tau * (q1 + deltaQ/2))/(exp(tau * (q1 + deltaQ/2)))) * (
+%% Determine p_dot
+
+pdot = @(Q, X) -1 * sum((p(Q + deltaQ) * v(Q + deltaQ, X) - p(Q) * v(Q, X))./deltaQ);
+
+%% Update p(t)
+
+for t = 0:deltaT:10
+   x = [0; 0];            
[…]

### 2020-02-24 MeanFieldDynwithMat.m

@@ -1,0 +1,62 @@
+%%
+clear
+
+global deltaQ;
+global deltaT;
+global tau;
+global eta;
+
+deltaQ = 1e-2;
+iterQ = 0:deltaQ:(1-deltaQ);
+deltaT = 1e-2;
+%% Set up game
+
+tau = 10;
+eta = 1;
+
+game = zeros(2, 2, 3);
+game(:, :, 1) = [3, 0; 0, 1];
+game(:, :, 2) = [3, 5; 5, 1];
+nAgents = 1e3;
+qValues = rand(2, nAgents);
+
+
+%% determine pInit
+p = @(Q)  nnz(find(((qValues(1, :) > Q(1)) & (qValues(1, :) < (Q(1) + deltaQ)) & (qValues(2, :) > Q(2)) & (qValues(2, :) < (Q(2) + deltaQ)))))/nAgents;
+
+pMAT = zeros(1/deltaQ, 1/deltaQ);
+for q1 = 1:1/deltaQ
+    for q2 = 1:1/deltaQ
+        pMAT(q1, q2) = p([iterQ(q1); iterQ(q2)]);
+    end
+end
+%%
+x = [0; 0];            
+for q1 = 1:1/deltaQ
+    for q2 = 1:1/deltaQ
+        x(1) = x(1) + ((exp(tau * (iterQ(q1) + deltaQ/2))/(exp(tau * (iterQ(q1) + deltaQ/2)) + exp(tau * (iterQ(q2) + deltaQ/2)))) * pMAT(q1, q2));
+        x(2) = x(2) + ((exp(tau * (iterQ(q2) + deltaQ/2))/(exp(tau * (iterQ(q1) + deltaQ/2)) + exp(tau * (iterQ(q2) + deltaQ/2)))) * pMAT(q1, q2));
+    end
+end
+
+xCurrent = x;
+
+%%
+
+v = @(Q, X) eta/(exp(tau * (Q(1))) + exp(tau * (Q(2)))) * [exp(tau * (Q(1))); exp(tau * (Q(2)))] .* (game(:, :, 1) * X - Q);
+
+
+
+
+
[…]

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309091335.tex
Ran Parameter Sweep

\documentclass{article}
\usepackage{xcolor}
\usepackage[margin=1in,letterpaper]{geometry}
\newcommand\NOTE[1]{\textcolor{purple}{#1}}

\title{Assigning Confidence to Clustering Algorithms}
\author{Aamal Hussain}

\begin{document}
    \maketitle

    \begin{itemize}
        \item Clustering algorithms in general, with a focus on route clustering
        \item Adding confidence bounds to clustering algorithms
    \end{itemize}

    \section{Clustering of time series data: A survey}

    In this case, the data features changes over time. These are divided into five categories

    \begin{enumerate}
        \item Partitioning: Constructs \[k \leq n\] partitions of the n data tuples. Each partition represents a cluster containing at least one object. This allows for objects to be in clusters with different degrees \NOTE{Allows for the use of fuzzy methods to calculate routes off fuzzy sets}.
        \begin{itemize}
            \item Fuzzy c-means
            \item Fuzzy c-medioids
        \end{itemize}
        \item Hierarchical: Groups data into trees of clusters. 
        \item Density Based: Grow a cluster as long as the density in the neighbourhood exceeds some threshold
        \item Grid based: Quantise the space into cells and perform clustering on these cells
        \item Model Based: Assumes a model for the data \NOTE{Would allow for Bayesian clustering, which would allow for the 'no class' property to be considered.} 
    \end{enumerate}

    Clustering for time series data the following methods are mentioned

    \begin{enumerate}
        \item Relocation clustering: Uses a particular criterion function and works by comparing the resulting function with members attached in different clusters. \NOTE{This would also allow for the 'no class' option to be considered.} This method works only when the time series data are of equal length.
        \item Agglomerative Hierarchical: Places each object into its own cluster and then merges these into larger clusters by trying to minimise the sum of squares variance. This method falters once clusters are chosen since it is unable to adjust
        \item Fuzzy k-means considers using a fuzzy membership scheme for partitions. By warping it is possible to make these more appropriate for time series data of unequal length, but then the distance metric needs to account for this.
    \end{enumerate}
\end{document}

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309100903.tex
Ran Parameter Sweep

--- 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309091335.tex
@@
     \begin{enumerate}
-        \item Partitioning: Constructs \[k \leq n\] partitions of the n data tuples.
+        \item Partitioning: Constructs $k \leq n$ partitions of the n data tuples.
 Each partition represents a cluster containing at least one object.
@@
     \end{enumerate}
+
+    \NOTE{The major problem here concerns the metric used to judge the distance between two paths.
+This is particularly a problem in route clustering as we have to take into account issues of varying traffic conditions etc.}
+
+    The modalities for distance/similarity measures which are proposed are
+
+    \begin{itemize}
+        \item Euclidean distance (\NOTE{Obviously if time is not taken into account this is shite})
+        \item Cross correlation coefficients (such as Pearson's rank etc.). Can also be a function of time
+        \item Short time series distance (STS): In which each time series is considered as a piecewise linear function
+        \item Dynamic time warping distance. First align the time series and then use Euclidean distance
+        \item KL divergence (\NOTE{I quite like this one if the data sets are somewhat aligned first})
+        \item J divergence/Chernoff divergence
+    \end{itemize}
+
 \end{document}

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309110212.tex
Ran Parameter Sweep

--- 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309100903.tex
@@
         \item Euclidean distance (\NOTE{Obviously if time is not taken into account this is shite})
-        \item Cross correlation coefficients (such as Pearson's rank etc.). Can also be a function of time
+        \item Cross correlation coefficients (such as Pearson's rank etc.).
+Can also be a function of time (\NOTE{Can also use these as the metric which considers the confidence of attaching a route to a cluster.})
         \item Short time series distance (STS): In which each time series is considered as a piecewise linear function
@@
 
+    \NOTE{The paper then suggests methods for clustering time series data.
+I focus on the ones which use the raw time series data since that's what we have.
+(The others are feature based approaches and model based approaches).}
+
+    \section{Adding Confidence to Gene Expression Clustering}
+
+    In this study, the authors consider how to cluster gene expression data which contains large amounts of random variation.
+\NOTE{I anticipate that this would be the same case in the GPS data which will be subject to noise.} Importantly, they are able to assign a statistical significance metric when clustering to improve the reliability of the cluster.
+Previous work relies on doing this by counting how many times a gene is assigned to the same cluster (\NOTE{seems long}).
+Other recent work which has used GWN to perturb data assigns a perturbed cluster to the original iff it contains a majority of elements in common with the original cluster.
+(\NOTE{If there is a way to extract features from the GPS data, we could consider this as a method of evaluation, e.g.
+if routes passed under the same 10 bridges}).
+
 \end{document}

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309110711.tex
Ran Parameter Sweep

--- 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309110212.tex
@@
 
+    Their dissimilarity metric, known as the 'Munneke metric' is able to take into account dissimilarity based on the magnitude and the pattern of gene expression (\NOTE{Perhaps such a combination of metrics would also be useful in route clustering}).
+Importantly, however, this metric provides a strong confidence measure of the clustering algorithm as it provides a non-negative real value to measure the dissimilarity between the data and a particular cluster.
+
 \end{document}

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309113818.tex
Ran Parameter Sweep

--- 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309110711.tex
@@
 
+    \section{Correlation based dynamic time warping of multivariate time series}
+
+    In this paper they also develop a similarity metric called correlation based dynamic time warping.
+This is particularly handy for multivariate time series data which presents some correlation between the variables.
+Then there is the standard 'our algorithm outperforms others'.
+
+    \section{A distance based time series classification framework}
+
+    In this, they develop a toolkit which contains different methods for time series
+
 \end{document}

### 2020-03-10 EGT-RL/MeanFieldSim/ParameterSweep.py

@@ -17,23 +17,30 @@ from MAgame1202 import runSim
 dirName = 'ParameterSweep Results'
 os.makedirs(dirName)
 
-nSimulations = 2
+nSimulations = 1
 gameName = 'PD'
 
 allMeanTraj = []
 allParams = []
 
+converged = []
 tau = 0.01
+
 for r in tqdm(np.linspace(0, 1, num=100)):
-        
+    for gamma in np.linspace(-1, 0, num=100):
+
          parameters = {'tau': tau, 'lr': r * tau}
          
          allParams.append([tau, r])
          
-         allxBar = runSim(nSimulations, parameters, gameName)
-         allMeanTraj.append(np.array(np.mean(np.array(allxBar).squeeze(), axis = 0)))
+         allxBar, converged = runSim(nSimulations, parameters, gamma)
+         allMeanTraj.append(np.array(allxBar))
 
-         with open(dirName + '/parameterSweep_tau_{0}_r_{1}.txt'.format(tau, r), 'w') as f:
+         # allMeanTraj.append(np.array(np.mean(np.array(allxBar).squeeze(), axis = 0)))
+
+         with open(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma), 'w') as f:
+            f.write('r: {0}, gamma: {1} \n'.format(r, gamma))
+            f.write('Converged: {0} \n'.format(str(converged)))
             for probs in allMeanTraj[-1]:
                 f.write(str(probs) + '\n')
             f.close()

### 2020-03-10 EGT-RL/_NIPS2019_code/MAS12/MAgame1202.py

@@ -13,6 +13,7 @@ import sys
 import os
 import numpy as np
 from collections import Counter
+import matplotlib.pyplot as plt
 
 from tqdm import tqdm
 sys.path.append('../MAS_Environments')
@@ -33,7 +34,7 @@ from GameAssignment01 import GameAssignment01
 #gameName = 'SH'
 #gameName = 'HD'
 
-def runSim(Nsim, parameters, gameName):
+def runSim(Nsim, parameters, gamma):
     
     T = 50
     Nagent = 1000
@@ -57,29 +58,22 @@ def runSim(Nsim, parameters, gameName):
     
     reward1s = {}
     reward2s = {}
+
+    cov = np.eye(8)
+    cov[:4, 4:] = np.eye(4) * gamma
+    cov[4:, :4] = np.eye(4) * gamma
+
+    rewards = np.random.multivariate_normal(np.zeros(8), cov=cov)
+
+    reward1s = rewards[0:4].reshape((2, 2))
+    reward2s = rewards[4:].reshape((2, 2)).T
     
-    # PD
-    reward1s['PD'] = np.array([[3, 0], [5, 1]])
-    reward2s['PD'] = np.array([[3, 5], [0, 1]])
-    
-    # CE2
-    reward1s['CE2'] = -1*np.ones((Nact,Nact))+2*np.eye(Nact)
-    reward2s['CE2'] = -1*np.ones((Nact,Nact))+2*np.eye(Nact)
-    
-    # SH
-    reward1s['SH'] = np.array([[1, 2], [0, 3]])
-    reward2s['SH'] = np.array([[1, 0], [2, 3]])
-    
-    # HD
-    reward1s['HD'] = np.array([[1, 0], [2, -1]])
-    reward2s['HD'] = np.array([[1, 2], [0, -1]])
-    
-    rMin = np.amin(reward1s[gameName])  #min and max rewards from the game, will help in defining the initial Q distribution
-    rMax = np.amax(reward1s[gameName])
+    rMin = np.amin(reward1s)  #min and max rewards from the game, will help in defining the initial Q distribution
+    rMax = np.amax(reward1s)
     strInitPara = initPara.split(',')
     intInitPara = [int(e) for e in strInitPara]
     
-    env = Environment02(Nact, reward1s[gameName], reward2s[gameName])
+    env = Environment02(Nact, reward1s, reward2s)
     ga = GameAssignment01()
     
     allxBar = []
@@ -105,12 +99,25 @@ def runSim(Nsim, parameters, gameName):
[…]

### 2020-03-27 Literature Review/Literature Review - Revised/sections/DynMARL.tex
Completed initial ParameterSweep

@@
 
+    \section{Applications}
+
+    The ability to predict learning is crucial towards understanding the behaviour of learning
+    agents. It provides a qualitative understanding of the differences between algorithms and allows
+    for a better understanding of the conditions under which each algorithm is appropriate, as well
+    as how to choose parameters in such a way to achieve desired effects. It can be argued
+    that the above methods presume some knowledge of the payoff matrices in order to generate these
+    predictions. However, a re
+
 \end{document}

### 2020-03-27 Royal Mail/ConfidenceBounds.tex
Completed initial ParameterSweep

\documentclass{report}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[margin=1in,letterpaper]{geometry}
\newcommand\NOTE[1]{\textcolor{purple}{#1}}

\title{Assigning Confidence to Clustering Algorithms}
\author{Aamal Hussain}

\begin{document}
    \maketitle

    \begin{itemize}
        \item Clustering algorithms in general, with a focus on route clustering
        \item Adding confidence bounds to clustering algorithms
    \end{itemize}

    \section{Clustering of time series data: A survey}

    In this case, the data features changes over time. These are divided into five categories

    \begin{enumerate}
        \item Partitioning: Constructs $k \leq n$ partitions of the n data tuples. Each partition represents a cluster containing at least one object. This allows for objects to be in clusters with different degrees \NOTE{Allows for the use of fuzzy methods to calculate routes off fuzzy sets}.
        \begin{itemize}
            \item Fuzzy c-means
            \item Fuzzy c-medioids
        \end{itemize}
        \item Hierarchical: Groups data into trees of clusters. 
        \item Density Based: Grow a cluster as long as the density in the neighbourhood exceeds some threshold
        \item Grid based: Quantise the space into cells and perform clustering on these cells
        \item Model Based: Assumes a model for the data \NOTE{Would allow for Bayesian clustering, which would allow for the 'no class' property to be considered.} 
    \end{enumerate}

    Clustering for time series data the following methods are mentioned

    \begin{enumerate}
        \item Relocation clustering: Uses a particular criterion function and works by comparing the resulting function with members attached in different clusters. \NOTE{This would also allow for the 'no class' option to be considered.} This method works only when the time series data are of equal length.
        \item Agglomerative Hierarchical: Places each object into its own cluster and then merges these into larger clusters by trying to minimise the sum of squares variance. This method falters once clusters are chosen since it is unable to adjust
        \item Fuzzy k-means considers using a fuzzy membership scheme for partitions. By warping it is possible to make these more appropriate for time series data of unequal length, but then the distance metric needs to account for this.
    \end{enumerate}

    \NOTE{The major problem here concerns the metric used to judge the distance between two paths. This is particularly a problem in route clustering as we have to take into account issues of varying traffic conditions etc.}

    The modalities for distance/similarity measures which are proposed are

    \begin{itemize}
        \item Euclidean distance (\NOTE{Obviously if time is not taken into account this is shite})
        \item Cross correlation coefficients (such as Pearson's rank etc.). Can also be a function of time (\NOTE{Can also use these as the metric which considers the confidence of attaching a route to a cluster.})
        \item Short time series distance (STS): In which each time series is considered as a piecewise linear function
        \item Dynamic time warping distance. First align the time series and then use Euclidean distance
        \item KL divergence (\NOTE{I quite like this one if the data sets are somewhat aligned first})
        \item J divergence/Chernoff divergence
    \end{itemize}

    \NOTE{The paper then suggests methods for clustering time series data. I focus on the ones which use the raw time series data since that's what we have. (The others are feature based approaches and model based approaches).}

    \section{Adding Confidence to Gene Expression Clustering}

    In this study, the authors consider how to cluster gene expression data which contains large amounts of random variation. \NOTE{I anticipate that this would be the same case in the GPS data which will be subject to noise.} Importantly, they are able to assign a statistical significance metric when clustering to improve the reliability of the cluster. Previous work relies on doing this by counting how many times a gene is assigned to the same cluster (\NOTE{seems long}). Other recent work which has used GWN to perturb data assigns a perturbed cluster to the original iff it contains a majority of elements in common with the original cluster. (\NOTE{If there is a way to extract features from the GPS data, we could consider this as a method of evaluation, e.g. if routes passed under the same 10 bridges}).

    Their dissimilarity metric, known as the 'Munneke metric' is able to take into account dissimilarity based on the magnitude and the pattern of gene expression (\NOTE{Perhaps such a combination of metrics would also be useful in route clustering}). Importantly, however, this metric provides a strong confidence measure of the clustering algorithm as it provides a non-negative real value to measure the dissimilarity between the data and a particular cluster.

    \section{Correlation based dynamic time warping of multivariate time series}

    In this paper they also develop a similarity metric called correlation based dynamic time warping. This is particularly handy for multivariate time series data which presents some correlation between the variables. Then there is the standard 'our algorithm outperforms others'.

    \section{Hierarchical Clustering Given Confidence Intervals of Metric Distances}

    They consider the case where the exact dissimilarity between two sets of data lie within some interval. The types of clustering algorithms which are currently available are

    \begin{itemize}
        \item Exclusive clustering: Only belongs in one cluster (e.g. k-means)
        \item Overlapping clustering: Belongs to multiple clusters with degree of membership (e.g. fuzzy means)
        \item Hierarchical clustering: Considers a family of partitions which are indexed by a connectivity parameter
        \item Probabilistic clustering which takes a probabilistic approach (Mixture of Gaussians)
    \end{itemize}

    Axiomatic hierarchical clustering is a sub-group in which algorithms must satisfy reasonable axioms. E.g.

    \begin{itemize}
        \item Value: Nodes form a single cluster determine by their distance
        \item Transformation: A space which is uniformly dominated by another space should have clusters which are uniformly dominated
    \end{itemize}

    The advantage of this method is that it takes into account the uncertainty in the metric itself and the interval effectively becomes the confidence of the clustering algorithm.

    They apply this method on moving point data \NOTE{(which shows its applicability to the problem in question)} and show that it is able to successfully determine the underlying clusters, although (as would be expected), the performance deteriorates with increasing distance intervals.

    \section{Scoring clustering solutions by their biological relevance}

    This study differs from the others in that it considers evaluating the performance of a clustering result after the algorithm is run. This essentially gives a method of assigning the confidence in the clustering algorithm once all the clusters are generated. The confidence is assigned based on prior knowledge and so some model is required for this to work. This model is given in the form of an attribute matrix whose rows correspond to data. The clusters $C_{1:n}$ are assigned to the data so that $a_{ij} = (a_{ij}^1 ...a_{ij}^p$ is the attribute vector of data point j in cluster i. Then the clustering of the data points is evaluated against A. \NOTE{It should be pointed out that this requires some prior understanding of the attributes of the data point and how they correspond to the cluster. In other words, a model is required for this to work.} In order to carry out the evaluation, an Analysis of Variance method is used This metric is given by

    \begin{equation}
        F_H = \frac{SSH/(l-1)}{SSE/(n-l)}
    \end{equation}

    where

    \begin{subequations}
    \begin{equation}
    SSH = \sum_{i = 1}^{l} s_i (\bar{a_i} - \bar{a})^2 \\
    \end{equation}

    \begin{equation}
    SSL = \sum_{i = 1}^l \sum_{j = 1}^{s_i} (a_{ij} - \bar{a_i})^2
    \end{equation}
    \end{subequations}

    Here, l is the number of population distibutions, $s_i = |C_i|$, $\bar{a_i}$ is the mean of the data points in cluster i and $\bar{a}$ is the total mean of all of the n elements.

    The evaluation is done as follows

    \begin{enumerate}
        \item Compute a linear combination of the attributes: Each data point is assigned a real-valued number by computing a weighted sum of each of its attributes. \NOTE{There is often not an a priori method for calculating these weights and so these will need to be determined at user preference.}

        \item Determine $-logp$ where p is the probability that all values in the projection have been taken from the same population

        \item Determine the sensitivity of the above metric to small modifications of the clustering solution. For a given solution, generate a group of perturbed clustering solutions by exchangin random pairs of data points across clusters. Determine the standard deviation of the above CQS metric. This will act as the confidence value.
    \end{enumerate}

    \section{clValid, an R package for cluster validation}

    This paper provides an introduction to a module which can be used for assessing the validity of clustering solutions. The method of validation used is user defined but falls into one of three categories:

    \begin{itemize}
        \item internal validation: takes only the dataset and clustering solution as input.
        \item Stability validation: considers the consistency of the clustering solution after small perturbations
        \item Biological validation: considers the ability to produce biologically relevant results. \NOTE{This would need to be replaced with considering information relevant to route clustering. Therefore, I do not focus on this one in the review}
    \end{itemize}

    \subsection{Internal Measures}

    The available measuers are:
    \begin{itemize}
        \item Connectivity: considers the extent to which observations are placed in the same cluster as their nearest neighbours.
        \item Silhouette Width: Considers the normalised average distance between the observation and others in the same cluster, as well as the distance between the observation and the nearest cluster. This metric results in a value between -1 and 1, where 1 denotes a perfect cluster. 
        \item Dunn Index: Considers the ratio of the smallest distance between observations which are not in the same cluster against the largest distance across clusters. 
    \end{itemize}

    \subsection{Stability measures}

    \begin{itemize}
        \item Average proportion of non-overlap (APN): First clusters based on the full data and then with a single column removed. The APN value considers the ration of numbers of data points which are still placed in the same cluster.
        \item Average distance: Measures the distance between observations placed in the same cluster when a single column is removed.
        \item Average Distance between Means: Distance between cluster centres when a column is removed
    \end{itemize}

    \NOTE{Handl et al. give a good review of internal measures}

    \chapter{Formal Write Up}

    \section{Clustering of time series data}

    To be specific, the problem that the data science team face regards clustering routes which is considered to be a form of time series data. As such, it is important that the method of clustering used is suited to this sort of problem. Methods which involve clustering time series data can largely be categorised into the following categories (as defined by \textbf{something et al.}) (GIVE EXAMPLES OF THESE TO SQUEEZE IN REFERENCES):

    \begin{enumerate}
        \item Partitioning: Divides the n data tuples into $k < n$ partitions, each of which represent a cluster containing at least one tuple. 
        \item Hierarchical: Groups data into trees of clusters and iteratively decides whether a new branch is required for each data tuple.
        \item Density Based: Clusters will continue to grow as long as the density of data tuples in the neighbourhood (in metric space) exceeds some threshold.
        \item Grid Based: Quantise the space into discrete cells and perform clustering on these cells independently.
        \item Model Based: Assumes a model for the data and assigns data tuples to these clusters based on the resulting agreement with the model.
    \end{enumerate}

    For the sake of brevity, I focus on the first two of these methods as they appear to be most relevant to the problem at hand.

    A common question which is expected to arise when new data arrives is whether the given tuple should be clustered within an existing cluster or whether it should be considered to be unique. To this end, Agglomerative Hierarchical methods (GIVE A REFERENCE) show particular promise. In this, each object is first placed into its own cluster. These clusters are then iteratively merged such that the sum of squares variance is minimised. Once this minimum is achieved the resulting clusters are chosen as the final solution. Note that it is possible to design hierarchical algorithms in such a manner that a maximum number of clusters can never be exceeded, i.e. the program terminates once a certain number of clusters is reached. This method gives each data tuple the opportunity to be classed as its own cluster and, in fact, if a route is completely unique, it should not be merged with another cluster. Whilst at first glance this seems to solve the aforementioned problem, it should be noted that when clusters are merged through the Agglomerative Hierarchical technique, they remain immutable and cannot be broken. Therefore, if a new data tuple arrives which requires that existing data tuples are merged into its cluster, then it may be necessary to run the algorithm from scratch. However, it is unlikely that this will be required often.

    A similar problem is that, often, routes will partially overlap with one another and therefore, they could be placed in clusters with different degrees rather than placed entirely in one. As mentioned in \textbf{Section 1.4}, Fuzzy clustering allows for this to be accounted for. However, with time series data, it is of particular importance that the metric be chosen to accurately compare routes with potential clusters. This is especially true when time series data is of inhomogeneous length. This will likely be the case with route clustering since the speed of all vehicles will not be the same at all times, due to varying traffic conditions. \textbf{This should probably be placed with Henrik's bit}

    In light of the issues surrounding the choice of distance measures, I provide a short review of potential metrics that can be used for time series data below. These are considered in further depth in \textbf{REF}.

    \begin{enumerate}
        \item Euclidean distance
        \item Cross correlation coefficients
        \item Short time series distance
        \item Dynamic time warping distance
        \item KL divergence
        \item J/Chernoff divergence
    \end{enumerate}

    \textbf{I'll go into more depth on these in the final write up}

    \section{Evaluation of clustering solutions}

    Alongside the clustering solution itself, the confidence in the solution must be considered. This gives the data science team an indication of the extent to which the solution can be trusted. In the literature, this problem has, for the most part, been explored in the context of gene expression clustering. Here, it is important for biological studies, that the clustering solutions provide some useful biological relavance. However, the ideas can be transferred towards route clustering which too contains large amounts of uncertainty and must hold geographical relevance.

    \textbf{More to come}
\end{document}

### 2020-03-27 EGT-RL/MeanFieldSim/ParameterSweep.py

@@ -15,9 +15,10 @@ from GameAssignment01 import GameAssignment01
 from MAgame1202 import runSim
 
 dirName = 'ParameterSweep Results'
-os.makedirs(dirName)
+if not os.path.exists(dirName):
+    os.makedirs(dirName)
 
-nSimulations = 1
+nSimulations = 5
 gameName = 'PD'
 
 allMeanTraj = []
@@ -26,21 +27,27 @@ allParams = []
 converged = []
 tau = 0.01
 
-for r in tqdm(np.linspace(0, 1, num=100)):
-    for gamma in np.linspace(-1, 0, num=100):
+for r in tqdm(np.linspace(0, 5, num=10)):
+    for gamma in np.linspace(-1, 1, num=10):
 
-         parameters = {'tau': tau, 'lr': r * tau}
-         
-         allParams.append([tau, r])
-         
-         allxBar, converged = runSim(nSimulations, parameters, gamma)
-         allMeanTraj.append(np.array(allxBar))
+        if not os.path.exists(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma)):
+             parameters = {'tau': tau, 'lr': r * tau}
 
-         # allMeanTraj.append(np.array(np.mean(np.array(allxBar).squeeze(), axis = 0)))
+             allParams.append([tau, r])
 
-         with open(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma), 'w') as f:
-            f.write('r: {0}, gamma: {1} \n'.format(r, gamma))
-            f.write('Converged: {0} \n'.format(str(converged)))
-            for probs in allMeanTraj[-1]:
-                f.write(str(probs) + '\n')
-            f.close()
+             meanConvergence = runSim(nSimulations, parameters, gamma)
+             # allMeanTraj.append(np.array(allxBar))
+
+             # allMeanTraj.append(np.array(np.mean(np.array(allxBar).squeeze(), axis = 0)))
+
+             with open(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma), 'w') as f:
+                f.write('r: {0}, gamma: {1} \n'.format(r, gamma))
+                f.write('Converged: {0} \n'.format(str(meanConvergence)))
+                # for probs in allMeanTraj[-1]:
+                #     f.write(str(probs) + '\n')
+                f.close()
+        else:
+            continue
+
+
+print('hi')

### 2020-03-27 EGT-RL/MeanFieldSim/readConvergence.py

@@ -1,0 +1,24 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+dirName = 'ParameterSweep Results'
+
+allmeanConvergence = np.zeros((10, 10))
+
+i = 0
+for r in tqdm(np.linspace(0, 5, num=10)):
+    j = 0
+    for gamma in np.linspace(-1, 1, num=10):
+        with open(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma), 'r') as f:
+            f.readline()
+            line = f.readline()
+            allmeanConvergence[i, 9 - j] = 1 - float(line[11:14])
+
+        j+=1
+    i+=1
+
+
+
+plt.imshow(allmeanConvergence.T, cmap='hot', interpolation='nearest')
+plt.show()

### 2020-03-27 EGT-RL/_NIPS2019_code/MAS12/MAgame1202.py

@@ -25,15 +25,6 @@ from Agent02 import Agent02
 from GameAssignment01 import GameAssignment01
 
 
-
-
-#epsilon = 0.2
-
-#gameName = 'PD'
-#gameName = 'CE2'
-#gameName = 'SH'
-#gameName = 'HD'
-
 def runSim(Nsim, parameters, gamma):
     
     T = 50
@@ -46,9 +37,9 @@ def runSim(Nsim, parameters, gamma):
     tau = parameters['tau']
     lr = parameters['lr']
     
-    initPara = '80,20,90,10' #Beta distribution parameters. Makes it so that action 1 has a higher probability than action 2
+    #initPara = '80,20,90,10' #Beta distribution parameters. Makes it so that action 1 has a higher probability than action 2
     #initPara = '20,80,80,20'
-    #initPara = '50,50,5,5'
+    initPara = '50,50,5,5'
     
     
     # dirName = 'result_Q-boltzmann_%s-%s_lr%.2f_temp%.1f_N%d_m%d'%(gameName, initPara, lr, tau, Nagent, m)
@@ -79,7 +70,7 @@ def runSim(Nsim, parameters, gamma):
     allxBar = []
     
     # This will run multiple simulations so that the results can be averaged over
-    
+    allConverged = []
     for sim in range(Nsim):
         countActionT = []
         convergenceT = []
@@ -102,6 +93,8 @@ def runSim(Nsim, parameters, gamma):
 
         maxT = 1e3
         xbar = np.zeros(Nact, dtype=np.float)
+
+
 
         stopCond = False
         tol = 1e-6
@@ -160,20 +153,22 @@ def runSim(Nsim, parameters, gamma):
             stopCond = normStep < tol
             t += 1
 
+        print('r: {0}, gamma: {1}, Simulation: {2}, Converged: {3}'.format(lr/tau, gamma, sim, stopCond))
+        allConverged.append(stopCond)
         allxBar.append(xbarT)
 
-    return allxBar, stopCond
+    return np.mean(allConverged)
 
 
 if __name__ == "__main__":
-    nSim = 1
-    gamma = 1
+    nSim = 2
+    gamma = -.3
     
-    parameters = {'tau': 2, 'lr': 0.1}
+    parameters = {'tau': 0.01, 'lr': 0.005}
     
-    allxBar = runSim(nSim, parameters, gamma)
+    meanConverged = runSim(nSim, parameters, gamma)
     
[…]

### 2020-05-18 ChaoticDynamics/WriteUp.tex
Added Write Up for Tuyls' Dynamics

\documentclass{article}

\usepackage[margin=2cm]{geometry}

\title{Derivation Write Up}
\author{Aamal Hussain}

\begin{document}

	\maketitle

	\section{Introduction} % (fold)
	\label{sec:introduction}

	\begin{itemize}
			\item For use in Multi-Agent Reinforcement Learning
			\item Requirement to get some desired behaviours out of the system (e.g. conforming to
			predefined values or constraints)
			\item For this, it is required that we are able to predict the outcome of the learning
			behaviour
			\item Work done on determining the dynamics of MARL gives an indication of what
			solutions an algorithm will produce
			\item We can use this, alongside stability theory, to understand the nature of the games
			which result in stable behaviours and which result in chaotic behaviours.
			\item Largely follows the work presented by Sanders et al. However, whilst they consider
			EWA, we consider Q-Learning, which is more popular in RL communities.
	\end{itemize}

	\subsection{Problem Statement} % (fold)
	\label{sub:problem_statement}

	Given a particular learning algorithm and game, is it possible to determine whether the game is
	likely to reach a unique fixed point or exhibit more complex behaviour? What are the factors
	which affect this resulting behaviour?

	% subsection problem_statement (end)

	\subsection{Objectives and Scope} % (fold)
	\label{sub:objectives_and_scope}

	Analyse the stability of Multiagent Q-Learning on iterated games. Brings the work presented by
	Sanders et al to the reinforcement learning community.

	Assumptions:

	\begin{itemize}
		\item Focuses on stateless games
		\item Homogeneous agents
		\item Discrete action spaces
		\item Small, finite number of agents.
	\end{itemize}

	% subsection objectives_and_scope (end)

	% section introduction (end)

\end{document}

### 2020-05-20 ChaoticDynamics/WriteUp.tex
Complete Chapter 8 on Swarm Control

@@
 \usepackage[margin=2cm]{geometry}
+\usepackage{amsmath}
 
@@
 		\item Homogeneous agents
-		\item Discrete action spaces
+		\item Discrete action spaces, with large number of actions.
 		\item Small, finite number of agents.
@@
 
+	\section{Derivation} % (fold)
+	\label{sec:derivation}
+
+	We start with the two-agent Q-Learning dynamics as presented by Tuyls et al.
+
+	\begin{subequations}
+		\begin{equation}
+			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
+			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
+		\end{equation}
+		\begin{equation}
+			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
+			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i})
+		\end{equation}
+	\end{subequations}
+
+	In order to follow the conventions of spin glass theory for the analysis of disordered systems,
+	we rescale the system so that the payoff matrix elements are of order $N^{-1/2}$. The motivation
+	for doing this is that, along the way, we will take the limit of the number of actions $N$ to
+	infinity. However, doing this will result in numerical underflow of the action probabilities 
+	(i.e. the probability of each action goes to zero). To compensate for this, we adjust the
+	system so that the sum of the probabilities add to $N$. The scaling goes as follows:
+
+	\begin{subequations*}
+		\begin{equation*}
+			a_{ij} = \sqrt{N} \tilde{a_{ij}}
+		\end{equation*}
+		\begin{equation*}
+			b_{ji} = \sqrt{N} \tilde{b_{ji}}
+		\end{equation*}
+	\end{subequations*}
+
+	We compensate for this change with
+	\begin{subequations*}
+		\begin{equation*}
+			x_{i} = \tilde{x_{i}}/N
+		\end{equation*}
+		\begin{equation*}
+			y_{i} = \tilde{y_i}/N
+		\end{equation*}
+	\end{subequations*}
+
+	This gives the original equations as
+
+	\begin{subequations}
+		\begin{equation}
+			\frac{\dot{\tilde{x_i}}(t)}{\tilde{x_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{a_
+			{ij}} 
+			\tilde{y_j} -
+			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{x_i} \tilde{a_{ij}} \tilde{y_j}
+			+ \tilde{\alpha} \sum_j \tilde{x_j} ln(\frac{\tilde{x_j}}{\tilde{x_i}}) 
+		\end{equation}
+		\begin{equation}
+			\frac{\dot{\tilde{y_i}}(t)}{\tilde{y_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{b_
+			{ij}} 
+			\tilde{x_j} -
+			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{y_i} \tilde{b_{ij}} \tilde{x_j}
+			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}) 
+		\end{equation}
+	\end{subequations}
+
+	% section derivation (end)
+
 \end{document}

### 2020-05-20 Literature Review/Literature Review - Revised/sections/SwarmControl.tex
Complete Chapter 8 on Swarm Control

\documentclass[../sample.tex]{subfiles}

\begin{document}

	This chapter elaborates on the research directions presented in Chapter \ref{ch::Proposals}.
	Elaborating on the previous discussion, we propose to consider the development of control
	methodologies for complex swarm systems. This is strongly influenced by the work presented by
	Bellomo et al. \cite{Bellomo2017} who consider swarms as large systems of living agents (termed
	'active particles'). Crucially, this accounts for agents which exhibit complex social
	agent-agent interactions. This interaction can range from simple attractive/repulsive
	interactions to strategy selection. To the best of my knowledge, no control methodologies have
	been proposed for this model of swarms. In detail, the authors consider the following features:

	\begin{enumerate}
		\item The swarm consists of a large number of active particles who interact with other
		particles within a sensitivity domain.
		\item Interactions are non-local and nonlinearly additive.
		\item The swarm occupies an initial domain which, through the overall dynamics, evolves in
		time.
		\item The swarm may contain different types of subgroups. For example, there may be leaders
		in the group. In a broad sense, the approach allows for groups which follow different
		strategies and interaction rules with other groups.
		\item The rules of interaction dynamics depend on the type of agents present, but is
		uniformly distributed within each group.
	\end{enumerate}

	The advantage to this view of swarming agents is that it is extremely general. In fact, to the best
	of my knowledge, it is the most general swarm description available in the literature. It accounts
	for heterogeneous groups, inter-agent interactions, which maybe both short and long-range. This is
	particularly important from a safety perspective; most existing considerations of swarms treat the
	agents as evolving through independent random motion and, therefore, do not account for collision
	avoidance behaviour. However, to control swarms of intelligent agents who do interact with one
	another, it is important that interactions are taken into account. Similarly, this is beneficial
	from an intelligence perspective. The inter-agent interactions can also incorporate the evolution
	of agent strategies through repeated interactions (i.e. Multi Agent Reinforcement Learning). This
	notion is expanded upon in Chapter \ref{ch::DynMARL}.

	With the ultimate goal of producing control strategies for swarms of active particles, the
	following studies are proposed:

	\begin{itemize}
		\item Control of a homogeneous swarm through field interaction,
		\item An experimental study of swarm field interaction,
		\item Control of a swarm through leadership,
		\item Generalisations of control strategies,
		\item Consideration of learning strategies through repeated interactions.
	\end{itemize}

	The above is ordered in an indicative manner of the general progress of research with
	complexity gradually being introduced over time. However, the order is not immutable. In
	particular the consideration of learning is one that may be introduced into each of the above
	studies. The remainder of this chapter addresses each of these points and elaborates on the
	suggested work.

	\section{Control through fields} % (fold)
	\label{sub:control_through_fields}

	This study extends the work of Zhang \cite{Zhang2018}, Elamvazuthi \cite{Elamvazhuthi2019} and
	Li et al. \cite{Li2017}. Here, the authors consider the dynamics of swarms through 'drifted
	brownian motion'. The control input, in this case, is some scalar field which is generated from the
	environment. Each agent measures this field at their location and uses it to adjust their
	velocity, which eventually results in the entire swarm achieving some desired distribution. This
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner.

	The hypothesis of this section is that the distribution of active particles may
	similarly be controlled through the application of scalar field. The dynamics derived by Bellomo
	et al. \cite{Bellomo2017} includes a 'flocking field' which agents can measure. By controlling
	the flocking field, we may be able to drive the swarm to specific
	distributions. Some applications of this study are:

	\begin{itemize}
		\item Search and Rescue, in which agents will be required to flock to specific areas (e.g.
		areas with survivors detected).
		\item Construction, in which agents will be required to take on desired formations based on
		the structure to be designed.
		\item Medical Robotics, in which agents are required to target specific areas of the body.
	\end{itemize}

	The contribution that this study presents over those using brownian motion is the inclusion of an
	interaction operator. This governs how agents interact with one another. By accounting for this, we
	are able to control swarms where agents, for instance, avoid collisions with one another. The
	complexity of this interaction term will need to be gradually increased over time. To begin with,
	we may entirely neglect this term. It is here that we will compare the model proposed by Zhang with
	that proposed by Bellomo et al. We may then consider only local interactions, which is typical for
	most swarming systems in the current literature, before then considering non-local interactions.
	This provides the scope for swarms to take on interact with a greater number of agents. At this
	stage, we may expand our study to consider the presence of interaction domains. This places
	constraints on how agents may interact with one another, allowing for a greater generalisation of
	inter-agent interactions. Ultimately, we would like to influence the interaction term, though this
	is discussed in Section \ref{sec:learning_strategies_through_iterated_interaction}. The questions
	we will consider here are:

	\begin{itemize}
		\item The controllability of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner?
		\item The guarantees of the system: Is it possible to ensure that the agents will not enter
		certain areas of state space, or exceed certain control constraints (e.g. max velocity)?
	\end{itemize}

	In conclusion, the results from this study already significantly expand the current capabilities of
	swarming agents by developing control methodologies which can drive the swarm towards desired
	distributions in a stable manner. This is accomplished through controlling the 'flocking field'
	which is indirectly used to adjust the velocity of the agents.

	% section control_through_fields (end)

	\section{Experimental Study of Fields} % (fold)
	\label{sec:experimental_study_of_fields}

	The natural question which arises from the previous discussion pertains to the 'flocking field' and
	what physical property this may correspond to. In other words, where does this field come from? In
	the previous section, we assumed, a priori, the existence of this field. However, this will not
	necessarily be the case in reality. We will therefore turn to experiment to determine how we might
	generate this field for given scenarios. Examples of how the field may be generated are:

	\begin{itemize}
		\item Measurements of physical properties, such as the intensity of light or heat 
		(particularly useful when aiming to avoid fires in urban search and rescue), or
		concentration of pollutants for enviromental applications.
		\item Density of the environment through computer vision. This may, for instance, include
		counting the density of survivors in a search and rescue scenario or the presence of
		obstacles for avoidance scenarios.
		\item Shape detection for manipulating objects. For instance, picking up beams and bringing
		them to desired locations may be solved by appropriately choosing an underlying field.
	\end{itemize}

	These suggestions give us the capability to verify the results presented in the previous
	section. They will also allow us to show the applicability of the results in a wide array of
	disciplines.
	% section experimental_study_of_fields (end)

	\section{Control through leadership} % (fold)
	\label{sec:control_through_leadership}

	It is here that we start to consider heterogeneity within the system. To this end, we consider
	the case that the majority of the swarm are comprised of 'followers' to whom controls cannot be
	directly applied. Instead, controls are applied to a select group of 'leaders' within the swarm.
	Then, by their mutual interaction, the leaders are able to herd the swarm towards particular
	states. This study will follow a similar structure to that of Borzi and Suttida 
	\cite{Borzi2015} and Ko and Zuazua \cite{Ko2019}. In both of these works, a
	drawback is that no requirements are placed on the final velocity of the followers. This
	means that whilst the swarm may reach a desired state, it will not remain in that
	position. The questions that we will consider here are similar in nature to those presented in
	Section \ref{sub:control_through_fields}, namely controllability and guarantees.

	The disadvantage to control through leadership is that we have induced points of failure (i.e.
	if the leaders fail, we can no longer control the system). However, its advantage as compared
	with control through fields is the capability to handle dynamic environments. Before, if we were
	to have dynamic environments, we would have to adjust the flocking field accordingly and
	communicate this change to the entire swarm. Here, the followers do not require any knowledge of
	the environment as they only interact with the leaders. This reduced computation allows for a
	greater capacity for the swarm behaviour to evolve dynamically.

	% section control_through_leadership (end)

	\section{Generalisation of Control Strategies} % (fold)
	\label{sec:generalisation_of_control_strategies}

	This section of study will be broken down into two areas of exploration. These are:

	\begin{enumerate}
		\item Agent Heterogeneity
		\item State Space Non-linearity
	\end{enumerate}

	\paragraph{Agent Heterogeneity} % (fold)
	\label{par:agent_heterogeneity}

	builds on Bellomo et al's proposal of sub-groups within the swarm. These groups may interact with
	the flocking field or the leader in different ways. For instance, one may be more strongly repulsed
	by the leader than another, or one group may experience a completely different flocking field than
	another. However, they all interact with one another through the interaction operator. In addition,
	we may consider that, through the course of the swarming process, some agents may fail, and
	therefore its internal dynamics and ability to interact with other agents will change. We must
	ensure that the control framework (which may now take on a hybrid control \cite{Lygeros2004}
	format) can account for this and still ensure the completion of the task and safety of the system.
	This will be a powerful extension to swarm literature since, to the best of my knowledge, there are
	no studies which provide a unified framework with which to control agents of different types.

	% paragraph agent_heterogeneity (end)

	\paragraph{State Space Non-Linearity} % (fold)
	\label{par:state_space_non_linearity}

	takes into account the mechanical constraints of the agents. This is inspired by the work of
	Elamvazuthi and Berman \cite{Elamvazuthi2018} who account for the fact that the behaviour of
	agents is best described by their configuration space, rather than simply their state space.
	For instance in order for a group of robot manipulators (robot arms) to pick up a heavy object,
	not only must they be in the correct position (e.g. surrounding the object), but also the arms
	must be in the correct configuration to perform the action. This will allow for more complex
	interactions between agents since, rather than simply achieving some desired position, the
	agents may actually be in the required configurations to perform tasks.

	% paragraph state_space_non_linearity (end)

	The above aim to generalise the control strategies developed in this study. These will be
	powerful additions to swarm literature since they will allow for systems to act in more complex
	manners by introducing heterogeneity and configurations within one control framework.

	% section generalisation_of_control_strategies (end)

	\section{Learning Strategies through Iterated Interaction} % (fold)
	\label{sec:learning_strategies_through_iterated_interaction}

	This section of the study is perhaps the strongest extension to swarm control proposed in this
	chapter, and will likely be the most challenging. Here, we attempt to control the interaction term
	in Bellomo et al's model and we consider that the behaviour of the entire swarm may be influenced
	by decision making on an individual level. This will involve agents learning their strategies
	through repeated interaction. The goal, then, is to design the agent parameters, reward structure
	and control strategy to achieve desired results. To accomplish this will require a unification of
	multi agent learning and control theory. Whilst, at first glance, such an endeavour seems
	incredibly challenging, our work in the predictability of mean field learning (Chapter 
	\ref{ch::DynMARL}) places us in a unique position to tackle the problem. This framework will
	first establish the desired strategy to be taken by the agents and choose the game's reward
	structure so that learning will converge to a stable fixed point. Then by accounting for this
	strategy within the interaction term, we apply the appropriate controls in the flocking field to
	drive the swarm in a stable manner. We will again consider the aforementioned controllability
	and guarantees questions and establish how the incorporation of learning affects these results.

	% section learning_strategies_through_iterated_interaction (end)

\end{document}

### 2020-05-21 ChaoticDynamics/WriteUp.tex
Updated Chapter 8 Swarm Control and Write Up for Tuyls Dynamics

@@
 \usepackage{amsmath}
+\usepackage{mathtools}
 
@@
 	\begin{subequations}
+	\label{eqn::EOM}
 		\begin{equation}
@@
 			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
-			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i})
+			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
 		\end{equation}
 	\end{subequations}
+
+	\subsection{Rescaling of Variables} % (fold)
+	\label{sub:rescaling_of_variables}
 
@@
 
-	\begin{subequations*}
-		\begin{equation*}
+	\begin{subequations}
+		\begin{equation}
 			a_{ij} = \sqrt{N} \tilde{a_{ij}}
-		\end{equation*}
-		\begin{equation*}
+		\end{equation}
+		\begin{equation}
 			b_{ji} = \sqrt{N} \tilde{b_{ji}}
-		\end{equation*}
-	\end{subequations*}
+		\end{equation}
+	\end{subequations}
 
 	We compensate for this change with
-	\begin{subequations*}
-		\begin{equation*}
+	\begin{subequations}
+		\begin{equation}
 			x_{i} = \tilde{x_{i}}/N
-		\end{equation*}
-		\begin{equation*}
-			y_{i} = \tilde{y_i}/N
-		\end{equation*}
-	\end{subequations*}
+		\end{equation}
+		\begin{equation}
+			y_{i} = \tilde{y_i}/N.
+		\end{equation}
+	\end{subequations}
 
@@
 	\begin{subequations}
+	\label{eqn::scaledEOM}
 		\begin{equation}
@@
 			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{y_i} \tilde{b_{ij}} \tilde{x_j}
-			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}) 
+			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}).
 		\end{equation}
@@
 
+	The need for the factor of $\frac{1}{\sqrt{N}}$ is to follow the conventions of the saddle point
+	method of integration. This will become clear after taking the expectation of the generating
+	functional. Note that we may drop the notation on time dependence for $x$ and $y$. However, these
+	will always be functions of time. Henceforth, we shall not write the tildes on $x, y, a_{ij},
+	b_{ij}$. We shall also abbreviate the final term as
+
+	\begin{equation*}
+		\rho_{x, i}(t) = \sum_j x_j ln(\frac{x_j}{x_i}) 
+	\end{equation*}
+
+	% subsection rescaling_of_variables (end)
+
+	\subsection{Generating Functional} % (fold)
+	\label{sub:generating_functional}
+
+	The generating functional allows us to take a path integral over all possible realisations of
+	learning \cite{SpinGlassTheory}. This is given as:
+
+	\begin{equation}
+		Z = \int D[\Vec{x}, \Vec{y}] \prod_i \delta(\textit{equation of motion}_i) exp(i
+		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t)]), 
+	\end{equation}
+
+	where the equations of motion are the Lagrange equations of motion given in (
+	\ref{eqn::scaledEOM}) and
+	the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
+	calculation. $\delta$ denotes the Dirac delta function. We write this in its Fourier
+	representation, which yields
+
+	\begin{equation}
+		\begin{split}
+	\label{eqn::generatingfunctional}
+		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i \sum_i \int dt[\hat{x}_i
+		(\frac{\dot{x_i}(t)}{x_i(t)} - \alpha \tilde{\tau} \sum_{j} a_
+			{ij} 
+			y_j +
+			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j
+			- \tilde{\alpha} \rho_{x, i}(t) + h_{x, i}(t))]) 
+			\\
+			\times exp(i \sum_i \int dt[\hat{y}_i
+		(\frac{\dot{y_i}(t)}{y_i(t)} - \alpha \tilde{\tau} \sum_{j} b_
+			{ij} 
+			x_j +
+			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j
+			- \tilde{\alpha} \rho_{y, i}(t)+ h_{y, i}(t))])\\
+			\times exp(i \sum_i
+		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))]),
+	\end{split}
+	\end{equation}
+
+	Here, the terms $a_{ij}, b_{ij}$ are the payoffs in the game and the term $h$ denotes a field
+	which will be set to zero at the end of the calculation. We recall that these are randomly
+	generated using a multivariate gaussian and then held fixed for the rest of the game. We call
+	this 'quenched disorder'. Isolating these terms allows us to rearrange the above as
+
+	\begin{equation}
+	\begin{split}
+	\label{eqn::moveddisorder}
+		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
+		\sum_i \int dt[\hat{x}_i
+		(\frac{\dot{x_i}(t)}{x_i(t)}
+			- \tilde{\alpha} \rho_{x, i}(t)+ h_{x, i}(t))]) 
+			\\
+			\times exp(i \sum_i \int dt[\hat{y}_i
+		(\frac{\dot{y_i}(t)}{y_i(t)} 
+			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
+			\times exp(i \sum_i
+		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))])\\
+		\times exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
+			{ij} 
+			y_j +
+			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
+			\alpha 
+			\tilde{\tau} \sum_{j} b_
+			{ij} 
+			x_j +
+			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
+	\end{split}
+	\end{equation}
+	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
+	that we moved the term containing the quenched disorder into a separate exponential. Since our
+	aim is to take an average over all possible realisations of this disorder, we will only need to
+	focus on the last exponential which we rewrite as
+
+	\begin{equation}
+		Q = exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
+			{ij} 
+			y_j +
+			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
+			\alpha 
+			\tilde{\tau} \sum_{j} b_
+			{ij} 
+			x_j +
+			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
+	\end{equation}
+
+	We will then separate the terms so that like sums are paired together
+
+	\begin{equation}
+	\begin{split}
+		Q = exp(-i \alpha \tilde{\tau} \sum_{ij} \int dt[\hat{x}_i a_{ij} y_j + \hat{y}_j b_
+			{ji} 
+			x_i])
+			\times
+			exp(i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{ijk} \int dt[\hat{x}_i x_j
+			a_{jk} y_k + \hat{y}_i y_k b_{kj} x_j])
+	\end{split}
+	\end{equation}
+
+	It should be noted that we have changed some of the subscripts on the terms. Since these terms
+	are all multiplied together and we sum over the subscripts, the letters we choose are of no
+	importance and we can exchange them freely. We will define both exponentials in $Q$ as $Q_1$ and
+	$Q_2$ respectively.
+
+	We are now ready to take the expectation of $Q$. To do this, we will exploit the fact that the
+	payoff elements are Gaussian distributed and use the identity \cite{QFTbook}
+
+	\begin{equation}
+	\label{eqn::expectationIdentity}
+		\int dz [e^{-A_2(z) + \Vec{b} \cdot \Vec{z}}] = (2 \pi)^{k/2} (det(A))^{-1/2} e^{\omega(b)},
+	\end{equation}
+
+	where
+
+	\begin{equation*}
+		\begin{split}
+			A_2(z) = 1/2 \sum_{ij} z_i A_{ij} z_j \\
+			\omega_2(z) = 1/2 \sum_{ij} b_i (A)^{-1}_{ij} b_j
+		\end{split}
+	\end{equation*}
+
+	\subsubsection{Expectation of $Q_1$} % (fold)
+	\label{ssub:expectation_of_Q1}
+
+	We can rewrite $Q_1$ as
+
+	\begin{equation*}
+		Q_1 = \prod_{ij} exp(\Vec{b} \cdot \Vec{z}),
+	\end{equation*}
+
+	where
+
+	\begin{equation*}
+		\begin{split}
+			b \coloneqq [-i \alpha \tilde{\tau} \int dt[\hat{x}_i y_j], -i \alpha \tilde{\tau} \int
+			dt[\hat{y}_j x_i]]^T \\
+			z \coloneqq [a_{ij}, b_{ji}]^T\\
+			A \coloneqq \Sigma^{-1}\\
+			\Sigma_{ij} \coloneqq Cov[z_i, z_j],
+		\end{split}
+	\end{equation*}
+
+	where $\Sigma$ is the covariance of $\Vec{z}$. We recall that the scaled system has
+	payoff elements chosen so that
+
+	\begin{equation*}
+		\begin{split}
+			\mathbb{E}[a_{ij}] = \mathbb{E}[b_{ji}] = 0\\
+			\mathbb{E}[a_{ij}^2] = \mathbb{E}[b_{ji}^2] = 1/N\\
+			\mathbb{E}[a_{ij} b_{ji}] = \Gamma /N.
+		\end{split}
+	\end{equation*}
+
+	Applying identity (\ref{eqn::expectationIdentity}) gives:
+
+	\begin{equation}
+	\begin{split}
+		\mathbb{E}[Q_1] = \prod_{ij} exp(- \alpha^2 \tilde{\tau}^2 \frac{1}{2N} \int dt dt'[
+		\hat{x}_i
+		(t) \hat{x}_i
+		(t') y_j(t) y_j(t') + \hat{y}_j(t) \hat{y_j}(t') x_i(t) x_i(t') \\ + \Gamma \hat{x}_i(t) 
+		{x}_i
+		(t') {y}_j(t) \hat{y}_j(t') + \Gamma \hat{y}_j(t) {y}_j(t') {x}_i(t) \hat{x}_i(t')]).
+	\end{split}
+	\end{equation}
+
+	% subsubsection expectation_of_Q1 (end)
+	% subsection generating_functional (end)
+
+	\subsubsection{Expectation of $Q_2$} % (fold)
+	\label{ssub:expectation_of_Q2}
+
+	We take a similar approach with the following definitions
+
+	\begin{equation*}
+		\begin{split}
+			b \coloneqq [i \tilde{\alpha} \tau \int dt[\hat{x}_i x_j y_k], i \tilde{\alpha} 
+			\tau
+			\int
+			dt[\hat{y}_i x_j y_k]]^T \\
+			z \coloneqq [a_{jk}, b_{kj}]^T\\
+			A \coloneqq \Sigma^{-1}\\
+			\Sigma_{ij} \coloneqq Cov[z_i, z_j],
+		\end{split}
+	\end{equation*}
+
+	% subsubsection expectation_of_Q2 (end)
+
+	Following the same procedure as for $Q_1$ yields
+
+	\begin{equation}
+	\begin{split}
+		\mathbb{E}[Q_2] = \prod_{ij} exp(- \tilde{\alpha}^2 \tau^2 \frac{1}{2N^2} \int dt dt'[
+		\hat{x}_i
+		(t) \hat{x}_i
+		(t') x_j(t) x_j(t') y_k(t) y_k(t') \\+ \hat{y}_i(t) \hat{y_i}(t') x_j(t) x_j(t') y_k(t)
+		y_k(t') \\ + \Gamma \hat{x}_i(t) \hat{y}_i(t')
+		{x}_j
+		(t) x_j{(t')} {y}_k(t) y_k(t') \\ + \Gamma \hat{y}_i(t) \hat{x}_i(t') {x}_j(t) {x}_j(t')
+		y_k(t) y_k(t')]).
+	\end{split}
+	\end{equation}
+
+	We now define the correlation functions
+
+		\begin{align*}
+C_x(t, t') &= N^{-1} \sum_i x_i(t) x_i(t') & C_y(t, t') &= N^{-1} \sum_i y_i(t) y_i(t')\\
+L_x(t, t') &= N^{-1} \sum_i \hat{x}_i(t) \hat{x}_i(t') & L_y(t, t') &= N^{-1} \sum_i \hat{y}_i(t) \hat{y}_i(t') \\
+K_x(t, t') &= N^{-1} \sum_i x_i(t) \hat{x}_i(t') & K_y(t, t') &= N^{-1} \sum_i y_i(t) \hat{y}_i(t')\\
+A_{xy}(t, t') &= N^{-1} \sum_i \hat{x}_i(t) \hat{y}_i(t').
+\end{align*}
 	% section derivation (end)
 
+We then rewrite $\mathbb{E}[Q]$ as
+
+\begin{equation}
+\begin{split}
+		\mathbb{E}[Q] = exp(- \alpha^2 \tilde{\tau}^2 \frac{N}{2} \int dt dt'[L_x(t, t')C_y(t, t')
+		+ L_y(t, t')C_x(t, t') + 2 \Gamma K_x(t, t') K_y(t', t)] \\
+	- \tilde{\alpha}^2 \tau^2 \frac{N}{2} \int dtdt' [L_x(t, t') C_x(t, t') C_y(t, t') + L_y(t, t')
+	C_x(t, t') C_y(t, t') \\ + \Gamma A_{xy}(t, t') C_x(t, t') C_y(t, t') + \Gamma A_{xy}(t', t) C_x
+	(t, t') C_y(t, t')] )
+\end{split}
+\end{equation}
+
+We can introduce these correlation functions into the expectation which gives
+
+\begin{equation}
+	\begin{split}
+		\mathbb{E}[Q] = \int D[C_x, \hat{C_x}, L_x, \hat{L_x}, K_x, 
+		\hat{K_x}, C_y, \hat{C_y}, L_y, \hat{L_y}, K_y, 
+		\hat{K_y}, A_{xy}, \hat{A}_{xy}] 
+		exp(N(\Psi, \Phi, \Lambda)),
+	\end{split}
+\end{equation}
+
+where
+\begin{equation}
+	\begin{split}
+	\Psi = i \int dtdt' [\hat{C}_x(t, t') C_x(t, t') + \hat{L}_x(t, t') L_x(t, t') + \hat{K}_x
+		(t, t') K_x(t, t') \\ + \hat{C}_y(t, t') C_y(t, t') + \hat{L}_y(t, t') L_y(t, t') + 
+		\hat{K}_y(t, t') K_y(t, t') + \hat{A}_{xy}(t, t') A_{xy}(t, t')]
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\begin{split}
+		\Phi = - \alpha^2 \tilde{\tau}^2 \frac{N}{2} \int dt dt'[L_x(t, t')C_y(t, t')
+		+ L_y(t, t')C_x(t, t') + 2 \Gamma K_x(t, t') K_y(t', t)] \\
+	- \tilde{\alpha}^2 \tau^2 \frac{N}{2} \int dtdt' [L_x(t, t') C_x(t, t') C_y(t, t') + L_y(t, t')
+	C_x(t, t') C_y(t, t') \\ + \Gamma A_{xy}(t, t') C_x(t, t') C_y(t, t') + \Gamma A_{xy}(t', t) C_x
+	(t, t') C_y(t, t')] 
+\end{split}
+\end{equation}
+
+\begin{equation}
+	\begin{split}
+		\Lambda = i \sum_i \int dt dt'[\hat{C}_x(t, t') x_i(t) x_i(t') + \hat{L}_x(t, t') \hat{x}_i
+		(t)\hat{x}_i(t') + \hat{K}_x(t, t') x_i(t) \hat{x}_i(t') \\ + \hat{C}_y(t, t') y_i(t) y_i
+		(t') +
+		\hat{L}_y(t, t') \hat{y}_i
+		(t)\hat{y}_i(t') + \hat{K}_y(t, t') y_i(t) \hat{y}_i(t') \\ 
+		+ \hat{A}_{xy}(t, t') \hat{x}_i(t) \hat{y}_i(t')].
+	\end{split}
+\end{equation}
+
+We insert this expectation back into the original generating functional which gives
+
+\begin{equation}
+	\begin{split}
+		\mathbb{E}[Z(\Vec{\psi}, \Vec{\phi})] = \int D[C_x, \hat{C_x}, L_x, \hat{L_x}, K_x, 
+		\hat{K_x}, C_y, \hat{C_y}, L_y, \hat{L_y}, K_y, 
+		\hat{K_y}, A_{xy}, \hat{A}_{xy}] 
+		exp(N(\Psi, \Phi, \Omega + (\mathcal{O}(N^{-1})))),
+	\end{split}
+\end{equation}
+
+where $\Omega$ includes all terms describing the time evolution of the system and is given by
+
+\begin{equation}
+	\begin{split}
+		\Omega = N^{-1} \sum_i log \int D[x_i, \hat{x}_i, y_i, \hat{y}_i] exp(i
+		\int dt[\hat{x}_i
+		(\frac{\dot{x_i}(t)}{x_i(t)}
+			- \tilde{\alpha} \rho_{x, i}(t) + h_{x, i}(t))]) 
+			\\
+		\times exp(i\int dt dt'[\hat{C}_x(t, t') x_i(t) x_i(t') + \hat{L}_x(t, t') \hat{x}_i
+		(t)\hat{x}_i(t') + \hat{K}_x(t, t') x_i(t) \hat{x}_i(t')])\\
+		\times exp(i \int dt[\hat{y}_i
+		(\frac{\dot{y_i}(t)}{y_i(t)} 
+			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
+		\times exp(i \int dt dt' [\hat{C}_y(t, t') y_i(t) y_i
+		(t') +
+		\hat{L}_y(t, t') \hat{y}_i
+		(t)\hat{y}_i(t') + \hat{K}_y(t, t') y_i(t) \hat{y}_i(t')])\\
+		\times exp(i \int dt dt'[\hat{A}_{xy}(t, t') \hat{x}_i(t) \hat{y}_i(t')]])
+			\times exp(i \sum_i
+		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))]).
+	\end{split}
+\end{equation}
+
+We will evaluate the path integral using the saddle point method for integration 
+\cite{saddlepoint}. In this method, we consider that the integration is dominated by the maximum of
+the function
+
+\begin{equation*}
+	f = \Psi + \Phi + \Omega,
+\end{equation*}
+
+and we take the limit as N extends to infinity. We therefore determine the relations which maximise
+this function. We find
+
+\begin{align*}
+	\frac{\partial f}{\partial C_x(t, t')} &\implies i \hat{C}_x(t, t') = \frac{\alpha^2 
+	\tilde{\tau}^2}{2} L_y(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(L_x(t, t')C_y(t, t') + L_y
+	(t, t')C_y(t, t') + 2\Gamma A_{xy}(t, t') C_y(t, t'))\\
+	\frac{\partial f}{\partial L_x(t, t')} &\implies i \hat{L}_x(t, t') = \frac{\alpha^2 
+	\tilde{\tau}^2}{2} C_y(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(C_x(t, t') C_y(t, t'))\\
+	\frac{\partial f}{\partial K_x(t, t')} &\implies i\hat{K}_x(t, t') = \alpha^2 
+	\tilde{\tau}^2 \Gamma K_y(t', t) \\
+	\frac{\partial f}{\partial C_y(t, t')} &\implies i \hat{C}_y(t, t') = \frac{\alpha^2 
+	\tilde{\tau}^2}{2} L_x(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(L_x(t, t')C_x(t, t') + L_y
+	(t, t')C_x(t, t') + 2\Gamma A_{xy}(t, t') C_x(t, t'))\\
+	\frac{\partial f}{\partial L_y(t, t')} &\implies i \hat{L}_y(t, t') = \frac{\alpha^2 
+	\tilde{\tau}^2}{2} C_x(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(C_x(t, t') C_y(t, t'))\\
+	\frac{\partial f}{\partial K_y(t, t')} &\implies i\hat{K}_y(t, t') = \alpha^2 
+	\tilde{\tau}^2 \Gamma K_x(t', t) \\
+	\frac{\partial f}{\partial A_{xy}(t, t')} &\implies i\hat{A}_{xy}(t, t') = \tilde{\alpha}^2
+	\tau^2 \Gamma C_x(t, t') C_y(t, t').
+\end{align*}
+
+Similarly,
+
+\begin{align*}
+	\frac{\partial f}{\partial \hat{C}_x(t, t')} &\implies C_x(t, t') = \lim_{N \rightarrow \infty}
+N^{-1} \sum_i <x_i(t) x_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \psi_i(t) \partial \psi_i (t')} \bigg|_{\Vec
+{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
+	\frac{\partial f}{\partial \hat{L}_x(t, t')} &\implies L_x(t, t') = \lim_{N \rightarrow \infty}
+N^{-1} \sum_i <\hat{x}_i(t) \hat{x}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial h_{x,i}(t) \partial h_{x, i} (t')} \bigg|_{\Vec
+{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
+	\frac{\partial f}{\partial \hat{K}_x(t, t')} &\implies K_x(t, t') = \lim_{N \rightarrow \infty}
+N^{-1} \sum_i <x_i(t) \hat{x}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \Vec{\psi}(t) \partial h_{x, i} (t')}
+\bigg|_{\Vec{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
+\frac{\partial f}{\partial \hat{C}_y(t, t')} &\implies C_y(t, t') = \lim_{N \rightarrow \infty}
+N^{-1} \sum_i <y_i(t) y_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \phi_i(t) \partial \phi_i (t')} \bigg|_{\Vec
+{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
+	\frac{\partial f}{\partial \hat{L}_y(t, t')} &\implies L_y(t, t') = \lim_{N \rightarrow \infty}
+N^{-1} \sum_i <\hat{y}_i(t) \hat{y}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial h_{y,i}(t) \partial h_{y, i} (t')} \bigg|_{\Vec
+{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
+	\frac{\partial f}{\partial \hat{K}_y(t, t')} &\implies K_y(t, t') = \lim_{N \rightarrow \infty}
+N^{-1} \sum_i <y_i(t) \hat{y}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \Vec{\phi}(t) \partial h_{x, i} (t')}
+\bigg|_{\Vec{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
+	\frac{\partial f}{\partial \hat{A}_{xy}(t, t')} &\implies A_{xy}(t, t') = \lim_{N \rightarrow
+	\infty}
+N^{-1} \sum_i <\hat{x}_i(t) \hat{y}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \partial h_{x, i} (t) \partial h_{y, i} (t')}
+\bigg|_{\Vec{\phi} = \Vec{\psi} = \Vec{h} = 0}.\\
+\end{align*}
+
+We implement these relations into the expression of $\Omega$, and make the assumption that all
+actions $i$ are independent and identically distributed (i.i.d.), which gives
+
+\begin{equation}
+	\begin{split}
+		\Omega =log \int D[x, \hat{x}, y, \hat{y}] exp(i
+		\int dt[\hat{x}(t)
+		(\frac{\dot{x}(t)}{x(t)}
+			- \tilde{\alpha} \rho_{x}(t))]) 
+			\\
+		\times exp(-\int dt dt'[\frac{1}{2} \alpha^2 \tilde{\tau}^2 C_y(t, t')\hat{x}(t)\hat{x}(t')
+		+ \frac{1}{2} \tilde{\alpha}^2 \tau^2 C_x(t, t')C_y(t, t')\hat{x}(t)\hat{x}(t') + i \alpha^2
+		\tilde{\tau}^2 \Gamma G_y(t', t) x(t) \hat{x}(t')])\\
+		\times exp(i \int dt[\hat{y}(t)
+		(\frac{\dot{y}(t)}{y(t)} - \tilde{\alpha} \rho_{y}(t))])\\
+		\times exp(-\int dt dt'[\frac{1}{2} \alpha^2 \tilde{\tau}^2 C_x(t, t')\hat{y}(t)\hat{y}(t')
+		+ \frac{1}{2} \tilde{\alpha}^2 \tau^2 C_x(t, t')C_y(t, t')\hat{y}(t)\hat{y}(t') + i \alpha^2
+		\tilde{\tau}^2 \Gamma G_x(t, t') y(t) \hat{y}(t')])\\
+		\times exp(-\int dt dt'[\tilde{\alpha}^2 \tau^2 \Gamma C_x(t, t') C_y(t, t') \hat{x}(t) 
+		\hat{y}
+		(t')]])
+	\end{split}
+\end{equation}
+
+Since this contains all of the information of the learning evolution, we consider $\Omega$ as an
+effective generating functional (and in fact we see that it has a similar structure to (
+\ref{sub:generating_functional}), without the existence of the fields $\psi, \phi$). In particular
+we recognise this as the generating functional of the 'effective dynamics' given as
+
+\begin{equation}
+	\begin{split}
+		\dot{x}(t) = x(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_y(t, t')x(t')] + \rho_x(t) +
+		\alpha \tilde{\tau} \eta_x(t) + \tilde{\alpha} \tau \frac{\eta_x(t) \eta_y(t)}{2} + 
+		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_x) \\
+		\dot{y}(t) = y(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_x(t, t')y(t')] + \rho_y(t) +
+		\alpha \tilde{\tau} \eta_y(t) + \tilde{\alpha} \tau \frac{\eta_x(t) \eta_y(t)}{2} + 
+		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_y) \\
+	\end{split}
+\end{equation}
+
+with the self-consistency relations
+
+\begin{align}
+	G_x(t, t') &= <\frac{\delta x(t)}{\delta \eta_x(t')}> & G_y(t, t') &= <\frac{\delta y(t)}{\delta
+	\eta_y(t')}> \\
+	<\eta_x(t) \eta_x(t')> &= C_y(t, t') & <\eta_y(t) \eta_y(t')> &= C_x(t, t')\\
+	<\mu_x(t) \mu_y(t')> &= C_x(t, t') C_y(t, t') & <\mu_x(t) \mu_x(t')> &= <\mu_y(t) \mu_y(t')> = 0
+\end{align}
+
+\section{Stability Analysis} % (fold)
+\label{sec:stability_analysis}
+
+We are now in a position to take the effective dynamics, which describes the evolution of the
+learning dynamics after averaging over all possible realisations of the payoff elements, and
+determine the stability of the system at fixed points. We will follow the procedure laid out by
+Opper et al \cite{Opper}. First, we rewrite $x(t)$, $y(t)$ as perturbations about their fixed
+points. We will then analyse the stability of these fixed points.
+
+Let
+
+\begin{align}
+	x(t) = x^* + \hat{x}(t) \\
+	y(t) = y^* + \hat{y}(t) \\
+	\eta_x(t) = \eta_x^* + \hat{\nu}_x(t)\\
+	\eta_y(t) = \eta_y^* + \hat{\nu}_y(t)\\
+	\mu_x(t) = \mu_x^* + \hat{\delta}_x(t)\\
+	\mu_y(t) = \mu_y^* + \hat{\delta}_y(t)
+\end{align}
+
+where terms denoted by $\cdot^*$ are the values that are taken at the fixed point and terms denoted
+by $\hat{\cdot}$ refer to deviations from the fixed point. This is not to be confused with
+the conjugate variable notation that we used in the previous section. We assume that these
+perturbations arise from additive noise, $\xi(t)$, $\zeta(t)$, drawn from the unit normal
+distribution which are applied to the dynamics. Rewriting the dynamics with all of these
+considerations gives
+
+\begin{equation}
+	\begin{split}
+		\frac{d}{dt} (x^* + \hat{x}(t)) = (x^* + \hat{x}(t))(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'
+		[G_y(t, t')(x^* + \hat{x}(t'))] + \rho_x(t) + \alpha \tilde{\tau} (\eta_x^* + \hat{\nu}_x
+		(t)) \\ + \tilde{\alpha} \tau \frac{(\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t))}
+		{2} + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_x^* + \hat{\delta}_x(t)) + \xi(t)) \\
+		\frac{d}{dt} (y^* + \hat{y}(t)) = (y^* + \hat{y}(t))(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'
+		[G_x(t, t')(y^* + \hat{y}(t'))] + \rho_y(t) + \alpha \tilde{\tau} (\eta_y^* + \hat{\nu}_y
+		(t)) \\ + \tilde{\alpha} \tau \frac{(\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t))}
+		{2} + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_y^* + \hat{\delta}_y(t)) + \zeta(t))
+	\end{split}
+\end{equation}
+
+Considering only terms which are linear in the deviations yields
+
+% section stability_analysis (end)
 \end{document}

### 2020-05-21 Literature Review/Literature Review - Revised/sections/SwarmControl.tex
Updated Chapter 8 Swarm Control and Write Up for Tuyls Dynamics

@@
 
-	This chapter elaborates on the research directions presented in Chapter \ref{ch::Proposals}.
+	This chapter expands upon the research directions presented in Chapter \ref{ch::Proposals}.
 	Elaborating on the previous discussion, we propose to consider the development of control
@@
 	Bellomo et al. \cite{Bellomo2017} who consider swarms as large systems of living agents (termed
-	'active particles'). Crucially, this accounts for agents which exhibit complex social
+	'active particles'). Crucially, this accounts for agents which exhibit complex
 	agent-agent interactions. This interaction can range from simple attractive/repulsive
-	interactions to strategy selection. To the best of my knowledge, no control methodologies have
+	forces to strategy selection. To the best of my knowledge, no control methodologies have
 	been proposed for this model of swarms. In detail, the authors consider the following features:
@@
 	particularly important from a safety perspective; most existing considerations of swarms treat the
-	agents as evolving through independent random motion and, therefore, do not account for collision
+	agents as evolving through independent, random motion and, therefore, do not account for collision
 	avoidance behaviour. However, to control swarms of intelligent agents who do interact with one
 	another, it is important that interactions are taken into account. Similarly, this is beneficial
-	from an intelligence perspective. The inter-agent interactions can also incorporate the evolution
+	from an intelligence perspective; the inter-agent interactions can also incorporate the evolution
 	of agent strategies through repeated interactions (i.e. Multi Agent Reinforcement Learning). This
@@
 
-	\begin{itemize}
+	\begin{enumerate}
 		\item Control of a homogeneous swarm through field interaction,
@@
 		\item Consideration of learning strategies through repeated interactions.
-	\end{itemize}
+	\end{enumerate}
 
@@
 	complexity gradually being introduced over time. However, the order is not immutable. In
-	particular the consideration of learning is one that may be introduced into each of the above
-	studies. The remainder of this chapter addresses each of these points and elaborates on the
+	particular, point 5, the consideration of learning, may be introduced into Points 1-4 throughout the study. The remainder of this chapter addresses each of these points and elaborates on the
 	suggested work.
@@
 	Li et al. \cite{Li2017}. Here, the authors consider the dynamics of swarms through 'drifted
-	brownian motion'. The control input, in this case, is some scalar field which is generated from the
+	brownian motion'. In this case, the control input is some scalar field which is generated from the
 	environment. Each agent measures this field at their location and uses it to adjust their
-	velocity, which eventually results in the entire swarm achieving some desired distribution. This
+	velocity, which eventually results in the entire swarm achieving a desired distribution. This technique
 	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
@@
 	The hypothesis of this section is that the distribution of active particles may
-	similarly be controlled through the application of scalar field. The dynamics derived by Bellomo
+	similarly be controlled through the influence of a scalar field. The dynamics derived by Bellomo
 	et al. \cite{Bellomo2017} includes a 'flocking field' which agents can measure. By controlling
 	the flocking field, we may be able to drive the swarm to specific
-	distributions. Some applications of this study are:
-
-	\begin{itemize}
-		\item Search and Rescue, in which agents will be required to flock to specific areas (e.g.
-		areas with survivors detected).
-		\item Construction, in which agents will be required to take on desired formations based on
-		the structure to be designed.
-		\item Medical Robotics, in which agents are required to target specific areas of the body.
-	\end{itemize}
+	distributions.
 
@@
 	most swarming systems in the current literature, before then considering non-local interactions.
-	This provides the scope for swarms to take on interact with a greater number of agents. At this
+	This provides the scope for swarms to interact with a greater number of agents. At this
 	stage, we may expand our study to consider the presence of interaction domains. This places
@@
 		\item The guarantees of the system: Is it possible to ensure that the agents will not enter
-		certain areas of state space, or exceed certain control constraints (e.g. max velocity)?
+		certain areas of state space, or exceed certain control constraints (e.g. max imum velocity)?
+	\end{itemize}
+
+	Some applications of this study are:
+
+	\begin{itemize}
+		\item Search and Rescue, in which agents will be required to flock to specific areas (e.g.
+		areas with survivors detected).
+		\item Construction, in which agents will be required to take on desired formations based on
+		the structure to be designed.
+		\item Medical Robotics, in which agents are required to target specific areas of the body.
 	\end{itemize}
@@
 	the previous section, we assumed, a priori, the existence of this field. However, this will not
-	necessarily be the case in reality. We will therefore turn to experiment to determine how we might
+	necessarily be the case in reality. We will therefore turn to experimentation to determine how we might
 	generate this field for given scenarios. Examples of how the field may be generated are:
@@
 		concentration of pollutants for enviromental applications.
-		\item Density of the environment through computer vision. This may, for instance, include
-		counting the density of survivors in a search and rescue scenario or the presence of
-		obstacles for avoidance scenarios.
-		\item Shape detection for manipulating objects. For instance, picking up beams and bringing
+		\item Density of the environment through computer vision. For instance, a centralised sytem may map the environment and artificially generate a field which it then communicates to the swarm.
+		\item Shape detection for moving objects. For instance, picking up beams and bringing
 		them to desired locations may be solved by appropriately choosing an underlying field.
@@
 
-	It is here that we start to consider heterogeneity within the system. To this end, we consider
-	the case that the majority of the swarm are comprised of 'followers' to whom controls cannot be
+	It is here that we start to consider heterogeneity within the system. To this end, we consider the
+	case that the majority of the swarm are comprised of 'followers' to whom controls cannot be
 	directly applied. Instead, controls are applied to a select group of 'leaders' within the swarm.
 	Then, by their mutual interaction, the leaders are able to herd the swarm towards particular
-	states. This study will follow a similar structure to that of Borzi and Suttida 
-	\cite{Borzi2015} and Ko and Zuazua \cite{Ko2019}. In both of these works, a
-	drawback is that no requirements are placed on the final velocity of the followers. This
-	means that whilst the swarm may reach a desired state, it will not remain in that
-	position. The questions that we will consider here are similar in nature to those presented in
-	Section \ref{sub:control_through_fields}, namely controllability and guarantees.
+	states. This study will follow a similar structure to that of Borzi and Suttida  \cite{Borzi2015}
+	and Ko and Zuazua \cite{Ko2019}. In both of these works, a drawback is that no requirements are
+	placed on the final velocity of the followers. This means that whilst the swarm may reach a desired
+	state, it will not remain in that position. The questions that we will consider here are similar in
+	nature to those presented in Section \ref{sub:control_through_fields}, namely controllability and
+	guarantees but will aim to resolve the issue of final velocity.
 
@@
 
-	builds on Bellomo et al's proposal of sub-groups within the swarm. These groups may interact with
+	* builds on Bellomo et al's proposal of sub-groups within the swarm. These groups may interact with
 	the flocking field or the leader in different ways. For instance, one may be more strongly repulsed
-	by the leader than another, or one group may experience a completely different flocking field than
-	another. However, they all interact with one another through the interaction operator. In addition,
+	by the leader than another, or one group may experience a completely different flocking field. However, they all interact with each other through the interaction operator. In addition,
 	we may consider that, through the course of the swarming process, some agents may fail, and
@@
 
-	The above aim to generalise the control strategies developed in this study. These will be
+	The above extensions aims to generalise the control strategies developed in this study. These will be
 	powerful additions to swarm literature since they will allow for systems to act in more complex

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203093818.tex
Reorganised Git

--- 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203155017.tex
@@
     This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
-    point is made that the vast majority of the work done in this area considers games with a finite
-    (usually two) number of agents. This limits the capability of the analysis to generalise to much
-    larger agent populations, such as swarms. To allieviate this concern, the authors present an
-    anaysis of the learning dynamics for a large agent population (which they approximate as
-    containing infinite agents) where each agent is an independent Q-Learning using Boltzmann
-    exploration. The emergent dynamics is given by a Fokker-Planck equation which is numerical shown
-    to be a strong approximation of the true learning dynamics. However, as the authors point out,
-    this is the first attempt at considering such a problem, and relies on heavy assumptions.
-    Possible extensions therefore require a consideration of asymmetic games, stateful games (which
-    ties in to Section \ref{sec::Stateful}) and heterogenous populations.
-
-    \section{Continuous Action Spaces}
-
-    Here lies the opportunity to extend the work of Tuyls' et al. \cite{Tuyls2006AnGames} towards
-    continuous action spaces. This would be particularly useful for most robotic applications, which
-    operate in continuous spaces.
-
-    Work has commenced in this area, but is still in its infancy. Notable examples are: 
-    \cite{Letcher2019DifferentiableMechanics}, in which Letcher et al. consider the dynamics of
-    Differentiable Games, though their focus is on its application to gradient descent in GANs as
-    opposed to reinforcement learning, and \cite{Galstyan2013}, in which the dynamics of Q-Learning,
-    with a Boltzmann action selection is considered. To achieve the result, the author replaces the
-    strategy vector with a probability density function (pdf) over the strategy space, which leads
-    to an integro-differential equation which describes the evolution of the pdf with time. Due to
-    its complexity, the dynamics cannot be analysed as easily as those in \cite{Tuyls2006AnGames},
-    and so Galstyan restricts the analysis to the steady-state solution (i.e. the fixed point) of
-    the dynamics. Their analysis shows strong agreement with the designed experiments, under varying
-    payoff conditions (note that the payoffs are now a function, rather than a discrete matrix).
-
-    Galstyan goes on to present avenues for further work. These are summarised below:
-
-    \begin{itemize}
-        \item  An analysis of the steady state equations, considering the existence and uniqueness
-        of solutions under varying payoff structures. How do these compare with the underlying Nash
-        Equilibrium. Tuyls and Westra also suggest the consideration of stability analysis in this regard.
-        \item A consideration of larger agent populations. No attempt towards this has yet been made
-        as far as I am aware.
-        \item A consideration of these dynamics under state transitions. Tuyls and Westra suggest
-        that an analysis using switching dynamics (Chapter \ref{ch::ControlTheory}) may be useful
-        here, but no attempt has yet been made as far as I am aware.
-    \end{itemize}
-
-    Tuyls and Westra \cite{TuylesWestra} also consider continuous action spaces from the same
-    perspective as Ruijgrok and Ruijgrok \cite{Ruijgrok}, namely that of the replicator dynamics.
-    The former extend the analysis of the latter by considering the case where mutations are
-    deterministic (e.g. through epsilon-greedy exploration) and these mutations only allow for small
-    changes within the strategy space. From an EGT perspective, this analysis provides a strong
-    characterisation of learning dynamics in continous action spaces and generalises the results of
-    Galstyan to generic update rules (rather than the traditional Q-Learning approach).
-
-    \section{Stateful environments} \label{sec::Stateful}
-
-    This is potentially the most relevant of the sections in regards to applicability to
-    reinforcement learning as it extends the typical consideration of stateless normal-form games,
-    in which the payoffs and strategies of each player is well defined, to stochastic games, in
-    which games have probabilistic transitions across them. I have yet to explore this section in
-    depth.
-
-    \section{Characterisation of Complex Dynamics}
-
-    The intention of this area of study is to consider the ideas presented in works such as 
-    \cite{Sanders2018} and \cite{Galla2011} which consider complex behaviour, including cycles and
-    chaos, in certain games using simple reinforcement learning algorithms. These provide a great
-    deal of insight into whether or not the game will converge and, if so, to what equilibrium.
-    Galla, for instance, shows that adjusting a memory parameter when learning to solve an Iterated
-    Prisoner's Dilemma game can shift the equilibrium from one showing purely defective behaviour to
-    one showing cycles of cooperations and defection. Sanders et al. generalise this result by
-    showing that, for a particular learning algorithm known as Experience Weighted Attraction,
-    learning dynamics varies dependent on the mutual effect of two parameters.
-
-    This determination of where RL algorithms will show complex dynamics is important, not only for
-    a priori understanding of resultant behaviour, but is particularly important for algorithms in
-    which agents aim to predict the behaviour of other agents. For this to be feasible, the learning
-    dynamics must not exhibit chaos, otherwise it would be impossible for an agent to make any
-    reasonable predictions about the future behaviour of its opponents.
+    point is made that the vast majority of the
 

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203153437.tex
Reorganised Git

--- 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200203155017.tex
@@
         of solutions under varying payoff structures. How do these compare with the underlying Nash
-        Equilibrium. Tuyls and Westra also suggest the consideration of stability analysis in this regard.
+        Equilibrium.
         \item A consideration of larger agent populations. No attempt towards this has yet been made
@@
     \end{itemize}
-
-    Tuyls and Westra \cite{TuylesWestra} also consider continuous action spaces from the same
-    perspective as Ruijgrok and Ruijgrok \cite{Ruijgrok}, namely that of the replicator dynamics.
-    The former extend the analysis of the latter by considering the case where mutations are
-    deterministic (e.g. through epsilon-greedy exploration) and these mutations only allow for small
-    changes within the strategy space. From an EGT perspective, this analysis provides a strong
-    characterisation of learning dynamics in continous action spaces and generalises the results of
-    Galstyan to generic update rules (rather than the traditional Q-Learning approach).
 

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/.history/sections/GameTheory_20200106085934.tex
Reorganised Git

--- 2020-01-06 Literature Review/Literature Review - Revised/.history/sections/GameTheory_20200106140400.tex
@@
 
+\section{Game Dynamics}
+
+Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
+problem of mathematically modelling Multi Agent Systems who repeatedly interact with one another.
+This model then serves to be able to predict the evolution of the system as well as to understand
+the trajectory of learning. Typically, this looks at considering whether or not the method is likely
+to converge towards a Nash equilibrium. This is generally a difficult problem to solve
+\cite{ShohamMultiagentFoundations} for all but toy problems. To extend this applicability into real
+world settings requires the study of stable equilbrium points;
+\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
+are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of the environment since a stable
+equilibrium will always be returned to even after perturbations. This extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
+
+\TODO{Add in the papers from Mendeley which are useful to this part of the study}
+
 \section{Game Theoretic Control}

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/sections/MARL.tex
Reorganised Git

--- 2020-01-02 Literature Review/Literature Review - Revised/sections/MARL.tex
@@
 
+\section{Game Dynamics}
+
+Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
+problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
+another. This model then serves to be able to predict the evolution of the system as well as to
+understand the trajectory of learning. Typically, this looks at considering whether or not the
+method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
+solve \cite{ShohamMultiagentFoundations} for all but toy problems.
+\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
+are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of the environment since a stable
+equilibrium will always be returned to even after perturbations. This extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
+
+The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
+evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
+considers similar assumptions to that of MARL: agents are no longer required to be rational and
+play the game optimise their expected return through repeated play. Importantly, players have no
+knowledge of the others' payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et al.
+determine the relation between the replicator dynamics concept of EGT (a differential equation
+defining the evolution of the proportion of a subgroup in an evolving population) and Q-Learning
+using Boltzmann probabilities as Q-values. The result was a dynamics equation which describes, for
+each action, the evolution of its selection probability which could even account for random
+exploration. There have since been a number of works which apply the same insight into different
+game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken into the following
+categories
+
+\begin{itemize}
+	\item Stateless games with discrete actions. Here, stateless refers to the idea that the game is
+	static and so the environment has no impact on the result. The aforementioned result 
+	\cite{Tuyls2006AnGames} fits into this category.
+	\item Stateless games with continuous actions. These consider more realistic MARL than the
+	previous category by replacing each agent's strategy vector with a probability density function 
+	(pdf) over a continuous action space.
+	\item Stateful games with discrete actions. This mostly considers stochastic games, where there
+	are multiple states with probabilistic (usually Markovian) transitions between them. However,
+	extensive form games, which considers more complex phenomena such as sequential moves and
+	imperfect information, are also briefly mentioned.
+	\item Stateful games with continuous actions. This is one of the more realistic assumptions
+	considered. However, the authors point out that this area is yet to see results, leaving it open
+	for possible research.
+\end{itemize}
+
+Though the above have seen success through experimental validation in games with 2 players and (in
+general) 2 to 3 discrete actions, recent work has begun the consideration of improving the models
+towards more complex scenarios with larger agent populations. A recent example of this is 
+\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
+Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
+its strategy based on the mean effect of the population. The result is a system of three equations
+which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
+presents an important first step in modelling the learning dynamics of large agent populations and
+has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
+games.
+
+An advantage of determining the evolutionary dynamics of learning is that it can describe the
+expected behaviour in different game settings. This is particularly important to understand the
+convergence of the methods; certain games will often show cyclic behaviour even with the existence
+of a strict NE. For instance, Imhof et al. show in \cite{Imhof2005} that a repeated prisoner's
+dilemma game results in cyclic behaviour when considering the options of cooperation or defection.
+
 \section{Stable Learning}

### 2020-05-22 Documents/Literature Review/Literature Review - Revised/sections/Swarms.tex
Reorganised Git

--- 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
@@
-\documentclass[preprint,11pt]{report}
-
-\usepackage{matlab-prettifier}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{float}
-\usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{csquotes}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[margin=0.5in,letterpaper]{geometry}
-\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
-\let\endchangemargin=\endlist 
-\usepackage{listings}
-\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
-\let\endchangemargin=\endlist
-\title{Literature Review - Informal}
-
-\newcommand\fr[1]{\textcolor{red}{FR: #1}}
-
-\author{Aamal Hussain}
-
-\date{\today}
+\documentclass[../sample.tex]{subfiles}
 
 \begin{document}
-
-\maketitle
-
-\tableofcontents
-
-\chapter*{Introduction}
-
-The areas of interest regarding Multi Agent Systems fall into two
-distinct categories (which have some slight overlap). The first is
-denoted as 'Decision Making', though the terms 'Planning' and
-'Distributed Control' may sometimes be used as substitutes. It is
-important to note that, in my case, I do not include Planning
-Formalisation techniques such as PDDL. Instead, I focus on the
-particular methods which involve interaction in the world. The second,
-I will refer to as 'Multi Agent Dynamics', though sometimes I will
-refer to this as 'Stability Analysis'.
-
-\subsection*{Scope}
-
-Both of the aforementioned topics have been applied to all variants of
-multi agent systems and have sufficient room for further
-exploration. The typical variants of multi agent systems that I will
-consider are
-
-\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
-Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
-Coded \end{itemize}
-
-In the above, 'Game Theoretic Approaches' cover a wide spectrum,
-including zero-sum (minimax) games, bayesian games, and many more. The
-final category, 'Hard Coded', refers to any approach which does not
-fit neatly into any of these categories. The name is chosen since they
-often refer to methods which revolve around a series of if-else
-statements.
-
-\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}
-
-I will first consider Decision Making as this is most closely related
-to the research proposal, before I consider Multi Agent Dynamics,
-which has strong implications for Safe and Trusted Multi Agent
-Systems.
-
-\subsection*{Objectives}
-
-The aim of the following sections is not to provide an exhaustive list of all work done in the
-aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
-identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
-these directions, we may be able to narrow down the remaining literature review and hone in on
-particular problems and, in fact, we may find that we address multiple of these over the next four
-years (while we, of course add more). As such, the end of each chapter will provide a list of
-research directions which I have identified from the preceding review.
-
-\chapter{Decision Making}
-
-Decision making refers to the generalised problem of considering how a multi-agent system should
-interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
-are aligned (cooperative) or in conflict with one another (competitive).
-
-The following sections will provide an overview of the literature aimed towards coordinating such
-systems as followed by interesting sub-fields in each approach which present avenues for research
-related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
-as the review progresses.
-
-\section{Swarms}
 
@@
 \cite{Rizk2018}.
+
+\section{Decision Making in Swarms}
 
@@
 
-\fr{What are the standard techniques used in swarms?
-that is, how are swarms and their interactions modelled?
-how are solutions computed?
-what kind of algorithms are used in this area?
-most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}
+\section{Approaches to Swarm Control}
 
-\subsection{Co-evolution and Self-Healing}
+Swarms systems are often developed by considering their natural analogues, such as those seen in
+fish, birds, bacteria, or (most commonly) ants.
 
-Recently, there has been an increased interest in introducing
-heterogeneity into the swarm systems to improve their real world
-applicability. An example of this which have been shown strong real
-world success can be found in
-\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
-swarm teams, referred to as 'foot bots' and 'eye bots' who work in
-unison to explore an environment and solve a navigation task.
+\TODO{Find typical approaches towards swarm solutions.}
 
-This area of research is sparsely populated and warrants further
-exploration. This is since the use of co-evolutionary teams can
-improve the robustness of the swarm optimisation. This is since it
-will be possible for a team to automatically determine when robots in
-the other team are not exhibiting expected behaviour and ensure that
-the other team self corrects. This process is referred to as
-'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
-user to define the goals of a swarm system. From this, a 'trust'
-metric can be defined which measures the deviation of each agent from
-the expected behaviour. The self-healing process occurs by limiting
-communication of all agents with 'untrusted' agents and encouraging
-communication with 'trusted' agents. The unison of self-healing with
-co-evolution may present the opportunity for heterogenous swarms to
-maintain their evolutionary stability, even in the face of
-environmental disturbances.
+Recent work has seen the advancement of swarms controlled in stochastic environments. This is
+particularly important for swarm intelligence in robots; many systems are developed with the
+motivation of search-and-rescue, in which the robot swarms will have to operate in environments
+where accounting for uncertainty is critical. To this end, swarm systems have seen the advent of
+stochastic control. In this, the swarm is modelled as a diffusive system using a stochastic
+equation, most often the Kolmogorov Forward Equation \cite{Hamann2008}. In \cite{Hamann2008}, the author shows that this equation can be derived by considering local trajectories of
+smaller subsets of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019} extend this idea to other
+stochastic models for swarms, importantly considering an advection-diffusion-reaction model which
+allows for hybrid agents to switch between different modes of operation.
 
-\subsection{Fault Detection}
+The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
+equations
+for stochastic forward processes (such as swarm foraging) in which, as the number of agents tends to
+infinity, the true macroscopic motion of the system tends to these equations. Importantly, however,
+these stochastic equations allow for an analysis of the swarm, as well as the ability to develop
+control laws. In \cite{Li2017}, Li et al show that these models can be used to develop control
+laws for robots in a swarm and drive them towards a target distribution. The method is shown to
+perform accurately both in simulation and on real robots. The advantage is that guarantees can be
+placed on the convergence and stabilisabiilty of the swarm towards the desired distribution.
+However, there appears to be significant scope to expand upon this methodology from a safety
+perspective. To begin with, the method does not consider inter-agent interactions and therefore does
+not formally guard against collisions. In \cite{Inoue2019}, a similar problem is considered,
+although collisions are avoided by having the robot simply move in the opposite direction when
+encountering an obstacle. It is here that the mean-field models are not as strong since they do not
+take these local interactions into account. It must be noted, however, that Inoue et al have
+identified this problem and are currently working towards its incorporation into the model.
 
-The above sections have considered the fact that swarm systems are
-robust to losses in the group.  However, any MAS system must first be
-able to recognise that an agent has undergone some failure.
+It would, therefore, be of particular interest from a safety perspective to consider agent
+interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
+swarm system to include agent interaction. This presents a first step towards considering the swarm
+as composed of intelligent agents rather than mindless particles and, as the authors suggest,
+presents the possibility of applying game theoretic approaches towards swarms, which also gives the
+ability to consider heterogeneous swarm systems who interact with one another through repeated play.
+Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
+\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
+leader-follower swarm system to achieve given tasks.
 
-To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
-a robust fault detection approach in which the swarm itself, in a
-decentralised manner, is capable of assessing deviation from 'normal'
-behaviour, even when the behaviour of the swarm itself is altered
-(perhaps by a remote operator). The authors achieve this by requiring
-that the agents themselves sense and characterise their own
-behaviour. This characterisation is formulated as a binary feature
-vector which is then communicated to the agent's neighbours. These
-neighbours will reach a consensus over whether the agent should be
-treated as faulty based on their collective behaviour. The results
-presented in \cite{Tarapore2019FaultDetection} show extremely
-promising results and suggest that their method is, in fact, able to
-determine faults with high accuracy in the presence of various fault
-types (including sensor and actuator failures), although poor
-performance is seen in actuation failures in some instances. It should
-be noted that this method requires that each robot transmit their
-feature vector to the nearest neighbours. In environments where
-communication may be severely limited, this may present further
-errors. Furthermore, it is unlikely that, when a robot is damaged,
-only one of its components will be affected. Therefore, it is
-important to determine the effect on performance in the face of
-multiple agent failures and in communication losses. This exploration
-may open the possibility of improving the state of the art in terms of
-failure detection in swarm systems. (Of course, this conclusion is
-based off two papers so further review is required).
+\section{Heterogeneous Swarms and Self-Healing}
 
-\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas.
-As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another.
-However, this depends essentially on the different modelling assumptions.}
+Recently, there has been an increased interest in introducing heterogeneity into the swarm systems
+to improve their real world applicability. An example of this which have been shown strong real
+world success can be found in \cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
+swarm teams, referred to as 'foot bots' and 'eye bots' who work in unison to explore an environment
+and solve a navigation task.
 
-\subsection{Verification}
+\TODO{Do more research into heterogeneous swarm systems to pad this out. Perhaps we could introduce
+heterogeneity from the point of view of hybrid systems in the stochastic control section.}
 
-Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
-require further reading
+This area of research is sparsely populated and warrants further exploration. This is since the use
+of co-evolutionary teams can improve the robustness of the swarm optimisation. This is since it will
+be possible for a team to automatically determine when robots in the other team are not exhibiting
+expected behaviour and ensure that the other team self corrects. This process is referred to as
+'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a user to define the goals of a
+swarm system. From this, a 'trust' metric can be defined which measures the deviation of each agent
+from the expected behaviour. The self healing process occurs by limiting communication of all agents
+with 'untrusted' agents and encouraging communication with 'trusted' agents. The unison of
+self-healing with co-evolution may present the opportunity for heterogenous swarms to maintain their
+evolutionary stability, even in the face of environmental disturbances.
 
-\subsection{Directions}
+\section{Fault Detection and Recovery}
 
-From the above consideration of swarms, the following research
-directions have been identified which, in my view, concern themselves
-with STAI.
+The above sections have considered the fact that swarm systems are robust to losses in the group. 
+However, any MAS system must first be able to recognise that an agent has undergone some failure.
 
-\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
-towards ensuring that emergent phenomenon and swarm behaviour are as
-expected by the user.
+To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop a robust fault detection
+approach in which the swarm itself, in a decentralised manner, is capable of assessing deviation
+from 'normal' behaviour, even when the behaviour of the swarm itself is altered (perhaps by a remote
+operator). The authors achieve this by requiring that the agents themselves sense and characterise
+their own behaviour. This characterisation is formulated as a binary feature vector which is then
+communicated to the agent's neighbours. These neighbours will reach a consensus over whether the
+agent should be treated as faulty based on their collective behaviour. The results presented in
+\cite{Tarapore2019FaultDetection} show extremely promising results and suggest that their method is,
+in fact, able to determine faults with high accuracy in the presence of various fault types
+(including sensor and actuator failures), although poor performance is seen in actuation failures in
+some instances. It should be noted that this method requires that each robot transmit their feature
+vector to the nearest neighbours. In environments where communication may be severely limited, this
+may present further errors. Furthermore, it is unlikely that, when a robot is damaged, only one of
+its components will be affected. Therefore, it is important to determine the effect on performance
+in the face of multiple agent failures and in communication losses. This exploration may open the
+possibility of improving the state of the art in terms of failure detection in swarm systems.
 
-\item Fault Detection in limited communication:
-Considering the ability of a swarm to, in a decentralised approach,
-consider which robots in the team have failed, even in cases of no
-communication or multiple failures.
-
-\fr{The second item looks promising, possibly in combinations with
-  techniques from Game Theory and MARL. Let's keep Fault R\&D in
-  mind.}
-
-\end{itemize}
-
-\section{Dec-POMDPs}
-
-The use of POMDPs in multi-agent settings is formalised as
-decentralised POMDP (Dec-POMDP) which aims for a team of agents to
-maximise a common utility. However, it has been found that determining
-the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
-so is intractable for all but toy problems. A number of methods have
-been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
-of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
-as brute force) are intractable for all but toy problems.
-
-Approximate solutions to Dec-POMDP have been proposed, perhaps most
-notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
-Amato et al. Here, macro actions (actions which extend over multiple
-time steps) are used, as opposed to low-level actions which are
-re-evaluated at each time step. This allows an exact solution to be
-found as it does not need to be evaluated at each time step. This
-method assumes that, once macro-actions are distributed, the policies
-(sequence of state-action pairs) are known. Since this is not the
-case, Amato also proposes the use of a Dec-POSMDP
-\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
-'Semi-Markov Decision Process, in which a high level model is defined
-without the underlying Dec-POMDP's actions and observations.
-
-However, this is largely applicable in passive settings where common
-payoffs can be determined by an offline planner. They also require a
-significant amount of data with which to allow the system to learn the
-underlying models and payoff structures. This limits the applicability
-of the system when communication is limited and the system is
-presented with environments that it has not seen before.  Recent work
-in MDPs \cite{Klima2019RobustDomains} has considered learning in the
-face of Significant Rare Events (SREs) which the system has not yet
-observed. Currently, it is required that a model of such SREs is known
-and so it would be interesting to consider the application of
-Dec-POMDPs in situations where the SRE model is incomplete or
-erroneous and assess the robustness of the Dec-POMDP framework against
-such events.
-
-\subsection{Directions}
-
-The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
-developed by Amato as he seems to largely dominate the field. Based on this initial review of the
-area, a potential direction for research is
-
-\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
-  SREs which have a limited or erroneous model.
-
-\item Agent Failures: The Dec-POMDP model uses a
-centralised planner which acts offline. It therefore assumes that the agents will be able to carry
-out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
-planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}
-
-\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
-Also, it might be interesting to understand why swarms scale up better
-than MDPs, and in general why the former have better computational
-properties than the latter: is it a matter of
-``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
-some other swarm-like restriction? It might be interesting to combine
-the two approaches in order to get the ``best of both worlds''.}
-
-\section{Game Theoretic Approaches}
-
-Game theoretic models are generally the go-to method for understanding
-multi-agent systems. As such they fit into all of the categories in
-this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
-methods have both used game theory to support their frameworks. In
-fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
-(POSG), in which all agents use the same payoff. \fr{That's an
-  interesting remark. It might be worth to check whether we can
-  leverage on this and similar observations.} Game theory can,
-therefore, be used in an applied capacity to direct task allocation
-across heterogenous teams.
-
-\subsection{Market Based Methods}
-
-Garapati et al. \cite{Garapati2018AMissions} define a market based
-method as the setting where agents "follow their own interests and
-establish the mechanism of a market for distributing the
-tasks". Auctioning is the most widely used sub-field of market
-approaches and so I will use them interchangeably.
-
-Whilst there are different variants to autioning, the general
-procedure is that an auctioneer who has knowledge of a task (or
-multiple tasks) will set up an auction for said task. Agents can then
-make bids on these tasks and, once the auction is complete, the
-highest bid will win the task. In the specific application to
-robotics, a robot's bid will often reflect the costs, suitability or
-utility their undertaking the task
-\cite{BernardineDias2006Market-basedAnalysis}. This immediately
-highlights a few points. The first is that the method is not too
-heavily reliant upon a single processor to determine some joint
-policy. Tasks are allocated on a case-by-case basis and the utilities
-are calculated by the agent themselves. The only centralised process
-is the auctioneer's assessment of the winner which then relays this
-information back to them. The downside of this is that the system is
-heavily reliant upon strong communication channels, without which
-tasks may not be assigned, incorrect utilities may be communicated
-and, in general, sub-optimal solutions reached.  Furthermore, the
-requirement that the agents themselves determine the cost of their
-actions assumes that they have the computational capability to do
-so. Furthermore, the bids placed by each agent need to be a strong
-representation of their capability to perform a task which may be hard
-to estimate without expert knowledge. However, market based methods
-are well suited to explanation through argumentation (similar to
-\cite{Jung2001DistributedArgumentation}.
-
-\fr{The game-theoretic approaches described above might suffer from the
-  same drawbacks identified above for fault detection, namely reliance
-  on communication and on a single central authority. I'd rather
-  favour distributed approaches. Also, market-based mechanisms and
-  negotiation might lead us to a completely different direction.}
-
-With well chosen payoffs, market based approaches work extremely
-well. For instance, in \cite{Dias2000ASystem}, the authors show that a
-free market approach (where agents try to maximise their own profits)
-can lead to a strong collaborative effort across teams. Similarly, in
-\cite{Thomas2005Multi-robotScenarios}, Thomas et al. apply the
-auctioning scheme presented in \cite{Gerkey2002Sold:Coordination}
-towards a robot construction team. However, it is important to note
-that these are both passive settings; tasks were assigned before the
-team were in the field and, in the case of
-\cite{Gerkey2002Sold:Coordination}, the system would repeat the
-bidding process if a robot failed. While both show strong performance,
-it cannot be said that either would be applicable in dangerous
-environments in which dynamic reassignment must happen within strict
-time constraints. Stancliff et
-al. \cite{Stancliff2009PlanningAllocation} suggest that a more robust
-method to planning would be to account for failures a priori, a
-philosophy which is exemplified in \cite{Chen2010ACollaboration} who
-consider the robot's reliability and relevance to a task as well as
-'history relevance' which considers the relationship between pairs of
-robots with the aim of producing more effective teams.
-
-There has also been some interesting work in probabilistic
-verification of market based approaches.  Most notable to me is
-\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
-of conflict avoidance. Though their method focuses on collision
-avoidance, it highlights the need for verification of conflict
-resolution and goal achievement in market based approaches with
-different payoff structures. Sirigineedi et
-al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
-direction by considering the verification of cooperative surveillance
-along a route network.  From my understanding, this means that they
-were able to verify that their agents were able to traverse along the
-network without interference. However, this, as always, requires
-further analysis to truly understand.
-
-\subsection{Directions}
-
-The particular considerations which have jumped out to me from the above analysis are as follows:
-
-\begin{itemize} 
-	\item Verification of goal achievement under different payoffs: can we ensure that
-	self-interested agents will, in fact, show cooperative emergent properties? A similar question
-	arises in terms of valuations (how much cost each agent incurs). 
-	\item A priori consideration of
-	reliability: Can we learn and take into account the fact that robots may fail throughout the
-	progress of a mission when we assign tasks? 
-\end{itemize}
-
-\subsection*{Stochastic Games}
-
-\section{Hard Coded}
-
-\section{MARL}
-
-Reinforcement learning extends the Markov Decision Process problem by
-considering the case where the payoff model is not known. This, of
-course, is the case for most real world environments. As such, MARL
-algorithms can perhaps be considered to be more applicable than
-Dec-POMDP models.
-\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}
-
-Fortunately, MARL has picked up a lot of traction in
-research recently, with a large body dedicated towards solving the
-many problems it presents.
-
-The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
-single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
-in the Multi Agent setting since other agents in the environment will be learning concurrently. This
-learning will be based on their own history of interactions which extend beyond the previous state.
-As such, we must now consider that the policy for any one agent will depend on the policy of all
-other agents. As such, a big concern in this area is regarding convergence guarantees and the
-stability of the learner system. Approaches to this will be discussed in the next chapter.
-
-\subsection*{Agent Modelling}
-
-Returning to the problem of non-stationarity, solutions have been presented in which the agent
-models the learning of other agents. A noteworthy example of this is found in
-\cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other
-agents' learning and optimises with respect to this expected return. They show that this leads to
-stable learning and can even lead to emergent cooperation from competition. However, the method
-requires that both agents have exact knowledge of the others' value functions in order to perform
-the one step lookahead. Furthermore, it has only been considered for the case of a two agent
-adversarial game and so the scalability of the system to multiple agents is not yet understood.
-Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect
-the actions and observations of all agents and allows it to model the joint policy of teammates.
-This is shown to generate cooperative behaviour across four agents and so is more applicable to real
-world settings. However, its disadvantage over the method presented in
-\cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this
-requires the presence of an agent (perhaps a laptop) which is able to handle the computational load
-of determining a joint policy across all agents and must then communicate the Q-values of all agents
-back to them. This is both a taxing both in terms of computation and time.
-
-Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by
-tasking a CNN with determining the policy features of other agents and then embedding these as
-features in its own DQN. This shows strong performance in settings where other agents dynamically
-change their policies. The concerns with this, however, are that, as the number of agents in the
-field increase, the CNN in each agent must perform another approximation. This places strong
-requirements on the performance of the CNN since errors in estimation will accumulate as the number
-of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are
-added.
-
-Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent
-modelling is an important one to ensure stable learning and to understand the evolution of the
-system. It also presents a strong challenge and is open to exploration. To put it in context the
-methods described in this section are all from 2018-19, so its all very new.
-
-\subsection{Directions}
-
-I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
-However, on initial assessment I put forward
-
-\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
-the stability of the learning process. However, the particular problem I suggest is to consider the
-modelling in a decentralised manner and with the consideration of evolving numbers of agents in
-teams. \end{itemize}
-
-\fr{This looks like an interesting, non-trivial problem: how can we
-  represent the other agents within the agent model itself, in order
-  to improve learning in MARL? Shall we have a closer look at this problem?}
-
-\section{MARL Approaches} \label{sec::MARL Approaches}
-
-The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
-policy may be the concatenation of all the individual policy or it may just be options for each
-agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
-and so, in this section, I will try to consider the broad spectrum of methods which attempt to
-achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
-all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
-to help guide this review. I am not referencing the individual papers immediately, though the
-references can be found in the book.
-
-\subsubsection*{Learning in Two Player Matrix Games}
-
-The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
-method of linear programming (in which constraints are linear). This will be important in
-considering more current methods. A similar consideration is given to the infinitesimal gradient
-ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
-infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
-not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
-particular problem in games where there are multiple Nash equilibria. However, in practice it is
-difficult to choose a convergence rate of the step size and, without an appropriate choice the
-strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
-to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
-payoff matrix (which is not so much of a problem for model based methods) and the opponent's
-strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
-method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
-(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
-oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
-players with minimal oscillation.
-
-The above methods are all centralised techniques, in which a controller determines the optimal joint
-policy for both agents. However, in real scenarios it is often preferable that each agent learns
-their own strategy, a task which must be completed without information of the other agent's
-strategy. The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which
-guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$)
-which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor
-algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$
-lagging anchor algorithm which can converge to both pure and mixed NEs.
-
-\subsubsection*{Learning in Multiplayer Stochastic Games}
-
-Stochastic Games (or Markov Games) form a basis for MARL
-settings. However, in this case the agents must learn about the
-equilibrium strategies by playing the game, which means they do not
-have a priori knowledge of the reward or transition functions. Schwarz
-considers two properties which should be used for evaluating MARL
-algorithm: rationality and convergence. The latter simply states that
-the method should converge to some equilibrium whereas the former
-suggests that the method should learn the best response to stationary
-opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
-shortly. Schwarz then presents a review of MARL methods (as of
-September 2014)
-
-\fr{All the above looks extremely interesting. I would explore the
-  above for decentralized and partially observable settings. What
-  results are mentioned \cite{SchwartzMulti-agentApproach} under such
-  assumptions?}
-
-\subsection*{Dec-POMDP and MARL}
-
-As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
-methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
-\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
-The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
-is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
-Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
-however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
-Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
-order to make this work, we would also need to consider how to select the feature space of sub-trees
-and how to collect this information. \end{itemize}
-
-\chapter{Multi Agent Control}
-
-\section{Stochastic and Robust Model Predictive Control}
-
-The idea of Stochastic Control is best described in the research statement of the Control and
-Analysis of Stochastic Systems (CASS) group at Penn State:
-
-\begin{displayquote}
-	"...to model, predict and control uncertain engineering systems where the interplay between
-	dynamics and uncertainty (stochasticity) is important."
-\end{displayquote}
-
-When operating in the real world, systems are subject to uncertainty and environment perturbations.
-Despite this, for their safe operation, they must provide certain guarantees (such as collision
-avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
-system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
-control have found their way into controlling power distribution, chemical processes and (of course)
-robotics.
-
-\subsection*{Model Predictive Control}
-
-Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
-of operating real-world agents safely in the face of environmental disturbances. The overarching
-idea begins with the assumpion that we have a model of the environment. As an example, in
-the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
-affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
-environment state for a few time steps ahead, and generate a policy for this horizon. The agent
-performs the immediate action generated by the policy, and then we repeat the process, after taking
-measurements of the environment to determine the error in the system. Throughout this process, the
-controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
-example, a likely constraint would be that the controller will never result in the car going on the
-pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
-the requirement of stability that the system is required to remain safe throughout operation. To
-that end, mathematical proofs of these properties are provided in the literature ensuring that we
-can trust in the system's performance.
-
-Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
-knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
-computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
-provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
-of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
-we no longer assume the exact nature of the environment and can guard against worst case scenarios.
-This is extremely effective in closed environments or for simple tasks, but falters in more complex
-environments.
-
-Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
-perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
-define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
-optimality is defined in terms of the minimisation of the expectation of a probabilistic
-cost function. This formulation brings about controllers which are more applicable and robust when
-deployed. However, the field is in its infancy and presents a number of theoretical challenges.
-These are best described by Mesbah in \cite{Mesbah2016}
-
-\begin{itemize}
-	\item The arbitrary form of the feedback control laws
-	\item The non-convexity and intractability of the chance constraints
-	\item The complexity of the uncertainty propagations
-	\item Establishing stability of the control problem
-\end{itemize}
-
-Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
-some of
-these problems, most notably the intractability of the chance contraints. For instance, in 
-\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
-time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
-suited to non-linear systems, which itself is an open problem in the MPC sphere.
-
-The research in using Distributed Predictive Control is quite sparse as compared with, for example,
-single agent predictive control. The added complexity of stochastic environments has meant that this
-area of research is still very open for looking into. With this said, the main works that I have
-found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
-\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
-Usually these are some combination of the following:
-
-\begin{itemize}
-	\item The agents act in a deterministic environment. This suggests that predicted futures will
-	be close enough to the ground truth.
-	\item The agents are uncoupled from one another. This is a strong assumption to make and
-	essentially allows us to consider the agents as completely independent of one another. 
-	\item The agents can easily communicate with one another. This allows for longer pieces of
-	communication (most often predicted trajectories) to be communicated between agents.
-\end{itemize}
-
-\subsection{Directions}
-
-The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
-and applied problems. Control in autonomous systems is also one of the more applicable problems
-related to STAI since it requires that we place mathematical guarantees on the performance and
-stability of the system as well as guarantees on the satisfaction of constraints. This is, of
-course, an ever present problem in autonomous systems which operate in the real world. I begin by
-listing the more theoretical areas for exploration in MPC before then considering their application
-domains.
-
-\begin{itemize}
-	\item Significant exploration is required with regards to the optimisation problem. Especially
-	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
-	approximate methods (such as sampling) should be explored and their effect on the system
-	guarantees presented.
-	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
-	determine the uncertainty in the environment model in order to generate control laws. We should
-	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
-	particle filters, against modern deep learning methods for propagation.
-	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
-	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
-	together whilst maintaining a specified distance from one another). Consider, then, the case
-	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
-	and hence requires adaptation. It would again be interesting to consider the use of neural
-	networks in this manner. However, specifically we should consider whether the use of a function
-	approximator in the form of an NN might result in a violation of the constraints.
-	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
-	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
-	effect that each agent has on the other, the effect of the environment on all agents, estimating the
-	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
-	here that I believe game-theoretic notions (especially differential games) will come to our
-	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
-	in the case of multiple disturbances, but I will elaborate on this in the applied problems
-	section.
-\end{itemize}
-
-the following presents a consideration of the applied end of MPC problems. I have tried to focus on
-the domain independent suggestions, since the domain specific ones are virtually limitless.
-
-\begin{itemize}
-	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
-	interact with each other. In addition, we may consider that there are multiple known disturbances
-	acting on the system. This, at first seems like an impossible problem to solve due to the many
-	interactions between all elements of the system. However, we can consider this as a game
-	theoretic problem in which the components and the disturbances are players. The relatively new
-	class of 'mean-field games' is a method which allows the many body problem to be approximated as
-	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
-	predictive control' remain, this may prove to be a valuable area of applied research.
-	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
-	which emerge into more complex results. It would be interesting to consider the application of
-	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
-	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
-	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
-	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
-	adaptive stochastic model would be interesting to examine here to remain robust to agent
-	failures in the group.
-	\item Modular Robotics?
-\end{itemize}
-
-\section*{Multi Agent Dynamics}
-
-Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
-Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
-well as to understand the trajectory of learning. Typically, this looks at considering whether or
-not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
-problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
-applicability into real world settings requires the study of stable equilbrium points;
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world
-environments.
-
-\section{Stability of Learning Agents}
-
-Stability may be looked at from the view point of two perspectives. The first is from an
-optimisation point of view. This considers the dynamics of the learning model, allowing us to better
-choose our parameters and design our models so that they may converge to a stable result. The second
-is from the view point of the state-action space of a learnt model. This allows us to determine,
-before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This
-knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability
-analysis allows us to build multi agent systems which will learn and act in the way that we expect
-them to.
-
-In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of
-generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is
-one in which the loss function is twice differentiable. Using this formulation, they are able to
-analyse the system from new perspectives by considering the current state-of-the-art understanding
-of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical
-exercise, they go on to show that the insights gained allow them to develop a new multi-objective
-optimisation technique for GANs which shows stronger convergence properties, most notably of which
-is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the
-two players' loss functions.
-
-Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement
-learning agent as a non-linear, time varying feedback controller. Using this notion, they then
-consider the bounded-input-bounded-output stability of the system. They do this by analysing the
-ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains
-finite then the system may be considered to be stable. They then apply these considerations on
-real-world applications including multi-agent flight formation and obtain stability certificates
-(essentially confirming that the system will remain stable under certain conditions) for the learned
-controller.
-
-Berkenkamp et al. \cite{Berkenkamp2017SafeGuarantees} consider a similar problem from a different
-definition of stability. Specifically, they look at stability from the point of view of Lyapunov
-functions. A system is said to be stable if the applying the policy will result in stricly lower
-evaluations of the function. In other words, a system is stable if its corresponding Lyapunov
-function is decreasing towards a minimum point. The authors use this idea to define a 'region of
-attraction' in which the system is stable in the sense of Lyapunov. The goal of Safe Lyapunov
-Learning, a method which they develop from these insights, is to learn a policy without leaving this
-region of attraction. They do this by taking measurements within the set and using this to learn
-about the system dynamics, thereby increasing the safe set. With this, we now have a guarantee that
-policy optimisation will not result in unsafe behaviour, even in the presence of stochasticity and
-exploration.
-
-As we can see from the discussion thus far, there are many definitions and perpectives of stability,
-each lending to a new understanding of learning systems. To add another to the mix, Milchtaich in
-\cite{Milchtaich2007StaticGames}, presents a notion of static stability. This means that it is based
-solely on the incentives of the players and does not require a consideration of the dynamics of the
-system. Milchtaich's definition of a stable system is one in which, when perturbed, it is more
-beneficial for an agent to move back towards the equilibrium than it is for them to move away. This
-is perhaps the most fundamental definition of a stable equilibrium and, as such, Milchtaich shows
-that it is applicable to all strategic games, within certain assumptions (finite set of player and
-continuous strategy space) and considers probabilistic perturbations from the original state. This
-is particular applicable to Multi Robot Reinforcement Learning (or any MARL in continuous strategy
-spaces) since these systems require random exploration of the strategy space and the dynamics are
-not known a priori. However, the lack of dynamics means that we do not consider the evolution of
-learning.
-
-\section{Learning Stable Agents}
-
-The above discussion has considered how notions of stability and control are important to
-Multi-Agent Learning. It stands to reason, therefore, that Multi-Agent Learning and, more
-specifically, game theory, can be used to develop controllers which drive systems to stable states.
-This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
-which the players are a controller and an adversarial environment. The design of the controller must
-be such that it is able to drive the system to zero error. To illustrate, consider the problem of
-designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
-vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
-efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
-agent may encounter without actually encountering them. The same notion is explored by Bardi et al
-\cite{Bardi1991DifferentialDisturbances}.
-
- Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
- avoidance problem, similarly from the point of view of differential game theory. They develop a
- robust feedback system for the robots which they show to be able to drive the system towards
- predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
- In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
- systems in a distributed manner. Here, agents only consider their own payoff structure and have
- limited communication with one another. The author shows that the an approximate equilibrium can be
- found using algebraic methods and illustrate the capabilities of the technique using a collision
- avoidance example. For the sake of brevity, I will not include all of the numerous strides that
- Mylvaganam has introduced to the area. However, I must conclude with those presented in
- \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
- games, including linear-quadratic differential games (in which system dynamics are linear functions
- whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
- induced across the players (a notion was suggested in the research proposal) and mean-field games,
- which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
- differential game is the stability of the solution; solutions for the Nash equilibria are
- admissable iff they are locally exponentially stable (which the author often shows with the aid of
- Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
- calculate online. The author then shows that this is not simply a theoretical exercise by applying
- the novel methods towards multi-agent collision problems and designs dynamic control laws which
- guarantee that each agent will reach their desired state whilst avoiding collision with the other
- agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
- robot system.
-
-\subsection{Directions}
-
-I will briefly summarise the research directions which I develop in this section, to save ourselves
-some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}
-
-The above discussion has illustrated a few points. The first, and perhaps most important, is that
-stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
-that learning agents, especially in real world environments, are subject to uncertainty and
-perturbations as well as epsilon-random exploration. As such, it is important that the system is
-able to return to a stable state after such perturbations. This leads to the need to develop
-learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
-equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
-equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
-Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
-to stable fixed points.
-
-The second point is that the notion of stability has multiple definitions. Each one is appropriate
-in different conditions and, as such, it is important to explore stability from various viewpoints
-to consider how to best understand the evolution of a learning system.
-
-Another factor to consider is suggested in \cite{Milchtaich2007StaticGames}; multiplayer games do
-not necessarily contain stable fixed points. The existence of stable equilibria is therefore an open
-question and is well worth consideration. This would help guide the choice of loss functions and
-strategy spaces. This is likely to be an extremely difficult problem to generalise but would have a
-dramatic impact on the safety certification of MARL systems.
-
-The problem of finding stable solutions through multi agent dynamics also opens the door for a large
-degree of application domains which are currently quite sparse. I would recommend looking at the
-contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
-of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
-control and economic modelling. My particular interest, as always, lies within robotic control
-problems. This appears to be the most direct and relevant application of stable MAS systems. An
-example of this might be the problem of Cooperative Moving Path Following Control considered by
-\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
-pre-defined path without interfering with one another. It is clear then that each player's control
-is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
-determine control rules which lead to stable coordination across the team. Similarly, we can model
-consider modelling a controller and an adversarial environment as a zero-sum game as examined in
-\cite{Marden2018AnnualControl}.
-
-Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
-of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
-differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
-the differential game problem from the point of view of different information structures. In
-real-world systems, it is unlikely that all agents will have access to the information of other
-agent' cost functions and current positions. It could, however, be interesting to explore the use of
-localisation methods to determine and track this information through observation (e.g. through
-Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
-considers the case where system dynamics are linear. A whole new set of problems arise in the more
-realistic case where we must consider the non-linearity of system dynamics. Such a consideration
-would also allow us to extend these technique to the more difficult (and important) problems in
-control.
-
-The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
-Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
-Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
-particularly relevant to this study. However, they will require some further analysis before I write
-about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
-entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
-document out.)
-
-\chapter{Research Directions}
-
-\section{Stochastic Model Predictive Control for Distributed Systems}
-
-The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
-that end, I propose the following techniques towards improving DSMPC.
-
-\begin{itemize}
-	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
-	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
-	distribution of the action that will likely be selected by $j$, effectively performing a
-	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
-	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
-	this may seem computationally expensive, its advantage lies in the fact that it requires little
-	communication across the agents. An immediate disadvantage of this is that, as the number of
-	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
-	not yet confident on the feasibility or the usefulness of this technique, but looking further
-	into the literature (which seems to add new things every day) may provide insights which could
-	help refine the technique. This method is, in many ways, similar to that presented in 
-	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
-	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
-	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
-	all systems to update at each time step.
-
-	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
-	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
-	public belief based on the observed actions of all agents. This joint belief will likely provide
-	some representation of the trajectories that each agent will carry out or an understanding of
-	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
-	will be chosen from a family of existing models using a recursive Bayesian update. The idea
-	would be for this update to be conditioned on the history of observations as is done in 
-	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
-	state and use this, in combination with their own system models to determine a feasible
-	trajectory. The challenge here would be proving the stability and controllability of the system
-	and that it requires communication with a central controller. However, it would appear to be a
-	feasible area of exploration.
-\end{itemize}
-
-\section{Stochastic Control of Swarms}
-
-Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
-when considering its application in stochastic environments. In particular, the ideas presented
-below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
-desired distribution.
-
-\begin{itemize}
-	\item Consideration of state constraints or boundary conditions (terms which I will use
-interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
-particular stochastic difference equation (the Ito equation). However, this does not account for any
-boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
-obstacle avoidance. However, in environments where there are human operators, or in general areas
-where we do not want swarms to enter, it is important to have a guarantee of constraint
-satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
-conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
-confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
-Furthermore, it may present an opportunity for us to consider the decentralised control of the
-agents which can ensure state constraint satisfaction. The resources which are most relevant to this
-study (and from which the ideas are derived) are
-\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.
-
-\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
-the diffusion models, as mentioned above, do not take into consideration the interactions between
-agents, since it adds a large degree of complexity to the model. However, it would be important from
-a safety perspective to take these into account by looking at the attractive and repulsive
-potentials across agents. This would allow us to provide a guarantee of inter-agent collision
-avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
-mention that they are already looking into this problem and have proposed a similar manner of
-tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
-they publish?
-
-\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
-By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
-number of their nearest neighbours. However, this may not always be the case. It will often be that
-in different environmental conditions, the observation or communication capabilities of the robots
-may increase or decrease. To better accomodate for this fact, I propose the extension of the model
-with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
-'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
-success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
-way into swarm dynamics. It will, however, become particularly important in cases where we can no
-longer take the consistency of agent communication for granted. 
-\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
-not seem like the connection of MJD and swarm dynamics has been made yet.
-\end{itemize}
-
-\section{Multi Agent Reinforcement Learning}
-
-The ideas I have down here are a little more sparsely populated, but further reading may provide
-some insights into potential directions.
-
-\begin{itemize}
-	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
-	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
-	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
-	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
-	required that we determine a safe manner in which MARL agents may explore without leading to
-	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
-	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
-	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
-	independent learners who do not consider the effect that they have on the other agent(s). The
-	particular extension that I propose is to consider the coupled effect between agents as part of
-	the determination of a safe set for exploration.
-
-	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
-	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
-	problems. Although it makes strong assumptions about the nature of the system, in practice it
-	has shown strong results. Particular examples of this are found in 
-	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
-	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
-	systems by considering sub-groups within the population. Each of these may be updated
-	individually. It would be interesting to examine how this might increase the complexity, and
-	also the generalisability of the mean-field method.
-	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
-	part but the potential directions are largely summarised in Section 2.3.1.
-\end{itemize}
-
-\bibliographystyle{IEEEtran}
-
-\bibliography{IEEEfull,references}
+It may be interesting to consider failure from the point of view of stochastic control with
+jump dynamics (See 'Hybrid Control'). For instance, we could consider the development of systems
+which are robust to different modes of operation based on failure. Similarly an exploration into
+adaptive control could allow us to develop swarm systems who can recover from discrete jumps based
+on belief models.
 

### 2020-05-22 Code/MeanFieldSim/ParameterSweep.py

@@ -1,0 +1,53 @@
+# -*- coding: utf-8 -*-
+
+import sys
+import os
+import numpy as np
+from tqdm import tqdm
+
+sys.path.append('../_NIPS2019_code/MAS_Environments')
+sys.path.append('../_NIPS2019_code/MAS_Agents')
+sys.path.append('../_NIPS2019_code/MAS12')
+
+from Agent02 import Agent02
+from Environment02 import Environment02
+from GameAssignment01 import GameAssignment01
+from MAgame1202 import runSim
+
+dirName = 'ParameterSweep Results'
+if not os.path.exists(dirName):
+    os.makedirs(dirName)
+
+nSimulations = 10
+gameName = 'PD'
+
+allMeanTraj = []
+allParams = []
+
+converged = []
+tau = 0.01
+
+for r in tqdm(np.linspace(0, 5, num=10)):
+    for gamma in np.linspace(-1, 1, num=10):
+
+        if not os.path.exists(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma)):
+             parameters = {'tau': tau, 'lr': r * tau}
+
+             allParams.append([tau, r])
+
+             meanConvergence = runSim(nSimulations, parameters, gamma)
+             # allMeanTraj.append(np.array(allxBar))
+
+             # allMeanTraj.append(np.array(np.mean(np.array(allxBar).squeeze(), axis = 0)))
+
+             with open(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma), 'w') as f:
+                f.write('r: {0}, gamma: {1} \n'.format(r, gamma))
+                f.write('Converged: {0} \n'.format(str(meanConvergence)))
+                # for probs in allMeanTraj[-1]:
+                #     f.write(str(probs) + '\n')
+                f.close()
+        else:
+            continue
+
+
+print('hi')

### 2020-05-22 Code/_NIPS2019_code/MAS12/MAgame1202.py

@@ -1,0 +1,177 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Mon May 13 18:40:55 2019
+
+@author: cwleung
+"""
+# concurrent learning (2p), 1 vs m
+# no network
+# matrix game
+# Q
+
+import sys
+import os
+import numpy as np
+from collections import Counter
+import matplotlib.pyplot as plt
+
+from tqdm import tqdm
+sys.path.append('../MAS_Environments')
+sys.path.append('../MAS_Agents')
+
+from Environment02 import Environment02
+from Agent02 import Agent02
+
+from GameAssignment01 import GameAssignment01
+
+
+def runSim(Nsim, parameters, gamma):
+    
+    T = 50
+    Nagent = 2
+    m = 1
+    
+    Nact = 2
+    
+    tau = parameters['tau']
+    lr = parameters['lr']
+
+    initPara = '50,50,5,5'
+    
+    reward1s = {}
+    reward2s = {}
+
+    cov = np.eye(8)
+    cov[:4, 4:] = np.eye(4) * gamma
+    cov[4:, :4] = np.eye(4) * gamma
+
+    rewards = np.random.multivariate_normal(np.zeros(8), cov=cov)
+
+    reward1s = rewards[0:4].reshape((2, 2))
+    reward2s = rewards[4:].reshape((2, 2)).T
+    
+    rMin = np.amin(reward1s)  #min and max rewards from the game, will help in defining the initial Q distribution
+    rMax = np.amax(reward1s)
+    strInitPara = initPara.split(',')
+    intInitPara = [int(e) for e in strInitPara]
+    
+    env = Environment02(Nact, reward1s, reward2s)
+    ga = GameAssignment01()
+    
+    allxBar = []
+    
+    # This will run multiple simulations so that the results can be averaged over
+    allConverged = []
+    for sim in range(Nsim):
+        countActionT = []
+        convergenceT = []
+        xbarT = []
+        QbarT = []
+        
+        #initialize
+        agents = []
+        for i in range(Nagent):
+            agent = Agent02(env,
+                            lr=lr,
+                            tau=tau)
+            
+            x0 = np.random.beta(intInitPara[0],intInitPara[1])
+            x1 = np.random.beta(intInitPara[2],intInitPara[3])
+            agent.Q[0] = x0*(rMax-rMin)+rMin # scales the distribution to ensure that the Q0 values lie within the given range
[…]

### 2020-05-22 EGT-RL/MeanFieldSim/ParameterSweep.py

@@ -1,53 +1,0 @@
-# -*- coding: utf-8 -*-
-
-import sys
-import os
-import numpy as np
-from tqdm import tqdm
-
-sys.path.append('../_NIPS2019_code/MAS_Environments')
-sys.path.append('../_NIPS2019_code/MAS_Agents')
-sys.path.append('../_NIPS2019_code/MAS12')
-
-from Agent02 import Agent02
-from Environment02 import Environment02
-from GameAssignment01 import GameAssignment01
-from MAgame1202 import runSim
-
-dirName = 'ParameterSweep Results'
-if not os.path.exists(dirName):
-    os.makedirs(dirName)
-
-nSimulations = 5
-gameName = 'PD'
-
-allMeanTraj = []
-allParams = []
-
-converged = []
-tau = 0.01
-
-for r in tqdm(np.linspace(0, 5, num=10)):
-    for gamma in np.linspace(-1, 1, num=10):
-
-        if not os.path.exists(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma)):
-             parameters = {'tau': tau, 'lr': r * tau}
-
-             allParams.append([tau, r])
-
-             meanConvergence = runSim(nSimulations, parameters, gamma)
-             # allMeanTraj.append(np.array(allxBar))
-
-             # allMeanTraj.append(np.array(np.mean(np.array(allxBar).squeeze(), axis = 0)))
-
-             with open(dirName + '/parameterSweep_r_{0}_gamma_{1}.txt'.format(r, gamma), 'w') as f:
-                f.write('r: {0}, gamma: {1} \n'.format(r, gamma))
-                f.write('Converged: {0} \n'.format(str(meanConvergence)))
-                # for probs in allMeanTraj[-1]:
-                #     f.write(str(probs) + '\n')
-                f.close()
-        else:
-            continue
-
-
-print('hi')

### 2020-05-22 EGT-RL/_NIPS2019_code/MAS12/MAgame1202.py

@@ -1,188 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Mon May 13 18:40:55 2019
-
-@author: cwleung
-"""
-# concurrent learning (2p), 1 vs m
-# no network
-# matrix game
-# Q
-
-import sys
-import os
-import numpy as np
-from collections import Counter
-import matplotlib.pyplot as plt
-
-from tqdm import tqdm
-sys.path.append('../MAS_Environments')
-sys.path.append('../MAS_Agents')
-
-from Environment02 import Environment02
-from Agent02 import Agent02
-
-from GameAssignment01 import GameAssignment01
-
-
-def runSim(Nsim, parameters, gamma):
-    
-    T = 50
-    Nagent = 1000
-    Nplayer = 2
-    m = 50
-    
-    Nact = 2
-    
-    tau = parameters['tau']
-    lr = parameters['lr']
-    
-    #initPara = '80,20,90,10' #Beta distribution parameters. Makes it so that action 1 has a higher probability than action 2
-    #initPara = '20,80,80,20'
-    initPara = '50,50,5,5'
-    
-    
-    # dirName = 'result_Q-boltzmann_%s-%s_lr%.2f_temp%.1f_N%d_m%d'%(gameName, initPara, lr, tau, Nagent, m)
-    
-    #if not os.path.exists(dirName):
-    #    os.makedirs(dirName)
-    
-    reward1s = {}
-    reward2s = {}
-
-    cov = np.eye(8)
-    cov[:4, 4:] = np.eye(4) * gamma
-    cov[4:, :4] = np.eye(4) * gamma
-
-    rewards = np.random.multivariate_normal(np.zeros(8), cov=cov)
-
-    reward1s = rewards[0:4].reshape((2, 2))
-    reward2s = rewards[4:].reshape((2, 2)).T
-    
-    rMin = np.amin(reward1s)  #min and max rewards from the game, will help in defining the initial Q distribution
-    rMax = np.amax(reward1s)
-    strInitPara = initPara.split(',')
-    intInitPara = [int(e) for e in strInitPara]
-    
-    env = Environment02(Nact, reward1s, reward2s)
-    ga = GameAssignment01()
-    
-    allxBar = []
-    
-    # This will run multiple simulations so that the results can be averaged over
-    allConverged = []
-    for sim in range(Nsim):
-        countActionT = []
-        convergenceT = []
-        xbarT = []
-        QbarT = []
-        
-        #initialize
-        agents = []
[…]

### 2020-05-22 MeanFieldDyn.m

@@ -1,55 +1,0 @@
-%%
-clear
-
-global deltaQ;
-global deltaT;
-global tau;
-global eta;
-
-deltaQ = 1e-2;
-deltaT = 1e-2;
-%% Set up game
-
-tau = 10;
-eta = 1;
-
-game = zeros(2, 2, 3);
-game(:, :, 1) = [3, 0; 0, 1];
-game(:, :, 2) = [3, 5; 5, 1];
-nAgents = 1e3;
-qValues = rand(2, nAgents);
-
-%% Determine p_init
-
-p = @(Q)  nnz(find(((qValues(1, :) > Q(1)) & (qValues(1, :) < (Q(1) + deltaQ)) & (qValues(2, :) > Q(2)) & (qValues(2, :) < (Q(2) + deltaQ)))))/nAgents;
-
-%% Determine v(t)
-
-v = @(Q, X) eta/(exp(tau * (Q(1))) + exp(tau * (Q(2)))) * [exp(tau * (Q(1))); exp(tau * (Q(2)))] .* (game(:, :, 2) * X - Q);
-
-%% Determine p_dot
-
-pdot = @(Q, X) -1 * sum((p(Q + deltaQ) * v(Q + deltaQ, X) - p(Q) * v(Q, X))./deltaQ);
-
-%% Update p(t)
-
-for t = 0:deltaT:10
-   x = [0; 0];            
-    for q1 = 0:deltaQ:(1 - deltaQ)
-        for q2 = 0:deltaQ:(1 - deltaQ)
-            x(1) = x(1) + ((exp(tau * (q1 + deltaQ/2))/(exp(tau * (q1 + deltaQ/2)) + exp(tau * (q2 + deltaQ/2)))) * p([q1; q2]));
-            x(2) = x(2) + ((exp(tau * (q2 + deltaQ/2))/(exp(tau * (q1 + deltaQ/2)) + exp(tau * (q2 + deltaQ/2)))) * p([q1; q2]));
-        end
-    end
-   
-   xCurrent = x
-    
-   p_old = p;   
-   p = @(Q) p_old(Q) + pdot(Q, xCurrent) * deltaT;
-   
-   v = @(Q, X) eta/(exp(tau * (Q(1))) + exp(tau * (Q(2)))) * [exp(tau * (Q(1))); exp(tau * (Q(2)))] .* (game(:, :, 1) * X - Q);
[…]

### 2020-05-22 MeanFieldDynwithMat.m

@@ -1,62 +1,0 @@
-%%
-clear
-
-global deltaQ;
-global deltaT;
-global tau;
-global eta;
-
-deltaQ = 1e-2;
-iterQ = 0:deltaQ:(1-deltaQ);
-deltaT = 1e-2;
-%% Set up game
-
-tau = 10;
-eta = 1;
-
-game = zeros(2, 2, 3);
-game(:, :, 1) = [3, 0; 0, 1];
-game(:, :, 2) = [3, 5; 5, 1];
-nAgents = 1e3;
-qValues = rand(2, nAgents);
-
-
-%% determine pInit
-p = @(Q)  nnz(find(((qValues(1, :) > Q(1)) & (qValues(1, :) < (Q(1) + deltaQ)) & (qValues(2, :) > Q(2)) & (qValues(2, :) < (Q(2) + deltaQ)))))/nAgents;
-
-pMAT = zeros(1/deltaQ, 1/deltaQ);
-for q1 = 1:1/deltaQ
-    for q2 = 1:1/deltaQ
-        pMAT(q1, q2) = p([iterQ(q1); iterQ(q2)]);
-    end
-end
-%%
-x = [0; 0];            
-for q1 = 1:1/deltaQ
-    for q2 = 1:1/deltaQ
-        x(1) = x(1) + ((exp(tau * (iterQ(q1) + deltaQ/2))/(exp(tau * (iterQ(q1) + deltaQ/2)) + exp(tau * (iterQ(q2) + deltaQ/2)))) * pMAT(q1, q2));
-        x(2) = x(2) + ((exp(tau * (iterQ(q2) + deltaQ/2))/(exp(tau * (iterQ(q1) + deltaQ/2)) + exp(tau * (iterQ(q2) + deltaQ/2)))) * pMAT(q1, q2));
-    end
-end
-
-xCurrent = x;
-
-%%
-
-v = @(Q, X) eta/(exp(tau * (Q(1))) + exp(tau * (Q(2)))) * [exp(tau * (Q(1))); exp(tau * (Q(2)))] .* (game(:, :, 1) * X - Q);
-
-
-
-
-
[…]

### 2020-05-28 Documents/ChaoticDynamics/WriteUp.tex
minor mods

--- 2020-05-21 ChaoticDynamics/WriteUp.tex
@@
 \usepackage[margin=2cm]{geometry}
-\usepackage{amsmath}
+\usepackage{amsmath,amsfonts}
 \usepackage{mathtools}
+
+\usepackage{color}
+\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
 
@@
 \maketitle
+
+\fb{the bibfile is missing.}
 
@@
 
+ \fb{you might discuss in which way any of the points above differs from the relevant reference.}
+
 	% subsection objectives_and_scope (end)
@@
 	\label{sec:derivation}
+
+        \fb{it would be good to have a overall description of the goal of the derivation.}
 
@@
 
-		In order to follow the conventions of spin glass theory for the analysis of disordered systems,
-	we rescale the system so that the payoff matrix elements are of order $N^{-1/2}$. The motivation
-	for doing this is that, along the way, we will take the limit of the number of actions $N$ to
-	infinity. However, doing this will result in numerical underflow of the action probabilities 
-	(i.e. the probability of each action goes to zero). To compensate for this, we adjust the
-	system so that the sum of the probabilities add to $N$. The scaling goes as follows:
-
+		In order to follow the conventions of spin glass
+                theory for the analysis of disordered systems, we
+                rescale the system so that the payoff matrix elements
+                are of order $N^{-1/2}$. The motivation for doing this
+                is that, along the way, we will take the limit of the
+                number of actions $N$ to infinity. However, doing this
+                will result in numerical underflow of the action
+                probabilities (i.e. the probability of each action
+                goes to zero). To compensate for this, we adjust the
+                system so that the sum of the probabilities add to
+                $N$. The scaling goes as follows:
+%
 	\begin{subequations}
@@
 
-	The need for the factor of $\frac{1}{\sqrt{N}}$ is to follow the conventions of the saddle point
-	method of integration. This will become clear after taking the expectation of the generating
-	functional. Note that we may drop the notation on time dependence for $x$ and $y$. However, these
-	will always be functions of time. Henceforth, we shall not write the tildes on $x, y, a_{ij},
-	b_{ij}$. We shall also abbreviate the final term as
-
+	The need for the factor of $\frac{1}{\sqrt{N}}$ is to follow
+        the conventions of the saddle point method of
+        integration. This will become clear after taking the
+        expectation of the generating functional. Note that we may
+        drop the notation on time dependence for $x$ and $y$. However,
+        these will always be functions of time. Henceforth, we shall
+        not write the tildes on $x, y, a_{ij}, b_{ij}$. We shall also
+        abbreviate the final term as
+%
 	\begin{equation*}
@@
 	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
-	that we moved the term containing the quenched disorder into a separate exponential. Since our
+	that we moved the term \fb{which one exactly?} containing the quenched disorder into a separate exponential. Since our
 	aim is to take an average over all possible realisations of this disorder, we will only need to
@@
 	are all multiplied together and we sum over the subscripts, the letters we choose are of no
-	importance and we can exchange them freely. We will define both exponentials in $Q$ as $Q_1$ and
+	importance and we can exchange them freely \fb{perhaps some more justification might be helpful}. We will define both exponentials in $Q$ as $Q_1$ and
 	$Q_2$ respectively.
@@
 	\frac{\partial f}{\partial \hat{C}_x(t, t')} &\implies C_x(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i <x_i(t) x_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle x_i(t) x_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \psi_i(t) \partial \psi_i (t')} \bigg|_{\Vec
@@
 	\frac{\partial f}{\partial \hat{L}_x(t, t')} &\implies L_x(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i <\hat{x}_i(t) \hat{x}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle \hat{x}_i(t) \hat{x}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial h_{x,i}(t) \partial h_{x, i} (t')} \bigg|_{\Vec
@@
 	\frac{\partial f}{\partial \hat{K}_x(t, t')} &\implies K_x(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i <x_i(t) \hat{x}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle x_i(t) \hat{x}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \Vec{\psi}(t) \partial h_{x, i} (t')}
@@
 \frac{\partial f}{\partial \hat{C}_y(t, t')} &\implies C_y(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i <y_i(t) y_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle y_i(t) y_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \phi_i(t) \partial \phi_i (t')} \bigg|_{\Vec
@@
 	\frac{\partial f}{\partial \hat{L}_y(t, t')} &\implies L_y(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i <\hat{y}_i(t) \hat{y}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle \hat{y}_i(t) \hat{y}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial h_{y,i}(t) \partial h_{y, i} (t')} \bigg|_{\Vec
@@
 	\frac{\partial f}{\partial \hat{K}_y(t, t')} &\implies K_y(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i <y_i(t) \hat{y}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle y_i(t) \hat{y}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \Vec{\phi}(t) \partial h_{x, i} (t')}
@@
 	\infty}
-N^{-1} \sum_i <\hat{x}_i(t) \hat{y}_i(t')>_\Omega = -\lim_{N \rightarrow \infty} \sum_i
+N^{-1} \sum_i \langle \hat{x}_i(t) \hat{y}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
 \frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \partial h_{x, i} (t) \partial h_{y, i} (t')}
@@
 \begin{align}
-	G_x(t, t') &= <\frac{\delta x(t)}{\delta \eta_x(t')}> & G_y(t, t') &= <\frac{\delta y(t)}{\delta
-	\eta_y(t')}> \\
-	<\eta_x(t) \eta_x(t')> &= C_y(t, t') & <\eta_y(t) \eta_y(t')> &= C_x(t, t')\\
-	<\mu_x(t) \mu_y(t')> &= C_x(t, t') C_y(t, t') & <\mu_x(t) \mu_x(t')> &= <\mu_y(t) \mu_y(t')> = 0
+	G_x(t, t') &= \langle \frac{\delta x(t)}{\delta \eta_x(t')}\rangle  & G_y(t, t') &= \langle \frac{\delta y(t)}{\delta
+	\eta_y(t')}\rangle  \\
+	\langle \eta_x(t) \eta_x(t')\rangle  &= C_y(t, t') & \langle \eta_y(t) \eta_y(t')\rangle  &= C_x(t, t')\\
+	\langle \mu_x(t) \mu_y(t')\rangle  &= C_x(t, t') C_y(t, t') & \langle \mu_x(t) \mu_x(t')\rangle  &= \langle \mu_y(t) \mu_y(t')\rangle  = 0
 \end{align}

### 2020-06-03 Documents/ChaoticDynamics/WriteUp.tex
Included ESA, updated Write Up

--- 2020-05-21 ChaoticDynamics/WriteUp.tex
@@
 
-	Analyse the stability of Multiagent Q-Learning on iterated games. Brings the work presented by
-	Sanders et al to the reinforcement learning community.
+	Analyse the stability of Multiagent Q-Learning on iterated games.
 
@@
 	\end{itemize}
+
+	The work by Sanders et al. considers agents who have these same assumptions, but learn with a
+	reduced version of the Experience Weighted Attraction algorithm. For the Reinforcement Learning
+	community, it is of interest to consider the question of stability from the point of view of
+	agents who follow the popular Q-Learning algorithm.
+
+ \fb{you might discuss in which way any of the points above differs from the relevant reference.}
 
@@
 	\end{subequations}
+
+	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al.
+refer to these as the memory and intensity of choice parameters respectively.
+Agent 1 takes action i with probability $x_i$ while Agent 2 takes action j with probability $y_j$.
+If these actions are taken, the agents receive payoff $a_{ij}$ and $b_{ji}$ respectively.
 
@@
 	where the equations of motion are the Lagrange equations of motion given in (
-	\ref{eqn::scaledEOM}) and
+	\ref{eqn::scaledEOM}) andSince
 	the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
@@
 		\hat{y}
-		(t')]])
+		(t')]).
 	\end{split}
@@
 	\begin{split}
-		\dot{x}(t) = x(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_y(t, t')x(t')] + \rho_x(t) +
-		\alpha \tilde{\tau} \eta_x(t) + \tilde{\alpha} \tau \frac{\eta_x(t) \eta_y(t)}{2} + 
+		\dot{x}(t) &= x(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_y(t, t')x(t')] + 
+		\tilde{\alpha}
+		\rho_x(t) + \alpha \tilde{\tau} \eta_x(t) + \tilde{\alpha} \tau \eta_x(t) \eta_y(t) +
 		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_x) \\
-		\dot{y}(t) = y(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_x(t, t')y(t')] + \rho_y(t) +
-		\alpha \tilde{\tau} \eta_y(t) + \tilde{\alpha} \tau \frac{\eta_x(t) \eta_y(t)}{2} + 
-		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_y) \\
+		\dot{y}(t) &= y(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_x(t, t')y(t')] + 
+		\tilde{\alpha} \rho_y(t) +
+		\alpha \tilde{\tau} \eta_y(t) + \tilde{\alpha} \tau \eta_x(t) \eta_y(t)+ 
+		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_y), \\
 	\end{split}
@@
 	<\eta_x(t) \eta_x(t')> &= C_y(t, t') & <\eta_y(t) \eta_y(t')> &= C_x(t, t')\\
-	<\mu_x(t) \mu_y(t')> &= C_x(t, t') C_y(t, t') & <\mu_x(t) \mu_x(t')> &= <\mu_y(t) \mu_y(t')> = 0
+	<\mu_x(t) \mu_y(t')> &= C_x(t, t') C_y(t, t') & <\mu_x(t) \mu_x(t')> &= <\mu_y(t) \mu_y(t')> = 0.
 \end{align}
@@
 	\mu_x(t) = \mu_x^* + \hat{\delta}_x(t)\\
-	\mu_y(t) = \mu_y^* + \hat{\delta}_y(t)
+	\mu_y(t) = \mu_y^* + \hat{\delta}_y(t),
 \end{align}
@@
 		\frac{d}{dt} (x^* + \hat{x}(t)) = (x^* + \hat{x}(t))(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'
-		[G_y(t, t')(x^* + \hat{x}(t'))] + \rho_x(t) + \alpha \tilde{\tau} (\eta_x^* + \hat{\nu}_x
-		(t)) \\ + \tilde{\alpha} \tau \frac{(\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t))}
-		{2} + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_x^* + \hat{\delta}_x(t)) + \xi(t)) \\
+		[G_y(t, t')(x^* + \hat{x}(t'))] + \tilde{\alpha} \rho_x(t) + \alpha \tilde{\tau} (\eta_x^* + \hat{\nu}_x
+		(t)) \\ + \tilde{\alpha} \tau (\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t)) + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_x^* + \hat{\delta}_x(t)) + \xi(t)) \\
 		\frac{d}{dt} (y^* + \hat{y}(t)) = (y^* + \hat{y}(t))(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'
-		[G_x(t, t')(y^* + \hat{y}(t'))] + \rho_y(t) + \alpha \tilde{\tau} (\eta_y^* + \hat{\nu}_y
-		(t)) \\ + \tilde{\alpha} \tau \frac{(\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t))}
-		{2} + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_y^* + \hat{\delta}_y(t)) + \zeta(t))
+		[G_x(t, t')(y^* + \hat{y}(t'))] + \tilde{\alpha} \rho_y(t) + \alpha \tilde{\tau} (\eta_y^* + \hat{\nu}_y
+		(t)) \\ + \tilde{\alpha} \tau (\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t))
+		 + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_y^* + \hat{\delta}_y(t)) + \zeta(t)).
 	\end{split}
@@
 
+\begin{equation} 
+	\label{eqn::Linearisation}
+	\begin{split}
+	\frac{d}{dt} \hat{x}(t) = (x^* + \hat{x}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_x \right] \\
+	+ x^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_y(t - t') \hat{x}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_x(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_x(t) + \xi(t) \right]\\
+	\frac{d}{dt} \hat{y}(t) = (y^* + \hat{y}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_x(t - t') dt' + \tilde{\alpha} \rho_y^* + \alpha \tilde{\tau} \eta_y^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_y \right] \\
+	+ y^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_x(t - t') \hat{y}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_y(t) + \zeta(t) \right].\\
+	\end{split}
+\end{equation}
+
+If we consider the long term behaviour of the system near a stable fixed point, then $\hat{x}(t)$ goes to zero as $t \rightarrow \infty$.
+This yields the requirement that a fixed point $x^*$ must satisfy
+
+\begin{equation}
+	0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x \right].
+\end{equation}
+
+The implication here is that the resulting value of $x^*$ can take two solutions.
+However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values.
+If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$.
+Numerical experiments will shed more light on the likelihood of convergence.
+If this ansatz turns out to be incorrect (i.e.
+we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
+
+We continue to follow the method of Opper et al.
+by taking the Fourier transform of (\ref{eqn::Linearisation}).
+For both agents, the first term in square brackets is constant with respect to time and so will not affect the long term behaviour of the system.
+We can, therefore, ignore this and focus on the second term.
+For the sake of brevity, we will only write the equations for Agent 1 (i.e.
+for $x$), though the equations for y can be equivalently obtained.
+Taking the Fourier transform yields
+
+\begin{equation}
+	\left[ \frac{i \omega}{x^*} - \Gamma \alpha^2 \tilde{\tau}^2 \mathcal{G}_y(\omega)\right] \mathcal{X}(w) = \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega).
+\end{equation}
+
+Then,
+
+\begin{equation} \label{eqn::Transformed}
+	\left<[|\mathcal{X}(\omega)|^2 \right> = \left< | \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega) |^2 \right> \frac{1}{\left< |\mathcal{A}(\omega, x^*) |^2 \right>},
+\end{equation}
+
+where
+
+\begin{equation}
+	\mathcal{A}(\omega, x^*) = \frac{i \omega}{x^*} - \Gamma \alpha^2 \tilde{\tau}^2 \mathcal{G}_y(\omega)
+\end{equation}
+
+The behaviour of this line for $\omega = 0$ gives the long term behaviour of the system.
+By considering that, for a stable fixed point to exist, $\left<[|\mathcal{X}(\omega = 0)|^2 \right>$, we arrive at an expression for a stability line (i.e.
+the phase transition between the existence of stable fixed points and unstable behaviour).
+
 % section stability_analysis (end)

### 2020-06-03 Documents/ESA/main.tex
Included ESA, updated Write Up

\documentclass[11pt]{report}

\usepackage{graphicx}
\usepackage{subfiles}
\usepackage[margin=.8in,letterpaper]{geometry}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{calc}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{\leftmark}

\begin{document}

\clearpage\thispagestyle{empty}
\begin{titlepage}
    \begin{tikzpicture}[overlay, remember picture]
        \node[anchor=north west, %anchor is upper left corner of the graphic
        xshift=0.5cm, %shifting around
        yshift=-0.5cm] 
        at (current page.north west) %left upper corner of the page
        {\includegraphics[width= 0.5 \textwidth]{Figures/ImperialLogo.jpg}}; 
    \end{tikzpicture}

	\flushright
    \hfill
    \vfill
	{\Huge Early Stage Report \par} 
	\rule[5pt]{\textwidth}{.4pt} \par
	{\Large Aamal Abbas Hussain \\ CID: 01060230}
	\vfill 
    {\Large Department of Computing\\Imperial College London\\Supervisor: Francesco Belardinelli\\
	June 2020 \\}
\end{titlepage}

\subfile{sections/Abstract.tex}

\tableofcontents

\chapter{Introduction} \subfile{sections/Intro.tex} \label{ch::Intro}

\chapter{Literature Review} \subfile{sections/LitReview.tex} \label{ch::Lit_Review}

\chapter{Proposed Research} \subfile{sections/ProposedResearch.tex} \label{ch::ProposedResearch}

\chapter{Short Term Goals} \subfile{sections/ShortTermGoals.tex} \label{ch::ShortTermGoals}

\chapter{Research Timeline} \subfile{sections/ResearchTimeline.tex} \label{ch::ResearchTimeline}

\end{document}

### 2020-06-03 Documents/ESA/sections/Abstract.tex
Included ESA, updated Write Up

\documentclass[.../main.tex]{subfiles}

\begin{abstract}

\end{abstract}

### 2020-06-03 Documents/ESA/sections/Intro.tex
Included ESA, updated Write Up

\documentclass[.../main.tex]{subfiles}

\begin{document}

    \section{Problem Statement} \label{sec::Problem_Statement}

    \section{Objectives and Scope} \label{sec::Objectives_and_Scope}

    \section{Methodology} \label{sec::Methodology}

\end{document}

### 2020-06-03 Documents/ESA/sections/LitReview.tex
Included ESA, updated Write Up

\documentclass[.../main.tex]{subfiles}

\begin{document}

    \section{Multi Agent Systems} \label{sec::Multi_Agent_Systems}

    \section{Game Theory} \label{sec::Game_Theory}
    \subsection{Stochatic Games} \label{sec::Stochastic_Games}
    \subsection{Game Theoretic Control} \label{Game Theoretic Control}

    \section{Multi Agent Reinforcement Learning} \label{sec::MARL}
    \subsection{Learning in Two Player Games} \label{sec::Two_Player_Games}
    \subsection{Learning in Stochastic Games} \label{sec::Learning_Stochastic_Games}
    \subsection{Multi Agent Learning Dynamics} \label{sec::MARL_Dynamics}

    \section{Control Theory} \label{sec::Control_Theory}
    \subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}
    \subsection{Approaches to Swarm Control} \label{sec::Swarm Control}

    \section{Swarms} \label{sec::Swarms}
    \subsection{Decision Making in Swarms} \label{sec::Decisions_in_Swarms}

\end{document}

### 2020-06-03 Documents/ESA/sections/ProposedResearch.tex
Included ESA, updated Write Up

\documentclass[.../main.tex]{subfiles}

\begin{document}
    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
\end{document}

### 2020-06-03 Documents/ESA/sections/ShortTermGoals.tex
Included ESA, updated Write Up

\documentclass[.../main.tex]{subfiles}

\begin{document}
    \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}
    \subsection{Research Summary} \label{sec::Research Summary}

    \section{Control of Swarms with Independent Agents} \label{sec::Independent_Swarm_Control}

\end{document}

### 2020-06-03 Documents/ChaoticDynamics/WriteUp.tex
Merged Conflicts

@@
 
+        \fb{it would be good to have a overall description of the goal of the derivation.}
+
 	We start with the two-agent Q-Learning dynamics as presented by Tuyls et al.
@@
 \begin{align}
-	G_x(t, t') &= <\frac{\delta x(t)}{\delta \eta_x(t')}> & G_y(t, t') &= <\frac{\delta y(t)}{\delta
-	\eta_y(t')}> \\
-	<\eta_x(t) \eta_x(t')> &= C_y(t, t') & <\eta_y(t) \eta_y(t')> &= C_x(t, t')\\
-	<\mu_x(t) \mu_y(t')> &= C_x(t, t') C_y(t, t') & <\mu_x(t) \mu_x(t')> &= <\mu_y(t) \mu_y(t')> = 0.
+	G_x(t, t') &= \langle \frac{\delta x(t)}{\delta \eta_x(t')}\rangle  & G_y(t, t') &= \langle \frac{\delta y(t)}{\delta
+	\eta_y(t')}\rangle  \\
+	\langle \eta_x(t) \eta_x(t')\rangle  &= C_y(t, t') & \langle \eta_y(t) \eta_y(t')\rangle  &= C_x(t, t')\\
+	\langle \mu_x(t) \mu_y(t')\rangle  &= C_x(t, t') C_y(t, t') & \langle \mu_x(t) \mu_x(t')\rangle  &= \langle \mu_y(t) \mu_y(t')\rangle  = 0
 \end{align}

### 2020-06-03 Documents/ChaoticDynamics/WriteUp.tex
Added Results to Chaotic Dynamics

@@
 \usepackage{mathtools}
-
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{color}
@@
 
-The behaviour of this line for $\omega = 0$ gives the long term behaviour of the system.
-By considering that, for a stable fixed point to exist, $\left<[|\mathcal{X}(\omega = 0)|^2 \right>$, we arrive at an expression for a stability line (i.e.
-the phase transition between the existence of stable fixed points and unstable behaviour).
+The behaviour of this line for $\omega = 0$ gives the long term behaviour of the system. By
+considering that, for a stable fixed point to exist, $\left<[|\mathcal{X}(\omega = 0)|^2 \right>$,
+we arrive at an expression for a stability line (i.e. the phase transition between the existence of
+stable fixed points and unstable behaviour).
 
 % section stability_analysis (end)
+
+\section{Numerical Simulations} % (fold)
+\label{sec:numerical_simulations}
+
+\begin{figure}[h]
+
+	\centering
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
+	\end{subfigure}
+
+	\caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
+	simulation is run for 1e5 iterations and tested for convergence. The game is said to have
+	converged based on a tolerance of 1\% difference between action probabilities. For each
+	combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
+	and initial conditions. The average number of converged games (giving an indication of
+	probability of convergence) is shown in each cell of the heatmap.}
+\end{figure}
+
+% section numerical_simulations (end)
 \end{document}

### 2020-06-03 Documents/ESA/sections/Intro.tex
Added Results to Chaotic Dynamics

@@
 \begin{document}
+
+    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
+    the overall success of the system \cite{HammanFormalApproach}. The union of populations of
+    agents who share the same goal can give rise to behaviours that are far more complex than
+    individual robots can achieve. The same, of course, is true for humans; whilst an individual may
+    be capable of building a house, it takes many more to build a city.
+
+    The ability to exhibit complex
 

### 2020-06-03 Documents/ESA/sections/Intro.tex
Updated Introduction

--- 2020-06-03 Documents/ESA/sections/Intro.tex
@@
 
+    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
+    the overall success of the system \cite{HammanFormalApproach}. The collaboration of many agents
+    who share the same goal can give rise to behaviours that are far more complex than individual
+    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
+    we are presented with ever more challenging tasks including: search and rescue, cleaning up
+    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
+    and so we must leverage the capacity for agents in a swarm to collectively achieve our
+    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
+    towards this very problem and address the question: how does the dynamical behaviour of a
+    population of agents change under the influence of control? Note that we use the term 'agent'
+    loosely here, an agent can refer to anything from a simple particle \cite{BorziCollectiveMotion}
+    to a complex robot \cite{ElamvazuthisThesis}. In answering this question, researchers have
+    gained a stronger understanding of how a swarm may be controlled to achieve desired results.
+
+    Another technique which has made incredible strides towards improving the capability of
+    autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
+    \cite{Schwarz}. This builds on the ideas of classical Reinforcement Learning which allows an
+    agent to optimise its strategies towards tackling a task through repeated exposure to that task.
+    MARL utilises this same principle with the caveat that agents must adapt their strategies based
+    not only on the outcome of the action, but also on the actions of the other agents. This has
+    shown strong results in practical applications \textbf{APPLICATIONREFERENCES}. Whilst MARL was
+    once considered to be non-identifiable (there is no clear way of identifying the algorithm that
+    a particular agent was trained on) and black box (there is no clear way of ensuring a desired
+    result from a learning algorithm), a steady stream of research is emerging to lift this fog
+    \cite{TuylsSurvey}. This allows for researchers to choose the parameters of their learning
+    algorithms appropriately to ensure that learning agents behave in the desired manner.
+
     \section{Problem Statement} \label{sec::Problem_Statement}
 
+    Based on the successes of the swarm control and MARL communities, a natural question to ask is
+    whether the promises of these disciplines may be unified. Such a combination would radically
+    improve the capabilities of autonomous system. Ultimately such a system must be driven under the
+    influence of control inputs to perform given tasks. Examples of this might be: forming around
+    individual components of space debris and moving them to a desired location (e.g. a bin), or
+    relocating to multiple areas in a disaster zone to provide immediate relief. For such tasks to
+    be achieved in dynamic environments, which is typically the case, the system must be able to
+    constantly adapt its approach and respond accordingly. Given these considerations, the problem
+    may be stated as follows
+
+    \begin{enumerate}
+    	\item A population of robots is given a goal which must be achieved, which can often be
+    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
+    	\item These are to be performed in a dynamic environment with obstacles present and where
+    	the number of tasks, and their priorities may be in constant flux.
+    	\item The agents in the system must, therefore, make decisions collectively which will in
+    	the system achieving the given goals. Due to the dynamic quality of the problem, these
+    	decisions may need to be evaluated online and in a decentralised fashion, as it may not be
+    	possible for a centralised decision maker to communicate with all agents.
+    	\item It is desirable, therefore, to control the dynamical behaviour of
+    	a system composed of agents who learn and adapt through interactions with each other. In
+    	addition, to ensure the safe operation of the system, properties such as state and control
+    	constraints must be satisfied.
+    \end{enumerate}
+
+    With the goal of addressing this problem in mind, the aim of this PhD is to address the question
+    posed by the final point: how does the dynamical behaviour of a swarm of intelligent, adaptive
+    agents evolve under the influence of defined control inputs?
+
     \section{Objectives and Scope} \label{sec::Objectives_and_Scope}
+
+    In particular, we will study
+
+    \begin{itemize}
+    	\item How the strategies of a population of agents evolves as the iteratively interact
+    	with one another. We will examine whether the system evolves to a stable equilibrium, or
+    	whether it exhibits complex, even chaotic behaviour.
+    	\item The extent to which the dynamical behaviour of a population of learning agents is
+    	influenced under given control. We seek to understand the conditions under which guarantees
+    	on theoretical results such as controllability, stability, and well-posedness may be
+    	established.
+    \end{itemize}
+
+    The resultant work will provide novel insights into the behaviour of swarm systems and provide
+    new methods for which they may be practically used. Importantly, the study will seek to
+    understand the guarantees that can be placed on the safety of such systems in terms of their
+    stability and constraint satisfaction.
+
+    \textbf{Need to talk about the scope of the project: what assumptions will be made to ensure
+    that the above can be achieved within the given time constraints?}
 

### 2020-06-04 Documents/ChaoticDynamics/WriteUp.tex
Updated ESA and Write Up

@@
 \begin{figure}[h]
-
 	\centering
@@
 	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
+	\caption{$\alpha = 0.1$}
 	\end{subfigure}
@@
 	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
+	\caption{$\alpha = 0.1$}
+	\end{subfigure}
+	%
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2.png}
+	\caption{$\alpha = 0.2$}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2_Run_2.png}
+	\caption{$\alpha = 0.1$}
 	\end{subfigure}
@@
 	and initial conditions. The average number of converged games (giving an indication of
-	probability of convergence) is shown in each cell of the heatmap.}
+	probability of convergence) is shown in each cell of the heatmap. \label{fig::Toys}}
 \end{figure}
+
+To generate the numerical simulations in Figure \ref{fig::Toys} we used the following procedure.
+
+\begin{enumerate}
+	\item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
+	it does not affect the long term behaviour of the system (it does not appear in (
+	\ref{eqn::EOM})).
+	\item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
+	over.
+	\item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
+	(variables are the payoff elements) with covariance parameterised by $\Gamma$.
+	\item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
+	\item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
+	\item Every 100 iterations, check to see if the action probabilities have changed significantly.
+	If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
+	considered to have converged.
+	\item This process is repeated 5 times with random payoff matrices generated based on the value
+	of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
+	converged}}{5}$.
+	\item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
+	heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
+	tested.
+\end{enumerate}
 

### 2020-06-04 Documents/ESA/sections/LitReview.tex
Updated ESA and Write Up

@@
 
+In this chapter, we explore the current state of the art in Multi-Agent Systems (MAS). We will
+consider the main techniques that have been proposed towards task allocation and control.
+
 \section{Multi Agent Systems} \label{sec::Multi_Agent_Systems}
 
+\textbf{TODO: Elaborate on each of the metrics}
+
+We will keep the problem statement defined in Section \ref{sec::Objectives_and_Scope} in mind as
+we define several metrics which a Multi Agent System (MAS) may be assessed against.
+
+\begin{enumerate}
+    \item Scalable
+    \item Distributed
+    \item Generality
+    \item Low Computational Load
+    \item Robustness
+\end{enumerate}
+
+We will use these metrics, alongside the problem statement to approach the current literature
+surrounding the theory and practices of Multi-Agent Systems.
+
 \section{Game Theory} \label{sec::Game_Theory}
-    \subsection{Stochatic Games} \label{sec::Stochastic_Games}
+
+Game Theory has a rich history when considering an understanding of multi-agent systems and it
+is impossible to examine MAS without an understanding of Game Theory. These
+begin in economics but have found a strong application in computation due to the rising need for
+distributed systems. Game Theory, therefore, branches across all of the categories in this
+chapter although its synergy with swarms requires development) since Dec-POMDP
+and MARL methods have both base their theory upon the foundations of Game Theory.
+
+\subsection{Partially Observed Stochatic Games (POSG)} \label{sec::Stochastic_Games}
+
+POSGs act as a game theoretic corollary to the Dec-POMDP.
+Here, an optimal solution is found by fixing the strategy (a manner of selecting an action \cite{Rizk2018DecisionSurvey}) of all agents except one.
+The optimal strategy of the chosen agent is then computed.
+This is fixed so that the next agent may determine its optimal strategy.
+This process is iterated over all agents in a process known as Alternating Maximisation \cite{Ray2010AnCooperation}.
+By choosing strategies which maximise a common payoff, a globally optimal solution can be found.
+
+Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is sometimes referred to as an ‘incomplete information game’).
+This allows for a POSG to be approximated by a sequence of smaller, more tractable games \cite{Emery-MontemerloApproximatePayoffs}.
+However, iterating through the entire team of agents to find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic situations.
+To address this, \cite{Ray2010AnCooperation} propose to place distinct payoffs on each agent and to consider team formation based on social hierarchy as well as preferred partners.
+This allows the complexity of the problem to be broken down into smaller game units and also provides a clear order in which the games are to be played.
+This minimises the interference across robots and allows for more immediate action to be taken by agents who choose their strategy early on, while leaving more passive tasks for those later in the sequence.
+
+The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and dynamic decision making.
+However, as found by Dai et.
+al \cite{Dai2018TaskSystems} this is conditional on an understanding by each robot of the strategy of others, which in turn requires adequate communication between robots.
+Therefore, the game theoretical formulation will fail where communication is not possible amongst team members.
+However, the addition of heuristics, such as deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other members of its team without the need for significant explicit communication.
+
+\textbf{Add in any recent literature in these fields}
+
 \subsection{Game Theoretic Control} \label{Game Theoretic Control}
 
+Game theory can often be applied to problems of control theory (particularly where there are
+multiple agents) to develop robust controllers which guarantee properties of stability and
+constraint satisfaction.
+
+This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
+which the players are a controller and an adversarial environment. The design of the controller must
+be such that it is able to drive the system to zero error. To illustrate, consider the problem of
+designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
+vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
+efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
+agent may encounter without actually encountering them. The same notion is explored by Bardi et al
+\cite{Bardi1991DifferentialDisturbances}.
+
+Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
+avoidance problem, similarly from the point of view of differential game theory. They develop a
+robust feedback system for the robots which they show to be able to drive the system towards
+predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
+In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
+systems in a distributed manner. Here, agents only consider their own payoff structure and have
+limited communication with one another. The author shows that an approximate equilibrium can be
+found using algebraic methods and illustrate the capabilities of the technique using a collision
+avoidance example. For the sake of brevity the numerous contributions that Mylvaganam has made to
+this field is not presented here. However, we will conclude with those presented in
+\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
+games, including linear-quadratic differential games (in which system dynamics are linear functions
+whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
+induced across the players (a notion was suggested in the research proposal) and mean-field games,
+which is discussed in 'MARL'. The importance of the linear-quadratic
+differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
+admissable iff they are locally exponentially stable (which the author often shows with the aid of
+Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
+calculate online. The author then shows that this is not simply a theoretical exercise by applying
+the novel methods towards multi-agent collision problems and designs dynamic control laws which
+guarantee that each agent will reach their desired state whilst avoiding collision with the other
+agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
+robot system.
+
 \section{Multi Agent Reinforcement Learning} \label{sec::MARL}
+
+Reinforcement learning extends the Markov Decision Process problem by considering the case where the
+reward model is not initially known to the agent. In a similar manner, Multi Agent Reinforcement
+Learning (MARL) extends the Markov Game setting to one where the payoff structure is not a priori
+knowledge.
+
+The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
+policy may be the concatenation of all the individual policy or it may just be options for each
+agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
+and so, in this section, I will try to consider the broad spectrum of methods which attempt to
+achieve this Nash equilibria. The largest problem in MARL is the non-stationarity of the environment
+\cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian.
+However, this must be lifted in the Multi Agent setting since other agents in the environment will
+be learning concurrently. As such, we must now consider that the policy for any one agent will
+depend on the policy of all other agents.
+
+This chapter begins with a selection of the foundational methods which were developed towards
+solving the MARL problem. The interested reader may find additional methods and implementations of
+these techniques in \cite{SchwartzMulti-agentApproach}.
+
 \subsection{Learning in Two Player Games} \label{sec::Two_Player_Games}
+
+The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
+method of linear programming (in which constraints are linear). This will be important in
+considering more current methods. A similar consideration is given to the infinitesimal gradient
+ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
+infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
+not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
+particular problem in games where there are multiple Nash equilibria. However, in practice it is
+difficult to choose a convergence rate of the step size and, without an appropriate choice the
+strategy may oscillate as shown in the book. To address this, a modified approach is presented by
+Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
+WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
+to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
+payoff matrix (which is not so much of a problem for model based methods) and the opponent's
+strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
+method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
+(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
+oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
+players with minimal oscillation.
+
 \subsection{Learning in Stochastic Games} \label{sec::Learning_Stochastic_Games}
+
+Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
+must learn about the equilibrium strategies by playing the game, which means they do not have a
+priori knowledge of the reward or transition functions. Schwarz considers two properties which
+should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
+that the method should converge to some equilibrium whereas the former suggests that the method
+should learn the best response to stationary opponents. A similar set of conditions is considered by
+Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
+then presents a review of MARL methods (as of September 2014)
+
+\textbf{Add in more recent literature r.e. learning in stochastic games}
+
 \subsection{Multi Agent Learning Dynamics} \label{sec::MARL_Dynamics}
 
+Multi Agent Learning Dynamics (often referred to as Game Dynamics or Learning Dynamics)
+considers the
+problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
+another. This model then serves to be able to predict the evolution of the system as well as to
+understand the trajectory of learning. Typically, this looks at considering whether or not the
+method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
+solve \cite{ShohamMultiagentFoundations} for all but toy problems.
+\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
+are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of the environment since a stable
+equilibrium will always be returned to even after perturbations. This extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
+
+The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
+evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
+considers similar assumptions to that of MARL: agents are no longer required to be rational and
+play the game optimise their expected return through repeated play. Importantly, players have no
+knowledge of the others' payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et al.
+determine the relation between the replicator dynamics concept of EGT (a differential equation
+defining the evolution of the proportion of a subgroup in an evolving population) and Q-Learning
+using Boltzmann probabilities as Q-values. The result was a dynamics equation which describes, for
+each action, the evolution of its selection probability which could even account for random
+exploration. There have since been a number of works which apply the same insight into different
+game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken into the following
+categories
+
+\begin{itemize}
+    \item Stateless games with discrete actions. Here, stateless refers to the idea that the game is
+    static and so the environment has no impact on the result. The aforementioned result 
+    \cite{Tuyls2006AnGames} fits into this category.
+    \item Stateless games with continuous actions. These consider more realistic MARL than the
+    previous category by replacing each agent's strategy vector with a probability density function 
+    (pdf) over a continuous action space.
+    \item Stateful games with discrete actions. This mostly considers stochastic games, where there
+    are multiple states with probabilistic (usually Markovian) transitions between them. However,
+    extensive form games, which considers more complex phenomena such as sequential moves and
+    imperfect information, are also briefly mentioned.
+    \item Stateful games with continuous actions. This is one of the more realistic assumptions
+    considered. However, the authors point out that this area is yet to see results, leaving it open
+    for possible research.
+\end{itemize}
+
+Though the above have seen success through experimental validation in games with 2 players and (in
+general) 2 to 3 discrete actions, recent work has begun the consideration of improving the models
+towards more complex scenarios with larger agent populations. A recent example of this is 
+\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
+Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
+its strategy based on the mean effect of the population. The result is a system of three equations
+which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
+presents an important first step in modelling the learning dynamics of large agent populations and
+has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
+games.
+
+An advantage of determining the evolutionary dynamics of learning is that it can describe the
+expected behaviour in different game settings. This is particularly important to understand the
+convergence of the methods; certain games will often show cyclic behaviour even with the existence
+of a strict NE. For instance, Imhof et al. show in \cite{Imhof2005} that a repeated prisoner's
+dilemma game results in cyclic behaviour when considering the options of cooperation or defection.
+
 \section{Control Theory} \label{sec::Control_Theory}
+
+The control theoretic perspective considers generating a set of control laws for the system. These
+are chosen with the aim to satisfy certain properties. The main properties are
+
+\begin{itemize}
+    \item Stability, that a system will return to the desired setpoint (or within a neighbourhood) if
+    perturbed.
+
+    \item Robustness, that a system will perform its function in the presence of uncertainty and
+    noise
+
+    \item Optimality, that the system will achieve some defined function
+
+    \item Feasibility, that the controller will always be able to generate a control law which
+    satisfies the desired properties.
+\end{itemize}
+
+There are a number of approaches towards control systems. However, the interest of this review lies
+in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
+stochastic and distributed control. The literature of the control communnity is vast and can be
+divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
+those which are particularly relevant to this study and review them in this section.
+
 \subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}
+
+Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
+categories: decentralised control, non-cooperative control, cooperative control, and centralised
+control. The last of these is not considered in the text since it only considers the case in which a
+centralised controller has access and can manipulate multiple agents at once.
+
+Decentralised control is the scheme in which agents do not have information about the actions of
+other agents and can only optimise for their own objective. This has the advantage of requiring no
+communication, but can often lead to poor performance when the agents are strongly coupled as each
+agent’s model is incomplete. In the non-cooperative setting, each agent optimises their own loss
+function whilst treating the others’ actions as a known disturbance. In this setting, each agent has
+knowledge of the others’ control laws and their effect. In this case, the agents must communicate
+their intended actions to one another and iterate to achieve a consensus (or Nash equilibrium). This
+is the same for cooperative control, except that the loss function is now shared across the team.
+
+Of all of these systems, cooperative control has found greatest applicability in autonomous systems
+\cite{Negenborn2014}, perhaps due to the favourable stability properties \cite{Venkat2006}. One
+particularly strong application of this system is in vehicle platooning. Here, self-driving cars or
+unmanned aerial vehicles (UAVs) must move in a certain formation without colliding into one another.
+A number of examples can be found such as in \cite{Liu2019, VanParys2017, Zheng2017}. Distributed
+MPC provides the advantage that guarantees can be placed regarding coupled constraint satisfaction
+and feasibility.
+
+The advances in stochastic and robust MPC, however, do lend themselves towards revisiting the
+capabilities of decentralised control. Recall that, in this scheme, the agents cannot communicate
+with one another. However, advances in MARL show us that this disadvantage can be made less
+prevalent if each agent has a model of the other \cite{Foerster}. To this end, a methodology such as
+presented in \cite{Heirung2019} may prove beneficial in the decentralised scheme. Here, the system
+chooses amongst a family of system models when choosing its control laws. Similarly, agents who
+determine (or perhaps learn) models of the other agents may be able to leverage this information,
+minimising the model error when optimising.
+
 \subsection{Approaches to Swarm Control} \label{sec::Swarm Control}
 
+Recent work has seen the advancement of swarms controlled in stochastic environments. This is
+particularly important for swarm intelligence in robots; many systems are developed with the
+motivation of search-and-rescue, in which the robot swarms will have to operate in environments
+where accounting for uncertainty is critical. To this end, swarm systems have seen the advent of
+stochastic control. In this, the swarm is modelled as a diffusive system using a stochastic
+equation, most often the Kolmogorov Forward Equation \cite{Hamann2008}. In \cite{Hamann2008}, the author shows that this equation can be derived by considering local trajectories of
+smaller subsets of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019} extend this idea to other
+stochastic models for swarms, importantly considering an advection-diffusion-reaction model which
+allows for hybrid agents to switch between different modes of operation.
+
+The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
+equations
+for stochastic forward processes (such as swarm foraging) in which, as the number of agents tends to
+infinity, the true macroscopic motion of the system tends to these equations. Importantly, however,
+these stochastic equations allow for an analysis of the swarm, as well as the ability to develop
+control laws. In \cite{Li2017}, Li et al show that these models can be used to develop control
+laws for robots in a swarm and drive them towards a target distribution. The method is shown to
+perform accurately both in simulation and on real robots. The advantage is that guarantees can be
+placed on the convergence and stabilisabiilty of the swarm towards the desired distribution.
+However, there appears to be significant scope to expand upon this methodology from a safety
+perspective. To begin with, the method does not consider inter-agent interactions and therefore does
+not formally guard against collisions. In \cite{Inoue2019}, a similar problem is considered,
+although collisions are avoided by having the robot simply move in the opposite direction when
+encountering an obstacle. It is here that the mean-field models are not as strong since they do not
+take these local interactions into account. It must be noted, however, that Inoue et al have
+identified this problem and are currently working towards its incorporation into the model.
+
+It would, therefore, be of particular interest from a safety perspective to consider agent
+interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
+swarm system to include agent interaction. This presents a first step towards considering the swarm
+as composed of intelligent agents rather than mindless particles and, as the authors suggest,
+presents the possibility of applying game theoretic approaches towards swarms, which also gives the
+ability to consider heterogeneous swarm systems who interact with one another through repeated play.
+Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
+\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
+leader-follower swarm system to achieve given tasks.
+
+\textbf{Include recent updates in here}
+
 \section{Swarms} \label{sec::Swarms}
+
+Swarm systems comprise of a population of (typically) homogeneous agents who are able to organise
+themselves
+into formations using a series of simple local interactions with their neighbours
+\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
+may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
+ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
+performance in reaching globally optimal solutions in search-based tasks. The advantage of many
+swarm algorithms is that they are based on local interactions and so are incredibly scalable
+\cite{Rizk2018}.
+
 \subsection{Decision Making in Swarms} \label{sec::Decisions_in_Swarms}
 
+\textbf{Include Marco Dorigo and Recent AAMAS literature in here}
+
+The reduction of the complexity in interactions between agents also allows for the robots to perform
+other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
+considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
+manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
+whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
+sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
+readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
+divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
+
+Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
+central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
+adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
+made regarding the homogeneity of individual agents and the simplicity of their local interactions
+result in significant limitations placed on the complexity of the tasks that swarm systems can
+accomplish.
+
+\section{Remarks} \label{sec:remarks}
+
+\textbf{TODO: Go through each of the sections and explicitly evaluate them against the defined
+metrics}
+
 \end{document}

### 2020-06-04 Documents/ESA/sections/ProposedResearch.tex
Updated ESA and Write Up

@@
 \begin{document}
+
+	\textbf{Major restructuring and rephrasing is required here}
+
     \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
+    The intention of this area of study is to consider the ideas presented in works such as 
+    \cite{Sanders2018} and \cite{Galla2011} which consider complex behaviour, including cycles and
+    chaos, in certain games using simple reinforcement learning algorithms. These provide a great
+    deal of insight into whether or not the game will converge and, if so, to what equilibrium.
+    Galla, for instance, shows that adjusting a memory parameter when learning to solve an Iterated
+    Prisoner's Dilemma game can shift the equilibrium from one showing purely defective behaviour to
+    one showing cycles of cooperations and defection. Sanders et al. generalise this result by
+    showing that, for a particular learning algorithm known as Experience Weighted Attraction,
+    learning dynamics varies dependent on the mutual effect of two parameters.
+
+    This determination of where RL algorithms will show complex dynamics is important, not only for
+    a priori understanding of resultant behaviour, but is particularly important for algorithms in
+    which agents aim to predict the behaviour of other agents. For this to be feasible, the learning
+    dynamics must not exhibit chaos, otherwise it would be impossible for an agent to make any
+    reasonable predictions about the future behaviour of its opponents.
+
+    To this end, the potential avenue for research in this regard is to extend the ideas of Sanders
+    et al. and Galla et al. towards games learnt using classical reinforcement learning algorithms 
+    (such as Q-Learning with Boltzmann exploration, which seems to be a common choice). The work may
+    then be able to extend beyond this, and towards continuous spaces, stateful games and large
+    agent populations. This would allow for an understanding of the important parameters which
+    define the behaviour of reinforcement learning algorithms and allow for a characterisation of
+    the expected resultant behaviour when applying a particular algorithm to a particular game. It
+    would also allow for a characterisation of the conditions under which MARL algorithms may
+    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
+    payoff matrices and parameters accordingly.
     \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
+    This suggestion aims to build upon the work presented by Leung et
+    al. \cite{Hu2019} in which the point is made that the vast
+    majority of the work done in this area considers games with a
+    finite (usually two) number of agents. This limits the capability
+    of the analysis to generalise to much larger agent populations,
+    such as swarms. To allieviate this concern, the authors present an
+    anaysis of the learning dynamics for a large agent population
+    (which they approximate as containing infinite agents) where each
+    agent is an independent Q-Learning using Boltzmann
+    exploration. The emergent dynamics is given by a Fokker-Planck
+    equation which is numerical shown to be a strong approximation of
+    the true learning dynamics. However, as the authors point out,
+    this is the first attempt at considering such a problem, and
+    relies on heavy assumptions.  Possible extensions therefore
+    require a consideration of:
+
+    \begin{itemize}
+        \item Asymmetric games, in which agents have different
+          payoffs, introducing heterogeneity and competition into the
+          system. \fr{this is not really a problem  in relation with swarms, is it?}
+        \item Stateful Games. \fr{what is the interest of stateful games?}
+        \item Heterogeneous populations, in which there are p different populations of agents.
+    \end{itemize}
+
+    To the best of my knowledge, in the particular case of $N >> 1$ agent populations, none of the
+    above have yet been attempted.
+
     \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
+    This study extends the work of Zhang \cite{Zhang2018}, Elamvazuthi \cite{Elamvazhuthi2019} and
+	Li et al. \cite{Li2017}. Here, the authors consider the dynamics of swarms through 'drifted
+	brownian motion'. In this case, the control input is some scalar field which is generated from the
+	environment. Each agent measures this field at their location and uses it to adjust their
+	velocity, which eventually results in the entire swarm achieving a desired distribution. This technique
+	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
+	manner.
+
+	The hypothesis of this section is that the distribution of active particles may
+	similarly be controlled through the influence of a scalar field. The dynamics derived by Bellomo
+	et al. \cite{Bellomo2017} includes a 'flocking field' which agents can measure. By controlling
+	the flocking field, we may be able to drive the swarm to specific
+	distributions.
+
+	The contribution that this study presents over those using brownian motion is the inclusion of an
+	interaction operator. This governs how agents interact with one another. By accounting for this, we
+	are able to control swarms where agents, for instance, avoid collisions with one another. The
+	complexity of this interaction term will need to be gradually increased over time. To begin with,
+	we may entirely neglect this term. It is here that we will compare the model proposed by Zhang with
+	that proposed by Bellomo et al. We may then consider only local interactions, which is typical for
+	most swarming systems in the current literature, before then considering non-local interactions.
+	This provides the scope for swarms to interact with a greater number of agents. At this
+	stage, we may expand our study to consider the presence of interaction domains. This places
+	constraints on how agents may interact with one another, allowing for a greater generalisation of
+	inter-agent interactions. Ultimately, we would like to influence the interaction term, though this
+	is discussed in Section \ref{sec:learning_strategies_through_iterated_interaction}. The questions
+	we will consider here are:
+
+	\begin{itemize}
+		\item The controllability of the system: Under what conditions is it possible to drive the
+		swarm from one configuration to another in a stable manner?
+		\item The guarantees of the system: Is it possible to ensure that the agents will not enter
+		certain areas of state space, or exceed certain control constraints (e.g. max imum velocity)?
+	\end{itemize}
+
+	Some applications of this study are:
+
+	\begin{itemize}
+		\item Search and Rescue, in which agents will be required to flock to specific areas (e.g.
+		areas with survivors detected).
+		\item Construction, in which agents will be required to take on desired formations based on
+		the structure to be designed.
+		\item Medical Robotics, in which agents are required to target specific areas of the body.
+	\end{itemize}
+
+	In conclusion, the results from this study already significantly expand the current capabilities of
+	swarming agents by developing control methodologies which can drive the swarm towards desired
+	distributions in a stable manner. This is accomplished through controlling the 'flocking field'
+	which is indirectly used to adjust the velocity of the agents.
+
     \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
+
+    This section of the study is perhaps the strongest extension to swarm control proposed in this
+	chapter, and will likely be the most challenging. Here, we attempt to control the interaction term
+	in Bellomo et al's model and we consider that the behaviour of the entire swarm may be influenced
+	by decision making on an individual level. This will involve agents learning their strategies
+	through repeated interaction. The goal, then, is to design the agent parameters, reward structure
+	and control strategy to achieve desired results. To accomplish this will require a unification of
+	multi agent learning and control theory. Whilst, at first glance, such an endeavour seems
+	incredibly challenging, our work in the predictability of mean field learning (Chapter 
+	\ref{ch::DynMARL}) places us in a unique position to tackle the problem. This framework will
+	first establish the desired strategy to be taken by the agents and choose the game's reward
+	structure so that learning will converge to a stable fixed point. Then by accounting for this
+	strategy within the interaction term, we apply the appropriate controls in the flocking field to
+	drive the swarm in a stable manner. We will again consider the aforementioned controllability
+	and guarantees questions and establish how the incorporation of learning affects these results.
+
 \end{document}

### 2020-06-04 Documents/Literature Review/Literature Review - Revised/sections/SwarmControl.tex
Updated ESA and Write Up

--- 2020-05-21 Literature Review/Literature Review - Revised/sections/SwarmControl.tex
@@
 		(particularly useful when aiming to avoid fires in urban search and rescue), or
-		concentration of pollutants for enviromental applications.
+		concentration of pollutants for environmental applications.
 		\item Density of the environment through computer vision. For instance, a centralised sytem may map the environment and artificially generate a field which it then communicates to the swarm.

### 2020-06-04 Code/EGT-RL/MeanFieldCode/Game.py

@@ -1,0 +1,51 @@
+import random
+
+class Game:
+
+    def __init__(self, rewards):
+        self.rewards = rewards
+        self.allGames = np.eye((len(rewards)))
+
+    def generateOpponents(self, p):
+        # players = np.array(range(nAgents))
+        # np.random.shuffle(players[np.where(gamesPlayed < nOpponents)])
+        return np.where(self.allGames[:, p] == 1)[0].tolist()
+        # return players[0:nOpponents - gamesPlayed[p]]
+
+    def generateGames(self, players, nOpponents):
+        nAgents = len(players)
+        self.allGames = np.zeros((nAgents, nAgents))
+        for p in range(nAgents):
+            availableOpponents = np.array(range(nAgents))[np.where((np.array(range(nAgents)) != p) & (self.allGames[:, p] != 1) & (np.sum(self.allGames, axis = 1) < nOpponents))].tolist()
+            opponents = random.sample(availableOpponents, nOpponents - len(np.where(self.allGames[:,  p] == 1)[0]))
+            self.allGames[opponents, p] = 1
+            self.allGames[p, opponents] = 1
+
+    def playGame(self, players, P):
+        players = np.array(players)
+        opponents = self.generateOpponents(P)
+        players[P].payOffs += self.rewards[0][players[P].action, [players[O].action for O in opponents]].tolist()
+        for O in opponents:
+            players[O].payOffs += [self.rewards[1][players[P].action, players[O].action]]
+            self.allGames[P, O], self.allGames[O, P] = 0, 0
+        return players
+
+if __name__ == "__main__":
+    from MeanFieldCode.QLearner import QLearner
+    from MeanFieldCode.GamePlay import *
+
+    alpha = 0.1
+    tau = 1
+    gamma = 0
+
+    nAgent = 2
+    nAct = 2
+
+    game = generateGame(gamma, nAct)
+
+    players = [QLearner([alpha, tau, gamma], nAct, game.rewards[i], nAgent - 1) for i in range(nAgent)]
+    selectActions(players)
+
+    game.generateGames(players, nAgent-1)
+    game.playGame(players, 0)
+    print('hi')

### 2020-06-04 Code/EGT-RL/MeanFieldCode/GamePlay.py

@@ -1,0 +1,124 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+from MeanFieldCode.QLearner import QLearner
+from MeanFieldCode.Game import Game
+
+# Generate Random Games
+# Initialise players
+# Iterate Game
+    # Choose actions
+    # Receive rewards
+    # Update Q-values
+
+def generateGame(gamma, nAct):
+    reward1s = {}
+    reward2s = {}
+
+    nElements = nAct**2 #number of payoff elements in the matrix
+
+    cov = np.eye(2 *  nElements)
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+    rewards = np.array([2, 0, 0, 1, 1, 0, 0, 2])
+
+    reward1s = rewards[0:nElements].reshape((nAct, nAct))
+    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
+
+    return Game([reward1s, reward2s])
+
+def initialisePlayers(params, nAgent, nAct, game):
+    return [QLearner(params, nAct, game.rewards[i], nAgent-1) for i in range(nAgent)]
+
+def selectActions(players):
+    [player.selectAction() for player in players]
+    return players
+
+def playGame(players, game):
+    nAgents = len(players)
+    # players = np.array(players)
+    game.generateGames(players, players[0].nOpponents)
+    for p in players:
+        p.payOffs = []
+
+    for p in range(nAgents):
+        players = game.playGame(players, p)
+
+    return players.tolist()
+
+def updateQValues(players):
+    [player.qUpdate() for player in players]
+    return players
+
+
+def iterateGame(players, game):
+    players = selectActions(players)
+    players = playGame(players, game)
+    players = updateQValues(players)
+
+    return players
+
+def runSimulation(params, nAgent, nAct):
+    game = generateGame(params[2], nAct)
+    players = initialisePlayers(params, nAgent, nAct, game)
+
+    nIter = int(1e3)
+
+    probs = []
+
+    for cIter in tqdm(range(nIter)):
+        players = iterateGame(players, game)
+        probs.append(np.array([p.actionProb[0] for p in players]))
+
[…]

### 2020-06-04 Code/EGT-RL/MeanFieldCode/QLearner.py

@@ -1,0 +1,42 @@
+import numpy as np
+
+class QLearner:
+    def __init__(self, params, nActions, payOff, nOpponents):
+        self.gamma = 0.1
+        self.tau   = params[0]
+        self.alpha = params[1]
+
+        self.nActions = nActions
+        self.nOpponents = nOpponents
+
+        rMin = np.amin(payOff)
+        rMax = np.amax(payOff)
+
+        self.qValues = np.random.rand(nActions)*(rMax-rMin)+rMin
+        self.partitionFunction = np.sum([np.exp(self.tau * i) for i in self.qValues])
+        self.actionProb = [np.exp(self.tau * i) / self.partitionFunction for i in self.qValues]
+
+        self.action = 0
+        self.payOffs = []
+
+        self.gamesPlayed = 0
+
+    def selectAction(self):
+        self.partitionFunction = np.sum([np.exp(self.tau * i) for i in self.qValues])
+        self.actionProb = [np.exp(self.tau * i) / self.partitionFunction for i in self.qValues]
+
+        self.action = np.random.choice([0, 1], p=self.actionProb)
+
+    def playGame(self, opponents, game):
+        payOffs = np.array(game[self.action, np.array([o.action for o in opponents])]).T
+        self.payOffs += list(payOffs[0])
+        for o in range(len(opponents)):
+            opponents[o].payOffs += [payOffs[1, o]]
+
+
+    def qUpdate(self):
+
+        self.payoff = np.mean(self.payOffs[0:self.nOpponents])
+        # self.qValues[self.action] = (1 - self.alpha) * self.qValues[self.action] + self.alpha * self.payoff
+
+        self.qValues[self.action] += self.alpha * (self.payoff + self.gamma * max(self.qValues) - self.qValues[self.action])

### 2020-06-04 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -1,0 +1,120 @@
+from tqdm import tqdm
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import shutil
+
+def generateGame(gamma, nAct):
+    reward1s = {}
+    reward2s = {}
+
+    nElements = nAct**2 #number of payoff elements in the matrix
+
+    cov = np.eye(2 *  nElements)
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+    reward1s = rewards[0:nElements].reshape((nAct, nAct))
+    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
+
+    return [reward1s, reward2s]
+
+def checkConvergence(actionProb, oldxBar, tol):
+    normStep = np.linalg.norm(actionProb - oldxBar)
+    return normStep < tol
+
+def runSim(params, nSim, tol):
+
+    alpha = params[0]
+    tau = params[1]
+    gamma = params[2]
+    Gamma = params[3]
+
+    xsAll = []
+    converged = []
+
+    for cSim in range(nSim):
+        stopCond = False
+
+        [payoffA, payoffB] = generateGame(Gamma, 2)
+
+        qValues = np.random.rand(2, 2)
+        xs = []
+        oldxBar = np.array([1, 1])
+        for cIter in range(int(5e5)):
+
+            partitionFunction = [np.sum([np.exp(tau * i) for i in qValues[p, :]]) for p in range(2)]
+            actionProbs = np.array([[np.exp(tau * i)/partitionFunction[p] for i in qValues[p, :]] for p in range(2)])
+
+            xs += [actionProbs[:, 0]]
+
+            if cIter % (int(1e4)) == 0 and cIter != 0:
+                stopCond = checkConvergence(actionProbs[:, 0], oldxBar, tol)
+                if stopCond:
+                    break
+                oldxBar = actionProbs[:, 0]
+
+            boltzmannChoices = [np.random.choice([0, 1], p=actionProbs[p, :]) for p in range(2)]
+
+            rewards = [payoffA[boltzmannChoices[0], boltzmannChoices[1]], payoffB[boltzmannChoices[0], boltzmannChoices[1]]]
+
[…]

### 2020-06-12 Documents/ESA/sections/ResearchSummary.tex
Updated Write Up and ESA

--- 2020-06-04 Documents/ChaoticDynamics/WriteUp.tex
@@
-\documentclass{article}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage{amsmath,amsfonts}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{color}
-\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
-
-\title{Derivation Write Up}
-\author{Aamal Hussain}
+\documentclass[.../main.tex]{subfiles}
 
 \begin{document}
-
-\maketitle
-
-\fb{the bibfile is missing.}
-
-	\section{Introduction} % (fold)
-	\label{sec:introduction}
-
-	\begin{itemize}
-			\item For use in Multi-Agent Reinforcement Learning
-			\item Requirement to get some desired behaviours out of the system (e.g. conforming to
-			predefined values or constraints)
-			\item For this, it is required that we are able to predict the outcome of the learning
-			behaviour
-			\item Work done on determining the dynamics of MARL gives an indication of what
-			solutions an algorithm will produce
-			\item We can use this, alongside stability theory, to understand the nature of the games
-			which result in stable behaviours and which result in chaotic behaviours.
-			\item Largely follows the work presented by Sanders et al. However, whilst they consider
-			EWA, we consider Q-Learning, which is more popular in RL communities.
-	\end{itemize}
-
-	\subsection{Problem Statement} % (fold)
-	\label{sub:problem_statement}
-
-	Given a particular learning algorithm and game, is it possible to determine whether the game is
-	likely to reach a unique fixed point or exhibit more complex behaviour? What are the factors
-	which affect this resulting behaviour?
-
-	% subsection problem_statement (end)
-
-	\subsection{Objectives and Scope} % (fold)
-	\label{sub:objectives_and_scope}
-
-	Analyse the stability of Multiagent Q-Learning on iterated games.
-
-	Assumptions:
-
-	\begin{itemize}
-		\item Focuses on stateless games
-		\item Homogeneous agents
-		\item Discrete action spaces, with large number of actions.
-		\item Small, finite number of agents.
-	\end{itemize}
-
-	The work by Sanders et al. considers agents who have these same assumptions, but learn with a
-	reduced version of the Experience Weighted Attraction algorithm. For the Reinforcement Learning
-	community, it is of interest to consider the question of stability from the point of view of
-	agents who follow the popular Q-Learning algorithm.
-
- \fb{you might discuss in which way any of the points above differs from the relevant reference.}
-
-	% subsection objectives_and_scope (end)
-
-	% section introduction (end)
-
-	\section{Derivation} % (fold)
-	\label{sec:derivation}
-
-        \fb{it would be good to have a overall description of the goal of the derivation.}
 
@@
 	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
-	that we moved the term \fb{which one exactly?} containing the quenched disorder into a separate exponential. Since our
+	that we moved the term containing the quenched disorder into a separate exponential. Since our
 	aim is to take an average over all possible realisations of this disorder, we will only need to
@@
 	are all multiplied together and we sum over the subscripts, the letters we choose are of no
-	importance and we can exchange them freely \fb{perhaps some more justification might be helpful}. We will define both exponentials in $Q$ as $Q_1$ and
+	importance and we can exchange them freely. We will define both exponentials in $Q$ as $Q_1$ and
 	$Q_2$ respectively.
@@
 	\end{subfigure}
+	%
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width = 0.7 \textwidth]{Figures/tau_005.png}
+	\caption{$\tau = 0.0$}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width = 0.7 \textwidth]{Figures/tau_015.png}
+	\caption{$\tau = 0.15$}
+	\end{subfigure}
 
@@
 
-% section numerical_simulations (end)
 \end{document}

### 2020-06-12 Documents/ESA/sections/ShortTermGoals.tex
Updated Write Up and ESA

@@
     \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}
-    \subsection{Research Summary} \label{sec::Research Summary}
+
+    We begin by considering the evolution of learning with agents who follow a Q-Learning approach.
+    Specifically, we look at characterising the stability of agents learning strategies. This
+    technique was first carried out by Sanders et al \cite{Sanders}, in which the authors
+    characterised the strategy evolution of agents who learn using an 'Experience Weighted
+    Attraction' (EWA) algorithm, which is seen to be a strong representation of how people learn in
+    games. The authors were able to determine the regions of parameter space in which learning is
+    likely to converge towards stable equilibriums, as opposed to complex behaviours (such as limit
+    cycles or chaotic dynamics). The aim of this study is to format these techniques for the study
+    of computational agents who follow the popular Q-Learning approach \cite{SuttonBarto,Schwarz}.
+
+    We aim, similarly, to determine the regions of parameter space in which the agents are likely to
+    converge to stable equilibria. In this way it will be possible to, a priori, determine whether,
+    for a particular game, the behaviour is likely to converge and even how to choose the agent or
+    game parameters to ensure the predicatability of the resulting behaviour. To achieve this, we
+    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{TuylsDynamics}. In this study, the
+    authors were able to derive a continuous time dynamical system describing how agents following a
+    Q-Learning approach adjust the probabilities of choosing actions as they iteratively play a
+    game. These equations are shown in \cite{TuylsDynamics} to accurately model the expected
+    behaviour of agents as they iterate a game, and the experiments which verified this model are
+    shown in \textbf{Figures ...} .
+
+    With the accuracy of the continuous time dynamical system (\ref{eqn::EOM}) established, we analyse the
+    stability of this system in the following section. Note that whilst the derivation provided is
+    for the particular case of two agents for the sake of brevity, the problem of p-player games is
+    equivalent to that of two players and so the solutions to the former can (and will) be
+    presented.
+
+    \subsection{Research Summary} % \subfile{./sections/ResearchSummary.tex} \label{sec::Research
+    % Summary}
+
+    \subsection*{Future Work} \label{sec::Future Work}
+
+    As mentioned, the above system considers only a two player game. This was done with the intention
+    of simplifying the notation and reducing the complexity of the experiments. However, the next
+    immediate action is to present the equivalent solutions for the case of a general p-player game.
+    We then seek to expand this study to a population of agents. For this, we will study the
+    stability of the system presented by Leung et al \cite{Leung} which presents a mean-field model
+    describing the evolution of learning of a population of Q-Learning agents who play co-operative
+    games against one another. This last point is an important limitation - the derived dynamics
+    will only consider populations who must co-operate with one another (i.e. the $\Gamma$ value of
+    the game is one).
 
@@
 
+    This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
+    mode of inquiry upon the completion of the work described in \ref{sec::Chaos_in_Q-Learning}.
+    Recall that Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
+    through
+
+    \begin{equation}
+    \begin{align*}    
+        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
+        = 0 \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
+        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
+        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*.
+    \end{align*}
+    \end{equation}
+
+    In this study we will attempt to formulate an optimal control problem in which the term $F_a[f]
+    (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a fixed value
+    of $\psi$ to reduce complexity). Note that $F_a$ is dependent on the density function f and so
+    we aim to apply feedback controls to the swarm.
+
 \end{document}

### 2020-06-16 Documents/ESA/sections/ResearchTimeline.tex
Included ESA, updated Write Up
Updated ESA

--- 2020-06-03 Documents/ESA/sections/ProposedResearch.tex
@@
 \begin{document}
-    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
-    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
-    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
-    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
+
+	This chapter outlines a tentative timeline of the research described thus far. The numbers in
+	brackets denote the estimated months of the PhD that these are likely to take place with zero
+	being the beginning of the PhD (October 2019) and 48 marking the end (September 2023). Note that
+	there is a period of six months at the end which exists to allow for a margin of error.
+
+	\begin{enumerate}
+		\item Characterisation of Complex Dynamics in Reinforcement Learning Games (\textbf{9 - 12})
+		\begin{itemize}
+			\item Determining and plotting a simplified expression for a stability line general
+			p-player games using Q-Learning (\textbf{9 - 10}).
+			\item Running large scale simulations of Q-Learning games to experimentally verify
+			results. (\textbf{9 - 11}).
+			\item Characterising the Lyapunov exponent for modes of unstable behaviour in Q-Learning
+			Dynamics (\textbf{11 - 14})
+		\end{itemize}
+
+		\item Control of Swarms with Independent Agents (\textbf{11 - 18})
+		\begin{itemize}
+			\item Setting up a model predictive control problem for the reduced assumptions of
+			particles with no (or limited) interactions (\textbf{11 - 12}) and solving the resulting
+			optimisation problem (\textbf{12 - 18}). 
+			\item Designing and running simulation code. (\textbf{15 - 18})
+		\end{itemize}
+
+		\item Characterisation of the Learning Dynamics of Co-operative Mean Field Games (\textbf{11
+				- 18})
+		\begin{itemize}
+			\item Evaluating the stability of co-operative ($\Gamma = 1$) mean-field games (\textbf{11 - 13})
+			\item Evaluating the Lyapunov exponent of the unstable behaviour (\textbf{13 - 16})
+			\item Running large scale simulations to verify results (\textbf{15 - 18})
+		\end{itemize}
+
+		\item Control of Interacting Swarming Agents (\textbf{19 - 30})
+		\begin{itemize}
+			\item Setting up and solving MPC optimisation problem on the collisional Vlasov
+			equation with short-range interactions between agents. (\textbf{19 - 25})
+			\item Designing and running simulation code. (\textbf{24 - 30})
+		\end{itemize}
+
+		\item Control of Co-operative Intelligent Swarming Agents (\textbf{28 - 34})
+		\begin{itemize}
+			\item Setting up and solving MPC optimisation problem on the collisional Vlasov
+			equation with augmented interaction term constrained on learning dynamics. (\textbf{28 -
+			33})
+			\item Designing and running simulation code. (\textbf{32 - 37})
+		\end{itemize}
+
+		\item Thesis Completion (\textbf{34 - 42})
+		\begin{itemize}
+			\item Writing Up (\textbf{34 - 38})
+			\item Proof Reading and Editing (\textbf{39 - 41})
+			\item PhD Completion (\textbf{41 - 42})
+		\end{itemize}
+
+	\end{enumerate}
+
 \end{document}

### 2020-06-16 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

@@
 
-    \subsection{Research Summary} % \subfile{./sections/ResearchSummary.tex} \label{sec::Research
+    \subsection{Research Summary} %\subfile{./sections/ResearchSummary.tex} \label{sec::Research
     % Summary}
@@
     This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
-    mode of inquiry upon the completion of the work described in \ref{sec::Chaos_in_Q-Learning}.
-    Recall that Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
+    mode of inquiry upon the completion \ref{sec::Chaos_in_Q-Learning}.
+    Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
     through
 
-    \begin{equation}
-    \begin{align*}    
+    \begin{equation*}
+    \begin{split}    
         \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
@@
         F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
-        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*.
-    \end{align*}
-    \end{equation}
+        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*, 
+    \end{split}
+    \end{equation*}
 
-    In this study we will attempt to formulate an optimal control problem in which the term $F_a[f]
-    (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a fixed value
-    of $\psi$ to reduce complexity). Note that $F_a$ is dependent on the density function f and so
-    we aim to apply feedback controls to the swarm.
+    in which $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
+    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$. $\kappa \geq 0$ is a scalar
+    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
+    {v}^*$) gives the position in phase space of a 'field particle'.
+
+    In this study we will attempt to formulate an model predictive control problem in which the term
+    $F_a[f] (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a
+    fixed value of $\psi$ to reduce complexity). The process will be inspired from the works of
+    Burger et al. \cite{Berger2019} and Borzi et al. \cite{Borzi2014} However, we will aim to
+    control the behaviour of the system through interactions with 'field particles' (determined by
+    $F_a[f]$) rather than through the leader-follower interactions posed by the aforementioned
+    studies. We will illustrate the effectiveness of the results through 2D numerical simulation. It
+    will be interesting to perform a similar analysis to Ko and Zuazua \cite{Ko2019} in which the
+    cost functional is altered to favour particular metrics  (e.g. running cost, control time etc.)
+    and also analyse the effect of varying the time horizon.
 

### 2020-06-19 Documents/ESA/sections/LitReview.tex
Updated ESA

@@
 \begin{enumerate}
-    \item Scalable
-    \item Distributed
-    \item Generality
-    \item Low Computational Load
-    \item Robustness
+    \item Distributed. It will often be the case that a multi-agent system must spread out across a
+    large area or operate in regions where communication is limited. As such it is beneficial that
+    such a system does not rely too heavily on communication with a central body. The individual
+    agents must, therefore, be able to make their own decisions and act as independent entities.
+    Aside from the advantage of communication, this ensures that the system is not tied to a single
+    point of failure; in a system governed by a centralised decision maker, any faults in the
+    central body propagates throughout the group. Of course, this comes at the price of
+    computational load - if the agents are required to act independently, they must possess the
+    resources to do so. The term distributed should not be confused with decentralised. The latter
+    refers to a regime in which agents all communicate with one another before making a decision.
+    Whilst this is preferable to a centralised decision maker in terms of the requirement for one
+    entity to communicate with all agents, it still places a high cost on the requirement that
+    agents be in constant communication with one another. In fact it may pose the additional risk
+    that if any agent in the team fails, the whole pipeline falls apart. Distributivity, on the
+    other hand, requires that agents make independent decisions so that, though agents may
+    communicate with each other, they are still able to operate when this is not possible.
+    \item Generality. MAS come in many different flavours; sometimes a small group of heterogeneous 
+    (agents with different capabilities) agents may be required to perform a delicate task whilst
+    in others, it may be required that a large population of homogeneous (all of the same type)
+    agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
+    strategy whilst in the middle of a task. It would be a hindrance if the agents were required to
+    be reprogrammed with a completely different control methodology each time the situation changes
+    slightly. It would be preferable if the method could apply to all different types of scenarios,
+    with homogenous or heteregeneous agents, with single tasks or multiple, in any environment with
+    only minor customisation required. Better still if the agents are able to adapt themselves to
+    the specifics of the scenario.
+    \item Low Computational Load. As mentioned in the previous chapter, a MAS will often be used in
+    complex situations, many of which will be too dangerous for human intervention. As such, the
+    system will be required to carry out its tasks online. For this reason, it is vital that the
+    control method be one which produces low computational load - especially where the time frame
+    for adjusting agent behaviour is limited. Monetary concerns also play a part in this metric; it
+    would not do to impose that every member of the team be equipped with high performance computing
+    power as this would likely fall outside of the budget of any practical usage.
+    \item Robustness. Particularly for physical robots, a MAS should be able to operate in
+    situations which present sensor noise, communication noise, latency, and environmental
+    disturbances. This is rather important in unseen environments where full a priori knowledge of
+    the map cannot be assumed.
+    \item Scalable. This is mentioned last since the ability for a MAS to scale comes from its
+    distributivity  and low computational load. Scalability is the capacity for any method of
+    controlling a MAS to successfully operate as the size of the team increases. This, of course, is
+    related to the complexity of the algorithms involved. However, it should be noted that it is not
+    always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the
+    task at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to
+    perform the task, rather than a large population. 
 \end{enumerate}
 
-We will use these metrics, alongside the problem statement to approach the current literature
-surrounding the theory and practices of Multi-Agent Systems.
+We begin by presenting a subset of the vast array of literature regarding MAS and focus on those
+which are relevant to the study at hand. We conclude this chapter by providing some remarks about
+how these methods hold against the above metrics.
 
@@
 
-POSGs act as a game theoretic corollary to the Dec-POMDP.
-Here, an optimal solution is found by fixing the strategy (a manner of selecting an action \cite{Rizk2018DecisionSurvey}) of all agents except one.
-The optimal strategy of the chosen agent is then computed.
-This is fixed so that the next agent may determine its optimal strategy.
-This process is iterated over all agents in a process known as Alternating Maximisation \cite{Ray2010AnCooperation}.
-By choosing strategies which maximise a common payoff, a globally optimal solution can be found.
+POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by
+fixing the strategy (a manner of selecting an action \cite{Rizk2018DecisionSurvey}) of all agents
+except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
+next agent may determine its optimal strategy. This process is iterated over all agents in a process
+known as Alternating Maximisation \cite{Ray2010AnCooperation}. By choosing strategies which maximise
+a common payoff, a globally optimal solution can be found.
 
-Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is sometimes referred to as an ‘incomplete information game’).
-This allows for a POSG to be approximated by a sequence of smaller, more tractable games \cite{Emery-MontemerloApproximatePayoffs}.
-However, iterating through the entire team of agents to find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic situations.
-To address this, \cite{Ray2010AnCooperation} propose to place distinct payoffs on each agent and to consider team formation based on social hierarchy as well as preferred partners.
-This allows the complexity of the problem to be broken down into smaller game units and also provides a clear order in which the games are to be played.
-This minimises the interference across robots and allows for more immediate action to be taken by agents who choose their strategy early on, while leaving more passive tasks for those later in the sequence.
+Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
+sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be
+approximated by a sequence of smaller, more tractable games
+\cite{Emery-MontemerloApproximatePayoffs}. However, iterating through the entire team of agents to
+find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
+situations. To address this, \cite{Ray2010AnCooperation} propose to place distinct payoffs on each
+agent and to consider team formation based on social hierarchy as well as preferred partners. This
+allows the complexity of the problem to be broken down into smaller game units and also provides a
+clear order in which the games are to be played. This minimises the interference across robots and
+allows for more immediate action to be taken by agents who choose their strategy early on, while
+leaving more passive tasks for those later in the sequence.
 
-The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and dynamic decision making.
-However, as found by Dai et.
-al \cite{Dai2018TaskSystems} this is conditional on an understanding by each robot of the strategy of others, which in turn requires adequate communication between robots.
-Therefore, the game theoretical formulation will fail where communication is not possible amongst team members.
-However, the addition of heuristics, such as deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other members of its team without the need for significant explicit communication.
+The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
+dynamic decision making. However, as found by Dai et. al \cite{Dai2018TaskSystems} this is
+conditional on an understanding by each robot of the strategy of others, which in turn requires
+adequate communication between robots. Therefore, the game theoretical formulation will fail where
+communication is not possible amongst team members. However, the addition of heuristics, such as
+deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
+members of its team without the need for significant explicit communication.
 
@@
 
-\textbf{Add in more recent literature r.e. learning in stochastic games}
+\textbf{Add in more recent literature r.e. learning in stochastic games and the robustness of MARL}
 
@@
 
-\subsection{Approaches to Swarm Control} \label{sec::Swarm Control}
-
-Recent work has seen the advancement of swarms controlled in stochastic environments. This is
-particularly important for swarm intelligence in robots; many systems are developed with the
-motivation of search-and-rescue, in which the robot swarms will have to operate in environments
-where accounting for uncertainty is critical. To this end, swarm systems have seen the advent of
-stochastic control. In this, the swarm is modelled as a diffusive system using a stochastic
-equation, most often the Kolmogorov Forward Equation \cite{Hamann2008}. In \cite{Hamann2008}, the author shows that this equation can be derived by considering local trajectories of
-smaller subsets of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019} extend this idea to other
-stochastic models for swarms, importantly considering an advection-diffusion-reaction model which
-allows for hybrid agents to switch between different modes of operation.
-
-The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
-equations
-for stochastic forward processes (such as swarm foraging) in which, as the number of agents tends to
-infinity, the true macroscopic motion of the system tends to these equations. Importantly, however,
-these stochastic equations allow for an analysis of the swarm, as well as the ability to develop
-control laws. In \cite{Li2017}, Li et al show that these models can be used to develop control
-laws for robots in a swarm and drive them towards a target distribution. The method is shown to
-perform accurately both in simulation and on real robots. The advantage is that guarantees can be
-placed on the convergence and stabilisabiilty of the swarm towards the desired distribution.
-However, there appears to be significant scope to expand upon this methodology from a safety
-perspective. To begin with, the method does not consider inter-agent interactions and therefore does
-not formally guard against collisions. In \cite{Inoue2019}, a similar problem is considered,
-although collisions are avoided by having the robot simply move in the opposite direction when
-encountering an obstacle. It is here that the mean-field models are not as strong since they do not
-take these local interactions into account. It must be noted, however, that Inoue et al have
-identified this problem and are currently working towards its incorporation into the model.
-
-It would, therefore, be of particular interest from a safety perspective to consider agent
-interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
-swarm system to include agent interaction. This presents a first step towards considering the swarm
-as composed of intelligent agents rather than mindless particles and, as the authors suggest,
-presents the possibility of applying game theoretic approaches towards swarms, which also gives the
-ability to consider heterogeneous swarm systems who interact with one another through repeated play.
-Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
-\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
-leader-follower swarm system to achieve given tasks.
-
 \textbf{Include recent updates in here}
@@
 \cite{Rizk2018}.
+
+\subsection{Approaches to Swarm Control} \label{sec::Swarm Control}
+
+Recent work has seen the advancement of swarms controlled in stochastic environments. This is
+particularly important for swarm intelligence in robots; many systems are developed with the
+motivation of search-and-rescue, in which the robot swarms will have to operate in environments
+where accounting for uncertainty is critical. To this end, swarm systems have seen the advent of
+stochastic control. In this, the swarm is modelled as a diffusive system using a stochastic
+equation, most often the Kolmogorov Forward Equation \cite{Hamann2008}. In \cite{Hamann2008}, the
+author shows that this equation can be derived by considering local trajectories of smaller subsets
+of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019} extend this idea to other stochastic
+models for swarms, importantly considering an advection-diffusion-reaction model which allows for
+hybrid agents to switch between different modes of operation.
+
+The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
+equations for stochastic forward processes (such as swarm foraging) in which, as the number of
+agents tends to infinity, the true macroscopic motion of the system tends to these equations.
+Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
+ability to develop control laws. In \cite{Li2017}, Li et al show that these models can be used to
+develop control laws for robots in a swarm and drive them towards a target distribution. The method
+is shown to perform accurately both in simulation and on real robots. The advantage is that
+guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
+distribution. However, there appears to be significant scope to expand upon this methodology from a
+safety perspective. To begin with, the method does not consider inter-agent interactions and
+therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
+considered, although collisions are avoided by having the robot simply move in the opposite
+direction when encountering an obstacle. It is here that the mean-field models are not as strong
+since they do not take these local interactions into account. It must be noted, however, that Inoue
+et al have identified this problem and are currently working towards its incorporation into the
+model.
+
+It would, therefore, be of particular interest from a safety perspective to consider agent
+interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
+swarm system to include agent interaction. This presents a first step towards considering the swarm
+as composed of intelligent agents rather than mindless particles and, as the authors suggest,
+presents the possibility of applying game theoretic approaches towards swarms, which also gives the
+ability to consider heterogeneous swarm systems who interact with one another through repeated play.
+Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
+\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
+leader-follower swarm system to achieve given tasks.
 
@@
 
+Each of the above methods present different advantages in their approach towards MAS, as well as a
+particular set of disadvantages.
+
+Game Theoretic methods have long provided a rigorous approach for
+modelling the behaviour of any MAS. It places no limitation on the heterogeneity of the agents or
+the task demanded. An appropriate choice of payoff matrices will account for both of these
+specifications. Recent advances in POSGs have lifted the strong assumptions on prior knowledge that
+was required to achieve a Nash Equilibrium and Game Theoretic Control allows for such methods to be
+applied in continuous state spaces. Whilst the latter shows particular promise, game theoretic
+methods still fall short in terms of distributivity as they are heavily reliant on communication
+with a centralised decision maker to supply rewards, or within the team to determine each others'
+actions. They also require a priori knowledge of the situation in order to set up payoff matrices
+and so cannot be regarded as robust to environmental uncertainty.
+
+Multi-Agent Reinforcement Learning builds on the latter two shortcomings of game theory by allowing
+the environment to supply rewards to agents who adapt their behaviour accordingly. MARL is proving
+to be a powerful method to control MAS, and is rapidly improving, but cannot yet be regarded as
+robust. Studies repeatedly show that small alterations or noise in the environment can result in
+large deviations in behaviour. Furthermore, few guarantees can be placed on the resulting behaviour
+of a MARL system, though progress is being made in closing this gap.
+
+Control Theory, on the other hand, takes pride in the guarantees placed on the MAS such as:
+controllability, stability, and robustness. However, control techniques are often centralised or
+decentralised. Distributed methods of control is still an evolving field, particularly in terms of
+robustness to uncertainty. In order to establish guarantees, assumptions are also made on the
+specifics of the MAS, and so control theoretic methods have yet to evolve into general,
+heterogeneous systems with any given task.
+
+Swarm systems have their strongest advantage in scalability and, in fact, swarm techniques are built
+to scale due to the distributivity and low computational load placed on each agent. This has often
+come with the assumption that agents in the swarm act as simple, homogeneous, particles who follow
+very simple rules of interaction. Recent work is showing that this is not a necessary assumption
+and, in fact, swarms can leverage heterogeneity and agent capabilities to ensure robustness and
+generalisation.
+
+It is clear that each method presents its own set of advantages and disadvantages. In fact, the
+greater contributions are made from a unification of techniques (e.g. game theoretic control) which
+leverage the strengths of one technique to mitigate the drawbacks of another. To this end, we
+consider the unification of swarm control and multi-agent learning. The aim is to unify the
+strengths of swarm theory, MPC and game theory to study populations of agents who can make
+decisions on an individual basis but perform tasks through large scale collaboration. In the
+subsequent chapters, we propose a line of research which explores the properties of a system as well
+as establishing practical control methodologies along the way.
+
 \end{document}

### 2020-06-19 Documents/ESA/sections/ProposedResearch.tex
Updated Write Up and ESA
Updated ESA

--- 2020-06-03 Documents/ESA/sections/ProposedResearch.tex
@@
 \begin{document}
-    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
+
+	This chapter describes a proposed line of research which aims to study the evolution of swarm
+	systems with independent, learning agents under the influence of predictive controls. We detail
+	the novel lines of research which this work aims to undertake, providing suggestions of the
+	hypotheses posed by these lines. With this in mind the following studies are proposed and
+	developed subsequently:
+
+	\begin{itemize}
+		\item \textbf{Stability and Chaos in MARL:} in which we seek to understand the dynamics of
+		agent strategies when using Q-Learning to learn a game through iteration. We will establish
+		the stability, as a function of parameters, when learning general p-player N-action games.
+		This study enables the appropriate selection of parameters and payoff matrices to ensure the
+		stability of the strategies of a finite set of agents, such as leaders in a swarm.
+		\item \textbf{Dynamics of Mean-Field Q-Learning Games:} in which we examine the
+		strategy dynamics for large populations of agents learning through iterated games and
+		mean-field Q-Learning. We seek to understand the long term behaviour of such mean-field
+		systems in terms of its strategy selection. This study extends the previous and allows for
+		the stability of the strategies of a population of agents to be established.
+		\item \textbf{Model Predictive Control of Active Particles through Fields:} in which we
+		investigate the interaction of a swarm of active particles with potential fields. We
+		establish the stabilisability of an MPC scheme with defined stage costs, as well as an
+		analysis of the suboptimality of the method.
+		\item \textbf{Incorporation of Intelligence in Control:} in which we adapt the dynamical
+		system from the above point to include an interaction term, accounting for strategy
+		selection by agents who learn through iterated games against one another. Interactions with
+		an MPC scheme is then to be examined in a similar capacity.
+
+	\end{itemize}
+
+	\textbf{TODO: Ensure all references here are in the Lit Review}
+
+    \section{Stability and Chaos in MARL} \label{sec::Chaos_in_MARL}
+
+    This segment of research is aimed towards a deeper understanding of the strategy evolution
+    of agents following a Q-Learning approach. This allows for guarantees to be placed on the
+    behaviour of such agents, in particular the conditions under which the game will converge to a
+    stable equilibrium.
+
+    It has long been established that, upon lifting the strong assumptions made by traditional
+    game theory (such as the rationality of agents and complete information), that player
+    strategies can result in much more complex behaviour than convergence to a Nash Equilibrium 
+    (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
+    as tic-tac-toe and prisoner's dilemma \cite{Galla's work and I think Sato's work}. These
+    behaviours include: convergence to a unique equilibrium (though not always to an NE),
+    convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
+    Figure ... Of these, the most preferable is, of course, convergence to a unique equilibrium,
+    although it is still possible to study systems with multiple equilibria or limit cycles 
+    \cite{One of the textbooks}. However, it would be difficult to control systems whose dynamics
+    are governed by chaos (though research into controlling chaos is ongoing and rife with
+    opportunity \cite{CyberneticalPhysics}) and so MARL techniques should avoid this. It would,
+    therefore, be a useful endeavour to determine the conditions under which these sorts of
+    behaviours arise.
+
+    The behaviour of a system may be studied given a model of its dynamics. It is through this
+    process that a wide array of physical systems, from harmonic pendulums to geophysical fluids,
+    can be understood. A growing body of research aims to understand multi-agent reinforcement
+    learning through the lens of its dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames}
+    were able to derive a model of the strategy evolution of agents learning through iterated games.
+    Through this, they were able to arrive at the following model of Multi-Agent Q-Learning
+
+	\begin{subequations}
+	\label{eqn::EOM}
+		\begin{equation}
+			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
+			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
+		\end{equation}
+		\begin{equation}
+			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
+			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
+		\end{equation}
+	\end{subequations}
+
+	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
+	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
+	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
+	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
+	predict the expected behaviour of Q-Learning agents, as shown in Figure ...
+
+	It is clear, both from (\ref{eqn::EOM}) and Figure ... that the long-term strategy selection of
+	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
+	then pose the question: how do these elements influence the types of behaviours seen during
+	learning on an iterated game? In other words, under what parameter selections are we likely to
+	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?
+
+	With this in mind, the intention of this area of study is to consider the analysis presented in
+	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
+	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
+	learning behaviour of human players in a game \cite{whatevertheycite}. The authors are able to
+	determine the regions of parameter space in which complex behaviour,
+	including cycles and chaos, predominantly occur and those in which a given game converges to a
+	stable equilibrium. Figure ... reproduces the graphs shown in \cite{Sanders2018} which
+	illustrates the successful derivation of a 'phase line', across which learning shifts from
+	convergent to chaotic.
+
+    We propose to bridge the analysis presented by Sanders
+    et al. and Galla et al. towards games learnt using MARL, particularly Q-Learning with
+    Boltzmann exploration as considered by Tuyls et al. This would allow for a characterisation of
+    the expected resultant behaviour under given parameters for a particular game. The vision for
+    this is to provide guarantees on the stability of a finite set of agents within a swarm, such as
+    leaders in a flock. Without this, it would be impossible to ensure the stability of a swarm in
+    which intelligent, social interactions must be accounted for. However, this analysis
+    would also allow for a characterisation of the conditions under which MARL algorithms may
+    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
+    payoff matrices and parameters accordingly.
+
+    This segment of research is currently underway and approaching completion. The analysis can be
+    seen in Section \ref{sec::Chaos_in_Q-Learning}.
+
     \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
+
+    This segment of research aims to model the game dynamics of large populations of agents
+    learning through iterated games and mean-field Q-Learning. The aim is to provide similar
+    guarantees of stability as in the previous sections with the caveat that all agents in the
+    population can learn, rather than a finite subset.
+
+    One of the main results shown by Sanders et al. \cite{Sanders2018} is that as the number of
+    players in a game increases, the learning behaviour is more likely to be chaotic, regardless of
+    the choice of parameters. This is intuitive since a higher number of players would result in a
+    greater strategy space and more agents for any particular player to learn against and is
+    verified by their presented results as in Figure ...
+
+    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
+    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
+    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
+    cursory verification of this intuition. Here, the authors present an anaysis of the learning
+    dynamics for a large agent population (which they approximate as containing infinite agents)
+    where each agent is an independent Q-Learning using Boltzmann action selection. The
+    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
+    strong predictor of the overall strategy selection of the population. Indeed, rather than
+    examining the strategies of every agent in the population (which the authors approximate as
+    infinitely large), they model the evolution of a probability density function which, for each
+    action, defines the density of agents who retain a given Q-value for that action. This is
+    illustrated in Figure ...
+
+   	As the authors point out, this is the first attempt at considering such a problem, and relies on
+	heavy assumptions. The strongest of these is placed on the game itself, which is always
+	assumed to be cooperative (in Sanders' terms, $\Gamma = 1$). We, therefore, propose extending
+	this model to accomodate an arbitrary choice of games.
+
+	Two proposals for how this might work
+
+	\begin{itemize}
+		\item Estimate the population state using a Random Finite Set (RFS) and apply the models
+		from the previous study. This is a new hypothesis so more research is required.
+		\item Decompose a generic game into a weighted sum of a competitive and a cooperative game.
+		Treat these as two separate agents and invoke the mean field approximation so that any given
+		agent is effectively engaged in a three-player game where the strategy of the opponents is
+		the average strategy of the population.
+	\end{itemize}
+
+	\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}
+
     \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
+
+    Here we aim to study the interaction of a swarm of 'active particles' with a potential field. In
+    particular this field is to be generated by 'field particles'. A model predictive control 
+    (MPC) scheme
+    is to be devised to drive this system to desired configurations, with guarantees placed on
+    stability and satisfaction of input constraints. The sub-optimality of the control
+    scheme is to be studied.
+
+    As described in the previous chapter, the control of swarms has been examined through the use of
+    mean field models. These models resolve the fact that it is impossible to view the entire system
+    as simply the sum of all of the agents and rather model the overall state of the system through
+    density functions. Controls are then applied to this function whose evolution is described
+    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
+    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
+    some success in recent literature \cite{Zhang2018, Elamvazhuthi2019, Li2017,
+    BorziCollectiveMotion}, though it makes the assumption that the system evolves through 'drifted
+    brownian motion'. This means that the agents are considered to move about independently and
+    randomly, though under the influence of a field which affects their velocity. This technique
+	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
+	manner \cite{Any paper of Fokker Planck control}. The latter is beginning to show promise 
+	though control is typically through leadership rather than fields \cite{VlasovMPC}.
+
+	The hypothesis of this section is that the distribution of active particles, whose evolution is
+	described through a Vlasov equation, may be controlled through the influence of a scalar field
+	generated by 'field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
+	\cite{Bellomo2017}
+
+	\begin{equation}
+	\label{eqn::Vlasov}
+    \begin{split}    
+        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
+        = \epsilon Q(f, f) \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
+        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
+        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*, 
+    \end{split}
+    \end{equation}
+
+    Here, $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
+    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$ which represents the state of
+    the system. $\kappa \geq 0$ is a scalar
+    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
+    {v}^*$) gives the position in phase space of a 'field particle'. It can be seen that the these
+    field particles influence the velocity of the swarm agents.
+
+	The contribution that this study presents over those using brownian motion is the inclusion of an
+	interaction operator $Q(f, f)$. This governs how agents interact with one another. With this
+	term included, the dynamics account for the tendency of agents to avoid collisions. However,
+	the term is intended to account also for social interactions between agents, which we aim to
+	leverage in the subsequent section.
+
+	The complexity of this interaction term will need to be gradually increased over time. To begin
+	with, we may entirely neglect this term. It is here that we will compare the model proposed by Zhang
+	with that proposed by Bellomo et al. We may then consider only local interactions, which is typical
+	for most swarming systems in the current literature, before then considering non-local interactions.
+	This provides the scope for swarms to interact with a greater number of agents. At this stage, we
+	may expand our study to consider the presence of interaction domains. This places constraints on how
+	agents may interact with one another, allowing for a greater generalisation of inter-agent
+	interactions. Ultimately, we would like to influence the interaction term, though this is discussed
+	in Section \ref{sec::Intelligence_in_control}. The questions we will
+	consider here are:
+
+	\begin{itemize}
+		\item The stablity of the system: Under what conditions is it possible to drive the
+		swarm from one configuration to another in a stable manner?
+		\item The guarantees of the system: Is it possible to ensure that controls remain within an
+		admissible set (typically a closed, bounded and convex set \cite{PDEControl}).
+	\end{itemize}
+
+	These results will be established theoretically alongside the sub-optimality of the MPC scheme
+	and verified through numerical simulations in a 2D environment. It
+    will be of interest to perform a similar analysis to Ko and Zuazua \cite{Ko2019} in which the
+    cost functional is altered to favour particular metrics  (e.g. running cost, control time etc.)
+    and also analyse the effect of varying the time horizon.
+
     \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
+
+    This section of the study is perhaps the strongest extension proposed in this
+	chapter, and will likely be the most challenging. Here, we examine the dynamics (
+	\ref{eqn::Vlasov}) in which the interaction term accounts for the social dynamics of the
+	decision making of individual agents who have learnt through an iterated game. We leverage the
+	strategy evolution dynamics and stability analysis established in 
+	\ref{sec::Chaos_in_MARL} and \ref{sec::Large_Agent_Dynamics}.
+
+	Two proposals for incorporation of social interaction:
+	\begin{itemize}
+		\item Addition of the agent decisions as a constant in the state $f$. This should be fine if
+		it's fixed but note that the controls have no influence over this.
+		\item Multiplicative term in the turning probability which acts as a weighting term where
+		weights are equal to the agent strategy. This extends to both the swarms in
+		which the leaders are making decisions (only leaders have this term) as well as in
+		swarms where the population makes decisions (everyone has this term). This will need to be
+		done with care though to ensure that normalisation holds.
+	\end{itemize}
+
+	The MPC scheme from the previous section will then be adapted to this dynamical system with the
+	same questions of well-posedness and stability considered.
+
+	A possible extension of this would be to consider online learning by incorporating the time
+	evolution of the strategy space within the social interaction term, which would now be
+	time-varying. The proper integration of these dynamical systems would depend on the form of the
+	systems derived in Section \ref{sec::Large_Agent_Dynamics} and it is likely that relaxations would
+	be required in terms of controllability results. A likely relaxation would be to examine only the
+	behaviour in the long-enough time frame, which means that we could not impose a final time. Of
+	course, this means that we could only consider optimal control rather than model predictive.
+	However, without establishing the models from Section \ref{sec::Large_Agent_Dynamics}, this
+	extension is speculative and it is likely that such an extension would fall outside the scope of
+	the PhD.
+
+	\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
+	the conservation laws}
+
 \end{document}

### 2020-06-19 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

--- 2020-06-12 Documents/ESA/sections/ShortTermGoals.tex
@@
 \begin{document}
+
+    In this chapter, we summarise and present the research and results which have been obtained thus
+    far. These tackle the problems described in Section \ref{sec::Chaos_in_MARL}. We detail the
+    derivation of a stability phase line as presented in Sanders et al. \cite{Sanders2018} as well
+    as the numerical simulations performed to verify these results. The steps to be completed
+    subseqent to this study are then given.
+
     \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}
@@
     of computational agents who follow the popular Q-Learning approach \cite{SuttonBarto,Schwarz}.
-
+    {}
     We aim, similarly, to determine the regions of parameter space in which the agents are likely to
@@
 
-    \subsection{Research Summary} % \subfile{./sections/ResearchSummary.tex} \label{sec::Research
-    % Summary}
+     \textbf{Derivation suppressed, uncomment to see}
+     %\subfile{./sections/ResearchSummary.tex}
 
@@
     We then seek to expand this study to a population of agents. For this, we will study the
-    stability of the system presented by Leung et al \cite{Leung} which presents a mean-field model
+    stability of the system presented by Leung et al \cite{Hu2019} which presents a mean-field model
     describing the evolution of learning of a population of Q-Learning agents who play co-operative
@@
 
-    \section{Control of Swarms with Independent Agents} \label{sec::Independent_Swarm_Control}
-
-    This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
-    mode of inquiry upon the completion of the work described in \ref{sec::Chaos_in_Q-Learning}.
-    Recall that Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
-    through
-
-    \begin{equation}
-    \begin{align*}    
-        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
-        = 0 \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
-        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
-        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*.
-    \end{align*}
-    \end{equation}
-
-    In this study we will attempt to formulate an optimal control problem in which the term $F_a[f]
-    (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a fixed value
-    of $\psi$ to reduce complexity). Note that $F_a$ is dependent on the density function f and so
-    we aim to apply feedback controls to the swarm.
-
 \end{document}

### 2020-06-19 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -4,14 +4,21 @@ import numpy as np
 import matplotlib.pyplot as plt
 import shutil
 
+
 def generateGame(gamma, nAct):
-    reward1s = {}
-    reward2s = {}
+    """
+    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
 
-    nElements = nAct**2 #number of payoff elements in the matrix
+    gamma: Choice of co-operation parameter
+    nAct: Number of actions in the game
 
-    cov = np.eye(2 *  nElements)
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma
+    [reward1s, reward2s]: list of payoff matrices
+    """
+
+    nElements = nAct ** 2  # number of payoff elements in the matrix
+
+    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
     cov[nElements:, :nElements] = np.eye(nElements) * gamma
 
     rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
@@ -22,11 +29,25 @@ def generateGame(gamma, nAct):
     return [reward1s, reward2s]
 
 def checkConvergence(actionProb, oldxBar, tol):
-    normStep = np.linalg.norm(actionProb - oldxBar)
-    return normStep < tol
+    """
+      Evaluates the distance between action probabilities and checks if the change is
+      below some tolerance.
+
+      params
+      actionProb: Agent action probabilities at current time step
+      oldxBar: Previous action probabilities
+      tol: tolerance level
+
+      returns
+
+      (normStep1 < tol) and (normStep2 < tol): Whether change in both agents' action
+      probabilities is below a tolerance.
+    """
+    normStep1 = np.linalg.norm(actionProb[0, :] - oldxBar[0, :])
+    normStep2 = np.linalg.norm(actionProb[1, :] - oldxBar[1, :])
+    return (normStep1 < tol) and (normStep2 < tol)
 
 def runSim(params, nSim, tol):
-
     alpha = params[0]
     tau = params[1]
     gamma = params[2]
@@ -36,40 +57,60 @@ def runSim(params, nSim, tol):
     converged = []
 
     for cSim in range(nSim):
+
+        fig = plt.figure()
+        ax = fig.add_subplot(111)
[…]

### 2020-06-19 Code/Practice/Tuyls.py

@@ -1,10 +1,10 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-alpha = .8
-A = np.array([[2, 0], [0, 1]])
-B = np.array([[1, 0], [0, 2]])
-tau = 0.1
+alpha = .1
+A = np.array([[1, 5], [0, 3]])
+B = np.array([[1, 0], [5, 3]])
+tau = 0.9
 
 x = np.linspace(0, 1, 50)
 y = np.linspace(0, 1, 50)

### 2020-06-23 Documents/ESA/sections/Intro.tex
Updated ESA

@@
     Swarm robotics bases its success upon the collaboration of many agents who contribute towards
-    the overall success of the system \cite{HammanFormalApproach}. The collaboration of many agents
+    the overall success of the system \cite{Hamann2018}. The collaboration of many agents
     who share the same goal can give rise to behaviours that are far more complex than individual
@@
     population of agents change under the influence of control? Note that we use the term 'agent'
-    loosely here, an agent can refer to anything from a simple particle \cite{BorziCollectiveMotion}
-    to a complex robot \cite{ElamvazuthisThesis}. In answering this question, researchers have
+    loosely here, an agent can refer to anything from a simple particle \cite{Roy2017}
+    to a complex robot \cite{Elamvazhuthi2019}. In answering this question, researchers have
     gained a stronger understanding of how a swarm may be controlled to achieve desired results.
@@
     autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
-    \cite{Schwarz}. This builds on the ideas of classical Reinforcement Learning which allows an
+    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning which allows an
     agent to optimise its strategies towards tackling a task through repeated exposure to that task.
@@
     not only on the outcome of the action, but also on the actions of the other agents. This has
-    shown strong results in practical applications \textbf{APPLICATIONREFERENCES}. Whilst MARL was
+    shown strong results in practical applications \cite{Woolridge2009, SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was
     once considered to be non-identifiable (there is no clear way of identifying the algorithm that
@@
     result from a learning algorithm), a steady stream of research is emerging to lift this fog
-    \cite{TuylsSurvey}. This allows for researchers to choose the parameters of their learning
+    \cite{Bloembergen2015}. This allows for researchers to choose the parameters of their learning
     algorithms appropriately to ensure that learning agents behave in the desired manner.
@@
 
-    \textbf{Need to talk about the scope of the project: what assumptions will be made to ensure
-    that the above can be achieved within the given time constraints?}
-
-    \section{Methodology} \label{sec::Methodology}
+    % \section{Methodology} \label{sec::Methodology}
 

### 2020-06-23 Documents/ESA/sections/LitReview.tex
Updated ESA

@@
 \section{Multi Agent Systems} \label{sec::Multi_Agent_Systems}
-
-\textbf{TODO: Elaborate on each of the metrics}
 
@@
 POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by
-fixing the strategy (a manner of selecting an action \cite{Rizk2018DecisionSurvey}) of all agents
+fixing the strategy (a manner of selecting an action \cite{Rizk2018}) of all agents
 except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
 next agent may determine its optimal strategy. This process is iterated over all agents in a process
-known as Alternating Maximisation \cite{Ray2010AnCooperation}. By choosing strategies which maximise
+known as Alternating Maximisation \cite{Ray2010}. By choosing strategies which maximise
 a common payoff, a globally optimal solution can be found.
@@
 approximated by a sequence of smaller, more tractable games
-\cite{Emery-MontemerloApproximatePayoffs}. However, iterating through the entire team of agents to
+\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
 find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
-situations. To address this, \cite{Ray2010AnCooperation} propose to place distinct payoffs on each
+situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
 agent and to consider team formation based on social hierarchy as well as preferred partners. This
@@
 The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
-dynamic decision making. However, as found by Dai et. al \cite{Dai2018TaskSystems} this is
+dynamic decision making. However, as found by Dai et. al \cite{Dai2018} this is
 conditional on an understanding by each robot of the strategy of others, which in turn requires
@@
 
-\textbf{Add in any recent literature in these fields}
+% \textbf{Add in any recent literature in these fields}
 
@@
 strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
+Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA
+\cite{Bowling2002}.
 WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
@@
 
-\textbf{Add in more recent literature r.e. learning in stochastic games and the robustness of MARL}
+% \textbf{Add in more recent literature r.e. learning in stochastic games and the robustness of
+% MARL}
 
@@
 
-\textbf{Include recent updates in here}
+% \textbf{Include recent updates in here}
 
@@
 
-\textbf{Include Marco Dorigo and Recent AAMAS literature in here}
+% \textbf{Include Marco Dorigo and Recent AAMAS literature in here}
 
@@
 \section{Remarks} \label{sec:remarks}
-
-\textbf{TODO: Go through each of the sections and explicitly evaluate them against the defined
-metrics}
 

### 2020-06-23 Documents/ESA/sections/ProposedResearch.tex
Updated ESA

@@
 
-	\textbf{TODO: Ensure all references here are in the Lit Review}
+	% \textbf{TODO: Ensure all references here are in the Lit Review}
 
@@
     (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
-    as tic-tac-toe and prisoner's dilemma \cite{Galla's work and I think Sato's work}. These
+    as tic-tac-toe and prisoner's dilemma \cite{Galla2011, Sato2002}. These
     behaviours include: convergence to a unique equilibrium (though not always to an NE),
     convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
-    Figure ... Of these, the most preferable is, of course, convergence to a unique equilibrium,
+    Figure \ref{fig::DynamicalBehaviours} Of these, the most preferable is, of course, convergence to a unique equilibrium,
     although it is still possible to study systems with multiple equilibria or limit cycles 
-    \cite{One of the textbooks}. However, it would be difficult to control systems whose dynamics
+    \cite{Strogatz2000}. However, it would be difficult to control systems whose dynamics
     are governed by chaos (though research into controlling chaos is ongoing and rife with
-    opportunity \cite{CyberneticalPhysics}) and so MARL techniques should avoid this. It would,
+    opportunity \cite{Fradkov2009}) and so MARL techniques should avoid this. It would,
     therefore, be a useful endeavour to determine the conditions under which these sorts of
     behaviours arise.
+
+    \begin{figure}[h]
+    	\centering
+    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
+    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour displayed
+    	by learning agents. a)
+    	Convergence
+    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
+    	that all trajectories, regardless of initialisation, will converge to this point 
+    	\cite{Tuyls2006AnGames}. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
+    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
+    	exponentially \cite{Sanders2018}.}
+    \end{figure}
 
@@
 	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-	predict the expected behaviour of Q-Learning agents, as shown in Figure ...
+	predict the expected behaviour of Q-Learning agents, as shown in Figure 
+	\ref{fig::TuylsExperiments}.
 
-	It is clear, both from (\ref{eqn::EOM}) and Figure ... that the long-term strategy selection of
+	\begin{figure}[h]
+		\centering
+		\begin{subfigure}[b]{0.9 \textwidth}
+			\centering
+			\includegraphics[width=0.75 \textwidth]{Figures/Dynamics}
+			\caption{}
+		\end{subfigure}
+
+		\begin{subfigure}[b]{0.9 \textwidth}
+			\centering
+			\includegraphics[width=0.7 \textwidth]{Figures/Q-Learners}
+			\caption{}
+		\end{subfigure}
+
+		\caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
+		plot showing the expected behaviour of Q-Learning agents trained by iterating the
+		Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
+		have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
+		randomised initial conditions displayed through numerical simulation. It is clear that the
+		trajectories in b) follow the predictions in a), after stochasticity is accounted for. }
+	\end{figure}
+
+	It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments} that the long-term strategy selection of
 	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
@@
 	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
-	learning behaviour of human players in a game \cite{whatevertheycite}. The authors are able to
+	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
 	determine the regions of parameter space in which complex behaviour,
 	including cycles and chaos, predominantly occur and those in which a given game converges to a
-	stable equilibrium. Figure ... reproduces the graphs shown in \cite{Sanders2018} which
+	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
 	illustrates the successful derivation of a 'phase line', across which learning shifts from
 	convergent to chaotic.
+
+    \begin{figure}[h]
+    	\centering
+    	\includegraphics[width=0.6\textwidth]{Figures/GallaPredictions}
+    	\caption{ \label{fig::GallaPredictions} Results as produced in the supplementary material
+    	of Sanders et al \cite{Sanders2018}. Here, $p$ is the number of players, $N$ is the number
+    	of actions, $\Gamma$ represents the competitiveness of the game (-1 represents zero-sum, 1
+    	represents shared rewards) and $\alpha$ is the memory parameter of the agent as before.
+    	Here $\tau$ is held constant at 0.05 (though it is referred to as $\beta$ in the paper).
+    	The black region represents where games converged to a fixed point through all simulations,
+    	whilst the hotter regions represent the more complex dynamics - red shows the presence of
+    	limit cycles and white regions signal the onset of chaos. The green line is a theoretical
+    	estimation for the phase line which separates the convergent dynamics from complex.}
+    \end{figure}
 
@@
 
-    This segment of research is currently underway and approaching completion. The analysis can be
-    seen in Section \ref{sec::Chaos_in_Q-Learning}.
+    This segment of research is currently underway and approaching completion. The analysis was
+    described in Section \ref{sec::Chaos_in_Q-Learning}.
 
-    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
+    \section{Large Population Dynamics} \label{sec::Large_Agent_Dynamics}
 
@@
     greater strategy space and more agents for any particular player to learn against and is
-    verified by their presented results as in Figure ...
+    verified by their presented results as in Figure \ref{fig::GallaPrevalence} - the hotter
+    regions occupy a larger area as
+
+    \begin{figure}[h]
+    	\centering
+    	\includegraphics[width=0.6\textwidth]{Figures/GallaPrevalence}
+    	\caption{ \label{fig::GallaPrevalence} Results as produced in the supplementary material
+    	of Sanders et al \cite{Sanders2018}. The same items appear here as in Figure 
+    	\ref{fig::GallaPredictions}, except the value of p (number of players) increases moving
+    	from top left to bottom right. It is clear that the hotter region occupies a larger region
+    	of parameter space, indicating that as the bumber of players in the game increase, chaos
+    	becomes more prevalent.}
+    \end{figure}
 
@@
     action, defines the density of agents who retain a given Q-value for that action. This is
-    illustrated in Figure ...
+    illustrated in Figure \ref{fig::LeungPredictions}.
+
+    \begin{figure}[h]
+    	\centering
+    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
+    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al \cite{Hu2019}.
+    	Here, the solid and dotted lines represent the evolution of thhe expectation of Q-values of
+    	two actions across a population of 50 or 999 agents respectively who are trained on an
+    	iterated Stag Hunt game. The circled and crossed
+    	lines represent the dynamics of these Q-values as predicted by the system of equations
+    	derived in the paper. These are seen to closely match the results of the numerical
+    	experiments.}
+    \end{figure}
 
@@
 
-	Two proposals for how this might work
+	The following are suggestions for approaching the estimation of large population dynamics.
 
 	\begin{itemize}
-		\item Estimate the population state using a Random Finite Set (RFS) and apply the models
-		from the previous study. This is a new hypothesis so more research is required.
-		\item Decompose a generic game into a weighted sum of a competitive and a cooperative game.
-		Treat these as two separate agents and invoke the mean field approximation so that any given
-		agent is effectively engaged in a three-player game where the strategy of the opponents is
-		the average strategy of the population.
+		\item Estimate the population state through Random Finite Sets (RFS) and
+	apply the models from the previous study. The aim here is to determine a state
+	estimation for a swarm of unknown size through a random finite set by solving
+	an optimal estimation problem  (typically iterated through a Kalman Filter
+	\cite{Doerr2019}. As the swarm is treated probailistically, the theory can
+	accomodate an arbitrarily large system. Importantly, this may allow for the
+	results from the previous section to be leveraged towards an arbitrary
+	population.
+
+	\item Decompose a generic game into a weighted sum of a
+	competitive and a cooperative game. Treat these as two separate agents and
+	invoke the mean field approximation (MFA) so that any given agent is
+	effectively engaged in a three-player game where the strategy of the opponents
+	is the average strategy of the population. This leverages the existing results
+	on the dynamics of three body problems in game theory \cite{Nagarajan2018} in
+	a mixture of co-operative and competitive settings.
 	\end{itemize}
 
-	\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}
+	%\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}
 
@@
     referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
-    some success in recent literature \cite{Zhang2018, Elamvazhuthi2019, Li2017,
-    BorziCollectiveMotion}, though it makes the assumption that the system evolves through 'drifted
+    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
+    Roy2017}, though it makes the assumption that the system evolves through 'drifted
     brownian motion'. This means that the agents are considered to move about independently and
@@
 	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
-	manner \cite{Any paper of Fokker Planck control}. The latter is beginning to show promise 
-	though control is typically through leadership rather than fields \cite{VlasovMPC}.
+	manner \cite{Fleig}. The latter is beginning to show promise 
+	though control is typically through leadership rather than fields \cite{Burger2019}.
 
@@
 		\item The stablity of the system: Under what conditions is it possible to drive the
-		swarm from one configuration to another in a stable manner?
+		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al
+		present a candidate lyapunov functional upon which dissipation can be evaluated, though it
+		will need to be adapted for the consideration of the consensus models.
 		\item The guarantees of the system: Is it possible to ensure that controls remain within an
-		admissible set (typically a closed, bounded and convex set \cite{PDEControl}).
+		admissible set (typically a closed, bounded and convex set \cite{Fredi2010}).
+		\item Whether the conservation laws of normalisation and total mass, as presented in 
+		\cite{Bellomo2017} can be guaranteed.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Addition of the agent decisions as a constant in the state $f$. This should be fine if
-		it's fixed but note that the controls have no influence over this.
-		\item Multiplicative term in the turning probability which acts as a weighting term where
-		weights are equal to the agent strategy. This extends to both the swarms in
+		\item Addition of the agent decisions as a constant in the state $f$. This will require that
+		the decisions remain fixed in the state and so it will be required to make sure that the
+		controls have no influence on this element.
+		\item Weighted summation term in the probability of an agent changing its velocity from
+		$v_*$ to
+		$v$ due to a field particle with velocity $v^*$ $A[f](v_* \rightarrow v | v_*, v^*)$.
+		Here, weights are equal to the agent strategy. This extends to both the swarms in
 		which the leaders are making decisions (only leaders have this term) as well as in
 		swarms where the population makes decisions (everyone has this term). This will need to be
-		done with care though to ensure that normalisation holds.
+		done with care though to ensure that normalisation holds. Note that, as this a probabilistic
+		approach, we will need to examine the stochastic behaviour of the system and the extent to
+		which constraint and conservation satisfaction can be guaranteed.
 	\end{itemize}
@@
 
-	\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
-	the conservation laws}
+	%\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
+	%the conservation laws}
 

### 2020-06-23 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

@@
     Specifically, we look at characterising the stability of agents learning strategies. This
-    technique was first carried out by Sanders et al \cite{Sanders}, in which the authors
-    characterised the strategy evolution of agents who learn using an 'Experience Weighted
+    technique is carried out by Sanders et al \cite{Sanders2018}, in which the authors
+    characterise the strategy evolution of agents who learn using an 'Experience Weighted
     Attraction' (EWA) algorithm, which is seen to be a strong representation of how people learn in
-    games. The authors were able to determine the regions of parameter space in which learning is
+    games. The authors are able to determine the regions of parameter space in which learning is
     likely to converge towards stable equilibriums, as opposed to complex behaviours (such as limit
     cycles or chaotic dynamics). The aim of this study is to format these techniques for the study
-    of computational agents who follow the popular Q-Learning approach \cite{SuttonBarto,Schwarz}.
-    {}
+    of computational agents who follow the popular Q-Learning approach \cite{Sutton2018,SchwartzMulti-agentApproach}.
+
     We aim, similarly, to determine the regions of parameter space in which the agents are likely to
@@
     game parameters to ensure the predicatability of the resulting behaviour. To achieve this, we
-    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{TuylsDynamics}. In this study, the
+    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{Tuyls2006AnGames}. In this study, the
     authors were able to derive a continuous time dynamical system describing how agents following a
     Q-Learning approach adjust the probabilities of choosing actions as they iteratively play a
-    game. These equations are shown in \cite{TuylsDynamics} to accurately model the expected
+    game. These equations are shown in \cite{Tuyls2006AnGames} to accurately model the expected
     behaviour of agents as they iterate a game, and the experiments which verified this model are
-    shown in \textbf{Figures ...} .
+    shown in Figures \ref{fig::TuylsExperiments}.
 
@@
 
-     \textbf{Derivation suppressed, uncomment to see}
-     %\subfile{./sections/ResearchSummary.tex}
+     \subsection{Derivation of stability line} % (fold)
+     \label{sub:derivation_of_stability_line}
+
+     We begin with the equations as described by Tuyls et al \cite{Tuyls2006AnGames}
+
+    \begin{subequations}
+    \label{eqn::EOM}
+        \begin{equation}
+            \frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
+            + \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
+        \end{equation}
+        \begin{equation}
+            \frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
+            + \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
+        \end{equation}
+    \end{subequations}
+
+    Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al.
+refer to these as the memory and intensity of choice parameters respectively.
+Agent 1 takes action i with probability $x_i$ while Agent 2 takes action j with probability $y_j$.
+If these actions are taken, the agents receive payoff $a_{ij}$ and $b_{ji}$ respectively.
+
+    Our goal is to analyse the dynamics of any game, regardless of payoff elements. As such, we
+    follow the approach of Sanders et al. in deriving the full set of 'effective dynamics' averaged
+    over all possible realisations of the payoff matrices. Note that these elements are drawn from a
+    Multivariate Gaussian such that
+
+    \begin{equation*}
+        \begin{split}
+            \mathbb{E}[a_{ij}] = \mathbb{E}[b_{ji}] = 0\\
+            \mathbb{E}[a_{ij}^2] = \mathbb{E}[b_{ji}^2] = 1\\
+            \mathbb{E}[a_{ij} b_{ji}] = \Gamma.
+        \end{split}
+    \end{equation*}
+
+    where $\Gamma$ is a parameter which defines the 'competitiveness' of the game. For a two player
+    game, $\Gamma \in [-1, 1]$ where -1 denotes a zero-sum game and 1 denotes a game with positive
+    correlation across payoff elements. Taking this average yields
+
+    \begin{equation}
+    \begin{split}
+        \dot{x}(t) &= x(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_y(t, t')x(t')] + 
+        \tilde{\alpha}
+        \rho_x(t) + \alpha \tilde{\tau} \eta_x(t) + \tilde{\alpha} \tau \eta_x(t) \eta_y(t) +
+        \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x) \\
+        \dot{y}(t) &= y(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_x(t, t')y(t')] + 
+        \tilde{\alpha} \rho_y(t) +
+        \alpha \tilde{\tau} \eta_y(t) + \tilde{\alpha} \tau \eta_x(t) \eta_y(t)+ 
+        \sqrt{\Gamma} \tilde{\alpha} \tau \mu_y), \\
+    \end{split}
+    \end{equation}
+
+    Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
+    (see Appendix \ref{app::ResearchSummary}). We now analyse the stability of this dynamical system
+    by linearising about
+    a
+    fixed point. This yields the requirement that a fixed point $x^*$ satisfy
+
+    \begin{equation}
+    0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x \right].
+    \end{equation}
+
+    The implication here is that the resulting value of $x^*$ can take two solutions.
+However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values.
+If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$.
+Numerical experiments will shed more light on the likelihood of convergence.
+If this ansatz turns out to be incorrect (i.e.
+we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
+
+    We take the Fourier transform of this system to determine the long term behaviour of thhe system
+    after a disturbance. To neglect all transient behaviour, we consider the equation at $\omega =
+    0$
+
+    \begin{equation} \label{eqn::Transformed}
+    \left<[|\mathcal{X}(\omega)|^2 \right> = \left< | \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega) |^2 \right> \frac{1}{\left< |\mathcal{A}(\omega, x^*) |^2 \right>},
+    \end{equation}
+
+    where
+
+    \begin{equation}
+        \mathcal{A}(\omega, x^*) = \frac{i \omega}{x^*} - \Gamma \alpha^2 \tilde{\tau}^2 \mathcal{G}_y(\omega)
+    \end{equation}
+
+    By
+    considering that $\left<[|\mathcal{X}(\omega =
+    0)|^2
+    \right> \geq 0$  we arrive at an expression for a stability line (i.e. the phase transition
+    between the
+    existence of stable fixed points and unstable behaviour) as the equality (\ref{eqn::Transformed}
+    )$>0$.
+
+    % subsection derivation_of_stability_line (end)
+
+    \subsection{Numerical Experiments} % (fold)
+    \label{sub:numerical_experiments}
+
+    To verify the results of our theory, and to examine the underlying structure of stability and
+    chaos in Multi-Agent Q Learning, we perform a series of numerical experiments by varying the
+    parameters $\Gamma$ and $\alpha$ whilst keeping $\tau$ fixed. This yields the result shown in
+    Figure \ref{fig::NumericalExperiments}. We see from this, and from the further experiments shown
+    in Appendix \ref{app::ResearchSummary}, that the stability of the system is highly dependent on
+    the value of $\tau$.
+    For
+    low values, the system converges almost everywhere, whilst increasing $\tau$ to 0.15 decreases
+    the probability of convergence significantly.
+
+    \begin{figure}[h]
+        \centering
+         \begin{subfigure}[b]{0.45 \textwidth}
+        \centering
+        \includegraphics[width = 0.7 \textwidth]{Figures/AlphaRun_tau_005.png}
+        \caption{$\tau = 0.05$}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45 \textwidth}
+        \centering
+        \includegraphics[width = 0.7 \textwidth]{Figures/tau_015.png}
+        \caption{$\tau = 0.15$}
+        \end{subfigure}
+
+        \caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
+        simulation is run for 1e5 iterations and tested for convergence. The game is said to have
+        converged based on a tolerance of 1\% difference between action probabilities. For each
+        combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
+        and initial conditions. The average number of converged games (giving an indication of
+        probability of convergence) is shown in each cell of the heatmap. 
+        \label{fig::NumericalExperiments}}
+    \end{figure}
+
+   To generate the numerical simulations in Figure \ref{fig::NumericalExperiments} we used the
+   following procedure.
+
+\begin{enumerate}
+    \item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
+    it does not affect the long term behaviour of the system (it does not appear in (
+    \ref{eqn::EOM})).
+    \item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
+    over.
+    \item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
+    (variables are the payoff elements) with covariance parameterised by $\Gamma$.
+    \item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
+    \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
+    \item Every 100 iterations, check to see if the action probabilities have changed significantly.
+    If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
+    considered to have converged.
+    \item This process is repeated 5 times with random payoff matrices generated based on the value
+    of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
+    converged}}{5}$.
+    \item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
+    heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
+    tested.
+\end{enumerate}
+
+    % subsection numerical_experiments (end)
 
     \subsection*{Future Work} \label{sec::Future Work}
+
+    We are currently running a set of numerical experiments varying over all three parameters
+    $\Gamma, \alpha, \tau$ to identify any islands of stability in parameter space. We will then
+    plot (\ref{eqn::Transformed}) to verify our results.
 
@@
     immediate action is to present the equivalent solutions for the case of a general p-player game.
+
     We then seek to expand this study to a population of agents. For this, we will study the

### 2020-06-24 Documents/ESA/sections/Intro.tex
minor mods in intro

@@
 
-    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
-    the overall success of the system \cite{Hamann2018}. The collaboration of many agents
-    who share the same goal can give rise to behaviours that are far more complex than individual
-    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
-    we are presented with ever more challenging tasks including: search and rescue, cleaning up
-    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
-    and so we must leverage the capacity for agents in a swarm to collectively achieve our
-    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
-    towards this very problem and address the question: how does the dynamical behaviour of a
-    population of agents change under the influence of control? Note that we use the term 'agent'
-    loosely here, an agent can refer to anything from a simple particle \cite{Roy2017}
-    to a complex robot \cite{Elamvazhuthi2019}. In answering this question, researchers have
-    gained a stronger understanding of how a swarm may be controlled to achieve desired results.
+\fr{from the paragraph below it looks like we only deal with collaborative multi-agent systems. Is this really the case?}
 
-    Another technique which has made incredible strides towards improving the capability of
-    autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
-    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning which allows an
-    agent to optimise its strategies towards tackling a task through repeated exposure to that task.
-    MARL utilises this same principle with the caveat that agents must adapt their strategies based
-    not only on the outcome of the action, but also on the actions of the other agents. This has
-    shown strong results in practical applications \cite{Woolridge2009, SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was
-    once considered to be non-identifiable (there is no clear way of identifying the algorithm that
-    a particular agent was trained on) and black box (there is no clear way of ensuring a desired
-    result from a learning algorithm), a steady stream of research is emerging to lift this fog
-    \cite{Bloembergen2015}. This allows for researchers to choose the parameters of their learning
-    algorithms appropriately to ensure that learning agents behave in the desired manner.
+    Swarm robotics bases its success upon the collaboration of many
+    agents who contribute towards the overall goal of the system
+    \cite{Hamann2018}. The collaboration of many agents who share the
+    same goal give rise to behaviours that are far more complex
+    than individual robots can achieve. The capacity for complexity is
+    becoming increasingly important as robots are presented
+    with ever more challenging tasks including: search and rescue,
+    cleaning up space debris, and robotic assembly. Such tasks are
+    beyond the capabilities of individual robots and so we must
+    leverage the capacity for agents in a swarm to collectively
+    achieve our goals. Fortunately, a growing subset of the Control
+    Theory community has turned their attention towards this very
+    problem and address the question: how does the dynamical behaviour
+    of a population of agents change under the influence of control?
+    Note that we use the term `agent' loosely here, an agent can refer
+    to anything from a simple particle \cite{Roy2017} to a complex
+    robot \cite{Elamvazhuthi2019}. In answering this question,
+    researchers have gained a stronger understanding of how a swarm
+    may be controlled to achieve desired results.
+
+    Another technique which has made incredible strides towards
+    improving the capability of autonomous systems to communally
+    achieve results is Multi-Agent Reinforcement Learning (MARL)
+    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of
+    classical Reinforcement Learning which allows an agent to optimise
+    its strategies towards tackling a task through repeated exposure
+    to that task.  MARL utilises this same principle with the caveat
+    that agents must adapt their strategies based not only on the
+    outcome of the action, but also on the actions of the other
+    agents. This has shown strong results in practical applications
+    \cite{Woolridge2009, SchwartzMulti-agentApproach,
+      Yang2004}. Whilst MARL was once considered to be
+    non-identifiable (there is no clear way of identifying the
+    algorithm that a particular agent was trained on) and black box
+    (there is no clear way of ensuring a desired result from a
+    learning algorithm), a steady stream of research is emerging to
+    lift this fog \cite{Bloembergen2015}. This allows for researchers
+    to choose the parameters of their learning algorithms
+    appropriately to ensure that learning agents behave in the desired
+    manner.
 
@@
 
-    Based on the successes of the swarm control and MARL communities, a natural question to ask is
-    whether the promises of these disciplines may be unified. Such a combination would radically
-    improve the capabilities of autonomous system. Ultimately such a system must be driven under the
-    influence of control inputs to perform given tasks. Examples of this might be: forming around
-    individual components of space debris and moving them to a desired location (e.g. a bin), or
-    relocating to multiple areas in a disaster zone to provide immediate relief. For such tasks to
-    be achieved in dynamic environments, which is typically the case, the system must be able to
-    constantly adapt its approach and respond accordingly. Given these considerations, the problem
-    may be stated as follows
+    Based on the successes of the swarm control and MARL communities,
+    a natural question to ask is whether the promises of these
+    disciplines may be unified. Such a combination would radically
+    improve the capabilities of autonomous system. Ultimately such a
+    system must be driven under the influence of control inputs to
+    perform given tasks. Examples of this might be: forming around
+    individual components of space debris and moving them to a desired
+    location (e.g.~a bin), or relocating to multiple areas in a
+    disaster zone to provide immediate relief. For such tasks to be
+    achieved in dynamic environments, which is typically the case, the
+    system must be able to constantly adapt its approach and respond
+    accordingly. Given these considerations, the problem may be stated
+    as follows
 
     \begin{enumerate}
-    	\item A population of robots is given a goal which must be achieved, which can often be
-    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
-    	\item These are to be performed in a dynamic environment with obstacles present and where
-    	the number of tasks, and their priorities may be in constant flux.
-    	\item The agents in the system must, therefore, make decisions collectively which will in
-    	the system achieving the given goals. Due to the dynamic quality of the problem, these
-    	decisions may need to be evaluated online and in a decentralised fashion, as it may not be
-    	possible for a centralised decision maker to communicate with all agents.
-    	\item It is desirable, therefore, to control the dynamical behaviour of
-    	a system composed of agents who learn and adapt through interactions with each other. In
-    	addition, to ensure the safe operation of the system, properties such as state and control
-    	constraints must be satisfied.
+    	\item A population of robots is given a goal which must be
+          achieved, which can often be deconstructed into a set of
+          smaller tasks, to be executed simultaneously.
+    	\item These are to be performed in a dynamic environment with
+          obstacles present and where the number of tasks, and their
+          priorities may be in constant flux.
+    	\item The agents in the system must, therefore, make decisions
+          collectively which \fb{will in the system achieving?} the given
+          goals. Due to the dynamic quality of the problem, these
+          decisions may need to be evaluated online and in a
+          decentralised fashion, as it may not be possible for a
+          centralised decision maker to communicate with all agents.
+    	\item It is desirable, therefore, to control the dynamical
+          behaviour of a system composed of agents who learn and adapt
+          through interactions with each other. In addition, to ensure
+          the safe operation of the system, properties such as state
+          and control constraints must be satisfied.
     \end{enumerate}
@@
 
+\fr{I would add here the paragraph describing the relevance to the CDT.}
+
 \end{document}

### 2020-06-24 Documents/ESA/sections/LitReview.tex
minor mods in intro

@@
 
-In this chapter, we explore the current state of the art in Multi-Agent Systems (MAS). We will
-consider the main techniques that have been proposed towards task allocation and control.
+In this chapter, we explore the current state of the art in
+Multi-Agent Systems (MAS). We will consider the main techniques that
+have been proposed towards task allocation and control.
+
+\fr{you might provide an overview of the introduction with the
+  different sections.}
 
 \section{Multi Agent Systems} \label{sec::Multi_Agent_Systems}
+
+\fr{I wonder whether this section would fit better in Intro.}
 
@@
 \begin{enumerate}
-    \item Distributed. It will often be the case that a multi-agent system must spread out across a
-    large area or operate in regions where communication is limited. As such it is beneficial that
-    such a system does not rely too heavily on communication with a central body. The individual
-    agents must, therefore, be able to make their own decisions and act as independent entities.
-    Aside from the advantage of communication, this ensures that the system is not tied to a single
-    point of failure; in a system governed by a centralised decision maker, any faults in the
-    central body propagates throughout the group. Of course, this comes at the price of
-    computational load - if the agents are required to act independently, they must possess the
-    resources to do so. The term distributed should not be confused with decentralised. The latter
-    refers to a regime in which agents all communicate with one another before making a decision.
-    Whilst this is preferable to a centralised decision maker in terms of the requirement for one
-    entity to communicate with all agents, it still places a high cost on the requirement that
-    agents be in constant communication with one another. In fact it may pose the additional risk
-    that if any agent in the team fails, the whole pipeline falls apart. Distributivity, on the
-    other hand, requires that agents make independent decisions so that, though agents may
-    communicate with each other, they are still able to operate when this is not possible.
-    \item Generality. MAS come in many different flavours; sometimes a small group of heterogeneous 
-    (agents with different capabilities) agents may be required to perform a delicate task whilst
-    in others, it may be required that a large population of homogeneous (all of the same type)
-    agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
-    strategy whilst in the middle of a task. It would be a hindrance if the agents were required to
-    be reprogrammed with a completely different control methodology each time the situation changes
-    slightly. It would be preferable if the method could apply to all different types of scenarios,
-    with homogenous or heteregeneous agents, with single tasks or multiple, in any environment with
-    only minor customisation required. Better still if the agents are able to adapt themselves to
-    the specifics of the scenario.
-    \item Low Computational Load. As mentioned in the previous chapter, a MAS will often be used in
-    complex situations, many of which will be too dangerous for human intervention. As such, the
-    system will be required to carry out its tasks online. For this reason, it is vital that the
-    control method be one which produces low computational load - especially where the time frame
-    for adjusting agent behaviour is limited. Monetary concerns also play a part in this metric; it
-    would not do to impose that every member of the team be equipped with high performance computing
-    power as this would likely fall outside of the budget of any practical usage.
-    \item Robustness. Particularly for physical robots, a MAS should be able to operate in
-    situations which present sensor noise, communication noise, latency, and environmental
-    disturbances. This is rather important in unseen environments where full a priori knowledge of
-    the map cannot be assumed.
-    \item Scalable. This is mentioned last since the ability for a MAS to scale comes from its
-    distributivity  and low computational load. Scalability is the capacity for any method of
-    controlling a MAS to successfully operate as the size of the team increases. This, of course, is
-    related to the complexity of the algorithms involved. However, it should be noted that it is not
-    always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the
-    task at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to
+    \item {\em Distributed}. It will often be the case that a
+      multi-agent system must spread out across a large area or
+      operate in regions where communication is limited. As such it is
+      beneficial that such a system does not rely too heavily on
+      communication with a central body. The individual agents must,
+      therefore, be able to make their own decisions and act as
+      independent entities.  Aside from the advantage of
+      communication, this ensures that the system is not tied to a
+      single point of failure; in a system governed by a centralised
+      decision maker, any faults in the central body propagates
+      throughout the group. Of course, this comes at the price of
+      computational load - if the agents are required to act
+      independently, they must possess the resources to do so. The
+      term distributed should not be confused with decentralised. The
+      latter refers to a regime in which agents all communicate with
+      one another before making a decision.  Whilst this is preferable
+      to a centralised decision maker in terms of the requirement for
+      one entity to communicate with all agents, it still places a
+      high cost on the requirement that agents be in constant
+      communication with one another. In fact it may pose the
+      additional risk that if any agent in the team fails, the whole
+      pipeline falls apart. Distributivity, on the other hand,
+      requires that agents make independent decisions so that, though
+      agents may communicate with each other, they are still able to
+      operate when this is not possible.
+
+    \item {\em Generality}. MAS come in many different flavours; sometimes a
+      small group of heterogeneous
+      %(agents with different capabilities)
+      agents may be required to perform a delicate task
+      whilst in others, it may be required that a large population of
+      homogeneous
+      %(all of the same type)
+      agents perform multiple tasks
+      simultaneously. Indeed the same MAS may have to adapt its
+      strategy whilst in the middle of a task. It would be a hindrance
+      if the agents were required to be reprogrammed with a completely
+      different control methodology each time the situation changes
+      slightly. It would be preferable if the method could apply to
+      all different types of scenarios, with homogenous or
+      heteregeneous agents, with single tasks or multiple, in any
+      environment with only minor customisation required. Better still
+      if the agents are able to adapt themselves to the specifics of
+      the scenario.
+
+\item {\em Low Computational Load}. As mentioned in the previous chapter, a
+  MAS will often be used in complex situations, many of which will be
+  too dangerous for human intervention. As such, the system will be
+  required to carry out its tasks online. For this reason, it is vital
+  that the control method be one which produces low computational load
+  - especially where the time frame for adjusting agent behaviour is
+  limited. Monetary concerns also play a part in this metric; it would
+  not do to impose that every member of the team be equipped with high
+  performance computing power as this would likely fall outside of the
+  budget of any practical usage.
+
+    \item {\em Robustness}. Particularly for physical robots, a MAS
+      should be able to operate in situations which present sensor
+      noise, communication noise, latency, and environmental
+      disturbances. This is rather important in unseen environments
+      where full a priori knowledge of the map cannot be assumed.
+
+    \item {\em Scalable}. This is mentioned last since the ability for
+      a MAS to scale comes from its distributivity and low
+      computational load. Scalability is the capacity for any method
+      of controlling a MAS to successfully operate as the size of the
+      team increases. This, of course, is related to the complexity of
+      the algorithms involved. However, it should be noted that it is
+      not always required that a MAS be formed of dozens (or even
+      hundreds) of agents. Depending on the task at hand (e.g. robotic
+      surgery), it may be beneficial for fewer, more capable agents to
       perform the task, rather than a large population.
@@
 
-Game Theory has a rich history when considering an understanding of multi-agent systems and it
-is impossible to examine MAS without an understanding of Game Theory. These
-begin in economics but have found a strong application in computation due to the rising need for
-distributed systems. Game Theory, therefore, branches across all of the categories in this
-chapter although its synergy with swarms requires development) since Dec-POMDP
-and MARL methods have both base their theory upon the foundations of Game Theory.
+Game Theory has a rich history when considering an understanding of
+multi-agent systems and it is impossible to examine MAS without an
+understanding of Game Theory. These begin in economics but have found
+a strong application in computation due to the rising need for
+distributed systems. Game Theory, therefore, branches across all of
+the categories in this chapter although its synergy with swarms
+requires development\fr{)?} since Dec-POMDP \fr{not yet defined} and MARL methods have both base
+their theory upon the foundations of Game Theory.
+
+\fr{we might want to motivate the restriction to partial observability. Dimension to add to the presentation of MAS?}
 
@@
 
-POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by
-fixing the strategy (a manner of selecting an action \cite{Rizk2018}) of all agents
-except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
-next agent may determine its optimal strategy. This process is iterated over all agents in a process
-known as Alternating Maximisation \cite{Ray2010}. By choosing strategies which maximise
-a common payoff, a globally optimal solution can be found.
+POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an
+optimal solution \fr{to what?} is found by fixing the strategy (a
+manner of selecting an action \cite{Rizk2018}) of all agents except
+one. The optimal strategy of the chosen agent is then computed. This
+is fixed so that the next agent may determine its optimal
+strategy. This process is iterated over all agents in a process known
+as Alternating Maximisation \cite{Ray2010}. By choosing strategies
+which maximise a common payoff, a globally optimal solution can be
+found.
 
-Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
-sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be
-approximated by a sequence of smaller, more tractable games
-\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
-find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
-situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
-agent and to consider team formation based on social hierarchy as well as preferred partners. This
-allows the complexity of the problem to be broken down into smaller game units and also provides a
-clear order in which the games are to be played. This minimises the interference across robots and
-allows for more immediate action to be taken by agents who choose their strategy early on, while
-leaving more passive tasks for those later in the sequence.
+Similarly Bayesian Games is a game theoretic approach with incomplete
+information (thus it is sometimes referred to as an ‘incomplete
+information game’). This allows for a POSG to be approximated by a
+sequence of smaller, more tractable games
+\cite{Emery-Montemerlo}. However, iterating through the entire team of
+agents to find an optimal solution is a lengthy process and does not
+allow for immediate actions in dynamic situations. To address this,
+\cite{Ray2010} propose to place distinct payoffs on each agent and to
+consider team formation based on social hierarchy as well as preferred
+partners. This allows the complexity of the problem to be broken down
+into smaller game units and also provides a clear order in which the
+games are to be played. This minimises the interference across robots
+and allows for more immediate action to be taken by agents who choose
+their strategy early on, while leaving more passive tasks for those
+later in the sequence.
 
-The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
-dynamic decision making. However, as found by Dai et. al \cite{Dai2018} this is
-conditional on an understanding by each robot of the strategy of others, which in turn requires
-adequate communication between robots. Therefore, the game theoretical formulation will fail where
-communication is not possible amongst team members. However, the addition of heuristics, such as
-deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
-members of its team without the need for significant explicit communication.
+The Bayesian Game formulation therefore provides a strong candidate
+for rapid task re-allocation and dynamic decision making. However, as
+found by Dai et. al \cite{Dai2018} this is conditional on an
+understanding by each robot of the strategy of others, which in turn
+requires adequate communication between robots. Therefore, the game
+theoretical formulation will fail where communication is not possible
+amongst team members. However, the addition of heuristics, such as
+deep learning, may be able to advance an agent’s ability to recognise
+the strategies taken by other members of its team without the need for
+significant explicit communication.
 
@@
 
-Game theory can often be applied to problems of control theory (particularly where there are
-multiple agents) to develop robust controllers which guarantee properties of stability and
-constraint satisfaction.
+Game theory can often be applied to problems of control theory
+(particularly where there are multiple agents) to develop robust
+controllers which guarantee properties of stability and constraint
+satisfaction.
 
-This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
-which the players are a controller and an adversarial environment. The design of the controller must
-be such that it is able to drive the system to zero error. To illustrate, consider the problem of
-designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
-vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
-efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
-agent may encounter without actually encountering them. The same notion is explored by Bardi et al
+This idea is explored in \cite{Marden2018AnnualControl}. Here, a
+zero-sum game is considered in which the players are a controller and
+an adversarial environment. The design of the controller must be such
+that it is able to drive the system to zero error. To illustrate,
+consider the problem of designing a controller for a re-entry vehicle,
+as in \cite{Breitner1994ReentryGame}, in which vortices seek to
+destabilise the agent. This will allow us to build stable agents in a
+much more efficient manner since we can simulate the adversarial
+environment and hypothetical scenarios the agent may encounter without
+actually encountering them. The same notion is explored by Bardi et al
 \cite{Bardi1991DifferentialDisturbances}.
 
-Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
-avoidance problem, similarly from the point of view of differential game theory. They develop a
-robust feedback system for the robots which they show to be able to drive the system towards
-predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
-In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
-systems in a distributed manner. Here, agents only consider their own payoff structure and have
-limited communication with one another. The author shows that an approximate equilibrium can be
-found using algebraic methods and illustrate the capabilities of the technique using a collision
-avoidance example. For the sake of brevity the numerous contributions that Mylvaganam has made to
-this field is not presented here. However, we will conclude with those presented in
-\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
-games, including linear-quadratic differential games (in which system dynamics are linear functions
-whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
-induced across the players (a notion was suggested in the research proposal) and mean-field games,
-which is discussed in 'MARL'. The importance of the linear-quadratic
-differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
-admissable iff they are locally exponentially stable (which the author often shows with the aid of
-Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
-calculate online. The author then shows that this is not simply a theoretical exercise by applying
-the novel methods towards multi-agent collision problems and designs dynamic control laws which
-guarantee that each agent will reach their desired state whilst avoiding collision with the other
-agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
-robot system.
+Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider
+the $N$-robot collision avoidance problem, similarly from the point of
+view of differential game theory. They develop a robust feedback
+system for the robots which they show to be able to drive the system
+towards predefined targets whilst providing guarantees of interference
+from other agents (or lack thereof).  In \cite{MylvaganamASystems},
+Mylvaganam also considers a game theoretic control of multi-agent
+systems in a distributed manner. Here, agents only consider their own
+payoff structure and have limited communication with one another. The
+author shows that an approximate equilibrium can be found using
+algebraic methods and illustrate the capabilities of the technique
+using a collision avoidance example. For the sake of brevity the
+numerous contributions that Mylvaganam has made to this field is not
+presented here. However, we will conclude with those presented in
+\cite{Mylvaganam2014}. Here, the author presents approximate solutions
+to a number of differential games, including linear-quadratic
+differential games (in which system dynamics are linear functions
+whilst payoff functions are quadratic), Stackelberg differential
+games, where a hierarchy is induced across the players (a notion was
+suggested in the research proposal) and mean-field games, which are
+discussed under `MARL'. The importance of the linear-quadratic
+differential game is the stability of the solution; solutions for the
+Nash equilibria (NE) are admissable iff they are locally exponentially
+stable (which the author often shows with the aid of Lyapunov
+functions). Approximate solutions to the NE are developed which are
+more feasible to calculate online. The author then shows that this is
+not simply a theoretical exercise by applying the novel methods
+towards multi-agent collision problems and designs dynamic control
+laws which guarantee that each agent will reach their desired state
+whilst avoiding collision with the other agents. Similarly, the
+Stackelberg game is applied to the problem of optimal monitoring by a
+multi robot system.
 
@@
 
-Reinforcement learning extends the Markov Decision Process problem by considering the case where the
-reward model is not initially known to the agent. In a similar manner, Multi Agent Reinforcement
-Learning (MARL) extends the Markov Game setting to one where the payoff structure is not a priori
-knowledge.
+Reinforcement learning extends the Markov Decision Process problem by
+considering the case where the reward model is not initially known to
+the agent. In a similar manner, Multi Agent Reinforcement Learning
+(MARL) extends the Markov Game setting to one where the payoff
+structure is not a priori knowledge.
 
-The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
-policy may be the concatenation of all the individual policy or it may just be options for each
-agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
-and so, in this section, I will try to consider the broad spectrum of methods which attempt to
-achieve this Nash equilibria. The largest problem in MARL is the non-stationarity of the environment
-\cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian.
-However, this must be lifted in the Multi Agent setting since other agents in the environment will
-be learning concurrently. As such, we must now consider that the policy for any one agent will
-depend on the policy of all other agents.
+The task of MARL is to determine an optimal joint policy for all
+agents across the game. This joint policy may be the concatenation of
+all the individual policy or it may just be options for each agent to
+take. In either case, optimality is defined through the standard
+notions of Nash equilibria and so, in this section, I will try to
+consider the broad spectrum of methods which attempt to achieve
+Nash equilibria. The largest problem in MARL is the non-stationarity
+of the environment \cite{Hernandez-LealA}. In single-agent settings,
+it is assumed that the environment is Markovian.  However, this must
+be lifted in the Multi Agent setting since other agents in the
+environment will be learning concurrently. As such, we must now
+consider that the policy for any one agent will depend on the policy
+of all other agents.
 
-This chapter begins with a selection of the foundational methods which were developed towards
-solving the MARL problem. The interested reader may find additional methods and implementations of
-these techniques in \cite{SchwartzMulti-agentApproach}.
+This chapter begins with a selection of the foundational methods which
+were developed towards solving the MARL problem. The interested reader
+may find additional methods and implementations of these techniques in
+\cite{SchwartzMulti-agentApproach}.
 
@@
 
-The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
-method of linear programming (in which constraints are linear). This will be important in
-considering more current methods. A similar consideration is given to the infinitesimal gradient
-ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
-infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
-not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
-particular problem in games where there are multiple Nash equilibria. However, in practice it is
-difficult to choose a convergence rate of the step size and, without an appropriate choice the
-strategy may oscillate as shown in the book. To address this, a modified approach is presented by
-Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA
-\cite{Bowling2002}.
-WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
-to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
-payoff matrix (which is not so much of a problem for model based methods) and the opponent's
-strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
-method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
-(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
-oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
-players with minimal oscillation.
+The most fundamental method to learning in Matrix games is the simplex
+algorithm. This is a popular method of linear programming (in which
+constraints are linear). This will be important in considering more
+current methods. A similar consideration is given to the infinitesimal
+gradient ascent algorithm, in which the step size converges to
+zero. This method guarantees that, in the infite horizon limit, the
+payoffs will converge to the Nash equilibrium payoff. Note that this
+does not necessarily mean that both agents will converge to a single
+Nash equilibrium. This is a particular problem in games where there
+are multiple Nash equilibria. However, in practice it is difficult to
+choose a convergence rate of the step size and, without an appropriate
+choice the strategy may oscillate as shown in the book \fr{please add ref}. To address
+this, a modified approach is presented by Bowling and Veloso which
+incorporates the notion of Win or Learn Fast (WoLF) to produce
+WoLF-IGA \cite{Bowling2002}.  WoLF is a notion we will come across
+often in MARL and is shown by the authors to converge to always to a
+NE. The concern with WoLF methods, however, is that it requires
+explicit knowledge of the payoff matrix (which is not so much of a
+problem for model based methods) and the opponent's strategy (which is
+more of a problem in real-world methods). Finally, the Policy Hill
+Climbing method (PHC) is shown to converge to an optimal mixed
+strategy if the other agents are stationary (i.e.~are not
+learning). However, it is shown that, when this is not the case, the
+algorithm again oscillates. The WoLF-PHC adaptation of this method is
+shown to converge to a NE strategy for both players with minimal
+oscillation.
 
@@
 
-Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
-must learn about the equilibrium strategies by playing the game, which means they do not have a
-priori knowledge of the reward or transition functions. Schwarz considers two properties which
-should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
-that the method should converge to some equilibrium whereas the former suggests that the method
-should learn the best response to stationary opponents. A similar set of conditions is considered by
-Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
-then presents a review of MARL methods (as of September 2014)
+Stochastic Games (or Markov Games) form a basis for MARL
+settings. However, in this case the agents must learn about the
+equilibrium strategies by playing the game, which means they do not
+have a priori knowledge of the reward or transition functions. Schwarz
+considers \fr{where?} two properties which should be used for evaluating MARL
+algorithm: rationality and convergence. The latter simply states that
+the method should converge to some equilibrium whereas the former
+suggests that the method should learn the best response to stationary
+opponents. A similar set of conditions is considered by Conitzer and
+Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
+shortly. Schwarz then presents a review of MARL methods (as of
+September 2014)
 
@@
 
-Multi Agent Learning Dynamics (often referred to as Game Dynamics or Learning Dynamics)
-considers the
-problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
-another. This model then serves to be able to predict the evolution of the system as well as to
-understand the trajectory of learning. Typically, this looks at considering whether or not the
-method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
-solve \cite{ShohamMultiagentFoundations} for all but toy problems.
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
+Multi Agent Learning Dynamics (often referred to as Game Dynamics or
+Learning Dynamics) considers the problem of mathematically modelling
+Multi Agent Systems who adapt through repeated interact with one
+another. This model then serves to be able to predict the evolution of
+the system as well as to understand the trajectory of
+learning. Typically, this looks at considering whether or not the
+method is likely to converge towards a Nash equilibrium. This is
+generally a difficult problem to solve
+\cite{ShohamMultiagentFoundations} for all but toy problems.
+\cite{Letcher2019DifferentiableMechanics} shows that the stable
+equilbrium and Nash equilibrium (NE) are not necessarily the same and,
+in fact, argue that stable points are more informative than NEs.
+Stability provides some guarantees against the stochastic nature of
+the environment since a stable equilibrium will always be returned to
+even after perturbations. This feature is extremely important in Safe
+and Trusted AI as it provides guarantees against undesired behaviour
+in real world environments.
 
-The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
-evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
-considers similar assumptions to that of MARL: agents are no longer required to be rational and
-play the game optimise their expected return through repeated play. Importantly, players have no
-knowledge of the others' payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et al.
-determine the relation between the replicator dynamics concept of EGT (a differential equation
-defining the evolution of the proportion of a subgroup in an evolving population) and Q-Learning
-using Boltzmann probabilities as Q-values. The result was a dynamics equation which describes, for
-each action, the evolution of its selection probability which could even account for random
-exploration. There have since been a number of works which apply the same insight into different
-game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken into the following
-categories
+The area of dynamics which has shown most promise in Multi-Agent
+Reinforcement Learning is that of evolutionary dynamics. This draws
+from the principles of Evolutionary Game Theory (EGT) which considers
+similar assumptions to that of MARL: agents are no longer required to
+be rational and play the game optimise their expected return through
+repeated play. Importantly, players have no knowledge of the others'
+payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et
+al.  determine the relation between the replicator dynamics concept of
+EGT (a differential equation defining the evolution of the proportion
+of a subgroup in an evolving population) and Q-Learning using
+Boltzmann probabilities as Q-values. The result was a dynamics
+equation which describes, for each action, the evolution of its
+selection probability which could even account for random
+exploration. There have since been a number of works which apply the
+same insight into different game types and MARL algorithms. In
+\cite{Bloembergen2015}, these are broken into the following categories
 
@@
 
-\section{Remarks} \label{sec:remarks}
+\section{Discussion} \label{sec:remarks}
 

### 2020-06-24 Documents/ESA/sections/LitReview.tex
minor mods in intro

@@
 \begin{itemize}
-    \item Stability, that a system will return to the desired setpoint (or within a neighbourhood) if
+    \item {\em Stability}: a system will return to the desired setpoint (or within a neighbourhood) if
     perturbed.
 
-    \item Robustness, that a system will perform its function in the presence of uncertainty and
+    \item {\em Robustness}: a system will perform its function in the presence of uncertainty and
     noise
 
-    \item Optimality, that the system will achieve some defined function
+    \item {\em Optimality}: the system will achieve some defined function
 
-    \item Feasibility, that the controller will always be able to generate a control law which
+    \item {\em Feasibility}: the controller will always be able to generate a control law which
     satisfies the desired properties.
@@
 
-There are a number of approaches towards control systems. However, the interest of this review lies
-in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
-stochastic and distributed control. The literature of the control communnity is vast and can be
-divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
-those which are particularly relevant to this study and review them in this section.
+There are a number of approaches towards control systems. However, the
+interest of this review lies in multi-agent systems which must operate
+in the face of uncertainty. As such, we focus on stochastic and
+distributed control. The relevant literature of the control community
+is vast and can be divided into a number of sub-fields. We consider
+Distributed MPC (DMPC) and Swarm Optimal Control as those which are
+particularly relevant to this study and review them hereafter.
 
-\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}
+\subsection{Distributed Model Predictive Control} \label{sec::Distributed_MPC}
 
-Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
-categories: decentralised control, non-cooperative control, cooperative control, and centralised
-control. The last of these is not considered in the text since it only considers the case in which a
-centralised controller has access and can manipulate multiple agents at once.
+Rawlings et al.~\cite{rawlings2017model} divide the problem of
+distributed control into four distinct categories: decentralised
+control, non-cooperative control, cooperative control, and centralised
+control. The last of these is not considered in the text since it only
+considers the case in which a centralised controller has access and
+can manipulate multiple agents at once \fr{so then?}.
 
-Decentralised control is the scheme in which agents do not have information about the actions of
-other agents and can only optimise for their own objective. This has the advantage of requiring no
-communication, but can often lead to poor performance when the agents are strongly coupled as each
-agent’s model is incomplete. In the non-cooperative setting, each agent optimises their own loss
-function whilst treating the others’ actions as a known disturbance. In this setting, each agent has
-knowledge of the others’ control laws and their effect. In this case, the agents must communicate
-their intended actions to one another and iterate to achieve a consensus (or Nash equilibrium). This
-is the same for cooperative control, except that the loss function is now shared across the team.
+Decentralised control is the scheme in which agents do not have
+information about the actions of other agents and can only optimise
+for their own objective. This has the advantage of requiring no
+communication, but can often lead to poor performance when the agents
+are strongly coupled as each agent’s model is incomplete. In the
+non-cooperative setting, each agent optimises their own loss function
+whilst treating the others’ actions as a known disturbance. In this
+setting, each agent has knowledge of the others’ control laws and
+their effect. In this case, the agents must communicate their intended
+actions to one another and iterate to achieve a consensus (or Nash
+equilibrium). This is the same for cooperative control, except that
+the loss function is now shared across the team.
 
-Of all of these systems, cooperative control has found greatest applicability in autonomous systems
-\cite{Negenborn2014}, perhaps due to the favourable stability properties \cite{Venkat2006}. One
-particularly strong application of this system is in vehicle platooning. Here, self-driving cars or
-unmanned aerial vehicles (UAVs) must move in a certain formation without colliding into one another.
-A number of examples can be found such as in \cite{Liu2019, VanParys2017, Zheng2017}. Distributed
-MPC provides the advantage that guarantees can be placed regarding coupled constraint satisfaction
-and feasibility.
+Of all of these systems, cooperative control has found greatest
+applicability in autonomous systems \cite{Negenborn2014}, perhaps due
+to the favourable stability properties \cite{Venkat2006}. One
+particularly strong application of this approach is in vehicle
+platooning. Here, self-driving cars or unmanned aerial vehicles (UAVs)
+must move in a certain formation without colliding into one another.
+A number of examples can be found such as in \cite{Liu2019,
+  VanParys2017, Zheng2017}. Distributed MPC provides the advantage
+that guarantees can be placed regarding coupled constraint
+satisfaction and feasibility.
 
-The advances in stochastic and robust MPC, however, do lend themselves towards revisiting the
-capabilities of decentralised control. Recall that, in this scheme, the agents cannot communicate
-with one another. However, advances in MARL show us that this disadvantage can be made less
-prevalent if each agent has a model of the other \cite{Foerster}. To this end, a methodology such as
-presented in \cite{Heirung2019} may prove beneficial in the decentralised scheme. Here, the system
-chooses amongst a family of system models when choosing its control laws. Similarly, agents who
-determine (or perhaps learn) models of the other agents may be able to leverage this information,
-minimising the model error when optimising.
+The advances in stochastic and robust MPC, however, do lend themselves
+towards revisiting the capabilities of decentralised control. Recall
+that, in this scheme, the agents cannot communicate with one
+another. However, advances in MARL show us that this disadvantage can
+be made less prevalent if each agent has a model of the other
+\cite{Foerster}. To this end, a methodology such as presented in
+\cite{Heirung2019} may prove beneficial in the decentralised
+scheme. Here, the system chooses amongst a family of system models
+when choosing its control laws. Similarly, agents who determine (or
+perhaps learn) models of the other agents may be able to leverage this
+information, minimising the model error when optimising.
 
@@
 
-Swarm systems comprise of a population of (typically) homogeneous agents who are able to organise
-themselves
-into formations using a series of simple local interactions with their neighbours
-\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
-may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
-ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
-performance in reaching globally optimal solutions in search-based tasks. The advantage of many
-swarm algorithms is that they are based on local interactions and so are incredibly scalable
-\cite{Rizk2018}.
+Swarm systems comprise of a population of (typically) homogeneous
+agents who are able to organise themselves into formations using a
+series of simple local interactions with their neighbours
+\cite{Couceiro2015}. Whilst the individual agents are generally
+simplistic, the collective behaviour may exhibit complex phenomena
+emulating systems observed in biological organisations such as bee or
+ant colonies \cite{Sethi2017}. Hybrid algorithms such as in
+\cite{Gao2018} show an accelerated performance in reaching globally
+optimal solutions in search-based tasks. The advantage of many swarm
+algorithms is that they are based on local interactions and so are
+incredibly scalable \cite{Rizk2018}.
 
@@
 
-Recent work has seen the advancement of swarms controlled in stochastic environments. This is
-particularly important for swarm intelligence in robots; many systems are developed with the
-motivation of search-and-rescue, in which the robot swarms will have to operate in environments
-where accounting for uncertainty is critical. To this end, swarm systems have seen the advent of
-stochastic control. In this, the swarm is modelled as a diffusive system using a stochastic
-equation, most often the Kolmogorov Forward Equation \cite{Hamann2008}. In \cite{Hamann2008}, the
-author shows that this equation can be derived by considering local trajectories of smaller subsets
-of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019} extend this idea to other stochastic
-models for swarms, importantly considering an advection-diffusion-reaction model which allows for
+Recent work has seen the advancement of swarms controlled in
+stochastic environments. This is particularly important for swarm
+intelligence in robots; many systems are developed with the motivation
+of search-and-rescue, in which the robot swarms will have to operate
+in environments where accounting for uncertainty is critical. To this
+end, swarm systems have seen the advent of stochastic control. In
+this, the swarm is modelled as a diffusive system using a stochastic
+equation, most often the Kolmogorov Forward Equation
+\cite{Hamann2008}. In \cite{Hamann2008}, the author shows that this
+equation can be derived by considering local trajectories of smaller
+subsets of the swarm. Elamvazhuthi and Berman \cite{Elamvazhuthi2019}
+extend this idea to other stochastic models for swarms, importantly
+considering an advection-diffusion-reaction model which allows for
 hybrid agents to switch between different modes of operation.
 
-The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
-equations for stochastic forward processes (such as swarm foraging) in which, as the number of
-agents tends to infinity, the true macroscopic motion of the system tends to these equations.
-Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
-ability to develop control laws. In \cite{Li2017}, Li et al show that these models can be used to
-develop control laws for robots in a swarm and drive them towards a target distribution. The method
-is shown to perform accurately both in simulation and on real robots. The advantage is that
-guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
-distribution. However, there appears to be significant scope to expand upon this methodology from a
-safety perspective. To begin with, the method does not consider inter-agent interactions and
-therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
-considered, although collisions are avoided by having the robot simply move in the opposite
-direction when encountering an obstacle. It is here that the mean-field models are not as strong
-since they do not take these local interactions into account. It must be noted, however, that Inoue
-et al have identified this problem and are currently working towards its incorporation into the
-model.
+The above models come under the term `mean-field models’
+\cite{Elamvazhuthi2019b}, a series of equations for stochastic forward
+processes (such as swarm foraging) in which, as the number of agents
+tends to infinity, the true macroscopic motion of the system tends to
+these equations.  Importantly, however, these stochastic equations
+allow for an analysis of the swarm, as well as the ability to develop
+control laws. In \cite{Li2017}, Li et al.~show that these models can
+be used to develop control laws for robots in a swarm and drive them
+towards a target distribution. The method is shown to perform
+accurately both in simulation and on real robots. The advantage is
+that guarantees can be placed on the convergence and stabilisabiilty
+of the swarm towards the desired distribution. However, there appears
+to be significant scope to expand upon this methodology from a safety
+perspective. To begin with, the method does not consider inter-agent
+interactions and therefore does not formally guard against
+collisions. In \cite{Inoue2019}, a similar problem is considered,
+although collisions are avoided by having the robot simply move in the
+opposite direction when encountering an obstacle. It is here that the
+mean-field models are not as strong since they do not take these local
+interactions into account. It must be noted, however, that Inoue et
+al.~(\fr{or rather the authors}) have identified this problem and are
+currently working towards its incorporation into the model.
 
-It would, therefore, be of particular interest from a safety perspective to consider agent
-interactions. A starting point may be \cite{Bellomo2017} which extends the dynamical model of a
-swarm system to include agent interaction. This presents a first step towards considering the swarm
-as composed of intelligent agents rather than mindless particles and, as the authors suggest,
-presents the possibility of applying game theoretic approaches towards swarms, which also gives the
-ability to consider heterogeneous swarm systems who interact with one another through repeated play.
-Similarly, it would allow for a stronger control perspective on swarm systems such as presented in
-\cite{Borzi2015}, in which a model predictive control (MPC) scheme is presented for a
-leader-follower swarm system to achieve given tasks.
+It would, therefore, be of particular interest from a safety
+perspective to consider agent interactions. A starting point may be
+\cite{Bellomo2017}, which extends the dynamical model of a swarm system
+to include agent interaction. This presents a first step towards
+considering the swarm as composed of intelligent agents rather than
+mindless particles and, as the authors suggest, presents the
+possibility of applying game theoretic approaches towards swarms,
+which also gives the ability to consider heterogeneous swarm systems
+who interact with one another through repeated play.  Similarly, it
+would allow for a stronger control perspective on swarm systems such
+as presented in \cite{Borzi2015}, in which a model predictive control
+(MPC) scheme is presented for a leader-follower swarm system to
+achieve given tasks.
 
@@
 
-The reduction of the complexity in interactions between agents also allows for the robots to perform
-other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
-considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
-manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
-whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
-sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
-readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
-divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).
+The reduction of the complexity in interactions between agents also
+allows for the robots to perform other calculations on board. In
+\cite{Pini2011TaskSelection}, Pini et al.~leverage this by considering
+adaptive task partitioning across swarms. This allows a swarm, in a
+decentralised manner, to deliberate whether to partition a task into
+its sub-tasks or to perform the task in its whole. As of now (to the
+best of my knowledge) the problem of partitioning general tasks into
+its $N$ sub-tasks is unexplored. This, however, highlights another
+advantage of swarm systems; they are readily divided into sub-groups
+(as in \cite{Zahadat2016DivisionInhibition}) to perform a
+{\em divide-et-impera}
+%(divide and conquer)
+approach to solving problems
+\cite{Pini2011TaskSelection}).
 
-Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
-central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
-adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
-made regarding the homogeneity of individual agents and the simplicity of their local interactions
-result in significant limitations placed on the complexity of the tasks that swarm systems can
-accomplish.
+Furthermore, swarm systems may be designed in a leaderless manner and
+so do not require the use of a central controller
+\cite{Couceiro2015}. This presents the advantage that the system can
+rapidly adapt to the loss of agents or separation of groups throughout
+the task. However, the assumptions made regarding the homogeneity of
+individual agents and the simplicity of their local interactions
+result in significant limitations placed on the complexity of the
+tasks that swarm systems can accomplish.
 
@@
 
-Each of the above methods present different advantages in their approach towards MAS, as well as a
-particular set of disadvantages.
+\fr{I really liked this section.}
+
+Each of the above methods present different advantages in their
+approach towards MAS, as well as a particular set of disadvantages.
 
 Game Theoretic methods have long provided a rigorous approach for
-modelling the behaviour of any MAS. It places no limitation on the heterogeneity of the agents or
-the task demanded. An appropriate choice of payoff matrices will account for both of these
-specifications. Recent advances in POSGs have lifted the strong assumptions on prior knowledge that
-was required to achieve a Nash Equilibrium and Game Theoretic Control allows for such methods to be
-applied in continuous state spaces. Whilst the latter shows particular promise, game theoretic
-methods still fall short in terms of distributivity as they are heavily reliant on communication
-with a centralised decision maker to supply rewards, or within the team to determine each others'
-actions. They also require a priori knowledge of the situation in order to set up payoff matrices
-and so cannot be regarded as robust to environmental uncertainty.
+modelling the behaviour of any MAS. It places no limitation on the
+heterogeneity of the agents or the task demanded. An appropriate
+choice of payoff matrices will account for both of these
+specifications. Recent advances in POSGs have lifted the strong
+assumptions on prior knowledge that was required to achieve a Nash
+Equilibrium and Game Theoretic Control allows for such methods to be
+applied in continuous state spaces. Whilst the latter shows particular
+promise, game theoretic methods still fall short in terms of
+distributivity as they are heavily reliant on communication with a
+centralised decision maker to supply rewards, or within the team to
+determine each others' actions. They also require a priori knowledge
+of the situation in order to set up payoff matrices and so cannot be
+regarded as robust to environmental uncertainty.
 
-Multi-Agent Reinforcement Learning builds on the latter two shortcomings of game theory by allowing
-the environment to supply rewards to agents who adapt their behaviour accordingly. MARL is proving
-to be a powerful method to control MAS, and is rapidly improving, but cannot yet be regarded as
-robust. Studies repeatedly show that small alterations or noise in the environment can result in
-large deviations in behaviour. Furthermore, few guarantees can be placed on the resulting behaviour
-of a MARL system, though progress is being made in closing this gap.
+Multi-Agent Reinforcement Learning builds on the latter two
+shortcomings of game theory by allowing the environment to supply
+rewards to agents who adapt their behaviour accordingly. MARL is
+proving to be a powerful method to control MAS, and is rapidly
+improving, but cannot yet be regarded as robust. Studies repeatedly
+show that small alterations or noise in the environment can result in
+large deviations in behaviour. Furthermore, few guarantees can be
+placed on the resulting behaviour of a MARL system, though progress is
+being made in closing this gap.
 
-Control Theory, on the other hand, takes pride in the guarantees placed on the MAS such as:
-controllability, stability, and robustness. However, control techniques are often centralised or
-decentralised. Distributed methods of control is still an evolving field, particularly in terms of
-robustness to uncertainty. In order to establish guarantees, assumptions are also made on the
-specifics of the MAS, and so control theoretic methods have yet to evolve into general,
-heterogeneous systems with any given task.
+Control Theory, on the other hand, takes pride in the guarantees
+placed on the MAS such as: controllability, stability, and
+robustness. However, control techniques are often centralised or
+decentralised. Distributed methods of control is still an evolving
+field, particularly in terms of robustness to uncertainty. In order to
+establish guarantees, assumptions are also made on the specifics of
+the MAS, and so control theoretic methods have yet to evolve into
+general, heterogeneous systems with any given task.
 
-Swarm systems have their strongest advantage in scalability and, in fact, swarm techniques are built
-to scale due to the distributivity and low computational load placed on each agent. This has often
-come with the assumption that agents in the swarm act as simple, homogeneous, particles who follow
-very simple rules of interaction. Recent work is showing that this is not a necessary assumption
-and, in fact, swarms can leverage heterogeneity and agent capabilities to ensure robustness and
-generalisation.
+Swarm systems have their strongest advantage in scalability and, in
+fact, swarm techniques are built to scale due to the distributivity
+and low computational load placed on each agent. This has often come
+with the assumption that agents in the swarm act as simple,
+homogeneous, particles who follow very simple rules of
+interaction. Recent work is showing that this is not a necessary
+assumption and, in fact, swarms can leverage heterogeneity and agent
+capabilities to ensure robustness and generalisation.
 
-It is clear that each method presents its own set of advantages and disadvantages. In fact, the
-greater contributions are made from a unification of techniques (e.g. game theoretic control) which
-leverage the strengths of one technique to mitigate the drawbacks of another. To this end, we
-consider the unification of swarm control and multi-agent learning. The aim is to unify the
-strengths of swarm theory, MPC and game theory to study populations of agents who can make
-decisions on an individual basis but perform tasks through large scale collaboration. In the
-subsequent chapters, we propose a line of research which explores the properties of a system as well
-as establishing practical control methodologies along the way.
+It is clear that each method presents its own set of advantages and
+disadvantages. In fact, the greater contributions are made from a
+unification of techniques (e.g., game theoretic control) which leverage
+the strengths of one technique to mitigate the drawbacks of
+another. To this end, we consider the unification of swarm control and
+multi-agent learning. The aim is to unify the strengths of swarm
+theory, MPC and game theory to study populations of agents who can
+make decisions on an individual basis but perform tasks through large
+scale collaboration. In the subsequent chapters, we propose a line of
+research which explores the properties of a system as well as
+establishing practical control methodologies along the way.
+
+\fr{what about some use cases/application scenarios.}
 

### 2020-06-25 Documents/ESA/sections/ProposedResearch.tex
minor edits throughout the document

@@
 
-	This chapter describes a proposed line of research which aims to study the evolution of swarm
-	systems with independent, learning agents under the influence of predictive controls. We detail
-	the novel lines of research which this work aims to undertake, providing suggestions of the
-	hypotheses posed by these lines. With this in mind the following studies are proposed and
-	developed subsequently:
+	This chapter describes a proposed line of research which aims
+        to study the evolution of swarm systems with independent,
+        learning agents under the influence of predictive controls. We
+        detail the novel lines of research which this work aims to
+        undertake, providing suggestions of the hypotheses posed by
+        these lines. With this in mind the following studies are
+        proposed and developed subsequently:
 
 	\begin{itemize}
-		\item \textbf{Stability and Chaos in MARL:} in which we seek to understand the dynamics of
-		agent strategies when using Q-Learning to learn a game through iteration. We will establish
-		the stability, as a function of parameters, when learning general p-player N-action games.
-		This study enables the appropriate selection of parameters and payoff matrices to ensure the
-		stability of the strategies of a finite set of agents, such as leaders in a swarm.
+		\item \textbf{Stability and Chaos in MARL:} in which
+                  we seek to understand the dynamics of agent
+                  strategies when using Q-Learning to learn a game
+                  through iteration. We will establish the stability,
+                  as a function of parameters, when learning general
+                  p-player N-action games.  This study enables the
+                  appropriate selection of parameters and payoff
+                  matrices to ensure the stability of the strategies
+                  of a finite set of agents, such as leaders in a
+                  swarm.
+
+                  \fr{this is already attempted in the currect
+                    research section, isn't it?}
+
               \item \textbf{Dynamics of Mean-Field Q-Learning Games:} in which we examine the
@@
 
+        \fr{we analyze each topic in a section \ldots}
+
 	% \textbf{TODO: Ensure all references here are in the Lit Review}
@@
 
-    This segment of research is aimed towards a deeper understanding of the strategy evolution
-    of agents following a Q-Learning approach. This allows for guarantees to be placed on the
-    behaviour of such agents, in particular the conditions under which the game will converge to a
-    stable equilibrium.
+    This segment of research is aimed towards a deeper understanding
+    of the strategy evolution of agents following a Q-Learning
+    approach. This allows for guarantees to be placed on the behaviour
+    of such agents, in particular the conditions under which the game
+    will converge to a stable equilibrium.
 
-    It has long been established that, upon lifting the strong assumptions made by traditional
-    game theory (such as the rationality of agents and complete information), that player
-    strategies can result in much more complex behaviour than convergence to a Nash Equilibrium 
-    (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
-    as tic-tac-toe and prisoner's dilemma \cite{Galla2011, Sato2002}. These
-    behaviours include: convergence to a unique equilibrium (though not always to an NE),
-    convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
-    Figure \ref{fig::DynamicalBehaviours} Of these, the most preferable is, of course, convergence to a unique equilibrium,
-    although it is still possible to study systems with multiple equilibria or limit cycles 
-    \cite{Strogatz2000}. However, it would be difficult to control systems whose dynamics
-    are governed by chaos (though research into controlling chaos is ongoing and rife with
-    opportunity \cite{Fradkov2009}) and so MARL techniques should avoid this. It would,
-    therefore, be a useful endeavour to determine the conditions under which these sorts of
-    behaviours arise.
+    It has long been established that, upon lifting the strong
+    assumptions made by traditional game theory (such as the
+    rationality of agents and complete information), that player
+    strategies can result in much more complex behaviour than
+    convergence to a Nash Equilibrium (NE). In fact, this is even true
+    on what would commonly be regarded as 'simple' games such as
+    tic-tac-toe and prisoner's dilemma \cite{Galla2011,
+      Sato2002}. These behaviours include: convergence to a unique
+    equilibrium (though not always to an NE), convergence to one of
+    multiple equilibria, limit cycles and chaos. These behaviours are
+    shown in Figure \ref{fig::DynamicalBehaviours} Of these, the most
+    preferable is, of course, convergence to a unique equilibrium,
+    although it is still possible to study systems with multiple
+    equilibria or limit cycles \cite{Strogatz2000}. However, it would
+    be difficult to control systems whose dynamics are governed by
+    chaos (though research into controlling chaos is ongoing and rife
+    with opportunity \cite{Fradkov2009}) and so MARL techniques should
+    avoid this. It would, therefore, be a useful endeavour to
+    determine the conditions under which these sorts of behaviours
+    arise.
 
@@
     	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
-    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour displayed
-    	by learning agents. a)
-    	Convergence
-    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
-    	that all trajectories, regardless of initialisation, will converge to this point 
-    	\cite{Tuyls2006AnGames}. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
-    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
-    	exponentially \cite{Sanders2018}.}
+    	\caption{ \label{fig::DynamicalBehaviours} Different types of
+          dynamial behaviour displayed by learning agents. a)
+          Convergence to a unique fixed point in the upper right
+          corner (1, 1). This fixed point is unique, in that all
+          trajectories, regardless of initialisation, will converge to
+          this point \cite{Tuyls2006AnGames}. b) Limit Cycle, the
+          trajectories converge to cyclic behaviour c, d) Chaotic
+          behaviour, here small deviatons in the initial conditions
+          can grow exponentially \cite{Sanders2018}.}
     \end{figure}
 
-    The behaviour of a system may be studied given a model of its dynamics. It is through this
-    process that a wide array of physical systems, from harmonic pendulums to geophysical fluids,
-    can be understood. A growing body of research aims to understand multi-agent reinforcement
-    learning through the lens of its dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames}
-    were able to derive a model of the strategy evolution of agents learning through iterated games.
-    Through this, they were able to arrive at the following model of Multi-Agent Q-Learning
+    The behaviour of a system may be studied given a model of its
+    dynamics. It is through this process that a wide array of physical
+    systems, from harmonic pendulums to geophysical fluids, can be
+    understood. A growing body of research aims to understand
+    multi-agent reinforcement learning through the lens of its
+    dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames} were
+    able to derive a model of the strategy evolution of agents
+    learning through iterated games.  Through this, they were able to
+    arrive at the following model of Multi-Agent Q-Learning
 
@@
 
-	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
-	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
-	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
-	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-	predict the expected behaviour of Q-Learning agents, as shown in Figure 
+        \fr{I understand the equations are the same as in the previous section. I suggest we move the explanation there and remove it from here.}
+
+	Here, $\alpha$ and $\tau$ are the parameters of the agent;
+        Sanders et al. refer to these as the memory and intensity of
+        choice parameters respectively. Agent 1 takes action i with
+        probability $x_i$ while Agent 2 takes action j with
+        probability $y_j$. If these actions are taken, the agents
+        receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these
+        equations, it is possible to predict the expected behaviour of
+        Q-Learning agents, as shown in Figure
         \ref{fig::TuylsExperiments}.
@@
 
+    \fr{I would move all of the above to the previous section.}
+
     \section{Large Population Dynamics} \label{sec::Large_Agent_Dynamics}
 
-    This segment of research aims to model the game dynamics of large populations of agents
-    learning through iterated games and mean-field Q-Learning. The aim is to provide similar
-    guarantees of stability as in the previous sections with the caveat that all agents in the
-    population can learn, rather than a finite subset.
+    This segment of research aims to model the game dynamics of large
+    populations of agents learning through iterated games and
+    mean-field Q-Learning. The aim is to provide similar guarantees of
+    stability as in the previous sections with the caveat that all
+    agents in the population can learn, rather than a finite subset.
 
-    One of the main results shown by Sanders et al. \cite{Sanders2018} is that as the number of
-    players in a game increases, the learning behaviour is more likely to be chaotic, regardless of
-    the choice of parameters. This is intuitive since a higher number of players would result in a
-    greater strategy space and more agents for any particular player to learn against and is
-    verified by their presented results as in Figure \ref{fig::GallaPrevalence} - the hotter
-    regions occupy a larger area as
+    One of the main results shown by Sanders et al. \cite{Sanders2018}
+    is that as the number of players in a game increases, the learning
+    behaviour is more likely to be chaotic, regardless of the choice
+    of parameters. This is intuitive since a higher number of players
+    would result in a greater strategy space and more agents for any
+    particular player to learn against and is verified by their
+    presented results as in Figure \ref{fig::GallaPrevalence} - the
+    hotter regions occupy a larger area as \fr{?}
 
@@
     	\includegraphics[width=0.6\textwidth]{Figures/GallaPrevalence}
-    	\caption{ \label{fig::GallaPrevalence} Results as produced in the supplementary material
-    	of Sanders et al \cite{Sanders2018}. The same items appear here as in Figure 
-    	\ref{fig::GallaPredictions}, except the value of p (number of players) increases moving
-    	from top left to bottom right. It is clear that the hotter region occupies a larger region
-    	of parameter space, indicating that as the bumber of players in the game increase, chaos
-    	becomes more prevalent.}
+    	\caption{ \label{fig::GallaPrevalence} Results as produced in
+          the supplementary material of Sanders et al
+          \cite{Sanders2018}. The same items appear here as in Figure
+          \ref{fig::GallaPredictions}, except the value of p (number
+          of players) increases moving from top left to bottom
+          right. It is clear that the hotter region occupies a larger
+          region of parameter space, indicating that as the bumber of
+          players in the game increase, chaos becomes more prevalent.}
     \end{figure}
 
-    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
-    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
-    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
-    cursory verification of this intuition. Here, the authors present an anaysis of the learning
-    dynamics for a large agent population (which they approximate as containing infinite agents)
-    where each agent is an independent Q-Learning using Boltzmann action selection. The
-    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
-    strong predictor of the overall strategy selection of the population. Indeed, rather than
-    examining the strategies of every agent in the population (which the authors approximate as
-    infinitely large), they model the evolution of a probability density function which, for each
-    action, defines the density of agents who retain a given Q-value for that action. This is
-    illustrated in Figure \ref{fig::LeungPredictions}.
+    Yet it can be argued that, for large populations of agents (e.g.,
+    a crowd), the aggregate behaviour may be predictable \fr{provide some justification to this claim?}. This
+    intuition is the foundation upon which crowd dynamics and flocking
+    systems are based. In fact, the work presented by Leung et
+    al.~\cite{Hu2019} provides a cursory verification of this
+    intuition. Here, the authors present an analysis of the learning
+    dynamics for a large agent population (which they approximate as
+    containing infinite agents) where each agent is an independent
+    Q-Learning using Boltzmann action selection. The result is a
+    system of equations, governed by a Fokker-Planck model which is
+    numerical shown to be a strong predictor of the overall strategy
+    selection of the population. Indeed, rather than examining the
+    strategies of every agent in the population (which the authors
+    approximate as infinitely large), they model the evolution of a
+    probability density function which, for each action, defines the
+    density of agents who retain a given Q-value for that action. This
+    is illustrated in Figure \ref{fig::LeungPredictions}.
 
@@
 
-    This section of the study is perhaps the strongest extension proposed in this
-	chapter, and will likely be the most challenging. Here, we examine the dynamics (
-	\ref{eqn::Vlasov}) in which the interaction term accounts for the social dynamics of the
-	decision making of individual agents who have learnt through an iterated game. We leverage the
-	strategy evolution dynamics and stability analysis established in 
-	\ref{sec::Chaos_in_MARL} and \ref{sec::Large_Agent_Dynamics}.
+    This section of the study is perhaps the strongest extension
+    proposed in this chapter, and will likely be the most
+    challenging. Here, we examine the dynamics (\ref{eqn::Vlasov}) in
+    which the interaction term accounts for the social dynamics of the
+    decision making of individual agents who have learnt through an
+    iterated game. We leverage the strategy evolution dynamics and
+    stability analysis established in \ref{sec::Chaos_in_MARL} and
+    \ref{sec::Large_Agent_Dynamics}.
 

### 2020-06-25 Documents/ESA/sections/ShortTermGoals.tex
minor edits throughout the document

@@
 
-    In this chapter, we summarise and present the research and results which have been obtained thus
-    far. These tackle the problems described in Section \ref{sec::Chaos_in_MARL}. We detail the
-    derivation of a stability phase line as presented in Sanders et al. \cite{Sanders2018} as well
-    as the numerical simulations performed to verify these results. The steps to be completed
+    In this chapter, we summarise and present the research and results
+    which have been obtained thus far. These tackle the problems
+    described in Section \ref{sec::Chaos_in_MARL}. We detail the
+    derivation of a stability phase line as presented in Sanders et
+    al.~\cite{Sanders2018} as well as the numerical simulations
+    performed to verify these results. The steps to be completed
     subseqent to this study are then given.
+
+\fr{perhaps we can provide a bit more of context. Also, we can refer to the appendix for the details of the derivation and mention that we are aiming for a submission to AAAI.}
 
@@
 
-    We begin by considering the evolution of learning with agents who follow a Q-Learning approach.
-    Specifically, we look at characterising the stability of agents learning strategies. This
-    technique is carried out by Sanders et al \cite{Sanders2018}, in which the authors
-    characterise the strategy evolution of agents who learn using an 'Experience Weighted
-    Attraction' (EWA) algorithm, which is seen to be a strong representation of how people learn in
-    games. The authors are able to determine the regions of parameter space in which learning is
-    likely to converge towards stable equilibriums, as opposed to complex behaviours (such as limit
-    cycles or chaotic dynamics). The aim of this study is to format these techniques for the study
-    of computational agents who follow the popular Q-Learning approach \cite{Sutton2018,SchwartzMulti-agentApproach}.
+    We begin by considering the evolution of learning with agents who
+    follow a Q-Learning approach.  Specifically, we look at
+    characterising the stability of agents learning strategies. This
+    technique is carried out by Sanders et al.~\cite{Sanders2018}, in
+    which the authors characterise the strategy evolution of agents
+    who learn using an 'Experience Weighted Attraction' (EWA)
+    algorithm \cite{?}, which is seen to be a strong \fr{why?} representation of how
+    people learn in games. The authors are able to determine the
+    regions of parameter space in which learning is likely to converge
+    towards stable equilibriums, as opposed to complex behaviours
+    (such as limit cycles or chaotic dynamics). The aim of this study
+    is to format these techniques for the study of computational
+    agents who follow the popular Q-Learning approach
+    \cite{Sutton2018,SchwartzMulti-agentApproach}.
 
-    We aim, similarly, to determine the regions of parameter space in which the agents are likely to
-    converge to stable equilibria. In this way it will be possible to, a priori, determine whether,
-    for a particular game, the behaviour is likely to converge and even how to choose the agent or
-    game parameters to ensure the predicatability of the resulting behaviour. To achieve this, we
-    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{Tuyls2006AnGames}. In this study, the
-    authors were able to derive a continuous time dynamical system describing how agents following a
-    Q-Learning approach adjust the probabilities of choosing actions as they iteratively play a
-    game. These equations are shown in \cite{Tuyls2006AnGames} to accurately model the expected
-    behaviour of agents as they iterate a game, and the experiments which verified this model are
-    shown in Figures \ref{fig::TuylsExperiments}.
+    We aim, similarly, to determine the regions of parameter space in
+    which the agents are likely to converge to stable equilibria. In
+    this way it will be possible to, a priori, determine whether, for
+    a particular game, the behaviour is likely to converge and even
+    how to choose the agent or game parameters to ensure the
+    predicatability of the resulting behaviour. To achieve this, we
+    consult the Q-Learning Dynamics proposed by Tuyls et al
+    \cite{Tuyls2006AnGames}. In this study, the authors were able to
+    derive a continuous time dynamical system describing how agents
+    following a Q-Learning approach adjust the probabilities of
+    choosing actions as they iteratively play a game. These equations
+    are shown in \cite{Tuyls2006AnGames} to accurately model the
+    expected behaviour of agents as they iterate a game, and the
+    experiments which verified this model are shown in Figures
+    \ref{fig::TuylsExperiments}.
 
-    With the accuracy of the continuous time dynamical system (\ref{eqn::EOM}) established, we analyse the
-    stability of this system in the following section. Note that whilst the derivation provided is
-    for the particular case of two agents for the sake of brevity, the problem of p-player games is
-    equivalent to that of two players and so the solutions to the former can (and will) be
+    With the accuracy of the continuous time dynamical system
+    (\ref{eqn::EOM}) established, we analyse the stability of this
+    system in the following section. Note that whilst the derivation
+    provided is for the particular case of two agents for the sake of
+    brevity, the problem of $p$-player games is equivalent to that of
+    two players and so the solutions to the former can (and will) be
     presented.
+
+    \fr{differences/similarities between EWA and Q-learning?}
 
@@
 
-     We begin with the equations as described by Tuyls et al \cite{Tuyls2006AnGames}
+     We begin with the equations as described by Tuyls et al \cite{Tuyls2006AnGames} \fr{describing \ldots}
 
@@
 
-    Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al.
-refer to these as the memory and intensity of choice parameters respectively.
-Agent 1 takes action i with probability $x_i$ while Agent 2 takes action j with probability $y_j$.
-If these actions are taken, the agents receive payoff $a_{ij}$ and $b_{ji}$ respectively.
+    Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders
+    et al. refer to these as the {\em memory} and {\em intensity of choice}
+    parameters respectively. Agent 1 takes action $i$ with probability
+    $x_i$ while Agent 2 takes action $j$ with probability $y_j$. If
+    these actions are taken, the agents receive payoff $a_{ij}$ and
+    $b_{ji}$ respectively.
 
-    Our goal is to analyse the dynamics of any game, regardless of payoff elements. As such, we
-    follow the approach of Sanders et al. in deriving the full set of 'effective dynamics' averaged
-    over all possible realisations of the payoff matrices. Note that these elements are drawn from a
-    Multivariate Gaussian such that
-
+    Our goal is to analyse the dynamics of any game, regardless of
+    payoff structure. As such, we follow the approach of Sanders et
+    al. in deriving the full set of 'effective dynamics' averaged over
+    all possible realisations of the payoff matrices. Note that these
+    elements are drawn from a Multivariate Gaussian such that
     \begin{equation*}
@@
     \end{equation*}
-
-    where $\Gamma$ is a parameter which defines the 'competitiveness' of the game. For a two player
+    where $\Gamma$ is a parameter which defines the `competitiveness' of the game. For a two player
     game, $\Gamma \in [-1, 1]$ where -1 denotes a zero-sum game and 1 denotes a game with positive
-    correlation across payoff elements. Taking this average yields
-
+    correlation across payoff elements. Taking this average \fr{some more details?} yields
+%
     \begin{equation}
@@
 
-    Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
-    (see Appendix \ref{app::ResearchSummary}). We now analyse the stability of this dynamical system
-    by linearising about
-    a
-    fixed point. This yields the requirement that a fixed point $x^*$ satisfy
-
+    Here, $G, \rho, \eta, \mu$ are correlation functions, generated
+    due to the averaging process (see Appendix
+    \ref{app::ResearchSummary}). We now analyse the stability of this
+    dynamical system by linearising about a fixed point. This yields
+    the requirement that a fixed point $x^*$ satisfy
+%
     \begin{equation}
@@
 Numerical experiments will shed more light on the likelihood of convergence.
-If this ansatz turns out to be incorrect (i.e.
-we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
+If this ansatz turns out to be incorrect (i.e., we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
 
-    We take the Fourier transform of this system to determine the long term behaviour of thhe system
+    We take the Fourier transform of this system \ref{} to determine the long term behaviour of the system
     after a disturbance. To neglect all transient behaviour, we consider the equation at $\omega =
@@
     (variables are the payoff elements) with covariance parameterised by $\Gamma$.
-    \item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
+    \item Initialise the agents with random initial conditions
+      (i.e., random action probabilities).
     \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
-    \item Every 100 iterations, check to see if the action probabilities have changed significantly.
-    If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
-    considered to have converged.
+    \item Every 100 iterations, check to see if the action
+      probabilities have changed significantly.  If not (i.e., the
+      change over the last 100 iterations is less than 1\%) the
+      learning process is considered to have converged.
+
     \item This process is repeated 5 times with random payoff matrices generated based on the value
@@
     converged}}{5}$.
+
   \item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
@@
 
-    We then seek to expand this study to a population of agents. For this, we will study the
-    stability of the system presented by Leung et al \cite{Hu2019} which presents a mean-field model
-    describing the evolution of learning of a population of Q-Learning agents who play co-operative
-    games against one another. This last point is an important limitation - the derived dynamics
-    will only consider populations who must co-operate with one another (i.e. the $\Gamma$ value of
-    the game is one).
+    We then seek to expand this study to a population of agents. For
+    this, we will study the stability of the system presented by Leung
+    et al \cite{Hu2019} which presents a mean-field model describing
+    the evolution of learning of a population of Q-Learning agents who
+    play co-operative games against one another. This last point is an
+    important limitation - the derived dynamics will only consider
+    populations who must co-operate with one another (i.e., the
+    $\Gamma$ value of the game is 1).
 

### 2020-06-25 Documents/ESA/sections/Intro.tex
minor mods in intro
Updated ESA

--- 2020-06-23 Documents/ESA/sections/Intro.tex
@@
     Swarm robotics bases its success upon the collaboration of many agents who contribute towards
-    the overall success of the system \cite{Hamann2018}. The collaboration of many agents
-    who share the same goal can give rise to behaviours that are far more complex than individual
-    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
-    we are presented with ever more challenging tasks including: search and rescue, cleaning up
-    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
-    and so we must leverage the capacity for agents in a swarm to collectively achieve our
-    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
+    the overall success of the system \cite{Hamann2018}. The collaboration of many agents who share
+    the same goal can give rise to behaviours that are far more complex than individual robots can
+    achieve. The capacity for complexity is becoming increasingly important as robots are we are
+    presented with ever more challenging tasks including: search and rescue, cleaning up space
+    debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots and so
+    we must leverage the capacity for agents in a swarm to collectively achieve our goals.
+    Fortunately, a growing subset of the Control Theory community have turned their attention
     towards this very problem and address the question: how does the dynamical behaviour of a
-    population of agents change under the influence of control? Note that we use the term 'agent'
-    loosely here, an agent can refer to anything from a simple particle \cite{Roy2017}
-    to a complex robot \cite{Elamvazhuthi2019}. In answering this question, researchers have
-    gained a stronger understanding of how a swarm may be controlled to achieve desired results.
+    population of agents change under the influence of control? Note that we use the term `agent'
+    loosely here, an agent can refer to any entity to which controls may be applied, from a simple
+    particle \cite{Roy2017} to a complex robot \cite{Elamvazhuthi2019}. In answering this question,
+    researchers have gained a stronger understanding of how a swarm may be controlled to achieve
+    desired results.
 
@@
     autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
-    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning which allows an
-    agent to optimise its strategies towards tackling a task through repeated exposure to that task.
-    MARL utilises this same principle with the caveat that agents must adapt their strategies based
-    not only on the outcome of the action, but also on the actions of the other agents. This has
-    shown strong results in practical applications \cite{Woolridge2009, SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was
-    once considered to be non-identifiable (there is no clear way of identifying the algorithm that
-    a particular agent was trained on) and black box (there is no clear way of ensuring a desired
-    result from a learning algorithm), a steady stream of research is emerging to lift this fog
-    \cite{Bloembergen2015}. This allows for researchers to choose the parameters of their learning
-    algorithms appropriately to ensure that learning agents behave in the desired manner.
+    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning
+    which allows an agent to optimise its strategies towards tackling a task through repeated
+    exposure to that task. MARL utilises this same principle with the caveat that agents must adapt
+    their strategies based not only on the outcome of the action, but also on the actions of the
+    other agents. This has shown strong results in practical applications \cite{Woolridge2009,
+    SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was once considered to be non-identifiable
+    (there is no clear way for a third party to identify the algorithm that a particular agent was
+    trained on) and black box (there is no clear way of ensuring a desired result from a learning
+    algorithm from its behaviour during and after learning), a steady stream of research is emerging
+    to lift this fog \cite{Bloembergen2015}. This allows for researchers to choose the parameters of
+    their learning algorithms appropriately to ensure that learning agents behave in the desired
+    manner.
 
@@
     	the number of tasks, and their priorities may be in constant flux.
-    	\item The agents in the system must, therefore, make decisions collectively which will in
-    	the system achieving the given goals. Due to the dynamic quality of the problem, these
+    	\item The agents in the system must, therefore, make decisions collectively which will result
+        in the system achieving the given goals. Due to the dynamic quality of the problem, these
         decisions may need to be evaluated online and in a decentralised fashion, as it may not be

### 2020-06-25 Documents/ESA/sections/LitReview.tex
Updated ESA

--- 2020-06-23 Documents/ESA/sections/LitReview.tex
@@
 \begin{enumerate}
-    \item Distributed. It will often be the case that a multi-agent system must spread out across a
-    large area or operate in regions where communication is limited. As such it is beneficial that
-    such a system does not rely too heavily on communication with a central body. The individual
-    agents must, therefore, be able to make their own decisions and act as independent entities.
-    Aside from the advantage of communication, this ensures that the system is not tied to a single
-    point of failure; in a system governed by a centralised decision maker, any faults in the
-    central body propagates throughout the group. Of course, this comes at the price of
-    computational load - if the agents are required to act independently, they must possess the
-    resources to do so. The term distributed should not be confused with decentralised. The latter
-    refers to a regime in which agents all communicate with one another before making a decision.
-    Whilst this is preferable to a centralised decision maker in terms of the requirement for one
-    entity to communicate with all agents, it still places a high cost on the requirement that
-    agents be in constant communication with one another. In fact it may pose the additional risk
-    that if any agent in the team fails, the whole pipeline falls apart. Distributivity, on the
-    other hand, requires that agents make independent decisions so that, though agents may
-    communicate with each other, they are still able to operate when this is not possible.
-    \item Generality. MAS come in many different flavours; sometimes a small group of heterogeneous 
-    (agents with different capabilities) agents may be required to perform a delicate task whilst
-    in others, it may be required that a large population of homogeneous (all of the same type)
-    agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
-    strategy whilst in the middle of a task. It would be a hindrance if the agents were required to
-    be reprogrammed with a completely different control methodology each time the situation changes
-    slightly. It would be preferable if the method could apply to all different types of scenarios,
-    with homogenous or heteregeneous agents, with single tasks or multiple, in any environment with
-    only minor customisation required. Better still if the agents are able to adapt themselves to
-    the specifics of the scenario.
-    \item Low Computational Load. As mentioned in the previous chapter, a MAS will often be used in
-    complex situations, many of which will be too dangerous for human intervention. As such, the
-    system will be required to carry out its tasks online. For this reason, it is vital that the
-    control method be one which produces low computational load - especially where the time frame
-    for adjusting agent behaviour is limited. Monetary concerns also play a part in this metric; it
-    would not do to impose that every member of the team be equipped with high performance computing
-    power as this would likely fall outside of the budget of any practical usage.
-    \item Robustness. Particularly for physical robots, a MAS should be able to operate in
-    situations which present sensor noise, communication noise, latency, and environmental
-    disturbances. This is rather important in unseen environments where full a priori knowledge of
-    the map cannot be assumed.
-    \item Scalable. This is mentioned last since the ability for a MAS to scale comes from its
-    distributivity  and low computational load. Scalability is the capacity for any method of
+    \item \textbf{Distributed}. It will often be the case that a multi-agent system must spread out
+across a large area or operate in regions where communication is limited. As such it is beneficial
+that such a system does not rely too heavily on communication with a central body. The individual
+agents must, therefore, be able to make their own decisions and act as independent entities. Aside
+from the low communication load, this ensures that the system is not tied to a single point of
+failure; in a system governed by a centralised decision maker, any faults in the central body
+propagates throughout the group. Of course, this comes at the price of computational load - if the
+agents are required to act independently, they must possess the resources to do so. The term
+distributed should not be confused with decentralised. The latter refers to a regime in which agents
+all communicate with one another before making a decision. Whilst this is preferable to a
+centralised decision maker in terms of the requirement for one entity to communicate with all
+agents, it still places a high cost on the requirement that agents be in constant communication with
+one another. In fact it may pose the additional risk that if any agent in the team fails, the whole
+pipeline falls apart. Distributivity, on the other hand, requires that agents make independent
+decisions so that, though agents may communicate with each other, they are still able to operate
+when this is not possible.
+    \item \textbf{Generality}. MAS come in many different flavours; sometimes a small group of
+heterogeneous  (agents with different capabilities) agents may be required to perform a delicate
+task whilst in others, it may be required that a large population of homogeneous (all of the same
+type) agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
+strategy whilst in the middle of a task. It would be a hindrance if the agents were required to be
+reprogrammed with a completely different control methodology each time the situation changes
+slightly. It would be preferable if the method could apply to all different types of scenarios, with
+homogenous or heteregeneous agents, with single tasks or multiple, in any environment with only
+minor customisation required. Better still if the agents are able to adapt themselves to the
+specifics of the scenario.
+    \item \textbf{Low Computational Load}. As mentioned in the previous chapter, a MAS will often be
+used in complex situations, many of which will be too dangerous for human intervention. As such, the
+system will be required to carry out its tasks online. For this reason, it is vital that the control
+method be one which produces low computational load - especially where the time frame for adjusting
+agent behaviour is limited. Monetary concerns also play a part in this metric; it would not do to
+impose that every member of the team be equipped with high performance computing power as this would
+likely fall outside of the budget of any practical usage.
+    \item \textbf{Robustness}. Particularly for physical robots, a MAS should be able to operate in
+situations which present sensor noise, communication noise, latency, and environmental disturbances.
+This is rather important in unseen environments where full a priori knowledge of the map cannot be
+assumed.
+    \item \textbf{Scalable}. This is mentioned last since the ability for a MAS to scale comes from
+its distributivity  and low computational load. Scalability is the capacity for any method of
 controlling a MAS to successfully operate as the size of the team increases. This, of course, is
 related to the complexity of the algorithms involved. However, it should be noted that it is not
-    always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the
-    task at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to
-    perform the task, rather than a large population. 
+always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the task
+at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to perform the
+task, rather than a large population. 
 \end{enumerate}
@@
 
-Game Theory has a rich history when considering an understanding of multi-agent systems and it
-is impossible to examine MAS without an understanding of Game Theory. These
-begin in economics but have found a strong application in computation due to the rising need for
-distributed systems. Game Theory, therefore, branches across all of the categories in this
-chapter although its synergy with swarms requires development) since Dec-POMDP
-and MARL methods have both base their theory upon the foundations of Game Theory.
+Game Theory has a rich history when considering an understanding of multi-agent systems and it is
+impossible to examine MAS without an understanding of Game Theory. These begin in economics but have
+found a strong application in computation due to the rising need for distributed systems. Game
+Theory, therefore, branches across all of the categories in this chapter although its synergy with
+swarms requires development) since Dec-POMDP (Decentralised Partial Observable Markov Decision
+Processes) and MARL methods have both base their theory upon the foundations of Game Theory.
 
@@
 Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
-sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be
+sometimes referred to as an `incomplete information game’). This allows for a POSG to be
 approximated by a sequence of smaller, more tractable games
@@
 The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
-dynamic decision making. However, as found by Dai et. al \cite{Dai2018} this is
+dynamic decision making. However, as found by Dai et al. \cite{Dai2018} this is
 conditional on an understanding by each robot of the strategy of others, which in turn requires
@@
 efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
-agent may encounter without actually encountering them. The same notion is explored by Bardi et al
+agent may encounter without actually encountering them. The same notion is explored by Bardi et al.
 \cite{Bardi1991DifferentialDisturbances}.
@@
 induced across the players (a notion was suggested in the research proposal) and mean-field games,
-which is discussed in 'MARL'. The importance of the linear-quadratic
+which is discussed in `MARL'. The importance of the linear-quadratic
 differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
@@
 in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
-stochastic and distributed control. The literature of the control communnity is vast and can be
+stochastic and distributed control. The literature of the control community is vast and can be
 divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
@@
 
-\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}
+\subsection{Distributed Model Predictive Control} \label{sec::Distributed_MPC}
 
-Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
+Rawlings et al. \cite{rawlings2017model} divide the problem of distributed control into four distinct
 categories: decentralised control, non-cooperative control, cooperative control, and centralised
@@
 Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
-ability to develop control laws. In \cite{Li2017}, Li et al show that these models can be used to
+ability to develop control laws. In \cite{Li2017}, Li et al. show that these models can be used to
 develop control laws for robots in a swarm and drive them towards a target distribution. The method
@@
 since they do not take these local interactions into account. It must be noted, however, that Inoue
-et al have identified this problem and are currently working towards its incorporation into the
+et al. have identified this problem and are currently working towards its incorporation into the
 model.

### 2020-06-25 Documents/ESA/sections/ProposedResearch.tex
Updated ESA

--- 2020-06-23 Documents/ESA/sections/ProposedResearch.tex
@@
 	This chapter describes a proposed line of research which aims to study the evolution of swarm
-	systems with independent, learning agents under the influence of predictive controls. We detail
+	systems with learning agents under the influence of predictive controls. We detail
 	the novel lines of research which this work aims to undertake, providing suggestions of the
@@
     	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
-    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour displayed
-    	by learning agents. a)
+    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour
+       displayed
+    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
     	Convergence
     	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
-    	that all trajectories, regardless of initialisation, will converge to this point 
-    	\cite{Tuyls2006AnGames}. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
+    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
     	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
-    	exponentially \cite{Sanders2018}.}
+    	exponentially. b-d drawn from \cite{Sanders2018}}
     \end{figure}
@@
 	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
-	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
-	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
+	memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
+	$x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
 	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
@@
 	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
-	illustrates the successful derivation of a 'phase line', across which learning shifts from
+	illustrates the successful derivation of a `phase line', across which learning shifts from
 	convergent to chaotic.
@@
     dynamics for a large agent population (which they approximate as containing infinite agents)
-    where each agent is an independent Q-Learning using Boltzmann action selection. The
+    where each agent is an independent Q-Learner using Boltzmann action selection. The
     result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
@@
     	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
-    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al \cite{Hu2019}.
-    	Here, the solid and dotted lines represent the evolution of thhe expectation of Q-values of
+    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al. \cite{Hu2019}.
+    	Here, the solid and dotted lines represent the evolution of the expectation of Q-values of
     	two actions across a population of 50 or 999 agents respectively who are trained on an
@@
 
-    As described in the previous chapter, the control of swarms has been examined through the use of
+    As described in Chapter \ref{ch::Lit_Review}, the control of swarms has been examined through the
+    use of
     mean field models. These models resolve the fact that it is impossible to view the entire system
@@
 		\item The stablity of the system: Under what conditions is it possible to drive the
-		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al
+		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al.
 		present a candidate lyapunov functional upon which dissipation can be evaluated, though it
@@
 	systems derived in Section \ref{sec::Large_Agent_Dynamics} and it is likely that relaxations would
-	be required in terms of controllability results. A likely relaxation would be to examine only the
+	be required in terms of controllability results. An example would be to examine only the
 	behaviour in the long-enough time frame, which means that we could not impose a final time. Of

### 2020-06-25 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

--- 2020-06-23 Documents/ESA/sections/ShortTermGoals.tex
@@
     Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
-    (see Appendix \ref{app::ResearchSummary}). We now analyse the stability of this dynamical system
-    by linearising about
-    a
-    fixed point. This yields the requirement that a fixed point $x^*$ satisfy
+    and the notation $\tilde{\cdot}$ denotes a term which has been scaled with respect to $N$ (see
+    Appendix \ref{app::ResearchSummary} for method and notation). We now analyse the stability of
+    this dynamical system by linearising about a fixed point. This yields the requirement that a
+    fixed point $x^*$ satisfy
 
@@
 
-    The implication here is that the resulting value of $x^*$ can take two solutions.
-However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values.
-If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$.
-Numerical experiments will shed more light on the likelihood of convergence.
-If this ansatz turns out to be incorrect (i.e.
-we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
+    The implication here is that the resulting value of $x^*$ can take two solutions. However, one
+    of these is $x^* = 0$, which is found to rarely occur \cite{Coolen2005}, while the second solution
+    contains a term $\sqrt{\Gamma}$, which would yield complex values. Such a result, of course, is
+    not possible for a quantity denoting probabilities and so it appears that the theory cannot hold
+    for $\Gamma < 0$. However, numerical experiments will shed light on the likelihood of
+    convergence and the islands of stability in parameter space for this region.
 
-    We take the Fourier transform of this system to determine the long term behaviour of thhe system
-    after a disturbance. To neglect all transient behaviour, we consider the equation at $\omega =
-    0$
+    We take the Fourier transform of this system to determine the long term behaviour of the system
+    after a disturbance. To neglect all transient behaviour (high frequency disturbances), we
+    consider the equation at $\omega = 0$
 
@@
     By
-    considering that $\left<[|\mathcal{X}(\omega =
+    considering that $\left<|\mathcal{X}(\omega =
     0)|^2
@@
     (variables are the payoff elements) with covariance parameterised by $\Gamma$.
-    \item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
+    \item Initialise the agents with random initial conditions (i.e. random action probabilities).
     \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
@@
     of simplifying the notation and reducing the complexity of the experiments. However, the next
-    immediate action is to present the equivalent solutions for the case of a general p-player game.
+    immediate action is to present the equivalent solutions for the case of a general $p$-player
+    game.
 

### 2020-06-26 Documents/ESA/sections/Intro.tex

--- 2020-06-24 Documents/ESA/sections/Intro.tex
@@
     individual components of space debris and moving them to a desired
-    location (e.g.~a bin), or relocating to multiple areas in a
+    location (e.g. a bin), or relocating to multiple areas in a
     disaster zone to provide immediate relief. For such tasks to be
@@
     \begin{enumerate}
-    	\item A population of robots is given a goal which must be
-          achieved, which can often be deconstructed into a set of
-          smaller tasks, to be executed simultaneously.
-    	\item These are to be performed in a dynamic environment with
-          obstacles present and where the number of tasks, and their
-          priorities may be in constant flux.
-    	\item The agents in the system must, therefore, make decisions
-          collectively which \fb{will in the system achieving?} the given
-          goals. Due to the dynamic quality of the problem, these
-          decisions may need to be evaluated online and in a
-          decentralised fashion, as it may not be possible for a
-          centralised decision maker to communicate with all agents.
-    	\item It is desirable, therefore, to control the dynamical
-          behaviour of a system composed of agents who learn and adapt
-          through interactions with each other. In addition, to ensure
-          the safe operation of the system, properties such as state
-          and control constraints must be satisfied.
+    	\item A population of robots is given a goal which must be achieved, which can often be
+    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
+    	\item These are to be performed in a dynamic environment with obstacles present and where
+    	the number of tasks, and their priorities may be in constant flux.
+    	\item The agents in the system must, therefore, make decisions collectively which will result
+        in the system achieving the given goals. Due to the dynamic quality of the problem, these
+        decisions may need to be evaluated online and in a decentralised fashion, as it may not be
+        possible for a centralised decision maker to communicate with all agents. 
+        \item It is desirable, therefore, to control the dynamical behaviour of
+    	a system composed of agents who learn and adapt through interactions with each other. In
+    	addition, to ensure the safe operation of the system, properties such as state and control
+    	constraints must be satisfied.
     \end{enumerate}

### 2020-06-26 Documents/ESA/sections/LitReview.tex

--- 2020-06-24 Documents/ESA/sections/LitReview.tex
@@
 \begin{enumerate}
-    \item {\em Distributed}. It will often be the case that a
-      multi-agent system must spread out across a large area or
-      operate in regions where communication is limited. As such it is
-      beneficial that such a system does not rely too heavily on
-      communication with a central body. The individual agents must,
-      therefore, be able to make their own decisions and act as
-      independent entities.  Aside from the advantage of
-      communication, this ensures that the system is not tied to a
-      single point of failure; in a system governed by a centralised
-      decision maker, any faults in the central body propagates
-      throughout the group. Of course, this comes at the price of
-      computational load - if the agents are required to act
-      independently, they must possess the resources to do so. The
-      term distributed should not be confused with decentralised. The
-      latter refers to a regime in which agents all communicate with
-      one another before making a decision.  Whilst this is preferable
-      to a centralised decision maker in terms of the requirement for
-      one entity to communicate with all agents, it still places a
-      high cost on the requirement that agents be in constant
-      communication with one another. In fact it may pose the
-      additional risk that if any agent in the team fails, the whole
-      pipeline falls apart. Distributivity, on the other hand,
-      requires that agents make independent decisions so that, though
-      agents may communicate with each other, they are still able to
-      operate when this is not possible.
-
-    \item {\em Generality}. MAS come in many different flavours; sometimes a
-      small group of heterogeneous
-      %(agents with different capabilities)
-      agents may be required to perform a delicate task
-      whilst in others, it may be required that a large population of
-      homogeneous
-      %(all of the same type)
-      agents perform multiple tasks
-      simultaneously. Indeed the same MAS may have to adapt its
-      strategy whilst in the middle of a task. It would be a hindrance
-      if the agents were required to be reprogrammed with a completely
-      different control methodology each time the situation changes
-      slightly. It would be preferable if the method could apply to
-      all different types of scenarios, with homogenous or
-      heteregeneous agents, with single tasks or multiple, in any
-      environment with only minor customisation required. Better still
-      if the agents are able to adapt themselves to the specifics of
-      the scenario.
-
-\item {\em Low Computational Load}. As mentioned in the previous chapter, a
-  MAS will often be used in complex situations, many of which will be
-  too dangerous for human intervention. As such, the system will be
-  required to carry out its tasks online. For this reason, it is vital
-  that the control method be one which produces low computational load
-  - especially where the time frame for adjusting agent behaviour is
-  limited. Monetary concerns also play a part in this metric; it would
-  not do to impose that every member of the team be equipped with high
-  performance computing power as this would likely fall outside of the
-  budget of any practical usage.
-
-    \item {\em Robustness}. Particularly for physical robots, a MAS
-      should be able to operate in situations which present sensor
-      noise, communication noise, latency, and environmental
-      disturbances. This is rather important in unseen environments
-      where full a priori knowledge of the map cannot be assumed.
-
-    \item {\em Scalable}. This is mentioned last since the ability for
-      a MAS to scale comes from its distributivity and low
-      computational load. Scalability is the capacity for any method
-      of controlling a MAS to successfully operate as the size of the
-      team increases. This, of course, is related to the complexity of
-      the algorithms involved. However, it should be noted that it is
-      not always required that a MAS be formed of dozens (or even
-      hundreds) of agents. Depending on the task at hand (e.g. robotic
-      surgery), it may be beneficial for fewer, more capable agents to
-      perform the task, rather than a large population.
+    \item {\em Distributed}. It will often be the case that a multi-agent system must spread out
+across a large area or operate in regions where communication is limited. As such it is beneficial
+that such a system does not rely too heavily on communication with a central body. The individual
+agents must, therefore, be able to make their own decisions and act as independent entities. Aside
+from the low communication load, this ensures that the system is not tied to a single point of
+failure; in a system governed by a centralised decision maker, any faults in the central body
+propagates throughout the group. Of course, this comes at the price of computational load - if the
+agents are required to act independently, they must possess the resources to do so. The term
+distributed should not be confused with decentralised. The latter refers to a regime in which agents
+all communicate with one another before making a decision. Whilst this is preferable to a
+centralised decision maker in terms of the requirement for one entity to communicate with all
+agents, it still places a high cost on the requirement that agents be in constant communication with
+one another. In fact it may pose the additional risk that if any agent in the team fails, the whole
+pipeline falls apart. Distributivity, on the other hand, requires that agents make independent
+decisions so that, though agents may communicate with each other, they are still able to operate
+when this is not possible.
+    \item {\em Generality}. MAS come in many different flavours; sometimes a small group of
+heterogeneous  (agents with different capabilities) agents may be required to perform a delicate
+task whilst in others, it may be required that a large population of homogeneous (all of the same
+type) agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
+strategy whilst in the middle of a task. It would be a hindrance if the agents were required to be
+reprogrammed with a completely different control methodology each time the situation changes
+slightly. It would be preferable if the method could apply to all different types of scenarios, with
+homogenous or heteregeneous agents, with single tasks or multiple, in any environment with only
+minor customisation required. Better still if the agents are able to adapt themselves to the
+specifics of the scenario.
+    \item {\em Low Computational Load}. As mentioned in the previous chapter, a MAS will often be
+used in complex situations, many of which will be too dangerous for human intervention. As such, the
+system will be required to carry out its tasks online. For this reason, it is vital that the control
+method be one which produces low computational load - especially where the time frame for adjusting
+agent behaviour is limited. Monetary concerns also play a part in this metric; it would not do to
+impose that every member of the team be equipped with high performance computing power as this would
+likely fall outside of the budget of any practical usage.
+    \item {\em Robustness}. Particularly for physical robots, a MAS should be able to operate in
+situations which present sensor noise, communication noise, latency, and environmental disturbances.
+This is rather important in unseen environments where full a priori knowledge of the map cannot be
+assumed.
+    \item {\em Scalable}. This is mentioned last since the ability for a MAS to scale comes from
+its distributivity  and low computational load. Scalability is the capacity for any method of
+controlling a MAS to successfully operate as the size of the team increases. This, of course, is
+related to the complexity of the algorithms involved. However, it should be noted that it is not
+always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the task
+at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to perform the
+task, rather than a large population. 
 \end{enumerate}
@@
 
-Game Theory has a rich history when considering an understanding of
-multi-agent systems and it is impossible to examine MAS without an
-understanding of Game Theory. These begin in economics but have found
-a strong application in computation due to the rising need for
-distributed systems. Game Theory, therefore, branches across all of
-the categories in this chapter although its synergy with swarms
-requires development\fr{)?} since Dec-POMDP \fr{not yet defined} and MARL methods have both base
-their theory upon the foundations of Game Theory.
-
-\fr{we might want to motivate the restriction to partial observability. Dimension to add to the presentation of MAS?}
+Game Theory has a rich history when considering an understanding of multi-agent systems and it is
+impossible to examine MAS without an understanding of Game Theory. These begin in economics but have
+found a strong application in computation due to the rising need for distributed systems. Game
+Theory, therefore, branches across all of the categories in this chapter although its synergy with
+swarms requires development) since Dec-POMDP (Decentralised Partial Observable Markov Decision
+Processes) and MARL methods have both base their theory upon the foundations of Game Theory.
 
@@
 
-POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an
-optimal solution \fr{to what?} is found by fixing the strategy (a
-manner of selecting an action \cite{Rizk2018}) of all agents except
-one. The optimal strategy of the chosen agent is then computed. This
-is fixed so that the next agent may determine its optimal
-strategy. This process is iterated over all agents in a process known
-as Alternating Maximisation \cite{Ray2010}. By choosing strategies
-which maximise a common payoff, a globally optimal solution can be
-found.
+POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution to a multi-agent
+decision making problem is found by
+fixing the strategy (a manner of selecting an action \cite{Rizk2018}) of all agents
+except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
+next agent may determine its optimal strategy. This process is iterated over all agents in a process
+known as Alternating Maximisation \cite{Ray2010}. By choosing strategies which maximise
+a common payoff, a globally optimal solution can be found.
 
-Similarly Bayesian Games is a game theoretic approach with incomplete
-information (thus it is sometimes referred to as an ‘incomplete
-information game’). This allows for a POSG to be approximated by a
-sequence of smaller, more tractable games
-\cite{Emery-Montemerlo}. However, iterating through the entire team of
-agents to find an optimal solution is a lengthy process and does not
-allow for immediate actions in dynamic situations. To address this,
-\cite{Ray2010} propose to place distinct payoffs on each agent and to
-consider team formation based on social hierarchy as well as preferred
-partners. This allows the complexity of the problem to be broken down
-into smaller game units and also provides a clear order in which the
-games are to be played. This minimises the interference across robots
-and allows for more immediate action to be taken by agents who choose
-their strategy early on, while leaving more passive tasks for those
-later in the sequence.
+Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
+sometimes referred to as an `incomplete information game’). This allows for a POSG to be
+approximated by a sequence of smaller, more tractable games
+\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
+find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
+situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
+agent and to consider team formation based on social hierarchy as well as preferred partners. This
+allows the complexity of the problem to be broken down into smaller game units and also provides a
+clear order in which the games are to be played. This minimises the interference across robots and
+allows for more immediate action to be taken by agents who choose their strategy early on, while
+leaving more passive tasks for those later in the sequence.
 
-The Bayesian Game formulation therefore provides a strong candidate
-for rapid task re-allocation and dynamic decision making. However, as
-found by Dai et. al \cite{Dai2018} this is conditional on an
-understanding by each robot of the strategy of others, which in turn
-requires adequate communication between robots. Therefore, the game
-theoretical formulation will fail where communication is not possible
-amongst team members. However, the addition of heuristics, such as
-deep learning, may be able to advance an agent’s ability to recognise
-the strategies taken by other members of its team without the need for
-significant explicit communication.
+The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
+dynamic decision making. However, as found by Dai et al. \cite{Dai2018} this is
+conditional on an understanding by each robot of the strategy of others, which in turn requires
+adequate communication between robots. Therefore, the game theoretical formulation will fail where
+communication is not possible amongst team members. However, the addition of heuristics, such as
+deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
+members of its team without the need for significant explicit communication.
 
@@
 
-\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}
+\subsection{Distributed Model Predictive Control} \label{sec::Distributed_MPC}
 
-Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
+Rawlings et al. \cite{rawlings2017model} divide the problem of distributed control into four distinct
 categories: decentralised control, non-cooperative control, cooperative control, and centralised
 control. The last of these is not considered in the text since it only considers the case in which a
-centralised controller has access and can manipulate multiple agents at once.
+centralised controller has access and can manipulate multiple agents at once. This immediately
+violates the desired property of distributivity.
 
@@
 direction when encountering an obstacle. It is here that the mean-field models are not as strong
-since they do not take these local interactions into account. It must be noted, however, that Inoue
-et al have identified this problem and are currently working towards its incorporation into the
+since they do not take these local interactions into account. It must be noted, however, that the authors have identified this problem and are currently working towards its incorporation into the
 model.
@@
 
-Each of the above methods present different advantages in their approach towards MAS, as well as a
-particular set of disadvantages.
+\fr{I really liked this section.}
+
+Each of the above methods present different advantages in their
+approach towards MAS, as well as a particular set of disadvantages.
 
 Game Theoretic methods have long provided a rigorous approach for
-modelling the behaviour of any MAS. It places no limitation on the heterogeneity of the agents or
-the task demanded. An appropriate choice of payoff matrices will account for both of these
-specifications. Recent advances in POSGs have lifted the strong assumptions on prior knowledge that
-was required to achieve a Nash Equilibrium and Game Theoretic Control allows for such methods to be
-applied in continuous state spaces. Whilst the latter shows particular promise, game theoretic
-methods still fall short in terms of distributivity as they are heavily reliant on communication
-with a centralised decision maker to supply rewards, or within the team to determine each others'
-actions. They also require a priori knowledge of the situation in order to set up payoff matrices
-and so cannot be regarded as robust to environmental uncertainty.
+modelling the behaviour of any MAS. It places no limitation on the
+heterogeneity of the agents or the task demanded. An appropriate
+choice of payoff matrices will account for both of these
+specifications. Recent advances in POSGs have lifted the strong
+assumptions on prior knowledge that was required to achieve a Nash
+Equilibrium and Game Theoretic Control allows for such methods to be
+applied in continuous state spaces. Whilst the latter shows particular
+promise, game theoretic methods still fall short in terms of
+distributivity as they are heavily reliant on communication with a
+centralised decision maker to supply rewards, or within the team to
+determine each others' actions. They also require a priori knowledge
+of the situation in order to set up payoff matrices and so cannot be
+regarded as robust to environmental uncertainty.
 
-Multi-Agent Reinforcement Learning builds on the latter two shortcomings of game theory by allowing
-the environment to supply rewards to agents who adapt their behaviour accordingly. MARL is proving
-to be a powerful method to control MAS, and is rapidly improving, but cannot yet be regarded as
-robust. Studies repeatedly show that small alterations or noise in the environment can result in
-large deviations in behaviour. Furthermore, few guarantees can be placed on the resulting behaviour
-of a MARL system, though progress is being made in closing this gap.
+Multi-Agent Reinforcement Learning builds on the latter two
+shortcomings of game theory by allowing the environment to supply
+rewards to agents who adapt their behaviour accordingly. MARL is
+proving to be a powerful method to control MAS, and is rapidly
+improving, but cannot yet be regarded as robust. Studies repeatedly
+show that small alterations or noise in the environment can result in
+large deviations in behaviour. Furthermore, few guarantees can be
+placed on the resulting behaviour of a MARL system, though progress is
+being made in closing this gap.
 
-Control Theory, on the other hand, takes pride in the guarantees placed on the MAS such as:
-controllability, stability, and robustness. However, control techniques are often centralised or
-decentralised. Distributed methods of control is still an evolving field, particularly in terms of
-robustness to uncertainty. In order to establish guarantees, assumptions are also made on the
-specifics of the MAS, and so control theoretic methods have yet to evolve into general,
-heterogeneous systems with any given task.
+Control Theory, on the other hand, takes pride in the guarantees
+placed on the MAS such as: controllability, stability, and
+robustness. However, control techniques are often centralised or
+decentralised. Distributed methods of control is still an evolving
+field, particularly in terms of robustness to uncertainty. In order to
+establish guarantees, assumptions are also made on the specifics of
+the MAS, and so control theoretic methods have yet to evolve into
+general, heterogeneous systems with any given task.
 
-Swarm systems have their strongest advantage in scalability and, in fact, swarm techniques are built
-to scale due to the distributivity and low computational load placed on each agent. This has often
-come with the assumption that agents in the swarm act as simple, homogeneous, particles who follow
-very simple rules of interaction. Recent work is showing that this is not a necessary assumption
-and, in fact, swarms can leverage heterogeneity and agent capabilities to ensure robustness and
-generalisation.
+Swarm systems have their strongest advantage in scalability and, in
+fact, swarm techniques are built to scale due to the distributivity
+and low computational load placed on each agent. This has often come
+with the assumption that agents in the swarm act as simple,
+homogeneous, particles who follow very simple rules of
+interaction. Recent work is showing that this is not a necessary
+assumption and, in fact, swarms can leverage heterogeneity and agent
+capabilities to ensure robustness and generalisation.
 
-It is clear that each method presents its own set of advantages and disadvantages. In fact, the
-greater contributions are made from a unification of techniques (e.g. game theoretic control) which
-leverage the strengths of one technique to mitigate the drawbacks of another. To this end, we
-consider the unification of swarm control and multi-agent learning. The aim is to unify the
-strengths of swarm theory, MPC and game theory to study populations of agents who can make
-decisions on an individual basis but perform tasks through large scale collaboration. In the
-subsequent chapters, we propose a line of research which explores the properties of a system as well
-as establishing practical control methodologies along the way.
+It is clear that each method presents its own set of advantages and
+disadvantages. In fact, the greater contributions are made from a
+unification of techniques (e.g., game theoretic control) which leverage
+the strengths of one technique to mitigate the drawbacks of
+another. To this end, we consider the unification of swarm control and
+multi-agent learning. The aim is to unify the strengths of swarm
+theory, MPC and game theory to study populations of agents who can
+make decisions on an individual basis but perform tasks through large
+scale collaboration. In the subsequent chapters, we propose a line of
+research which explores the properties of a system as well as
+establishing practical control methodologies along the way.
+
+\fr{\textbf{what about some use cases/application scenarios.}}
 

### 2020-06-26 Documents/ESA/sections/ProposedResearch.tex

--- 2020-06-25 Documents/ESA/sections/ProposedResearch.tex
@@
 
-                  \fr{this is already attempted in the currect
+                  \fr{this is already attempted in the current
                     research section, isn't it?}
@@
 
+	The remainder of this chapter analyses each of these topics in turn, providing suggestions for
+	the course of research.
         \fr{we analyze each topic in a section \ldots}
@@
     	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
-    	\caption{ \label{fig::DynamicalBehaviours} Different types of
-          dynamial behaviour displayed by learning agents. a)
-          Convergence to a unique fixed point in the upper right
-          corner (1, 1). This fixed point is unique, in that all
-          trajectories, regardless of initialisation, will converge to
-          this point \cite{Tuyls2006AnGames}. b) Limit Cycle, the
-          trajectories converge to cyclic behaviour c, d) Chaotic
-          behaviour, here small deviatons in the initial conditions
-          can grow exponentially \cite{Sanders2018}.}
+    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
+       displayed
+    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
+    	Convergence
+    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
+    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
+    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
+    	exponentially. b-d drawn from \cite{Sanders2018}}
     \end{figure}
@@
 
-	Here, $\alpha$ and $\tau$ are the parameters of the agent;
-        Sanders et al. refer to these as the memory and intensity of
-        choice parameters respectively. Agent 1 takes action i with
-        probability $x_i$ while Agent 2 takes action j with
-        probability $y_j$. If these actions are taken, the agents
-        receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these
-        equations, it is possible to predict the expected behaviour of
-        Q-Learning agents, as shown in Figure
+	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
+	memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
+	$x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
+	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
+	predict the expected behaviour of Q-Learning agents, as shown in Figure 
 	\ref{fig::TuylsExperiments}.

### 2020-06-26 Documents/ESA/sections/ShortTermGoals.tex

--- 2020-06-25 Documents/ESA/sections/ShortTermGoals.tex
@@
 
-    Here, $G, \rho, \eta, \mu$ are correlation functions, generated
-    due to the averaging process (see Appendix
-    \ref{app::ResearchSummary}). We now analyse the stability of this
-    dynamical system by linearising about a fixed point. This yields
-    the requirement that a fixed point $x^*$ satisfy
-%
+    Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
+    and the notation $\tilde{\cdot}$ denotes a term which has been scaled with respect to $N$ (see
+    Appendix \ref{app::ResearchSummary} for method and notation). We now analyse the stability of
+    this dynamical system by linearising about a fixed point. This yields the requirement that a
+    fixed point $x^*$ satisfy
+
     \begin{equation}
@@
 
-    The implication here is that the resulting value of $x^*$ can take two solutions.
-However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values.
-If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$.
-Numerical experiments will shed more light on the likelihood of convergence.
-If this ansatz turns out to be incorrect (i.e., we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
+    The implication here is that the resulting value of $x^*$ can take two solutions. However, one
+    of these is $x^* = 0$, which is found to rarely occur \cite{Coolen2005}, while the second solution
+    contains a term $\sqrt{\Gamma}$, which would yield complex values. Such a result, of course, is
+    not possible for a quantity denoting probabilities and so it appears that the theory cannot hold
+    for $\Gamma < 0$. However, numerical experiments will shed light on the likelihood of
+    convergence and the islands of stability in parameter space for this region.
 
-    We take the Fourier transform of this system \ref{} to determine the long term behaviour of the system
-    after a disturbance. To neglect all transient behaviour, we consider the equation at $\omega =
-    0$
+    We take the Fourier transform of this system to determine the long term behaviour of the system
+    after a disturbance. To neglect all transient behaviour (high frequency disturbances), we
+    consider the equation at $\omega = 0$
 
@@
     (variables are the payoff elements) with covariance parameterised by $\Gamma$.
-    \item Initialise the agents with random initial conditions
-      (i.e., random action probabilities).
+    \item Initialise the agents with random initial conditions (i.e. random action probabilities).
     \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.

### 2020-06-26 Documents/ESA/main.tex
Updated Write Up and ESA
Updated ESA
minor mods in intro
Restructuring of ESA

@@
 \documentclass[11pt]{report}
-
+\usepackage[toc,page]{appendix}
+\usepackage{amsmath,amsfonts}
+\usepackage{mathtools}
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{color}
 \usepackage{subfiles}
@@
 \usetikzlibrary{calc}
+
+\newcommand\fr[1]{\textcolor{red}{FR: #1}}
 
@@
 
-\chapter{Proposed Research} \subfile{sections/ProposedResearch.tex} \label{ch::ProposedResearch}
+\part*{Proposed Research}
 
-\chapter{Short Term Goals} \subfile{sections/ShortTermGoals.tex} \label{ch::ShortTermGoals}
+\chapter{Introduction to Proposals} \subfile{sections/IntrotoProposals.tex} 
+\label{ch::IntrotoProposals}
+
+\chapter{Stability and Chaos in MARL} \subfile{sections/ShortTermGoals.tex} 
+\label{ch::ShortTermGoals}
+
+\chapter{Proposals for Future Research} \subfile{sections/ProposedResearch.tex} 
+\label{ch::ProposedResearch}
 
@@
 
+\bibliographystyle{IEEEtran}
+
+\bibliography{IEEEfull,references}
+
+\begin{appendices}
+      \chapter{Research Summary} \subfile{sections/ResearchSummary} \label{app::ResearchSummary}
+\end{appendices}
+
 \end{document}

### 2020-06-26 Documents/ESA/sections/Intro.tex
Restructuring of ESA

@@
 
-\fr{from the paragraph below it looks like we only deal with collaborative multi-agent systems. Is this really the case?}
-
     Swarm robotics bases its success upon the collaboration of many
     agents who contribute towards the overall goal of the system
-    \cite{Hamann2018}. The collaboration of many agents who share the
-    same goal give rise to behaviours that are far more complex
-    than individual robots can achieve. The capacity for complexity is
+    \cite{Hamann2018}. Such a collaboration can take the form of cooperative efforts or even
+    competition, both resulting in behaviours that are far more complex thhan individual robots can
+    achieve. The capacity for complexity is
     becoming increasingly important as robots are presented
@@
     disciplines may be unified. Such a combination would radically
-    improve the capabilities of autonomous system. Ultimately such a
+    improve the capabilities of autonomous systems. Ultimately such a
     system must be driven under the influence of control inputs to
@@
     \begin{enumerate}
-    	\item A population of robots is given a goal which must be achieved, which can often be
+    	\item A population of robots is given a goal which must be achieved, and can often be
     	deconstructed into a set of smaller tasks, to be executed simultaneously. 
@@
     \begin{itemize}
-    	\item How the strategies of a population of agents evolves as the iteratively interact
+    	\item How the strategies of a population of agents evolves as they iteratively interact
     	with one another. We will examine whether the system evolves to a stable equilibrium, or
@@
     	\item The extent to which the dynamical behaviour of a population of learning agents is
-    	influenced under given control. We seek to understand the conditions under which guarantees
+    	influenced under given controls. We seek to understand the conditions under which guarantees
     	on theoretical results such as controllability, stability, and well-posedness may be
@@
     The resultant work will provide novel insights into the behaviour of swarm systems and provide
-    new methods for which they may be practically used. Importantly, the study will seek to
-    understand the guarantees that can be placed on the safety of such systems in terms of their
-    stability and constraint satisfaction.
+    new methods for which they may be practically used.
 
-    % \section{Methodology} \label{sec::Methodology}
-
-\fr{I would add here the paragraph describing the relevance to the CDT.}
+    Importantly, the study will seek to understand the guarantees that can be
+    placed on the safety of such systems in terms of their stability and
+    constraint satisfaction. In doing so, we can ensure that a user can have
+    confidence in the decision making and manipulation of the system.
 

### 2020-06-26 Documents/ESA/sections/IntrotoProposals.tex
Restructuring of ESA

--- 2020-06-25 Documents/ESA/sections/ProposedResearch.tex
@@
 
-	This chapter describes a proposed line of research which aims to study the evolution of swarm
-	systems with learning agents under the influence of predictive controls. We detail
-	the novel lines of research which this work aims to undertake, providing suggestions of the
-	hypotheses posed by these lines. With this in mind the following studies are proposed and
-	developed subsequently:
+	In the following chapters, we describe our proposed lines of research which aims
+    to study the evolution of swarm systems with independent,
+    learning agents under the influence of predictive controls. We
+    detail the novel lines of research which this work aims to
+    undertake, providing suggestions of the hypotheses posed by
+    these lines. With this in mind the following studies are
+    proposed and developed subsequently:
 
-	\begin{itemize}
-		\item \textbf{Stability and Chaos in MARL:} in which we seek to understand the dynamics of
-		agent strategies when using Q-Learning to learn a game through iteration. We will establish
-		the stability, as a function of parameters, when learning general p-player N-action games.
-		This study enables the appropriate selection of parameters and payoff matrices to ensure the
+    \begin{enumerate}
+		\item \textbf{Stability and Chaos in MARL:} in which we seek to understand the dynamics of agent
+		strategies when using Q-Learning to learn a game through iteration. We will establish the
+		stability, as a function of parameters, when learning general p-player N-action games.  This
+		study enables the appropriate selection of parameters and payoff matrices to ensure the
 		stability of the strategies of a finite set of agents, such as leaders in a swarm.
@@
 		an MPC scheme is then to be examined in a similar capacity. 	 
+    \end{enumerate}
 
-	\end{itemize}
-
-	% \textbf{TODO: Ensure all references here are in the Lit Review}
-
-    \section{Stability and Chaos in MARL} \label{sec::Chaos_in_MARL}
-
-    This segment of research is aimed towards a deeper understanding of the strategy evolution
-    of agents following a Q-Learning approach. This allows for guarantees to be placed on the
-    behaviour of such agents, in particular the conditions under which the game will converge to a
-    stable equilibrium.
-
-    It has long been established that, upon lifting the strong assumptions made by traditional
-    game theory (such as the rationality of agents and complete information), that player
-    strategies can result in much more complex behaviour than convergence to a Nash Equilibrium 
-    (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
-    as tic-tac-toe and prisoner's dilemma \cite{Galla2011, Sato2002}. These
-    behaviours include: convergence to a unique equilibrium (though not always to an NE),
-    convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
-    Figure \ref{fig::DynamicalBehaviours} Of these, the most preferable is, of course, convergence to a unique equilibrium,
-    although it is still possible to study systems with multiple equilibria or limit cycles 
-    \cite{Strogatz2000}. However, it would be difficult to control systems whose dynamics
-    are governed by chaos (though research into controlling chaos is ongoing and rife with
-    opportunity \cite{Fradkov2009}) and so MARL techniques should avoid this. It would,
-    therefore, be a useful endeavour to determine the conditions under which these sorts of
-    behaviours arise.
-
-    \begin{figure}[h]
-    	\centering
-    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
-    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour
-       displayed
-    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
-    	Convergence
-    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
-    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
-    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
-    	exponentially. b-d drawn from \cite{Sanders2018}}
-    \end{figure}
-
-    The behaviour of a system may be studied given a model of its dynamics. It is through this
-    process that a wide array of physical systems, from harmonic pendulums to geophysical fluids,
-    can be understood. A growing body of research aims to understand multi-agent reinforcement
-    learning through the lens of its dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames}
-    were able to derive a model of the strategy evolution of agents learning through iterated games.
-    Through this, they were able to arrive at the following model of Multi-Agent Q-Learning
-
-	\begin{subequations}
-	\label{eqn::EOM}
-		\begin{equation}
-			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
-			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
-		\end{equation}
-		\begin{equation}
-			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
-			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
-		\end{equation}
-	\end{subequations}
-
-	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
-	memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
-	$x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
-	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-	predict the expected behaviour of Q-Learning agents, as shown in Figure 
-	\ref{fig::TuylsExperiments}.
-
-	\begin{figure}[h]
-		\centering
-		\begin{subfigure}[b]{0.9 \textwidth}
-			\centering
-			\includegraphics[width=0.75 \textwidth]{Figures/Dynamics}
-			\caption{}
-		\end{subfigure}
-
-		\begin{subfigure}[b]{0.9 \textwidth}
-			\centering
-			\includegraphics[width=0.7 \textwidth]{Figures/Q-Learners}
-			\caption{}
-		\end{subfigure}
-
-		\caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
-		plot showing the expected behaviour of Q-Learning agents trained by iterating the
-		Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
-		have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
-		randomised initial conditions displayed through numerical simulation. It is clear that the
-		trajectories in b) follow the predictions in a), after stochasticity is accounted for. }
-	\end{figure}
-
-	It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments} that the long-term strategy selection of
-	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
-	then pose the question: how do these elements influence the types of behaviours seen during
-	learning on an iterated game? In other words, under what parameter selections are we likely to
-	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?
-
-	With this in mind, the intention of this area of study is to consider the analysis presented in
-	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
-	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
-	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
-	determine the regions of parameter space in which complex behaviour,
-	including cycles and chaos, predominantly occur and those in which a given game converges to a
-	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
-	illustrates the successful derivation of a `phase line', across which learning shifts from
-	convergent to chaotic.
-
-    \begin{figure}[h]
-    	\centering
-    	\includegraphics[width=0.6\textwidth]{Figures/GallaPredictions}
-    	\caption{ \label{fig::GallaPredictions} Results as produced in the supplementary material
-    	of Sanders et al \cite{Sanders2018}. Here, $p$ is the number of players, $N$ is the number
-    	of actions, $\Gamma$ represents the competitiveness of the game (-1 represents zero-sum, 1
-    	represents shared rewards) and $\alpha$ is the memory parameter of the agent as before.
-    	Here $\tau$ is held constant at 0.05 (though it is referred to as $\beta$ in the paper).
-    	The black region represents where games converged to a fixed point through all simulations,
-    	whilst the hotter regions represent the more complex dynamics - red shows the presence of
-    	limit cycles and white regions signal the onset of chaos. The green line is a theoretical
-    	estimation for the phase line which separates the convergent dynamics from complex.}
-    \end{figure}
-
-    We propose to bridge the analysis presented by Sanders
-    et al. and Galla et al. towards games learnt using MARL, particularly Q-Learning with
-    Boltzmann exploration as considered by Tuyls et al. This would allow for a characterisation of
-    the expected resultant behaviour under given parameters for a particular game. The vision for
-    this is to provide guarantees on the stability of a finite set of agents within a swarm, such as
-    leaders in a flock. Without this, it would be impossible to ensure the stability of a swarm in
-    which intelligent, social interactions must be accounted for. However, this analysis
-    would also allow for a characterisation of the conditions under which MARL algorithms may
-    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
-    payoff matrices and parameters accordingly.
-
-    This segment of research is currently underway and approaching completion. The analysis was
-    described in Section \ref{sec::Chaos_in_Q-Learning}.
-
-    \section{Large Population Dynamics} \label{sec::Large_Agent_Dynamics}
-
-    This segment of research aims to model the game dynamics of large populations of agents
-    learning through iterated games and mean-field Q-Learning. The aim is to provide similar
-    guarantees of stability as in the previous sections with the caveat that all agents in the
-    population can learn, rather than a finite subset.
-
-    One of the main results shown by Sanders et al. \cite{Sanders2018} is that as the number of
-    players in a game increases, the learning behaviour is more likely to be chaotic, regardless of
-    the choice of parameters. This is intuitive since a higher number of players would result in a
-    greater strategy space and more agents for any particular player to learn against and is
-    verified by their presented results as in Figure \ref{fig::GallaPrevalence} - the hotter
-    regions occupy a larger area as
-
-    \begin{figure}[h]
-    	\centering
-    	\includegraphics[width=0.6\textwidth]{Figures/GallaPrevalence}
-    	\caption{ \label{fig::GallaPrevalence} Results as produced in the supplementary material
-    	of Sanders et al \cite{Sanders2018}. The same items appear here as in Figure 
-    	\ref{fig::GallaPredictions}, except the value of p (number of players) increases moving
-    	from top left to bottom right. It is clear that the hotter region occupies a larger region
-    	of parameter space, indicating that as the bumber of players in the game increase, chaos
-    	becomes more prevalent.}
-    \end{figure}
-
-    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
-    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
-    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
-    cursory verification of this intuition. Here, the authors present an anaysis of the learning
-    dynamics for a large agent population (which they approximate as containing infinite agents)
-    where each agent is an independent Q-Learner using Boltzmann action selection. The
-    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
-    strong predictor of the overall strategy selection of the population. Indeed, rather than
-    examining the strategies of every agent in the population (which the authors approximate as
-    infinitely large), they model the evolution of a probability density function which, for each
-    action, defines the density of agents who retain a given Q-value for that action. This is
-    illustrated in Figure \ref{fig::LeungPredictions}.
-
-    \begin{figure}[h]
-    	\centering
-    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
-    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al. \cite{Hu2019}.
-    	Here, the solid and dotted lines represent the evolution of the expectation of Q-values of
-    	two actions across a population of 50 or 999 agents respectively who are trained on an
-    	iterated Stag Hunt game. The circled and crossed
-    	lines represent the dynamics of these Q-values as predicted by the system of equations
-    	derived in the paper. These are seen to closely match the results of the numerical
-    	experiments.}
-    \end{figure}
-
-   	As the authors point out, this is the first attempt at considering such a problem, and relies on
-	heavy assumptions. The strongest of these is placed on the game itself, which is always
-	assumed to be cooperative (in Sanders' terms, $\Gamma = 1$). We, therefore, propose extending
-	this model to accomodate an arbitrary choice of games.
-
-	The following are suggestions for approaching the estimation of large population dynamics.
-
-	\begin{itemize}
-		\item Estimate the population state through Random Finite Sets (RFS) and
-	apply the models from the previous study. The aim here is to determine a state
-	estimation for a swarm of unknown size through a random finite set by solving
-	an optimal estimation problem  (typically iterated through a Kalman Filter
-	\cite{Doerr2019}. As the swarm is treated probailistically, the theory can
-	accomodate an arbitrarily large system. Importantly, this may allow for the
-	results from the previous section to be leveraged towards an arbitrary
-	population.
-
-	\item Decompose a generic game into a weighted sum of a
-	competitive and a cooperative game. Treat these as two separate agents and
-	invoke the mean field approximation (MFA) so that any given agent is
-	effectively engaged in a three-player game where the strategy of the opponents
-	is the average strategy of the population. This leverages the existing results
-	on the dynamics of three body problems in game theory \cite{Nagarajan2018} in
-	a mixture of co-operative and competitive settings.
-	\end{itemize}
-
-	%\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}
-
-    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
-
-    Here we aim to study the interaction of a swarm of 'active particles' with a potential field. In
-    particular this field is to be generated by 'field particles'. A model predictive control 
-    (MPC) scheme
-    is to be devised to drive this system to desired configurations, with guarantees placed on
-    stability and satisfaction of input constraints. The sub-optimality of the control
-    scheme is to be studied.
-
-    As described in Chapter \ref{ch::Lit_Review}, the control of swarms has been examined through the
-    use of
-    mean field models. These models resolve the fact that it is impossible to view the entire system
-    as simply the sum of all of the agents and rather model the overall state of the system through
-    density functions. Controls are then applied to this function whose evolution is described
-    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
-    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
-    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
-    Roy2017}, though it makes the assumption that the system evolves through 'drifted
-    brownian motion'. This means that the agents are considered to move about independently and
-    randomly, though under the influence of a field which affects their velocity. This technique
-	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
-	manner \cite{Fleig}. The latter is beginning to show promise 
-	though control is typically through leadership rather than fields \cite{Burger2019}.
-
-	The hypothesis of this section is that the distribution of active particles, whose evolution is
-	described through a Vlasov equation, may be controlled through the influence of a scalar field
-	generated by 'field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
-	\cite{Bellomo2017}
-
-	\begin{equation}
-	\label{eqn::Vlasov}
-    \begin{split}    
-        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
-        = \epsilon Q(f, f) \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
-        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
-        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*, 
-    \end{split}
-    \end{equation}
-
-    Here, $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
-    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$ which represents the state of
-    the system. $\kappa \geq 0$ is a scalar
-    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
-    {v}^*$) gives the position in phase space of a 'field particle'. It can be seen that the these
-    field particles influence the velocity of the swarm agents.
-
-	The contribution that this study presents over those using brownian motion is the inclusion of an
-	interaction operator $Q(f, f)$. This governs how agents interact with one another. With this
-	term included, the dynamics account for the tendency of agents to avoid collisions. However,
-	the term is intended to account also for social interactions between agents, which we aim to
-	leverage in the subsequent section.
-
-	The complexity of this interaction term will need to be gradually increased over time. To begin
-	with, we may entirely neglect this term. It is here that we will compare the model proposed by Zhang
-	with that proposed by Bellomo et al. We may then consider only local interactions, which is typical
-	for most swarming systems in the current literature, before then considering non-local interactions.
-	This provides the scope for swarms to interact with a greater number of agents. At this stage, we
-	may expand our study to consider the presence of interaction domains. This places constraints on how
-	agents may interact with one another, allowing for a greater generalisation of inter-agent
-	interactions. Ultimately, we would like to influence the interaction term, though this is discussed
-	in Section \ref{sec::Intelligence_in_control}. The questions we will
-	consider here are:
-
-	\begin{itemize}
-		\item The stablity of the system: Under what conditions is it possible to drive the
-		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al.
-		present a candidate lyapunov functional upon which dissipation can be evaluated, though it
-		will need to be adapted for the consideration of the consensus models.
-		\item The guarantees of the system: Is it possible to ensure that controls remain within an
-		admissible set (typically a closed, bounded and convex set \cite{Fredi2010}).
-		\item Whether the conservation laws of normalisation and total mass, as presented in 
-		\cite{Bellomo2017} can be guaranteed.
-	\end{itemize}
-
-	These results will be established theoretically alongside the sub-optimality of the MPC scheme
-	and verified through numerical simulations in a 2D environment. It
-    will be of interest to perform a similar analysis to Ko and Zuazua \cite{Ko2019} in which the
-    cost functional is altered to favour particular metrics  (e.g. running cost, control time etc.)
-    and also analyse the effect of varying the time horizon.
-
-    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
-
-    This section of the study is perhaps the strongest extension proposed in this
-	chapter, and will likely be the most challenging. Here, we examine the dynamics (
-	\ref{eqn::Vlasov}) in which the interaction term accounts for the social dynamics of the
-	decision making of individual agents who have learnt through an iterated game. We leverage the
-	strategy evolution dynamics and stability analysis established in 
-	\ref{sec::Chaos_in_MARL} and \ref{sec::Large_Agent_Dynamics}.
-
-	Two proposals for incorporation of social interaction:
-	\begin{itemize}
-		\item Addition of the agent decisions as a constant in the state $f$. This will require that
-		the decisions remain fixed in the state and so it will be required to make sure that the
-		controls have no influence on this element.
-		\item Weighted summation term in the probability of an agent changing its velocity from
-		$v_*$ to
-		$v$ due to a field particle with velocity $v^*$ $A[f](v_* \rightarrow v | v_*, v^*)$.
-		Here, weights are equal to the agent strategy. This extends to both the swarms in
-		which the leaders are making decisions (only leaders have this term) as well as in
-		swarms where the population makes decisions (everyone has this term). This will need to be
-		done with care though to ensure that normalisation holds. Note that, as this a probabilistic
-		approach, we will need to examine the stochastic behaviour of the system and the extent to
-		which constraint and conservation satisfaction can be guaranteed.
-	\end{itemize}
-
-	The MPC scheme from the previous section will then be adapted to this dynamical system with the
-	same questions of well-posedness and stability considered.
-
-	A possible extension of this would be to consider online learning by incorporating the time
-	evolution of the strategy space within the social interaction term, which would now be
-	time-varying. The proper integration of these dynamical systems would depend on the form of the
-	systems derived in Section \ref{sec::Large_Agent_Dynamics} and it is likely that relaxations would
-	be required in terms of controllability results. An example would be to examine only the
-	behaviour in the long-enough time frame, which means that we could not impose a final time. Of
-	course, this means that we could only consider optimal control rather than model predictive.
-	However, without establishing the models from Section \ref{sec::Large_Agent_Dynamics}, this
-	extension is speculative and it is likely that such an extension would fall outside the scope of
-	the PhD.
-
-	%\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
-	%the conservation laws}
+    The remainder of this report analyses each of these topics in turn, providing
+    motivation and suggestions for the course of research. The first of these `Stability and
+    Chaos in MARL' is currently being studied and so is given its own Chapter (Chapter 
+    \ref{ch::ShortTermGoals}) which includes a summary of the research.
 

### 2020-06-26 Documents/ESA/sections/LitReview.tex
Restructuring of ESA

@@
 
+\textbf{TODO: Mention the parts of literature which we are not considering and explain why: Recent
+MARL techniques (including MDRL), Marco Dorigo's work on Swarms. Add in the Learning in Stochastic
+Games literature from Schwartz et al. Explain the concepts in Control Theory and how MPC works. Add
+in suggestions for applications and papers supporting said applications.}
+
 In this chapter, we explore the current state of the art in
 Multi-Agent Systems (MAS). We will consider the main techniques that
-have been proposed towards task allocation and control.
+have been proposed towards task allocation and control. In this review we cover
 
-\fr{you might provide an overview of the introduction with the
-  different sections.}
+\begin{enumerate}
+    \item Game Theory: The most well studied model for solving multi-agent decision making problems.
+    \item Multi-Agent Reinforcement Learning (MARL): A contemporary technique which requires that
+    agents learn and adopt their own strategies.
+    \item Control Theory: Methods focusing on low-level manipulation of a system (e.g. the position
+    and velocity of an agent) which aims to provide guarantees on its behaviour.
+    \item Swarms: Systems whose success are founded on the emergent phenomena exhibited by large
+    populations of interacting entities.
+\end{enumerate}
+
+There are, of course, a number of techniques which we do not discuss here, as they are not relevant
+to the proposals in this report. Most notable is that of Decentralised Partially Observable Markov
+Decision Processes (Dec-POMDPs) which is a multi-agent extension of the MDP framework in which
+agents aim to maximise a common reward (or utility) function. This method does not scale to large
+populations and so is not considered relevant to our study. The interested reader should consult
+\cite{OliehoekDecentralizedPOMDPs} for an excellent introduction to Dec-POMDPs.
 
 \section{Multi Agent Systems} \label{sec::Multi_Agent_Systems}
-
-\fr{I wonder whether this section would fit better in Intro.}
 
@@
 take. In either case, optimality is defined through the standard
-notions of Nash equilibria and so, in this section, I will try to
+notions of Nash equilibria and so, in this section we
 consider the broad spectrum of methods which attempt to achieve
-Nash equilibria. The largest problem in MARL is the non-stationarity
+Nash equilibria.
+
+The largest problem in MARL is the non-stationarity
 of the environment \cite{Hernandez-LealA}. In single-agent settings,
@@
 
-This chapter begins with a selection of the foundational methods which
+This section begins with a selection of the foundational methods which
 were developed towards solving the MARL problem. The interested reader
@@
 choose a convergence rate of the step size and, without an appropriate
-choice the strategy may oscillate as shown in the book \fr{please add ref}. To address
+choice the strategy may oscillate as shown in the book \cite{SchwartzMulti-agentApproach}. To
+address
 this, a modified approach is presented by Bowling and Veloso which
@@
 equilibrium strategies by playing the game, which means they do not
-have a priori knowledge of the reward or transition functions. Schwarz
-considers \fr{where?} two properties which should be used for evaluating MARL
+have a priori knowledge of the reward or transition functions. Schwarz \cite{SchwartzMulti-agentApproach}
+considers two properties which should be used for evaluating MARL
 algorithm: rationality and convergence. The latter simply states that
@@
 opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
-shortly. Schwarz then presents a review of MARL methods (as of
-September 2014)
+Sandholm in \cite{ConitzerAWESOME:}. Schwarz then presents a review of MARL methods (as of
+September 2014).
 
@@
 direction when encountering an obstacle. It is here that the mean-field models are not as strong
-since they do not take these local interactions into account. It must be noted, however, that the authors have identified this problem and are currently working towards its incorporation into the
-model.
+since they do not take these local interactions into account. It must be noted, however, that the
+authors of \cite{Inoue2019} have identified this problem and are currently working towards its
+incorporation into the model.
 
@@
 \section{Discussion} \label{sec:remarks}
-
-\fr{I really liked this section.}
 
@@
 
-\fr{\textbf{what about some use cases/application scenarios.}}
-
 \end{document}

### 2020-06-26 Documents/ESA/sections/ProposedResearch.tex
Restructuring of ESA

@@
 
-	This chapter describes a proposed line of research which aims
-        to study the evolution of swarm systems with independent,
-        learning agents under the influence of predictive controls. We
-        detail the novel lines of research which this work aims to
-        undertake, providing suggestions of the hypotheses posed by
-        these lines. With this in mind the following studies are
-        proposed and developed subsequently:
-
-	\begin{itemize}
-		\item \textbf{Stability and Chaos in MARL:} in which
-                  we seek to understand the dynamics of agent
-                  strategies when using Q-Learning to learn a game
-                  through iteration. We will establish the stability,
-                  as a function of parameters, when learning general
-                  p-player N-action games.  This study enables the
-                  appropriate selection of parameters and payoff
-                  matrices to ensure the stability of the strategies
-                  of a finite set of agents, such as leaders in a
-                  swarm.
-
-                  \fr{this is already attempted in the current
-                    research section, isn't it?}
-
-              \item \textbf{Dynamics of Mean-Field Q-Learning Games:} in which we examine the
-		strategy dynamics for large populations of agents learning through iterated games and
-		mean-field Q-Learning. We seek to understand the long term behaviour of such mean-field
-		systems in terms of its strategy selection. This study extends the previous and allows for
-		the stability of the strategies of a population of agents to be established.
-		\item \textbf{Model Predictive Control of Active Particles through Fields:} in which we
-		investigate the interaction of a swarm of active particles with potential fields. We
-		establish the stabilisability of an MPC scheme with defined stage costs, as well as an
-		analysis of the suboptimality of the method.
-		\item \textbf{Incorporation of Intelligence in Control:} in which we adapt the dynamical
-		system from the above point to include an interaction term, accounting for strategy
-		selection by agents who learn through iterated games against one another. Interactions with
-		an MPC scheme is then to be examined in a similar capacity.
-
-	\end{itemize}
-
-	The remainder of this chapter analyses each of these topics in turn, providing suggestions for
-	the course of research.
-        \fr{we analyze each topic in a section \ldots}
+    This chapter continues to describe the proposed research outined in Chapter 
+    \ref{ch::IntrotoProposals}. These proposals are to be addressed following the completion of the
+    research in Chapter \ref{ch::ShortTermGoals}.
 
 	% \textbf{TODO: Ensure all references here are in the Lit Review}
-
-    \section{Stability and Chaos in MARL} \label{sec::Chaos_in_MARL}
-
-    This segment of research is aimed towards a deeper understanding
-    of the strategy evolution of agents following a Q-Learning
-    approach. This allows for guarantees to be placed on the behaviour
-    of such agents, in particular the conditions under which the game
-    will converge to a stable equilibrium.
-
-    It has long been established that, upon lifting the strong
-    assumptions made by traditional game theory (such as the
-    rationality of agents and complete information), that player
-    strategies can result in much more complex behaviour than
-    convergence to a Nash Equilibrium (NE). In fact, this is even true
-    on what would commonly be regarded as 'simple' games such as
-    tic-tac-toe and prisoner's dilemma \cite{Galla2011,
-      Sato2002}. These behaviours include: convergence to a unique
-    equilibrium (though not always to an NE), convergence to one of
-    multiple equilibria, limit cycles and chaos. These behaviours are
-    shown in Figure \ref{fig::DynamicalBehaviours} Of these, the most
-    preferable is, of course, convergence to a unique equilibrium,
-    although it is still possible to study systems with multiple
-    equilibria or limit cycles \cite{Strogatz2000}. However, it would
-    be difficult to control systems whose dynamics are governed by
-    chaos (though research into controlling chaos is ongoing and rife
-    with opportunity \cite{Fradkov2009}) and so MARL techniques should
-    avoid this. It would, therefore, be a useful endeavour to
-    determine the conditions under which these sorts of behaviours
-    arise.
-
-    \begin{figure}[h]
-    	\centering
-    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
-    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
-       displayed
-    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
-    	Convergence
-    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
-    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
-    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
-    	exponentially. b-d drawn from \cite{Sanders2018}}
-    \end{figure}
-
-    The behaviour of a system may be studied given a model of its
-    dynamics. It is through this process that a wide array of physical
-    systems, from harmonic pendulums to geophysical fluids, can be
-    understood. A growing body of research aims to understand
-    multi-agent reinforcement learning through the lens of its
-    dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames} were
-    able to derive a model of the strategy evolution of agents
-    learning through iterated games.  Through this, they were able to
-    arrive at the following model of Multi-Agent Q-Learning
-
-	\begin{subequations}
-	\label{eqn::EOM}
-		\begin{equation}
-			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
-			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
-		\end{equation}
-		\begin{equation}
-			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
-			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
-		\end{equation}
-	\end{subequations}
-
-\fr{I understand the equations are the same as in the previous section. I suggest we move the explanation there and remove it from here.}
-
-	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
-	memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
-	$x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
-	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-	predict the expected behaviour of Q-Learning agents, as shown in Figure 
-	\ref{fig::TuylsExperiments}.
-
-	\begin{figure}[h]
-		\centering
-		\begin{subfigure}[b]{0.9 \textwidth}
-			\centering
-			\includegraphics[width=0.75 \textwidth]{Figures/Dynamics}
-			\caption{}
-		\end{subfigure}
-
-		\begin{subfigure}[b]{0.9 \textwidth}
-			\centering
-			\includegraphics[width=0.7 \textwidth]{Figures/Q-Learners}
-			\caption{}
-		\end{subfigure}
-
-		\caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
-		plot showing the expected behaviour of Q-Learning agents trained by iterating the
-		Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
-		have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
-		randomised initial conditions displayed through numerical simulation. It is clear that the
-		trajectories in b) follow the predictions in a), after stochasticity is accounted for. }
-	\end{figure}
-
-	It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments} that the long-term strategy selection of
-	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
-	then pose the question: how do these elements influence the types of behaviours seen during
-	learning on an iterated game? In other words, under what parameter selections are we likely to
-	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?
-
-	With this in mind, the intention of this area of study is to consider the analysis presented in
-	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
-	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
-	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
-	determine the regions of parameter space in which complex behaviour,
-	including cycles and chaos, predominantly occur and those in which a given game converges to a
-	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
-	illustrates the successful derivation of a `phase line', across which learning shifts from
-	convergent to chaotic.
-
-    \begin{figure}[h]
-    	\centering
-    	\includegraphics[width=0.6\textwidth]{Figures/GallaPredictions}
-    	\caption{ \label{fig::GallaPredictions} Results as produced in the supplementary material
-    	of Sanders et al \cite{Sanders2018}. Here, $p$ is the number of players, $N$ is the number
-    	of actions, $\Gamma$ represents the competitiveness of the game (-1 represents zero-sum, 1
-    	represents shared rewards) and $\alpha$ is the memory parameter of the agent as before.
-    	Here $\tau$ is held constant at 0.05 (though it is referred to as $\beta$ in the paper).
-    	The black region represents where games converged to a fixed point through all simulations,
-    	whilst the hotter regions represent the more complex dynamics - red shows the presence of
-    	limit cycles and white regions signal the onset of chaos. The green line is a theoretical
-    	estimation for the phase line which separates the convergent dynamics from complex.}
-    \end{figure}
-
-    We propose to bridge the analysis presented by Sanders
-    et al. and Galla et al. towards games learnt using MARL, particularly Q-Learning with
-    Boltzmann exploration as considered by Tuyls et al. This would allow for a characterisation of
-    the expected resultant behaviour under given parameters for a particular game. The vision for
-    this is to provide guarantees on the stability of a finite set of agents within a swarm, such as
-    leaders in a flock. Without this, it would be impossible to ensure the stability of a swarm in
-    which intelligent, social interactions must be accounted for. However, this analysis
-    would also allow for a characterisation of the conditions under which MARL algorithms may
-    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
-    payoff matrices and parameters accordingly.
-
-    This segment of research is currently underway and approaching completion. The analysis was
-    described in Section \ref{sec::Chaos_in_Q-Learning}.
-
-    \fr{I would move all of the above to the previous section.}
 
@@
     presented results as in Figure \ref{fig::GallaPrevalence} - the
-    hotter regions occupy a larger area as \fr{?}
+    hotter regions occupy a larger area as $p$ increases.
 
@@
     Yet it can be argued that, for large populations of agents (e.g.,
-    a crowd), the aggregate behaviour may be predictable \fr{provide some justification to this claim?}. This
+    a crowd), the aggregate behaviour may be predictable, since the individual effect on the overall
+    population is negligible \cite{Elamvazhuthi2019b}. This
     intuition is the foundation upon which crowd dynamics and flocking
     systems are based. In fact, the work presented by Leung et
-    al.~\cite{Hu2019} provides a cursory verification of this
+    al. \cite{Hu2019} provides a cursory verification of this
     intuition. Here, the authors present an analysis of the learning
@@
     system of equations, governed by a Fokker-Planck model which is
-    numerical shown to be a strong predictor of the overall strategy
+    numerically shown to be a strong predictor of the overall strategy
     selection of the population. Indeed, rather than examining the
@@
 	an optimal estimation problem  (typically iterated through a Kalman Filter
-	\cite{Doerr2019}. As the swarm is treated probailistically, the theory can
+	\cite{Doerr2019}. As the swarm is treated probabilistically, the theory can
 	accomodate an arbitrarily large system. Importantly, this may allow for the
@@
 
-    Here we aim to study the interaction of a swarm of 'active particles' with a potential field. In
-    particular this field is to be generated by 'field particles'. A model predictive control 
+    Here we aim to study the interaction of a swarm of `active particles' with a potential field.
+    In
+    particular this field is to be generated by `field particles'. A Model Predictive Control 
     (MPC) scheme
@@
     some success in recent literature \cite{Elamvazhuthi2019, Li2017,
-    Roy2017}, though it makes the assumption that the system evolves through 'drifted
-    brownian motion'. This means that the agents are considered to move about independently and
+    Roy2017}, though it makes the assumption that the system evolves through `drifted
+    brownian motion'. This means that the agents are considered to move independently and
     randomly, though under the influence of a field which affects their velocity. This technique
@@
 	described through a Vlasov equation, may be controlled through the influence of a scalar field
-	generated by 'field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
+	generated by `field paricles'. This is drawn from the dynamics posed by Bellomo et al. 
 	\cite{Bellomo2017}
@@
     coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
-    {v}^*$) gives the position in phase space of a 'field particle'. It can be seen that the these
+    {v}^*$) gives the position in phase space of a `field particle'. It can be seen that the these
     field particles influence the velocity of the swarm agents.
@@
     iterated game. We leverage the strategy evolution dynamics and
-    stability analysis established in \ref{sec::Chaos_in_MARL} and
+    stability analysis established in \ref{ch::ShortTermGoals} and
     \ref{sec::Large_Agent_Dynamics}.

### 2020-06-26 Documents/ESA/sections/ResearchSummary.tex
Updated ESA
Restructuring of ESA

@@
 	\begin{subequations}
-	\label{eqn::EOM}
+	\label{eqn::appEOM}
 		\begin{equation}
@@
 
-	\subsection{Rescaling of Variables} % (fold)
-	\label{sub:rescaling_of_variables}
+	\section{Rescaling of Variables} % (fold)
+	\label{sub:apprescaling_of_variables}
 
@@
 	\begin{subequations}
-	\label{eqn::scaledEOM}
+	\label{eqn::appscaledEOM}
 		\begin{equation}
@@
 
-	\subsection{Generating Functional} % (fold)
-	\label{sub:generating_functional}
+	\section{Generating Functional} % (fold)
+	\label{sub:appgenerating_functional}
 
 	The generating functional allows us to take a path integral over all possible realisations of
-	learning \cite{SpinGlassTheory}. This is given as:
+	learning \cite{Mezard1986}. This is given as:
 
@@
 	where the equations of motion are the Lagrange equations of motion given in (
-	\ref{eqn::scaledEOM}) andSince
+	\ref{eqn::appscaledEOM}) and
 	the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
@@
 		\begin{split}
-	\label{eqn::generatingfunctional}
+	\label{eqn::appgeneratingfunctional}
 		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i \sum_i \int dt[\hat{x}_i
@@
 	\begin{split}
-	\label{eqn::moveddisorder}
+	\label{eqn::appmoveddisorder}
 		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
@@
 	\end{equation}
-	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
+	The only difference between (\ref{eqn::appgeneratingfunctional}) and (\ref{eqn::appmoveddisorder}) is
 	that we moved the term containing the quenched disorder into a separate exponential. Since our
@@
 	\begin{equation}
-	\label{eqn::expectationIdentity}
+	\label{eqn::appexpectationIdentity}
 		\int dz [e^{-A_2(z) + \Vec{b} \cdot \Vec{z}}] = (2 \pi)^{k/2} (det(A))^{-1/2} e^{\omega(b)},
@@
 
-	\subsubsection{Expectation of $Q_1$} % (fold)
-	\label{ssub:expectation_of_Q1}
+	\subsection{Expectation of $Q_1$} % (fold)
+	\label{ssub:appexpectation_of_Q1}
 
@@
 
-	Applying identity (\ref{eqn::expectationIdentity}) gives:
+	Applying identity (\ref{eqn::appexpectationIdentity}) gives:
 
@@
 
-	\subsubsection{Expectation of $Q_2$} % (fold)
-	\label{ssub:expectation_of_Q2}
+	\subsection{Expectation of $Q_2$} % (fold)
+	\label{ssub:appexpectation_of_Q2}
 
@@
 effective generating functional (and in fact we see that it has a similar structure to (
-\ref{sub:generating_functional}), without the existence of the fields $\psi, \phi$). In particular
+\ref{sub:appgenerating_functional}), without the existence of the fields $\psi, \phi$). In particular
 we recognise this as the generating functional of the 'effective dynamics' given as
@@
 \section{Stability Analysis} % (fold)
-\label{sec:stability_analysis}
+\label{sec:appstability_analysis}
 
@@
 determine the stability of the system at fixed points. We will follow the procedure laid out by
-Opper et al \cite{Opper}. First, we rewrite $x(t)$, $y(t)$ as perturbations about their fixed
+Opper et al \cite{Opper1992}. First, we rewrite $x(t)$, $y(t)$ as perturbations about their fixed
 points. We will then analyse the stability of these fixed points.
@@
 \begin{equation} 
-	\label{eqn::Linearisation}
+	\label{eqn::appLinearisation}
 	\begin{split}
@@
 We continue to follow the method of Opper et al.
-by taking the Fourier transform of (\ref{eqn::Linearisation}).
+by taking the Fourier transform of (\ref{eqn::appLinearisation}).
 For both agents, the first term in square brackets is constant with respect to time and so will not affect the long term behaviour of the system.
@@
 
-\begin{equation} \label{eqn::Transformed}
+\begin{equation} \label{eqn::appTransformed}
 	\left<[|\mathcal{X}(\omega)|^2 \right> = \left< | \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega) |^2 \right> \frac{1}{\left< |\mathcal{A}(\omega, x^*) |^2 \right>},
@@
 \section{Numerical Simulations} % (fold)
-\label{sec:numerical_simulations}
+\label{sec:appnumerical_simulations}
 
@@
 	\centering
-	\includegraphics[width = 0.7 \textwidth]{Figures/tau_005.png}
-	\caption{$\tau = 0.0$}
+	\includegraphics[width = 0.7 \textwidth]{Figures/AlphaRun_tau_005.png}
+	\caption{$\tau = 0.05$}
 	\end{subfigure}
@@
 	and initial conditions. The average number of converged games (giving an indication of
-	probability of convergence) is shown in each cell of the heatmap. \label{fig::Toys}}
+	probability of convergence) is shown in each cell of the heatmap. \label{fig::appToys}}
 \end{figure}
 
-To generate the numerical simulations in Figure \ref{fig::Toys} we used the following procedure.
+To generate the numerical simulations in Figure \ref{fig::appToys} we used the following procedure.
 
@@
 	it does not affect the long term behaviour of the system (it does not appear in (
-	\ref{eqn::EOM})).
+	\ref{eqn::appEOM})).
 	\item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep

### 2020-06-26 Documents/ESA/sections/ShortTermGoals.tex
Restructuring of ESA

@@
 
+    This segment of research aims to achieve a deeper understanding
+    of the strategy evolution of agents following a Q-Learning
+    approach. This allows for guarantees to be placed on the behaviour
+    of such agents, in particular the conditions under which the game
+    will converge to a stable equilibrium.
+
+    It has long been established that, upon lifting the strong
+    assumptions made by traditional game theory (such as the
+    rationality of agents and complete information), that player
+    strategies can result in much more complex behaviour than
+    convergence to a Nash Equilibrium (NE). In fact, this is even true
+    on what would commonly be regarded as 'simple' games such as
+    tic-tac-toe and prisoner's dilemma \cite{Galla2011,
+      Sato2002}. These behaviours include: convergence to a unique
+    equilibrium (though not always to an NE), convergence to one of
+    multiple equilibria, limit cycles and chaos. These behaviours are
+    shown in Figure \ref{fig::DynamicalBehaviours}. Of these, the most
+    preferable is, of course, convergence to a unique equilibrium,
+    although it is still possible to study systems with multiple
+    equilibria or limit cycles \cite{Strogatz2000}. However, it would
+    be difficult to control systems whose dynamics are governed by
+    chaos (though research into controlling chaos is ongoing and rife
+    with opportunity \cite{Fradkov2009}) and so MARL techniques should
+    avoid this. It would, therefore, be a useful endeavour to
+    determine the conditions under which these sorts of behaviours
+    arise.
+
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
+        \caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
+       displayed
+        by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
+        Convergence
+        to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
+        that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
+        d) Chaotic behaviour, here small deviatons in the initial conditions can grow
+        exponentially. b-d drawn from \cite{Sanders2018}}
+    \end{figure}
+
+    The behaviour of a system may be studied given a model of its
+    dynamics. It is through this process that a wide array of physical
+    systems, from harmonic pendulums to geophysical fluids, can be
+    understood. A growing body of research aims to understand
+    multi-agent reinforcement learning through the lens of its
+    dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames} were
+    able to derive a model of the strategy evolution of agents
+    learning through iterated games.  Through this, they were able to
+    arrive at the following model of Multi-Agent Q-Learning
+
+    \begin{subequations}
+    \label{eqn::EOM}
+        \begin{equation}
+            \frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
+            + \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
+        \end{equation}
+        \begin{equation}
+            \frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
+            + \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
+        \end{equation}
+    \end{subequations}
+
+    Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
+    memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
+    $x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
+    receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
+    predict the expected behaviour of Q-Learning agents, as shown in Figure 
+    \ref{fig::TuylsExperiments}.
+
+    \begin{figure}[h]
+        \centering
+        \begin{subfigure}[b]{0.9 \textwidth}
+            \centering
+            \includegraphics[width=0.75 \textwidth]{Figures/Dynamics}
+            \caption{}
+        \end{subfigure}
+
+        \begin{subfigure}[b]{0.9 \textwidth}
+            \centering
+            \includegraphics[width=0.7 \textwidth]{Figures/Q-Learners}
+            \caption{}
+        \end{subfigure}
+
+        \caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
+        plot showing the expected behaviour of Q-Learning agents trained by iterating the
+        Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
+        have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
+        randomised initial conditions displayed through numerical simulation. It is clear that the
+        trajectories in b) follow the predictions in a), after stochasticity is accounted for. }
+    \end{figure}
+
+    It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments}, that the long-term strategy selection of
+    these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
+    then pose the question: how do these elements influence the types of behaviours seen during
+    learning on an iterated game? In other words, under what parameter selections are we likely to
+    see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?
+
+    With this in mind, the intention of this area of study is to consider the analysis presented in
+    works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
+    Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
+    learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
+    determine the regions of parameter space in which complex behaviour,
+    including cycles and chaos, predominantly occur and those in which a given game converges to a
+    stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
+    illustrates the successful derivation of a `phase line', across which learning shifts from
+    convergent to chaotic.
+
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{Figures/GallaPredictions}
+        \caption{ \label{fig::GallaPredictions} Results as produced in the supplementary material
+        of Sanders et al \cite{Sanders2018}. Here, $p$ is the number of players, $N$ is the number
+        of actions, $\Gamma$ represents the competitiveness of the game (-1 represents zero-sum, 1
+        represents shared rewards) and $\alpha$ is the memory parameter of the agent as before.
+        Here $\tau$ is held constant at 0.05 (though it is referred to as $\beta$ in the paper).
+        The black region represents where games converged to a fixed point through all simulations,
+        whilst the hotter regions represent the more complex dynamics - red shows the presence of
+        limit cycles and white regions signal the onset of chaos. The green line is a theoretical
+        estimation for the phase line which separates the convergent dynamics from complex.}
+    \end{figure}
+
+    We propose to bridge the analysis presented by Sanders
+    et al. and Galla et al. towards games learnt using MARL, particularly Q-Learning with
+    Boltzmann exploration as considered by Tuyls et al. This would allow for a characterisation of
+    the expected resultant behaviour under given parameters for a particular game. The vision for
+    this is to provide guarantees on the stability of a finite set of agents within a swarm, such as
+    leaders in a flock. Without this, it would be impossible to ensure the stability of a swarm in
+    which intelligent, social interactions must be accounted for. In addition, this analysis
+    would allow for a characterisation of the conditions under which MARL algorithms may
+    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
+    payoff matrices and parameters accordingly.
+
+\section{Summary of Research}
+
     In this chapter, we summarise and present the research and results
     which have been obtained thus far. These tackle the problems
-    described in Section \ref{sec::Chaos_in_MARL}. We detail the
+    described thus far in this chapter. We summarise the
     derivation of a stability phase line as presented in Sanders et
-    al.~\cite{Sanders2018} as well as the numerical simulations
-    performed to verify these results. The steps to be completed
-    subseqent to this study are then given.
-
-\fr{perhaps we can provide a bit more of context. Also, we can refer to the appendix for the details of the derivation and mention that we are aiming for a submission to AAAI.}
+    al. \cite{Sanders2018} as well as the numerical simulations
+    performed to verify these results. These details of the derivation are provided in Appendix 
+    \ref{app::ResearchSummary}. The steps to be completed
+    subseqent to this study are then given. Note that the results in the section form the basis of a
+    tentative submission to AAAI 2021.
 
@@
     characterising the stability of agents learning strategies. This
-    technique is carried out by Sanders et al.~\cite{Sanders2018}, in
+    technique is carried out by Sanders et al. \cite{Sanders2018}, in
     which the authors characterise the strategy evolution of agents
     who learn using an 'Experience Weighted Attraction' (EWA)
-    algorithm \cite{?}, which is seen to be a strong \fr{why?} representation of how
-    people learn in games. The authors are able to determine the
+    algorithm, which has been shown to be a strong representation of how
+    people learn in games \cite{Camerer1999, Camerer2003}. The authors are able to determine the
     regions of parameter space in which learning is likely to converge
-    towards stable equilibriums, as opposed to complex behaviours
+    towards stable equilibria, as opposed to complex behaviours
     (such as limit cycles or chaotic dynamics). The aim of this study
@@
 
-     \subsection{Derivation of stability line} % (fold)
-     \label{sub:derivation_of_stability_line}
+    \subsection{Dynamics of Q-Learning} % (fold)
+    \label{sub:dynamics_of_q_learning}
 
-     We begin with the equations as described by Tuyls et al \cite{Tuyls2006AnGames} \fr{describing \ldots}
+    We begin with the popular Q-Learning algorithm in which each agent keeps a record of a `Q-Value'
+    for each action, which is its own estimation of the performance of said action. This estimation
+    is based on the expected reward that the agent will receive if it were to choose this action. In
+    a multi-agent game setting, the reward that an agent receives will be drawn from a payoff
+    matrix and will depend on the behaviour of the other players. Taking this into consideration,
+    an agent updates their Q-Value of action $i$ with the equation
+
+    \begin{equation}
+    \label{eq::Q-Learning}
+    Q_{t+1}(a_i) = (1 - \alpha) Q_t(a_i) + \alpha (\sum_j a_{ij} y_{j} + \gamma max_{a_j}Q_t(a_j)).
+    \end{equation}
+
+    Here, $\alpha \in [0, 1]$ is a parameter of the agent which is considered the {\em memory} of
+    the agent. For low values of $\alpha$, the agent places a higher weight on their pre-existing
+    choice for $Q_t(a)$, and so is considered to have a longer memory, whereas for higher values of
+    $\alpha$, the agent has a higher propensity to disregard previous estimations in favour of new
+    information. Note that the term $\sum_{j} a_{ij} y_j$ denotes the expected reward that the agent
+    will receive for selecting action $i$, drawn from its payoff matrix $A$, given the probabilities
+    that its opponent chooses any action $j$. At each iteration of the game, our agent selects an
+    action to play randomly with probabilities given by
+
+    \begin{equation}
+    \label{eq::actionselection}
+    x_{i} = \frac{e^{\tau Q_t(a_i)}}{\sum_j e^{\tau Q_t(a_j)}}.
+    \end{equation}
+
+    This introductes a new parameter, $\tau \in [0, \infty)$, which is considered the {\em intensity
+    of choice} by Sanders et al. \cite{Sanders2018}. When $\tau$ is close to zero, each action $i$
+    is played with the same probability, regardless of its Q-value. However, for large values of
+    $\tau$, the action with the highest Q-value dominates all others and is played with a large
+    probability at each step. The value of $\tau$, then, denotes an agent's propensity to explore
+    its strategy space. Note that in this derivation, as in \cite{Tuyls2006AnGames}, the
+    action probabilities of one agent are denoted with $x$ and those of its opponent are denoted
+    with $y$. The payoffs received by these agents are given by $a_{ij}$ and $b_{ij}$ respectively.
+
+    Tuyls et al. use this Q-Learning formulation to determine the time evolution of $x$ and $y$.
+    Given a continuous time approximation of this behaviour, they arrive at the equation 
+    \ref{eqn::EOM} which is repeated below for convenience.
 
      \begin{subequations}
-    \label{eqn::EOM}
         \begin{equation}
@@
 
-    Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders
-    et al. refer to these as the {\em memory} and {\em intensity of choice}
-    parameters respectively. Agent 1 takes action $i$ with probability
-    $x_i$ while Agent 2 takes action $j$ with probability $y_j$. If
-    these actions are taken, the agents receive payoff $a_{ij}$ and
-    $b_{ji}$ respectively.
+    We now seek to analyse the stability of these dynamics based on the payoff values and agent
+    parameters ($\alpha, \tau$).
+    % subsection dynamics_of_q_learning (end)
 
-    Our goal is to analyse the dynamics of any game, regardless of
-    payoff structure. As such, we follow the approach of Sanders et
-    al. in deriving the full set of 'effective dynamics' averaged over
-    all possible realisations of the payoff matrices. Note that these
-    elements are drawn from a Multivariate Gaussian such that
+     \subsection{Derivation of stability line} % (fold)
+     \label{sub:derivation_of_stability_line}
+
+    The dynamics given by Tuyls et al. describe the time evolution of agent
+    strategies for a given choice of $a_{ij}, b_{ij}$. However, our goal is to
+    analyse the dynamics of any game, regardless of payoff elements. As such,
+    we follow the approach of Sanders et al. in deriving the full set of
+    'effective dynamics' averaged over all possible realisations of the payoff
+    matrices. We consider that these elements are drawn from a Multivariate Gaussian
+    such that
+
     \begin{equation*}
@@
     \end{equation*}
+
     where $\Gamma$ is a parameter which defines the `competitiveness' of the game. For a two player
     game, $\Gamma \in [-1, 1]$ where -1 denotes a zero-sum game and 1 denotes a game with positive
-    correlation across payoff elements. Taking this average \fr{some more details?} yields
+    correlation across payoff elements. Taking this average (details given in Appendix 
+    \ref{app::ResearchSummary}) yields
 %
@@
     Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
-    and the notation $\tilde{\cdot}$ denotes a term which has been scaled with respect to $N$ (see
-    Appendix \ref{app::ResearchSummary} for method and notation). We now analyse the stability of
-    this dynamical system by linearising about a fixed point. This yields the requirement that a
-    fixed point $x^*$ satisfy
+    and the notation $\tilde{\cdot}$ denotes a term which has been scaled with respect to $N$ 
+    (again, see Appendix \ref{app::ResearchSummary} for method and notation). We now analyse the
+    stability of this dynamical system by linearising about a fixed point. This yields the
+    requirement that a fixed point $x^*$ satisfy
 
     \begin{equation}
-    0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x \right].
+    0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^*
+    + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} 
+    \tilde{\alpha} \tau \mu_x \right],
     \end{equation}
 
-    The implication here is that the resulting value of $x^*$ can take two solutions. However, one
-    of these is $x^* = 0$, which is found to rarely occur \cite{Coolen2005}, while the second solution
-    contains a term $\sqrt{\Gamma}$, which would yield complex values. Such a result, of course, is
-    not possible for a quantity denoting probabilities and so it appears that the theory cannot hold
-    for $\Gamma < 0$. However, numerical experiments will shed light on the likelihood of
-    convergence and the islands of stability in parameter space for this region.
+    and similary for y. The reader should be aware that, for the sake of brevity, only the equations
+    for $x$ are presented henceforth as those for $y$ are equivalent.
+
+    The implication here is that the resulting value of $x^*$ can take two
+    solutions. However, one of these is $x^* = 0$, which is found to rarely
+    occur \cite{Coolen2005} and we do not consider, while the second,
+    non-trivial solution contains a term $\sqrt{\Gamma}$, which would yield
+    complex values. Such a result, of course, is not possible for a quantity
+    denoting probabilities and so it appears that the theory cannot hold for
+    $\Gamma < 0$. However, numerical experiments will shed light on the
+    likelihood of convergence and the islands of stability in parameter space
+    for this region.
 
@@
         \caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
-        simulation is run for 1e5 iterations and tested for convergence. The game is said to have
+        simulation is run for 1 $\times 10^5$ iterations and tested for convergence. The game is
+        said to have
         converged based on a tolerance of 1\% difference between action probabilities. For each
@@
     the evolution of learning of a population of Q-Learning agents who
-    play co-operative games against one another. This last point is an
-    important limitation - the derived dynamics will only consider
-    populations who must co-operate with one another (i.e., the
-    $\Gamma$ value of the game is 1).
+    play co-operative games against one another. This is discussed further in the subsequent chapter
+    on proposed research.
 

### 2020-06-29 Documents/ESA/sections/Intro.tex
Updated Literature Review and Introduction

@@
     researchers have gained a stronger understanding of how a swarm
-    may be controlled to achieve desired results.
+    may be controlled to achieve desired results and have shown its capabilites in a wide array of
+    domains \cite{Sahin2005}.
 
@@
     placed on the safety of such systems in terms of their stability and
-    constraint satisfaction. In doing so, we can ensure that a user can have
-    confidence in the decision making and manipulation of the system.
+    constraint satisfaction. If it is possible to determine, a priori, the decision making
+    behaviour of a population through its learning dynamics in terms of known quantities (e.g. the
+    agent parameters), then the system may be considered safe. Similarly, if it can be shown
+    to be robust, and satisfy desired constraints (e.g. controls lying within desired limits), then
+    we may be assured of its long-term safety. In doing so, we can ensure
+    that a user can have confidence in the system's decision making and manipulation.
 

### 2020-06-29 Documents/ESA/sections/LitReview.tex
Updated Literature Review and Introduction

@@
 \begin{document}
-
-\textbf{TODO: Mention the parts of literature which we are not considering and explain why: Recent
-MARL techniques (including MDRL), Marco Dorigo's work on Swarms. Add in the Learning in Stochastic
-Games literature from Schwartz et al. Explain the concepts in Control Theory and how MPC works. Add
-in suggestions for applications and papers supporting said applications.}
 
@@
 controllers which guarantee properties of stability and constraint
-satisfaction.
+satisfaction. We define these in our review on Control Theory (see Section 
+\ref{sec::Control_Theory}).
 
@@
 opponents. A similar set of conditions is considered by Conitzer and
-Sandholm in \cite{ConitzerAWESOME:}. Schwarz then presents a review of MARL methods (as of
-September 2014).
+Sandholm in \cite{ConitzerAWESOME:}.
+
+A plethora of MARL techniques emerged towards tackling this problem. Most notable of these are the
+minimax Q-Learning algorithms proposed by Littman \cite{Littman} which focuses on zero-sum games and
+Nash Q-Learning algorithm put forward by Hu and Wellman \cite{Hu} which extends the framework
+towards general sum games. The details of such stochastic algorithms are beyond the scope of this
+review as they consider multi-stage games (i.e. games in which the payoff matrix changes according
+to state). Establishing the robustness of such systems is an ongoing area of research. However, as
+of this review, it is not yet possible to place guarantees on the behaviour of MARL algorithms which
+tackle multi-stage games. This is also true of more contemporary MARL algorithms, including that of
+Multi-Agent Deep Reinforcement Learning (MDRL or MADRL), which are found to be incredibly sensitive
+to changes in input \cite{Gleave}. Therefore, due to importance we place on the stability and
+robustness guarantees of our MAS, we focus on those whose dynamics have been studies, as discussed
+in the following section.
 
@@
     \item {\em Robustness}: a system will perform its function in the presence of uncertainty and
-    noise
+    noise.
 
-    \item {\em Optimality}: the system will achieve some defined function
+    \item {\em Optimality}: the system will achieve its goal in the best way possible. This is
+    determined using a loss function which the control laws must minimise.
 
     \item {\em Feasibility}: the controller will always be able to generate a control law which
-    satisfies the desired properties.
+    satisfies the desired properties. Many texts will refer to the well-posedness of the control
+    problem which strictly requires that the control law: a) exist, b) be unique, c) vary
+    continuously with initial conditions.
 \end{itemize}
@@
 those which are particularly relevant to this study and review them in this section.
+
+\subsection{A Brief Introduction to Model Predictive Control} % (fold)
+\label{sub:a_brief_introduction_to_model_predictive_control}
+
+We begin by providing a brief introduction to the theory underlying model predictive control (MPC).
+This begins with the theory of Optimal Control which, simply put, is the theoretical study of
+controls which minimise a given cost function subject to system dynamics. More formally, an optimal
+control problem is presented as
+
+\begin{equation}
+    \begin{split}
+        \text{minimise } J(x, u) \\
+        \text{s.t. }
+        x(k + 1) = f(x(x_0; k, u(k)), u(k))\\
+        u \in U_{ad},
+    \end{split}
+\end{equation}
+
+where $J(x, u)$ is a given cost function, which is dependent on the state $x = x(x_0; k, u(k)) \in
+X$ and control
+$u(k)$, both of which are functions of the time step $k$. The first condition gives the dynamics of
+system (i.e. how the state evolves in time given the controls). Here, we show the dynamical
+system as an iterated map, though this may also be described through ordinary differential equations
+(ODEs) or partial differential equations (PDEs). The second condition places constraints on the
+controls $u$, which must lie within an admissible set. An example of this is bounded controls, in
+which case the admissible set is given by
+
+\begin{equation}
+    U_{ad} := \{u \; | \; u_a(x) \leq u(x) \leq u_b(x) \; a.e. \; x \in X\}
+\end{equation}
+
+Our goal is to find the optimal control $\bar{u}$ which satisfies the condition
+
+\begin{equation}
+    J(\bar{x}, \bar{u}) \leq J(x, u) \; \forall u \in U_{ad}.
+\end{equation}
+
+The trouble with optimal controls is that they are open-loop, in that the controls are determined
+for the model $x(k + 1) = f(x(k; x_0), u(k))$ a priori and simply applied to the system. Of course,
+in the presence of noise, disturbances, or even errors in parameter estimation in the model itself,
+such a control scheme is not practical.
+
+The idea of MPC is to reduce the open-loop optimal control problem to a series of finite horizon
+optimal control problems and solve these. For this reason, it is also referred to as `Receding
+Horizon Control'. The control problem is, therefore, transformed to
+
+\begin{equation}
+    \begin{split}
+        \text{minimise } J_N(x, u) := \sum_{k = 0}^{N-1} l(x(k), u(k)) \\
+        \text{s.t. }
+        x(k + 1) = f(x(k), u(k))\\
+        u \in U_{ad},
+    \end{split}
+\end{equation}
+
+where $l(x, u)$ are 'stage costs', defining the cost function at each time step of the horizon,
+which is of length $N$. At each time step, the system updates its measurement of its state $x$ 
+(which we have assumed here to be exact but may only be obtained through a measurement map). Solving
+this yields the optimal control sequence for this horizon $\bar{u}(0), ... , \bar{u}(N-1)$ and the
+first of these (i.e. $\bar{u}(0)$) is applied. Then, the system repeats this process at each time
+step.
+
+% subsection a_brief_introduction_to_model_predictive_control (end)
 
@@
 incredibly scalable \cite{Rizk2018}.
+
+Swarms are generally considered to be a special case of multi-agent systems and so, to this end,
+Sahin \cite{Sahin2005} puts forward five qualities which must be satisfied for a system to be
+considered a swarm. Note that Sahin's work considers swarm robotics, though these qualities apply to
+any agent type (computational or biological).
+
+\begin{enumerate}
+    \item Autonomous agents: the agents can, independently, interact with the environment
+    \item Large Number of Agents
+    \item Few Homogenous groups of agents: Agents are considered homogenous if they follow similar
+    rules and perform the same function.
+    \item Relative incapability of the agent: The agents should not be able to carry out the task on
+    their own, but rather efficient and robust handling of the task should emerge from the
+    collaboration of the agents.
+    \item Local sensing and communication: The agents should only have local sensing and
+    communication capabilities.
+\end{enumerate}
 

### 2020-06-29 Documents/ESA/sections/LitReview.tex
Added Application Papers

@@
 (MARL) extends the Markov Game setting to one where the payoff
-structure is not a priori knowledge.
+structure is not a priori knowledge. MARL has found success in a number of applications,
+particularly in robotics \cite{Yang2004} and but also in sensor/communication networks and finance
+\cite{Zhang2019}.
 
@@
 stochastic and distributed control. The literature of the control community is vast and can be
-divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
-those which are particularly relevant to this study and review them in this section.
+divided into a number of sub-fields. We consider Distributed MPC (DMPC) as
+a topic which is particularly relevant to this study and provide a review in this section.
 
@@
 Sahin \cite{Sahin2005} puts forward five qualities which must be satisfied for a system to be
-considered a swarm. Note that Sahin's work considers swarm robotics, though these qualities apply to
-any agent type (computational or biological).
+considered a swarm. Note that Sahin's work considers swarm robotics and its applicationns, though
+these qualities apply to any agent type (computational or biological).
 
@@
 \end{enumerate}
+
+Sahin goes on to describe the typical domains of application for swarm systems, which broadly fall
+into four categories:
+
+\begin{itemize}
+    \item Tasks that cover a region: Environmental Monitoring and Mapping, as well as Search and
+    Rescue fall into these categories. These leverage the fact that there are many agents, in a
+    distributed setting, to ensure complete coverage of an area.
+    \item Tasks that are dangerous: An example would be scoping out an environment with potential
+    hazards before human operators are involved.
+    \item Tasks that scale-up or down: This leverages the fact that the agents are independent and
+    the control methodology scales. These qualities allow the number of agents to be fluid and so
+    it is possible to add more or less agents to a task as its requirements vary. An example might
+    be providing emergency services to individuals in a disaster relief zone, in which initial
+    population estimates may be revised as the situation progresses.
+    \item Tasks that require redundancy: The fact that the system is not tied to any single point of
+    failure means that a task in which an agent is vulnerable to attack (cyber or physical) may be
+    tackled by a swarm.
+\end{itemize}
 

### 2020-06-29 Documents/ESA/sections/Abstract.tex
Included Abstract

@@
 
+	This project aims to study the evolution of a swarm of intelligent `active particles' under the
+	influence of Model Predictive Controls. We specifically aim to investigate the learning dynamics
+	of a population of agents following a Q-Learning approach. We also aim to study the evolution of
+	such a swarm under Model Predictive Controls generated by field particles. The goal of this
+	study is to bridge the gap between swarm theory and multi-agent reinforcement learning to enable
+	the study of complex populations of agents, who are capable of independent decision making, as
+	well as producing control methodologies to enable the safe operation of intelligent swarms.
+
 \end{abstract}

### 2020-06-30 Documents/ESA/sections/Intro.tex
removed aux files

@@
     agents who contribute towards the overall goal of the system
-    \cite{Hamann2018}. Such a collaboration can take the form of cooperative efforts or even
-    competition, both resulting in behaviours that are far more complex thhan individual robots can
-    achieve. The capacity for complexity is
-    becoming increasingly important as robots are presented
-    with ever more challenging tasks including: search and rescue,
-    cleaning up space debris, and robotic assembly. Such tasks are
-    beyond the capabilities of individual robots and so we must
-    leverage the capacity for agents in a swarm to collectively
-    achieve our goals. Fortunately, a growing subset of the Control
-    Theory community has turned their attention towards this very
-    problem and address the question: how does the dynamical behaviour
-    of a population of agents change under the influence of control?
-    Note that we use the term `agent' loosely here, an agent can refer
-    to anything from a simple particle \cite{Roy2017} to a complex
-    robot \cite{Elamvazhuthi2019}. In answering this question,
-    researchers have gained a stronger understanding of how a swarm
-    may be controlled to achieve desired results and have shown its capabilites in a wide array of
-    domains \cite{Sahin2005}.
+    \cite{Hamann2018}. Such a collaboration can take the form of
+    cooperative efforts or even competition, both resulting in
+    behaviours that are far more complex thhan individual robots can
+    achieve. The capacity for complexity is becoming increasingly
+    important as robots are presented with ever more challenging tasks
+    including: search and rescue, cleaning up space debris, and
+    robotic assembly. Such tasks are beyond the capabilities of
+    individual robots and so we must leverage the capacity for agents
+    in a swarm to collectively achieve our goals. Fortunately, a
+    growing subset of the Control Theory community has turned their
+    attention towards this very problem and address the question: how
+    does the dynamical behaviour of a population of agents change
+    under the influence of control?  Note that we use the term `agent'
+    loosely here, an agent can refer to anything from a simple
+    particle \cite{Roy2017} to a complex robot
+    \cite{Elamvazhuthi2019}. In answering this question, researchers
+    have gained a stronger understanding of how a swarm may be
+    controlled to achieve desired results and have shown its
+    capabilites in a wide array of domains \cite{Sahin2005}.
 
@@
 
-    Importantly, the study will seek to understand the guarantees that can be
-    placed on the safety of such systems in terms of their stability and
-    constraint satisfaction. If it is possible to determine, a priori, the decision making
-    behaviour of a population through its learning dynamics in terms of known quantities (e.g. the
-    agent parameters), then the system may be considered safe. Similarly, if it can be shown
-    to be robust, and satisfy desired constraints (e.g. controls lying within desired limits), then
-    we may be assured of its long-term safety. In doing so, we can ensure
-    that a user can have confidence in the system's decision making and manipulation.
+\paragraph{Relevance to Safe and Trusted AI} This study will seek to understand the guarantees that can be
+    placed on the safety of such systems in terms of their stability
+    and constraint satisfaction. If it is possible to determine, a
+    priori, the decision making behaviour of a population through its
+    learning dynamics in terms of known quantities (e.g. the agent
+    parameters), then the system may be considered safe. Similarly, if
+    it can be shown to be robust, and satisfy desired constraints
+    (e.g. controls lying within desired limits), then we may be
+    assured of its long-term safety. In doing so, we can ensure that a
+    user can have confidence in the system's decision making and
+    manipulation.
 

### 2020-06-30 Documents/ESA/sections/ResearchSummary.tex
Added Missing Reference in Appendix

@@
 	We are now ready to take the expectation of $Q$. To do this, we will exploit the fact that the
-	payoff elements are Gaussian distributed and use the identity \cite{QFTbook}
+	payoff elements are Gaussian distributed and use the identity \cite{ZinnJustin2009}
 
@@
 
-We will evaluate the path integral using the saddle point method for integration 
-\cite{saddlepoint}. In this method, we consider that the integration is dominated by the maximum of
+We will evaluate the path integral using the saddle point method for integration. In this method, we consider that the integration is dominated by the maximum of
 the function

### 2020-07-21 Documents/ChaoticDynamics/AAAI Submission/main.tex
Updated Code

\def\year{2020}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{graphicx}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
 \pdfinfo{
/Title (Working Title)
/Author (Aamal Hussain, Francesco Belardinelli)
} %Leave this	
% /Title ()
% Put your actual complete title (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case
% Leave the space between \Title and the beginning parenthesis alone
% /Author ()
% Put your actual complete list of authors (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case. 
% Each author should be only by a comma. If the name contains accents, remove them. If there are any LaTeX commands, 
% remove them.

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{caption} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \natbib} -- This package is specifically forbidden -- use the following workaround:
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai20.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\setlength\titlebox{2.5in} % If your paper contains an overfull \vbox too high warning at the beginning of the document, use this
% command to correct it. You may not alter the value below 2.5 in
\title{Working Title}
%Your title must be in mixed case, not sentence case. 
% That means all verbs (including short verbs like be, is, using,and go), 
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\author{Aamal Hussain, Francesco Belardinelli\textsuperscript{\rm 1}\thanks{Something to do with the
CDT}\\ % All authors must be in the same font size and format. Use \Large and \textbf to achieve this result when breaking a line
\textsuperscript{\rm 1}Imperial College London\\ %If you have multiple authors and multiple
% affiliations
% use superscripts in text and roman font to identify them. For example, Sunil Issar,\textsuperscript{\rm 2} J. Scott Penberthy\textsuperscript{\rm 3} George Ferguson,\textsuperscript{\rm 4} Hans Guesgen\textsuperscript{\rm 5}. Note that the comma should be placed BEFORE the superscript for optimum readability
Do we give the address?\\
publications20@aaai.org % email address must be in roman text type, not monospace or sans serif
}
 \begin{document}

\maketitle

\begin{abstract}
Working Abstract
\end{abstract}

\section{Introduction}

\subsection{Contribution}

\section{Preliminaries}

\subsection{Dynamical Behaviours}

\subsection{Dynamics of Q-Learning}

\section{Stability and Chaos in Multi-Agent Reinforcement Learning}

\section{Experimental Evaluation}

\section{Conclusion}

\subsection{Future Work}

The instructions herein are provided as a general guide for experienced \LaTeX{} users. If you do not know how to use \LaTeX{}, please obtain assistance locally. AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work. If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.

These instructions are generic. Consequently, they do not include specific dates, page charges, and so forth. Please consult your specific written conference instructions for details regarding your submission. Please review the entire document for specific instructions that might apply to your particular situation. All authors must comply with the following:

\begin{itemize}
\item You must use the 2020 AAAI Press \LaTeX{} style file and the aaai.bst bibliography style file, which are located in the 2020 AAAI Author Kit (aaai20.sty and aaai.bst).
\item You must complete, sign, and return by the deadline the AAAI copyright form (unless directed by AAAI Press to use the AAAI Distribution License instead).
\item You must read and format your paper source and PDF according to the formatting instructions for authors.
\item You must submit your electronic files and abstract using our electronic submission form \textbf{on time.}
\item You must pay any required page or formatting charges to AAAI Press so that they are received by the deadline.
\item You must check your paper before submitting it, ensuring that it compiles without error, and complies with the guidelines found in the AAAI Author Kit.
\end{itemize}

\section{Copyright}
All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form. There are no exceptions to this requirement. You must send us the original version of this form. However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms20@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office. If you fail to send in a signed copyright or permission form, we will be unable to publish your paper. There are \textbf{no exceptions} to this policy.You will find PDF versions of the AAAI copyright and permission to distribute forms in the AAAI AuthorKit.

\section{Formatting Requirements in Brief}
We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices. The design and appearance of the paper is strictly governed by the aaai style file (aaai20.sty). 
\textbf{You must not make any changes to the aaai style file, nor use any commands, packages, style files, or macros within your own paper that alter that design, including, but not limited to spacing, floats, margins, fonts, font size, and appearance.} AAAI imposes requirements on your source and PDF files that must be followed. Most of these requirements are based on our efforts to standardize conference manuscript properties and layout. All papers submitted to AAAI for publication will be recompiled for standardization purposes. Consequently, every paper submission must comply with the following requirements:

\begin{quote}
\begin{itemize}
\item Your .tex file must compile in PDF\LaTeX{} --- ( you may not include .ps or .eps figure files.)
\item All fonts must be embedded in the PDF file --- including includes your figures.
\item Modifications to the style file, whether directly or via commands in your document may not ever be made, most especially when made in an effort to avoid extra page charges or make your paper fit in a specific number of pages.
\item No type 3 fonts may be used (even in illustrations).
\item You may not alter the spacing above and below captions, figures, headings, and subheadings.
\item You may not alter the font sizes of text elements, footnotes, heading elements, captions, or title information (for references and mathematics, please see the the limited exceptions provided herein).
\item You may not alter the line spacing of text.
\item Your title must follow Title Case capitalization rules (not sentence case).
\item Your .tex file must include completed metadata to pass-through to the PDF (see PDFINFO below)
\item \LaTeX{} documents must use the Times or Nimbus font package (you may not use Computer Modern for the text of your paper).
\item No \LaTeX{} 209 documents may be used or submitted.
\item Your source must not require use of fonts for non-Roman alphabets within the text itself. If your paper includes symbols in other languages (such as, but not limited to, Arabic, Chinese, Hebrew, Japanese, Thai, Russian and other Cyrillic languages), you must restrict their use to bit-mapped figures. Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or 300 dpi bitmap or removed from the document (even if they are in a graphics file embedded in the document). 
\item Two-column format in AAAI style is required for all papers.
\item The paper size for final submission must be US letter without exception.
\item The source file must exactly match the PDF.
\item The document margins may not be exceeded (no overfull boxes).
\item The number of pages and the file size must be as specified for your event.
\item No document may be password protected.
\item Neither the PDFs nor the source may contain any embedded links or bookmarks (no hyperref or navigator packages).
\item Your source and PDF must not have any page numbers, footers, or headers (no pagestyle commands).
\item Your PDF must be compatible with Acrobat 5 or higher.
\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" or ``trim'' command) .
\end{itemize}
\end{quote}

If you do not follow these requirements, you will be required to correct the deficiencies and resubmit the paper. A resubmission fee will apply.

\section{What Files to Submit}
You must submit the following items to ensure that your paper is published:
\begin{itemize}
\item A fully-compliant PDF file that includes PDF metadata.
\item Your \LaTeX{} source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file). (The only allowable exception is .bib file, which should be included separately). 
\item The bibliography (.bib) file(s).
\item Your source must compile on our system, which includes only standard \LaTeX{} 2019 TeXLive support files. 
\item Only the graphics files used in compiling paper.
\item The \LaTeX{}-generated files (e.g. .aux,  .bbl file, PDF, etc.).
\end{itemize}

Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you will be required to resubmit, which will incur fees). \textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros.

Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution.

\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, style files, additional material sent for the purpose of the paper review, and so forth.

\textbf{Do not send supporting files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, style files, additional material sent for the purpose of the paper review, and so forth.

\textbf{Obsolete style files.} The commands for some common packages (such as some used for algorithms), may have changed. Please be certain that you are not compiling your paper using old or obsolete style files. 
\textbf{Final Archive.} Place your PDF and source files in a single archive which should be compressed using .zip. The final file size may not exceed 10 MB.
Name your source file with the last (family) name of the first author, even if that is not you.

\section{Using \LaTeX{} to Format Your Paper}

The latest version of the AAAI style file is available on AAAI's website. Download this file and place it in the \TeX\ search path. Placing it in the same directory as the paper should also work. You must download the latest version of the complete AAAI Author Kit so that you will have the latest instruction set and style file.

\subsection{Document Preamble}

In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection. This command set-up is for three authors. Add or subtract author and address lines as necessary, and uncomment the portions that apply to you. In most instances, this is all you need to do to format your paper in the Times font. The helvet package will cause Helvetica to be used for sans serif. These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).

Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper. If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers). The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.

If (and only if) your author title information will not fit within the specified height allowed, put \textbackslash setlength \textbackslash titlebox{2.5in} in your preamble. Increase the height until the height error disappears from your log. You may not use the \textbackslash setlength command elsewhere in your paper, and it may not be used to reduce the height of the author-title box.

\subsubsection{The Following Must Appear in Your Preamble}
\begin{quote}
\begin{scriptsize}\begin{verbatim}
\documentclass[letterpaper]{article}
\usepackage{aaai20}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage[hyphens]{url} 
\usepackage{graphicx}
\urlstyle{rm}
\def\UrlFont{\rm}
\usepackage{graphicx}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
% Add additional packages here, but check 
% the list of disallowed packages 
% (including, but not limited to
% authblk, caption, CJK, float, fullpage, geometry, 
% hyperref, layout, nameref, natbib, savetrees, 
% setspace, titlesec, tocbibind, ulem)
% and illegal commands provided in the 
% common formatting errors document
% included in the  Author Kit before doing so. 
%
% PDFINFO
% You are required to complete the following
% for pass-through to the PDF. 
% No LaTeX commands of any kind may be
% entered. The parentheses and spaces 
% are an integral part of the 
% pdfinfo script and must not be removed.
%
\pdfinfo{
/Title (Type Your Paper Title Here in Mixed Case)
/Author (John Doe, Jane Doe)
/Keywords (Input your keywords in this optional area)
}
%
% Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0}

% Title and Author Information Must Immediately Follow
% the pdfinfo within the preamble
%
\title{Title}\\
\author\{Author 1 \ and Author 2\\
Address line\\
Address line\\
\ And\\
Author 3\\
Address line\\
Address line
}\\
\end{verbatim}\end{scriptsize}
\end{quote}

\subsection{Preparing Your Paper}

After the preamble above, you should prepare your paper as follows:
\begin{quote}
\begin{scriptsize}\begin{verbatim}
%
\begin{document}
\maketitle
\begin{abstract}
%...
\end{abstract}\end{verbatim}\end{scriptsize}
\end{quote}

\subsubsection{The Following Must Conclude Your Document}
\begin{quote}
\begin{scriptsize}\begin{verbatim}
% References and End of Paper
% These lines must be placed at the end of your paper
\bibliography{Bibliography-File}
\bibliographystyle{aaai}
\end{document}
\end{verbatim}\end{scriptsize}
\end{quote}

\subsection{Inserting Document Metadata with \LaTeX{}}
PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately. \textit{Document metadata for author and title are REQUIRED.} You may not apply any script or macro to implementation of the title, author, and metadata information in your paper.

\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata. The data in the metadata must be completely plain ascii. It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands. Type the title exactly as it appears on the paper (minus all formatting). Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma. You may also include keywords in the optional Keywords field.

\begin{quote}
\begin{scriptsize}\begin{verbatim}
\begin{document}\\
\maketitle\\
...\\
\bibliography{Bibliography-File}\\
\bibliographystyle{aaai}\\
\end{document}\\
\end{verbatim}\end{scriptsize}
\end{quote}

\subsection{Commands and Packages That May Not Be Used}
\begin{table*}[t]
\centering
\caption{Commands that must not be used}\smallskip
\begin{tabular}{l|l|l|l}
\textbackslash abovecaption & 
\textbackslash abovedisplay & 
\textbackslash addevensidemargin & 
\textbackslash addsidemargin \\ 
\textbackslash addtolength & 
\textbackslash baselinestretch & 
\textbackslash belowcaption & 
\textbackslash belowdisplay \\ 
\textbackslash break &
\textbackslash clearpage & 
\textbackslash clip & 
\textbackslash columnsep \\ 
\textbackslash float & 
\textbackslash input & 
\textbackslash input & 
\textbackslash linespread \\ 
\textbackslash newpage &
\textbackslash pagebreak & 
\textbackslash renewcommand & 
\textbackslash setlength \\ 
\textbackslash text height & 
\textbackslash tiny & 
\textbackslash top margin & 
\textbackslash trim \\ 
\textbackslash vskip\{- & 
\textbackslash vspace\{- \\ 
\end{tabular}
%}
\label{table1}
\end{table*}

\begin{table}[t]
\caption{LaTeX style packages that must not be used.}\smallskip
\centering
%\resizebox{.95\columnwidth}{!}{
\smallskip\begin{tabular}{l|l|l|l}
authblk & babel & caption & cjk\\
dvips & epsf & epsfig & euler\\
float & fullpage & geometry & graphics\\
hyperref & layout & linespread & lmodern\\
maltepaper & natbib & navigator & pdfcomment\\
pgfplots & psfig & pstricks & t1enc \\
titlesec & tocbind & ulem\\
\end{tabular}
\label{table2}
\end{table}

There are a number of packages, commands, scripts, and macros that are incompatable with aaai20.sty. The common ones are listed in tables \ref{table1} and \ref{table2}. Generally, if a command, package, script, or macro alters floats, margins, fonts, sizing, linespacing, or the presentation of the references and citations, it is unacceptable. Note that negative vskip and vspace may not be used except in certain rare occurances, and may never be used around tables, figures, captions, sections, subsections, subsections, or references.

\subsection{Page Breaks}
For your final camera ready copy, you must not use any page break commands. References must flow directly after the text without breaks. Note that some conferences require references to be on a separate page during the review process. AAAI Press, however, does not require this condition for the final paper.

\subsection{Paper Size, Margins, and Column Width}
Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
\begin{itemize}
\item Top margin: .75 inches
\item Left margin: .75 inches
\item Right margin: .75 inches
\item Bottom margin: 1.25 inches
\end{itemize}

The default paper size in most installations of \LaTeX{} is A4. However, because we require that your electronic paper be formatted in US letter size, the preamble we have provided includes commands that alter the default to US letter size. Please note that using any other package to alter page size (such as, but not limited to the Geometry package) will result in your final paper being returned to you for correction and payment of a resubmission fee.

\subsubsection{Column Width and Margins.}
To ensure maximum readability, your paper must include two columns. Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns. The aaai20.sty file will automatically create these columns for you.

\subsection{Overlength Papers}
If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods. Next, shrink the size of your graphics. Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment. For mathematical environments, you may reduce fontsize {\bf but not below 6.5 point}. You may also alter the size of your bibliography and tables by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
right before the bibliography (the minimum size is \textbackslash fontsize\{9.0pt\}\{10.0pt\}. You may not use any commands that further reduce point size. Be careful when scaling tables and figures. Tables that do not fit in a single column, even after the font size reduction to 9 point, must be placed across double columns. If your table won't fit within the margins even in double columns, you must split it. We will not accept single (or double) column tables that have been scaled to anything below 9 point.

Commands that alter page layout are forbidden. These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive). If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee. Other commands that are questionable and may cause your paper to be rejected include \textbackslash parindent, and \textbackslash parskip. Commands that alter the space between sections are forbidden. The title sec package is not allowed. Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted. Options for reducing the length of a paper include reducing the size of your graphics, cutting text, or paying the extra page charge (if it is offered).

\subsection{Figures}
Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.

If you normally create your figures using pgfplots, please create the figures first, and then import them as pdfs with proper bounding boxes, as the bounding and trim boxes created by pfgplots are fragile, and not valid.

When you include your figures, you must crop them \textbf{outside} of \LaTeX{}. The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear (and obscure whatever it is overlapping) when page numbers are applied or color space is standardized. Figures \ref{fig1}, and \ref{fig2} display some unwanted results that often occur.

Do not use minipage to group figures. Additionally, the font and size of figure captions must be 10 point roman. Do not make them smaller, bold, or italic. (Individual words may be italicized if the context requires differentiation.)

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figure1} % Reduce the figure size so that it is slightly narrower than the column. Don't use precise values for figure width.This setup will avoid overfull boxes. 
\caption{Using the trim and clip commands produces fragile layers that can result in disasters (like this one from an actual paper) when the color space is corrected or the PDF combined with others for the final proceedings. Crop your figures properly in a graphics program -- not in LaTeX}
\label{fig1}
\end{figure}

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{figure2} % Reduce the figure size so that it is slightly narrower than the column.
\caption{Adjusting the bounding box instead of actually removing the unwanted data resulted multiple layers in this paper. It also needlessly increased the PDF size. In this case, the size of the unwanted layer doubled the paper's size, and produced the following surprising results in final production. Crop your figures properly in a graphics program. Don't just alter the bounding box.}
\label{fig2}
\end{figure*}

% Using the \centering command instead of \begin{center} ... \end{center} will save space
% Positioning your figure at the top of the page will save space and make the paper more readable
% Using 0.95\columnwidth in conjunction with the

\subsection{Type Font and Size}
Your paper must be formatted in Times Roman or Nimbus. We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface. Sans serif, when used, should be Courier. Use Symbol or Lucida or Computer Modern for \textit{mathematics only. }

Do not use type 3 fonts for any portion of your paper, including graphics. Type 3 bitmapped fonts are designed for fixed resolution printers. Most print at 300 dpi even if the printer resolution is 1200 dpi or higher. They also often cause high resolution imagesetter devices and our PDF indexing software to crash. Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts. Files containing those fonts (even in graphics) will be rejected.

Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts. The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e. (Note that papers formatted in this way will still use Computer Modern for the mathematics. To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")

If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader. The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document. If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.

The default size for your type must be ten-point with twelve-point leading (line spacing). Start all pages (except the first) directly under the top margin. (See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.

\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}

If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts. They are available without charge from the American Mathematical Society:
http://www.ams.org/tex/type1-fonts.html.

\subsubsection{Nonroman Fonts}
If your paper includes symbols in other languages (such as, but not limited to, Arabic, Chinese, Hebrew, Japanese, Thai, Russian and other Cyrillic languages), you must restrict their use to bit-mapped figures.

\subsection{Title and Authors}
Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading). This style is called ``mixed case," which means that means all verbs (including short verbs like be, is, using,and go), nouns, adverbs, adjectives, and pronouns should be capitalized, (including both words in hyphenated terms), while articles, conjunctions, and prepositions are lower case unless they directly follow a colon or long dash. Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading). (If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.

\subsubsection{Formatting Author Information}
Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display. In formatting your author information, however, you may not use a table nor may you employ the \textbackslash authorblk.sty package. For several authors from the same institution, please just separate with commas:

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{Author 1, ... Author n\\ 
Address line \\ ... \\ Address line}
\end{verbatim}\end{scriptsize}\end{quote}

\noindent If the names do not fit well on one line use:

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{Author 1} ... \\
{\bf \Large Author ... Author}\\ 
Address line \\ ... \\ Address line
}
\end{verbatim}\end{scriptsize}\end{quote}

\noindent For two (or three) authors from different institutions, use \textbackslash And:

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{Author 1\\ Address line \\ ... \\ Address line 
\And ... \And Author n\\
Address line\\ ... \\ Address line}
\end{verbatim}\end{scriptsize}\end{quote}

\noindent To start a separate ``row" of authors, use \textbackslash AND:

If the title and author information does not fit in the area allocated, place
\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
after the \textbackslash documentclass line where \{\textit{height}\} is 2.5in or greater. (This one of the only allowable uses of the setlength command. Check with AAAI Press before using it elsewhere.)

\subsubsection{Formatting Author Information --- Alternative Method}
If your paper has a large number of authors from different institutions, you may use the following alternative method for displaying the author information.

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{AuthorOne},\textsuperscript{\rm 1} 
AuthorTwo,\textsuperscript{\rm 2}
AuthorThree,\textsuperscript{\rm 3}
\\bf \Large AuthorFour,\textsuperscript{\rm 4} 
AuthorFive, \textsuperscript{\rm 5}\\
\textsuperscript{\rm 1}AffiliationOne, 
\textsuperscript{\rm 2}AffiliationTwo, 
\textsuperscript{\rm 3}AffiliationThree\\
\textsuperscript{\rm 4}AffiliationFour, 
\textsuperscript{\rm 5}AffiliationFive 
\{email, email\}@affiliation.com,
email@affiliation.com,
email@affiliation.com, 
email@affiliation.com
\end{verbatim}\end{scriptsize}\end{quote}

Note that you should break the author list before it extends into the right column margin. Put a line break, followed by   \textbackslash bf  \textbackslash Large to put the second line of authors in the same font and size as the first line (you may not make authors names smaller to save space.) Affiliations can be broken with a simple line break (\textbackslash  \textbackslash).
\subsection{\LaTeX{} Copyright Notice}
The copyright notice automatically appears if you use aaai20.sty. It has been hardcoded and may not be disabled.

\subsection{Credits}
Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
For example:
\begin{quote}
\begin{small}
\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
 supported by everybody.\}\}
\end{small}
\end{quote}
Multiple \textbackslash thanks commands can be given. Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document. Note that the \textbackslash thanks command is fragile. You will need to use \textbackslash protect.

Please do not include \textbackslash pubnote commands in your document.

\subsection{Abstract}
Follow the example commands in this document for creation of your abstract. The command \textbackslash begin\{abstract\} will automatically indent the text block. Please do not indent it further. {Do not include references in your abstract!}

\subsection{Page Numbers}

Do not \textbf{ever} print any page numbers on your paper. The use of \textbackslash pagestyle is forbidden.

\subsection{Text }
The main body of the paper must be formatted in black, ten-point Times Roman with twelve-point leading (line spacing). You may not reduce font size or the linespacing. Commands that alter font size or line spacing (including, but not limited to baselinestretch, baselineshift, linespread, and others) are expressly forbidden. In addition, you may not use color in the text.

\subsection{Citations}
Citations within the text should include the author's last name and year, for example (Newell 1980). Append lower-case letters to the year in cases of ambiguity. Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992). In the case of four or more authors, list only the first author, followed by et al. (Ford et al. 1997).

\subsection{Extracts}
Long quotations and extracts should be indented ten points from the left and right margins.

\begin{quote}
This is an example of an extract or quotation. Note the indent on both sides. Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.

\end{quote}

\subsection{Footnotes}
Avoid footnotes as much as possible; they interrupt the reading of the text. When essential, they should be consecutively numbered throughout with superscript Arabic numbers. Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.

\subsection{Headings and Sections}
When necessary, headings should be used to separate major sections of your paper. Remember, you are writing a short paper, not a lengthy book! An overabundance of headings will tend to make your paper look more like an outline than a paper. The aaai.sty package will create headings for you. Do not alter their size nor their spacing above or below.

\subsubsection{Section Numbers}
The use of section numbers in AAAI Press papers is optional. To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2. Section numbers should not be used in short poster papers.

\subsubsection{Section Headings.}
Sections should be arranged and headed as follows:

\subsubsection{Acknowledgments.}
The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish. Please acknowledge other contributors, grant support, and so forth, in this section. Do not put acknowledgments in a footnote on the first page. If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back. Please try to limit acknowledgments to no more than three sentences.

\subsubsection{Appendices.}
Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.

\subsubsection{References}
The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page). A sample list of references is given later on in these instructions. Please use a consistent format for references. Poorly prepared or sloppy references reflect badly on the quality of your paper and your research. Please prepare complete and accurate citations.

\subsection{Illustrations and Figures}
Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed. Do not group them together at the end of the paper. If placed at the top or bottom of the paper, illustrations may run across both columns. Figures must not invade the top, bottom, or side margin areas. Figures must be inserted using the \textbackslash usepackage\{graphicx\}. Number figures sequentially, for example, figure 1, and so on.

The illustration number and caption should appear under the illustration. Labels, and other text with the actual illustration must be at least nine-point type.

If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them. The epstopdf package will usually work for eps files. You will need to convert your ps files to PDF however.

\subsubsection{Low-Resolution Bitmaps.}
You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed. If they are color, they will become an indecipherable mess when converted to black and white. This is always the case with gif files, which should never be used. The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels. You can also enlarge files by manipulating them in software such as PhotoShop. Your figures should be 300 dpi when incorporated into your document.

\subsubsection{\LaTeX{} Overflow.}
\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin. If this happens, you need to scale the figure or table down, or reformat the equation.{ \bf Check your log file!} You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}). \textbf{Nothing is permitted to intrude into the margin or gutter.}

The most efficient and trouble-free way to fix overfull boxes in graphics is with the following command:

\begin{quote}
\begin{small}
\textbackslash resizebox\{.95\textbackslash columnwidth\}{!}\{
\}
\end{small}\end{quote}

Be certain, however, that your figures remain legible without magnification.

\subsubsection{Using Color.}
Use of color is restricted to figures only. It must be WACG 2.0 compliant. (That is, the contrast ratio must be greater than 4.5:1 no matter the font size.) It must be CMYK, NOT RGB. It may never be used for any portion of the text of your paper. The archival version of your paper will be printed in black and white and grayscale.The web version must be readable by persons with disabilities. Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document. If you do include color figures, you must (1) use the CMYK (not RGB) colorspace and (2) be mindful of readers who may happen to have trouble distinguishing colors. Your paper must be decipherable without using color for distinction.

\subsubsection{Drawings.}
We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations. Do not use Microsoft Publisher. These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas. Shading should be 133 lines per inch if possible. Use Times Roman or Helvetica for all figure call-outs. \textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt. Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.

\subsubsection{Photographs and Images.}
Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 300 dpi. Do not prescreen images.

\subsubsection{Resizing Graphics.}
Resize your graphics \textbf{before} you include them with LaTeX. You may \textbf{not} use trim or clip options as part of your \textbackslash includegraphics command. Resize the media box of your PDF using a graphics program instead.

\subsubsection{Fonts in Your Illustrations}
You must embed all fonts in your graphics before including them in your LaTeX document.

\subsection{References} 
The AAAI style includes a set of definitions for use in formatting references with BibTeX. These definitions make the bibliography style fairly close to the one specified below. To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the AAAI Author Kit on the AAAI web site. Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:

\begin{quote}
\begin{small}
\textbackslash bibliographystyle\{aaai\}
\textbackslash bibliography\{bibfile1,bibfile2,...\}
\end{small}
\end{quote}

Please note that you are required to use \textbackslash bibliographystyle\{aaai\} for your references. You may not use named, plain, apalike, acm, ieeetr, siam, chicago, or any other style. Use of natbib is also not acceptable. (In addition to natbib, the aaai20.sty file is also incompatible with the hyperref and navigator packages. If you use either, your references will be garbled and your paper will be returned to you.) If you used natbib commands, an imprecise workaround is available (although it does not always work). You may put the following in your preamble (after removing \textbackslash usepackage\{natbib\}

\begin{quote}\small
\textbackslash newcommand\{\textbackslash citet\}[1]\{\textbackslash citeauthor\{\#1\}~\textbackslash shortcite\{\#1\}\}
\textbackslash newcommand\{\textbackslash citep\}\{\textbackslash cite\}
\textbackslash newcommand\{\textbackslash citealp\}[1]\{\textbackslash citeauthor\{\#1\}~\textbackslash citeyear\{\#1\}\}
\end{quote}

References may be the same size as surrounding text. However, in this section (only), you may reduce the size to \textbackslash small if your paper exceeds the allowable number of pages. Making it any smaller than 9 point with 10 point linespacing, however, is not allowed. A more precise and exact method of reducing the size of your references minimally is by means of the following command: \begin{quote}
\textbackslash fontsize\{9.8pt\}\{10.8pt\}
\textbackslash selectfont\end{quote}

\noindent You must reduce the size equally for both font size and line spacing, and may not reduce the size beyond \{9.0pt\}\{10.0pt\}.

The list of files in the \textbackslash bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).

The following commands are available for your use in citing references:
\begin{quote}
{\em \textbackslash cite:} Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\smallskip\\
{\em \textbackslash shortcite:} Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\smallskip\\
{\em \textbackslash citeauthor:} Cites the given reference(s) with just the author name(s) and no parentheses.\smallskip\\
{\em \textbackslash citeyear:} Cites the given reference(s) with just the date(s) and no parentheses.
\end{quote}

Formatted bibliographies should look like the following examples.

\smallskip \noindent \textit{Book with Multiple Authors}\\
Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.

\smallskip \noindent \textit{Journal Article}\\
Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.

\smallskip \noindent \textit{Magazine Article}\\
Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.

\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
Clancey, W. J. 1983. Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education. In \textit{Proceedings of the Eighth International Joint Conference on Artificial Intelligence,} 556--560. Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.

\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.

\smallskip \noindent \textit{University Technical Report}\\
Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.

\smallskip \noindent \textit{Dissertation or Thesis}\\
Clancey, W. J. 1979. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.

\smallskip \noindent \textit{Forthcoming Publication}\\
Clancey, W. J. 2021. The Engineering of Qualitative Models. Forthcoming.

For the most up to date version of the AAAI reference style, please consult the \textit{AI Magazine} Author Guidelines at \url{https://aaai.org/ojs/index.php/aimagazine/about/submissions#authorGuidelines}

\section{Proofreading Your PDF}
Please check all the pages of your PDF file. The most commonly forgotten element is the acknowledgements --- especially the correct grant number. Authors also commonly forget to add the metadata to the source, use the wrong reference style file, or don't follow the capitalization rules or comma placement for their author-title information properly. A final common problem is text (expecially equations) that runs into the margin. You will need to fix these common errors before submitting your file.

\section{Improperly Formatted Files }
In the past, AAAI has corrected improperly formatted files submitted by the authors. Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb (we are charged double for papers that require reformatting). Consequently, if your file is improperly formatted, it will probably be returned to you by the outside Production agency. If that happens, you will be required to fix your file and pay a resubmission fee.

\subsection{\LaTeX{} 209 Warning}
If you use \LaTeX{} 209 your paper will be returned to you unpublished. Convert your paper to \LaTeX{}2e.

\section{Naming Your Electronic File}
We require that you name your \LaTeX{} source file with the last name (family name) of the first author so that it can easily be differentiated from other submissions. Complete file-naming instructions will be provided to you in the submission instructions.

\section{Submitting Your Electronic Files to AAAI}
Instructions on paper submittal will be provided to you in your acceptance letter.

\section{Inquiries} 
If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below. If you have technical questions about implementation of the aaai style file, please contact an expert at your site. We do not provide technical support for \LaTeX{} or any other software package. To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.

\begin{quote}
\noindent AAAI Press\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\ 
\textit{Telephone:} (650) 328-3123\\ 
\textit{E-mail:} See the submission instructions for your particular conference or event.
\end{quote}

\section{Additional Resources}
\LaTeX{} is a difficult program to master. If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems. (It was written for another purpose, but it has general application as well). It is available at www.ctan.org in the tex-archive.

\section{ Acknowledgments}
AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton. We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.

The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press. Bibliography style changes were added by Sunil Issar. \verb+\+pubnote was added by J. Scott Penberthy. George Ferguson added support for printing the AAAI copyright slug. Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.

\bigskip
\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!

\end{document}

### 2020-07-21 Code/EGT-RL/TwoPlayerCode/LiapunovExponent.py

@@ -1,0 +1,90 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from time import time
+from tqdm import tqdm
+
+alpha = .1
+gamma = .1
+Gamma = 0.1
+tau = 1
+
+delta_0 = 1e-3
+nSim = 5
+nIter = 1e5
+
+def generateGame(gamma, nAct):
+    """
+    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
+
+    gamma: Choice of co-operation parameter
+    nAct: Number of actions in the game
+
+    [reward1s, reward2s]: list of payoff matrices
+    """
+
+    nElements = nAct ** 2  # number of payoff elements in the matrix
+
+    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+    reward1s = rewards[0:nElements].reshape((nAct, nAct))
+    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
+
+    return [reward1s, reward2s]
+
+def getActionProbs(qValues):
+    partitionFunction = [np.sum([np.exp(tau * i) for i in qValues[p, :]]) for p in range(2)]
+    actionProbs = np.array([[np.exp(tau * i) / partitionFunction[p] for i in qValues[p, :]] for p in range(2)])
+    
+    return actionProbs
+
+def qUpdate(qValues):
+    actionProbs = getActionProbs(qValues)
+
+    boltzmannChoices = [np.random.choice([0, 1], p=actionProbs[p, :]) for p in range(2)]
+
+    rewards = [payoffA[boltzmannChoices[0], boltzmannChoices[1]],
+                       payoffB[boltzmannChoices[0], boltzmannChoices[1]]]
+
+    qValues[0, boltzmannChoices[0]] += alpha * (rewards[0] - qValues[0, boltzmannChoices[0]] + gamma * max(qValues[0, :]))
+    
+    qValues[1, boltzmannChoices[1]] += alpha * (rewards[1] - qValues[1, boltzmannChoices[1]] + gamma * max(qValues[1, :]))
+
+    return qValues
+
+all_actionProbs = np.eye(2)
+
[…]

### 2020-07-21 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -1,11 +1,19 @@
-from tqdm import tqdm
-import os
 import numpy as np
 import matplotlib.pyplot as plt
-import shutil
+from time import time
+from tqdm import tqdm
+
+alpha = .1
+gamma = .75
+Gamma = 0.1
+tau = 2
+
+delta_0 = 1e-3
+nSim = 10
+nIter = int(1e4)
 
 
-def generateGame(gamma, nAct):
+def generateGames(gamma, nSim, nAct):
     """
     Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
 
@@ -21,133 +29,72 @@ def generateGame(gamma, nAct):
     cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
     cov[nElements:, :nElements] = np.eye(nElements) * gamma
 
-    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+    rewardAs, rewardBs = np.eye(2), np.eye(2)
 
-    reward1s = rewards[0:nElements].reshape((nAct, nAct))
-    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
+    for i in range(nSim):
 
-    return [reward1s, reward2s]
+        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
 
-def checkConvergence(actionProb, oldxBar, tol):
-    """
-      Evaluates the distance between action probabilities and checks if the change is
-      below some tolerance.
+        # rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
+        rewardAs = np.dstack((rewardAs, np.array([[1, 0], [0, 2]])))
+        # rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
+        rewardBs = np.dstack((rewardBs, np.array([[2, 0], [0, 1]])))
+    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
 
-      params
-      actionProb: Agent action probabilities at current time step
-      oldxBar: Previous action probabilities
-      tol: tolerance level
+def getActionProbs(qValues, nSim):
+    partitionFunction = np.sum(np.exp(tau * qValues), axis = 1)
[…]

### 2020-07-21 Code/Practice/Tuyls.py

@@ -2,9 +2,9 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 alpha = .1
-A = np.array([[1, 5], [0, 3]])
-B = np.array([[1, 0], [5, 3]])
-tau = 0.9
+A = np.array([[2, 0], [0, 1]])
+B = np.array([[1, 0], [0, 2]])
+tau = .9
 
 x = np.linspace(0, 1, 50)
 y = np.linspace(0, 1, 50)

### 2020-07-23 Documents/ChaoticDynamics/AAAI Submission/main.tex
Added AAAI Submission 2020

@@
 \usepackage{aaai20}  % DO NOT CHANGE THIS
+\usepackage{mathtools}
 \usepackage{times}  % DO NOT CHANGE THIS
 \usepackage{helvet} % DO NOT CHANGE THIS
+
 \usepackage{courier}  % DO NOT CHANGE THIS
@@
 \usepackage{graphicx}  % DO NOT CHANGE THIS
+\usepackage{subcaption}
 \frenchspacing  % DO NOT CHANGE THIS
@@
  \pdfinfo{
-/Title (Working Title)
+/Title (Stability and Chaos in Multi Agent Reinforcement Learning)
 /Author (Aamal Hussain, Francesco Belardinelli)
@@
 % command to correct it. You may not alter the value below 2.5 in
-\title{Working Title}
+\title{Stability and Chaos in Multi Agent Reinforcement Learning}
 %Your title must be in mixed case, not sentence case. 
@@
 
+In this section we will establish some of the preliminaries which are required to follow the subsequent sections.
+The first is 'Dynamical Behaviours' which considers the evolution of agent strategies as they learn on an iterated game.
+This study aims to classify, based on the agent parameters and the payoff matrices, which of these behaviours will be seen.
+The second is 'Dynamics of Q-Learning'.
+These are a set of equations which model the aforementioned strategy evolution.
+It is on these dynamics that we will perform our analysis.
+
 \subsection{Dynamical Behaviours}
 
+ This segment of research aims to achieve a deeper understanding
+    of the strategy evolution of agents following a Q-Learning
+    approach. This allows for guarantees to be placed on the behaviour
+    of such agents, in particular the conditions under which the game
+    will converge to a stable equilibrium.
+
+    It has long been established that, upon lifting the strong
+    assumptions made by traditional game theory (such as the
+    rationality of agents and complete information), player
+    strategies can result in much more complex behaviour than
+    convergence to a Nash Equilibrium (NE). In fact, this is even true
+    on what would commonly be regarded as 'simple' games such as
+    tic-tac-toe and prisoner's dilemma \cite{Galla2011,
+      Sato2002}. These behaviours include: convergence to a unique
+    equilibrium (though not always to an NE), convergence to one of
+    multiple equilibria, limit cycles and chaos. These behaviours are
+    shown in Figure \ref{fig::DynamicalBehaviours}. Of these, the most
+    preferable is, of course, convergence to a unique equilibrium,
+    although it is still possible to study systems with multiple
+    equilibria or limit cycles \cite{Strogatz2000}. However, it would
+    be difficult to control systems whose dynamics are governed by
+    chaos (though research into controlling chaos is ongoing and rife
+    with opportunity \cite{Fradkov2009}) and so MARL techniques should
+    avoid this. It would, therefore, be a useful endeavour to
+    determine the conditions under which these sorts of behaviours
+    arise.
+
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
+        \caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
+       displayed
+        by learning agents.
+Here the x-axis is the probability with which agent 1 chooses a given action, whilst the y-axis denotes the same probability for agent 2.
+a) Figure drawn from \cite{Tuyls2006AnGames}.
+        Convergence
+        to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
+        that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
+        d) Chaotic behaviour, here small deviatons in the initial conditions can grow
+        exponentially. b-d drawn from \cite{Sanders2018}}
+    \end{figure}
+
 \subsection{Dynamics of Q-Learning}
+
+The behaviour of a system may be studied given a model of its
+    dynamics. It is through this process that a wide array of physical
+    systems, from harmonic pendulums to geophysical fluids, can be
+    understood. A growing body of research aims to understand
+    multi-agent reinforcement learning through the lens of its
+    dynamics. In this light, Tuyls et al. \cite{Tuyls2006AnGames} were able to derive a continuous time dynamical
+system describing how agents following a Q-Learning approach adjust the probabilities of choosing actions
+as they iteratively play a game.  Through this, they were able to
+    arrive at the following model of Multi-Agent Q-Learning
+
+    \begin{subequations}
+    \label{eqn::EOM}
+        \begin{equation}
+            \frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
+            + \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
+        \end{equation}
+        \begin{equation}
+            \frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
+            + \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
+        \end{equation}
+    \end{subequations}
+
+    Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
+    memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
+    $x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
+    receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
+    predict the expected behaviour of Q-Learning agents, as shown in Figure 
+    \ref{fig::TuylsExperiments}.
+
+    \begin{figure}
+    \centering
+        \begin{subfigure}[b]{0.9 \textwidth}
+            \includegraphics[width=0.52 \textwidth]{Figures/Dynamics}
+            \caption{}
+        \end{subfigure}
+
+        \begin{subfigure}[b]{0.9 \textwidth}
+            \includegraphics[width=0.5 \textwidth]{Figures/Q-Learners}
+            \caption{}
+        \end{subfigure}
+
+        \caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
+        plot showing the expected behaviour of Q-Learning agents trained by iterating the
+        Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
+        have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
+        randomised initial conditions displayed through numerical simulation. It is clear that the
+        trajectories in b) follow the predictions in a), if transients are neglected. }
+    \end{figure}
+
+    It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments}, that the long-term strategy selection of
+    these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
+    then pose the question: how do these elements influence the types of behaviours seen during
+    learning on an iterated game? In other words, under what parameter selections are we likely to
+    see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?
 
@@
 
+To verify our theoretical results, and to examine the underlying structure of stability and chaos in
+Multi-Agent Q Learning, we perform a series of numerical experiments by varying the parameters $\Gamma$ and
+$\alpha$ whilst keeping $\tau$ fixed.
+The purpose of this experiment was to determine a heuristic estimate for the Liapunov exponent, which determines whether initial conditions which start close to one another will converge or diverge from each other.
+The former indicates a stable system (in the sense of Liapunov) whilst the latter signals instability.
+
+This yields the result shown in
+Figure \ref{fig::NumericalExperiments}. We see from this that the stability of the system is highly dependent on
+the value of $\tau$.
+For
+low values, the system converges almost everywhere, whilst increasing $\tau$ to 0.15 decreases
+the probability of convergence significantly.
+
+\begin{figure}[h]
+    \centering
+     \begin{subfigure}[b]{0.45 \textwidth}
+    \centering
+    \includegraphics[width = 0.7 \textwidth]{Figures/AlphaRun_tau_005.png}
+    \caption{$\tau = 0.05$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45 \textwidth}
+    \centering
+    \includegraphics[width = 0.7 \textwidth]{Figures/tau_015.png}
+    \caption{$\tau = 0.15$}
+    \end{subfigure}
+
+    \caption{$\tau = 0.05$, $\gamma = 0.75$, $\alpha \in [0, 1]$, $\Gamma \in [-1, 1]$. Each
+    simulation is run for 1 $\times 10^4$ iterations and the Liapunov exponent is determined. For each
+    combination of $\alpha$, $\Gamma$ the game is played 100 times, each with random payoff matrices
+    and initial conditions. The average liapunov exponent is determined and shown in the heatmap.
+    \label{fig::NumericalExperiments}}
+\end{figure}
+
+   To generate the numerical simulations in Figure \ref{fig::NumericalExperiments} we used the
+   following procedure.
+
+   \begin{enumerate}
+   	\item Fix the paremeters $\tau, \gamma$. The latter is held at 0.75 in all experiments as (\ref{eqn::EOM}) indicates that the value of $\gamma$ does not affect the overall behaviour of the system.
+   	\item Initialise values of $\Gamma, \alpha$. These will be swept over in the experiment.
+	\item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
+    (variables are the payoff elements) with mean zero and covariance parameterised by $\Gamma$. \textbf{Put these in the derivation}.
+    \item Initialise 2 sets of agents (denote their action probabilities as $\Vec{A_1}$ and $\Vec{A_2}$ respectively) each with random initial conditions (i.e. random action probabilities).
+    \item Allow both sets of agents to learn over a maximum of $1 \times 10^4$ iterations.
+    \item After 300 iterations measure the distance $\Vec{\delta_1} = |A_2 - A_1|$
+    \item After 10000 iterations measure the distance $\Vec{\delta_n} = |A_2 - A_1|$
+    \item Determine
+
+    \begin{equation}
+        \lambda_n = \max_{i} 10^{-4} ln(\delta_{n, i}/\delta_{1, i})
+    \end{equation}
+
+   \end{enumerate}
+
 \section{Conclusion}
@@
 
-The instructions herein are provided as a general guide for experienced \LaTeX{} users.
-If you do not know how to use \LaTeX{}, please obtain assistance locally.
-AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work.
-If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.
-
-These instructions are generic.
-Consequently, they do not include specific dates, page charges, and so forth.
-Please consult your specific written conference instructions for details regarding your submission.
-Please review the entire document for specific instructions that might apply to your particular situation.
-All authors must comply with the following:
-
-\begin{itemize}
-\item You must use the 2020 AAAI Press \LaTeX{} style file and the aaai.bst bibliography style file, which are located in the 2020 AAAI Author Kit (aaai20.sty and aaai.bst).
-\item You must complete, sign, and return by the deadline the AAAI copyright form (unless directed by AAAI Press to use the AAAI Distribution License instead).
-\item You must read and format your paper source and PDF according to the formatting instructions for authors.
-\item You must submit your electronic files and abstract using our electronic submission form \textbf{on time.}
-\item You must pay any required page or formatting charges to AAAI Press so that they are received by the deadline.
-\item You must check your paper before submitting it, ensuring that it compiles without error, and complies with the guidelines found in the AAAI Author Kit.
-\end{itemize}
-
-\section{Copyright}
-All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form.
-There are no exceptions to this requirement.
-You must send us the original version of this form.
-However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms20@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office.
-If you fail to send in a signed copyright or permission form, we will be unable to publish your paper.
-There are \textbf{no exceptions} to this policy.You will find PDF versions of the AAAI copyright and permission to distribute forms in the AAAI AuthorKit.
-
-\section{Formatting Requirements in Brief}
-We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices.
-The design and appearance of the paper is strictly governed by the aaai style file (aaai20.sty).
-\textbf{You must not make any changes to the aaai style file, nor use any commands, packages, style files, or macros within your own paper that alter that design, including, but not limited to spacing, floats, margins, fonts, font size, and appearance.} AAAI imposes requirements on your source and PDF files that must be followed.
-Most of these requirements are based on our efforts to standardize conference manuscript properties and layout.
-All papers submitted to AAAI for publication will be recompiled for standardization purposes.
-Consequently, every paper submission must comply with the following requirements:
-
-\begin{quote}
-\begin{itemize}
-\item Your .tex file must compile in PDF\LaTeX{} --- ( you may not include .ps or .eps figure files.)
-\item All fonts must be embedded in the PDF file --- including includes your figures.
-\item Modifications to the style file, whether directly or via commands in your document may not ever be made, most especially when made in an effort to avoid extra page charges or make your paper fit in a specific number of pages.
-\item No type 3 fonts may be used (even in illustrations).
-\item You may not alter the spacing above and below captions, figures, headings, and subheadings.
-\item You may not alter the font sizes of text elements, footnotes, heading elements, captions, or title information (for references and mathematics, please see the the limited exceptions provided herein).
-\item You may not alter the line spacing of text.
-\item Your title must follow Title Case capitalization rules (not sentence case).
-\item Your .tex file must include completed metadata to pass-through to the PDF (see PDFINFO below)
-\item \LaTeX{} documents must use the Times or Nimbus font package (you may not use Computer Modern for the text of your paper).
-\item No \LaTeX{} 209 documents may be used or submitted.
-\item Your source must not require use of fonts for non-Roman alphabets within the text itself.
-If your paper includes symbols in other languages (such as, but not limited to, Arabic, Chinese, Hebrew, Japanese, Thai, Russian and other Cyrillic languages), you must restrict their use to bit-mapped figures.
-Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or 300 dpi bitmap or removed from the document (even if they are in a graphics file embedded in the document).
-\item Two-column format in AAAI style is required for all papers.
-\item The paper size for final submission must be US letter without exception.
-\item The source file must exactly match the PDF.
-\item The document margins may not be exceeded (no overfull boxes).
-\item The number of pages and the file size must be as specified for your event.
-\item No document may be password protected.
-\item Neither the PDFs nor the source may contain any embedded links or bookmarks (no hyperref or navigator packages).
-\item Your source and PDF must not have any page numbers, footers, or headers (no pagestyle commands).
-\item Your PDF must be compatible with Acrobat 5 or higher.
-\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
-\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" or ``trim'' command) .
-\end{itemize}
-\end{quote}
-
-If you do not follow these requirements, you will be required to correct the deficiencies and resubmit the paper. A resubmission fee will apply.
-
-\section{What Files to Submit}
-You must submit the following items to ensure that your paper is published:
-\begin{itemize}
-\item A fully-compliant PDF file that includes PDF metadata.
-\item Your \LaTeX{} source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file).
-(The only allowable exception is .bib file, which should be included separately).
-\item The bibliography (.bib) file(s).
-\item Your source must compile on our system, which includes only standard \LaTeX{} 2019 TeXLive support files. 
-\item Only the graphics files used in compiling paper.
-\item The \LaTeX{}-generated files (e.g. .aux,  .bbl file, PDF, etc.).
-\end{itemize}
-
-Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you will be required to resubmit, which will incur fees).
-\textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros.
-
-Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution.
-
-\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, style files, additional material sent for the purpose of the paper review, and so forth.
-
-\textbf{Do not send supporting files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, style files, additional material sent for the purpose of the paper review, and so forth.
-
-\textbf{Obsolete style files.} The commands for some common packages (such as some used for algorithms), may have changed.
-Please be certain that you are not compiling your paper using old or obsolete style files.
-\textbf{Final Archive.} Place your PDF and source files in a single archive which should be compressed using .zip. The final file size may not exceed 10 MB.
-Name your source file with the last (family) name of the first author, even if that is not you.
-
-\section{Using \LaTeX{} to Format Your Paper}
-
-The latest version of the AAAI style file is available on AAAI's website.
-Download this file and place it in the \TeX\ search path.
-Placing it in the same directory as the paper should also work.
-You must download the latest version of the complete AAAI Author Kit so that you will have the latest instruction set and style file.
-
-\subsection{Document Preamble}
-
-In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection.
-This command set-up is for three authors.
-Add or subtract author and address lines as necessary, and uncomment the portions that apply to you.
-In most instances, this is all you need to do to format your paper in the Times font.
-The helvet package will cause Helvetica to be used for sans serif.
-These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).
-
-Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper.
-If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers).
-The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.
-
-If (and only if) your author title information will not fit within the specified height allowed, put \textbackslash setlength \textbackslash titlebox{2.5in} in your preamble.
-Increase the height until the height error disappears from your log.
-You may not use the \textbackslash setlength command elsewhere in your paper, and it may not be used to reduce the height of the author-title box.
-
-\subsubsection{The Following Must Appear in Your Preamble}
-\begin{quote}
-\begin{scriptsize}\begin{verbatim}
-\documentclass[letterpaper]{article}
-\usepackage{aaai20}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
-\usepackage[hyphens]{url} 
-\usepackage{graphicx}
-\urlstyle{rm}
-\def\UrlFont{\rm}
-\usepackage{graphicx}
-\frenchspacing
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
-% Add additional packages here, but check 
-% the list of disallowed packages 
-% (including, but not limited to
-% authblk, caption, CJK, float, fullpage, geometry, 
-% hyperref, layout, nameref, natbib, savetrees, 
-% setspace, titlesec, tocbibind, ulem)
-% and illegal commands provided in the 
-% common formatting errors document
-% included in the  Author Kit before doing so. 
-%
-% PDFINFO
-% You are required to complete the following
-% for pass-through to the PDF. 
-% No LaTeX commands of any kind may be
-% entered. The parentheses and spaces 
-% are an integral part of the 
-% pdfinfo script and must not be removed.
-%
-\pdfinfo{
-/Title (Type Your Paper Title Here in Mixed Case)
-/Author (John Doe, Jane Doe)
-/Keywords (Input your keywords in this optional area)
-}
-%
-% Section Numbers
-% Uncomment if you want to use section numbers
-% and change the 0 to a 1 or 2
-% \setcounter{secnumdepth}{0}
-
-% Title and Author Information Must Immediately Follow
-% the pdfinfo within the preamble
-%
-\title{Title}\\
-\author\{Author 1 \ and Author 2\\
-Address line\\
-Address line\\
-\ And\\
-Author 3\\
-Address line\\
-Address line
-}\\
-\end{verbatim}\end{scriptsize}
-\end{quote}
-
-\subsection{Preparing Your Paper}
-
-After the preamble above, you should prepare your paper as follows:
-\begin{quote}
-\begin{scriptsize}\begin{verbatim}
-%
-\begin{document}
-\maketitle
-\begin{abstract}
-%...
-\end{abstract}\end{verbatim}\end{scriptsize}
-\end{quote}
-
-\subsubsection{The Following Must Conclude Your Document}
-\begin{quote}
-\begin{scriptsize}\begin{verbatim}
-% References and End of Paper
-% These lines must be placed at the end of your paper
-\bibliography{Bibliography-File}
+\bibliography{references}
 \bibliographystyle{aaai}
 \end{document}
-\end{verbatim}\end{scriptsize}
-\end{quote}
-
-\subsection{Inserting Document Metadata with \LaTeX{}}
-PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately.
-\textit{Document metadata for author and title are REQUIRED.} You may not apply any script or macro to implementation of the title, author, and metadata information in your paper.
-
-\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata.
-The data in the metadata must be completely plain ascii.
-It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands.
-Type the title exactly as it appears on the paper (minus all formatting).
-Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma.
-You may also include keywords in the optional Keywords field.
-
-\begin{quote}
-\begin{scriptsize}\begin{verbatim}
-\begin{document}\\
-\maketitle\\
-...\\
-\bibliography{Bibliography-File}\\
-\bibliographystyle{aaai}\\
-\end{document}\\
-\end{verbatim}\end{scriptsize}
-\end{quote}
-
-\subsection{Commands and Packages That May Not Be Used}
-\begin{table*}[t]
-\centering
-\caption{Commands that must not be used}\smallskip
-\begin{tabular}{l|l|l|l}
-\textbackslash abovecaption & 
-\textbackslash abovedisplay & 
-\textbackslash addevensidemargin & 
-\textbackslash addsidemargin \\ 
-\textbackslash addtolength & 
-\textbackslash baselinestretch & 
-\textbackslash belowcaption & 
-\textbackslash belowdisplay \\ 
-\textbackslash break &
-\textbackslash clearpage & 
-\textbackslash clip & 
-\textbackslash columnsep \\ 
-\textbackslash float & 
-\textbackslash input & 
-\textbackslash input & 
-\textbackslash linespread \\ 
-\textbackslash newpage &
-\textbackslash pagebreak & 
-\textbackslash renewcommand & 
-\textbackslash setlength \\ 
-\textbackslash text height & 
-\textbackslash tiny & 
-\textbackslash top margin & 
-\textbackslash trim \\ 
-\textbackslash vskip\{- & 
-\textbackslash vspace\{- \\ 
-\end{tabular}
-%}
-\label{table1}
-\end{table*}
-
-\begin{table}[t]
-\caption{LaTeX style packages that must not be used.}\smallskip
-\centering
-%\resizebox{.95\columnwidth}{!}{
-\smallskip\begin{tabular}{l|l|l|l}
-authblk & babel & caption & cjk\\
-dvips & epsf & epsfig & euler\\
-float & fullpage & geometry & graphics\\
-hyperref & layout & linespread & lmodern\\
-maltepaper & natbib & navigator & pdfcomment\\
-pgfplots & psfig & pstricks & t1enc \\
-titlesec & tocbind & ulem\\
-\end{tabular}
-\label{table2}
-\end{table}
-
-There are a number of packages, commands, scripts, and macros that are incompatable with aaai20.sty.
-The common ones are listed in tables \ref{table1} and \ref{table2}.
-Generally, if a command, package, script, or macro alters floats, margins, fonts, sizing, linespacing, or the presentation of the references and citations, it is unacceptable.
-Note that negative vskip and vspace may not be used except in certain rare occurances, and may never be used around tables, figures, captions, sections, subsections, subsections, or references.
-
-\subsection{Page Breaks}
-For your final camera ready copy, you must not use any page break commands.
-References must flow directly after the text without breaks.
-Note that some conferences require references to be on a separate page during the review process.
-AAAI Press, however, does not require this condition for the final paper.
-
-\subsection{Paper Size, Margins, and Column Width}
-Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
-\begin{itemize}
-\item Top margin: .75 inches
-\item Left margin: .75 inches
-\item Right margin: .75 inches
-\item Bottom margin: 1.25 inches
-\end{itemize}
-
-The default paper size in most installations of \LaTeX{} is A4.
-However, because we require that your electronic paper be formatted in US letter size, the preamble we have provided includes commands that alter the default to US letter size.
-Please note that using any other package to alter page size (such as, but not limited to the Geometry package) will result in your final paper being returned to you for correction and payment of a resubmission fee.
-
-\subsubsection{Column Width and Margins.}
-To ensure maximum readability, your paper must include two columns.
-Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns.
-The aaai20.sty file will automatically create these columns for you.
-
-\subsection{Overlength Papers}
-If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods.
-Next, shrink the size of your graphics.
-Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment.
-For mathematical environments, you may reduce fontsize {\bf but not below 6.5 point}.
-You may also alter the size of your bibliography and tables by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
-right before the bibliography (the minimum size is \textbackslash fontsize\{9.0pt\}\{10.0pt\}.
-You may not use any commands that further reduce point size.
-Be careful when scaling tables and figures.
-Tables that do not fit in a single column, even after the font size reduction to 9 point, must be placed across double columns.
-If your table won't fit within the margins even in double columns, you must split it.
-We will not accept single (or double) column tables that have been scaled to anything below 9 point.
-
-Commands that alter page layout are forbidden.
-These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive).
-If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee.
-Other commands that are questionable and may cause your paper to be rejected include \textbackslash parindent, and \textbackslash parskip.
-Commands that alter the space between sections are forbidden.
-The title sec package is not allowed.
-Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted.
-Options for reducing the length of a paper include reducing the size of your graphics, cutting text, or paying the extra page charge (if it is offered).
-
-\subsection{Figures}
-Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.
-
-If you normally create your figures using pgfplots, please create the figures first, and then import them as pdfs with proper bounding boxes, as the bounding and trim boxes created by pfgplots are fragile, and not valid.
-
-When you include your figures, you must crop them \textbf{outside} of \LaTeX{}.
-The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear (and obscure whatever it is overlapping) when page numbers are applied or color space is standardized.
-Figures \ref{fig1}, and \ref{fig2} display some unwanted results that often occur.
-
-Do not use minipage to group figures.
-Additionally, the font and size of figure captions must be 10 point roman.
-Do not make them smaller, bold, or italic.
-(Individual words may be italicized if the context requires differentiation.)
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.9\columnwidth]{figure1} % Reduce the figure size so that it is slightly narrower than the column.
-Don't use precise values for figure width.This setup will avoid overfull boxes.
-\caption{Using the trim and clip commands produces fragile layers that can result in disasters (like this one from an actual paper) when the color space is corrected or the PDF combined with others for the final proceedings.
-Crop your figures properly in a graphics program -- not in LaTeX}
-\label{fig1}
-\end{figure}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.8\textwidth]{figure2} % Reduce the figure size so that it is slightly narrower than the column.
-\caption{Adjusting the bounding box instead of actually removing the unwanted data resulted multiple layers in this paper.
-It also needlessly increased the PDF size.
-In this case, the size of the unwanted layer doubled the paper's size, and produced the following surprising results in final production.
-Crop your figures properly in a graphics program.
-Don't just alter the bounding box.}
-\label{fig2}
-\end{figure*}
-
-% Using the \centering command instead of \begin{center} ... \end{center} will save space
-% Positioning your figure at the top of the page will save space and make the paper more readable
-% Using 0.95\columnwidth in conjunction with the
-
-\subsection{Type Font and Size}
-Your paper must be formatted in Times Roman or Nimbus.
-We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface.
-Sans serif, when used, should be Courier.
-Use Symbol or Lucida or Computer Modern for \textit{mathematics only.
-}
-
-Do not use type 3 fonts for any portion of your paper, including graphics.
-Type 3 bitmapped fonts are designed for fixed resolution printers.
-Most print at 300 dpi even if the printer resolution is 1200 dpi or higher.
-They also often cause high resolution imagesetter devices and our PDF indexing software to crash.
-Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts.
-Files containing those fonts (even in graphics) will be rejected.
-
-Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts.
-The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e.
-(Note that papers formatted in this way will still use Computer Modern for the mathematics.
-To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")
-
-If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader.
-The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document.
-If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.
-
-The default size for your type must be ten-point with twelve-point leading (line spacing).
-Start all pages (except the first) directly under the top margin.
-(See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.
-
-\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}
-
-If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts.
-They are available without charge from the American Mathematical Society:
-http://www.ams.org/tex/type1-fonts.html.
-
-\subsubsection{Nonroman Fonts}
-If your paper includes symbols in other languages (such as, but not limited to, Arabic, Chinese, Hebrew, Japanese, Thai, Russian and other Cyrillic languages), you must restrict their use to bit-mapped figures.
-
-\subsection{Title and Authors}
-Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading).
-This style is called ``mixed case," which means that means all verbs (including short verbs like be, is, using,and go), nouns, adverbs, adjectives, and pronouns should be capitalized, (including both words in hyphenated terms), while articles, conjunctions, and prepositions are lower case unless they directly follow a colon or long dash.
-Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading).
-(If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.
-
-\subsubsection{Formatting Author Information}
-Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display.
-In formatting your author information, however, you may not use a table nor may you employ the \textbackslash authorblk.sty package.
-For several authors from the same institution, please just separate with commas:
-
-\begin{quote}\begin{scriptsize}\begin{verbatim}
-\author{Author 1, ... Author n\\ 
-Address line \\ ... \\ Address line}
-\end{verbatim}\end{scriptsize}\end{quote}
-
-\noindent If the names do not fit well on one line use:
-
-\begin{quote}\begin{scriptsize}\begin{verbatim}
-\author{Author 1} ... \\
-{\bf \Large Author ... Author}\\ 
-Address line \\ ... \\ Address line
-}
-\end{verbatim}\end{scriptsize}\end{quote}
-
-\noindent For two (or three) authors from different institutions, use \textbackslash And:
-
-\begin{quote}\begin{scriptsize}\begin{verbatim}
-\author{Author 1\\ Address line \\ ... \\ Address line 
-\And ... \And Author n\\
-Address line\\ ... \\ Address line}
-\end{verbatim}\end{scriptsize}\end{quote}
-
-\noindent To start a separate ``row" of authors, use \textbackslash AND:
-
-If the title and author information does not fit in the area allocated, place
-\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
-after the \textbackslash documentclass line where \{\textit{height}\} is 2.5in or greater.
-(This one of the only allowable uses of the setlength command.
-Check with AAAI Press before using it elsewhere.)
-
-\subsubsection{Formatting Author Information --- Alternative Method}
-If your paper has a large number of authors from different institutions, you may use the following alternative method for displaying the author information.
-
-\begin{quote}\begin{scriptsize}\begin{verbatim}
-\author{AuthorOne},\textsuperscript{\rm 1} 
-AuthorTwo,\textsuperscript{\rm 2}
-AuthorThree,\textsuperscript{\rm 3}
-\\bf \Large AuthorFour,\textsuperscript{\rm 4} 
-AuthorFive, \textsuperscript{\rm 5}\\
-\textsuperscript{\rm 1}AffiliationOne, 
-\textsuperscript{\rm 2}AffiliationTwo, 
-\textsuperscript{\rm 3}AffiliationThree\\
-\textsuperscript{\rm 4}AffiliationFour, 
-\textsuperscript{\rm 5}AffiliationFive 
-\{email, email\}@affiliation.com,
-email@affiliation.com,
-email@affiliation.com, 
-email@affiliation.com
-\end{verbatim}\end{scriptsize}\end{quote}
-
-Note that you should break the author list before it extends into the right column margin.
-Put a line break, followed by   \textbackslash bf  \textbackslash Large to put the second line of authors in the same font and size as the first line (you may not make authors names smaller to save space.) Affiliations can be broken with a simple line break (\textbackslash  \textbackslash).
-\subsection{\LaTeX{} Copyright Notice}
-The copyright notice automatically appears if you use aaai20.sty. It has been hardcoded and may not be disabled.
-
-\subsection{Credits}
-Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
-\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
-For example:
-\begin{quote}
-\begin{small}
-\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
- supported by everybody.\}\}
-\end{small}
-\end{quote}
-Multiple \textbackslash thanks commands can be given.
-Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document.
-Note that the \textbackslash thanks command is fragile.
-You will need to use \textbackslash protect.
-
-Please do not include \textbackslash pubnote commands in your document.
-
-\subsection{Abstract}
-Follow the example commands in this document for creation of your abstract.
-The command \textbackslash begin\{abstract\} will automatically indent the text block.
-Please do not indent it further.
-{Do not include references in your abstract!}
-
-\subsection{Page Numbers}
-
-Do not \textbf{ever} print any page numbers on your paper. The use of \textbackslash pagestyle is forbidden.
-
-\subsection{Text }
-The main body of the paper must be formatted in black, ten-point Times Roman with twelve-point leading (line spacing).
-You may not reduce font size or the linespacing.
-Commands that alter font size or line spacing (including, but not limited to baselinestretch, baselineshift, linespread, and others) are expressly forbidden.
-In addition, you may not use color in the text.
-
-\subsection{Citations}
-Citations within the text should include the author's last name and year, for example (Newell 1980).
-Append lower-case letters to the year in cases of ambiguity.
-Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992).
-In the case of four or more authors, list only the first author, followed by et al.
-(Ford et al.
-1997).
-
-\subsection{Extracts}
-Long quotations and extracts should be indented ten points from the left and right margins.
-
-\begin{quote}
-This is an example of an extract or quotation.
-Note the indent on both sides.
-Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.
-
-\end{quote}
-
-\subsection{Footnotes}
-Avoid footnotes as much as possible; they interrupt the reading of the text.
-When essential, they should be consecutively numbered throughout with superscript Arabic numbers.
-Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.
-
-\subsection{Headings and Sections}
-When necessary, headings should be used to separate major sections of your paper.
-Remember, you are writing a short paper, not a lengthy book!
-An overabundance of headings will tend to make your paper look more like an outline than a paper.
-The aaai.sty package will create headings for you.
-Do not alter their size nor their spacing above or below.
-
-\subsubsection{Section Numbers}
-The use of section numbers in AAAI Press papers is optional.
-To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2.
-Section numbers should not be used in short poster papers.
-
-\subsubsection{Section Headings.}
-Sections should be arranged and headed as follows:
-
-\subsubsection{Acknowledgments.}
-The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish.
-Please acknowledge other contributors, grant support, and so forth, in this section.
-Do not put acknowledgments in a footnote on the first page.
-If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back.
-Please try to limit acknowledgments to no more than three sentences.
-
-\subsubsection{Appendices.}
-Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.
-
-\subsubsection{References}
-The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page).
-A sample list of references is given later on in these instructions.
-Please use a consistent format for references.
-Poorly prepared or sloppy references reflect badly on the quality of your paper and your research.
-Please prepare complete and accurate citations.
-
-\subsection{Illustrations and Figures}
-Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed.
-Do not group them together at the end of the paper.
-If placed at the top or bottom of the paper, illustrations may run across both columns.
-Figures must not invade the top, bottom, or side margin areas.
-Figures must be inserted using the \textbackslash usepackage\{graphicx\}.
-Number figures sequentially, for example, figure 1, and so on.
-
-The illustration number and caption should appear under the illustration. Labels, and other text with the actual illustration must be at least nine-point type.
-
-If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them.
-The epstopdf package will usually work for eps files.
-You will need to convert your ps files to PDF however.
-
-\subsubsection{Low-Resolution Bitmaps.}
-You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed.
-If they are color, they will become an indecipherable mess when converted to black and white.
-This is always the case with gif files, which should never be used.
-The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels.
-You can also enlarge files by manipulating them in software such as PhotoShop.
-Your figures should be 300 dpi when incorporated into your document.
-
-\subsubsection{\LaTeX{} Overflow.}
-\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin.
-If this happens, you need to scale the figure or table down, or reformat the equation.{ \bf Check your log file!} You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}).
-\textbf{Nothing is permitted to intrude into the margin or gutter.}
-
-The most efficient and trouble-free way to fix overfull boxes in graphics is with the following command:
-
-\begin{quote}
-\begin{small}
-\textbackslash resizebox\{.95\textbackslash columnwidth\}{!}\{
-\}
-\end{small}\end{quote}
-
-Be certain, however, that your figures remain legible without magnification.
-
-\subsubsection{Using Color.}
-Use of color is restricted to figures only.
-It must be WACG 2.0 compliant.
-(That is, the contrast ratio must be greater than 4.5:1 no matter the font size.) It must be CMYK, NOT RGB.
-It may never be used for any portion of the text of your paper.
-The archival version of your paper will be printed in black and white and grayscale.The web version must be readable by persons with disabilities.
-Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document.
-If you do include color figures, you must (1) use the CMYK (not RGB) colorspace and (2) be mindful of readers who may happen to have trouble distinguishing colors.
-Your paper must be decipherable without using color for distinction.
-
-\subsubsection{Drawings.}
-We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations.
-Do not use Microsoft Publisher.
-These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas.
-Shading should be 133 lines per inch if possible.
-Use Times Roman or Helvetica for all figure call-outs.
-\textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt.
-Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.
-
-\subsubsection{Photographs and Images.}
-Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 300 dpi.
-Do not prescreen images.
-
-\subsubsection{Resizing Graphics.}
-Resize your graphics \textbf{before} you include them with LaTeX.
-You may \textbf{not} use trim or clip options as part of your \textbackslash includegraphics command.
-Resize the media box of your PDF using a graphics program instead.
-
-\subsubsection{Fonts in Your Illustrations}
-You must embed all fonts in your graphics before including them in your LaTeX document.
-
-\subsection{References} 
-The AAAI style includes a set of definitions for use in formatting references with BibTeX.
-These definitions make the bibliography style fairly close to the one specified below.
-To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the AAAI Author Kit on the AAAI web site.
-Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:
-
-\begin{quote}
-\begin{small}
-\textbackslash bibliographystyle\{aaai\}
-\textbackslash bibliography\{bibfile1,bibfile2,...\}
-\end{small}
-\end{quote}
-
-Please note that you are required to use \textbackslash bibliographystyle\{aaai\} for your references.
-You may not use named, plain, apalike, acm, ieeetr, siam, chicago, or any other style.
-Use of natbib is also not acceptable.
-(In addition to natbib, the aaai20.sty file is also incompatible with the hyperref and navigator packages.
-If you use either, your references will be garbled and your paper will be returned to you.) If you used natbib commands, an imprecise workaround is available (although it does not always work).
-You may put the following in your preamble (after removing \textbackslash usepackage\{natbib\}
-
-\begin{quote}\small
-\textbackslash newcommand\{\textbackslash citet\}[1]\{\textbackslash citeauthor\{\#1\}~\textbackslash shortcite\{\#1\}\}
-\textbackslash newcommand\{\textbackslash citep\}\{\textbackslash cite\}
-\textbackslash newcommand\{\textbackslash citealp\}[1]\{\textbackslash citeauthor\{\#1\}~\textbackslash citeyear\{\#1\}\}
-\end{quote}
-
-References may be the same size as surrounding text.
-However, in this section (only), you may reduce the size to \textbackslash small if your paper exceeds the allowable number of pages.
-Making it any smaller than 9 point with 10 point linespacing, however, is not allowed.
-A more precise and exact method of reducing the size of your references minimally is by means of the following command: \begin{quote}
-\textbackslash fontsize\{9.8pt\}\{10.8pt\}
-\textbackslash selectfont\end{quote}
-
-\noindent You must reduce the size equally for both font size and line spacing, and may not reduce the size beyond \{9.0pt\}\{10.0pt\}.
-
-The list of files in the \textbackslash bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).
-
-The following commands are available for your use in citing references:
-\begin{quote}
-{\em \textbackslash cite:} Cites the given reference(s) with a full citation.
-This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\smallskip\\
-{\em \textbackslash shortcite:} Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\smallskip\\
-{\em \textbackslash citeauthor:} Cites the given reference(s) with just the author name(s) and no parentheses.\smallskip\\
-{\em \textbackslash citeyear:} Cites the given reference(s) with just the date(s) and no parentheses.
-\end{quote}
-
-Formatted bibliographies should look like the following examples.
-
-\smallskip \noindent \textit{Book with Multiple Authors}\\
-Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.
-
-\smallskip \noindent \textit{Journal Article}\\
-Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.
-
-\smallskip \noindent \textit{Magazine Article}\\
-Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
-Clancey, W.
-J.
-1983.
-Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education.
-In \textit{Proceedings of the Eighth International Joint Conference on Artificial Intelligence,} 556--560.
-Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
-Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.
-
-\smallskip \noindent \textit{University Technical Report}\\
-Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.
-
-\smallskip \noindent \textit{Dissertation or Thesis}\\
-Clancey, W. J. 1979. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.
-
-\smallskip \noindent \textit{Forthcoming Publication}\\
-Clancey, W. J. 2021. The Engineering of Qualitative Models. Forthcoming.
-
-For the most up to date version of the AAAI reference style, please consult the \textit{AI Magazine} Author Guidelines at \url{https://aaai.org/ojs/index.php/aimagazine/about/submissions#authorGuidelines}
-
-\section{Proofreading Your PDF}
-Please check all the pages of your PDF file.
-The most commonly forgotten element is the acknowledgements --- especially the correct grant number.
-Authors also commonly forget to add the metadata to the source, use the wrong reference style file, or don't follow the capitalization rules or comma placement for their author-title information properly.
-A final common problem is text (expecially equations) that runs into the margin.
-You will need to fix these common errors before submitting your file.
-
-\section{Improperly Formatted Files }
-In the past, AAAI has corrected improperly formatted files submitted by the authors.
-Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb (we are charged double for papers that require reformatting).
-Consequently, if your file is improperly formatted, it will probably be returned to you by the outside Production agency.
-If that happens, you will be required to fix your file and pay a resubmission fee.
-
-\subsection{\LaTeX{} 209 Warning}
-If you use \LaTeX{} 209 your paper will be returned to you unpublished. Convert your paper to \LaTeX{}2e.
-
-\section{Naming Your Electronic File}
-We require that you name your \LaTeX{} source file with the last name (family name) of the first author so that it can easily be differentiated from other submissions.
-Complete file-naming instructions will be provided to you in the submission instructions.
-
-\section{Submitting Your Electronic Files to AAAI}
-Instructions on paper submittal will be provided to you in your acceptance letter.
-
-\section{Inquiries} 
-If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below.
-If you have technical questions about implementation of the aaai style file, please contact an expert at your site.
-We do not provide technical support for \LaTeX{} or any other software package.
-To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.
-
-\begin{quote}
-\noindent AAAI Press\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\ 
-\textit{Telephone:} (650) 328-3123\\ 
-\textit{E-mail:} See the submission instructions for your particular conference or event.
-\end{quote}
-
-\section{Additional Resources}
-\LaTeX{} is a difficult program to master.
-If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems.
-(It was written for another purpose, but it has general application as well).
-It is available at www.ctan.org in the tex-archive.
-
-\section{ Acknowledgments}
-AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton.
-We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.
-
-The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press.
-Bibliography style changes were added by Sunil Issar.
-\verb+\+pubnote was added by J.
-Scott Penberthy.
-George Ferguson added support for printing the AAAI copyright slug.
-Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.
-
-\bigskip
-\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!
-
-\end{document}

### 2020-07-24 Documents/ChaoticDynamics/AAAI Submission/main.tex
minor mods

@@
 Note that the comma should be placed BEFORE the superscript for optimum readability
-Do we give the address?\\
+Do we give the address? \fb{normally the submission is blind.}\\
 publications20@aaai.org % email address must be in roman text type, not monospace or sans serif
 }
+
+\input{macros}
+
  \begin{document}
@@
 
+\fb{possibly add research question below.}
+
+\subsection{Related Work}
+
+\fb{feel free to add the Related Work}
+
 \section{Preliminaries}
 
-In this section we will establish some of the preliminaries which are required to follow the subsequent sections.
-The first is 'Dynamical Behaviours' which considers the evolution of agent strategies as they learn on an iterated game.
-This study aims to classify, based on the agent parameters and the payoff matrices, which of these behaviours will be seen.
-The second is 'Dynamics of Q-Learning'.
-These are a set of equations which model the aforementioned strategy evolution.
-It is on these dynamics that we will perform our analysis.
+In this section we will establish some of the preliminaries which are
+required to follow the subsequent sections. The first is 'Dynamical
+Behaviours' \fb{maybe italics?} which considers the evolution of agent strategies as they
+learn on an iterated game. This study aims to classify, based on the
+agent parameters and the payoff matrices, which of these behaviours
+will be seen. The second is 'Dynamics of Q-Learning'. These are a set
+of equations which model the aforementioned strategy evolution. It is
+on these dynamics that we will perform our analysis.
 
@@
 
-    It has long been established that, upon lifting the strong
+    It has long been established \fb{add refs?} that, upon lifting the strong
     assumptions made by traditional game theory (such as the
@@
         exponentially. b-d drawn from \cite{Sanders2018}}
+\fb{one figure from a reference is fine, but two maybe are not necessary.}
     \end{figure}
@@
     Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
-    memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
+    memory and intensity of choice parameters respectively \fb{what are $\alpha$ and $\tau$ exactly?}. Agent 1 takes action $i$ with probability
     $x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
@@
     predict the expected behaviour of Q-Learning agents, as shown in Figure 
-    \ref{fig::TuylsExperiments}.
+    \ref{fig::TuylsExperiments} \fb{discuss limitations as well}.
 
@@
     learning on an iterated game? In other words, under what parameter selections are we likely to
-    see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?
+    see convergence to unique equilibria, multiple equilibria, limit cycles or chaos? \fb{state this explicitly as a research question, possibly in the contribution.}
 
 \section{Stability and Chaos in Multi-Agent Reinforcement Learning}
+
+\fb{what will be the content of this section? is it the derivations?}
 
@@
 $\alpha$ whilst keeping $\tau$ fixed.
-The purpose of this experiment was to determine a heuristic estimate for the Liapunov exponent, which determines whether initial conditions which start close to one another will converge or diverge from each other.
-The former indicates a stable system (in the sense of Liapunov) whilst the latter signals instability.
+The purpose of this experiment was to determine a heuristic estimate for the Lyapunov exponent, which determines whether initial conditions which start close to one another will converge or diverge from each other.
+The former indicates a stable system (in the sense of Lyapunov) whilst the latter signals instability \fb{add refs to all of this?}.
 
@@
     \caption{$\tau = 0.05$, $\gamma = 0.75$, $\alpha \in [0, 1]$, $\Gamma \in [-1, 1]$. Each
-    simulation is run for 1 $\times 10^4$ iterations and the Liapunov exponent is determined. For each
+    simulation is run for 1 $\times 10^4$ iterations and the Lyapunov exponent is determined. For each
     combination of $\alpha$, $\Gamma$ the game is played 100 times, each with random payoff matrices
-    and initial conditions. The average liapunov exponent is determined and shown in the heatmap.
+    and initial conditions. The average Lyapunov exponent is determined and shown in the heatmap.
     \label{fig::NumericalExperiments}}
@@
 
+\fb{Liapunov $\to$ Lyapunov}
+
 \section{Conclusion}

### 2020-08-12 Code/EGT-RL/TwoPlayerCode/LiapunovExponent.py
Generalised Code to p-players

@@ -1,18 +1,24 @@
 import numpy as np
+import itertools
+import scipy.sparse as sps
 import matplotlib.pyplot as plt
 from time import time
 from tqdm import tqdm
 
+
 alpha = .1
 gamma = .1
 Gamma = 0.1
-tau = 1
+tau = 0.05
 
 delta_0 = 1e-3
 nSim = 5
-nIter = 1e5
+nIter = int(1e4)
 
-def generateGame(gamma, nAct):
+nPlayers = 3
+nActions = 2
+
+def generateGames(gamma, nSim, nAct, nPlayers):
     """
     Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
 
@@ -22,69 +28,81 @@ def generateGame(gamma, nAct):
     [reward1s, reward2s]: list of payoff matrices
     """
 
-    nElements = nAct ** 2  # number of payoff elements in the matrix
+    nElements = nAct ** nPlayers  # number of payoff elements in a player's matrix
 
-    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+    cov = sps.lil_matrix(sps.eye(nPlayers * nElements))
+    idX = list(itertools.product(list(range(1, nAct + 1)), repeat=nPlayers)) * nPlayers
+    for idx in range(nElements):
+        for b in range(1, nPlayers):
+            rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
+            cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
 
-    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+    cov = cov.toarray()
 
-    reward1s = rewards[0:nElements].reshape((nAct, nAct))
-    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
+    allPayoffs = np.zeros(shape=(nPlayers, nElements))
 
-    return [reward1s, reward2s]
+    for i in range(nSim):
+        rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
+        each = np.array_split(rewards, nPlayers)
[…]

### 2020-08-26 Documents/ChaoticDynamics/AAAI Submission/main.tex
Generalised Code to p-players
Included NR Method

@@
 
+In this study, we will be considering the question: under what parameter selections are is a
+multi-agent system, which is trained on an iterated game using Q-Learning, likely to converge to an
+equilibrium as opposed to complex behaviours? In investigating this question, we will make the
+following assumptions:
+
+\begin{enumerate}
+    \item There are a finite set of agent, though the length $p$ of the set is arbitrary. 
+    \item The agents have a large, but discrete, strategy space: during the theoretical study, we
+    will make the assumption that the number of actions $N \rightarrow \infty$.
+    \item The agents are homogeneous. This requires that all agents have the same parameters and are
+    trained using the same algorithm. Since this is typically the case in reinforcement learning
+    studies, it is not an unreasonable assumption, but does present an interesting avenue for future
+    work.
+    \item The agents are trained on stateless, normal form games (i.e. the environment is static).
+\end{enumerate}
+
+The parameters that we will consider are:
+
+\begin{enumerate}
+    \item $\alpha \in [0, 1]$: the \em{step length}. Low values of $\alpha$ denote smaller
+    updates. Heuristically we can consider this to be the memory of the agent: lower $\alpha$
+    denotes longer memory.
+    \item $\tau in [0, \infty)$: the \em{intensity of choice}, as termed by Sanders et al. 
+    \cite{Sanders2018}. This is sometimes written as $\beta$ in the literature \cite{Sutton2018}.
+    $\tau = 0$ results in all actions being selected with equal probability, regardless of their
+    Q-value, whilst $\tau \rightarrow \infty$ results in the action with the highest Q-value chosen
+    at every step. This may be considered the \em{exploration-exploitation parameter}. For greater
+    details into these parameters, the interested reader should consult \cite{Sutton2018}.
+    \item $\Gamma \in [-1, p-1]$: the \em{payoff correlation}. This term controls the choice of
+    covariance matrix from which random payoff matrices are drawn. $\Gamma = -1$ indicates a zero
+    sum game, in which the sum of payoffs for a given action across all agents is 0, resulting in a
+    purely competitive game. $\Gamma = p-1$ gives a purely co=operative game in which all agents
+    share the same payoffs. The manner in which a game is generated from the choice of $\Gamma$ is
+    described in Section \ref{sec::Theory} and follows the same procedure as outlined in \cite{Sanders2018}.
+\end{enumerate}
+
 \subsection{Related Work}
@@
 In this section we will establish some of the preliminaries which are
-required to follow the subsequent sections. The first is 'Dynamical
-Behaviours' \fb{maybe italics?} which considers the evolution of agent strategies as they
+required to follow the subsequent sections. The first is \em{Dynamical Behaviours} \fb{maybe italics?} 
+which considers the evolution of agent strategies as they
 learn on an iterated game. This study aims to classify, based on the
 agent parameters and the payoff matrices, which of these behaviours
-will be seen. The second is 'Dynamics of Q-Learning'. These are a set
+will be seen. The second is \em{Dynamics of Q-Learning}. These are a set
 of equations which model the aforementioned strategy evolution. It is
@@
 
-    It has long been established \fb{add refs?} that, upon lifting the strong
+    It has long been established that, upon lifting the strong
     assumptions made by traditional game theory (such as the
@@
     predict the expected behaviour of Q-Learning agents, as shown in Figure 
-    \ref{fig::TuylsExperiments} \fb{discuss limitations as well}.
+    \ref{fig::TuylsExperiments}. Upon examination of the derivation in \cite{Tuyls2006AnGames}, it
+    is clear that the dynamics generated give the expected behaviour and, therefore , cannot account
+    for transients. It is also interesting to note that the dynamics (\ref{eqn::EOM}) do not include
+    the parameter $\gamma$, which moderates the Q-update. The implication is that this has no effect
+    on the expected behaviour of the system. \textbf{Shall I include some tests to confirm this?
+    It does turn out to be mostly true, the value of $\gamma$ doesn't affect the overall behaviour,
+    but rather results in smaller or larger steps. What do you think?}.
+    as well}.
 
@@
 
-\section{Stability and Chaos in Multi-Agent Reinforcement Learning}
+\section{Determination of Phase Transition Line} \label{sec::Theory}
 
@@
 The purpose of this experiment was to determine a heuristic estimate for the Lyapunov exponent, which determines whether initial conditions which start close to one another will converge or diverge from each other.
-The former indicates a stable system (in the sense of Lyapunov) whilst the latter signals instability \fb{add refs to all of this?}.
+The former indicates a stable system (in the sense of Lyapunov) whilst the latter signals instability \cite{Strogatz2000}.
 

### 2020-08-26 Code/EGT-RL/TwoPlayerCode/LiapunovExponent.py

@@ -1,90 +1,107 @@
 import numpy as np
+import itertools
+import scipy.sparse as sps
 import matplotlib.pyplot as plt
 from time import time
 from tqdm import tqdm
 
+
 alpha = .1
 gamma = .1
 Gamma = 0.1
-tau = 1
+tau = 0.05
 
 delta_0 = 1e-3
-nSim = 5
-nIter = 1e5
+nSim = 10
+nIter = int(1e3)
+nTests = 10
 
-def generateGame(gamma, nAct):
+nPlayers = 2
+nActions = 5
+
+def generateGames(gamma, nSim, nAct, nPlayers):
     """
     Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
-
     gamma: Choice of co-operation parameter
     nAct: Number of actions in the game
-
     [reward1s, reward2s]: list of payoff matrices
     """
 
-    nElements = nAct ** 2  # number of payoff elements in the matrix
+    nElements = nAct ** nPlayers  # number of payoff elements in a player's matrix
 
-    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+    cov = sps.lil_matrix(sps.eye(nPlayers * nElements))
+    idX = list(itertools.product(list(range(1, nAct + 1)), repeat=nPlayers)) * nPlayers
+    for idx in range(nElements):
+        for b in range(1, nPlayers):
+            rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
+            cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
 
-    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+    cov = cov.toarray()
 
-    reward1s = rewards[0:nElements].reshape((nAct, nAct))
-    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
+    allPayoffs = np.zeros(shape=(nPlayers, nElements))
 
-    return [reward1s, reward2s]
+    for i in range(nSim):
+        rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
+        each = np.array_split(rewards, nPlayers)
[…]

### 2020-08-26 Code/EGT-RL/TwoPlayerCode/NumericalInt.py

@@ -1,0 +1,80 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+# q = int Dz x^2
+# 1 = int Dz x
+# X = 1/q int dx/dz
+
+# initialise values of z
+# for every z initialise a guess of x and x_d where x_d differs from x by some delta
+# use these choices for x to determine X, p, q
+# evaluate f and f' at this guess (f' given by finite approximation with x_d)
+# update x using Newton Raphson with all the finite approximations
+
+# determine q and X off that
+
+def getOrderParams(Xs, dz, Zs):
+    q = np.sum((Xs ** 2) * dz)
+    dx = np.array([Xs[i + 1] - Xs[i] for i in range(len(Zs[:-1]))])
+    X = (1 / q) * np.sum((dx/dz) * dz)
+
+    return q, X
+
+def normaliseX(Xs):
+    return abs(abs(Xs)/np.sum(abs(Xs)))
+
+nPlayers = 3
+nActions = 2
+
+allOrders = np.zeros((10, 10, 2))
+
+idx1 = 0
+for alpha in np.linspace(0, 1, num=10):
+    idx2 = 1
+    for Gamma in np.linspace(-1, 1, num=10):
+
+        # alpha = 0.1
+        tau = 1
+        # Gamma = 1
+        talpha = alpha/nActions
+        ttau = tau/np.sqrt(nActions ** (nPlayers - 1))
+
+        dz = 1e-1
+
+        Zs = np.arange(-20, 20, dz)
+
+        p = lambda xi, dz, Xs: np.sum((Xs * np.log(Xs/Xs[xi])) * dz)
+        F = lambda xi, z, Xs, q, n, chi: (alpha**2) * (ttau ** 2) * Gamma * Xs[xi] * (q**(n-1)) * chi + alpha * ttau * (q**(n/2)) * z + talpha * tau * (q**((n+1)/2)) * z + talpha * p(xi, dz, Xs)
+
+        Xs = normaliseX(np.random.random((len(Zs), )))
+        Xd = normaliseX(np.random.random((len(Zs), )))
+
+        allF = []
+        stopCond = False
+        tol = 1e-5
+
+
+        for i in range(1000):
+
+            q, chi = getOrderParams(Xs, dz=dz, Zs=Zs)
+            qd, chid = getOrderParams(Xd, dz=dz, Zs=Zs)
[…]

### 2020-08-26 Code/EGT-RL/TwoPlayerCode/LiapunovExponent.py
Redone Liapunov Code

@@ -9,23 +9,15 @@ from tqdm import tqdm
 alpha = .1
 gamma = .1
 Gamma = 0.1
-tau = 0.05
+tau = 1
 
 delta_0 = 1e-3
-<<<<<<< HEAD
 nSim = 10
 nIter = int(1e3)
 nTests = 10
 
 nPlayers = 2
 nActions = 5
-=======
-nSim = 5
-nIter = int(1e4)
-
-nPlayers = 3
-nActions = 2
->>>>>>> 36f29f6d9cb7ef58d405114de30b9148e85c94aa
 
 def generateGames(gamma, nSim, nAct, nPlayers):
     """
@@ -43,7 +35,6 @@ def generateGames(gamma, nSim, nAct, nPlayers):
         for b in range(1, nPlayers):
             rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
             cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
-<<<<<<< HEAD
 
     cov = cov.toarray()
 
@@ -54,18 +45,6 @@ def generateGames(gamma, nSim, nAct, nPlayers):
         each = np.array_split(rewards, nPlayers)
         allPayoffs = np.dstack((allPayoffs, np.array(each)))
 
-=======
-
-    cov = cov.toarray()
-
-    allPayoffs = np.zeros(shape=(nPlayers, nElements))
-
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
-        each = np.array_split(rewards, nPlayers)
-        allPayoffs = np.dstack((allPayoffs, np.array(each)))
-
->>>>>>> 36f29f6d9cb7ef58d405114de30b9148e85c94aa
     return allPayoffs
 
 
@@ -79,19 +58,11 @@ def getActionProbs(qValues):
 def qUpdate(qValues, payoffs):
     idX = list(itertools.product(list(range(0, nActions)), repeat=nPlayers))
     actionProbs = getActionProbs(qValues)
-<<<<<<< HEAD
     bChoice = np.array([[np.random.choice(list(range(nActions)), p=actionProbs[p, :, s]) for s in range(nSim)] for p in range(nPlayers)])
 
[…]

### 2020-10-02 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Added AAMAS Submission

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% LaTeX Template for AAMAS-2021 (based on sample-sigconf.tex)
%%% Prepared by Natasha Alechina and Ulle Endriss (version 2020-08-06)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Start your document with the \documentclass command.
%%% Use the first variant below for the final paper.
%%% Use the second variant below for submission.

\documentclass[sigconf]{aamas} 
%\documentclass[sigconf,anonymous]{aamas}

%%% Load required packages here (note that many are included already).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\xmu}[2]{x_{#1_#2}^{#2}(t)}
\newcommand{\payoff}[2]{P^{#2}_{#1_#2, #1_{-#2}}}

\newcommand{\txmu}[2]{\tilde{x}_{#1_#2}^{#2}(t)}
\newcommand{\tpayoff}[2]{\tilde{P}^{#2}_{#1_#2, #1_{-#2}}}
\newcommand{\talpha}{\tilde{\alpha}}
\newcommand{\ttau}{\tilde{\tau}}
\newcommand{\htau}{\hat{\tau}}

\newcommand{\xfixed}{x_\infty}
\newcommand{\ezerof}{\eta_{0, \infty}}
\newcommand{\eonef}{\eta_{1, \infty}}

\newcommand{\xpert}{\hat{x}(t)}
\newcommand{\xpertdash}{\hat{x}(t')}
\newcommand{\ezeropert}{\hat{\eta}_0(t)}
\newcommand{\eonepert}{\hat{\eta}_1(t)}

\newcommand{\ah}[1]{\textcolor{red}{AH: #1}}
\usepackage{xcolor} % REMOVE THIS AT THE END
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% AAMAS-2021 copyright block (do not change!)

\setcopyright{ifaamas}
\acmConference[AAMAS '21]{Proc.\@ of the 20th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2021)}{May 3--7, 2021}{London, UK}{U.~Endriss, A.~Now\'{e}, F.~Dignum, A.~Lomuscio (eds.)}
\copyrightyear{2021}
\acmYear{2021}
\acmDOI{}
\acmPrice{}
\acmISBN{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Use this command to specify your EasyChair submission number.
%%% In anonymous mode, it will be printed on the first page.

\acmSubmissionID{???}

%%% Use this command to specify the title of your paper.

\title[InstabilityinMARL]{Instability in Multi Agent Reinforcement Learning}

%%% Provide names, affiliations, and email addresses for all authors.

\author{Aamal Hussain}
\affiliation{
  \institution{Secret Intelligence Service}
  \city{Vauxhall, London}}
\email{agent007@mi6.gov.uk}

\author{Francesco Belardinelli}
\affiliation{
  \institution{Analytical Engines, Inc.}
  \city{Ockham Park}
  \state{Surrey}}
\email{ada@analytical-engines.com}

\author{Alan M. Turing}
\affiliation{
  \department{Computing Machine Laboratory}
  \institution{Victoria University of Manchester}}
\email{amt@vum.ac.uk}

%%% Use this environment to specify a short abstract for your paper.

\begin{abstract}
Modelling the dynamics of Q-Learning is an active and important topic for the sake of developing an {\em a priori} understanding of Reinforcement Learning. In this paper, we use methods from evolutionary game theory to analyse the stability of Q-Learning in $p$-player games, where payoffs are randomly generated. We determine the parameter range in which Q-Learning is expected to settle to a stable fixed point and the range in which the dynamics are unstable.

This study allows for parameters to be appropriately chosen to ensure the safe convergence of a learning algorithm and as a first step towards understanding the range of behaviours that can be displayed by learning using the Q-Learning algorithm. We validate our theoretical results through numerical simulation and show that, within the bounds of experimental error, the region of instability can be characterised by the learning dynamics. We also note a few important implications of the study: 1) convergence is rare in Multi-Agent Reinforcement Learning. It is found that convergence to a unique fixed point occurs for simple games with 2 players and 2 actions. However, once either of these increase, convergence no longer occurs. 2) the existence of instability is not affected by the structure of the game itself. In fact, at least in the competitive regime, the payoff structure does not affect whether the game converges or not. 3) Convergence is guaranteed for low step-lengths but rapidly decreases as the step length increases. 
\end{abstract}

%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
%%% Please replace this example with code appropriate for your own paper.

%%% Use this command to specify a few keywords describing your work.
%%% Keywords should be separated by commas.

\keywords{Auction Theory, Reinforcement Learning, Social Simulation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Include any author-defined commands here.

\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%% The following commands remove the headers in your paper. For final 
%%% papers, these will be inserted during the pagination process.

\pagestyle{fancy}
\fancyhead{}

%%% The next command prints the information defined in the preamble.

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Single agent reinforcement learning (RL) is a well established framework for allowing agents to learn optimal strategies when trained on an iterated task 
For a particularly strong example of this see \cite{Vinyals2019}. However, for the realisation of complex tasks, such as air traffic control, market negotiations and multi-robot coordination, it is required that the system be modelled as a multi-agent system (MAS). Such systems are not as well understood since a given agent is tasked with optimising a reward function which depends not only on a non-stationary environment, but also on the actions of other, possibly loosely coupled, agents \cite{SchwartzMulti-agentApproach}.

It is, therefore, of paramount importance to develop a strong theoretical understanding of multi-agent reinforcement learning (MARL) to allow an {\em a-priori} understanding of the behaviour of a given learning algorithm. Fortunately, the study of MAS is not unique to the field of AI and has been extensively studied from the point of view of economics and game theory as well \cite{ShohamMultiagentFoundations}. In particular, the study of evolutionary game theory (EGT) considers the problem of a MAS which is repeatedly exposed to an iterated game. 
his idea shares a strong resemblance with MARL and, in fact, in \cite{Tuyls2006AnGames}, it was shown that, techniques from EGT may be fruitfully used to analyse Q-Learning \cite{Sutton2018}.

An important result in modelling such multi agent systems from the EGT perspective is that, when games are learnt and the assumptions of rationality and perfect information are lifted, games may not converge to an equilibrium. Instead, as shown in \cite{Sanders2018}, the dynamics may be more complex, and even chaotic (see Section~\ref{sec::DynamicalBehaviours}). The present work further describes that the emergence of such behaviours depends on the parameters of the games and the learning algorithm. For the analysis of multi-agent systems whose behaviour is inter-dependent, it is desirable that the system be such that the game convergence to a stable equilibrium. Without this, it is inherently impossible to predict the outcome of learning.

\paragraph{Contribution}
In this study, we will be considering the question: under what choice of parameters is a
multi-agent system, which is trained on an iterated game using Q-Learning, likely to converge to an
equilibrium as opposed to displaying complex, or chaotic behaviours? In investigating this question, we will make the
following assumptions:

\begin{enumerate}
    \item There are a finite set of agent, though the size $p$ of the set is arbitrary. 
    \item The agents have a large, but discrete, strategy space: during the theoretical study, we
    will make the assumption that the number of actions $N$ goes to infinity.
    \item The agents are homogeneous. This requires that all agents have the same parameters and are
    trained using the same algorithm. Since this is typically the case in reinforcement learning
    studies, it is not an unreasonable assumption, but does present an interesting avenue for future
    work.
    \item The agents are trained on stateless, normal form games (i.e. the environment is static).
\end{enumerate}

\subsection{Related Work}

In this section we present an overview of the vast literature which considers the study of Reinforcement Learning (RL) from an evolutionary game dynamics perspective, as well as touching upon some important results and research within the field of game dynamics.

\paragraph{Evolutionary Game Dynamics} The theory of evolutionary game dynamics \cite{Morgenstern44} considers the case in which agents must repeatedly interact with one another. The outcome of this interaction depends on a payoff matrix; 'strong' strategies which maximise the reward are promoted whilst 'weaker' strategies diminish. The \textit{replicator dynamic} models this behaviour, and allows one to determine whether, after a number of iterations, the game is likely to converge to some fixed equilibrium and, if so, the probabilities with which strategies are played in this equilibrium. \cite{ShohamMultiagentFoundations} provides an excellent introduction to the replicator dynamic for the interested reader.

Analyses have been performed from the point of view of the replicator dynamic towards the various types of behaviours that can emerge from iterated games. Such games are considered imperfect, in that agents do not make decisions based on a rational process derived from perfect information of the game, but rather through attempting to anticipate their opponents' behaviour based on experience \cite{Galla2011}. \cite{Imhof2005} presents the observation that, in the game of Prisoner's Dilemma, cyclic behaviour emerges in which the optimal strategy cycles across defection, cooperation and tit-for-tat despite defection being the NE. \cite{Galla2011} builds on this notion by showing that, in fact, such behaviour is highly dependent on the presence of memory loss in the system. In the absence of memory loss, the learning converges to the NE as expected. However, as this parameter is increased, the stability of the NE is removed and other stable points are created.

Taking this notion even further, \cite{Sato2002} presents a study in which it is shown that learning, even on a simple two player game (they choose rock-paper-scissors), demonstrates Hamiltonian chaos (see \cite{Strogatz2000} for details on chaos). In this regime, there are no stable equilibria and the game will never converge to an equilibrium. To analyse this phenomena further, \cite{Galla2013} describes an investigation of two-person iterated games in which the players learn using \textit{Experience Weighted Attraction} (EWA), a form of reinforcement learning whose analysis typically falls under the purview of experimental economics \cite{Camerer2009}. Through numerical simulations, the authors were able to show that, once again, the emergence of chaos and cycles, is dependent on the choice of parameters. A rigorous theoretical analysis, which follows the techniques presented in \cite{Opper1992}, of the replicator dynamic corresponding to EWA presented a method for characterising the regions in parameter space in which a game is likely to converge, exhibit chaos or limit cycles. More recently, the authors presented an extended study in \cite{Sanders2018}, in which this analysis was extended towards a generic $p$-player game, which showed that chaotic dynamics are more likely to be observed as the number of players \textit{p} increases, whilst a similar study \cite{Pangallo2019} indicates that an increase in the number of actions $N$ in the strategy space similarly increases the likelihood of unstable behaviour.

It is evident, therefore, that in the case of learning on iterated games, convergence to stable equilibria cannot be taken for granted and, in fact, is rare. It would therefore be fruitful to bring these analyses from EGT to better understand Reinforcement Learning from an AI perspective.

\paragraph{Dynamics of RL} The earliest example of such an analysis may be found in \cite{Borgers1997}, in which the \textit{Cross Learning} algorithm is analysed and it is shown that, in a continuous time limit, the learning model converges to the replicator dynamic. Adapting this work for the benefit of the AI community, the authors of \cite{Tuyls2006AnGames} similarly derive a relation between Q-Learning (see \cite{Barber2012}) and the replicator dynamic. In doing so, the authors present an evolutionary model which accurately predicts the dynamics of Q-Learning. This sprung forward a vast array of literature which perform similar derivations for various reinforcement learning algorithms. \cite{Bloembergen2015} presents an excellent review of these for the interested reader. In particular it should be noted that many of these studies focus on normal form games, in which the payoff matrix does not change (i.e. the environment is static). Recent work, such as \cite{Hennes2008}, extends this work towards multi-state games, though this is restricted to 2 state games. Similarly, \cite{Galstyan2013}, extends the work in \cite{Tuyls2006AnGames} towards games with continuous action spaces. Most recently, \cite{Hu2019} considers Q-learning in the mean-field limit, in which the strategies of populations of agents are considered.

The analysis of RL from an EGT perspective is a growing field, with a significant scope for expansion, as is discussed in our conclusion. 
However, the relation between RL and the replicator dynamic allows for the assumption of convergence in reinforcement learning to be lifted and instead for the emergence of cyclic behaviour and chaos to be examined. In particular, this study aims to perform a similar analysis to that in \cite{Sanders2018} and establish the regions in parameter space in which Q-Learning converges to stable fixed points and where the learning is unstable. To the best of our knowledge, no such work exists in this context. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminaries}

In this section we \st{will} establish some of the preliminaries which are
required to follow the subsequent sections. The first is \textit{dynamical behaviours}, 
which considers the evolution of agent strategies as they
learn on an iterated game. This study aims to classify, based on the
agent parameters and the payoff matrices, which of these behaviours
will be observed. The second is \textit{dynamics of Q-Learning}, which are a set
of equations that model the aforementioned strategy evolution. It is
on these dynamics that we \st{will} perform our analysis.

\subsection{Dynamical Behaviours}
\label{sec::DynamicalBehaviours}

    As discussed in the previous section, when learning on iterated games, player
    strategies may exhibit much more complex behaviour than
    convergence to a Nash Equilibrium (NE), \st{These behaviours include:}
    including convergence to a unique
    equilibrium (though not always to an NE), convergence to one of
    multiple equilibria, limit cycles and chaos. These behaviours are
    illustrated in Fig.\ref{fig::DynamicalBehaviours}. To be able to predict the behaviour of a learning algorithm, it should ideally converge to a stable equilibrium
    although it is still possible to study systems with multiple
    equilibria or limit cycles \cite{Strogatz2000}. However, it would
    be difficult to control systems whose dynamics are governed by
    chaos (though research into controlling chaos is ongoing and rife
    with opportunity \cite{Fradkov2009}). It would, therefore, be a useful endeavour to
    determine the conditions under which these sorts of behaviours
    arise.

    \begin{figure}[h]
        \centering

        \begin{subfigure}[b]{0.9 \textwidth}
        \includegraphics[width=0.5\textwidth]{Figures/DynamicalBehavioursTop.png}
        \end{subfigure}

        \begin{subfigure}[b]{0.9 \textwidth}
        \includegraphics[width=0.5\textwidth]{Figures/DynamicalBehaviourschaos.png}
        \end{subfigure}

        \caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
       displayed
        by learning agents. Here the $x$-axis (resp.~$y$-axis) is the probability with which agent 1 (resp.~agent 2) chooses a given action. a) Figure drawn from \cite{Tuyls2006AnGames}.
        Convergence
        to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
        that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
        d) Chaotic behaviour, here small deviations in the initial conditions can grow
        exponentially. b-d drawn from \cite{Sanders2018}}

    \end{figure}

\subsection{Dynamics of Q-Learning}

The behaviour of a system may be studied given a model of its
dynamics. It is through this process that a wide array of physical
systems, from harmonic pendulums to geophysical fluids, can be
understood. A growing body of research aims to understand
multi-agent reinforcement learning through the lens of its
dynamics. In this light, \cite{Tuyls2006AnGames} presents of derivation of a continuous time dynamical
system describing how agents following a Q-Learning approach adjust the probabilities of choosing actions
as they iteratively play a game. The Q-Learning approach considered requires an agent to choose an action $i$ at step $k+1$ with probability

\begin{equation}
    x_i(k) = \frac{e^{\tau Q_i(k)}}{\sum_j e^{\tau Q_j(k)}}
\end{equation}

where $\tau$ is the \textit{intensity of choice} as defined at the end of this section and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to
%
\begin{equation}
\label{eqn::Qupdate}
    Q_i(k+1) = (1 - \alpha) Q_i(k) + \alpha (r + \gamma \max_j Q_j(k))
\end{equation}

where $\alpha$ is the \textit{step length} parameter defined below, $r$ is the immediate reward received and $\gamma$ is a discount factor.

Through their analysis, Tuyls et al. were able to
arrive at the following dynamical model of Multi-Agent Q-Learning
%
\begin{subequations}
\label{eqn::EOM}
    \begin{equation}
        \frac{\dot{x}_i(t)}{x_i(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
        + \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
    \end{equation}
    \begin{equation}
        \frac{\dot{y}_i(t)}{y_i(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
        + \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
    \end{equation}
\end{subequations}

Here, $\alpha$ and $\tau$ are the parameters of the agent as described at the end of this section. Agent 1 (resp.~agent 2) takes action $i$ with probability
$x_i$ (resp.~$y_j$).
\st{while Agent 2 takes action $j$ with probability $y_j$}. When these actions are taken, the agents
receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
predict the expected behaviour of Q-Learning agentswhich they go on to verify.

It is clear from (\ref{eqn::EOM}) that the long-term strategy selection of
these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. In light of this, the following sections aim to address the question presented in the introduction: how do these elements influence the types of behaviours seen during
learning on an iterated game? Specifically, the parameters we will consider are:

\begin{enumerate}
    \item $\alpha \in [0, 1]$: the \textit{step length}. Low values of $\alpha$ denote smaller
    updates. Heuristically, we can consider this to be the memory of the agent: lower $\alpha$
    denotes longer memory.
    \item $\tau \in [0, \infty)$: the \textit{intensity of choice}, as termed by Sanders et al. 
    \cite{Sanders2018}. This is sometimes written as $\beta$ in the literature \cite{Sutton2018}.
    $\tau = 0$ results in all actions being selected with equal probability, regardless of their
    Q-value, whilst $\tau \rightarrow \infty$ results in the action with the highest Q-value chosen
    at every step. This may be considered the \textit{exploration-exploitation parameter}. For greater
    details into these parameters, the interested reader should consult \cite{Sutton2018}.
    \item $\Gamma \in [-1, p-1]$: the \textit{payoff correlation}. Since there are an infinite number of realisations of the payoffs $a_{ij}, b_{ij}$, we instead analyse the behaviour for the average payoff case. To do this, we assume that the payoff matrices are drawn from a multi-variate Gaussian with mean zero and
    covariance matrix parameterised by $\Gamma$. We then average over this Gaussian. $\Gamma = -1$ indicates a zero
    sum game, in which the sum of payoffs for a given action across all agents is 0, resulting in a
    purely competitive game. $\Gamma = p-1$ gives a purely cooperative game in which all agents
    share the same payoffs. The manner in which a game is generated from the choice of $\Gamma$ is
    described in (\ref{eqn::Payoffs}) and follows the same procedure as outlined in \cite{Sanders2018}.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Stability Analysis of Q-Learning} \label{sec::Theory}

In this section we aim to determine how the choice of parameters $\alpha$ and $\tau$, alongside the choice of payoff matrix, affect the stability of the dynamics of Q-learning. However, as the values in the payoff matrix can take any real number, there are an infinite number of possible realisations of games. Of course, it would not be possible to analyse every possible game, we instead follow the procedure outlined in \cite{Coolen2005} and \cite{Galla2013} to average over these realisations and, instead, analyse the \textit{effective dynamics}, the dynamics averaged over all realisations of payoff matrices. Then, we perform a linear stability analysis around equilibrium points to determine the conditions under which a fixed point is stable.

Our first point of call is to extend the dynamics of Tuyls et al.~in  (\ref{eqn::EOM}a) and (\ref{eqn::EOM}b) \st{and extend it} to a general $p$-player game. This yields the dynamics (\ref{eqn::pEOM}). Here, player $\mu$ chooses action $i_{\mu}$ from its action space $\mathcal{A}$ at time $t$ with probability $\xmu{i}{\mu}$ and receives a reward $\payoff{i}{\mu}$ from its payoff matrix $P^\mu$ depending on its own action and the actions of all other agents $i_{-\mu}$. Formally, the notation $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2, ..., p\} \backslash \{\mu\} \}$ and $-i_{\mu}$ denotes the set $\mathcal{A} \backslash {i_\mu}$.

\begin{equation}
\begin{split}
    \label{eqn::pEOM}
    \frac{\dot{\xmu{i}{\mu}}}{\xmu{i}{\mu}} = \alpha \tau ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} - \\ \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} ) + \alpha \sum_{j_\mu \in -i_\mu} \xmu{j}{\mu} ln \frac{\xmu{j}{\mu}}{\xmu{i}{\mu}}
\end{split}
\end{equation}

We now need to scale the system so that $\sum_{i_\mu} \xmu{i}{\mu} = 1$. The reason for this scaling is that, as the number of agents $p$ and number of actions $N$ increases, the expected payoffs that agent $\xmu{i}{\mu}$ receives becomes less distinguishable across its action space. Therefore, the system must be scaled to ensure appreciable differences across actions, so that the agent can choose its actions appropriately (see the discussion in \cite{Sanders2018} or the Supplementary Material for further details). Accordingly we choose scaled variables (denoted with a tilde) as
%
\begin{eqnarray*}
%    \begin{split}
        \payoff{i}{\mu} & = & \tpayoff{i}{\mu} \sqrt{N^{p-1}}\\
        \xmu{i}{\mu} & = & \frac{\txmu{i}{\mu}}{N} \\
        \talpha & = & \frac{\alpha}{N} \\
        \ttau & = & N^{-(p-1)/2} \tau \\
        \htau & = & N^{-p/2} \tau.
%    \end{split}
\end{eqnarray*}

Note that the scaled probabilities now satisfy the constraint $\sum_{i_\mu} \txmu{i}{\mu} = N$. For the remainder of this derivation we concern ourselves only with the scaled system so we drop the tilde notation on $P$ and $x$.

As mentioned, we now wish to generalise the dynamics to account for all the possible realisations of the payoff matrix. To do this, we assert that the payoff elements (after scaling) are generated by a multivariate Gaussian distribution with mean zero and covariance given as

%
\begin{equation}
\label{eqn::Payoffs}
    \begin{split}
        \mathbb{E}\left [ \payoff{i}{\mu} \payoff{i}{\nu} \right] = \begin{cases}
        \frac{1}{N^{p-1}}  \text{ if } \nu = \mu \\
        \frac{\Gamma}{(p-1) N^{p-1}} \text{ otherwise. }
        \end{cases}
    \end{split}
\end{equation}

The motivation for choosing that the payoffs should be generated by a Gaussian is that it allows for the use of Gaussian identities when determining the average.

We then use a generating functional approach as outlined in \cite{Mezard1986} to average the dynamics over this multivariate Gaussian. The generating functional is a method derived from statistical mechanics which allows for expectations to be taken over equations of motion and, more specifically, allows for the analysis of systems with `quenched disorder'. These are variables which are random but held fixed in time as the system evolves (in our case these variables are the payoff elements). This yields the \textit{effective dynamics}

\begin{equation}
    \label{eqn::EffectiveDynamics}
    \begin{split}
            \frac{1}{x} \frac{d}{dt} x(t) = \alpha^2 \ttau^2 \Gamma \int dt' \left [G(t, t')C^{p - 2}(t, t') x(t') \right ]\\ + \sqrt{2} \alpha \ttau \eta_1(t) + \sqrt{2} \alpha \htau \eta_0(t) + \talpha \rho(t), 
    \end{split}
\end{equation}

in which we have assumed that all players' actions are drawn from the same initial distribution (\ref{eqn::Payoffs})
 and therefore dropped the distinction between players and strategy components . The terms $G, C, \eta_1, \eta_0$ are correlation functions, generated during when averaging the Gaussian. These are given by 
\begin{eqnarray*}
%    \begin{split}
        C(t, t') & = & \mathbb{E}[x(t) x(t')] \\
        \mathbb{E}[\eta_1(t)] & = & 1, \text{ \space } \mathbb{E}[\eta_1(t) \eta_1(t')]  =  C^{p-1}(t, t') \\
        \mathbb{E}[\eta_0(t)] & = & 1, \text{ \space } \mathbb{E}[\eta_0(t) \eta_0(t')] = C^{p}(t, t') \\
        G(t, t') & = & \mathbb{E}\left [ \frac{\delta x(t)}{ \delta \eta_1(t')} \right].
%    \end{split}
\end{eqnarray*}

We now analyse the stability of this system in a neighbourhood around the fixed point. This follows a similar procedure as in \cite{Opper1992}, in which the fixed point dynamics are proposed to be perturbed by a disturbance $\xi(t)$ which is drawn from a Gaussian of zero mean and unit variance. The disturbance causes the values of $x(t)$ and $\eta_0(t), \eta_1(t)$ to deviate from their fixed point position $\xfixed, \ezerof, \eonef$ by an amount $\xpert, \ezeropert, \eonepert$.
If we consider only the terms which are linear in these perturbations, we arrive at the dynamics

\begin{equation}
\label{eqn::Linearised}
    \begin{split}
        \frac{d}{dt} \xpert = (\xfixed + \xpert) [ \alpha^2 \ttau^2 \Gamma \xfixed \int dt' [ G(t, t')C^{p - 2}(t, t') ]\\ + \sqrt{2} \alpha \ttau \eonef + \sqrt{2} \alpha \htau \ezerof + \talpha \rho] \\
        + \xfixed [\alpha^2 \ttau^2 \Gamma \int dt' [ G(t, t')C^{p - 2}(t, t') \xpertdash ] \\ + \sqrt{2} \alpha \ttau \eonepert + \sqrt{2} \alpha \htau \ezeropert + \xi(t)].
    \end{split}
\end{equation}

At a fixed point, then, the perturbations $\xpert$ will be zero, leaving

\begin{equation}
    \begin{split}
    \label{eqn::fixed_point}
        0 = \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{n-1} \chi + \\ + \sqrt{2} \alpha \ttau q^{n/2}z + \sqrt{2} \alpha \htau q^{(n+1)/2} z^{(n+1)/n}],
    \end{split}
\end{equation}

where $\chi = \int dt' G(t - t')$ (at a fixed point where the probabilities do not vary with time, this is equal to $\int dt' G(t, t')$), $\eta_0(t) = q^{n/2}z$ and $z$ is drawn from a Gaussian of zero mean and unit variance and $n = p - 1$. Having arrived at a condition for the fixed point, we then examine the long-term behaviour of the perturbation $\xpert$. To do this, we take the Fourier transform of (\ref{eqn::Linearised}) and analyse its behaviour at $\omega = 0$. After some manipulation, which are given in the Supplementary Material, this gives

\begin{equation}
\begin{split}
        \mathbb{E}[|\mathcal{X}(\omega = 0)|^2] = \frac{1}{\left[ (-\alpha^2 \ttau^2 \Gamma q^{n-1} \chi)^2 - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2}\right]} \\
\end{split}
\end{equation}

As the left hand side of this equation must be greater than zero by definition, we arrive at the condition that, at a fixed point, the long term perturbations must satisfy

\begin{equation}
    \label{eqn::Final}
    0 \leq \left [(\alpha^2 \ttau^2 \Gamma q^{n-1} \chi)^{2} - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2} \right ]
\end{equation}

It should be noted that, to arrive at this result, we have had to take the assumption that $2 >> 1/n$.

\paragraph{Discussion}
The fixed point condition (\ref{eqn::Final}) yields a number of testable implications, of which we test the validity through in the subsequent section. These implications are as follows.

\begin{enumerate}
    \item Convergence is rare. This is seen by the fact that, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is positive, which violates the stability criterion. This implies that games, in general, will not converge.
    \item The probability of convergence decreases with increasing $\alpha$, regardless of the choice of $N, p$. We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e. further from the region of stability).
    \item At low values of $\alpha$, the game is everywhere convergent, regardless of the choice of $\Gamma$. In fact, the choice of $\Gamma$ does not affect the outcome of the stability analysis at all. This is more easily interpreted from the heatmapts in Figure \ref{fig:theory}.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Evaluation} \label{sec:exev}

\begin{figure}
    \centering
    \includegraphics[width = 1.1 \linewidth]{Figures/Theory.png}
    \caption{Results of numerical experiments. The heatmaps show the value of the Liapunov Exponent determined by the procedure outlined in Section~\ref{sec:exev} scaled by $1 \times 10^5$ for convenience. Lighter values show a higher exponent whilst darker values indicate lower values. Each experiment is run with $\tau = 0.05$. (Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 4$, (Mid-Left) $p = 2, N = 10$, (Mid-Right) $p = 2, N = 20$, (Bottom) $p = 3, N = 5$.}
    \label{fig:theory}
\end{figure}
%\fb{Can we arrange Fig.~\ref{fig:theory} in a 2x2 square?}

We illustrate these implications in Figure \ref{fig:theory} which plots the value (and takes the absolute value for convenience) obtained by the right hand side of (\ref{eqn::Final}). In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for \st{the values of} $q$ and $\chi$. We ignore the choice $\xfixed  = 0$, since the proportion of agents who choose a non zero action probability is considered to be 1 \fb{the meaning of this is not clear to me}, an intuitive result \fb{assumption?} which is also considered in \cite{Sanders2018} and \cite{Coolen2005}. As such, we solve for $\xfixed$ using a Newton-Raphson root-finding approach and use the given \fb{obtained} expressions for $q, \chi$ to determine their value \fb{can we give such expressions?}. It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.

We evaluate (\ref{eqn::Final}) for varying values of $\alpha$ and $\Gamma$, whilst keeping $\tau$ fixed at 0.05 and restricting the range of $\Gamma$ to $[-1, 0]$, as it is only for this range that the solution to (\ref{eqn::fixed_point}) is defined. The range of $\alpha$ is also restricted to $[0.01, 0.05]$ as it is found that for larger values \st{of $\alpha$,} convergence is not seen.

\fb{Equation} (\ref{eqn::Final}) always evaluates to a positive value, suggesting that Q-learning in games is always unstable. We believe that this is due to the heavy assumptions made during the derivation of the analytic result, the strongest of which was to drop the discrepancy between players and actions, treating each action of each player to be equal \fb{in which sense equal?}. However, even within the error that this assumption generates, it is still clear (and is verified experimentally) that convergence in Q-Learning is rare. We therefore interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero). A choice of parameters which evaluates close to the stability boundary has a higher chance of being convergent than one which lies further from the boundary. Therefore, the heat-maps in Figure \ref{fig:theory} should be considered to show the probability of convergence for a choice of $(\alpha, \Gamma)$. Darker regions denote a higher probability of convergence whereas lighter regions are those whose values are further from zero and therefore show a lower probability of convergence.

In addition, we can visualise the implications 2 and 3 in Sec.~\ref{sec::Theory} by comparing the heat-maps. We see in all of the heat-maps that the probability of convergence decreases as $\alpha$ increases (i.e., moving from left to right). At low values of $\alpha$, convergence is seen for all choices of $\Gamma$. However, as $\alpha$ increases, the overall likelihood of convergence rapidly decreases and 
%the convergence 
it is more sensitive to the choice of $\Gamma$. A point to note is the implication that, with the increase of $p$ and $N$ comes a significant increase in the likelihood of convergence. This implication experimental evaluation \fb{?} and therefore can be seen as a limitation of (\ref{eqn::Final}). Instead, it should be viewed that, for a choice of $p, N$, the variation in stability of a system can be determined from $\alpha$ and $\Gamma$.

\subsection{Construction of Numerical Experiments}

To verify \fb{experimentally the theoretical results}, and to examine the underlying structure of stability and chaos in
Multi-Agent Q-Learning, we perform a series of numerical experiments by varying the parameters $\Gamma$ and
$\alpha$ whilst keeping $\tau$ fixed. The purpose 
\st{of this experiment} is to determine a heuristic estimate for the Lyapunov exponent, which measures the degree to which initial conditions which start close to one another converge or diverge as the dynamics evolve \cite{Strogatz2000}. The former indicates a stable system (in the sense of Lyapunov \cite{}) whilst the latter signals instability. The procedure for calculating the Lyapunov exponent is given in (\ref{eq::LiapExpo}).

To generate the numerical simulations in Figure~\ref{fig:NumericalExperiments} we used the
following procedure.
\begin{enumerate}
   \item Fix the paremeters $\tau, \gamma$. The latter is held at 0.5 in all experiments as (\ref{eqn::EOM}) indicates that the value of $\gamma$ does not affect the overall behaviour of the system.
   \item Initialise values of $\Gamma, \alpha$. These will be swept over in the experiment.
\item Generate 5 payoff matrices for both agents by sampling from a multi-variate Gaussian 
(variables are the payoff elements) with mean zero and covariance parameterised by $\Gamma$.
\item Initialise 2 sets of agents (denote their action probabilities as $\Vec{A_1}$ and $\Vec{A_2}$ respectively) each with random initial conditions (i.e., random action probabilities).
\item Allow both sets of agents to learn over a maximum of $1 \times 10^4$ iterations.
\item After 500 iterations measure the distance $\Vec{\delta_1} = |A_2 - A_1|$
\item After 10000 iterations measure the distance $\Vec{\delta_n} = |A_2 - A_1|$
\item Determine \fb{the Lyapunov exponent} 
\begin{eqnarray*}
\label{eq::LiapExpo}
    \lambda_n & = & \max_{i} 10^{-4} ln(\delta_{n, i}/\delta_{1, i})
\end{eqnarray*}
for each action $i$ and average this value over all five realisations of the payoff matrix. 
\end{enumerate}

This yields the result shown in Figure~\ref{fig:NumericalExperiments}. We see from this that the stability of the system is highly dependent on
the value of $\alpha$ and (although less so) on $\Gamma$.

\begin{figure}[t]
    \centering
    \includegraphics[width = 0.9 \linewidth]{Figures/Experiments.png}
    \caption{Results of numerical experiments. The heat-maps show the value of the Lyapunov Exponent determined by the procedure outlined in this section scaled by $1 \times 10^5$ for convenience. Lighter values show a higher exponent whilst darker values indicate lower values. Each experiment is run with $\tau = 0.05$. (Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 4$, (Mid-Left) $p = 2, N = 10$, (Mid-Right) $p = 2, N = 20$, (Bottom) $p = 3, N = 5$.}
    \label{fig:NumericalExperiments}
\end{figure}

\subsection{Discussion}

We note that the numerical experiments confirm the predictions suggested by the analytic results shown in Figure .... We notice that convergence occurs almost only for low values of $\alpha$. This observation remains as we increase the value of $N$. We do, however, notice some discrepancy between the boundary of stability predicted by the analytic result and that revealed in experiments. This is largely due to the assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made during the derivation. The remaining discrepancy is partially due to the aforementioned error \fb{approximation?} in the calculation of $q$, $\chi$ and \st{partially due to} the fact that the analytic result considers the expected behaviour of Q-Learning. We expect that averaging over a greater number of payoff realisations and initial conditions will yield a more representative assessment of the average behaviour of Q-Learning. However, running these experiments is a computationally expensive procedure: for $p$ players and $N$ actions we require operations on $p$ matrices with $N^{p}$ elements. As such, due to a reduced availability of computational facilities, a large scale averaging was not possible.

A point which we wish to discuss here is the difference in the result found w.r.t.~\cite{Sanders2018}, which considered the stability of \textit{Experience Weighted Attraction} (EWA). \st{and those found in this study.} Namely, Sanders et al.~found that convergence is seen for higher values of $\alpha$, whereas lower values give rise to chaos, the opposite of what is found here. The reason for this can be seen in the update equation of Q-Learning (\ref{eqn::Qupdate}), whereby
\st{in which we see that} 
smaller values of $\alpha$ result in the agent placing a lower weight on the reward received at each step. As such, lower values of $\alpha$ result in the agent taking more conservative steps and yields a higher probability of convergence. In contrast, the update for EWA does not discount the reward received at all and, instead, only discounts the previous knowledge of the Q-value based on higher choices of $\alpha$. In essence, the difference is the fact that Q-Learning discounts new information by a factor of $\alpha$, whilst EWA does not. Yet, the difference in stability caused by this change is significant. We believe this highlights the importance of performing analyses such as the present work; it allows for a method to analytically compare the difference between learning algorithms and, for practitioners, ensure that the appropriate algorithm is chosen for the parameters of their specific task.

A limitation of (\ref{eqn::Final}) is that it predicts that convergence should increase as $N$ and $p$ decreases \fb{or increase?}, a notion that does not seem to hold true in our experimental results. We hypothesize that this is a feature of raising the system to the $N \rightarrow \infty$ limit. \fb{The following paragraph seems a rather daunting criticism of the paper. Any chance it can be rephrased to emphasize the positive contribution?  This assumption means that the analytic result does not lie on the true boundary between convergence and chaos and, in the particular case of Q-Learning, predicts a higher overall probability of convergence than is actually the case.} Instead, as the experiments show, the probability of convergence is higher for games with lower numbers of actions and, in fact, convergence is almost ubiquitous for a 2-player, 2-action game.

To summarise, we have shown that the analytic result (\ref{eqn::Final}) provides a strong assessment for the effect that $\alpha$, $\Gamma$ and $p$ have on the likelihood of convergence of Q-Learning. We show that the behaviour of the stability line differs from that of EWA and suggest that this shows that a stability analysis is an important mode of analysis for reinforcement learning equations to ensure that parameters are being chosen appropriately to guarantee the safe convergence of learning.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

In this study, we characterise the behaviours of Q-Learning in $p$-player, $N$-action games. To do this, we analyse the replicator model of Q-Learning derived by Tuyls et al. Specifically, we search for the regions in parameter space where the dynamics are expected to converge to a stable equilibrium and those where learning is unstable. This yields a number of important results. We find that convergence to a unique fixed point is found for low values of $\alpha$, the \textit{step length} of the algorithm and for negatively correlated payoff matrices. As $\alpha$ increases, the likelihood of convergence decreases. For positively correlated payoffs, our analysis no longer guarantees the uniqueness of a fixed point.

As future work, our first aim is to verify the analytic result at a finer resolution and by averaging over a greater number of payoff realisations. This will give a greater insight into the boundary between convergent and non-convergent behaviour and allow for practitioners to choose their parameters in such a way that convergence to a unique fixed point is expected. In addition we noted that one of the conclusions to our study is that convergence to a unique fixed point is rare in Q-Learning. In fact, complex behaviour (such as the existence of multiple fixed points, limit cycles and chaos) is more likely. We, therefore, aim to characterise these complex behaviours in parameter space both theoretically and numerically.

The present work gives a first step towards considering the stability of Multi-Agent Reinforcement Learning and focuses on the limiting case of stateless normal-form games played by homogeneous agents. As research into the dynamics of Reinforcement Learning algorithms progresses, it would be prudent to apply this analysis to various other algorithm. Algorithms whose dynamics are established, and are therefore open to a stability analysis, include piecewise Q-Learning and Cross Learning. This would provide a strong method by which to compare and provide safety guarantees to different algorithms for a particular use case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% The acknowledgments section is defined using the "acks" environment
%%% (rather than an unnumbered section). The use of this environment 
%%% ensures the proper identification of the section in the article 
%%% metadata as well as the consistent spelling of the heading.

\begin{acks}
If you wish to include any acknowledgments in your paper (e.g., to 
people or funding agencies), please do so using the `\texttt{acks}' 
environment. Note that the text of your acknowledgments will be omitted
if you compile your document with the `\texttt{anonymous}' option.
\end{acks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% The next two lines define, first, the bibliography style to be 
%%% applied, and, second, the bibliography file to be used.

\bibliographystyle{ACM-Reference-Format} 
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-10-02 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py
Updated Experimental Code

@@ -1,16 +1,21 @@
 import numpy as np
+import seaborn as sns
 import matplotlib.pyplot as plt
 from time import time
 from tqdm import tqdm
 
-alpha = .1
-gamma = .75
+# alpha = .1
+gamma = .1
 Gamma = 0.1
-tau = 2
+tau = 5e-2
+
+nActions = 2
+t0 = 500
+
+initnSim = 15
 
 delta_0 = 1e-3
-nSim = 10
-nIter = int(1e4)
+nIter = int(5e4)
 
 
 def generateGames(gamma, nSim, nAct):
@@ -29,72 +34,105 @@ def generateGames(gamma, nSim, nAct):
     cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
     cov[nElements:, :nElements] = np.eye(nElements) * gamma
 
-    rewardAs, rewardBs = np.eye(2), np.eye(2)
+    rewardAs, rewardBs = np.eye(nAct), np.eye(nAct)
 
     for i in range(nSim):
-
         rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
 
-        # rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
-        rewardAs = np.dstack((rewardAs, np.array([[1, 0], [0, 2]])))
-        # rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
-        rewardBs = np.dstack((rewardBs, np.array([[2, 0], [0, 1]])))
+        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
+        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
+
     return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
 
+
 def getActionProbs(qValues, nSim):
-    partitionFunction = np.sum(np.exp(tau * qValues), axis = 1)
-    actionProbs = np.array([np.array([np.exp(tau * qValues[p, :, s])/partitionFunction[p, s] for p in range(2)]) for s in range(nSim)])
+    partitionFunction = np.sum(np.exp(tau * qValues), axis=1)
+    actionProbs = np.array(
[…]

### 2020-10-02 Code/EGT-RL/TwoPlayerCode/pPlayers.py

@@ -4,14 +4,15 @@ import scipy.sparse as sps
 import matplotlib.pyplot as plt
 from tqdm import tqdm
 
+t0 = 500
 gamma = .1
-tau = 10
+tau = 5e-2
 
-nSim = 10
-nIter = int(1e4)
+initnSim = 10
+nIter = int(5e4)
 nTests = 10
 
-nPlayers = 3
+nPlayers = 2
 nActions = 2
 
 def generateGames(gamma, nSim, nAct, nPlayers):
@@ -33,14 +34,14 @@ def generateGames(gamma, nSim, nAct, nPlayers):
 
     cov = cov.toarray()
 
-    allPayoffs = np.zeros(shape=(nPlayers, nElements))
+    allPayoffs = np.array(([1, 5, 0, 3], [1, 5, 0, 3]))
 
     for i in range(nSim):
         rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
         each = np.array_split(rewards, nPlayers)
         allPayoffs = np.dstack((allPayoffs, np.array(each)))
 
-    return allPayoffs
+    return allPayoffs[:, :, 1:]
 
 def getActionProbs(qValues):
     partitionFunction = np.expand_dims(np.sum(np.exp(tau * qValues), axis=1), axis = 1)
@@ -49,7 +50,7 @@ def getActionProbs(qValues):
     return actionProbs
 
 
-def qUpdate(qValues, payoffs):
+def qUpdate(qValues, payoffs, nSim):
     idX = list(itertools.product(list(range(0, nActions)), repeat=nPlayers))
     actionProbs = getActionProbs(qValues)
     bChoice = np.array([[np.random.choice(list(range(nActions)), p=actionProbs[p, :, s]) for s in range(nSim)] for p in range(nPlayers)])
@@ -60,46 +61,41 @@ def qUpdate(qValues, payoffs):
 
     return qValues
 
-def checkConvergence(x, xOld, tol):
-  """
-    Evaluates the distance between action probabilities and checks if the change is
-    below some tolerance.
-
-    params
-    actionProb: Agent action probabilities at current time step
-    oldxBar: Previous action probabilities
-    tol: tolerance level
-
-    returns
-
-    (normStep1 < tol) and (normStep2 < tol): Whether change in both agents' action 
-    probabilities is below a tolerance.
-  """
-
-  normSteps = np.array([[np.linalg.norm((x - xOld)[p, :, i]) for i in range(nSim)] for p in range(nPlayers)])
[…]

### 2020-10-02 Code/EGT-RL/TwoPlayerCode/untitled0.py

@@ -1,0 +1,76 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Sep  6 20:49:19 2020
+
+@author: aamalh
+"""
+
+import numpy as np
+import itertools
+
+nAct = 2
+nPlayers = 2
+nSim = 1
+
+alpha = 0.5
+gamma = 0.5
+tau = 1
+Gamma = -1
+
+
+def generateGames(gamma, nSim, nAct):
+    """
+    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
+
+    gamma: Choice of co-operation parameter
+    nAct: Number of actions in the game
+
+    [reward1s, reward2s]: list of payoff matrices
+    """
+
+    nElements = nAct ** nPlayers  # number of payoff elements in the matrix
+
+    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    for i in range(nSim):
+
+        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+    return np.array([1, 5, 0, 3, 1, 5, 0, 3])
+
+def getActionProbs(qValues):
+    partitionFunction = np.sum(np.exp(tau * qValues0.reshape((2, 2))), axis = 1)
+    actionProbs = [np.exp(tau * qValues0[i:i + nAct])/partitionFunction[int(i/2)] for i in range(0, nPlayers + 1, nAct)]
+
+    return np.array(actionProbs).squeeze()
+
+rewards = generateGames(Gamma, nSim, nAct)
+qValues0 = np.random.rand(nPlayers * nAct, nSim)
+
+for cIter in range(1000):
+
+    actionProbs = getActionProbs(qValues0)
+    bChoices = [np.random.choice([0, 1], p = actionProbs[p]) for p in range(nPlayers)]
+    
+    rows = [i + j + 1 for (j, i) in enumerate(bChoices)]
+    rows[0] -= 1
+    idX = list(itertools.product(list(range(0, nAct)), repeat = nPlayers))
+    idX = [list(i) for i in idX]
+    
[…]

### 2020-10-02 Code/Practice/Tuyls.py

@@ -1,24 +1,52 @@
 import numpy as np
 import matplotlib.pyplot as plt
+from tqdm import tqdm
 
-alpha = .1
-A = np.array([[2, 0], [0, 1]])
-B = np.array([[1, 0], [0, 2]])
-tau = .9
+def generateGames(gamma, nSim, nAct):
+    """
+    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
+
+    gamma: Choice of co-operation parameter
+    nAct: Number of actions in the game
+
+    [reward1s, reward2s]: list of payoff matrices
+    """
+
+    nElements = nAct ** 2  # number of payoff elements in the matrix
+
+    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    rewardAs, rewardBs = np.eye(nAct), np.eye(nAct)
+
+    for i in range(nSim):
+
+        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+        # rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
+        rewardAs = np.dstack((rewardAs, np.array([[1, 5], [0, 3]])))
+        # rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
+        rewardBs = np.dstack((rewardBs, np.array([[1, 3], [0, 5]]).T))
+    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
+
+alpha = 2e-2
+tau = 10
 
 x = np.linspace(0, 1, 50)
 y = np.linspace(0, 1, 50)
+
+X, Y = np.meshgrid(x, y)
+
+A, B = np.array(([[-1.08563096,  1.7272803],   [0.0719464,   0.22215408]])), np.array(([[-0.04231243,  0.57071329],  [1.0930919,  -1.68208477]]))
 
 E = lambda R: (R * np.log(R/R)) + ((1 - R) * np.log((1 - R)/R))
 
[…]

### 2020-10-02 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Included AAMAS submission with additions to analytic result

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%   MACROS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \newcommand{\xmu}[2]{x_{#1_#2}^{#2}(t)}
+\newcommand{\xmudash}[2]{x_{#1_#2}^{#2}(t')}
 \newcommand{\payoff}[2]{P^{#2}_{#1_#2, #1_{-#2}}}
 
+\newcommand{\dxmu}[1]{\dot{x}_{#1_\mu}^{\mu} (t)}
+\newcommand{\hxmu}[1]{\hat{x}_{#1_\mu}^{\mu} (t)}
+\newcommand{\hxnu}[1]{\hat{x}_{#1_\nu}^{\nu} (t)}
+\newcommand{\hxmudash}[1]{\hat{x}_{#1_\mu}^{\mu} (t')}
+\newcommand{\hxnudash}[1]{\hat{x}_{#1_\nu}^{\nu} (t')}
+
 \newcommand{\txmu}[2]{\tilde{x}_{#1_#2}^{#2}(t)}
+\newcommand{\dtxmu}[2]{\dot{\tilde{x}}_{#1_#2}^{#2}(t)}
 \newcommand{\tpayoff}[2]{\tilde{P}^{#2}_{#1_#2, #1_{-#2}}}
@@
 \newcommand{\htau}{\hat{\tau}}
-
 \newcommand{\xfixed}{x_\infty}
@@
 
-\newcommand{\ah}[1]{\textcolor{red}{AH: #1}}
-\usepackage{xcolor} % REMOVE THIS AT THE END
-\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
+\newcommand{\eom}{\frac{\dxmu{i}}{\xmu{i}{\mu}} - \alpha \ttau \left ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) + \\ \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) - \talpha \rho^{\mu}_{i}(t)}
 
@@
 \affiliation{
-  \institution{Secret Intelligence Service}
-  \city{Vauxhall, London}}
-\email{agent007@mi6.gov.uk}
+  \department{Department of Computing}
+  \institution{Imperial College London}}
+\email{aamal.hussain15@imperial.ac.uk}
 
@@
 \affiliation{
-  \institution{Analytical Engines, Inc.}
-  \city{Ockham Park}
-  \state{Surrey}}
-\email{ada@analytical-engines.com}
-
-\author{Alan M. Turing}
-\affiliation{
-  \department{Computing Machine Laboratory}
-  \institution{Victoria University of Manchester}}
-\email{amt@vum.ac.uk}
+  \department{Department of Computing}
+  \institution{Imperial College London}}
+\email{francesco.belardinelli@imperial.ac.uk}
 
@@
 
+This yields the scaled equation
+
+\begin{equation}
+\begin{split}
+    \label{eqn::scaledEOM}
+    \frac{\dtxmu{i}{\mu}}{\txmu{i}{\mu}} = \alpha \ttau \left ( \sum_{i_{-\mu}} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) \\ - \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \txmu{i}{\mu} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) \\ + \talpha \sum_{j_\mu \in -i_\mu} \txmu{j}{\mu} ln \frac{\txmu{j}{\mu}}{\txmu{i}{\mu}}
+\end{split}
+\end{equation}
+
 Note that the scaled probabilities now satisfy the constraint $\sum_{i_\mu} \txmu{i}{\mu} = N$.
@@
 To do this, we assert that the payoff elements (after scaling) are generated by a multivariate Gaussian distribution with mean zero and covariance given as
-
 %
@@
 
+\subsection{Generating Functional Analysis}
+
 We then use a generating functional approach as outlined in \cite{Mezard1986} to average the dynamics over this multivariate Gaussian.
@@
 These are variables which are random but held fixed in time as the system evolves (in our case these variables are the payoff elements).
-This yields the \textit{effective dynamics}
+The generating functional is given as \cite{SpinGlassTheory}
+
+\begin{equation}
+	Z = \int D[\Vec{x}] \prod_i \delta(\textit{equation of motion}_i) exp(i
+	\int dt[x_i(t) \psi_i(t)]), 
+\end{equation}
+
+where the equations of motion are the Lagrange equations of motion given in (
+\ref{eqn::scaledEOM}) and
+the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
+calculation. $\delta$ denotes the Dirac delta function. Implementing our equation of motion yields
+
+\begin{equation}
+	\begin{split}
+	Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] exp( i \sum_{i, \mu} \int dt [ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t))]) \times \\ exp(-i \alpha \ttau \sum_{\mu} \sum_{i_\mu, i_{-\mu}} \int dt [\hxmu{i} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} )]))
+    \times \\ exp(-i \alpha \ttau \sum_{\mu} \sum_{j_\mu, i_\mu, i_{-\mu}} \int dt [\hxmu{j}  \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}])) 
+	\times \\ exp(i \sum_{i, \mu}
+	\int dt[\xmu{i} \psi^\mu_i(t)]),
+\end{split}
+\end{equation}
+
+The last two exponentials contain the payoffs of the game.
+These are randomly generated using a multivariate gaussian and then held fixed for the rest of the game.
+As such these comprise the aforementioned 'quenched disorder'.
+We will average over this quenched disorder (and therefore average over all possible realisations of payoff matrices).
+
+By taking this average, described in further detail in the Supplementary Material, we obtain the \textit{effective dynamics}
 
@@
 
-in which we have assumed that all players' actions are drawn from the same initial distribution (\ref{eqn::Payoffs})
- and therefore dropped the distinction between players and strategy components .
+in which we have assumed that all players' actions are independent and drawn from the same initial distribution (\ref{eqn::Payoffs})
+and therefore dropped the distinction between players and strategy components.
 The terms $G, C, \eta_1, \eta_0$ are correlation functions, generated during when averaging the Gaussian.
 These are given by
+
 \begin{eqnarray*}
@@
 \end{eqnarray*}
+
+It is important to note the effect of the former assumption (that all actions of all agents are i.i.d) is substantial.
+With this assumption, we reduce the second summation term, which couples actions from all agents $\xmu{i}{\mu}$ in (\ref{eqn::EOM}) to the uncoupled term $\sqrt{2} \alpha \htau \eta_0(t)$ in (\ref{eqn::EffectiveDynamics}).
+This is a strong assumption which is required to analyse the stability of the dynamics in the competitive regime.
+However, as shown by the experimental evaluation, it does not produce a strong discrepancy in describing the qualitative effect on stability caused by the parameters $\alpha, \Gamma, \tau$.
+
+\subsection{Linear Stability Analysis}
 
@@
 
-As the left hand side of this equation must be greater than zero by definition, we arrive at the condition that, at a fixed point, the long term perturbations must satisfy
+As the left hand side of this equation must be greater than zero, we arrive at the condition that, at a fixed point, the long term perturbations must satisfy
 

### 2020-10-02 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
-\documentclass[sigconf]{aamas} 
-%\documentclass[sigconf,anonymous]{aamas}
+%\documentclass[sigconf]{aamas} 
+\documentclass[sigconf,anonymous]{aamas}
 
@@
 \newcommand{\eom}{\frac{\dxmu{i}}{\xmu{i}{\mu}} - \alpha \ttau \left ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) + \\ \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) - \talpha \rho^{\mu}_{i}(t)}
+
+\usepackage{xcolor} % REMOVE THIS AT THE END
+\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
+
+\usepackage{soul}
+\usepackage{subcaption}
 
@@
 \begin{abstract}
-Modelling the dynamics of Q-Learning is an active and important topic for the sake of developing an {\em a priori} understanding of Reinforcement Learning.
-In this paper, we use methods from evolutionary game theory to analyse the stability of Q-Learning in $p$-player games, where payoffs are randomly generated.
-We determine the parameter range in which Q-Learning is expected to settle to a stable fixed point and the range in which the dynamics are unstable.
-
-This study allows for parameters to be appropriately chosen to ensure the safe convergence of a learning algorithm and as a first step towards understanding the range of behaviours that can be displayed by learning using the Q-Learning algorithm.
-We validate our theoretical results through numerical simulation and show that, within the bounds of experimental error, the region of instability can be characterised by the learning dynamics.
-We also note a few important implications of the study: 1) convergence is rare in Multi-Agent Reinforcement Learning.
-It is found that convergence to a unique fixed point occurs for simple games with 2 players and 2 actions.
-However, once either of these increase, convergence no longer occurs.
-2) the existence of instability is not affected by the structure of the game itself.
-In fact, at least in the competitive regime, the payoff structure does not affect whether the game converges or not.
-3) Convergence is guaranteed for low step-lengths but rapidly decreases as the step length increases.
+Modelling the dynamics of Q-Learning is an active and important topic
+for the sake of developing an {\em a priori} understanding of
+Reinforcement Learning. In this paper, we use methods from
+evolutionary game theory to analyse the stability of Q-Learning in
+$p$-player games, where payoffs are randomly generated. We determine
+the parameter range in which Q-Learning is expected to settle to a
+stable fixed point and the range in which the dynamics are unstable.
+%
+This study allows for parameters to be appropriately chosen to ensure
+the safe convergence of a learning algorithm.
+%and as a first step
+%towards understanding the range of behaviours that can be displayed by
+%learning using the Q-Learning algorithm.
+We validate our theoretical
+results through numerical simulations and show that, within the bounds
+of experimental error, the region of instability can be characterised
+by the learning dynamics.
+\fb{I think all of the following can be removed from the abstract:
+We also note a few important implications of
+the study: 1) convergence is rare in Multi-Agent Reinforcement
+Learning. It is found that convergence to a unique fixed point occurs
+for simple games with 2 players and 2 actions. However, once either of
+these increase, convergence no longer occurs. 2) the existence of
+instability is not affected by the structure of the game itself. In
+fact, at least in the competitive regime, the payoff structure does
+not affect whether the game converges or not. 3) Convergence is
+guaranteed for low step-lengths but rapidly decreases as the step
+length increases.
+}
 \end{abstract}

### 2020-10-06 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Updated Discussion in AAMAS Submission

--- 2020-10-02 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 %\documentclass[sigconf,anonymous]{aamas}
+
+\usepackage{soul}
+\usepackage{subcaption}
 
@@
 
+\usepackage{xcolor} % REMOVE THIS AT THE END
+\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\acmSubmissionID{???}
+\acmSubmissionID{489}
 
@@
 
-\title[InstabilityinMARL]{Instability in Multi Agent Reinforcement Learning}
+\title[InstabilityinMARL]{Stability and Chaos in Multi Agent Reinforcement Learning}
 
@@
 We validate our theoretical results through numerical simulation and show that, within the bounds of experimental error, the region of instability can be characterised by the learning dynamics.
-We also note a few important implications of the study: 1) convergence is rare in Multi-Agent Reinforcement Learning.
-It is found that convergence to a unique fixed point occurs for simple games with 2 players and 2 actions.
-However, once either of these increase, convergence no longer occurs.
-2) the existence of instability is not affected by the structure of the game itself.
-In fact, at least in the competitive regime, the payoff structure does not affect whether the game converges or not.
-3) Convergence is guaranteed for low step-lengths but rapidly decreases as the step length increases.
 \end{abstract}
@@
 
-\keywords{Auction Theory, Reinforcement Learning, Social Simulation}
+\keywords{Game Theory, Reinforcement Learning, Dynamical Systems}
 
@@
 multi-agent system, which is trained on an iterated game using Q-Learning, likely to converge to an
-equilibrium as opposed to displaying complex, or chaotic behaviours? In investigating this question, we will make the
+equilibrium as opposed to displaying complex, or unstable behaviours? In investigating this question, we will make the
 following assumptions:
@@
 Analyses have been performed from the point of view of the replicator dynamic towards the various types of behaviours that can emerge from iterated games.
-Such games are considered imperfect, in that agents do not make decisions based on a rational process derived from perfect information of the game, but rather through attempting to anticipate their opponents' behaviour based on experience \cite{Galla2011}.
+Such games are considered imperfect, in that agents make decisions by attempting to anticipate their opponents' behaviour based on experience \cite{Galla2011}.
 \cite{Imhof2005} presents the observation that, in the game of Prisoner's Dilemma, cyclic behaviour emerges in which the optimal strategy cycles across defection, cooperation and tit-for-tat despite defection being the NE.
@@
 
-Taking this notion even further, \cite{Sato2002} presents a study in which it is shown that learning, even on a simple two player game (they choose rock-paper-scissors), demonstrates Hamiltonian chaos (see \cite{Strogatz2000} for details on chaos).
-In this regime, there are no stable equilibria and the game will never converge to an equilibrium.
-To analyse this phenomena further, \cite{Galla2013} describes an investigation of two-person iterated games in which the players learn using \textit{Experience Weighted Attraction} (EWA), a form of reinforcement learning whose analysis typically falls under the purview of experimental economics \cite{Camerer2009}.
-Through numerical simulations, the authors were able to show that, once again, the emergence of chaos and cycles, is dependent on the choice of parameters.
-A rigorous theoretical analysis, which follows the techniques presented in \cite{Opper1992}, of the replicator dynamic corresponding to EWA presented a method for characterising the regions in parameter space in which a game is likely to converge, exhibit chaos or limit cycles.
-More recently, the authors presented an extended study in \cite{Sanders2018}, in which this analysis was extended towards a generic $p$-player game, which showed that chaotic dynamics are more likely to be observed as the number of players \textit{p} increases, whilst a similar study \cite{Pangallo2019} indicates that an increase in the number of actions $N$ in the strategy space similarly increases the likelihood of unstable behaviour.
+Taking this notion even further,  \cite{Galla2013} describes an investigation of two-person iterated games in which the players learn using \textit{Experience Weighted Attraction} (EWA), a form of reinforcement learning whose analysis typically falls under the purview of experimental economics \cite{Camerer2009}.
+Through numerical simulations, the authors were able to show that, once again, the emergence of chaos and cycles (see \cite{Strogatz2000} for details on chaotic and periodic motion), is dependent on the choice of parameters.
+A rigorous theoretical analysis, which applies the techniques presented in \cite{Opper1992}, of the replicator dynamic corresponding to EWA presented a method for characterising the regions in parameter space in which a game is likely to converge, exhibit chaos or limit cycles.
+More recently, the authors presented an extended study in \cite{Sanders2018}, in which this analysis was extended towards a generic $p$-player game, which showed that chaotic dynamics are more likely to be observed as the number of players \textit{p} increases.
 
@@
 
-\paragraph{Dynamics of RL} The earliest example of such an analysis may be found in \cite{Borgers1997}, in which the \textit{Cross Learning} algorithm is analysed and it is shown that, in a continuous time limit, the learning model converges to the replicator dynamic.
-Adapting this work for the benefit of the AI community, the authors of \cite{Tuyls2006AnGames} similarly derive a relation between Q-Learning (see \cite{Barber2012}) and the replicator dynamic.
+\paragraph{Dynamics of RL} In \cite{Tuyls2006AnGames}, the authors are able to derive a relation between Q-Learning (see \cite{Barber2012}) and the replicator dynamic.
 In doing so, the authors present an evolutionary model which accurately predicts the dynamics of Q-Learning.
 This sprung forward a vast array of literature which perform similar derivations for various reinforcement learning algorithms.
-\cite{Bloembergen2015} presents an excellent review of these for the interested reader.
+\cite{Bloembergen2015} presents an excellent review of these.
 In particular it should be noted that many of these studies focus on normal form games, in which the payoff matrix does not change (i.e.
@@
 
-The analysis of RL from an EGT perspective is a growing field, with a significant scope for expansion, as is discussed in our conclusion. 
-However, the relation between RL and the replicator dynamic allows for the assumption of convergence in reinforcement learning to be lifted and instead for the emergence of cyclic behaviour and chaos to be examined.
+The relation between RL and the replicator dynamic allows for the assumption of convergence in reinforcement learning to be lifted and instead for the emergence of more complex behaviour to be examined.
 In particular, this study aims to perform a similar analysis to that in \cite{Sanders2018} and establish the regions in parameter space in which Q-Learning converges to stable fixed points and where the learning is unstable.
@@
     strategies may exhibit much more complex behaviour than
-    convergence to a Nash Equilibrium (NE), \st{These behaviours include:}
+    convergence to a Nash Equilibrium (NE),
     including convergence to a unique
@@
 $x_i$ (resp.~$y_j$).
-\st{while Agent 2 takes action $j$ with probability $y_j$}. When these actions are taken, the agents
+When these actions are taken, the agents
 receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-predict the expected behaviour of Q-Learning agentswhich they go on to verify.
+predict the expected behaviour of Q-Learning agents which they go on to verify.
 
@@
 
-Our first point of call is to extend the dynamics of Tuyls et al.~in  (\ref{eqn::EOM}a) and (\ref{eqn::EOM}b) \st{and extend it} to a general $p$-player game.
+Our first point of call is to extend the dynamics of Tuyls et al.~in  (\ref{eqn::EOM}a) and (\ref{eqn::EOM}b) to a general $p$-player game.
 This yields the dynamics (\ref{eqn::pEOM}).
@@
 \begin{equation}
+\label{eqn::separatePayoffs}
 	\begin{split}
@@
 We will average over this quenched disorder (and therefore average over all possible realisations of payoff matrices).
+We define $Q$ to be the product of the second and third exponentials in (\ref{eqn::separatePayoffs})
+
+\begin{equation}
+\begin{split}
+        <Q> = exp(- \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] ) \times \\
+        exp(- \frac{\alpha^2 \htau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} A^{\mu \nu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] )
+\end{split}
+\end{equation}
+
+In which
+
+\begin{align}
+\label{eqn::correlations}
+    \begin{split}
+        C^\mu (t, t') & :=  N^{-1} \sum_i \xmu{i}{\mu} \xmudash{i}{\mu} \\
+        L^\mu (t, t') & :=  N^{-1} \sum_i \hxmu{i} \hxmudash{i} \\
+        K^\mu (t, t') & :=  N^{-1} \sum_i \xmu{i}{\mu} \hxmudash{i} \\
+        A^{\mu, \nu} (t, t') & :=  N^{-1} \sum_i \hxmu{i} \hxnudash{i}.
+    \end{split}
+\end{align}
 
@@
 
-in which we have assumed that all players' actions are independent and drawn from the same initial distribution (\ref{eqn::Payoffs})
+in which we have assumed that all players' actions are independent and drawn from the same initial distribution (i.i.d)
 and therefore dropped the distinction between players and strategy components.
@@
 It is important to note the effect of the former assumption (that all actions of all agents are i.i.d) is substantial.
-With this assumption, we reduce the second summation term, which couples actions from all agents $\xmu{i}{\mu}$ in (\ref{eqn::EOM}) to the uncoupled term $\sqrt{2} \alpha \htau \eta_0(t)$ in (\ref{eqn::EffectiveDynamics}).
-This is a strong assumption which is required to analyse the stability of the dynamics in the competitive regime.
+With this assumption, we identify the coupled term $A^{\mu, \nu} (t, t')$ in (\ref{eqn::correlations}) with the uncoupled term $L^\mu (t, t')$ (since there is no distinction between the actions of agents $\mu$ and $\nu$).
+This is a strong assumption which removes the interdependency between agents in the analysis.
 However, as shown by the experimental evaluation, it does not produce a strong discrepancy in describing the qualitative effect on stability caused by the parameters $\alpha, \Gamma, \tau$.
@@
 
-where $\chi = \int dt' G(t - t')$ (at a fixed point where the probabilities do not vary with time, this is equal to $\int dt' G(t, t')$), $\eta_0(t) = q^{n/2}z$ and $z$ is drawn from a Gaussian of zero mean and unit variance and $n = p - 1$.
+where $\chi = \int dt' G(t - t')$, $\eta_0(t) = q^{n/2}z$ and $z$ is drawn from a Gaussian of zero mean and unit variance and $n = p - 1$.
+This gives us an expression for calculating $\xfixed$.
+We disregard the choice $\xfixed  = 0$, since we assume that no action will be chosen with exactly zero probability, an intuitive assumption which is also considered in \cite{Sanders2018} and \cite{Coolen2005}.
+The expression inside the squared bracket admits a positive solution only in the region $\Gamma \in [-1, 0]$, whilst for positive $\Gamma$, the nature of solutions may not be guaranteed.
+Therefore, we restrict our analysis to this region.
+
 Having arrived at a condition for the fixed point, we then examine the long-term behaviour of the perturbation $\xpert$.
@@
 \begin{enumerate}
+    \item A trivial result is that the game is everywhere convergent (i.e.
+regardless of the choice of $\Gamma, N, p$) for the cases of $\alpha$ = 0 and/or $\tau$ = 0.
+We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) yielding a value of zero which falls within the stable region.
     \item Convergence is rare.
-This is seen by the fact that, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is positive, which violates the stability criterion.
+This is seen by the fact that the analytic result overestimates the region of instability.
+In fact, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is negative, which violates the stability criterion.
 This implies that games, in general, will not converge.
-    \item The probability of convergence decreases with increasing $\alpha$, regardless of the choice of $N, p$.
+    \item The likelihood of convergence decreases with increasing $\alpha$ and $\tau$, regardless of the choice of $N, p$.
 We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e.
 further from the region of stability).
-    \item At low values of $\alpha$, the game is everywhere convergent, regardless of the choice of $\Gamma$.
-In fact, the choice of $\Gamma$ does not affect the outcome of the stability analysis at all.
-This is more easily interpreted from the heatmapts in Figure \ref{fig:theory}.
+    \item The choice of $\Gamma$ does not affect the stability of the game in the negatively-correlated regime.
+Therefore, the only dependent factors are $\alpha, \tau, N, p$.
+This is more easily interpreted from the heatmaps in Figure \ref{fig:theory}.
+    \item The likelihood of convergence decreases as $p$ increases.
+We see this by noticing the weighting that the $(p-1)$ in the second term of (\ref{eqn::Final}) places.
+As $p$ increases, this term drives the system further from the stability boundary.
+
 \end{enumerate}
@@
 
-We illustrate these implications in Figure \ref{fig:theory} which plots the value (and takes the absolute value for convenience) obtained by the right hand side of (\ref{eqn::Final}).
-In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for \st{the values of} $q$ and $\chi$.
-We ignore the choice $\xfixed  = 0$, since the proportion of agents who choose a non zero action probability is considered to be 1 \fb{the meaning of this is not clear to me}, an intuitive result \fb{assumption?} which is also considered in \cite{Sanders2018} and \cite{Coolen2005}.
-As such, we solve for $\xfixed$ using a Newton-Raphson root-finding approach and use the given \fb{obtained} expressions for $q, \chi$ to determine their value \fb{can we give such expressions?}.
+We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}).
+In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$.
+We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
+
+\begin{equation*}
+    \begin{split}
+        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
+        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
+        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+    \end{split}
+\end{equation*}
+
 It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.
 
-We evaluate (\ref{eqn::Final}) for varying values of $\alpha$ and $\Gamma$, whilst keeping $\tau$ fixed at 0.05 and restricting the range of $\Gamma$ to $[-1, 0]$, as it is only for this range that the solution to (\ref{eqn::fixed_point}) is defined.
-The range of $\alpha$ is also restricted to $[0.01, 0.05]$ as it is found that for larger values \st{of $\alpha$,} convergence is not seen.
+We consider each of the implications 2-5 from the previous section in turn, choosing to forego illustrating 1 as it can be seen trivially from the expression.
+In those heatmaps for which $\tau$ is held fixed \textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$.
+For those in which $\alpha$ is held fixed, \textbf{denote them} we choose $\alpha =  0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
 
-\fb{Equation} (\ref{eqn::Final}) always evaluates to a positive value, suggesting that Q-learning in games is always unstable.
-We believe that this is due to the heavy assumptions made during the derivation of the analytic result, the strongest of which was to drop the discrepancy between players and actions, treating each action of each player to be equal \fb{in which sense equal?}.
+By looking at the values of the heatmap, we see that, for all choices of the parameters, other than $\alpha = 0, \tau = 0$, (\ref{eqn::Final}) evaluates to a negative value, which signals instability.
+As such, the analysis over-estimates the region of instability.
+We believe that this is due to the heavy assumptions made during the derivation of the analytic result, the strongest of which was to drop the discrepancy between players and actions, treating each action of each player to be independent and identically distributed.
 However, even within the error that this assumption generates, it is still clear (and is verified experimentally) that convergence in Q-Learning is rare.
-We therefore interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero).
-A choice of parameters which evaluates close to the stability boundary has a higher chance of being convergent than one which lies further from the boundary.
+Indeed as the choice of $N$ increases, the stability boundary determined by experiment (Figure \ref{fig:NumericalExperiments}) tends towards $\alpha = 0, \tau = 0$.
+
+Similarly, as the value of $N$ increases, the values in the heatmap (seen on the right of the map) reduce.
+This is due to the assumption made in the derivation of the analytic result that $N \rightarrow \infty$.
+As the value of N increases, the discrepancy between the true behaviour of the system and analytic result decreases.
+This does, however, give rise to a limitation of the result - namely that the effect of the number of actions $N$ cannot be accurately inferred from the (\ref{eqn::Final}).
+However, it should still be noted that, even with the increase of N, the values in parameter space remain negative and still, accurately, predict instability.
+We go on to verify that the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured by (\ref{eqn::Final}).
+
+We interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero).
+A choice of parameters which evaluates close to the stability boundary has a higher chance (by the analytic error) of being convergent than one which lies further from the boundary.
 Therefore, the heat-maps in Figure \ref{fig:theory} should be considered to show the probability of convergence for a choice of $(\alpha, \Gamma)$.
-Darker regions denote a higher probability of convergence whereas lighter regions are those whose values are further from zero and therefore show a lower probability of convergence.
+Lighter regions denote a higher probability of convergence whereas darker regions are those whose values are further from zero and therefore show a lower probability of convergence.
 
-In addition, we can visualise the implications 2 and 3 in Sec.~\ref{sec::Theory} by comparing the heat-maps.
-We see in all of the heat-maps that the probability of convergence decreases as $\alpha$ increases (i.e., moving from left to right).
-At low values of $\alpha$, convergence is seen for all choices of $\Gamma$.
-However, as $\alpha$ increases, the overall likelihood of convergence rapidly decreases and
-%the convergence 
-it is more sensitive to the choice of $\Gamma$.
-A point to note is the implication that, with the increase of $p$ and $N$ comes a significant increase in the likelihood of convergence.
-This implication experimental evaluation \fb{?} and therefore can be seen as a limitation of (\ref{eqn::Final}).
-Instead, it should be viewed that, for a choice of $p, N$, the variation in stability of a system can be determined from $\alpha$ and $\Gamma$.
+We can visualise the implication 3 by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
+This occurs independent of the choice of $N$ or $p$.
+The implication 4 can be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$.
+The choice of $\Gamma$
+makes almost no difference in the evaluation of (\ref{eqn::Final}).
+We anticipate that this is due to the restriction of $\Gamma$ to be in the range $[-1, 0]$.
+In this range, the scaling effect of $\Gamma^2$ is dominated by the $\alpha^4$ and $\tau^4$ terms which appear in (\ref{eqn::Final}).
+
+Finally we can see implication 5, by comparing the heatmaps for different values of $p$ \textbf{denote them}.
+We see that, though the overall trend is the same, the heatmaps tend to be darker for higher $p$, suggesting that these lie further from the stability boundary.
 
@@
 
-To verify \fb{experimentally the theoretical results}, and to examine the underlying structure of stability and chaos in
+To verify experimentally the theoretical results, and to examine the underlying structure of stability and chaos in
 Multi-Agent Q-Learning, we perform a series of numerical experiments by varying the parameters $\Gamma$ and
-$\alpha$ whilst keeping $\tau$ fixed. The purpose 
-\st{of this experiment} is to determine a heuristic estimate for the Lyapunov exponent, which measures the degree to which initial conditions which start close to one another converge or diverge as the dynamics evolve \cite{Strogatz2000}.
+$\alpha$ whilst keeping $\tau$ fixed.
+The aim is to determine the regions in which games learnt using Q-Learning converge to an equilibrium.
+The results of these experiments are shown in Figure \ref{fig:NumericalExperiments}, with parameters chosen to match those in the analytic assessment (Figure \ref{fig:theory}).
+% By examination it is found that, in many cases the system oscillates about some equilibrium point in a low dimensional chaotic manner (i.e.
+the manner in which the action probabilities change is indistinguishable from random motion) \textbf{get some graphs for this}
+
+% The purpose 
+% \st{of this experiment} is to determine a heuristic estimate for the Lyapunov exponent, which measures the degree to which initial conditions which start close to one another converge or diverge as the dynamics evolve \cite{Strogatz2000}.
 The former indicates a stable system (in the sense of Lyapunov \cite{}) whilst the latter signals instability.
@@
 To generate the numerical simulations in Figure~\ref{fig:NumericalExperiments} we used the
-following procedure.
+following procedure. Note in the following that for any heatmap in which $\tau$ is swept over, the roles of $\alpha$ and $\tau$ are swapped.
 \begin{enumerate}
-   \item Fix the paremeters $\tau, \gamma$. The latter is held at 0.5 in all experiments as (\ref{eqn::EOM}) indicates that the value of $\gamma$ does not affect the overall behaviour of the system.
-   \item Initialise values of $\Gamma, \alpha$. These will be swept over in the experiment.
-\item Generate 5 payoff matrices for both agents by sampling from a multi-variate Gaussian 
+   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05 and the latter at 0.1. For the heatmaps in which $\tau$ is swept over $\alpha$ is held fixed at 0.05.
+   \item Initialise values of $\Gamma, \alpha$ (or $\tau$ appropriately). These will be swept over in the experiment.
+\item Generate 15 payoff matrices for both agents by sampling from a multi-variate Gaussian 
 (variables are the payoff elements) with mean zero and covariance parameterised by $\Gamma$.
-\item Initialise 2 sets of agents (denote their action probabilities as $\Vec{A_1}$ and $\Vec{A_2}$ respectively) each with random initial conditions (i.e., random action probabilities).
-\item Allow both sets of agents to learn over a maximum of $1 \times 10^4$ iterations.
-\item After 500 iterations measure the distance $\Vec{\delta_1} = |A_2 - A_1|$
-\item After 10000 iterations measure the distance $\Vec{\delta_n} = |A_2 - A_1|$
-\item Determine \fb{the Lyapunov exponent} 
-\begin{eqnarray*}
-\label{eq::LiapExpo}
-    \lambda_n & = & \max_{i} 10^{-4} ln(\delta_{n, i}/\delta_{1, i})
-\end{eqnarray*}
-for each action $i$ and average this value over all five realisations of the payoff matrix. 
+\item For each of these payoff matrices, initialise a set of agents with random initial conditions (i.e., random action probabilities).
+\item Allow both sets of agents to learn over a maximum of $1.5 \times 10^4$ iterations.
+\item Keep track of the action probabilities over a window of 500 iterations.
+At the end of each window, determine the percentage difference between the maximum and minimum values of each strategy component
+\item If the difference is less than 1 \% consider the game converged. Otherwise continue to the next window.
+\item If the game reaches $1.5 \times 10^4$ iterations without satisfying the relative distance criterion, consider it to be non-convergent.
+Determine the fraction of these 15 games which have converged.
+
+% \item After 500 iterations measure the distance $\Vec{\delta_1} = |A_2 - A_1|$
+% \item After 10000 iterations measure the distance $\Vec{\delta_n} = |A_2 - A_1|$
+% \item Determine \fb{the Lyapunov exponent} 
+% \begin{eqnarray*}
+% \label{eq::LiapExpo}
+%     \lambda_n & = & \max_{i} 10^{-4} ln(\delta_{n, i}/\delta_{1, i})
+% \end{eqnarray*}
+% for each action $i$ and average this value over all five realisations of the payoff matrix. 
 \end{enumerate}
 
-This yields the result shown in Figure~\ref{fig:NumericalExperiments}. We see from this that the stability of the system is highly dependent on
-the value of $\alpha$ and (although less so) on $\Gamma$.
+We see in Figure \ref{fig:NumericalExperiments} that the stability of the system is highly dependent on
+the value of $\alpha$ and $\tau$ but not on $\Gamma$.
 
@@
 This observation remains as we increase the value of $N$.
-We do, however, notice some discrepancy between the boundary of stability predicted by the analytic result and that revealed in experiments.
-This is largely due to the assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made during the derivation.
-The remaining discrepancy is partially due to the aforementioned error \fb{approximation?} in the calculation of $q$, $\chi$ and \st{partially due to} the fact that the analytic result considers the expected behaviour of Q-Learning.
-We expect that averaging over a greater number of payoff realisations and initial conditions will yield a more representative assessment of the average behaviour of Q-Learning.
+As noted, the analytic result over-estimates the region of instability due to the assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made during the derivation.
+Remaining discrepancies are partially due to the aforementioned approximation in the calculation of $q$, $\chi$ and the fact that the analytic result considers a continuous time approximation of the expected behaviour of Q-Learning.
+We expect that testing over a greater number of payoff realisations and initial conditions will yield a more representative assessment of the average behaviour of Q-Learning.
 However, running these experiments is a computationally expensive procedure: for $p$ players and $N$ actions we require operations on $p$ matrices with $N^{p}$ elements.
@@
 A point which we wish to discuss here is the difference in the result found w.r.t.~\cite{Sanders2018}, which considered the stability of \textit{Experience Weighted Attraction} (EWA).
-\st{and those found in this study.} Namely, Sanders et al.~found that convergence is seen for higher values of $\alpha$, whereas lower values give rise to chaos, the opposite of what is found here.
+Namely, Sanders et al.~found that convergence is seen for higher values of $\alpha$, whereas lower values give rise to chaos, the opposite of what is found here.
 The reason for this can be seen in the update equation of Q-Learning (\ref{eqn::Qupdate}), whereby
-\st{in which we see that} 
 smaller values of $\alpha$ result in the agent placing a lower weight on the reward received at each step.
@@
 Yet, the difference in stability caused by this change is significant.
-We believe this highlights the importance of performing analyses such as the present work; it allows for a method to analytically compare the difference between learning algorithms and, for practitioners, ensure that the appropriate algorithm is chosen for the parameters of their specific task.
+This highlights the importance of performing analyses such as the present work; it allows for a method to analytically compare the difference between learning algorithms and, for practitioners, ensure that the appropriate algorithm is chosen for the parameters of their specific task.
 
-A limitation of (\ref{eqn::Final}) is that it predicts that convergence should increase as $N$ and $p$ decreases \fb{or increase?}, a notion that does not seem to hold true in our experimental results.
-We hypothesize that this is a feature of raising the system to the $N \rightarrow \infty$ limit.
-\fb{The following paragraph seems a rather daunting criticism of the paper.
-Any chance it can be rephrased to emphasize the positive contribution?
-This assumption means that the analytic result does not lie on the true boundary between convergence and chaos and, in the particular case of Q-Learning, predicts a higher overall probability of convergence than is actually the case.} Instead, as the experiments show, the probability of convergence is higher for games with lower numbers of actions and, in fact, convergence is almost ubiquitous for a 2-player, 2-action game.
+To summarise, we have shown that the analytic result (\ref{eqn::Final}) provides a strong assessment for the effect that $\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of convergence of Q-Learning.
+We show that, at least for negatively correlated payoffs, the strength of correlation plays no role in determining the stability of the system.
+Furthermore, though (\ref{eqn::Final}) overestimates the region of instability, it accurately conveys that convergence of Q-Learning is unlikely for games with many players and actions.
+In fact, our experimental results also verify that stability may only be guaranteed for the limiting case of two-player, two-action games.
 
-To summarise, we have shown that the analytic result (\ref{eqn::Final}) provides a strong assessment for the effect that $\alpha$, $\Gamma$ and $p$ have on the likelihood of convergence of Q-Learning.
-We show that the behaviour of the stability line differs from that of EWA and suggest that this shows that a stability analysis is an important mode of analysis for reinforcement learning equations to ensure that parameters are being chosen appropriately to guarantee the safe convergence of learning.
+Finally, we show that the behaviour of the stability line differs from that of EWA and suggest that this shows that a stability analysis is an important mode of analysis for reinforcement learning equations to ensure that parameters are being chosen appropriately to guarantee the safe convergence of learning.
 
@@
 This yields a number of important results.
-We find that convergence to a unique fixed point is found for low values of $\alpha$, the \textit{step length} of the algorithm and for negatively correlated payoff matrices.
+We find that convergence to a unique fixed point is found for low values of $\alpha$, the \textit{step length} of the algorithm and for negatively correlated payoff matrices, though the strength of correlation $\Gamma$ does not influence stability.
 As $\alpha$ increases, the likelihood of convergence decreases.
-For positively correlated payoffs, our analysis no longer guarantees the uniqueness of a fixed point.
+The same is true for the \textit{intensity of choice} parameter $\tau$.
+Our analysis also shows that the likelihood of convergence decreases, regardless of parameter choice as the number of players $p$ in the system increases.
 

### 2020-10-06 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -9,7 +9,7 @@ gamma = .1
 Gamma = 0.1
 tau = 5e-2
 
-nActions = 2
+nActions = 5
 t0 = 500
 
 initnSim = 15

### 2020-10-06 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor edits

@@
 \begin{abstract}
-Modelling the dynamics of Q-Learning is an active and important topic for the sake of developing an {\em a priori} understanding of Reinforcement Learning.
-In this paper, we use methods from evolutionary game theory to analyse the stability of Q-Learning in $p$-player games, where payoffs are randomly generated.
-We determine the parameter range in which Q-Learning is expected to settle to a stable fixed point and the range in which the dynamics are unstable.
+Modelling the dynamics of Q-Learning is an active and important topic
+for the sake of developing an {\em a priori} understanding of
+Reinforcement Learning. In this paper, we use methods from
+evolutionary game theory to analyse the stability of Q-Learning in
+$p$-player games, where payoffs are randomly generated. We determine
+the parameter range in which Q-Learning is expected to settle to a
+stable fixed point and the range in which the dynamics are unstable.
 
-This study allows for parameters to be appropriately chosen to ensure the safe convergence of a learning algorithm and as a first step towards understanding the range of behaviours that can be displayed by learning using the Q-Learning algorithm.
-We validate our theoretical results through numerical simulation and show that, within the bounds of experimental error, the region of instability can be characterised by the learning dynamics.
+This study allows for parameters to be appropriately chosen to ensure
+the safe convergence of a learning algorithm and as a first step
+towards understanding the range of behaviours that can be displayed by
+learning using the Q-Learning algorithm. We validate our theoretical
+results through numerical simulation and show that, within the bounds
+of experimental error, the region of instability can be characterised
+by the learning dynamics.
 \end{abstract}
@@
 
-In this section we \st{will} establish some of the preliminaries which are
-required to follow the subsequent sections. The first is \textit{dynamical behaviours}, 
-which considers the evolution of agent strategies as they
-learn on an iterated game. This study aims to classify, based on the
-agent parameters and the payoff matrices, which of these behaviours
-will be observed. The second is \textit{dynamics of Q-Learning}, which are a set
-of equations that model the aforementioned strategy evolution. It is
-on these dynamics that we \st{will} perform our analysis.
+In this section we establish some of the preliminaries which
+are required to follow the subsequent sections. The first regards
+\textit{dynamical behaviours}, which considers the evolution of agent
+strategies as they learn how to play an iterated game. This study aims to
+classify, based on the agent parameters and the payoff matrices, which
+of these behaviours will be observed. The second is the \textit{dynamics
+  of Q-Learning}, which are a set of equations that model the
+aforementioned strategy evolution. It is on these dynamics that we
+%\st{will}
+perform our analysis.
 
@@
 
-    As discussed in the previous section, when learning on iterated games, player
-    strategies may exhibit much more complex behaviour than
-    convergence to a Nash Equilibrium (NE),
-    including convergence to a unique
-    equilibrium (though not always to an NE), convergence to one of
-    multiple equilibria, limit cycles and chaos. These behaviours are
-    illustrated in Fig.\ref{fig::DynamicalBehaviours}. To be able to predict the behaviour of a learning algorithm, it should ideally converge to a stable equilibrium
-    although it is still possible to study systems with multiple
-    equilibria or limit cycles \cite{Strogatz2000}. However, it would
-    be difficult to control systems whose dynamics are governed by
-    chaos (though research into controlling chaos is ongoing and rife
-    with opportunity \cite{Fradkov2009}). It would, therefore, be a useful endeavour to
-    determine the conditions under which these sorts of behaviours
+    As discussed in the previous section, when learning on iterated
+    games, player strategies may exhibit much more complex behaviours
+    than convergence to a Nash Equilibrium (NE), including convergence
+    to a unique equilibrium (though not always to an NE), convergence
+    to one of multiple equilibria, limit cycles, and chaos. These
+    behaviours are illustrated in
+    Fig.\ref{fig::DynamicalBehaviours}. To be able to predict the
+    behaviour of a learning algorithm, it should ideally converge to a
+    stable equilibrium although it is still possible to study systems
+    with multiple equilibria or limit cycles
+    \cite{Strogatz2000}. However, it would be difficult to control
+    systems whose dynamics are governed by chaos (though research into
+    controlling chaos is ongoing and rife with opportunity
+    \cite{Fradkov2009}). It would, therefore, be a useful endeavour to
+    determine the conditions under which the different sorts of behaviours
     arise.
@@
         d) Chaotic behaviour, here small deviations in the initial conditions can grow
-        exponentially. b-d drawn from \cite{Sanders2018}}
-
+        exponentially. b-d drawn from \cite{Sanders2018}.}
     \end{figure}
@@
 systems, from harmonic pendulums to geophysical fluids, can be
-understood. A growing body of research aims to understand
-multi-agent reinforcement learning through the lens of its
-dynamics. In this light, \cite{Tuyls2006AnGames} presents of derivation of a continuous time dynamical
-system describing how agents following a Q-Learning approach adjust the probabilities of choosing actions
-as they iteratively play a game. The Q-Learning approach considered requires an agent to choose an action $i$ at step $k+1$ with probability
+understood. A growing body of research aims to understand multi-agent
+reinforcement learning through the lens of its dynamics. In this
+light, \cite{Tuyls2006AnGames} presents of derivation of a continuous-time dynamical system describing how agents following a Q-Learning
+approach adjust the probabilities of choosing actions as they
+iteratively play a game. The Q-Learning approach considered requires
+an agent to choose an action $i$ at step $k+1$ with probability
 
@@
 \end{equation}
-
-where $\tau$ is the \textit{intensity of choice} as defined at the end of this section and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to
+%
+where $\tau \in [0, \infty)$ is the \textit{intensity of choice} as described at the end of this section and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to
 %
@@
 \end{equation}
-
-where $\alpha$ is the \textit{step length} parameter defined below, $r$ is the immediate reward received and $\gamma$ is a discount factor.
+%
+where $\alpha \in [0, 1]$ is the \textit{step length} parameter described below, $r$ is the immediate reward received, and $\gamma \in [0, 1]$ is the discount factor.
 
 Through their analysis, Tuyls et al. were able to
-arrive at the following dynamical model of Multi-Agent Q-Learning
+arrive at the following dynamical model of multi-agent Q-Learning
 %
@@
 
-Here, $\alpha$ and $\tau$ are the parameters of the agent as described at the end of this section. Agent 1 (resp.~agent 2) takes action $i$ with probability
+Here,
+%$\alpha$ and $\tau$ are the parameters of the agent as described at the end of this section.
+agent 1 (resp.~agent 2) takes action $i$ with probability
 $x_i$ (resp.~$y_j$).
@@
 receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-predict the expected behaviour of Q-Learning agents which they go on to verify.
+predict the expected behaviour of Q-Learning agents which they go on to verify \fb{how? empirically?}.
 
-It is clear from (\ref{eqn::EOM}) that the long-term strategy selection of
-these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$.
-In light of this, the following sections aim to address the question presented in the introduction: how do these elements influence the types of behaviours seen during
-learning on an iterated game? Specifically, the parameters we will consider are:
-
+It is clear from (\ref{eqn::EOM}) that the long-term strategy
+selection of these agents is determined by the parameters $\alpha,
+\tau$ and the payoffs $a_{ij}, b_{ij}$. In light of this, this
+contributions aims to address the question presented in the
+introduction: how do these parameters influence the types of behaviours
+seen during learning on an iterated game? Specifically, the parameters
+we will consider are:
+%
 \begin{enumerate}
@@
     denotes longer memory.
-    \item $\tau \in [0, \infty)$: the \textit{intensity of choice}, as termed by Sanders et al. 
-    \cite{Sanders2018}. This is sometimes written as $\beta$ in the literature \cite{Sutton2018}.
-    $\tau = 0$ results in all actions being selected with equal probability, regardless of their
-    Q-value, whilst $\tau \rightarrow \infty$ results in the action with the highest Q-value chosen
-    at every step. This may be considered the \textit{exploration-exploitation parameter}. For greater
-    details into these parameters, the interested reader should consult \cite{Sutton2018}.
-    \item $\Gamma \in [-1, p-1]$: the \textit{payoff correlation}.
-Since there are an infinite number of realisations of the payoffs $a_{ij}, b_{ij}$, we instead analyse the behaviour for the average payoff case.
-To do this, we assume that the payoff matrices are drawn from a multi-variate Gaussian with mean zero and
-    covariance matrix parameterised by $\Gamma$. We then average over this Gaussian. $\Gamma = -1$ indicates a zero
-    sum game, in which the sum of payoffs for a given action across all agents is 0, resulting in a
-    purely competitive game. $\Gamma = p-1$ gives a purely cooperative game in which all agents
-    share the same payoffs. The manner in which a game is generated from the choice of $\Gamma$ is
-    described in (\ref{eqn::Payoffs}) and follows the same procedure as outlined in \cite{Sanders2018}.
+
+    \item $\tau \in [0, \infty)$: the \textit{intensity of choice}, as
+      termed by Sanders et al.  \cite{Sanders2018}. This is sometimes
+      written as $\beta$ in the literature \cite{Sutton2018}.  $\tau =
+      0$ results in all actions being selected with equal probability,
+      regardless of their Q-value, whilst $\tau \rightarrow \infty$
+      results in the action with the highest Q-value chosen at every
+      step. This may be seen as the \textit{exploration-exploitation
+        parameter}. For greater details into these parameters, the
+      interested reader should consult \cite{Sutton2018}.
+
+    \item $\Gamma \in [-1, p-1]$: the \textit{payoff
+      correlation}. Since there are an infinite number of realisations
+      of the payoffs $a_{ij}, b_{ij}$, we instead analyse the
+      behaviour for the average payoff case. To do this, we assume
+      that the payoff matrices are drawn from a multi-variate Gaussian
+      with mean zero and covariance matrix parameterised by
+      $\Gamma$. We then average over this Gaussian. $\Gamma = -1$
+      indicates a zero sum game, in which the sum of payoffs for a
+      given action across all agents is 0, resulting in a purely
+      competitive game. $\Gamma = p-1$ gives a purely cooperative game
+      in which all agents share the same payoffs. The manner in which
+      a game is generated from the choice of $\Gamma$ is described in
+      (\ref{eqn::Payoffs}) below and follows the same procedure as
+      outlined in \cite{Sanders2018}.
 \end{enumerate}
@@
 
-In this section we aim to determine how the choice of parameters $\alpha$ and $\tau$, alongside the choice of payoff matrix, affect the stability of the dynamics of Q-learning.
-However, as the values in the payoff matrix can take any real number, there are an infinite number of possible realisations of games.
-Of course, it would not be possible to analyse every possible game, we instead follow the procedure outlined in \cite{Coolen2005} and \cite{Galla2013} to average over these realisations and, instead, analyse the \textit{effective dynamics}, the dynamics averaged over all realisations of payoff matrices.
-Then, we perform a linear stability analysis around equilibrium points to determine the conditions under which a fixed point is stable.
+In this section we aim to determine how the choice of parameters
+$\alpha$ and $\tau$, alongside the choice of payoff matrix, affect the
+stability of the dynamics of Q-learning. However, as the values in the
+payoff matrix can take any real number, there are an infinite number
+of possible realisations of games. Of course, it would not be possible
+to analyse every possible game, we instead follow the procedure
+outlined in \cite{Coolen2005} and \cite{Galla2013} to average over
+these realisations and, instead, analyse the \textit{effective
+  dynamics}, the dynamics averaged over all realisations of payoff
+matrices. Then, we perform a linear stability analysis around
+equilibrium points to determine the conditions under which a fixed
+point is stable.
 
-Our first point of call is to extend the dynamics of Tuyls et al.~in  (\ref{eqn::EOM}a) and (\ref{eqn::EOM}b) to a general $p$-player game.
-This yields the dynamics (\ref{eqn::pEOM}).
-Here, player $\mu$ chooses action $i_{\mu}$ from its action space $\mathcal{A}$ at time $t$ with probability $\xmu{i}{\mu}$ and receives a reward $\payoff{i}{\mu}$ from its payoff matrix $P^\mu$ depending on its own action and the actions of all other agents $i_{-\mu}$.
-Formally, the notation $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2, ..., p\} \backslash \{\mu\} \}$ and $-i_{\mu}$ denotes the set $\mathcal{A} \backslash {i_\mu}$.
+Our first point of call is to extend the dynamics of Tuyls et al.~in
+(\ref{eqn::EOM}a) and (\ref{eqn::EOM}b) to a general $p$-player
+game. This yields the dynamics (\ref{eqn::pEOM}). Here, player $\mu$
+chooses action $i_{\mu}$ from its action space $\mathcal{A}$ at time
+$t$ with probability $\xmu{i}{\mu}$ and receives a reward
+$\payoff{i}{\mu}$ from its payoff matrix $P^\mu$ depending on its own
+action and the actions of all other agents $i_{-\mu}$. Formally, the
+notation $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2,
+\ldots , p\} \backslash \{\mu\} \}$ and $-i_{\mu}$ denotes the set
+$\mathcal{A} \backslash {i_\mu}$.
 

### 2020-10-07 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor edits

@@
 stability of the dynamics of Q-learning. However, as the values in the
-payoff matrix can take any real number, there are an infinite number
+payoff matrix can take any real number, there is an infinite number
 of possible realisations of games. Of course, it would not be possible
@@
 
+\fb{do we mention anywhere the format of these games?}
+
 Our first point of call is to extend the dynamics of Tuyls et al.~in
@@
 $\payoff{i}{\mu}$ from its payoff matrix $P^\mu$ depending on its own
-action and the actions of all other agents $i_{-\mu}$. Formally, the
-notation $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2,
-\ldots , p\} \backslash \{\mu\} \}$ and $-i_{\mu}$ denotes the set
-$\mathcal{A} \backslash {i_\mu}$.
+action and the actions of all other agents $i_{-\mu}$, where $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2,
+\ldots , p\} \setminus \{\mu\} \}$ and $-i_{\mu}$ denotes the set
+$\mathcal{A} \setminus {i_\mu}$.
+%
+\begin{eqnarray}
+%\begin{split}
+    \frac{\dot{\xmu{i}{\mu}}}{\xmu{i}{\mu}} \!
+\!
+\!
+\!
+\!
+\!
+& = \!
+\!
+\!
+\!
+\!
+\!
+& \alpha \tau \left( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} -  \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right) \nonumber \\
+    & & + \alpha \sum_{j_\mu \in -i_\mu} \xmu{j}{\mu} ln \frac{\xmu{j}{\mu}}{\xmu{i}{\mu}}     \label{eqn::pEOM}
+%\end{split}
+\end{eqnarray}
 
-\begin{equation}
-\begin{split}
-    \label{eqn::pEOM}
-    \frac{\dot{\xmu{i}{\mu}}}{\xmu{i}{\mu}} = \alpha \tau ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} - \\ \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} ) + \alpha \sum_{j_\mu \in -i_\mu} \xmu{j}{\mu} ln \frac{\xmu{j}{\mu}}{\xmu{i}{\mu}}
-\end{split}
-\end{equation}
-
-We now need to scale the system so that $\sum_{i_\mu} \xmu{i}{\mu} = 1$.
-The reason for this scaling is that, as the number of agents $p$ and number of actions $N$ increases, the expected payoffs that agent $\xmu{i}{\mu}$ receives becomes less distinguishable across its action space.
-Therefore, the system must be scaled to ensure appreciable differences across actions, so that the agent can choose its actions appropriately (see the discussion in \cite{Sanders2018} or the Supplementary Material for further details).
-Accordingly we choose scaled variables (denoted with a tilde) as
+We now scale the system so that $\sum_{i_\mu} \xmu{i}{\mu} = 1$. The
+reason for this scaling is that, as the number of agents $p$ and
+number of actions $N$ increases, the expected payoffs that agent
+$\xmu{i}{\mu}$ receives becomes less distinguishable \fb{? all converge to the same value?} across its action
+space. Therefore, the system must be scaled to ensure appreciable
+differences across actions, so that the agent can choose its actions
+appropriately (see the discussion in \cite{Sanders2018} or the
+Supplementary Material for further details \fb{we might need to provide the actual section in the supplementary material}). Accordingly we choose
+scaled variables (denoted with a tilde) as
 %
@@
 
-This yields the scaled equation
+The substitution in (\ref{eqn::pEOM}) yields the scaled equation
+%
+\begin{eqnarray}
+%\begin{split}
+    \frac{\dtxmu{i}{\mu}}{\txmu{i}{\mu}} & = & \alpha \ttau \left ( \sum_{i_{-\mu}} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) \nonumber \\ & &  - \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \txmu{i}{\mu} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) \nonumber  \\  & & + \talpha \sum_{j_\mu \in -i_\mu} \txmu{j}{\mu} ln \frac{\txmu{j}{\mu}}{\txmu{i}{\mu}}    \label{eqn::scaledEOM}
+%\end{split}
+\end{eqnarray}
 
-\begin{equation}
-\begin{split}
-    \label{eqn::scaledEOM}
-    \frac{\dtxmu{i}{\mu}}{\txmu{i}{\mu}} = \alpha \ttau \left ( \sum_{i_{-\mu}} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) \\ - \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \txmu{i}{\mu} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) \\ + \talpha \sum_{j_\mu \in -i_\mu} \txmu{j}{\mu} ln \frac{\txmu{j}{\mu}}{\txmu{i}{\mu}}
-\end{split}
-\end{equation}
+Note that the scaled probabilities now satisfy the constraint
+$\sum_{i_\mu} \txmu{i}{\mu} = N$ \fb{but what about the constraint $\sum_{i_\mu} \xmu{i}{\mu} = 1$ mentioned above?}. For the remainder of this derivation
+we concern ourselves only with the scaled system so we drop the tilde
+notation on $P$ and $x$ \fb{on $\alpha$ and $\tau$ as well?}.
 
-Note that the scaled probabilities now satisfy the constraint $\sum_{i_\mu} \txmu{i}{\mu} = N$.
-For the remainder of this derivation we concern ourselves only with the scaled system so we drop the tilde notation on $P$ and $x$.
-
-As mentioned, we now wish to generalise the dynamics to account for all the possible realisations of the payoff matrix.
-To do this, we assert that the payoff elements (after scaling) are generated by a multivariate Gaussian distribution with mean zero and covariance given as
+As mentioned, we now
+%wish to
+generalise these dynamics to account for all the possible realisations
+of the payoff matrix. To do this, we assert that the payoff elements
+(after scaling) are generated by a multivariate Gaussian distribution
+with mean zero and covariance given as
 %
@@
 \label{eqn::Payoffs}
-    \begin{split}
+%    \begin{split}
         \mathbb{E}\left [ \payoff{i}{\mu} \payoff{i}{\nu} \right] = \begin{cases}
-        \frac{1}{N^{p-1}}  \text{ if } \nu = \mu \\
-        \frac{\Gamma}{(p-1) N^{p-1}} \text{ otherwise. }
+        \frac{1}{N^{p-1}} &  \text{ if } \nu = \mu \\
+        \frac{\Gamma}{(p-1) N^{p-1}} & \text{ otherwise. }
         \end{cases}
-    \end{split}
+%    \end{split}
 \end{equation}
 
-The motivation for choosing that the payoffs should be generated by a Gaussian is that it allows for the use of Gaussian identities when determining the average.
+The motivation for choosing that the payoffs is generated by a
+Gaussian is that it allows for the use of Gaussian identities when
+determining the average.
+
+\fb{can we give the equation already with the Gaussian?}
 
@@
 
-We then use a generating functional approach as outlined in \cite{Mezard1986} to average the dynamics over this multivariate Gaussian.
-The generating functional is a method derived from statistical mechanics which allows for expectations to be taken over equations of motion and, more specifically, allows for the analysis of systems with `quenched disorder'.
-These are variables which are random but held fixed in time as the system evolves (in our case these variables are the payoff elements).
-The generating functional is given as \cite{SpinGlassTheory}
-
+We then use a generating functional approach as outlined in
+\cite{Mezard1986} to average the dynamics over this multivariate
+Gaussian. The generating functional is a method derived from
+statistical mechanics which allows for expectations to be taken over
+equations of motion and, more specifically, allows for the analysis of
+systems with `quenched disorder': these are
+variables which are random but held fixed in time as the system
+evolves (in our case these variables are the payoff elements). The
+generating functional is given as \cite{SpinGlassTheory}
+%
+\fb{check for missing references, i.e., '?'}
 \begin{equation}
@@
 
-where the equations of motion are the Lagrange equations of motion given in (
-\ref{eqn::scaledEOM}) and
-the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
-calculation. $\delta$ denotes the Dirac delta function. Implementing our equation of motion yields
-
+where the equations of motion are the Lagrange equations of motion
+given in ( \ref{eqn::scaledEOM}) and the fields $\Vec{\psi_i(t)}$ and
+$\Vec{\phi_i(t)}$ will be set to zero at the end of the
+calculation. $\delta$ denotes the Dirac delta function. Substituting
+for our equation of motion yields
+%
+{\small
 \begin{equation}
@@
 \end{equation}
-
+}
 The last two exponentials contain the payoffs of the game.
@@
 We define $Q$ to be the product of the second and third exponentials in (\ref{eqn::separatePayoffs})
-
+%
+\fb{why $<Q>$?}
 \begin{equation}
@@
 In which
+%
+\begin{eqnarray*}
+\label{eqn::correlations}
+%    \begin{split}
+        C^\mu (t, t') &  := & N^{-1} \sum_i \xmu{i}{\mu} \xmudash{i}{\mu} \\
+        L^\mu (t, t') & :=  & N^{-1} \sum_i \hxmu{i} \hxmudash{i} \\
+        K^\mu (t, t') & :=  & N^{-1} \sum_i \xmu{i}{\mu} \hxmudash{i} \\
+        A^{\mu, \nu} (t, t') & := &  N^{-1} \sum_i \hxmu{i} \hxnudash{i}.
+%    \end{split}
+\end{eqnarray*}
+\fb{why using symbol $:=$ here?}
 
-\begin{align}
-\label{eqn::correlations}
-    \begin{split}
-        C^\mu (t, t') & :=  N^{-1} \sum_i \xmu{i}{\mu} \xmudash{i}{\mu} \\
-        L^\mu (t, t') & :=  N^{-1} \sum_i \hxmu{i} \hxmudash{i} \\
-        K^\mu (t, t') & :=  N^{-1} \sum_i \xmu{i}{\mu} \hxmudash{i} \\
-        A^{\mu, \nu} (t, t') & :=  N^{-1} \sum_i \hxmu{i} \hxnudash{i}.
-    \end{split}
-\end{align}
-
-By taking this average, described in further detail in the Supplementary Material, we obtain the \textit{effective dynamics}
+By taking this average, described in further detail in the Supplementary Material \fb{just say this at the beginning only}, we obtain the \textit{effective dynamics}
 
@@
 in which we have assumed that all players' actions are independent and drawn from the same initial distribution (i.i.d)
-and therefore dropped the distinction between players and strategy components.
-The terms $G, C, \eta_1, \eta_0$ are correlation functions, generated during when averaging the Gaussian.
-These are given by
-
+and therefore dropped the distinction between players and strategy components. The terms $G, C, \eta_1, \eta_0$ are correlation functions, generated when averaging the Gaussian. These are given as 
+%
 \begin{eqnarray*}
@@
 
-It is important to note the effect of the former assumption (that all actions of all agents are i.i.d) is substantial.
-With this assumption, we identify the coupled term $A^{\mu, \nu} (t, t')$ in (\ref{eqn::correlations}) with the uncoupled term $L^\mu (t, t')$ (since there is no distinction between the actions of agents $\mu$ and $\nu$).
-This is a strong assumption which removes the interdependency between agents in the analysis.
-However, as shown by the experimental evaluation, it does not produce a strong discrepancy in describing the qualitative effect on stability caused by the parameters $\alpha, \Gamma, \tau$.
+It is important to note the effect of the former assumption (that all
+actions of all agents are i.i.d) is substantial. With this assumption,
+we identify the coupled term $A^{\mu, \nu} (t, t')$ in
+(\ref{eqn::correlations}) with the uncoupled term $L^\mu (t, t')$
+(since there is no distinction between the actions of agents $\mu$ and
+$\nu$). This is a strong assumption which removes the interdependency
+between agents in the analysis. However, as shown by the experimental
+evaluation, it does not produce a strong discrepancy in describing the
+qualitative effect on stability caused by the parameters $\alpha$,
+$\Gamma$, and $\tau$.
+
+\fb{you can also mention the simplification in calculation.}
 
@@
 
-We now analyse the stability of this system in a neighbourhood around the fixed point.
-This follows a similar procedure as in \cite{Opper1992}, in which the fixed point dynamics are proposed to be perturbed by a disturbance $\xi(t)$ which is drawn from a Gaussian of zero mean and unit variance.
-The disturbance causes the values of $x(t)$ and $\eta_0(t), \eta_1(t)$ to deviate from their fixed point position $\xfixed, \ezerof, \eonef$ by an amount $\xpert, \ezeropert, \eonepert$.
-If we consider only the terms which are linear in these perturbations, we arrive at the dynamics
+We now analyse the stability of this system in a neighbourhood around
+the fixed point \fb{how do we know there is a fixed point in first
+  place?}. This follows a similar procedure as in \cite{Opper1992}, in
+which the fixed point dynamics are proposed to be perturbed by a
+disturbance $\xi(t)$ which is drawn from a Gaussian of zero mean and
+unit variance. The disturbance causes the values of $x(t)$ and
+$\eta_0(t), \eta_1(t)$ to deviate from their fixed point position
+$\xfixed, \ezerof, \eonef$ by an amount $\xpert, \ezeropert,
+\eonepert$.  If we consider only the terms which are linear in these
+perturbations \fb{why only those?}, we arrive at the dynamics
 
-\begin{equation}
+\begin{eqnarray}
+%    \begin{split}
+\frac{d}{dt} \xpert & = & (\xfixed + \xpert) [ \alpha^2 \ttau^2 \Gamma \xfixed \int dt' [ G(t, t')C^{p - 2}(t, t') ] \nonumber \\
+  & & + \sqrt{2} \alpha \ttau \eonef + \sqrt{2} \alpha \htau \ezerof + \talpha \rho] \nonumber \\
+& &  + \xfixed [\alpha^2 \ttau^2 \Gamma \int dt' [ G(t, t')C^{p - 2}(t, t') \xpertdash ] \nonumber \\
+  & & + \sqrt{2} \alpha \ttau \eonepert + \sqrt{2} \alpha \htau \ezeropert + \xi(t)].
 \label{eqn::Linearised}
-    \begin{split}
-        \frac{d}{dt} \xpert = (\xfixed + \xpert) [ \alpha^2 \ttau^2 \Gamma \xfixed \int dt' [ G(t, t')C^{p - 2}(t, t') ]\\ + \sqrt{2} \alpha \ttau \eonef + \sqrt{2} \alpha \htau \ezerof + \talpha \rho] \\
-        + \xfixed [\alpha^2 \ttau^2 \Gamma \int dt' [ G(t, t')C^{p - 2}(t, t') \xpertdash ] \\ + \sqrt{2} \alpha \ttau \eonepert + \sqrt{2} \alpha \htau \ezeropert + \xi(t)].
-    \end{split}
-\end{equation}
+%    \end{split}
+\end{eqnarray}
 
 At a fixed point, then, the perturbations $\xpert$ will be zero, leaving
+%
+\begin{eqnarray}
+%    \begin{split}
+    0 & = & \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{n-1} \chi + \nonumber \\
+      &  & + \sqrt{2} \alpha \ttau q^{n/2}z + \sqrt{2} \alpha \htau q^{(n+1)/2} z^{(n+1)/n}]
+    \label{eqn::fixed_point}
+%    \end{split}
+\end{eqnarray}
+%
+where $\chi = \int dt' G(t - t')$, $\eta_0(t) = q^{n/2}z$, $z$ is
+drawn from a Gaussian of zero mean and unit variance, and $n = p -
+1$. By using (\ref{eqn::fixed_point}) we can
+%his gives us an expression for
+calculate $\xfixed$. We disregard the choice $\xfixed = 0$, since we
+assume that no action will be chosen with exactly zero probability, an
+intuitive assumption which is also considered in \cite{Sanders2018}
+and \cite{Coolen2005}. The expression inside the squared bracket
+admits a positive solution only in the region $\Gamma \in [-1, 0]$,
+whilst for positive $\Gamma \leq p -1$, the nature of solutions may
+not be guaranteed. Therefore, we restrict our analysis to the region
+$[-1, 0]$.
 
-\begin{equation}
-    \begin{split}
-    \label{eqn::fixed_point}
-        0 = \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{n-1} \chi + \\ + \sqrt{2} \alpha \ttau q^{n/2}z + \sqrt{2} \alpha \htau q^{(n+1)/2} z^{(n+1)/n}],
-    \end{split}
-\end{equation}
-
-where $\chi = \int dt' G(t - t')$, $\eta_0(t) = q^{n/2}z$ and $z$ is drawn from a Gaussian of zero mean and unit variance and $n = p - 1$.
-This gives us an expression for calculating $\xfixed$.
-We disregard the choice $\xfixed  = 0$, since we assume that no action will be chosen with exactly zero probability, an intuitive assumption which is also considered in \cite{Sanders2018} and \cite{Coolen2005}.
-The expression inside the squared bracket admits a positive solution only in the region $\Gamma \in [-1, 0]$, whilst for positive $\Gamma$, the nature of solutions may not be guaranteed.
-Therefore, we restrict our analysis to this region.
-
-Having arrived at a condition for the fixed point, we then examine the long-term behaviour of the perturbation $\xpert$.
-To do this, we take the Fourier transform of (\ref{eqn::Linearised}) and analyse its behaviour at $\omega = 0$.
-After some manipulation, which are given in the Supplementary Material, this gives
+Having arrived at a condition for the fixed point, we then examine the
+long-term behaviour of the perturbation $\xpert$. To do this, we take
+the Fourier transform of (\ref{eqn::Linearised}) and analyse its
+behaviour at $\omega = 0$. After some manipulation (see the supplementary material), this gives
 
@@
 
-It should be noted that, to arrive at this result, we have had to take the assumption that $2 >> 1/n$.
+It should be noted that, to arrive at this result, we have had to take the assumption that $2 >> 1/n$ \fb{is it justified?}.
 
@@
 As $p$ increases, this term drives the system further from the stability boundary.
+
+      \fb{how are these remarks corroborated by the experimental results?}
 

### 2020-10-07 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Included p variation

--- 2020-10-06 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-Finally we can see implication 5, by comparing the heatmaps for different values of $p$ \textbf{denote them}.
-We see that, though the overall trend is the same, the heatmaps tend to be darker for higher $p$, suggesting that these lie further from the stability boundary.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width = 0.9 \linewidth]{Figures/p variation.png}
+    \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$.
+Here, $\alpha$ is fixed at 0.02, $\tau = 0.05$, $N = 2$ and $\Gamma = -1$.
+$p$ is varied from 2 to 12.
+We see that the value obtained by (\ref{eqn::Final}) tends away from zero monotonically.}
+    \label{fig:pvariation}
+\end{figure}
+
+Finally we can see implication 5, by considering Figure \ref{fig:pvariation}.
+In this we keep all parameters, except for $p$, fixed and evaluate the right hand side of (\ref{eqn::Final}) for varying $p$.
+We see that the trend is to tend away from the stability boundary, indicating that as the number of players in the system increases, so too does the region of instability.
 
@@
     \centering
-    \includegraphics[width = 0.9 \linewidth]{Figures/Experiments.png}
-    \caption{Results of numerical experiments.
-The heat-maps show the value of the Lyapunov Exponent determined by the procedure outlined in this section scaled by $1 \times 10^5$ for convenience.
-Lighter values show a higher exponent whilst darker values indicate lower values.
+    \includegraphics[width = 1.2 \linewidth]{Figures/Experiments.png}
+    \caption{Results of numerical experiments in which $\alpha$ is varied.
+The heatmaps show the fraction of games which converge to an equilibrium.
+Lighter values show higher convergence.
 Each experiment is run with $\tau = 0.05$.
-(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 4$, (Mid-Left) $p = 2, N = 10$, (Mid-Right) $p = 2, N = 20$, (Bottom) $p = 3, N = 5$.}
+(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 5$, (Bottom Left) $p = 2, N = 20$, (Bottom Right) $p=3, N = 2$.}
     \label{fig:NumericalExperiments}
@@
 
-We note that the numerical experiments confirm the predictions suggested by the analytic results shown in Figure ....
+We note that the numerical experiments confirm the predictions suggested by the analytic results shown in Figure \ref{sec::Theory}.
 We notice that convergence occurs almost only for low values of $\alpha$.

### 2020-10-07 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
rollback
minor edits

--- 2020-10-07 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}).
-In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$.
-We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
+We illustrate these implications \fb{which implications? we might need a some more introductory beginning.} in Figure \ref{fig:theory}
+which plots the value obtained by the right hand side of
+(\ref{eqn::Final}). In order to determine these values, we first had
+to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the
+$\xfixed$ which solves the expression inside the square brackets of
+(\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach
+and use the following expressions for $q, \chi$ to determine their
+value.
 
-\begin{equation*}
-    \begin{split}
-        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
-        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
-        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
-    \end{split}
-\end{equation*}
+\begin{eqnarray*}
+%    \begin{split}
+        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
+        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
+        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+%    \end{split}
+\end{eqnarray*}
 
-It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.
-
-We consider each of the implications 2-5 from the previous section in turn, choosing to forego illustrating 1 as it can be seen trivially from the expression.
-In those heatmaps for which $\tau$ is held fixed \textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$.
-For those in which $\alpha$ is held fixed, \textbf{denote them} we choose $\alpha =  0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
-
-By looking at the values of the heatmap, we see that, for all choices of the parameters, other than $\alpha = 0, \tau = 0$, (\ref{eqn::Final}) evaluates to a negative value, which signals instability.
-As such, the analysis over-estimates the region of instability.
-We believe that this is due to the heavy assumptions made during the derivation of the analytic result, the strongest of which was to drop the discrepancy between players and actions, treating each action of each player to be independent and identically distributed.
-However, even within the error that this assumption generates, it is still clear (and is verified experimentally) that convergence in Q-Learning is rare.
-Indeed as the choice of $N$ increases, the stability boundary determined by experiment (Figure \ref{fig:NumericalExperiments}) tends towards $\alpha = 0, \tau = 0$.
-
-Similarly, as the value of $N$ increases, the values in the heatmap (seen on the right of the map) reduce.
-This is due to the assumption made in the derivation of the analytic result that $N \rightarrow \infty$.
-As the value of N increases, the discrepancy between the true behaviour of the system and analytic result decreases.
-This does, however, give rise to a limitation of the result - namely that the effect of the number of actions $N$ cannot be accurately inferred from the (\ref{eqn::Final}).
-However, it should still be noted that, even with the increase of N, the values in parameter space remain negative and still, accurately, predict instability.
-We go on to verify that the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured by (\ref{eqn::Final}).
-
-We interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero).
-A choice of parameters which evaluates close to the stability boundary has a higher chance (by the analytic error) of being convergent than one which lies further from the boundary.
-Therefore, the heat-maps in Figure \ref{fig:theory} should be considered to show the probability of convergence for a choice of $(\alpha, \Gamma)$.
-Lighter regions denote a higher probability of convergence whereas darker regions are those whose values are further from zero and therefore show a lower probability of convergence.
-
-We can visualise the implication 3 by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
-This occurs independent of the choice of $N$ or $p$.
-The implication 4 can be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$.
-The choice of $\Gamma$
-makes almost no difference in the evaluation of (\ref{eqn::Final}).
-We anticipate that this is due to the restriction of $\Gamma$ to be in the range $[-1, 0]$.
-In this range, the scaling effect of $\Gamma^2$ is dominated by the $\alpha^4$ and $\tau^4$ terms which appear in (\ref{eqn::Final}).
-
-Finally we can see implication 5, by comparing the heatmaps for different values of $p$ \textbf{denote them}.
-We see that, though the overall trend is the same, the heatmaps tend to be darker for higher $p$, suggesting that these lie further from the stability boundary.
+It should be noted that this method of finding $\xfixed$ yields only
+an approximate value and so the $q, \chi$ which are found are
+estimates of their true value.
 
@@
 
+\subsection{Evaluating the Stability Analysis}
+
+\fb{I would restructure this section so that each point (2)-(5) is treated individually.}
+
+We consider each of the implications (2)-(5) from the previous section
+in turn, choosing to forego illustrating (1) as it can be seen immediately
+from the expression. In those heatmaps where $\tau$ is held fixed
+\textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in
+the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For
+those in which $\alpha$ is held fixed, \textbf{denote them} we choose
+$\alpha = 0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
+
+By looking at the values of the heatmap, we see that, for all choices
+of the parameters, other than $\alpha = 0, \tau = 0$,
+(\ref{eqn::Final}) evaluates to a negative value, which signals
+instability. As such, the analysis over-estimates the region of
+instability. We believe that this is due to the
+%heavy
+assumptions made during the derivation of the analytic result, the
+strongest of which was to drop the discrepancy between players and
+actions, treating each action of each player to be independent and
+identically distributed. However, even within the error that this
+assumption generates, it is still clear (and is verified
+experimentally) that convergence in Q-Learning is rare. Indeed as the
+value of $N$ increases, the stability boundary determined by
+experiment (Figure \ref{fig:NumericalExperiments}) tends towards
+$\alpha = 0, \tau = 0$.
+
+Similarly, as the value of $N$ increases, the values in the heatmap
+(seen on the right of the map) reduce. This is due to the assumption
+made in the derivation of the analytic result that $N \rightarrow
+\infty$. As the value of N increases, the discrepancy between the true
+behaviour of the system and analytic result decreases. This does,
+however, give rise to a limitation of the result - namely that the
+effect of the number of actions $N$ cannot be accurately inferred from
+ (\ref{eqn::Final}). However, it should still be noted that, even
+with the increase of $N$, the values in parameter space remain negative
+and still, accurately, predict instability. We go on to verify that
+the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured
+by (\ref{eqn::Final}).
+
+We interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero).
+A choice of parameters which evaluates close to the stability boundary has a higher chance (by the analytic error) of being convergent than one which lies further from the boundary.
+Therefore, the heat-maps in Figure \ref{fig:theory} should be considered to show the probability of convergence for a choice of $(\alpha, \Gamma)$.
+Lighter regions denote a higher probability of convergence whereas darker regions are those whose values are further from zero and therefore show a lower probability of convergence.
+
+We can visualise the implication 3 by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
+This occurs independent of the choice of $N$ or $p$.
+The implication 4 can be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$.
+The choice of $\Gamma$
+makes almost no difference in the evaluation of (\ref{eqn::Final}).
+We anticipate that this is due to the restriction of $\Gamma$ to be in the range $[-1, 0]$.
+In this range, the scaling effect of $\Gamma^2$ is dominated by the $\alpha^4$ and $\tau^4$ terms which appear in (\ref{eqn::Final}).
+
+Finally we can see implication 5, by comparing the heatmaps for different values of $p$ \textbf{denote them}.
+We see that, though the overall trend is the same, the heatmaps tend to be darker for higher $p$, suggesting that these lie further from the stability boundary.
+
 \subsection{Discussion}
 
-We note that the numerical experiments confirm the predictions suggested by the analytic results shown in Figure ....
-We notice that convergence occurs almost only for low values of $\alpha$.
-This observation remains as we increase the value of $N$.
-As noted, the analytic result over-estimates the region of instability due to the assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made during the derivation.
-Remaining discrepancies are partially due to the aforementioned approximation in the calculation of $q$, $\chi$ and the fact that the analytic result considers a continuous time approximation of the expected behaviour of Q-Learning.
-We expect that testing over a greater number of payoff realisations and initial conditions will yield a more representative assessment of the average behaviour of Q-Learning.
-However, running these experiments is a computationally expensive procedure: for $p$ players and $N$ actions we require operations on $p$ matrices with $N^{p}$ elements.
-As such, due to a reduced availability of computational facilities, a large scale averaging was not possible.
+We note that the numerical experiments confirm the predictions
+suggested by the analytic results shown in Figure .... We notice that
+convergence occurs almost only for low values of $\alpha$. This
+observation remains as we increase the value of $N$. As noted, the
+analytic result over-estimates the region of instability due to the
+assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made
+during the derivation. Remaining discrepancies are partially due to
+the aforementioned approximation in the calculation of $q$, $\chi$ and
+the fact that the analytic result considers a continuous time
+approximation of the expected behaviour of Q-Learning. We expect that
+testing over a greater number of payoff realisations and initial
+conditions will yield a more representative assessment of the average
+behaviour of Q-Learning. However, running these experiments is a
+computationally expensive procedure: for $p$ players and $N$ actions
+we require operations on $p$ matrices with $N^{p}$ elements. As such,
+due to a reduced availability of computational facilities, a large
+scale averaging was not possible.
 
-A point which we wish to discuss here is the difference in the result found w.r.t.~\cite{Sanders2018}, which considered the stability of \textit{Experience Weighted Attraction} (EWA).
-Namely, Sanders et al.~found that convergence is seen for higher values of $\alpha$, whereas lower values give rise to chaos, the opposite of what is found here.
-The reason for this can be seen in the update equation of Q-Learning (\ref{eqn::Qupdate}), whereby
-smaller values of $\alpha$ result in the agent placing a lower weight on the reward received at each step.
-As such, lower values of $\alpha$ result in the agent taking more conservative steps and yields a higher probability of convergence.
-In contrast, the update for EWA does not discount the reward received at all and, instead, only discounts the previous knowledge of the Q-value based on higher choices of $\alpha$.
-In essence, the difference is the fact that Q-Learning discounts new information by a factor of $\alpha$, whilst EWA does not.
-Yet, the difference in stability caused by this change is significant.
-This highlights the importance of performing analyses such as the present work; it allows for a method to analytically compare the difference between learning algorithms and, for practitioners, ensure that the appropriate algorithm is chosen for the parameters of their specific task.
+A point which we wish to discuss here is the difference in the result
+found w.r.t.~\cite{Sanders2018}, which considered the stability of
+\textit{Experience Weighted Attraction} (EWA). Namely, Sanders et
+al.~found that convergence is seen for higher values of $\alpha$,
+whereas lower values give rise to chaos, the opposite of what is found
+here. The reason for this can be seen in the update equation of
+Q-Learning (\ref{eqn::Qupdate}), whereby smaller values of $\alpha$
+result in the agent placing a lower weight on the reward received at
+each step. As such, lower values of $\alpha$ result in the agent
+taking more conservative steps and yields a higher probability of
+convergence. In contrast, the update for EWA does not discount the
+reward received at all and, instead, only discounts the previous
+knowledge of the Q-value based on higher choices of $\alpha$. In
+essence, the difference is the fact that Q-Learning discounts new
+information by a factor of $\alpha$, whilst EWA does not. Yet, the
+difference in stability caused by this change is significant. This
+highlights the importance of performing analyses such as the present
+work; it allows for a method to analytically compare the difference
+between learning algorithms and, for practitioners, ensure that the
+appropriate algorithm is chosen for the parameters of their specific
+task.
 
-To summarise, we have shown that the analytic result (\ref{eqn::Final}) provides a strong assessment for the effect that $\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of convergence of Q-Learning.
-We show that, at least for negatively correlated payoffs, the strength of correlation plays no role in determining the stability of the system.
-Furthermore, though (\ref{eqn::Final}) overestimates the region of instability, it accurately conveys that convergence of Q-Learning is unlikely for games with many players and actions.
-In fact, our experimental results also verify that stability may only be guaranteed for the limiting case of two-player, two-action games.
+To summarise, we have shown that the analytic result
+(\ref{eqn::Final}) provides a strong assessment for the effect that
+$\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of
+convergence of Q-Learning. We show that, at least for negatively
+correlated payoffs, the strength of correlation plays no role in
+determining the stability of the system. Furthermore, though
+(\ref{eqn::Final}) overestimates the region of instability, it
+accurately conveys that convergence of Q-Learning is unlikely for
+games with many players and actions. In fact, our experimental results
+also verify that stability may only be guaranteed for the limiting
+case of two-player, two-action games.
 
-Finally, we show that the behaviour of the stability line differs from that of EWA and suggest that this shows that a stability analysis is an important mode of analysis for reinforcement learning equations to ensure that parameters are being chosen appropriately to guarantee the safe convergence of learning.
+Finally, we show that the behaviour of the stability line differs from
+that of EWA and suggest that this shows that a stability analysis is
+an important mode of analysis for reinforcement learning equations to
+ensure that parameters are being chosen appropriately to guarantee the
+safe convergence of learning.
 
@@
 
-In this study, we characterise the behaviours of Q-Learning in $p$-player, $N$-action games.
-To do this, we analyse the replicator model of Q-Learning derived by Tuyls et al.
-Specifically, we search for the regions in parameter space where the dynamics are expected to converge to a stable equilibrium and those where learning is unstable.
-This yields a number of important results.
-We find that convergence to a unique fixed point is found for low values of $\alpha$, the \textit{step length} of the algorithm and for negatively correlated payoff matrices, though the strength of correlation $\Gamma$ does not influence stability.
-As $\alpha$ increases, the likelihood of convergence decreases.
-The same is true for the \textit{intensity of choice} parameter $\tau$.
-Our analysis also shows that the likelihood of convergence decreases, regardless of parameter choice as the number of players $p$ in the system increases.
+In this study, we characterise the behaviours of Q-Learning in
+$p$-player, $N$-action games. To do this, we analyse the replicator
+model of Q-Learning derived by Tuyls et al. Specifically, we search
+for the regions in parameter space where the dynamics are expected to
+converge to a stable equilibrium and those where learning is
+unstable. This yields a number of important results. We find that
+convergence to a unique fixed point is found for low values of
+$\alpha$, the \textit{step length} of the algorithm and for negatively
+correlated payoff matrices, though the strength of correlation
+$\Gamma$ does not influence stability. As $\alpha$ increases, the
+likelihood of convergence decreases. The same is true for the
+\textit{intensity of choice} parameter $\tau$. Our analysis also shows
+that the likelihood of convergence decreases, regardless of parameter
+choice as the number of players $p$ in the system increases.
 
-As future work, our first aim is to verify the analytic result at a finer resolution and by averaging over a greater number of payoff realisations.
-This will give a greater insight into the boundary between convergent and non-convergent behaviour and allow for practitioners to choose their parameters in such a way that convergence to a unique fixed point is expected.
-In addition we noted that one of the conclusions to our study is that convergence to a unique fixed point is rare in Q-Learning.
-In fact, complex behaviour (such as the existence of multiple fixed points, limit cycles and chaos) is more likely.
-We, therefore, aim to characterise these complex behaviours in parameter space both theoretically and numerically.
+As future work, our first aim is to verify the analytic result at a
+finer resolution and by averaging over a greater number of payoff
+realisations. This will give a greater insight into the boundary
+between convergent and non-convergent behaviour and allow for
+practitioners to choose their parameters in such a way that
+convergence to a unique fixed point is expected. In addition we noted
+that one of the conclusions to our study is that convergence to a
+unique fixed point is rare in Q-Learning. In fact, complex behaviour
+(such as the existence of multiple fixed points, limit cycles and
+chaos) is more likely. We, therefore, aim to characterise these
+complex behaviours in parameter space both theoretically and
+numerically.
 
-The present work gives a first step towards considering the stability of Multi-Agent Reinforcement Learning and focuses on the limiting case of stateless normal-form games played by homogeneous agents.
-As research into the dynamics of Reinforcement Learning algorithms progresses, it would be prudent to apply this analysis to various other algorithm.
-Algorithms whose dynamics are established, and are therefore open to a stability analysis, include piecewise Q-Learning and Cross Learning.
-This would provide a strong method by which to compare and provide safety guarantees to different algorithms for a particular use case.
+The present work gives a first step towards considering the stability
+of Multi-Agent Reinforcement Learning and focuses on the limiting case
+of stateless normal-form games played by homogeneous agents. As
+research into the dynamics of Reinforcement Learning algorithms
+progresses, it would be prudent to apply this analysis to various
+other algorithm. Algorithms whose dynamics are established, and are
+therefore open to a stability analysis, include piecewise Q-Learning
+and Cross Learning. This would provide a strong method by which to
+compare and provide safety guarantees to different algorithms for a
+particular use case.
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Updated AAMAS document with varying p experiments

--- 2020-10-07 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
+%%% Load required packages here (note that many are included already).
 \usepackage{soul}
 \usepackage{subcaption}
-
-%%% Load required packages here (note that many are included already).
+\usepackage[export]{adjustbox}
 
@@
 \newcommand\fb[1]{\textcolor{blue}{FB: #1}}
-
+\newcommand\ah[1]{\textcolor{red}{AH: #1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title[InstabilityinMARL]{Stability and Chaos in Multi Agent Reinforcement Learning}
+\title[InstabilityinMARL]{Stability and Chaos in Multi-Agent Reinforcement Learning}
 
@@
 are required to follow the subsequent sections. The first regards
-\textit{dynamical behaviours}, which considers the evolution of agent
+\textit{dynamical behaviours}, which considers the evolution of agent (note we use the terms \textit{agent} and \textit{player} interchangeably)
 strategies as they learn how to play an iterated game. This study aims to
@@
 
-    \begin{figure}[h]
+    \begin{figure}[t]
         \centering
@@
 approach adjust the probabilities of choosing actions as they
-iteratively play a game. The Q-Learning approach considered requires
+iteratively play a game.
+
+\ah{Explanation of games:} The games we consider are \textit{normal form games}.
+These consist of: a finite set of players, with individual strategy spaces $\mathcal{A}$ (though we assume that all players share the same strategy space) and payoff functions for each player.
+The agents choose an action from their strategy space and receive a reward from their payoff matrix dependent on the actions of all players.
+The payoffs remain unchanged across iterations.
+Examples of these normal form games include the popular Prisoner's Dilemma or Matching Pennies games \cite{Tuyls2006AnGames}.
+
+The Q-Learning approach considered requires
 an agent to choose an action $i$ at step $k+1$ with probability
@@
 Here,
-%$\alpha$ and $\tau$ are the parameters of the agent as described at the end of this section.
 agent 1 (resp.~agent 2) takes action $i$ with probability
@@
 receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-predict the expected behaviour of Q-Learning agents which they go on to verify \fb{how? empirically?}.
+predict the expected behaviour of Q-Learning agents which they go on to empirically verify.
 
@@
 point is stable.
-
-\fb{do we mention anywhere the format of these games?}
+As this process is rather involved, we focus on the main steps in this paper, and refer to the Supplementary Material for the technical details.
+Sections from the Supplementary Material are denoted with the prefix S.
 
@@
 game. This yields the dynamics (\ref{eqn::pEOM}). Here, player $\mu$
-chooses action $i_{\mu}$ from its action space $\mathcal{A}$ at time
+chooses action $i_{\mu}$ from its strategy space $\mathcal{A}$ at time
 $t$ with probability $\xmu{i}{\mu}$ and receives a reward
@@
 
-We now scale the system so that $\sum_{i_\mu} \xmu{i}{\mu} = 1$. The
+We now scale the system so that the probabilities sum to $N$. The
 reason for this scaling is that, as the number of agents $p$ and
 number of actions $N$ increases, the expected payoffs that agent
-$\xmu{i}{\mu}$ receives becomes less distinguishable \fb{? all converge to the same value?} across its action
+$\xmu{i}{\mu}$ receives all converge to the same value across its action
 space. Therefore, the system must be scaled to ensure appreciable
 differences across actions, so that the agent can choose its actions
-appropriately (see the discussion in \cite{Sanders2018} or the
-Supplementary Material for further details \fb{we might need to provide the actual section in the supplementary material}). Accordingly we choose
+appropriately (see the discussion in \cite{Sanders2018} or
+Section S2.2 for further details). Accordingly we choose
 scaled variables (denoted with a tilde) as
@@
 Note that the scaled probabilities now satisfy the constraint
-$\sum_{i_\mu} \txmu{i}{\mu} = N$ \fb{but what about the constraint $\sum_{i_\mu} \xmu{i}{\mu} = 1$ mentioned above?}. For the remainder of this derivation
+$\sum_{i_\mu} \txmu{i}{\mu} = N$. For the remainder of this derivation
 we concern ourselves only with the scaled system so we drop the tilde
-notation on $P$ and $x$ \fb{on $\alpha$ and $\tau$ as well?}.
+notation on $P$ and $x$.
 
@@
 
-\fb{can we give the equation already with the Gaussian?}
-
-\subsection{Generating Functional Analysis}
+\subsection{The Effective Dynamics}
 
@@
 statistical mechanics which allows for expectations to be taken over
-equations of motion and, more specifically, allows for the analysis of
+equations of motion and, in particular, allows for the analysis of
 systems with `quenched disorder': these are
@@
 evolves (in our case these variables are the payoff elements). The
-generating functional is given as \cite{SpinGlassTheory}
-%
-\fb{check for missing references, i.e., '?'}
+generating functional is given as \cite{Mezard1986}
+
 \begin{equation}
@@
 As such these comprise the aforementioned 'quenched disorder'.
-We will average over this quenched disorder (and therefore average over all possible realisations of payoff matrices).
+We will average over this quenched disorder (and therefore average over all possible realisations of payoff matrices) using the mean and covariance expressions given in (\ref{eqn::Payoffs}).
 We define $Q$ to be the product of the second and third exponentials in (\ref{eqn::separatePayoffs})
 %
-\fb{why $<Q>$?}
+
 \begin{equation}
 \begin{split}
-        <Q> = exp(- \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] ) \times \\
+        \mathbb{E}[Q] = exp(- \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] ) \times \\
         exp(- \frac{\alpha^2 \htau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} A^{\mu \nu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] )
@@
 \end{eqnarray*}
-\fb{why using symbol $:=$ here?}
 
-By taking this average, described in further detail in the Supplementary Material \fb{just say this at the beginning only}, we obtain the \textit{effective dynamics}
+By taking this average (Section S2.3), we obtain the \textit{effective dynamics}
 
@@
 $\nu$). This is a strong assumption which removes the interdependency
-between agents in the analysis. However, as shown by the experimental
+between agents in the analysis and is required to ensure that (\ref{eqn::EffectiveDynamics}) yields real-valued action probabilities. However, as shown by the experimental
 evaluation, it does not produce a strong discrepancy in describing the
-qualitative effect on stability caused by the parameters $\alpha$,
-$\Gamma$, and $\tau$.
-
-\fb{you can also mention the simplification in calculation.}
+qualitative effect on stability caused by the parameters $\alpha$, $\Gamma$, and $\tau$.
 
@@
 
-We now analyse the stability of this system in a neighbourhood around
-the fixed point \fb{how do we know there is a fixed point in first
-  place?}. This follows a similar procedure as in \cite{Opper1992}, in
+We first find a fixed point $\xfixed$ of (\ref{eqn::EffectiveDynamics}) by letting $\dot{x}(t)= 0$. This yields the expression
+
+\begin{eqnarray}
+%    \begin{split}
+    0 & = & \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{p-2} \chi + \nonumber \\
+      &  & + \sqrt{2} \alpha \ttau q^{(p-1)/2}z + \sqrt{2} \alpha \htau q^{p/2} z^{p/p-1} + \talpha \rho]
+    \label{eqn::fixed_point}
+%    \end{split}
+\end{eqnarray}
+%
+where $\chi = \int dt' G(t - t')$, $\eta_0(t) = q^{(p-1)/2}z$, $z$ is
+drawn from a Gaussian of zero mean and unit variance. By using (\ref{eqn::fixed_point}) we can
+%his gives us an expression for
+calculate $\xfixed$. We disregard the choice $\xfixed = 0$, since we
+assume that no action will be chosen with exactly zero probability, an
+intuitive assumption which is also considered in \cite{Sanders2018}
+and \cite{Coolen2005}. The expression inside the squared bracket
+admits a positive solution only in the region $\Gamma \in [-1, 0]$,
+whilst for positive $\Gamma \leq p-1$, the nature of solutions may
+not be guaranteed. Therefore, we restrict our analysis to the region
+$[-1, 0]$.
+
+We now analyse the stability of the system (\ref{eqn::EffectiveDynamics}) in a neighbourhood around
+this fixed point. This follows a similar procedure as in \cite{Opper1992}, in
 which the fixed point dynamics are proposed to be perturbed by a
@@
 \eonepert$.  If we consider only the terms which are linear in these
-perturbations \fb{why only those?}, we arrive at the dynamics
+perturbations, we arrive at the dynamics
 
@@
 
-At a fixed point, then, the perturbations $\xpert$ will be zero, leaving
-%
-\begin{eqnarray}
-%    \begin{split}
-    0 & = & \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{n-1} \chi + \nonumber \\
-      &  & + \sqrt{2} \alpha \ttau q^{n/2}z + \sqrt{2} \alpha \htau q^{(n+1)/2} z^{(n+1)/n}]
-    \label{eqn::fixed_point}
-%    \end{split}
-\end{eqnarray}
-%
-where $\chi = \int dt' G(t - t')$, $\eta_0(t) = q^{n/2}z$, $z$ is
-drawn from a Gaussian of zero mean and unit variance, and $n = p -
-1$. By using (\ref{eqn::fixed_point}) we can
-%his gives us an expression for
-calculate $\xfixed$. We disregard the choice $\xfixed = 0$, since we
-assume that no action will be chosen with exactly zero probability, an
-intuitive assumption which is also considered in \cite{Sanders2018}
-and \cite{Coolen2005}. The expression inside the squared bracket
-admits a positive solution only in the region $\Gamma \in [-1, 0]$,
-whilst for positive $\Gamma \leq p -1$, the nature of solutions may
-not be guaranteed. Therefore, we restrict our analysis to the region
-$[-1, 0]$.
-
-Having arrived at a condition for the fixed point, we then examine the
+We then examine the
 long-term behaviour of the perturbation $\xpert$. To do this, we take
 the Fourier transform of (\ref{eqn::Linearised}) and analyse its
-behaviour at $\omega = 0$. After some manipulation (see the supplementary material), this gives
+behaviour at $\omega = 0$. After some manipulation (Section S4), this gives
 
@@
 \begin{split}
-        \mathbb{E}[|\mathcal{X}(\omega = 0)|^2] = \frac{1}{\left[ (-\alpha^2 \ttau^2 \Gamma q^{n-1} \chi)^2 - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2}\right]} \\
+        \mathbb{E}[|\mathcal{X}(\omega = 0)|^2] = \frac{1}{\left[ (-\alpha^2 \ttau^2 \Gamma q^{p-2} \chi)^2 - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2}\right]} \\
 \end{split}
@@
     \label{eqn::Final}
-    0 \leq \left [(\alpha^2 \ttau^2 \Gamma q^{n-1} \chi)^{2} - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2} \right ]
+    0 \leq \left [(\alpha^2 \ttau^2 \Gamma q^{p-2} \chi)^{2} - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2} \right ]
 \end{equation}
 
-It should be noted that, to arrive at this result, we have had to take the assumption that $2 >> 1/n$ \fb{is it justified?}.
+It should be noted that, to arrive at this result, we have had to take the assumption that p is large enough so that $p/p-1 \approx 1$ so that the fractional power on $z$ in (\ref{eqn::fixed_point}) is reduced to $1$.
+As $z$ can take any value, including negative values, this again ensures that the expression for $\xfixed$ remains real valued.
 
-\paragraph{Discussion}
+\subsection{Discussion}
 The fixed point condition (\ref{eqn::Final}) yields a number of testable implications, of which we test the validity through in the subsequent section. These implications are as follows.
@@
 
-      \fb{how are these remarks corroborated by the experimental results?}
-
 \end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Experimental Evaluation} \label{sec:exev}
-
-\begin{figure}
-    \centering
-    \includegraphics[width = 1.1 \linewidth]{Figures/Theory.png}
-    \caption{Results of numerical experiments.
-The heatmaps show the value of the Liapunov Exponent determined by the procedure outlined in Section~\ref{sec:exev} scaled by $1 \times 10^5$ for convenience.
-Lighter values show a higher exponent whilst darker values indicate lower values.
-Each experiment is run with $\tau = 0.05$.
-(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 4$, (Mid-Left) $p = 2, N = 10$, (Mid-Right) $p = 2, N = 20$, (Bottom) $p = 3, N = 5$.}
-    \label{fig:theory}
-\end{figure}
-%\fb{Can we arrange Fig.~\ref{fig:theory} in a 2x2 square?}
 
@@
 
-We consider each of the implications 2-5 from the previous section in turn, choosing to forego illustrating 1 as it can be seen trivially from the expression.
-In those heatmaps for which $\tau$ is held fixed \textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$.
-For those in which $\alpha$ is held fixed, \textbf{denote them} we choose $\alpha =  0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
+We consider each of the implications (2)-(5) from the previous section
+in turn, choosing to forego illustrating (1) as it can be seen immediately
+from the expression. In those heatmaps where $\tau$ is held fixed
+\textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in
+the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For
+those in which $\alpha$ is held fixed, \textbf{denote them} we choose
+$\alpha = 0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
 
-By looking at the values of the heatmap, we see that, for all choices of the parameters, other than $\alpha = 0, \tau = 0$, (\ref{eqn::Final}) evaluates to a negative value, which signals instability.
-As such, the analysis over-estimates the region of instability.
-We believe that this is due to the heavy assumptions made during the derivation of the analytic result, the strongest of which was to drop the discrepancy between players and actions, treating each action of each player to be independent and identically distributed.
-However, even within the error that this assumption generates, it is still clear (and is verified experimentally) that convergence in Q-Learning is rare.
-Indeed as the choice of $N$ increases, the stability boundary determined by experiment (Figure \ref{fig:NumericalExperiments}) tends towards $\alpha = 0, \tau = 0$.
+\paragraph{Implication 2:} By looking at the values of the heatmap, we see that, for all choices
+of the parameters, other than $\alpha = 0, \tau = 0$,
+(\ref{eqn::Final}) evaluates to a negative value, which signals
+instability. As such, the analysis over-estimates the region of
+instability. We believe that this is due to the
+%heavy
+assumptions made during the derivation of the analytic result, the
+strongest of which was to drop the discrepancy between players and
+actions, treating each action of each player to be independent and
+identically distributed. However, even within the error that this
+assumption generates, it is still clear (and is verified
+experimentally) that (\ref{eqn::Final}) predicts convergence in Q-Learning to be rare. Indeed as the
+value of $N$ increases, the stability boundary determined by
+experiment (Figure \ref{fig:NumericalExperiments}) tends towards
+$\alpha = 0, \tau = 0$.
 
-Similarly, as the value of $N$ increases, the values in the heatmap (seen on the right of the map) reduce.
-This is due to the assumption made in the derivation of the analytic result that $N \rightarrow \infty$.
-As the value of N increases, the discrepancy between the true behaviour of the system and analytic result decreases.
-This does, however, give rise to a limitation of the result - namely that the effect of the number of actions $N$ cannot be accurately inferred from the (\ref{eqn::Final}).
-However, it should still be noted that, even with the increase of N, the values in parameter space remain negative and still, accurately, predict instability.
-We go on to verify that the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured by (\ref{eqn::Final}).
+Similarly, as the value of $N$ increases, the values in the heatmap
+(seen on the right of the map) reduce. This is due to the assumption
+made in the derivation of the analytic result that $N \rightarrow
+\infty$. As the value of N increases, the discrepancy between the true
+behaviour of the system and analytic result decreases. This does,
+however, give rise to a limitation of the result - namely that the
+effect of the number of actions $N$ cannot be accurately inferred from
+ (\ref{eqn::Final}). However, it should still be noted that, even
+with the increase of $N$, the values in parameter space remain negative
+and still, accurately, predict instability. We go on to verify that
+the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured
+by (\ref{eqn::Final}).
 
@@
 
-We can visualise the implication 3 by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
+\paragraph{Implication 3} can be visualised by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
 This occurs independent of the choice of $N$ or $p$.
-The implication 4 can be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$.
-The choice of $\Gamma$
+
+\paragraph{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$. The choice of $\Gamma$
 makes almost no difference in the evaluation of (\ref{eqn::Final}).
@@
     \centering
-    \includegraphics[width = 0.9 \linewidth]{Figures/p variation.png}
+    \includegraphics[width = 0.8 \linewidth]{Figures/pVariance.png}
     \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$.
-Here, $\alpha$ is fixed at 0.02, $\tau = 0.05$, $N = 2$ and $\Gamma = -1$.
+Here, $\alpha$ is fixed at $0.02$, $\tau = 0.05$, $N = 2$ and $\Gamma = -1$.
 $p$ is varied from 2 to 12.
@@
 
-Finally we can see implication 5, by considering Figure \ref{fig:pvariation}.
-In this we keep all parameters, except for $p$, fixed and evaluate the right hand side of (\ref{eqn::Final}) for varying $p$.
+\paragraph{Implication 5}, finally, is considered in Figure \ref{fig:pvariation}.
+In this we keep all parameters, except for $p$, fixed and evaluate the right hand side of (\ref{eqn::Final}) for varying $p$, taking the absolute value for convenience.
 We see that the trend is to tend away from the stability boundary, indicating that as the number of players in the system increases, so too does the region of instability.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Experimental Evaluation} \label{sec:exev}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width = 1.1 \linewidth]{Figures/Theory.png}
+%     \caption{Results of numerical experiments.
+The heatmaps show the value of the Liapunov Exponent determined by the procedure outlined in Section~\ref{sec:exev} scaled by $1 \times 10^5$ for convenience.
+Lighter values show a higher exponent whilst darker values indicate lower values.
+Each experiment is run with $\tau = 0.05$.
+(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 4$, (Mid-Left) $p = 2, N = 10$, (Mid-Right) $p = 2, N = 20$, (Bottom) $p = 3, N = 5$.}
+%     \label{fig:theory}
+% \end{figure}
+% %\fb{Can we arrange Fig.~\ref{fig:theory} in a 2x2 square?}
 
@@
 \begin{figure}[t]
-    \centering
-    \includegraphics[width = 1.2 \linewidth]{Figures/Experiments.png}
+    \includegraphics[width = 1.1 \linewidth, center]{Figures/Experiments.png}
     \caption{Results of numerical experiments in which $\alpha$ is varied.
@@
 \end{figure}
+
+\begin{figure}[t]
+    \includegraphics[width = 1.1 \linewidth, center]{Figures/a5e2var.png}
+    \caption{Figures showing the trajectory of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$.
+(Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
+    \label{fig:AlphaVariation}
+\end{figure}
+
+In Figure \ref{fig:AlphaVariation}, we explicitly plot the trajectories taken by the action probabilities as two agents are trained on a game of $\Gamma = -0.5$.
+In the left figure, we choose $\alpha = 0.01$ whilst in the right we choose $\alpha = 0.05$.
+This gives a qualitative assessment of the behaviour at both extremes parameters considered.
+We note that the typical behaviour of the system is that the system first moves towards a fixed point and then vary in a pseudo-random manner within a vicinity of the fixed point.
+Critically though, the amount of variation in the case $\alpha = 0.05$ is greater than that of $\alpha = 0.01$, and so it does not settle to a fixed point (i.e.
+is considered unstable).
+
+\begin{figure}[t]
+    \includegraphics[width = 0.75 \linewidth, center]{Figures/pVarianceExpt.png}
+    \caption{Figure showing the variation $V(t)$ about a fixed point as $p$ is varied from 2 - 6.
+$N = 2$, $\alpha = 0.02$, $\tau = 0.05$, $\Gamma = [-1, 0]$.
+The experiment is conducted for 10 choices of $\Gamma$ and the mean (line) is plotted alongside the standard deviation (shaded region).}
+    \label{fig:pVarianceExpt}
+\end{figure}
+
+Finally, Figure \ref{fig:pVarianceExpt} plot the degree variation about the fixed point displayed as the number of players $p$ increases.
+The variation is determined by first allowing the game to iterate for 5000 steps, so that it can be assumed to have reached the vicinity of the fixed point.
+Then, the action probabilities are recorded for a further 5000 iterations.
+At the end of this second period, the variance of the actions are calculated as
+
+\begin{equation*}
+    V(t) = \frac{1}{N} \sum_i \frac{1}{5000} \sum_t x_i(t)^2 - \left[\frac{1}{5000} \sum_t x_i(t) \right]^2 .
+\end{equation*}
+
+This gives a measure of the degree of variability about the fixed point and, therefore, gives some notion of the `degree of instability'.
+For example, the right hand plot of Figure \ref{fig:AlphaVariation} has a higher $V(t)$ than the left and so is considered to show a higher degree of instability.
+
+Due to computational restraints, which we discuss further in the discussion, we are only able to increase $p$ to a maximum value of 6 and must restrict also to $N = 2$.
+We maintain $\alpha = 0.02$ and $\tau = 0.05$ to match with the parameters used for Figure \ref{fig:pvariation}.
+Finally, in Figure \ref{fig:pVarianceExpt}, we are averaging over 10 choices of $\Gamma$ in the range $[-1, 0]$.
 
@@
 As such, due to a reduced availability of computational facilities, a large scale averaging was not possible.
+
+However, due to the abundance of non-convergent behaviour, shown by the dark regions in Figure \ref{fig:NumericalExperiments} other than at low values of $\alpha, \tau$, we can conclude that the implications 1, 2 are verified.
+Indeed implications 3 and 4 are also verified as the proportion of games converged decrease monotonically with $\alpha, \tau$, but there does not appear to be any discernible dependence on $\Gamma$.
+Finally, we can conclude that implication 5 is verified by comparing Figures \ref{fig:pvariation} and \ref{fig:pVarianceExpt}.
+It is clear that the instability of the system increases monotonically with $p$.
+A point to note is that Figure \ref{fig:pVarianceExpt} shows a logarithmic dependence of the instability on $p$, whilst Figure \ref{fig:pvariation} suggests that the dependence should be exponential.
+Due to the limited range of $p$ that was used to generate Figure \ref{fig:pVarianceExpt}, it cannot yet be concluded that the dependence on $p$ is logarithmic.
+However, the important result is that the unstable behaviour increases, regardless of parameter choice as $p$ increases, which is corroborated by both theory and experiment.
+This phenomenon was referred to by Sanders et.
+al as `the prevalence of chaotic dynamics in games with many players' \cite{Sanders2018}.
 

### 2020-10-08 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -7,15 +7,13 @@ from tqdm import tqdm
 # alpha = .1
 gamma = .1
 Gamma = 0.1
-tau = 5e-2
+tau = 1
 
-nActions = 5
-t0 = 500
-
-initnSim = 15
+nActions = 2
 
 delta_0 = 1e-3
-nIter = int(5e4)
+nSim = 15
+nIter = int(1.5e4)
 
 
 def generateGames(gamma, nSim, nAct):
@@ -39,9 +37,10 @@ def generateGames(gamma, nSim, nAct):
     for i in range(nSim):
         rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
 
-        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
-        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
-
+        # rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
+        rewardAs = np.dstack((rewardAs, np.array([[1, 5], [0, 3]])))
+        # rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
+        rewardBs = np.dstack((rewardBs, np.array([[1, 0], [5, 3]])))
     return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
 
 
@@ -53,7 +52,7 @@ def getActionProbs(qValues, nSim):
     return actionProbs
 
 
-def qUpdate(qValues, payoffs, nSim):
+def qUpdate(qValues, payoffs):
     actionProbs = getActionProbs(qValues, nSim)
 
     boltzmannChoices = np.array(
@@ -78,61 +77,28 @@ def getDelta(qValues0, qValues1, nSim):
     return np.mean(abs(actionProbs1 - actionProbs0), axis=0)
 
 
-def checkminMax(allActions, nSim, tol):
-    a = np.reshape(allActions, (t0, nSim, nActions * 2))
-    relDiff = ((np.max(a, axis=0) - np.min(a, axis=0))/np.min(a, axis=0))
-    return np.all(relDiff < tol, axis=1)
-
-def checkVariance(allActions, cIter, tol):
-    h = (1 / nActions) * np.sum((1 / t0) * np.sum(allActions ** 2, axis=0) - ((1 / t0) * np.sum(allActions, axis=0)) ** 2,
[…]

### 2020-10-08 Code/Practice/Tuyls3p.py

@@ -1,5 +1,6 @@
 import numpy as np
 import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
 from tqdm import tqdm
 
 alpha = .01
@@ -7,16 +8,19 @@ tau = 1
 
 x = np.linspace(0, 1, 50)
 y = np.linspace(0, 1, 50)
+z = np.linspace(0, 1, 50)
 
-X, Y = np.meshgrid(x, y)
+X, Y, Z = np.meshgrid(x, y, z)
 
 A, B = np.array([[1, 5], [0, 3]]), np.array([[1, 0], [5, 3]])
 
 E = lambda R: (R * np.log(R/R)) + ((1 - R) * np.log((1 - R)/R))
 
-x_dot = lambda M, N: alpha * M * tau * ((A @ [N, 1-N])[0] - np.dot([M, 1-M], A@[N, 1-N])) + M * alpha * E(M)
+x_dot = lambda M, N, O: alpha * M * tau * ((A @ [N, 1-N])[0] - np.dot([M, 1-M], A@[N, 1-N])) + M * alpha * E(M)
 
-y_dot = lambda M, N: alpha * N * tau * ((B.T @ [M, 1-M])[0] - np.dot([N, 1-N], B.T@[M, 1-M])) + N * alpha * E(N)
+y_dot = lambda M, N, O: alpha * N * tau * ((B.T @ [M, 1-M])[0] - np.dot([N, 1-N], B.T@[M, 1-M])) + N * alpha * E(N)
+
+z_dot = lambda M, N, O: alpha * O * tau
 
 U, V = np.zeros(X.shape), np.zeros(X.shape)
 NI, NJ = X.shape
@@ -27,7 +31,8 @@ for i in range(NI):
         V[i, j] = y_dot(X[i, j], Y[i, j])
 
 fig = plt.figure(dpi=500)
-ax = fig.add_subplot(111)
+ax = fig.add_subplot(111, projection='3d')
+
 ax.quiver(X, Y, U, V, color = 'b', width=2e-3)
 plt.xlabel('Probability of Action 1 (Agent 1)')
 plt.ylabel('Probability of Action 1 (Agent 2)')

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
+\fb{it would be good to have some introduction to the section here.}
+
 \subsection{Construction of Numerical Experiments}
 
-To verify experimentally the theoretical results, and to examine the underlying structure of stability and chaos in
-Multi-Agent Q-Learning, we perform a series of numerical experiments by varying the parameters $\Gamma$ and
-$\alpha$ whilst keeping $\tau$ fixed.
-The aim is to determine the regions in which games learnt using Q-Learning converge to an equilibrium.
-The results of these experiments are shown in Figure \ref{fig:NumericalExperiments}, with parameters chosen to match those in the analytic assessment (Figure \ref{fig:theory}).
+To verify experimentally the theoretical results and to examine the
+underlying structure of stability and chaos in multi-agent Q-Learning,
+we perform a series of numerical experiments by varying the parameters
+$\Gamma$ and $\alpha$ whilst keeping $\tau$ fixed. The aim is to
+determine the regions in which games learnt using Q-Learning converge
+to an equilibrium. The results of these experiments are shown in
+Figure \ref{fig:NumericalExperiments}, with parameters chosen to match
+those in the analytic assessment (Figure \ref{fig:theory}).
 % By examination it is found that, in many cases the system oscillates about some equilibrium point in a low dimensional chaotic manner (i.e.
@@
 \begin{enumerate}
-   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05 and the latter at 0.1. For the heatmaps in which $\tau$ is swept over $\alpha$ is held fixed at 0.05.
-   \item Initialise values of $\Gamma, \alpha$ (or $\tau$ appropriately). These will be swept over in the experiment.
-\item Generate 15 payoff matrices for both agents by sampling from a multi-variate Gaussian 
-(variables are the payoff elements) with mean zero and covariance parameterised by $\Gamma$.
-\item For each of these payoff matrices, initialise a set of agents with random initial conditions (i.e., random action probabilities).
-\item Allow both sets of agents to learn over a maximum of $1.5 \times 10^4$ iterations.
-\item Keep track of the action probabilities over a window of 500 iterations.
-At the end of each window, determine the percentage difference between the maximum and minimum values of each strategy component
-\item If the difference is less than 1 \% consider the game converged. Otherwise continue to the next window.
-\item If the game reaches $1.5 \times 10^4$ iterations without satisfying the relative distance criterion, consider it to be non-convergent.
-Determine the fraction of these 15 games which have converged.
+   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05
+     and the latter at 0.1. For the heatmaps in which $\tau$ is swept
+     over, $\alpha$ is held fixed at 0.05.
+
+   \item Initialise values of $\Gamma, \alpha$ (or $\tau$
+     appropriately). These will be swept over in the experiment.
+
+   \item Generate 15 payoff matrices for both agents by sampling from
+     a multi-variate Gaussian (variables are the payoff elements) with
+     mean zero and covariance parameterised by $\Gamma$.
+
+   \item For each of these payoff matrices, initialise a set of agents
+     with random initial conditions (i.e., random action
+     probabilities).
+
+   \item Allow both sets of agents to learn over a maximum of $1.5
+     \times 10^4$ iterations.
+
+   \item Keep track of the action probabilities over a window of 500
+     iterations. At the end of each window, determine the percentage
+     difference between the maximum and minimum values of each
+     strategy component
+
+   \item If the difference is less than 1 \% consider the game
+     converged. Otherwise continue to the next window.
+
+   \item If the game reaches $1.5 \times 10^4$ iterations without
+     satisfying the relative distance criterion, consider it to be
+     non-convergent.
+
+     \item Determine the fraction of these 15 games which
+     have converged.
 
@@
 
-We see in Figure \ref{fig:NumericalExperiments} that the stability of the system is highly dependent on
-the value of $\alpha$ and $\tau$ but not on $\Gamma$.
+We see in Figure \ref{fig:NumericalExperiments} that the stability of the system is highly dependent on the values of $\alpha$ and $\tau$, but not on $\Gamma$.
 
@@
     \includegraphics[width = 1.1 \linewidth, center]{Figures/a5e2var.png}
-    \caption{Figures showing the trajectory of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$.
+    \caption{Figures showing the trajectory of action probabilities for 2 players with 5 actions trained on a game with $\Gamma = -0.5$ and $\tau = 0.05$.
 (Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
@@
 
-In Figure \ref{fig:AlphaVariation}, we explicitly plot the trajectories taken by the action probabilities as two agents are trained on a game of $\Gamma = -0.5$.
-In the left figure, we choose $\alpha = 0.01$ whilst in the right we choose $\alpha = 0.05$.
-This gives a qualitative assessment of the behaviour at both extremes parameters considered.
-We note that the typical behaviour of the system is that the system first moves towards a fixed point and then vary in a pseudo-random manner within a vicinity of the fixed point.
-Critically though, the amount of variation in the case $\alpha = 0.05$ is greater than that of $\alpha = 0.01$, and so it does not settle to a fixed point (i.e.
-is considered unstable).
+In Figure \ref{fig:AlphaVariation}, we explicitly plot the
+trajectories taken by the action probabilities as two agents are
+trained on a game with $\Gamma = -0.5$. In the left figure, we choose
+$\alpha = 0.01$, whilst on the right we choose $\alpha = 0.05$. This
+gives a qualitative assessment of the behaviour at both extremes
+considered. We note that the typical behaviour of the
+system is to first move towards a fixed point and then
+vary in a pseudo-random manner within a vicinity of the fixed
+point. Critically though, the amount of variation in the case for $\alpha
+= 0.05$ is greater than that of $\alpha = 0.01$, and so it does not
+settle to a fixed point (i.e., is considered unstable).
+
+\fb{how can we say that in one case it converges to a fixed point and in the other it doesn't?}
 
@@
 At the end of this second period, the variance of the actions are calculated as
-
-\begin{equation*}
-    V(t) = \frac{1}{N} \sum_i \frac{1}{5000} \sum_t x_i(t)^2 - \left[\frac{1}{5000} \sum_t x_i(t) \right]^2 .
-\end{equation*}
+%
+\begin{eqnarray*}
+    V(t) & = & \frac{1}{N} \sum_i \frac{1}{5000} \sum_t x_i(t)^2 - \left[\frac{1}{5000} \sum_t x_i(t) \right]^2 
+\end{eqnarray*}
 
@@
 
-Due to computational restraints, which we discuss further in the discussion, we are only able to increase $p$ to a maximum value of 6 and must restrict also to $N = 2$.
-We maintain $\alpha = 0.02$ and $\tau = 0.05$ to match with the parameters used for Figure \ref{fig:pvariation}.
-Finally, in Figure \ref{fig:pVarianceExpt}, we are averaging over 10 choices of $\Gamma$ in the range $[-1, 0]$.
+Due to computational restraints, which we discuss further in the
+following section, we are only able to increase $p$ to a maximum value
+of 6 and must also restrict to $N = 2$. We maintain $\alpha = 0.02$
+and $\tau = 0.05$ to match with the parameters used in Figure
+\ref{fig:pvariation}. Finally, in Figure \ref{fig:pVarianceExpt}, we
+are averaging over 10 choices of $\Gamma$ in the range $[-1, 0]$.
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
-We note that the numerical experiments confirm the predictions suggested by the analytic results shown in Figure \ref{sec::Theory}.
-We notice that convergence occurs almost only for low values of $\alpha$.
-This observation remains as we increase the value of $N$.
-As noted, the analytic result over-estimates the region of instability due to the assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made during the derivation.
-Remaining discrepancies are partially due to the aforementioned approximation in the calculation of $q$, $\chi$ and the fact that the analytic result considers a continuous time approximation of the expected behaviour of Q-Learning.
-We expect that testing over a greater number of payoff realisations and initial conditions will yield a more representative assessment of the average behaviour of Q-Learning.
-However, running these experiments is a computationally expensive procedure: for $p$ players and $N$ actions we require operations on $p$ matrices with $N^{p}$ elements.
-As such, due to a reduced availability of computational facilities, a large scale averaging was not possible.
+We note that the numerical experiments confirm the predictions
+suggested by the analytic results shown in Figure \ref{sec::Theory}
+\fb{but Figure \ref{sec::Theory} concerns the numerical
+  experiments}. We notice that convergence occurs almost only for low
+values of $\alpha$. This observation remains as we increase the value
+of $N$. As noted, the analytic result over-estimates the region of
+instability due to the assumptions of $N \rightarrow \infty$ and
+$\frac{1}{p-1} << 2$ made during the derivation. Remaining
+discrepancies are partially due to the aforementioned approximation in
+the calculation of $q$, $\chi$, and the fact that the analytic result
+considers a continuous-time approximation of the expected behaviour of
+Q-Learning. We expect that testing over a greater number of payoff
+realisations and initial conditions will yield a more representative
+assessment of the average behaviour of Q-Learning. However, running
+these experiments is a computationally expensive procedure: for $p$
+players and $N$ actions it requires operations on $p$ matrices with
+$N^{p}$ elements. As such, due to a reduced availability of
+computational facilities, a large scale averaging was not possible.
 
-However, due to the abundance of non-convergent behaviour, shown by the dark regions in Figure \ref{fig:NumericalExperiments} other than at low values of $\alpha, \tau$, we can conclude that the implications 1, 2 are verified.
-Indeed implications 3 and 4 are also verified as the proportion of games converged decrease monotonically with $\alpha, \tau$, but there does not appear to be any discernible dependence on $\Gamma$.
-Finally, we can conclude that implication 5 is verified by comparing Figures \ref{fig:pvariation} and \ref{fig:pVarianceExpt}.
-It is clear that the instability of the system increases monotonically with $p$.
-A point to note is that Figure \ref{fig:pVarianceExpt} shows a logarithmic dependence of the instability on $p$, whilst Figure \ref{fig:pvariation} suggests that the dependence should be exponential.
-Due to the limited range of $p$ that was used to generate Figure \ref{fig:pVarianceExpt}, it cannot yet be concluded that the dependence on $p$ is logarithmic.
-However, the important result is that the unstable behaviour increases, regardless of parameter choice as $p$ increases, which is corroborated by both theory and experiment.
-This phenomenon was referred to by Sanders et.
-al as `the prevalence of chaotic dynamics in games with many players' \cite{Sanders2018}.
+However, due to the abundance of non-convergent behaviour, shown by
+the dark regions in Figure \ref{fig:NumericalExperiments} other than
+at low values of $\alpha, \tau$, we can conclude that the implications
+(1), (2) in Sec.~\ref{} are verified. Indeed implications (3) and (4) are also verified as
+the proportion of converging games
+%converged
+decreases monotonically with $\alpha,
+\tau$, but there does not appear to be any discernible dependence on
+$\Gamma$. Finally, we can conclude that implication (5) is verified by
+comparing Figures \ref{fig:pvariation} and \ref{fig:pVarianceExpt}: it
+is clear that the instability of the system increases monotonically
+with $p$. A point to note is that Figure \ref{fig:pVarianceExpt} shows
+a logarithmic dependence of the instability on $p$, whilst Figure
+\ref{fig:pvariation} suggests that the dependence should be
+exponential. Due to the limited range of $p$ that was used to generate
+Figure \ref{fig:pVarianceExpt}, it cannot yet be concluded that the
+dependence on $p$ is logarithmic. However, the important result is
+that the unstable behaviour increases, regardless of parameter choice
+as $p$ increases, which is corroborated by both theory and
+experiment. This phenomenon was referred to by Sanders et. al as `the
+prevalence of chaotic dynamics in games with many players'
+\cite{Sanders2018}.
 
-A point which we wish to discuss here is the difference in the result found w.r.t.~\cite{Sanders2018}, which considered the stability of \textit{Experience Weighted Attraction} (EWA).
-Namely, Sanders et al.~found that convergence is seen for higher values of $\alpha$, whereas lower values give rise to chaos, the opposite of what is found here.
-The reason for this can be seen in the update equation of Q-Learning (\ref{eqn::Qupdate}), whereby
-smaller values of $\alpha$ result in the agent placing a lower weight on the reward received at each step.
-As such, lower values of $\alpha$ result in the agent taking more conservative steps and yields a higher probability of convergence.
-In contrast, the update for EWA does not discount the reward received at all and, instead, only discounts the previous knowledge of the Q-value based on higher choices of $\alpha$.
-In essence, the difference is the fact that Q-Learning discounts new information by a factor of $\alpha$, whilst EWA does not.
-Yet, the difference in stability caused by this change is significant.
-This highlights the importance of performing analyses such as the present work; it allows for a method to analytically compare the difference between learning algorithms and, for practitioners, ensure that the appropriate algorithm is chosen for the parameters of their specific task.
+A point which we wish to discuss here is the difference in the result
+found w.r.t.~\cite{Sanders2018}, which considered the stability of
+\textit{Experience Weighted Attraction} (EWA). Namely, Sanders et
+al.~found that convergence is seen for higher values of $\alpha$,
+whereas lower values give rise to chaos, the opposite of what is found
+here. The reason for this can be seen in the update equation of
+Q-Learning (\ref{eqn::Qupdate}), whereby smaller values of $\alpha$
+result in the agent placing a lower weight on the reward received at
+each step. As such, lower values of $\alpha$ result in the agent
+taking more conservative steps and yields a higher probability of
+convergence. In contrast, the update for EWA does not discount the
+reward received at all and, instead, only discounts the previous
+knowledge of the Q-value based on higher choices of $\alpha$. In
+essence, the difference is the fact that Q-Learning discounts new
+information by a factor of $\alpha$, whilst EWA does not. Yet, the
+difference in stability caused by this change is significant. This
+highlights the importance of performing analyses such as the present
+work; it allows for a method to analytically compare the difference
+between learning algorithms and, for practitioners, ensure that the
+appropriate algorithm is chosen for the parameters of their specific
+task.
 
-To summarise, we have shown that the analytic result (\ref{eqn::Final}) provides a strong assessment for the effect that $\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of convergence of Q-Learning.
-We show that, at least for negatively correlated payoffs, the strength of correlation plays no role in determining the stability of the system.
-Furthermore, though (\ref{eqn::Final}) overestimates the region of instability, it accurately conveys that convergence of Q-Learning is unlikely for games with many players and actions.
-In fact, our experimental results also verify that stability may only be guaranteed for the limiting case of two-player, two-action games.
-
-Finally, we show that the behaviour of the stability line differs from that of EWA and suggest that this shows that a stability analysis is an important mode of analysis for reinforcement learning equations to ensure that parameters are being chosen appropriately to guarantee the safe convergence of learning.
+To summarise, we have shown that the analytic result
+(\ref{eqn::Final}) provides a strong assessment for the effect that
+$\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of
+convergence of Q-Learning. We showed that, at least for negatively
+correlated payoffs, the strength of correlation plays no role in
+determining the stability of the system. Furthermore, though
+(\ref{eqn::Final}) overestimates the region of instability, it
+accurately conveys that convergence of Q-Learning is unlikely for
+games with many players and actions. In fact, our experimental results
+also verify that stability may only be guaranteed for the limiting
+case of two-player, two-action games \fb{actually we consider 3
+  players as well}.
+%
+Finally, we showed that the behaviour of the stability line differs
+from that of EWA and suggest that this shows that a stability analysis
+is an important mode of analysis for reinforcement learning algorithms
+to ensure that parameters are being chosen appropriately to guarantee
+the safe convergence of learning.
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Edit Section 4

--- 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-%\documentclass[sigconf]{aamas} 
+% \documentclass[sigconf]{aamas} 
 \documentclass[sigconf,anonymous]{aamas}
@@
     \centering
-
-        \begin{subfigure}[b]{0.9 \textwidth}
-        \includegraphics[width=0.5\textwidth]{Figures/DynamicalBehavioursTop.png}
-        \end{subfigure}
-
-        \begin{subfigure}[b]{0.9 \textwidth}
-        \includegraphics[width=0.5\textwidth]{Figures/DynamicalBehaviourschaos.png}
-        \end{subfigure}
-
-        \caption{ \label{fig::DynamicalBehaviours} Different types of dynamical behaviour
+    \includegraphics[width = 0.8 \linewidth]{Figures/DynamicalBehaviours.png}
+    \caption{Evaluation of (\label{fig::DynamicalBehaviours} Different types of dynamical behaviour
        displayed
-        by learning agents. Here the $x$-axis (resp.~$y$-axis) is the probability with which agent 1 (resp.~agent 2) chooses a given action. a) Figure drawn from \cite{Tuyls2006AnGames}.
+        by learning agents. Here the $x$-axis (resp.~$y$-axis) is the probability with which agent 1 (resp.~agent 2) chooses a given action. (Top Left) Figure drawn from \cite{Tuyls2006AnGames}.
         Convergence
         to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
-        that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
-        d) Chaotic behaviour, here small deviations in the initial conditions can grow
-        exponentially. b-d drawn from \cite{Sanders2018}.}
+        that all trajectories, regardless of initialisation, will converge to this point. (Top Right) Limit Cycle, the trajectories converge to cyclic behaviour (Bottom)
+        Chaotic behaviour, here small deviations in the initial conditions can grow
+        exponentially. (Top Right) and (Bottom) drawn from \cite{Sanders2018}.}
 \end{figure}
@@
 
+\small{
 \begin{eqnarray}
 %    \begin{split}
-    0 & = & \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{p-2} \chi + \nonumber \\
-      &  & + \sqrt{2} \alpha \ttau q^{(p-1)/2}z + \sqrt{2} \alpha \htau q^{p/2} z^{p/p-1} + \talpha \rho]
+    0  = \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{p-2} \chi + \sqrt{2} \alpha \ttau q^{(p-1)/2}z + \sqrt{2} \alpha \htau q^{p/2} z^{p/p-1} + \talpha \rho]
     \label{eqn::fixed_point}
@@
 \end{eqnarray}
+}
 %
@@
 We then examine the
-long-term behaviour of the perturbation $\xpert$. To do this, we take
-the Fourier transform of (\ref{eqn::Linearised}) and analyse its
+long-term behaviour of the perturbation $\xpert$. by taking
+the Fourier transform of (\ref{eqn::Linearised}) and analysing its
 behaviour at $\omega = 0$. After some manipulation (Section S4), this gives
@@
 \subsection{Discussion}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width = 1.1 \linewidth]{Figures/Theory.png}
+    \caption{Evaluation of (\ref{eqn::Final}) over a range of $\alpha$ and $\Gamma$ values.
+Ligher regions indicate where (\ref{eqn::Final}) is close to zero (i.e.
+close to the stability boundary) whilst darker regions are further away.
+We vary $\alpha$ in the range $[0.01, 0.05]$ and $\Gamma$ in the range $[-1, 0]$.
+$\tau = 0.05$.
+(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 5$, (Bottom Left) $p = 2, N = 20$, (Bottom Right) $p=3, N = 2$.}
+    \label{fig:theory}
+\end{figure}
+
 The fixed point condition (\ref{eqn::Final}) yields a number of testable implications, of which we test the validity through in the subsequent section. These implications are as follows.
@@
     \centering
-    \includegraphics[width = 0.8 \linewidth]{Figures/pVariance.png}
+    \includegraphics[width = 0.7 \linewidth]{Figures/pVariance.png}
     \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$.
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width = 1.1 \linewidth]{Figures/Theory.png}
-%     \caption{Results of numerical experiments.
-The heatmaps show the value of the Liapunov Exponent determined by the procedure outlined in Section~\ref{sec:exev} scaled by $1 \times 10^5$ for convenience.
-Lighter values show a higher exponent whilst darker values indicate lower values.
-Each experiment is run with $\tau = 0.05$.
-(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 4$, (Mid-Left) $p = 2, N = 10$, (Mid-Right) $p = 2, N = 20$, (Bottom) $p = 3, N = 5$.}
-%     \label{fig:theory}
-% \end{figure}
-% %\fb{Can we arrange Fig.~\ref{fig:theory} in a 2x2 square?}
+In this section, we describe and discuss the numerical experiments we use to verify the implications described in the discussion of Section \ref{sec::Theory}.
+We first describe how these experiments were conducted and then, having presented the results in Figures \ref{fig:NumericalExperiments} and \ref{fig:pVarianceExpt}, we discuss the correlation with the theory.
 
@@
 The results of these experiments are shown in Figure \ref{fig:NumericalExperiments}, with parameters chosen to match those in the analytic assessment (Figure \ref{fig:theory}).
-% By examination it is found that, in many cases the system oscillates about some equilibrium point in a low dimensional chaotic manner (i.e.
-the manner in which the action probabilities change is indistinguishable from random motion) \textbf{get some graphs for this}
-
-% The purpose 
-% \st{of this experiment} is to determine a heuristic estimate for the Lyapunov exponent, which measures the degree to which initial conditions which start close to one another converge or diverge as the dynamics evolve \cite{Strogatz2000}.
-The former indicates a stable system (in the sense of Lyapunov \cite{}) whilst the latter signals instability.
-The procedure for calculating the Lyapunov exponent is given in (\ref{eq::LiapExpo}).
 
@@
    \item Initialise values of $\Gamma, \alpha$ (or $\tau$ appropriately). These will be swept over in the experiment.
-\item Generate 15 payoff matrices for both agents by sampling from a multi-variate Gaussian 
+\item Generate 15 payoff matrices by sampling from a multi-variate Gaussian 
 (variables are the payoff elements) with mean zero and covariance parameterised by $\Gamma$.
@@
 
-% \item After 500 iterations measure the distance $\Vec{\delta_1} = |A_2 - A_1|$
-% \item After 10000 iterations measure the distance $\Vec{\delta_n} = |A_2 - A_1|$
-% \item Determine \fb{the Lyapunov exponent} 
-% \begin{eqnarray*}
-% \label{eq::LiapExpo}
-%     \lambda_n & = & \max_{i} 10^{-4} ln(\delta_{n, i}/\delta_{1, i})
-% \end{eqnarray*}
-% for each action $i$ and average this value over all five realisations of the payoff matrix. 
 \end{enumerate}
@@
 \begin{figure}[t]
-    \includegraphics[width = 1.1 \linewidth, center]{Figures/a5e2var.png}
+    \includegraphics[width = 1 \linewidth, center]{Figures/a5e2var.png}
     \caption{Figures showing the trajectory of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$.
@@
 This gives a qualitative assessment of the behaviour at both extremes parameters considered.
-We note that the typical behaviour of the system is that the system first moves towards a fixed point and then vary in a pseudo-random manner within a vicinity of the fixed point.
-Critically though, the amount of variation in the case $\alpha = 0.05$ is greater than that of $\alpha = 0.01$, and so it does not settle to a fixed point (i.e.
-is considered unstable).
+We note that the typical behaviour of the system is that the system first moves towards a fixed point and then varies in a pseudo-random manner within a vicinity of the fixed point.
+Critically though, the amount of variation in the case $\alpha = 0.05$ is greater than that of $\alpha = 0.01$.
 
 \begin{figure}[t]
-    \includegraphics[width = 0.75 \linewidth, center]{Figures/pVarianceExpt.png}
+    \includegraphics[width = 0.7 \linewidth, center]{Figures/pVarianceExpt.png}
     \caption{Figure showing the variation $V(t)$ about a fixed point as $p$ is varied from 2 - 6.
@@
 
-To summarise, we have shown that the analytic result (\ref{eqn::Final}) provides a strong assessment for the effect that $\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of convergence of Q-Learning.
-We show that, at least for negatively correlated payoffs, the strength of correlation plays no role in determining the stability of the system.
-Furthermore, though (\ref{eqn::Final}) overestimates the region of instability, it accurately conveys that convergence of Q-Learning is unlikely for games with many players and actions.
-In fact, our experimental results also verify that stability may only be guaranteed for the limiting case of two-player, two-action games.
-
-Finally, we show that the behaviour of the stability line differs from that of EWA and suggest that this shows that a stability analysis is an important mode of analysis for reinforcement learning equations to ensure that parameters are being chosen appropriately to guarantee the safe convergence of learning.
+To summarise, we have shown that the analytic result
+(\ref{eqn::Final}) provides a strong assessment for the effect that
+$\alpha$, $\tau$, $\Gamma$ and $p$ have on the likelihood of
+convergence of Q-Learning. We showed that, at least for negatively
+correlated payoffs, the strength of correlation plays no role in
+determining the stability of the system. Furthermore, though
+(\ref{eqn::Final}) overestimates the region of instability, it
+accurately conveys that convergence of Q-Learning is unlikely for
+games with many players and actions. In fact, our experimental results
+also verify that stability may only be guaranteed for the limiting
+case of two-player, two-action games. Once either of these parameters increase, the region of instability increases rapidly.
+%
+Finally, we showed that the behaviour of the stability line differs
+from that of EWA and suggest that this shows that a stability analysis
+is an important mode of analysis for reinforcement learning algorithms
+to ensure that parameters are being chosen appropriately to guarantee
+the safe convergence of learning.
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

--- 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 \begin{enumerate}
-    \item A trivial result is that the game is everywhere convergent (i.e.
-regardless of the choice of $\Gamma, N, p$) for the cases of $\alpha$ = 0 and/or $\tau$ = 0.
-We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) yielding a value of zero which falls within the stable region.
-    \item Convergence is rare.
-This is seen by the fact that the analytic result overestimates the region of instability.
-In fact, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is negative, which violates the stability criterion.
-This implies that games, in general, will not converge.
-    \item The likelihood of convergence decreases with increasing $\alpha$ and $\tau$, regardless of the choice of $N, p$.
-We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e.
-further from the region of stability).
-    \item The choice of $\Gamma$ does not affect the stability of the game in the negatively-correlated regime.
-Therefore, the only dependent factors are $\alpha, \tau, N, p$.
-This is more easily interpreted from the heatmaps in Figure \ref{fig:theory}.
-    \item The likelihood of convergence decreases as $p$ increases.
-We see this by noticing the weighting that the $(p-1)$ in the second term of (\ref{eqn::Final}) places.
-As $p$ increases, this term drives the system further from the stability boundary.
+    \item A trivial result is that the game is everywhere convergent
+      (i.e., regardless of the choice of $\Gamma$, $N$, $p$) for the cases
+      of $\alpha = 0$ and/or $\tau = 0$.  We see that choosing these
+      values would result in the right hand side of (\ref{eqn::Final})
+      yielding a value of zero which falls within the stable region.
+
+    \item Convergence is rare. This is seen by the fact that the
+      analytic result overestimates the region of instability. In
+      fact, for all allowed choices of $\Gamma$, $\alpha$, $\tau$, the
+      right hand side of (\ref{eqn::Final}) is negative, which
+      violates the stability criterion. This implies that games, in
+      general, will not converge.
+
+    \item The likelihood of convergence decreases with increasing
+      $\alpha$ and $\tau$, regardless of the choice of $N$, $p$. We can
+      see this since the right hand side of (\ref{eqn::Final}) tends
+      further away from zero (i.e., further from the region of
+      stability).
+
+    \item The choice of $\Gamma$ does not affect the stability of the
+      game in the negatively-correlated regime. Therefore, the only
+      dependent factors are $\alpha$, $\tau$, $N$, $p$. This is more easily
+      interpreted from the heatmaps in Figure~\ref{fig:theory} \fb{broken link}.
+
+    \item The likelihood of convergence decreases as $p$ increases. We
+      see this by noticing the weighting placed by $(p-1)$ in the
+      second term of (\ref{eqn::Final}). As $p$ increases, this
+      term drives the system further from the stability boundary.
 
@@
 
-We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}).
-In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$.
-We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
-
-\begin{equation*}
-    \begin{split}
-        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
-        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
-        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
-    \end{split}
-\end{equation*}
-
-It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.
-
-We consider each of the implications (2)-(5) from the previous section
-in turn, choosing to forego illustrating (1) as it can be seen immediately
-from the expression. In those heatmaps where $\tau$ is held fixed
-\textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in
-the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For
-those in which $\alpha$ is held fixed, \textbf{denote them} we choose
-$\alpha = 0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
+We illustrate these implications in Figure \ref{fig:theory} \fb{broken link} which
+plots the value obtained by the right hand side of
+(\ref{eqn::Final}). In order to determine these values, we first had
+to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the
+$\xfixed$ which solves the expression inside the square brackets of
+(\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach
+and use the following expressions for $q$, $\chi$ to determine their
+value.
+%
+\begin{eqnarray*}
+%    \begin{split}
+        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
+        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
+        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+%    \end{split}
+\end{eqnarray*}
+
+It should note that this method of finding $\xfixed$ yields only an
+approximate value and so the $q$, $\chi$ which are found are estimates
+of their true value.
+
+We consider each of the implications (2)-(5)
+%from the previous section
+in turn, choosing to forego illustrating (1) as it can be seen
+immediately from the expression \fb{add number}. In those heatmaps
+where $\tau$ is held fixed \textbf{denote them}, we choose $\tau =
+0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the
+range $[0.01, 0.05]$. For those in which $\alpha$ is held fixed,
+\textbf{denote them} we choose $\alpha = 0.05$ and vary $\tau$ in the
+range $[0.01, 0.05]$. \fb{I assume heatmaps are to be added.}
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex

--- 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}).
-In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$.
-We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
+We illustrate these implications in Figure \ref{fig:theory} \fb{broken link} which
+plots the value obtained by the right hand side of
+(\ref{eqn::Final}). In order to determine these values, we first had
+to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the
+$\xfixed$ which solves the expression inside the square brackets of
+(\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach
+and use the following expressions for $q$, $\chi$ to determine their
+value.
+%
+\begin{eqnarray*}
+%    \begin{split}
+        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
+        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
+        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+%    \end{split}
+\end{eqnarray*}
 
-\begin{equation*}
-    \begin{split}
-        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
-        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
-        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
-    \end{split}
-\end{equation*}
+It should note that this method of finding $\xfixed$ yields only an
+approximate value and so the $q$, $\chi$ which are found are estimates
+of their true value.
 
-It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.
-
-We consider each of the implications (2)-(5) from the previous section
-in turn, choosing to forego illustrating (1) as it can be seen immediately
-from the expression. In those heatmaps where $\tau$ is held fixed
-\textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in
-the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For
-those in which $\alpha$ is held fixed, \textbf{denote them} we choose
-$\alpha = 0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.
+We consider each of the implications (2)-(5)
+%from the previous section
+in turn, choosing to forego illustrating (1) as it can be seen
+immediately from the expression \fb{add number}. In those heatmaps
+where $\tau$ is held fixed \textbf{denote them}, we choose $\tau =
+0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the
+range $[0.01, 0.05]$. For those in which $\alpha$ is held fixed,
+\textbf{denote them} we choose $\alpha = 0.05$ and vary $\tau$ in the
+range $[0.01, 0.05]$. \fb{I assume heatmaps are to be added.}
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
-\paragraph{Implication 2:} By looking at the values of the heatmap, we see that, for all choices
+\paragraph{Implication (2):} By looking at the values of the heatmap, we see that, for all choices
 of the parameters, other than $\alpha = 0, \tau = 0$,
@@
 experiment (Figure \ref{fig:NumericalExperiments}) tends towards
-$\alpha = 0, \tau = 0$.
+$\alpha = 0$, $\tau = 0$.
 
@@
 and still, accurately, predict instability. We go on to verify that
-the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured
+the effect of $p$, $\alpha$, $\Gamma$, and $\tau$ are accurately captured
 by (\ref{eqn::Final}).
 
-We interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero).
-A choice of parameters which evaluates close to the stability boundary has a higher chance (by the analytic error) of being convergent than one which lies further from the boundary.
-Therefore, the heat-maps in Figure \ref{fig:theory} should be considered to show the probability of convergence for a choice of $(\alpha, \Gamma)$.
-Lighter regions denote a higher probability of convergence whereas darker regions are those whose values are further from zero and therefore show a lower probability of convergence.
+We interpret (\ref{eqn::Final}), for given parameters, by determining
+how close the right hand side is to the stability boundary (i.e., how
+close the value is to zero). A choice of parameters which evaluates
+close to the stability boundary has a higher chance (by the analytic
+error) of being convergent than one which lies further from the
+boundary. Therefore, the heat-maps in Figure \ref{fig:theory} should
+be considered to show the probability of convergence for a choice of
+$(\alpha, \Gamma)$. Lighter regions denote a higher probability of
+convergence whereas darker regions are those whose values are further
+from zero and therefore show a lower probability of convergence.
 
-\paragraph{Implication 3} can be visualised by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
+\paragraph{Implication (3)} can be visualised by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
 This occurs independent of the choice of $N$ or $p$.
 
-\paragraph{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$. The choice of $\Gamma$
+\paragraph{Implication (4)} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$. The choice of $\Gamma$
 makes almost no difference in the evaluation of (\ref{eqn::Final}).
 We anticipate that this is due to the restriction of $\Gamma$ to be in the range $[-1, 0]$.
-In this range, the scaling effect of $\Gamma^2$ is dominated by the $\alpha^4$ and $\tau^4$ terms which appear in (\ref{eqn::Final}).
+In this range, the scaling effect of $\Gamma^2$ is dominated by the $\alpha^4$ and $\tau^4$ terms appearing in (\ref{eqn::Final}).
 
@@
 
-\paragraph{Implication 5}, finally, is considered in Figure \ref{fig:pvariation}.
-In this we keep all parameters, except for $p$, fixed and evaluate the right hand side of (\ref{eqn::Final}) for varying $p$, taking the absolute value for convenience.
-We see that the trend is to tend away from the stability boundary, indicating that as the number of players in the system increases, so too does the region of instability.
+\paragraph{Implication (5)}, finally, is considered in Figure \ref{fig:pvariation}, where we keep all parameters, except for $p$, fixed and evaluate the right hand side of (\ref{eqn::Final}) for varying $p$, taking the absolute value for convenience.
+We see that the trend is to tend away from the stability boundary, indicating that, as the number of players in the system increases, so too does the region of instability.
 

### 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Update Section 4

--- 2020-10-08 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 To the best of our knowledge, no such work exists in this context.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\ah{Explanation of games:} The games we consider are \textit{normal form games}.
+The games we consider are \textit{normal form games}.
 These consist of: a finite set of players, with individual strategy spaces $\mathcal{A}$ (though we assume that all players share the same strategy space) and payoff functions for each player.
@@
 \begin{figure}[t]
-    \centering
-    \includegraphics[width = 1.1 \linewidth]{Figures/Theory.png}
+    \includegraphics[width = 1.2 \linewidth, center]{Figures/Theory.png}
     \caption{Evaluation of (\ref{eqn::Final}) over a range of $\alpha$ and $\Gamma$ values.
@@
 \begin{enumerate}
-    \item A trivial result is that the game is everywhere convergent
-      (i.e., regardless of the choice of $\Gamma$, $N$, $p$) for the cases
-      of $\alpha = 0$ and/or $\tau = 0$.  We see that choosing these
-      values would result in the right hand side of (\ref{eqn::Final})
-      yielding a value of zero which falls within the stable region.
-
-    \item Convergence is rare. This is seen by the fact that the
-      analytic result overestimates the region of instability. In
-      fact, for all allowed choices of $\Gamma$, $\alpha$, $\tau$, the
-      right hand side of (\ref{eqn::Final}) is negative, which
-      violates the stability criterion. This implies that games, in
-      general, will not converge.
-
-    \item The likelihood of convergence decreases with increasing
-      $\alpha$ and $\tau$, regardless of the choice of $N$, $p$. We can
-      see this since the right hand side of (\ref{eqn::Final}) tends
-      further away from zero (i.e., further from the region of
-      stability).
-
-    \item The choice of $\Gamma$ does not affect the stability of the
-      game in the negatively-correlated regime. Therefore, the only
-      dependent factors are $\alpha$, $\tau$, $N$, $p$. This is more easily
-      interpreted from the heatmaps in Figure~\ref{fig:theory} \fb{broken link}.
-
-    \item The likelihood of convergence decreases as $p$ increases. We
-      see this by noticing the weighting placed by $(p-1)$ in the
-      second term of (\ref{eqn::Final}). As $p$ increases, this
-      term drives the system further from the stability boundary.
+    \item A trivial result is that the game is everywhere convergent (i.e.
+regardless of the choice of $\Gamma, N, p$) for the cases of $\alpha$ = 0 and/or $\tau$ = 0.
+We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) yielding a value of zero which falls within the stable region.
+    \item Convergence is rare.
+This is seen by the fact that the analytic result overestimates the region of instability.
+In fact, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is negative, which violates the stability criterion.
+This implies that games, in general, will not converge.
+    \item The likelihood of convergence decreases with increasing $\alpha$ and $\tau$, regardless of the choice of $N, p$.
+We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e.
+further from the region of stability).
+    \item The choice of $\Gamma$ does not affect the stability of the game in the negatively-correlated regime.
+Therefore, the only dependent factors are $\alpha, \tau, N, p$.
+This is more easily interpreted from the heatmaps in Figure \ref{fig:theory}.
+    \item The likelihood of convergence decreases as $p$ increases.
+We see this by noticing the weighting that the $(p-1)$ in the second term of (\ref{eqn::Final}) places.
+As $p$ increases, this term drives the system further from the stability boundary.
 
@@
 
-We illustrate these implications in Figure \ref{fig:theory} \fb{broken link} which
-plots the value obtained by the right hand side of
-(\ref{eqn::Final}). In order to determine these values, we first had
-to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the
-$\xfixed$ which solves the expression inside the square brackets of
-(\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach
-and use the following expressions for $q$, $\chi$ to determine their
-value.
-%
-\begin{eqnarray*}
-%    \begin{split}
-        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
-        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
-        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
-%    \end{split}
-\end{eqnarray*}
+We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}).
+In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$.
+We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
 
-It should note that this method of finding $\xfixed$ yields only an
-approximate value and so the $q$, $\chi$ which are found are estimates
-of their true value.
+\begin{equation*}
+    \begin{split}
+        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
+        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
+        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+    \end{split}
+\end{equation*}
 
-We consider each of the implications (2)-(5)
-%from the previous section
-in turn, choosing to forego illustrating (1) as it can be seen
-immediately from the expression \fb{add number}. In those heatmaps
-where $\tau$ is held fixed \textbf{denote them}, we choose $\tau =
-0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the
-range $[0.01, 0.05]$. For those in which $\alpha$ is held fixed,
-\textbf{denote them} we choose $\alpha = 0.05$ and vary $\tau$ in the
-range $[0.01, 0.05]$. \fb{I assume heatmaps are to be added.}
+It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.
+
+We consider each of the implications (2)-(5) from the previous section
+in turn, choosing to forego illustrating (1) as it can be seen immediately
+from (\ref{eqn::Final}). $\tau$ is held fixed
+at $0.05$ and vary $\Gamma$ in
+the range $[-1, 0]$, $\alpha$ in the range $[0.01, 0.05]$.
 
 \paragraph{Implication 2:} By looking at the values of the heatmap, we see that, for all choices
-of the parameters, other than $\alpha = 0, \tau = 0$,
+of the parameters
 (\ref{eqn::Final}) evaluates to a negative value, which signals
@@
 
-\paragraph{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$ and $\tau$. The choice of $\Gamma$
+\paragraph{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$. The choice of $\Gamma$
 makes almost no difference in the evaluation of (\ref{eqn::Final}).
@@
     \centering
-    \includegraphics[width = 0.7 \linewidth]{Figures/pVariance.png}
+    \includegraphics[width = 0.95 \linewidth]{Figures/pVariance.png}
     \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$.
@@
 To generate the numerical simulations in Figure~\ref{fig:NumericalExperiments} we used the
-following procedure. Note in the following that for any heatmap in which $\tau$ is swept over, the roles of $\alpha$ and $\tau$ are swapped.
+following procedure.
 \begin{enumerate}
-   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05 and the latter at 0.1. For the heatmaps in which $\tau$ is swept over $\alpha$ is held fixed at 0.05.
+   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05 and the latter at 0.1.
    \item Initialise values of $\Gamma, \alpha$ (or $\tau$ appropriately). These will be swept over in the experiment.
@@
 At the end of each window, determine the percentage difference between the maximum and minimum values of each strategy component
-\item If the difference is less than 1 \% consider the game converged. Otherwise continue to the next window.
+\item If the difference is less than 1\% consider the game converged. Otherwise continue to the next window.
 \item If the game reaches $1.5 \times 10^4$ iterations without satisfying the relative distance criterion, consider it to be non-convergent.
@@
 \begin{figure}[t]
-    \includegraphics[width = 1.1 \linewidth, center]{Figures/Experiments.png}
+    \includegraphics[width = 1.2 \linewidth, center]{Figures/Experiments.png}
     \caption{Results of numerical experiments in which $\alpha$ is varied.
@@
 \begin{figure}[t]
-    \includegraphics[width = 1 \linewidth, center]{Figures/a5e2var.png}
+    \includegraphics[width = 1.1 \linewidth, center]{Figures/a5e2var.png}
     \caption{Figures showing the trajectory of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$.
@@
 \begin{figure}[t]
-    \includegraphics[width = 0.7 \linewidth, center]{Figures/pVarianceExpt.png}
+    \includegraphics[width = 0.95 \linewidth, center]{Figures/pVarianceExpt.png}
     \caption{Figure showing the variation $V(t)$ about a fixed point as $p$ is varied from 2 - 6.
@@
 
-As future work, our first aim is to verify the analytic result at a finer resolution and by averaging over a greater number of payoff realisations.
+\subsection*{Future Work}
+
+Our first aim is to verify the analytic result at a finer resolution and by averaging over a greater number of payoff realisations.
 This will give a greater insight into the boundary between convergent and non-convergent behaviour and allow for practitioners to choose their parameters in such a way that convergence to a unique fixed point is expected.

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
-\keywords{Game Theory, Reinforcement Learning, Dynamical Systems}
+\keywords{Reinforcement Learning, Dynamical Systems, Game Theory.}
 
@@
 
-Single agent reinforcement learning (RL) is a well established framework for allowing agents to learn optimal strategies when trained on an iterated task 
-For a particularly strong example of this see \cite{Vinyals2019}.
-However, for the realisation of complex tasks, such as air traffic control, market negotiations and multi-robot coordination, it is required that the system be modelled as a multi-agent system (MAS).
-Such systems are not as well understood since a given agent is tasked with optimising a reward function which depends not only on a non-stationary environment, but also on the actions of other, possibly loosely coupled, agents \cite{SchwartzMulti-agentApproach}.
+Single agent reinforcement learning (RL) is a well-established
+framework for allowing agents to learn optimal strategies when trained
+on an iterated task
+%For a particularly strong example of this see
+\cite{Vinyals2019}. However, for the realisation of complex tasks,
+such as air traffic control, market negotiations and multi-robot
+coordination, it is required that the system be modelled as a
+multi-agent system (MAS). Such systems are not as well understood
+since a given agent is tasked with optimising a reward function which
+depends not only on a non-stationary environment, but also on the
+actions of other, possibly loosely coupled, agents
+\cite{SchwartzMulti-agentApproach}.
 
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \centering
-    \includegraphics[width = 0.8 \linewidth]{Figures/DynamicalBehaviours.png}
+    \includegraphics[width = \linewidth]{Figures/DynamicalBehaviours.png}
     \caption{Evaluation of (\label{fig::DynamicalBehaviours} Different types of dynamical behaviour
@@
     \centering
-    \includegraphics[width = 0.95 \linewidth]{Figures/pVariance.png}
+    \includegraphics[width = \linewidth]{Figures/pVariance.png}
     \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$.
@@
     \includegraphics[width = 1.1 \linewidth, center]{Figures/a5e2var.png}
-    \caption{Figures showing the trajectory of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$.
-(Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
+    \caption{The trajectories of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$. (Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
     \label{fig:AlphaVariation}
@@
 \begin{figure}[t]
-    \includegraphics[width = 0.95 \linewidth, center]{Figures/pVarianceExpt.png}
-    \caption{Figure showing the variation $V(t)$ about a fixed point as $p$ is varied from 2 - 6.
+    \includegraphics[width = \linewidth, center]{Figures/pVarianceExpt.png}
+    \caption{Variation $V(t)$ about a fixed point as $p$ ranges from 2 - 6.
 $N = 2$, $\alpha = 0.02$, $\tau = 0.05$, $\Gamma = [-1, 0]$.

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
-\title[InstabilityinMARL]{Stability and Chaos in Multi-Agent Reinforcement Learning}
+\title[InstabilityinMARL]{Stability and Chaos in Multi-agent Reinforcement Learning}
 
@@
 \cite{Vinyals2019}. However, for the realisation of complex tasks,
-such as air traffic control, market negotiations and multi-robot
+such as air traffic control, market negotiations, and multi-robot
 coordination, it is required that the system be modelled as a
-multi-agent system (MAS). Such systems are not as well understood
-since a given agent is tasked with optimising a reward function which
-depends not only on a non-stationary environment, but also on the
-actions of other, possibly loosely coupled, agents
-\cite{SchwartzMulti-agentApproach}.
+multi-agent system (MAS). Such systems are not as well-understood as
+single-agent systems in RL, since a given agent is tasked with
+optimising a reward function which depends not only on a
+non-stationary environment, but also on the actions of other, possibly
+loosely coupled, agents \cite{SchwartzMulti-agentApproach}.
 
-It is, therefore, of paramount importance to develop a strong theoretical understanding of multi-agent reinforcement learning (MARL) to allow an {\em a-priori} understanding of the behaviour of a given learning algorithm.
-Fortunately, the study of MAS is not unique to the field of AI and has been extensively studied from the point of view of economics and game theory as well \cite{ShohamMultiagentFoundations}.
-In particular, the study of evolutionary game theory (EGT) considers the problem of a MAS which is repeatedly exposed to an iterated game.
-his idea shares a strong resemblance with MARL and, in fact, in \cite{Tuyls2006AnGames}, it was shown that, techniques from EGT may be fruitfully used to analyse Q-Learning \cite{Sutton2018}.
+It is, therefore, of paramount importance to develop a strong
+theoretical understanding of multi-agent reinforcement learning (MARL)
+to allow an {\em a priori} understanding of the behaviour of a given
+learning algorithm. Fortunately, the study of MAS is not unique to the
+field of AI and has been extensively investigated from the point of view of
+economics and game theory as well
+\cite{ShohamMultiagentFoundations}. In particular,
+%the study of
+evolutionary game theory (EGT) considers the problem of a MAS which is
+repeatedly exposed to an iterated game. This idea shares a strong
+resemblance with MARL and, in fact, in \cite{Tuyls2006AnGames} it was
+shown that techniques from EGT may be fruitfully applied to the analysis of
+Q-Learning \cite{Sutton2018}.
 
-An important result in modelling such multi agent systems from the EGT perspective is that, when games are learnt and the assumptions of rationality and perfect information are lifted, games may not converge to an equilibrium.
-Instead, as shown in \cite{Sanders2018}, the dynamics may be more complex, and even chaotic (see Section~\ref{sec::DynamicalBehaviours}).
-The present work further describes that the emergence of such behaviours depends on the parameters of the games and the learning algorithm.
-For the analysis of multi-agent systems whose behaviour is inter-dependent, it is desirable that the system be such that the game convergence to a stable equilibrium.
-Without this, it is inherently impossible to predict the outcome of learning.
+An important result in modelling such multi-agent systems \fb{check
+  consistency of multi agent $\to$ multi-agent.} from the EGT
+perspective is that, when games are learnt and the assumptions of
+rationality and perfect information are lifted, games may not converge
+to an equilibrium. Instead, as shown in \cite{Sanders2018}, the
+dynamics may be more complex, and even chaotic (see
+Section~\ref{sec::DynamicalBehaviours}). The present work further
+describes that the emergence of such behaviours depends on the
+parameters of the games and the learning algorithm. For the analysis
+of multi-agent systems whose behaviour is inter-dependent, it is
+desirable that the system be such that the game convergence to a
+stable equilibrium. Without this, it is inherently impossible to
+predict the outcome of learning.
 

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 dynamics may be more complex, and even chaotic (see
-Section~\ref{sec::DynamicalBehaviours}). The present work further
+Sec.~\ref{sec::DynamicalBehaviours}) \fb{Section $\to$ Sec.}. The present work further
 describes that the emergence of such behaviours depends on the
@@
 \paragraph{Contribution}
-In this study, we will be considering the question: under what choice of parameters is a
-multi-agent system, which is trained on an iterated game using Q-Learning, likely to converge to an
-equilibrium as opposed to displaying complex, or unstable behaviours? In investigating this question, we will make the
-following assumptions:
+In this study, we will be considering the question: under what choice
+of parameters is a multi-agent system, which is trained on an iterated \fb{normal-form}
+game using Q-Learning, likely to converge to an equilibrium as opposed
+to displaying complex, or unstable behaviours? In investigating this
+question, we will make the following assumptions:
 
 \begin{enumerate}
-    \item There are a finite set of agent, though the size $p$ of the set is arbitrary. 
-    \item The agents have a large, but discrete, strategy space: during the theoretical study, we
-    will make the assumption that the number of actions $N$ goes to infinity.
-    \item The agents are homogeneous. This requires that all agents have the same parameters and are
-    trained using the same algorithm. Since this is typically the case in reinforcement learning
-    studies, it is not an unreasonable assumption, but does present an interesting avenue for future
-    work.
-    \item The agents are trained on stateless, normal form games (i.e. the environment is static).
+    \item There is a finite set of agent, though its size $p$ can be
+      arbitrarily large.
+
+    \item The agents have a large, but discrete, strategy space:
+      during the theoretical study, we will make the assumption that
+      the number $N$ of actions goes to infinity.
+
+  \item The agents are homogeneous. This requires that all agents have
+    the same parameters and are trained using the same
+    algorithm. Since this is typically the case in reinforcement
+    learning studies, it is not an unreasonable assumption, but does
+    present an interesting avenue for future work.
+
+  \item The agents are trained on stateless, normal form games
+    (i.e., the environment is static).
 \end{enumerate}
+
+\fb{I would summarize here the main findings of the paper in 10-15 lines.}
 
@@
 
-In this section we present an overview of the vast literature which considers the study of Reinforcement Learning (RL) from an evolutionary game dynamics perspective, as well as touching upon some important results and research within the field of game dynamics.
+In this section we present an overview of the vast literature which
+considers the study of reinforcement learning from an evolutionary
+game dynamics perspective, as well as touching upon some important
+results and research within the field of game dynamics.
 
-\paragraph{Evolutionary Game Dynamics} The theory of evolutionary game dynamics \cite{Morgenstern44} considers the case in which agents must repeatedly interact with one another.
-The outcome of this interaction depends on a payoff matrix; 'strong' strategies which maximise the reward are promoted whilst 'weaker' strategies diminish.
-The \textit{replicator dynamic} models this behaviour, and allows one to determine whether, after a number of iterations, the game is likely to converge to some fixed equilibrium and, if so, the probabilities with which strategies are played in this equilibrium.
-\cite{ShohamMultiagentFoundations} provides an excellent introduction to the replicator dynamic for the interested reader.
+\paragraph{Evolutionary Game Dynamics}
+The theory of evolutionary game dynamics \cite{Morgenstern44}
+considers the case in which agents must repeatedly interact with one
+another. The outcome of this interaction depends on a payoff matrix;
+'strong' strategies which maximise the reward are promoted whilst
+'weaker' strategies diminish. The \textit{replicator dynamic} models
+this behaviour, and allows one to determine whether, after a number of
+iterations, the game is likely to converge to some fixed equilibrium
+and, if so, the probabilities with which strategies are played in this
+equilibrium. \cite{ShohamMultiagentFoundations} provides an excellent
+introduction to the replicator dynamic for the interested reader.
 
-Analyses have been performed from the point of view of the replicator dynamic towards the various types of behaviours that can emerge from iterated games.
-Such games are considered imperfect, in that agents make decisions by attempting to anticipate their opponents' behaviour based on experience \cite{Galla2011}.
-\cite{Imhof2005} presents the observation that, in the game of Prisoner's Dilemma, cyclic behaviour emerges in which the optimal strategy cycles across defection, cooperation and tit-for-tat despite defection being the NE.
-\cite{Galla2011} builds on this notion by showing that, in fact, such behaviour is highly dependent on the presence of memory loss in the system.
-In the absence of memory loss, the learning converges to the NE as expected.
-However, as this parameter is increased, the stability of the NE is removed and other stable points are created.
+Analyses have been performed from the point of view of the replicator
+dynamic towards the various types of behaviours that can emerge from
+iterated games. Such games are considered imperfect, in that agents
+make decisions by attempting to anticipate their opponents' behaviour
+based on experience \cite{Galla2011}. \cite{Imhof2005} presents the
+observation that, in the game of Prisoner's Dilemma, cyclic behaviour
+emerges in which the optimal strategy cycles across defection,
+cooperation and tit-for-tat despite defection being the
+NE. \cite{Galla2011} builds on this notion by showing that, in fact,
+such behaviour is highly dependent on the presence of memory loss in
+the system. In the absence of memory loss, the learning converges to
+the NE as expected. However, as this parameter is increased, the
+stability of the NE is removed and other stable points are created.
 
-Taking this notion even further,  \cite{Galla2013} describes an investigation of two-person iterated games in which the players learn using \textit{Experience Weighted Attraction} (EWA), a form of reinforcement learning whose analysis typically falls under the purview of experimental economics \cite{Camerer2009}.
-Through numerical simulations, the authors were able to show that, once again, the emergence of chaos and cycles (see \cite{Strogatz2000} for details on chaotic and periodic motion), is dependent on the choice of parameters.
-A rigorous theoretical analysis, which applies the techniques presented in \cite{Opper1992}, of the replicator dynamic corresponding to EWA presented a method for characterising the regions in parameter space in which a game is likely to converge, exhibit chaos or limit cycles.
-More recently, the authors presented an extended study in \cite{Sanders2018}, in which this analysis was extended towards a generic $p$-player game, which showed that chaotic dynamics are more likely to be observed as the number of players \textit{p} increases.
+Taking this notion even further, \cite{Galla2013} describes an
+investigation of two-person iterated games in which the players learn
+using \textit{Experience Weighted Attraction} (EWA), a form of
+reinforcement learning whose analysis typically falls under the
+purview of experimental economics \cite{Camerer2009}. Through
+numerical simulations, the authors were able to show that, once again,
+the emergence of chaos and cycles (see \cite{Strogatz2000} for details
+on chaotic and periodic motion), is dependent on the choice of
+parameters. A rigorous theoretical analysis, which applies the
+techniques presented in \cite{Opper1992}, of the replicator dynamic
+corresponding to EWA presented a method for characterising the regions
+in parameter space in which a game is likely to converge, exhibit
+chaos or limit cycles. More recently, the authors presented an
+extended study in \cite{Sanders2018}, in which this analysis was
+extended towards a generic $p$-player game, which showed that chaotic
+dynamics are more likely to be observed as the number of players
+\textit{p} increases.
 
-It is evident, therefore, that in the case of learning on iterated games, convergence to stable equilibria cannot be taken for granted and, in fact, is rare.
-It would therefore be fruitful to bring these analyses from EGT to better understand Reinforcement Learning from an AI perspective.
+It is evident, therefore, that in the case of learning on iterated
+games, convergence to stable equilibria cannot be taken for granted
+and, in fact, is rare. It would therefore be fruitful to bring these
+analyses from EGT to better understand Reinforcement Learning from an
+AI perspective.
 
-\paragraph{Dynamics of RL} In \cite{Tuyls2006AnGames}, the authors are able to derive a relation between Q-Learning (see \cite{Barber2012}) and the replicator dynamic.
-In doing so, the authors present an evolutionary model which accurately predicts the dynamics of Q-Learning.
-This sprung forward a vast array of literature which perform similar derivations for various reinforcement learning algorithms.
-\cite{Bloembergen2015} presents an excellent review of these.
-In particular it should be noted that many of these studies focus on normal form games, in which the payoff matrix does not change (i.e.
-the environment is static).
-Recent work, such as \cite{Hennes2008}, extends this work towards multi-state games, though this is restricted to 2 state games.
-Similarly, \cite{Galstyan2013}, extends the work in \cite{Tuyls2006AnGames} towards games with continuous action spaces.
-Most recently, \cite{Hu2019} considers Q-learning in the mean-field limit, in which the strategies of populations of agents are considered.
+\paragraph{Dynamics of RL}
+In \cite{Tuyls2006AnGames}, the authors are able to derive a relation
+between Q-Learning (see \cite{Barber2012}) and the replicator
+dynamic. In doing so, the authors present an evolutionary model which
+accurately predicts the dynamics of Q-Learning. This sprung forward a
+vast array of literature which perform similar derivations for various
+reinforcement learning algorithms. \cite{Bloembergen2015} presents an
+excellent review of these. In particular it should be noted that many
+of these studies focus on normal form games, in which the payoff
+matrix does not change (i.e. the environment is static). Recent work,
+such as \cite{Hennes2008}, extends this work towards multi-state
+games, though this is restricted to 2 state games. Similarly,
+\cite{Galstyan2013}, extends the work in \cite{Tuyls2006AnGames}
+towards games with continuous action spaces. Most recently,
+\cite{Hu2019} considers Q-learning in the mean-field limit, in which
+the strategies of populations of agents are considered.
 
-The relation between RL and the replicator dynamic allows for the assumption of convergence in reinforcement learning to be lifted and instead for the emergence of more complex behaviour to be examined.
-In particular, this study aims to perform a similar analysis to that in \cite{Sanders2018} and establish the regions in parameter space in which Q-Learning converges to stable fixed points and where the learning is unstable.
-To the best of our knowledge, no such work exists in this context.
+The relation between RL and the replicator dynamic allows for the
+assumption of convergence in reinforcement learning to be lifted and
+instead for the emergence of more complex behaviour to be examined. In
+particular, this study aims to perform a similar analysis to that in
+\cite{Sanders2018} and establish the regions in parameter space in
+which Q-Learning converges to stable fixed points and where the
+learning is unstable. To the best of our knowledge, no such work
+exists in this context.
 

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 The theory of evolutionary game dynamics \cite{Morgenstern44}
-considers the case in which agents must repeatedly interact with one
-another. The outcome of this interaction depends on a payoff matrix;
-'strong' strategies which maximise the reward are promoted whilst
-'weaker' strategies diminish. The \textit{replicator dynamic} models
-this behaviour, and allows one to determine whether, after a number of
-iterations, the game is likely to converge to some fixed equilibrium
-and, if so, the probabilities with which strategies are played in this
-equilibrium. \cite{ShohamMultiagentFoundations} provides an excellent
-introduction to the replicator dynamic for the interested reader.
+considers game-like settings in which agents must repeatedly interact
+with one another. The outcome of this interaction depends on a payoff
+matrix; 'strong' strategies which maximise the reward are promoted,
+whilst 'weaker' strategies diminish. The \textit{replicator dynamic}
+models this behaviour, and allows one to determine whether, after a
+number of iterations, the game is likely to converge to some fixed
+equilibrium and, if so, the probabilities with which strategies are
+played in this equilibrium (see \cite{ShohamMultiagentFoundations}
+for an excellent introduction to the replicator dynamics).
 
@@
 cooperation and tit-for-tat despite defection being the
-NE. \cite{Galla2011} builds on this notion by showing that, in fact,
+NE. \cite{Galla2011} builds on this observation by showing that, in fact,
 such behaviour is highly dependent on the presence of memory loss in
 the system. In the absence of memory loss, the learning converges to
-the NE as expected. However, as this parameter is increased, the
-stability of the NE is removed and other stable points are created.
+the NE as expected. \fb{I think we can remove this last couple of lines if need be: However, as this parameter is increased, the
+stability of the NE is removed and other stable points are created.}
 
-Taking this notion even further, \cite{Galla2013} describes an
-investigation of two-person iterated games in which the players learn
-using \textit{Experience Weighted Attraction} (EWA), a form of
-reinforcement learning whose analysis typically falls under the
-purview of experimental economics \cite{Camerer2009}. Through
-numerical simulations, the authors were able to show that, once again,
-the emergence of chaos and cycles (see \cite{Strogatz2000} for details
-on chaotic and periodic motion), is dependent on the choice of
-parameters. A rigorous theoretical analysis, which applies the
-techniques presented in \cite{Opper1992}, of the replicator dynamic
-corresponding to EWA presented a method for characterising the regions
-in parameter space in which a game is likely to converge, exhibit
-chaos or limit cycles. More recently, the authors presented an
-extended study in \cite{Sanders2018}, in which this analysis was
-extended towards a generic $p$-player game, which showed that chaotic
-dynamics are more likely to be observed as the number of players
-\textit{p} increases.
+Taking this notion \fb{which one?} even further, \cite{Galla2013}
+describes an analysis of two-person iterated games in which the
+players learn using \textit{experience weighted attraction} (EWA), a
+form of reinforcement learning typically applied in experimental
+economics \cite{Camerer2009}. Through numerical simulations, the
+authors were able to show that the emergence of chaos and cycles is
+dependent on the choice of parameters (see \cite{Strogatz2000} for
+details on chaotic and periodic motion). A rigorous theoretical
+analysis of the replicator dynamic corresponding to EWA, which applies
+the techniques in \cite{Opper1992}, presented a method for
+characterising the regions in parameter space in which a game is
+likely to converge, exhibit chaos or limit cycles. More recently, the
+same authors presented an extended study in \cite{Sanders2018}, in which
+this analysis was extended towards a generic $p$-player game, which
+showed that chaotic dynamics are more likely to be observed as the
+number of players \textit{p} increases.
 
@@
 vast array of literature which perform similar derivations for various
-reinforcement learning algorithms. \cite{Bloembergen2015} presents an
-excellent review of these. In particular it should be noted that many
-of these studies focus on normal form games, in which the payoff
-matrix does not change (i.e. the environment is static). Recent work,
-such as \cite{Hennes2008}, extends this work towards multi-state
-games, though this is restricted to 2 state games. Similarly,
-\cite{Galstyan2013}, extends the work in \cite{Tuyls2006AnGames}
-towards games with continuous action spaces. Most recently,
-\cite{Hu2019} considers Q-learning in the mean-field limit, in which
-the strategies of populations of agents are considered.
+reinforcement learning algorithms (see \cite{Bloembergen2015} for an
+excellent literature review). In particular it should be noted that
+many of these studies focus on normal form games, in which the payoff
+matrix does not change (i.e., the environment is static). Recent work,
+such as \cite{Hennes2008}, extends this framework towards multi-state
+games.
+%though this is restricted to 2 state games.
+Similarly, \cite{Galstyan2013}, extends the work in
+\cite{Tuyls2006AnGames} towards games with continuous action
+spaces. Most recently, \cite{Hu2019} considers Q-learning in the
+mean-field limit, in which the strategies of populations of agents are
+considered, rather than individuals.
 

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods
Updated introduction

@@
 \section{Introduction}
+\label{sec::Intro}
 
@@
 
-An important result in modelling such multi-agent systems \fb{check
-  consistency of multi agent $\to$ multi-agent.} from the EGT
+An important result in modelling such multi-agent systems from the EGT
 perspective is that, when games are learnt and the assumptions of
@@
 dynamics may be more complex, and even chaotic (see
-Sec.~\ref{sec::DynamicalBehaviours}) \fb{Section $\to$ Sec.}. The present work further
+Sec.~\ref{sec::DynamicalBehaviours}). The present work further
 describes that the emergence of such behaviours depends on the
@@
 In this study, we will be considering the question: under what choice
-of parameters is a multi-agent system, which is trained on an iterated \fb{normal-form}
-game using Q-Learning, likely to converge to an equilibrium as opposed
+of parameters is a multi-agent system, which is trained on an iterated normal-form game using Q-Learning, likely to converge to an equilibrium as opposed
 to displaying complex, or unstable behaviours? In investigating this
@@
 
-\fb{I would summarize here the main findings of the paper in 10-15 lines.}
+Through our analysis and experiments we find that likelihood of displaying unstable dynamics increases as the \textit{step length} $\alpha$ and \textit{intensity of choice} $\tau$ parameters in the Q-Learning algorithm \cite{Barber2012} increase.
+However, the correlation between payoffs $\Gamma$, which measures how cooperative or competitive a game is, does not affect the stability of the system.
+In addition, we find that regardless of the choice of these parameters, the likelihood of unstable behaviours increases as the number of players $p$ in the game increase.
 
@@
 cooperation and tit-for-tat despite defection being the
-NE. \cite{Galla2011} builds on this observation by showing that, in fact,
+NE. In \cite{Galla2011}, Galla builds on this observation by showing that, in fact,
 such behaviour is highly dependent on the presence of memory loss in
 the system. In the absence of memory loss, the learning converges to
-the NE as expected. \fb{I think we can remove this last couple of lines if need be: However, as this parameter is increased, the
-stability of the NE is removed and other stable points are created.}
+the NE as expected.However, as this parameter is increased, the
+stability of the NE is removed and other stable points are created.
 
-Taking this notion \fb{which one?} even further, \cite{Galla2013}
+Taking the notion of parameter dependence even further, \cite{Galla2013}
 describes an analysis of two-person iterated games in which the
@@
 showed that chaotic dynamics are more likely to be observed as the
-number of players \textit{p} increases.
+number of players \textit{p} increases. By contrast to the present work, \cite{Barber2012} focuses on the analysis of the EWA algorithm, while we consider the Q-Learning \cite{Barber2012} algorithm.
 
@@
 which Q-Learning converges to stable fixed points and where the
-learning is unstable. To the best of our knowledge, no such work
+learning is unstable.
+In doing so, we extend the dynamics considered by Tuyls et al.
+towards a general $p$-player scenario, rather than only two players, thereby allowing an analysis of how the number of players in a game affects its stability.
+To the best of our knowledge, no such work
 exists in this context.
-
-\newpage
 
@@
 
-    As discussed in the previous section, when learning on iterated
+    As discussed in the Sec. \ref{sec::Intro}, when learning on iterated
     games, player strategies may exhibit much more complex behaviours
@@
 appropriately (see the discussion in \cite{Sanders2018} or
-Section S2.2 for further details). Accordingly we choose
+Sec. S2.2 for further details). Accordingly we choose
 scaled variables (denoted with a tilde) as
@@
 of the payoff matrix. To do this, we assert that the payoff elements
-(after scaling) are generated by a multivariate Gaussian distribution
+(after scaling) are generated by a multi-variate Gaussian distribution
 with mean zero and covariance given as
@@
 We then use a generating functional approach as outlined in
-\cite{Mezard1986} to average the dynamics over this multivariate
+\cite{Mezard1986} to average the dynamics over this multi-variate
 Gaussian. The generating functional is a method derived from
@@
 The last two exponentials contain the payoffs of the game.
-These are randomly generated using a multivariate gaussian and then held fixed for the rest of the game.
+These are randomly generated using a multi-variate gaussian and then held fixed for the rest of the game.
 As such these comprise the aforementioned 'quenched disorder'.
@@
 
-By taking this average (Section S2.3), we obtain the \textit{effective dynamics}
+By taking this average (Sec. S2.3), we obtain the \textit{effective dynamics}
 
@@
 the Fourier transform of (\ref{eqn::Linearised}) and analysing its
-behaviour at $\omega = 0$. After some manipulation (Section S4), this gives
+behaviour at $\omega = 0$. After some manipulation (Sec. S4), this gives
 
@@
 
-The fixed point condition (\ref{eqn::Final}) yields a number of testable implications, of which we test the validity through in the subsequent section. These implications are as follows.
+The fixed point condition (\ref{eqn::Final}) yields a number of testable implications, of which we subsequently test the validity. These implications are as follows.
 
@@
 
-We consider each of the implications (2)-(5) from the previous section
+We consider each of the implications (2)-(5) from the Sec. \ref{sec::Theory}
 in turn, choosing to forego illustrating (1) as it can be seen immediately
@@
 
-In this section, we describe and discuss the numerical experiments we use to verify the implications described in the discussion of Section \ref{sec::Theory}.
+In this section, we describe and discuss the numerical experiments we use to verify the implications described in the discussion of Sec.
+\ref{sec::Theory}.
 We first describe how these experiments were conducted and then, having presented the results in Figures \ref{fig:NumericalExperiments} and \ref{fig:pVarianceExpt}, we discuss the correlation with the theory.
@@
 \begin{figure}[t]
-    \includegraphics[width = 1.1 \linewidth, center]{Figures/a5e2var.png}
+    \includegraphics[width = 0.75 \linewidth, center]{Figures/alphavar5e2.png}
     \caption{The trajectories of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$. (Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}

### 2020-10-09 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -7,9 +7,9 @@ from tqdm import tqdm
 # alpha = .1
 gamma = .1
 Gamma = 0.1
-tau = 1
+tau = 0.05
 
-nActions = 2
+nActions = 5
 
 delta_0 = 1e-3
 nSim = 15
@@ -37,10 +37,10 @@ def generateGames(gamma, nSim, nAct):
     for i in range(nSim):
         rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
 
-        # rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
-        rewardAs = np.dstack((rewardAs, np.array([[1, 5], [0, 3]])))
-        # rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
-        rewardBs = np.dstack((rewardBs, np.array([[1, 0], [5, 3]])))
+        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
+        # rewardAs = np.dstack((rewardAs, np.array([[1, 5], [0, 3]])))
+        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
+        # rewardBs = np.dstack((rewardBs, np.array([[1, 0], [5, 3]])))
     return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
 
 
@@ -80,7 +80,7 @@ def getDelta(qValues0, qValues1, nSim):
 plotExpo = []
 
 for alpha in np.linspace(1e-2, 5e-2, num=1):
-    for Gamma in np.linspace(-1, 0, num=1):
+    for Gamma in np.linspace(-0.5, 0, num=1):
 
         payoffs = generateGames(Gamma, nSim, nActions)
         allActions = []
@@ -96,9 +96,8 @@ allActions = np.array(allActions)
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
 
-for i in range(nSim):
-    plt.plot(allActions[:, i, 0, 0], allActions[:, i, 1, 0])
-
+plt.plot(allActions[:, 0, 0, 0], allActions[:, 0, 1, 0])
+plt.rc('axes', labelsize=12)
 plt.xlabel('Player 1 Action 1')
 plt.ylabel('Player 2 Action 1')
[…]

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex

@@
     arise.
-
+%
     \begin{figure}[t]
@@
 
-In this study, we characterise the behaviours of Q-Learning in $p$-player, $N$-action games.
-To do this, we analyse the replicator model of Q-Learning derived by Tuyls et al.
-Specifically, we search for the regions in parameter space where the dynamics are expected to converge to a stable equilibrium and those where learning is unstable.
-This yields a number of important results.
-We find that convergence to a unique fixed point is found for low values of $\alpha$, the \textit{step length} of the algorithm and for negatively correlated payoff matrices, though the strength of correlation $\Gamma$ does not influence stability.
-As $\alpha$ increases, the likelihood of convergence decreases.
-The same is true for the \textit{intensity of choice} parameter $\tau$.
-Our analysis also shows that the likelihood of convergence decreases, regardless of parameter choice as the number of players $p$ in the system increases.
-
-\subsection*{Future Work}
-
-Our first aim is to verify the analytic result at a finer resolution and by averaging over a greater number of payoff realisations.
-This will give a greater insight into the boundary between convergent and non-convergent behaviour and allow for practitioners to choose their parameters in such a way that convergence to a unique fixed point is expected.
-In addition we noted that one of the conclusions to our study is that convergence to a unique fixed point is rare in Q-Learning.
-In fact, complex behaviour (such as the existence of multiple fixed points, limit cycles and chaos) is more likely.
-We, therefore, aim to characterise these complex behaviours in parameter space both theoretically and numerically.
-
-The present work gives a first step towards considering the stability of Multi-Agent Reinforcement Learning and focuses on the limiting case of stateless normal-form games played by homogeneous agents.
-As research into the dynamics of Reinforcement Learning algorithms progresses, it would be prudent to apply this analysis to various other algorithm.
-Algorithms whose dynamics are established, and are therefore open to a stability analysis, include piecewise Q-Learning and Cross Learning.
-This would provide a strong method by which to compare and provide safety guarantees to different algorithms for a particular use case.
+In this study, we made a first contribution towards the
+characterisation of the behaviours of agents learning how to play
+$p$-player, $N$-action games through Q-Learning. To this end, we
+analysed the replicator model of Q-Learning derived in \cite{Tuyls2006AnGames}. Specifically, we searched for the regions in parameter space
+where the dynamics are expected to converge to a stable equilibrium
+and those where learning is unstable. This yielded a number of
+important results. We showed that convergence to a unique fixed point is
+found for low values of $\alpha$, the \textit{step length} of the
+algorithm, and for negatively correlated payoff matrices, though the
+strength of correlation $\Gamma$ does not influence stability. As
+$\alpha$ increases, the likelihood of convergence decreases. The same
+is true for the \textit{intensity of choice} parameter $\tau$. Our
+analysis also shows that the likelihood of convergence decreases,
+regardless of parameter choice as the number of players $p$ in the
+system increases.
+
+\paragraph{Future Work}
+Our first aim is to verify the analytic results at a finer resolution
+and by averaging over a greater number of payoff realisations. This
+will give a greater insight into the boundary between convergent and
+non-convergent behaviour and allow for practitioners to choose their
+parameters in such a way that convergence to a (possibly unique) fixed
+point is expected. In addition we noted that one of the conclusions of
+our study is that convergence to a unique fixed point is rare in
+Q-Learning. In fact, complex behaviours (such as the existence of
+multiple fixed points, limit cycles, and chaos) are more likely. We,
+therefore, aim to characterise these complex behaviours in parameter
+space both theoretically and numerically.
+
+The present work represents a first step towards considering the stability
+of multi-agent reinforcement learning and focuses on the limiting case
+of stateless normal-form games played by homogeneous agents. As
+research into the dynamics of RL algorithms
+progresses, it would be prudent to apply this analysis to various
+other algorithm. Algorithms whose dynamics are established, and are
+therefore open to a stability analysis, include piecewise Q-Learning
+and Cross Learning. This would provide a strong method by which to
+compare and provide safety guarantees to different algorithms for a
+particular use case.
 

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

--- 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-In this study, we characterise the behaviours of Q-Learning in $p$-player, $N$-action games.
-To do this, we analyse the replicator model of Q-Learning derived by Tuyls et al.
-Specifically, we search for the regions in parameter space where the dynamics are expected to converge to a stable equilibrium and those where learning is unstable.
-This yields a number of important results.
-We find that convergence to a unique fixed point is found for low values of $\alpha$, the \textit{step length} of the algorithm and for negatively correlated payoff matrices, though the strength of correlation $\Gamma$ does not influence stability.
-As $\alpha$ increases, the likelihood of convergence decreases.
-The same is true for the \textit{intensity of choice} parameter $\tau$.
-Our analysis also shows that the likelihood of convergence decreases, regardless of parameter choice as the number of players $p$ in the system increases.
+In this study, we made a first contribution towards the
+characterisation of the behaviours of agents learning how to play
+$p$-player, $N$-action games through Q-Learning. To this end, we
+analysed the replicator model of Q-Learning derived in \cite{Tuyls2006AnGames}. Specifically, we searched for the regions in parameter space
+where the dynamics are expected to converge to a stable equilibrium
+and those where learning is unstable. This yielded a number of
+important results. We showed that convergence to a unique fixed point is
+found for low values of $\alpha$, the \textit{step length} of the
+algorithm, and for negatively correlated payoff matrices, though the
+strength of correlation $\Gamma$ does not influence stability. As
+$\alpha$ increases, the likelihood of convergence decreases. The same
+is true for the \textit{intensity of choice} parameter $\tau$. Our
+analysis also shows that the likelihood of convergence decreases,
+regardless of parameter choice as the number of players $p$ in the
+system increases.
 
-\subsection*{Future Work}
+\paragraph{Future Work}
+Our first aim is to verify the analytic results at a finer resolution
+and by averaging over a greater number of payoff realisations. This
+will give a greater insight into the boundary between convergent and
+non-convergent behaviour and allow for practitioners to choose their
+parameters in such a way that convergence to a (possibly unique) fixed
+point is expected. In addition we noted that one of the conclusions of
+our study is that convergence to a unique fixed point is rare in
+Q-Learning. In fact, complex behaviours (such as the existence of
+multiple fixed points, limit cycles, and chaos) are more likely. We,
+therefore, aim to characterise these complex behaviours in parameter
+space both theoretically and numerically.
 
-Our first aim is to verify the analytic result at a finer resolution and by averaging over a greater number of payoff realisations.
-This will give a greater insight into the boundary between convergent and non-convergent behaviour and allow for practitioners to choose their parameters in such a way that convergence to a unique fixed point is expected.
-In addition we noted that one of the conclusions to our study is that convergence to a unique fixed point is rare in Q-Learning.
-In fact, complex behaviour (such as the existence of multiple fixed points, limit cycles and chaos) is more likely.
-We, therefore, aim to characterise these complex behaviours in parameter space both theoretically and numerically.
-
-The present work gives a first step towards considering the stability of Multi-Agent Reinforcement Learning and focuses on the limiting case of stateless normal-form games played by homogeneous agents.
-As research into the dynamics of Reinforcement Learning algorithms progresses, it would be prudent to apply this analysis to various other algorithm.
-Algorithms whose dynamics are established, and are therefore open to a stability analysis, include piecewise Q-Learning and Cross Learning.
-This would provide a strong method by which to compare and provide safety guarantees to different algorithms for a particular use case.
+The present work represents a first step towards considering the stability
+of multi-agent reinforcement learning and focuses on the limiting case
+of stateless normal-form games played by homogeneous agents. As
+research into the dynamics of RL algorithms
+progresses, it would be prudent to apply this analysis to various
+other algorithm. Algorithms whose dynamics are established, and are
+therefore open to a stability analysis, include piecewise Q-Learning
+and Cross Learning. This would provide a strong method by which to
+compare and provide safety guarantees to different algorithms for a
+particular use case.
 

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

--- 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-Through our analysis and experiments we find that likelihood of displaying unstable dynamics increases as the \textit{step length} $\alpha$ and \textit{intensity of choice} $\tau$ parameters in the Q-Learning algorithm \cite{Barber2012} increase.
-However, the correlation between payoffs $\Gamma$, which measures how cooperative or competitive a game is, does not affect the stability of the system.
-In addition, we find that regardless of the choice of these parameters, the likelihood of unstable behaviours increases as the number of players $p$ in the game increase.
+Through our analysis and experiments we find that likelihood of
+displaying unstable dynamics increases as the \textit{step length}
+$\alpha$ and \textit{intensity of choice} $\tau$ parameters in the
+Q-Learning algorithm
+%\cite{Barber2012}
+increase. However, the
+correlation $\Gamma$ between payoffs, which measures how cooperative
+or competitive a game is, does not affect the stability of the
+system. In addition, we find that regardless of the choice of these
+parameters, the likelihood of unstable behaviours increases as the
+number  $p$ of players in the game increases.
 
@@
 
+\subsection{Rescaling of Variables}
+
 Our first point of call is to extend the dynamics of Tuyls et al.~in
@@
 generating functional is given as \cite{Mezard1986}
-
-\begin{equation}
-	Z = \int D[\Vec{x}] \prod_i \delta(\textit{equation of motion}_i) exp(i
-	\int dt[x_i(t) \psi_i(t)]), 
-\end{equation}
-
+%
+\begin{eqnarray}
+	Z  =  \int D[\Vec{x}] \prod_i \delta(\textit{equation of
+          motion}_i) exp(i \int dt[x_i(t) \psi_i(t)])
+\end{eqnarray}
+%
 where the equations of motion are the Lagrange equations of motion
@@
 	\times \\ exp(i \sum_{i, \mu}
-	\int dt[\xmu{i} \psi^\mu_i(t)]),
+	\int dt[\xmu{i} \psi^\mu_i(t)])
 \end{split}
@@
 %
-
 \begin{equation}
@@
 \end{equation}
-
-In which
+%
+in which
 %
@@
 By taking this average (Sec. S2.3), we obtain the \textit{effective dynamics}
-
-\begin{equation}
+%
+\begin{eqnarray}
     \label{eqn::EffectiveDynamics}
-    \begin{split}
-            \frac{1}{x} \frac{d}{dt} x(t) = \alpha^2 \ttau^2 \Gamma \int dt' \left [G(t, t')C^{p - 2}(t, t') x(t') \right ]\\ + \sqrt{2} \alpha \ttau \eta_1(t) + \sqrt{2} \alpha \htau \eta_0(t) + \talpha \rho(t),
-    \end{split}
-\end{equation}
-
+%    \begin{split}
+            \frac{1}{x} \frac{d}{dt} x(t) & = & \alpha^2 \ttau^2 \Gamma \int dt' \left [G(t, t')C^{p - 2}(t, t') x(t') \right ] \nonumber \\ && + \sqrt{2} \alpha \ttau \eta_1(t) + \sqrt{2} \alpha \htau \eta_0(t) + \talpha \rho(t),
+%    \end{split}
+\end{eqnarray}
+%
 in which we have assumed that all players' actions are independent and drawn from the same initial distribution (i.i.d)
@@
 We first find a fixed point $\xfixed$ of (\ref{eqn::EffectiveDynamics}) by letting $\dot{x}(t)= 0$. This yields the expression 
-
-\small{
-\begin{eqnarray}
+%
+%\small{
+\begin{equation}
 %    \begin{split}
@@
 %    \end{split}
-\end{eqnarray}
-}
+\end{equation}
+%}
 %
@@
 perturbations, we arrive at the dynamics
-
+%
 \begin{eqnarray}
@@
 behaviour at $\omega = 0$. After some manipulation (Sec. S4), this gives
-
+%
 \begin{equation}
-\begin{split}
-        \mathbb{E}[|\mathcal{X}(\omega = 0)|^2] = \frac{1}{\left[ (-\alpha^2 \ttau^2 \Gamma q^{p-2} \chi)^2 - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2}\right]} \\
-\end{split}
+%\begin{split}
+        \mathbb{E}[|\mathcal{X}(\omega = 0)|^2] = \frac{1}{\left[ (-\alpha^2 \ttau^2 \Gamma q^{p-2} \chi)^2 - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2}\right]} 
+%\end{split}
 \end{equation}
@@
 As the left hand side of this equation must be greater than zero, we arrive at the condition that, at a fixed point, the long term perturbations must satisfy
-
+%
 \begin{equation}
@@
 We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
-
-\begin{equation*}
-    \begin{split}
-        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
-        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
-        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
-    \end{split}
-\end{equation*}
+%
+\begin{eqnarray*}
+%    \begin{split}
+        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
+        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
+        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+%    \end{split}
+\end{eqnarray*}
 
@@
 
-We interpret (\ref{eqn::Final}), for given parameters, by determining how close the right hand side is to the stability boundary (i.e., how close the value is to zero).
-A choice of parameters which evaluates close to the stability boundary has a higher chance (by the analytic error) of being convergent than one which lies further from the boundary.
-Therefore, the heat-maps in Figure \ref{fig:theory} should be considered to show the probability of convergence for a choice of $(\alpha, \Gamma)$.
-Lighter regions denote a higher probability of convergence whereas darker regions are those whose values are further from zero and therefore show a lower probability of convergence.
+We interpret (\ref{eqn::Final}), for given parameters, by determining
+how close the right hand side is to the stability boundary (i.e., how
+close the value is to zero). A choice of parameters which evaluates
+close to the stability boundary has a higher chance (by the analytic
+error) of being convergent than one which lies further from the
+boundary. Therefore, the heat-maps in Figure \ref{fig:theory} should
+be considered to show the probability of convergence for a choice of
+$(\alpha, \Gamma)$. Lighter regions denote a higher probability of
+convergence whereas darker regions are those whose values are further
+from zero and therefore show a lower probability of convergence.
 
@@
 \paragraph{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$. The choice of $\Gamma$
-makes almost no difference in the evaluation of (\ref{eqn::Final}).
-We anticipate that this is due to the restriction of $\Gamma$ to be in the range $[-1, 0]$.
-In this range, the scaling effect of $\Gamma^2$ is dominated by the $\alpha^4$ and $\tau^4$ terms which appear in (\ref{eqn::Final}).
+makes almost no difference in the evaluation of (\ref{eqn::Final}). We
+anticipate that this is due to the restriction of $\Gamma$ to be in
+the range $[-1, 0]$. In this range, the scaling effect of $\Gamma^2$
+is dominated by the $\alpha^4$ and $\tau^4$ terms which appear in
+(\ref{eqn::Final}).
 
@@
     \centering
-    \includegraphics[width = \linewidth]{Figures/pVariance.png}
+    \includegraphics[width = .75\linewidth]{Figures/pVariance.png}
     \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$.
@@
 \begin{figure}[t]
-    \includegraphics[width = \linewidth, center]{Figures/pVarianceExpt.png}
+    \includegraphics[width = .75\linewidth, center]{Figures/pVarianceExpt.png}
     \caption{Variation $V(t)$ about a fixed point as $p$ ranges from 2 - 6.
@@
 At the end of this second period, the variance of the actions are calculated as
-
+%
 \begin{equation*}
@@
 
+\newpage
+
 \bibliographystyle{ACM-Reference-Format} 

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

@@
 
-\subsection{Related Work}
+\subsection*{Related Work}
 
@@
 equilibrium and, if so, the probabilities with which strategies are
-played in this equilibrium (see \cite{ShohamMultiagentFoundations}
-for an excellent introduction to the replicator dynamics).
-
-Analyses have been performed from the point of view of the replicator
-dynamic towards the various types of behaviours that can emerge from
+played in this equilibrium \cite{ShohamMultiagentFoundations}.
+%for an excellent introduction to the replicator dynamics).
+
+Analyses have been performed from the perspective of the replicator
+dynamic w.r.t.~the various types of behaviours that can emerge from
 iterated games. Such games are considered imperfect, in that agents
@@
 based on experience \cite{Galla2011}. \cite{Imhof2005} presents the
-observation that, in the game of Prisoner's Dilemma, cyclic behaviour
+observation that, in the Prisoner's Dilemma, cyclic behaviour
 emerges in which the optimal strategy cycles across defection,
@@
 the system. In the absence of memory loss, the learning converges to
-the NE as expected.However, as this parameter is increased, the
-stability of the NE is removed and other stable points are created.
-
-Taking the notion of parameter dependence even further, \cite{Galla2013}
-describes an analysis of two-person iterated games in which the
+the NE as expected.
+%However, as this parameter is increased, the stability of the NE is
+%removed and other stable points are created.
+
+Taking the notion of parameter dependence further, \cite{Galla2013}
+describes an analysis of two-player iterated games in which the
 players learn using \textit{experience weighted attraction} (EWA), a
@@
 economics \cite{Camerer2009}. Through numerical simulations, the
-authors were able to show that the emergence of chaos and cycles is
-dependent on the choice of parameters (see \cite{Strogatz2000} for
-details on chaotic and periodic motion). A rigorous theoretical
-analysis of the replicator dynamic corresponding to EWA, which applies
-the techniques in \cite{Opper1992}, presented a method for
-characterising the regions in parameter space in which a game is
-likely to converge, exhibit chaos or limit cycles. More recently, the
-same authors presented an extended study in \cite{Sanders2018}, in which
-this analysis was extended towards a generic $p$-player game, which
-showed that chaotic dynamics are more likely to be observed as the
-number of players \textit{p} increases. By contrast to the present work, \cite{Barber2012} focuses on the analysis of the EWA algorithm, while we consider the Q-Learning \cite{Barber2012} algorithm.
+authors are able to show that the emergence of chaos and cycles is
+dependent on the choice of parameters.
+%(see \cite{Strogatz2000} for
+%details on chaotic and periodic motion).
+A rigorous theoretical analysis of the replicator dynamic
+corresponding to EWA, which applies the techniques in
+\cite{Opper1992}, results in a method for characterising the regions
+in parameter space in which a game is likely to converge, exhibit
+chaos or limit cycles. More recently, the same authors presented an
+extended study in \cite{Sanders2018}, in which the same analysis is
+applied to generic $p$-player games, which showed that chaotic
+dynamics are more likely to be observed as the number $p$ of players
+increases. Differently from this line, we here consider 
+%By contrast to the present work, \cite{Barber2012} focuses
+%on the analysis of the EWA algorithm, while we consider
+ Q-Learning \cite{Barber2012}, which is one of the most popular
+ algorithms in RL.
 
@@
 and, in fact, is rare. It would therefore be fruitful to bring these
-analyses from EGT to better understand Reinforcement Learning from an
+analyses from EGT to better understand reinforcement learning from an
 AI perspective.
@@
 In \cite{Tuyls2006AnGames}, the authors are able to derive a relation
-between Q-Learning (see \cite{Barber2012}) and the replicator
+between Q-Learning
+%(see \cite{Barber2012})
+and the replicator
 dynamic. In doing so, the authors present an evolutionary model which
 accurately predicts the dynamics of Q-Learning. This sprung forward a
-vast array of literature which perform similar derivations for various
-reinforcement learning algorithms (see \cite{Bloembergen2015} for an
-excellent literature review). In particular it should be noted that
+vast array of literature which performs similar derivations for various
+RL algorithms \cite{Bloembergen2015}.
+%for an
+%excellent literature review).
+In particular,
+%it should be noted that
 many of these studies focus on normal form games, in which the payoff
@@
 %though this is restricted to 2 state games.
-Similarly, \cite{Galstyan2013}, extends the work in
+Similarly, \cite{Galstyan2013} extends the work in
 \cite{Tuyls2006AnGames} towards games with continuous action
-spaces. Most recently, \cite{Hu2019} considers Q-learning in the
+spaces. More recently, \cite{Hu2019} considers Q-learning in the
 mean-field limit, in which the strategies of populations of agents are
@@
 
-The relation between RL and the replicator dynamic allows for the
-assumption of convergence in reinforcement learning to be lifted and
-instead for the emergence of more complex behaviour to be examined. In
-particular, this study aims to perform a similar analysis to that in
-\cite{Sanders2018} and establish the regions in parameter space in
-which Q-Learning converges to stable fixed points and where the
-learning is unstable.
-In doing so, we extend the dynamics considered by Tuyls et al.
-towards a general $p$-player scenario, rather than only two players, thereby allowing an analysis of how the number of players in a game affects its stability.
-To the best of our knowledge, no such work
-exists in this context.
+The relation between reinforcement learning and the replicator dynamic
+allows for the assumption of convergence in RL to be lifted and
+instead for the emergence of more complex behaviours to be
+examined. In particular, this study aims to perform an analysis
+similarly to \cite{Sanders2018} and establish the regions in parameter
+space in which Q-Learning converges to stable fixed points.
+%and where the learning is unstable.
+In doing so, we extend the dynamics considered by Tuyls et al.~to
+a general $p$-player setting, rather than two players only, thereby
+allowing an analysis of how the number of players in a game affects
+its stability.
+%To the best of our knowledge, this is the first work exists in
+%this context.
 
@@
     \centering
-    \includegraphics[width = \linewidth]{Figures/DynamicalBehaviours.png}
+    \includegraphics[width = .85\linewidth]{Figures/DynamicalBehaviours.png}
     \caption{Evaluation of (\label{fig::DynamicalBehaviours} Different types of dynamical behaviour

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Reduced length

@@
 of multi-agent systems whose behaviour is inter-dependent, it is
-desirable that the system be such that the game convergence to a
+desirable that the system be such that the game converges to a
 stable equilibrium. Without this, it is inherently impossible to
@@
 \begin{enumerate}
-    \item There is a finite set of agent, though its size $p$ can be
+    \item There is a finite set of agents, though its size $p$ can be
       arbitrarily large.
@@
 its stability.
-%To the best of our knowledge, this is the first work exists in
-%this context.
 
@@
     \centering
-    \includegraphics[width = .85\linewidth]{Figures/DynamicalBehaviours.png}
-    \caption{Evaluation of (\label{fig::DynamicalBehaviours} Different types of dynamical behaviour
+    \includegraphics[width = \linewidth]{Figures/DynamicalBehaviours.png}
+    \caption{Different types of dynamical behaviour
        displayed
@@
         Convergence
-        to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
-        that all trajectories, regardless of initialisation, will converge to this point. (Top Right) Limit Cycle, the trajectories converge to cyclic behaviour (Bottom)
+        to a unique fixed point at the point (1, 1). (Top Right) Limit Cycle, the trajectories converge to cyclic behaviour (Bottom)
         Chaotic behaviour, here small deviations in the initial conditions can grow
@@
 Sec. S2.2 for further details). Accordingly we choose
-scaled variables (denoted with a tilde) as
+scaled variables (denoted with a tilde or hat) as
 %
@@
         \xmu{i}{\mu} & = & \frac{\txmu{i}{\mu}}{N} \\
-        \talpha & = & \frac{\alpha}{N} \\
-        \ttau & = & N^{-(p-1)/2} \tau \\
-        \htau & = & N^{-p/2} \tau.
+        \talpha & = & \frac{\alpha}{N}, \: 
+        \ttau  =  N^{-(p-1)/2} \tau, \:
+        \htau  =  N^{-p/2} \tau.
 %    \end{split}
@@
 evolves (in our case these variables are the payoff elements). The
-generating functional is given as \cite{Mezard1986}
-%
-\begin{eqnarray}
-	Z  =  \int D[\Vec{x}] \prod_i \delta(\textit{equation of
-          motion}_i) exp(i \int dt[x_i(t) \psi_i(t)])
-\end{eqnarray}
-%
-where the equations of motion are the Lagrange equations of motion
-given in ( \ref{eqn::scaledEOM}) and the fields $\Vec{\psi_i(t)}$ and
-$\Vec{\phi_i(t)}$ will be set to zero at the end of the
-calculation. $\delta$ denotes the Dirac delta function. Substituting
-for our equation of motion yields
-%
+generating functional for the equation of motion (\ref{eqn::scaledEOM}) is given as \cite{Mezard1986}
+
 {\small
@@
 	\times \\ exp(i \sum_{i, \mu}
-	\int dt[\xmu{i} \psi^\mu_i(t)])
+	\int dt[\xmu{i} \psi^\mu_i(t)]),
 \end{split}
@@
 }
+where the `generating fields' \cite{Coolen2005} $\Vec{\psi_i(t)}$ and
+$\Vec{\phi_i(t)}$ will be set to zero at the end of the
+calculation.
+
 The last two exponentials contain the payoffs of the game.
 These are randomly generated using a multi-variate gaussian and then held fixed for the rest of the game.
-As such these comprise the aforementioned 'quenched disorder'.
+As such these comprise the aforementioned `quenched disorder'.
 We will average over this quenched disorder (and therefore average over all possible realisations of payoff matrices) using the mean and covariance expressions given in (\ref{eqn::Payoffs}).
@@
 \eonepert$.  If we consider only the terms which are linear in these
-perturbations, we arrive at the dynamics
+perturbations, we arrive at 
 %
@@
 \subsection{Discussion}
-
-\begin{figure}[t]
-    \includegraphics[width = 1.2 \linewidth, center]{Figures/Theory.png}
-    \caption{Evaluation of (\ref{eqn::Final}) over a range of $\alpha$ and $\Gamma$ values.
-Ligher regions indicate where (\ref{eqn::Final}) is close to zero (i.e.
-close to the stability boundary) whilst darker regions are further away.
-We vary $\alpha$ in the range $[0.01, 0.05]$ and $\Gamma$ in the range $[-1, 0]$.
-$\tau = 0.05$.
-(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 5$, (Bottom Left) $p = 2, N = 20$, (Bottom Right) $p=3, N = 2$.}
-    \label{fig:theory}
-\end{figure}
 
@@
 \begin{figure}[t]
+    \includegraphics[width = 1.2 \linewidth, center]{Figures/Theory.png}
+    \caption{Evaluation of (\ref{eqn::Final}) over a range of $\alpha$ and $\Gamma$ values.
+Ligher regions indicate where (\ref{eqn::Final}) is close to zero (i.e.
+close to the stability boundary) whilst darker regions are further away.
+We vary $\alpha$ in the range $[0.01, 0.05]$ and $\Gamma$ in the range $[-1, 0]$.
+$\tau = 0.05$.
+(Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 5$, (Bottom Left) $p = 2, N = 20$, (Bottom Right) $p=3, N = 2$.}
+    \label{fig:theory}
+\end{figure}
+
+\begin{figure}[t]
     \centering
@@
 \begin{figure}[t]
-    \includegraphics[width = 0.75 \linewidth, center]{Figures/alphavar5e2.png}
+    \includegraphics[width =  \linewidth, center]{Figures/alphavar5e2.png}
     \caption{The trajectories of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$. (Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
@@
 In the left figure, we choose $\alpha = 0.01$ whilst in the right we choose $\alpha = 0.05$.
-This gives a qualitative assessment of the behaviour at both extremes parameters considered.
 We note that the typical behaviour of the system is that the system first moves towards a fixed point and then varies in a pseudo-random manner within a vicinity of the fixed point.
@@
 the safe convergence of learning.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 parameters in such a way that convergence to a (possibly unique) fixed
-point is expected. In addition we noted that one of the conclusions of
+point can be expected. In addition we noted that one of the conclusions of
 our study is that convergence to a unique fixed point is rare in
@@
 
-The present work represents a first step towards considering the stability
-of multi-agent reinforcement learning and focuses on the limiting case
-of stateless normal-form games played by homogeneous agents. As
+% The present work represents a first step towards considering the stability
+% of multi-agent reinforcement learning and focuses on the limiting case
+% of stateless normal-form games played by homogeneous agents.
+As
 research into the dynamics of RL algorithms

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

--- 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-We note that the numerical experiments confirm the predictions suggested by the analytic results shown in Figure \ref{sec::Theory}.
-We notice that convergence occurs almost only for low values of $\alpha$.
-This observation remains as we increase the value of $N$.
-As noted, the analytic result over-estimates the region of instability due to the assumptions of $N \rightarrow \infty$ and $\frac{1}{p-1} << 2$ made during the derivation.
-Remaining discrepancies are partially due to the aforementioned approximation in the calculation of $q$, $\chi$ and the fact that the analytic result considers a continuous time approximation of the expected behaviour of Q-Learning.
-We expect that testing over a greater number of payoff realisations and initial conditions will yield a more representative assessment of the average behaviour of Q-Learning.
-However, running these experiments is a computationally expensive procedure: for $p$ players and $N$ actions we require operations on $p$ matrices with $N^{p}$ elements.
-As such, due to a reduced availability of computational facilities, a large scale averaging was not possible.
-
-However, due to the abundance of non-convergent behaviour, shown by the dark regions in Figure \ref{fig:NumericalExperiments} other than at low values of $\alpha, \tau$, we can conclude that the implications 1, 2 are verified.
-Indeed implications 3 and 4 are also verified as the proportion of games converged decrease monotonically with $\alpha, \tau$, but there does not appear to be any discernible dependence on $\Gamma$.
-Finally, we can conclude that implication 5 is verified by comparing Figures \ref{fig:pvariation} and \ref{fig:pVarianceExpt}.
-It is clear that the instability of the system increases monotonically with $p$.
-A point to note is that Figure \ref{fig:pVarianceExpt} shows a logarithmic dependence of the instability on $p$, whilst Figure \ref{fig:pvariation} suggests that the dependence should be exponential.
-Due to the limited range of $p$ that was used to generate Figure \ref{fig:pVarianceExpt}, it cannot yet be concluded that the dependence on $p$ is logarithmic.
-However, the important result is that the unstable behaviour increases, regardless of parameter choice as $p$ increases, which is corroborated by both theory and experiment.
-This phenomenon was referred to by Sanders et.
-al as `the prevalence of chaotic dynamics in games with many players' \cite{Sanders2018}.
-
-A point which we wish to discuss here is the difference in the result found w.r.t.~\cite{Sanders2018}, which considered the stability of \textit{Experience Weighted Attraction} (EWA).
-Namely, Sanders et al.~found that convergence is seen for higher values of $\alpha$, whereas lower values give rise to chaos, the opposite of what is found here.
-The reason for this can be seen in the update equation of Q-Learning (\ref{eqn::Qupdate}), whereby
-smaller values of $\alpha$ result in the agent placing a lower weight on the reward received at each step.
-As such, lower values of $\alpha$ result in the agent taking more conservative steps and yields a higher probability of convergence.
-In contrast, the update for EWA does not discount the reward received at all and, instead, only discounts the previous knowledge of the Q-value based on higher choices of $\alpha$.
-In essence, the difference is the fact that Q-Learning discounts new information by a factor of $\alpha$, whilst EWA does not.
-Yet, the difference in stability caused by this change is significant.
-This highlights the importance of performing analyses such as the present work; it allows for a method to analytically compare the difference between learning algorithms and, for practitioners, ensure that the appropriate algorithm is chosen for the parameters of their specific task.
+We note that the numerical experiments confirm the predictions
+suggested by the analytic results in Figure
+\ref{sec::Theory}. We notice that convergence occurs almost only for
+low values of $\alpha$. This observation remains as we increase the
+value of $N$. As noted, the analytic result over-estimates the region
+of instability due to the assumptions of $N \rightarrow \infty$ and
+$\frac{1}{p-1} << 2$ made during the derivation. Remaining
+discrepancies are partially due to the aforementioned approximation in
+the calculation of $q$, $\chi$ and the fact that the analytic result
+considers a continuous time approximation of the expected behaviour of
+Q-Learning. We expect that testing over a greater number of payoff
+realisations and initial conditions will yield a more representative
+assessment of the average behaviour of Q-Learning. However, running
+these experiments is a computationally expensive procedure: for $p$
+players and $N$ actions we require operations on $p$ matrices with
+$N^{p}$ elements. As such, due to a reduced availability of
+computational facilities, a large scale averaging was not possible.
+
+However, due to the prevalence of non-convergent behaviour, shown by
+the dark regions in Figure \ref{fig:NumericalExperiments} other than
+at low values of $\alpha, \tau$, we conclude that implications (1),
+(2) are verified. Indeed, implication (3) and (4) are also verified as
+the proportion of games converged decrease monotonically with
+$\alpha$, $\tau$, but there does not appear to be any discernible
+dependence on $\Gamma$. Finally, we can conclude that implication 5 is
+verified by comparing Figures \ref{fig:pvariation} and
+\ref{fig:pVarianceExpt}. It is clear that the instability of the
+system increases monotonically with $p$. A point to note is that
+Figure \ref{fig:pVarianceExpt} shows a logarithmic dependence of the
+instability on $p$, whilst Figure \ref{fig:pvariation} suggests that
+the dependence should be exponential. Due to the limited range of $p$
+that was used to generate Figure \ref{fig:pVarianceExpt}, it cannot
+yet be concluded that the dependence on $p$ is logarithmic. However,
+the key point is that, as $p$ increases, the unstable behaviour
+increases, regardless of parameter choice, which is corroborated by
+both theory and experiments. This phenomenon was referred to in
+\cite{Sanders2018}
+%by Sanders et. al
+as `the prevalence of chaotic dynamics in games with many
+players'.
+
+A point which we wish to discuss here is the difference in the result
+found w.r.t.~\cite{Sanders2018}, which considered the stability of
+\textit{experience weighted attraction} (EWA). Namely, Sanders et
+al.~found that convergence is seen for higher values of $\alpha$,
+whereas lower values give rise to chaos, the opposite of what is found
+here. The reason for this can be seen in the update equation of
+Q-Learning (\ref{eqn::Qupdate}), whereby smaller values of $\alpha$
+result in the agent placing a lower weight on the reward received at
+each step. As such, lower values of $\alpha$ result in the agent
+taking more conservative steps and yields a higher probability of
+convergence. In contrast, the update for EWA does not discount the
+reward received at all and, instead, only discounts the previous
+knowledge of the Q-value based on higher choices of $\alpha$. In
+essence, the difference is the fact that Q-Learning discounts new
+information by a factor of $\alpha$, whilst EWA does not. Yet, the
+difference in stability caused by this change is significant. This
+highlights the importance of performing analyses such as the present
+work; it allows for a method to analytically compare the difference
+between learning algorithms and, for practitioners, ensure that the
+appropriate algorithm is chosen for the parameters of their specific
+task.
 

### 2020-10-19 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py
Updated Two Player Code

@@ -9,7 +9,7 @@ gamma = .1
 Gamma = 0.1
 tau = 5e-2
 
-nActions = 5
+nActions = 2
 t0 = 500
 
 initnSim = 15

### 2020-10-19 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex

@@
 \textit{experience weighted attraction} (EWA). Namely, Sanders et
-al.~found that convergence is seen for higher values of $\alpha$,
+al.~observe that convergence is seen for higher values of $\alpha$,
 whereas lower values give rise to chaos, the opposite of what is found
-here. The reason for this can be seen in the update equation of
-Q-Learning (\ref{eqn::Qupdate}), whereby smaller values of $\alpha$
-result in the agent placing a lower weight on the reward received at
-each step. As such, lower values of $\alpha$ result in the agent
-taking more conservative steps and yields a higher probability of
-convergence. In contrast, the update for EWA does not discount the
-reward received at all and, instead, only discounts the previous
+here. The reason for this can be seen in the update equation
+(\ref{eqn::Qupdate}) for Q-Learning, whereby smaller values of
+$\alpha$ result in the agent placing a lower weight on the reward
+received at each step. As such, lower values of $\alpha$ result in the
+agent taking more conservative steps and yields a higher probability
+of convergence. In contrast, the update for EWA does not discount the
+reward received and, instead, only discounts the previous
 knowledge of the Q-value based on higher choices of $\alpha$. In
@@
 work; it allows for a method to analytically compare the difference
-between learning algorithms and, for practitioners, ensure that the
+between learning algorithms and, for practitioners, to ensure that the
 appropriate algorithm is chosen for the parameters of their specific

### 2020-11-09 Documents/ChaoticDynamics/Characterisation of Dynamics/main.tex
Added Research on Network Games

--- 2020-06-03 Documents/ChaoticDynamics/WriteUp.tex
@@
 \documentclass{article}
+\usepackage[margin = 2cm]{geometry}
 
-\usepackage[margin=2cm]{geometry}
-\usepackage{amsmath,amsfonts}
-\usepackage{mathtools}
-
-\usepackage{color}
-\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
-
-\title{Derivation Write Up}
+\title{Hello World}
 \author{Aamal Hussain}
+\date{}
 
 \begin{document}
-
     \maketitle
 
-\fb{the bibfile is missing.}
-
-	\section{Introduction} % (fold)
-	\label{sec:introduction}
-
-	\begin{itemize}
-			\item For use in Multi-Agent Reinforcement Learning
-			\item Requirement to get some desired behaviours out of the system (e.g. conforming to
-			predefined values or constraints)
-			\item For this, it is required that we are able to predict the outcome of the learning
-			behaviour
-			\item Work done on determining the dynamics of MARL gives an indication of what
-			solutions an algorithm will produce
-			\item We can use this, alongside stability theory, to understand the nature of the games
-			which result in stable behaviours and which result in chaotic behaviours.
-			\item Largely follows the work presented by Sanders et al. However, whilst they consider
-			EWA, we consider Q-Learning, which is more popular in RL communities.
-	\end{itemize}
-
-	\subsection{Problem Statement} % (fold)
-	\label{sub:problem_statement}
-
-	Given a particular learning algorithm and game, is it possible to determine whether the game is
-	likely to reach a unique fixed point or exhibit more complex behaviour? What are the factors
-	which affect this resulting behaviour?
-
-	% subsection problem_statement (end)
-
-	\subsection{Objectives and Scope} % (fold)
-	\label{sub:objectives_and_scope}
-
-	Analyse the stability of Multiagent Q-Learning on iterated games.
-
-	Assumptions:
-
-	\begin{itemize}
-		\item Focuses on stateless games
-		\item Homogeneous agents
-		\item Discrete action spaces, with large number of actions.
-		\item Small, finite number of agents.
-	\end{itemize}
-
-	The work by Sanders et al. considers agents who have these same assumptions, but learn with a
-	reduced version of the Experience Weighted Attraction algorithm. For the Reinforcement Learning
-	community, it is of interest to consider the question of stability from the point of view of
-	agents who follow the popular Q-Learning algorithm.
-
- \fb{you might discuss in which way any of the points above differs from the relevant reference.}
-
-	% subsection objectives_and_scope (end)
-
-	% section introduction (end)
-
-	\section{Derivation} % (fold)
-	\label{sec:derivation}
-
-        \fb{it would be good to have a overall description of the goal of the derivation.}
-
-	We start with the two-agent Q-Learning dynamics as presented by Tuyls et al.
-
-	\begin{subequations}
-	\label{eqn::EOM}
-		\begin{equation}
-			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
-			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
-		\end{equation}
-		\begin{equation}
-			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
-			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
-		\end{equation}
-	\end{subequations}
-
-	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al.
-refer to these as the memory and intensity of choice parameters respectively.
-Agent 1 takes action i with probability $x_i$ while Agent 2 takes action j with probability $y_j$.
-If these actions are taken, the agents receive payoff $a_{ij}$ and $b_{ji}$ respectively.
-
-	\subsection{Rescaling of Variables} % (fold)
-	\label{sub:rescaling_of_variables}
-
-		In order to follow the conventions of spin glass
-                theory for the analysis of disordered systems, we
-                rescale the system so that the payoff matrix elements
-                are of order $N^{-1/2}$. The motivation for doing this
-                is that, along the way, we will take the limit of the
-                number of actions $N$ to infinity. However, doing this
-                will result in numerical underflow of the action
-                probabilities (i.e. the probability of each action
-                goes to zero). To compensate for this, we adjust the
-                system so that the sum of the probabilities add to
-                $N$. The scaling goes as follows:
-%
-	\begin{subequations}
-		\begin{equation}
-			a_{ij} = \sqrt{N} \tilde{a_{ij}}
-		\end{equation}
-		\begin{equation}
-			b_{ji} = \sqrt{N} \tilde{b_{ji}}
-		\end{equation}
-	\end{subequations}
-
-	We compensate for this change with
-	\begin{subequations}
-		\begin{equation}
-			x_{i} = \tilde{x_{i}}/N
-		\end{equation}
-		\begin{equation}
-			y_{i} = \tilde{y_i}/N.
-		\end{equation}
-	\end{subequations}
-
-	This gives the original equations as
-
-	\begin{subequations}
-	\label{eqn::scaledEOM}
-		\begin{equation}
-			\frac{\dot{\tilde{x_i}}(t)}{\tilde{x_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{a_
-			{ij}} 
-			\tilde{y_j} -
-			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{x_i} \tilde{a_{ij}} \tilde{y_j}
-			+ \tilde{\alpha} \sum_j \tilde{x_j} ln(\frac{\tilde{x_j}}{\tilde{x_i}}) 
-		\end{equation}
-		\begin{equation}
-			\frac{\dot{\tilde{y_i}}(t)}{\tilde{y_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{b_
-			{ij}} 
-			\tilde{x_j} -
-			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{y_i} \tilde{b_{ij}} \tilde{x_j}
-			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}).
-		\end{equation}
-	\end{subequations}
-
-	The need for the factor of $\frac{1}{\sqrt{N}}$ is to follow
-        the conventions of the saddle point method of
-        integration. This will become clear after taking the
-        expectation of the generating functional. Note that we may
-        drop the notation on time dependence for $x$ and $y$. However,
-        these will always be functions of time. Henceforth, we shall
-        not write the tildes on $x, y, a_{ij}, b_{ij}$. We shall also
-        abbreviate the final term as
-%
-	\begin{equation*}
-		\rho_{x, i}(t) = \sum_j x_j ln(\frac{x_j}{x_i}) 
-	\end{equation*}
-
-	% subsection rescaling_of_variables (end)
-
-	\subsection{Generating Functional} % (fold)
-	\label{sub:generating_functional}
-
-	The generating functional allows us to take a path integral over all possible realisations of
-	learning \cite{SpinGlassTheory}. This is given as:
-
-	\begin{equation}
-		Z = \int D[\Vec{x}, \Vec{y}] \prod_i \delta(\textit{equation of motion}_i) exp(i
-		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t)]), 
-	\end{equation}
-
-	where the equations of motion are the Lagrange equations of motion given in (
-	\ref{eqn::scaledEOM}) andSince
-	the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
-	calculation. $\delta$ denotes the Dirac delta function. We write this in its Fourier
-	representation, which yields
-
-	\begin{equation}
-		\begin{split}
-	\label{eqn::generatingfunctional}
-		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i \sum_i \int dt[\hat{x}_i
-		(\frac{\dot{x_i}(t)}{x_i(t)} - \alpha \tilde{\tau} \sum_{j} a_
-			{ij} 
-			y_j +
-			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j
-			- \tilde{\alpha} \rho_{x, i}(t) + h_{x, i}(t))]) 
-			\\
-			\times exp(i \sum_i \int dt[\hat{y}_i
-		(\frac{\dot{y_i}(t)}{y_i(t)} - \alpha \tilde{\tau} \sum_{j} b_
-			{ij} 
-			x_j +
-			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j
-			- \tilde{\alpha} \rho_{y, i}(t)+ h_{y, i}(t))])\\
-			\times exp(i \sum_i
-		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))]),
-	\end{split}
-	\end{equation}
-
-	Here, the terms $a_{ij}, b_{ij}$ are the payoffs in the game and the term $h$ denotes a field
-	which will be set to zero at the end of the calculation. We recall that these are randomly
-	generated using a multivariate gaussian and then held fixed for the rest of the game. We call
-	this 'quenched disorder'. Isolating these terms allows us to rearrange the above as
-
-	\begin{equation}
-	\begin{split}
-	\label{eqn::moveddisorder}
-		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
-		\sum_i \int dt[\hat{x}_i
-		(\frac{\dot{x_i}(t)}{x_i(t)}
-			- \tilde{\alpha} \rho_{x, i}(t)+ h_{x, i}(t))]) 
-			\\
-			\times exp(i \sum_i \int dt[\hat{y}_i
-		(\frac{\dot{y_i}(t)}{y_i(t)} 
-			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
-			\times exp(i \sum_i
-		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))])\\
-		\times exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
-			{ij} 
-			y_j +
-			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
-			\alpha 
-			\tilde{\tau} \sum_{j} b_
-			{ij} 
-			x_j +
-			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
-	\end{split}
-	\end{equation}
-	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
-	that we moved the term \fb{which one exactly?} containing the quenched disorder into a separate exponential. Since our
-	aim is to take an average over all possible realisations of this disorder, we will only need to
-	focus on the last exponential which we rewrite as
-
-	\begin{equation}
-		Q = exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
-			{ij} 
-			y_j +
-			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
-			\alpha 
-			\tilde{\tau} \sum_{j} b_
-			{ij} 
-			x_j +
-			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
-	\end{equation}
-
-	We will then separate the terms so that like sums are paired together
-
-	\begin{equation}
-	\begin{split}
-		Q = exp(-i \alpha \tilde{\tau} \sum_{ij} \int dt[\hat{x}_i a_{ij} y_j + \hat{y}_j b_
-			{ji} 
-			x_i])
-			\times
-			exp(i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{ijk} \int dt[\hat{x}_i x_j
-			a_{jk} y_k + \hat{y}_i y_k b_{kj} x_j])
-	\end{split}
-	\end{equation}
-
-	It should be noted that we have changed some of the subscripts on the terms. Since these terms
-	are all multiplied together and we sum over the subscripts, the letters we choose are of no
-	importance and we can exchange them freely \fb{perhaps some more justification might be helpful}. We will define both exponentials in $Q$ as $Q_1$ and
-	$Q_2$ respectively.
-
-	We are now ready to take the expectation of $Q$. To do this, we will exploit the fact that the
-	payoff elements are Gaussian distributed and use the identity \cite{QFTbook}
-
-	\begin{equation}
-	\label{eqn::expectationIdentity}
-		\int dz [e^{-A_2(z) + \Vec{b} \cdot \Vec{z}}] = (2 \pi)^{k/2} (det(A))^{-1/2} e^{\omega(b)},
-	\end{equation}
-
-	where
-
-	\begin{equation*}
-		\begin{split}
-			A_2(z) = 1/2 \sum_{ij} z_i A_{ij} z_j \\
-			\omega_2(z) = 1/2 \sum_{ij} b_i (A)^{-1}_{ij} b_j
-		\end{split}
-	\end{equation*}
-
-	\subsubsection{Expectation of $Q_1$} % (fold)
-	\label{ssub:expectation_of_Q1}
-
-	We can rewrite $Q_1$ as
-
-	\begin{equation*}
-		Q_1 = \prod_{ij} exp(\Vec{b} \cdot \Vec{z}),
-	\end{equation*}
-
-	where
-
-	\begin{equation*}
-		\begin{split}
-			b \coloneqq [-i \alpha \tilde{\tau} \int dt[\hat{x}_i y_j], -i \alpha \tilde{\tau} \int
-			dt[\hat{y}_j x_i]]^T \\
-			z \coloneqq [a_{ij}, b_{ji}]^T\\
-			A \coloneqq \Sigma^{-1}\\
-			\Sigma_{ij} \coloneqq Cov[z_i, z_j],
-		\end{split}
-	\end{equation*}
-
-	where $\Sigma$ is the covariance of $\Vec{z}$. We recall that the scaled system has
-	payoff elements chosen so that
-
-	\begin{equation*}
-		\begin{split}
-			\mathbb{E}[a_{ij}] = \mathbb{E}[b_{ji}] = 0\\
-			\mathbb{E}[a_{ij}^2] = \mathbb{E}[b_{ji}^2] = 1/N\\
-			\mathbb{E}[a_{ij} b_{ji}] = \Gamma /N.
-		\end{split}
-	\end{equation*}
-
-	Applying identity (\ref{eqn::expectationIdentity}) gives:
-
-	\begin{equation}
-	\begin{split}
-		\mathbb{E}[Q_1] = \prod_{ij} exp(- \alpha^2 \tilde{\tau}^2 \frac{1}{2N} \int dt dt'[
-		\hat{x}_i
-		(t) \hat{x}_i
-		(t') y_j(t) y_j(t') + \hat{y}_j(t) \hat{y_j}(t') x_i(t) x_i(t') \\ + \Gamma \hat{x}_i(t) 
-		{x}_i
-		(t') {y}_j(t) \hat{y}_j(t') + \Gamma \hat{y}_j(t) {y}_j(t') {x}_i(t) \hat{x}_i(t')]).
-	\end{split}
-	\end{equation}
-
-	% subsubsection expectation_of_Q1 (end)
-	% subsection generating_functional (end)
-
-	\subsubsection{Expectation of $Q_2$} % (fold)
-	\label{ssub:expectation_of_Q2}
-
-	We take a similar approach with the following definitions
-
-	\begin{equation*}
-		\begin{split}
-			b \coloneqq [i \tilde{\alpha} \tau \int dt[\hat{x}_i x_j y_k], i \tilde{\alpha} 
-			\tau
-			\int
-			dt[\hat{y}_i x_j y_k]]^T \\
-			z \coloneqq [a_{jk}, b_{kj}]^T\\
-			A \coloneqq \Sigma^{-1}\\
-			\Sigma_{ij} \coloneqq Cov[z_i, z_j],
-		\end{split}
-	\end{equation*}
-
-	% subsubsection expectation_of_Q2 (end)
-
-	Following the same procedure as for $Q_1$ yields
-
-	\begin{equation}
-	\begin{split}
-		\mathbb{E}[Q_2] = \prod_{ij} exp(- \tilde{\alpha}^2 \tau^2 \frac{1}{2N^2} \int dt dt'[
-		\hat{x}_i
-		(t) \hat{x}_i
-		(t') x_j(t) x_j(t') y_k(t) y_k(t') \\+ \hat{y}_i(t) \hat{y_i}(t') x_j(t) x_j(t') y_k(t)
-		y_k(t') \\ + \Gamma \hat{x}_i(t) \hat{y}_i(t')
-		{x}_j
-		(t) x_j{(t')} {y}_k(t) y_k(t') \\ + \Gamma \hat{y}_i(t) \hat{x}_i(t') {x}_j(t) {x}_j(t')
-		y_k(t) y_k(t')]).
-	\end{split}
-	\end{equation}
-
-	We now define the correlation functions
-
-		\begin{align*}
-C_x(t, t') &= N^{-1} \sum_i x_i(t) x_i(t') & C_y(t, t') &= N^{-1} \sum_i y_i(t) y_i(t')\\
-L_x(t, t') &= N^{-1} \sum_i \hat{x}_i(t) \hat{x}_i(t') & L_y(t, t') &= N^{-1} \sum_i \hat{y}_i(t) \hat{y}_i(t') \\
-K_x(t, t') &= N^{-1} \sum_i x_i(t) \hat{x}_i(t') & K_y(t, t') &= N^{-1} \sum_i y_i(t) \hat{y}_i(t')\\
-A_{xy}(t, t') &= N^{-1} \sum_i \hat{x}_i(t) \hat{y}_i(t').
-\end{align*}
-	% section derivation (end)
-
-We then rewrite $\mathbb{E}[Q]$ as
-
-\begin{equation}
-\begin{split}
-		\mathbb{E}[Q] = exp(- \alpha^2 \tilde{\tau}^2 \frac{N}{2} \int dt dt'[L_x(t, t')C_y(t, t')
-		+ L_y(t, t')C_x(t, t') + 2 \Gamma K_x(t, t') K_y(t', t)] \\
-	- \tilde{\alpha}^2 \tau^2 \frac{N}{2} \int dtdt' [L_x(t, t') C_x(t, t') C_y(t, t') + L_y(t, t')
-	C_x(t, t') C_y(t, t') \\ + \Gamma A_{xy}(t, t') C_x(t, t') C_y(t, t') + \Gamma A_{xy}(t', t) C_x
-	(t, t') C_y(t, t')] )
-\end{split}
-\end{equation}
-
-We can introduce these correlation functions into the expectation which gives
-
-\begin{equation}
-	\begin{split}
-		\mathbb{E}[Q] = \int D[C_x, \hat{C_x}, L_x, \hat{L_x}, K_x, 
-		\hat{K_x}, C_y, \hat{C_y}, L_y, \hat{L_y}, K_y, 
-		\hat{K_y}, A_{xy}, \hat{A}_{xy}] 
-		exp(N(\Psi, \Phi, \Lambda)),
-	\end{split}
-\end{equation}
-
-where
-\begin{equation}
-	\begin{split}
-	\Psi = i \int dtdt' [\hat{C}_x(t, t') C_x(t, t') + \hat{L}_x(t, t') L_x(t, t') + \hat{K}_x
-		(t, t') K_x(t, t') \\ + \hat{C}_y(t, t') C_y(t, t') + \hat{L}_y(t, t') L_y(t, t') + 
-		\hat{K}_y(t, t') K_y(t, t') + \hat{A}_{xy}(t, t') A_{xy}(t, t')]
-	\end{split}
-\end{equation}
-
-\begin{equation}
-	\begin{split}
-		\Phi = - \alpha^2 \tilde{\tau}^2 \frac{N}{2} \int dt dt'[L_x(t, t')C_y(t, t')
-		+ L_y(t, t')C_x(t, t') + 2 \Gamma K_x(t, t') K_y(t', t)] \\
-	- \tilde{\alpha}^2 \tau^2 \frac{N}{2} \int dtdt' [L_x(t, t') C_x(t, t') C_y(t, t') + L_y(t, t')
-	C_x(t, t') C_y(t, t') \\ + \Gamma A_{xy}(t, t') C_x(t, t') C_y(t, t') + \Gamma A_{xy}(t', t) C_x
-	(t, t') C_y(t, t')] 
-\end{split}
-\end{equation}
-
-\begin{equation}
-	\begin{split}
-		\Lambda = i \sum_i \int dt dt'[\hat{C}_x(t, t') x_i(t) x_i(t') + \hat{L}_x(t, t') \hat{x}_i
-		(t)\hat{x}_i(t') + \hat{K}_x(t, t') x_i(t) \hat{x}_i(t') \\ + \hat{C}_y(t, t') y_i(t) y_i
-		(t') +
-		\hat{L}_y(t, t') \hat{y}_i
-		(t)\hat{y}_i(t') + \hat{K}_y(t, t') y_i(t) \hat{y}_i(t') \\ 
-		+ \hat{A}_{xy}(t, t') \hat{x}_i(t) \hat{y}_i(t')].
-	\end{split}
-\end{equation}
-
-We insert this expectation back into the original generating functional which gives
-
-\begin{equation}
-	\begin{split}
-		\mathbb{E}[Z(\Vec{\psi}, \Vec{\phi})] = \int D[C_x, \hat{C_x}, L_x, \hat{L_x}, K_x, 
-		\hat{K_x}, C_y, \hat{C_y}, L_y, \hat{L_y}, K_y, 
-		\hat{K_y}, A_{xy}, \hat{A}_{xy}] 
-		exp(N(\Psi, \Phi, \Omega + (\mathcal{O}(N^{-1})))),
-	\end{split}
-\end{equation}
-
-where $\Omega$ includes all terms describing the time evolution of the system and is given by
-
-\begin{equation}
-	\begin{split}
-		\Omega = N^{-1} \sum_i log \int D[x_i, \hat{x}_i, y_i, \hat{y}_i] exp(i
-		\int dt[\hat{x}_i
-		(\frac{\dot{x_i}(t)}{x_i(t)}
-			- \tilde{\alpha} \rho_{x, i}(t) + h_{x, i}(t))]) 
-			\\
-		\times exp(i\int dt dt'[\hat{C}_x(t, t') x_i(t) x_i(t') + \hat{L}_x(t, t') \hat{x}_i
-		(t)\hat{x}_i(t') + \hat{K}_x(t, t') x_i(t) \hat{x}_i(t')])\\
-		\times exp(i \int dt[\hat{y}_i
-		(\frac{\dot{y_i}(t)}{y_i(t)} 
-			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
-		\times exp(i \int dt dt' [\hat{C}_y(t, t') y_i(t) y_i
-		(t') +
-		\hat{L}_y(t, t') \hat{y}_i
-		(t)\hat{y}_i(t') + \hat{K}_y(t, t') y_i(t) \hat{y}_i(t')])\\
-		\times exp(i \int dt dt'[\hat{A}_{xy}(t, t') \hat{x}_i(t) \hat{y}_i(t')]])
-			\times exp(i \sum_i
-		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))]).
-	\end{split}
-\end{equation}
-
-We will evaluate the path integral using the saddle point method for integration 
-\cite{saddlepoint}. In this method, we consider that the integration is dominated by the maximum of
-the function
-
-\begin{equation*}
-	f = \Psi + \Phi + \Omega,
-\end{equation*}
-
-and we take the limit as N extends to infinity. We therefore determine the relations which maximise
-this function. We find
-
-\begin{align*}
-	\frac{\partial f}{\partial C_x(t, t')} &\implies i \hat{C}_x(t, t') = \frac{\alpha^2 
-	\tilde{\tau}^2}{2} L_y(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(L_x(t, t')C_y(t, t') + L_y
-	(t, t')C_y(t, t') + 2\Gamma A_{xy}(t, t') C_y(t, t'))\\
-	\frac{\partial f}{\partial L_x(t, t')} &\implies i \hat{L}_x(t, t') = \frac{\alpha^2 
-	\tilde{\tau}^2}{2} C_y(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(C_x(t, t') C_y(t, t'))\\
-	\frac{\partial f}{\partial K_x(t, t')} &\implies i\hat{K}_x(t, t') = \alpha^2 
-	\tilde{\tau}^2 \Gamma K_y(t', t) \\
-	\frac{\partial f}{\partial C_y(t, t')} &\implies i \hat{C}_y(t, t') = \frac{\alpha^2 
-	\tilde{\tau}^2}{2} L_x(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(L_x(t, t')C_x(t, t') + L_y
-	(t, t')C_x(t, t') + 2\Gamma A_{xy}(t, t') C_x(t, t'))\\
-	\frac{\partial f}{\partial L_y(t, t')} &\implies i \hat{L}_y(t, t') = \frac{\alpha^2 
-	\tilde{\tau}^2}{2} C_x(t, t') + \frac{\tilde{\alpha}^2 \tau^2}{2}(C_x(t, t') C_y(t, t'))\\
-	\frac{\partial f}{\partial K_y(t, t')} &\implies i\hat{K}_y(t, t') = \alpha^2 
-	\tilde{\tau}^2 \Gamma K_x(t', t) \\
-	\frac{\partial f}{\partial A_{xy}(t, t')} &\implies i\hat{A}_{xy}(t, t') = \tilde{\alpha}^2
-	\tau^2 \Gamma C_x(t, t') C_y(t, t').
-\end{align*}
-
-Similarly,
-
-\begin{align*}
-	\frac{\partial f}{\partial \hat{C}_x(t, t')} &\implies C_x(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i \langle x_i(t) x_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \psi_i(t) \partial \psi_i (t')} \bigg|_{\Vec
-{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
-	\frac{\partial f}{\partial \hat{L}_x(t, t')} &\implies L_x(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i \langle \hat{x}_i(t) \hat{x}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial h_{x,i}(t) \partial h_{x, i} (t')} \bigg|_{\Vec
-{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
-	\frac{\partial f}{\partial \hat{K}_x(t, t')} &\implies K_x(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i \langle x_i(t) \hat{x}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \Vec{\psi}(t) \partial h_{x, i} (t')}
-\bigg|_{\Vec{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
-\frac{\partial f}{\partial \hat{C}_y(t, t')} &\implies C_y(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i \langle y_i(t) y_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \phi_i(t) \partial \phi_i (t')} \bigg|_{\Vec
-{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
-	\frac{\partial f}{\partial \hat{L}_y(t, t')} &\implies L_y(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i \langle \hat{y}_i(t) \hat{y}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial h_{y,i}(t) \partial h_{y, i} (t')} \bigg|_{\Vec
-{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
-	\frac{\partial f}{\partial \hat{K}_y(t, t')} &\implies K_y(t, t') = \lim_{N \rightarrow \infty}
-N^{-1} \sum_i \langle y_i(t) \hat{y}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \Vec{\phi}(t) \partial h_{x, i} (t')}
-\bigg|_{\Vec{\phi} = \Vec{\psi} = \Vec{h} = 0}\\
-	\frac{\partial f}{\partial \hat{A}_{xy}(t, t')} &\implies A_{xy}(t, t') = \lim_{N \rightarrow
-	\infty}
-N^{-1} \sum_i \langle \hat{x}_i(t) \hat{y}_i(t')\rangle _\Omega = -\lim_{N \rightarrow \infty} \sum_i
-\frac{\partial^2\mathbb{E}[Z(\psi, \phi)]}{\partial \partial h_{x, i} (t) \partial h_{y, i} (t')}
-\bigg|_{\Vec{\phi} = \Vec{\psi} = \Vec{h} = 0}.\\
-\end{align*}
-
-We implement these relations into the expression of $\Omega$, and make the assumption that all
-actions $i$ are independent and identically distributed (i.i.d.), which gives
-
-\begin{equation}
-	\begin{split}
-		\Omega =log \int D[x, \hat{x}, y, \hat{y}] exp(i
-		\int dt[\hat{x}(t)
-		(\frac{\dot{x}(t)}{x(t)}
-			- \tilde{\alpha} \rho_{x}(t))]) 
-			\\
-		\times exp(-\int dt dt'[\frac{1}{2} \alpha^2 \tilde{\tau}^2 C_y(t, t')\hat{x}(t)\hat{x}(t')
-		+ \frac{1}{2} \tilde{\alpha}^2 \tau^2 C_x(t, t')C_y(t, t')\hat{x}(t)\hat{x}(t') + i \alpha^2
-		\tilde{\tau}^2 \Gamma G_y(t', t) x(t) \hat{x}(t')])\\
-		\times exp(i \int dt[\hat{y}(t)
-		(\frac{\dot{y}(t)}{y(t)} - \tilde{\alpha} \rho_{y}(t))])\\
-		\times exp(-\int dt dt'[\frac{1}{2} \alpha^2 \tilde{\tau}^2 C_x(t, t')\hat{y}(t)\hat{y}(t')
-		+ \frac{1}{2} \tilde{\alpha}^2 \tau^2 C_x(t, t')C_y(t, t')\hat{y}(t)\hat{y}(t') + i \alpha^2
-		\tilde{\tau}^2 \Gamma G_x(t, t') y(t) \hat{y}(t')])\\
-		\times exp(-\int dt dt'[\tilde{\alpha}^2 \tau^2 \Gamma C_x(t, t') C_y(t, t') \hat{x}(t) 
-		\hat{y}
-		(t')]).
-	\end{split}
-\end{equation}
-
-Since this contains all of the information of the learning evolution, we consider $\Omega$ as an
-effective generating functional (and in fact we see that it has a similar structure to (
-\ref{sub:generating_functional}), without the existence of the fields $\psi, \phi$). In particular
-we recognise this as the generating functional of the 'effective dynamics' given as
-
-\begin{equation}
-	\begin{split}
-		\dot{x}(t) &= x(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_y(t, t')x(t')] + 
-		\tilde{\alpha}
-		\rho_x(t) + \alpha \tilde{\tau} \eta_x(t) + \tilde{\alpha} \tau \eta_x(t) \eta_y(t) +
-		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_x) \\
-		\dot{y}(t) &= y(t)(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'[G_x(t, t')y(t')] + 
-		\tilde{\alpha} \rho_y(t) +
-		\alpha \tilde{\tau} \eta_y(t) + \tilde{\alpha} \tau \eta_x(t) \eta_y(t)+ 
-		\sqrt{\Gamma} \tilde{\alpha} \tau \mu_y), \\
-	\end{split}
-\end{equation}
-
-with the self-consistency relations
-
-\begin{align}
-	G_x(t, t') &= \langle \frac{\delta x(t)}{\delta \eta_x(t')}\rangle  & G_y(t, t') &= \langle \frac{\delta y(t)}{\delta
-	\eta_y(t')}\rangle  \\
-	\langle \eta_x(t) \eta_x(t')\rangle  &= C_y(t, t') & \langle \eta_y(t) \eta_y(t')\rangle  &= C_x(t, t')\\
-	\langle \mu_x(t) \mu_y(t')\rangle  &= C_x(t, t') C_y(t, t') & \langle \mu_x(t) \mu_x(t')\rangle  &= \langle \mu_y(t) \mu_y(t')\rangle  = 0
-\end{align}
-
-\section{Stability Analysis} % (fold)
-\label{sec:stability_analysis}
-
-We are now in a position to take the effective dynamics, which describes the evolution of the
-learning dynamics after averaging over all possible realisations of the payoff elements, and
-determine the stability of the system at fixed points. We will follow the procedure laid out by
-Opper et al \cite{Opper}. First, we rewrite $x(t)$, $y(t)$ as perturbations about their fixed
-points. We will then analyse the stability of these fixed points.
-
-Let
-
-\begin{align}
-	x(t) = x^* + \hat{x}(t) \\
-	y(t) = y^* + \hat{y}(t) \\
-	\eta_x(t) = \eta_x^* + \hat{\nu}_x(t)\\
-	\eta_y(t) = \eta_y^* + \hat{\nu}_y(t)\\
-	\mu_x(t) = \mu_x^* + \hat{\delta}_x(t)\\
-	\mu_y(t) = \mu_y^* + \hat{\delta}_y(t),
-\end{align}
-
-where terms denoted by $\cdot^*$ are the values that are taken at the fixed point and terms denoted
-by $\hat{\cdot}$ refer to deviations from the fixed point. This is not to be confused with
-the conjugate variable notation that we used in the previous section. We assume that these
-perturbations arise from additive noise, $\xi(t)$, $\zeta(t)$, drawn from the unit normal
-distribution which are applied to the dynamics. Rewriting the dynamics with all of these
-considerations gives
-
-\begin{equation}
-	\begin{split}
-		\frac{d}{dt} (x^* + \hat{x}(t)) = (x^* + \hat{x}(t))(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'
-		[G_y(t, t')(x^* + \hat{x}(t'))] + \tilde{\alpha} \rho_x(t) + \alpha \tilde{\tau} (\eta_x^* + \hat{\nu}_x
-		(t)) \\ + \tilde{\alpha} \tau (\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t)) + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_x^* + \hat{\delta}_x(t)) + \xi(t)) \\
-		\frac{d}{dt} (y^* + \hat{y}(t)) = (y^* + \hat{y}(t))(\Gamma \alpha^2 \tilde{\tau}^2 \int dt'
-		[G_x(t, t')(y^* + \hat{y}(t'))] + \tilde{\alpha} \rho_y(t) + \alpha \tilde{\tau} (\eta_y^* + \hat{\nu}_y
-		(t)) \\ + \tilde{\alpha} \tau (\eta_x^* + \hat{\nu}_x(t)) (\eta_y^* + \hat{\nu}_y(t))
-		 + \sqrt{\Gamma} \tilde{\alpha} \tau (\mu_y^* + \hat{\delta}_y(t)) + \zeta(t)).
-	\end{split}
-\end{equation}
-
-Considering only terms which are linear in the deviations yields
-
-\begin{equation} 
-	\label{eqn::Linearisation}
-	\begin{split}
-	\frac{d}{dt} \hat{x}(t) = (x^* + \hat{x}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_x \right] \\
-	+ x^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_y(t - t') \hat{x}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_x(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_x(t) + \xi(t) \right]\\
-	\frac{d}{dt} \hat{y}(t) = (y^* + \hat{y}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_x(t - t') dt' + \tilde{\alpha} \rho_y^* + \alpha \tilde{\tau} \eta_y^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_y \right] \\
-	+ y^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_x(t - t') \hat{y}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_y(t) + \zeta(t) \right].\\
-	\end{split}
-\end{equation}
-
-If we consider the long term behaviour of the system near a stable fixed point, then $\hat{x}(t)$ goes to zero as $t \rightarrow \infty$.
-This yields the requirement that a fixed point $x^*$ must satisfy
-
-\begin{equation}
-	0 = x^* \left[\Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \sqrt{\Gamma} \tilde{\alpha} \tau \mu_x \right].
-\end{equation}
-
-The implication here is that the resulting value of $x^*$ can take two solutions.
-However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values.
-If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$.
-Numerical experiments will shed more light on the likelihood of convergence.
-If this ansatz turns out to be incorrect (i.e.
-we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.
-
-We continue to follow the method of Opper et al.
-by taking the Fourier transform of (\ref{eqn::Linearisation}).
-For both agents, the first term in square brackets is constant with respect to time and so will not affect the long term behaviour of the system.
-We can, therefore, ignore this and focus on the second term.
-For the sake of brevity, we will only write the equations for Agent 1 (i.e.
-for $x$), though the equations for y can be equivalently obtained.
-Taking the Fourier transform yields
-
-\begin{equation}
-	\left[ \frac{i \omega}{x^*} - \Gamma \alpha^2 \tilde{\tau}^2 \mathcal{G}_y(\omega)\right] \mathcal{X}(w) = \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega).
-\end{equation}
-
-Then,
-
-\begin{equation} \label{eqn::Transformed}
-	\left<[|\mathcal{X}(\omega)|^2 \right> = \left< | \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega) |^2 \right> \frac{1}{\left< |\mathcal{A}(\omega, x^*) |^2 \right>},
-\end{equation}
-
-where
-
-\begin{equation}
-	\mathcal{A}(\omega, x^*) = \frac{i \omega}{x^*} - \Gamma \alpha^2 \tilde{\tau}^2 \mathcal{G}_y(\omega)
-\end{equation}
-
-The behaviour of this line for $\omega = 0$ gives the long term behaviour of the system.
-By considering that, for a stable fixed point to exist, $\left<[|\mathcal{X}(\omega = 0)|^2 \right>$, we arrive at an expression for a stability line (i.e.
-the phase transition between the existence of stable fixed points and unstable behaviour).
-
-% section stability_analysis (end)
 \end{document}

### 2020-11-09 Documents/Network Games/ResearchCompilation.tex
Added Research on Network Games

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=2cm}
\usepackage{xcolor}

\newcommand{\ah}[1]{\textcolor{blue}{#1}}

\title{Controlled Swarms through Learning on Network Games: Research Compilation}
\author{Aamal Hussain}
\date{}

\begin{document}
    \maketitle

The goal of this revision is to re-evaluate the assumptions and guarantees placed on the
following problem: to what extent is it possible to control the behaviour of a large group of agents
subject to partial information. In particular, we seek to provide theoretical guarantees concerning
the behaviour of these agents from the point of view of safety. It is, therefore, required that we
ensure that the tools we are using are suited to such an analysis. In this spirit, this document
outlines an overview of the research into the game-theoretic and learning approaches towards
learning for large systems of agents.

\subsection*{Network-aggregative games are a stronger model for swarm systems than mean-field}

In particular, I focus this research on the problem of network-aggregative games \cite{Parise}. In this
class of game, we consider an aggregative (large population) system which has an underlying
communication network, i.e. agents adapt their behaviour dependent on the behaviours of their
neighbours in the network, but their knowledge of the other agents is limited (or even
non-existent), This form of game appears to be better suited to the problem of swarms than the
mean-field model, in which an agent would be required to have knowledge of the average behaviour of
the entire population \cite{Paccagnan2019}. This assumption is infeasible for a fully distributed
system, unless the agent is somehow able to communicate with the entire population and perform the
necessary calculations to find the average behaviour of the population.

In addition, the research on learning on network games (sometimes referred to as graphical games
\cite{Li2017}) is a topic which is increasingly being turned to from the
learning and game-theoretic communities alike. The major classes of learning algorithms which have
been explored in this context are: Fictitious Play \cite{Ewerhart2019}, Q-Learning 
\cite{Vamvoudakis2017} and No-Regret \cite{Nagarajan2018}. All
of these continue to undergo rigorous theoretical analysis from the game theoretic and computational
learning communities.

In this spirit, important facts about learning on networks have been established for each of the
learning algorithms. This includes, most importantly, convergence to Nash Equilibria. For each of
these classes of games, the conditions required for this behaviour are established in: 
\cite{Ewerhart2019} for Fictitious Play, \cite{Nagarajan2018} for no-regret, and
\cite{Li2017} for Reinforcement Learning. For the last of these, however, it is important to note that,
whilst the paper presents an algorithm for finding the NE, the focus of the study concerns forming
control policies based on the NE. This is not a disadvantage of the paper but rather an advantage:
namely that the learning community tends to be more invested in the application of the algorithms
towards real-world problems than the game-theoretic community.

The existence of these results means that there is a basis towards forming safe learning systems on
network games, since we can study the convergence towards an equilibrium. In addition, this class of
game can, particularly for Fictitious Play and Q-Learning, be extended towards network-aggregative
games, thereby allowing its study for larger populations. Such a study can be found in \cite{Parise},
in which the authors produce two NE seeking algorithms which, although they do not call it so,
is remarkably similar to Fictitious Play. This provides a useful (and perhaps only) study on
network-aggregative games which can be used to compare future work against.

\subsection*{The work on learning on network games is quite recent.}

To qualify the above statements, it is important to note that the work in learning on network-games
and, in particular, network-aggregative games is quite new. Indeed the publications listed in this
review, which represent some of the major breakthroughs in network games, all fall within the span
of 2015-2020. Whilst these, of course, build on previous work, it is important to note that the
specific problem of learning and control on network-aggregative games is an open problem. This is
because network games can be considered to be one of the more generalised forms of game since it
imposes an underlying communication network across the system. Indeed, a game in which an agent acts
according to all of the other agents in the group can simply be considered a fully-connected
network. There are, however, still further generalisations that could be made. For instance,
learning on  weighted networks has received some attention \cite{Bayer2019} but still
requires maturity. Furthermore, directed, or asymmetric networks and time-varying networks are
topics left, as of yet, unexplored. This exposition is not to suggest directions for our own
research, but merely to present the fact that the problem of learning on network games is a valuable
one to consider due to its generality.

\subsection*{Then comes the question of which learning algorithm to study.} % (fold)

Hopefully, I have made a strong argument for why network-aggregative games are a good class of games
to focus the study on for the problem of learning swarm behaviour. It then becomes incumbent on us
to choose a class of algorithm to consider. Whilst each algorithm presents its own set of pros and
cons, I argue that choosing the algorithm is merely a matter of considering the assumptions that
would be realistic to place on our system. As you mentioned in our discussion, if it is the case
that the problem we consider satisfies the assumptions for one of these classes, it becomes
necessary that we choose this class to study.

I would argue that the major conditions that we need to place on our system is that the agents have
no knowledge of the behaviour of the other agents and must, instead, infer that behaviour. Swarm
systems are built on the assumption that an agent is able to interact with, and observe, only a few
agents in the population. This would typically include its nearest neighbours and, if the situation
demands, a leader or set of leaders.

The other typical assumption placed on learning systems is that the agent does not have access to
the utlity function, from which it derives its behaviours. Such a problem would occur in games which
need to be repeated over time (e.g. traffic routing problem) or for the design of a system which is
aimed to be generalisable. However, it is unlikely that, for the problem of controlling a swarm,
this assumption would be required in general. For the most part, a control problem is designed for a
specific task in mind (e.g. coverage or foraging) and so the objective functional is fixed.
Furthermore, as long as complex gradients or Hessian inverses do not need to be calculated, it can
be assumed that the agent is capable of carrying out the necessary calculations in order to perform
its task. Otherwise, it would be required that a centralised controller, who has access to the cost
function and can carry out the optimisation, would need to communicate with each agent to identify
its behaviour and deliver its next action. Whilst there is nothing inherently wrong with this
method, such a system can no longer be called `distributed'.

With these in mind, then, I suggest that the Fictitious Play (FP) and (perhaps less so)
Reinforcement Learning (RL) algorithms would be appropriate classes of games to study. This is
because no-regret learning considers that the agent is aware of the actions of his/her neighbours
and therefore, does not fulful our requirements. I argue that FP is a stronger class for this
problem description since it is assumed that the agent knows her objective function and explicitly
tries to learn the behaviour of her neighbours. On the other hand, RL does not require knowledge of
neighbours or of the objective function but implicitly attempts to learn both of these by evaluating
the actions. Whilst Q-Learning is more general, then, it lacks the explicit modelling aspect that FP
offers and, as such, its analytical basis is not as strong. I propose, therefore, that a study of FP
on network-aggregative games provides the strongest model of swarm systems. I am not, however,
ruling out the option of looking at both of these algorithms and comparing their performance and
guarantees.

\subsection*{Conclusions}

In summary, I propose that, for the problem that we are considering, namely the problem of
controlling swarms of intelligent active particles, the strongest model to study would be that of
Fictitious Play (and/or RL) on network-aggregative games. This suggestion is due partly on the
similarity between the assumptions placed on this class of games and that of swarm systems as well
as the growing attention that this class of games has received from an analytic perspective. I
believe that the best way to proceed would be to extend the work of \cite{Ewerhart2019} with the
assumptions made in \cite{Parise}. A point which I would like to discuss with you is whether it would
be to attempt a similar extension of the work in \cite{Li2017} or \cite{Vamvoudakis2017}
(i.e. that of RL) and provide a comparison of the results. Regardless, both of these would lend
themselves well to considering the problem of distributed control as shown in 
\cite{Vamvoudakis2017} and \cite{Bianchi, DePersis2020}. Both of these allow for us to
consider the physical side of the problem by imposing that the learning algorithm must respect the
physical dynamics of the agents involved.

I believe this to be a stronger suggestion towards the problem of Active Particle Control than that
which was suggested in the ESA as it allows for us to directly build on our current work with only a
minor modification directing our assumptions closer to the ones required by our problem. It also
allows us to bypass the section of controlling a swarm through PDEs and instead narrows our focus on
game-theoretic learning methods.

\bibliographystyle{IEEEtran}

\bibliography{IEEEfull,references}

\end{document}

### 2020-11-13 Documents/ChaoticDynamics/Characterisation of Dynamics/main.tex
Created Document Outlining the Characterisation of Chaotic Dynamics

@@
 
-\title{Hello World}
+\title{Characterisation of Dynamics}
 \author{Aamal Hussain}
@@
 
+    The first techniques explored are from the paper: "Characterization of nonlinear dynamic systems
+    for engineering purposes – a partial review".
+
+    \paragraph*{Approach based on 1D time series}
+
+    The fractal dimension tells us how the detail in a pattern changes with the scale at which that
+    pattern is measured. It also gives us a reasonable measure for what the 'space-filling' capacity
+    of a pattern is. The proposed dimension that this paper offers is
+
+    \begin{equation}
+        D = \frac{log_{10} n}{log_{10} (L/l) + log_{10}n},
+    \end{equation}
+
+    where $n = L/u$. Here, L is the total length of the curve and l is the distance between the
+    first point of the curve and the furthest from the first, u is the average distance between two
+    successive points. This seems like it'll give a reasonable estimate for how crazy the curve is.
+    If it goes straight to an equilibrium, it should be close to 1. However, if it is crazy, the
+    dimension will be higher than 1.
+
+    Other viable options include spectral analysis (which I actually should consider), recurrence
+    plots (which the authors don't talk about but is useful for detecting periodicity) and average
+    time spent in a small region around the attractor.
+
+    I think this actually covers all of the problems that I would need to consider. The main ones
+    which I will want to have a look at implementing tomorrow are: the fractal dimension outlined
+    above, the recurrence plot and time spent in a region of phase space. In addition, I'd like to
+    find something which gives an indication r.e. the spectral analysis problem and then I can put
+    everything into code and hopefully get it running with some results.
+
 \end{document}

### 2020-11-18 Documents/Network Games/ResearchCompilation.tex
minor mods

@@
 \newcommand{\ah}[1]{\textcolor{blue}{#1}}
+\newcommand{\fb}[1]{\textcolor{red}{FB: #1}}
 
@@
 
-The goal of this revision is to re-evaluate the assumptions and guarantees placed on the
-following problem: to what extent is it possible to control the behaviour of a large group of agents
-subject to partial information. In particular, we seek to provide theoretical guarantees concerning
-the behaviour of these agents from the point of view of safety. It is, therefore, required that we
-ensure that the tools we are using are suited to such an analysis. In this spirit, this document
-outlines an overview of the research into the game-theoretic and learning approaches towards
-learning for large systems of agents.
+The goal of this revision is to re-evaluate the assumptions and
+guarantees placed on the following problem: to what extent is it
+possible to control the behaviour of a large group of agents subject
+to partial information. In particular, we seek to provide theoretical
+guarantees concerning the behaviour of these agents from the point of
+view of safety. It is, therefore, required that we ensure that the
+tools we are using are suited to such an analysis. In this spirit,
+this document outlines an overview of the research into the
+game-theoretic and learning approaches towards learning for large
+systems of agents.
 
@@
 
-In particular, I focus this research on the problem of network-aggregative games \cite{Parise}. In this
-class of game, we consider an aggregative (large population) system which has an underlying
-communication network, i.e. agents adapt their behaviour dependent on the behaviours of their
-neighbours in the network, but their knowledge of the other agents is limited (or even
-non-existent), This form of game appears to be better suited to the problem of swarms than the
-mean-field model, in which an agent would be required to have knowledge of the average behaviour of
-the entire population \cite{Paccagnan2019}. This assumption is infeasible for a fully distributed
-system, unless the agent is somehow able to communicate with the entire population and perform the
-necessary calculations to find the average behaviour of the population.
+In particular, I focus this research on the problem of
+network-aggregative games \cite{Parise}. In this class of game, we
+consider an aggregative (large population) system which has an
+underlying communication network, i.e. agents adapt their behaviour
+dependent on the behaviours of their neighbours in the network, but
+their knowledge of the other agents is limited (or even non-existent),
+This form of game appears to be better suited to the problem of swarms
+than the mean-field model, in which an agent would be required to have
+knowledge of the average behaviour of the entire population
+\cite{Paccagnan2019}. This assumption is infeasible for a fully
+distributed system, unless the agent is somehow able to communicate
+with the entire population and perform the necessary calculations to
+find the average behaviour of the population.
 
@@
 
-In this spirit, important facts about learning on networks have been established for each of the
-learning algorithms. This includes, most importantly, convergence to Nash Equilibria. For each of
-these classes of games, the conditions required for this behaviour are established in: 
-\cite{Ewerhart2019} for Fictitious Play, \cite{Nagarajan2018} for no-regret, and
-\cite{Li2017} for Reinforcement Learning. For the last of these, however, it is important to note that,
-whilst the paper presents an algorithm for finding the NE, the focus of the study concerns forming
-control policies based on the NE. This is not a disadvantage of the paper but rather an advantage:
-namely that the learning community tends to be more invested in the application of the algorithms
-towards real-world problems than the game-theoretic community.
+In this spirit, important facts about learning on networks have been
+established for each of the learning algorithms. This includes, most
+importantly, convergence to Nash Equilibria. For each of these classes
+of games, the conditions required for this behaviour are established
+in: \cite{Ewerhart2019} for Fictitious Play, \cite{Nagarajan2018} for
+no-regret, and \cite{Li2017} for Reinforcement Learning. For the last
+of these, however, it is important to note that, whilst the paper
+presents an algorithm for finding the NE, the focus of the study
+concerns forming control policies based on the NE. This is not a
+disadvantage of the paper but rather an advantage: namely that the
+learning community tends to be more invested in the application of the
+algorithms towards real-world problems than the game-theoretic
+community.
 
-The existence of these results means that there is a basis towards forming safe learning systems on
-network games, since we can study the convergence towards an equilibrium. In addition, this class of
-game can, particularly for Fictitious Play and Q-Learning, be extended towards network-aggregative
-games, thereby allowing its study for larger populations. Such a study can be found in \cite{Parise},
-in which the authors produce two NE seeking algorithms which, although they do not call it so,
-is remarkably similar to Fictitious Play. This provides a useful (and perhaps only) study on
-network-aggregative games which can be used to compare future work against.
+The existence of these results means that there is a basis towards
+forming safe learning systems on network games, since we can study the
+convergence towards an equilibrium. In addition, this class of game
+can, particularly for Fictitious Play and Q-Learning, be extended
+towards network-aggregative games, thereby allowing its study for
+larger populations. Such a study can be found in \cite{Parise}, in
+which the authors produce two NE seeking algorithms which, although
+they do not call it so, is remarkably similar to Fictitious Play. This
+provides a useful (and perhaps only) study on network-aggregative
+games which can be used to compare future work against.
+
+\fb{idea: an analysis as in our aamas paper, but grounded on network games?}
 
@@
 
-To qualify the above statements, it is important to note that the work in learning on network-games
-and, in particular, network-aggregative games is quite new. Indeed the publications listed in this
-review, which represent some of the major breakthroughs in network games, all fall within the span
-of 2015-2020. Whilst these, of course, build on previous work, it is important to note that the
-specific problem of learning and control on network-aggregative games is an open problem. This is
-because network games can be considered to be one of the more generalised forms of game since it
-imposes an underlying communication network across the system. Indeed, a game in which an agent acts
-according to all of the other agents in the group can simply be considered a fully-connected
-network. There are, however, still further generalisations that could be made. For instance,
-learning on  weighted networks has received some attention \cite{Bayer2019} but still
-requires maturity. Furthermore, directed, or asymmetric networks and time-varying networks are
-topics left, as of yet, unexplored. This exposition is not to suggest directions for our own
-research, but merely to present the fact that the problem of learning on network games is a valuable
-one to consider due to its generality.
+To qualify the above statements, it is important to note that the work
+in learning on network-games and, in particular, network-aggregative
+games is quite new. Indeed the publications listed in this review,
+which represent some of the major breakthroughs in network games, all
+fall within the span of 2015-2020. Whilst these, of course, build on
+previous work, it is important to note that the specific problem of
+learning and control on network-aggregative games is an open
+problem. This is because network games can be considered to be one of
+the more generalised forms of game since it imposes an underlying
+communication network across the system. Indeed, a game in which an
+agent acts according to all of the other agents in the group can
+simply be considered a fully-connected network. There are, however,
+still further generalisations that could be made. For instance,
+learning on weighted networks has received some attention
+\cite{Bayer2019} but still requires maturity. Furthermore, directed,
+or asymmetric networks and time-varying networks are topics left, as
+of yet, unexplored. This exposition is not to suggest directions for
+our own research, but merely to present the fact that the problem of
+learning on network games is a valuable one to consider due to its
+generality.
 
@@
 
-Hopefully, I have made a strong argument for why network-aggregative games are a good class of games
-to focus the study on for the problem of learning swarm behaviour. It then becomes incumbent on us
-to choose a class of algorithm to consider. Whilst each algorithm presents its own set of pros and
-cons, I argue that choosing the algorithm is merely a matter of considering the assumptions that
-would be realistic to place on our system. As you mentioned in our discussion, if it is the case
-that the problem we consider satisfies the assumptions for one of these classes, it becomes
-necessary that we choose this class to study.
+Hopefully, I have made a strong argument for why network-aggregative
+games are a good class of games to focus the study on for the problem
+of learning swarm behaviour. It then becomes incumbent on us to choose
+a class of algorithm to consider. Whilst each algorithm presents its
+own set of pros and cons, I argue that choosing the algorithm is
+merely a matter of considering the assumptions that would be realistic
+to place on our system. As you mentioned in our discussion, if it is
+the case that the problem we consider satisfies the assumptions for
+one of these classes, it becomes necessary that we choose this class
+to study.
 
-I would argue that the major conditions that we need to place on our system is that the agents have
-no knowledge of the behaviour of the other agents and must, instead, infer that behaviour. Swarm
-systems are built on the assumption that an agent is able to interact with, and observe, only a few
-agents in the population. This would typically include its nearest neighbours and, if the situation
-demands, a leader or set of leaders.
+I would argue that the major conditions that we need to place on our
+system is that the agents have no knowledge of the behaviour of the
+other agents and must, instead, infer that behaviour. Swarm systems
+are built on the assumption that an agent is able to interact with,
+and observe, only a few agents in the population. This would typically
+include its nearest neighbours and, if the situation demands, a leader
+or set of leaders.
 
-The other typical assumption placed on learning systems is that the agent does not have access to
-the utlity function, from which it derives its behaviours. Such a problem would occur in games which
-need to be repeated over time (e.g. traffic routing problem) or for the design of a system which is
-aimed to be generalisable. However, it is unlikely that, for the problem of controlling a swarm,
-this assumption would be required in general. For the most part, a control problem is designed for a
-specific task in mind (e.g. coverage or foraging) and so the objective functional is fixed.
-Furthermore, as long as complex gradients or Hessian inverses do not need to be calculated, it can
-be assumed that the agent is capable of carrying out the necessary calculations in order to perform
-its task. Otherwise, it would be required that a centralised controller, who has access to the cost
-function and can carry out the optimisation, would need to communicate with each agent to identify
-its behaviour and deliver its next action. Whilst there is nothing inherently wrong with this
-method, such a system can no longer be called `distributed'.
+The other typical assumption placed on learning systems is that the
+agent does not have access to the utlity function, from which it
+derives its behaviours. Such a problem would occur in games which need
+to be repeated over time (e.g. traffic routing problem) or for the
+design of a system which is aimed to be generalisable. However, it is
+unlikely that, for the problem of controlling a swarm, this assumption
+would be required in general. For the most part, a control problem is
+designed for a specific task in mind (e.g. coverage or foraging) and
+so the objective functional is fixed.  Furthermore, as long as complex
+gradients or Hessian inverses do not need to be calculated, it can be
+assumed that the agent is capable of carrying out the necessary
+calculations in order to perform its task. Otherwise, it would be
+required that a centralised controller, who has access to the cost
+function and can carry out the optimisation, would need to communicate
+with each agent to identify its behaviour and deliver its next
+action. Whilst there is nothing inherently wrong with this method,
+such a system can no longer be called `distributed'.
 
-With these in mind, then, I suggest that the Fictitious Play (FP) and (perhaps less so)
-Reinforcement Learning (RL) algorithms would be appropriate classes of games to study. This is
-because no-regret learning considers that the agent is aware of the actions of his/her neighbours
-and therefore, does not fulful our requirements. I argue that FP is a stronger class for this
-problem description since it is assumed that the agent knows her objective function and explicitly
-tries to learn the behaviour of her neighbours. On the other hand, RL does not require knowledge of
-neighbours or of the objective function but implicitly attempts to learn both of these by evaluating
-the actions. Whilst Q-Learning is more general, then, it lacks the explicit modelling aspect that FP
-offers and, as such, its analytical basis is not as strong. I propose, therefore, that a study of FP
-on network-aggregative games provides the strongest model of swarm systems. I am not, however,
-ruling out the option of looking at both of these algorithms and comparing their performance and
-guarantees.
+With these in mind, then, I suggest that the Fictitious Play (FP) and
+(perhaps less so) Reinforcement Learning (RL) algorithms would be
+appropriate classes of games to study. This is because no-regret
+learning considers that the agent is aware of the actions of his/her
+neighbours and therefore, does not fulful our requirements. I argue
+that FP is a stronger class for this problem description since it is
+assumed that the agent knows her objective function and explicitly
+tries to learn the behaviour of her neighbours. On the other hand, RL
+does not require knowledge of neighbours or of the objective function
+but implicitly attempts to learn both of these by evaluating the
+actions. Whilst Q-Learning is more general, then, it lacks the
+explicit modelling aspect that FP offers and, as such, its analytical
+basis is not as strong. I propose, therefore, that a study of FP on
+network-aggregative games provides the strongest model of swarm
+systems. I am not, however, ruling out the option of looking at both
+of these algorithms and comparing their performance and guarantees.
+
+\fb{the above seems reasonable and well-motivated to me.}
 

### 2020-11-24 aamas2021-formatting-instructions/Responses to Reviews for AAMAS.txt
added file

Review 1:

We thank the reviewer for their comments.

FB: it is not entirely clear to me what are you referring to in the following paragraph. I would suggest to focus on the question for rebuttal and leave this for later. 
Regarding your point on the links to evolutionary dynamics, actually the paper by Tuyls' et al (2006) show that, by deriving the continuous time dynamics of Q-Learning, we arrive at a dynamical system which is similar to the replicator dynamic from Evolutionary Game Theory. Our goal in this paper is solely focused on understanding the stability of these dynamics.

As regards specifically the questions for rebuttal:

1. We aim to focus our study on all normal form games. As you have pointed out, whilst the strategy space of the agents includes a finite set of actions, they are able to play mixed strategies as well as pure ones. The goal of the paper is to identify the evolution of the strategy as the agents learn. Thank you for pointing this out, we will be sure to clarify it in revision.

2 and 3. These are excellent points and we are, in fact, using the results of this study to address the problem of how to allow the agents to 'steer' the learning towards stable equilibria. However, as you have mentioned, there are cases in which there are multiple equilibria. In such cases, we have not yet determined a closed form method for steering the system towards a given one. This is an incredibly important question, however, and an important avenue for future work.

Review 2:

Thanks for the insightful remarks. Indeed, many of the techniques applied in this study are inspired by statistical physics, including the analysis of dynamical systems. We believe that such methods can be fruitfully applied to learning on games (as already shown by a wealth of works in the literature), as these contains many random variable elements: the strategies of the agents change during play, but also the payoff elements themselves can vary from game to game. We aimed, as much as possible, to focus the paper on the main, theoretical points of our contribution, while providing as many details as possible about the derivation in the supplementary material. We thank you for taking the time to look at the supplementary material, and for doing so with such rigour.

As you mentioned, the main contribution of this paper is equation (13) which establishes the region of stability. To validate this equation, we were sure to test each of its predictions, including the rather remarkable ones that independent Q-Learning rarely converges, and that the payoff correlations make no difference to stability.

As regards the style of presentation, we are aware that normally, papers at AAMAS present results in a theorem-proof format. However, we felt that this format would not be appropriate for the results described herein, as the statement of each result would just amount to the last equation in the derivation.

Review 3:

We thank the reviewer for the several points they raise, they will certainly be useful to improve the paper. They also allow us to provide some clarification, even though the reviewer does not ask any question explicitly.

The reviewer mentions that there is a disconnect between the theoretical analysis and the experimental evaluation. Nonetheless, we find that the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoff elements), as well as the fact that the majority of the phase space is unstable. These predictions hold for the limiting case of an infinite action set and a large number of players. However, there are practical restrictions when conducting an experiment with an incredibly large action/player set. Namely, this requires storage and calculations on matrices with N^p elements. This results in severe limitations for the scale of the experiments that can be run. We do however, present a number of results in our empirical evaluation which show that the overall trend, i.e., as p and N increase. Consider, Figure 6, which considers the case of 6 players. We show that the trend is towards the theoretical predictions. It is in this sense that we mention that the size of the unstable region is overestimated by the theory, a point which was also found in [15]. The message of the paper is to highlight the sensitivity of the stability to p and N, and argue that it is required for algorithms to be analysed with stability in mind, as well as to design algorithms which focus on maintaining the stability of the system.

One of your queries regards the sentence "... in the Prisoner's Dilemma, cyclic behaviour emerges". The paper mentioned in this context is actually different from that of Figure 1. In the paper you are referencing, the authors make use of an established dynamics of the 'Experience Weighted Attraction' Learning algorithm, which shows cyclic behaviour. However, Figure 1 depicts the convergence of Q-Learning in the same PD problem. We will ensure that we clarify this distinction since it shows that different algorithms may give different results on the same problem, hence the need for such a convergence study.

Regarding the class of games considered: In this study, we aimed to make as little assumptions on the game as possible. Therefore, you are correct in saying that the payoff elements were already in a general form. However, even within this, we have the different classes of games (zero-sum, potential and everything in between). Further still, there are an infinite number of different payoff elements which could achieve a zero-sum game. We aim to parameterise the structure of the game by the Gamma, which measures the 'zero-sumness' of the game. Therefore, our study is focused on how this parameter affects the stability of the system, rather than having to vary every payoff element. It is in this sense that we make the assertion that we generalise the nature of the study to its minimal elements: the learning parameters and a parameterisation of the payoff matrix.

Your point: The convergence criterion used in the empirical evaluation should depend on the step size alpha, otherwise for a given alpha, 1% might be outside of the margin of error.

Response: (for francesco) I'm not sure what they mean by this, the empirical evaluation is already based on alpha?

Regarding the choice of tau: You are right that the values chosen are rather small. We chose these for two reasons. The first was to remain consistent with the results provided in [15], thereby justifying the comparison to it made in the discussion. Further, as our results show, the degree of instability rises as alpha and tau increase. Therefore, it is immediate to see that, for higher values of tau and alpha, the game is trivially unstable and so does not show the transition to stability.

### 2020-11-24 aamas2021-formatting-instructions/Responses to Reviews for AAMAS.txt
added file

@@
 
-We thank the reviewer for their comments.
-
-FB: it is not entirely clear to me what are you referring to in the following paragraph. I would suggest to focus on the question for rebuttal and leave this for later. 
-Regarding your point on the links to evolutionary dynamics, actually the paper by Tuyls' et al (2006) show that, by deriving the continuous time dynamics of Q-Learning, we arrive at a dynamical system which is similar to the replicator dynamic from Evolutionary Game Theory.
-Our goal in this paper is solely focused on understanding the stability of these dynamics.
-
-As regards specifically the questions for rebuttal:
+We thank the reviewer for their comments. As regards specifically the questions for rebuttal:
 
@@
 This is an incredibly important question, however, and an important avenue for future work.
+
+Finally, regarding your point on the links with evolutionary dynamics (weaknesses), we notice that [20] shows that, by deriving the continuous time dynamics of Q-Learning, we arrive at a dynamical system which is similar to the replicator dynamic from Evolutionary Game Theory.
+Our goal in this paper is solely focused on understanding the stability of these dynamics.
 
@@
 These predictions hold for the limiting case of an infinite action set and a large number of players.
-However, there are practical restrictions when conducting an experiment with an incredibly large action/player set.
+However, there are practical restrictions when conducting an experiment with a large action/player set.
 Namely, this requires storage and calculations on matrices with N^p elements.
-This results in severe limitations for the scale of the experiments that can be run.
+As the reviewer remarks, this results in severe limitations for the scale of the experiments that can be run.
 We do however, present a number of results in our empirical evaluation which show that the overall trend, i.e., as p and N increase.

### 2020-11-24 Documents/ChaoticDynamics/aamas2021-formatting-instructions/Responses to Reviews for AAMAS.txt
Adjusted responses to AAMAS reviews

Review 1:

We thank the reviewer for their comments. For the questions:

1. We aim to focus our study on all normal form games. As you have pointed out, whilst the strategy space of the agents includes a finite set of actions, they are able to play mixed strategies as well as pure ones. The goal of the paper is to identify the evolution of the strategy as the agents learn. Thank you for pointing this out, we will be sure to clarify it in revision.

2 and 3. These are excellent points and we are, in fact, using the results of this study to consider how to 'steer' the learning towards stable equilibria. As you have mentioned, there are cases in which there are multiple stable equilibria. In such cases, we have not yet determined a closed form method for steering the system towards a given one. This is an incredibly important question, however, and an important avenue for future work.

Finally, on the links to evolutionary dynamics, (weaknesses), we notice that [20] shows that, by deriving the continuous time dynamics of Q-Learning, we arrive at a system which similar to the replicator dynamic . Our goal in this paper is solely focused on understanding the stability of these dynamics.

Review 2:

Thanks for the insightful remarks. Indeed, many of the techniques applied in this study are inspired by statistical physics. We believe that such methods can be fruitfully applied to learning on games (as already shown by a wealth of works in the literature), as these contains many random variable elements: the strategies of the agents change during play, but also the payoff elements themselves can vary from game to game. We aimed, as much as possible, to focus the paper on the main, theoretical points of our contribution, while providing all details about the derivation in the supplementary material. We thank you for taking the time to look at the supplementary material with such rigour.

As you mentioned, the main contribution of this paper is equation (13) which establishes the region of stability. To validate this equation, we were sure to test each of its predictions, including the rather remarkable ones that independent Q-Learning rarely converges, and that the payoff correlations make no difference to stability.

As regards the style of presentation, we are aware that normally, papers at AAMAS present results in a theorem-proof format. However, we felt that this format would not be appropriate for the results described herein, as the statement of each result would just amount to the last equation in the derivation.

Review 3:

We thank the reviewer for the several points they raise, they will certainly be useful to improve the paper, and also to provide some clarification.

The reviewer mentions that there is a disconnect between the theoretical analysis and the experimental evaluation. Nonetheless, we find that the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoff elements), and, for the limiting case of an infinite action set and a large number of players, that the majority of the phase space is unstable. There are, however, practical restrictions when conducting an experiment with an incredibly large action/player set; this requires storage and calculations on matrices with N^p elements, resulting in severe limitations for the scale of the experiments that can be run. We do however, present a number of results in our empirical evaluation which show the overall trend, i.e., as p and N increase. Consider, Figure 6, which considers 2-6 players, and shows the trend is towards the theoretical predictions. It is in this sense that the size of the unstable region is overestimated by the theory, a point which was also found in [15]. The message of the paper is to highlight the dependence of stability to these parameters, and argue that it is required for algorithms to be analysed with stability in mind, and to design algorithms which focus on maintaining stability.

One of your queries regards the sentence "... in the Prisoner's Dilemma, cyclic behaviour emerges". The study this references is actually different to that which Figure 1 depicts and, in fact, discusses a different learning algorithm (EWA) to that of the figure (Q-Learning). We will ensure that we clarify this distinction.

Method:

As discussed in the preceding paragraph to (4), i_mu refers to the action taken by player mu whilst i_kappa refers to that taken by kappa. This allows us to forego using different letters (i,j,k...) for different players, when we do not assume how many players there are.

The point regarding scaling the system was given in brief on page 4 to conserve space. A detailed discussion can be found in Section S2.2 of the supplementary material.

You are correct in saying that the payoff elements were already in a general form. To then analyse the system we parameterised these payoffs by 'Gamma' which measures the correlation between elements. To study the expected behaviour of a system which would result from a given Gamma, we average over all the possible realisations that this choice could take. This means that we can focus on how, on average, the payoff correlations affect stability rather than look at all of the (infinite) possible variations of payoff matrices.

Experiment:

The value of tau was chosen for two reasons 
1) to remain consistent with the results provided in [15], thereby justifying the comparison made in the discussion. 
2) as our results show, the degree of instability rises with tau. It is immediate to see that, for higher values of tau, the game is trivially unstable everywhere.

Your reading of the 'variance of actions' is correct, it denotes how much the actions vary about the fixed point. We will be sure to explicitly state how x_i(t) should be read

TODO: Make the points in the first paragraph, PD and Game assumptions as brief as possible. Respond to comments on notation, scaling the system and variance of the actions

### 2020-11-25 Documents/ChaoticDynamics/aamas2021-formatting-instructions/Responses to Reviews for AAMAS.txt
edits on the rebuttal

@@
 We aim to focus our study on all normal form games.
-As you have pointed out, whilst the strategy space of the agents includes a finite set of actions, they are able to play mixed strategies as well as pure ones.
+As you point out, whilst the strategy space of the agents includes a finite set of actions, they are able to play mixed strategies as well as pure ones.
 The goal of the paper is to identify the evolution of the strategy as the agents learn.
-Thank you for pointing this out, we will be sure to clarify it in revision.
+Thank you for pointing this out, we will clarify it in revision.
 
@@
 These are excellent points and we are, in fact, using the results of this study to consider how to 'steer' the learning towards stable equilibria.
-As you have mentioned, there are cases in which there are multiple stable equilibria.
+As you mention, there are cases in which there are multiple stable equilibria.
 In such cases, we have not yet determined a closed form method for steering the system towards a given one.
-This is an incredibly important question, however, and an important avenue for future work.
+This is an important avenue for future work.
 
-Finally, on the links to evolutionary dynamics, (weaknesses), we notice that [20] shows that, by deriving the continuous time dynamics of Q-Learning, we arrive at a system which similar to the replicator dynamic .
+Finally, on the links to evolutionary dynamics (weaknesses), we notice that by deriving the continuous time dynamics of Q-Learning, [20] arrives at a system similar to the replicator dynamic.
 Our goal in this paper is solely focused on understanding the stability of these dynamics.
@@
 Thanks for the insightful remarks.
-Indeed, many of the techniques applied in this study are inspired by statistical physics.
-We believe that such methods can be fruitfully applied to learning on games (as already shown by a wealth of works in the literature), as these contains many random variable elements: the strategies of the agents change during play, but also the payoff elements themselves can vary from game to game.
-We aimed, as much as possible, to focus the paper on the main, theoretical points of our contribution, while providing all details about the derivation in the supplementary material.
+Indeed, many of the techniques we apply are inspired by statistical physics.
+We believe that these methods can be fruitfully applied to learning on games (as discussed in the Related Work), as the latter makes use of many random variable: the strategies of the agents, the payoffs, etc.
+We aimed, as much as possible, to focus the paper on the main, theoretical contributions, while providing details about the derivation in the supplementary material.
 We thank you for taking the time to look at the supplementary material with such rigour.
 
-As you mentioned, the main contribution of this paper is equation (13) which establishes the region of stability.
-To validate this equation, we were sure to test each of its predictions, including the rather remarkable ones that independent Q-Learning rarely converges, and that the payoff correlations make no difference to stability.
+As you mention, one of the main contributions of the paper is equation (13), which establishes the region of stability.
+To validate this equation, we tested each of its predictions, including the rather remarkable ones that independent Q-Learning rarely converges, and payoff correlations make no difference to stability.
 
 As regards the style of presentation, we are aware that normally, papers at AAMAS present results in a theorem-proof format.
-However, we felt that this format would not be appropriate for the results described herein, as the statement of each result would just amount to the last equation in the derivation.
+However, we felt that this format would not be appropriate for the results proved here, as the statement of each result would just amount to the last equation in the derivation.
 
@@
 
-We thank the reviewer for the several points they raise, they will certainly be useful to improve the paper, and also to provide some clarification.
+We thank the reviewer for the several points they raise, they will certainly be useful to improve the paper, as well as to provide some clarification.
 
-The reviewer mentions that there is a disconnect between the theoretical analysis and the experimental evaluation.
-Nonetheless, we find that the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoff elements), and, for the limiting case of an infinite action set and a large number of players, that the majority of the phase space is unstable.
-There are, however, practical restrictions when conducting an experiment with an incredibly large action/player set; this requires storage and calculations on matrices with N^p elements, resulting in severe limitations for the scale of the experiments that can be run.
-We do however, present a number of results in our empirical evaluation which show the overall trend, i.e., as p and N increase.
-Consider, Figure 6, which considers 2-6 players, and shows the trend is towards the theoretical predictions.
-It is in this sense that the size of the unstable region is overestimated by the theory, a point which was also found in [15].
-The message of the paper is to highlight the dependence of stability to these parameters, and argue that it is required for algorithms to be analysed with stability in mind, and to design algorithms which focus on maintaining stability.
+The reviewer mentions that there is a disconnect between the theory and the empirical  evaluation. 
+Actually, the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoffs), and, for the limiting case of an infinite action set and a large number of players, that the majority of the phase space is unstable.
+There are, however, practical restrictions when conducting experiments with a large action/player set.
+We do however, present a number of empirical results that show the overall trend.
+Consider, e.g., Fig.
+6 for 2-6 players, which shows the trend is towards the theoretical predictions.
+It is in this sense (FB: in what sense?) that the size of the unstable region is overestimated by the theory, a point which was also found in [15].
+The message of the paper is to highlight the dependence of stability to these parameters, and argue that it is required for algorithms to be analysed with stability in mind.
 
-One of your queries regards the sentence "...
-in the Prisoner's Dilemma, cyclic behaviour emerges".
-The study this references is actually different to that which Figure 1 depicts and, in fact, discusses a different learning algorithm (EWA) to that of the figure (Q-Learning).
-We will ensure that we clarify this distinction.
+As regards cyclic behaviour in the Prisoner's Dilemma, the study we reference is actually different to that which Figure 1 depicts and, in fact, discusses a different learning algorithm (EWA) to that of the figure (Q-Learning).
+We will clarify this distinction.
 
@@
 
-As discussed in the preceding paragraph to (4), i_mu refers to the action taken by player mu whilst i_kappa refers to that taken by kappa.
-This allows us to forego using different letters (i,j,k...) for different players, when we do not assume how many players there are.
+As discussed at the beginning of Sec. 3.1, i_mu (resp. i_kappa) refers to the action taken by player mu (resp. kappa). This allows us to forego using different letters for different players.
 
-The point regarding scaling the system was given in brief on page 4 to conserve space. A detailed discussion can be found in Section S2.2 of the supplementary material.
+The point regarding scaling the system was given briefly on p. 4 to conserve space. A detailed discussion can be found in Section S2.2 of the supplementary material.
 
-You are correct in saying that the payoff elements were already in a general form.
-To then analyse the system we parameterised these payoffs by 'Gamma' which measures the correlation between elements.
+You are correct in saying that payoffs were already in a general form.
+To then analyse the system we parameterise these payoffs by 'Gamma' which measures their correlation.
 To study the expected behaviour of a system which would result from a given Gamma, we average over all the possible realisations that this choice could take.
@@
 
-Experiment:
+Experiments:
 
-The value of tau was chosen for two reasons 
-1) to remain consistent with the results provided in [15], thereby justifying the comparison made in the discussion. 
-2) as our results show, the degree of instability rises with tau. It is immediate to see that, for higher values of tau, the game is trivially unstable everywhere.
+The value of tau was chosen for two reasons: 
+1) To remain consistent with the results in [15], thereby justifying the comparison made in the discussion. 
+2) As our results show, instability increases with tau. Hence, for higher values of tau, the game is trivially unstable everywhere.
 
-Your reading of the 'variance of actions' is correct, it denotes how much the actions vary about the fixed point. We will be sure to explicitly state how x_i(t) should be read
+Your reading of 'variance of *actions*' is correct, it denotes how much the actions vary about the fixed point. We will state explicitly how x_i(t) should be read.
 

### 2020-11-25 Documents/ChaoticDynamics/aamas2021-formatting-instructions/Responses to Reviews for AAMAS.txt
Reduced length of document

@@
 
-1.
 We aim to focus our study on all normal form games.
 As you point out, whilst the strategy space of the agents includes a finite set of actions, they are able to play mixed strategies as well as pure ones.
-The goal of the paper is to identify the evolution of the strategy as the agents learn.
+The goal of the paper is to identify the evolution of the strategy as agents learn.
 Thank you for pointing this out, we will clarify it in revision.
 
-2 and 3.
-These are excellent points and we are, in fact, using the results of this study to consider how to 'steer' the learning towards stable equilibria.
-As you mention, there are cases in which there are multiple stable equilibria.
+These are excellent points and we are, in fact, using the results of this study to consider how to 'steer' learning towards stable equilibria.
+As you mention, there are cases in which multiple stable equilibria exist.
 In such cases, we have not yet determined a closed form method for steering the system towards a given one.
@@
 Indeed, many of the techniques we apply are inspired by statistical physics.
-We believe that these methods can be fruitfully applied to learning on games (as discussed in the Related Work), as the latter makes use of many random variable: the strategies of the agents, the payoffs, etc.
-We aimed, as much as possible, to focus the paper on the main, theoretical contributions, while providing details about the derivation in the supplementary material.
-We thank you for taking the time to look at the supplementary material with such rigour.
+We believe that these methods can be fruitfully applied to learning on games (as discussed in Sec.
+1.), as the latter makes use of many random variables: strategies of agents, payoffs, etc.
+We aimed to focus the paper on the main, theoretical contributions, while providing details in the supplementary material.
+We thank you for taking the time to look at this material with such rigour.
 
-As you mention, one of the main contributions of the paper is equation (13), which establishes the region of stability.
-To validate this equation, we tested each of its predictions, including the rather remarkable ones that independent Q-Learning rarely converges, and payoff correlations make no difference to stability.
+As you mention, the main contribution of the paper is equation (13), which establishes the region of stability.
+To validate this equation, we tested each of its predictions, including the remarkable ones that independent Q-Learning rarely converges, and payoff correlations make no difference to stability.
 
@@
 
-We thank the reviewer for the several points they raise, they will certainly be useful to improve the paper, as well as to provide some clarification.
+We thank the reviewer for the several points they raise, they will be useful to improve the paper, as well as to provide some clarification.
 
-The reviewer mentions that there is a disconnect between the theory and the empirical  evaluation. 
-Actually, the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoffs), and, for the limiting case of an infinite action set and a large number of players, that the majority of the phase space is unstable.
+The reviewer suggests there is a disconnect between the theory and experiments. 
+Actually, the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoffs), and, for the limiting case of an infinite action set and a large number of players, the majority of the phase space is unstable.
 There are, however, practical restrictions when conducting experiments with a large action/player set.
-We do however, present a number of empirical results that show the overall trend.
+We do, however, present a number of empirical results that show the overall trend.
 Consider, e.g., Fig.
-6 for 2-6 players, which shows the trend is towards the theoretical predictions.
-It is in this sense (FB: in what sense?) that the size of the unstable region is overestimated by the theory, a point which was also found in [15].
-The message of the paper is to highlight the dependence of stability to these parameters, and argue that it is required for algorithms to be analysed with stability in mind.
+6 for 2-6 players, which shows the trend toward the predictions through increased instability.
+Therefore, (13) will hold in the limit, until then it overestimates the size of the unstable region, as in [15].
+The message of the paper is to highlight the dependence of stability on parameters, and that algorithms must be analysed with stability in mind.
 
-As regards cyclic behaviour in the Prisoner's Dilemma, the study we reference is actually different to that which Figure 1 depicts and, in fact, discusses a different learning algorithm (EWA) to that of the figure (Q-Learning).
+As regards cyclic behaviour in Prisoner's Dilemma, the study we reference is actually different to that of Figure 1 and discusses a different learning algorithm (EWA) to the figure (Q-Learning).
 We will clarify this distinction.
@@
 You are correct in saying that payoffs were already in a general form.
-To then analyse the system we parameterise these payoffs by 'Gamma' which measures their correlation.
-To study the expected behaviour of a system which would result from a given Gamma, we average over all the possible realisations that this choice could take.
+To analyse the system we parameterise these payoffs by 'Gamma' which measures their correlation and study the behaviour of the average system which would result from a given Gamma (the effective dynamics (9)).
 This means that we can focus on how, on average, the payoff correlations affect stability rather than look at all of the (infinite) possible variations of payoff matrices.
@@
 Your reading of 'variance of *actions*' is correct, it denotes how much the actions vary about the fixed point. We will state explicitly how x_i(t) should be read.
-
-TODO: Make the points in the first paragraph, PD and Game assumptions as brief as possible. Respond to comments on notation, scaling the system and variance of the actions

### 2020-12-03 Documents/ChaoticDynamics/aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
Updated AAMAS Submission

--- 2020-10-19 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 \begin{abstract}
-Modelling the dynamics of Q-Learning is an active and important topic
-for the sake of developing an {\em a priori} understanding of
-Reinforcement Learning. In this paper, we use methods from
-evolutionary game theory to analyse the stability of Q-Learning in
-$p$-player games, where payoffs are randomly generated. We determine
-the parameter range in which Q-Learning is expected to settle to a
-stable fixed point and the range in which the dynamics are unstable.
-
-This study allows for parameters to be appropriately chosen to ensure
-the safe convergence of a learning algorithm and as a first step
-towards understanding the range of behaviours that can be displayed by
-learning using the Q-Learning algorithm. We validate our theoretical
-results through numerical simulation and show that, within the bounds
-of experimental error, the region of instability can be characterised
-by the learning dynamics.
+Modelling the dynamics of Q-Learning is an active and important topic for the sake of developing an
+{\em a priori} understanding of Reinforcement Learning. In this paper, we use methods from
+evolutionary game theory to analyse the stability of Q-Learning in $p$-player normal form games,
+where payoffs are randomly generated. We determine the parameter range in which Q-Learning is
+expected to settle to a stable fixed point and the range in which the dynamics are unstable.
+
+This study allows for parameters to be appropriately chosen to ensure the safe convergence of a
+learning algorithm and is a first step towards understanding the range of behaviours that can be
+displayed by learning using the Q-Learning algorithm. We validate our theoretical results through
+numerical simulation and show that, within the bounds of experimental error, the region of
+instability can be characterised by the learning dynamics.
 \end{abstract}
@@
 multi-agent system (MAS). Such systems are not as well-understood as
-single-agent systems in RL, since a given agent is tasked with
+single-agent RL, since a given agent is tasked with
 optimising a reward function which depends not only on a
@@
 %the study of
-evolutionary game theory (EGT) considers the problem of a MAS which is
-repeatedly exposed to an iterated game. This idea shares a strong
+evolutionary game theory (EGT) considers the problem of a MAS which
+repeatedly plays an iterated game. This idea shares a strong
 resemblance with MARL and, in fact, in \cite{Tuyls2006AnGames} it was
@@
 \paragraph{Contribution}
-In this study, we will be considering the question: under what choice
-of parameters is a multi-agent system, which is trained on an iterated normal-form game using Q-Learning, likely to converge to an equilibrium as opposed
-to displaying complex, or unstable behaviours? In investigating this
-question, we will make the following assumptions:
+In this study, we analyse the stability of the dynamics of Q-Learning established by Tuyls et al.
+\cite{Tuyls2006AnGames}, which we discuss in Sec. \ref{sec::Prelims}. From this perspective, We
+consider the question: under what choice of parameters is a multi-agent system, which is trained on
+an iterated normal-form game using Q-Learning, likely to converge to an equilibrium as opposed to
+displaying complex, or unstable behaviours? In investigating this question, we will make the
+following assumptions:
 
@@
 make decisions by attempting to anticipate their opponents' behaviour
-based on experience \cite{Galla2011}. \cite{Imhof2005} presents the
-observation that, in the Prisoner's Dilemma, cyclic behaviour
-emerges in which the optimal strategy cycles across defection,
+based on experience \cite{Galla2011}. \cite{Imhof2005}, studies the evolutionary dynamics of
+strategies in the iterated Prisoner's Dilemma game, in which cyclic behaviour
+emerges. Here, the optimal strategy cycles across defection,
 cooperation and tit-for-tat despite defection being the
@@
 
-Taking the notion of parameter dependence further, \cite{Galla2013}
+Taking the notion of property (e.g. memory loss) dependence further, \cite{Galla2013}
 describes an analysis of two-player iterated games in which the
@@
 
-\section{Preliminaries}
+\section{Preliminaries} \label{sec::Prelims}
 
@@
 	\begin{split}
-	Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] exp( i \sum_{i, \mu} \int dt [ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t))]) \times \\ exp(-i \alpha \ttau \sum_{\mu} \sum_{i_\mu, i_{-\mu}} \int dt [\hxmu{i} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} )]))
-    \times \\ exp(-i \alpha \ttau \sum_{\mu} \sum_{j_\mu, i_\mu, i_{-\mu}} \int dt [\hxmu{j}  \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}])) 
-	\times \\ exp(i \sum_{i, \mu}
+	Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] \exp( i \sum_{i, \mu} \int dt [ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t))]) \times \\ \exp(-i \alpha \ttau \sum_{\mu} \sum_{i_\mu, i_{-\mu}} \int dt [\hxmu{i} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} )]))
+    \times \\ \exp(-i \alpha \ttau \sum_{\mu} \sum_{j_\mu, i_\mu, i_{-\mu}} \int dt [\hxmu{j}  \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}])) 
+	\times \\ \exp(i \sum_{i, \mu}
 	\int dt[\xmu{i} \psi^\mu_i(t)]),
@@
 \begin{split}
-        \mathbb{E}[Q] = exp(- \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] ) \times \\
-        exp(- \frac{\alpha^2 \htau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} A^{\mu \nu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] )
+        \mathbb{E}[Q] = \exp(- \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] ) \times \\
+        \exp(- \frac{\alpha^2 \htau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') + \\ \Gamma \sum_{\nu \neq \mu} A^{\mu \nu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] )
 \end{split}
@@
 We then examine the
-long-term behaviour of the perturbation $\xpert$. by taking
+long-term behaviour of the perturbation $\xpert$ by taking
 the Fourier transform of (\ref{eqn::Linearised}) and analysing its
@@
 %    \begin{split}
-        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
-        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
-        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
+        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) \exp(-\frac{z^2}{2}) dz \\ 
+        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 \exp(-\frac{z^2}{2}) dz \\ 
+        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} \exp(-\frac{z^2}{2}) dz
 %    \end{split}
@@
 
-In this section, we describe and discuss the numerical experiments we use to verify the implications described in the discussion of Sec.
-\ref{sec::Theory}.
-We first describe how these experiments were conducted and then, having presented the results in Figures \ref{fig:NumericalExperiments} and \ref{fig:pVarianceExpt}, we discuss the correlation with the theory.
+In this section, we describe and discuss the numerical experiments we use to verify the implications
+described in the discussion of Sec. \ref{sec::Theory}. We first describe how these experiments were
+conducted and then, having presented the results in Figures \ref{fig:NumericalExperiments} and 
+\ref{fig:pVarianceExpt}, we discuss the correlation with the theory. Of course, (\ref{eqn::Final}) 
+holds only in the limit of a large player set and $N \rightarrow \infty$, which is impossible to
+achieve experimentally. Our aim, therefore, is to show that, by assessing the stability at
+different choices of $p$, that the trend is towards everywhere instability across parameter
+space. Specifically, as $p$ increases, the likelihood of instability increases, regardless of
+parameter choice.
 
@@
 \begin{enumerate}
-   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05 and the latter at 0.1.
+   \item Fix the parameters $\tau, \gamma$. The former is held at 0.05 (to remain consistent with
+   \cite{Sanders2018}) and the latter at 0.1.
    \item Initialise values of $\Gamma, \alpha$ (or $\tau$ appropriately). These will be swept over in the experiment.
@@
 
-Finally, Figure \ref{fig:pVarianceExpt} plot the degree variation about the fixed point displayed as the number of players $p$ increases.
-The variation is determined by first allowing the game to iterate for 5000 steps, so that it can be assumed to have reached the vicinity of the fixed point.
-Then, the action probabilities are recorded for a further 5000 iterations.
-At the end of this second period, the variance of the actions are calculated as
+Finally, Figure \ref{fig:pVarianceExpt} plot the degree variation about the fixed point displayed as
+the number of players $p$ increases. The variation is determined by first allowing the game to
+iterate for 5000 steps (times steps are denoted with $t$), so that it can be assumed to have reached
+the vicinity of the fixed point. Then, the action probabilities $\x_i$ are recorded for a further
+5000 iterations. At the end of this second period, the variance of the actions are calculated as
 %
@@
 progresses, it would be prudent to apply this analysis to various
-other algorithm. Algorithms whose dynamics are established, and are
+other algorithms. Algorithms whose dynamics are established, and are
 therefore open to a stability analysis, include piecewise Q-Learning

### 2020-12-03 Code/FPinNAG/main.py

@@ -1,0 +1,213 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+"""
+DO in NAG simulation: 
+
+1. Set up adjacency matrix
+2. Create function for cost function
+3. Initialise agent preferences
+4. Set up initial references
+
+Until convergence:
+Each agent simultaneously:
+Computes optimal strategy
+Communicates the new optimal strategy to the neighbours
+"""
+
+def initialise():
+    """
+    Initialise all required components for the NAG problem in Parise et al.
+    :return: (NxN) Adjacency Matrix, (Nx1) q array with all entries > 1, (nxN) x0 array, (nxN) sigma array
+    """
+
+    adjMat = (np.eye(3) == False) * (1 / 2)  # Designed to conform to double stochastic property
+
+    initVectors = np.random.rand(2, 3)
+    initVectors /= initVectors.sum(axis=0)
+
+    initQ = np.random.randint(2, 5, (3,))  # Has to be higher than 1 but upper bound is arbitrary
+
+    initRef = (adjMat @ initVectors.T).T
+    return adjMat, initQ, initVectors, initRef
+
+def bestResponse(i, sigmaRef, Q, xPreF):
+    xPreF = np.expand_dims(xPreF[:, i], axis=1)
+    APV = np.vstack((np.linspace(0, 1, 50), 1 - np.linspace(0, 1, 50)))
+    term1 = Q[i] * np.linalg.norm(np.subtract(APV, xPreF), axis=0) ** 2
+    term2 = 2 * sigmaRef[:, i].T @ APV
+
+    bestCost = np.min(term1 + term2)
+    bestReply = np.argmin(term1 + term2)
+
+    return APV[:, bestReply], bestCost
+
+def updateSigma(adjMat, vectors):
+    return (adjMat @ vectors.T).T
+
+def addNoise(prob):
+    APV = np.vstack((np.linspace(0, 1, 50), 1 - np.linspace(0, 1, 50)))
+    approxIdx = np.argmin(np.linalg.norm(APV - np.expand_dims(prob, axis=1), axis=0))
+    noisyIdx = np.random.randint(-2, 2)
+    while not (approxIdx + noisyIdx >= len(APV) or approxIdx + noisyIdx < 0):
+        noisyIdx = np.random.randint(-2, 2)
+    return APV[:, approxIdx + noisyIdx]
+
+def EKF(z, x, P, Q, K, R):
+    Pf = P + Q
+    x += K(z - x)
[…]

### 2020-12-03 Code/StabilityofMARL/KMDMARL/DMD_RRR.py

@@ -1,28 +1,0 @@
-import numpy as np
-
-
-def DMD_RRR(snapshotsX, snapshotsY, eps):
-    Dx = np.diag(np.linalg.norm(snapshotsX, axis=0))
-
-    Xm1 = snapshotsX @ np.linalg.pinv(Dx)
-    Ym1 = snapshotsY @ np.linalg.pinv(Dx)
-
-    U, S, V = np.linalg.svd(Xm1)
-    allI = S[np.where(S > S[0] * eps)]
-    k = np.argmax(allI)
-
-    Uk = U[:, :k]
-    Vk = V[:, :k]
-    Sigk = np.eye(k) * S[:k]
-
-    Bk = Ym1 @ (Vk @ np.linalg.inv(Sigk))
-
-    Q, R = np.linalg.qr(np.hstack((Uk, Bk)))
-    Sk = np.diag(R)[:k] @ R[:k, k+1:2*k]
-
-    Lambdak = np.linalg.eig(Sk)
-
-    for i in range(k):
-        [sigmaL, wL] =
-
-    pass

### 2020-12-03 Code/StabilityofMARL/KMDMARL/EDMD.py

@@ -1,0 +1,30 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.special as sps
+from itertools import product
+"""
+EDMD Algorithm: 
+
+1. Define a series of observables: let's say Hermite Polynomials up to order 5 + [x, v] + [1]
+2. Collect a set of data pairs X_n-1 and X_n
+3. Apply the observable functions on the datasets to get \Phi(X), \Phi(Y)
+4. Compute G and A from EDMD paper
+5. Compute K
+
+Predicting the flow field:
+
+Apply K on the observable for some initial condition. 
+Extract the flow field using (3.2) and (3.3) of the KMD for Algs paper
+"""
+
+def eval_Phi(x, maxOrder = 5):
+    lenData = len(x)
+    allHermiteOrders = list(product(range(maxOrder), repeat=lenData))
+    allHermites = np.array([sps.eval_hermite(o,x) for o in range(maxOrder)])
+
+    allCombos = [np.prod(allHermites[oList, range(lenData)]) for oList in allHermiteOrders]
+
+    return allCombos
+
+def generatePhi(X, maxOrder=5):
+    return [eval_Phi(x, maxOrder=maxOrder) for x in X]

### 2020-12-03 Code/StabilityofMARL/KMDMARL/KMDAnalysis.py

@@ -4,24 +4,7 @@ import matplotlib.pyplot as plt
 from time import time
 from tqdm import tqdm
 from os import mkdir
-
 from pydmd import DMD
-
-# alpha = .1
-gamma = 0.1
-Gamma = 0.1
-tau = 2
-alpha = 0.1
-
-nActions = 5
-t0 = 500
-
-initnSim = 1
-
-delta_0 = 1e-3
-nSim = 10
-nIter = int(1.5e4)
-
 
 def generateGames(gamma, nSim, nAct):
     """
@@ -51,7 +34,6 @@ def generateGames(gamma, nSim, nAct):
         # rewardBs = np.dstack((rewardBs, np.array([[1, 0], [5, 3]])))
     return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
 
-
 def getActionProbs(qValues, nSim):
     """
 
@@ -71,7 +53,6 @@ def getActionProbs(qValues, nSim):
         [np.array([np.exp(tau * qValues[p, :, s]) / partitionFunction[p, s] for p in range(2)]) for s in range(nSim)])
 
     return actionProbs
-
 
 def qUpdate(qValues, payoffs):
     """
@@ -107,14 +88,28 @@ def qUpdate(qValues, payoffs):
 
     return qValues
 
-
 def stringActions(actionProbs):
     return actionProbs[0].T.reshape((nActions * 2))
     # return actionProbs.reshape((nSim, 2 * nActions))
 
-
 if __name__ == "__main__":
 
+    # alpha = .1
+    gamma = 0.1
+    Gamma = 0.1
+    tau = 2
+    alpha = 0.1
+
+    nActions = 5
+    t0 = 500
+
+    initnSim = 1
+
+    delta_0 = 1e-3
+    nSim = 10
+    nIter = int(1.5e4)
+
+    
     plotFractalDim = []
 
     for alpha in tqdm(np.linspace(1e-2, 5e-2, num=1)):
@@ -131,30 +126,44 @@ if __name__ == "__main__":
 
                     allActions += [stringActions(getActionProbs(qValues0, nSim))]
 
-                    if cIter == 1000:
-                        dmd = DMD(svd_rank=-1)
-
-                        dmd.fit(np.array(allActions).T)ed 
-                        dmd.plot_eigs()
-                        plt.show()
-
-                    if cIter % 12000 == 0 and cIter != 0:
-
+                    if cIter == 30:
                         dmd = DMD(svd_rank=-1)
 
[…]

### 2020-12-03 Code/StabilityofMARL/KMDMARL/pyDMDtest.py

@@ -1,29 +1,0 @@
-import numpy as np
-from pydmd import DMD
-import matplotlib.pyplot as plt
-
-dim = 10
-
-A = np.diag([np.random.rand() * np.random.choice([-1, 1]) for i in range(dim)])
-
-x0 = np.random.rand(dim)
-
-allSnapshots = [x0]
-
-x = x0
-
-for i in range(999):
-    x = A @ x
-    allSnapshots.append(x)
-    
-
-allSnapshots = np.array(allSnapshots).T
-
-
-dmd = DMD(svd_rank=-1)
-
-dmd.fit(allSnapshots)
-
-plt.plot(dmd.reconstructed_data[0])
-plt.plot(allSnapshots[0])
-plt.show()

### 2021-02-18 Documents/ChaoticDynamics/AAMAS 2021/Responses to Reviews for AAMAS.txt
Three Body QL problems first added

--- 2020-11-25 Documents/ChaoticDynamics/aamas2021-formatting-instructions/Responses to Reviews for AAMAS.txt
@@
 
-We thank the reviewer for their comments. For the questions:
+We thank the reviewer for their comments. As for the questions:
 
@@
 
-Finally, on the links to evolutionary dynamics (weaknesses), we notice that by deriving the continuous time dynamics of Q-Learning, [20] arrives at a system similar to the replicator dynamic.
-Our goal in this paper is solely focused on understanding the stability of these dynamics.
+Finally, on the links with evolutionary dynamics (weaknesses), we notice that by deriving the continuous time dynamics of Q-Learning, [20] arrives at a system similar to the replicator dynamic.
+Our goal in this paper is primarily focused on understanding the stability of these dynamics.
 
@@
 We believe that these methods can be fruitfully applied to learning on games (as discussed in Sec.
-1.), as the latter makes use of many random variables: strategies of agents, payoffs, etc.
+1), as the latter makes use of many random variables: strategies of agents, payoffs, etc.
 We aimed to focus the paper on the main, theoretical contributions, while providing details in the supplementary material.
@@
 The reviewer suggests there is a disconnect between the theory and experiments. 
-Actually, the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoffs), and, for the limiting case of an infinite action set and a large number of players, the majority of the phase space is unstable.
+Actually, the theoretical result (13) makes a number of predictions including: the decrease of stability for increasing alpha or tau, the (rather surprising) lack of dependence on Gamma (the correlation between payoffs), and that, for the limiting case of an infinite action set and a large number of players, the majority of the phase space is unstable.
 There are, however, practical restrictions when conducting experiments with a large action/player set.
@@
 
-As regards cyclic behaviour in Prisoner's Dilemma, the study we reference is actually different to that of Figure 1 and discusses a different learning algorithm (EWA) to the figure (Q-Learning).
+As regards cyclic behaviour in Prisoner's Dilemma, the study we refer to is actually different to that of Figure 1 and discusses a different learning algorithm (EWA) to the figure (Q-Learning).
 We will clarify this distinction.
@@
 
-You are correct in saying that payoffs were already in a general form.
+You are correct in saying that payoffs are already in a general form.
 To analyse the system we parameterise these payoffs by 'Gamma' which measures their correlation and study the behaviour of the average system which would result from a given Gamma (the effective dynamics (9)).
-This means that we can focus on how, on average, the payoff correlations affect stability rather than look at all of the (infinite) possible variations of payoff matrices.
+This means that we can focus on how, on average, the payoff correlations affect stability rather than look at all the (infinite) possible variations of payoff matrices.
 

### 2021-02-18 Documents/ChaoticDynamics/AAMAS 2021/aamas21-formatting-instructions/main.tex
Three Body QL problems first added

--- 2020-10-19 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
@@
 
-\title[InstabilityinMARL]{Stability and Chaos in Multi-agent Reinforcement Learning}
+\title[InstabilityinMARL]{Stability and Chaos in Multi-Agent Reinforcement Learning}
 
@@
 %For a particularly strong example of this see
-\cite{Vinyals2019}. However, for the realisation of complex tasks,
+\cite{Vinyals2019}. For the realisation of complex tasks,
 such as air traffic control, market negotiations, and multi-robot
-coordination, it is required that the system be modelled as a
+coordination, however, it is required that the system be modelled as a
 multi-agent system (MAS). Such systems are not as well-understood as
@@
 shown that techniques from EGT may be fruitfully applied to the analysis of
-Q-Learning \cite{Sutton2018}.
+Q-Learning \cite{Barber2012}.
 
@@
       during the theoretical study, we will make the assumption that
-      the number $N$ of actions goes to infinity.
+      the number of actions $N$ goes to infinity.
 
@@
 Through our analysis and experiments we find that likelihood of
-displaying unstable dynamics increases as the \textit{step length}
-$\alpha$ and \textit{intensity of choice} $\tau$ parameters in the
+displaying unstable dynamics increases as the \textit{step length},
+$\alpha$ and \textit{intensity of choice}, $\tau$ parameters in the
 Q-Learning algorithm
@@
 increase. However, the
-correlation $\Gamma$ between payoffs, which measures how cooperative
+correlation, $\Gamma$ between payoffs, which measures how cooperative
 or competitive a game is, does not affect the stability of the
@@
 parameters, the likelihood of unstable behaviours increases as the
-number  $p$ of players in the game increases.
+number of players $p$ in the game increases.
 
@@
 
-In this section we establish some of the preliminaries which
-are required to follow the subsequent sections. The first regards
-\textit{dynamical behaviours}, which considers the evolution of agent (note we use the terms \textit{agent} and \textit{player} interchangeably)
+In this section, we establish some of the preliminaries which
+are required in order to follow the subsequent sections. We first consider
+\textit{dynamical behaviours}, which describes the evolution of agent (note we use the terms \textit{agent} and \textit{player} interchangeably)
 strategies as they learn how to play an iterated game. This study aims to
@@
     with multiple equilibria or limit cycles
-    \cite{Strogatz2000}. However, it would be difficult to control
+    \cite{Strogatz2000}. It would be difficult, however, to control
     systems whose dynamics are governed by chaos (though research into
@@
     \centering
-    \includegraphics[width = \linewidth]{Figures/DynamicalBehaviours.png}
+    \includegraphics[width = \linewidth, center]{Figures/DynamicalBehaviours.png}
     \caption{Different types of dynamical behaviour
@@
         Chaotic behaviour, here small deviations in the initial conditions can grow
-        exponentially. (Top Right) and (Bottom) drawn from \cite{Sanders2018}.}
+        exponentially. (Top Right) and (Bottom) drawn from \cite{Sanders2018}. \label{fig::DynamicalBehaviours}}
 \end{figure}
@@
 reinforcement learning through the lens of its dynamics. In this
-light, \cite{Tuyls2006AnGames} presents of derivation of a continuous-time dynamical system describing how agents following a Q-Learning
+light, Tuyls et al. \cite{Tuyls2006AnGames} present a derivation of a continuous-time dynamical system describing how agents following a Q-Learning
 approach adjust the probabilities of choosing actions as they
@@
 %
-where $\tau \in [0, \infty)$ is the \textit{intensity of choice} as described at the end of this section and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to
+where $\tau \in [0, \infty)$ is the \textit{intensity of choice} as described at the end of this section, and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to
 %
@@
 agent 1 (resp.~agent 2) takes action $i$ with probability
-$x_i$ (resp.~$y_j$).
-When these actions are taken, the agents
-receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
-predict the expected behaviour of Q-Learning agents which they go on to empirically verify.
+$x_i$ (resp.~$y_i$).
+When these actions are taken, the agent
+receives payoff $a_{ij}$ (resp.~$b_{ji}$). With these equations, it is possible to
+predict the expected behaviour of Q-Learning agents, which they go on to empirically verify.
 
@@
 selection of these agents is determined by the parameters $\alpha,
-\tau$ and the payoffs $a_{ij}, b_{ij}$. In light of this, this
-contributions aims to address the question presented in the
+\tau$ and the payoffs $a_{ij}, b_{ij}$. In light of this, this study
+aims to address the question presented in the
 introduction: how do these parameters influence the types of behaviours
@@
       $\Gamma$. We then average over this Gaussian. $\Gamma = -1$
-      indicates a zero sum game, in which the sum of payoffs for a
+      indicates a zero-sum game, in which the sum of payoffs for a
       given action across all agents is 0, resulting in a purely
@@
       a game is generated from the choice of $\Gamma$ is described in
-      (\ref{eqn::Payoffs}) below and follows the same procedure as
+      (\ref{eqn::Payoffs}) and follows the same procedure as
       outlined in \cite{Sanders2018}.
@@
 
-In this section we aim to determine how the choice of parameters
+In this section, we aim to determine how the choice of parameters
 $\alpha$ and $\tau$, alongside the choice of payoff matrix, affect the
-stability of the dynamics of Q-learning. However, as the values in the
-payoff matrix can take any real number, there is an infinite number
+stability of the dynamics of Q-learning. As the values in the
+payoff matrix can take any real number, however, there is an infinite number
 of possible realisations of games. Of course, it would not be possible
-to analyse every possible game, we instead follow the procedure
+to analyse every possible game, so we instead follow the procedure
 outlined in \cite{Coolen2005} and \cite{Galla2013} to average over
@@
 regardless of the choice of $\Gamma, N, p$) for the cases of $\alpha$ = 0 and/or $\tau$ = 0.
-We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) yielding a value of zero which falls within the stable region.
+We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) evaluating to zero, which falls within the stable region.
     \item Convergence is rare.
@@
 This implies that games, in general, will not converge.
-    \item The likelihood of convergence decreases with increasing $\alpha$ and $\tau$, regardless of the choice of $N, p$.
+    \item The likelihood of convergence decreases with increasing $\alpha$ and $\tau$, regardless of the choice of $N$ and $p$.
 We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e.
@@
     \item The choice of $\Gamma$ does not affect the stability of the game in the negatively-correlated regime.
-Therefore, the only dependent factors are $\alpha, \tau, N, p$.
+Therefore, the only dependent factors are $\alpha, \tau, N$ and $p$.
 This is more easily interpreted from the heatmaps in Figure \ref{fig:theory}.
     \item The likelihood of convergence decreases as $p$ increases.
-We see this by noticing the weighting that the $(p-1)$ in the second term of (\ref{eqn::Final}) places.
+We see this by noticing the $(p-1)$ in the second term of (\ref{eqn::Final}).
 As $p$ increases, this term drives the system further from the stability boundary.
@@
 In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$.
-We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.
+We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q$ and $\chi$ to determine their value.
 %
@@
 
-It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.
-
-We consider each of the implications (2)-(5) from the Sec. \ref{sec::Theory}
+It should be noted that this method of finding $\xfixed$ yields only an approximate value and so the $q$ and $\chi$ which are found are estimates.
+
+We consider each of the implications (2)-(5) 
 in turn, choosing to forego illustrating (1) as it can be seen immediately
 from (\ref{eqn::Final}). $\tau$ is held fixed
-at $0.05$ and vary $\Gamma$ in
-the range $[-1, 0]$, $\alpha$ in the range $[0.01, 0.05]$.
-
-\paragraph{Implication 2:} By looking at the values of the heatmap, we see that, for all choices
-of the parameters
-(\ref{eqn::Final}) evaluates to a negative value, which signals
+at $0.05$ and  $\Gamma$ is varied in
+the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$.
+
+\paragraph{Implication 2:} By looking at the values on the heatmap (Fig \ref{fig:theory}), we see that, for all choices
+of the parameters,
+(\ref{eqn::Final}) evaluates to a value less then zero, which signals
 instability. As such, the analysis over-estimates the region of
 instability. We believe that this is due to the
-%heavy
 assumptions made during the derivation of the analytic result, the
@@
 assumption generates, it is still clear (and is verified
-experimentally) that (\ref{eqn::Final}) predicts convergence in Q-Learning to be rare. Indeed as the
+experimentally) that (\ref{eqn::Final}) predicts convergence in Q-Learning to be rare. Indeed, as the
 value of $N$ increases, the stability boundary determined by
@@
 however, give rise to a limitation of the result - namely that the
-effect of the number of actions $N$ cannot be accurately inferred from
+effect of the number of actions, $N$, cannot be accurately inferred from
  (\ref{eqn::Final}). However, it should still be noted that, even
 with the increase of $N$, the values in parameter space remain negative
-and still, accurately, predict instability. We go on to verify that
+and predict instability. We go on to verify that
 the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured
@@
 We interpret (\ref{eqn::Final}), for given parameters, by determining
-how close the right hand side is to the stability boundary (i.e., how
+how close the right hand side is to the stability boundary (i.e. how
 close the value is to zero). A choice of parameters which evaluates
@@
 error) of being convergent than one which lies further from the
-boundary. Therefore, the heat-maps in Figure \ref{fig:theory} should
+boundary. Therefore, the heatmaps in Figure \ref{fig:theory} should
 be considered to show the probability of convergence for a choice of
@@
 
-\paragraph{Implication 3} can be visualised by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
+\paragraph{Implication 3:} can be visualised by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$.
 This occurs independent of the choice of $N$ or $p$.
 
-\paragraph{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$. The choice of $\Gamma$
+\paragraph{Implication 4:} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$. The choice of $\Gamma$
 makes almost no difference in the evaluation of (\ref{eqn::Final}). We
-anticipate that this is due to the restriction of $\Gamma$ to be in
+anticipate that this is due to the restriction of $\Gamma$ to
 the range $[-1, 0]$. In this range, the scaling effect of $\Gamma^2$
@@
 
-\paragraph{Implication 5}, finally, is considered in Figure \ref{fig:pvariation}.
-In this we keep all parameters, except for $p$, fixed and evaluate the right hand side of (\ref{eqn::Final}) for varying $p$, taking the absolute value for convenience.
-We see that the trend is to tend away from the stability boundary, indicating that as the number of players in the system increases, so too does the region of instability.
+\paragraph{Implication 5:} is considered in Figure \ref{fig:pvariation}.
+In this, we keep all parameters except for $p$ fixed, and evaluate the right hand side of (\ref{eqn::Final}) different values of $p$, taking the absolute value for convenience.
+We see that the trend is to tend away from the stability boundary indicating that, as the number of players in the system increases, so too does the region of instability.
 
@@
 \begin{figure}[t]
-    \includegraphics[width =  \linewidth, center]{Figures/alphavar5e2.png}
+    \includegraphics[width = 1.1 \linewidth, center]{Figures/alphavar5e2.png}
     \caption{The trajectories of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$. (Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
@@
 
-Finally, Figure \ref{fig:pVarianceExpt} plot the degree variation about the fixed point displayed as the number of players $p$ increases.
+Finally, in Figure \ref{fig:pVarianceExpt} we plot the degree variation about the fixed point displayed as the number of players $p$ increases.
 The variation is determined by first allowing the game to iterate for 5000 steps, so that it can be assumed to have reached the vicinity of the fixed point.
 Then, the action probabilities are recorded for a further 5000 iterations.
-At the end of this second period, the variance of the actions are calculated as
+At the end of this second period, the variance of the actions is calculated as
 %
@@
 $\frac{1}{p-1} << 2$ made during the derivation. Remaining
-discrepancies are partially due to the aforementioned approximation in
+discrepancies are due to the aforementioned approximation in
 the calculation of $q$, $\chi$ and the fact that the analytic result
@@
 the dark regions in Figure \ref{fig:NumericalExperiments} other than
-at low values of $\alpha, \tau$, we conclude that implications (1),
+at low values of $\alpha$, we conclude that implications (1),
 (2) are verified. Indeed, implication (3) and (4) are also verified as
-the proportion of games converged decrease monotonically with
-$\alpha$, $\tau$, but there does not appear to be any discernible
+the proportion of convergent games decreases monotonically with
+$\alpha$, but there does not appear to be any discernible
 dependence on $\Gamma$. Finally, we can conclude that implication 5 is
@@
 system increases monotonically with $p$. A point to note is that
-Figure \ref{fig:pVarianceExpt} shows a logarithmic dependence of the
+Figure \ref{fig:pVarianceExpt} shows an almost logarithmic dependence of the
 instability on $p$, whilst Figure \ref{fig:pvariation} suggests that
@@
 
-A point which we wish to discuss here is the difference in the result
-found w.r.t.~\cite{Sanders2018}, which considered the stability of
+A point which we wish to discuss here is a comparison with the result
+found in~\cite{Sanders2018}, which considered the stability of
 \textit{experience weighted attraction} (EWA). Namely, Sanders et
@@
 strength of correlation $\Gamma$ does not influence stability. As
-$\alpha$ increases, the likelihood of convergence decreases. The same
-is true for the \textit{intensity of choice} parameter $\tau$. Our
+$\alpha$ increases, the likelihood of convergence decreases. Our
 analysis also shows that the likelihood of convergence decreases,
@@
 
-% The present work represents a first step towards considering the stability
-% of multi-agent reinforcement learning and focuses on the limiting case
-% of stateless normal-form games played by homogeneous agents.
-As
-research into the dynamics of RL algorithms
+As research into the dynamics of RL algorithms
 progresses, it would be prudent to apply this analysis to various

### 2021-02-18 Documents/ChaoticDynamics/Analytic Result/main.tex
Three Body QL problems first added

\documentclass{article}

\usepackage[margin=2cm]{geometry}
\usepackage{amsmath,amsfonts}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
\newcommand\ah[1]{\textcolor{red}{AH: #1}}
\usepackage{subfiles}

% -------- MACROS ----------%

\newcommand{\xmu}[2]{x_{#1_#2}^{#2}(t)}
\newcommand{\xmudash}[2]{x_{#1_#2}^{#2}(t')}
\newcommand{\payoff}[2]{P^{#2}_{#1_#2, #1_{-#2}}}

\newcommand{\dxmu}[1]{\dot{x}_{#1_\mu}^{\mu} (t)}
\newcommand{\hxmu}[1]{\hat{x}_{#1_\mu}^{\mu} (t)}
\newcommand{\hxnu}[1]{\hat{x}_{#1_\nu}^{\nu} (t)}
\newcommand{\hxmudash}[1]{\hat{x}_{#1_\mu}^{\mu} (t')}
\newcommand{\hxnudash}[1]{\hat{x}_{#1_\nu}^{\nu} (t')}

\newcommand{\txmu}[2]{\tilde{x}_{#1_#2}^{#2}(t)}
\newcommand{\dtxmu}[2]{\dot{\tilde{x}}_{#1_#2}^{#2}(t)}
\newcommand{\tpayoff}[2]{\tilde{P}^{#2}_{#1_#2, #1_{-#2}}}
\newcommand{\talpha}{\tilde{\alpha}}
\newcommand{\ttau}{\tilde{\tau}}
\newcommand{\htau}{\hat{\tau}}
\newcommand{\xfixed}{x_\infty}
\newcommand{\ezerof}{\eta_{0, \infty}}
\newcommand{\eonef}{\eta_{1, \infty}}

\newcommand{\xpert}{\hat{x}(t)}
\newcommand{\xpertdash}{\hat{x}(t')}
\newcommand{\ezeropert}{\hat{\eta}_0(t)}
\newcommand{\eonepert}{\hat{\eta}_1(t)}

\newcommand{\eom}{\frac{\dxmu{i}}{\xmu{i}{\mu}} - \alpha \ttau \left ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) + \\ \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) - \talpha \rho^{\mu}_{i}(t)}
% ---- END MACROS ------- %

% ----- PREAMBLE FOR CODE ---- %

    \usepackage[breakable]{tcolorbox}
    \usepackage{parskip} % Stop auto-indenting (to mimic markdown behaviour)

    \usepackage{iftex}
    \ifPDFTeX
    	\usepackage[T1]{fontenc}
    	\usepackage{mathpazo}
    \else
    	\usepackage{fontspec}
    \fi

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % Maintain compatibility with old templates. Remove in nbconvert 6.0
    \let\Oldincludegraphics\includegraphics
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionFormat{nocaption}{}
    \captionsetup{format=nocaption,aboveskip=0pt,belowskip=0pt}

    \usepackage{float}
    \floatplacement{figure}{H} % forces figures to be placed at the correct location
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range
    \makeatletter % fix for old versions of grffile with XeLaTeX
    \@ifpackagelater{grffile}{2019/11/01}
    {
      % Do nothing on new versions
    }
    {
      \def\Gread@@xetex#1{%
        \IfFileExists{"\Gin@base".bb}%
        {\Gread@eps{\Gin@base.bb}}%
        {\Gread@@xetex@aux#1}%
      }
    }
    \makeatother
    \usepackage[Export]{adjustbox} % Used to constrain images to a maximum size
    \adjustboxset{max size={0.9\linewidth}{0.9\paperheight}}

    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    % The default LaTeX title has an obnoxious amount of whitespace. By default,
    % titling removes some of it. It also provides customization options.
    \usepackage{titling}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

    % common color for the border for error outputs.
    \definecolor{outerrorbackground}{HTML}{FFDFDF}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{pPlayerJulia}

% Pygments definitions
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % For linebreaks inside Verbatim environment from package fancyvrb. 
    \makeatletter
        \newbox\Wrappedcontinuationbox 
        \newbox\Wrappedvisiblespacebox 
        \newcommand*\Wrappedvisiblespace {\textcolor{red}{\textvisiblespace}} 
        \newcommand*\Wrappedcontinuationsymbol {\textcolor{red}{\llap{\tiny$\m@th\hookrightarrow$}}} 
        \newcommand*\Wrappedcontinuationindent {3ex } 
        \newcommand*\Wrappedafterbreak {\kern\Wrappedcontinuationindent\copy\Wrappedcontinuationbox} 
        % Take advantage of the already applied Pygments mark-up to insert 
        % potential linebreaks for TeX processing. 
        %        {, <, #, %, $, ' and ": go to next line. 
        %        _, }, ^, &, >, - and ~: stay at end of broken line. 
        % Use of \textquotesingle for straight quote. 
        \newcommand*\Wrappedbreaksatspecials {% 
            \def\PYGZus{\discretionary{\char`\_}{\Wrappedafterbreak}{\char`\_}}% 
            \def\PYGZob{\discretionary{}{\Wrappedafterbreak\char`\{}{\char`\{}}% 
            \def\PYGZcb{\discretionary{\char`\}}{\Wrappedafterbreak}{\char`\}}}% 
            \def\PYGZca{\discretionary{\char`\^}{\Wrappedafterbreak}{\char`\^}}% 
            \def\PYGZam{\discretionary{\char`\&}{\Wrappedafterbreak}{\char`\&}}% 
            \def\PYGZlt{\discretionary{}{\Wrappedafterbreak\char`\<}{\char`\<}}% 
            \def\PYGZgt{\discretionary{\char`\>}{\Wrappedafterbreak}{\char`\>}}% 
            \def\PYGZsh{\discretionary{}{\Wrappedafterbreak\char`\#}{\char`\#}}% 
            \def\PYGZpc{\discretionary{}{\Wrappedafterbreak\char`\%}{\char`\%}}% 
            \def\PYGZdl{\discretionary{}{\Wrappedafterbreak\char`\$}{\char`\$}}% 
            \def\PYGZhy{\discretionary{\char`\-}{\Wrappedafterbreak}{\char`\-}}% 
            \def\PYGZsq{\discretionary{}{\Wrappedafterbreak\textquotesingle}{\textquotesingle}}% 
            \def\PYGZdq{\discretionary{}{\Wrappedafterbreak\char`\"}{\char`\"}}% 
            \def\PYGZti{\discretionary{\char`\~}{\Wrappedafterbreak}{\char`\~}}% 
        } 
        % Some characters . , ; ? ! / are not pygmentized. 
        % This macro makes them "active" and they will insert potential linebreaks 
        \newcommand*\Wrappedbreaksatpunct {% 
            \lccode`\~`\.\lowercase{\def~}{\discretionary{\hbox{\char`\.}}{\Wrappedafterbreak}{\hbox{\char`\.}}}% 
            \lccode`\~`\,\lowercase{\def~}{\discretionary{\hbox{\char`\,}}{\Wrappedafterbreak}{\hbox{\char`\,}}}% 
            \lccode`\~`\;\lowercase{\def~}{\discretionary{\hbox{\char`\;}}{\Wrappedafterbreak}{\hbox{\char`\;}}}% 
            \lccode`\~`\:\lowercase{\def~}{\discretionary{\hbox{\char`\:}}{\Wrappedafterbreak}{\hbox{\char`\:}}}% 
            \lccode`\~`\?\lowercase{\def~}{\discretionary{\hbox{\char`\?}}{\Wrappedafterbreak}{\hbox{\char`\?}}}% 
            \lccode`\~`\!\lowercase{\def~}{\discretionary{\hbox{\char`\!}}{\Wrappedafterbreak}{\hbox{\char`\!}}}% 
            \lccode`\~`\/\lowercase{\def~}{\discretionary{\hbox{\char`\/}}{\Wrappedafterbreak}{\hbox{\char`\/}}}% 
            \catcode`\.\active
            \catcode`\,\active 
            \catcode`\;\active
            \catcode`\:\active
            \catcode`\?\active
            \catcode`\!\active
            \catcode`\/\active 
            \lccode`\~`\~ 	
        }
    \makeatother

    \let\OriginalVerbatim=\Verbatim
    \makeatletter
    \renewcommand{\Verbatim}[1][1]{%
        %\parskip\z@skip
        \sbox\Wrappedcontinuationbox {\Wrappedcontinuationsymbol}%
        \sbox\Wrappedvisiblespacebox {\FV@SetupFont\Wrappedvisiblespace}%
        \def\FancyVerbFormatLine ##1{\hsize\linewidth
            \vtop{\raggedright\hyphenpenalty\z@\exhyphenpenalty\z@
                \doublehyphendemerits\z@\finalhyphendemerits\z@
                \strut ##1\strut}%
        }%
        % If the linebreak is at a space, the latter will be displayed as visible
        % space at end of first line, and a continuation symbol starts next line.
        % Stretch/shrink are however usually zero for typewriter font.
        \def\FV@Space {%
            \nobreak\hskip\z@ plus\fontdimen3\font minus\fontdimen4\font
            \discretionary{\copy\Wrappedvisiblespacebox}{\Wrappedafterbreak}
            {\kern\fontdimen2\font}%
        }%

        % Allow breaks at special characters using \PYG... macros.
        \Wrappedbreaksatspecials
        % Breaks at punctuation characters . , ; ? ! and / need catcode=\active 	
        \OriginalVerbatim[#1,codes*=\Wrappedbreaksatpunct]%
    }
    \makeatother

    % Exact colors from NB
    \definecolor{incolor}{HTML}{303F9F}
    \definecolor{outcolor}{HTML}{D84315}
    \definecolor{cellborder}{HTML}{CFCFCF}
    \definecolor{cellbackground}{HTML}{F7F7F7}

    % prompt
    \makeatletter
    \newcommand{\boxspacing}{\kern\kvtcb@left@rule\kern\kvtcb@boxsep}
    \makeatother
    \newcommand{\prompt}[4]{
        {\ttfamily\llap{{\color{#2}[#3]:\hspace{3pt}#4}}\vspace{-\baselineskip}}
    }

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

%---- END PREAMBLE ----%
\title{Stability and Chaos in Multi-Agent Reinforcement Learning: Supplementary Material}
\author{\large{Submission ID: 3289}}

\date{}

\begin{document}

\maketitle

\section{Introduction}

In this Supplementary Material we provide further details into the work presented in the main paper `Stability and Chaos in Multi-Agent Reinforcement Learning' \cite{MainPaper}. In particular we present the full derivation of the stability criterion, Equation 14, of \cite{MainPaper}.

\section{Stability Analysis of Q-Learning} % (fold)

\subsection{Dynamics of Q-Learning}

In Q-Learning, an agent is required to determine an optimal strategy for itself through repeated exposure to a game. In the case of a normal form game, the strategy corresponds to the probabilities with which the actions in the agent's strategy space $\mathcal{A}$ (which is assumed to be identical for all agents) are played. These probabilities are given by
%
\begin{eqnarray*}
    x_i(k) & = & \frac{e^{\tau Q_i(k)}}{\sum_j e^{\tau Q_j(k)}}
\end{eqnarray*}
%
where $\tau \in [0, \infty)$ is the \textit{intensity of choice} as described in Section 2 of \cite{MainPaper} and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to

\begin{eqnarray}
\label{eqn::Qupdate}
    Q_i(k+1) & = & (1 - \alpha) Q_i(k) + \alpha (r + \gamma \max_j Q_j(k))
\end{eqnarray}
%
where $\alpha \in [0, 1]$ is the \textit{step length} parameter described below, $r$ is the immediate reward received, and $\gamma \in [0, 1]$ is the discount factor.

In \cite{Tuyls2006AnGames}, the authors derive a continuous time model which approximates the manner in which agents adjust their action probabilities. This model is given as

\begin{subequations}
\label{eqn::EOM}
    \begin{equation}
        \frac{\dot{x}_i(t)}{x_i(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
        + \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
    \end{equation}
    \begin{equation}
        \frac{\dot{y}_i(t)}{y_i(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
        + \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
    \end{equation}
\end{subequations}

Here,
agent 1 (resp.~agent 2) takes action $i$ with probability
$x_i$ (resp.~$y_j$).
When these actions are taken, the agents
receive payoff $a_{ij}$ and $b_{ji}$ respectively.

Tuyls et al. go on to show experimentally that this model accurately predicts the long-term expected behaviour of Q-Learning. As such, this dynamics seem a natural starting point for examining the stability of Q-Learning. However, it should be noted that the system does not capture the influence that the discount factor $\gamma$ plays in the behaviour of the system. We illustrate this in Figure \ref{fig:Gamma Var}, where 
%In this we see that 
adjusting the choice of $\gamma$ from $0.1$ to $0.75$ resulted not only in a slight shift of the fixed point location, but also in the behaviour of the system around that fixed point. In particular, the higher choice of $\gamma$ led to significantly more variation about the fixed point. It would therefore be intuitive to suggest that the system with $\gamma = 0.75$ is in some sense more unstable than $\gamma = 0.1$ (in fact the variation about the fixed point is a metric by which we measure instability). These behaviours are not captured by (\ref{eqn::EOM}) and so it limits the applicability of these dynamics to our purposes. We therefore fix $\gamma$ at 0.01, which by a qualitative assessment (as in Figure \ref{fig:Gamma Var}) is seen to show the strongest correlation to the predictions of (\ref{eqn::EOM}).

\begin{figure}[t]
    \centering
    \includegraphics[width = \linewidth]{Figures/Gamma Var.png}
    \caption{Analysis of (\ref{eqn::EOM}) for the Prisoner's Dilemma Game. (Left) Vector field predicted by the continuous time model (\ref{eqn::EOM}). (Middle) Trajectories of action probabilities followed by Q-Learning agents trained on the iterated game with the parameters $\tau = 1$, $\alpha = 0.01$, $\gamma = 0.1$. (Right) Trajectories followed by agents with $\gamma = 0.75$.}
    \label{fig:Gamma Var}
\end{figure}

We then write the dynamics presented in \cite{Tuyls2006AnGames} in a general $p$-player game. This yields the expression
%
\begin{eqnarray}
%\begin{split}
    \label{eqn::pEOM}
    \frac{\dxmu{i}}{\xmu{i}{\mu}} & = & \alpha \tau ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} - \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} ) + \alpha \sum_{j_\mu \in -i_\mu} \xmu{j}{\mu} ln \frac{\xmu{j}{\mu}}{\xmu{i}{\mu}},
%\end{split}
\end{eqnarray}

in which player $\mu$
chooses action $i_{\mu}$ from its strategy space $\mathcal{A}$ at time
$t$ with probability $\xmu{i}{\mu}$ and receives a reward
$\payoff{i}{\mu}$ from its payoff matrix $P^\mu$ depending on its own
action and the actions of all other agents $i_{-\mu}$, where $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2,
\ldots , p\} \setminus \{\mu\} \}$ and $-i_{\mu}$ denotes the set
$\mathcal{A} \setminus {i_\mu}$.

\subsection{Rescaling of Variables}

Our next port of call is to rescale the action probabilities and payoff elements. The rationale for this is as follows. The action probabilities, by definition, must satisfy the condition $\sum_{i_\mu} \xmu{i}{\mu} = 1$ and therefore $\xmu{i}{\mu}$ are of order $1/N$. The payoff elements (before scaling) are assumed to be drawn from a multivariate gaussian of mean zero and covariance
%
\begin{eqnarray}
\label{eqn::Payoffs}
%    \begin{split}
        \mathbb{E}\left [ \payoff{i}{\mu} \payoff{i}{\nu} \right] & = & \begin{cases}
        1 &  \text{ if } \nu = \mu \\
        \frac{\Gamma}{(p-1)} & \text{ otherwise. }
        \end{cases}
%    \end{split}
\end{eqnarray}

Therefore, the payoff elements are independent of $N$. As such, the expected payoff (i.e., the reward) that an agent receives, which is given by the term $\sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}$, is of variance $1/N^{p-1}$. The standard deviation of this reward is therefore of order $1/\sqrt{N^{p-1}}$. As $N$ increases, and we shall be taking the limit $N \rightarrow \infty$, the expected payoffs will converge towards the same value and so appreciable steps in the Q-values will no longer be taken. To counteract this, the action probabilities and payoff elements are scaled as

\begin{eqnarray*}
%    \begin{split}
        \payoff{i}{\mu} & = & \tpayoff{i}{\mu} \sqrt{N^{p-1}}\\
        \xmu{i}{\mu} & = & \frac{\txmu{i}{\mu}}{N} 
%    \end{split}
\end{eqnarray*}

We also introduce the scaled parameters
\begin{eqnarray*}
%    \begin{split}
        \talpha & = & \frac{\alpha}{N} \\
        \ttau & = & N^{-(p-1)/2} \tau \\
        \htau & = & N^{-p/2} \tau
%    \end{split}
\end{eqnarray*}

which yields the scaled equation
%
\begin{eqnarray}
%\begin{split}
    \label{eqn::scaledEOM}
    \frac{\dtxmu{i}{\mu}}{\txmu{i}{\mu}} & = & \alpha \ttau \left ( \sum_{i_{-\mu}} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) - \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \txmu{i}{\mu} \tpayoff{i}{\mu} \prod_{\kappa \neq \mu} \txmu{i}{\kappa} \right ) + \talpha \sum_{j_\mu \in -i_\mu} \txmu{j}{\mu} ln \frac{\txmu{j}{\mu}}{\txmu{i}{\mu}}
%\end{split}
\end{eqnarray}

The factor $\frac{1}{\sqrt{N}}$ is required in the derivation of the \textit{effective dynamics} and will become clear after taking the
expectation of the generating functional in the following section. Henceforth, we shall
not write the tildes on the action probabilities and payoffs. We shall also
abbreviate the final term as
%
	\begin{eqnarray*}
		\rho^{\mu}_{i}(t) & = & \sum_{j_\mu \in -i_\mu} \xmu{j}{\mu} ln \frac{\xmu{j}{\mu}}{\xmu{i}{\mu}}
	\end{eqnarray*}

\subsection{Generating Functional} % (fold)

The generating functional allows us to take a path integral over all possible realisations of
learning \cite{Mezard1986}. This is given as
%
\begin{equation}
	Z = \int D[\Vec{x}] \prod_i \delta(\textit{equation of motion}_i) exp(i
	\int dt[x_i(t) \psi_i(t)]), 
\end{equation}
%
where the equations of motion are the Lagrange equations of motion given in (\ref{eqn::scaledEOM}) and
the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
calculation. $\delta$ denotes the Dirac delta function. We write this expression in its Fourier
representation which, after substituting (\ref{eqn::scaledEOM}) yields	
	%
\begin{equation}
	\begin{split}
\label{eqn::generatingfunctional}
	Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] exp(i \sum_{i, \mu} \int dt[\hxmu{i}  \{  \eom  -h_i^\mu (t) \} ) 
	\times exp(i \sum_{i, \mu}
	\int dt[\xmu{i} \psi^\mu_i(t)]),
\end{split}
\end{equation}

where the $\hxmu{i}$ indicates the Fourier transform of $\xmu{i}{\mu}$ and $h_i^\mu (t)$ denotes a perturbative field which too shall be set to zero. In order to determine the \textit{effective dynamics}, which gives the behaviour of an individual strategy component averaged over all payoff realisations, we will need to perform the averaging over $\payoff{i}{\mu}$. To do this, we first isolate the terms which contain $\payoff{i}{\mu}$.

\begin{equation}
	\begin{split}
	Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] exp \left( i \sum_{i, \mu} \int dt \left[ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t)) \right] \right) \\
	\times exp \left(-i \alpha \ttau \sum_{i, \mu} \int dt \left [\hxmu{i} \left ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) \right] \right) \\
    \times exp(-i \alpha \ttau \sum_{i, \mu} \int dt [\hxmu{i} \left ( \sum_{i_\mu, i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right )])) 
	\times exp(i \sum_{i, \mu}
	\int dt[\xmu{i} \psi^\mu_i(t)])
\end{split}
\end{equation}

We relabel $\hxmu{i}$ in the third exponential to $\hxmu{j}$ to distinguish it from $\xmu{i}{\mu}$. This is possible since $j_\mu$ is summed over.
%
\begin{equation}
	\begin{split}
	Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] exp \left( i \sum_{i, \mu} \int dt \left[ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t)) \right] \right) \\
	\times exp \left(-i \alpha \ttau \sum_{\mu} \sum_{i_\mu, i_{-\mu}} \int dt \left [\hxmu{i} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right] \right) \\
    \times exp \left(-i \alpha \ttau \sum_{\mu} \sum_{j_\mu, i_\mu, i_{-\mu}} \int dt \left[\hxmu{j}  \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right] \right)
	\times exp(i \sum_{i, \mu}
	\int dt[\xmu{i} \psi^\mu_i(t)])
\end{split}
\end{equation}

Having isolated the terms containing the payoff elements into their own exponentials, we are able, finally, to average over the possible realisations. In order to do this, we focus only on the exponentials which contain those elements, defining
%
\begin{subequations}
\begin{align}
    \mathbb{E}[Q_1] = \prod_{\mu, i_\mu, i_{-\mu}} \mathbb{E} \left[exp(-i \alpha \ttau \int dt \hxmu{i} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}) \right] \\
    \mathbb{E}[Q_2] = \prod_{\mu, j_\mu, i_\mu, i_{-\mu}} \mathbb{E} \left[exp(i \frac{\alpha \htau}{\sqrt{N}} \int dt \hxmu{j} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}) \right]
\end{align}
\end{subequations}

\subsubsection{Expectation of $Q_1$}

We first write $Q_1$ as 
%
\begin{eqnarray*}
    Q_1 & = & \prod_{ij} exp(\Vec{b} \cdot \Vec{z}),
\end{eqnarray*}
%
where
%
\begin{eqnarray*}
%    \begin{split}
       b & := & [ -i \alpha \ttau \int dt \hxmu{i} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} ]^T 
%    \end{split}
\end{eqnarray*}
%
is a vector which contains all of the permutations of the products $\hxmu{i} \prod_{\kappa \neq \mu} \xmu{i}{\kappa}$ and

\begin{eqnarray*}
%    \begin{split}
       z & := & [ \payoff{i}{\mu} ]^T, 
%    \end{split}
\end{eqnarray*}
%
is a vector containing all of the payoff elements corresponding to the products in $b$. We then apply the exponential identity (whose proof is given in \cite{ZinnJustin2009})
%
\begin{eqnarray}
	\label{eqn::expectationIdentity}
		\int dz [e^{-A_2(z) + \Vec{b} \cdot \Vec{z}}] & = & (2 \pi)^{k/2} (det(A))^{-1/2} e^{\omega(b)},
	\end{eqnarray}
%
where
%
\begin{eqnarray*}
%	\begin{split}
		A_2(z) & = & 1/2 \sum_{ij} z_i A_{ij} z_j \\
		\omega_2(z) &  = & 1/2 \sum_{ij} b_i (A)^{-1}_{ij} b_j\\
%	\end{split}
%\end{equation*}
%
%and
%
%\begin{eqnarray*}
%    \begin{split}
       A  & = & \Sigma^{-1} \\
       \Sigma_{ij} & = & Cov[z_i, z_j].
%    \end{split}
\end{eqnarray*}

We recall that the scaled system has payoffs chosen so that
%
\begin{eqnarray}
\label{eqn::Payoffs}
%    \begin{split}
        \mathbb{E} \left[ \payoff{i}{\mu} \payoff{i}{\nu} \right] & = & \begin{cases}
        \frac{1}{\sqrt{N^{p-1}}}  & \text{ if } \nu = \mu \\
        \frac{\Gamma}{(p-1)\sqrt{N^{p-1}}} & \text{ otherwise. }
        \end{cases}
%    \end{split}
\end{eqnarray}

Applying the identity (\ref{eqn::expectationIdentity}) to $Q_1$ gives

\begin{eqnarray}
%\begin{split}
        \mathbb{E}[Q_1] & = exp & \left(  -\frac{\alpha^2 \ttau^2}{2 N^{p-1}} \sum_{i_\mu} \sum_\mu \int dt dt' \hxmu{i} \hxmudash{i} \prod_{\kappa \neq \mu} \xmu{i}{\mu} \prod_{\lambda \neq \mu} \xmudash{i}{\lambda} \right. \\
       & & \left. + \Gamma \sum_{\nu \neq \mu} \int dt dt' \hxmu{i} \hxnudash{i} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \prod_{\lambda \neq \nu} \xmudash{i}{\lambda}\right)
%\end{split}
\end{eqnarray}

\subsubsection{Expectation of $Q_2$}

We take a similar approach to that of $Q_1$ by defining
%
\begin{eqnarray*}
%    \begin{split}
       b & := & [\ldots i \alpha \htau \int dt \hxmu{j} \xmu{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \ldots]^T \\
       z & := & [\ldots \payoff{i}{\mu} \ldots]^T, 
%    \end{split}
\end{eqnarray*}
%
in which $\ldots$ indicates that the entries are parameterised with respect to $\mu$ and then follow the same procedure to arrive at
%
\begin{eqnarray}
%\begin{split}
        \mathbb{E}[Q_2] & = exp & 
        \left(-\frac{\alpha^2 \htau^2}{2 N^{p}} \sum_{i_\mu} \sum_\mu \int dt dt' \hxmu{j} \xmu{i}{\mu} \hxmudash{j} \xmudash{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\mu} \prod_{\lambda \neq \mu} \xmudash{i}{\lambda} \right.\\
       & & \left. + \Gamma \sum_{\nu \neq \mu} \int dt dt' \hxmu{j} \hxnudash{j} \xmu{i}{\mu} \xmudash{i}{\nu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \prod_{\lambda \neq \nu} \xmudash{i}{\lambda}\right).
%\end{split}
\end{eqnarray}

Next, we define the correlation functions
%
\begin{eqnarray*}
%    \begin{split}
       C^\mu (t, t') & := & N^{-1} \sum_{i} \xmu{i}{\mu} \xmudash{i}{\mu} \\
       L^\mu (t, t') & := & N^{-1} \sum_{i} \hxmu{i} \hxmudash{i} \\
       K^\mu (t, t') & := & N^{-1} \sum_{i} \xmu{i}{\mu} \hxmudash{i} \\
       A^{\mu, \nu} (t, t') & := & N^{-1} \sum_{i} \hxmu{i} \hxnudash{i},
%    \end{split}
\end{eqnarray*}
%
which allows us to rewrite the expectations as
%
\begin{equation}
\begin{split}
        \mathbb{E}[Q] = exp \left(- \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') +  \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] \right) \times \\
        exp \left(- \frac{\alpha^2 \htau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') +  \Gamma \sum_{\nu \neq \mu} A^{\mu \nu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] \right)
\end{split}
\end{equation}

To introduce these correlation functions into the integral, we rely on the use of their Dirac delta functions in its Fourier transform, for example

\begin{equation}
    1 = \int D[C^\mu (t, t') \hat{C}^\mu (t, t')] \text{ } exp(iN \int dt dt' \text{ } \hat{C}^\mu (t, t') (C^\mu (t, t')) - N^{-1} \sum_{i} \xmu{i}{\mu} \xmudash{i}{\mu})
\end{equation}

\subsection{The Effective Dynamics}

Having performed the expectation of the variables $\payoff{i}{\mu}$ in the generating functional, we can now substitute (\ref{eqn::generatingfunctional}) to yield
%
\begin{equation}
    \label{eqn::averagedgf}
    \mathbb{E}[Z(\Vec{\psi})] = \int D[C, \hat{C}, L, \hat{L}, K, \hat{K}, A, \hat{A}] \text{ } exp(N (\Psi + \Phi + \Omega + \mathcal{O}(N^{-1}))),
\end{equation}
%
where
%
\small{
\begin{equation}
    \begin{split}
         \Psi = i \sum_\mu \int dt dt' \left[ C^\mu (t, t') \hat{C}^\mu (t, t') + L^\mu (t, t') \hat{L}^\mu (t, t') + K^\mu (t, t') \hat{K}^\mu (t, t') + \sum_{\nu \neq \mu} A^{\mu ]\nu} (t, t') \hat{A}^{\mu \nu} (t, t')]\right] \\
         \Phi = - \frac{\alpha^2 \ttau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') +  \Gamma \sum_{\nu \neq \mu} K^\mu (t, t') K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] \\
        - \frac{\alpha^2 \htau ^2}{2} N \sum_{\mu} \Big [ \int dt dt' L^\mu(t, t') C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') +  \Gamma \sum_{\nu \neq \mu} A^{\mu \nu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \Big ] \\
         \Omega = N^{-1} \sum_{\mu, i_\mu} ln \Big \{ \int D[\xmu{i}{\mu}, \hxmu{i}] p_{i, 0}^\mu exp \left(i \int dt \xmu{i}{\mu} \psi_{i_\mu}^\mu \right) \times exp \left(i\int dt \left[ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t)) \right] \right) \times \\ exp \left(-i \int dt dt' \left[\hat{C}^\mu (t, t') \xmu{i}{\mu} \xmudash{i}{\mu} + \hat{L}^\mu (t, t') )\hxmu{i} \hxmudash{i} + \hat{K}^\mu (t, t') )\xmu{i}{\mu} \hxmudash{i} + \sum_{\nu \neq \mu} \hat{A}^{\mu \nu} (t, t') \hxmu{i} \hxnudash{i} \right]  \right)  \Big \}.
    \end{split}
\end{equation}
}
Here, $p_{i, 0}^\mu$ denotes the initial distribution which the action is drawn from. It is important to note here that all of the information regarding the dynamics of the agent is included within $\Omega$, in the sense that the integral over the strategy components $x$ are contained within this expression.

\subsection{Saddle Point Integration}

We now wish to reduce the integral (\ref{eqn::averagedgf}) through the use of the saddle point method of integration. In this method, we take the limit $N \rightarrow \infty$ so that the area under the curve of (\ref{eqn::averagedgf}) is dominated by the maxima of the term $(\Psi + \Phi + \Omega + \mathcal{O}(N^{-1}))$. Therefore, we first find the maxima of this term with respect to the integral variables $[C, \hat{C}, L, \hat{L}, K, \hat{K}, A, \hat{A}]$. This yields

\begin{eqnarray}
\frac{\partial f}{\partial \hat{C}^\mu} = 0  & \implies & C^\mu (t, t') =  - \lim_{N \rightarrow \infty} N^{-1} \sum_i \mathbb{E}[\xmu{i}{\mu} \xmudash{i}{\mu}]_{\Omega}  = - \lim_{N \rightarrow \infty} N^{-1} \sum_i \frac{\partial^2 \mathbb{E}[Z(\Vec{\psi})]}{\delta \psi_{i_\mu}^\mu (t) \psi_{i_\mu}^\mu (t')} \Big \rvert_{\Vec{\psi} = \Vec{h} = 0} \\
\frac{\partial f}{\partial \hat{L}^\mu} = 0  & \implies & L^\mu (t, t') =  - \lim_{N \rightarrow \infty} N^{-1} \sum_i \mathbb{E}[\hxmu{i} \hxmudash{i}]_{\Omega}  = - \lim_{N \rightarrow \infty} N^{-1} \sum_i \frac{\partial^2 \mathbb{E}[Z(\Vec{\psi})]}{\delta h_{i_\mu}^\mu (t) h_{i_\mu}^\mu (t')} \Big \rvert_{\Vec{\psi} = \Vec{h} = 0} \\
\frac{\partial f}{\partial \hat{K}^\mu} = 0  & \implies & K^\mu (t, t') =  - \lim_{N \rightarrow \infty} N^{-1} \sum_i \mathbb{E}[\xmu{i}{\mu} \hxmudash{i}]_{\Omega}  = - \lim_{N \rightarrow \infty} N^{-1} \sum_i \frac{\partial^2 \mathbb{E}[Z(\Vec{\psi})]}{\delta \psi_{i_\mu}^\mu (t) h_{i_\mu}^\mu (t')} \Big \rvert_{\Vec{\psi} = \Vec{h} = 0} \\
\frac{\partial f}{\partial \hat{A}^{\mu \nu}} = 0  & \implies & A^{\mu \nu} (t, t') =  - \lim_{N \rightarrow \infty} N^{-1} \sum_i \mathbb{E}[\hxmu{i} \hxnudash{i}]_{\Omega}  = - \lim_{N \rightarrow \infty} N^{-1} \sum_i \frac{\partial^2 \mathbb{E}[Z(\Vec{\psi})]}{\delta h_{i_\mu}^\mu (t) h_{i_\nu}^\nu (t')} \Big \rvert_{\Vec{\psi} = \Vec{h} = 0},
\end{eqnarray}
%
where $\mathbb{E}[ \cdot ]_\Omega$ denotes an expectation to be taken over $\Omega$. The interested reader may consult \cite{Coolen2005} for details on how such an expectation may be formulated. However, for our purposes, the details are not required. What it is important to note, however, is that by normalisation of the generating functional it was required that $Z(\Vec{\psi = 0}) = 1$ for any choice of $h$. Therefore, the $Z(\Vec{\psi})$ is constant in $h$ and therefore we have that $L^\mu (t, t') = 0$ and $A^{\mu \nu} = 0$ for any $t, t'$. In addition, we know that past values of $\xmu{i}{\mu}$ cannot be affected by future values and so we have that $K^\mu(t, t') = 0$ for $t' > t$ and so $K^\mu(t, t') K^\mu(t', t) = 0$.

Continuing the extrema analysis we have
%
\begin{eqnarray}
\frac{\partial f}{\partial C^\mu} = 0  & \implies & i \hat{C}^\mu (t, t') =  0 \\
\frac{\partial f}{\partial L^\mu} = 0  & \implies & i \hat{L}^\mu (t, t') = \frac{\alpha^2 \ttau ^2}{2} \prod_{\kappa \neq \mu} C^\kappa (t, t') + \frac{\alpha^2 \htau ^2}{2} C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') \\
\frac{\partial f}{\partial K^\mu} = 0 & \implies & i \hat{K}^\mu (t, t') = \alpha^2 \ttau ^2 \Gamma \sum_{\nu \neq \mu} K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \\
\frac{\partial f}{\partial A^{\mu \nu}} = 0 & \implies & i \hat{A}^{\mu \nu} (t, t') = \frac{\alpha^2 \htau ^2}{2} \Gamma \sum_{\nu \neq \mu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t'),
\end{eqnarray}
%
where the first equality holds since in $\Omega$, $C^\mu (t, t')$ always appears in a product with $L^\mu (t, t')$, $A^{\mu \nu}$ or $K^\mu(t, t') K^\mu(t', t)$, which we have already established to be 0. By substituting these expressions back into (\ref{eqn::averagedgf}), we immediately get that $\Psi + \Phi = 0$ since each of the terms will contain one of the above terms which we found to be 0. For $\Omega$, we get

\begin{equation}
\begin{split}
        \Omega = N^{-1} \sum_{\mu, i_\mu} ln \Big \{ \int D[\xmu{i}{\mu}, \hxmu{i}] p_{i, 0}^\mu exp (i \int dt \xmu{i}{\mu} \psi_{i_\mu}^\mu) \times exp \left(i \int dt \left[ \hxmu{i} (\frac{\dxmu{i}}{\xmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t)) \right] \right) \times \\ exp \Bigg(-i \int dt dt' \left[\frac{\alpha^2 \ttau ^2}{2} \prod_{\kappa \neq \mu} C^\kappa (t, t') \hxmu{i} \hxmudash{i} + \frac{\alpha^2 \htau ^2}{2} C^\mu (t, t') \prod_{\kappa \neq \mu} C^\kappa (t, t') \hxmu{i} \hxmudash{i} + \\ \alpha^2 \ttau ^2 \Gamma \sum_{\nu \neq \mu} K^\nu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \xmu{i}{\mu} \hxmudash{i} + \\ \frac{\alpha^2 \htau ^2}{2} \Gamma \sum_{\nu \neq \mu} (t, t') C^\nu (t, t') C^\mu (t, t') \prod_{\kappa \not\in \{\mu, \nu\}} C^\kappa (t, t') \hxmu{i} \hxnudash{i} \right] \Bigg)   \Big \}.
\end{split}
\end{equation}

We make the assumption that all strategy components for all agents are drawn from the same initial distribution $p_0$, are under the influence of the same perturbative field $h(t)$ and also finally set the generating field $\psi = 0$, we are able to drop the distinction between agents and their action probabilities. Instead, we regard that all actions are independent and identically distributed (i.i.d). This is a strong assumption, but is required to ensure that the strategy components are all positive and real-valued (which is required for a probability). This gives $\Omega$ as
%
\begin{eqnarray}
%\begin{split}
        \Omega & = & pln \Big \{ \int D[x, \hat{x}] p_{0} exp \left(i \int dt \left[ \hat{x}(t) (\frac{\dot{x}}{x} - \talpha \rho (t) - h(t)) \right] \right) \times \nonumber \\ & & exp \Bigg(-i \int dt dt' \Big[\frac{\alpha^2 \ttau ^2}{2} C^{(p-1)} (t, t') \hat{x}(t) \hat{x}(t') + \frac{\alpha^2 \htau ^2}{2} C^{(p-1)} (t, t') \hat{x}(t) \hat{x}(t') + \nonumber  \\ & & \alpha^2 \ttau ^2 \Gamma (p-1) i G(t, t') C^{(p-1)} (t, t') x(t) \hat{x}(t') +  \frac{\alpha^2 \htau ^2}{2} \Gamma (p-1) A(t, t') C^{(p-1)} (t, t') \hat{x}(t) \hat{x}(t') \Big] \Bigg) \Big \},
%\end{split}
\end{eqnarray}
%
where $G(t, t') = -iK(t, t')$.

We note here that since we have dropped the distinction between players, the term $A^{\mu, \nu}$ which coupled the actions of players together is now no longer meaningful and can be identified with the uncoupled term $L(t, t')$. This identification is the strongest of our assumptions and results in a deviation from the initial, coupled, nature of the dynamics (\ref{eqn::pEOM}). However, as mentioned, it is required to yield a physically viable expression for action probabilities (i.e., positive real valued). In addition, since each strategy component is independent, the expression for $\Omega$ can be decomposed to yield an individual \textit{effective generating functional} for each component given as

\begin{eqnarray}
\label{eqn::zeff}
%\begin{split}
        Z_{eff} & = & \int D[x, \hat{x}] p_{0} exp \left(i \int dt \left[ \hat{x}(t) (\frac{\dot{x}}{x} - \talpha \rho (t) - h(t)) \right] \right) \times \nonumber \\
        & & exp \Bigg(-i \int dt dt' \Big[\alpha^2 \ttau ^2 C^{(p-1)} (t, t') \hat{x}(t) \hat{x}(t') + \alpha^2 \htau ^2 C^{(p-1)} (t, t') \hat{x}(t) \hat{x}(t') + \nonumber \\
        & & i \alpha^2 \ttau ^2 \Gamma  G(t, t') C^{(p-1)} (t, t') x(t) \hat{x}(t') \Big] \Bigg).
%\end{split}
\end{eqnarray}

We notice that (\ref{eqn::zeff}) is exactly the form of the generating functional for the dynamics
%
\begin{equation}
    \label{eqn::EffectiveDynamics}
    \begin{split}
            \frac{1}{x(t)} \frac{d}{dt} x(t) = \alpha^2 \ttau^2 \Gamma \int dt' \left [G(t, t')C^{p - 2}(t, t') x(t') \right ] + \sqrt{2} \alpha \ttau \eta_1(t) + \sqrt{2} \alpha \htau \eta_0(t) + \talpha \rho(t), 
    \end{split}
\end{equation}
%
where
%
\begin{eqnarray*}
%    \begin{split}
        C(t, t') & = & \mathbb{E}[x(t) x(t')] \\
        \mathbb{E}[\eta_1(t)] & = & 1, \text{ \space } \mathbb{E}[\eta_1(t) \eta_1(t')]  =  C^{p-1}(t, t') \\
        \mathbb{E}[\eta_0(t)] & = & 1, \text{ \space } \mathbb{E}[\eta_0(t) \eta_0(t')] = C^{p}(t, t') \\
        G(t, t') & = & \mathbb{E}\left [ \frac{\delta x(t)}{ \delta \eta_1(t')} \right].
%    \end{split}
\end{eqnarray*}

We therefore call (\ref{eqn::EffectiveDynamics}) the \textit{effective dynamics}. This gives an approximate expression for the expected behaviour of a strategy component averaged over all possible realisations of the payoff matrix. It is on this system that we will perform a stability analysis.

\section{Fixed Points of the System}

Before we can analyse the stability of a fixed point, we first need to establish that the fixed point exists for the system. At such a point $\dot{x}(t) = 0$. Furthermore, since there is no fluctuation of $x(t)$ with respect to time, the term $C(t, t')$ is constant and $G(t, t') \approx G(t - t')$. As $\eta_0, \eta_1$ are also both stationary at the fixed point, we rewrite $\eta_1$ as $q^{(p-1)/2}z$ where $q = \mathbb{E}[\xfixed^2]$ and $z$ is drawn from the standard normal distribution (mean 0, variance 1). This gives $\eta_0 = q^{p/2}z^{p/p-1}$. To ensure, once again, that $x(t)$ remains real valued, we must avoid fractional powers in $z$, which itself can be negative valued. Therefore, we make the assumption that $p$ is large enough so that $p \approx p-1$. Then $\eta_0 \approx q^{p-1/2}z = \eta_1$. With all of the above considered, (\ref{eqn::EffectiveDynamics}) reduces to the fixed point equation

\begin{eqnarray}
%    \begin{split}
    0 = \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{p-2} \chi 
       + \sqrt{2} q^{(p-1)/2}z (\alpha \ttau  + \alpha \htau) + \talpha \rho]
    \label{eqn::fixed_point}
%    \end{split}
\end{eqnarray}
%
where $\chi = \int G(t-t') dt $. Now, we have two possible choices for the fixed point: either $\xfixed$ is zero or $\xfixed$ is given by the expression in the squared brackets. The former is never achieved in practice; an agent will not assign an action to have exactly zero probability. Therefore, we only consider the latter term with $\xfixed$ given as

\begin{equation}
    \xfixed = \frac{- \sqrt{2} q^{(p-1)/2}z (\alpha \ttau  + \alpha \htau) + \talpha \rho}{\alpha^2 \ttau^2 \Gamma  q^{p-2} \chi}.
\end{equation}

Due to causality, we have that $\chi > 0$ for $\Gamma < 0$ \cite{Opper1992, Galla2013}. It is therefore in this region that the existence of a unique, positive solution to (\ref{eqn::fixed_point}) can be understood, for the case that the numerator remains negative. However, for positive $\Gamma$ this relation does not necessarily hold and so the behaviour of the system for positive $\Gamma$ is not well understood. Therefore, we must restrict our analysis to $\Gamma \in [-1, 0]$.

Of course, the expression in the brackets of (\ref{eqn::fixed_point}) is not trivial to solve and so a Newton-Raphson root finding method was employed to approximate the value. The parameters $q, \chi, \rho$ are determined as
%
\begin{eqnarray*}
        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz\\
        \rho & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z') ln \frac{\xfixed(z')}{\xfixed(z)} dz'
\end{eqnarray*}

\section{Stability of the Effective Dynamics}

With the region $\Gamma < 0$ established and the fixed point examined, we now look at the behaviour of the effective dynamics in a neighbourhood of the fixed point. In particular, we would like to establish whether, if perturbed from the $\xfixed$, the system will diverge away (unstable) or converge to $\xfixed$ (stable). A similar question was considered by Opper and Diederich in \cite{Opper1992} and so we progress along the same lines.

The dynamics are proposed to be perturbed by a
disturbance $\xi(t)$ which is drawn from a Gaussian of zero mean and
unit variance. The disturbance causes the values of $x(t)$ and
$\eta_0(t)$, $\eta_1(t)$ to deviate from their fixed point position
$\xfixed$, $\ezerof$, $\eonef$ by an amount $\xpert$, $\ezeropert$,
$\eonepert$. Rewriting the dynamics with all of these considerations yields
%
\begin{eqnarray}
 %   \begin{split}
            \frac{d}{dt} (\xfixed + \xpert(t)) & = & (\xfixed + \xpert(t)) \Big (\alpha^2 \ttau^2 \Gamma \int dt' \left [G(t, t')C^{p - 2}(t, t') (\xfixed + \xpert(t')) \right ]  \nonumber \\
            & & + \sqrt{2} \alpha \ttau (\eonef + \eonepert(t')) + \sqrt{2} \alpha \htau (\ezerof + \eonepert(t)) + \talpha \rho + \xi(t) \Big )
  %  \end{split}
\end{eqnarray}

In a neighbourhood of $\xfixed$, the linear terms would dominate and so we keep these, neglecting higher order terms. This yields
%
\begin{eqnarray}
%    \begin{split}
\frac{d}{dt} \xpert & = & (\xfixed + \xpert) [ \alpha^2 \ttau^2 \Gamma \xfixed \int dt' [ G(t, t')C^{p - 2}(t, t') ] \nonumber + \sqrt{2} \alpha \ttau \eonef + \sqrt{2} \alpha \htau \ezerof + \talpha \rho] \nonumber \\
& &  + \xfixed [\alpha^2 \ttau^2 \Gamma \int dt' [ G(t, t')C^{p - 2}(t, t') \xpertdash ] + \sqrt{2} \alpha \ttau \eonepert + \sqrt{2} \alpha \htau \ezeropert + \xi(t)]
\label{eqn::Linearised}
%    \end{split}
\end{eqnarray}

Now invoking the fixed point condition, we notice that the first square bracket in (\ref{eqn::Linearised}) equates to zero. Now, taking the Fourier transform of (\ref{eqn::Linearised}) gives

\begin{equation}
    \Big[ \frac{i \omega}{\xfixed} - \alpha^2 \ttau^2 \Gamma \tilde{H(\omega)} \Big] \tilde{X(\omega)} = \sqrt{2} \alpha \ttau \tilde{\eta_1 (\omega)} + \sqrt{2} \alpha \htau \tilde{\eta_0 (\omega)} + \tilde{\Xi(\omega)}
\end{equation}
%
where $H(t) = G(t, t')C^{(p-2)}(t, t')$.

Using the self-consistency relation that $\mathbb{E}[|\eonef^2|] = (p-1)\mathbb{E}[|\xfixed^2|]^{(p-2)}\mathbb{E}[|\tilde{X}(\omega)^2|]$ and, once again, the estimate $\mathbb{E}[|\tilde{\eta_1 (\omega)}^2|] \approx \mathbb{E}[|\tilde{\eta_0 (\omega)}^2|]$ in the region where $p \approx p-1$ we have

\begin{eqnarray}
    \mathbb{E}\Big[| \frac{i \omega}{\xfixed} - \alpha^2 \ttau^2 \Gamma \tilde{H(\omega)}|^2 \Big] \mathbb{E}[|\tilde{X(\omega)}|^2] & = & \mathbb{E}[|\sqrt{2} \alpha \ttau \tilde{\eta_1 (\omega)} + \sqrt{2} \alpha \htau \tilde{\eta_0 (\omega)} + \tilde{\Xi(\omega)}|^2] \nonumber \\
    & = & 2 \alpha^2 \ttau^2 \mathbb{E}[|\tilde{X(\omega)}|^2] + 4 \alpha^2 \ttau \htau \mathbb{E}[|\tilde{X(\omega)}|^2] + 2 \alpha^2 \htau^2 \mathbb{E}[|\tilde{X(\omega)}|^2] + 1 \nonumber \\
    \mathbb{E}[|\tilde{X(\omega)}|^2] & = & \Big ( \mathbb{E}\Big[| \frac{i \omega}{\xfixed} - \alpha^2 \ttau^2 \Gamma \tilde{H(\omega)}|^2 \Big] - 2(\alpha \ttau + \alpha \htau)^2 \Big )^{-1}
\end{eqnarray}

As we wish to examine the long time behaviour of the system, we must consider the case $\omega \rightarrow 0$. By definition, we require that $\mathbb{E}[|\tilde{X(\omega)}|^2] > 0$ (as it is a square, and an absolute). Therefore, if we find, for a given choice of parameters, that $\mathbb{E}[|\tilde{X(\omega)}|^2]$ yields a negative value, then the fixed point analysis breaks down and we have the onset of instability. As such, our criteria for a stable fixed point becomes

\begin{equation}
    \label{eqn::Final}
    0 \leq \left [(\alpha^2 \ttau^2 \Gamma q^{p-2} \chi)^{2} - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2} \right ]
\end{equation}

Finally, (\ref{eqn::Final}) is the expression whose predictions are analysed in \cite{MainPaper}.

\section{Experimental Code}

The following code was used to produce all of the experimental figures shown in the main paper \cite{MainPaper}. This is written in Julia 1.5 and the dependencies are listed in the first cell. To generate any of the heatmaps, first change the values of the parameters $\alpha, \tau, \Gamma, p, N$ to the desired choice. Then run the subsequent cells up to `plotHeatmap(a)'. To generate the variance plots run both the `getVariance' function and the subsequent cell.

\subfile{pPlayerJulia.tex}

\bibliographystyle{acm} 
\bibliography{references}

\end{document}

### 2021-02-18 Documents/ChaoticDynamics/Analytic Result/pPlayerJulia.tex
Three Body QL problems first added

\documentclass[main.tex]{subfiles}

\begin{document}

    \maketitle

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{using} \PY{n}{LinearAlgebra}
\PY{k}{using} \PY{n}{SparseArrays}
\PY{k}{using} \PY{n}{PyCall}
\PY{k}{using} \PY{n}{Plots}
\PY{k}{using} \PY{n}{IterTools}
\PY{k}{using} \PY{n}{Distributions}
\PY{k}{using} \PY{n}{ProgressMeter}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{py}\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
\PY{l+s}{d}\PY{l+s}{e}\PY{l+s}{f}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{l}\PY{l+s}{l}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{(}\PY{l+s}{n}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{s}\PY{l+s}{)}\PY{l+s}{:}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{m}\PY{l+s}{p}\PY{l+s}{o}\PY{l+s}{r}\PY{l+s}{t}\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{t}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{t}\PY{l+s}{o}\PY{l+s}{o}\PY{l+s}{l}\PY{l+s}{s}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{d}\PY{l+s}{X}\PY{l+s}{ }\PY{l+s}{=}\PY{l+s}{ }\PY{l+s}{l}\PY{l+s}{i}\PY{l+s}{s}\PY{l+s}{t}\PY{l+s}{(}\PY{l+s}{i}\PY{l+s}{t}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{t}\PY{l+s}{o}\PY{l+s}{o}\PY{l+s}{l}\PY{l+s}{s}\PY{l+s}{.}\PY{l+s}{p}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{d}\PY{l+s}{u}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{(}\PY{l+s}{l}\PY{l+s}{i}\PY{l+s}{s}\PY{l+s}{t}\PY{l+s}{(}\PY{l+s}{r}\PY{l+s}{a}\PY{l+s}{n}\PY{l+s}{g}\PY{l+s}{e}\PY{l+s}{(}\PY{l+s}{1}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{ }\PY{l+s}{+}\PY{l+s}{ }\PY{l+s}{1}\PY{l+s}{)}\PY{l+s}{)}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{r}\PY{l+s}{e}\PY{l+s}{p}\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{=}\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{s}\PY{l+s}{)}\PY{l+s}{)}\PY{l+s}{ }\PY{l+s}{*}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{s}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{r}\PY{l+s}{e}\PY{l+s}{t}\PY{l+s}{u}\PY{l+s}{r}\PY{l+s}{n}\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{d}\PY{l+s}{X}
\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
\PY{n}{allActions}\PY{p}{(}\PY{n}{nAct}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)} \PY{o}{=} \PY{n}{py}\PY{l+s}{\PYZdq{}}\PY{l+s}{a}\PY{l+s}{l}\PY{l+s}{l}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{\PYZdq{}}\PY{p}{(}\PY{n}{nAct}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{generateCorrespondences}\PY{p}{(}\PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}
    \PY{n}{nElements} \PY{o}{=} \PY{n}{nActions}\PY{o}{\PYZca{}}\PY{n}{nPlayers}
    \PY{n}{Actions} \PY{o}{=} \PY{n}{allActions}\PY{p}{(}\PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}
    \PY{n}{allCombos} \PY{o}{=} \PY{p}{[}\PY{p}{[}\PY{n}{findall}\PY{p}{(}\PY{n}{x} \PY{o}{\PYZhy{}}\PY{o}{\PYZgt{}} \PY{n}{x}\PY{o}{==}\PY{n}{tuple}\PY{p}{(}\PY{n}{circshift}\PY{p}{(}\PY{p}{[}\PY{n}{j} \PY{k}{for} \PY{n}{j} \PY{k+kp}{in} \PY{n}{Actions}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{]}\PY{p}{,} \PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{o}{*}\PY{p}{(}\PY{n}{p}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{o}{.}\PY{o}{.}\PY{p}{)}\PY{p}{,} \PY{n}{Actions}\PY{p}{)}\PY{p}{[}\PY{n}{p}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{]} \PY{k}{for} \PY{n}{p}\PY{o}{=}\PY{l+m+mi}{0}\PY{o}{:}\PY{n}{nPlayers}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]} \PY{k}{for} \PY{n}{i}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nElements}\PY{p}{]}

    \PY{k}{return} \PY{n}{Actions}\PY{p}{,} \PY{n}{allCombos}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{generateGames}\PY{p}{(}\PY{n}{Gamma}\PY{p}{,} \PY{n}{nSim}\PY{p}{,} \PY{n}{allCombos}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}
    \PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{C}\PY{l+s}{r}\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{C}\PY{l+s}{o}\PY{l+s}{v}\PY{l+s}{a}\PY{l+s}{r}\PY{l+s}{i}\PY{l+s}{a}\PY{l+s}{n}\PY{l+s}{c}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{M}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{r}\PY{l+s}{i}\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{f}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{m}\PY{l+s}{ }\PY{l+s}{G}\PY{l+s}{a}\PY{l+s}{m}\PY{l+s}{m}\PY{l+s}{a}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{R}\PY{l+s}{e}\PY{l+s}{t}\PY{l+s}{u}\PY{l+s}{r}\PY{l+s}{n}\PY{l+s}{ }\PY{l+s}{R}\PY{l+s}{a}\PY{l+s}{n}\PY{l+s}{d}\PY{l+s}{o}\PY{l+s}{m}\PY{l+s}{ }\PY{l+s}{P}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{o}\PY{l+s}{f}\PY{l+s}{f}\PY{l+s}{ }\PY{l+s}{M}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{r}\PY{l+s}{i}\PY{l+s}{c}\PY{l+s}{e}\PY{l+s}{s}\PY{l+s}{:}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{s}\PY{l+s}{*}\PY{l+s}{n}\PY{l+s}{E}\PY{l+s}{l}\PY{l+s}{e}\PY{l+s}{m}\PY{l+s}{e}\PY{l+s}{n}\PY{l+s}{t}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{S}\PY{l+s}{i}\PY{l+s}{m}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
    \PY{n}{nElements} \PY{o}{=} \PY{n}{nActions}\PY{o}{\PYZca{}}\PY{n}{nPlayers}
    \PY{n}{cov} \PY{o}{=} \PY{k+kt}{Matrix}\PY{p}{(}\PY{l+m+mf}{1.0}\PY{n+nb}{I}\PY{p}{,} \PY{n}{nPlayers} \PY{o}{*} \PY{n}{nElements}\PY{p}{,} \PY{n}{nPlayers} \PY{o}{*} \PY{n}{nElements}\PY{p}{)}

    \PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}\PY{l+s}{ }\PY{l+s}{C}\PY{l+s}{y}\PY{l+s}{c}\PY{l+s}{l}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{t}\PY{l+s}{h}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{u}\PY{l+s}{g}\PY{l+s}{h}\PY{l+s}{ }\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{h}\PY{l+s}{ }\PY{l+s}{o}\PY{l+s}{f}\PY{l+s}{ }\PY{l+s}{t}\PY{l+s}{h}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{c}\PY{l+s}{o}\PY{l+s}{m}\PY{l+s}{b}\PY{l+s}{i}\PY{l+s}{n}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{n}\PY{l+s}{d}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{s}\PY{l+s}{s}\PY{l+s}{i}\PY{l+s}{g}\PY{l+s}{n}\PY{l+s}{ }\PY{l+s}{t}\PY{l+s}{h}\PY{l+s}{e}\PY{l+s}{m}\PY{l+s}{ }\PY{l+s}{t}\PY{l+s}{h}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{p}\PY{l+s}{p}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{p}\PY{l+s}{r}\PY{l+s}{i}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{G}\PY{l+s}{a}\PY{l+s}{m}\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{ }\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
    \PY{k}{for} \PY{n}{c} \PY{k+kp}{in} \PY{n}{allCombos}
        \PY{n}{cov}\PY{p}{[}\PY{n}{c}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{c}\PY{p}{[}\PY{l+m+mi}{2}\PY{o}{:}\PY{k}{end}\PY{p}{]}\PY{p}{]} \PY{o}{.=} \PY{n}{Gamma}\PY{o}{/}\PY{p}{(}\PY{n}{nPlayers}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
        \PY{n}{cov}\PY{p}{[}\PY{n}{c}\PY{p}{[}\PY{l+m+mi}{2}\PY{o}{:}\PY{k}{end}\PY{p}{]}\PY{p}{,} \PY{n}{c}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]} \PY{o}{.=} \PY{n}{Gamma}\PY{o}{/}\PY{p}{(}\PY{n}{nPlayers}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
    \PY{k}{end}

    \PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}\PY{l+s}{ }\PY{l+s}{d}\PY{l+s}{r}\PY{l+s}{a}\PY{l+s}{w}\PY{l+s}{ }\PY{l+s}{f}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{m}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{ }\PY{l+s}{G}\PY{l+s}{a}\PY{l+s}{u}\PY{l+s}{s}\PY{l+s}{s}\PY{l+s}{i}\PY{l+s}{a}\PY{l+s}{n}\PY{l+s}{ }\PY{l+s}{u}\PY{l+s}{s}\PY{l+s}{i}\PY{l+s}{n}\PY{l+s}{g}\PY{l+s}{ }\PY{l+s}{t}\PY{l+s}{h}\PY{l+s}{i}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{c}\PY{l+s}{o}\PY{l+s}{v}\PY{l+s}{a}\PY{l+s}{r}\PY{l+s}{i}\PY{l+s}{a}\PY{l+s}{n}\PY{l+s}{c}\PY{l+s}{e}\PY{l+s}{ }\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{r}\PY{l+s}{i}\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}

    \PY{k}{return} \PY{n}{rand}\PY{p}{(}\PY{n}{MvNormal}\PY{p}{(}\PY{n}{zeros}\PY{p}{(}\PY{n}{nPlayers} \PY{o}{*} \PY{n}{nElements}\PY{p}{)}\PY{p}{,} \PY{n}{cov}\PY{p}{)}\PY{p}{,} \PY{n}{nSim}\PY{p}{)}

\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{getActionProbs}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{agentParams}\PY{p}{)}
    \PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{q}\PY{l+s}{V}\PY{l+s}{a}\PY{l+s}{l}\PY{l+s}{u}\PY{l+s}{e}\PY{l+s}{s}\PY{l+s}{:}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{S}\PY{l+s}{i}\PY{l+s}{m}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{r}\PY{l+s}{e}\PY{l+s}{t}\PY{l+s}{u}\PY{l+s}{r}\PY{l+s}{n}\PY{l+s}{:}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{S}\PY{l+s}{i}\PY{l+s}{m}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
    \PY{n}{alpha}\PY{p}{,} \PY{n}{tau}\PY{p}{,} \PY{n}{gamma} \PY{o}{=} \PY{n}{agentParams}

    \PY{k}{return} \PY{n}{exp}\PY{o}{.}\PY{p}{(}\PY{n}{tau} \PY{o}{*} \PY{n}{qValues}\PY{p}{)}\PY{o}{./}\PY{n}{sum}\PY{p}{(}\PY{n}{exp}\PY{o}{.}\PY{p}{(}\PY{n}{tau} \PY{o}{*} \PY{n}{qValues}\PY{p}{)}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{chooseActions}\PY{p}{(}\PY{n}{actionProbs}\PY{p}{,} \PY{n}{gameParams}\PY{p}{)}
    \PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{r}\PY{l+s}{g}\PY{l+s}{:}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{b}\PY{l+s}{s}\PY{l+s}{:}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{A}\PY{l+s}{c}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{S}\PY{l+s}{i}\PY{l+s}{m}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{r}\PY{l+s}{e}\PY{l+s}{t}\PY{l+s}{u}\PY{l+s}{r}\PY{l+s}{n}\PY{l+s}{:}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{P}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{y}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{S}\PY{l+s}{i}\PY{l+s}{m}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}

    \PY{n}{nSim}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions} \PY{o}{=} \PY{n}{gameParams}

    \PY{k}{return} \PY{p}{[}\PY{p}{[}\PY{n}{rand}\PY{p}{(}\PY{n}{Bernoulli}\PY{p}{(}\PY{n}{actionProbs}\PY{p}{[}\PY{n}{p}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{n}{s}\PY{p}{]}\PY{p}{)}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1} \PY{k}{for} \PY{n}{p}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nPlayers}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{findPayoffs}\PY{p}{(}\PY{n}{choices}\PY{p}{,} \PY{n}{gameParams}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{actions}\PY{p}{,} \PY{n}{payoffs}\PY{p}{)}
    \PY{n}{nSim}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions} \PY{o}{=} \PY{n}{gameParams}

    \PY{n}{choiceIdx} \PY{o}{=} \PY{p}{[}\PY{n}{corr}\PY{p}{[}\PY{n}{findall}\PY{p}{(}\PY{n}{x} \PY{o}{\PYZhy{}}\PY{o}{\PYZgt{}} \PY{n}{x}\PY{o}{==}\PY{n}{tuple}\PY{p}{(}\PY{n}{choices}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{o}{.}\PY{o}{.}\PY{o}{.}\PY{p}{)}\PY{p}{,} \PY{n}{actions}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}
    \PY{k}{return} \PY{p}{[}\PY{n}{payoffs}\PY{p}{[}\PY{n}{choiceIdx}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{,} \PY{n}{s}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{qUpdate!}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{payoffs}\PY{p}{,} \PY{n}{gameParams}\PY{p}{,} \PY{n}{agentParams}\PY{p}{,} \PY{n}{correlations}\PY{p}{,} \PY{n}{actions}\PY{p}{)}

    \PY{n}{nSim}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions} \PY{o}{=} \PY{n}{gameParams}
    \PY{n}{alpha}\PY{p}{,} \PY{n}{tau}\PY{p}{,} \PY{n}{gamma} \PY{o}{=} \PY{n}{agentParams}

    \PY{n}{actionProbs} \PY{o}{=} \PY{n}{getActionProbs}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{agentParams}\PY{p}{)}
    \PY{n}{bChoice} \PY{o}{=} \PY{n}{chooseActions}\PY{p}{(}\PY{n}{actionProbs}\PY{p}{,} \PY{n}{gameParams}\PY{p}{)}
    \PY{n}{rewards} \PY{o}{=} \PY{n}{findPayoffs}\PY{p}{(}\PY{n}{bChoice}\PY{p}{,} \PY{n}{gameParams}\PY{p}{,} \PY{n}{correlations}\PY{p}{,} \PY{n}{actions}\PY{p}{,} \PY{n}{payoffs}\PY{p}{)}

    \PY{n}{update} \PY{o}{=} \PY{p}{[}\PY{n}{rewards}\PY{p}{[}\PY{n}{s}\PY{p}{]} \PY{o}{\PYZhy{}} \PY{n}{diag}\PY{p}{(}\PY{n}{qValues}\PY{p}{[}\PY{o}{:}\PY{p}{,} \PY{n}{bChoice}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{,} \PY{n}{s}\PY{p}{]}\PY{p}{)} \PY{o}{+} \PY{n}{gamma} \PY{o}{*} \PY{n}{findmax}\PY{p}{(}\PY{n}{qValues}\PY{p}{[}\PY{o}{:}\PY{p}{,} \PY{o}{:}\PY{p}{,} \PY{n}{s}\PY{p}{]}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}

    \PY{k}{for} \PY{n}{s} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}
        \PY{k}{for} \PY{n}{p} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nPlayers}
            \PY{n}{qValues}\PY{p}{[}\PY{n}{p}\PY{p}{,} \PY{n}{bChoice}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{[}\PY{n}{p}\PY{p}{]}\PY{p}{,} \PY{n}{s}\PY{p}{]} \PY{o}{+=} \PY{n}{alpha} \PY{o}{*} \PY{n}{update}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{[}\PY{n}{p}\PY{p}{]}
        \PY{k}{end}
    \PY{k}{end}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{checkminMix}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{,} \PY{n}{nSim}\PY{p}{,} \PY{n}{tol}\PY{p}{)}
    \PY{n}{T} \PY{o}{=} \PY{n}{hcat}\PY{p}{(}\PY{p}{[}\PY{n}{reshape}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{,} \PY{n}{nPlayers} \PY{o}{*} \PY{n}{nSim} \PY{o}{*} \PY{n}{nActions}\PY{p}{)} \PY{k}{for} \PY{n}{i}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{length}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{)}\PY{p}{]}\PY{o}{.}\PY{o}{.}\PY{o}{.}\PY{p}{)}
    \PY{n}{relDiff} \PY{o}{=} \PY{p}{(}\PY{n}{findmax}\PY{p}{(}\PY{n}{T}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]} \PY{o}{\PYZhy{}} \PY{n}{findmin}\PY{p}{(}\PY{n}{T}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{o}{./}\PY{n}{findmin}\PY{p}{(}\PY{n}{T}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}

    \PY{n}{part} \PY{o}{=} \PY{p}{[}\PY{n}{relDiff}\PY{p}{[}\PY{n}{i}\PY{o}{*}\PY{p}{(}\PY{n}{nActions}\PY{o}{*}\PY{n}{nPlayers}\PY{p}{)}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{:}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{nActions}\PY{o}{*}\PY{n}{nPlayers}\PY{p}{)}\PY{p}{]} \PY{k}{for} \PY{n}{i}\PY{o}{=}\PY{l+m+mi}{0}\PY{o}{:}\PY{n}{nSim}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}
    \PY{n}{bRemove} \PY{o}{=} \PY{p}{[}\PY{n}{length}\PY{p}{(}\PY{n}{findall}\PY{p}{(}\PY{n}{x}\PY{o}{\PYZhy{}}\PY{o}{\PYZgt{}}\PY{n}{x}\PY{o}{\PYZlt{}}\PY{l+m+mf}{0.01}\PY{p}{,} \PY{n}{p}\PY{p}{)}\PY{p}{)}\PY{o}{\PYZgt{}=}\PY{n}{length}\PY{p}{(}\PY{n}{p}\PY{p}{)} \PY{k}{for} \PY{n}{p} \PY{k+kp}{in} \PY{n}{part}\PY{p}{]}

    \PY{k}{return} \PY{n}{bRemove}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{alpha} \PY{o}{=} \PY{l+m+mf}{0.01}
\PY{n}{tau} \PY{o}{=} \PY{l+m+mf}{0.05}
\PY{n}{gamma} \PY{o}{=} \PY{l+m+mf}{0.1}

\PY{n}{initnSim} \PY{o}{=} \PY{l+m+mi}{15}
\PY{n}{nPlayers} \PY{o}{=} \PY{l+m+mi}{3}
\PY{n}{nActions} \PY{o}{=} \PY{l+m+mi}{5}

\PY{n}{Gamma} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mf}{0.5}

\PY{c}{\PYZsh{} gameParams = (nSim, nPlayers, nActions)}
\PY{c}{\PYZsh{} agentParams = (alpha, tau, gamma)}

\PY{n}{t0} \PY{o}{=} \PY{l+m+mi}{5000}
\PY{n}{actions}\PY{p}{,} \PY{n}{corr} \PY{o}{=} \PY{n}{generateCorrespondences}\PY{p}{(}\PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}

\PY{n}{nIter} \PY{o}{=} \PY{n}{trunc}\PY{p}{(}\PY{k+kt}{Int}\PY{p}{,} \PY{l+m+mf}{5e4}\PY{p}{)}

\PY{n}{allconv} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n+nd}{@showprogress} \PY{k}{for} \PY{n}{a} \PY{k+kp}{in} \PY{n}{LinRange}\PY{p}{(}\PY{l+m+mf}{1e\PYZhy{}2}\PY{p}{,} \PY{l+m+mf}{5e\PYZhy{}2}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
    \PY{k+kd}{global} \PY{n}{alpha} \PY{o}{=} \PY{n}{a}
    \PY{k}{for} \PY{n}{Gamma} \PY{k+kp}{in} \PY{n}{LinRange}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
        \PY{k+kd}{global} \PY{n}{nSim} \PY{o}{=} \PY{n}{initnSim}

        \PY{n}{qValues} \PY{o}{=} \PY{n}{rand}\PY{p}{(}\PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nSim}\PY{p}{)}
        \PY{n}{payoffs} \PY{o}{=} \PY{n}{generateGames}\PY{p}{(}\PY{n}{Gamma}\PY{p}{,} \PY{n}{nSim}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}
        \PY{n}{actionTracker} \PY{o}{=} \PY{p}{[}\PY{p}{]}

        \PY{n}{converged} \PY{o}{=} \PY{l+m+mi}{0}

        \PY{k}{for} \PY{n}{cIter} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nIter}

            \PY{k}{if} \PY{n}{cIter}\PY{o}{==}\PY{n}{t0}
                \PY{n}{actionTracker} \PY{o}{=} \PY{p}{[}\PY{p}{]}
            \PY{k}{end}

            \PY{k}{if} \PY{n}{cIter}\PY{o}{\PYZpc{}}\PY{n}{t0}\PY{o}{==}\PY{l+m+mi}{0} \PY{o}{\PYZam{}\PYZam{}} \PY{n}{cIter!}\PY{o}{=}\PY{l+m+mi}{0} \PY{o}{\PYZam{}\PYZam{}} \PY{n}{cIter!}\PY{o}{=}\PY{n}{t0}
                \PY{n}{bRemove} \PY{o}{=} \PY{n}{checkminMix}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{,} \PY{n}{nSim}\PY{p}{,} \PY{l+m+mf}{1e\PYZhy{}2}\PY{p}{)}
                \PY{n}{removeIdx} \PY{o}{=} \PY{n}{findall}\PY{p}{(}\PY{n}{bRemove}\PY{p}{)}
                \PY{n}{qValues} \PY{o}{=} \PY{n}{qValues}\PY{p}{[}\PY{o}{:}\PY{p}{,} \PY{o}{:}\PY{p}{,} \PY{n}{setdiff}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{:}\PY{k}{end}\PY{p}{,} \PY{n}{removeIdx}\PY{p}{)}\PY{p}{]}
                \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoffs}\PY{p}{[}\PY{o}{:}\PY{p}{,} \PY{n}{setdiff}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{:}\PY{k}{end}\PY{p}{,} \PY{n}{removeIdx}\PY{p}{)}\PY{p}{]}
                \PY{n}{nSim} \PY{o}{\PYZhy{}=} \PY{n}{length}\PY{p}{(}\PY{n}{removeIdx}\PY{p}{)}
                \PY{n}{converged} \PY{o}{+=} \PY{n}{length}\PY{p}{(}\PY{n}{removeIdx}\PY{p}{)}

                \PY{n}{actionTracker} \PY{o}{=} \PY{p}{[}\PY{p}{]} 
            \PY{k}{end}

            \PY{k}{if} \PY{n}{nSim} \PY{o}{\PYZlt{}=} \PY{l+m+mi}{0}
                \PY{k}{break}
            \PY{k}{end}

            \PY{n}{gameParams} \PY{o}{=} \PY{p}{(}\PY{n}{nSim}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions}\PY{p}{)}
            \PY{n}{agentParams} \PY{o}{=} \PY{p}{(}\PY{n}{alpha}\PY{p}{,} \PY{n}{tau}\PY{p}{,} \PY{n}{gamma}\PY{p}{)}

            \PY{n}{qUpdate!}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{payoffs}\PY{p}{,} \PY{n}{gameParams}\PY{p}{,} \PY{n}{agentParams}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{actions}\PY{p}{)}
            \PY{n}{append!}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{,} \PY{p}{[}\PY{n}{getActionProbs}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{agentParams}\PY{p}{)}\PY{p}{]}\PY{p}{)}

        \PY{k}{end}
        \PY{n}{append!}\PY{p}{(}\PY{n}{allconv}\PY{p}{,} \PY{p}{[}\PY{n}{alpha}\PY{p}{,} \PY{n}{Gamma}\PY{p}{,} \PY{n}{converged}\PY{o}{/}\PY{n}{initnSim}\PY{p}{]}\PY{p}{)}
    \PY{k}{end}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{a} \PY{o}{=} \PY{n}{reshape}\PY{p}{(}\PY{n}{allconv}\PY{p}{[}\PY{l+m+mi}{3}\PY{o}{:}\PY{l+m+mi}{3}\PY{o}{:}\PY{k}{end}\PY{p}{]}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}\PY{p}{[}\PY{k}{end}\PY{o}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{o}{:}\PY{l+m+mi}{1}\PY{p}{,} \PY{o}{:}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{py}\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}
\PY{l+s}{d}\PY{l+s}{e}\PY{l+s}{f}\PY{l+s}{ }\PY{l+s}{p}\PY{l+s}{l}\PY{l+s}{o}\PY{l+s}{t}\PY{l+s}{H}\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{p}\PY{l+s}{(}\PY{l+s}{a}\PY{l+s}{)}\PY{l+s}{:}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{m}\PY{l+s}{p}\PY{l+s}{o}\PY{l+s}{r}\PY{l+s}{t}\PY{l+s}{ }\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{p}\PY{l+s}{l}\PY{l+s}{o}\PY{l+s}{t}\PY{l+s}{l}\PY{l+s}{i}\PY{l+s}{b}\PY{l+s}{.}\PY{l+s}{p}\PY{l+s}{y}\PY{l+s}{p}\PY{l+s}{l}\PY{l+s}{o}\PY{l+s}{t}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{p}\PY{l+s}{l}\PY{l+s}{t}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{m}\PY{l+s}{p}\PY{l+s}{o}\PY{l+s}{r}\PY{l+s}{t}\PY{l+s}{ }\PY{l+s}{s}\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{b}\PY{l+s}{o}\PY{l+s}{r}\PY{l+s}{n}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{s}\PY{l+s}{n}\PY{l+s}{s}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{i}\PY{l+s}{m}\PY{l+s}{p}\PY{l+s}{o}\PY{l+s}{r}\PY{l+s}{t}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{u}\PY{l+s}{m}\PY{l+s}{p}\PY{l+s}{y}\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{s}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{p}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{=}\PY{l+s}{ }\PY{l+s}{s}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{.}\PY{l+s}{h}\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{p}\PY{l+s}{(}\PY{l+s}{a}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{v}\PY{l+s}{m}\PY{l+s}{i}\PY{l+s}{n}\PY{l+s}{=}\PY{l+s}{0}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{v}\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{x}\PY{l+s}{=}\PY{l+s}{1}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{x}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{c}\PY{l+s}{k}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{b}\PY{l+s}{e}\PY{l+s}{l}\PY{l+s}{s}\PY{l+s}{=}\PY{l+s}{n}\PY{l+s}{p}\PY{l+s}{.}\PY{l+s}{l}\PY{l+s}{i}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{p}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{e}\PY{l+s}{(}\PY{l+s}{1}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{5}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{u}\PY{l+s}{m}\PY{l+s}{=}\PY{l+s}{2}\PY{l+s}{0}\PY{l+s}{)}\PY{l+s}{.}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{u}\PY{l+s}{n}\PY{l+s}{d}\PY{l+s}{(}\PY{l+s}{2}\PY{l+s}{)}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{y}\PY{l+s}{t}\PY{l+s}{i}\PY{l+s}{c}\PY{l+s}{k}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{b}\PY{l+s}{e}\PY{l+s}{l}\PY{l+s}{s}\PY{l+s}{=}\PY{l+s}{n}\PY{l+s}{p}\PY{l+s}{.}\PY{l+s}{l}\PY{l+s}{i}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{p}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{e}\PY{l+s}{(}\PY{l+s}{\PYZhy{}}\PY{l+s}{1}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{0}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{n}\PY{l+s}{u}\PY{l+s}{m}\PY{l+s}{=}\PY{l+s}{2}\PY{l+s}{0}\PY{l+s}{)}\PY{l+s}{[}\PY{l+s}{\PYZhy{}}\PY{l+s}{1}\PY{l+s}{:}\PY{l+s}{:}\PY{l+s}{\PYZhy{}}\PY{l+s}{1}\PY{l+s}{]}\PY{l+s}{.}\PY{l+s}{r}\PY{l+s}{o}\PY{l+s}{u}\PY{l+s}{n}\PY{l+s}{d}\PY{l+s}{(}\PY{l+s}{2}\PY{l+s}{)}\PY{l+s}{)}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{a}\PY{l+s}{x}\PY{l+s}{.}\PY{l+s}{s}\PY{l+s}{e}\PY{l+s}{t}\PY{l+s}{(}\PY{l+s}{x}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{b}\PY{l+s}{e}\PY{l+s}{l}\PY{l+s}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{α}\PY{l+s}{ }\PY{l+s}{(}\PY{l+s}{x}\PY{l+s}{ }\PY{l+s}{1}\PY{l+s}{e}\PY{l+s}{\PYZhy{}}\PY{l+s}{2}\PY{l+s}{)}\PY{l+s}{\PYZdq{}}\PY{l+s}{,}\PY{l+s}{ }\PY{l+s}{y}\PY{l+s}{l}\PY{l+s}{a}\PY{l+s}{b}\PY{l+s}{e}\PY{l+s}{l}\PY{l+s}{=}\PY{l+s}{\PYZdq{}}\PY{l+s}{Γ}\PY{l+s}{\PYZdq{}}\PY{l+s}{)}
\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{ }\PY{l+s}{p}\PY{l+s}{l}\PY{l+s}{t}\PY{l+s}{.}\PY{l+s}{s}\PY{l+s}{h}\PY{l+s}{o}\PY{l+s}{w}\PY{l+s}{(}\PY{l+s}{)}
\PY{l+s}{\PYZdq{}\PYZdq{}\PYZdq{}}

\PY{n}{plotHeatmap}\PY{p}{(}\PY{n}{a}\PY{p}{)} \PY{o}{=} \PY{n}{py}\PY{l+s}{\PYZdq{}}\PY{l+s}{p}\PY{l+s}{l}\PY{l+s}{o}\PY{l+s}{t}\PY{l+s}{H}\PY{l+s}{e}\PY{l+s}{a}\PY{l+s}{t}\PY{l+s}{m}\PY{l+s}{a}\PY{l+s}{p}\PY{l+s}{\PYZdq{}}\PY{p}{(}\PY{n}{a}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{using} \PY{n}{PyPlot}
\PY{n}{plotHeatmap}\PY{p}{(}\PY{n}{a}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{qValues} \PY{o}{=} \PY{n}{rand}\PY{p}{(}\PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nSim}\PY{p}{)}
\PY{n}{payoffs} \PY{o}{=} \PY{n}{generateGames}\PY{p}{(}\PY{n}{Gamma}\PY{p}{,} \PY{n}{nSim}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}

\PY{n}{probs} \PY{o}{=} \PY{n}{getActionProbs}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{p}{(}\PY{l+m+mf}{0.05}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
\PY{n}{bChoice} \PY{o}{=} \PY{p}{[}\PY{p}{[}\PY{n}{rand}\PY{p}{(}\PY{n}{Bernoulli}\PY{p}{(}\PY{n}{probs}\PY{p}{[}\PY{n}{p}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{n}{s}\PY{p}{]}\PY{p}{)}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1} \PY{k}{for} \PY{n}{p}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nPlayers}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}

\PY{n}{choiceIdx} \PY{o}{=} \PY{p}{[}\PY{n}{corr}\PY{p}{[}\PY{n}{findall}\PY{p}{(}\PY{n}{x} \PY{o}{\PYZhy{}}\PY{o}{\PYZgt{}} \PY{n}{x}\PY{o}{==}\PY{n}{tuple}\PY{p}{(}\PY{n}{bChoice}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{o}{.}\PY{o}{.}\PY{o}{.}\PY{p}{)}\PY{p}{,} \PY{n}{actions}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}

\PY{n}{rewards} \PY{o}{=} \PY{p}{[}\PY{n}{payoffs}\PY{p}{[}\PY{n}{choiceIdx}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{,} \PY{n}{s}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}

\PY{n}{update} \PY{o}{=} \PY{p}{[}\PY{n}{rewards}\PY{p}{[}\PY{n}{s}\PY{p}{]} \PY{o}{\PYZhy{}} \PY{n}{diag}\PY{p}{(}\PY{n}{qValues}\PY{p}{[}\PY{o}{:}\PY{p}{,} \PY{n}{bChoice}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{,} \PY{n}{s}\PY{p}{]}\PY{p}{)} \PY{o}{+} \PY{n}{gamma} \PY{o}{*} \PY{n}{findmax}\PY{p}{(}\PY{n}{qValues}\PY{p}{[}\PY{o}{:}\PY{p}{,} \PY{o}{:}\PY{p}{,} \PY{n}{s}\PY{p}{]}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]} \PY{k}{for} \PY{n}{s}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}\PY{p}{]}
\PY{c}{\PYZsh{} [i for i in bChoice[1]]}
\PY{k}{for} \PY{n}{s} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nSim}
    \PY{k}{for} \PY{n}{p} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nPlayers}
        \PY{n}{qValues}\PY{p}{[}\PY{n}{p}\PY{p}{,} \PY{n}{bChoice}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{[}\PY{n}{p}\PY{p}{]}\PY{p}{,} \PY{n}{s}\PY{p}{]} \PY{o}{+=} \PY{n}{alpha} \PY{o}{*} \PY{n}{update}\PY{p}{[}\PY{n}{s}\PY{p}{]}\PY{p}{[}\PY{n}{p}\PY{p}{]}
    \PY{k}{end}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{tau} \PY{o}{=} \PY{l+m+mf}{0.05}
\PY{n}{alpha} \PY{o}{=} \PY{l+m+mf}{0.02}
\PY{n}{gamma} \PY{o}{=} \PY{l+m+mf}{0.1}

\PY{n}{initnSim} \PY{o}{=} \PY{l+m+mi}{20}
\PY{n}{nActions} \PY{o}{=} \PY{l+m+mi}{2}

\PY{n}{t0} \PY{o}{=} \PY{l+m+mi}{25000}

\PY{n}{nIter} \PY{o}{=} \PY{n}{trunc}\PY{p}{(}\PY{k+kt}{Int}\PY{p}{,} \PY{l+m+mf}{5e4}\PY{p}{)}

\PY{n}{allVars} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function} \PY{n}{getVariance}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{)}

    \PY{n}{T} \PY{o}{=} \PY{n}{hcat}\PY{p}{(}\PY{p}{[}\PY{n}{reshape}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{,} \PY{n}{nPlayers} \PY{o}{*} \PY{n}{nSim} \PY{o}{*} \PY{n}{nActions}\PY{p}{)} \PY{k}{for} \PY{n}{i}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{:}\PY{n}{length}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{)}\PY{p}{]}\PY{o}{.}\PY{o}{.}\PY{o}{.}\PY{p}{)}
    \PY{n}{var} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1} \PY{o}{/}\PY{n}{length}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{)}\PY{p}{)} \PY{o}{*} \PY{n}{sum}\PY{p}{(}\PY{n}{T}\PY{o}{.\PYZca{}}\PY{l+m+mi}{2}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{length}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{)}\PY{p}{)} \PY{o}{*} \PY{n}{sum}\PY{p}{(}\PY{n}{T}\PY{p}{,} \PY{n}{dims}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{)}\PY{p}{)}\PY{o}{.\PYZca{}}\PY{l+m+mi}{2}
    \PY{n}{part} \PY{o}{=} \PY{p}{[}\PY{n}{var}\PY{p}{[}\PY{n}{i}\PY{o}{*}\PY{p}{(}\PY{n}{nActions}\PY{o}{*}\PY{n}{nPlayers}\PY{p}{)}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{:}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{nActions}\PY{o}{*}\PY{n}{nPlayers}\PY{p}{)}\PY{p}{]} \PY{k}{for} \PY{n}{i}\PY{o}{=}\PY{l+m+mi}{0}\PY{o}{:}\PY{n}{nSim}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}

    \PY{k}{return} \PY{n}{mean}\PY{p}{(}\PY{p}{[}\PY{n}{mean}\PY{p}{(}\PY{n}{p}\PY{p}{)} \PY{k}{for} \PY{n}{p} \PY{k+kp}{in} \PY{n}{part}\PY{p}{]}\PY{p}{)}

\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n+nd}{@showprogress} \PY{k}{for} \PY{n}{p} \PY{o}{=} \PY{l+m+mi}{3}\PY{o}{:}\PY{l+m+mi}{12}
    \PY{k+kd}{global} \PY{n}{nPlayers} \PY{o}{=} \PY{n}{p}
    \PY{n}{actions}\PY{p}{,} \PY{n}{corr} \PY{o}{=} \PY{n}{generateCorrespondences}\PY{p}{(}\PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}

    \PY{n}{varGamma} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n+nd}{@show} \PY{n}{nPlayers}
    \PY{k}{for} \PY{n}{Gamma} \PY{k+kp}{in} \PY{n}{LinRange}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{10}\PY{p}{)}

        \PY{k+kd}{global} \PY{n}{nSim} \PY{o}{=} \PY{n}{initnSim}

        \PY{n}{qValues} \PY{o}{=} \PY{n}{rand}\PY{p}{(}\PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nSim}\PY{p}{)}
        \PY{n}{payoffs} \PY{o}{=} \PY{n}{generateGames}\PY{p}{(}\PY{n}{Gamma}\PY{p}{,} \PY{n}{nSim}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{nActions}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{)}

        \PY{n}{actionTracker} \PY{o}{=} \PY{p}{[}\PY{p}{]}

        \PY{k}{for} \PY{n}{cIter} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{:}\PY{n}{nIter}

            \PY{n}{gameParams} \PY{o}{=} \PY{p}{(}\PY{n}{nSim}\PY{p}{,} \PY{n}{nPlayers}\PY{p}{,} \PY{n}{nActions}\PY{p}{)}
            \PY{n}{agentParams} \PY{o}{=} \PY{p}{(}\PY{n}{alpha}\PY{p}{,} \PY{n}{tau}\PY{p}{,} \PY{n}{gamma}\PY{p}{)}

            \PY{n}{qUpdate!}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{payoffs}\PY{p}{,} \PY{n}{gameParams}\PY{p}{,} \PY{n}{agentParams}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{actions}\PY{p}{)}

            \PY{k}{if} \PY{n}{cIter} \PY{o}{\PYZgt{}} \PY{n}{t0}
                \PY{n}{append!}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{,} \PY{p}{[}\PY{n}{getActionProbs}\PY{p}{(}\PY{n}{qValues}\PY{p}{,} \PY{n}{agentParams}\PY{p}{)}\PY{p}{]}\PY{p}{)}
            \PY{k}{end}

        \PY{k}{end}
        \PY{n}{append!}\PY{p}{(}\PY{n}{varGamma}\PY{p}{,} \PY{n}{getVariance}\PY{p}{(}\PY{n}{actionTracker}\PY{p}{)}\PY{p}{)}
    \PY{k}{end}

    \PY{n}{append!}\PY{p}{(}\PY{n}{allVars}\PY{p}{,} \PY{p}{[}\PY{n}{mean}\PY{p}{(}\PY{n}{varGamma}\PY{p}{)}\PY{p}{,} \PY{n}{std}\PY{p}{(}\PY{n}{varGamma}\PY{p}{)}\PY{p}{]}\PY{p}{)}
\PY{k}{end}
\end{Verbatim}
\end{tcolorbox}

    % Add a bibliography block to the postdoc

\end{document}

### 2021-02-18 Documents/ChaoticDynamics/IJCAI 2021/ijcai.tex
Three Body QL problems first added

%%%% ijcai21.tex

\typeout{IJCAI--21 Instructions for Authors}

% These are the instructions for authors for IJCAI-21.

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}

% Use the postscript times font!
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\urlstyle{same}
\usepackage[export]{adjustbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%   MACROS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\xmu}[2]{x_{#1_#2}^{#2}(t)}
\newcommand{\xnotmu}[2]{x_{#1_#2}^{#2}}
\newcommand{\xmudash}[2]{x_{#1_#2}^{#2}(t')}
\newcommand{\payoff}[2]{P^{#2}_{#1_#2, #1_{-#2}}}

\newcommand{\dxmu}[1]{\dot{x}_{#1_\mu}^{\mu} (t)}
\newcommand{\dnotxmu}[1]{\dot{x}_{#1_\mu}^{\mu}}
\newcommand{\hxmu}[1]{\hat{x}_{#1_\mu}^{\mu} (t)}
\newcommand{\hnotxmu}[1]{\hat{x}_{#1_\mu}^{\mu}}
\newcommand{\hxnu}[1]{\hat{x}_{#1_\nu}^{\nu} (t)}
\newcommand{\hxmudash}[1]{\hat{x}_{#1_\mu}^{\mu} (t')}
\newcommand{\hxnudash}[1]{\hat{x}_{#1_\nu}^{\nu} (t')}

\newcommand{\txmu}[2]{\tilde{x}_{#1_#2}^{#2}(t)}
\newcommand{\dtxmu}[2]{\dot{\tilde{x}}_{#1_#2}^{#2}(t)}
\newcommand{\tpayoff}[2]{\tilde{P}^{#2}_{#1_#2, #1_{-#2}}}
\newcommand{\talpha}{\tilde{\alpha}}
\newcommand{\ttau}{\tilde{\tau}}
\newcommand{\htau}{\hat{\tau}}
\newcommand{\xfixed}{x_\infty}
\newcommand{\ezerof}{\eta_{0, \infty}}
\newcommand{\eonef}{\eta_{1, \infty}}

\newcommand{\xpert}{\hat{x}(t)}
\newcommand{\xpertdash}{\hat{x}(t')}
\newcommand{\ezeropert}{\hat{\eta}_0(t)}
\newcommand{\eonepert}{\hat{\eta}_1(t)}

\newcommand{\eom}{\frac{\dxmu{i}}{\xmu{i}{\mu}} - \alpha \ttau \left ( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) + \\ \alpha \htau \left ( \frac{1}{\sqrt{N}} \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \right ) - \talpha \rho^{\mu}_{i}(t)}

\usepackage{xcolor} % REMOVE THIS AT THE END
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}
\newcommand\ah[1]{\textcolor{red}{AH: #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% the following package is optional:
%\usepackage{latexsym}

% See https://www.overleaf.com/learn/latex/theorems_and_proofs
% for a nice explanation of how to define new theorems, but keep
% in mind that the amsthm package is already included in this
% template and that you must *not* alter the styling.
\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

%PDF Info Is REQUIRED.
\pdfinfo{
/TemplateVersion (IJCAI.2021.0)
}

\title{Stability and Chaos in Multi-Agent Reinforcement Learning}

% Single author syntax
\author{Submission number 3289
%Aamal Hussain$^1$\footnote{Contact Author}\And
%Francesco Belardinelli$^1$\\
%\affiliations
%$^1$Imperial College London\\
%\emails
%\{aamal.hussain15, francesco.belardinelli\}@imperial.ac.uk,
}

\begin{document}

\maketitle

\begin{abstract}

Modelling the dynamics of Q-Learning is an active and important topic for the sake of developing an \textit{a priori} understanding of multi-agent reinforcement learning. In this paper, we apply methods from evolutionary game theory to analyse the stability of Q-Learning in $p$-player games with generalised payoff matrices. We determine the effect that the number of players, payoff correlations, and agent parameters have on the likelihood that the system converges to a stable fixed point, as opposed to displaying unstable behaviour. 
%
This study allows for parameters to be appropriately chosen to ensure the safe convergence of a learning algorithm and as a first step towards understanding the range of behaviours that can be displayed by 
%learning 
using Q-learning. We validate our theoretical results through numerical simulations and show that, within the bounds of experimental error, the region of instability can be characterised by the learning dynamics.

\end{abstract}

\section{Introduction}
%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%

\label{sec::Intro}

Single-agent reinforcement learning (RL) is a well-established
framework for allowing agents to learn optimal strategies when trained
on an iterated task \cite{Sutton2018}. For the realisation of complex tasks,
such as air traffic control, market negotiations, and multi-robot
coordination, however, it is required that the system be modelled as a
multi-agent system (MAS). Such systems are less well-understood, since a given agent is tasked with
optimising a reward function that depends not only on a,
non-stationary environment, but also on the actions of other, possibly
loosely coupled, agents \cite{schwartz:reinforcement}.

It is, therefore, of paramount importance to develop a strong
theoretical understanding of multi-agent reinforcement learning (MARL)
to allow an \textit{a priori} understanding of the behaviour of a given
learning algorithm. Fortunately, the study of MAS is not unique to the
field of AI and has been extensively investigated from the point of view of
economics and game theory as well
\cite{shoham_leyton-brown_2008,leslie:iql}. In particular,
evolutionary game theory (EGT) considers the problem of a MAS that is
repeatedly exposed to an iterated game. This idea shares a strong
resemblance with MARL and, in fact, in \cite{tuyls:iteratedgames} it was
shown that techniques from EGT may be fruitfully applied to the analysis of
Q-Learning.

An important result in modelling multi-agent systems from the EGT
perspective is that, when games are learnt and the assumptions of
rationality and perfect information are lifted, games may not converge
to an equilibrium. Instead, as shown in \cite{sanders:prevalence}, the
dynamics may be more complex and even chaotic \cite{strogatz:2000}. In fact, chaotic behaviour has been found in a wide range of learning algorithms \cite{svs:fp,piliouras:chaoticmaps} The present work further
describes to what extent the emergence of such behaviours depends on the
parameters of the games and the learning algorithm.

\paragraph{Contribution}
In this study, we will be considering the question: how does the likelihood of convergent behaviour, as opposed to instability, depend on the parameters of a homogeneous multi-agent system which is trained on an iterated normal-form game using Q-learning?
In investigating this
question, we will make the following assumptions:
%
%\begin{enumerate}
    %\item
    (1) There is a finite set of agents, though its size $p$ can be
      arbitrarily large.
    %\item 
    (2) The agents (sometimes referred to as players) have a discrete strategy space.
%
%  \item 
(3) The agents  are homogeneous, i.e., they all share the same parameters. 
%    
%\end{enumerate}

We find that our analysis gives a strong indication for how the stability of learning depends on its parameters, and that these predictions are confirmed in experiments. Specifically, we find that unstable dynamics become more prominent as the parameters \textit{step length}
$\alpha$ and \textit{intensity of choice} $\tau$  of
Q-learning increase. By comparison, the
correlation $\Gamma$ between payoffs, which measures how cooperative or competitive a game is, has a negligible affect on stability. In addition, we find that regardless of the choice of these
parameters, the likelihood of unstable behaviours increases monotonically with the number of players $p$.

%%%%%%%%%%%%% END INTRO %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%% LIT REVIEW %%%%%%%%%%%%%%%%%%%%%

\paragraph{Related Work}
The theory of evolutionary game dynamics \cite{von-Neumann:games}
considers game-like settings in which agents repeatedly interact
with one another (i.e., `iterated games'). The outcome of these interactions depends on a payoff
matrix; `strong' strategies which maximise the reward are promoted,
whilst `weaker' strategies diminish. The \textit{replicator dynamic}
models this behaviour as a differential equation, and allows one to determine whether, after a
number of iterations, the game is likely to converge to some fixed
equilibrium \cite{shoham_leyton-brown_2008}.

Iterated games are considered imperfect, in that agents make decisions by attempting to anticipate and respond to their opponents' behaviour
based on experience \cite{galla:cycles}.

In such games \cite{galla:complex}, it is found that cycles, as well as more complex behaviours, can emerge when two agents play using the \textit{experience weighted attraction} (EWA) learning algorithm \cite{hocamerer:ewa}. A rigorous theoretical analysis of EWA, results in a method for characterising how complex dynamics, such as chaos or cycles, depends on the game parameters. \cite{sanders:prevalence} extends this analysis to generic $p$-player games, and show that chaotic
dynamics are more likely to be observed as the number $p$ of players
increases.

It is evident, therefore, that in the case of learning on iterated
games, convergence to stable equilibria cannot be taken for granted. It would therefore be fruitful to bring these
analyses from EGT to better understand reinforcement learning from an
AI perspective.

In \cite{tuyls:iteratedgames}, the authors derive a continuous time deterministic approximation of  Q-Learning
and show its relation to the replicator
dynamic. In doing so, they present a dynamical system that
has been used to accurately analyse the behaviour of Q-Learning \cite{bloembergen:survey}. One such analysis is \cite{piliouras:catastrophe} which analyses a variant of the Q-Learning dynamics. The authors show that changes in the exploration parameter (here called the `intensity of choice' $\tau$) can lead to different qualitative behaviours. Their study shares the same general conclusions as our own, though through a different methodology. In addition, we aim also to characterise how the number $p$ of players  and the agent memory $\alpha$ affect the behaviour of Q-learning.

%%%%%%%%%%%%% END LIT REVIEW %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%% PRELIMS %%%%%%%%%%%%%%%%%%%%%

\section{Background on Q-learning}

%Before presenting the technical arguments of this study, 
We now provide the specifics of the types of games and algorithm that we analyse in the subsequent sections.
%
We consider \textit{normal form games} consisting of: a finite set of players, with individual action spaces $\mathcal{A}$ (though we assume that all players share the same strategy space), and payoff functions for each player. The agents choose an action from their strategy space and receive a reward from their payoff matrix depending on the actions of all players. The payoffs remain unchanged across iterations. Examples of these normal form games include the popular Prisoner's Dilemma or Matching Pennies games \cite{tuyls:iteratedgames}.

The Q-learning approach requires
an agent to choose an action $i \in \mathcal{A}$ at step $k$ with probability
%
\begin{equation}
    x_i(k) = \frac{e^{\tau Q_i(k)}}{\sum_j e^{\tau Q_j(k)}}
\end{equation}
%
where $\tau \in [0, \infty)$ is the \textit{intensity of choice} as described at the end of this section, and $Q_i$ denotes the \textit{Q-value} of an action $i$, which is to be updated at each step according to
%
\begin{equation}
\label{eqn::Qupdate}
    Q_i(k+1) = (1 - \alpha) Q_i(k) + \alpha (r + \gamma \max_j Q_j(k))
\end{equation}
%
where $\alpha \in [0, 1]$ is the \textit{step length} parameter described below, $r$ is the immediate reward received, and $\gamma \in [0, 1]$ is the discount factor. Note we use the terms `payoff' and `reward' interchangeably.

By analysing this algorithm, Tuyls et al. derive a continuous-time, deterministic model of Q-learning, and verify empirically its accuracy. This model (which can be found in \cite{tuyls:iteratedgames} and is reproduced in the supplementary material Sec~S2.1 for completeness) 
makes it clear that the long term strategy selection of the agents is dependent on parameters $\alpha$ and $\tau$, as well as the payoffs themselves. In this study, therefore, we aim to establish the nature of this dependence. Specifically, the parameters we consider are:

%\begin{enumerate}
1.~The \textit{step length} $\alpha \in [0, 1]$. Low values of $\alpha$ denote smaller
    updates. Heuristically, we can consider this to be the memory of the agent: lower $\alpha$
    denotes longer memory.

2.~The \textit{intensity of choice} $\tau \in [0, \infty)$,
%as
%      termed by Sanders et al.  \cite{Sanders2018}. This 
which is sometimes
      written as $\beta$ in the literature \cite{piliouras:catastrophe}.  $\tau =
      0$ results in all actions being selected with equal probability,
      regardless of their Q-value, whilst $\tau \rightarrow \infty$
      results in the action with the highest Q-value chosen at every
      step.

3.~The \textit{payoff
      correlation} $\Gamma \in [-1, p-1]$. Since there are an infinite number of realisations
      of the payoff matrices, we parameterise the payoffs by their correlations. To do this, we assume
      that the payoff matrices are drawn from a multi-variate Gaussian
      with mean zero and covariance matrix parameterised by
      $\Gamma$.In the subsequent sections, we will take an average over this Gaussian to determine the expected behaviour a MAS will take where the payoffs have a particular choice of $\Gamma$. $\Gamma = -1$
      indicates a zero-sum game, in which the sum of payoffs for a
      given action across all agents is zero, resulting in a purely
      competitive game. $\Gamma = p-1$ indicates a purely cooperative game
      in which all agents share the same payoffs. The manner in which
      a game is generated from the choice of $\Gamma$ is described in
      (\ref{eqn::Payoffs}) and follows the same procedure as
      outlined in \cite{sanders:prevalence}.
%\end{enumerate}

%%%%%%%%%%%%% THEORY %%%%%%%%%%%%%%%%%%%%%

\section{Stability Analysis of Q-Learning} \label{sec::Theory}

In this section, we determine how the choice of parameters
$\alpha$ and $\tau$, alongside the choice of payoff matrix and the number $p$ of players affects the
stability of the continuous-time model of Q-learning. As the values in the
payoff matrices can take any real number, however, there is an infinite number
of possible realisations of games. Of course, it would not be possible
to analyse every possible game, so we instead follow the procedure
outlined in \cite{coolen:minority,galla:complex} to average over
these realisations (Sec \ref{sec::eff_dyn}). This yields the \textit{effective
dynamics}, the dynamics averaged over all realisations of payoff
matrices. Then, in Sec \ref{sec::stability}, we perform a linear stability analysis on these dynamics around
equilibrium points to determine the conditions under which a fixed
point is stable. As this process is complex, we focus on the main steps in this paper, and refer to the supplementary material for the technical details. Sections from the Supplementary Material are denoted with the prefix S.

\subsection{Generalised Dynamics}
\label{sec::gen_dyn}

Our first point of call is to write  the dynamics of Tuyls et al. for a general $p$-player
game. This yields the dynamics (\ref{eqn::pEOM}), where player $\mu$
chooses action $i_{\mu}$ from its strategy space $\mathcal{A}$ at time
$t$ with probability $\xmu{i}{\mu}$ and receives a reward
$\payoff{i}{\mu}$ from its payoff matrix $P^\mu$ depending on its own
action and the actions of all other agents $i_{-\mu}$, where $i_{-\mu}$ denotes the set $\{ i_\kappa : \kappa \in \{1, 2,
\ldots , p\} \setminus \{\mu\} \}$ and $-i_{\mu}$ denotes the set
$\mathcal{A} \setminus {i_\mu}$.
%
\begin{eqnarray}
\label{eqn::pEOM}
%\begin{split}
    \frac{\dot{\xmu{i}{\mu}}}{\xmu{i}{\mu}} = \alpha \tau \big( \sum_{i_{-\mu}} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} - \\
    \sum_{i_\mu i_{-\mu}} \xmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xmu{i}{\kappa} \big) + \alpha \sum_{j_\mu \in -i_\mu} \xmu{j}{\mu} ln \frac{\xmu{j}{\mu}}{\xmu{i}{\mu}}    \nonumber
%\end{split}
\end{eqnarray}

For the sake of brevity, we sometimes drop the explicit dependence on $t$ in the notation of $\xmu{i}{\mu}$, and allow it to be inferred.

To average over all payoff elements , we assert that they
are generated by a multi-variate Gaussian distribution
with mean zero and covariance given as
%
\begin{equation}
\label{eqn::Payoffs}
%    \begin{split}
        \mathbb{E}\left [ \payoff{i}{\mu} \payoff{i}{\nu} \right] = \begin{cases}
        \frac{1}{N^{p-1}} &  \text{ if } \nu = \mu \\
        \frac{\Gamma}{(p-1) N^{p-1}} & \text{ otherwise. }
        \end{cases}
%    \end{split}
\end{equation}

The motivation for choosing a
Gaussian distribution is to allow for the use of Gaussian identities when
determining the average \cite{Zinn-Justin:QFT}. Furthermore, the domain of the multi-variate Gaussian is over all possible realisations of the payoff elements (i.e., over $\mathbb{R}^{p \cdot N^p}$). This means that we can accurately consider any set of payoff matrices to be drawn from a Gaussian.

\subsection{The Effective Dynamics}
\label{sec::eff_dyn}

Our aim is first find to the corollary of (\ref{eqn::pEOM}) for the case of averaged payoff elements, we call this the `effective dynamics'. In order to find these dynamics we take a similar approach to that outlined in \cite{mezard:spinglass}. The idea is as follows. We first take a path integral over the entire trajectory as the \textit{generating functional} $Z$. This gives a single value which can be assigned to the trajectory. We can then find an expression for the expected value of $Z$ by averaging over all payoff elements, giving $\mathbb{E}[Z]$. Finally, we notice that, in the same way that $Z$ was generated from an equation of motion, so $\mathbb{E}[Z]$ may be considered as generated from an `averaged' equation of motion, which we call the \textit{effective dynamics}. These dynamics, then, form the required average case of (\ref{eqn::pEOM}).

The generating functional of the dynamics (\ref{eqn::pEOM}) is given as

{\small
\begin{equation}
\label{eqn::separatePayoffs}
  \begin{split}
  Z(\Vec{\psi}) = \int D[\Vec{x}, \Vec{\hat{x}}] exp( i \sum_{i, \mu} \int dt [ \hnotxmu{i} (\frac{\dnotxmu{i}}{\xnotmu{i}{\mu}} - \talpha \rho_i^\mu (t) - h_i^\mu (t))]) \\ \times  exp(-i \alpha \ttau \sum_{\mu} \sum_{i_\mu, i_{-\mu}} \int dt [\hnotxmu{i} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xnotmu{i}{\kappa} )])) 
    \\ \times  exp(-i \alpha \ttau \sum_{\mu} \sum_{j_\mu, i_\mu, i_{-\mu}} \int dt [\hnotxmu{j}  \xnotmu{i}{\mu} \payoff{i}{\mu} \prod_{\kappa \neq \mu} \xnotmu{i}{\kappa}])) 
  \\ \times exp(i \sum_{i, \mu}
  \int dt[\xnotmu{i}{\mu} \psi^\mu_i(t)]),
\end{split}
\end{equation}
}

where $\Vec{\psi_i(t)}$ and
$\Vec{\phi_i(t)}$ generate the necessary correlation functions. These act simply as a mathematical tool and will be set to zero at the end of the calculation \cite{coolen:minority}.

The last two exponentials contain the payoff elements of the game. These are randomly generated using a multi-variate gaussian and then held fixed for the rest of the game. We employ the mean and covariance expressions given in (\ref{eqn::Payoffs}) to average over all possible realisations of these elements. This gives us a new form for an averaged generating functional. The technical details of how this averaging is performed is given in the supplementary material (Sec~S2.3-S2.5).

As mentioned, in the same way that (\ref{eqn::pEOM}) gives rise to the functional $Z(\Vec{\psi})$, so the averaged functional can be thought of as having arisen from averaged dynamics, the aforementioned `effective dynamics':
%
\begin{eqnarray}
    \label{eqn::EffectiveDynamics}
%    \begin{split}
            \frac{1}{x} \frac{d}{dt} x(t) & = & \alpha^2 \ttau^2 \Gamma \int dt' \left [G(t, t')C^{p - 2}(t, t') x(t') \right ] \nonumber \\ && + \sqrt{2} \alpha \ttau \eta_1(t) + \sqrt{2} \alpha \htau \eta_0(t) + \talpha \rho(t), 
%    \end{split}
\end{eqnarray}
%
in which we have assumed that all players' actions are independent and drawn from the same initial distribution (i.i.d)
and therefore dropped the distinction between players and strategy components. The terms $G, C, \eta_1, \eta_0$ are correlation functions, generated when averaging the Gaussian, given as: 
%
\begin{eqnarray*}
%    \begin{split}
        C(t, t') & = & \mathbb{E}[x(t) x(t')] \\
        \mathbb{E}[\eta_1(t)] & = & 1, \text{ \space } \mathbb{E}[\eta_1(t) \eta_1(t')]  =  C^{p-1}(t, t') \\
        \mathbb{E}[\eta_0(t)] & = & 1, \text{ \space } \mathbb{E}[\eta_0(t) \eta_0(t')] = C^{p}(t, t') \\
        G(t, t') & = & \mathbb{E}\left [ \frac{\delta x(t)}{ \delta \eta_1(t')} \right].
%    \end{split}
\end{eqnarray*}

It is important to note that the substantial impact of the assumption that all
actions of all agents are i.i.d. This is a strong assumption that removes the interdependency
between agents in the analysis and is required to ensure that (\ref{eqn::EffectiveDynamics}) yields real-valued action probabilities. However, as shown by the experimental
evaluation, it does not produce a strong discrepancy in describing the
qualitative effect on stability caused by parameters $p$, $\alpha$, $\tau$, and $\Gamma$.

\subsection{Linear Stability Analysis}
\label{sec::stability}

In this section we determine the condition under which the effective dynamics will converge to a stable fixed point. The process is as follows. We first find the expression for a fixed point $\xfixed$ of (\ref{eqn::EffectiveDynamics}) by letting $\dot{x}(t)= 0$ and find a linear approximation of (\ref{eqn::EffectiveDynamics}) close to this point. This gives an expression for the dynamics as a function of time. By taking the Fourier transform of this expression, we can examine the behaviour of the system at low frequencies (i.e. at large times) \cite{sewell:fourier}.

%
%\small{
\begin{eqnarray}
    % \begin{split}
    0 & = & \xfixed [ \alpha^2 \ttau^2 \Gamma \xfixed q^{p-2} \chi + \sqrt{2} \alpha \ttau q^{(p-1)/2}z \nonumber \\ && + \sqrt{2} \alpha \htau q^{p/2} z^{p/p-1} + \talpha \rho]
    \label{eqn::fixed_point}
    % \end{split}
\end{eqnarray}
%}
%
where $\chi = \int dt' G(t - t')$, $\eta_0(t) = q^{(p-1)/2}z$, $z$ is
drawn from a Gaussian of zero mean and unit variance. By using (\ref{eqn::fixed_point}) we can
calculate $\xfixed$. We disregard the choice $\xfixed = 0$, since
no action will be chosen with exactly zero probability \cite{coolen:minority}. The expression inside the squared bracket
admits a positive solution only in the region $\Gamma \in [-1, 0]$,
whilst for positive $\Gamma \leq p-1$, the nature of solutions may
not be guaranteed. Therefore, we restrict our analysis to 
%the region
$\Gamma \in [-1, 0]$.

We analyse the stability of (\ref{eqn::EffectiveDynamics}) in a neighbourhood around
this supposed fixed point, by following a similar procedure as in \cite{opper:phase}, in
which the fixed point dynamics are 
%proposed to be 
perturbed by a
disturbance $\xi(t)$ which is drawn from a Gaussian of zero mean and
unit variance. The disturbance causes the values of $x(t)$ and
$\eta_0(t), \eta_1(t)$ to deviate from their fixed point position
$\xfixed, \ezerof, \eonef$ by an amount $\xpert, \ezeropert,
\eonepert$.  If we consider only the terms which are linear in these
perturbations (since the deviations are considered to be small), we obtain 
%
\begin{eqnarray}
%    \begin{split}
\frac{d}{dt} \xpert=(\xfixed + \xpert) [ \alpha^2 \ttau^2 \Gamma \xfixed \int dt' [ G(t, t')C^{p - 2}(t, t') ] \nonumber \\
  + \sqrt{2} \alpha \ttau \eonef + \sqrt{2} \alpha \htau \ezerof + \talpha \rho] \nonumber \\
  + \xfixed [\alpha^2 \ttau^2 \Gamma \int dt' [ G(t, t')C^{p - 2}(t, t') \xpertdash ] \nonumber \\
   + \sqrt{2} \alpha \ttau \eonepert + \sqrt{2} \alpha \htau \ezeropert + \xi(t)] \nonumber.
\label{eqn::Linearised}
%    \end{split}
\end{eqnarray}

We then examine the
long-term behaviour of the perturbation $\xpert$ by taking
the Fourier transform of this linearisation, and analysing its
behaviour at $\omega = 0$. After some manipulation (Sec.~S4), we arrive at the condition that, at a fixed point, the long term perturbations must satisfy
%
\begin{equation}
    \label{eqn::Final}
    0 \leq \left [(\alpha^2 \ttau^2 \Gamma q^{p-2} \chi)^{2} - 2 (\alpha \ttau + \alpha \htau)^2 (p-1)q^{p-2} \right ]
\end{equation}

It should be noted that, to derive (\ref{eqn::Final}), we assumed that the number $p$ of players is large enough so that $p/p-1 \approx 1$ and therefore the fractional power on $z$ in (\ref{eqn::fixed_point}) is reduced to $1$. As $z$ can take any value, including negative values, this again ensures that the expression for $\xfixed$ remains real-valued. We discuss the effects of taking this limit, as well as $N \rightarrow \infty$ in Sec. \ref{sec::exev}.

\subsection{Discussion} \label{sec::discussion}

The fixed point condition (\ref{eqn::Final}) yields a number of verifiable implications, of which we test empirically the validity in Sec.~\ref{sec::exev}. These implications are as follows.
%
%\begin{enumerate}
%    \item 
    %A trivial result is that

1.~The game is everywhere convergent (i.e., regardless of the choice of $\Gamma, N, p$) for the cases of $\alpha$ = 0 and/or $\tau$ = 0.  We see that choosing these values would result in the right hand side of (\ref{eqn::Final}) evaluating to zero, which falls within the stable region.

%    \item

2.~Convergence is rare in the limit $N \rightarrow
 \infty$. This is seen by the fact that the analytic result overestimates the region of instability. In fact, for all allowed choices of $\Gamma, \alpha, \tau$, the right hand side of (\ref{eqn::Final}) is negative, which violates the stability criterion. As such, in the limit of infinite actions and a large number of players, games will not converge. Of course, this is not typically required in most normal form games. We are interested, therefore, in what the condition (\ref{eqn::Final}) predicts about the dependence of stability on the parameters rather than the size of the stable region itself.

   % \item 
   3.~The likelihood of convergence decreases for increasing $\alpha$ and $\tau$, regardless of the choice of $N$ and $p$. We can see this since the right hand side of (\ref{eqn::Final}) tends further away from zero (i.e., further from the region of stability).

    %\item 
    4.~The choice of $\Gamma$ has a negligible effect on the stability of the game in the negatively-correlated regime. Therefore, the only dependent factors are $\alpha, \tau, N$ and $p$. This is more easily interpreted from the heatmaps in Fig.~\ref{fig:theory}.

    %\item 
    5.~The likelihood of convergence decreases as $p$ increases. We see this by noticing the $(p-1)$ in the second term of (\ref{eqn::Final}). As $p$ increases, this term drives the system further from the stability boundary.

%\end{enumerate}

We illustrate these implications in Fig.~\ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}). In order to determine these values, we first solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the value of $\xfixed$ that solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach. It should be noted that this method of finding $\xfixed$ yields only an approximate value, and therefore the $q$ and $\chi$ which are found are estimates.

Finally, we consider each of the implications (2)-(5) 
in turn, choosing to forego illustrating (1) as it is immediate
from (\ref{eqn::Final}). $\tau$ is held fixed
at $0.05$ and  $\Gamma$ is varied in
the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$.

\textbf{Implication 2:} By looking at the values on the heatmap (Fig \ref{fig:theory}), we see that, for all choices
of parameters,
(\ref{eqn::Final}) evaluates to a value less then zero, which signals
instability. As such, the analysis suggests that learning is everywhere unstable. We believe that this is due to the
assumptions made during the derivation of the analytic result, the
strongest of which was to drop the discrepancy between players and
actions, treating each action of each player to be independent and
identically distributed. Indeed, this result holds also for the limiting case of $N \rightarrow \infty$. It would, therefore, be important to empirically assess whether this holds in games of finite actions and a lower number of players, a point which we discuss in Section \ref{sec::exev}.

This does,
however, give rise to a limitation of the result - namely that the
effect of the number of actions, $N$, cannot be accurately inferred from
 (\ref{eqn::Final}). We go on to verify that
the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured
by (\ref{eqn::Final}).

We interpret (\ref{eqn::Final}), for given parameters, by determining
how close the right hand side is to the stability boundary (i.e., how
close the value is to zero). A choice of parameters which evaluates
close to the stability boundary has a higher chance (by the analytic
error) of being convergent than one which lies further from the
boundary. Therefore, the heatmaps in Fig.~\ref{fig:theory} should
be considered to show the likelihood of convergence for a choice of
$(\alpha, \Gamma)$. Lighter regions denote greater
convergence and vice versa.

\textbf{Implication 3} can be visualised by noticing that the likelihood of convergence decreases (the heatmap becomes darker) as $\alpha$ increases, and similarly for $\tau$. This occurs independently from the choice of $N$ or $p$.

\textbf{Implication 4} can similarly be inferred by the trend of convergence, which occurs only in varying $\alpha$. The choice of $\Gamma$
makes almost no difference in the evaluation of (\ref{eqn::Final}). We
anticipate that this is due to the restriction of $\Gamma$ to
the range $[-1, 0]$. In this range, the scaling effect of $\Gamma^2$
is dominated by the $\alpha^4$ and $\tau^4$ terms appearing in
(\ref{eqn::Final}).

\begin{figure}[t]
    \includegraphics[width = 1.2 \linewidth, center]{Figures/Theory.png}
    \caption{Evaluation of (\ref{eqn::Final}) over a range of $\alpha$ and $\Gamma$ values. Lighter regions indicate where (\ref{eqn::Final}) is close to zero (i.e. close to the stability boundary) whilst darker regions are further away. We vary $\alpha$ in the range $[0.01, 0.05]$ and $\Gamma$ in the range $[-1, 0]$. $\tau = 0.05$. ( Left) $p = 2, N = 2$, (Right) $p = 3, N = 8$.}
    \label{fig:theory}
\end{figure}

%%% TO BE COMBINED WITH FIG 6

% \begin{figure}[t]
%     \centering
%     \includegraphics[width = .75\linewidth]{Figures/pVariance.png}
%     \caption{Evaluation of (\ref{eqn::Final}) for varying numbers of players $p$. Here, $\alpha$ is fixed at $0.02$, $\tau = 0.05$, $N = 2$ and $\Gamma = -1$. $p$ is varied from 2 to 12. We see that the value obtained by (\ref{eqn::Final}) tends away from zero monotonically.}
%     \label{fig:pvariation}
% \end{figure}

\textbf{Implication 5} can, as discussed, be seen directly from (\ref{eqn::Final}) itself. The prediction is that (\ref{eqn::Final}) will decrease (i.e. move away from the stability boundary) monotonically with $p$. This is due to the $(p - 1)$ term which appears in the equation.

%%%%%%%%%%%%% END THEORY %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%% EXPT %%%%%%%%%%%%%%%%%%%%%

\section{Experimental Evaluation} \label{sec::exev}

As mentioned, the analytic result (\ref{eqn::Final}) holds in the limit of a large number of players and an infinite number of actions. It is therefore prudent to assess whether Implications 2--5 hold for games which are not in this limit. In this section, we describe and discuss the numerical experiments to verify the implications in Sec.~\ref{sec::discussion}. We first describe how these experiments were conducted, and then
%having presented the results in Figures \ref{fig:NumericalExperiments} and \ref{fig:pVarianceExpt}, 
we discuss the correlation with the theory.

\subsection{Construction of Numerical Experiments}

To verify experimentally the theoretical results, and to examine the underlying structure of stability and chaos in
multi-agent Q-learning, we perform a series of numerical experiments by varying the parameters $\Gamma$ and
$\alpha$, whilst keeping $\tau$ fixed. The aim is to determine the regions in which games learnt using Q-learning converge to an equilibrium. The results of these experiments are shown in Fig.~\ref{fig:NumericalExperiments}, with parameters chosen to match those in the analytic assessment (Fig.~\ref{fig:theory}).

To generate the numerical simulations in Fig.~\ref{fig:NumericalExperiments} we used the
following procedure.

\begin{enumerate}
   \item Fix the parameters $\tau$ and $\gamma$. The former is held at 0.05 and the latter at 0.1.
   \item Initialise values of $\Gamma$ and $\alpha$. These will be swept over in the experiment.
\item Generate 15 payoff matrices by sampling from a multi-variate Gaussian 
(variables are the payoff elements) with mean zero and covariance parameterised by $\Gamma$.
\item For each of these payoff matrices, initialise a set of agents with random initial conditions (i.e., random action probabilities).
\item Allow both sets of agents to learn over a maximum of $5 \times 10^4$ iterations.
\item Keep track of the action probabilities over a window of 5000 iterations. At the end of each window, determine the percentage difference between the maximum and minimum values of each strategy component.
\item If the difference is less than 1\% consider the game converged. Otherwise continue to the next window.
\item If the game reaches $5 \times 10^4$ iterations without satisfying the relative distance criterion, consider it to be non-convergent. Determine the fraction of these 15 games which have converged.

\end{enumerate}

We see in Fig.~\ref{fig:NumericalExperiments} that the stability of the system is highly dependent on
the value of $\alpha$ and $\tau$, but not on $\Gamma$.
  \begin{center}
      \begin{figure}[t]
            \includegraphics[width = 1.2 \linewidth, center]{Figures/Experiments.png}
            \caption{Results of numerical experiments in which $\alpha$ is varied. The heatmaps show the fraction of games which converge to an equilibrium. Lighter values show higher convergence. Each experiment is run with $\tau = 0.05$. (Top Left) $p = 2, N = 2$, (Top Right) $p = 2, N = 5$, (Bottom Left) $p = 3, N = 5$, (Bottom Right) $p=3, N = 8$.}
            \label{fig:NumericalExperiments}
        \end{figure}
  \end{center}

% \begin{figure}[t]
%     \includegraphics[width = 1.1 \linewidth, center]{Figures/alphavar5e2.png}
%     \caption{The trajectories of action probabilities for 2 players with 5 actions trained on a game of $\Gamma = -0.5$ and $\tau = 0.05$. (Left) $\alpha = 0.01$, (Right) $\alpha = 0.05$.}
%     \label{fig:AlphaVariation}
% \end{figure}

\begin{figure}[t]
    \includegraphics[width = .9\linewidth, center]{Figures/pVarianceExpt.png}
    \caption{Variation $V(t)$ about a fixed point as $p$ ranges from 2 - 9. $N = 2$, $\alpha = 0.02$, $\tau = 0.05$, $\Gamma \in [-1, 0]$. The experiment is conducted for 10 choices of $\Gamma$ and the mean (line) is plotted alongside the standard deviation (vertical bars).}
    \label{fig:pVarianceExpt}
\end{figure}

Finally, in Fig.~\ref{fig:pVarianceExpt} we plot the degree variation about the fixed point displayed as the number of players $p$ increases. The variation is determined by first allowing the game to iterate for 5000 steps, so that it can be assumed to have reached the vicinity of the fixed point. Then, the action probabilities are recorded for a further 5000 iterations. At the end of this second period, the variance of the actions is calculated as
%
\begin{equation*}
    V(t) = \frac{1}{N} \sum_i \big ( \frac{1}{5000} \sum_t x_i(t)^2 - \left[\frac{1}{5000} \sum_t x_i(t) \right]^2 \big ).
\end{equation*}

This gives a measure of the degree of variability about the fixed point and, therefore, gives some notion of the `degree of instability'.

Due to computational constraints, which we discuss in the following section, we are only able to increase $p$ to a maximum value of 9 . We maintain $\alpha = 0.02$ and $\tau = 0.05$. Finally, in Fig.~\ref{fig:pVarianceExpt}, we are averaging over 10 choices of $\Gamma$ in the range $[-1, 0]$.

\subsection{Discussion}

We observe that the numerical experiments confirm the predictions
suggested by the analytic results in Fig.~\ref{sec::Theory}. We notice that convergence occurs almost only for
low values of $\alpha$. This observation stands as we increase the
number $N$ of actions. As noted in Sec. \ref{sec::discussion}, the analytic result over-estimates the region
of instability due to the assumptions $N \rightarrow \infty$ and
$\frac{1}{p-1} \ll 2$ made during the derivation. Remaining
discrepancies are due to the aforementioned approximation in
the calculation of $q$, $\chi$ and the fact that the analytic result
considers a continuous time approximation of the expected behaviour of
Q-learning. We expect that testing over a greater number of payoff
realisations and initial conditions will yield a more representative
assessment of the average behaviour of Q-learning. However, running
these experiments is a computationally expensive procedure: for $p$
players and $N$ actions we require operations on $p$ matrices with
$N^{p}$ elements. As such, due to a reduced availability of
computational facilities, a large scale averaging was not possible.

A key point which we wish to discuss here is a comparison with the result
found in~\cite{sanders:prevalence}, which considers the stability of
\textit{experience weighted attraction} (EWA). Namely, Sanders et
al.~observe that convergence is seen for higher values of $\alpha$,
whereas lower values give rise to chaos, the opposite of what is found
here. The reason for this can be seen in the update equation
(\ref{eqn::Qupdate}) for Q-learning, whereby smaller values of
$\alpha$ result in the agent placing a lower weight on the reward
received at each step. As such, lower values of $\alpha$ result in the
agent taking more conservative steps and yields a higher probability
of convergence. In contrast, the update for EWA does not discount the
reward received and, instead, only discounts the previous
knowledge of the Q-value based on higher choices of $\alpha$.  This
highlights the importance of performing analyses such as the present
work; it allows for a method to analytically compare the differences
between learning algorithms and, for practitioners, to ensure that the
appropriate algorithm is chosen for the parameters of their specific
task.

To summarise, we have shown that the analytic result
(\ref{eqn::Final}) provides a strong assessment of the effects that
parameters $\alpha$, $\tau$, $\Gamma$, and $p$ have on the likelihood of
convergence of Q-learning. Furthermore, though
(\ref{eqn::Final}) overestimates the region of instability by assuming $N \rightarrow \infty$, it
accurately conveys that convergence of Q-learning is increasingly unlikely for
games with many players and actions. In fact, our experimental results
also verify that stability may only be guaranteed for the limiting
case of two-player, two-action games.
%

\section{Conclusion}

In this study, we made a first contribution towards the
characterisation of the behaviours of agents learning how to play
$p$-player, $N$-action games through Q-learning. To this end, we
analysed the replicator model of Q-learning derived in \cite{tuyls:iteratedgames}. Specifically, we searched for the regions in parameter space
where the dynamics are expected to converge to a stable equilibrium
and those where learning is unstable. This yielded a number of
important results. We showed that for negatively correlated payoff matrices, the
strength of correlation $\Gamma$ does not influence stability; whereas, as
$\alpha$ and $\tau$ increase, the likelihood of convergence decreases. This behaviour differs from the stability of EWA, suggesting that different learning methods produce different qualitative behaviours. Similarly to EWA, however our
analysis also shows that the likelihood of convergence decreases,
regardless of parameter choice as the number of players $p$ in the
system increases.

As research into the dynamics of RL algorithms
progresses, it would be prudent to apply this analysis to various
other algorithm. Algorithms whose dynamics are established, and are
therefore open to a stability analysis, include piecewise Q-Learning
and Cross Learning. This would provide a strong method by which to
compare and provide safety guarantees to different algorithms for a
particular use case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{references}

\end{document}

### 2021-02-18 Code/FPinNAG/PayoffPerformance.py

@@ -1,0 +1,282 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+import numpy as np
+from tqdm import tqdm
+import nashpy as nash
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+
+def generateGallaGames(gamma, nSim, dim):
+    nElements = dim ** 2  # number of payoff elements in the matrix
+
+    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    rewardAs, rewardBs = np.eye(dim), np.eye(dim)
+
+    for i in range(nSim):
+        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((dim, dim))))
+        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((dim, dim))))
+
+    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
+
+
+def findNE(A, B):
+    rps = nash.Game(A, B)
+    eqs = rps.support_enumeration()
+    return list(eqs)
+
+
+def initialiseRandomVectors(dim, nInit, nSim):
+    pX = np.dstack([np.random.dirichlet(np.ones(dim), size=(nInit)).T for s in range(nSim)])
+    qY = np.dstack([np.random.dirichlet(np.ones(dim), size=(nInit)).T for s in range(nSim)])
+
+    return pX, qY
+
+
+def findclosestNEPayoff(pX, qY, allNE, A, B, nInit, nSim):
+    closestNE = np.vstack([np.argmin(
+        np.vstack([np.linalg.norm(pX[:, :, s].T - allNE[s][i][0], axis=1) for i in range(len(allNE[s]))]), axis=0) for s
+                           in range(nSim)]).T
+    # closestNE = np.argmin(distancetoNE, axis=0)
+
+    NEX = np.vstack(
[…]

### 2021-02-18 Code/FPinNAG/main.py

@@ -31,114 +31,9 @@ def initialise():
     initRef = (adjMat @ initVectors.T).T
     return adjMat, initQ, initVectors, initRef
 
-def bestResponse(i, sigmaRef, Q, xPreF):
-    xPreF = np.expand_dims(xPreF[:, i], axis=1)
-    APV = np.vstack((np.linspace(0, 1, 50), 1 - np.linspace(0, 1, 50)))
-    term1 = Q[i] * np.linalg.norm(np.subtract(APV, xPreF), axis=0) ** 2
-    term2 = 2 * sigmaRef[:, i].T @ APV
-
-    bestCost = np.min(term1 + term2)
-    bestReply = np.argmin(term1 + term2)
-
-    return APV[:, bestReply], bestCost
 
 def updateSigma(adjMat, vectors):
     return (adjMat @ vectors.T).T
-
-def addNoise(prob):
-    APV = np.vstack((np.linspace(0, 1, 50), 1 - np.linspace(0, 1, 50)))
-    approxIdx = np.argmin(np.linalg.norm(APV - np.expand_dims(prob, axis=1), axis=0))
-    noisyIdx = np.random.randint(-2, 2)
-    while not (approxIdx + noisyIdx >= len(APV) or approxIdx + noisyIdx < 0):
-        noisyIdx = np.random.randint(-2, 2)
-    return APV[:, approxIdx + noisyIdx]
-
-def EKF(z, x, P, Q, K, R):
-    Pf = P + Q
-    x += K(z - x)
-    Kk = Pf @ np.linalg.inv(Pf + R)
-    P = (np.eye(2) - Kk) @ Pf
-
-    return
-
-def KF(z, x, P):
-
-    Q = np.eye(4) * 0.05
-    R = np.eye(4) * 0.02
-    H = np.eye(4)
-
-    P += Q
-    K = P @ H.T @ np.linalg.inv(H @ P @ H.T + R)
-    dz = z - x
-
-    x += K @ dz
-    P = (np.eye(4) - K @ H) @ P
-
-    return x.reshape((2, 2)), P
-
-def createNoisyData(data):
-    noisyData = [np.vstack((data[:, 0], addNoise(data[:, 1]), addNoise(data[:, 2]))).T]
-    noisyData += [np.vstack((addNoise(data[:, 0]), data[:, 1], addNoise(data[:, 2]))).T]
-    noisyData += [np.vstack((addNoise(data[:, 0]), addNoise(data[:, 1]), data[:, 2])).T]
[…]

### 2021-02-18 Code/ThreeBodyQL/main.py

@@ -1,0 +1,78 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+def generateMatchingPennies():
+    """
+    Create Matching Pennies Matrix
+
+    :return:
+    """
+
+    A = np.array([[1, -1], [-1, 1]])
+    B = np.array([[-1, 1], [1, -1]])
+
+    return A, B
+
+def getActionProbs(Q, agentParams):
+    """
+        qValues: nPlayer x nActions x nSim
+        return: nPlayer x nActions x nSim
+        """
+    alpha, tau, gamma = agentParams
+
+    return np.exp(tau * Q) / np.sum(np.exp(tau * Q), axis=1)[:, None]
+
+def getCurrentActions(actionProbs):
+    return [np.random.choice([0, 1], p=actionProbs[p, :]) for p in range(3)]
+
+def getRewards(G, bChoice):
+    A, B = G
+
+    rewards = np.zeros(3)
+    rewards[0] = A[bChoice[0], bChoice[1]] + B[bChoice[2], bChoice[0]]
+    rewards[1] = B[bChoice[0], bChoice[1]] + A[bChoice[1], bChoice[2]]
+    rewards[2] = A[bChoice[2], bChoice[0]] + B[bChoice[1], bChoice[2]]
+
+    return rewards
+
+def qUpdate(Q, G, agentParams):
+
+    alpha, tau, gamma = agentParams
+
+    actionProbs = getActionProbs(Q, agentParams)
+    bChoice = getCurrentActions(actionProbs)
+    rewards = getRewards(G, bChoice)
+
+    for p in range(3):
+        Q[p, bChoice[p]] += alpha * (rewards[p] - Q[p, bChoice[p]] + gamma * np.max(Q[p, :]))
+    return Q
+
+def initialiseQ():
+    return np.random.rand(3, 2)
+
+def simulate(agentParams, nIter = 5e3):
+    nIter = int(nIter)
+
+    G = generateMatchingPennies()
+    Q = initialiseQ()
+
+    firstActionTracker = np.zeros((3, nIter))
+
+    for cIter in range(nIter):
+        Q = qUpdate(Q, G, agentParams)
+        firstActionTracker[:, cIter] = getActionProbs(Q, agentParams)[:, 0]
+
+    return firstActionTracker
+
+if __name__ == '__main__':
+
+    alpha, tau, gamma = 0.05, 0.1, 0.1
+
[…]

### 2021-02-18 Code/ThreeBodyQL/simulation.jl

@@ -1,0 +1,83 @@
+using LinearAlgebra
+using Distributions
+using ProgressMeter
+using PyPlot
+
+alpha = 0.05
+tau = 0.1
+gamma = 0.1
+
+agentParams = (alpha, tau, gamma)
+
+
+function generateMatchingPennies()
+    """
+    Create Matching Pennies Matrix
+    """
+
+    A, B = [1 -1; -1 1], [-1 1; 1 -1]
+
+    return A, B
+end
+
+function getActionProbs(qValues, agentParams)
+    """
+    qValues: nPlayer x nActions x nSim
+    return: nPlayer x nActions x nSim
+    """
+    alpha, tau, gamma = agentParams
+
+    return exp.(tau * qValues)./sum(exp.(tau * qValues), dims=2)
+end
+
+function chooseActions(actionProbs)
+    return [rand(Bernoulli(actionProbs[p, 1])) + 1 for p = 1:3]
+end
+
+function initialiseQ()
+    return rand(3, 2)
+end
+
+function getRewards(G, bChoice)
+    A, B = G
+
+    rewards = zeros(3)
+    rewards[1] = A[bChoice[1], bChoice[2]] + B[bChoice[1], bChoice[3]]
+    rewards[2] = B[bChoice[1], bChoice[2]] + A[bChoice[2], bChoice[3]]
+    rewards[3] = A[bChoice[3], bChoice[1]] + B[bChoice[2], bChoice[3]]
+
+    return rewards
+end
+
+function qUpdate!(Q, G, agentParams)
+
+    actionProbs = getActionProbs(Q, agentParams)
+    bChoice = chooseActions(actionProbs)
+    rewards = getRewards(G, bChoice)
+
+    for i = 1:3
+        Q[i, bChoice[i]] += alpha * (rewards[i] - Q[i, bChoice[i]] + gamma * findmax(Q[i, :])[1])
+    end
+
+end
+
+function simulate(nIter = 5e3)
+    nIter = trunc(Int, nIter)
+
+    G = generateMatchingPennies()
+    Q = initialiseQ()
+
+    global firstActionTracker = zeros(3, nIter)
+
+    for cIter = 1:trunc(Int, nIter)
+        qUpdate!(Q, G, agentParams)
+        firstActionTracker[:, cIter] = getActionProbs(Q, agentParams)[:, 1]
+    end
+
+    return firstActionTracker
+end
+
+firstActionTracker = simulate()
+
[…]

### 2021-02-18 Code/ThreeBodyQL/tests.jl

@@ -1,0 +1,5 @@
+using PyCall
+pygui(gui)
+using PyPlot
+
+surf(rand(30,40))

### 2021-02-18 Code/EGT-RL/MeanFieldCode/Game.py
Reorganised File Structure

@@ -1,51 +1,0 @@
-import random
-
-class Game:
-
-    def __init__(self, rewards):
-        self.rewards = rewards
-        self.allGames = np.eye((len(rewards)))
-
-    def generateOpponents(self, p):
-        # players = np.array(range(nAgents))
-        # np.random.shuffle(players[np.where(gamesPlayed < nOpponents)])
-        return np.where(self.allGames[:, p] == 1)[0].tolist()
-        # return players[0:nOpponents - gamesPlayed[p]]
-
-    def generateGames(self, players, nOpponents):
-        nAgents = len(players)
-        self.allGames = np.zeros((nAgents, nAgents))
-        for p in range(nAgents):
-            availableOpponents = np.array(range(nAgents))[np.where((np.array(range(nAgents)) != p) & (self.allGames[:, p] != 1) & (np.sum(self.allGames, axis = 1) < nOpponents))].tolist()
-            opponents = random.sample(availableOpponents, nOpponents - len(np.where(self.allGames[:,  p] == 1)[0]))
-            self.allGames[opponents, p] = 1
-            self.allGames[p, opponents] = 1
-
-    def playGame(self, players, P):
-        players = np.array(players)
-        opponents = self.generateOpponents(P)
-        players[P].payOffs += self.rewards[0][players[P].action, [players[O].action for O in opponents]].tolist()
-        for O in opponents:
-            players[O].payOffs += [self.rewards[1][players[P].action, players[O].action]]
-            self.allGames[P, O], self.allGames[O, P] = 0, 0
-        return players
-
-if __name__ == "__main__":
-    from MeanFieldCode.QLearner import QLearner
-    from MeanFieldCode.GamePlay import *
-
-    alpha = 0.1
-    tau = 1
-    gamma = 0
-
-    nAgent = 2
-    nAct = 2
-
-    game = generateGame(gamma, nAct)
-
-    players = [QLearner([alpha, tau, gamma], nAct, game.rewards[i], nAgent - 1) for i in range(nAgent)]
-    selectActions(players)
-
-    game.generateGames(players, nAgent-1)
-    game.playGame(players, 0)
-    print('hi')

### 2021-02-18 Code/EGT-RL/MeanFieldCode/GamePlay.py

@@ -1,124 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from tqdm import tqdm
-from MeanFieldCode.QLearner import QLearner
-from MeanFieldCode.Game import Game
-
-# Generate Random Games
-# Initialise players
-# Iterate Game
-    # Choose actions
-    # Receive rewards
-    # Update Q-values
-
-def generateGame(gamma, nAct):
-    reward1s = {}
-    reward2s = {}
-
-    nElements = nAct**2 #number of payoff elements in the matrix
-
-    cov = np.eye(2 *  nElements)
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
-
-    rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
-
-    rewards = np.array([2, 0, 0, 1, 1, 0, 0, 2])
-
-    reward1s = rewards[0:nElements].reshape((nAct, nAct))
-    reward2s = rewards[nElements:].reshape((nAct, nAct)).T
-
-    return Game([reward1s, reward2s])
-
-def initialisePlayers(params, nAgent, nAct, game):
-    return [QLearner(params, nAct, game.rewards[i], nAgent-1) for i in range(nAgent)]
-
-def selectActions(players):
-    [player.selectAction() for player in players]
-    return players
-
-def playGame(players, game):
-    nAgents = len(players)
-    # players = np.array(players)
-    game.generateGames(players, players[0].nOpponents)
-    for p in players:
-        p.payOffs = []
-
-    for p in range(nAgents):
-        players = game.playGame(players, p)
-
-    return players.tolist()
-
-def updateQValues(players):
-    [player.qUpdate() for player in players]
-    return players
-
-
-def iterateGame(players, game):
-    players = selectActions(players)
-    players = playGame(players, game)
-    players = updateQValues(players)
-
-    return players
-
-def runSimulation(params, nAgent, nAct):
-    game = generateGame(params[2], nAct)
-    players = initialisePlayers(params, nAgent, nAct, game)
-
-    nIter = int(1e3)
-
-    probs = []
-
-    for cIter in tqdm(range(nIter)):
-        players = iterateGame(players, game)
-        probs.append(np.array([p.actionProb[0] for p in players]))
-
[…]

### 2021-02-18 Code/EGT-RL/MeanFieldCode/QLearner.py

@@ -1,42 +1,0 @@
-import numpy as np
-
-class QLearner:
-    def __init__(self, params, nActions, payOff, nOpponents):
-        self.gamma = 0.1
-        self.tau   = params[0]
-        self.alpha = params[1]
-
-        self.nActions = nActions
-        self.nOpponents = nOpponents
-
-        rMin = np.amin(payOff)
-        rMax = np.amax(payOff)
-
-        self.qValues = np.random.rand(nActions)*(rMax-rMin)+rMin
-        self.partitionFunction = np.sum([np.exp(self.tau * i) for i in self.qValues])
-        self.actionProb = [np.exp(self.tau * i) / self.partitionFunction for i in self.qValues]
-
-        self.action = 0
-        self.payOffs = []
-
-        self.gamesPlayed = 0
-
-    def selectAction(self):
-        self.partitionFunction = np.sum([np.exp(self.tau * i) for i in self.qValues])
-        self.actionProb = [np.exp(self.tau * i) / self.partitionFunction for i in self.qValues]
-
-        self.action = np.random.choice([0, 1], p=self.actionProb)
-
-    def playGame(self, opponents, game):
-        payOffs = np.array(game[self.action, np.array([o.action for o in opponents])]).T
-        self.payOffs += list(payOffs[0])
-        for o in range(len(opponents)):
-            opponents[o].payOffs += [payOffs[1, o]]
-
-
-    def qUpdate(self):
-
-        self.payoff = np.mean(self.payOffs[0:self.nOpponents])
-        # self.qValues[self.action] = (1 - self.alpha) * self.qValues[self.action] + self.alpha * self.payoff
-
-        self.qValues[self.action] += self.alpha * (self.payoff + self.gamma * max(self.qValues) - self.qValues[self.action])

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/AttempttoVectorise/untitled0.py

@@ -1,89 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-"""
-Created on Sun Sep  6 20:49:19 2020
-
-@author: aamalh
-"""
-
-import numpy as np
-import itertools
-from time import time
-import matplotlib.pyplot as plt
-
-nAct = 2
-nPlayers = 2
-nSim = 1
-
-alpha = 0.01
-gamma = 0.1
-tau = 1
-Gamma = -1
-
-
-def generateGames(gamma, nSim, nAct):
-    """
-    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
-
-    gamma: Choice of co-operation parameter
-    nAct: Number of actions in the game
-
-    [reward1s, reward2s]: list of payoff matrices
-    """
-
-    nElements = nAct ** nPlayers  # number of payoff elements in the matrix
-
-    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
-
-    for i in range(nSim):
-
-        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
-
-    return np.array([1, 5, 0, 3, 1, 0, 5, 3])
-
-def getActionProbs(qValues):
-    partitionFunction = np.sum(np.exp(tau * qValues0.reshape((2, 2))), axis = 1)
-    actionProbs = [np.exp(tau * qValues0[i:i + nAct])/partitionFunction[int(i/2)] for i in range(0, nPlayers + 1, nAct)]
-
-    return np.array(actionProbs).squeeze()
-
-rewards = generateGames(Gamma, nSim, nAct)
-qValues0 = np.random.rand(nPlayers * nAct, nSim)
-
-iterTimes = []
-allActions = []
-
-for cIter in range(10000):
-
-    start = time()
-
-    actionProbs = getActionProbs(qValues0)
-    bChoices = [np.random.choice([0, 1], p = actionProbs[p]) for p in range(nPlayers)]
-    
-    rows = [i + j + 1 for (j, i) in enumerate(bChoices)]
-    rows[0] -= 1
[…]

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/AttempttoVectorise/untitled1.py

@@ -1,155 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-"""
-Created on Sun Sep  6 22:24:55 2020
-
-@author: aamalh
-"""
-
-import numpy as np
-import itertools
-import scipy.sparse as sps
-import matplotlib.pyplot as plt
-from time import time
-from tqdm import tqdm
-
-t0 = 500
-alpha = 4e-2
-gamma = .1
-Gamma = -1
-tau = 5e-2
-
-delta_0 = 1e-3
-initnSim = 10
-nIter = int(1e3)
-nTests = 10
-
-nPlayers = 3
-nActions = 5
-nElements = nActions ** nPlayers
-
-def generateGames(gamma, nSim, nAct, nPlayers):
-    """
-    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
-    gamma: Choice of co-operation parameter
-    nAct: Number of actions in the game
-    [reward1s, reward2s]: list of payoff matrices
-    """
-
-    nElements = nAct ** nPlayers  # number of payoff elements in a player's matrix
-
-    cov = sps.lil_matrix(sps.eye(nPlayers * nElements))
-    idX = list(itertools.product(list(range(1, nAct + 1)), repeat=nPlayers)) * nPlayers
-    for idx in range(nElements):
-        for b in range(1, nPlayers):
-            rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
-            cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
-
-    cov = cov.toarray()
-
-    rewards = np.zeros((nPlayers * nElements))
-
-    for i in range(nSim):
-        rewards = np.hstack((rewards, np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)))
-
-    return rewards[nPlayers * nElements: ]
-
-def getActionProbs(qValues):
-   
-    partitionFunction = np.sum(np.exp(tau * qValues0.reshape((nPlayers * nTests * nSim, nActions))), axis = 1)
-    actionProbs = [np.exp(tau * qValues0[i:i + nActions])/partitionFunction[int(i/nActions)] for i in range(0, len(qValues0), nActions)]
-
-    return np.array(actionProbs).squeeze()
-
-def checkConvergence(x, xOld, tol):
-  """
[…]

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/LiapunovExponent.py

@@ -1,105 +1,0 @@
-import numpy as np
-import itertools
-import scipy.sparse as sps
-import matplotlib.pyplot as plt
-from time import time
-from tqdm import tqdm
-
-
-alpha = .1
-gamma = .1
-Gamma = 0.1
-tau = 1
-
-delta_0 = 1e-3
-nSim = 10
-nIter = int(1e3)
-nTests = 10
-
-nPlayers = 2
-nActions = 5
-
-def generateGames(gamma, nSim, nAct, nPlayers):
-    """
-    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
-    gamma: Choice of co-operation parameter
-    nAct: Number of actions in the game
-    [reward1s, reward2s]: list of payoff matrices
-    """
-
-    nElements = nAct ** nPlayers  # number of payoff elements in a player's matrix
-
-    cov = sps.lil_matrix(sps.eye(nPlayers * nElements))
-    idX = list(itertools.product(list(range(1, nAct + 1)), repeat=nPlayers)) * nPlayers
-    for idx in range(nElements):
-        for b in range(1, nPlayers):
-            rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
-            cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
-
-    cov = cov.toarray()
-
-    allPayoffs = np.zeros(shape=(nPlayers, nElements))
-
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
-        each = np.array_split(rewards, nPlayers)
-        allPayoffs = np.dstack((allPayoffs, np.array(each)))
-
-    return allPayoffs
-
-
-def getActionProbs(qValues):
-    partitionFunction = np.expand_dims(np.sum(np.exp(tau * qValues), axis=1), axis = 1)
-    partitionFunction = np.hstack([partitionFunction]*nActions)
-    actionProbs = np.exp(tau * qValues)/partitionFunction
-    return actionProbs
-
-
-def qUpdate(qValues, payoffs):
-    idX = list(itertools.product(list(range(0, nActions)), repeat=nPlayers))
-    actionProbs = getActionProbs(qValues)
[…]

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/NumericalInt.py

@@ -1,103 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from tqdm import tqdm
-
-# q = int Dz x^2
-# 1 = int Dz x
-# X = 1/q int dx/dz
-
-# initialise values of z
-# for every z initialise a guess of x and x_d where x_d differs from x by some delta
-# use these choices for x to determine X, p, q
-# evaluate f and f' at this guess (f' given by finite approximation with x_d)
-# update x using Newton Raphson with all the finite approximations
-
-# determine q and X off that
-
-nPlayers = 5
-nActions = 50
-
-dz = 1e-1
-Zs = np.arange(-20, 20, dz)
-Dz = (dz/np.sqrt(2 *  np.pi)) * np.exp(-(Zs**2)/2)
-
-def getOrderParams(Xs, dz, Zs):
-    q = np.sum((Xs ** 2) * dz)
-    dx = np.array([Xs[i + 1] - Xs[i] for i in range(len(Zs[:-1]))])
-    X = (1 / (q ** (nPlayers - 1)/2)) * np.sum((dx/dz) *dz)
-
-    return q, X
-
-def normaliseX(Xs):
-    #Xs /= np.sum(abs(Xs))
-    #return abs(Xs)
-    return abs(abs(Xs)/np.sum(abs(Xs) * Dz))
-    #return abs(abs(Xs)/np.sum(abs(Xs)))
-
-allOrders = np.zeros((10, 10, 2))
-
-idx1 = 0
-for alpha in np.linspace(0.5, 1, num=1):
-    idx2 = 1
-    for Gamma in np.linspace(-1, 1, num=1):
-
-        # alpha = 0.1
-        tau = 1
-        # Gamma = 1
-        talpha = alpha/nActions
-        ttau = tau/np.sqrt(nActions ** (nPlayers - 1))
-
-
-        p = lambda xi, dz, Xs: np.sum((Xs * np.log(Xs/Xs[xi])) * dz)
-        F = lambda xi, z, Xs, q, n, chi: (alpha**2) * (ttau ** 2) * Gamma * Xs[xi] * (q**(n-1)) * chi + alpha * ttau * (q**(n/2)) * z + talpha * tau * (q**((n+1)/2)) * z
-        A = lambda xi, z, Xs, dz, q, n: -(q ** (n/2)) * z * (alpha * ttau + talpha * tau)
-
-        Xs = normaliseX(np.random.random((len(Zs), )))
[…]

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/SecondTry.py

@@ -1,98 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Fri Aug 28 11:24:15 2020
-
-@author: aamal
-"""
-
-import numpy as np
-import matplotlib.pyplot as plt
-from tqdm import tqdm
-
-nPlayers = 3
-nActions = 10
-nIter = 10
-dz = 1e-3
-Zs = np.arange(-1.5, 1.5, dz)
-Dz = (dz/np.sqrt(2 *  np.pi)) * np.exp(-(Zs**2)/2)
-step = 1e-3
-
-
-allOrders = []
-
-for a in np.linspace(0.222, 1, num=1):
-    for G in np.linspace(-1, 0, num=10):
-
-        t = 10
-        
-        ta = a/nActions
-        tt = t/np.sqrt(nActions ** (nPlayers - 1))
-        th = t/np.sqrt(nActions**nPlayers)
-        
-        p = lambda xi, Xs: np.sum((Xs * np.log(Xs/Xs[xi])) * Dz)
-        F = lambda xi, z, Xs, q, n, chi: a**2 * tt**2 * G * chi * q**(n-1) * Xs[xi] + q**(n/2) * z * (a * tt + a * th)**2 + ta * p(xi, Xs)
-        # F = lambda xi, z, Xs, q, n, chi: (a**2) * (tt**2) * G * chi * (q**(n-1)) * Xs[xi] + a * tt * q**(n/2) * z + ta * t * q**((n + 1)/2) * z + ta * p(xi, Xs)
-        
-        
-        def getOrderParams(Xs, dz, Zs):
-            q = np.sum((Xs ** 2) * Dz)
-            dx = np.array([Xs[i + 1] - Xs[i] for i in range(len(Zs[:-1]))])
-            X = (1 / (q ** (nPlayers - 1)/2)) * np.sum((dx/dz) * Dz[:-1])
-        
-            return q, X
-        
-        def normaliseX(Xs):
-            return abs(Xs)/np.sum(abs(Xs) * Dz)
-        
-        def getF(Xs):
-            qs, chis = getOrderParams(Xs, dz, Zs)
-            return np.array([F(i, Zs[i], Xs, qs, nPlayers - 1, chis) for i in range(len(Xs))])
-        
-        
-        Xs = normaliseX(np.ones((len(Zs), )))
-        XsOld = np.copy(Xs)
-        Xsmin = np.copy(Xs)
-        fs = np.ones((len(Xs), ))
[…]

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/TwoPlayers.py

@@ -1,149 +1,0 @@
-import numpy as np
-import seaborn as sns
-import matplotlib.pyplot as plt
-from time import time
-from tqdm import tqdm
-from os import mkdir
-
-# alpha = .1
-gamma = 0.1
-Gamma = 0.1
-tau = 1
-alpha = 0.1
-
-nActions = 5
-t0 = 500
-
-initnSim = 1
-
-delta_0 = 1e-3
-nSim = 10
-nIter = int(1.5e3)
-
-
-def generateGames(gamma, nSim, nAct):
-    """
-    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
-
-    gamma: Choice of co-operation parameter
-    nAct: Number of actions in the game
-
-    [reward1s, reward2s]: list of payoff matrices
-    """
-
-    nElements = nAct ** 2  # number of payoff elements in the matrix
-
-    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
-
-    rewardAs, rewardBs = np.eye(nAct), np.eye(nAct)
-
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
-
-        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
-        # rewardAs = np.dstack((rewardAs, np.array([[1, 5], [0, 3]])))
-        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
-        # rewardBs = np.dstack((rewardBs, np.array([[1, 0], [5, 3]])))
-    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
-
-
-def getActionProbs(qValues, nSim):
-    partitionFunction = np.sum(np.exp(tau * qValues), axis=1)
-    actionProbs = np.array(
-        [np.array([np.exp(tau * qValues[p, :, s]) / partitionFunction[p, s] for p in range(2)]) for s in range(nSim)])
-
-    return actionProbs
-
-
-def qUpdate(qValues, payoffs):
-    actionProbs = getActionProbs(qValues, nSim)
-
-    boltzmannChoices = np.array(
[…]

### 2021-02-18 Code/EGT-RL/TwoPlayerCode/pPlayers.py

@@ -1,106 +1,0 @@
-import numpy as np
-import itertools
-import scipy.sparse as sps
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from tqdm import tqdm
-
-t0 = 500
-gamma = .1
-tau = 1
-alpha = 0.01
-
-initnSim = 1
-nIter = int(1.5e4)
-nTests = 10
-
-nPlayers = 2
-nActions = 2
-
-def generateGames(gamma, nSim, nAct, nPlayers):
-    """
-    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
-    gamma: Choice of co-operation parameter
-    nAct: Number of actions in the game
-    [reward1s, reward2s]: list of payoff matrices
-    """
-
-    nElements = nAct ** nPlayers  # number of payoff elements in a player's matrix
-
-    cov = sps.lil_matrix(sps.eye(nPlayers * nElements))
-    idX = list(itertools.product(list(range(1, nAct + 1)), repeat=nPlayers)) * nPlayers
-    for idx in range(nElements):
-        for b in range(1, nPlayers):
-            rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
-            cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
-
-    cov = cov.toarray()
-
-    allPayoffs = np.zeros((nPlayers, nElements))
-
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
-        each = np.array_split(rewards, nPlayers)
-        allPayoffs = np.dstack((allPayoffs, np.array(each)))
-
-    return allPayoffs[:, :, 1:]
-
-def getActionProbs(qValues):
-    partitionFunction = np.expand_dims(np.sum(np.exp(tau * qValues), axis=1), axis = 1)
-    partitionFunction = np.hstack([partitionFunction]*nActions)
-    actionProbs = np.exp(tau * qValues)/partitionFunction
-    return actionProbs
-
-
-def qUpdate(qValues, payoffs, nSim):
-    idX = list(itertools.product(list(range(0, nActions)), repeat=nPlayers))
-    actionProbs = getActionProbs(qValues)
[…]

### 2021-02-18 Code/Practice/QLearner.py

@@ -1,41 +1,0 @@
-import numpy as np
-
-class QLearner:
-    def __init__(self, r, nOpponents):
-        self.gamma = .9
-        self.tau   = 2
-        self.alpha = 0.8 #self.tau * r
-
-        self.nOpponents = nOpponents
-
-        self.qValues = np.zeros(2)
-        self.qValues[0] = 1
-        self.qValues[1] = np.log((0.3 * np.exp(self.tau  * self.qValues[0]))/0.7)/self.tau
-        self.partitionFunction = np.sum([np.exp(self.tau * i) for i in self.qValues])
-        self.actionProb = [np.exp(self.tau * i) / self.partitionFunction for i in self.qValues]
-        self.action = 0
-        self.payOffs = []
-
-        self.gamesPlayed = 0
-
-    def selectAction(self):
-        self.partitionFunction = np.sum([np.exp(self.tau * i) for i in self.qValues])
-        self.actionProb = [np.exp(self.tau * i) / self.partitionFunction for i in self.qValues]
-
-        self.action = np.random.choice([0, 1], p=self.actionProb)
-
-    def playGame(self, opponents, game):
-        payOffs = np.array(game[self.action, np.array([o.action for o in opponents])]).T
-
-        self.payOffs += list(payOffs[0])
-        for o in range(len(opponents)):
-            opponents[o].payOffs += [payOffs[1, o]]
-
-    def qUpdate(self):
-
-        self.payoff = np.mean(self.payOffs[0:self.nOpponents])
-        self.qValues[self.action] = (1 - self.alpha) * self.qValues[self.action] + self.alpha * self.payoff
-
-        # self.qValues[self.action] += self.alpha * (self.payoff + self.gamma * max(self.qValues) - self.qValues[self.action])
-
-        self.gamesPlayed = 0

### 2021-02-18 Code/Practice/Tuyls3p.py

@@ -1,39 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from tqdm import tqdm
-
-alpha = .01
-tau = 1
-
-x = np.linspace(0, 1, 50)
-y = np.linspace(0, 1, 50)
-z = np.linspace(0, 1, 50)
-
-X, Y, Z = np.meshgrid(x, y, z)
-
-A, B = np.array([[1, 5], [0, 3]]), np.array([[1, 0], [5, 3]])
-
-E = lambda R: (R * np.log(R/R)) + ((1 - R) * np.log((1 - R)/R))
-
-x_dot = lambda M, N, O: alpha * M * tau * ((A @ [N, 1-N])[0] - np.dot([M, 1-M], A@[N, 1-N])) + M * alpha * E(M)
-
-y_dot = lambda M, N, O: alpha * N * tau * ((B.T @ [M, 1-M])[0] - np.dot([N, 1-N], B.T@[M, 1-M])) + N * alpha * E(N)
-
-z_dot = lambda M, N, O: alpha * O * tau
-
-U, V = np.zeros(X.shape), np.zeros(X.shape)
-NI, NJ = X.shape
-
-for i in range(NI):
-    for j in range(NJ):
-        U[i, j] = x_dot(X[i, j], Y[i, j])
-        V[i, j] = y_dot(X[i, j], Y[i, j])
-
-fig = plt.figure(dpi=500)
-ax = fig.add_subplot(111, projection='3d')
-
-ax.quiver(X, Y, U, V, color = 'b', width=2e-3)
-plt.xlabel('Probability of Action 1 (Agent 1)')
-plt.ylabel('Probability of Action 1 (Agent 2)')
-plt.show()

### 2021-02-18 Code/StabilityofMARL/Numerical Experiments/EDMD.py

@@ -1,69 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import scipy.special as sps
-from itertools import product
-from qUpdater import TwoPlayers
-"""
-EDMD Algorithm: 
-
-1. Define a series of observables: let's say Hermite Polynomials up to order 5 + [x, v] + [1]
-2. Collect a set of data pairs X_n-1 and X_n
-3. Apply the observable functions on the datasets to get \Phi(X), \Phi(Y)
-4. Compute G and A from EDMD paper
-5. Compute K
-
-Predicting the flow field:
-
-Apply K on the observable for some initial condition. 
-Extract the flow field using (3.2) and (3.3) of the KMD for Algs paper
-"""
-
-def eval_Phi(x, maxOrder = 5):
-    lenData = len(x)
-    allHermiteOrders = list(product(range(maxOrder), repeat=lenData))
-    allHermites = np.array([sps.eval_hermite(o,x) for o in range(maxOrder)])
-
-    allCombos = [np.prod(allHermites[oList, range(lenData)]) for oList in allHermiteOrders]
-
-    return allCombos
-
-def generatePhi(X, maxOrder=5, isX = True):
-    if isX:
-        return np.array(
-            [eval_Phi(X[i], maxOrder=maxOrder) + [*X[i]] + [*(X[i] - X[i-1]/1e-2)] + [i] for i in range(1, len(X))])
-    else:
-        return np.array(
-            [eval_Phi(X[i], maxOrder=maxOrder) + [*X[i]] + [*(X[i] - X[i - 1] / 1e-2)] + [i+1] for i in range(1, len(X))])
-
-def generateX_Y(gameParams, agentParams, sizeX):
-    (Gamma, nSim, nActions) = gameParams
-    (alpha, tau, gamma) = agentParams
-
-    payoffs = TwoPlayers.generateGames(*gameParams)
-
-
-    qValues = np.random.rand(2, nActions, nSim)
-
-    allActions = [TwoPlayers.getActionProbs(qValues, nSim, agentParams).reshape((2 ** nActions))]
-
-    for cIter in range(sizeX + 1):
-        qValues = TwoPlayers.qUpdate(qValues, payoffs, nSim, nActions, agentParams)
[…]

### 2021-02-18 Code/ThreeBodyQL/tests.jl

@@ -1,5 +1,0 @@
-using PyCall
-pygui(gui)
-using PyPlot
-
-surf(rand(30,40))

### 2021-03-11 Documents/FP in NAGs/FPNAG.tex
added FP in NAG document

\documentclass{article}
\usepackage[margin=2cm]{geometry}
\usepackage{amsmath, amsfonts, amsthm}
\usepackage{xcolor}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}

\newcommand{\ah}[1]{\textcolor{blue}{AH: \textit{#1}}}
\newcommand{\svs}[1]{\textcolor{red}{FB: \textit{#1}}}

\title{Fictitious Play in Network Aggregative Games}
\author{AH, FB}

\begin{document}

	\maketitle

	The idea is to require that each agent $i$ play a best response to the history of the aggregate strategy in their neighbourhood. We can think of this as the agent being able to `measure' the aggregate strategy of its neighbours or as some centralised observer giving this reference to the agent.

	To formalise this, we assume that we have a set of agents $V = \{1, ..., p \}$ which can be thought of as nodes on a graph $\{V, E, W\}$ where $E$ is the edge-set (i.e. the set of pairs $(i, j)$ such that i and j are connected) and $W$ is a weighted adjacency matrix $[W]_{ij} = w_{ij}$. Let $N_i := \{j \in V : (i, j) \in E\}$ be the set of player $i's$ neighbours. Note $w_{ij} = 0$ if $(i, j) \not\in E$, $w_{ij} \in (0, 1]$ if $(i, j) \in E$. We impose the normalisation condition that $\sum_{j \in N_i} w_{ij} = 1$. This requirement ensures that the aggregate strategy $\sum_{j \in N_i} w_{ij} x_j$ (where $x$ is a probability vector) remains a probability vector. For example, in the 3 player case:

	\begin{equation}
	\sigma_1 := w_{12} y + w_{13} z = 
	w_{12}
	\begin{bmatrix}
	y_1 \\ y_2 \\ 1 - y_1 - y_2
	\end{bmatrix}		
	+ 	w_{13}
	\begin{bmatrix}
	z_1 \\ z_2 \\ 1 - z_1 - z_2
	\end{bmatrix}	= 
	\begin{bmatrix}
	w_{12} y_1 + w_{13} z_1 \\ w_{12} y_2 + w_{13} z_2 \\ 1 - (w_{12} y_1 + w_{13} z_1) - (w_{12} y_2 + w_{13} z_2)
	\end{bmatrix}	
	\end{equation}

	In the continuous time case, we're also going to assume that each agent $i$ chooses a mixed strategy $x_i(t) \in \Delta_i$ at time $t$ from its strategy space $\Delta_i$ (which is an $N-$simplex). We assume that $i$ has just the one strategy that it can play against all of its neighbours.

	Once the strategy is chosen, the agent plays the game and receives payoff $u_i (x_i, \sigma_i)$, where $\sigma_i$ is the aggregate strategy vector that $i$ perceives. The best response map $BR_i$ maps any $\sigma_i$ to the set $\arg\max_{x \in \Delta_i} u_i (x, \sigma_i)$. Then $x_i$ is a `best response' to $\sigma_i$ if $x_i \in BR_i(\sigma_i)$.

	\begin{definition}(NE)
		The set of vectors $\{ x_i^*\}_{i = 1}^p$ is an NE if, for all $i$,

		\begin{equation*}
		x_i^* \in BR_i( w_{ii} x_i^* + \sum_{j \in N_i} w_{ij} x_j^*).
		\end{equation*}

	\end{definition}

	\subsection*{Case: Aggregation is dependent only on its neighbours}

	We start with the following assumption

	\begin{assumption}
	$w_{ii} = 0$ for all $i \in \{ 1, ..., N \}$
	\end{assumption}

	Under this assumption the $BR$ map becomes

	\begin{equation}
		BR_i(\sum_{j \in N_i} w_{ij} x_j) = \arg\max_{x \in \Delta_i} u_i(x_i,\sum_{j \in N_i} w_{ij} x_j)
	\end{equation}

	Let us now make the assumption that the payoff function is bilinear and can be written as $u_i(x_i, \sigma_i) = x_i \cdot A^i \sigma_i$. Then

	\begin{equation*}
		u_i(x_i, \sigma_i) = x_i \cdot A^i \sum_{j \in N_i} w_{ij} x_j = \sum_{j \in N_i} x_i \cdot A^{ij} x_j =: \sum_{j \in N_i} u_{ij}(x_i, x_j) 
	\end{equation*}

	where $A^{ij} := w_{ij} A^i$ and $u_{ij}$ is a bilinear payoff between $i$ and $j$ as defined by Ewerhart. With this transformation, we can move from a network aggregative system to a network game formulation (as in Ewerhart) in which each agent $i$ plays a game $G_{ij}$ against $j$ with payoff $A^{ij}$ and with the added requirement that each agent plays the same strategy against each of its neighbours.

	The Network Aggregative Fictitious Play requires that the agent plays a best response to the time average of $\sigma_i$. So let us have the following definitions:

	\begin{align}
		\alpha_{\sigma_i}(t) = \frac{1}{t} \int_{0}^{t} \sigma_i(t') \, dt'\nonumber \\
		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} x_i(t') \, dt', \nonumber
	\end{align}

	where $x_i(t')$ denotes the action played by $i$ at time $t'$. Now we notice

	\begin{align}
		\alpha_{\sigma_i}(t) = \frac{1}{t} \int_{0}^{t} \sigma_i(t') \, dt' = \frac{1}{t} \int_{0}^t \sum_{j \in N_i} w_{ij} x_j(t') \, dt' = \sum_{j \in N_i} w_{ij} \frac{1}{t} \int_{0}^t x_j(t') \, dt' = \sum_{j \in N_i} w_{ij} \alpha_j(t) \nonumber \\
	\end{align}

	So, then, a Continuous Time Fictitious Play (CTFP) is a map $m$ such that each of its components $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\sum_{j \in N_i} w_{ij} \alpha_j(t))$ for all $t \geq 1$. Using the transformation from before, this is the requirement that, in the equivalent network game, $m_i(t) \in \arg \max_{x \in \Delta_i} \sum_{j \in N_i} u_{ij}(x_i, \alpha_j)$ for all $t \geq 1$. Now, Ewerhart showed that, in a zero-sum network (where the sum of all $u_i$ is zero), such an $m$ exists and any such $m$ converges to an NE.

	To clarify what the convergence property means in this context, each $m$ is associated with an $\alpha(t; m) = \frac{1}{t} \int_{0}^t m_i(t') \, dt'$. Let $A(m)$ denote the set of accumulation points of $\alpha(t; m)$ (i.e. the set of $\mu$ where there exists a sequence $\{t_q\}_{q = 0}^{\infty}$ such that $\lim_{q \rightarrow \infty} t_q = \infty$ and $\lim_{q \rightarrow \infty} \alpha(t_q; m) = \mu$). Convergence to an NE means that $A(m)$ is contained within the set of NE of the game.

	In any case, the fact that $m$ converges to an NE for the equivalent network game means that it converges for the NAG also. \ah{To make this precise, I'll follow through the proof of Ewerhart}

	\begin{theorem}
		For any zero-sum Network Aggregative Game which follows the above assumption, any CTFP $m$ has the property that $A(m)$ is contained within the set of NE of the game.
	\end{theorem}

	\begin{proof}
		Take the Lyapunov function
		\begin{align}
			L(\mu) & = \sum_i \max_{x \in \Delta_i} \{u_i(x, \sum_{j \in N_i} w_{ij} \mu_j) - u_i(\mu_i, \sum_{j \in N_i} w_{ij} \mu_j) \} \nonumber \\
			& = \sum_i \max_{x \in \Delta_i} \{u_i(x, \sum_{j \in N_i} w_{ij} \mu_j)\} - \sum_i u_i(\mu_i, \sum_{j \in N_i} w_{ij} \mu_j) \nonumber \\
			& = \sum_i \max_{x \in \Delta_i} \{u_i(x, \sum_{j \in N_i} w_{ij} \mu_j)\} \nonumber
		\end{align}

		where the last equality holds because we made the assumption of a zero sum game. Making the usual transformation, we consider that $i$ is now involved in a network game in which it plays the same strategy against each of its neighbours $j$ giving

		\begin{align}
			L(\mu) = \sum_i \max_{x \in \Delta_i} \sum_{j \in N_i}  u_{ij}(x, \mu_j) \nonumber \\
		\end{align}

		Now we take any CTFP $m$ and recall that it is found by playing the best response to $\alpha(t; m)$, which of course means that it maximises $\sum_{j \in N_i} u_{ij}$. Therefore

		\begin{align}
			L(\alpha(t)) & = \sum_i \sum_{j \in N_i} u_{ij}(m_i(t), \alpha_j(t)) \nonumber \\
			& = \sum_i \sum_{j \in N_i} m_i(t) A^{ij} \alpha_j(t)
		\end{align}

		 Now if we were to follow on using Ewerhart's proof, we would find that any accumulation point of $\alpha(t; m)$ is an NE of the network game. I.e. if $\mu^*$ is this limit point, then it satisfies that, for any $x \in \Delta_i$

		 \begin{align}
		 	\sum_{j \in N_i} u_{ij}(x, \mu_j^*) \leq 	\sum_{j \in N_i} u_{ij}(\mu_i^*, \mu_j^*) \nonumber
		 \end{align}

		 Now if we reverse the transformation this means that, for the network aggregative game we have the condition that for any $x \in \Delta_i$

		 \begin{align}
		 	u_{i}(x, \sum_{j \in N_i} w_{ij} \mu_j^*) \leq u_{i}(\mu_i^*, \sum_{j \in N_i} w_{ij} \mu_j^*)
		 \end{align}

	\end{proof}
	\newpage

	\subsection*{Second Case}

	\begin{align}
		x_i^* &\in \arg\max_{x \in \Delta_i} u_i(x_i, w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j^*) \nonumber\\
		&= \arg\max_{x \in \Delta_i} \bar{u}_i(x_i, \sum_{j \in N_i} w_{ij} x_j^*)
	\end{align}

	Since $\sigma_i$ shares the same strategy space as $x_i$, and we assume that this space is finite, then a NE exists. $\ah{If we decide to lift the finite strategy space requirement, we'll have to show the existence of an NE.}$

	Now, for fictitious play, we require that the agent plays against the time average of this reference $\sigma_i$. We can write this as

	\begin{equation}
		x_i(t) \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right).
	\end{equation}

	By the definition of Continuous Time Fictitious Play (CTFP) given by Ewerhart, we require that $m: [0, \infty] \rightarrow \times_i \Delta_i$ is a measurable mapping such that, for each $i$, $m_i(t) \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right)$. Now notice,

	\begin{equation*}
		x_i \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right) \iff  \in x_i\in BR_i \left( \frac{1}{t} \int_{0}^{t} [w_{ii} m_i(t') + \sum_{j \in N_i} w_{ij} m_j(t')] \, dt' \right)
	\end{equation*}

	Let us assume that $u_i$ takes the form $x \cdot A_i \sigma_i$ where $A_i$ is the payoff matrix associated with agent $i$. Then,

	\begin{align}
		& x_i \in \arg\max_{x \in \Delta_i} u_i(x,\frac{1}{t} \int_{0}^{t} [w_{ii} m_i(t') + \sum_{j \in N_i} w_{ij} m_j(t')] \, dt') \nonumber \\
		\iff & x_i \in \arg\max_{x \in \Delta_i} x \cdot A_i \left(\frac{1}{t} \int_{0}^{t} [w_{ii} m_i(t') + \sum_{j \in N_i} w_{ij} m_j(t')] \, dt' \right) \nonumber \\
		\iff & x_i \in \arg \max_{x \in \Delta_i} x \cdot (w_{ii} A_i) \left( \frac{1}{t} \int_{0}^{t} m_i(t')\right) + \sum_{j \in N_i} x \cdot (w_{ij} A_i) \left( \frac{1}{t} \int_{0}^{t} m_j(t')\right) \nonumber \\
		\iff & x_i \in \arg \max_{x \in \Delta_i} x \cdot A_{ii} \alpha_i(t; m) + \sum_{j \in N_i} x \cdot A_{ij} \alpha_j(t; m).
	\end{align}

	where each $A_{ij} = w_{ij} A_i$ and $\alpha_i(t; m) =\frac{1}{t} \int_{0}^{t} m_i(t') dt'$ as defined by Ewerhart. We can, therefore, think of the network aggregative game as a network game in which each agent plays the same strategy against each of its neighbours, itself included. As such, any $m$ which satisfies the CTFP property for the equivalent network game also satisfies the CTFP requirement for the network aggregative game.

	Continuing with this approach, let us look at the case where $\sum_i A_i = \textbf{0}_{n\times n}$ (i.e. a zero sum game). This means that $\sum_i u_i = 0$. Let $\mu_i^* = \lim_{t \rightarrow \infty} \alpha_i(t; m)$. More specifically, $\mu_i^*$ belongs to the set of accumulation points of $\alpha_i(\cdot; m)$ (which is set valued since the $BR_i$ map is set valued). To say that the game has `converged' we require that every $\mu^* = (\mu_1^*, ... \mu_p^*)$ is an NE. \ah{I'll follow through the proof of Ewerhart for the sake of completeness: }

	Let us take the Lyapunov function

	\begin{equation}
		L(\mu) = \sum_i \max_{e_i \in \Delta_i} \{u_i(e_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) - u_i(\mu_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \}
	\end{equation}

	Using the same transformation as before:

	\begin{align}
		 u_i(e_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) & =  e_i \cdot A_i (w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \nonumber \\
		 & =  e_i \cdot (w_{ii} A_i) \mu_i + \sum_{j \in N_i} e_i \cdot (w_{ij} A_i) \mu_j \nonumber \\
		  & =  \sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j \nonumber 
	\end{align}

	Then

	\begin{align}
	L(\mu) &= \sum_i \max_{e_i \in \Delta_i}\sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j  - u_i(\mu_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \} \nonumber \\
	&= \sum_i \max_{e_i \in \Delta_i} \{\sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j  \} - \sum_i  u_i(\mu_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \nonumber \\
	&= \sum_i \max_{e_i \in \Delta_i} \{\sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j  \} \nonumber 
	\end{align}

	where the last equality holds because $\sum_i u_i = 0$. Again, if we were to relate this to a network game, in which each agent plays the same strategy against all its neighbours (itself included), then with the definition $ \tilde{u}_i (e_i, \mu_{-i}) := \sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j$, we still satisfy the zero sum condition for $\tilde{u}$. Now, we take a CTFP $m$ according to Ewerhart, with the condition that each agent plays the same strategy across all of its neighbours. This was shown by Ewerhart to converge. I.e. for any $\mu^*$ in the accumulation points of $\alpha(\cdot; m)$

	\begin{equation*}
		\tilde{u}_i(e_i, \mu_{-i}^*) \leq \tilde{u}_i(\mu_i^*, \mu_{-i}^*)
	\end{equation*}

	which, as we know, means that $\mu^*$ satisfies

	\begin{equation*}
		u_i(e_i, w_{ii} \mu_i^* + \sum_{j \in N_i} w_{ij} \mu_j^*) \leq  u_i(\mu_i^*, w_{ii} \mu_i^* + \sum_{j \in N_i} w_{ij} \mu_j^*)
	\end{equation*}

\end{document}

### 2021-03-18 Documents/FP in NAGs/FPNAG.tex
Update FPNAG.tex

@@
 \usepackage{xcolor}
+\usepackage{enumerate}
 
@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
+\newtheorem*{assumption}{Assumption}
 
@@
 
-	The idea is to require that each agent $i$ play a best response to the history of the aggregate strategy in their neighbourhood.
-We can think of this as the agent being able to `measure' the aggregate strategy of its neighbours or as some centralised observer giving this reference to the agent.
+	\subsection*{The Model}
 
-	To formalise this, we assume that we have a set of agents $V = \{1, ..., p \}$ which can be thought of as nodes on a graph $\{V, E, W\}$ where $E$ is the edge-set (i.e.
+	We have a set of agents $V = \{1, ..., N \}$ which can be thought of as nodes on a graph $\{V, E, W\}$ where $E$ is the edge-set (i.e.
 the set of pairs $(i, j)$ such that i and j are connected) and $W$ is a weighted adjacency matrix $[W]_{ij} = w_{ij}$.
@@
 	\begin{definition}(NE)
-		The set of vectors $\{ x_i^*\}_{i = 1}^p$ is an NE if, for all $i$,
+		The set of vectors $\{ x_i^*\}_{i = 1}^N$ is an NE if, for all $i$,
 
@@
 
-	\subsection*{Case: Aggregation is dependent only on its neighbours}
+	\subsection*{Starting Assumptions}
 
-	We start with the following assumption
+	\begin{enumerate}[I]
+		\item The weights $w_{ij}$ are constant for all $i, j$.
+		\item The payoffs $u_i$ are in matrix form, and so are bilinear.
+		\item All agents update their strategies synchronously
+		\item All agents have the same sized strategy space 
+		\item The network is zero-sum in the sense that $\sum_i u_i(x_i, w_{ii} x_i + \sum_{j} w_{ij} x_j)$ for any set of strategies $(x_1, ..., x_N)$. 
+	\end{enumerate}
 
-	\begin{assumption}
-	$w_{ii} = 0$ for all $i \in \{ 1, ..., N \}$
-	\end{assumption}
+	\subsection*{The Argument for Bilinear Payoffs}
 
-	Under this assumption the $BR$ map becomes
+	\textit{Zero-sum polymatrix games can model common situations in which nodes in a network interact pairwise and make decisions (for example, adopt one of many technologies, or choose one or more of their neighbors for preferential interaction)} (Cai et al (2016)))
 
-	\begin{equation}
-		BR_i(\sum_{j \in N_i} w_{ij} x_j) = \arg\max_{x \in \Delta_i} u_i(x_i,\sum_{j \in N_i} w_{ij} x_j)
-	\end{equation}
+	\ah{Need to find more references to put in here, most papers don't really give real world examples to justify this model.}
 
-	Let us now make the assumption that the payoff function is bilinear and can be written as $u_i(x_i, \sigma_i) = x_i \cdot A^i \sigma_i$. Then
+	\subsection*{Fictitious Play in Network Aggregative Games}
+
+	For Fictitious Play (FP), we require that the agent plays a best response to the time average to a \emph{reference signal} $\sigma_i$ which is some convex combination of the agent's own strategy and that of its neighbours on the network.
+Under the above assumptions, this reference is given as
 
 	\begin{equation*}
-		u_i(x_i, \sigma_i) = x_i \cdot A^i \sum_{j \in N_i} w_{ij} x_j = \sum_{j \in N_i} x_i \cdot A^{ij} x_j =: \sum_{j \in N_i} u_{ij}(x_i, x_j) 
+		\sigma_i (t) = \sum_{j} w_{ij} x_j (t).
 	\end{equation*}
 
-	where $A^{ij} := w_{ij} A^i$ and $u_{ij}$ is a bilinear payoff between $i$ and $j$ as defined by Ewerhart.
-With this transformation, we can move from a network aggregative system to a network game formulation (as in Ewerhart) in which each agent $i$ plays a game $G_{ij}$ against $j$ with payoff $A^{ij}$ and with the added requirement that each agent plays the same strategy against each of its neighbours.
-
-	The Network Aggregative Fictitious Play requires that the agent plays a best response to the time average of $\sigma_i$. So let us have the following definitions:
+	Let us have the following definitions:
 
@@
 	\begin{align}
-		\alpha_{\sigma_i}(t) = \frac{1}{t} \int_{0}^{t} \sigma_i(t') \, dt' = \frac{1}{t} \int_{0}^t \sum_{j \in N_i} w_{ij} x_j(t') \, dt' = \sum_{j \in N_i} w_{ij} \frac{1}{t} \int_{0}^t x_j(t') \, dt' = \sum_{j \in N_i} w_{ij} \alpha_j(t) \nonumber \\
+		\alpha_{\sigma_i}(t) = \frac{1}{t} \int_{0}^{t} \sigma_i(t') \, dt' = \frac{1}{t} \int_{0}^t \sum_{j} w_{ij} x_j(t') \, dt' = \sum_{j} w_{ij} \frac{1}{t} \int_{0}^t x_j(t') \, dt' = \sum_{j} w_{ij} \alpha_j(t) \nonumber \\
 	\end{align}
 
-	So, then, a Continuous Time Fictitious Play (CTFP) is a map $m$ such that each of its components $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\sum_{j \in N_i} w_{ij} \alpha_j(t))$ for all $t \geq 1$.
-Using the transformation from before, this is the requirement that, in the equivalent network game, $m_i(t) \in \arg \max_{x \in \Delta_i} \sum_{j \in N_i} u_{ij}(x_i, \alpha_j)$ for all $t \geq 1$.
+	\paragraph{Continuous Time Fictitious Play (CTFP)} A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
+
+	We can think of this definition as saying that the player plays some generic strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
+
+	\paragraph{Discrete Time Fictitious Play (DTFP)} A DTFP is defined a sequence $\{x_{k}\}_{k=1}^{\infty}$ with components $x_{k, i}$ such that, for all $i$ and, for all $k \geq 1$, $x_{k, i} \in BR_i\left( \frac{1}{k} \sum_{t = 0}^{k - 1} \sigma_{k, i} \right)$.
+
+	We can see that the DTFP is just the equivalent definition as the CTFP, except that the time domain is $\mathbb{Z}_+$ rather than $\mathbb{R}_+$.
+Nevertheless, the change from continuous to discrete is not trivial and we'll get to that soon.
+
+	\paragraph{Convergence} We write $\alpha$ as the concatenation of all $\alpha_i$.
+Let $\Omega(\alpha)$ be  the set of all limit points for $\alpha$.
+Then, CTFP is said to have converged if any $\mu^* \in \Omega(\alpha)$ is contained in the set of Nash Equilibria of the game.
+
+	With these definitions out of the way, we'll try to figure out whether, first, CTFP converges to a Nash Equilibrium. The process for doing this is as follows:
+
+	\begin{enumerate}
+		\item Show that a Nash equilibrium exists
+		\item Show that a path satisfying the CTFP property exists
+		\item Show that the associated $\Omega(\alpha)$ is contained in the set of NE.
+
+	\end{enumerate}
+
+	\subsection*{First Case: Aggregation is dependent only on its neighbours}
+
+	We start with the following assumption
+
+	\begin{assumption}[V]
+	$w_{ii} = 0$ for all $i \in \{ 1, ..., N \}$
+	\end{assumption}
+
+	Under this assumption the $BR_i$ map becomes
+
+	\begin{equation}
+		BR_i(\sum_{j \in N_i} w_{ij} x_j) = \arg\max_{x \in \Delta_i} u_i(x_i,\sum_{j \in N_i} w_{ij} x_j)
+	\end{equation}
+
+	Under the assumption that the payoff function is bilinear and can be written as $u_i(x_i, \sigma_i) = x_i \cdot A^i \sigma_i$. Then
+
+	\begin{equation*}
+		u_i(x_i, \sigma_i) = x_i \cdot A^i \sum_{j \in N_i} w_{ij} x_j = \sum_{j \in N_i} x_i \cdot A^{ij} x_j =: \sum_{j \in N_i} u_{ij}(x_i, x_j) 
+	\end{equation*}
+
+	where $A^{ij} := w_{ij} A^i$ and $u_{ij}$ is a bilinear payoff between $i$ and $j$ as defined by Ewerhart. Furthermore, the NE condition is now
+
+	\begin{align}
+			x_i^* & \in BR_i(\sum_{j \in N_i} w_{ij} x_j^*). \\
+			& = \arg \max_{x \in \Delta_i} \sum_{j \in N_i} u_{ij}(x_i, x_j) 
+	\end{align}
+
+	 With this transformation, we can move from a network aggregative system to a network game formulation (as in Ewerhart) in which each agent $i$ plays a game $G_{ij}$ against $j$ with payoff $A^{ij}$ and with the added requirement that each agent plays the same strategy against each of its neighbours.
+With this change, we can apply Nash's Theorem to state that the Nash Equilibrium exists.
+
+	Applying the same transformation, CTFP becomes the requirement that, in the equivalent network game, $m_i(t) \in \arg \max_{x \in \Delta_i} \sum_{j \in N_i} u_{ij}(x_i, \alpha_j)$ for all $t \geq 1$.
 Now, Ewerhart showed that, in a zero-sum network (where the sum of all $u_i$ is zero), such an $m$ exists and any such $m$ converges to an NE.
-
-	To clarify what the convergence property means in this context, each $m$ is associated with an $\alpha(t; m) = \frac{1}{t} \int_{0}^t m_i(t') \, dt'$.
-Let $A(m)$ denote the set of accumulation points of $\alpha(t; m)$ (i.e.
-the set of $\mu$ where there exists a sequence $\{t_q\}_{q = 0}^{\infty}$ such that $\lim_{q \rightarrow \infty} t_q = \infty$ and $\lim_{q \rightarrow \infty} \alpha(t_q; m) = \mu$).
-Convergence to an NE means that $A(m)$ is contained within the set of NE of the game.
+This must therefore also be true of the network aggregative game.
 
@@
 	\begin{theorem}
-		For any zero-sum Network Aggregative Game which follows the above assumption, any CTFP $m$ has the property that $A(m)$ is contained within the set of NE of the game.
+		For any zero-sum Network Aggregative Game which follows the above assumption, any CTFP $m$ has the property that $\Omega(\alpha)$ is contained within the set of NE of the game.
 	\end{theorem}
@@
 
+	This case is much more complex and requires that we take into account all of the steps properly.
+
+	\subsubsection*{Existence of the Nash Equilibrium}
+
+	The NE condition here is the same as the original definition that we had, but I'll repeat it here for the sake of convenience. The set of vectors $\{ x_i^*\}_{i = 1}^N$ is an NE if, for all $i$,
+
+	\begin{equation*}
+		x_i^* \in BR_i( w_{ii} x_i^* + \sum_{j \in N_i} w_{ij} x_j^*).
+	\end{equation*}
+
+	Note that this requires
+
 	\begin{align}
 		x_i^* &\in \arg\max_{x \in \Delta_i} u_i(x_i, w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j^*) \nonumber\\
-		&= \arg\max_{x \in \Delta_i} \bar{u}_i(x_i, \sum_{j \in N_i} w_{ij} x_j^*)
+		&= \arg\max_{x \in \Delta_i} \bar{u}_i(x_i, \sum_{j \in N_i} w_{ij} x_j^*),
 	\end{align}
 
-	Since $\sigma_i$ shares the same strategy space as $x_i$, and we assume that this space is finite, then a NE exists.
-$\ah{If we decide to lift the finite strategy space requirement, we'll have to show the existence of an NE.}$
+	where we can find $\bar{u}_i$ through the following argument
 
-	Now, for fictitious play, we require that the agent plays against the time average of this reference $\sigma_i$. We can write this as
+	\begin{align}
+		u_i(x_i, w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j^*) & = x_i \cdot A_i (w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j) \\
+		 & = x_i \cdot (w_{ii} A_i)  x_i + \sum_{j \in N_i} u_{ij}(x_i, x_j) \\
+		 & =: \bar{u}_i(x_i, \sum_{j \in N_i} w_{ij} x_j^*), \nonumber
+	\end{align}
+
+	where $u_{ij}$ is as previously defined. Note that, in order to get this formulation, we had to use the bilinear assumption (II) so that we could separate out the term involving $x_i$ easily.
+
+	Writing the NE condition out as a vector gives
+
+	\begin{equation}
+		\begin{bmatrix}
+			x_1^* \\ . \\ . \\ . \\ x_N^*
+		\end{bmatrix} \in
+		\begin{bmatrix}
+		\arg\max_{y \in \Delta_1} \bar{u}_1(y, \sum_{j \in N_i} w_{ij} x_j^*) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, \sum_{j \in N_i} w_{ij} x_j^*)
+		\end{bmatrix}	.
+	\end{equation}
+
+	We can rewrite the weighted summation in the $i$'th component of the right hand side as
+
+	\begin{equation}
+		\sum_{j \in N_i} w_{ij} x_j^* = (w_{-i}^T \otimes I_n) \begin{bmatrix}
+			x_1^* \\ . \\ . \\ . \\ x_N^*
+		\end{bmatrix},
+	\end{equation}
+
+	in which $w_{-i}$ is a column vector containing $w_{ij}$ in the $j$'th element for all $j \in N(i)$ and 0 everywhere else (including in the $i$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product.
+So our condition becomes
+
+	\begin{equation}
+		\begin{bmatrix}
+			x_1^* \\ . \\ . \\ . \\ x_N^*
+		\end{bmatrix} \in
+		\begin{bmatrix}
+			\arg\max_{y \in \Delta_1} \bar{u}_1(y, (w_{-1}^T \otimes I_n) \begin{bmatrix}
+				x_1^* \\ . \\ . \\ . \\ x_N^*
+			\end{bmatrix}) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n) \begin{bmatrix}
+			x_1^* \\ . \\ . \\ . \\ x_N^*
+		\end{bmatrix}))
+		\end{bmatrix}	.
+	\end{equation}
+
+	This means that we achieve a Nash Equilibrium iff $\{ x_i^*\}_{i = 1}^N$ is a fixed point of the map
+
+	\begin{equation}
+		\begin{bmatrix}
+			\arg\max_{y \in \Delta_1} \bar{u}_1(y, (w_{-1}^T \otimes I_n) ( \cdot )) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n)( \cdot )))
+		\end{bmatrix}	.
+	\end{equation}
+
+	Now, since the modified payoff $\bar{u}$ shares the same bilinear property as $u$, we can assert that it is continuous is its second argument.
+Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous (\ah{I think this argument is sound so I'm not sure if it's worth making it rigorous}).
+Furthermore, the map takes a point in $\Delta = \times_i \Delta_i$ into itself.
+As such, the space is non-empty, compact and convex.
+
+	We can then apply Kakutani's Fixed Point Theorem
+
+	\begin{theorem}[Kakutani]
+		If S is a nonempty, compact, convex set in $\mathbb{R}^n$ and $\Phi : S \rightarrow \textbf{P}(S)$ ($\textbf{P}(S)$ is the power set of S) is upper semi-continuous, then $\Phi$ has a fixed point.
+	\end{theorem}
+
+	Therefore, the existence of an NE follows from the above Theorem.
+
+	\subsubsection*{Existence of a CTFP}
+
+	Let us return to the definition of $\alpha_i$, which I repeat here for convenience
+
+	\begin{equation*}
+		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} x_i(t') \, dt'
+	\end{equation*}
+
+	Then
+
+	\begin{align}
+		\frac{d}{dt} \alpha_i(t) & = \frac{d}{dt} \frac{1}{t} \int_{0}^t m_i(t') dt' \nonumber \\
+		& = \frac{1}{t} m_i(t) - \frac{1}{t} \alpha_i(t)
+	\end{align}
+
+	Now, we since we can rewrite the best response function $BR_i$ as $\arg\max_{y \in \Delta_i} \bar{u}_i(y, (w_{-i}^T \otimes I_n) \begin{bmatrix}
+		x_1 \\ . \\ . \\ . \\ x_N
+	\end{bmatrix})$, we can rewrite the CTFP condition as, for all $i$ and all $t \geq 1$
+
+	\begin{equation}
+		m_i(t) \in BR_i((w_{-i}^T \otimes I_n) \begin{bmatrix}
+			x_1 \\ . \\ . \\ . \\ x_N
+		\end{bmatrix})
+	\end{equation}
+
+	This gives
+
+	\begin{equation}
+		\Dot{\alpha}_i(t) \in \frac{1}{t} (BR_i((w_{-i}^T \otimes I_n) \begin{bmatrix}
+			x_1 \\ . \\ . \\ . \\ x_N
+		\end{bmatrix}) - \alpha_i(t))
+	\end{equation}
+
+	\newpage
 
@@
 
-	By the definition of Continuous Time Fictitious Play (CTFP) given by Ewerhart, we require that $m: [0, \infty] \rightarrow \times_i \Delta_i$ is a measurable mapping such that, for each $i$, $m_i(t) \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right)$.
+	By the definition of Continuous Time Fictitious Play (CTFP) given by Ewerhart, we require that $m: [0, \infty) \rightarrow \times_i \Delta_i$ is a measurable mapping such that, for each $i$, $m_i(t) \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right)$.
 Now notice,

### 2021-03-19 Documents/Literature Review/Literature Review - Revised/.history/sections/MARL_20200106085934.tex
Reorganised Structure

--- 2020-05-22 Documents/Literature Review/Literature Review - Revised/sections/MARL.tex
@@
 
-\section{Game Dynamics}
-
-Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
-problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
-another. This model then serves to be able to predict the evolution of the system as well as to
-understand the trajectory of learning. Typically, this looks at considering whether or not the
-method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
-solve \cite{ShohamMultiagentFoundations} for all but toy problems.
-\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
-are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
-Stability provides some guarantees against the stochastic nature of the environment since a stable
-equilibrium will always be returned to even after perturbations. This extremely important in Safe
-and Trusted AI as it provides guarantees against undesired behaviour in real world environments.
-
-The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
-evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
-considers similar assumptions to that of MARL: agents are no longer required to be rational and
-play the game optimise their expected return through repeated play. Importantly, players have no
-knowledge of the others' payoffs \cite{Tuyls2006AnGames}. In \cite{Tuyls2006AnGames}, Tuyls et al.
-determine the relation between the replicator dynamics concept of EGT (a differential equation
-defining the evolution of the proportion of a subgroup in an evolving population) and Q-Learning
-using Boltzmann probabilities as Q-values. The result was a dynamics equation which describes, for
-each action, the evolution of its selection probability which could even account for random
-exploration. There have since been a number of works which apply the same insight into different
-game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken into the following
-categories
-
-\begin{itemize}
-	\item Stateless games with discrete actions. Here, stateless refers to the idea that the game is
-	static and so the environment has no impact on the result. The aforementioned result 
-	\cite{Tuyls2006AnGames} fits into this category.
-	\item Stateless games with continuous actions. These consider more realistic MARL than the
-	previous category by replacing each agent's strategy vector with a probability density function 
-	(pdf) over a continuous action space.
-	\item Stateful games with discrete actions. This mostly considers stochastic games, where there
-	are multiple states with probabilistic (usually Markovian) transitions between them. However,
-	extensive form games, which considers more complex phenomena such as sequential moves and
-	imperfect information, are also briefly mentioned.
-	\item Stateful games with continuous actions. This is one of the more realistic assumptions
-	considered. However, the authors point out that this area is yet to see results, leaving it open
-	for possible research.
-\end{itemize}
-
-Though the above have seen success through experimental validation in games with 2 players and (in
-general) 2 to 3 discrete actions, recent work has begun the consideration of improving the models
-towards more complex scenarios with larger agent populations. A recent example of this is 
-\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
-Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
-its strategy based on the mean effect of the population. The result is a system of three equations
-which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
-presents an important first step in modelling the learning dynamics of large agent populations and
-has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
-games.
-
-An advantage of determining the evolutionary dynamics of learning is that it can describe the
-expected behaviour in different game settings. This is particularly important to understand the
-convergence of the methods; certain games will often show cyclic behaviour even with the existence
-of a strict NE. For instance, Imhof et al. show in \cite{Imhof2005} that a repeated prisoner's
-dilemma game results in cyclic behaviour when considering the options of cooperation or defection.
-
 \section{Stable Learning}

### 2021-03-19 Code/Fictitious Play/Fictitious Play Payoff Performance/FPOrbit.py

@@ -1,0 +1,126 @@
+def FPOrbit(x0, G, nIter):
+    A, B = G
+    pX, qY = x0[0][:, 0], x0[1][:, 0]
+
+    print(pX.shape)
+
+    dim = np.shape(pX)[0]
+
+    allPX = np.zeros((dim, nIter))
+    allQY = np.zeros((dim, nIter))
+
+    erX, erY = pX.T @ A @ qY, pX.T @ B @ qY
+    allerX, allerY = np.zeros(nIter), np.zeros(nIter)
+
+    for n in tqdm(range(1, int(nIter) + 1)):
+        eX, eY = np.zeros(dim), np.zeros(dim)
+        brX, brY = np.argmax(A @ qY), np.argmax(pX.T @ B)
+        eX[brX] = 1
+        eY[brY] = 1
+
+        pX = (n * pX + eX) / (n + 1)
+        qY = (n * qY + eY) / (n + 1)
+
+        allPX[:, n-1] = pX
+        allQY[:, n-1] = qY
+
+        erX = (n * erX + (pX.T @ A @ qY)) / (n + 1)
+        erY = (n * erY + (pX.T @ B @ qY)) / (n + 1)
+
+        allerX[n-1] = erX
+        allerY[n-1] = erY
+
+    return allPX, allQY, allerX, allerY
+
+def plotOnSimplex(gamma, trajX, trajY):
+    f, (ax) = plt.subplots(1, 2)
+
+    proj = np.array(
+        [[-1 * np.cos(30 / 360 * 2 * np.pi), np.cos(30 / 360 * 2 * np.pi), 0],
+         [-1 * np.sin(30 / 360 * 2 * np.pi), -1 * np.sin(30 / 360 * 2 * np.pi), 1]
+         ])
+
+    ts = np.linspace(0, 1, 10000)
+
+    e1 = proj @ np.array([ts, 1 - ts, 0 * ts])
+    e2 = proj @ np.array([0 * ts, ts, 1 - ts])
+    e3 = proj @ np.array([ts, 0 * ts, 1 - ts])
+
+    ax[0].plot(e1[0], e1[1], 'k-', alpha = 0.3)
+    ax[0].plot(e2[0], e2[1], 'k-', alpha = 0.3)
+    ax[0].plot(e3[0], e3[1], 'k-', alpha = 0.3)
+
[…]

### 2021-03-19 Code/Fictitious Play/Fictitious Play Payoff Performance/PayoffPerformance.py

@@ -84,23 +84,38 @@ def getAllNEPayoffs(allNEPayoffs, nSim):
 
     return np.array(NEX).T, np.array(NEY).T
 
+def sampleFromSimplex(dim, nSamples=1.5e4):
+    nSamples = int(nSamples)
+    return np.random.dirichlet(np.ones(dim), size=nSamples)
+
+def ABar(samples, A, q):
+    return np.max(np.einsum('ni,ijs,jcs->ncs', samples, A, q), axis=0)
+
+def BBar(samples, B, p):
+    return np.max(np.einsum('ics,ijs,nj->ncs', p, B, samples), axis=0)
+
 def simulation(gamma, dim, nSim, nInit, nIter):
-    A, B = generateGallaGames(gamma, nSim, dim)
 
-    allNE = [findNE(A[:, :, i], B[:, :, i]) for i in range(nSim)]
+    nIter = int(nIter)
 
-    simsToKeep = np.where(np.array([len(sim) for sim in allNE]) != 0)[0]
-    allNE = np.array(allNE)[simsToKeep].tolist()
-
-    A, B = A[:, :, simsToKeep], B[:, :, simsToKeep]
-
-    allNEPayoffs = [[(np.dot(sim[i][0], A[:, :, s] @ sim[i][1]), np.dot(sim[i][0], B[:, :, s] @ sim[i][1])) for i in
-                     range(len(sim))] for s, sim in enumerate(allNE)]
+    # samples = sampleFromSimplex(dim)
+    #
+    # A, B = generateGallaGames(gamma, nSim, dim)
+    #
+    # allNE = [findNE(A[:, :, i], B[:, :, i]) for i in range(nSim)]
+    #
+    # simsToKeep = np.where(np.array([len(sim) for sim in allNE]) != 0)[0]
+    # allNE = np.array(allNE)[simsToKeep].tolist()
+    #
+    # A, B = A[:, :, simsToKeep], B[:, :, simsToKeep]
+    #
+    # allNEPayoffs = [[(np.dot(sim[i][0], A[:, :, s] @ sim[i][1]), np.dot(sim[i][0], B[:, :, s] @ sim[i][1])) for i in
+    #                  range(len(sim))] for s, sim in enumerate(allNE)]
 
     # NEX = [max([NEPayoff[0] for NEPayoff in sim]) for sim in allNEPayoffs]
[…]

### 2021-03-19 Code/Q-Learning/ThreeBodyQL/ThreeBodyFunctions.py

@@ -11,10 +11,10 @@ def generateMatchingPennies():
     :return:
     """
 
-    A = np.array([[1, -1], [-1, 1]])
-    B = np.array([[-1, 1], [1, -1]])
+    C = np.array([[5, -5], [-5, 5]])
+    Z = np.array([[1, -1], [-1, 1]])
 
-    return A, B
+    return C, Z
 
 def getActionProbs(Q, agentParams):
     """
@@ -69,7 +69,7 @@ def simulate(agentParams, nIter = 5e3):
 
 def TuylsODE(X, t, G, agentParams):
 
-    A, B = G
+    C, Z = G
 
     alpha, tau, gamma = agentParams
 
@@ -81,34 +81,53 @@ def TuylsODE(X, t, G, agentParams):
     ydot = np.zeros(2)
     zdot = np.zeros(2)
 
-    xdot[0] = alpha * x[0] * tau * ((A @ y)[0] + (z.T @ B)[0] - np.dot(x, (A @ y) + (z.T @ B))) + alpha * x[0] * (x[1] * np.log(x[1]/x[0]))
-    xdot[1] = alpha * x[1] * tau * ((A @ y)[1] + (z.T @ B)[1] - np.dot(x, (A @ y) + (z.T @ B))) + alpha * x[1] * (x[0] * np.log(x[0]/x[1]))
+    xdot[0] = alpha * x[0] * tau * ((Z @ y)[0] + (Z @ z)[0] - np.dot(x, (Z @ y) + (Z @ z))) + alpha * x[0] * (x[1] * np.log(x[1]/x[0]))
+    xdot[1] = alpha * x[1] * tau * ((Z @ y)[1] + (Z @ z)[1] - np.dot(x, (Z @ y) + (Z @ z))) + alpha * x[1] * (x[0] * np.log(x[0]/x[1]))
 
-    ydot[0] = alpha * y[0] * tau * ((A @ z)[0] + (x.T @ B)[0] - np.dot(y, (A @ z) + (x.T @ B))) + alpha * y[0] * (y[1] * np.log(y[1]/y[0]))
-    ydot[1] = alpha * y[1] * tau * ((A @ z)[1] + (x.T @ B)[1] - np.dot(y, (A @ z) + (x.T @ B))) + alpha * y[1] * (y[0] * np.log(y[0]/y[1]))
[…]

### 2021-03-19 Code/Q-Learning/ThreeBodyQL/fpNetwork.py

@@ -1,0 +1,72 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import scipy as sps
+from scipy.integrate import odeint
+from tqdm import tqdm
+
+def generateMatchingPennies():
+    """
+    Create Matching Pennies Matrix
+
+    :return:
+    """
+
+    C = np.array([[1, -1], [-1, 1]])
+    Z = np.array([[2.4, -2], [-2, 2]])
+
+    return C, Z
+
+def initialiseRandomVec():
+    return np.random.dirichlet(np.ones(2), size=(3)).reshape(6)
+
+def FPOrbit(x0, G, nIter):
+    Z, C = G
+
+    x, y, z = x0[0:2], x0[2:4], x0[4:]
+
+    allX = np.zeros((nIter, 6))
+
+    for n in tqdm(range(1, nIter + 1)):
+        eX, eY, eZ = np.zeros(2), np.zeros(2), np.zeros(2)
+        brX = np.argmax(C @ y + C @ z)
+        brY = np.argmax(C.T @ x + Z @ z)
+        brZ = np.argmax((C.T @ x + (-Z).T @ y))
+
+        eX[brX] = 1
+        eY[brY] = 1
+        eZ[brZ] = 1
+
+        x = (n * x + eX) / (n + 1)
+        y = (n * y + eY) / (n + 1)
+        z = (n * z + eZ) / (n + 1)
+
+        allX[n-1] = np.hstack((x, y, z))
+
+    return allX
+
+if __name__ == "__main__":
+    nInit = 5
+    nIter = 1e5
+
+    G = generateMatchingPennies()
+
+    fig = plt.figure()
+    ax = fig.add_subplot(111, projection='3d')
+    ax.set_xlabel('P1')
+    ax.set_ylabel('P2')
+    ax.set_zlabel('P3')
+
+    ax.set_xlim([0, 1])
+    ax.set_ylim([0, 1])
+    ax.set_zlim([0, 1])
+
+    for cInit in range(nInit):
+
+        x0 = initialiseRandomVec()
+        sol = FPOrbit(x0, G, int(nIter))
+
+        ax.plot(sol[:, 0], sol[:, 2], sol[:, 4])
+        ax.scatter(sol[0, 0], sol[0, 2], sol[0, 4], marker='o', color='r')
+
+    plt.show()

### 2021-03-19 Code/Q-Learning/ThreeBodyQL/reproducingNagarajan.py

@@ -11,12 +11,13 @@ def generateMatchingPennies():
     :return:
     """
 
-    A = np.array([[1, -1], [-1, 1]])
-    B = np.array([[-1, 1], [1, -1]])
+    C = np.array([[1, -1], [-1, 1]])
+    Z = np.array([[2.4, -2], [-2, 2]])
 
-    return A, B
+    return C, Z
 
-def replicatorODE(X, t, A, B):
+
+def replicatorODE(X, t, C, Z):
 
     x = X[0:2]
     y = X[2:4]
@@ -26,28 +27,23 @@ def replicatorODE(X, t, A, B):
     ydot = np.zeros(2)
     zdot = np.zeros(2)
 
-    xdot[0] = x[0] * ((A @ y)[0] + (B.T @ z)[0] - np.dot(x, (A @ y) + (B.T @ z)))
-    xdot[1] = x[1] * ((A @ y)[1] + (B.T @ z)[1] - np.dot(x, (A @ y) + (B.T @ z)))
+    xdot[0] = x[0] * ((C @ y)[0] + (C @ z)[0] - np.dot(x, (C @ y) + (C @ z)))
+    xdot[1] = x[1] * ((C @ y)[1] + (C @ z)[1] - np.dot(x, (C @ y) + (C @ z)))
 
-    ydot[0] = y[0] * ((A @ z)[0] + (B.T @ x)[0] - np.dot(y, (A @ z) + (B.T @ x)))
-    ydot[1] = y[1] * ((A @ z)[1] + (B.T @ x)[1] - np.dot(y, (A @ z) + (B.T @ x)))
+    ydot[0] = y[0] * ((Z @ z)[0] + (C.T @ x)[0] - np.dot(y, (Z @ z) + (C.T @ x)))
+    ydot[1] = y[1] * ((Z @ z)[1] + (C.T @ x)[1] - np.dot(y, (Z @ z) + (C.T @ x)))
 
-    zdot[0] = z[0] * ((A @ x)[0] + (B.T @ y)[0] - np.dot(z, (A @ x) + (B.T @ y)))
-    zdot[1] = z[1] * ((A @ x)[1] + (B.T @ y)[1] - np.dot(z, (A @ x) + (B.T @ y)))
+    zdot[0] = z[0] * ((C.T @ x)[0] + ((-Z).T @ y)[0] - np.dot(z, (C.T @ x) + ((-Z).T @ y)))
[…]

### 2021-03-25 Documents/FP in NAGs/FPNAG.tex
Update FP in NAG

@@
 
-	Writing the NE condition out as a vector gives
+	To show existence of an NE we will need the following definition and Theorem.
+
+	\begin{definition}[Upper Semi-Continuous]
+		A compact-valued correspondence $\Phi: A \rightarrow B$ is \emph{upper semi-continuous} at a point $a$ if $g(a)$ is non-empty and if, for every sequence $a_n \rightarrow a$ and every sequence $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a convergent subsequence of $(b_n)$ whose limit point $b$ is in $g(a)$.
+	\end{definition}
+
+	\begin{theorem}[Kakutani]
+		Let $K \subset \mathbb{R}^n$ be compact and convex and $\Phi: K \rightarrow K$ be closed or upper semi-continuous, with nonempty, convex and compact values. Then $\Phi$ has a fixed point.
+	\end{theorem}
+
+	Note that, when active on a simplex, the function $\Phi: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes the nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.
+
+	\begin{theorem}[Existence of NE]
+		Under the assumption (II), namely that the payoff function achieves a bilinear property, a Nash Equilibrium $\{x_i^*\}_{i = 1}^N$ exists.
+	\end{theorem}
+
+	\begin{proof}
+		We begin by rewriting the NE condition by concatenating the set of NE vectors into one long colunn vector. This gives
 
@@
 		in which $w_{-i}$ is a column vector containing $w_{ij}$ in the $j$'th element for all $j \in N(i)$ and 0 everywhere else (including in the $i$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product.
+For example, the form for agent 1, in the case of 2-action game is given by
+
+		\begin{equation}
+			(w_{-1}^T \otimes I_2) = [0, w_{12}, w_{13}, ..., w_{1n}] \otimes I_2 = 
+			\begin{bmatrix}
+				0 & 0 & w_{12} & 0 & ... & w_{1n} & 0 \\
+				0 & 0 & 0 & w_{12} & ... & 0 & w_{1n} \\
+			\end{bmatrix}
+		\end{equation}
+
 		So our condition becomes
-
 		\begin{equation}
@@
 		Now, since the modified payoff $\bar{u}$ shares the same bilinear property as $u$, we can assert that it is continuous is its second argument.
-Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous (\ah{I think this argument is sound so I'm not sure if it's worth making it rigorous}).
-Furthermore, the map takes a point in $\Delta = \times_i \Delta_i$ into itself.
-As such, the space is non-empty, compact and convex.
+Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous.
+This continuity can be extended to the above concatenation of best responses.
+As such, we can apply Kakutani's Fixed Point Theorem to assert that the above map admits a fixed point.
 
-	We can then apply Kakutani's Fixed Point Theorem
-
-	\begin{theorem}[Kakutani]
-		If S is a nonempty, compact, convex set in $\mathbb{R}^n$ and $\Phi : S \rightarrow \textbf{P}(S)$ ($\textbf{P}(S)$ is the power set of S) is upper semi-continuous, then $\Phi$ has a fixed point.
-	\end{theorem}
-
-	Therefore, the existence of an NE follows from the above Theorem.
+	\end{proof}
 
@@
 
-	Let us return to the definition of $\alpha_i$, which I repeat here for convenience
+	\begin{theorem}
+		There exists a path $m$ which satisfies the property that, for all $i$, $m_i \in BR_i
+		(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
+	\end{theorem}
+
+	\begin{proof}
+		Recall the definition of $\alpha_i(t)$
 
 		\begin{equation*}
-		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} x_i(t') \, dt'
+		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} m_i(t') \, dt'
 		\end{equation*}
@@
 
-	Now, we since we can rewrite the best response function $BR_i$ as $\arg\max_{y \in \Delta_i} \bar{u}_i(y, (w_{-i}^T \otimes I_n) \begin{bmatrix}
-		x_1 \\ . \\ . \\ . \\ x_N
-	\end{bmatrix})$, we can rewrite the CTFP condition as, for all $i$ and all $t \geq 1$
+		Now we assert that $m_i(t) \in BR_i(\alpha_{\sigma_t}) = \arg\max_{y \in \Delta_i} u_i(y,
+		w_{ii} \alpha_i(t) + \sum_{j \in N(i)} w_{ij} \alpha_j(t))$.
+
+		Let us then define $\alpha(t)$ as the concatenation of all $\alpha_i(t)$
 
 		\begin{equation}
-		m_i(t) \in BR_i((w_{-i}^T \otimes I_n) \begin{bmatrix}
-			x_1 \\ . \\ . \\ . \\ x_N
-		\end{bmatrix})
+			\alpha(t) = \begin{bmatrix}
+				\alpha_1(t)^T, \ldots, \alpha_N(t)^T
+			\end{bmatrix}^T \subset \mathbb{R}^{Nn}
 		\end{equation}
 
-	This gives
+		We can, therefore, write the aggregation as
 
 		\begin{equation}
-		\Dot{\alpha}_i(t) \in \frac{1}{t} (BR_i((w_{-i}^T \otimes I_n) \begin{bmatrix}
-			x_1 \\ . \\ . \\ . \\ x_N
-		\end{bmatrix}) - \alpha_i(t))
+			(W \otimes I_n) \alpha(t) = \begin{bmatrix}
+				\sum_{j \in N(1)} w_{1j} \alpha_j(t) \\
+				.\\
+				.\\
+				.\\
+				\sum_{j \in N(N)} w_{Nj} \alpha_j(t)
+			\end{bmatrix} \subset \mathbb{R}^{Nn}
 		\end{equation}
+
+		I will write $(W \otimes I_n) \alpha(t)$ as $\alpha_W$ for convenience. Furthermore, using
+		the bimatrix property of the game, we can say that
+
+		\begin{equation}
+			\begin{bmatrix}
+				\arg\max_{y \in \Delta_1} y \cdot A_1 ( \alpha_W(t)_1) \\
+				.\\
+				.\\
+				.\\
+				\arg \max_{y \in \Delta_N} y \cdot A_n (\alpha_W(t)_N) 
+			\end{bmatrix} = 
+			\arg \max_{y \in \Delta} y \cdot \begin{bmatrix}
+				A_1 & 0 & . & . & . & 0 \\
+				0 & A_2 & . & . & . & 0 \\
+				& & . & & & \\
+				& & & . & & \\
+				& & & & . & \\
+				0 & 0 & . & . & . & A_N \\
+			\end{bmatrix} \alpha_W(t) = \arg\max_{y \in \Delta} y \cdot \Lambda (W \otimes I_n)
+			\alpha(t)
+		\end{equation}
+
+		in which $\Delta = \times_i \Delta_i$ and $\Lambda$ is the block diagonal matrix containing
+		each $A_i$.
+
+		We can now write the differential inclusion as
+
+		\begin{equation}
+			\dot{\alpha(t)} \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
+			I_n)
+			\alpha(t) \}- \alpha(t))
+		\end{equation}
+
+		with the initial condition $\alpha(1) = \mu$. Then, the path $m$ is a CTFP if its
+		corresponding $\alpha(t; m)$ is a solution to the above differential inclusion. Following
+		the definition of (Harris 1998), a solution $\alpha(t)$ must satisfy
+
+		\begin{enumerate}
+			\item $\alpha(t)$ is locally Lipschitz
+			\item $\alpha(1) = \mu$
+			\item $\dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
+			I_n)
+			\alpha(t) \}- \alpha(t))$ for almost all $t \in [1, \infty)$ 
+		\end{enumerate}
+
+		The question then remains, does the differential inclusion admit a solution? Using the
+		results of Aubin and Cellina (see Harris 1998, paragraph below Prop. 6), can use the fact
+		that the $\arg \max$ function is non-empty, compact and convex valued, bounded (all of
+		these follow since the function acts from $\Delta$ to $\Delta$) and upper semi-continuous.
+		With these facts in place, we can say that there is a CTFP for any initial value $\mu$.
+		\ah{I believe this holds for any choice of $W$ as long as it is row stochastic so that
+		the values remain inside $\Delta$ after aggregation}.
+	\end{proof}
+
+	\newpage
+
+	\section*{Convergence Properties}
+
+	I've spent some time trying to show convergence of the CTFP to a Nash Equilibrium, without the
+	requirement that $w_{ii} = 0$. Unfortunately, it doesn't look like that is the case in general,
+	at least with the other assumptions that we have made. Perhaps changing the requirement of the
+	payoff functions or the aggregation method (e.g. to a non-linear one) would influence this, but
+	for the bimatrix games that we've looked at so far, no luck.
+	We can, however, say that there is a fixed point since the solution $\alpha(t; m)$, for any CTFP
+	$m$ maps from a compact space to itself. Therefore, any sequence $\{\alpha(\tau_q; m)\}$ where
+	$\tau_q \rightarrow \infty$ as $q \rightarrow \infty$ has all of its elements inside a compact
+	set. Therefore, by the Bolzano-Wierstrass Theorem, this sequence has at least one limit point.
+	We can say that this limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
+	determine any other structure of the limit point for when this does not hold. For example, is it
+	part of the `no regret' set?
 

### 2021-03-26 Documents/FP in NAGs/FPNAG.tex
Added Responses to IJCAI

@@
 	\end{enumerate}
+
+	\newpage
 
@@
 	for the bimatrix games that we've looked at so far, no luck.
-	We can, however, say that there is a fixed point since the solution $\alpha(t; m)$, for any CTFP
+	We can, however, say that there is at least one accumulation point since the solution $\alpha(t;
+	m)$, for any CTFP
 	$m$ maps from a compact space to itself. Therefore, any sequence $\{\alpha(\tau_q; m)\}$ where
@@
 	set. Therefore, by the Bolzano-Wierstrass Theorem, this sequence has at least one limit point.
-	We can say that this limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
-	determine any other structure of the limit point for when this does not hold. For example, is it
-	part of the `no regret' set?
-
-	\newpage
+	We can say that such a limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
+	determine any other structure of the limit point for when this does not hold. For example, is
+	the limit set a singleton (i.e. a fixed point) or a set. What are the properties of this set?
+	Do they satisfy the no-regret criterion?	\newpage
 

### 2021-03-26 Documents/ChaoticDynamics/IJCAI 2021/response/ijcai21-authors-response.tex
Added IJCAI responses

% IJCAI-21 Author's response

% Template file with author's reponse

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai21-authors-response}

\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{lipsum}
\urlstyle{same}

\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}

\begin{document}

\paragraph{Reviewer 4} % (fold)
\label{par:reviewer_4}

The reviewer makes a pertinent point regarding the model chosen for the analysis. Indeed our
analysis is of an iterated normal-form game, which has a strong history in the learning community.
The state of the art regarding evolutionary game theoretic analysis of learning processes is not yet
at a stage where multi-stage games, or continuous state spaces can be accurately analysed and,
indeed, we remark in the conclusion that, as EGT models are improved to capture such complex games 
(such as with active environments or heterogeneous agents), we must analyse those models to
understand their implications for the stability and behaviour of learning algorithms such as
Q-Learning. This is a point for future work which we consider.

Regarding the novelty of the work, it should be noted that the references (Tuyls et al,
Bloembergen et al) focus on developing models for learning algorithms. We, on the other hand, focus
on understanding what these models tell us about the behaviour of Q-Learning. The closest analogue
to our own work is that of Leonardos and Piliouras, who show that the behaviour of Q-Learning can
vary
depending on the exploration-exploitation parameter. For this specific case, they find , as we do,
that the behaviour of Q-Learning can become rather complex. We, however, aim to analyse also the
influence that the number of players and number of actions has, which we show through both our
analysis and our experimentation.

% paragraph reviewer_4 (end)

\paragraph{Reviewer 6} % (fold)
\label{par:reviewer_6}

We thank the reviewer for their analysis and comments. Specifically, we wish to address the
reviewer's concerns regarding the averaging over payoff matrices. We should start by pointing out
that we do not average the effect over all possible games of interaction. Our aim instead is to
understand how the `type' of game (e.g. zero-sum, coordination etc) affects the stability of the
system. We make the point that, for example, there are an infinite number of zero-sum games, and so
it would not be instructive if we were to just take one zero-sum game (e.g. matching pennies) and
claim that the stability of the specific case is indicative of all zero-sum games. Rather, we choose
a parameter $\Gamma$, as was performed in (Sanders et al 2018) and (Galla and Farmer 2013), which
gives an insight into the correlations between the payoff matrices. For example, for a two-player
game, $\Gamma = -1$ corresponds to a zero-sum game, while $\Gamma = 1$ is a coordination game.

Now, with $\Gamma$ defined as such, if we are to analyse its effect on stability, we must average
over all games which share the same $\Gamma$. To only look at one would not be indicative of the
whole class. Therefore, we find the `average' dynamics for a particular choice of $\Gamma$ (i.e.
the `effective' dynamics). Similarly, in our experiment, if we are to analyse how the `type' of game
affects stability, we must average over multiple games of the same type. It is our finding that, for
Q-Learning, the type of game has almost no influence on the stability of the learning dynamics - an
interesting result which is contrary to that found for the Experience Weighted Attraction algorithm.

% paragraph reviewer_6 (end)

\paragraph{Reviewer 37} % (fold)
\label{par:reviewer_37}

The reviewer makes some very interesting points regarding the domain considered and the dynamical
aspect of our analysis. Regarding the former, it is true that we focus on the restricted domain for
$\Gamma$, as we were able to ensure that our theoretical analysis was sound for this domain.
Unfortunately, the analysis does not extend to the positive $\Gamma$ region, whose interest we
cannot neglect. Indeed you are correct in stating that the behaviour in this regime could be
analysed through a numerical study and, in fact, this is a point of work that we considered
immediately on the conclusion of our present work. However, we felt that it was important to focus
on the region in which the stability of the system could be analytically determined. We shall be
sure to clarify your point in revision.

We thank the reviewer for making their point regarding the existence of chaotic dynamics. Indeed it
is true that our results focus on the instability of the system. However, we also numerically
estimated Lypapunov exponents using the Kantz algorithm and found positive exponents for games of
large numbers of players or actions. We will be sure to make this point clear in our revision also.
Regarding the existence of periodic orbits, we conducted experiments which look for recurrent
behaviour, but were unable to find any, even for small classes of 2x2 games. A point of work which
we are looking at is to consider the possibility that, in fact, Q-Learning may not admit any
periodic solutions at all. As you mention, we will be sure to make these distinctions clear and we
thank the reviewer for pointing them out.

% paragraph reviewer_37 (end)

\paragraph{Reviewer 65} % (fold)
\label{par:reviewer_65}

We thank the reviewer for pointing out the clarification needed in the payoff matrices and that of
other RL methods. Regarding the former point, we must clarify that the payoffs themselves are not
Gaussian. Each agent receives their reward from a payoff matrix, as is typically the case in normal
form games. Our analysis requires that we understand how the structure of the payoff matrices
affects stability. As such, we parameterise the correlations between the payoff elements by
$\Gamma$. Now to truly understand the effect of this parameter, we must analyse the `average'
behaviour over all games which share the same $\Gamma$. To do this, we assert that the payoffs are
drawn from a multi-variate Gaussian, allowing us to leverage Gaussian identities in performing
averages. Therefore, we are not restricting to a particular class of payoffs, but rather
generalising over all possible payoff matrices and averaging the effect of those who share the same
payoff correlations.

Regarding the analysis of other reinforcement learning algorithms, we definitely believe that this
is an important and interesting line of inquiry. We mention in our conclusion that, as
dynamical models are developed for the algorithms you mention, analyses such as the present work
will help provide insight into what they predict regarding the stabilty and behaviour of those
algorithms.
% paragraph reviewer_65 (end)

\paragraph{Reviewer 90} % (fold)
\label{par:reviewer_90}

The reviewer makes quite useful suggestions regarding using some standard references for game
theoretic concepts. Indeed, our choice of references was focused on those which give the most
relevant insights into the results of the present work. We will, however, add these references in
our revision.

Regarding the behaviour of $\tau$, which partially encodes the propensity to exploit vs explore, we
chose not to focus on this result as it was analysed in (Leonardos and Piliouras 2020). Furthermore,
the analytic result shows that the dependence of stability on $\tau$ shares the same relationship as
$\alpha$. We shall be sure to clarify this, and we thank the reviewer for pointing it out.

Finally regarding the number of iterations for the numerical analysis and number of payoff matrices
analysed, we ensured that our analysis covered a number of initial conditions for each payoff
matrix, and that a small enough criterion for convergence was applied by visually assessing the
games to make sure they have converged. Furthermore, we can see that the numerical results
confidently confirm the predictions 1 - 5 made in the Discussion (Sec 3.4). 
  % paragraph reviewer_90 (end)
\end{document}

### 2021-03-27 Documents/ChaoticDynamics/IJCAI 2021/response/ijcai21-authors-response.tex
removed binaries

@@
 
+\usepackage{color}
+\newcommand\fb[1]{\textcolor{red}{FB: #1}}
+
 \newtheorem{example}{Example}
@@
 
+\fb{the first paragraph can be reduced if we need space.}
 The reviewer makes a pertinent point regarding the model chosen for the analysis. Indeed our
@@
 Q-Learning. This is a point for future work which we consider.
+
+\fb{what you write is fine, but I'd stress even further the difference and elements of novelty wrt SOTA.}
 
@@
 \label{par:reviewer_6}
+
+\fb{we could stress even further that taking $\Gamma$ to average over a certain type of reward is completely standard in the literature.}
 
@@
 Regarding the analysis of other reinforcement learning algorithms, we definitely believe that this
-is an important and interesting line of inquiry. We mention in our conclusion that, as
+is an important and interesting line of inquiry, \fb{but far beyond the scope of the current contribution}. We mention in our conclusion that, as
 dynamical models are developed for the algorithms you mention, analyses such as the present work
-will help provide insight into what they predict regarding the stabilty and behaviour of those
+will help provide insight into what they predict regarding the stability and behaviour of those
 algorithms.

### 2021-03-28 Documents/ChaoticDynamics/IJCAI 2021/response/ijcai21-authors-response.tex
Updated Author Response

--- 2021-03-26 Documents/ChaoticDynamics/IJCAI 2021/response/ijcai21-authors-response.tex
@@
 
-The reviewer makes a pertinent point regarding the model chosen for the analysis. Indeed our
-analysis is of an iterated normal-form game, which has a strong history in the learning community.
-The state of the art regarding evolutionary game theoretic analysis of learning processes is not yet
-at a stage where multi-stage games, or continuous state spaces can be accurately analysed and,
-indeed, we remark in the conclusion that, as EGT models are improved to capture such complex games 
+The reviewer makes a pertinent point regarding the assumptions made in the model chosen for the analysis.
+Indeed, we remark in the conclusion that, as EGT models are improved to capture such complex games as you mention
 (such as with active environments or heterogeneous agents), we must analyse those models to
-understand their implications for the stability and behaviour of learning algorithms such as
-Q-Learning. This is a point for future work which we consider.
+understand their implications for stability. This is a point for future work.
 
@@
 vary
-depending on the exploration-exploitation parameter. For this specific case, they find , as we do,
+depending on the exploration-exploitation parameter. For this specific case, they find, as we do,
 that the behaviour of Q-Learning can become rather complex. We, however, aim to analyse also the
@@
 analysis and our experimentation.
+There has not been a statistical study, such as ours, which aims at comprehensively classifying how stability can be affected by increasing the number of players as well as learning parameters in the Q-Learning literature.
 
@@
 system. We make the point that, for example, there are an infinite number of zero-sum games, and so
-it would not be instructive if we were to just take one zero-sum game (e.g. matching pennies) and
-claim that the stability of the specific case is indicative of all zero-sum games. Rather, we choose
-a parameter $\Gamma$, as was performed in (Sanders et al 2018) and (Galla and Farmer 2013), which
-gives an insight into the correlations between the payoff matrices. For example, for a two-player
+it would not be instructive if we were to just take one zero-sum game and
+claim that the stability in this case is indicative of all zero-sum games. Rather, we choose
+a parameter $\Gamma$ which
+gives an insight into the correlations between the payoff matrices. This is a completely standard method in the literature (c.f. (Sanders et al 2018, Galla 2013)). For example, for a two-player
 game, $\Gamma = -1$ corresponds to a zero-sum game, while $\Gamma = 1$ is a coordination game.
@@
 Now, with $\Gamma$ defined as such, if we are to analyse its effect on stability, we must average
-over all games which share the same $\Gamma$. To only look at one would not be indicative of the
-whole class. Therefore, we find the `average' dynamics for a particular choice of $\Gamma$ (i.e.
-the `effective' dynamics). Similarly, in our experiment, if we are to analyse how the `type' of game
-affects stability, we must average over multiple games of the same type. It is our finding that, for
-Q-Learning, the type of game has almost no influence on the stability of the learning dynamics - an
-interesting result which is contrary to that found for the Experience Weighted Attraction algorithm.
+over all games which share the same $\Gamma$.
+We must stress that to only analyse one zero-sum game would not be indicative of all such games.
+Therefore, we find the `average' dynamics for a particular choice of $\Gamma$ (again, this is an established technique in the literature).
+Similarly, in our experiments, if we are to analyse how the `type' of game
+affects stability, we must average over multiple games of the same type. A critical finding is that, for
+Q-Learning, the type of game has almost no influence on the stability of the learning dynamics..
 
@@
 
-The reviewer makes some very interesting points regarding the domain considered and the dynamical
-aspect of our analysis. Regarding the former, it is true that we focus on the restricted domain for
-$\Gamma$, as we were able to ensure that our theoretical analysis was sound for this domain.
-Unfortunately, the analysis does not extend to the positive $\Gamma$ region, whose interest we
-cannot neglect. Indeed you are correct in stating that the behaviour in this regime could be
-analysed through a numerical study and, in fact, this is a point of work that we considered
-immediately on the conclusion of our present work. However, we felt that it was important to focus
-on the region in which the stability of the system could be analytically determined. We shall be
-sure to clarify your point in revision.
+The reviewer makes some very interesting points regarding the domain considered. It is true that we focus on the restricted domain for
+$\Gamma$, as we were able to ensure that our theoretical analysis was sound.
+Unfortunately, the analysis does not extend to positive $\Gamma$.
+You are correct in stating that the behaviour in this regime can be analysed through a numerical study.
+This is a point of work that we considered immediately upon conclusion of our present work.
+However, we felt that it was important to focus on the region in which the stability of the system could be analytically determined.
+We shall be sure to clarify your point in revision.
 
-We thank the reviewer for making their point regarding the existence of chaotic dynamics. Indeed it
+We thank the reviewer for making their point regarding the onset of chaos. Indeed it
 is true that our results focus on the instability of the system. However, we also numerically
-estimated Lypapunov exponents using the Kantz algorithm and found positive exponents for games of
-large numbers of players or actions. We will be sure to make this point clear in our revision also.
+estimated Lypapunov exponents using the Kantz algorithm and found them to be positive in games of large players/actions. We will be sure to make this point clear in our revision also.
 Regarding the existence of periodic orbits, we conducted experiments which look for recurrent
 behaviour, but were unable to find any, even for small classes of 2x2 games. A point of work which
-we are looking at is to consider the possibility that, in fact, Q-Learning may not admit any
-periodic solutions at all. As you mention, we will be sure to make these distinctions clear and we
-thank the reviewer for pointing them out.
+we are looking at is to consider the possibility that Q-Learning may not admit any
+periodic solutions at all.
 
@@
 
-We thank the reviewer for pointing out the clarification needed in the payoff matrices and that of
-other RL methods. Regarding the former point, we must clarify that the payoffs themselves are not
-Gaussian. Each agent receives their reward from a payoff matrix, as is typically the case in normal
-form games. Our analysis requires that we understand how the structure of the payoff matrices
+We thank the reviewer for pointing out the clarification needed in the payoff matrices. We must clarify that the payoffs themselves are not
+Gaussian. Each agent receives their reward from a payoff matrix. Our analysis requires that we understand how the structure of the `type' of game
 affects stability. As such, we parameterise the correlations between the payoff elements by
@@
 behaviour over all games which share the same $\Gamma$. To do this, we assert that the payoffs are
-drawn from a multi-variate Gaussian, allowing us to leverage Gaussian identities in performing
-averages. Therefore, we are not restricting to a particular class of payoffs, but rather
+drawn from a multi-variate Gaussian, allowing us to leverage Gaussian identities. Therefore, we are not restricting to a particular class of game, but rather
 generalising over all possible payoff matrices and averaging the effect of those who share the same
@@
 Regarding the analysis of other reinforcement learning algorithms, we definitely believe that this
-is an important and interesting line of inquiry. We mention in our conclusion that, as
+is an important and interesting line of inquiry, but far beyond the scope of the current contribution. We mention in our conclusion that, as
 dynamical models are developed for the algorithms you mention, analyses such as the present work
-will help provide insight into what they predict regarding the stabilty and behaviour of those
-algorithms.
+will help provide insight into what they predict regarding stability.
 % paragraph reviewer_65 (end)
@@
 
-Regarding the behaviour of $\tau$, which partially encodes the propensity to exploit vs explore, we
+Regarding the behaviour of $\tau$, which partially encodes exploration-exploitation, we
 chose not to focus on this result as it was analysed in (Leonardos and Piliouras 2020). Furthermore,

### 2021-04-07 Documents/FP in NAGs/FPNAG.tex
Included CCE Proof (Need to formalise notation)

--- 2021-03-25 Documents/FP in NAGs/FPNAG.tex
@@
 
-	I've spent some time trying to show convergence of the CTFP to a Nash Equilibrium, without the
-	requirement that $w_{ii} = 0$. Unfortunately, it doesn't look like that is the case in general,
-	at least with the other assumptions that we have made. Perhaps changing the requirement of the
-	payoff functions or the aggregation method (e.g. to a non-linear one) would influence this, but
-	for the bimatrix games that we've looked at so far, no luck.
-	We can, however, say that there is a fixed point since the solution $\alpha(t; m)$, for any CTFP
-	$m$ maps from a compact space to itself. Therefore, any sequence $\{\alpha(\tau_q; m)\}$ where
-	$\tau_q \rightarrow \infty$ as $q \rightarrow \infty$ has all of its elements inside a compact
-	set. Therefore, by the Bolzano-Wierstrass Theorem, this sequence has at least one limit point.
-	We can say that this limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
-	determine any other structure of the limit point for when this does not hold. For example, is it
-	part of the `no regret' set?
+	In this section I will show that the NA-CTFP process converges to the set of coarse correlated
+	equilibria. So first I will define what this means. \ah{For Francesco: Please forgive me for
+	changing notation, I'll make everything consistent.}
+
+	The notion of the CCE set is best considered through \emph{regret} which, for agent $\mu$ is given as
+
+	\begin{equation}
+		R^{\mu} = \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\}
+	\end{equation}
+
+	To illustrate this, let us consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$ is given by
+
+	\begin{equation}
+		u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
+	\end{equation}
+
+	On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(x_{i'}^\mu(t), \sigma(t))$, then
+
+	\begin{equation}
+		\max_{x_{i'}^\mu \in S^\mu} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu
+	\end{equation}
+
+	By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change.
+As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time.
+An agent achives \emph{no regret} if $R^\mu$ is non-positive.
+	% \begin{definition}[Coarse Correlated Equilibrium]
+	% 	A distribution $D$ over action profiles $\times_{\mu} A^{\mu}$ is a \emph{coarse correlated
+	% 	equilibrium} if, for
+	% 	all players $\mu$ and
+	% 	all
+	% 	actions $i' \in A^{\mu}$
+
+	% 	\begin{equation}
+	% 		\mathbb{E}_{a \sim D}[u^{\mu}(a)] \geq \mathbb{E}_{a \sim D}[u^{\mu}(a^\mu_{i'}, a
+	% 		^{- \mu})]
+	% 	\end{equation}
+
+	% \end{definition}
+	\begin{theorem}
+		Assuming that $w_{ii} = 0$, then for any choice of payoff matrix, agents following the NA-FP process achieve zero regret in the limit, i.e.
+		\begin{equation}
+			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
+		\end{equation}
+
+	\end{theorem}
+
+	\begin{proof}
+		We will adapt the techniques of Ostrovski and van Strein for this proof.
+Their result was found for a two player game, we will leverage the fact that the NA process means that we can reduce an $N$ player game down to a series of two player games.
+
+		For any agent $\mu$ define
+		\begin{equation}
+			\bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu)
+		\end{equation}
+
+		Now, if the agents are following the NA-FP process, then we know that $m^\mu (t) \in \Delta_\mu$ is the strategy which maximises $u^\mu( \cdot, \alpha_\sigma^\mu)$ so we can write
+
+		\begin{equation}
+			\bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu) = m^\mu(t) \cdot A^\mu (\alpha_\sigma^\mu)
+		\end{equation}
+
+		Then, applying the \emph{envelope theorem} we have
+
+		\begin{equation}
+			\frac{d}{d \alpha_\sigma^\mu} \bar{u}^\mu (\alpha_\sigma^\mu) = \frac{d}{d \alpha_\sigma^\mu} x^\mu \cdot A^\mu (\alpha_\sigma^\mu) \Big |_{x^\mu = m^\mu} = m^\mu \cdot A^\mu
+		\end{equation}
+
+		Which gives that
+
+		\begin{equation}
+			\frac{d}{dt} \bar{u}^\mu (\alpha_\sigma^\mu (t)) = m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt}
+		\end{equation}
+
+		Then,
+
+		\begin{align}
+			\frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & =  \bar{u}^\mu (\alpha_\sigma^\mu (t)) + t m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt} \\
+			& = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + t (m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{d}{dt} \alpha^\nu(t))
+		\end{align}
+
+		Now, we know that the differential inclusion for the NA-FP process can be written as
+
+		\begin{equation}
+			\frac{d}{dt} \alpha^\mu (t) = \frac{1}{t} (m^\mu(t) - \alpha^\mu (t))
+		\end{equation}
+
+		We insert this into the previous equation to yield
+
+		\begin{align}
+			\frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t)) + t(m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{1}{t} (m^\nu(t) - \alpha^\nu (t))) \\
+			& = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} (m^\nu(t) - \alpha^\nu (t)) \\
+			& = m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} m^\nu(t) = m^\mu \cdot A^\mu \sigma^\mu(t) 
+		\end{align}
+
+		Now if we integrate both sides with respect to $t$ in the bound $[1, T]$ (on which the NA-FP) process is defined, we get
+
+		\begin{align}
+			&  T \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
+			& \implies \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \frac{1}{T} \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
+			& \implies \lim_{T \rightarrow \infty} \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \int_0^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt = 0
+		\end{align}
+
+		Now notice
+
+		\begin{align}
+			\bar{u}^\mu (\alpha_\sigma^\mu (T)) = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\alpha_{\sigma}^\mu (T))_j & = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\frac{1}{T} \int_{0}^{T} \sigma^\mu(t) \; dt)_j \\
+			& = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} \frac{1}{T} \int_{0}^{T} \sum_i (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
+			& = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T \sum_{ij} a_{i'j} (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
+			& = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T u^\mu(x^\mu_{i'}, \sigma^\mu(t))
+		\end{align}
+
+		So we recover
+
+		\begin{equation}
+			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
+		\end{equation}
+
+		which was precisely the regret condition that we required.
+
+		\ah{Note: I think that this means that the NA-FP process converges to the coarse correlated equilibrium (CCE) set, but I'm a little hesitant to write it just because I'm not sure if the terminology lines up}
+	\end{proof}
 

### 2021-04-12 Documents/FP in NAGs/FPNAG.tex
Updated FP NAG

@@
 \newtheorem{theorem}{Theorem}
-\newtheorem*{assumption}{Assumption}
+\newtheorem{assumption}{Assumption}
 
 \newcommand{\ah}[1]{\textcolor{blue}{AH: \textit{#1}}}
-\newcommand{\svs}[1]{\textcolor{red}{FB: \textit{#1}}}
+\newcommand{\fb}[1]{\textcolor{red}{FB: \textit{#1}}}
+
+\newcommand{\agentset}{\mathcal{N}}
+\newcommand{\edgeset}{\mathcal{E}}
+\newcommand{\weightset}{W}
+
+\newcommand{\actionset}[1]{S^{#1}}
+\newcommand{\utility}[1]{u^{#1}}
+
+\newcommand{\wmunu}{w^{\mu \nu}}
+\newcommand{\xmu}{x^{\mu}}
+\newcommand{\xnu}{x^{\nu}}
+\newcommand{\refmu}{\sigma^{\mu}}
+\newcommand{\avgref}[1]{\alpha_\sigma^{#1}}
+\newcommand{\NE}[1]{\bar{x}^{#1}}
+\newcommand{\weightedsum}{ \sum_{\nu \in N^\mu} \wmunu \xnu}
+\newcommand{\xnotmu}{x^{-\mu}}
+\newcommand{\xmuaction}[1]{x^{\mu}_{#1}}
 
@@
 
+	\section{Paper Structure}
+
+	\begin{enumerate}
+		\item Introduction: Explain the notion of a Network Aggregative Game, and Fictitious Play
+		with literature on the state of the art. Assumptions made as well as summary of results
+		\item Maybe? Relation with the model of Grammatico
+		\item Preliminaries \begin{itemize}
+			\item The Network Aggregative Game model
+			\item Fictitious Play, as well as the CTFP property
+		\end{itemize}
+		\item Convergence of Fictitious Play \begin{itemize}
+			\item Existence of the Nash Equilibrium
+			\item Existence of a CTFP
+			\item Convergence of CTFP to a fixed point
+			\item Corrolary: when $w_{ii} = 0$ (i.e. the interaction graph is simple) CTFP converges
+			to a NE
+			\item Convergence of CTFP to the NA-CCE set
+		\end{itemize}
+		\item Numerical Experiments \begin{itemize}
+			\item Convergence rates w.r.t. connectivity and size
+			\item Non-convergent examples
+			\item Agent based simulations
+		\end{itemize}
+		\item Discussion of Experiments
+		\item Concluding Remarks
+	\end{enumerate}
+
+	\newpage
+	\section{Introduction}
+
+	\section{Preliminaries}
+	\subsection{Network Aggregative Games}
+	\label{sec::NAG}
+
+	The model we consider is that there is a set $\agentset = {1, ... ,
+	N}$ of agents who are connected through an underlying interaction graph. This graph is given by
+	the tuple $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is the set of all pairs $(\mu,
+	\nu) \in \agentset \times \agentset$ such that agent $\mu$ and agent $\nu$ are connected. Then,
+	the set of neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu,
+	\nu) \in \edgeset\}$. $\weightset
+	\in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu \nu}$ expresses the
+	importance that agent $\mu$ places on agent $\nu$. Note that if $(\mu, \nu) \not \in \edgeset$
+	then $w^{\mu \nu} = 0$ and $\wmunu \in (0, 1]$ otherwise.
+
+	As a network game, each agent $\mu$ has an associated set of pure strategies $\actionset{\mu}$
+	which has cardinality $|\actionset{\mu}| = n$. Then we can construct the unit-simplex on this
+	action set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i \xmuaction{i} = 1\}$ where
+	$\xmuaction{i}$ is the probability with which agent $\mu$ plays the pure strategy $i$. As such
+	we refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is often referred to as $\mu$'s
+	mixed strategy). Also associated with each agent is a utility function $u^\mu(\xmu, \xnotmu)$ in
+	which we use the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that
+	this requires that each agent plays the same strategy against all of their neighbours.
+
+	With all of the above definitions, we can formalise the network aggregative (NA) game as the tuple
+	$\Gamma = (\agentset, (\edgeset, \weightset), (\actionset{\mu}, \utility{\mu})_{\mu \in \mathcal{N}})$.
+
+	What is unique about the NA game is the structure of the payoffs themselves. In this format,
+	each agent is receives a reference $\sigma$ which is a weighted sum of each of their
+	neighbours state. Formally
+
+	\begin{equation}
+		\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
+	\end{equation}
+
+	Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
+	instead of having to consider the actions of the entire population, or play individual games
+	against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a `measurement'
+	of the local aggregate state and optimise with respect to this measurement. This allows us to
+	make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider that
+	the agent is engaged in a matrix game against the reference vector so that
+
+	\begin{equation}
+		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu \cdot A^\mu \weightedsum.
+	\end{equation}
+
+	where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we could have
+	written the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
+	$\utility{\mu}$. The NA game allows for the reduction of a
+	multiplayer game into a series of two-player games. The agent's goal is to maximise their payoff
+	with respect to the reference vector. As such, we define the best response correspondence
+	$BR^\mu$ which maps any $\refmu$ the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
+	leads naturally to the definition of a Nash Equilibrium in an NA Game as
+
+	\begin{definition}(NE)
+		The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,
+
+		\begin{equation*}
+		\NE{\mu} \in BR_i( \sum_{\nu \in N^\mu} \wmunu \NE{\nu}).
+		\end{equation*}
+
+	\end{definition}
+
+	We will show that such an equilibrium exists in ...
+
+	\subsection{Continuous Time Fictitious Play}
+	\label{sec::CTFP}
+
+	\ah{For Francesco: is it worth giving a quick introduction to Fictitious Play by talking about two player games?}
+
+	Fictitious Play requires that, at the current time, each agent considers the average behaviour
+	of their opponent in the past and play a best response to that strategy. This is best
+	illustrated in the two-player setting. Consider the two player normal form game $\Gamma_2 = (\{
+	1, 2\}, ((S^1, A), (S^2, B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$ and $2$
+	respectively. As a remark, note that we can write the two player normal form game as an NA game
+	simply by requiring that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2 matrix with
+	zeros on its leading diagonal and ones on the off diagonal. We write the time-average of both
+	agents' strategies as
+
+	\begin{align}
+		\alpha^1 = \frac{1}{t} \int_0^T x^1(t) \, dt \\
+		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
+	\end{align}
+
+	In this manner, the $\alpha^\mu(t)$ denotes the time average of the strategies played by agent
+	$\mu$ up to time $t$. Then, fictitious play requires that the agents update their strategy as
+	$x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in
+	BR^2(\alpha^1(t))$.
+
+	We extend this naturally to the NA game $\Gamma$ by requiring that each agent update their
+	strategy according to the time average of their reference vector $\refmu$. To formalise this, we
+	write
+
+	\begin{equation}
+		\avgref{\mu} = \frac{1}{t} \int_0^t \refmu(s) \; ds.
+	\end{equation}
+
+	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
+	Fictitious Play in continuous time.
+
+	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
+		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
+
+		We can think of this definition as saying that the player plays some arbitrary strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
+	\end{definition}
+
+	\subsection{Assumption}
+
+	With the above preliminaries in place, we can state the assumptions that we make in this study.
+
+	\begin{assumption}
+		The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
+		that the sum elements in each row of $\weightset$ is equal to one.
+	\end{assumption}
+
+	\begin{assumption}
+		The payoffs are given through matrix games and, therefore, are bilinear.
+	\end{assumption}
+
+	\begin{assumption}
+		The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents.
+	\end{assumption}
+
+	\begin{assumption}
+		The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
+		of states $(x^\mu)_{\mu \in N^\mu}$
+	\end{assumption}
+
+	\section{Convergence of Fictitious Play}
+
+	\subsection{Existence of the Nash Equilibrium}
+
+	Note that the NE Condition requires
+
+	\begin{align}
+		\NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber \\
+		& =: \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
+	\end{align}
+
+	where we can find $\bar{u}_i$ through the following argument
+
+	\begin{align}
+		u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \\
+		 & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \\
+		 & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
+	\end{align}
+
+	where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$. Note that, in order to get this
+	formulation, we had to use the assumption of payoffs being bilinear so that we could separate
+	out the term in the weighted sum involving $x$ from $\bar{x}^\nu$.
+
+	To show existence of an NE we will need the following definition and theorem.
+
+	\begin{definition}[Upper Semi-Continuous]
+		A compact-valued correspondence $\Phi: A \rightarrow B$ is \emph{upper semi-continuous} at a point $a$ if $g(a)$ is non-empty and if, for every sequence $a_n \rightarrow a$ and every sequence $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a convergent subsequence of $(b_n)$ whose limit point $b$ is in $g(a)$.
+	\end{definition}
+
+	\begin{theorem}[Kakutani]
+		Let $K \subset \mathbb{R}^n$ be compact and convex and $\Phi: K \rightarrow K$ be closed or upper semi-continuous, with nonempty, convex and compact values. Then $\Phi$ has a fixed point.
+	\end{theorem}
+
+	Note that, when acting on a simplex, the function $\Phi: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes the nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.
+
+	\begin{theorem}[Existence of NE]
+		Under the assumption (II), namely that the payoff function achieves a bilinear property, a
+		Nash Equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
+	\end{theorem}
+
+	\begin{proof}
+		We begin by rewriting the NE condition by concatenating the set of NE vectors into one long colunn vector. This gives
+
+		\begin{equation}
+			\begin{bmatrix}
+				\bar{x}^1 \\ . \\ . \\ . \\ \bar{x}^N
+			\end{bmatrix} \in
+			\begin{bmatrix}
+			\arg\max_{y \in \Delta_1} \bar{u}^1(y, \sum_{\nu \in N^1} w^{1 \nu} \bar{x}^\nu) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}^1(y, \sum_{\nu \in N^N} w^{N \nu} \bar{x}^\nu)
+			\end{bmatrix}	.
+		\end{equation}
+
+		We can rewrite the weighted summation for $\mu$ as
+
+		\begin{equation}
+			\sum_{\nu \in N^\mu} w^{\mu \nu} \bar{x}^\nu = (w_{-\mu}^T \otimes I_n) \begin{bmatrix}
+				\bar{x}^1 \\ . \\ . \\ . \\ \bar{x}^N
+			\end{bmatrix},
+		\end{equation}
+
+		in which $w_{-\mu}$ is a column vector containing $w^{\mu \nu}$ in the $\nu$'th element for all $j \in N^\mu$ and 0 everywhere else (including in the $\mu$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product.
+For example, the form for agent 1, in the case of 2-action game is given by
+
+		\begin{equation}
+			(w_{-1}^T \otimes I_2) = [0, w_{12}, w_{13}, ..., w_{1n}] \otimes I_2 = 
+			\begin{bmatrix}
+				0 & 0 & w_{12} & 0 & ... & w_{1n} & 0 \\
+				0 & 0 & 0 & w_{12} & ... & 0 & w_{1n} \\
+			\end{bmatrix}
+		\end{equation}
+
+		Returning to the $N$-player NA game our condition becomes
+		\begin{equation}
+			\begin{bmatrix}
+				\NE{1} \\ . \\ . \\ . \\ \bar{N}
+			\end{bmatrix} \in
+			\begin{bmatrix}
+				\arg\max_{y \in \Delta_1} \bar{u}^1(y, (w_{-1}^T \otimes I_n) \begin{bmatrix}
+					\NE{1} \\ . \\ . \\ . \\ \NE{N}
+				\end{bmatrix}) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n) \begin{bmatrix}
+				\NE{1} \\ . \\ . \\ . \\ \NE{N}
+			\end{bmatrix}))
+			\end{bmatrix}	.
+		\end{equation}
+
+		This means that we achieve a Nash Equilibrium iff $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the map
+
+		\begin{equation}
+			\begin{bmatrix}
+				\arg\max_{y \in \Delta_1} \bar{u}^1(y, (w_{-1}^T \otimes I_n) ( \cdot )) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}^N(y, (w_{-N}^T \otimes I_n)( \cdot ))
+			\end{bmatrix}	.
+		\end{equation}
+
+		Now, since the modified payoff $\bar{u}^\mu$ shares the same bilinear property as $u^\mu$, we can assert that it is continuous is its second argument.
+Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous.
+As such, we can apply Kakutani's Fixed Point Theorem to assert that the above map admits a fixed point.
+
+	\end{proof}
+
+	\newpage
 	\subsection*{The Model}
 
-	We have a set of agents $V = \{1, ..., N \}$ which can be thought of as nodes on a graph $\{V, E, W\}$ where $E$ is the edge-set (i.e.
-the set of pairs $(i, j)$ such that i and j are connected) and $W$ is a weighted adjacency matrix $[W]_{ij} = w_{ij}$.
-Let $N_i := \{j \in V : (i, j) \in E\}$ be the set of player $i's$ neighbours.
-Note $w_{ij} = 0$ if $(i, j) \not\in E$, $w_{ij} \in (0, 1]$ if $(i, j) \in E$.
-We impose the normalisation condition that $\sum_{j \in N_i} w_{ij} = 1$.
-This requirement ensures that the aggregate strategy $\sum_{j \in N_i} w_{ij} x_j$ (where $x$ is a probability vector) remains a probability vector.
-For example, in the 3 player case:
+	We have a set of agents $V = \{1, ..., N \}$ which can be thought of as nodes on a graph $\{V,
+	E, W\}$ where $E$ is the edge-set (i.e. the set of pairs $(i, j)$ such that i and j are
+	connected) and $W$ is a weighted adjacency matrix $[W]_{ij} = w_{ij}$. Let $N_i := \{j \in V :
+	(i, j) \in E\}$ be the set of player $i's$ neighbours. Note $w_{ij} = 0$ if $(i, j) \not\in E$,
+	$w_{ij} \in (0, 1]$ if $(i, j) \in E$. We impose the normalisation condition that $\sum_{j \in
+	N_i} w_{ij} = 1$. This requirement ensures that the aggregate strategy $\sum_{j \in N_i} w_{ij}
+	x_j$ (where $x$ is a probability vector) remains a probability vector. For example, in the 3
+	player case:
 
@@
 
-	Once the strategy is chosen, the agent plays the game and receives payoff $u_i (x_i, \sigma_i)$, where $\sigma_i$ is the aggregate strategy vector that $i$ perceives.
-The best response map $BR_i$ maps any $\sigma_i$ to the set $\arg\max_{x \in \Delta_i} u_i (x, \sigma_i)$.
-Then $x_i$ is a `best response' to $\sigma_i$ if $x_i \in BR_i(\sigma_i)$.
+	\subsection{Existence of a CTFP}
 
-	\begin{definition}(NE)
-		The set of vectors $\{ x_i^*\}_{i = 1}^N$ is an NE if, for all $i$,
-
-		\begin{equation*}
-		x_i^* \in BR_i( w_{ii} x_i^* + \sum_{j \in N_i} w_{ij} x_j^*).
-		\end{equation*}
-
-	\end{definition}
+	We adapt the techniques of Ewerhart to show that any CTFP path converges
 

### 2021-04-14 Documents/FP in NAGs/FPNAG.tex
Completed Restructuring of FPNAG file

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
 \newtheorem{assumption}{Assumption}
@@
 		\begin{equation*}
-		\NE{\mu} \in BR_i( \sum_{\nu \in N^\mu} \wmunu \NE{\nu}).
+		\NE{\mu} \in \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
 		\end{equation*}
@@
 
-	We will show that such an equilibrium exists in ...
+	We will show that such an equilibrium exists in ....
+Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$.
+Formally
+
+	\begin{equation}
+		\sum_\mu u^\mu(\xmu, \weightedsum) = 0.
+	\end{equation}
 
@@
 
+	\subsection{Existence of CTFP}
+
+	\begin{theorem}
+		There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
+		BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
+	\end{theorem}
+
+	\begin{proof}
+		Recall the definition of $\alpha^\mu(t)$
+
+		\begin{equation*}
+		\alpha^\mu(t) = \frac{1}{t} \int_{0}^{t} m^\mu(s) \, ds
+		\end{equation*}
+
+		Then
+
+		\begin{align}
+		\frac{d}{dt} \alpha^\mu(t) & = \frac{d}{dt} \frac{1}{t} \int_{0}^t m^\mu(s) ds \nonumber \\
+		& = \frac{1}{t} m^\mu(t) - \frac{1}{t} \alpha^\mu(t)
+		\end{align}
+
+		Now we assert that $m^\mu(t) \in BR^\mu(\alpha_{\sigma}^\mu) = \arg\max_{y \in \Delta_\mu} u^\mu(y,
+		w^{\mu \mu} \alpha^\mu(t) + \sum_{\nu \in N^\mu} w_{ij} \alpha^\nu(t))$.
+
+		Let us then define $\alpha(t)$ as the concatenation of all $\alpha_i(t)$
+
+		\begin{equation}
+			\alpha(t) = \begin{bmatrix}
+				\alpha^1(t)^T, \ldots, \alpha^N(t)^T
+			\end{bmatrix}^T \subset \mathbb{R}^{Nn}
+		\end{equation}
+
+		We can, therefore, write the aggregation as
+
+		\begin{equation}
+			(W \otimes I_n) \alpha(t) = \begin{bmatrix}
+				\sum_{\nu \in N^1} w^{1 \nu} \alpha^\nu(t) \\
+				.\\
+				.\\
+				.\\
+				\sum_{\nu \in N^N} w^{N \nu} \alpha^\nu(t)
+			\end{bmatrix} \subset \mathbb{R}^{Nn}
+		\end{equation}
+
+		I will write $(W \otimes I_n) \alpha(t)$ as $\alpha_W$ for convenience. Furthermore, using
+		the bilinear property of the game, we can say that
+
+		\begin{equation}
+			\begin{bmatrix}
+				\arg\max_{y_1 \in \Delta_1} y \cdot A^1 ( \alpha_W(t))_1 \\
+				.\\
+				.\\
+				.\\
+				\arg \max_{y_N \in \Delta_N} y \cdot A^N (\alpha_W(t))_N 
+			\end{bmatrix} = 
+			\arg \max_{y \in \Delta} y \cdot \begin{bmatrix}
+				A^1 & 0 & . & . & . & 0 \\
+				0 & A^2 & . & . & . & 0 \\
+				& & . & & & \\
+				& & & . & & \\
+				& & & & . & \\
+				0 & 0 & . & . & . & A^N \\
+			\end{bmatrix} \alpha_W(t) = \arg\max_{y \in \Delta} y \cdot \Lambda (W \otimes I_n)
+			\alpha(t)
+		\end{equation}
+
+		in which $\Delta = \times_i \Delta_i$ and $\Lambda$ is the block diagonal matrix containing
+		each $A^i$.
+
+		We can now write the differential inclusion as
+
+		\begin{equation}
+			\dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
+			I_n)
+			\alpha(t) \}- \alpha(t))
+		\end{equation}
+
+		with the initial condition $\alpha(1) = x_0$. Then, the path $m$ is a CTFP if its
+		corresponding $\alpha(t; m)$ is a solution to the above differential inclusion. Following
+		the definition of (Harris 1998), a solution $\alpha(t)$ must satisfy
+
+		\begin{enumerate}
+			\item $\alpha(t)$ is locally Lipschitz
+			\item $\alpha(1) = x_0$
+			\item $\dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
+			I_n)
+			\alpha(t) \}- \alpha(t))$ for almost all $t \in [1, \infty)$ 
+		\end{enumerate}
+
+		The question then remains, does the differential inclusion admit a solution? Using the
+		results of Aubin and Cellina (see Harris 1998, paragraph below Prop. 6), can use the fact
+		that the $\arg \max$ function is non-empty, compact and convex valued, bounded (all of
+		these follow since the function acts from $\Delta$ to $\Delta$) and upper semi-continuous. 
+		With these facts in place, we can say that there is a CTFP $m$ for any initial value $x_0$. Further, the solution $m(t)$ is Lipschitz for almost all $t \geq 0$.
+
+	\end{proof}
+
+	With the existence of the CTFP in place, we can show that it converges to a fixed point.
+In particular, let $\Omega(\alpha)$ be the set of all limit points for $\alpha(t)$.
+Then, a CTFP path is said to have converged if $\Omega(\alpha)$ is contained within the set of Nash Equilibria of the game.
+If this is for any such CTFP path, then the game is said to have the \emph{CTFP property}.
+We adapt the techniques of (Ewerhart 2020) to prove that zero-sum NA games have the CTFP property.
+\ah{I also want to attempt this with the techniques of Harris (which is quite similar) to see if it yields any new results}.
+
+	\begin{theorem}
+		Any zero-sum NA game has the property that, for any CTFP path $m$, the corresponding $\alpha(t; m)$ converges to a set of fixed points.
+	\end{theorem}
+
+	\begin{proof}
+
+		\begin{equation}
+			m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(s) ds \right).
+		\end{equation}
+
+		By the definition of Continuous Time Fictitious Play (CTFP) given by Ewerhart, we require that $m: [0, \infty) \rightarrow \times_\mu \Delta_\mu$ is a measurable mapping such that, for each $\mu$, $m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(t') dt' \right)$.
+Now notice,
+
+		\begin{equation*}
+			m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(t') dt' \right) \iff  \in x^\mu\in BR^\mu \left( \frac{1}{t} \int_{0}^{t} [w^{\mu \mu} m^\mu(s) + \sum_{\nu \in N^\mu} w^{\mu \nu} m^\nu(s)] \, ds \right)
+		\end{equation*}
+
+		Let us assume that $u^\mu$ takes the form $x \cdot A^\mu \sigma^\mu$ where $A^\mu$ is the payoff matrix associated with agent $\mu$. Then,
+
+		\begin{align}
+			& m^\mu \in \arg\max_{x \in \Delta^\mu} u^\mu(x,\frac{1}{t} \int_{0}^{t} [w^{\mu \mu} m^\mu(t') + \sum_{\nu \in N^\mu} w^{\mu \nu} m^\nu(s)] \, ds) \nonumber \\
+			\iff & m^\mu \in \arg\max_{x \in \Delta_\mu} x \cdot A^\mu \left(\frac{1}{t} \int_{0}^{t} [w^{\mu \mu} m^\mu(t') + \sum_{\nu \in N^\mu} w^{\mu \nu} m^\nu(s)] \, ds \right) \nonumber \\
+			\iff & m^\mu \in \arg \max_{x \in \Delta_\mu} x \cdot (w^{\mu \mu} A^\mu) \left( \frac{1}{t} \int_{0}^{t} m^\mu(s) ds\right) + \sum_{\nu \in N^\mu} x \cdot (\wmunu A^\nu) \left( \frac{1}{t} \int_{0}^{t} m^\nu(s) ds \right) \nonumber \\
+			\iff & m^\mu \in \arg \max_{x \in \Delta_i} x \cdot A^{\mu \mu} \alpha^\mu(t; m) + \sum_{\nu \in N^\mu} x \cdot A^{\mu \nu} \alpha^\nu(t; m).
+		\end{align}
+
+		where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m) =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined by Ewerhart.
+We can, therefore, think of the NA game as a network game in which each agent plays the same strategy against each of its neighbours, itself included.
+As such, any $m$ which satisfies the CTFP property for the equivalent network game also satisfies the CTFP requirement for the network aggregative game.
+
+		Continuing with this approach, let us look at the case where $\sum_\mu A^\mu = \textbf{0}_{n\times n}$ (i.e.
+a zero sum game).
+This means that $\sum_i u_i = 0$.
+Let $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$.
+More specifically, $\xmu_\infty$ belongs to the set of accumulation points of $\alpha^\mu(\cdot; m)$ (which is set valued since the $BR^\mu$ map is set valued).
+To say that the game has `converged' we require that every $\xmu_\infty = (x^1_\infty, ...
+x^N_\infty)$ is an NE.
+\ah{I'll follow through the proof of Ewerhart for the sake of completeness: }
+
+		Let us take the Lyapunov function
+
+		\begin{equation}
+			L(x) = \sum_\mu \max_{y \in \Delta_\mu} \{u^\mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) - u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \}
+		\end{equation}
+
+		Using the same transformation as before:
+
+		\begin{align}
+			 u^mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} w_{\mu \nu} \xnu) & =  y \cdot A^\mu (w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \nonumber \\
+			 & =  y \cdot (w^{\mu \mu} A^\mu) \xmu + \sum_{\nu \in N^\mu} y \cdot (\wmunu A^\mu) \xnu \nonumber \\
+			  & =  \sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu \nonumber 
+		\end{align}
+
+		Then,
+
+		\begin{align}
+		L(x) &= \sum_\mu \max_{y \in \Delta_\mu}\sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu  - u^mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} w^{\mu \nu} \xnu) \} \nonumber \\
+		&= \sum_\mu \max_{y \in \Delta_\mu} \{\sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu  \} - \sum_\mu  u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} w^{\mu \nu} \xnu) \nonumber \\
+		&= \sum_\mu \max_{y \in \Delta_\mu} \{\sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu  \} \nonumber 
+		\end{align}
+
+		where the last equality holds because $\sum_\mu u^\mu = 0$. Now, in parallel with (Ewerhart 2020) we recall that we defined $m^\mu(t)$ as the best response to $\alpha(t)$. As such,
+
+		\begin{align}
+			L(\alpha(t)) & = \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \alpha^\nu(t) \\
+			t L(\alpha(t)) & = \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} t \alpha^\nu(t) \\
+			t L(\alpha(t)) & = \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_0^t m^\nu(s) ds
+		\end{align}
+
+		Similarly, since we know that $m^\mu(t')$ is a best response to $\alpha(t')$ at time $t'$ we have
+
+		\begin{align}
+			\sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t') \cdot A^{\mu \nu} \alpha^\nu(t') & \geq \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \alpha^\nu(t') \\
+			t' \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t') \cdot A^{\mu \nu} \alpha^\nu(t') & \geq \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_0^{t'} m^\nu(s) ds \\
+			t' L(\alpha(t')) & \geq \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_0^{t'} m^\nu(s) ds 
+		\end{align}
+
+		Combining the above equations in $t L(\alpha(t))$ and $t' L(\alpha(t'))$, we get
+
+		\begin{align}
+			t L(\alpha(t)) - t' L(\alpha(t')) \leq \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_{t'}^{t} m^\nu(s) ds 
+		\end{align}
+
+		We can divide this expression by $t - t'$ and take the limit for $t' \rightarrow t$. This yields the derivative (in particular the upper right Dini derivative)
+
+		\begin{equation}
+			\limsup_{t' \rightarrow t, t' < t}\frac{t L(\alpha(t)) - t' L(\alpha(t'))}{t - t'} \leq 0
+		\end{equation}
+
+		As this derivative is (weakly) negative, and we know that $tL(\alpha(t))$ is continuous in $t$, we have the result that $t L(\alpha(t))$ is monotone decreasing.
+Therefore, it is bounded, i.e.
+there is some $C \geq 0$ such that $L(\alpha(t)) \leq C/t$.
+In addition, we know that each term in the summation in the original expression of the Lyapunov function is non-negative and so we can say that
+
+		\begin{align}
+			& \max_{y \in \Delta_\mu} \{u^\mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) - u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \} \leq \frac{C}{t}\\
+			& \implies u^\mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) - u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \leq \frac{C}{t} \; \forall y \in \Delta_n
+		\end{align}
+
+		Now let us take some $\xmu_\infty \in \Omega(\alpha)$.
+Since this is a limit point, there exists a sequence $\{t_n\}_{n = 0}^\infty \rightarrow \infty$ such that $\{\alpha^\mu(t_n)\}_{n = 0}^{\infty} \rightarrow \xmu_\infty$.
+So if we take the limit as $t_n \rightarrow \infty$ we get
+
+		\begin{equation}
+			u^\mu(y, w^{\mu \mu} \xmu_\infty + \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) - u^\mu(\xmu_\infty, w^{\mu \mu} \xmu_\infty + \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq 0
+		\end{equation}
+
+		This means that $(\xmu_\infty)_{\mu \in \agentset}$ is a best response to itself and so is a fixed point of the NA-CTFP dynamic. 
+	\end{proof}
+
+	We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality yields that, for all $\mu$
+
+	\begin{equation}
+		u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
+	\end{equation}
+
+	which is precisely the NA-Nash Equilibrium condition. This leads to the next result
+
+	\begin{corollary}
+		With the additional assumption that, for all agents $\mu$, all zero-sum NA games have the CTFP property
+	\end{corollary}
+
+	\section{Convergence to the CCE set}
+
+	In this section we aim to find some convergence structure for the case in which the NA game is not zero-sum.
+In particular, we  show that the NA-CTFP process converges to the set of coarse correlated equilibria.
+So first I will define what this means.
+
+	The notion of the CCE set is best considered through \emph{regret} which, for agent $\mu$ we define as
+
+	\begin{equation}
+		R^{\mu} = \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\}
+	\end{equation}
+
+	Note, this is the \emph{average regret} for the agent $\mu$ and, of course, can be related to the \emph{cumulative regret} which is used for analysis in, e.g.
+(Leonardos and Piliouras, Cesa-Bianchi).
+To illustrate the average regret, let us consider the case where each agent has only two actions.
+Then $u^{\mu}(x^\mu(t), \sigma(t))$ is given by
+
+	\begin{equation}
+		u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
+	\end{equation}
+
+	On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(x_{i'}^\mu(t), \sigma(t))$, then
+
+	\begin{equation}
+		\max_{x_{i'}^\mu \in S^\mu} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu
+	\end{equation}
+
+	By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change.
+As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time.
+An agent achives \emph{no regret} if $R^\mu$ is non-positive.
+	% \begin{definition}[Coarse Correlated Equilibrium]
+	% 	A distribution $D$ over action profiles $\times_{\mu} A^{\mu}$ is a \emph{coarse correlated
+	% 	equilibrium} if, for
+	% 	all players $\mu$ and
+	% 	all
+	% 	actions $i' \in A^{\mu}$
+
+	% 	\begin{equation}
+	% 		\mathbb{E}_{a \sim D}[u^{\mu}(a)] \geq \mathbb{E}_{a \sim D}[u^{\mu}(a^\mu_{i'}, a
+	% 		^{- \mu})]
+	% 	\end{equation}
+
+	% \end{definition}
+
+	\begin{theorem}
+		Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the NA-FP process achieve zero regret in the limit, i.e.
+		\begin{equation}
+			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
+		\end{equation}
+
+	\end{theorem}
+
+	\begin{proof}
+		We will adapt the techniques of Ostrovski and van Strein for this proof.
+Their result was found for a two player game, we will leverage the fact that the NA process means that we can reduce an $N$ player game down to a series of two player games.
+
+		For any agent $\mu$ define
+		\begin{equation}
+			\bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu)
+		\end{equation}
+
+		Now, if the agents are following the NA-FP process, then we know that $m^\mu (t) \in \Delta_\mu$ is the strategy which maximises $u^\mu( \cdot, \alpha_\sigma^\mu)$ so we can write
+
+		\begin{equation}
+			\bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu) = m^\mu(t) \cdot A^\mu (\alpha_\sigma^\mu)
+		\end{equation}
+
+		Then, applying the \emph{envelope theorem} we have
+
+		\begin{equation}
+			\frac{d}{d \alpha_\sigma^\mu} \bar{u}^\mu (\alpha_\sigma^\mu) = \frac{d}{d \alpha_\sigma^\mu} x^\mu \cdot A^\mu (\alpha_\sigma^\mu) \Big |_{x^\mu = m^\mu} = m^\mu \cdot A^\mu
+		\end{equation}
+
+		Which gives that
+
+		\begin{equation}
+			\frac{d}{dt} \bar{u}^\mu (\alpha_\sigma^\mu (t)) = m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt}
+		\end{equation}
+
+		Then,
+
+		\begin{align}
+			\frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & =  \bar{u}^\mu (\alpha_\sigma^\mu (t)) + t m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt} \\
+			& = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + t (m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{d}{dt} \alpha^\nu(t))
+		\end{align}
+
+		Now, we know that the differential inclusion for the NA-FP process can be written as
+
+		\begin{equation}
+			\frac{d}{dt} \alpha^\mu (t) = \frac{1}{t} (m^\mu(t) - \alpha^\mu (t))
+		\end{equation}
+
+		We insert this into the previous equation to yield
+
+		\begin{align}
+			\frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t)) + t(m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{1}{t} (m^\nu(t) - \alpha^\nu (t))) \\
+			& = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} (m^\nu(t) - \alpha^\nu (t)) \\
+			& = m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} m^\nu(t) = m^\mu \cdot A^\mu \sigma^\mu(t) 
+		\end{align}
+
+		Now if we integrate both sides with respect to $t$ in the bound $[1, T]$ (on which the NA-FP) process is defined, we get
+
+		\begin{align}
+			&  T \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
+			& \implies \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \frac{1}{T} \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
+			& \implies \lim_{T \rightarrow \infty} \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \int_0^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt = 0
+		\end{align}
+
+		Now notice
+
+		\begin{align}
+			\bar{u}^\mu (\alpha_\sigma^\mu (T)) = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\alpha_{\sigma}^\mu (T))_j & = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\frac{1}{T} \int_{0}^{T} \sigma^\mu(t) \; dt)_j \\
+			& = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} \frac{1}{T} \int_{0}^{T} \sum_i (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
+			& = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T \sum_{ij} a_{i'j} (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
+			& = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T u^\mu(x^\mu_{i'}, \sigma^\mu(t))
+		\end{align}
+
+		So we recover
+
+		\begin{equation}
+			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
+		\end{equation}
+
+		which was precisely the regret condition that we required.
+
+		\ah{Note: I'm just figuring out how best to formulate the notion of the NA-CCE set and then I can add it in as a definition to say that NA-CTFP converges to this set.}
+	\end{proof}
+
 	\newpage
@@
 We assume that $i$ has just the one strategy that it can play against all of its neighbours.
-
-	\subsection{Existence of a CTFP}
-
-	We adapt the techniques of Ewerhart to show that any CTFP path converges
 
@@
 
-	\begin{equation}
-		x_i(t) \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right).
-	\end{equation}
-
-	By the definition of Continuous Time Fictitious Play (CTFP) given by Ewerhart, we require that $m: [0, \infty) \rightarrow \times_i \Delta_i$ is a measurable mapping such that, for each $i$, $m_i(t) \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right)$.
-Now notice,
-
-	\begin{equation*}
-		x_i \in BR_i \left( \frac{1}{t} \int_{0}^{t} \sigma_i(t') dt' \right) \iff  \in x_i\in BR_i \left( \frac{1}{t} \int_{0}^{t} [w_{ii} m_i(t') + \sum_{j \in N_i} w_{ij} m_j(t')] \, dt' \right)
-	\end{equation*}
-
-	Let us assume that $u_i$ takes the form $x \cdot A_i \sigma_i$ where $A_i$ is the payoff matrix associated with agent $i$. Then,
-
-	\begin{align}
-		& x_i \in \arg\max_{x \in \Delta_i} u_i(x,\frac{1}{t} \int_{0}^{t} [w_{ii} m_i(t') + \sum_{j \in N_i} w_{ij} m_j(t')] \, dt') \nonumber \\
-		\iff & x_i \in \arg\max_{x \in \Delta_i} x \cdot A_i \left(\frac{1}{t} \int_{0}^{t} [w_{ii} m_i(t') + \sum_{j \in N_i} w_{ij} m_j(t')] \, dt' \right) \nonumber \\
-		\iff & x_i \in \arg \max_{x \in \Delta_i} x \cdot (w_{ii} A_i) \left( \frac{1}{t} \int_{0}^{t} m_i(t')\right) + \sum_{j \in N_i} x \cdot (w_{ij} A_i) \left( \frac{1}{t} \int_{0}^{t} m_j(t')\right) \nonumber \\
-		\iff & x_i \in \arg \max_{x \in \Delta_i} x \cdot A_{ii} \alpha_i(t; m) + \sum_{j \in N_i} x \cdot A_{ij} \alpha_j(t; m).
-	\end{align}
-
-	where each $A_{ij} = w_{ij} A_i$ and $\alpha_i(t; m) =\frac{1}{t} \int_{0}^{t} m_i(t') dt'$ as defined by Ewerhart.
-We can, therefore, think of the network aggregative game as a network game in which each agent plays the same strategy against each of its neighbours, itself included.
-As such, any $m$ which satisfies the CTFP property for the equivalent network game also satisfies the CTFP requirement for the network aggregative game.
-
-	Continuing with this approach, let us look at the case where $\sum_i A_i = \textbf{0}_{n\times n}$ (i.e.
-a zero sum game).
-This means that $\sum_i u_i = 0$.
-Let $\mu_i^* = \lim_{t \rightarrow \infty} \alpha_i(t; m)$.
-More specifically, $\mu_i^*$ belongs to the set of accumulation points of $\alpha_i(\cdot; m)$ (which is set valued since the $BR_i$ map is set valued).
-To say that the game has `converged' we require that every $\mu^* = (\mu_1^*, ...
-\mu_p^*)$ is an NE.
-\ah{I'll follow through the proof of Ewerhart for the sake of completeness: }
-
-	Let us take the Lyapunov function
-
-	\begin{equation}
-		L(\mu) = \sum_i \max_{e_i \in \Delta_i} \{u_i(e_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) - u_i(\mu_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \}
-	\end{equation}
-
-	Using the same transformation as before:
-
-	\begin{align}
-		 u_i(e_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) & =  e_i \cdot A_i (w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \nonumber \\
-		 & =  e_i \cdot (w_{ii} A_i) \mu_i + \sum_{j \in N_i} e_i \cdot (w_{ij} A_i) \mu_j \nonumber \\
-		  & =  \sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j \nonumber 
-	\end{align}
-
-	Then
-
-	\begin{align}
-	L(\mu) &= \sum_i \max_{e_i \in \Delta_i}\sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j  - u_i(\mu_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \} \nonumber \\
-	&= \sum_i \max_{e_i \in \Delta_i} \{\sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j  \} - \sum_i  u_i(\mu_i, w_{ii} \mu_i + \sum_{j \in N_i} w_{ij} \mu_j) \nonumber \\
-	&= \sum_i \max_{e_i \in \Delta_i} \{\sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j  \} \nonumber 
-	\end{align}
-
-	where the last equality holds because $\sum_i u_i = 0$.
-Again, if we were to relate this to a network game, in which each agent plays the same strategy against all its neighbours (itself included), then with the definition $ \tilde{u}_i (e_i, \mu_{-i}) := \sum_{j \in N_i \cup \{i\}} e_i \cdot A_{ij} \mu_j$, we still satisfy the zero sum condition for $\tilde{u}$.
-Now, we take a CTFP $m$ according to Ewerhart, with the condition that each agent plays the same strategy across all of its neighbours.
-This was shown by Ewerhart to converge.
-I.e.
-for any $\mu^*$ in the accumulation points of $\alpha(\cdot; m)$
-
-	\begin{equation*}
-		\tilde{u}_i(e_i, \mu_{-i}^*) \leq \tilde{u}_i(\mu_i^*, \mu_{-i}^*)
-	\end{equation*}
-
-	which, as we know, means that $\mu^*$ satisfies
-
-	\begin{equation*}
-		u_i(e_i, w_{ii} \mu_i^* + \sum_{j \in N_i} w_{ij} \mu_j^*) \leq  u_i(\mu_i^*, w_{ii} \mu_i^* + \sum_{j \in N_i} w_{ij} \mu_j^*)
-	\end{equation*}
-
 \end{document}

### 2021-04-14 Documents/FP in NAGs/FPNAG.tex
Completed Restructuring of FPNAG file

@@
 	\section{Introduction}
+		\subsection{Related Work}
+		Main articles: Ewerhart (FP in Networks), Grammatico (Nash Equilibrium seeking in NA games), Perrin (FP in mean field games), Harris (FP in 2 player games).
+		\subsection{Contributions}
 
+		The main contribution of this work is to study the behaviour of the Fictitious Play Learning Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game.
+We first show that a Nash Equilibrium exists and that Fictitious Play admits solutions in this setting.
+In particular, we study zero-sum games and show that Fictitious Play converges to a fixed point, which for a simple network corresponds to a Nash Equilibrium.
+In addition, we find that, for games which are not zero-sum, agents following Continuous Time Fictitious Play are able to achieve no regret.
+
+		Finally, we explore the Fictitious Play algorithm through numerical simulations to understand how convergence rates depend on the network size and connectivity.
+We also show that it does not necessarily converge for more complex games and can, in fact, lead to more complex dynamics.
+In addition, we experiment the Fictitious Play algorithm on an agent based model for (resource allocation?
+voting?).
+Finally, our experiments document how noise affects the convergence of fictitious play, whose theoretical analysis we point out as an interesting direction for future work.
+
+		\ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}
 		\section{Preliminaries}
@@
 
-	\newpage
-	\subsection*{The Model}
+	\section{Numerical Experiments}
 
-	We have a set of agents $V = \{1, ..., N \}$ which can be thought of as nodes on a graph $\{V,
-	E, W\}$ where $E$ is the edge-set (i.e. the set of pairs $(i, j)$ such that i and j are
-	connected) and $W$ is a weighted adjacency matrix $[W]_{ij} = w_{ij}$. Let $N_i := \{j \in V :
-	(i, j) \in E\}$ be the set of player $i's$ neighbours. Note $w_{ij} = 0$ if $(i, j) \not\in E$,
-	$w_{ij} \in (0, 1]$ if $(i, j) \in E$. We impose the normalisation condition that $\sum_{j \in
-	N_i} w_{ij} = 1$. This requirement ensures that the aggregate strategy $\sum_{j \in N_i} w_{ij}
-	x_j$ (where $x$ is a probability vector) remains a probability vector. For example, in the 3
-	player case:
+	\section{Convergence rates w.r.t connectivity and size}
+	\section{Non-convergent examples}
+	\section{Agent based simulations}
+	\section{Addition of Noise}
 
-	\begin{equation}
-	\sigma_1 := w_{12} y + w_{13} z = 
-	w_{12}
-	\begin{bmatrix}
-	y_1 \\ y_2 \\ 1 - y_1 - y_2
-	\end{bmatrix}		
-	+ 	w_{13}
-	\begin{bmatrix}
-	z_1 \\ z_2 \\ 1 - z_1 - z_2
-	\end{bmatrix}	= 
-	\begin{bmatrix}
-	w_{12} y_1 + w_{13} z_1 \\ w_{12} y_2 + w_{13} z_2 \\ 1 - (w_{12} y_1 + w_{13} z_1) - (w_{12} y_2 + w_{13} z_2)
-	\end{bmatrix}	
-	\end{equation}
+	\section{Discussion}
 
-	In the continuous time case, we're also going to assume that each agent $i$ chooses a mixed strategy $x_i(t) \in \Delta_i$ at time $t$ from its strategy space $\Delta_i$ (which is an $N-$simplex).
-We assume that $i$ has just the one strategy that it can play against all of its neighbours.
-
-	\subsection*{Starting Assumptions}
-
-	\begin{enumerate}[I]
-		\item The weights $w_{ij}$ are constant for all $i, j$.
-		\item The payoffs $u_i$ are in matrix form, and so are bilinear.
-		\item All agents update their strategies synchronously
-		\item All agents have the same sized strategy space 
-		\item The network is zero-sum in the sense that $\sum_i u_i(x_i, w_{ii} x_i + \sum_{j} w_{ij} x_j)$ for any set of strategies $(x_1, ..., x_N)$. 
-	\end{enumerate}
-
-	\subsection*{The Argument for Bilinear Payoffs}
-
-	\textit{Zero-sum polymatrix games can model common situations in which nodes in a network interact pairwise and make decisions (for example, adopt one of many technologies, or choose one or more of their neighbors for preferential interaction)} (Cai et al (2016)))
-
-	\ah{Need to find more references to put in here, most papers don't really give real world examples to justify this model.}
-
-	\subsection*{Fictitious Play in Network Aggregative Games}
-
-	For Fictitious Play (FP), we require that the agent plays a best response to the time average to a \emph{reference signal} $\sigma_i$ which is some convex combination of the agent's own strategy and that of its neighbours on the network.
-Under the above assumptions, this reference is given as
-
-	\begin{equation*}
-		\sigma_i (t) = \sum_{j} w_{ij} x_j (t).
-	\end{equation*}
-
-	Let us have the following definitions:
-
-	\begin{align}
-		\alpha_{\sigma_i}(t) = \frac{1}{t} \int_{0}^{t} \sigma_i(t') \, dt'\nonumber \\
-		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} x_i(t') \, dt', \nonumber
-	\end{align}
-
-	where $x_i(t')$ denotes the action played by $i$ at time $t'$. Now we notice
-
-	\begin{align}
-		\alpha_{\sigma_i}(t) = \frac{1}{t} \int_{0}^{t} \sigma_i(t') \, dt' = \frac{1}{t} \int_{0}^t \sum_{j} w_{ij} x_j(t') \, dt' = \sum_{j} w_{ij} \frac{1}{t} \int_{0}^t x_j(t') \, dt' = \sum_{j} w_{ij} \alpha_j(t) \nonumber \\
-	\end{align}
-
-	\paragraph{Continuous Time Fictitious Play (CTFP)} A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
-
-	We can think of this definition as saying that the player plays some generic strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
-
-	\paragraph{Discrete Time Fictitious Play (DTFP)} A DTFP is defined a sequence $\{x_{k}\}_{k=1}^{\infty}$ with components $x_{k, i}$ such that, for all $i$ and, for all $k \geq 1$, $x_{k, i} \in BR_i\left( \frac{1}{k} \sum_{t = 0}^{k - 1} \sigma_{k, i} \right)$.
-
-	We can see that the DTFP is just the equivalent definition as the CTFP, except that the time domain is $\mathbb{Z}_+$ rather than $\mathbb{R}_+$.
-Nevertheless, the change from continuous to discrete is not trivial and we'll get to that soon.
-
-	\paragraph{Convergence} We write $\alpha$ as the concatenation of all $\alpha_i$.
-Let $\Omega(\alpha)$ be  the set of all limit points for $\alpha$.
-Then, CTFP is said to have converged if any $\mu^* \in \Omega(\alpha)$ is contained in the set of Nash Equilibria of the game.
-
-	With these definitions out of the way, we'll try to figure out whether, first, CTFP converges to a Nash Equilibrium. The process for doing this is as follows:
-
-	\begin{enumerate}
-		\item Show that a Nash equilibrium exists
-		\item Show that a path satisfying the CTFP property exists
-		\item Show that the associated $\Omega(\alpha)$ is contained in the set of NE.
-
-	\end{enumerate}
-
-	\newpage
-
-	\subsection*{First Case: Aggregation is dependent only on its neighbours}
-
-	We start with the following assumption
-
-	\begin{assumption}[V]
-	$w_{ii} = 0$ for all $i \in \{ 1, ..., N \}$
-	\end{assumption}
-
-	Under this assumption the $BR_i$ map becomes
-
-	\begin{equation}
-		BR_i(\sum_{j \in N_i} w_{ij} x_j) = \arg\max_{x \in \Delta_i} u_i(x_i,\sum_{j \in N_i} w_{ij} x_j)
-	\end{equation}
-
-	Under the assumption that the payoff function is bilinear and can be written as $u_i(x_i, \sigma_i) = x_i \cdot A^i \sigma_i$. Then
-
-	\begin{equation*}
-		u_i(x_i, \sigma_i) = x_i \cdot A^i \sum_{j \in N_i} w_{ij} x_j = \sum_{j \in N_i} x_i \cdot A^{ij} x_j =: \sum_{j \in N_i} u_{ij}(x_i, x_j) 
-	\end{equation*}
-
-	where $A^{ij} := w_{ij} A^i$ and $u_{ij}$ is a bilinear payoff between $i$ and $j$ as defined by Ewerhart. Furthermore, the NE condition is now
-
-	\begin{align}
-			x_i^* & \in BR_i(\sum_{j \in N_i} w_{ij} x_j^*). \\
-			& = \arg \max_{x \in \Delta_i} \sum_{j \in N_i} u_{ij}(x_i, x_j) 
-	\end{align}
-
-	 With this transformation, we can move from a network aggregative system to a network game formulation (as in Ewerhart) in which each agent $i$ plays a game $G_{ij}$ against $j$ with payoff $A^{ij}$ and with the added requirement that each agent plays the same strategy against each of its neighbours.
-With this change, we can apply Nash's Theorem to state that the Nash Equilibrium exists.
-
-	Applying the same transformation, CTFP becomes the requirement that, in the equivalent network game, $m_i(t) \in \arg \max_{x \in \Delta_i} \sum_{j \in N_i} u_{ij}(x_i, \alpha_j)$ for all $t \geq 1$.
-Now, Ewerhart showed that, in a zero-sum network (where the sum of all $u_i$ is zero), such an $m$ exists and any such $m$ converges to an NE.
-This must therefore also be true of the network aggregative game.
-
-	In any case, the fact that $m$ converges to an NE for the equivalent network game means that it converges for the NAG also. \ah{To make this precise, I'll follow through the proof of Ewerhart}
-
-	\begin{theorem}
-		For any zero-sum Network Aggregative Game which follows the above assumption, any CTFP $m$ has the property that $\Omega(\alpha)$ is contained within the set of NE of the game.
-	\end{theorem}
-
-	\begin{proof}
-		Take the Lyapunov function
-		\begin{align}
-			L(\mu) & = \sum_i \max_{x \in \Delta_i} \{u_i(x, \sum_{j \in N_i} w_{ij} \mu_j) - u_i(\mu_i, \sum_{j \in N_i} w_{ij} \mu_j) \} \nonumber \\
-			& = \sum_i \max_{x \in \Delta_i} \{u_i(x, \sum_{j \in N_i} w_{ij} \mu_j)\} - \sum_i u_i(\mu_i, \sum_{j \in N_i} w_{ij} \mu_j) \nonumber \\
-			& = \sum_i \max_{x \in \Delta_i} \{u_i(x, \sum_{j \in N_i} w_{ij} \mu_j)\} \nonumber
-		\end{align}
-
-		where the last equality holds because we made the assumption of a zero sum game.
-Making the usual transformation, we consider that $i$ is now involved in a network game in which it plays the same strategy against each of its neighbours $j$ giving
-
-		\begin{align}
-			L(\mu) = \sum_i \max_{x \in \Delta_i} \sum_{j \in N_i}  u_{ij}(x, \mu_j) \nonumber \\
-		\end{align}
-
-		Now we take any CTFP $m$ and recall that it is found by playing the best response to $\alpha(t; m)$, which of course means that it maximises $\sum_{j \in N_i} u_{ij}$. Therefore
-
-		\begin{align}
-			L(\alpha(t)) & = \sum_i \sum_{j \in N_i} u_{ij}(m_i(t), \alpha_j(t)) \nonumber \\
-			& = \sum_i \sum_{j \in N_i} m_i(t) A^{ij} \alpha_j(t)
-		\end{align}
-
-		 Now if we were to follow on using Ewerhart's proof, we would find that any accumulation point of $\alpha(t; m)$ is an NE of the network game.
-I.e.
-if $\mu^*$ is this limit point, then it satisfies that, for any $x \in \Delta_i$
-
-		 \begin{align}
-		 	\sum_{j \in N_i} u_{ij}(x, \mu_j^*) \leq 	\sum_{j \in N_i} u_{ij}(\mu_i^*, \mu_j^*) \nonumber
-		 \end{align}
-
-		 Now if we reverse the transformation this means that, for the network aggregative game we have the condition that for any $x \in \Delta_i$
-
-		 \begin{align}
-		 	u_{i}(x, \sum_{j \in N_i} w_{ij} \mu_j^*) \leq u_{i}(\mu_i^*, \sum_{j \in N_i} w_{ij} \mu_j^*)
-		 \end{align}
-
-	\end{proof}
-	\newpage
-
-	\subsection*{Second Case}
-
-	This case is much more complex and requires that we take into account all of the steps properly.
-
-	\subsubsection*{Existence of the Nash Equilibrium}
-
-	The NE condition here is the same as the original definition that we had, but I'll repeat it here for the sake of convenience. The set of vectors $\{ x_i^*\}_{i = 1}^N$ is an NE if, for all $i$,
-
-	\begin{equation*}
-		x_i^* \in BR_i( w_{ii} x_i^* + \sum_{j \in N_i} w_{ij} x_j^*).
-	\end{equation*}
-
-	Note that this requires
-
-	\begin{align}
-		x_i^* &\in \arg\max_{x \in \Delta_i} u_i(x_i, w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j^*) \nonumber\\
-		&= \arg\max_{x \in \Delta_i} \bar{u}_i(x_i, \sum_{j \in N_i} w_{ij} x_j^*),
-	\end{align}
-
-	where we can find $\bar{u}_i$ through the following argument
-
-	\begin{align}
-		u_i(x_i, w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j^*) & = x_i \cdot A_i (w_{ii} x_i + \sum_{j \in N_i} w_{ij} x_j) \\
-		 & = x_i \cdot (w_{ii} A_i)  x_i + \sum_{j \in N_i} u_{ij}(x_i, x_j) \\
-		 & =: \bar{u}_i(x_i, \sum_{j \in N_i} w_{ij} x_j^*), \nonumber
-	\end{align}
-
-	where $u_{ij}$ is as previously defined. Note that, in order to get this formulation, we had to use the bilinear assumption (II) so that we could separate out the term involving $x_i$ easily.
-
-	To show existence of an NE we will need the following definition and Theorem.
-
-	\begin{definition}[Upper Semi-Continuous]
-		A compact-valued correspondence $\Phi: A \rightarrow B$ is \emph{upper semi-continuous} at a point $a$ if $g(a)$ is non-empty and if, for every sequence $a_n \rightarrow a$ and every sequence $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a convergent subsequence of $(b_n)$ whose limit point $b$ is in $g(a)$.
-	\end{definition}
-
-	\begin{theorem}[Kakutani]
-		Let $K \subset \mathbb{R}^n$ be compact and convex and $\Phi: K \rightarrow K$ be closed or upper semi-continuous, with nonempty, convex and compact values. Then $\Phi$ has a fixed point.
-	\end{theorem}
-
-	Note that, when active on a simplex, the function $\Phi: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes the nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.
-
-	\begin{theorem}[Existence of NE]
-		Under the assumption (II), namely that the payoff function achieves a bilinear property, a Nash Equilibrium $\{x_i^*\}_{i = 1}^N$ exists.
-	\end{theorem}
-
-	\begin{proof}
-		We begin by rewriting the NE condition by concatenating the set of NE vectors into one long colunn vector. This gives
-
-		\begin{equation}
-			\begin{bmatrix}
-				x_1^* \\ . \\ . \\ . \\ x_N^*
-			\end{bmatrix} \in
-			\begin{bmatrix}
-			\arg\max_{y \in \Delta_1} \bar{u}_1(y, \sum_{j \in N_i} w_{ij} x_j^*) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, \sum_{j \in N_i} w_{ij} x_j^*)
-			\end{bmatrix}	.
-		\end{equation}
-
-		We can rewrite the weighted summation in the $i$'th component of the right hand side as
-
-		\begin{equation}
-			\sum_{j \in N_i} w_{ij} x_j^* = (w_{-i}^T \otimes I_n) \begin{bmatrix}
-				x_1^* \\ . \\ . \\ . \\ x_N^*
-			\end{bmatrix},
-		\end{equation}
-
-		in which $w_{-i}$ is a column vector containing $w_{ij}$ in the $j$'th element for all $j \in N(i)$ and 0 everywhere else (including in the $i$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product.
-For example, the form for agent 1, in the case of 2-action game is given by
-
-		\begin{equation}
-			(w_{-1}^T \otimes I_2) = [0, w_{12}, w_{13}, ..., w_{1n}] \otimes I_2 = 
-			\begin{bmatrix}
-				0 & 0 & w_{12} & 0 & ... & w_{1n} & 0 \\
-				0 & 0 & 0 & w_{12} & ... & 0 & w_{1n} \\
-			\end{bmatrix}
-		\end{equation}
-
-		So our condition becomes
-		\begin{equation}
-			\begin{bmatrix}
-				x_1^* \\ . \\ . \\ . \\ x_N^*
-			\end{bmatrix} \in
-			\begin{bmatrix}
-				\arg\max_{y \in \Delta_1} \bar{u}_1(y, (w_{-1}^T \otimes I_n) \begin{bmatrix}
-					x_1^* \\ . \\ . \\ . \\ x_N^*
-				\end{bmatrix}) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n) \begin{bmatrix}
-				x_1^* \\ . \\ . \\ . \\ x_N^*
-			\end{bmatrix}))
-			\end{bmatrix}	.
-		\end{equation}
-
-		This means that we achieve a Nash Equilibrium iff $\{ x_i^*\}_{i = 1}^N$ is a fixed point of the map
-
-		\begin{equation}
-			\begin{bmatrix}
-				\arg\max_{y \in \Delta_1} \bar{u}_1(y, (w_{-1}^T \otimes I_n) ( \cdot )) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n)( \cdot )))
-			\end{bmatrix}	.
-		\end{equation}
-
-		Now, since the modified payoff $\bar{u}$ shares the same bilinear property as $u$, we can assert that it is continuous is its second argument.
-Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous.
-This continuity can be extended to the above concatenation of best responses.
-As such, we can apply Kakutani's Fixed Point Theorem to assert that the above map admits a fixed point.
-
-	\end{proof}
-
-	\subsubsection*{Existence of a CTFP}
-
-	\begin{theorem}
-		There exists a path $m$ which satisfies the property that, for all $i$, $m_i \in BR_i
-		(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
-	\end{theorem}
-
-	\begin{proof}
-		Recall the definition of $\alpha_i(t)$
-
-		\begin{equation*}
-		\alpha_i(t) = \frac{1}{t} \int_{0}^{t} m_i(t') \, dt'
-		\end{equation*}
-
-		Then
-
-		\begin{align}
-		\frac{d}{dt} \alpha_i(t) & = \frac{d}{dt} \frac{1}{t} \int_{0}^t m_i(t') dt' \nonumber \\
-		& = \frac{1}{t} m_i(t) - \frac{1}{t} \alpha_i(t)
-		\end{align}
-
-		Now we assert that $m_i(t) \in BR_i(\alpha_{\sigma_t}) = \arg\max_{y \in \Delta_i} u_i(y,
-		w_{ii} \alpha_i(t) + \sum_{j \in N(i)} w_{ij} \alpha_j(t))$.
-
-		Let us then define $\alpha(t)$ as the concatenation of all $\alpha_i(t)$
-
-		\begin{equation}
-			\alpha(t) = \begin{bmatrix}
-				\alpha_1(t)^T, \ldots, \alpha_N(t)^T
-			\end{bmatrix}^T \subset \mathbb{R}^{Nn}
-		\end{equation}
-
-		We can, therefore, write the aggregation as
-
-		\begin{equation}
-			(W \otimes I_n) \alpha(t) = \begin{bmatrix}
-				\sum_{j \in N(1)} w_{1j} \alpha_j(t) \\
-				.\\
-				.\\
-				.\\
-				\sum_{j \in N(N)} w_{Nj} \alpha_j(t)
-			\end{bmatrix} \subset \mathbb{R}^{Nn}
-		\end{equation}
-
-		I will write $(W \otimes I_n) \alpha(t)$ as $\alpha_W$ for convenience. Furthermore, using
-		the bimatrix property of the game, we can say that
-
-		\begin{equation}
-			\begin{bmatrix}
-				\arg\max_{y \in \Delta_1} y \cdot A_1 ( \alpha_W(t)_1) \\
-				.\\
-				.\\
-				.\\
-				\arg \max_{y \in \Delta_N} y \cdot A_n (\alpha_W(t)_N) 
-			\end{bmatrix} = 
-			\arg \max_{y \in \Delta} y \cdot \begin{bmatrix}
-				A_1 & 0 & . & . & . & 0 \\
-				0 & A_2 & . & . & . & 0 \\
-				& & . & & & \\
-				& & & . & & \\
-				& & & & . & \\
-				0 & 0 & . & . & . & A_N \\
-			\end{bmatrix} \alpha_W(t) = \arg\max_{y \in \Delta} y \cdot \Lambda (W \otimes I_n)
-			\alpha(t)
-		\end{equation}
-
-		in which $\Delta = \times_i \Delta_i$ and $\Lambda$ is the block diagonal matrix containing
-		each $A_i$.
-
-		We can now write the differential inclusion as
-
-		\begin{equation}
-			\dot{\alpha(t)} \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
-			I_n)
-			\alpha(t) \}- \alpha(t))
-		\end{equation}
-
-		with the initial condition $\alpha(1) = \mu$. Then, the path $m$ is a CTFP if its
-		corresponding $\alpha(t; m)$ is a solution to the above differential inclusion. Following
-		the definition of (Harris 1998), a solution $\alpha(t)$ must satisfy
-
-		\begin{enumerate}
-			\item $\alpha(t)$ is locally Lipschitz
-			\item $\alpha(1) = \mu$
-			\item $\dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
-			I_n)
-			\alpha(t) \}- \alpha(t))$ for almost all $t \in [1, \infty)$ 
-		\end{enumerate}
-
-		The question then remains, does the differential inclusion admit a solution? Using the
-		results of Aubin and Cellina (see Harris 1998, paragraph below Prop. 6), can use the fact
-		that the $\arg \max$ function is non-empty, compact and convex valued, bounded (all of
-		these follow since the function acts from $\Delta$ to $\Delta$) and upper semi-continuous.
-		With these facts in place, we can say that there is a CTFP for any initial value $\mu$.
-		\ah{I believe this holds for any choice of $W$ as long as it is row stochastic so that
-		the values remain inside $\Delta$ after aggregation}.
-	\end{proof}
-
-	\newpage
-
-	\section*{Convergence Properties}
-
-	In this section I will show that the NA-CTFP process converges to the set of coarse correlated
-	equilibria. So first I will define what this means. \ah{For Francesco: Please forgive me for
-	changing notation, I'll make everything consistent.}
-
-	The notion of the CCE set is best considered through \emph{regret} which, for agent $\mu$ is given as
-
-	\begin{equation}
-		R^{\mu} = \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\}
-	\end{equation}
-
-	To illustrate this, let us consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$ is given by
-
-	\begin{equation}
-		u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
-	\end{equation}
-
-	On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(x_{i'}^\mu(t), \sigma(t))$, then
-
-	\begin{equation}
-		\max_{x_{i'}^\mu \in S^\mu} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu
-	\end{equation}
-
-	By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change.
-As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time.
-An agent achives \emph{no regret} if $R^\mu$ is non-positive.
-	% \begin{definition}[Coarse Correlated Equilibrium]
-	% 	A distribution $D$ over action profiles $\times_{\mu} A^{\mu}$ is a \emph{coarse correlated
-	% 	equilibrium} if, for
-	% 	all players $\mu$ and
-	% 	all
-	% 	actions $i' \in A^{\mu}$
-
-	% 	\begin{equation}
-	% 		\mathbb{E}_{a \sim D}[u^{\mu}(a)] \geq \mathbb{E}_{a \sim D}[u^{\mu}(a^\mu_{i'}, a
-	% 		^{- \mu})]
-	% 	\end{equation}
-
-	% \end{definition}
-	\begin{theorem}
-		Assuming that $w_{ii} = 0$, then for any choice of payoff matrix, agents following the NA-FP process achieve zero regret in the limit, i.e.
-		\begin{equation}
-			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
-		\end{equation}
-
-	\end{theorem}
-
-	\begin{proof}
-		We will adapt the techniques of Ostrovski and van Strein for this proof.
-Their result was found for a two player game, we will leverage the fact that the NA process means that we can reduce an $N$ player game down to a series of two player games.
-
-		For any agent $\mu$ define
-		\begin{equation}
-			\bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu)
-		\end{equation}
-
-		Now, if the agents are following the NA-FP process, then we know that $m^\mu (t) \in \Delta_\mu$ is the strategy which maximises $u^\mu( \cdot, \alpha_\sigma^\mu)$ so we can write
-
-		\begin{equation}
-			\bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu) = m^\mu(t) \cdot A^\mu (\alpha_\sigma^\mu)
-		\end{equation}
-
-		Then, applying the \emph{envelope theorem} we have
-
-		\begin{equation}
-			\frac{d}{d \alpha_\sigma^\mu} \bar{u}^\mu (\alpha_\sigma^\mu) = \frac{d}{d \alpha_\sigma^\mu} x^\mu \cdot A^\mu (\alpha_\sigma^\mu) \Big |_{x^\mu = m^\mu} = m^\mu \cdot A^\mu
-		\end{equation}
-
-		Which gives that
-
-		\begin{equation}
-			\frac{d}{dt} \bar{u}^\mu (\alpha_\sigma^\mu (t)) = m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt}
-		\end{equation}
-
-		Then,
-
-		\begin{align}
-			\frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & =  \bar{u}^\mu (\alpha_\sigma^\mu (t)) + t m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt} \\
-			& = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + t (m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{d}{dt} \alpha^\nu(t))
-		\end{align}
-
-		Now, we know that the differential inclusion for the NA-FP process can be written as
-
-		\begin{equation}
-			\frac{d}{dt} \alpha^\mu (t) = \frac{1}{t} (m^\mu(t) - \alpha^\mu (t))
-		\end{equation}
-
-		We insert this into the previous equation to yield
-
-		\begin{align}
-			\frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t)) + t(m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{1}{t} (m^\nu(t) - \alpha^\nu (t))) \\
-			& = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} (m^\nu(t) - \alpha^\nu (t)) \\
-			& = m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} m^\nu(t) = m^\mu \cdot A^\mu \sigma^\mu(t) 
-		\end{align}
-
-		Now if we integrate both sides with respect to $t$ in the bound $[1, T]$ (on which the NA-FP) process is defined, we get
-
-		\begin{align}
-			&  T \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
-			& \implies \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \frac{1}{T} \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
-			& \implies \lim_{T \rightarrow \infty} \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \int_0^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt = 0
-		\end{align}
-
-		Now notice
-
-		\begin{align}
-			\bar{u}^\mu (\alpha_\sigma^\mu (T)) = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\alpha_{\sigma}^\mu (T))_j & = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\frac{1}{T} \int_{0}^{T} \sigma^\mu(t) \; dt)_j \\
-			& = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} \frac{1}{T} \int_{0}^{T} \sum_i (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
-			& = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T \sum_{ij} a_{i'j} (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
-			& = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T u^\mu(x^\mu_{i'}, \sigma^\mu(t))
-		\end{align}
-
-		So we recover
-
-		\begin{equation}
-			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
-		\end{equation}
-
-		which was precisely the regret condition that we required.
-
-		\ah{Note: I think that this means that the NA-FP process converges to the coarse correlated equilibrium (CCE) set, but I'm a little hesitant to write it just because I'm not sure if the terminology lines up}
-	\end{proof}
-
-	\newpage
-
+	\section{Concluding remarks}
 \end{document}

### 2021-04-20 Documents/FP in NAGs/FPNAG.tex
Updated Experimental section with non-convergent plots

@@
 \usepackage{enumerate}
+\usepackage{graphicx}
 
@@
 		\item Numerical Experiments \begin{itemize}
-			\item Convergence rates w.r.t. connectivity and size
 			\item Non-convergent examples
-			\item Agent based simulations
+			\item Fictitious Play with Noise
 		\end{itemize}
@@
 		\subsection{Related Work}
-		Main articles: Ewerhart (FP in Networks), Grammatico (Nash Equilibrium seeking in NA games), Perrin (FP in mean field games), Harris (FP in 2 player games).
+		Main articles: 
+		\begin{enumerate}
+			\item Ewerhart (FP in Networks).
+Main difference is in the model we consider - i.e.
+agents only track the aggregate strategy rather than strategies of all neighbours.
+Further, our analysis shows that in non-simple networks, FP still converges to a fixed point, although not an NE.
+			\item Grammatico (NE seeking in NA games).
+Main difference is that we look at the case where the payoffs are bilinear (since in matrix form), so that we need to consider best response correspondences rather than assuming a unique minimiser.
+			\item Perrin (FP in Mean Field Games).
+Main difference is that we assume an underlying communication network rather than assuming that the players play against the entire population (which is a special case of our analysis, in which you assume that all players are connected to each other).
+			\item Sela (FP in one-against-all networks) Similarly, this paper doesn't assume an underlying communication network or any form of weighted communication between the agents.
+		\end{enumerate}
+
 		\subsection{Contributions}
@@
 
-	\section{Convergence rates w.r.t connectivity and size}
 	\section{Non-convergent examples}
-	\section{Agent based simulations}
+	The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.
+
+	As a example of nonconvergence we consider the Shapley family of games \cite{}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by
+
+	\begin{equation}
+		A_\beta = \begin{bmatrix}
+			1 & 0 & \beta \\
+			\beta & 1 & 0 \\
+			0 & \beta & 1
+		\end{bmatrix}, \; B_\beta =  \begin{bmatrix}
+			- \beta & 1 & 0 \\
+			0 & -\beta & 1 \\
+			1 & 0 & -\beta
+		\end{bmatrix}
+	\end{equation}
+
+	where $\beta \in (0, 1)$. In \cite{} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.
+
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width = 0.7\textwidth]{Figures/ThreePlayerNetwork.png}
+		\caption{\label{fig::ThreePlayerNetwork}}
+	\end{figure}
+
+	As an adaptation, we take the example of a three player chain, as depicted in Figure \ref{fig::ThreePlayerNetwork}.
+In this example, we first assume that the network is simple (i.e.
+there are no self-loops and $w^{\mu \mu} = 0$).
+The aggregation matrix can be given as
+
+	\begin{equation}
+		W = \begin{bmatrix}
+			0 & 1 & 0 \\
+			w & 0 & 1 - w \\
+			0 & 1 & 0
+		\end{bmatrix}, \; w \in (0, 1).
+	\end{equation}
+
+	We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected. Note that the zero-sum condition given for the three player chain is given as
+
+	\begin{equation}
+		x \cdot A y + y \cdot B (w x + (1-w)z) + z \cdot C y = 0. \hspace{0.5cm} \forall x, y, z \in \Delta_1 \times \Delta_2 \times \Delta_3
+	\end{equation}
+
+	in which we use the notation that $x, y, z$ (resp. $A, B, C$) denote the strategies (resp. payoffs) of agents 1, 2 and 3 respectively. This condition is satisfied if we fix $B$ and choose
+
+	\begin{align}
+		A & = - w B^T \\
+		C & = - (1 - w) B^T. 
+	\end{align}
+
+	As such in the following example, we will set $B = B_\beta$ with the choice $\beta \approx 0.576$ and set $A$ and $C$ according to the above with the choice $w \approx 0.288$.
+The orbits that these payoff matrices generate can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which, for each player, lies in the centre of the simplex.
+
+	Let us now make the slight modification in the definition of C so that
+
+	\begin{equation}
+		C  = - (1 - w) B, 
+	\end{equation}
+
+	with no alteration to $A$.
+The modification itself is small, however it results in the zero-sum assumption being violated.
+With the same choices of $\beta$ and $w$, this results in the periodic orbit seen in Figure \ref{fig::nonconvergentShapley}.
+Here, the orbits reach a stable limit cycle which to be centred around the interior NE.
+
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width = 0.7\textwidth]{Figures/convergentShapley.png}
+		\caption{\label{fig::convergentShapley}}
+	\end{figure}
+
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width = 0.7\textwidth]{Figures/nonconvergentShapley.png}
+		\caption{\label{fig::nonconvergentShapley}}
+	\end{figure}
+
+	As such, we can see that convergent behaviour is not necessarily the norm in the NA-CTFP dynamics.
+In fact, for the family of games discussed above, we were unable to find non-periodic behaviour for any choice of $\beta$ strictly between 0.5 and 1 for any $w$ between 0.2 and 0.8 (so that the influence of player 1 and player 3 on player 2 is not negligible).
+This suggests that, far from being rare, in fact NA-CTFP lends itself to an incredibly rich variety of dynamics which can be explored as future work.
+
 	\section{Addition of Noise}
+
+	The fictitious play process in NA games requires that, at each time step, an agent takes a `measurement' of the aggregate strategy of its neighbours.
+It is on this measurement that they update their own strategy.
+It stands to reason that, in real environments, this measurement may be corrupted by noise.
+As such, we investigate the effect that introducing noise has on CTFP in a zero-sum NA game.
+
+	\ah{To discuss with F before including in the document}.
 

### 2021-04-23 Documents/FP in NAGs/FPNAG.tex
minor edits

--- 2021-04-14 Documents/FP in NAGs/FPNAG.tex
@@
 	\section{Introduction}
-		\subsection{Related Work}
-		Main articles: Ewerhart (FP in Networks), Grammatico (Nash Equilibrium seeking in NA games), Perrin (FP in mean field games), Harris (FP in 2 player games).
 		\subsection{Contributions}
 
-		The main contribution of this work is to study the behaviour of the Fictitious Play Learning Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game.
-We first show that a Nash Equilibrium exists and that Fictitious Play admits solutions in this setting.
-In particular, we study zero-sum games and show that Fictitious Play converges to a fixed point, which for a simple network corresponds to a Nash Equilibrium.
-In addition, we find that, for games which are not zero-sum, agents following Continuous Time Fictitious Play are able to achieve no regret.
+		The main contribution of this work is to study the
+                behaviour of the Fictitious Play Learning Algorithm,
+                in continuous time, when applied on a Network
+                Aggregative Matrix Game.
+\fb{why FP and NAG are important?}
 
-		Finally, we explore the Fictitious Play algorithm through numerical simulations to understand how convergence rates depend on the network size and connectivity.
-We also show that it does not necessarily converge for more complex games and can, in fact, lead to more complex dynamics.
-In addition, we experiment the Fictitious Play algorithm on an agent based model for (resource allocation?
-voting?).
-Finally, our experiments document how noise affects the convergence of fictitious play, whose theoretical analysis we point out as an interesting direction for future work.
+                We first show that a Nash
+                Equilibrium exists and that Fictitious Play admits
+                solutions in this setting. In particular, we study
+                zero-sum games and show that Fictitious Play converges
+                to a fixed point, which for a simple \fb{define simple} network
+                corresponds to a Nash Equilibrium. In addition, we
+                find that, for games which are not zero-sum, agents
+                following Continuous Time Fictitious Play are able to
+                achieve no regret.
 
-		\ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}
+		Finally, we explore the Fictitious Play algorithm
+                through numerical simulations to understand how
+                convergence rates depend on the network size and
+                connectivity. We also show that it does not
+                necessarily converge for more complex games and can,
+                in fact, lead to more complex dynamics. In addition,
+                we experiment the Fictitious Play algorithm on an
+                agent based model for (resource allocation?
+                voting?). Finally, our experiments document how noise
+                affects the convergence of fictitious play, whose
+                theoretical analysis we point out as an interesting
+                direction for future work.
+
+		\ah{Possible additions: 1) Show that the flow is
+                  unique almost everywhere in CTFP. 2) Show the same
+                  results (i.e. existence and convergence) for
+                  Discrete Time Fictitious Play.}
+
+		\subsection{Related Work}
+		Main articles: Ewerhart (FP in Networks), Grammatico
+                (Nash Equilibrium seeking in NA games), Perrin (FP in
+                mean field games), Harris (FP in 2 player games).
+
 		\section{Preliminaries}
@@
 
-	The model we consider is that there is a set $\agentset = {1, ... ,
-	N}$ of agents who are connected through an underlying interaction graph. This graph is given by
-	the tuple $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is the set of all pairs $(\mu,
-	\nu) \in \agentset \times \agentset$ such that agent $\mu$ and agent $\nu$ are connected. Then,
-	the set of neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu,
-	\nu) \in \edgeset\}$. $\weightset
-	\in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu \nu}$ expresses the
-	importance that agent $\mu$ places on agent $\nu$. Note that if $(\mu, \nu) \not \in \edgeset$
-	then $w^{\mu \nu} = 0$ and $\wmunu \in (0, 1]$ otherwise.
+	The model we consider is that there is a set $\agentset = {1,
+         \ldots , N}$ of agents who are connected through an underlying
+        interaction graph. This graph is given by the tuple
+        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
+        the set of all pairs $(\mu, \nu) \in \agentset \times
+        \agentset$ such that agent $\mu$ and agent $\nu$ are
+        connected.
+        \fb{
+          \begin{definition}[Interaction Graph]
+  Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset, \weightset))$ such that
+  \begin{itemize}
+  \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent $\mu$ is
+        denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in
+        \edgeset\}$.
+    \item $\weightset \in M_N(\mathbb{R})$ is the weighted
+        adjacency matrix whose elements $w^{\mu \nu}$ expresses the
+        importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
+  \end{itemize}
+\end{definition}
+}
 
-	As a network game, each agent $\mu$ has an associated set of pure strategies $\actionset{\mu}$
-	which has cardinality $|\actionset{\mu}| = n$. Then we can construct the unit-simplex on this
-	action set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i \xmuaction{i} = 1\}$ where
-	$\xmuaction{i}$ is the probability with which agent $\mu$ plays the pure strategy $i$. As such
-	we refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is often referred to as $\mu$'s
-	mixed strategy). Also associated with each agent is a utility function $u^\mu(\xmu, \xnotmu)$ in
-	which we use the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that
-	this requires that each agent plays the same strategy against all of their neighbours.
+	As a network game, each agent $\mu$ has an associated set of
+        pure strategies $\actionset{\mu}$ which has cardinality
+        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
+          we define them if we didn't introduce actions?}
 
-	With all of the above definitions, we can formalise the network aggregative (NA) game as the tuple
-	$\Gamma = (\agentset, (\edgeset, \weightset), (\actionset{\mu}, \utility{\mu})_{\mu \in \mathcal{N}})$.
+        Then we can construct the \fb{unit-simplex ?} on this action
+        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
+        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
+        with which agent $\mu$ plays the pure strategy $i$. As such we
+        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
+        often referred to as $\mu$'s mixed strategy). Also associated
+        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
+        in which we use the standard notation $-\mu$ to refer to all
+        agents other than $\mu$. Notice that this requires that each
+        agent plays the same strategy against all of their neighbours.
 
-	What is unique about the NA game is the structure of the payoffs themselves. In this format,
-	each agent is receives a reference $\sigma$ which is a weighted sum of each of their
+	With all of the above definitions, we can formalise the
+        network aggregative (NA) game as the tuple $\Gamma =
+        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
+        \utility{\mu})_{\mu \in \mathcal{N}})$. \fb{preferably use a
+          definition environment.}
+
+	What is unique about the NA game is the structure of the
+        payoffs themselves. In this format, each agent is receives a
+        reference $\sigma$ which is a weighted sum of each of their
         neighbours state. Formally
-
+%
 	\begin{equation}
@@
 
-	Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
-	instead of having to consider the actions of the entire population, or play individual games
-	against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a `measurement'
-	of the local aggregate state and optimise with respect to this measurement. This allows us to
-	make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider that
-	the agent is engaged in a matrix game against the reference vector so that
-
+	Then, the agent's must optimise their payoff with respect to
+        this reference vector. Thus, instead of having to consider the
+        actions of the entire population, or play individual games
+        against each of their neighbours, the agent only has to
+        consider $\sigma^\mu$ as a `measurement' of the local
+        aggregate state and optimise with respect to this
+        measurement. This allows us to make the reduction $u^\mu(\xmu,
+        \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider
+        that the agent is engaged in a matrix game against the
+        reference vector so that
+%
 	\begin{equation}
-		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu \cdot A^\mu \weightedsum.
+		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
+                \cdot A^\mu \weightedsum.
 	\end{equation}
-
-	where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we could have
-	written the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
-	$\utility{\mu}$. The NA game allows for the reduction of a
-	multiplayer game into a series of two-player games. The agent's goal is to maximise their payoff
-	with respect to the reference vector. As such, we define the best response correspondence
-	$BR^\mu$ which maps any $\refmu$ the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
-	leads naturally to the definition of a Nash Equilibrium in an NA Game as
+	where $A^\mu$ is the payoff matrix associated to agent
+        $\mu$. Note that this means we can write the game
+        $\Gamma$ with the payoff matrices $A^mu$ in place of the
+        utility functions $\utility{\mu}$. The NA game allows for the
+        reduction of a multiplayer game into a series of two-player
+        games. The agent's goal is to maximise their payoff with
+        respect to the reference vector. As such, we define the best
+        response correspondence $BR^\mu$ which maps any $\refmu$ the
+        set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
+        leads naturally to the definition of a Nash Equilibrium in an
+        NA Game as
 
@@
 		The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,	
-
 		\begin{equation*}
@@
 		\end{equation*}	
-
 	\end{definition}
+        \fb{It this a definition or rather a lemma?}
 
@@
 	\ah{For Francesco: is it worth giving a quick introduction to Fictitious Play by talking about two player games?}
+\fb{I'd rather give the definition first and then the example.}
 
-	Fictitious Play requires that, at the current time, each agent considers the average behaviour
-	of their opponent in the past and play a best response to that strategy. This is best
-	illustrated in the two-player setting. Consider the two player normal form game $\Gamma_2 = (\{
-	1, 2\}, ((S^1, A), (S^2, B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$ and $2$
-	respectively. As a remark, note that we can write the two player normal form game as an NA game
-	simply by requiring that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2 matrix with
-	zeros on its leading diagonal and ones on the off diagonal. We write the time-average of both
-	agents' strategies as
+	Fictitious Play requires that, at the current time, each agent
+        considers the average behaviour of their opponent in the past
+        and play a best response to that strategy. This is best
+        illustrated in the two-player setting. Consider the two player
+        normal form game $\Gamma_2 = (\{ 1, 2\}, ((S^1, A), (S^2,
+        B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$
+        and $2$ respectively. As a remark, note that we can write the
+        two player normal form game as an NA game simply by requiring
+        that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2
+        matrix with zeros on its leading diagonal and ones on the off
+        diagonal. We write the time-average of both agents' strategies
+        as
+%
+	\begin{align}
+		\alpha^i = \frac{1}{t} \int_0^T x^i(t) \, dt & \text{ for $i \in \{1, 2\}$}
+%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
+	\end{align}
+        \fb{why using an integral rather than a simple summation?}
 
-	\begin{align}
-		\alpha^1 = \frac{1}{t} \int_0^T x^1(t) \, dt \\
-		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
-	\end{align}
+        \fb{decide whether you start enumerations from 1 or 0.}
 
@@
 	write
-
 	\begin{equation}
@@
 	Fictitious Play in continuous time.
-
+%
 	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
 		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
+	\end{definition}
 
 		We can think of this definition as saying that the player plays some arbitrary strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
-	\end{definition}
 
@@
 	\end{assumption}
+
+\fb{discuss how restrictive each of these assumptions is.}
 

### 2021-04-23 Documents/FP in NAGs/FPNAG.tex
Most recent version

--- 2021-04-20 Documents/FP in NAGs/FPNAG.tex
@@
 	\section{Introduction}
+
+		\subsection{Contributions}
+
+		The main contribution of this work is to study the
+                behaviour of the Fictitious Play Learning Algorithm,
+                in continuous time, when applied on a Network
+                Aggregative Matrix Game.
+\fb{why FP and NAG are important?}
+
+                We first show that a Nash
+                Equilibrium exists and that Fictitious Play admits
+                solutions in this setting. In particular, we study
+                zero-sum games and show that Fictitious Play converges
+                to a fixed point, which for a network without any self-loops
+                corresponds to a Nash Equilibrium. In addition, we
+                find that, for games which are not zero-sum, agents
+                following Continuous Time Fictitious Play are able to
+                achieve no regret.
+
+		Finally, we explore the Fictitious Play algorithm
+                through numerical simulations to understand how
+                convergence rates depend on the network size and
+                connectivity. We also show that it does not
+                necessarily converge for more complex games and can,
+                in fact, lead to more complex dynamics. In addition,
+                we experiment the Fictitious Play algorithm on an
+                agent based model for \ah{resource allocation? 
+                voting?}. Finally, our experiments document how noise
+                affects the convergence of fictitious play, whose
+                theoretical analysis we point out as an interesting
+                direction for future work.
+
+		\ah{Possible additions: 1) Show that the flow is
+                  unique almost everywhere in CTFP. 2) Show the same
+                  results (i.e. existence and convergence) for
+                  Discrete Time Fictitious Play.}
+
 		\subsection{Related Work}
@@
 
-		\subsection{Contributions}
-
-		The main contribution of this work is to study the behaviour of the Fictitious Play Learning Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game.
-We first show that a Nash Equilibrium exists and that Fictitious Play admits solutions in this setting.
-In particular, we study zero-sum games and show that Fictitious Play converges to a fixed point, which for a simple network corresponds to a Nash Equilibrium.
-In addition, we find that, for games which are not zero-sum, agents following Continuous Time Fictitious Play are able to achieve no regret.
-
-		Finally, we explore the Fictitious Play algorithm through numerical simulations to understand how convergence rates depend on the network size and connectivity.
-We also show that it does not necessarily converge for more complex games and can, in fact, lead to more complex dynamics.
-In addition, we experiment the Fictitious Play algorithm on an agent based model for (resource allocation?
-voting?).
-Finally, our experiments document how noise affects the convergence of fictitious play, whose theoretical analysis we point out as an interesting direction for future work.
-
-		\ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}
 		\section{Preliminaries}
@@
 
-	The model we consider is that there is a set $\agentset = {1, ... ,
-	N}$ of agents who are connected through an underlying interaction graph. This graph is given by
-	the tuple $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is the set of all pairs $(\mu,
-	\nu) \in \agentset \times \agentset$ such that agent $\mu$ and agent $\nu$ are connected. Then,
-	the set of neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu,
-	\nu) \in \edgeset\}$. $\weightset
-	\in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu \nu}$ expresses the
-	importance that agent $\mu$ places on agent $\nu$. Note that if $(\mu, \nu) \not \in \edgeset$
-	then $w^{\mu \nu} = 0$ and $\wmunu \in (0, 1]$ otherwise.
+	The model we consider is that there is a set $\agentset = {1,
+         \ldots , N}$ of agents who are connected through an underlying
+        interaction graph. This graph is given by the tuple
+        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
+        the set of all pairs $(\mu, \nu) \in \agentset \times
+        \agentset$ such that agent $\mu$ and agent $\nu$ are
+        connected. Formally,
 
-	As a network game, each agent $\mu$ has an associated set of pure strategies $\actionset{\mu}$
-	which has cardinality $|\actionset{\mu}| = n$. Then we can construct the unit-simplex on this
-	action set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i \xmuaction{i} = 1\}$ where
-	$\xmuaction{i}$ is the probability with which agent $\mu$ plays the pure strategy $i$. As such
-	we refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is often referred to as $\mu$'s
-	mixed strategy). Also associated with each agent is a utility function $u^\mu(\xmu, \xnotmu)$ in
-	which we use the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that
-	this requires that each agent plays the same strategy against all of their neighbours.
+          \begin{definition}[Interaction Graph]
+  Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset, \weightset))$ such that
+  \begin{itemize}
+  \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent $\mu$ is
+        denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in
+        \edgeset\}$.
+    \item $\weightset \in M_N(\mathbb{R})$ is the weighted
+        adjacency matrix whose elements $w^{\mu \nu}$ expresses the
+        importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
+  \end{itemize}
+\end{definition}
 
-	With all of the above definitions, we can formalise the network aggregative (NA) game as the tuple
-	$\Gamma = (\agentset, (\edgeset, \weightset), (\actionset{\mu}, \utility{\mu})_{\mu \in \mathcal{N}})$.
+	As a network game, each agent $\mu$ has an associated set of
+        actions $\actionset{\mu}$ which has cardinality
+        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
+          we define them if we didn't introduce actions?}
 
-	What is unique about the NA game is the structure of the payoffs themselves. In this format,
-	each agent is receives a reference $\sigma$ which is a weighted sum of each of their
+        We can construct the \fb{unit-simplex ?} on the action
+        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
+        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
+        with which agent $\mu$ plays the action $i$. As such we
+        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
+        often referred to as $\mu$'s mixed strategy). Also associated
+        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
+        in which we use the standard notation $-\mu$ to refer to all
+        agents other than $\mu$. Notice that this requires that each
+        agent plays the same strategy against all of their neighbours.
+
+	With all of the above definitions, we can formalise the
+        network aggregative (NA) game:
+
+	\begin{definition}[Network Aggregative Game]
+		A Network Aggregative game is defined as the tuple $\Gamma =
+        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
+        \utility{\mu})_{\mu \in \mathcal{N}})$, where $\agentset$, $\edgeset$, $\weightset$ are as
+        defined in the Interaction graph. $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
+        actions and the utility function of agent $\mu$ respectively..
+	\end{definition}
+
+	What is unique about the NA game is the structure of the
+        payoffs themselves. In this format, each agent is receives a
+        reference $\sigma$ which is a weighted sum of each of their
         neighbours state. Formally
-
+%
 	\begin{equation}
@@
 	Fictitious Play in continuous time.
-
+%
 	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
-		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
+		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and
+		all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in
+		BR_i(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
+	\end{definition}
 
 		We can think of this definition as saying that the player plays some arbitrary strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
-	\end{definition}
 
@@
 		There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
-		BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
+		BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
 	\end{theorem}
@@
 
-	\section{Non-convergent examples}
+	\subsection{Non-convergent examples}
 	The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.
@@
 
-	\section{Addition of Noise}
+	\subsection{Addition of Noise}
 

### 2021-04-23 Documents/FP in NAGs/FPNAG.tex
minor edits

@@
                 zero-sum games and show that Fictitious Play converges
-                to a fixed point, which for a network without any self-loops
+                to a fixed point, which for a simple \fb{define simple} network
                 corresponds to a Nash Equilibrium. In addition, we
@@
                 we experiment the Fictitious Play algorithm on an
-                agent based model for \ah{resource allocation? 
-                voting?}. Finally, our experiments document how noise
+                agent based model for (resource allocation?
+                voting?). Finally, our experiments document how noise
                 affects the convergence of fictitious play, whose
@@
         \agentset$ such that agent $\mu$ and agent $\nu$ are
-        connected. Formally,
-
+        connected.
+        \fb{
           \begin{definition}[Interaction Graph]
@@
 \end{definition}
+}
 
 	As a network game, each agent $\mu$ has an associated set of
-        actions $\actionset{\mu}$ which has cardinality
+        pure strategies $\actionset{\mu}$ which has cardinality
         $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
@@
 
-        We can construct the \fb{unit-simplex ?} on the action
+        Then we can construct the \fb{unit-simplex ?} on this action
         set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
         \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
-        with which agent $\mu$ plays the action $i$. As such we
+        with which agent $\mu$ plays the pure strategy $i$. As such we
         refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
@@
 	With all of the above definitions, we can formalise the
-        network aggregative (NA) game:
-
-	\begin{definition}[Network Aggregative Game]
-		A Network Aggregative game is defined as the tuple $\Gamma =
+        network aggregative (NA) game as the tuple $\Gamma =
         (\agentset, (\edgeset, \weightset), (\actionset{\mu},
-        \utility{\mu})_{\mu \in \mathcal{N}})$, where $\agentset$, $\edgeset$, $\weightset$ are as
-        defined in the Interaction graph. $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
-        actions and the utility function of agent $\mu$ respectively..
-	\end{definition}
+        \utility{\mu})_{\mu \in \mathcal{N}})$. \fb{preferably use a
+          definition environment.}
 
@@
 	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
-		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and
-		all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in
-		BR_i(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
+		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
 	\end{definition}
@@
 		There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
-		BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
+		BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
 	\end{theorem}
@@
 
-	\subsection{Non-convergent examples}
+	\section{Non-convergent examples}
 	The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.
@@
 
-	\subsection{Addition of Noise}
+	\section{Addition of Noise}
 

### 2021-04-23 Code/Fictitious Play/FP in NAGs/FPNAGFunctions.py
Updated Figures

@@ -3,22 +3,22 @@ import matplotlib.pyplot as plt
 import itertools
 import scipy.sparse as sps
 
-def generateGallaGames(gamma, nSim, dim):
-    nElements = dim ** 2  # number of payoff elements in the matrix
-
-    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
-
-    rewardAs, rewardBs = np.eye(dim), np.eye(dim)
-
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
-
-        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((dim, dim))))
-        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((dim, dim))))
-
-    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
+# def generateGallaGames(gamma, nSim, dim):
+#     nElements = dim ** 2  # number of payoff elements in the matrix
+#
+#     cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+#     cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
+#     cov[nElements:, :nElements] = np.eye(nElements) * gamma
+#
+#     rewardAs, rewardBs = np.eye(dim), np.eye(dim)
+#
+#     for i in range(nSim):
+#         rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+#
+#         rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((dim, dim))))
+#         rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((dim, dim))))
+#
+#     return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
 
 # def generateGames(gamma, dim, nAgents):
 #     """
@@ -44,7 +44,7 @@ def generateGallaGames(gamma, nSim, dim):
 #
 #     return np.array(each)
 
-def generateZeroSumNetworkGame(dim, nAgents):
+def generateNetworkGame(dim, nAgents):
 
     G = np.random.randint(0, 10, size=(dim, dim, nAgents))
[…]

### 2021-04-23 Code/Fictitious Play/FP in NAGs/ThreePlayerChain.py

@@ -1,0 +1,59 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import FPNAGFunctions as fpn
+
+def plotOnSimplex(traj, nAgents, nInit):
+    f, ax = plt.subplots(1, nAgents, sharex='all', sharey='all')
+
+    proj = np.array(
+        [[-1 * np.cos(30 / 360 * 2 * np.pi), np.cos(30 / 360 * 2 * np.pi), 0],
+         [-1 * np.sin(30 / 360 * 2 * np.pi), -1 * np.sin(30 / 360 * 2 * np.pi), 1]
+         ])
+
+    ts = np.linspace(0, 1, 10000)
+
+    e1 = proj @ np.array([ts, 1 - ts, 0 * ts])
+    e2 = proj @ np.array([0 * ts, ts, 1 - ts])
+    e3 = proj @ np.array([ts, 0 * ts, 1 - ts])
+
+    for cAgent in range(nAgents):
+
+        ax[cAgent].plot(e1[0], e1[1], 'k')
+        ax[cAgent].plot(e2[0], e2[1], 'k')
+        ax[cAgent].plot(e3[0], e3[1], 'k')
+
+        for i in range(nInit):
+            d = proj @ traj[:, cAgent, i, :]
+            ax[cAgent].plot(d[0], d[1], '--', alpha=0.4)
+        for i in range(nInit):
+            ax[cAgent].scatter(d[0, -1], d[1, -1], color='k', marker='+')
+
+    plt.show()
+
+if __name__ == "__main__":
+    dim = 3
+    nInit = 5
+
+    # Normal Three Player Chain
+    w = 0.2882028455979141
+    W = np.array([[0, 1, 0], [w, 0, 1-w], [0, 1, 0]])
+
+    # Generic Aggregation Matrix
+    # W = fpn.initialiseAggregationMatrix(3)
+
+    # Three Player Chain without the diagonal condition
+
+    # w1, w2, w3 = np.random.rand(), np.random.rand(), np.random.rand()
+    # W = np.array([[w1, 1 - w1, 0], [w2, 0, 1 - w2], [0, w3, 1 - w3]])
+
+    # G = fpn.generateThreePlayerChain(dim, W)
+
+    # Shapley Orbit
+    beta = 0.5756078897829536
+    B = np.array([[-beta, 1, 0], [0, -beta, 1], [1, 0, -beta]])
[…]

### 2021-04-23 Code/Fictitious Play/FP in NAGs/ThreePlayerRing.py

@@ -1,0 +1,50 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import FPNAGFunctions as fpn
+
+def plotOnSimplex(traj, nAgents, nInit):
+    f, ax = plt.subplots(1, nAgents, sharex='all', sharey='all')
+
+    proj = np.array(
+        [[-1 * np.cos(30 / 360 * 2 * np.pi), np.cos(30 / 360 * 2 * np.pi), 0],
+         [-1 * np.sin(30 / 360 * 2 * np.pi), -1 * np.sin(30 / 360 * 2 * np.pi), 1]
+         ])
+
+    ts = np.linspace(0, 1, 10000)
+
+    e1 = proj @ np.array([ts, 1 - ts, 0 * ts])
+    e2 = proj @ np.array([0 * ts, ts, 1 - ts])
+    e3 = proj @ np.array([ts, 0 * ts, 1 - ts])
+
+    for cAgent in range(nAgents):
+
+        ax[cAgent].plot(e1[0], e1[1], 'k')
+        ax[cAgent].plot(e2[0], e2[1], 'k')
+        ax[cAgent].plot(e3[0], e3[1], 'k')
+
+        for i in range(nInit):
+            d = proj @ traj[:, cAgent, i, :]
+            ax[cAgent].plot(d[0], d[1], '--', alpha=0.4)
+        for i in range(nInit):
+            ax[cAgent].scatter(d[0, -1], d[1, -1], color='k', marker='+')
+
+    plt.show()
+
+
+if __name__ == "__main__":
+    dim = 3
+    nInit = 5
+
+    wx = np.random.rand()
+    wy = np.random.rand()
+    wz = np.random.rand()
+    W = np.array([[0, wx, 1 - wx], [wy, 0, 1 - wy], [wz, 1 - wz, 0]])
+
+    beta = np.random.rand()
+    B = np.array([[-beta, 1, 0], [0, -beta, 1], [1, 0, -beta]])
+    A = -W[1, 0] * B.T
+    C = -W[1, 2] * B
+    G = np.dstack((A, B, C))
+
+    strats = fpn.simulate(dim, G, W, 3, nInit=nInit, nIter=1e5, noise=False, sigma=.275)
+    plotOnSimplex(strats, 3, nInit)

### 2021-04-23 Code/Fictitious Play/FP in NAGs/genericGames.py

@@ -1,0 +1,42 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import FPNAGFunctions as fpn
+
+def plotOnSimplex(traj, nAgents, nInit):
+    for cAgent in range(nAgents):
+        f, ax = plt.subplots(1, 1, sharex='all', sharey='all')
+
+        proj = np.array(
+            [[-1 * np.cos(30 / 360 * 2 * np.pi), np.cos(30 / 360 * 2 * np.pi), 0],
+             [-1 * np.sin(30 / 360 * 2 * np.pi), -1 * np.sin(30 / 360 * 2 * np.pi), 1]
+             ])
+
+        ts = np.linspace(0, 1, 10000)
+
+        e1 = proj @ np.array([ts, 1 - ts, 0 * ts])
+        e2 = proj @ np.array([0 * ts, ts, 1 - ts])
+        e3 = proj @ np.array([ts, 0 * ts, 1 - ts])
+
+        ax.plot(e1[0], e1[1], 'k')
+        ax.plot(e2[0], e2[1], 'k')
+        ax.plot(e3[0], e3[1], 'k')
+
+        for i in range(nInit):
+            d = proj @ traj[:, cAgent, i, :]
+            ax.plot(d[0], d[1], '--', alpha=0.6)
+            ax.scatter(d[0, -1], d[1, -1], color='r', marker='+')
+
+        plt.show()
+
+if __name__ == "__main__":
+    dim = 3
+    nAgents = 10
+    nInit = 10
+    W = fpn.initialiseAggregationMatrix(nAgents=10)
+
+    G = fpn.generateNetworkGame(dim, nAgents)
+
+    strats = fpn.simulate(dim, G, W, nAgents, nInit=nInit, nIter=1e5, noise=False, sigma=1.5)
+
+    plotOnSimplex(strats, nAgents, nInit)
+

### 2021-04-23 Code/Fictitious Play/Fictitious Play Payoff Performance/FPOrbit.py

@@ -1,126 +1,0 @@
-def FPOrbit(x0, G, nIter):
-    A, B = G
-    pX, qY = x0[0][:, 0], x0[1][:, 0]
-
-    print(pX.shape)
-
-    dim = np.shape(pX)[0]
-
-    allPX = np.zeros((dim, nIter))
-    allQY = np.zeros((dim, nIter))
-
-    erX, erY = pX.T @ A @ qY, pX.T @ B @ qY
-    allerX, allerY = np.zeros(nIter), np.zeros(nIter)
-
-    for n in tqdm(range(1, int(nIter) + 1)):
-        eX, eY = np.zeros(dim), np.zeros(dim)
-        brX, brY = np.argmax(A @ qY), np.argmax(pX.T @ B)
-        eX[brX] = 1
-        eY[brY] = 1
-
-        pX = (n * pX + eX) / (n + 1)
-        qY = (n * qY + eY) / (n + 1)
-
-        allPX[:, n-1] = pX
-        allQY[:, n-1] = qY
-
-        erX = (n * erX + (pX.T @ A @ qY)) / (n + 1)
-        erY = (n * erY + (pX.T @ B @ qY)) / (n + 1)
-
-        allerX[n-1] = erX
-        allerY[n-1] = erY
-
-    return allPX, allQY, allerX, allerY
-
-def plotOnSimplex(gamma, trajX, trajY):
-    f, (ax) = plt.subplots(1, 2)
-
-    proj = np.array(
-        [[-1 * np.cos(30 / 360 * 2 * np.pi), np.cos(30 / 360 * 2 * np.pi), 0],
-         [-1 * np.sin(30 / 360 * 2 * np.pi), -1 * np.sin(30 / 360 * 2 * np.pi), 1]
-         ])
-
-    ts = np.linspace(0, 1, 10000)
-
-    e1 = proj @ np.array([ts, 1 - ts, 0 * ts])
-    e2 = proj @ np.array([0 * ts, ts, 1 - ts])
-    e3 = proj @ np.array([ts, 0 * ts, 1 - ts])
-
-    ax[0].plot(e1[0], e1[1], 'k-', alpha = 0.3)
-    ax[0].plot(e2[0], e2[1], 'k-', alpha = 0.3)
-    ax[0].plot(e3[0], e3[1], 'k-', alpha = 0.3)
-
[…]

### 2021-04-23 Code/Fictitious Play/Fictitious Play Payoff Performance/nonConvergentPayoffs.py

@@ -1,208 +1,0 @@
-import numpy as np
-import nashpy as nash
-from tqdm import tqdm
-import matplotlib.pyplot as plt
-import os
-
-
-def generateGallaGames(gamma, nSim, dim):
-    nElements = dim ** 2  # number of payoff elements in the matrix
-
-    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
-    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
-    cov[nElements:, :nElements] = np.eye(nElements) * gamma
-
-    rewardAs, rewardBs = np.eye(dim), np.eye(dim)
-
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
-
-        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((dim, dim))))
-        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((dim, dim))))
-
-    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
-
-def initialiseRandomVectors(dim, nInit, nSim):
-    pX = np.dstack([np.random.dirichlet(np.ones(dim), size=(nInit)).T for s in range(nSim)])
-    qY = np.dstack([np.random.dirichlet(np.ones(dim), size=(nInit)).T for s in range(nSim)])
-
-    return pX, qY
-
-def findNE(A, B):
-    rps = nash.Game(A, B)
-    eqs = rps.support_enumeration()
-    return list(eqs)
-
-def sampleFromSimplex(dim, nSamples=1.5e3):
-    nSamples = int(nSamples)
-    return np.random.dirichlet(np.ones(dim), size=nSamples)
-
-def ABar(samples, A, q):
-    return np.max(np.einsum('ni,ijs,jcs->ncs', samples, A, q), axis=0)
-
-def BBar(samples, B, p):
-    return np.max(np.einsum('ics,ijs,nj->ncs', p, B, samples), axis=0)
-
-def simulation(gamma, dim, nSim, nInit, nIter):
-
-    samples = sampleFromSimplex(dim, nSamples=1e4)
-
-    A, B = generateGallaGames(gamma, nSim, dim)
-
[…]

### 2021-04-23 Code/Q-Learning/StabilityandChaos/qUpdater/pPlayers.py

@@ -18,22 +18,21 @@ def generateGames(gamma, nSim, nAct, nPlayers):
     nElements = nAct ** nPlayers  # number of payoff elements in a player's matrix
 
     cov = sps.lil_matrix(sps.eye(nPlayers * nElements))
-    idX = list(itertools.product(list(range(1, nAct + 1)), repeat=nPlayers)) * nPlayers
-    for idx in range(nElements):
-        for b in range(1, nPlayers):
-            rollPlayers = np.where([np.all(idX[i] == np.roll(idX[idx], -1 * b)) for i in range(len(idX))])[0][b]
-            cov[idx, rollPlayers], cov[rollPlayers, idx] = gamma/(nPlayers - 1), gamma/(nPlayers - 1)
 
-    cov = cov.toarray()
+    for i in range(nElements):
+        for p in range(1, nPlayers):
+            cov[i, i + nElements * p] = gamma / (nPlayers - 1)
+            cov[i + nElements * p, i] = gamma / (nPlayers - 1)
 
-    allPayoffs = np.zeros((nPlayers, nElements))
+    allPayoffs = np.zeros((nPlayers, nElements, nSim))
 
-    for i in range(nSim):
-        rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov)
+    for cSim in range(nSim):
+        rewards = np.zeros(nPlayers * nElements) + np.linalg.cholesky(cov.todense()) @ np.random.standard_normal(nPlayers * nElements)
+        # rewards = np.random.multivariate_normal(np.zeros(nPlayers * nElements), cov=cov.todense())
         each = np.array_split(rewards, nPlayers)
-        allPayoffs = np.dstack((allPayoffs, np.array(each)))
+        allPayoffs[:, :, cSim] = each
 
-    return allPayoffs[:, :, 1:]
+    return allPayoffs
 
 def getActionProbs(qValues, gameParams, agentParams):
     

### 2021-04-23 Code/Q-Learning/StabilityandChaos/testFunctions.py

@@ -1,0 +1,43 @@
+import numpy as np
+from qUpdater.pPlayers import generateGames
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import scipy as sps
+from scipy.integrate import odeint
+import itertools
+from tqdm import tqdm
+
+
+def TuylsODE(X0, t, payoffs, agentParams):
+
+	alpha, tau, gamma = agentParams
+
+	x = X0[0:2]
+	y = X0[2:4]
+	# z = X0[4:]
+
+	xdot = np.zeros(2)
+	ydot = np.zeros(2)
+	# zdot = np.zeros(2)
+
+	rewards = np.array([np.sum(np.reshape(payoffs[p], (nAct, nAct**(nPlayers - 1))) * np.array([(np.prod(X[T[np.where(T[:, p] == i + nAct*p)]], axis = 1)/X.reshape((nPlayers, nAct))[p, i]) for i in range(nAct)]), axis = 1) for p in range(nPlayers)])
+
+	xdot[0] = x[0] * tau * (rewards[0, 0] - np.dot(x, rewards[0])) + alpha * x[0] * (x[1] * np.log(x[1]/x[0]))
+	xdot[1] = x[1] * tau * (rewards[0, 1] - np.dot(x, rewards[0])) + alpha * x[1] * (x[0] * np.log(x[0]/x[1]))
+
+	ydot[0] = y[0] * tau * (rewards[1, 0] - np.dot(y, rewards[1])) + alpha * y[0] * (y[1] * np.log(y[1]/y[0]))
+	ydot[1] = y[1] * tau * (rewards[1, 1] - np.dot(y, rewards[1])) + alpha * y[1] * (y[0] * np.log(y[0]/y[1]))
+
+	# zdot[0] = z[0] * tau * (rewards[2, 0] - np.dot(x, rewards[2])) + alpha * z[0] * (z[1] * np.log(z[1]/z[0]))
+	# zdot[1] = z[1] * tau * (rewards[2, 1] - np.dot(x, rewards[2])) + alpha * z[1] * (z[0] * np.log(z[0]/z[1]))
+
+	# return np.hstack((xdot, ydot, zdot))
+	return np.hstack((xdot, ydot))
+nPlayers = 2
+nAct = 2
+
+alpha = 0.1
+tau  = 2
+
+nIter = 1000
+

### 2021-04-23 Code/Q-Learning/ThreeBodyQL/ChakrabortyExpt.py

@@ -1,0 +1,118 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import scipy as sps
+from scipy.integrate import odeint
+from tqdm import tqdm
+
+
+def TuylsChakraborty(X, t, C, agentParams):
+
+    alpha, tau, gamma = agentParams
+
+    x = X[0:2]
+    y = X[2:4]
+    z = X[4:]
+
+    xdot = np.zeros(2)
+    ydot = np.zeros(2)
+    zdot = np.zeros(2)
+
+    xdot[0] = alpha * x[0] * tau * ((C @ z)[0] - np.dot(x, (C @ z))) + alpha * x[0] * (x[1] * np.log(x[1]/x[0]))
+    xdot[1] = alpha * x[1] * tau * ((C @ z)[1] - np.dot(x, (C @ z))) + alpha * x[1] * (x[0] * np.log(x[0]/x[1]))
+
+    ydot[0] = alpha * y[0] * tau * ((C @ x)[0] - np.dot(y, (C @ x))) + alpha * y[0] * (y[1] * np.log(y[1]/y[0]))
+    ydot[1] = alpha * y[1] * tau * ((C @ x)[1] - np.dot(y, (C @ x))) + alpha * y[1] * (y[0] * np.log(y[0]/y[1]))
+
+    zdot[0] = alpha * z[0] * tau * ((C @ y)[0] - np.dot(z, (C @ y))) + alpha * z[0] * (z[1] * np.log(z[1]/z[0]))
+    zdot[1] = alpha * z[1] * tau * ((C @ y)[1] - np.dot(z, (C @ y))) + alpha * z[1] * (z[0] * np.log(z[0]/z[1]))
+
+    return np.hstack((xdot, ydot, zdot))
+
+
+if __name__ == '__main__':
+
+    stopCond = False
+
+    while not stopCond:
+
+        S = np.round(np.random.uniform(low=-1, high=8), 2)
+        T = np.round(np.random.uniform(low= 0, high=9), 2)
+
+        C = np.array([[1, S], [T, 0]])
+
+        if T > 1:
+            if S < 0:
+                case = 1
+            elif S > 0 and S < 1:
+                case = 2
+            elif S > 1 and T > S:
+                case = 3
+            elif S > 1 and T < S:
+                case = 4
+        elif T > 0 and T < 1:
+            if S < 0 and T > S:
+                case = 5
+            elif S > 0 and S < 1 and T > S:
+                case = 6
[…]

### 2021-04-23 Code/Q-Learning/ThreeBodyQL/ThreeBodyFunctions.py

@@ -3,6 +3,14 @@ import matplotlib.pyplot as plt
 from mpl_toolkits.mplot3d import Axes3D
 import scipy as sps
 from scipy.integrate import odeint
+from tqdm import tqdm
+
+def generateRandomGames():
+    
+    C = np.random.multivariate_normal(np.zeros(4), np.eye(4)).reshape((2, 2))
+    Z = np.random.multivariate_normal(np.zeros(4), np.eye(4)).reshape((2, 2))
+    
+    return C, Z
 
 def generateMatchingPennies():
     """
@@ -67,7 +75,7 @@ def simulate(agentParams, nIter = 5e3):
 
     return firstActionTracker
 
-def TuylsODE(X, t, G, agentParams):
+def TuylsZZC(X, t, G, agentParams):
 
     C, Z = G
 
@@ -87,47 +95,167 @@ def TuylsODE(X, t, G, agentParams):
     ydot[0] = alpha * y[0] * tau * ((C @ z)[0] + ((-Z).T @ x)[0] - np.dot(y, (C @ z) + ((-Z).T @ x))) + alpha * y[0] * (y[1] * np.log(y[1]/y[0]))
     ydot[1] = alpha * y[1] * tau * ((C @ z)[1] + ((-Z).T @ x)[1] - np.dot(y, (C @ z) + ((-Z).T @ x))) + alpha * y[1] * (y[0] * np.log(y[0]/y[1]))
 
-    zdot[0] = alpha * z[0] * tau * (((-Z) @ x)[0] + (C.T @ y)[0] - np.dot(z, ((-Z) @ x) + (C.T @ y))) + alpha * z[0] * (z[1] * np.log(z[1]/z[0]))
-    zdot[1] = alpha * z[1] * tau * (((-Z) @ x)[1] + (C.T @ y)[1] - np.dot(z, ((-Z) @ x) + (C.T @ y))) + alpha * z[1] * (z[0] * np.log(z[0]/z[1]))
+    zdot[0] = alpha * z[0] * tau * (((-Z).T @ x)[0] + (C.T @ y)[0] - np.dot(z, ((-Z).T @ x) + (C.T @ y))) + alpha * z[0] * (z[1] * np.log(z[1]/z[0]))
+    zdot[1] = alpha * z[1] * tau * (((-Z).T @ x)[1] + (C.T @ y)[1] - np.dot(z, ((-Z).T @ x) + (C.T @ y))) + alpha * z[1] * (z[0] * np.log(z[0]/z[1]))
 
[…]

### 2021-04-23 Code/Q-Learning/ThreeBodyQL/TwoBodyTests.py

@@ -1,94 +1,11 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from mpl_toolkits.mplot3d import Axes3D
-import scipy as sps
-from scipy.integrate import odeint
 
+alpha = 1
 
-def generateMatchingPennies():
-    """
-    Create Matching Pennies Matrix
-
-    :return:
-    """
-
-    A = np.array([[1, -1], [-1, 1]])
-    B = np.array([[-1, 1], [1, -1]])
-
-    return A, B
-    
-def generate
-    
-def getActionProbs(Q, agentParams):
-    """
-        qValues: nPlayer x nActions x nSim
-        return: nPlayer x nActions x nSim
-        """
-    alpha, tau, gamma = agentParams
-
-    return np.exp(tau * Q) / np.sum(np.exp(tau * Q), axis=1)[:, None]
-
-def getCurrentActions(actionProbs):
-    return [np.random.choice([0, 1], p=actionProbs[p, :]) for p in range(2)]
-
-
-def getRewards(G, bChoice):
-    A, B = G
-
-    rewards = np.zeros(2)
-    rewards[0] = A[bChoice[0], bChoice[1]]
-    rewards[1] = B[bChoice[0], bChoice[1]]
-
-    return rewards
-
-def qUpdate(Q, G, agentParams):
-
-    alpha, tau, gamma = agentParams
-
-    actionProbs = getActionProbs(Q, agentParams)
-    bChoice = getCurrentActions(actionProbs)
-    rewards = getRewards(G, bChoice)
-
-    for p in range(2):
-        Q[p, bChoice[p]] += alpha * (rewards[p] - Q[p, bChoice[p]] + gamma * np.max(Q[p, :]))
-    return Q
-
-def initialiseQ():
-    return np.random.rand(2, 2)
-
-def simulate(agentParams, nIter = 5e3):
-    nIter = int(nIter)
-
-    G = generateMatchingPennies()
-    Q = initialiseQ()
-
-    firstActionTracker = np.zeros((2, nIter))
-
-    for cIter in range(nIter):
-        Q = qUpdate(Q, G, agentParams)
-        firstActionTracker[:, cIter] = getActionProbs(Q, agentParams)[:, 0]
-
[…]

### 2021-04-23 Code/Q-Learning/ThreeBodyQL/fpNetwork.py

@@ -1,72 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-import scipy as sps
-from scipy.integrate import odeint
-from tqdm import tqdm
-
-def generateMatchingPennies():
-    """
-    Create Matching Pennies Matrix
-
-    :return:
-    """
-
-    C = np.array([[1, -1], [-1, 1]])
-    Z = np.array([[2.4, -2], [-2, 2]])
-
-    return C, Z
-
-def initialiseRandomVec():
-    return np.random.dirichlet(np.ones(2), size=(3)).reshape(6)
-
-def FPOrbit(x0, G, nIter):
-    Z, C = G
-
-    x, y, z = x0[0:2], x0[2:4], x0[4:]
-
-    allX = np.zeros((nIter, 6))
-
-    for n in tqdm(range(1, nIter + 1)):
-        eX, eY, eZ = np.zeros(2), np.zeros(2), np.zeros(2)
-        brX = np.argmax(C @ y + C @ z)
-        brY = np.argmax(C.T @ x + Z @ z)
-        brZ = np.argmax((C.T @ x + (-Z).T @ y))
-
-        eX[brX] = 1
-        eY[brY] = 1
-        eZ[brZ] = 1
-
-        x = (n * x + eX) / (n + 1)
-        y = (n * y + eY) / (n + 1)
-        z = (n * z + eZ) / (n + 1)
-
-        allX[n-1] = np.hstack((x, y, z))
-
-    return allX
-
-if __name__ == "__main__":
-    nInit = 5
-    nIter = 1e5
-
-    G = generateMatchingPennies()
-
-    fig = plt.figure()
-    ax = fig.add_subplot(111, projection='3d')
-    ax.set_xlabel('P1')
-    ax.set_ylabel('P2')
-    ax.set_zlabel('P3')
-
-    ax.set_xlim([0, 1])
-    ax.set_ylim([0, 1])
-    ax.set_zlim([0, 1])
-
-    for cInit in range(nInit):
-
-        x0 = initialiseRandomVec()
-        sol = FPOrbit(x0, G, int(nIter))
-
-        ax.plot(sol[:, 0], sol[:, 2], sol[:, 4])
-        ax.scatter(sol[0, 0], sol[0, 2], sol[0, 4], marker='o', color='r')
-
-    plt.show()

### 2021-04-23 Code/Q-Learning/ThreeBodyQL/mixedtests.py

@@ -1,38 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-import scipy as sps
-from scipy.integrate import odeint
-
-def generateMixedTests():
-    """
-    Create Matching Pennies Matrix
-
-    :return:
-    """
-
-    A = np.array([[1, -1], [-1, 1]])
-    B = np.array([[-1, 1], [1, -1]])
-    # C = np.copy([[0.2, -0.2], [-0.2, 0.2]])
-    return A, B, C
-
-def replicatorzcc(X, t, A, B, C):
-
-    x = X[0:2]
-    y = X[2:4]
-    z = X[4:]
-
-    xdot = np.zeros(2)
-    ydot = np.zeros(2)
-    zdot = np.zeros(2)
-
-    xdot[0] = x[0] * ((A @ y)[0] + (B.T @ z)[0] - np.dot(x, (A @ y) + (B.T @ z)))
-    xdot[1] = x[1] * ((A @ y)[1] + (B.T @ z)[1] - np.dot(x, (A @ y) + (B.T @ z)))
-
-    ydot[0] = y[0] * ((B @ z)[0] + (B.T @ x)[0] - np.dot(y, (5*A @ z) + (B.T @ x)))
-    ydot[1] = y[1] * ((5*A @ z)[1] + (B.T @ x)[1] - np.dot(y, (5*A @ z) + (B.T @ x)))
-
-    zdot[0] = z[0] * ((A @ x)[0] + (5*B.T @ y)[0] - np.dot(z, (A @ x) + (5*B.T @ y)))
-    zdot[1] = z[1] * ((A @ x)[1] + (5*B.T @ y)[1] - np.dot(z, (A @ x) + (5*B.T @ y)))
-
-    return np.hstack((xdot, ydot, zdot))

### 2021-04-23 Code/Q-Learning/ThreeBodyQL/simulationJulia.jl

@@ -1,83 +1,0 @@
-using LinearAlgebra
-using Distributions
-using ProgressMeter
-using PyPlot
-
-alpha = 0.05
-tau = 0.1
-gamma = 0.1
-
-agentParams = (alpha, tau, gamma)
-
-
-function generateMatchingPennies()
-    """
-    Create Matching Pennies Matrix
-    """
-
-    A, B = [1 -1; -1 1], [-1 1; 1 -1]
-
-    return A, B
-end
-
-function getActionProbs(qValues, agentParams)
-    """
-    qValues: nPlayer x nActions x nSim
-    return: nPlayer x nActions x nSim
-    """
-    alpha, tau, gamma = agentParams
-
-    return exp.(tau * qValues)./sum(exp.(tau * qValues), dims=2)
-end
-
-function chooseActions(actionProbs)
-    return [rand(Bernoulli(actionProbs[p, 1])) + 1 for p = 1:3]
-end
-
-function initialiseQ()
-    return rand(3, 2)
-end
-
-function getRewards(G, bChoice)
-    A, B = G
-
-    rewards = zeros(3)
-    rewards[1] = A[bChoice[1], bChoice[2]] + B[bChoice[1], bChoice[3]]
-    rewards[2] = B[bChoice[1], bChoice[2]] + A[bChoice[2], bChoice[3]]
-    rewards[3] = A[bChoice[3], bChoice[1]] + B[bChoice[2], bChoice[3]]
-
-    return rewards
-end
-
-function qUpdate!(Q, G, agentParams)
-
-    actionProbs = getActionProbs(Q, agentParams)
-    bChoice = chooseActions(actionProbs)
-    rewards = getRewards(G, bChoice)
-
-    for i = 1:3
-        Q[i, bChoice[i]] += alpha * (rewards[i] - Q[i, bChoice[i]] + gamma * findmax(Q[i, :])[1])
-    end
-
-end
-
-function simulate(nIter = 5e3)
-    nIter = trunc(Int, nIter)
-
-    G = generateMatchingPennies()
-    Q = initialiseQ()
-
-    global firstActionTracker = zeros(3, nIter)
-
-    for cIter = 1:trunc(Int, nIter)
-        qUpdate!(Q, G, agentParams)
-        firstActionTracker[:, cIter] = getActionProbs(Q, agentParams)[:, 1]
-    end
-
-    return firstActionTracker
-end
-
-firstActionTracker = simulate()
-
[…]

### 2021-04-26 Documents/FP in NAGs/FPNAG.tex
Resolved Conflicts

--- 2021-04-23 Documents/FP in NAGs/FPNAG.tex
@@
 
-		\subsection{Related Work}
-					Main articles: 
-					\begin{enumerate}
-						\item Ewerhart (FP in Networks).
-Main difference is in the model we consider - i.e.
-agents only track the aggregate strategy rather than strategies of all neighbours.
-Further, our analysis shows that in non-simple networks, FP still converges to a fixed point, although not an NE.
-						\item Grammatico (NE seeking in NA games).
-Main difference is that we look at the case where the payoffs are bilinear (since in matrix form), so that we need to consider best response correspondences rather than assuming a unique minimiser.
-						\item Perrin (FP in Mean Field Games).
-Main difference is that we assume an underlying communication network rather than assuming that the players play against the entire population (which is a special case of our analysis, in which you assume that all players are connected to each other).
-						\item Sela (FP in one-against-all networks) Similarly, this paper doesn't assume an underlying communication network or any form of weighted communication between the agents.
-					\end{enumerate}
-
-		\section{Preliminaries}
 	\subsection{Network Aggregative Games}
@@
         $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
-        the set of all pairs $(\mu, \nu) \in \agentset \times
-        \agentset$ such that agent $\mu$ and agent $\nu$ are
+        the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
         connected. Formally,
@@
         We can construct the \fb{unit-simplex ?} on the action
-        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
+        set as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
         \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
@@
 		A Network Aggregative game is defined as the tuple $\Gamma =
-        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
-        \utility{\mu})_{\mu \in \mathcal{N}})$, where $\agentset$, $\edgeset$, $\weightset$ are as
-        defined in the Interaction graph. $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
-        actions and the utility function of agent $\mu$ respectively..
+        (I, (\actionset{\mu},
+        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph, $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
+        actions and the utility function of agent $\mu$ respectively.
 	\end{definition}
@@
 	\begin{align}
-		\alpha^i = \frac{1}{t} \int_0^T x^i(t) \, dt & \text{ for $i \in \{1, 2\}$}
+		\alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
 %		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
@@
 	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
-		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and
-		all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in
-		BR_i(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
+		A CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
+		and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
+		BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
 	\end{definition}
@@
 
-	\subsection{Assumption}
+	\subsection{Assumptions}
 

### 2021-04-29 Documents/FP in NAGs/FPNAG.tex
Included Expt

@@
 \newtheorem{assumption}{Assumption}
+\newtheorem*{remark}{Remark}
 
@@
 \newcommand{\xmuaction}[1]{x^{\mu}_{#1}}
+
+\newcommand{\pure}[2]{e^{#1}_{#2}}
 
@@
 		\end{itemize}
-		\item Numerical Experiments \begin{itemize}
+		\item Numerical Experiments + Discussion \begin{itemize}
 			\item Non-convergent examples
@@
 		\end{itemize}
-		\item Discussion of Experiments
 		\item Concluding Remarks
@@
 	\begin{definition}[Interaction Graph]
-  Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset, \weightset))$ such that
+		Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
+		\weightset))$ such that
 		\begin{itemize}
-  \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent $\mu$ is
-        denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in
-        \edgeset\}$.
-    \item $\weightset \in M_N(\mathbb{R})$ is the weighted
-        adjacency matrix whose elements $w^{\mu \nu}$ expresses the
-        importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
+		\item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent
+				$\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in \edgeset\}$.
+			\item $\weightset \in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu
+				\nu}$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
+				\in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
 		\end{itemize}
@@
 
-	As a network game, each agent $\mu$ has an associated set of
-        actions $\actionset{\mu}$ which has cardinality
-        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
-          we define them if we didn't introduce actions?}
-
-        We can construct the \fb{unit-simplex ?} on the action
-        set as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
-        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
-        with which agent $\mu$ plays the action $i$. As such we
-        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
-        often referred to as $\mu$'s mixed strategy). Also associated
-        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
-        in which we use the standard notation $-\mu$ to refer to all
-        agents other than $\mu$. Notice that this requires that each
-        agent plays the same strategy against all of their neighbours.
-
-	With all of the above definitions, we can formalise the
-        network aggregative (NA) game:
+	With the above definition, we can formalise the network aggregative (NA) game:
 
 	\begin{definition}[Network Aggregative Game]
-		A Network Aggregative game is defined as the tuple $\Gamma =
-        (I, (\actionset{\mu},
-        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph, $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
-        actions and the utility function of agent $\mu$ respectively.
+		A Network Aggregative game is defined as the tuple $\Gamma = (I, (\actionset{\mu},
+        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph,
+        $\actionset{\mu}$ and $\utility{\mu}$ refer to $\mu$'s set of actions (with cardinality
+        $|\actionset{\mu}| = n$) and utility function respectively.
 	\end{definition}
 
-	What is unique about the NA game is the structure of the
-        payoffs themselves. In this format, each agent is receives a
-        reference $\sigma$ which is a weighted sum of each of their
-        neighbours state. Formally
+	We consider the \emph{state} of agent $\mu$ to be the probability vector $\xmu \in
+	\mathbb{R}^n$ where $\xmu_i$ is the probability with which the agent plays action $i$. It
+	should be noted that this probability vector is often referred to as $\mu$'s \emph{mixed
+	strategy}. With this in mind, we can construct, as their state space, the unit simplex on
+	agent $\mu$'s action set. This is given as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \,
+	\sum_i \xmuaction{i} = 1\}$. Also associated with each agent is a utility function
+
+	The utility function, for each agent $\mu$, is given as $u^\mu(\xmu, \xnotmu)$ in which we use
+	the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that this requires
+	that each agent play the same strategy against all of their neighbours. What is unique about the
+	NA game is the structure of the payoffs themselves. In this format, each agent is receives a
+	reference $\sigma$ which is a weighted sum of each of their neighbours
+	state. Formally
 %
@@
 
-	Then, the agent's must optimise their payoff with respect to
-        this reference vector. Thus, instead of having to consider the
-        actions of the entire population, or play individual games
-        against each of their neighbours, the agent only has to
-        consider $\sigma^\mu$ as a `measurement' of the local
-        aggregate state and optimise with respect to this
-        measurement. This allows us to make the reduction $u^\mu(\xmu,
-        \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider
-        that the agent is engaged in a matrix game against the
+	Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
+	instead of having to consider the actions of the entire population, or play individual games
+	against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a
+	`measurement' of the local aggregate state and optimise with respect to this measurement.
+	This allows us to make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
+	particular, we consider that the agent is engaged in a matrix game against the
 	reference vector so that
@@
 	\end{equation}
-	where $A^\mu$ is the payoff matrix associated to agent
-        $\mu$. Note that this means we can write the game
-        $\Gamma$ with the payoff matrices $A^mu$ in place of the
-        utility functions $\utility{\mu}$. The NA game allows for the
-        reduction of a multiplayer game into a series of two-player
-        games. The agent's goal is to maximise their payoff with
-        respect to the reference vector. As such, we define the best
-        response correspondence $BR^\mu$ which maps any $\refmu$ the
-        set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
-        leads naturally to the definition of a Nash Equilibrium in an
-        NA Game as
+
+	where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we can write
+	the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
+	$\utility{\mu}$. The NA game allows for the reduction of a multiplayer game into a series of
+	two-player games. The agent's goal is to maximise their payoff with respect to the reference
+	vector. As such, we define the best response correspondence $BR^\mu$ which maps any $\refmu$
+	the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$.
+
+	Finally, a central concept of game theory is that of the Nash Equilibrium, in which no rational
+	agent has the incentive to deviate from their current state. This can be formalised by saying
+	that all agents are playing the best response to each other.
+
+	This leads naturally to the definition of a Nash Equilibrium in an NA Game as
 
@@
 		\begin{equation*}
-		\NE{\mu} \in \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
+		\NE{\mu} \in BR^\mu (\refmu) = \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
 		\end{equation*}	
 	\end{definition}
-        \fb{It this a definition or rather a lemma?}
 
-	We will show that such an equilibrium exists in ....
-Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$.
-Formally
+	\begin{remark}
+		It can be seen that the concept of the Nash Equilibrium in the NA game is a natural
+		extension of the NE in a bimatrix game $(A, B)$. In particular, if we consider an NA game
+		with only two players and no self-loops then the above definition yields
+
+		\begin{equation*}
+			\NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2}), 
+		\end{equation*}
+
+		and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
+	\end{remark}
+
+	We will show that the NE exists for an NA game in Section \ref{sec::ExistenceofNE}.
+
+	Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally
 
@@
 
-	\ah{For Francesco: is it worth giving a quick introduction to Fictitious Play by talking about two player games?}
-\fb{I'd rather give the definition first and then the example.}
+	Fictitious Play requires that, at the current time, each agent considers the average state
+	of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
+	opponent. As such, each agent $\mu$ must update their state according to the time-average of
+	$\refmu$. To formalise this we write
 
-	Fictitious Play requires that, at the current time, each agent
-        considers the average behaviour of their opponent in the past
-        and play a best response to that strategy. This is best
-        illustrated in the two-player setting. Consider the two player
-        normal form game $\Gamma_2 = (\{ 1, 2\}, ((S^1, A), (S^2,
-        B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$
-        and $2$ respectively. As a remark, note that we can write the
-        two player normal form game as an NA game simply by requiring
-        that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2
-        matrix with zeros on its leading diagonal and ones on the off
-        diagonal. We write the time-average of both agents' strategies
-        as
-%
-	\begin{align}
-		\alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
-%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
-	\end{align}
-        \fb{why using an integral rather than a simple summation?}
-
-        \fb{decide whether you start enumerations from 1 or 0.}
-
-	In this manner, the $\alpha^\mu(t)$ denotes the time average of the strategies played by agent
-	$\mu$ up to time $t$. Then, fictitious play requires that the agents update their strategy as
-	$x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in
-	BR^2(\alpha^1(t))$.
-
-	We extend this naturally to the NA game $\Gamma$ by requiring that each agent update their
-	strategy according to the time average of their reference vector $\refmu$. To formalise this, we
-	write
 	\begin{equation}
@@
 
-		We can think of this definition as saying that the player plays some arbitrary strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
+	We can think of this definition as saying that the player plays some arbitrary strategy before
+	$t = 1$, but beyond this it must play a best response to the time average of its reference
+	signal.
+
+	\begin{remark}
+		As an illustration, consider the NA game with two players, in which $\edgeset = \{(1, 2),
+		(2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
+		the off diagonal. We write the time-average of both agents' state as
+
+		\begin{align}
+			\alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
+	%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
+		\end{align}
+
+		In this manner, the $\alpha^\mu(t)$ denotes the time average of the strategies played by
+		agent $\mu$ up to time $t$. Then, fictitious play requires that the agents update their
+		strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
+		seen, therefore, that the CTFP in an NA game is a natural extension of CTFP in the classical
+		two-player setting \cite{}.
+	\end{remark}
 
@@
 		The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
-		that the sum elements in each row of $\weightset$ is equal to one.
+		that the sum elements in each row of $\weightset$ is equal to one. This assumption is
+		made to ensure that the analysis of NA games can be derived as a natural extension to the
+		classical setting of two-player games. We can think of the row stochastic condition as the
+		ability of each agent to prioritise the state information it receives from each of its
+		neighbours. It is also a classical assumption made in the analysis of network games
+		\cite{one of the network game papers} and can is straightforward to implement \cite{Eyad}.
 	\end{assumption}
@@
 	\begin{assumption}
-		The payoffs are given through matrix games and, therefore, are bilinear.
+		The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
+		have a rich history in game theory and has generated a number of prototypical examples for
+		economic study including the Prisoner's Dilemma game (see \cite{Axelrod} for an interesting
+		implementation of this). They also allow for the design of multi-agent systems in
+		computational settings, particularly in the case of task and resource allocation \cite{AGT
+		and some of the Applied Game Theory Papers}. It should be noted, however, that game
+		theoretic analysis is starting to consider various other forms of utility functions,
+		including monotone \cite{Maryam} and convex \cite{Parise}. We believe that the analysis of
+		Fictitious Play should follow in these developments and we consider it as an important area
+		of future work.
 	\end{assumption}
@@
 	\begin{assumption}
-		The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents.
+		\ah{I've been thinking about this a little, and I think it could be the case that
+		we don't need to make this assumption at all. I will investigate this further, since I don't
+		think this assumption has appeared in any of our results.} The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
+		a classical assumption which is made in most game theoretic settings and includes, as a
+		special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
+		in \cite{Ewerhart}, CTFP was analysed without this requirement.  
 	\end{assumption}
@@
 		The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
-		of states $(x^\mu)_{\mu \in N^\mu}$
+		of states $(x^\mu)_{\mu \in N^\mu}$. This is, perhaps, one of the stronger assumptions in
+		our analysis, and is required for the fixed point analysis. However, in Section
+		\ref{sec::CCEConvergence}, we perform a regret analysis that considers the long term
+		behaviour of CTFP without this assumption.
 	\end{assumption}
-
-\fb{discuss how restrictive each of these assumptions is.}
 
@@
 	\subsection{Existence of the Nash Equilibrium}
+	\label{sec::ExistenceofNE}
 
@@
 
-	which is precisely the NA-Nash Equilibrium condition. This leads to the next result
+	which is precisely the Nash Equilibrium condition in the NA game. This leads to the next result
 
@@
 
-	\section{Convergence to the CCE set}
+	\section{CTFP achieves no regret}
+	\label{sec::CCEConvergence}
 
-	In this section we aim to find some convergence structure for the case in which the NA game is not zero-sum.
-In particular, we  show that the NA-CTFP process converges to the set of coarse correlated equilibria.
-So first I will define what this means.
+	In this section we aim to find some convergence structure for the case in which the NA game is
+	not necessarily zero-sum. In particular, we  show that the NA-CTFP process converges to the set
+	of coarse correlated equilibria \cite{}.
 
-	The notion of the CCE set is best considered through \emph{regret} which, for agent $\mu$ we define as
+	\begin{definition}
+		A distribution $\mathcal{D}$ over the joint action set $S = \times_\mu S^\mu$ is
+		called a \emph{coarse correlated equilibrium} (CCE) if, for all $\mu$
 
 		\begin{equation}
-		R^{\mu} = \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\}
+			\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{- \mu})] \hspace{1cm} \forall j \in S^\mu.
+		\end{equation}
+	\end{definition}
+
+	In words, the above definition says that, if the agents are given a probability distribution
+	with which the can play their actions, then the expected payoff, for all agents is greater than
+	or equal to the payoff that they would get by playing any of their other available actions,
+	assuming that the other agents keep to the distribution.
+
+	For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is drawn from a joint probability
+	distribution $\mathcal{D}$, then there is a corresponding set of reference vectors $\sigma =
+	(\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu s^\nu$.
+	Therefore, $\mathcal{D}$ is a probability distribution over all actions and all references.
+	Consider, then, a vector of joint distributions over actions and references which is generated
+	by CTFP. In particular, if by playing with CTFP, the agents reach the state $(\xmu)_{i = 1}^N$
+	with references $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} = (\mathcal{D}^1, ...,
+	\mathcal{D}^N)$ such that $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected payoff
+	that the agent would receive for playing this strategy is
+
+	\begin{align}
+		u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu \nonumber \\
+		& = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
+	\end{align}
+
+	As such, we would say that CTFP has converged to the set of CCE if, in the limit of $t
+	\rightarrow \infty$, we have that for all $\mu$
+
+	\begin{equation}
+		u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu) \hspace{1cm} \forall i' \in S^\mu.
 	\end{equation}
 
-	Note, this is the \emph{average regret} for the agent $\mu$ and, of course, can be related to the \emph{cumulative regret} which is used for analysis in, e.g.
-(Leonardos and Piliouras, Cesa-Bianchi).
-To illustrate the average regret, let us consider the case where each agent has only two actions.
-Then $u^{\mu}(x^\mu(t), \sigma(t))$ is given by
+	\begin{remark}
+		As usual, the notion of CCE in an NA game is a natural extension of the CCE for two player
+		games. In fact, if we consider the NA game to be a two player game with no self-loops, then
+		we recover exactly the definition of the CCE set in two player games \cite{PayoffPerformance}.
+	\end{remark}
+
+	\begin{remark}
+		The notion of the CCE set is related to the idea of \emph{average external regret} (for the
+		sake of brevity we drop the term `external' and refer the reader to \cite{AGT}). Here, we
+		will present what is meant by average regret and state that if at some time $T$ all agents'
+		average regret is non-positive, then the game is said to have reached the CCE set. The
+		reader should consult \cite{PayoffPerformance} for an excellent exposition regarding the
+		link between the CCE set and average regret in two player games which, of course, extends
+		naturally to the NA game.
+
+		Average regret, for agent $\mu$ is defined as
+
+		\begin{equation}
+			R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(\pure{\mu}{i'}, \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\},
+		\end{equation}
+
+		in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
+		$i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
+		and, of course, can be related to the \emph{cumulative regret} which is used for analysis
+		in \cite{Leonardos and Piliouras, Cesa-Bianchi}.  To illustrate the average regret, let us
+		consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
+		is given by
 
@@
 
-	On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(x_{i'}^\mu(t), \sigma(t))$, then
+		On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(\pure{\mu}{1}, \sigma(t))$, then
 
 		\begin{equation}
-		\max_{x_{i'}^\mu \in S^\mu} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu
+			u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
 		\end{equation}
@@
 An agent achives \emph{no regret} if $R^\mu$ is non-positive.
-	% \begin{definition}[Coarse Correlated Equilibrium]
-	% 	A distribution $D$ over action profiles $\times_{\mu} A^{\mu}$ is a \emph{coarse correlated
-	% 	equilibrium} if, for
-	% 	all players $\mu$ and
-	% 	all
-	% 	actions $i' \in A^{\mu}$
-
-	% 	\begin{equation}
-	% 		\mathbb{E}_{a \sim D}[u^{\mu}(a)] \geq \mathbb{E}_{a \sim D}[u^{\mu}(a^\mu_{i'}, a
-	% 		^{- \mu})]
-	% 	\end{equation}
-
-	% \end{definition}
+	\end{remark}
 
 	\begin{theorem}
-		Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the NA-FP process achieve zero regret in the limit, i.e.
+		Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the
+		CTFP process achieve \emph{no regret} in the limit $t \rightarrow \infty$, i.e.
 		\begin{equation}
@@
 		\end{equation}
+
+		In particular, CTFP in an NA game converges to the set of CCE.
 
@@
 
-		Then, applying the \emph{envelope theorem} we have
+		Then, applying the \emph{envelope theorem} \cite{} we have
 
@@
 
-		\ah{Note: I'm just figuring out how best to formulate the notion of the NA-CCE set and then I can add it in as a definition to say that NA-CTFP converges to this set.}
 	\end{proof}
@@
 
-	The fictitious play process in NA games requires that, at each time step, an agent takes a `measurement' of the aggregate strategy of its neighbours.
-It is on this measurement that they update their own strategy.
-It stands to reason that, in real environments, this measurement may be corrupted by noise.
-As such, we investigate the effect that introducing noise has on CTFP in a zero-sum NA game.
+	The fictitious play process in NA games requires that, at each time step, an agent takes a
+	`measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
+	update their own strategy. It stands to reason then, that in real environments this measurement
+	may be corrupted by noise. As such, we investigate the effect that introducing noise has on CTFP
+	in a zero-sum NA game.
 
-	\ah{To discuss with F before including in the document}.
+	Noisy Experiments
+	\begin{enumerate}
+		\item Large (p = 20) game with noise, vary the amount of noise to see at what point we break
+		convergence. Main questions: \begin{itemize}
+			\item At what point do we stop reaching the NE?
+			\item Does it start converging to something else, or just go haywire?
+			\item Would increasing the number of iterations make it converge again?
+		\end{itemize}
 
-	\section{Discussion}
+		\item 3 Player chain. Vary the amount of noise to see the qualitative change in behaviour.
+		Main questions \begin{itemize}
+			\item At what point does periodic behaviour break?
+			\item Do we actually always converge towards the NE?
+			\item Does this happen for all periodic behaviour?
+		\end{itemize}
+	\end{enumerate}
 

### 2021-04-29 Documents/FP in NAGs/neurips_2020.tex
Included NeurIPS version

--- 2021-04-29 Documents/FP in NAGs/FPNAG.tex
@@
 \documentclass{article}
-\usepackage[margin=2cm]{geometry}
+
+% if you need to pass options to natbib, use, e.g.:
+%     \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading neurips_2020
+
+% ready for submission
+% \usepackage{neurips_2020}
+
+% to compile a preprint version, e.g., for submission to arXiv, add add the
+% [preprint] option:
+%     \usepackage[preprint]{neurips_2020}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+    % \usepackage[final]{neurips_2020}
+
+% to avoid loading the natbib package, add option nonatbib:
+     \usepackage[nonatbib]{neurips_2020}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+
 \usepackage{amsmath, amsfonts, amsthm}
@@
 \title{Fictitious Play in Network Aggregative Games}
-\author{AH, FB}
+
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to LaTeX to determine where to break the
+% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
+% authors names on the first line, and the last on the second line, try using
+% \AND instead of \And before the third author name.
+
+\author{%
+ Aamal Hussain  \\
+  Department of Computing\\
+  Imperial College London\\
+  South Kensington, London \\
+  \texttt{aamal.hussain15@imperial.ac.uk} \\
+  % examples of more authors
+  \And
+  Francesco Belardinelli
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \AND
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+  % \And
+  % Coauthor \\
+  % Affiliation \\
+  % Address \\
+  % \texttt{email} \\
+}
 
@@
 
-	\section{Paper Structure}
+\begin{abstract}
+  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
+  both the left- and right-hand margins. Use 10~point type, with a vertical
+  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
+  bold, and in point size 12. Two line spaces precede the abstract. The abstract
+  must be limited to one paragraph.
+\end{abstract}
 
-	\begin{enumerate}
-		\item Introduction: Explain the notion of a Network Aggregative Game, and Fictitious Play
-		with literature on the state of the art. Assumptions made as well as summary of results
-		\item Maybe? Relation with the model of Grammatico
-		\item Preliminaries \begin{itemize}
-			\item The Network Aggregative Game model
-			\item Fictitious Play, as well as the CTFP property
-		\end{itemize}
-		\item Convergence of Fictitious Play \begin{itemize}
-			\item Existence of the Nash Equilibrium
-			\item Existence of a CTFP
-			\item Convergence of CTFP to a fixed point
-			\item Corrolary: when $w_{ii} = 0$ (i.e. the interaction graph is simple) CTFP converges
-			to a NE
-			\item Convergence of CTFP to the NA-CCE set
-		\end{itemize}
-		\item Numerical Experiments + Discussion \begin{itemize}
-			\item Non-convergent examples
-			\item Fictitious Play with Noise
-		\end{itemize}
-		\item Concluding Remarks
-	\end{enumerate}
-
-	\newpage
 \section{Introduction}
@@
 
-		The main contribution of this work is to study the
-                behaviour of the Fictitious Play Learning Algorithm,
-                in continuous time, when applied on a Network
-                Aggregative Matrix Game.
-\fb{why FP and NAG are important?}
+  The main contribution of this work is to study the behaviour of the Fictitious Play Learning
+  Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game. \fb{why FP and NAG are important?}
 
-                We first show that a Nash
-                Equilibrium exists and that Fictitious Play admits
-                solutions in this setting. In particular, we study
-                zero-sum games and show that Fictitious Play converges
-                to a fixed point, which for a network without any self-loops
-                corresponds to a Nash Equilibrium. In addition, we
-                find that, for games which are not zero-sum, agents
-                following Continuous Time Fictitious Play are able to
+  We first show that a Nash Equilibrium exists and that Fictitious Play admits
+  solutions in this setting. In particular, we study zero-sum games and show that
+  Fictitious Play converges to a fixed point, which for a network without any
+  self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
+  which are not zero-sum, agents following Continuous Time Fictitious Play are able to
   achieve no regret.
 
-		Finally, we explore the Fictitious Play algorithm
-                through numerical simulations to understand how
-                convergence rates depend on the network size and
-                connectivity. We also show that it does not
-                necessarily converge for more complex games and can,
-                in fact, lead to more complex dynamics. In addition,
-                we experiment the Fictitious Play algorithm on an
-                agent based model for \ah{resource allocation? 
-                voting?}. Finally, our experiments document how noise
-                affects the convergence of fictitious play, whose
-                theoretical analysis we point out as an interesting
-                direction for future work.
+  Finally, we explore the Fictitious Play algorithm through numerical simulations to understand
+  how convergence rates depend on the network size and connectivity. We also show that it does not
+  necessarily converge for more complex games and can, in fact, lead to more complex dynamics. In
+  addition, we experiment the Fictitious Play algorithm on an agent based model for \ah{resource
+  allocation?  voting?}. Finally, our experiments document how noise affects the convergence of
+  fictitious play, whose theoretical analysis we point out as an interesting direction for future
+  work.
 
-		\ah{Possible additions: 1) Show that the flow is
-                  unique almost everywhere in CTFP. 2) Show the same
-                  results (i.e. existence and convergence) for
-                  Discrete Time Fictitious Play.}
+  \ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the
+  same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}
 
+\section{Preliminaries}
 \subsection{Network Aggregative Games}
@@
 
+\subsection{Convergence of CTFP}
+
 With the existence of the CTFP in place, we can show that it converges to a fixed point.
@@
     \centering
-		\includegraphics[width = 0.7\textwidth]{Figures/nonconvergentShapley.png}
+    \includegraphics[width = 0.7\textwidth]{Figures/nonConvergentShapley.png}
     \caption{\label{fig::nonconvergentShapley}}
@@
   \subsection{Addition of Noise}
+
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width = \columnwidth]{Figures/Noise10Player.png}
+    \caption{\label{fig::Noise10Player}}
+  \end{figure}
+
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
+    \caption{\label{fig::Noise10Player}}
+  \end{figure}
 
@@
 \section{Concluding remarks}
+
+\section*{Broader Impact}
+
+Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
+Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
+who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
+biases in the data. If authors believe this is not applicable to them, authors can simply state this.
+
+Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}
+
+\begin{ack}
+Use unnumbered first level headings for the acknowledgments. All acknowledgments
+go at the end of the paper before the list of references. Moreover, you are required to declare 
+funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work). 
+More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2020/PaperInformation/FundingDisclosure}.
+
+Do {\bf not} include this section in the anonymized submission, only in the final paper.
+You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
+\end{ack}
+
+\section*{References}
+
+References follow the acknowledgments. Use unnumbered first-level heading for
+the references. Any choice of citation style is acceptable as long as you are
+consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
+when listing the references.
+{\bf Note that the Reference section does not count towards the eight pages of content that are allowed.}
+\medskip
+
+\small
+
+[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
+connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
+(eds.), {\it Advances in Neural Information Processing Systems 7},
+pp.\ 609--616. Cambridge, MA: MIT Press.
+
+[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
+  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
+TELOS/Springer--Verlag.
+
+[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
+recall at excitatory recurrent synapses and cholinergic modulation in rat
+hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
+
 \end{document}

### 2021-05-05 Documents/FP in NAGs/neurips_2020.tex
Updated NeurIPS
added stylefile

@@
 
-  Note that the NE Condition requires
-
+  Note that the NE Condition requires \fb{why?}
+%
   \begin{align}
@@
 
-  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$. Note that, in order to get this
-  formulation, we had to use the assumption of payoffs being bilinear so that we could separate
-  out the term in the weighted sum involving $x$ from $\bar{x}^\nu$.
+  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$. Note
+  that, in order to get this formulation, we had to use the assumption
+  of payoffs being bilinear so that we could separate out the term in
+  the weighted sum involving $x$ from $\bar{x}^\nu$.
 
@@
   \begin{definition}[Upper Semi-Continuous]
-    A compact-valued correspondence $\Phi: A \rightarrow B$ is \emph{upper semi-continuous} at a point $a$ if $g(a)$ is non-empty and if, for every sequence $a_n \rightarrow a$ and every sequence $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a convergent subsequence of $(b_n)$ whose limit point $b$ is in $g(a)$.
+    A compact-valued correspondence $\Phi: A \rightarrow B$ is
+    \emph{upper semi-continuous} at a point $a$ \fb{domain?} if $g(a)$ \fb{what is $g$?} is non-empty
+    and if, for every sequence $a_n \rightarrow a$ and every sequence
+    $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a
+    convergent subsequence of $(b_n)$ whose limit point $b$ is in
+    $g(a)$.
   \end{definition}
+
+  \fb{perhaps we have to introduce some terminology from topology to keep the results self-contained?}
 
@@
 
-    This means that we achieve a Nash Equilibrium iff $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the map
+    This means that we achieve a Nash Equilibrium iff $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the map \fb{why?}
 
@@
   \begin{theorem}
-    There exists a path $m$ which satisfies the property that, for all $\mu$, $m^\mu \in
+    There exists a path $m$ which satisfies the property that, for all $\mu$ \fb{remind what this is.}, $m^\mu \in
     BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
@@
 
-With the existence of the CTFP in place, we can show that it converges to a fixed point.
-In particular, let $\Omega(\alpha)$ be the set of all limit points for $\alpha(t)$.
-Then, a CTFP path is said to have converged if $\Omega(\alpha)$ is contained within the set of Nash Equilibria of the game.
-If this is for any such CTFP path, then the game is said to have the \emph{CTFP property}.
-We adapt the techniques of (Ewerhart 2020) to prove that zero-sum NA games have the CTFP property.
-\ah{I also want to attempt this with the techniques of Harris (which is quite similar) to see if it yields any new results}.
+With the existence of the CTFP in place, we can show that it converges
+to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
+all limit points for $\alpha(t)$. Then, a CTFP path is said to have
+converged if $\Omega(\alpha)$ is contained within the set of Nash
+Equilibria of the game. If this is for any such CTFP path, then the
+game is said to have the \emph{CTFP property}. We adapt the techniques
+of (Ewerhart 2020) to prove that zero-sum NA games have the CTFP
+property. \ah{I also want to attempt this with the techniques of
+  Harris (which is quite similar) to see if it yields any new
+  results}.
 
@@
 
+   \fb{what is the meaning of the following equation?}
+%
     \begin{equation}
@@
 
-    where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m) =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined by Ewerhart.
-We can, therefore, think of the NA game as a network game in which each agent plays the same strategy against each of its neighbours, itself included.
-As such, any $m$ which satisfies the CTFP property for the equivalent network game also satisfies the CTFP requirement for the network aggregative game.
+    where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m)
+    =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined by Ewerhart \fb{use the reference rather than the name of the author.}. We
+    can, therefore, think of the NA game as a network game in which
+    each agent plays the same strategy against each of its neighbours,
+    itself included. As such, any $m$ which satisfies the CTFP
+    property for the equivalent network game also satisfies the CTFP
+    requirement for the network aggregative game.
 
@@
 
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoNoise.png}
+    \caption{\label{fig::Noise10Player}}
+  \end{figure}
+
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoise.png}
+    \caption{\label{fig::Noise10Player}}
+  \end{figure}
+
   The fictitious play process in NA games requires that, at each time step, an agent takes a

### 2021-05-06 Documents/FP in NAGs/neurips_2020.tex
added stylefile

@@
 
-  In this section we aim to find some convergence structure for the case in which the NA game is
-  not necessarily zero-sum. In particular, we  show that the NA-CTFP process converges to the set
-  of coarse correlated equilibria \cite{}.
-
+  In this section we aim to find some convergence structure for the
+  case in which the NA game is not necessarily zero-sum. In
+  particular, we show that the NA-CTFP process converges to the set of
+  coarse correlated equilibria \cite{}.
+  %
   \begin{definition}
-    A distribution $\mathcal{D}$ over the joint action set $S = \times_\mu S^\mu$ is
-    called a \emph{coarse correlated equilibrium} (CCE) if, for all $\mu$
-
-    \begin{equation}
-      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{- \mu})] \hspace{1cm} \forall j \in S^\mu.
+    A distribution $\mathcal{D}$ over the joint action set $S =
+    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
+    (CCE) if, for all $\mu$
+    \begin{equation}
+      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
+      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
+          \mu})] \hspace{1cm} \forall j \in S^\mu.
     \end{equation}
@@
 
-  In words, the above definition says that, if the agents are given a probability distribution
-  with which the can play their actions, then the expected payoff, for all agents is greater than
-  or equal to the payoff that they would get by playing any of their other available actions,
-  assuming that the other agents keep to the distribution.
-
-  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is drawn from a joint probability
-  distribution $\mathcal{D}$, then there is a corresponding set of reference vectors $\sigma =
-  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu s^\nu$.
-  Therefore, $\mathcal{D}$ is a probability distribution over all actions and all references.
-  Consider, then, a vector of joint distributions over actions and references which is generated
-  by CTFP. In particular, if by playing with CTFP, the agents reach the state $(\xmu)_{i = 1}^N$
-  with references $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} = (\mathcal{D}^1, ...,
-  \mathcal{D}^N)$ such that $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected payoff
-  that the agent would receive for playing this strategy is
+  In words, the above definition says that, if the agents are given a
+  probability distribution with which they can play their actions, then
+  the expected payoff, for all agents is greater than or equal to the
+  payoff that they would get by playing any of their other available
+  actions, assuming that the other agents keep to the distribution.
+
+  \fb{perhaps what is below could go into a theorem/lemma.}
+
+  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ \fb{$s$ is normally used for actions} is
+  drawn from a joint probability distribution $\mathcal{D}$, then
+  there is a corresponding set of reference vectors $\sigma =
+  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
+    N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
+  distribution over all actions and all references.  Consider, then, a
+  vector of joint distributions over actions and references which is
+  generated by CTFP. In particular, if by playing with CTFP, the
+  agents reach the state $(\xmu)_{i = 1}^N$ with references
+  $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} =
+  (\mathcal{D}^1, ..., \mathcal{D}^N)$ such that
+  $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
+  payoff that the agent would receive for playing this strategy is
 
@@
 As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time.
-An agent achives \emph{no regret} if $R^\mu$ is non-positive.
+An agent achieves \emph{no regret} if $R^\mu$ is non-positive.
   \end{remark}
@@
 
-    For any agent $\mu$ define
+    For any agent $\mu$ define \fb{what are we defining here?}
     \begin{equation}
@@
 
-    We insert this into the previous equation to yield
+    We insert this \fb{use enumeration} into the previous equation to yield
 

### 2021-05-06 Documents/FP in NAGs/neurips_2020.tex
Updated sty file and Introduction

--- 2021-04-29 Documents/FP in NAGs/neurips_2020.tex
@@
 %     \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2020
+% before loading neurips_2021
 
 % ready for submission
-% \usepackage{neurips_2020}
+\usepackage{neurips_2021}
 
@@
 % [preprint] option:
-%     \usepackage[preprint]{neurips_2020}
+%     \usepackage[preprint]{neurips_2021}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-    % \usepackage[final]{neurips_2020}
+%     \usepackage[final]{neurips_2021}
 
 % to avoid loading the natbib package, add option nonatbib:
-     \usepackage[nonatbib]{neurips_2020}
+%    \usepackage[nonatbib]{neurips_2021}
 
@@
 \usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
 \usepackage{microtype}      % microtypography
+\usepackage{xcolor}         % colors
 
 \usepackage{amsmath, amsfonts, amsthm}
-\usepackage{xcolor}
 \usepackage{enumerate}
 \usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 
+Multi Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
+each agent must adapt in response to the behaviour of the other agents. This leads to a
+fundamentally non-stationary problem, which presents a challenge to designing effective learning
+policies. Even when there are a small number of agents in the game, learning has been shown to lead
+to non-stationary, and even chaotic behaviour \cite{SatoChaos}, and this problem becomes even more
+pronounced as the number of agents increase \cite{Sanders}. In this light, it would appear that
+learning when there is a large population of agents is an impossible task.
+
+To deal with this problem, one must attempt to reduce the many player game to something which is
+tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
+and \emph{Aggregative} Games. The former makes the assumption of an infinite
+number of agents, so that the population can be represented through a distribution over players'
+states \cite{CainesPaper} . Every agent then updates their action profiles depending on this
+distribution. In the latter each agent plays considers a real valued function which is a convex
+combination of the states of the other agents. In both formulations, a many player game is reduced
+to the set of two player games which each agent is involved in, allowing the problem to maintain
+tractability.
+
+Whilst both formulations have shown success in multi-agent learning settings, allowing agents to
+reach equilibrium strategies (c.f. \cite{MFGLearningPapers} for Mean Field Games and
+\cite{Aggregative Papers} for Aggregative Games), they also present a fundamental limitation.
+Namely, they both require that agents have access to the action profiles of the entire population.
+This could be through communication with all other agents, or through the intervention of a central
+coordinator who is able to the entire population. Whilst recent work aims to relax this assumption
+through the introduction of noise \cite{MFG-FP} or partial observability \cite{AAMASPaper}, the
+requirement that each agent updates their actions based on the entire population is rather strong.
+
+In this study, we investigate a variant of the aggregative game known as the \emph{Network
+Aggregative} (NA) Game. This format assumes that there is an underlying communication network
+through which agents interact. Then each agent updates their actions according only to those agents
+with whom they communicate. This significantly relaxes the communication load on each agent and
+lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
+for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Grammatico,
+LeaderFollower, MyopicAgents}. We contribute in this direction by showing that learning on an NA
+game can lead to an equilibrium strategy. In particular, we analyse the Fictitious Play Learning
+Algorithm \cite{Brown, Harris}, in which agents are assumed to be myopic, in that they react solely
+to the previous behaviour of the others.
+
 \subsection{Contributions}
 
-  The main contribution of this work is to study the behaviour of the Fictitious Play Learning
-  Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game. \fb{why FP and NAG are important?}
-
-  We first show that a Nash Equilibrium exists and that Fictitious Play admits
+  The main contribution of this work is to study the behaviour of the Fictitious Play (FP) learning
+  algorithm, in continuous time, when applied on a Network Aggregative Matrix Game.
+
+  We first show that a Nash Equilibrium exists and that FP admits
   solutions in this setting. In particular, we study zero-sum games and show that
@@
   self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
-  which are not zero-sum, agents following Continuous Time Fictitious Play are able to
+  which are not zero-sum, agents following Fictitious Play are able to
   achieve no regret.
 
-  Finally, we explore the Fictitious Play algorithm through numerical simulations to understand
-  how convergence rates depend on the network size and connectivity. We also show that it does not
-  necessarily converge for more complex games and can, in fact, lead to more complex dynamics. In
-  addition, we experiment the Fictitious Play algorithm on an agent based model for \ah{resource
-  allocation?  voting?}. Finally, our experiments document how noise affects the convergence of
-  fictitious play, whose theoretical analysis we point out as an interesting direction for future
-  work.
-
-  \ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the
-  same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}
+  Finally, we explore FP through numerical simulations to consider the
+  question of whether it always converges. We answer this in the negative by finding a family of
+  games in which action profiles cycle around the Nash Equilibrium. Finally, our experiments
+  document how noise affects the convergence of Fictitious Play. Our experiments suggest that, under
+  the presence of noise, the algorithm still reaches a fixed point, but perhaps not the Nash
+  Equilibrium. This presents an interesting avenue for future research.
+
+\subsection{Related Work}
+
+\paragraph{Network Aggregative Games}
+
+The NA game is a recent introduction \cite{Parise2015} which presents a variant of aggregative games
+by adding an underlying structure to the population. Since its introduction, distributed algorithms
+have been built with the aim of finding NE. In particular, \cite{Parise2015, Parise2020} consider
+the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
+topological fixed point towards designing algorithms which will converge to the NE. We note that the
+\emph{Mann Iteration}, one of the algorithms applied in \cite{Parise2020} shares a remarkably
+similar form with the discrete variant of FP. To the best of our knowledge, this link has not been
+explored in the literature and is an avenue for research which we are currently pursuing. Another
+common algorithm for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
+which is explored in \cite{Zhang2020} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
+the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
+common assumption in works concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due to
+its ubiquity in control settings. We have not yet come across works which consider NA games from the
+point of view of payoff matrices, which are more common in multi agent learning settings.
+Furthermore, to the best of our knowledge, this is the first work which introduces the application
+of a strict learning algorithm in the NA setting.
+
+\paragraph{Fictitious Play}
+
+Fictitious Play was introduced by Brown in 1951 \cite{BrownPublished, BrownUnpublished} as a
+'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
+time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
+\cite{Robinson}. Since then a number of proofs of convergence were determined in 2 player games
+\cite{Miyasawa, Polak, Berger, Monderer and Sela, Monderer and Shapley}, as well as corresponding
+convergence rates \cite{Harris, Shapiro}. Many results hold for both the discrete and continuous
+variants of FP. Their relation was finally solved by Hofbauer \cite{Hofbauer}, who showed that
+attractors of the discrete time process are also attractors for the continuous time variant. As
+such, most of the analysis on FP focuses on the continuous time variant \cite{Ostrovski}. It was
+later shown in \cite{Shapley} that there is a family of games (now called the \emph{Shapley family})
+for which FP does not converge at all but rather shows periodic behaviour. This led to research
+which looks at this non convergent behaviour, specifically showing the existence of more periodic
+orbits as well as chaotic behaviour \cite{Sparrow}. However, the work looking at fictitious play
+where there are more than two agents is sparse. \cite{Sela} considers a game in which a multi-player
+game is decomposed by requiring that each agent engage in a two person game against each of the
+opponent. Their payoff is given by the sum of payoffs in all of these subgames. It was found that,
+if this game is zero sum, then FP will converge. Similar results for more than two players were
+found for games with identical interests in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
+of FP was considered in a Mean Field Game, and it was found again that the algorithm converges for
+zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
+and Valkanova in 2020 \cite{Ewerhart} in which they showed that fictitious play converges in network
+games, where each agent is engaged in a two-player game with each of their neighbours. The rate of
+convergence was found to be independent of the network size.  Our work extends the analysis of FP in
+multiplayer games by considering its action in NA Games, so that the agents do not play individual
+games against each of their neighbours but rather a single game against the aggregate of their
+neighbours. In particular we also extend a result for two player games found by Ostrovski and van
+Strein \cite{Payoff Performance} which showed that FP achieves no-regret to the multi-player
+setting.
 
@@
   \begin{assumption}
-    \ah{I've been thinking about this a little, and I think it could be the case that
-    we don't need to make this assumption at all. I will investigate this further, since I don't
-    think this assumption has appeared in any of our results.} The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
+    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
     a classical assumption which is made in most game theoretic settings and includes, as a
@@
 
-    Continuing with this approach, let us look at the case where $\sum_\mu A^\mu = \textbf{0}_{n\times n}$ (i.e.
-a zero sum game).
-This means that $\sum_i u_i = 0$.
-Let $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$.
-More specifically, $\xmu_\infty$ belongs to the set of accumulation points of $\alpha^\mu(\cdot; m)$ (which is set valued since the $BR^\mu$ map is set valued).
-To say that the game has `converged' we require that every $\xmu_\infty = (x^1_\infty, ...
-x^N_\infty)$ is an NE.
-\ah{I'll follow through the proof of Ewerhart for the sake of completeness: }
+    Continuing with this approach, let us look at the case where $\sum_\mu A^\mu =
+    \textbf{0}_{n\times n}$ (i.e. a zero sum game). This means that $\sum_i u_i = 0$. Let
+    $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$. More specifically, $\xmu_\infty$
+    belongs to the set of accumulation points of $\alpha^\mu(\cdot; m)$ (which is set valued since
+    the $BR^\mu$ map is set valued). To say that the game has `converged' we require that every
+    $\xmu_\infty = (x^1_\infty, ... x^N_\infty)$ is an NE. Under these conditions, we may adapt the
+    techniques of (\cite{Ewerhart} Prop. 1) to show convergence.
 
@@
 
-  \subsection{Non-convergent examples}
+  \subsection{Non-convergent examples} \label{sec::NonConv}
   The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.
@@
     \centering
-    \includegraphics[width = 0.7\textwidth]{Figures/convergentShapley.png}
+    \begin{subfigure}[b]{0.4 \textwidth}
+      \includegraphics[width = \textwidth]{Figures/convergentShapley.png}
     \caption{\label{fig::convergentShapley}}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.4 \textwidth}
+      \includegraphics[width = \textwidth]{Figures/nonConvergentShapley.png}
+      \caption{\label{fig::nonconvergentShapley}}
+    \end{subfigure}
+    \caption{\label{fig::Shapley}}
   \end{figure}
@@
     \centering
-    \includegraphics[width = 0.7\textwidth]{Figures/nonConvergentShapley.png}
-    \caption{\label{fig::nonconvergentShapley}}
+    \includegraphics[width = 0.7 \textwidth]{Figures/3PlayerChainNoNoise.png}
+    \caption{\label{fig::3PlayerChainNoNoise}}
   \end{figure}
@@
     \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
-    \caption{\label{fig::Noise10Player}}
+    \caption{\label{fig::Noise20Player}}
+  \end{figure}
+
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoise.png}
+    \caption{\label{fig::3PlayerChainNoise}}
   \end{figure}
@@
   update their own strategy. It stands to reason then, that in real environments this measurement
-  may be corrupted by noise. As such, we investigate the effect that introducing noise has on CTFP
-  in a zero-sum NA game.
-
-  Noisy Experiments
-  \begin{enumerate}
-    \item Large (p = 20) game with noise, vary the amount of noise to see at what point we break
-    convergence. Main questions: \begin{itemize}
-      \item At what point do we stop reaching the NE?
-      \item Does it start converging to something else, or just go haywire?
-      \item Would increasing the number of iterations make it converge again?
-    \end{itemize}
-
-    \item 3 Player chain. Vary the amount of noise to see the qualitative change in behaviour.
-    Main questions \begin{itemize}
-      \item At what point does periodic behaviour break?
-      \item Do we actually always converge towards the NE?
-      \item Does this happen for all periodic behaviour?
-    \end{itemize}
-  \end{enumerate}
+  may be corrupted by noise.
+
+  As such, we investigate the effect that introducing additive noise has
+  on CTFP in a zero-sum NA game. We do this in the following manner: at each time step, the
+  reference signal $\refmu(t)$ is adjusted to $\refmu + \gamma \xi$ where $\xi$ is drawn from the
+  standard normal distribution (zero mean and unit variance). By varying $\gamma$, we vary the
+  strength of the noise. We vary $\gamma$ up to $0.5$ since, above this value, noisy measurements
+  are likely to lie outside of the simplex. Since $\refmu$ is constrained to lie within $\Delta$, we
+  can consider the range $\gamma \in [0, 0.5]$ to be the \emph{physical region}, in which noise is meaningful.
+
+  In Figure \ref{fig::Noise10Player}, we consider a zero-sum NA game with 10 players. When there is
+  no noise, it can be seen that FP reaches a fixed point which, since we set $w^{\mu \mu} = 0$,
+  corresponds to an NE. After increasing $\gamma$, however, we find that the agents no longer
+  converge to this NE, but rather shift away from it. What is interesting, however, is that the
+  orbits do still reach a stationary state in the long run which suggests that FP is still able to
+  converge with the introduction of noise. Figure \ref{fig::Noise20Player} shows similar behaviour
+  for $N = 20$, and in our experiments we found this to be ubiquitous regardless of the choice of
+  $N$ or $n$.
+
+  In Figure \ref{fig::3PlayerChainNoise} we revisit the Three Player Chain of Section
+  \ref{sec::NonConv}, now under the influence of additive noise. For the sake of brevity, we only
+  display the distance to the Nash Equilibrium of the first player's action, since the other agents
+  behave in the same way. It can be seen that a small amount of noise has the effect of decreasing
+  the size of the periodic orbit (c.f. Figure \ref{fig::3PlayerChainNoNoise}). However, as $\gamma$
+  is increased to $0.5$, the algorithm seems to exhibit convergence to the NE. The implication is
+  that the addition of noise may cause periodic behaviour to break and lead to the Nash Equilibrium.
+  An interesting point to note is that this behaviour is in stark contrast to the replicator
+  dynamic (RD) \cite{Maynard-Smith}, another adaptive algorithm linked to multi agent learning
+  \cite{CyclesAdversarialLearning}. In \cite{Imhof} and \cite{Galla}, it was found that the
+  introduction of random mutations can remove convergent behaviour and instead lead to periodicity.
 

### 2021-05-06 Documents/FP in NAGs/neurips_2020.tex
Figure Captions

@@
     \centering
-    \includegraphics[width = 0.7\textwidth]{Figures/ThreePlayerNetwork.png}
-    \caption{\label{fig::ThreePlayerNetwork}}
+    \includegraphics[width = 0.6\textwidth]{Figures/ThreePlayerNetwork.png}
+    \caption{\label{fig::ThreePlayerNetwork} A NA game where the network is defined by a chain of
+    three players, as described in Section \ref{sec::NonConv}.}
   \end{figure}
@@
 
-  \begin{align}
-    A & = - w B^T \\
+  \begin{align} \label{eq::zeroSumShapley}
+    A & = - w B^T \nonumber \\
     C & = - (1 - w) B^T. 
@@
 
-  \begin{equation}
+  \begin{equation} \label{eq::nonzeroSumShapley}
     C  = - (1 - w) B, 
@@
 
-  with no alteration to $A$.
-The modification itself is small, however it results in the zero-sum assumption being violated.
-With the same choices of $\beta$ and $w$, this results in the periodic orbit seen in Figure \ref{fig::nonconvergentShapley}.
-Here, the orbits reach a stable limit cycle which to be centred around the interior NE.
+  with no alteration to $A$. The modification itself is small, however it results in the zero-sum
+  assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic
+  orbit seen in Figures \ref{fig::nonconvergentShapley} and \ref{fig::3PlayerChainNoNoise}. Here,
+  the orbits reach a stable limit cycle which to be centred around the interior NE.
 
@@
     \centering
-    \begin{subfigure}[b]{0.4 \textwidth}
+    \begin{subfigure}[b]{0.45 \textwidth}
       \includegraphics[width = \textwidth]{Figures/convergentShapley.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.4 \textwidth}
+    \begin{subfigure}[b]{0.45 \textwidth}
       \includegraphics[width = \textwidth]{Figures/nonConvergentShapley.png}
@@
     \end{subfigure}
-    \caption{\label{fig::Shapley}}
+    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain (c.f.
+    Figure \ref{fig::ThreePlayerNetwork}) with payoff matrices given by (a)
+    (\ref{eq::zeroSumShapley}) showing convergence to the interior NE (b)
+    (\ref{eq::nonzeroSumShapley}) showing cycles around the interior NE.}
   \end{figure}
@@
     \includegraphics[width = 0.7 \textwidth]{Figures/3PlayerChainNoNoise.png}
-    \caption{\label{fig::3PlayerChainNoNoise}}
+    \caption{\label{fig::3PlayerChainNoNoise} Distance to the Nash Equilibrium strategy along orbits
+    of FP showing oscillations which are bounded away from the NE (i.e. they do not cross the NE).
+    The x-axis shows logarithmic time since FP includes a factor of $1/t$, which has the effect of
+    slowing down the orbit over time.}
   \end{figure}

### 2021-05-07 Documents/FP in NAGs/neurips_2020.tex
Updated Introand Conclusion

@@
 \theoremstyle{definition}
-\newtheorem*{definition}{Definition}
+\newtheorem{definition}{Definition}
 \newtheorem{theorem}{Theorem}
@@
 to non-stationary, and even chaotic behaviour \cite{SatoChaos}, and this problem becomes even more
-pronounced as the number of agents increase \cite{Sanders}. In this light, it would appear that
-learning when there is a large population of agents is an impossible task.
+pronounced as the number of agents increase \cite{Sanders}.
+In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi agent learning \cite{PiliourasChaoticMaps}.
+This, of course, poses a problem for AI safety, for which it is necessary that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
 
@@
 combination of the states of the other agents. In both formulations, a many player game is reduced
-to the set of two player games which each agent is involved in, allowing the problem to maintain
-tractability.
-
-Whilst both formulations have shown success in multi-agent learning settings, allowing agents to
-reach equilibrium strategies (c.f. \cite{MFGLearningPapers} for Mean Field Games and
-\cite{Aggregative Papers} for Aggregative Games), they also present a fundamental limitation.
+to the set of two player games which each agent is involved in.
+
+Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{MFGLearningPapers} for Mean Field Games and
+\cite{Aggregative Papers} for Aggregative Games). However, both also present a fundamental limitation.
 Namely, they both require that agents have access to the action profiles of the entire population.
@@
 for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Grammatico,
-LeaderFollower, MyopicAgents}. We contribute in this direction by showing that learning on an NA
-game can lead to an equilibrium strategy. In particular, we analyse the Fictitious Play Learning
+LeaderFollower, MyopicAgents}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
 Algorithm \cite{Brown, Harris}, in which agents are assumed to be myopic, in that they react solely
@@
 
-  \begin{definition}(NE)
+  \begin{definition}(NE) \label{def::NE}
     The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,  
@@
   Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
-  Fictitious Play in continuous time.
+  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
 %
-  \begin{definition}[Continuous Time Fictitious Play (CTFP)]
-    A CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
+  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)]
+    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
     and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
@@
     \begin{align}
-      \alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
+      \alpha^\mu(t; x) = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
   %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
@@
 
-    In this manner, the $\alpha^\mu(t)$ denotes the time average of the strategies played by
-    agent $\mu$ up to time $t$. Then, fictitious play requires that the agents update their
+    In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
+    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
     strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
-    seen, therefore, that the CTFP in an NA game is a natural extension of CTFP in the classical
+    seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
     two-player setting \cite{}.
@@
 
-  \begin{assumption}
+  \begin{assumption}\label{ass::rowstochastic}
     The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
@@
 
-  \begin{assumption}
+  \begin{assumption}\label{ass::matrixgame}
     The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
@@
 
-  \begin{assumption}
+  \begin{assumption}\label{ass::sameactions}
     The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
@@
 
-  \begin{assumption}
+  \begin{assumption}\label{ass::zerosum}
     The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
@@
     \ref{sec::CCEConvergence}, we perform a regret analysis that considers the long term
-    behaviour of CTFP without this assumption.
+    behaviour of NA-CTFP without this assumption.
   \end{assumption}
@@
 
-  Note that the NE Condition requires \fb{why?}
+  As a reminder, the NE condition (Def. \ref{def::NE}) states
 %
@@
 
-  To show existence of an NE we will need the following definition and theorem.
+  To show existence of an NE we will need the following definitions which can be found in most texts on topology \cite{Munkres}.
+
+  \begin{definition}[Convexity]
+  	A set $\mathcal{X}$ is \emph{convex} if, for every $x, y \in \mathcal{X}$ and every $\lambda \in [0, 1]$ we have that $\lambda x + (1 - \lambda)y \in \mathcal{X}$.
+  \end{definition}
+
+	\begin{definition}[Convex Combinations]
+		The point $\sum_{i = 1}^{n} \lambda_i x_i$ is a \emph{convex combination} of the points $x_1, \ldots, x_n$ if $\lambda_i \geq 0$ for all $i$ and $\sum_i \lambda_i = 1$.
+	\end{definition}
+
+	\begin{definition}[Unit Simplex]
+		The $n$-dimensional \emph{unit simplex} is defined as the convex combination of the $n$ standard basis vectors $(e_i)_{i = 1}^n$ in $\mathbb{R}^n$ in which $e_i$ has $1$ in the $i$'th component and $0$ in all others.
+In particular this is given by
+
+		\begin{equation}
+			\Delta = \{x \in \mathbb{R}^n : x = \sum_{i = 1}^n \lambda_i e_i \text{ for some } \lambda_1, \ldots, \lambda_n \geq 0, \sum_i \lambda_i = 1\}
+		\end{equation}
+	\end{definition}
+
+	It follows from the definitions, then, that the unit simplex is a convex set.
+In addition we have that the simplex is \emph{closed} and \emph{bounded} in $\mathbb{R}^n$.
+By the Heine-Borel Theorem \cite{Royden} it is therefore also \emph{compact}.
+The definitions of each of these terms can be found in any standard topology reference and we point the reader to \cite{Royden} for further details.
 
   \begin{definition}[Upper Semi-Continuous] 
-    A compact-valued correspondence $\Phi: A \rightarrow B$ is
-    \emph{upper semi-continuous} at a point $a$ \fb{domain?} if $g(a)$ \fb{what is $g$?} is non-empty
+    A compact-valued correspondence $g: A \rightarrow B$ is
+    \emph{upper semi-continuous} \cite{Findforthis} at a point $a \in A$ if $g(a)$ is non-empty
     and if, for every sequence $a_n \rightarrow a$ and every sequence
@@
   \begin{theorem}[Kakutani] 
-    Let $K \subset \mathbb{R}^n$ be compact and convex and $\Phi: K \rightarrow K$ be closed or upper semi-continuous, with nonempty, convex and compact values. Then $\Phi$ has a fixed point.
+    Let $A \subset \mathbb{R}^n$ be compact and convex and $g: A \rightarrow A$ be closed or upper semi-continuous, with nonempty, convex and compact values.
+Then $g$ has a fixed point, that is a point $\bar{a}$ such that $\bar{a} \in g(\bar{a})$.
+\cite{Kakutani}
   \end{theorem}
 
-  Note that, when acting on a simplex, the function $\Phi: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes the nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.
+  Note that, when acting on a simplex, the function $g: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes all nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.
+
+	\ah{Probably need a quick intro into why the argmax is closed, convex and nonempty.}
 
@@
 
-    in which $w_{-\mu}$ is a column vector containing $w^{\mu \nu}$ in the $\nu$'th element for all $j \in N^\mu$ and 0 everywhere else (including in the $\mu$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the kronecker product.
+    in which $w_{-\mu}$ is a column vector containing $w^{\mu \nu}$ in the $\nu$'th element for all $j \in N^\mu$ and 0 everywhere else (including in the $\mu$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the Kronecker product \cite{Findforthis}.
+It is important to note at this point that we use Assumption \ref{ass::sameactions} here, so that all $w_{-\mu}^T$ is acted upon by the same $I_n$ in the Kronecker product.
 For example, the form for agent 1, in the case of 2-action game is given by
@@
     Returning to the $N$-player NA game our condition becomes
-    \begin{equation}
+    \begin{equation} \label{eq::fixedpointNE}
       \begin{bmatrix}
-        \NE{1} \\ . \\ . \\ . \\ \bar{N}
+        \NE{1} \\ . \\ . \\ . \\ \NE{N}
       \end{bmatrix} \in
@@
 
-    This means that we achieve a Nash Equilibrium iff $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the map \fb{why?}
-
-    \begin{equation}
+    The condition (\ref{eq::fixedpointNE}) takes on the form of a fixed point condition.
+In particular, it states that we achieve a Nash Equilibrium if and only if $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the vector function defined by
+
+    \begin{equation}
+    	\mathbf{f}(\mathbf{x}) = 
       \begin{bmatrix}
-        \arg\max_{y \in \Delta_1} \bar{u}^1(y, (w_{-1}^T \otimes I_n) ( \cdot )) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}^N(y, (w_{-N}^T \otimes I_n)( \cdot ))
+        \arg\max_{y \in \Delta_1} \bar{u}^1(y, (w_{-1}^T \otimes I_n) ( \mathbf{x} )) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}^N(y, (w_{-N}^T \otimes I_n)( \mathbf{x} ))
       \end{bmatrix} .
@@
 
-    Now, since the modified payoff $\bar{u}^\mu$ shares the same bilinear property as $u^\mu$, we can assert that it is continuous is its second argument.
+    Now, since the modified payoff $\bar{u}^\mu$ shares the same bilinear property as $u^\mu$, we can assert that it is continuous in its second argument.
 Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous.
@@
 
-\subsection{Existence of CTFP}
+\subsection{Existence of NA-CTFP}
 
   \begin{theorem}
-    There exists a path $m$ which satisfies the property that, for all $\mu$ \fb{remind what this is.}, $m^\mu \in
-    BR^\mu(\alpha_\sigma^\mu)$ for almost aall $t \geq 1$.
+    There exists a path $m$ which satisfies the property that, for all agents $\mu$, $m^\mu \in
+    BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
   \end{theorem}
@@
     \begin{equation*}
-    \alpha^\mu(t) = \frac{1}{t} \int_{0}^{t} m^\mu(s) \, ds
+    \alpha^\mu(t; m) = \frac{1}{t} \int_{0}^{t} m^\mu(s) \, ds
     \end{equation*}
@@
 
-    with the initial condition $\alpha(1) = x_0$. Then, the path $m$ is a CTFP if its
+    with the initial condition $\alpha(1) = x_0$. Then, the path $m$ is a NA-CTFP if its
     corresponding $\alpha(t; m)$ is a solution to the above differential inclusion. Following
@@
 
-    The question then remains, does the differential inclusion admit a solution? Using the
-    results of Aubin and Cellina (see Harris 1998, paragraph below Prop. 6), can use the fact
-    that the $\arg \max$ function is non-empty, compact and convex valued, bounded (all of
-    these follow since the function acts from $\Delta$ to $\Delta$) and upper semi-continuous. 
-    With these facts in place, we can say that there is a CTFP $m$ for any initial value $x_0$. Further, the solution $m(t)$ is Lipschitz for almost all $t \geq 0$.
+    The question then remains, does the differential inclusion admit a solution? To do this we use the
+    results of Aubin and Cellina (see \cite{Harris1998}, paragraph below Prop. 6), alongside the fact
+    that the $\arg \max$ function is non-empty, compact and convex valued, bounded (\ah{Will need to discuss as part of intro to topology}) and upper semi-continuous. 
+    With these facts in place, we can say that there is a NA-CTFP $m$ for any initial value $x_0$. Further, the solution $m(t)$ is Lipschitz for almost all $t \geq 0$.
 
@@
 
-\subsection{Convergence of CTFP}
-
-With the existence of the CTFP in place, we can show that it converges
+\subsection{Convergence of NA-CTFP}
+
+With the existence of the NA-CTFP in place, we can show that it converges
 to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
-all limit points for $\alpha(t)$. Then, a CTFP path is said to have
+all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to have
 converged if $\Omega(\alpha)$ is contained within the set of Nash
-Equilibria of the game. If this is for any such CTFP path, then the
+Equilibria of the game. If this is for any such NA-CTFP path, then the
 game is said to have the \emph{CTFP property}. We adapt the techniques
 of (Ewerhart 2020) to prove that zero-sum NA games have the CTFP
-property. \ah{I also want to attempt this with the techniques of
-  Harris (which is quite similar) to see if it yields any new
-  results}.
+property.
 
   \begin{theorem}
-    Any zero-sum NA game has the property that, for any CTFP path $m$, the corresponding $\alpha(t; m)$ converges to a set of fixed points.
+    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, the corresponding $\alpha(t; m)$ converges to a set of fixed points.
   \end{theorem}
@@
 
-   \fb{what is the meaning of the following equation?}
+   As a reminder, the definition of the NA-CTFP path $m$ requires that, for all agents $\mu$ and for almost all $t \geq 0$
 %
@@
 
-    By the definition of Continuous Time Fictitious Play (CTFP) given by Ewerhart, we require that $m: [0, \infty) \rightarrow \times_\mu \Delta_\mu$ is a measurable mapping such that, for each $\mu$, $m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(t') dt' \right)$.
+    By the definition of Continuous Time Fictitious Play (CTFP) given in \cite{Ewerhart}, we require that $m: [0, \infty) \rightarrow \times_\mu \Delta_\mu$ is a measurable mapping such that, for each $\mu$, $m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(t') dt' \right)$.
 Now notice,
@@
     where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m)
-    =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined by Ewerhart \fb{use the reference rather than the name of the author.}. We
+    =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined in \cite{Ewerhart2020}. We
     can, therefore, think of the NA game as a network game in which
@@
     itself included. As such, any $m$ which satisfies the CTFP
-    property for the equivalent network game also satisfies the CTFP
+    property for the equivalent network game also satisfies the NA-CTFP
     requirement for the network aggregative game.
@@
     $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$. More specifically, $\xmu_\infty$
-    belongs to the set of accumulation points of $\alpha^\mu(\cdot; m)$ (which is set valued since
+    belongs to the set of accumulation points of $\alpha^\mu$ (which is set valued since
     the $BR^\mu$ map is set valued). To say that the game has `converged' we require that every
@@
 
-    We can divide this expression by $t - t'$ and take the limit for $t' \rightarrow t$. This yields the derivative (in particular the upper right Dini derivative)
+    We can divide this expression by $t - t'$ and take the limit for $t' \rightarrow t$. This yields the derivative (in particular the upper right Dini derivative \cite{Royden})
 
@@
 
-\section{CTFP achieves no regret}
+\section{NA-CTFP achieves no regret}
   \label{sec::CCEConvergence}
@@
   vector of joint distributions over actions and references which is
-  generated by CTFP. In particular, if by playing with CTFP, the
+  generated by NA-CTFP. In particular, if by playing with NA-CTFP, the
   agents reach the state $(\xmu)_{i = 1}^N$ with references
@@
 
-  As such, we would say that CTFP has converged to the set of CCE if, in the limit of $t
+  As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
   \rightarrow \infty$, we have that for all $\mu$
@@
     Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the
-    CTFP process achieve \emph{no regret} in the limit $t \rightarrow \infty$, i.e.
+    NA-CTFP process achieve \emph{no regret} in the limit $t \rightarrow \infty$, i.e.
     \begin{equation}
@@
 
-    In particular, CTFP in an NA game converges to the set of CCE.
+    In particular, NA-CTFP converges to the set of CCE.
 
@@
 
-    For any agent $\mu$ define \fb{what are we defining here?}
+    For any agent $\mu$ define the \emph{maximal payoff} as 
     \begin{equation}
@@
 
-    Now, if the agents are following the NA-FP process, then we know that $m^\mu (t) \in \Delta_\mu$ is the strategy which maximises $u^\mu( \cdot, \alpha_\sigma^\mu)$ so we can write
+    This is the maximum payoff that agent $\mu$ can receive when playing against the average reference $\alpha_{\sigma}^\mu$.
+Now, if the agents are following the NA-CTFP process, then we know that $m^\mu (t) \in \Delta_\mu$ is the strategy which maximises $u^\mu( \cdot, \alpha_\sigma^\mu)$ so we can write
 
@@
 
-    Then, applying the \emph{envelope theorem} \cite{} we have
+    Then, applying the \emph{envelope theorem} \cite{MathematicalEconomics} we have
 
@@
 
-    \begin{align}
-      \frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & =  \bar{u}^\mu (\alpha_\sigma^\mu (t)) + t m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt} \\
+    \begin{align} \label{eq::dtA}
+      \frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & =  \bar{u}^\mu (\alpha_\sigma^\mu (t)) + t m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt} \nonumber \\
       & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + t (m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{d}{dt} \alpha^\nu(t))
@@
 
-    Now, we know that the differential inclusion for the NA-FP process can be written as
-
-    \begin{equation}
+    Now, we know that the differential inclusion for the NA-CTFP process can be written as
+
+    \begin{equation} \label{eq::NAFP}
       \frac{d}{dt} \alpha^\mu (t) = \frac{1}{t} (m^\mu(t) - \alpha^\mu (t))
@@
 
-    We insert this \fb{use enumeration} into the previous equation to yield
-
-    \begin{align}
-      \frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t)) + t(m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{1}{t} (m^\nu(t) - \alpha^\nu (t))) \\
-      & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} (m^\nu(t) - \alpha^\nu (t)) \\
+    We insert \ref{eq::NAFP} into (\ref{eq::dtA}) to yield
+
+    \begin{align}
+      \frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t)) + t(m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{1}{t} (m^\nu(t) - \alpha^\nu (t))) \nonumber \\
+      & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} (m^\nu(t) - \alpha^\nu (t)) \nonumber \\
       & = m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} m^\nu(t) = m^\mu \cdot A^\mu \sigma^\mu(t) 
@@
 
-    Now if we integrate both sides with respect to $t$ in the bound $[1, T]$ (on which the NA-FP) process is defined, we get
-
-    \begin{align}
+    Now if we integrate both sides with respect to $t$ in the bound $[1, T]$, on which the NA-CTFP process is defined, we get
+
+    \begin{align*}
       &  T \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
@@
       & \implies \lim_{T \rightarrow \infty} \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \int_0^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt = 0
-    \end{align}
+    \end{align*}
 
@@
 
-    \begin{align}
+    \begin{align*}
       \bar{u}^\mu (\alpha_\sigma^\mu (T)) = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\alpha_{\sigma}^\mu (T))_j & = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\frac{1}{T} \int_{0}^{T} \sigma^\mu(t) \; dt)_j \\
@@
       & = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T u^\mu(x^\mu_{i'}, \sigma^\mu(t))
-    \end{align}
+    \end{align*}
 
@@
     \includegraphics[width = \columnwidth]{Figures/Noise10Player.png}
-    \caption{\label{fig::Noise10Player}}
+    \caption{\label{fig::Noise10Player} Trajectories of NA-CTFP in a 10 player game with additive noise (Left) No noise is introduced and learning converges directly to an NE.
+(Middle) $\gamma = 0.1$, the trajectories converge to a fixed point but removed from the NE.
+(Right) $\gamma = 0.5$, the trajectories converge to a fixed point which is even further away from the NE.}
   \end{figure}
@@
     \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
-    \caption{\label{fig::Noise20Player}}
+    \caption{\label{fig::Noise20Player} Trajectories of NA-CTFP in a 20 player game with additive noise (Left) No noise is introduced and learning converges directly to an NE.
+(Middle) $\gamma = 0.05$, the trajectories converge to a fixed point but removed from the NE.
+(Right) $\gamma = 0.1$, the trajectories converge to a fixed point which is even further away from the NE.}
   \end{figure}
@@
     \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoise.png}
-    \caption{\label{fig::3PlayerChainNoise}}
+    \caption{\label{fig::3PlayerChainNoise} Trajectories of NA-CTFP on the Three Player Chain of Section \ref{sec::NonConv} with additive noise.
+(Left) $\gamma = 0.1$ leads to a decrease in the size of the cyclic orbit (Middle) $\gamma = 0.5$, no periodicity is seen but the trajectory converges to the NE (Right) $\gamma = 0.75$, NA-CTFP still converges, though after a greater amount of time has elapsed.}
   \end{figure}
@@
   As such, we investigate the effect that introducing additive noise has
-  on CTFP in a zero-sum NA game. We do this in the following manner: at each time step, the
+  on NA-CTFP in a zero-sum NA game. We do this in the following manner: at each time step, the
   reference signal $\refmu(t)$ is adjusted to $\refmu + \gamma \xi$ where $\xi$ is drawn from the
@@
 \section{Concluding remarks}
+	In this work, we have considered the action of the Fictitious Play learning algorithm in Network Aggregative Games and investigated its long term behaviour through a continuous time analysis.
+We find that, under a zero-sum condition, the algorithm converges to a fixed point.
+However, we find experimentally that this is not always the case.
+In fact, we find a family of NA games, based on the Shapley family, for which FP cycles about the NE.
+For these cases, we also perform a regret analysis which shows that, regardless of the type of game, the FP algorithm achieves no regret.
+
+	We also investigate the influence of noise on the algorithm and find that even with the introduction of additive noise, FP converges to a fixed point, though not necessarily the NE.
+In fact, for our cyclic family of games, we find that the introduction of noise can actually remove the periodicity, resulting in FP converging to a fixed point.
+
+	Our work opens a number of lines for future work.
+Most notable is the effect of noise.
+It would be prudent to analyse this theoretically, as was done in \cite{MFGFP}, and consider the conditions under which FP will still converge to a fixed point.
+Furthermore, it would be interesting to investigate the phenomenon we report experimentally in a theoretical framework.
+Namely, the question of why noise breaks periodicity in FP and results in convergence to an NE should be investigated and, indeed, this is a line which we are currently pursuing.
+
+	In addition, we note that the \emph{Mann Iteration}, a method of approximating fixed points which is investigated in \cite{Parise2020}, shares a remarkably similar structure to the discrete variant of FP.
+This may present an avenue by which NA-CTFP may be analysed in the case of convex cost functions.
+
+	Finally, we note that in recent years FP in two player games has shown a remarkable variety of dynamical behaviours, including periodicity and chaos.
+In our work we have shown convergence to a fixed point and, through experiments, periodicity.
+It stands to reason, therefore, that a greater variety of dynamical behaviours exist for NA-CTFP for certain classes of games.
+It would be important to determine what these classes are.
+Short from being merely a curiosity, this would allow for the identification of games in which NA-CTFP leads to inherently unpredictable behaviour, an important question from the point of view of building Safe and Trusted AI.
 

### 2021-05-12 Documents/FP in NAGs/neurips_2020.tex
updated FP document

@@
 
-  The main contribution of this work is to study the behaviour of the Fictitious Play (FP) learning
-  algorithm, in continuous time, when applied on a Network Aggregative Matrix Game.
+  The main contribution of this work is to introduce learning on the Network Aggregative Game
+  through the action of Fictitious Play (FP).
 
@@
   solutions in this setting. In particular, we study zero-sum games and show that
-  Fictitious Play converges to a fixed point, which for a network without any
+  FP converges to a fixed point, which for a network without any
   self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
-  which are not zero-sum, agents following Fictitious Play are able to
+  which are not zero-sum, agents following FP are able to
   achieve no regret.
@@
   games in which action profiles cycle around the Nash Equilibrium. Finally, our experiments
-  document how noise affects the convergence of Fictitious Play. Our experiments suggest that, under
+  document how noise affects the convergence of FP. Our experiments suggest that, under
   the presence of noise, the algorithm still reaches a fixed point, but perhaps not the Nash
@@
   \begin{theorem}[Kakutani] 
-    Let $A \subset \mathbb{R}^n$ be compact and convex and $g: A \rightarrow A$ be closed or upper semi-continuous, with nonempty, convex and compact values.
+    Let $A$ be a compact and convex in a Euclidean space and $g: A \rightarrow \mathbf{P}(A)$ (where
+    $\mathbf{P}(A)$ denotes the power set of A) be upper semi-continuous, with nonempty, convex and compact values.
     Then $g$ has a fixed point, that is a point $\bar{a}$ such that $\bar{a} \in g(\bar{a})$.
@@
 
-Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
-Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
-who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
-biases in the data. If authors believe this is not applicable to them, authors can simply state this.
-
-Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}
+The dynamics of learning is an important consideration for all practitioners. In particular, it has
+been shown a number of times \cite{noneqmbehaviour} that convergence of learning cannot always be
+assumed. Rather, learning generally presents much more complex dynamics \cite{gallaandfarmer}, which
+only increases as the number of players increases \cite{sanders}. Our work presents practitioners
+who applies Fictitious Play with a case in which rigorous stability properties may be guaranteed.
+We also elucidate the behaviour of the algorithm under more general assumptions, both by
+understanding its regret properties as well as through an experimental study of the impact of noise.
+
+As regards FP  itself, the learning strategy has strong applications in robotic control
+\cite{Smyrnakis, Hernandez, Sharma} as well as economic modelling \cite{vonNeumann}. As such we
+Furthermore, the algorithm has links to other learning protocols including the replicator dynamic
+\cite{Benaim} and reinforcement learning \cite{LeslieandCollins}. Therefore, we believe that an
+understanding of FP has subsequent impacts on a number of fields.
+
+Finally, our work has a strong impact on the study of the Network Aggregative Game, which has strong
+applications in multi agent control \cite{GrammaticoAggregativeControl}. We 
+believe that our work makes a strong step towards ensuring that systems which learn and adapt on
+NA games maintain stability and, therefore, can be considered safe.
 

### 2021-05-13 Documents/FP in NAGs/neurips_2020.tex
Removed Proofs

@@
 
-  \begin{proof}
-    We begin by rewriting the NE condition by concatenating the set of NE vectors into one long colunn vector. This gives
-
-    \begin{equation}
-      \begin{bmatrix}
-        \bar{x}^1 \\ . \\ . \\ . \\ \bar{x}^N
-      \end{bmatrix} \in
-      \begin{bmatrix}
-      \arg\max_{y \in \Delta_1} \bar{u}^1(y, \sum_{\nu \in N^1} w^{1 \nu} \bar{x}^\nu) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}^1(y, \sum_{\nu \in N^N} w^{N \nu} \bar{x}^\nu)
-      \end{bmatrix} .
-    \end{equation}
-
-    We can rewrite the weighted summation for $\mu$ as
-
-    \begin{equation}
-      \sum_{\nu \in N^\mu} w^{\mu \nu} \bar{x}^\nu = (w_{-\mu}^T \otimes I_n) \begin{bmatrix}
-        \bar{x}^1 \\ . \\ . \\ . \\ \bar{x}^N
-      \end{bmatrix},
-    \end{equation}
-
-    in which $w_{-\mu}$ is a column vector containing $w^{\mu \nu}$ in the $\nu$'th element for all $j \in N^\mu$ and 0 everywhere else (including in the $\mu$'th slot), $I_n$ is the $n \times n$ identity matrix and $\otimes$ is the Kronecker product \cite{Findforthis}.
-It is important to note at this point that we use Assumption \ref{ass::sameactions} here, so that all $w_{-\mu}^T$ is acted upon by the same $I_n$ in the Kronecker product.
-For example, the form for agent 1, in the case of 2-action game is given by
-
-    \begin{equation}
-      (w_{-1}^T \otimes I_2) = [0, w_{12}, w_{13}, ..., w_{1n}] \otimes I_2 = 
-      \begin{bmatrix}
-        0 & 0 & w_{12} & 0 & ... & w_{1n} & 0 \\
-        0 & 0 & 0 & w_{12} & ... & 0 & w_{1n} \\
-      \end{bmatrix}
-    \end{equation}
-
-    Returning to the $N$-player NA game our condition becomes
-    \begin{equation} \label{eq::fixedpointNE}
-      \begin{bmatrix}
-        \NE{1} \\ . \\ . \\ . \\ \NE{N}
-      \end{bmatrix} \in
-      \begin{bmatrix}
-        \arg\max_{y \in \Delta_1} \bar{u}^1(y, (w_{-1}^T \otimes I_n) \begin{bmatrix}
-          \NE{1} \\ . \\ . \\ . \\ \NE{N}
-        \end{bmatrix}) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}_N(y, (w_{-N}^T \otimes I_n) \begin{bmatrix}
-        \NE{1} \\ . \\ . \\ . \\ \NE{N}
-      \end{bmatrix}))
-      \end{bmatrix} .
-    \end{equation}
-
-    The condition (\ref{eq::fixedpointNE}) takes on the form of a fixed point condition.
-In particular, it states that we achieve a Nash Equilibrium if and only if $(\NE{\mu})_{\mu \in \agentset}$ is a fixed point of the vector function defined by
-
-    \begin{equation}
-    	\mathbf{f}(\mathbf{x}) = 
-      \begin{bmatrix}
-        \arg\max_{y \in \Delta_1} \bar{u}^1(y, (w_{-1}^T \otimes I_n) ( \mathbf{x} )) \\ . \\ . \\ . \\ \arg\max_{y \in \Delta_N} \bar{u}^N(y, (w_{-N}^T \otimes I_n)( \mathbf{x} ))
-      \end{bmatrix} .
-    \end{equation}
-
-    Now, since the modified payoff $\bar{u}^\mu$ shares the same bilinear property as $u^\mu$, we can assert that it is continuous in its second argument.
-Therefore, the above vector valued map can be asserted to be continuous and so is upper semi-continuous.
-As such, we can apply Kakutani's Fixed Point Theorem to assert that the above map admits a fixed point.
-
-  \end{proof}
-
 \subsection{Existence of NA-CTFP}
@@
   \end{theorem}
-
-  \begin{proof}
-    Recall the definition of $\alpha^\mu(t)$
-
-    \begin{equation*}
-    \alpha^\mu(t; m) = \frac{1}{t} \int_{0}^{t} m^\mu(s) \, ds
-    \end{equation*}
-
-    Then
-
-    \begin{align}
-    \frac{d}{dt} \alpha^\mu(t) & = \frac{d}{dt} \frac{1}{t} \int_{0}^t m^\mu(s) ds \nonumber \\
-    & = \frac{1}{t} m^\mu(t) - \frac{1}{t} \alpha^\mu(t)
-    \end{align}
-
-    Now we assert that $m^\mu(t) \in BR^\mu(\alpha_{\sigma}^\mu) = \arg\max_{y \in \Delta_\mu} u^\mu(y,
-    w^{\mu \mu} \alpha^\mu(t) + \sum_{\nu \in N^\mu} w_{ij} \alpha^\nu(t))$.
-
-    Let us then define $\alpha(t)$ as the concatenation of all $\alpha_i(t)$
-
-    \begin{equation}
-      \alpha(t) = \begin{bmatrix}
-        \alpha^1(t)^T, \ldots, \alpha^N(t)^T
-      \end{bmatrix}^T \subset \mathbb{R}^{Nn}
-    \end{equation}
-
-    We can, therefore, write the aggregation as
-
-    \begin{equation}
-      (W \otimes I_n) \alpha(t) = \begin{bmatrix}
-        \sum_{\nu \in N^1} w^{1 \nu} \alpha^\nu(t) \\
-        .\\
-        .\\
-        .\\
-        \sum_{\nu \in N^N} w^{N \nu} \alpha^\nu(t)
-      \end{bmatrix} \subset \mathbb{R}^{Nn}
-    \end{equation}
-
-    I will write $(W \otimes I_n) \alpha(t)$ as $\alpha_W$ for convenience. Furthermore, using
-    the bilinear property of the game, we can say that
-
-    \begin{equation}
-      \begin{bmatrix}
-        \arg\max_{y_1 \in \Delta_1} y \cdot A^1 ( \alpha_W(t))_1 \\
-        .\\
-        .\\
-        .\\
-        \arg \max_{y_N \in \Delta_N} y \cdot A^N (\alpha_W(t))_N 
-      \end{bmatrix} = 
-      \arg \max_{y \in \Delta} y \cdot \begin{bmatrix}
-        A^1 & 0 & . & . & . & 0 \\
-        0 & A^2 & . & . & . & 0 \\
-        & & . & & & \\
-        & & & . & & \\
-        & & & & . & \\
-        0 & 0 & . & . & . & A^N \\
-      \end{bmatrix} \alpha_W(t) = \arg\max_{y \in \Delta} y \cdot \Lambda (W \otimes I_n)
-      \alpha(t)
-    \end{equation}
-
-    in which $\Delta = \times_i \Delta_i$ and $\Lambda$ is the block diagonal matrix containing
-    each $A^i$.
-
-    We can now write the differential inclusion as
-
-    \begin{equation}
-      \dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
-      I_n)
-      \alpha(t) \}- \alpha(t))
-    \end{equation}
-
-    with the initial condition $\alpha(1) = x_0$. Then, the path $m$ is a NA-CTFP if its
-    corresponding $\alpha(t; m)$ is a solution to the above differential inclusion. Following
-    the definition of (Harris 1998), a solution $\alpha(t)$ must satisfy
-
-    \begin{enumerate}
-      \item $\alpha(t)$ is locally Lipschitz
-      \item $\alpha(1) = x_0$
-      \item $\dot{\alpha}(t) \in \frac{1}{t} (\arg \max_{y \in \Delta}  \{y \cdot \Lambda (W \otimes
-      I_n)
-      \alpha(t) \}- \alpha(t))$ for almost all $t \in [1, \infty)$ 
-    \end{enumerate}
-
-    The question then remains, does the differential inclusion admit a solution? To do this we use the
-    results of Aubin and Cellina (see \cite{Harris1998}, paragraph below Prop. 6), alongside the fact
-    that the $\arg \max$ function is non-empty, compact and convex valued, bounded (\ah{Will need to discuss as part of intro to topology}) and upper semi-continuous. 
-    With these facts in place, we can say that there is a NA-CTFP $m$ for any initial value $x_0$. Further, the solution $m(t)$ is Lipschitz for almost all $t \geq 0$.
-
-  \end{proof}
 
@@
   \end{theorem}
-
-  \begin{proof}
-
-   As a reminder, the definition of the NA-CTFP path $m$ requires that, for all agents $\mu$ and for almost all $t \geq 0$
-%
-    \begin{equation}
-      m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(s) ds \right).
-    \end{equation}
-
-    By the definition of Continuous Time Fictitious Play (CTFP) given in \cite{Ewerhart}, we require that $m: [0, \infty) \rightarrow \times_\mu \Delta_\mu$ is a measurable mapping such that, for each $\mu$, $m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(t') dt' \right)$.
-Now notice,
-
-    \begin{equation*}
-      m^\mu(t) \in BR^\mu \left( \frac{1}{t} \int_{0}^{t} \sigma^\mu(t') dt' \right) \iff  \in x^\mu\in BR^\mu \left( \frac{1}{t} \int_{0}^{t} [w^{\mu \mu} m^\mu(s) + \sum_{\nu \in N^\mu} w^{\mu \nu} m^\nu(s)] \, ds \right)
-    \end{equation*}
-
-    Let us assume that $u^\mu$ takes the form $x \cdot A^\mu \sigma^\mu$ where $A^\mu$ is the payoff matrix associated with agent $\mu$. Then,
-
-    \begin{align}
-      & m^\mu \in \arg\max_{x \in \Delta^\mu} u^\mu(x,\frac{1}{t} \int_{0}^{t} [w^{\mu \mu} m^\mu(t') + \sum_{\nu \in N^\mu} w^{\mu \nu} m^\nu(s)] \, ds) \nonumber \\
-      \iff & m^\mu \in \arg\max_{x \in \Delta_\mu} x \cdot A^\mu \left(\frac{1}{t} \int_{0}^{t} [w^{\mu \mu} m^\mu(t') + \sum_{\nu \in N^\mu} w^{\mu \nu} m^\nu(s)] \, ds \right) \nonumber \\
-      \iff & m^\mu \in \arg \max_{x \in \Delta_\mu} x \cdot (w^{\mu \mu} A^\mu) \left( \frac{1}{t} \int_{0}^{t} m^\mu(s) ds\right) + \sum_{\nu \in N^\mu} x \cdot (\wmunu A^\nu) \left( \frac{1}{t} \int_{0}^{t} m^\nu(s) ds \right) \nonumber \\
-      \iff & m^\mu \in \arg \max_{x \in \Delta_i} x \cdot A^{\mu \mu} \alpha^\mu(t; m) + \sum_{\nu \in N^\mu} x \cdot A^{\mu \nu} \alpha^\nu(t; m).
-    \end{align}
-
-    where each $A^{\mu \nu} = \wmunu A^\mu$ and $\alpha^\mu(t; m)
-    =\frac{1}{t} \int_{0}^{t} m^\mu(s) ds$ as defined in \cite{Ewerhart2020}. We
-    can, therefore, think of the NA game as a network game in which
-    each agent plays the same strategy against each of its neighbours,
-    itself included. As such, any $m$ which satisfies the CTFP
-    property for the equivalent network game also satisfies the NA-CTFP
-    requirement for the network aggregative game.
-
-    Continuing with this approach, let us look at the case where $\sum_\mu A^\mu =
-    \textbf{0}_{n\times n}$ (i.e. a zero sum game). This means that $\sum_i u_i = 0$. Let
-    $\xmu_\infty = \lim_{t \rightarrow \infty} \alpha^\mu(t; m)$. More specifically, $\xmu_\infty$
-    belongs to the set of accumulation points of $\alpha^\mu$ (which is set valued since
-    the $BR^\mu$ map is set valued). To say that the game has `converged' we require that every
-    $\xmu_\infty = (x^1_\infty, ... x^N_\infty)$ is an NE. Under these conditions, we may adapt the
-    techniques of (\cite{Ewerhart} Prop. 1) to show convergence.
-
-    Let us take the Lyapunov function
-
-    \begin{equation}
-      L(x) = \sum_\mu \max_{y \in \Delta_\mu} \{u^\mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) - u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \}
-    \end{equation}
-
-    Using the same transformation as before:
-
-    \begin{align}
-       u^mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} w_{\mu \nu} \xnu) & =  y \cdot A^\mu (w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \nonumber \\
-       & =  y \cdot (w^{\mu \mu} A^\mu) \xmu + \sum_{\nu \in N^\mu} y \cdot (\wmunu A^\mu) \xnu \nonumber \\
-        & =  \sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu \nonumber 
-    \end{align}
-
-    Then,
-
-    \begin{align}
-    L(x) &= \sum_\mu \max_{y \in \Delta_\mu}\sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu  - u^mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} w^{\mu \nu} \xnu) \} \nonumber \\
-    &= \sum_\mu \max_{y \in \Delta_\mu} \{\sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu  \} - \sum_\mu  u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} w^{\mu \nu} \xnu) \nonumber \\
-    &= \sum_\mu \max_{y \in \Delta_\mu} \{\sum_{\nu \in N^\mu \cup \{\mu\}} y \cdot A^{\mu \nu} \xnu  \} \nonumber 
-    \end{align}
-
-    where the last equality holds because $\sum_\mu u^\mu = 0$. Now, in parallel with (Ewerhart 2020) we recall that we defined $m^\mu(t)$ as the best response to $\alpha(t)$. As such,
-
-    \begin{align}
-      L(\alpha(t)) & = \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \alpha^\nu(t) \\
-      t L(\alpha(t)) & = \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} t \alpha^\nu(t) \\
-      t L(\alpha(t)) & = \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_0^t m^\nu(s) ds
-    \end{align}
-
-    Similarly, since we know that $m^\mu(t')$ is a best response to $\alpha(t')$ at time $t'$ we have
-
-    \begin{align}
-      \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t') \cdot A^{\mu \nu} \alpha^\nu(t') & \geq \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \alpha^\nu(t') \\
-      t' \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t') \cdot A^{\mu \nu} \alpha^\nu(t') & \geq \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_0^{t'} m^\nu(s) ds \\
-      t' L(\alpha(t')) & \geq \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_0^{t'} m^\nu(s) ds 
-    \end{align}
-
-    Combining the above equations in $t L(\alpha(t))$ and $t' L(\alpha(t'))$, we get
-
-    \begin{align}
-      t L(\alpha(t)) - t' L(\alpha(t')) \leq \sum_\mu \sum_{\nu \in N^\mu \cup \{\mu\}} m^\mu(t) \cdot A^{\mu \nu} \int_{t'}^{t} m^\nu(s) ds 
-    \end{align}
-
-    We can divide this expression by $t - t'$ and take the limit for $t' \rightarrow t$. This yields the derivative (in particular the upper right Dini derivative \cite{Royden})
-
-    \begin{equation}
-      \limsup_{t' \rightarrow t, t' < t}\frac{t L(\alpha(t)) - t' L(\alpha(t'))}{t - t'} \leq 0
-    \end{equation}
-
-    As this derivative is (weakly) negative, and we know that $tL(\alpha(t))$ is continuous in $t$, we have the result that $t L(\alpha(t))$ is monotone decreasing.
-Therefore, it is bounded, i.e.
-there is some $C \geq 0$ such that $L(\alpha(t)) \leq C/t$.
-In addition, we know that each term in the summation in the original expression of the Lyapunov function is non-negative and so we can say that
-
-    \begin{align}
-      & \max_{y \in \Delta_\mu} \{u^\mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) - u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \} \leq \frac{C}{t}\\
-      & \implies u^\mu(y, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) - u^\mu(\xmu, w^{\mu \mu} \xmu + \sum_{\nu \in N^\mu} \wmunu \xnu) \leq \frac{C}{t} \; \forall y \in \Delta_n
-    \end{align}
-
-    Now let us take some $\xmu_\infty \in \Omega(\alpha)$.
-Since this is a limit point, there exists a sequence $\{t_n\}_{n = 0}^\infty \rightarrow \infty$ such that $\{\alpha^\mu(t_n)\}_{n = 0}^{\infty} \rightarrow \xmu_\infty$.
-So if we take the limit as $t_n \rightarrow \infty$ we get
-
-    \begin{equation}
-      u^\mu(y, w^{\mu \mu} \xmu_\infty + \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) - u^\mu(\xmu_\infty, w^{\mu \mu} \xmu_\infty + \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq 0
-    \end{equation}
-
-    This means that $(\xmu_\infty)_{\mu \in \agentset}$ is a best response to itself and so is a fixed point of the NA-CTFP dynamic. 
-  \end{proof}
 
@@
   \end{theorem}
-
-  \begin{proof}
-    We will adapt the techniques of Ostrovski and van Strein for this proof.
-Their result was found for a two player game, we will leverage the fact that the NA process means that we can reduce an $N$ player game down to a series of two player games.
-
-    For any agent $\mu$ define the \emph{maximal payoff} as 
-    \begin{equation}
-      \bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu)
-    \end{equation}
-
-    This is the maximum payoff that agent $\mu$ can receive when playing against the average reference $\alpha_{\sigma}^\mu$.
-Now, if the agents are following the NA-CTFP process, then we know that $m^\mu (t) \in \Delta_\mu$ is the strategy which maximises $u^\mu( \cdot, \alpha_\sigma^\mu)$ so we can write
-
-    \begin{equation}
-      \bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu) = m^\mu(t) \cdot A^\mu (\alpha_\sigma^\mu)
-    \end{equation}
-
-    Then, applying the \emph{envelope theorem} \cite{MathematicalEconomics} we have
-
-    \begin{equation}
-      \frac{d}{d \alpha_\sigma^\mu} \bar{u}^\mu (\alpha_\sigma^\mu) = \frac{d}{d \alpha_\sigma^\mu} x^\mu \cdot A^\mu (\alpha_\sigma^\mu) \Big |_{x^\mu = m^\mu} = m^\mu \cdot A^\mu
-    \end{equation}
-
-    Which gives that
-
-    \begin{equation}
-      \frac{d}{dt} \bar{u}^\mu (\alpha_\sigma^\mu (t)) = m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt}
-    \end{equation}
-
-    Then,
-
-    \begin{align} \label{eq::dtA}
-      \frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & =  \bar{u}^\mu (\alpha_\sigma^\mu (t)) + t m^\mu \cdot A^\mu \frac{d \alpha_\sigma^\mu (t)}{dt} \nonumber \\
-      & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + t (m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{d}{dt} \alpha^\nu(t))
-    \end{align}
-
-    Now, we know that the differential inclusion for the NA-CTFP process can be written as
-
-    \begin{equation} \label{eq::NAFP}
-      \frac{d}{dt} \alpha^\mu (t) = \frac{1}{t} (m^\mu(t) - \alpha^\mu (t))
-    \end{equation}
-
-    We insert \ref{eq::NAFP} into (\ref{eq::dtA}) to yield
-
-    \begin{align}
-      \frac{d}{dt} (t \bar{u}^\mu (\alpha_\sigma^\mu (t))) & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t)) + t(m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} \frac{1}{t} (m^\nu(t) - \alpha^\nu (t))) \nonumber \\
-      & = m^\mu \cdot A^\mu (\sum_{\nu \in N(\mu)} w^{\mu \nu} \alpha^\nu (t) + m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} (m^\nu(t) - \alpha^\nu (t)) \nonumber \\
-      & = m^\mu \cdot A^\mu \sum_{\nu \in N(\mu)} w^{\mu \nu} m^\nu(t) = m^\mu \cdot A^\mu \sigma^\mu(t) 
-    \end{align}
-
-    Now if we integrate both sides with respect to $t$ in the bound $[1, T]$, on which the NA-CTFP process is defined, we get
-
-    \begin{align*}
-      &  T \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
-      & \implies \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \bar{u}^\mu (\alpha_\sigma^\mu (1)) = \frac{1}{T} \int_1^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt \\
-      & \implies \lim_{T \rightarrow \infty} \bar{u}^\mu (\alpha_\sigma^\mu (T)) - \frac{1}{T} \int_0^T u^\mu (m^\mu(t), \sigma^\mu(t)) \; dt = 0
-    \end{align*}
-
-    Now notice
-
-    \begin{align*}
-      \bar{u}^\mu (\alpha_\sigma^\mu (T)) = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\alpha_{\sigma}^\mu (T))_j & = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} (\frac{1}{T} \int_{0}^{T} \sigma^\mu(t) \; dt)_j \\
-      & = \max_{x^\mu_{i'} \in S^\mu} \sum_{j} a_{i'j} \frac{1}{T} \int_{0}^{T} \sum_i (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
-      & = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T \sum_{ij} a_{i'j} (m^\mu (t))_i (\sigma^\mu(t))_j \; dt\\
-      & = \max_{x^\mu_{i'} \in S^\mu} \frac{1}{T} \int_0^T u^\mu(x^\mu_{i'}, \sigma^\mu(t))
-    \end{align*}
-
-    So we recover
-
-    \begin{equation}
-      \lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
-    \end{equation}
-
-    which was precisely the regret condition that we required.
-
-  \end{proof}
 

### 2021-05-20 Documents/FP in NAGs/neurips_2020.tex
minor mods

@@
 
-Multi Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
-each agent must adapt in response to the behaviour of the other agents. This leads to a
-fundamentally non-stationary problem, which presents a challenge to designing effective learning
-policies. Even when there are a small number of agents in the game, learning has been shown to lead
-to non-stationary, and even chaotic behaviour \cite{SatoChaos}, and this problem becomes even more
-pronounced as the number of agents increase \cite{Sanders}.
-In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi agent learning \cite{PiliourasChaoticMaps}.
-This, of course, poses a problem for AI safety, for which it is necessary that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
+Multi-Agent Learning requires a number of agents to adapt in response
+to the behaviour of the other agents as well as the environment
+\cite{Schwartz}. This feature leads to a fundamentally non-stationary
+problem, which presents a challenge to designing effective learning
+policies. Even for a small number of agents in the game,
+learning has been shown to lead to non-stationary, even chaotic
+behaviour \cite{SatoChaos}, and this problem becomes even more
+pronounced as the number of agents increase \cite{Sanders}. In this
+light, it would seem that, when there is a large population of agents,
+it is almost impossible to understand the long term behaviour of multi-agent learning \cite{PiliourasChaoticMaps}. This, of course, poses a
+problem for AI safety, for which it is \fb{desirable} that learning systems
+are designed so that their ultimate behaviour is guaranteed to satisfy
+some predetermined goals.
 
-To deal with this problem, one must attempt to reduce the many player game to something which is
-tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
-and \emph{Aggregative} Games. The former makes the assumption of an infinite
-number of agents, so that the population can be represented through a distribution over players'
-states \cite{CainesPaper} . Every agent then updates their action profiles depending on this
-distribution. In the latter each agent plays considers a real valued function which is a convex
-combination of the states of the other agents. In both formulations, a many player game is reduced
-to the set of two player games which each agent is involved in.
+\fb{if space allows, you might consider to contrast the situation with
+  single-agent learning.}
 
-Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{MFGLearningPapers} for Mean Field Games and
-\cite{Aggregative Papers} for Aggregative Games). However, both also present a fundamental limitation.
-Namely, they both require that agents have access to the action profiles of the entire population.
-This could be through communication with all other agents, or through the intervention of a central
-coordinator who is able to the entire population. Whilst recent work aims to relax this assumption
-through the introduction of noise \cite{MFG-FP} or partial observability \cite{AAMASPaper}, the
-requirement that each agent updates their actions based on the entire population is rather strong.
+A promising approach to solve multi-agent learning
+%To deal with this problem, one must attempt
+consists in reducing the many player game to something which is more
+tractable. A number of reduction methods have been proposed in recent
+years, most notably \emph{mean field} games \cite{} and \emph{aggregative}
+games \cite{}. The former make the assumption of an infinite number of
+agents, so that the population can be represented through a
+distribution over players' states \cite{CainesPaper} . Every agent
+then updates their action profiles depending on this distribution. In
+the latter each agent plays \fb{?} considers a real valued function which is
+a convex combination of the states of the other agents. In both
+formulations, a many-player game is reduced to the set of two-player
+games which each agent is involved in \fb{?}.
 
-In this study, we investigate a variant of the aggregative game known as the \emph{Network
-Aggregative} (NA) Game. This format assumes that there is an underlying communication network
-through which agents interact. Then each agent updates their actions according only to those agents
-with whom they communicate. This significantly relaxes the communication load on each agent and
-lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
-for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Grammatico,
-LeaderFollower, MyopicAgents}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
-Algorithm \cite{Brown, Harris}, in which agents are assumed to be myopic, in that they react solely
-to the previous behaviour of the others.
+Both approaches have been the object of rigorous study and it has been
+shown that agents reach an equilibrium when learning on such games
+(cf.~\cite{MFGLearningPapers} for mean field games and
+\cite{Aggregative Papers} for aggregative games). However, both also
+present a fundamental limitation.  Namely, they both require that
+agents have access to the action profiles of the entire population.
+This could be through communication with all other agents, or through
+the intervention of a central coordinator who is able to \fb{?} the
+entire population. Whilst recent work aims to relax this assumption
+through the introduction of noise \cite{MFG-FP} or partial
+observability \cite{AAMASPaper}, the requirement that each agent
+updates their actions based on the entire population is rather strong
+\fb{and not always supported by empirical evidence}.
+
+In this study, we investigate a variant of aggregative games:
+%known as the
+\emph{network aggregative} (NA) games. This format assumes that
+there is an underlying communication network through which agents
+interact. Then each agent updates their actions according only to
+those agents with whom they communicate. This assumption significantly relaxes
+the communication load on each agent and lifts the need for a central
+coordinator. Recent work on NA games has shown that it is possible
+for agents to reach an equilibrium strategy in an entirely distributed
+manner \cite{Grammatico, LeaderFollower, MyopicAgents}. We contribute
+in this direction by analysing the long term behaviour of multi-agent learning on
+ NA games. In particular, we analyse the fictitious play learning
+algorithm \cite{Brown, Harris}, in which agents are assumed to be
+myopic, in that they react solely to the previous behaviour of the
+others.
+
+\fb{maybe above we can reduce a bit the discussion of NA and motivate
+  a bit more FP.}
 
@@
 
-  The main contribution of this work is to introduce learning on the Network Aggregative Game
-  through the action of Fictitious Play (FP).
+  The main contribution of this work is to introduce learning in
+  network aggregative game through the action of fictitious play (FP).
 
-  We first show that a Nash Equilibrium exists and that FP admits
-  solutions in this setting. In particular, we study zero-sum games and show that
-  FP converges to a fixed point, which for a network without any
-  self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
-  which are not zero-sum, agents following FP are able to
-  achieve no regret.
+  We first show that \fb{in aggregative games played with FP} a Nash Equilibrium exists and that FP admits
+  solutions in this setting. Specifically, we consider zero-sum games
+  and show that FP converges to a fixed point, which for networks
+  without self-loops corresponds to a Nash equilibrium. In
+  addition, we find that, for games which are not zero-sum, agents
+  following FP are able to achieve no regret.
 
-  Finally, we explore FP through numerical simulations to consider the
-  question of whether it always converges. We answer this in the negative by finding a family of
-  games in which action profiles cycle around the Nash Equilibrium. Finally, our experiments
-  document how noise affects the convergence of FP. Our experiments suggest that, under
-  the presence of noise, the algorithm still reaches a fixed point, but perhaps not the Nash
-  Equilibrium. This presents an interesting avenue for future research.
+  Further, we explore FP through numerical simulations to check
+%onsider the question of
+whether it converges in non-zero sum games. We answer this in the
+negative by finding a family of games in which action profiles cycle
+around the Nash equilibrium. Finally, our experiments document how
+noise affects the convergence of FP, suggesting
+%Our experiments suggest
+that,
+under the presence of noise, the algorithm still reaches a fixed
+point, but perhaps not the Nash equilibrium. This presents an
+interesting avenue for future research.
 
@@
 
-The NA game is a recent introduction \cite{Parise2015} which presents a variant of aggregative games
-by adding an underlying structure to the population. Since its introduction, distributed algorithms
-have been built with the aim of finding NE. In particular, \cite{Parise2015, Parise2020} consider
-the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
-topological fixed point towards designing algorithms which will converge to the NE. We note that the
-\emph{Mann Iteration}, one of the algorithms applied in \cite{Parise2020} shares a remarkably
-similar form with the discrete variant of FP. To the best of our knowledge, this link has not been
-explored in the literature and is an avenue for research which we are currently pursuing. Another
-common algorithm for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
-which is explored in \cite{Zhang2020} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
-the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
-common assumption in works concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due to
-its ubiquity in control settings. We have not yet come across works which consider NA games from the
-point of view of payoff matrices, which are more common in multi agent learning settings.
-Furthermore, to the best of our knowledge, this is the first work which introduces the application
+NA games are a recent \cite{Parise2015} extension of
+%introduction  which presents
+%a variant of
+aggregative games by adding an underlying structure to
+the agent population. Since its introduction, distributed algorithms have
+been built with the aim of finding NE in NA games. In particular,
+\cite{Parise2015,Parise2020} consider the case in which payoffs are
+given by Lipschitz functions with unique minimisers and apply standard
+topological fixed-point towards designing algorithms that
+converge to NE. We note that the \emph{Mann Iteration}, one of the
+algorithms applied in \cite{Parise2020} shares a remarkably similar
+form with the discrete variant of FP. To the best of our knowledge,
+this link has not been explored in the literature and is an avenue for
+research which we are currently pursuing. Another common algorithm for
+distributed NE seeking is the projected gradient (resp. subgradient)
+dynamics which is explored in \cite{Zhang2020}
+(resp. \cite{Shokri2020, Shokri2021}). In all of these works, the cost
+function is assumed to be convex, and therefore have a unique
+minimiser. In fact this is a common assumption in works concerning NA
+Games \cite{Zhu2021, Lei2020}, which we believe is due to its ubiquity
+in control settings. We have not yet come across works which consider
+NA games from the point of view of payoff matrices, which are more
+common in multi agent learning settings.  Furthermore, to the best of
+our knowledge, this is the first work which introduces the application
 of a strict learning algorithm in the NA setting.

### 2021-05-20 Documents/FP in NAGs/neurips_2021.tex

--- 2021-05-13 Documents/FP in NAGs/neurips_2020.tex
@@
 
-\title{Fictitious Play in Network Aggregative Games}
+\title{Equilibria and Convergence of Fictitious Play on Network Aggregative Games}
 
@@
 \begin{abstract}
-  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
-  both the left- and right-hand margins. Use 10~point type, with a vertical
-  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
-  bold, and in point size 12. Two line spaces precede the abstract. The abstract
-  must be limited to one paragraph.
+  Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.
+However, as the number of players in a game increase, it is known that the dynamics of learning becomes increasingly chaotic.
+As such, the most rigorous results of learning dynamics are limited to two player games.
+
+  In this study, we contribute towards the study of learning with multiple agents.
+We do this through the introduction of learning on network aggregative games, in which each player's reward is dependent on its own strategy and a convex combination of its neighbours.
+In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game.
+We reach a number of conclusions.
+In particular, we show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium.
+In addition, we show that agents learning through Fictitious Play achieve no-regret, regardless of the choice of game.
+Finally, we present experimental evidence of a family of games for which Fictitious Play reaches a limit cycle and evidence that the introduction of noise has the potential to break this cyclic behaviour and allow agents to reach the Nash Equilibrium.
 \end{abstract}
@@
 
-  \subsection{Existence of the Nash Equilibrium}
-  \label{sec::ExistenceofNE}
+  In this section we present our main results.
+First, we establish the existence of a Nash Equilibrium in the NA game, as in Def.
+\refname{def::NE}.
+Then we show that the Fictitious Play dynamic on the NA game admits solutions (i.e.
+the NA-CTFP exists).
+Finally, we show that NA-CTFP reaches a fixed point when the NA game is zero-sum and that, when the network has no self-loops (i.e.
+is simple), NA-CTFP reaches a Nash Equilibrium.
+For the sake of brevity, we defer the proofs of our statements, as well as the standard topological arguments used to derive them to the Supplementary Material (Sections (S4 - S6)).
 
@@
 
-  To show existence of an NE we will need the following definitions which can be found in most texts on topology \cite{Munkres}.
-
-  \begin{definition}[Convexity]
-  	A set $\mathcal{X}$ is \emph{convex} if, for every $x, y \in \mathcal{X}$ and every $\lambda \in [0, 1]$ we have that $\lambda x + (1 - \lambda)y \in \mathcal{X}$.
-  \end{definition}
-
-	\begin{definition}[Convex Combinations]
-		The point $\sum_{i = 1}^{n} \lambda_i x_i$ is a \emph{convex combination} of the points $x_1, \ldots, x_n$ if $\lambda_i \geq 0$ for all $i$ and $\sum_i \lambda_i = 1$.
-	\end{definition}
-
-	\begin{definition}[Unit Simplex]
-		The $n$-dimensional \emph{unit simplex} is defined as the convex combination of the $n$ standard basis vectors $(e_i)_{i = 1}^n$ in $\mathbb{R}^n$ in which $e_i$ has $1$ in the $i$'th component and $0$ in all others.
-In particular this is given by
-
-		\begin{equation}
-			\Delta = \{x \in \mathbb{R}^n : x = \sum_{i = 1}^n \lambda_i e_i \text{ for some } \lambda_1, \ldots, \lambda_n \geq 0, \sum_i \lambda_i = 1\}
-		\end{equation}
-	\end{definition}
-
-	It follows from the definitions, then, that the unit simplex is a convex set.
-In addition we have that the simplex is \emph{closed} and \emph{bounded} in $\mathbb{R}^n$.
-By the Heine-Borel Theorem \cite{Royden} it is therefore also \emph{compact}.
-The definitions of each of these terms can be found in any standard topology reference and we point the reader to \cite{Royden} for further details.
-
-  \begin{definition}[Upper Semi-Continuous] 
-    A compact-valued correspondence $g: A \rightarrow B$ is
-    \emph{upper semi-continuous} \cite{Findforthis} at a point $a \in A$ if $g(a)$ is non-empty
-    and if, for every sequence $a_n \rightarrow a$ and every sequence
-    $(b_n)$ such that $b_n \in g(a_n)$ for all $n$, there exists a
-    convergent subsequence of $(b_n)$ whose limit point $b$ is in
-    $g(a)$.
-  \end{definition}
-
-  \fb{perhaps we have to introduce some terminology from topology to keep the results self-contained?}
-
-  \begin{theorem}[Kakutani] 
-    Let $A$ be a compact and convex in a Euclidean space and $g: A \rightarrow \mathbf{P}(A)$ (where
-    $\mathbf{P}(A)$ denotes the power set of A) be upper semi-continuous, with nonempty, convex and compact values.
-    Then $g$ has a fixed point, that is a point $\bar{a}$ such that $\bar{a} \in g(\bar{a})$.
-    \cite{Kakutani}
-  \end{theorem}
-
-  Note that, when acting on a simplex, the function $g: \Delta \rightarrow \textbf{P}(\Delta)$, where $\textbf{P}(\Delta)$ denotes all nonempty, closed and convex subsets of $\Delta$ only has to satisfy the upper-semi continuity condition to admit a fixed point.
-
-	\ah{Probably need a quick intro into why the argmax is closed, convex and nonempty.}
+  With these in place, we can state our main results.
 
@@
 
-\subsection{Existence of NA-CTFP}
-
   \begin{theorem}
@@
   \end{theorem}
-
-\subsection{Convergence of NA-CTFP}
 
@@
   assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic
-  orbit seen in Figures \ref{fig::nonconvergentShapley} and \ref{fig::3PlayerChainNoNoise}. Here,
+  orbit seen in Figures \ref{fig::nonconvergentShapley}. Here,
   the orbits reach a stable limit cycle which to be centred around the interior NE.
@@
 
-  \begin{figure}[t]
-    \centering
-    \includegraphics[width = 0.7 \textwidth]{Figures/3PlayerChainNoNoise.png}
-    \caption{\label{fig::3PlayerChainNoNoise} Distance to the Nash Equilibrium strategy along orbits
-    of FP showing oscillations which are bounded away from the NE (i.e. they do not cross the NE).
-    The x-axis shows logarithmic time since FP includes a factor of $1/t$, which has the effect of
-    slowing down the orbit over time.}
-  \end{figure}
-
   As such, we can see that convergent behaviour is not necessarily the norm in the NA-CTFP dynamics.
@@
   \subsection{Addition of Noise}
-
-  \begin{figure}[t]
-    \centering
-    \includegraphics[width = \columnwidth]{Figures/Noise10Player.png}
-    \caption{\label{fig::Noise10Player} Trajectories of NA-CTFP in a 10 player game with additive noise (Left) No noise is introduced and learning converges directly to an NE.
-(Middle) $\gamma = 0.1$, the trajectories converge to a fixed point but removed from the NE.
-(Right) $\gamma = 0.5$, the trajectories converge to a fixed point which is even further away from the NE.}
-  \end{figure}
 
@@
 
-  In Figure \ref{fig::Noise10Player}, we consider a zero-sum NA game with 10 players. When there is
+  In Figure \ref{fig::Noise20Player}, we consider a zero-sum NA game with 20 players. When there is
   no noise, it can be seen that FP reaches a fixed point which, since we set $w^{\mu \mu} = 0$,
@@
   orbits do still reach a stationary state in the long run which suggests that FP is still able to
-  converge with the introduction of noise. Figure \ref{fig::Noise20Player} shows similar behaviour
-  for $N = 20$, and in our experiments we found this to be ubiquitous regardless of the choice of
-  $N$ or $n$.
+  converge with the introduction of noise.
 
@@
   behave in the same way. It can be seen that a small amount of noise has the effect of decreasing
-  the size of the periodic orbit (c.f. Figure \ref{fig::3PlayerChainNoNoise}). However, as $\gamma$
+  the size of the periodic orbit. However, as $\gamma$
   is increased to $0.5$, the algorithm seems to exhibit convergence to the NE. The implication is

### 2021-05-20 Documents/FP in NAGs/neurips_2020.tex
minor mods

@@
 
+\fb{multi agent $\to$ multi-agent}
+
 Multi-Agent Learning requires a number of agents to adapt in response
@@
 converge to NE. We note that the \emph{Mann Iteration}, one of the
-algorithms applied in \cite{Parise2020} shares a remarkably similar
+algorithms applied in \cite{Parise2020}, shares a remarkably similar
 form with the discrete variant of FP. To the best of our knowledge,
-this link has not been explored in the literature and is an avenue for
-research which we are currently pursuing. Another common algorithm for
+this link has not been explored in the literature and is a venue for
+research that we are currently pursuing. Another common algorithm for
 distributed NE seeking is the projected gradient (resp. subgradient)
-dynamics which is explored in \cite{Zhang2020}
-(resp. \cite{Shokri2020, Shokri2021}). In all of these works, the cost
+dynamics, which is explored in \cite{Zhang2020}
+(resp.~\cite{Shokri2020, Shokri2021}). In all of these works, the cost
 function is assumed to be convex, and therefore have a unique
@@
 NA games from the point of view of payoff matrices, which are more
-common in multi agent learning settings.  Furthermore, to the best of
+common in multi-agent learning settings.  Furthermore, to the best of
 our knowledge, this is the first work which introduces the application
-of a strict learning algorithm in the NA setting.
+of a strict \fb{?} learning algorithm in the NA setting.
+
+\fb{the section on FP is very well-read, but maybe not everything is
+  relevant for the following. I'd rather try to focus on what is
+  relevant for our paper and contrast approaches.  Also, it is not
+  clear what is the interest of FP for multi-agent learning.  }
 
 \paragraph{Fictitious Play}
-
-Fictitious Play was introduced by Brown in 1951 \cite{BrownPublished, BrownUnpublished} as a
-'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
-time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
-\cite{Robinson}. Since then a number of proofs of convergence were determined in 2 player games
-\cite{Miyasawa, Polak, Berger, Monderer and Sela, Monderer and Shapley}, as well as corresponding
-convergence rates \cite{Harris, Shapiro}. Many results hold for both the discrete and continuous
-variants of FP. Their relation was finally solved by Hofbauer \cite{Hofbauer}, who showed that
-attractors of the discrete time process are also attractors for the continuous time variant. As
-such, most of the analysis on FP focuses on the continuous time variant \cite{Ostrovski}. It was
-later shown in \cite{Shapley} that there is a family of games (now called the \emph{Shapley family})
-for which FP does not converge at all but rather shows periodic behaviour. This led to research
-which looks at this non convergent behaviour, specifically showing the existence of more periodic
-orbits as well as chaotic behaviour \cite{Sparrow}. However, the work looking at fictitious play
-where there are more than two agents is sparse. \cite{Sela} considers a game in which a multi-player
-game is decomposed by requiring that each agent engage in a two person game against each of the
-opponent. Their payoff is given by the sum of payoffs in all of these subgames. It was found that,
-if this game is zero sum, then FP will converge. Similar results for more than two players were
-found for games with identical interests in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
-of FP was considered in a Mean Field Game, and it was found again that the algorithm converges for
-zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
-and Valkanova in 2020 \cite{Ewerhart} in which they showed that fictitious play converges in network
-games, where each agent is engaged in a two-player game with each of their neighbours. The rate of
-convergence was found to be independent of the network size.  Our work extends the analysis of FP in
-multiplayer games by considering its action in NA Games, so that the agents do not play individual
-games against each of their neighbours but rather a single game against the aggregate of their
-neighbours. In particular we also extend a result for two player games found by Ostrovski and van
-Strein \cite{Payoff Performance} which showed that FP achieves no-regret to the multi-player
-setting.
+%
+Fictitious Play \cite{BrownPublished,
+  BrownUnpublished}
+was introduced
+%by Brown in 1951
+as a 'natural' way
+%in which
+to approximate Nash Equilibris in zero-sum games. At the time, it was
+shown that a discrete variant of FP
+%the algorithm would
+converge to 
+NE in two-player zero-sum games \cite{Robinson}. Since then, a number
+of results on convergence were proved in two-player games
+\cite{Miyasawa, Polak, Berger, Monderer and Sela, Monderer and
+  Shapley}, including
+%as well as
+corresponding convergence rates \cite{Harris,
+  Shapiro}.
+%Many results hold for both the discrete and continuous
+%variants of FP.
+The relation between the discrete and continuous variants of FP was
+finally solved by Hofbauer \cite{Hofbauer}, who showed that attractors
+of the discrete time process are also attractors for the continuous
+time variant. As such, most of the analysis on FP focuses on the
+continuous time variant \cite{Ostrovski}. It was later shown in
+\cite{Shapley} that there is a family of games (now called the
+\emph{Shapley family}) for which FP does not converge, but
+rather shows periodic behaviour. \fb{we might remove the following: This led to research which looks at
+this non convergent behaviour, specifically showing the existence of
+more periodic orbits as well as chaotic behaviour
+\cite{Sparrow}.} However, the work looking at fictitious play
+%where there are
+with more than two agents is sparse. In \cite{Sela}
+%considers a game in which a
+multi-player games are decomposed
+%by requiring that each agent engage in a
+in two-player games between each pair of players in the game.
+%against each of the opponent.
+Each agent's payoff is given by the sum of payoffs in all of these
+subgames. It was found that, if this game is zero-sum, then FP will
+converge. Similar results for more than two players were found for
+games with identical interests \fb{?} in \cite{MondererShapley1994}. In
+\cite{FPMFG}, the action of FP was considered in a mean field game,
+and it was found again that the algorithm converges for zero-sum
+games. The most general result, and the one most similar to our own,
+appears in
+%was found by Ewerhart and Valkanova in 2020
+\cite{Ewerhart}, in which
+the authors show that fictitious play converges in network games, where
+each agent is engaged in a two-player game with each of their
+neighbours. The rate of convergence was found to be independent of the
+network size.  Our work extends the analysis of FP in multi-player
+games by considering its action in NA Games, so that the agents do not
+play individual games against each of their neighbours but rather a
+single game against the aggregate of their neighbours. In particular
+we also extend a result for two player games found by Ostrovski and
+van Strein \cite{Payoff Performance} which showed that FP achieves
+no-regret in the multi-player setting.
 
 \section{Preliminaries}
+
+\fb{I'd rather not leave an empty space between section and
+  subsection.}
+
 \subsection{Network Aggregative Games}
@@
 
-  The model we consider is that there is a set $\agentset = {1,
-           \ldots , N}$ of agents who are connected through an underlying
-          interaction graph. This graph is given by the tuple
-          $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
-          the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
-          connected. Formally,
+The model we consider consists of
+%is that there is
+a set $\agentset = \{1,
+           \ldots , N \}$ of agents, who are connected through an underlying
+           interaction graph.
+           %This graph is given by the tuple
+          %$(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
+          %the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
+           %connected.
+           More formally:
+%        
+  \begin{definition}[Interaction Graph] \label{interactiongraph}
+    Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
+    \weightset))$ is such that
+    \begin{itemize}
 
-  \begin{definition}[Interaction Graph]
-    Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
-    \weightset))$ such that
-    \begin{itemize}
-    \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent
-        $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in \edgeset\}$.
-      \item $\weightset \in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu
-        \nu}$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
+    \item $\edgeset \subseteq \agentset^2$.  Then, the set of
+      neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in
+      \agentset \mid (\mu, \nu) \in \edgeset\}$.
+
+    \item $\weightset \in M_N(\mathbb{R})$ is the weighted \fb{or weight?} adjacency matrix, whose elements $w^{\mu
+        \nu} \in [0, 1]$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
         \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
@@
 
-  With the above definition, we can formalise the network aggregative (NA) game:
-
-  \begin{definition}[Network Aggregative Game]
-    A Network Aggregative game is defined as the tuple $\Gamma = (I, (\actionset{\mu},
-        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph,
-        $\actionset{\mu}$ and $\utility{\mu}$ refer to $\mu$'s set of actions (with cardinality
-        $|\actionset{\mu}| = n$) and utility function respectively.
+  Given Def.~\ref{interactiongraph} of interaction graph,
+  %With the above definition,
+  we introduce network aggregative (NA) games:
+%
+  \begin{definition}[NA Game]
+    A {\em network aggregative game} is
+    %defined as the
+a tuple $\Gamma = (I, (\actionset{\mu},
+    \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is an
+    interaction graph, and for every agent $\mu \in \mathcal{N}$, $\actionset{\mu}$ and $\utility{\mu}$
+    %refer to
+    are $\mu$'s set of actions (with cardinality $|\actionset{\mu}| = n$)
+    and utility function respectively.
   \end{definition}
 
-  We consider the \emph{state} of agent $\mu$ to be the probability vector $\xmu \in
-  \mathbb{R}^n$ where $\xmu_i$ is the probability with which the agent plays action $i$. It
-  should be noted that this probability vector is often referred to as $\mu$'s \emph{mixed
-  strategy}. With this in mind, we can construct, as their state space, the unit simplex on
-  agent $\mu$'s action set. This is given as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \,
-  \sum_i \xmuaction{i} = 1\}$. Also associated with each agent is a utility function
+  We define the \emph{state} of agent $\mu$ to be the probability
+  vector $\xmu \in \mathbb{R}^n$, where $\xmu_i$ is the probability
+  with which agent $\mu$ plays action $i$.
+  %It should be noted that
+  This
+  probability vector is often referred to as $\mu$'s \emph{mixed
+    strategy}. With this in mind, we can construct, as their state
+  space, the {\em unit simplex} $\Delta_\mu$ on agent $\mu$'s action set, which
+  is defined
+  as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
+  \xmuaction{i} = 1\}$. Also associated with each agent is a utility
+  function
 
-  The utility function, for each agent $\mu$, is given as $u^\mu(\xmu, \xnotmu)$ in which we use
-  the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that this requires
-  that each agent play the same strategy against all of their neighbours. What is unique about the
-  NA game is the structure of the payoffs themselves. In this format, each agent is receives a
-  reference $\sigma$ which is a weighted sum of each of their neighbours
-  state. Formally
+  The utility, for each agent $\mu$ and action profile
+  $(\xmu, \xnotmu)$, is given as $u^\mu(\xmu, \xnotmu)$ in which we
+  use the standard notation $-\mu$ to refer to all agents other than
+  $\mu$. Notice that this requires that each agent plays the same
+  strategy against all of their neighbours. What is unique about 
+  NA games is the structure of the payoffs themselves. In this format,
+  each agent $\mu$ receives a reference $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a weighted sum
+  of each of their neighbours state.
+  %Formally
   %
-  \begin{equation}
-    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
-  \end{equation}
+%  \begin{equation}
+%    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
+%  \end{equation}
 
-  Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
-  instead of having to consider the actions of the entire population, or play individual games
-  against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a
-  `measurement' of the local aggregate state and optimise with respect to this measurement.
-  This allows us to make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
-  particular, we consider that the agent is engaged in a matrix game against the
-  reference vector so that
+  Then, the agent must optimise their payoff with respect to the
+  reference vector $\sigma^{\mu}$. Thus, instead of considering
+  the actions of the entire population, or play individual games
+  against each of their neighbours, the agent only considers
+  $\sigma^\mu$ as a `measurement' of the local aggregate state and
+  optimises with respect to this measurement.  This allows us to make
+  the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
+  particular, we consider that the agent is engaged in a matrix game
+  against the reference vector so that
   %
@@
   \end{equation}
+%
+  where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can write the game $\Gamma$ with the payoff
+  matrices $A^\mu$ in place of the utility functions
+  $\utility{\mu}$. Hence, the NA game allows for the reduction of a
+  multi-player game into a series of two-player games. The agent's goal
+  is to maximise their payoff with respect to the reference vector. As
+  such, we define the best response correspondence $BR^\mu$, which maps
+  every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
+    \refmu)}$.
 
-  where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we can write
-  the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
-  $\utility{\mu}$. The NA game allows for the reduction of a multiplayer game into a series of
-  two-player games. The agent's goal is to maximise their payoff with respect to the reference
-  vector. As such, we define the best response correspondence $BR^\mu$ which maps any $\refmu$
-  the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$.
-
-  Finally, a central concept of game theory is that of the Nash Equilibrium, in which no rational
-  agent has the incentive to deviate from their current state. This can be formalised by saying
-  that all agents are playing the best response to each other.
-
-  This leads naturally to the definition of a Nash Equilibrium in an NA Game as
-
+  Finally, a central concept of game theory is that of the Nash
+  Equilibrium, in which no rational agent has the incentive to deviate
+  from their current state. This can be formalised by saying that all
+  agents are playing their best response to each other.
+%
+  This leads naturally to the definition of a Nash Equilibrium in an NA game as
+%
   \begin{definition}(NE) \label{def::NE}
-    The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,  
+    The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is a {\em
+      Nash equilibrium} if, for all $\mu$,
     \begin{equation*}
@@
   \begin{remark}
-    It can be seen that the concept of the Nash Equilibrium in the NA game is a natural
-    extension of the NE in a bimatrix game $(A, B)$. In particular, if we consider an NA game
-    with only two players and no self-loops then the above definition yields
-
-    \begin{equation*}
-      \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2}), 
-    \end{equation*}
-
+    %It can be seen that
+The notion of Nash equilibrium in the NA game is a natural
+extension of the NE in a bimatrix game.
+%$(A, B)$.
+In particular, if we consider an NA game with only two players and no
+self-loops then the above definition yields that $ \NE{1}$ is an NE iff
+%
+%    \begin{equation*}
+ $     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2})$,
+%    \end{equation*}
+%
     and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
@@
 
-  Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally
-
-  \begin{equation}
-    \sum_\mu u^\mu(\xmu, \weightedsum) = 0.
-  \end{equation}
+  Finally, we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally,
+%
+%  \begin{equation}
+    $\sum_\mu u^\mu(\xmu, \weightedsum) = 0$.
+%  \end{equation}
 

### 2021-05-20 Documents/FP in NAGs/neurips_2020.tex
minor mods

@@
 
-  Fictitious Play requires that, at the current time, each agent considers the average state
-  of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
-  opponent. As such, each agent $\mu$ must update their state according to the time-average of
-  $\refmu$. To formalise this we write
+  Fictitious Play requires that, at the current time, each agent
+  considers the average state of their opponent in the past, and
+  respond optimally (i.e., play a best response) to this state. In the
+  case of an NA game, each agent considers their reference vector to
+  be their opponent. As such, each agent $\mu$ must update their state
+  according to the time-average of $\refmu$. To formalise this we
+  write
+
+  \fb{What is $\avgref{\mu}$?}
 
@@
 
-  Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
-  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
+  Using this, we follow \cite{Ewerhart,Harris}
+  %in the footsteps of Ewerhart \cite{} and Harris \cite{}
+  to define
+  Fictitious Play in continuous time, but adapted
+  %with a slight adaptation for the
+  to NA games.
   %
-  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)]
-    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
-    and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
-    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
+  \fb{is there any way we can make the following definition more intuitive?}
+  \begin{definition}[NA-CTFP]
+    A {\em network aggregative - continuous time fictitious play} is
+    defined as a measurable map $m$ with components $m^\mu$ such that
+    for all $\mu$ and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow
+      \Delta_\mu$ satisfies $m^\mu(t) \in BR^\mu(\alpha_{\sigma}^\mu)$
+      for almost all $t \geq 1$.
   \end{definition}
@@
     the off diagonal. We write the time-average of both agents' state as
+%  
+%    \begin{align}
+ $     \alpha^\mu(t; x) = \frac{1}{t} \int_0^{\fb{t}} \xmu(t) \, dt$, for $\mu \in \{1, 2\}$.
+  %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
+    %    \end{align}
 
-    \begin{align}
-      \alpha^\mu(t; x) = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
-  %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
-    \end{align}
+   Hence, $\alpha^\mu(t; m)$ denotes the time average of the
+   strategies played by agent $\mu$ up to time $t$ when the strategies
+   are given by $\xmu(t)$. Note that we often reduce the notation to
+   $\alpha^\mu(t)$. Then, fictitious play requires that the agents
+   update their strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t)
+   \in BR^2(\alpha^1(t))$. It can be seen, therefore, that the NA-CTFP
+   is a natural extension of CTFP in the classical two-player setting
+   \cite{}.
+  \end{remark}
 
-    In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
-    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
-    strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
-    seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
-    two-player setting \cite{}.
-  \end{remark}
+  \fb{these remarks are very helpful.}
 
@@
   \begin{assumption}\label{ass::rowstochastic}
-    The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
-    that the sum elements in each row of $\weightset$ is equal to one. This assumption is
-    made to ensure that the analysis of NA games can be derived as a natural extension to the
-    classical setting of two-player games. We can think of the row stochastic condition as the
-    ability of each agent to prioritise the state information it receives from each of its
-    neighbours. It is also a classical assumption made in the analysis of network games
-    \cite{one of the network game papers} and can is straightforward to implement \cite{Eyad}.
+    The weighted adjacency matrix $\weightset$ is constant and
+    \emph{row stochastic}, meaning that the sum elements in each row
+    of $\weightset$ is equal to one. This assumption is made to ensure
+    that the analysis of NA games can be derived as a natural
+    extension to the classical setting of two-player games. We can
+    think of the row stochastic condition as the ability of each agent
+    to prioritise the state information it receives from each of its
+    neighbours. It is also a classical assumption made in the analysis
+    of network games \cite{one of the network game papers} and is
+    straightforward to implement \cite{Eyad}.
   \end{assumption}
@@
   \begin{assumption}\label{ass::matrixgame}
-    The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
-    have a rich history in game theory and has generated a number of prototypical examples for
-    economic study including the Prisoner's Dilemma game (see \cite{Axelrod} for an interesting
-    implementation of this). They also allow for the design of multi-agent systems in
-    computational settings, particularly in the case of task and resource allocation \cite{AGT
-    and some of the Applied Game Theory Papers}. It should be noted, however, that game
-    theoretic analysis is starting to consider various other forms of utility functions,
-    including monotone \cite{Maryam} and convex \cite{Parise}. We believe that the analysis of
-    Fictitious Play should follow in these developments and we consider it as an important area
-    of future work.
+    The payoffs are given through matrix games and, therefore, are
+    bilinear. Payoff matrices have a rich history in game theory and
+    has generated a number of prototypical examples for economic study
+    including the Prisoner's Dilemma game (see \cite{Axelrod} for an
+    interesting implementation of this). They also allow for the
+    design of multi-agent systems in computational settings,
+    particularly in the case of task and resource allocation \cite{AGT
+      and some of the Applied Game Theory Papers}. It should be noted,
+    however, that game theoretic analysis is starting to consider
+    various other forms of utility functions, including monotone
+    \cite{Maryam} and convex \cite{Parise}. We believe that the
+    analysis of Fictitious Play should follow in these developments
+    and we consider it as an important area of future work.
   \end{assumption}
@@
   \begin{assumption}\label{ass::sameactions}
-    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
-    a classical assumption which is made in most game theoretic settings and includes, as a
-    special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
-    in \cite{Ewerhart}, CTFP was analysed without this requirement.  
+    The cardinality of each action set $|\actionset{\mu}|$ is equal
+    for all agents. This is a classical assumption which is made in
+    most game-theoretic settings and includes, as a special case, the
+    analysis of homogeneous agents \cite{}. However, it should be
+    noted that, in \cite{Ewerhart}, CTFP was analysed without this
+    requirement.
   \end{assumption}
@@
   \begin{assumption}\label{ass::zerosum}
-    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
-    of states $(x^\mu)_{\mu \in N^\mu}$. This is, perhaps, one of the stronger assumptions in
-    our analysis, and is required for the fixed point analysis. However, in Section
-    \ref{sec::CCEConvergence}, we perform a regret analysis that considers the long term
-    behaviour of NA-CTFP without this assumption.
+    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu,
+    \weightedsum)$ for any set of states $(x^\mu)_{\mu \in
+      N^\mu}$. This is, perhaps, one of the strongest assumptions in
+    our analysis, and is required for the fixed point
+    analysis \fb{repetition}. Nonetheless, in Section \ref{sec::CCEConvergence}, we
+    perform a regret analysis that considers the long term behaviour
+    of NA-CTFP without this assumption.
   \end{assumption}

### 2021-05-21 Documents/FP in NAGs/neurips_2021.tex
Updated 2021 doc

@@
 
-Multi Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
+Multi-Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
 each agent must adapt in response to the behaviour of the other agents. This leads to a
@@
 pronounced as the number of agents increase \cite{Sanders}.
-In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi agent learning \cite{PiliourasChaoticMaps}.
-This, of course, poses a problem for AI safety, for which it is necessary that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
+In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi-agent learning \cite{PiliourasChaoticMaps}.
+This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
 
@@
 states \cite{CainesPaper} . Every agent then updates their action profiles depending on this
-distribution. In the latter each agent plays considers a real valued function which is a convex
-combination of the states of the other agents. In both formulations, a many player game is reduced
-to the set of two player games which each agent is involved in.
+distribution. In the latter each agent considers a real valued function which is a convex
+combination of the states of the other agents. Both formulation allows for a many player game to be reduced to a set of two-player games.
 
@@
 This could be through communication with all other agents, or through the intervention of a central
-coordinator who is able to the entire population. Whilst recent work aims to relax this assumption
+coordinator who is able view the entire population. Whilst recent work aims to relax this assumption
 through the introduction of noise \cite{MFG-FP} or partial observability \cite{AAMASPaper}, the
-requirement that each agent updates their actions based on the entire population is rather strong.
+requirement that each agent updates their actions based on the entire population is rather strong and not always supported by empirical evidence.
 
@@
 
-  We first show that a Nash Equilibrium exists and that FP admits
+  We first show that, in aggregative games played with FP, a Nash Equilibrium exists and that FP admits
   solutions in this setting. In particular, we study zero-sum games and show that
@@
 its ubiquity in control settings. We have not yet come across works which consider NA games from the
-point of view of payoff matrices, which are more common in multi agent learning settings.
+point of view of payoff matrices, which are more common in multi-agent learning settings.
 Furthermore, to the best of our knowledge, this is the first work which introduces the application
-of a strict learning algorithm in the NA setting.
+of a learning algorithm in the NA setting.
 
@@
 later shown in \cite{Shapley} that there is a family of games (now called the \emph{Shapley family})
-for which FP does not converge at all but rather shows periodic behaviour. This led to research
-which looks at this non convergent behaviour, specifically showing the existence of more periodic
-orbits as well as chaotic behaviour \cite{Sparrow}. However, the work looking at fictitious play
+for which FP does not converge at all but rather shows periodic behaviour. However, the work looking at fictitious play
 where there are more than two agents is sparse. \cite{Sela} considers a game in which a multi-player
@@
 if this game is zero sum, then FP will converge. Similar results for more than two players were
-found for games with identical interests in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
+found for games where all agents share the same payoff in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
 of FP was considered in a Mean Field Game, and it was found again that the algorithm converges for
@@
 \section{Preliminaries}
+In this section we introduce the network aggregative game framework, as well as defining FP on such a game.
+
 \subsection{Network Aggregative Games}
@@
   An interesting point to note is that this behaviour is in stark contrast to the replicator
-  dynamic (RD) \cite{Maynard-Smith}, another adaptive algorithm linked to multi agent learning
+  dynamic (RD) \cite{Maynard-Smith}, another adaptive algorithm linked to multi-agent learning
   \cite{CyclesAdversarialLearning}. In \cite{Imhof} and \cite{Galla}, it was found that the
@@
 Finally, our work has a strong impact on the study of the Network Aggregative Game, which has strong
-applications in multi agent control \cite{GrammaticoAggregativeControl}. We 
+applications in multi-agent control \cite{GrammaticoAggregativeControl}. We 
 believe that our work makes a strong step towards ensuring that systems which learn and adapt on

### 2021-05-24 Documents/FP in NAGs/neurips_2021.tex
Included Bib File for Neurips

@@
 \begin{abstract}
-  Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.
-However, as the number of players in a game increase, it is known that the dynamics of learning becomes increasingly chaotic.
-As such, the most rigorous results of learning dynamics are limited to two player games.
-
-  In this study, we contribute towards the study of learning with multiple agents.
-We do this through the introduction of learning on network aggregative games, in which each player's reward is dependent on its own strategy and a convex combination of its neighbours.
+Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.In this study, we contribute towards the study of learning with multiple agents.
+We do this through the introduction of learning on network aggregative games, in which each player's reward depends only on its own strategy and a convex combination of its neighbours.
 In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game.
-We reach a number of conclusions.
-In particular, we show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium.
+We show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium.
 In addition, we show that agents learning through Fictitious Play achieve no-regret, regardless of the choice of game.
@@
 
-Multi-Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
+Multi-Agent Learning \cite{Schwartz2014} requires a number of agents to adapt in an environment where
 each agent must adapt in response to the behaviour of the other agents. This leads to a
@@
 policies. Even when there are a small number of agents in the game, learning has been shown to lead
-to non-stationary, and even chaotic behaviour \cite{SatoChaos}, and this problem becomes even more
-pronounced as the number of agents increase \cite{Sanders}.
-In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi-agent learning \cite{PiliourasChaoticMaps}.
+to non-stationary, and even chaotic behaviour \cite{Sato2002}, and this problem becomes even more
+pronounced as the number of agents increase \cite{Sanders2018}.
+In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi-agent learning \cite{Chotibut2021}.
 This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
@@
 number of agents, so that the population can be represented through a distribution over players'
-states \cite{CainesPaper} . Every agent then updates their action profiles depending on this
+states \cite{Huang2006} . Every agent then updates their action profiles depending on this
 distribution. In the latter each agent considers a real valued function which is a convex
@@
 
-Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{MFGLearningPapers} for Mean Field Games and
-\cite{Aggregative Papers} for Aggregative Games). However, both also present a fundamental limitation.
+Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{Perrin2020} for Mean Field Games and
+\cite{Jensen2010, DePersis2020, Parise2020} for Aggregative Games). However, both also present a fundamental limitation.
 Namely, they both require that agents have access to the action profiles of the entire population.
@@
 coordinator who is able view the entire population. Whilst recent work aims to relax this assumption
-through the introduction of noise \cite{MFG-FP} or partial observability \cite{AAMASPaper}, the
+through the introduction of noise \cite{Perrin2020} or partial observability \cite{Elie2020}, the
 requirement that each agent updates their actions based on the entire population is rather strong and not always supported by empirical evidence.
@@
 lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
-for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Grammatico,
-LeaderFollower, MyopicAgents}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
-Algorithm \cite{Brown, Harris}, in which agents are assumed to be myopic, in that they react solely
+for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}.
+We contribute in this direction by analysing the long term behaviour of learning on an NA game.
+In particular, we analyse the Fictitious Play Learning
+Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely
 to the previous behaviour of the others.
@@
 the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
-topological fixed point towards designing algorithms which will converge to the NE. We note that the
-\emph{Mann Iteration}, one of the algorithms applied in \cite{Parise2020} shares a remarkably
-similar form with the discrete variant of FP. To the best of our knowledge, this link has not been
-explored in the literature and is an avenue for research which we are currently pursuing. Another
-common algorithm for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
-which is explored in \cite{Zhang2020} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
+topological fixed point towards designing algorithms which will converge to the NE. Another
+approach for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
+which is explored in \cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
 the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
@@
 
-Fictitious Play was introduced by Brown in 1951 \cite{BrownPublished, BrownUnpublished} as a
+Fictitious Play was introduced in 1951 \cite{Brown1949} as a
 'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
 time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
-\cite{Robinson}. Since then a number of proofs of convergence were determined in 2 player games
-\cite{Miyasawa, Polak, Berger, Monderer and Sela, Monderer and Shapley}, as well as corresponding
-convergence rates \cite{Harris, Shapiro}. Many results hold for both the discrete and continuous
-variants of FP. Their relation was finally solved by Hofbauer \cite{Hofbauer}, who showed that
-attractors of the discrete time process are also attractors for the continuous time variant. As
-such, most of the analysis on FP focuses on the continuous time variant \cite{Ostrovski}. It was
-later shown in \cite{Shapley} that there is a family of games (now called the \emph{Shapley family})
-for which FP does not converge at all but rather shows periodic behaviour. However, the work looking at fictitious play
-where there are more than two agents is sparse. \cite{Sela} considers a game in which a multi-player
+\cite{Robinson1951}. Since then a number of proofs of convergence were determined in 2 player games
+\cite{Miyasawa1961, Metrick1994, Berger2007, Monderer1997, Monderer1996}. Many results hold for both the discrete and continuous variants of FP. However, the work looking at FP
+where there are more than two agents is sparse. \cite{Sela1999} considers a game in which a multi-player
 game is decomposed by requiring that each agent engage in a two person game against each of the
@@
 if this game is zero sum, then FP will converge. Similar results for more than two players were
-found for games where all agents share the same payoff in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
-of FP was considered in a Mean Field Game, and it was found again that the algorithm converges for
+found for games where all agents share the same payoff in \cite{Monderer1996}. In \cite{Perrin2020}, the action
+of FP was considered in a Mean Field Game, with convergence in
 zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
-and Valkanova in 2020 \cite{Ewerhart} in which they showed that fictitious play converges in network
-games, where each agent is engaged in a two-player game with each of their neighbours. The rate of
-convergence was found to be independent of the network size.  Our work extends the analysis of FP in
+and Valkanova in 2020 \cite{Ewerhart2020} in which it was found that FP converges in network
+games, where each agent is engaged in a two-player game with each of their neighbours Our work extends the analysis of FP in
 multiplayer games by considering its action in NA Games, so that the agents do not play individual
@@
 neighbours. In particular we also extend a result for two player games found by Ostrovski and van
-Strein \cite{Payoff Performance} which showed that FP achieves no-regret to the multi-player
+Strien \cite{Ostrovski2014} which showed that FP achieves no-regret to the multi-player
 setting.
@@
 
-  The model we consider is that there is a set $\agentset = {1,
-           \ldots , N}$ of agents who are connected through an underlying
-          interaction graph. This graph is given by the tuple
-          $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
-          the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
-          connected. Formally,
+The model we consider consists of
+%is that there is
+a set $\agentset = \{1,
+\ldots , N \}$ of agents, who are connected through an underlying
+interaction graph.
+%This graph is given by the tuple
+%$(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
+%the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
+%connected.
+More formally:
+%        
+\begin{definition}[Interaction Graph] \label{interactiongraph}
+	Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
+	\weightset))$ is such that
+	\begin{itemize}
 
-  \begin{definition}[Interaction Graph]
-    Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
-    \weightset))$ such that
-    \begin{itemize}
-    \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent
-        $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in \edgeset\}$.
-      \item $\weightset \in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu
-        \nu}$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
+		\item $\edgeset \subseteq \agentset^2$.  Then, the set of
+		neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in
+		\agentset \mid (\mu, \nu) \in \edgeset\}$.
+
+		\item $\weightset \in M_N(\mathbb{R})$ is the weight adjacency matrix, whose elements $w^{\mu
+			\nu} \in [0, 1]$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
 		\in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
@@
 
-  With the above definition, we can formalise the network aggregative (NA) game:
-
-  \begin{definition}[Network Aggregative Game]
-    A Network Aggregative game is defined as the tuple $\Gamma = (I, (\actionset{\mu},
-        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph,
-        $\actionset{\mu}$ and $\utility{\mu}$ refer to $\mu$'s set of actions (with cardinality
-        $|\actionset{\mu}| = n$) and utility function respectively.
+Given Def.~\ref{interactiongraph} of interaction graph,
+%With the above definition,
+we introduce network aggregative (NA) games:
+%
+\begin{definition}[NA Game]
+	A {\em network aggregative game} is
+	%defined as the
+	a tuple $\Gamma = (I, (\actionset{\mu},
+	\utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is an
+	interaction graph, and for every agent $\mu \in \mathcal{N}$, $\actionset{\mu}$ and $\utility{\mu}$
+	%refer to
+	are $\mu$'s set of actions (with cardinality $|\actionset{\mu}| = n$)
+	and utility function respectively.
 \end{definition}
 
-  We consider the \emph{state} of agent $\mu$ to be the probability vector $\xmu \in
-  \mathbb{R}^n$ where $\xmu_i$ is the probability with which the agent plays action $i$. It
-  should be noted that this probability vector is often referred to as $\mu$'s \emph{mixed
-  strategy}. With this in mind, we can construct, as their state space, the unit simplex on
-  agent $\mu$'s action set. This is given as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \,
-  \sum_i \xmuaction{i} = 1\}$. Also associated with each agent is a utility function
+We define the \emph{state} of agent $\mu$ to be the probability
+vector $\xmu \in \mathbb{R}^n$, where $\xmu_i$ is the probability
+with which agent $\mu$ plays action $i$.
+%It should be noted that
+This
+probability vector is often referred to as $\mu$'s \emph{mixed
+	strategy}. With this in mind, we can construct, as their state
+space, the {\em unit simplex} $\Delta_\mu$ on agent $\mu$'s action set, which
+is defined
+as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
+\xmuaction{i} = 1\}$. Also associated with each agent is a utility
+function
 
-  The utility function, for each agent $\mu$, is given as $u^\mu(\xmu, \xnotmu)$ in which we use
-  the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that this requires
-  that each agent play the same strategy against all of their neighbours. What is unique about the
-  NA game is the structure of the payoffs themselves. In this format, each agent is receives a
-  reference $\sigma$ which is a weighted sum of each of their neighbours
-  state. Formally
+The utility, for each agent $\mu$ and action profile
+$(\xmu, \xnotmu)$, is given as $u^\mu(\xmu, \xnotmu)$ in which we
+use the standard notation $-\mu$ to refer to all agents other than
+$\mu$. Notice that this requires that each agent plays the same
+strategy against all of their neighbours. What is unique about 
+NA games is the structure of the payoffs themselves. In this format,
+each agent $\mu$ receives a reference $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a weighted sum
+of each of their neighbours state.
+%Formally
 %
-  \begin{equation}
-    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
-  \end{equation}
+%  \begin{equation}
+%    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
+%  \end{equation}
 
-  Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
-  instead of having to consider the actions of the entire population, or play individual games
-  against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a
-  `measurement' of the local aggregate state and optimise with respect to this measurement.
-  This allows us to make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
-  particular, we consider that the agent is engaged in a matrix game against the
-  reference vector so that
+Then, the agent must optimise their payoff with respect to the
+reference vector $\sigma^{\mu}$. Thus, instead of considering
+the actions of the entire population, or play individual games
+against each of their neighbours, the agent only considers
+$\sigma^\mu$ as a `measurement' of the local aggregate state and
+optimises with respect to this measurement.  This allows us to make
+the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
+particular, we consider that the agent is engaged in a matrix game
+against the reference vector so that
 %
@@
 \end{equation}
+%
+where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can write the game $\Gamma$ with the payoff
+matrices $A^\mu$ in place of the utility functions
+$\utility{\mu}$. Hence, the NA game allows for the reduction of a
+multi-player game into a series of two-player games. The agent's goal
+is to maximise their payoff with respect to the reference vector. As
+such, we define the best response correspondence $BR^\mu$, which maps
+every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
+	\refmu)}$.
 
-  where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we can write
-  the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
-  $\utility{\mu}$. The NA game allows for the reduction of a multiplayer game into a series of
-  two-player games. The agent's goal is to maximise their payoff with respect to the reference
-  vector. As such, we define the best response correspondence $BR^\mu$ which maps any $\refmu$
-  the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$.
-
-  Finally, a central concept of game theory is that of the Nash Equilibrium, in which no rational
-  agent has the incentive to deviate from their current state. This can be formalised by saying
-  that all agents are playing the best response to each other.
-
-  This leads naturally to the definition of a Nash Equilibrium in an NA Game as
-
+Finally, a central concept of game theory is that of the Nash
+Equilibrium, in which no rational agent has the incentive to deviate
+from their current state. This can be formalised by saying that all
+agents are playing their best response to each other.
+%
+This leads naturally to the definition of a Nash Equilibrium in an NA game as
+%
 \begin{definition}(NE) \label{def::NE}
-    The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,  
+	The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is a {\em
+		Nash equilibrium} if, for all $\mu$,
 	\begin{equation*}
@@
 \begin{remark}
-    It can be seen that the concept of the Nash Equilibrium in the NA game is a natural
-    extension of the NE in a bimatrix game $(A, B)$. In particular, if we consider an NA game
-    with only two players and no self-loops then the above definition yields
-
-    \begin{equation*}
-      \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2}), 
-    \end{equation*}
-
+	%It can be seen that
+	The notion of Nash equilibrium in the NA game is a natural
+	extension of the NE in a bimatrix game.
+	%$(A, B)$.
+	In particular, if we consider an NA game with only two players and no
+	self-loops then the above definition yields that $ \NE{1}$ is an NE iff
+	%
+	%    \begin{equation*}
+	$     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2})$,
+	%    \end{equation*}
+	%
 	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
@@
 
-  We will show that the NE exists for an NA game in Section \ref{sec::ExistenceofNE}.
+We will show that the NE exists for an NA game in Section \ref{sec::CTFPAnalysis}.
 
-  Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally
-
-  \begin{equation}
-    \sum_\mu u^\mu(\xmu, \weightedsum) = 0.
-  \end{equation}
+Finally, we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally,
+%
+%  \begin{equation}
+$\sum_\mu u^\mu(\xmu, \weightedsum) = 0$.
+%  \end{equation}
 
@@
   opponent. As such, each agent $\mu$ must update their state according to the time-average of
-  $\refmu$. To formalise this we write
+  $\refmu$. To formalise this we define $\avgref{\mu}$ as the time average of agent $\mu$'s reference $\refmu$ up until time $t$.
 
@@
 
-  Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
+  Using this, we follow in the footsteps of Ewerhart \cite{Ostrovski2014} and Harris \cite{Harris1998} to define
   Fictitious Play in continuous time, but with a slight adaptation for the NA game.
@@
     seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
-    two-player setting \cite{}.
+    two-player setting \cite{Hofbauer2006}.
   \end{remark}
@@
     ability of each agent to prioritise the state information it receives from each of its
-    neighbours. It is also a classical assumption made in the analysis of network games
-    \cite{one of the network game papers} and can is straightforward to implement \cite{Eyad}.
+    neighbours. It is also a classical assumption made in the analysis of networks
+    and is straightforward to implement \cite{Mai2019}.
   \end{assumption}
@@
     have a rich history in game theory and has generated a number of prototypical examples for
-    economic study including the Prisoner's Dilemma game (see \cite{Axelrod} for an interesting
+    economic study including the Prisoner's Dilemma game (see \cite{Axelrod1980} for an interesting
     implementation of this). They also allow for the design of multi-agent systems in
-    computational settings, particularly in the case of task and resource allocation \cite{AGT
-    and some of the Applied Game Theory Papers}. It should be noted, however, that game
+    computational settings, particularly in the case of task and resource allocation \cite{Nisan2007}. It should be noted, however, that game
     theoretic analysis is starting to consider various other forms of utility functions,
-    including monotone \cite{Maryam} and convex \cite{Parise}. We believe that the analysis of
+    including monotone \cite{Tatarenko2020} and convex \cite{Parise2020}. We believe that the analysis of
     Fictitious Play should follow in these developments and we consider it as an important area
@@
     a classical assumption which is made in most game theoretic settings and includes, as a
-    special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
-    in \cite{Ewerhart}, CTFP was analysed without this requirement.  
+    special case. However, it should be noted that,
+    in \cite{Ewerhart2020}, CTFP was analysed without this requirement.  
   \end{assumption}
@@
 \section{Convergence of Fictitious Play}
+\label{sec::CTFPAnalysis}
 
@@
   particular, we show that the NA-CTFP process converges to the set of
-  coarse correlated equilibria \cite{}.
+  coarse correlated equilibria \cite{Nisan2007}.
   %
@@
     games. In fact, if we consider the NA game to be a two player game with no self-loops, then
-    we recover exactly the definition of the CCE set in two player games \cite{PayoffPerformance}.
+    we recover exactly the definition of the CCE set in two player games \cite{Ostrovski2014}.
   \end{remark}
@@
     The notion of the CCE set is related to the idea of \emph{average external regret} (for the
-    sake of brevity we drop the term `external' and refer the reader to \cite{AGT}). Here, we
+    sake of brevity we drop the term `external' and refer the reader to \cite{Nisan2007}). Here, we
     will present what is meant by average regret and state that if at some time $T$ all agents'
     average regret is non-positive, then the game is said to have reached the CCE set. The
-    reader should consult \cite{PayoffPerformance} for an excellent exposition regarding the
+    reader should consult \cite{Ostrovski2014} for an excellent exposition regarding the
     link between the CCE set and average regret in two player games which, of course, extends
@@
     and, of course, can be related to the \emph{cumulative regret} which is used for analysis
-    in \cite{Leonardos and Piliouras, Cesa-Bianchi}.  To illustrate the average regret, let us
+    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
     consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
@@
 
-  As a example of nonconvergence we consider the Shapley family of games \cite{}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by
+  As a example of nonconvergence we consider the Shapley family of games \cite{Shapley2016}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by
 
@@
 
-  where $\beta \in (0, 1)$. In \cite{} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.
+  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.
 
@@
   An interesting point to note is that this behaviour is in stark contrast to the replicator
-  dynamic (RD) \cite{Maynard-Smith}, another adaptive algorithm linked to multi-agent learning
-  \cite{CyclesAdversarialLearning}. In \cite{Imhof} and \cite{Galla}, it was found that the
+  dynamic (RD) \cite{Smith1982}, another adaptive algorithm linked to multi-agent learning
+  \cite{Mertikopoulos2018}. In \cite{Imhof2005} and \cite{Galla2011}, it was found that the
   introduction of random mutations can remove convergent behaviour and instead lead to periodicity.
@@
 Most notable is the effect of noise.
-It would be prudent to analyse this theoretically, as was done in \cite{MFGFP}, and consider the conditions under which FP will still converge to a fixed point.
+It would be prudent to analyse this theoretically, as was done in \cite{Perrin2020}, and consider the conditions under which FP will still converge to a fixed point.
 Furthermore, it would be interesting to investigate the phenomenon we report experimentally in a theoretical framework.
@@
 The dynamics of learning is an important consideration for all practitioners. In particular, it has
-been shown a number of times \cite{noneqmbehaviour} that convergence of learning cannot always be
-assumed. Rather, learning generally presents much more complex dynamics \cite{gallaandfarmer}, which
-only increases as the number of players increases \cite{sanders}. Our work presents practitioners
+been shown a number of times \cite{Mertikopoulos2018} that convergence of learning cannot always be
+assumed. Rather, learning generally presents much more complex dynamics \cite{Galla2013}, which
+only increases as the number of players increases \cite{Sanders2018}. Our work presents practitioners
 who applies Fictitious Play with a case in which rigorous stability properties may be guaranteed.
@@
 As regards FP  itself, the learning strategy has strong applications in robotic control
-\cite{Smyrnakis, Hernandez, Sharma} as well as economic modelling \cite{vonNeumann}. As such we
+\cite{Smyrnakis2016, Hernandez2013, Sharma2015} as well as economic modelling \cite{vonNeumann1944}. As such we
 Furthermore, the algorithm has links to other learning protocols including the replicator dynamic
-\cite{Benaim} and reinforcement learning \cite{LeslieandCollins}. Therefore, we believe that an
+\cite{Benaim2006} and reinforcement learning \cite{Leslie2006}. Therefore, we believe that an
 understanding of FP has subsequent impacts on a number of fields.
@@
 Finally, our work has a strong impact on the study of the Network Aggregative Game, which has strong
-applications in multi-agent control \cite{GrammaticoAggregativeControl}. We 
+applications in multi-agent control \cite{Bianchi2019, DePersis2020}. We 
 believe that our work makes a strong step towards ensuring that systems which learn and adapt on
@@
 
-\section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-when listing the references.
-{\bf Note that the Reference section does not count towards the eight pages of content that are allowed.}
-\medskip
-
-\small
-
-[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
-connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
-(eds.), {\it Advances in Neural Information Processing Systems 7},
-pp.\ 609--616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
-  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
-TELOS/Springer--Verlag.
-
-[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
-recall at excitatory recurrent synapses and cholinergic modulation in rat
-hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
+\bibliographystyle{acm}
+\bibliography{references}
 

### 2021-05-24 Documents/FP in NAGs/neurips_2021.tex
Up to Date Refs
various edits

@@
 
-The NA game is a recent introduction \cite{Parise2015} which presents a variant of aggregative games
-by adding an underlying structure to the population. Since its introduction, distributed algorithms
-have been built with the aim of finding NE. In particular, \cite{Parise2015, Parise2020} consider
-the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
-topological fixed point towards designing algorithms which will converge to the NE. Another
-approach for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
-which is explored in \cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
-the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
-common assumption in works concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due to
-its ubiquity in control settings. We have not yet come across works which consider NA games from the
-point of view of payoff matrices, which are more common in multi-agent learning settings.
-Furthermore, to the best of our knowledge, this is the first work which introduces the application
-of a learning algorithm in the NA setting.
+The NA game is a recent introduction \cite{Parise2015} which presents
+a variant of aggregative games by adding an underlying structure to
+the population. Since its introduction, distributed algorithms have
+been built with the aim of finding NE. In particular,
+\cite{Parise2015, Parise2020} consider the case in which payoffs are
+given by Lipschitz functions with unique minimisers and apply standard
+topological fixed point towards designing algorithms which will
+converge to the NE. Another approach for distributed NE seeking is the
+projected gradient (resp. subgradient) dynamics which is explored in
+\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
+works, the cost function is assumed to be convex, and therefore have a
+unique minimiser. In fact this is a common assumption in works
+concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due
+to its ubiquity in control settings. We have not yet come across works
+which consider NA games from the point of view of payoff matrices,
+which are more common in multi-agent learning settings.  Furthermore,
+to the best of our knowledge, this is the first work which introduces
+the application of a learning algorithm in the NA setting.
 
@@
 
-Fictitious Play was introduced in 1951 \cite{Brown1949} as a
-'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
-time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
-\cite{Robinson1951}. Since then a number of proofs of convergence were determined in 2 player games
-\cite{Miyasawa1961, Metrick1994, Berger2007, Monderer1997, Monderer1996}. Many results hold for both the discrete and continuous variants of FP. However, the work looking at FP
-where there are more than two agents is sparse. \cite{Sela1999} considers a game in which a multi-player
-game is decomposed by requiring that each agent engage in a two person game against each of the
-opponent. Their payoff is given by the sum of payoffs in all of these subgames. It was found that,
-if this game is zero sum, then FP will converge. Similar results for more than two players were
-found for games where all agents share the same payoff in \cite{Monderer1996}. In \cite{Perrin2020}, the action
-of FP was considered in a Mean Field Game, with convergence in
-zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
-and Valkanova in 2020 \cite{Ewerhart2020} in which it was found that FP converges in network
-games, where each agent is engaged in a two-player game with each of their neighbours Our work extends the analysis of FP in
-multiplayer games by considering its action in NA Games, so that the agents do not play individual
-games against each of their neighbours but rather a single game against the aggregate of their
-neighbours. In particular we also extend a result for two player games found by Ostrovski and van
-Strien \cite{Ostrovski2014} which showed that FP achieves no-regret to the multi-player
-setting.
+Fictitious Play was introduced in 1951 \cite{Brown1949} as a 'natural'
+way in which to approximate the Nash Equilibrium in zero sum games. It
+was known at the time that a discrete variant of the algorithm would
+converge to the NE in two player zero-sum games
+\cite{Robinson1951}. Since then a number of proofs of convergence were
+determined in 2 player games \cite{Miyasawa1961, Metrick1994,
+  Berger2007, Monderer1997, Monderer1996}. Many results hold for both
+the discrete and continuous variants of FP. However, the work looking
+at FP where there are more than two agents is sparse. \cite{Sela1999}
+considers a game in which a multi-player game is decomposed by
+requiring that each agent engage in a two person game against each of
+the opponent. Their payoff is given by the sum of payoffs in all of
+these subgames. It was found that, if this game is zero sum, then FP
+will converge. Similar results for more than two players were found
+for games where all agents share the same payoff in
+\cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
+considered in a Mean Field Game, with convergence in zero sum
+games. The most general result, and the one most similar to our own,
+was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020} in
+which it was found that FP converges in network games, where each
+agent is engaged in a two-player game with each of their neighbours
+Our work extends the analysis of FP in multiplayer games by
+considering its action in NA Games, so that the agents do not play
+individual games against each of their neighbours but rather a single
+game against the aggregate of their neighbours. In particular we also
+extend a result for two player games found by Ostrovski and van Strien
+\cite{Ostrovski2014} which showed that FP achieves no-regret to the
+multi-player setting.
 
 \section{Preliminaries}
-In this section we introduce the network aggregative game framework, as well as defining FP on such a game.
+In this section we introduce the network aggregative game framework,
+as well as defining FP on such a game.
 
@@
 
-  Fictitious Play requires that, at the current time, each agent considers the average state
-  of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
-  opponent. As such, each agent $\mu$ must update their state according to the time-average of
-  $\refmu$. To formalise this we define $\avgref{\mu}$ as the time average of agent $\mu$'s reference $\refmu$ up until time $t$.
+  Fictitious Play requires that, at the current time, each agent
+  considers the average state of their opponent in the past, and
+  respond optimally (i.e. play a best response) to this state. In the
+  case of an NA game, each agent considers their reference vector to
+  be their opponent. As such, each agent $\mu$ must update their state
+  according to the time-average of $\refmu$. To formalise this we
+  define $\avgref{\mu}$ as the time average of agent $\mu$'s reference
+  $\refmu$ up until time $t$.
 
@@
   \begin{assumption}\label{ass::rowstochastic}
-    The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
-    that the sum elements in each row of $\weightset$ is equal to one. This assumption is
-    made to ensure that the analysis of NA games can be derived as a natural extension to the
-    classical setting of two-player games. We can think of the row stochastic condition as the
-    ability of each agent to prioritise the state information it receives from each of its
-    neighbours. It is also a classical assumption made in the analysis of networks
-    and is straightforward to implement \cite{Mai2019}.
+    The weighted adjacency matrix $\weightset$ is constant and
+    \emph{row stochastic} meaning that the sum elements in each row of
+    $\weightset$ is equal to one. This assumption is made to ensure
+    that the analysis of NA games can be derived as a natural
+    extension to the classical setting of two-player games. We can
+    think of the row stochastic condition as the ability of each agent
+    to prioritise the state information it receives from each of its
+    neighbours. It is also a classical assumption made in the analysis
+    of networks and is straightforward to implement \cite{Mai2019}.
   \end{assumption}
@@
 
-  In this section we present our main results.
-First, we establish the existence of a Nash Equilibrium in the NA game, as in Def.
-\refname{def::NE}.
-Then we show that the Fictitious Play dynamic on the NA game admits solutions (i.e.
-the NA-CTFP exists).
-Finally, we show that NA-CTFP reaches a fixed point when the NA game is zero-sum and that, when the network has no self-loops (i.e.
-is simple), NA-CTFP reaches a Nash Equilibrium.
-For the sake of brevity, we defer the proofs of our statements, as well as the standard topological arguments used to derive them to the Supplementary Material (Sections (S4 - S6)).
+  In this section we present our main results. First, we establish the
+  existence of a Nash equilibrium in NA games, as in
+  Def.~\refname{def::NE}. Then we show that the Fictitious Play
+  dynamic on the NA game admits solutions (i.e., the NA-CTFP
+  exists \fb{?}). Finally, we show that NA-CTFP reaches a fixed point when
+  the NA game is zero-sum and that, when the network has no self-loops
+  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
+  of brevity, we defer the proofs of our statements, as well as the
+  standard topological arguments used to derive them to the
+  supplementary material (Sections (S4 - S6)).
 
-  As a reminder, the NE condition (Def. \ref{def::NE}) states
+  As a reminder, the NE condition (Def. \ref{def::NE}) states that \fb{$\NE{\mu}$ is an NE iff}
 %
-  \begin{align}
-    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber \\
-    & =: \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
-  \end{align}
-
-  where we can find $\bar{u}_i$ through the following argument
-
+  \begin{align*}
+    \NE{\mu} &\in \arg\max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu}x + \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}) \nonumber  = \arg\max_{x \in \Delta_i} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu})
+  \end{align*}
+%
+  where we can find \fb{what is?} $\bar{u}_i$ through the following argument
+%  
   \begin{align}
@@
   \end{align}
+%  
+  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.
 
-  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$. Note
+  Note
   that, in order to get this formulation, we had to use the assumption
-  of payoffs being bilinear so that we could separate out the term in
+  of payoffs being bilinear \fb{can we point to the exact step?} so that we could separate out the term in
   the weighted sum involving $x$ from $\bar{x}^\nu$.
@@
   \begin{theorem}[Existence of NE]
-    Under the assumption (II), namely that the payoff function achieves a bilinear property, a
-    Nash Equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
+    Under assumption (II), namely that the payoff function achieves a bilinear property, a
+    Nash equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
   \end{theorem}
+
+  \fb{can we say something about the relation between these two results? Is it the second one a corollary of the first one?}
 
@@
 
-With the existence of the NA-CTFP in place, we can show that it converges
+With the existence of the NA-CTFP in place \fb{?}, we can show that it converges
 to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
@@
 Equilibria of the game. If this is for any such NA-CTFP path, then the
-game is said to have the \emph{CTFP property}. We adapt the techniques
-of (Ewerhart 2020) to prove that zero-sum NA games have the CTFP
+game is said to have the \emph{CTFP property} \fb{we do not really need to introduce this definition}. We adapt the techniques
+of \ref{Ewerhart} to prove that zero-sum NA games have the CTFP
 property.
-
+%
   \begin{theorem}
-    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, the corresponding $\alpha(t; m)$ converges to a set of fixed points.
+    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, the corresponding \fb{what?} $\alpha(t; m)$ converges to a set of fixed points.
   \end{theorem}
@@
   We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality yields that, for all $\mu$
-
+%
   \begin{equation}
@@
 
-  which is precisely the Nash Equilibrium condition in the NA game. This leads to the next result
-
+  which is precisely the Nash equilibrium condition \fb{number?} in the NA game. This leads to the next result
+%
   \begin{corollary}
-    With the additional assumption that, for all agents $\mu$, all zero-sum NA games have the CTFP property
+    With the additional assumption that, for all agents $\mu$, all zero-sum NA games have the CTFP property. \fb{this statement is not well-formed.}
   \end{corollary}
@@
 
-  In this section we aim to find some convergence structure for the
+  In this section we aim to find some convergence structure \fb{?} for the
   case in which the NA game is not necessarily zero-sum. In
@@
   %
-  \begin{definition}
+  \begin{definition}[CCE]
     A distribution $\mathcal{D}$ over the joint action set $S =
     \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
-    (CCE) if, for all $\mu$
+     if, for all $\mu$
     \begin{equation}
@@
   payoff that the agent would receive for playing this strategy is
-
-  \begin{align}
-    u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu \nonumber \\
-    & = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
-  \end{align}
+%
+  \begin{align*}
+    u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
+  \end{align*}
 
   As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
-  \rightarrow \infty$, we have that for all $\mu$
-
-  \begin{equation}
-    u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu) \hspace{1cm} \forall i' \in S^\mu.
-  \end{equation}
+  \rightarrow \infty$, we have that for all agents $\mu$,
+%  \begin{equation}
+  $u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu)$
+  %\hspace{1cm} \
+  for all $i' \in S^\mu$.
+%  \end{equation}
 
@@
     Average regret, for agent $\mu$ is defined as
-
+%
     \begin{equation}
@@
     is given by
-
+%    
     \begin{equation}
@@
 
+    \fb{It is not clear to me the relation between CCE and no regret. In particular, why is the following the case?}
+
     In particular, NA-CTFP converges to the set of CCE.
@@
   \subsection{Non-convergent examples} \label{sec::NonConv}
-  The purpose of this section is to show that, whilst wwe have shown that it converges in zero-sum games, NA-CTFP is not guaranteed to converge in general games, and can in fact give rise to a rich variety of dynamics.
+
+  The purpose of this section is to show that, whilst we proved in \fb{?}
+  %have shown
+  that it converges in zero-sum games, NA-CTFP is not guaranteed to
+  converge in general games, and can in fact give rise to a rich
+  variety of dynamics.
 
   As a example of nonconvergence we consider the Shapley family of games \cite{Shapley2016}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by
-
+%
   \begin{equation}
@@
 
-  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.
+  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$. \fb{do we need to provide this example?}
 
@@
 
-  As an adaptation, we take the example of a three player chain, as depicted in Figure \ref{fig::ThreePlayerNetwork}.
-In this example, we first assume that the network is simple (i.e.
-there are no self-loops and $w^{\mu \mu} = 0$).
-The aggregation matrix can be given as
-
+  As an adaptation, we take the example of a three player chain, as
+  depicted in Figure \ref{fig::ThreePlayerNetwork} \fb{do we need this
+    figure? it is rather simple}. In this example, we first assume
+  that the network is simple (i.e. there are no self-loops and $w^{\mu
+    \mu} = 0$). The aggregation matrix can be given as
+%
   \begin{equation}
@@
   We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected. Note that the zero-sum condition given for the three player chain is given as
-
+%
   \begin{equation}
@@
   \end{equation}
-
+  %
   in which we use the notation that $x, y, z$ (resp. $A, B, C$) denote the strategies (resp. payoffs) of agents 1, 2 and 3 respectively. This condition is satisfied if we fix $B$ and choose
-
+%
   \begin{align} \label{eq::zeroSumShapley}
@@
 
-  Let us now make the slight modification in the definition of C so that
-
-  \begin{equation} \label{eq::nonzeroSumShapley}
-    C  = - (1 - w) B, 
-  \end{equation}
-
+  Let us now make the slight modification in the definition of $C$ so that
+%
+%  \begin{equation} \label{eq::nonzeroSumShapley}
+    $C  = - (1 - w) B$, 
+%  \end{equation}
   with no alteration to $A$. The modification itself is small, however it results in the zero-sum
@@
   may be corrupted by noise. 
-
+%  
   As such, we investigate the effect that introducing additive noise has
@@
 	In this work, we have considered the action of the Fictitious Play learning algorithm in Network Aggregative Games and investigated its long term behaviour through a continuous time analysis.
-We find that, under a zero-sum condition, the algorithm converges to a fixed point.
+We find that, under a zero-sum condition, the algorithm converges to a fixed point \fb{what kind of FP?
+we might want to mention individual theorems}.
 However, we find experimentally that this is not always the case.
@@
 For these cases, we also perform a regret analysis which shows that, regardless of the type of game, the FP algorithm achieves no regret.
-
+%	
 	We also investigate the influence of noise on the algorithm and find that even with the introduction of additive noise, FP converges to a fixed point, though not necessarily the NE.
@@
 Namely, the question of why noise breaks periodicity in FP and results in convergence to an NE should be investigated and, indeed, this is a line which we are currently pursuing.
-
+%	
 	In addition, we note that the \emph{Mann Iteration}, a method of approximating fixed points which is investigated in \cite{Parise2020}, shares a remarkably similar structure to the discrete variant of FP.
 This may present an avenue by which NA-CTFP may be analysed in the case of convex cost functions.
-
+%	
 	Finally, we note that in recent years FP in two player games has shown a remarkable variety of dynamical behaviours, including periodicity and chaos.
@@
 
-\bibliographystyle{acm}
-\bibliography{references}
+\bibliographystyle{named}
+\bibliography{referencesT}
 

### 2021-05-25 Documents/FP in NAGs/neurips_2021.tex
Updated Corrections

@@
 Fictitious Play was introduced in 1951 \cite{Brown1949} as a 'natural'
-way in which to approximate the Nash Equilibrium in zero sum games. It
-was known at the time that a discrete variant of the algorithm would
-converge to the NE in two player zero-sum games
-\cite{Robinson1951}. Since then a number of proofs of convergence were
-determined in 2 player games \cite{Miyasawa1961, Metrick1994,
-  Berger2007, Monderer1997, Monderer1996}. Many results hold for both
-the discrete and continuous variants of FP. However, the work looking
+way in which to approximate the Nash Equilibrium in zero sum games.
+Since then, a number of proofs of convergence have been determined for 2 player games \cite{Robinson1951, Miyasawa1961, Metrick1994,Berger2007, Monderer1997, Monderer1996}.
+However, the work looking
 at FP where there are more than two agents is sparse. \cite{Sela1999}
@@
 games. The most general result, and the one most similar to our own,
-was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020} in
-which it was found that FP converges in network games, where each
+was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020}. It was found that FP converges in network games, where each
 agent is engaged in a two-player game with each of their neighbours
-Our work extends the analysis of FP in multiplayer games by
-considering its action in NA Games, so that the agents do not play
+Our work adapts this model to consider NA Games, so that the agents do not play
 individual games against each of their neighbours but rather a single
-game against the aggregate of their neighbours. In particular we also
+game against the aggregate of their neighbours. We also
 extend a result for two player games found by Ostrovski and van Strien
@@
 
-		\item $\edgeset \subseteq \agentset^2$.  Then, the set of
+		\item $\edgeset \subseteq \agentset \times \agentset$.  Then, the set of
 		neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in
@@
 %
-  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)]
+  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)] \label{def::NACTFP}
     An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
@@
   existence of a Nash equilibrium in NA games, as in
-  Def.~\refname{def::NE}. Then we show that the Fictitious Play
-  dynamic on the NA game admits solutions (i.e., the NA-CTFP
-  exists \fb{?}). Finally, we show that NA-CTFP reaches a fixed point when
+  Def.~\ref{def::NE}. Then we show that the Fictitious Play
+  dynamic on the NA game admits solutions. Finally, we show that NA-CTFP reaches a fixed point when
   the NA game is zero-sum and that, when the network has no self-loops
@@
 
-  As a reminder, the NE condition (Def. \ref{def::NE}) states that \fb{$\NE{\mu}$ is an NE iff}
+  As a reminder, the NE condition (Def. \ref{def::NE}) states that $\NE{\mu}$ is an NE iff
 %
@@
 %
-  where we can find \fb{what is?} $\bar{u}_i$ through the following argument
+  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
 %  
   \begin{align}
-    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \\
-     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \\
+    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
+     & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
      & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
@@
   that, in order to get this formulation, we had to use the assumption
-  of payoffs being bilinear \fb{can we point to the exact step?} so that we could separate out the term in
-  the weighted sum involving $x$ from $\bar{x}^\nu$.
+  of payoffs being bilinear so that we could separate out the term in
+  the weighted sum involving $x$ from $\bar{x}^\nu$. In particular, we used this assumption to move from (\ref{eq::bilinear1}) to (\ref{eq::bilinear2}).
 
-  With these in place, we can state our main results.
+  With these in place, we can build towards our main result, namely that of convergence of NA-CTFP to an NE.
+In order to do this, we first need to establish that the NE, and an NA-CTFP (i.e.
+a path which satisfies Def.~\ref{def::NACTFP}) exists.
 
@@
 
-  \fb{can we say something about the relation between these two results? Is it the second one a corollary of the first one?}
-
   \begin{theorem}
@@
 
-With the existence of the NA-CTFP in place \fb{?}, we can show that it converges
+With these results in place, we can show that NA-CTFP converges
 to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
@@
 converged if $\Omega(\alpha)$ is contained within the set of Nash
-Equilibria of the game. If this is for any such NA-CTFP path, then the
-game is said to have the \emph{CTFP property} \fb{we do not really need to introduce this definition}. We adapt the techniques
-of \ref{Ewerhart} to prove that zero-sum NA games have the CTFP
+Equilibria of the game. We adapt the techniques
+of \cite{Ewerhart2020} to prove that zero-sum NA games have the CTFP
 property.
 %
-  \begin{theorem}
-    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, the corresponding \fb{what?} $\alpha(t; m)$ converges to a set of fixed points.
+  \begin{theorem} \label{thm::NACTFPtoFixed}
+    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, $\alpha(t; m)$ (i.e. the time-averaged state) converges to a set of fixed points.
   \end{theorem}
@@
 
-  which is precisely the Nash equilibrium condition \fb{number?} in the NA game. This leads to the next result
+  which is precisely the Nash equilibrium condition (Def.~\ref{def::NE}) in the NA game. This leads to the next result
 %
-  \begin{corollary}
-    With the additional assumption that, for all agents $\mu$, all zero-sum NA games have the CTFP property. \fb{this statement is not well-formed.}
+  \begin{corollary} \label{thm::NACTFPtoNE}
+    With the additional assumption that $w^{\mu \mu} = 0$ for all agents $\mu$, all zero-sum NA games have the property that any NA-CTFP path converges to the set of Nash Equilibria.
   \end{corollary}
@@
 
-  In this section we aim to find some convergence structure \fb{?} for the
+  In this section we aim to understand the long term behaviour of NA-CTFP for the
   case in which the NA game is not necessarily zero-sum. In
@@
 
-  \fb{perhaps what is below could go into a theorem/lemma.}
-
-  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ \fb{$s$ is normally used for actions} is
+  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is
   drawn from a joint probability distribution $\mathcal{D}$, then
@@
 
-  \begin{remark}
+  \begin{remark} \label{rem::regretvsCCE}
     The notion of the CCE set is related to the idea of \emph{average external regret} (for the
@@
 
-  \begin{theorem}
+  \begin{theorem} \label{thm::NACTFPtoCCE}
     Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the
@@
 
-    \fb{It is not clear to me the relation between CCE and no regret. In particular, why is the following the case?}
-
-    In particular, NA-CTFP converges to the set of CCE.
+    In particular, due to the relation between regret and CCE (Remark \ref{rem::regretvsCCE}), NA-CTFP converges to the set of CCE.
 
@@
 
-  The purpose of this section is to show that, whilst we proved in \fb{?}
-  %have shown
+  The purpose of this section is to show that, whilst we proved in Sec.~\ref{sec::CTFPAnalysis}
   that it converges in zero-sum games, NA-CTFP is not guaranteed to
@@
 
-  As a example of nonconvergence we consider the Shapley family of games \cite{Shapley2016}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by
-%
-  \begin{equation}
-    A_\beta = \begin{bmatrix}
-      1 & 0 & \beta \\
-      \beta & 1 & 0 \\
-      0 & \beta & 1
-    \end{bmatrix}, \; B_\beta =  \begin{bmatrix}
-      - \beta & 1 & 0 \\
-      0 & -\beta & 1 \\
-      1 & 0 & -\beta
-    \end{bmatrix}
-  \end{equation}
+  As a example of non-convergence we consider the Shapley family of games \cite{Shapley2016}.
+In \cite{VanStrien2011} this family was shown to contain games for which FP gives periodic and even chaotic behaviour.
 
-  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$. \fb{do we need to provide this example?}
-
-  \begin{figure}[t]
-    \centering
-    \includegraphics[width = 0.6\textwidth]{Figures/ThreePlayerNetwork.png}
-    \caption{\label{fig::ThreePlayerNetwork} A NA game where the network is defined by a chain of
-    three players, as described in Section \ref{sec::NonConv}.}
-  \end{figure}
-
-  As an adaptation, we take the example of a three player chain, as
-  depicted in Figure \ref{fig::ThreePlayerNetwork} \fb{do we need this
-    figure? it is rather simple}. In this example, we first assume
-  that the network is simple (i.e. there are no self-loops and $w^{\mu
-    \mu} = 0$). The aggregation matrix can be given as
+  As an adaptation, we take the example of a three player chain, in which player $2$ is connected to $1$ and $3$. The aggregation matrix can be given as
 %
@@
 
-  As such in the following example, we will set $B = B_\beta$ with the choice $\beta \approx 0.576$ and set $A$ and $C$ according to the above with the choice $w \approx 0.288$.
+  As such in the following example, we will set
+  \begin{equation}
+    B =  \begin{bmatrix}
+      - \beta & 1 & 0 \\
+      0 & -\beta & 1 \\
+      1 & 0 & -\beta
+    \end{bmatrix}
+  \end{equation}
+
+  with the choice $\beta \approx 0.576$ and set $A$ and $C$ according to the above with the choice $w \approx 0.288$.
 The orbits that these payoff matrices generate can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which, for each player, lies in the centre of the simplex.
@@
   Let us now make the slight modification in the definition of $C$ so that
-%
+%m
 %  \begin{equation} \label{eq::nonzeroSumShapley}
@@
   assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic
-  orbit seen in Figures \ref{fig::nonconvergentShapley}. Here,
+  orbit seen in Figure \ref{fig::nonconvergentShapley}. Here,
   the orbits reach a stable limit cycle which to be centred around the interior NE.
@@
 	In this work, we have considered the action of the Fictitious Play learning algorithm in Network Aggregative Games and investigated its long term behaviour through a continuous time analysis.
-We find that, under a zero-sum condition, the algorithm converges to a fixed point \fb{what kind of FP?
-we might want to mention individual theorems}.
+We find that, under a zero-sum condition, NA-CTFP converges to a fixed point (Theorem \ref{thm::NACTFPtoFixed}).
 However, we find experimentally that this is not always the case.

### 2021-05-25 Documents/FP in NAGs/neurips_2021.tex
Within Page Limit

@@
 In this study, we investigate a variant of the aggregative game known as the \emph{Network
-Aggregative} (NA) Game. This format assumes that there is an underlying communication network
-through which agents interact. Then each agent updates their actions according only to those agents
-with whom they communicate. This significantly relaxes the communication load on each agent and
+Aggregative} (NA) Game.
+This format assumes that each agent updates their actions according only to those agents with whom they are connected on an underlying network.
+This significantly relaxes the communication load on each agent and
 lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
@@
 In particular, we analyse the Fictitious Play Learning
-Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely
-to the previous behaviour of the others.
+Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the previous behaviour of the others.
 
@@
 
-  Using this, we follow in the footsteps of Ewerhart \cite{Ostrovski2014} and Harris \cite{Harris1998} to define
+  Using this, we follow in the footsteps of  \cite{Ewerhart2020} and \cite{Harris1998} to define
   Fictitious Play in continuous time, but with a slight adaptation for the NA game.
@@
     The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
-    have a rich history in game theory and has generated a number of prototypical examples for
-    economic study including the Prisoner's Dilemma game (see \cite{Axelrod1980} for an interesting
-    implementation of this). They also allow for the design of multi-agent systems in
+    have a rich history in game theory and allow for the design of multi-agent systems in
     computational settings, particularly in the case of task and resource allocation \cite{Nisan2007}. It should be noted, however, that game
@@
   \begin{assumption}\label{ass::zerosum}
-    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
+    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum) = 0$ for any set
     of states $(x^\mu)_{\mu \in N^\mu}$. This is, perhaps, one of the stronger assumptions in
@@
 
-  Note
-  that, in order to get this formulation, we had to use the assumption
-  of payoffs being bilinear so that we could separate out the term in
-  the weighted sum involving $x$ from $\bar{x}^\nu$. In particular, we used this assumption to move from (\ref{eq::bilinear1}) to (\ref{eq::bilinear2}).
+  Note that, in order to get this formulation, we had to use Assumption \ref{ass::matrixgame}
+ to move from (\ref{eq::bilinear1}) to (\ref{eq::bilinear2}).
 
@@
 Equilibria of the game. We adapt the techniques
-of \cite{Ewerhart2020} to prove that zero-sum NA games have the CTFP
-property.
+of \cite{Ewerhart2020} to prove that this is the case.
 %
@@
     N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
-  distribution over all actions and all references.  Consider, then, a
+  distribution over both the actions and the references.  Consider, then, a
   vector of joint distributions over actions and references which is
   generated by NA-CTFP. In particular, if by playing with NA-CTFP, the
-  agents reach the state $(\xmu)_{i = 1}^N$ with references
-  $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} =
-  (\mathcal{D}^1, ..., \mathcal{D}^N)$ such that
+  agents reach state $(\xmu)_{i = 1}^N$ with references
+  $(\refmu)_{i = 1}^N$, $\mathcal{D} =
+  (\mathcal{D}^1, ..., \mathcal{D}^N)$ is such that
   $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
@@
   \begin{remark} \label{rem::regretvsCCE}
-    The notion of the CCE set is related to the idea of \emph{average external regret} (for the
-    sake of brevity we drop the term `external' and refer the reader to \cite{Nisan2007}). Here, we
+    The notion of the CCE set is related to the idea of \emph{average regret}  \cite{Nisan2007}. Here, we
     will present what is meant by average regret and state that if at some time $T$ all agents'
@@
     \begin{subfigure}[b]{0.45 \textwidth}
-      \includegraphics[width = \textwidth]{Figures/convergentShapley.png}
+      \includegraphics[width = 0.8\textwidth]{Figures/convergentShapley.png}
     \caption{\label{fig::convergentShapley}}
@@
     \begin{subfigure}[b]{0.45 \textwidth}
-      \includegraphics[width = \textwidth]{Figures/nonConvergentShapley.png}
+      \includegraphics[width = 0.8 \textwidth]{Figures/nonConvergentShapley.png}
       \caption{\label{fig::nonconvergentShapley}}

### 2021-05-25 Documents/FP in NAGs/neurips_2021.tex
various edits

@@
   In this section we present our main results. First, we establish the
-  existence of a Nash equilibrium in NA games, as in
+  existence of a Nash equilibrium in NA games, as defined in
   Def.~\ref{def::NE}. Then we show that the Fictitious Play
-  dynamic on the NA game admits solutions. Finally, we show that NA-CTFP reaches a fixed point when
+  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?}. Finally, we show that NA-CTFP reaches a fixed point when
   the NA game is zero-sum and that, when the network has no self-loops
@@
   of brevity, we defer the proofs of our statements, as well as the
-  standard topological arguments used to derive them to the
+  standard topological arguments used to derive them, to the
   supplementary material (Sections (S4 - S6)).
 
-  As a reminder, the NE condition (Def. \ref{def::NE}) states that $\NE{\mu}$ is an NE iff
+  As a reminder,
+  %the NE condition (
+  Def. \ref{def::NE} states that $\NE{\mu}$ is an NE iff
 %
@@
 
+  \fb{why symbol $=:$? is it a definition?}
+
   Note that, in order to get this formulation, we had to use Assumption \ref{ass::matrixgame}
@@
 
-  With these in place, we can build towards our main result, namely that of convergence of NA-CTFP to an NE.
-In order to do this, we first need to establish that the NE, and an NA-CTFP (i.e.
-a path which satisfies Def.~\ref{def::NACTFP}) exists.
+  With these in place, we can build towards our main result, namely
+  the convergence of NA-CTFP to an NE. In order to do this, we first
+  need to establish that the NE, and an NA-CTFP (i.e. a path which
+  satisfies Def.~\ref{def::NACTFP}) exists.
 
@@
     BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
+    \fb{why parameter $t$ if it does not appear anywhere in the statement?}
   \end{theorem}
@@
 to a fixed point. In particular, let $\Omega(\alpha)$ be the set of
-all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to have
-converged if $\Omega(\alpha)$ is contained within the set of Nash
+all limit points for $\alpha(t)$. Then, a NA-CTFP path is said to {\em 
+converge} if $\Omega(\alpha)$ is contained within the set of Nash
 Equilibria of the game. We adapt the techniques
@@
 
-  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality yields that, for all $\mu$
+  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality \fb{which inequality?} yields that, for all agents $\mu$,
 %

### 2021-05-25 Documents/FP in NAGs/neurips_2021.tex
Edits to Section 3

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
 \newtheorem{corollary}{Corollary}
@@
   Def.~\ref{def::NE}. Then we show that the Fictitious Play
-  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?}. Finally, we show that NA-CTFP reaches a fixed point when
+  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?} \ah{So the existence of the NE and the FP dynamic are independent of one another.
+The NE is a property of the game only, whereas FP is a separate differential equation (12 in the supplementary material).
+Whilst it is intuitive that the solutions to (S12) exists, on a technical sense we still have to prove it.}.
+Finally, we show that NA-CTFP reaches a fixed point when
   the NA game is zero-sum and that, when the network has no self-loops
@@
      & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
-     & =: \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
+     & \stackrel{\text{def}}{=} \bar{u}^\mu(x, \sum_{\nu \in N^\mu} w^{\mu \nu} \NE{\nu}), \nonumber
   \end{align}
@@
   where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.
-
-  \fb{why symbol $=:$? is it a definition?}
 
@@
 
-  \begin{theorem}[Existence of NE]
+  \begin{lemma}[Existence of NE]
     Under assumption (II), namely that the payoff function achieves a bilinear property, a
     Nash equilibrium $\{\bar{x}^\mu\}_{\mu \in \agentset}$ exists.
-  \end{theorem}
+  \end{lemma}
 
-  \begin{theorem}
-    There exists a path $m$ which satisfies the property that, for all agents $\mu$, $m^\mu \in
-    BR^\mu(\alpha_\sigma^\mu)$ for almost all $t \geq 1$.
-    \fb{why parameter $t$ if it does not appear anywhere in the statement?}
-  \end{theorem}
+  \begin{lemma}
+    There exists a path $m(t)$ which satisfies the property that, for all agents $\mu$, $m^\mu(t) \in
+    BR^\mu(\alpha_\sigma^\mu(t))$ for almost all $t \geq 1$.
+  \end{lemma}
 
@@
 
-  We now point out that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the final inequality \fb{which inequality?} yields that, for all agents $\mu$,
-%
-  \begin{equation} 
-    u^\mu(y, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty) \leq u^\mu(\xmu_\infty, \sum_{\nu \in N^\mu} \wmunu \xnu_\infty)
-  \end{equation}
-
-  which is precisely the Nash equilibrium condition (Def.~\ref{def::NE}) in the NA game. This leads to the next result
+  In the proof of Theorem \ref{thm::NACTFPtoFixed} it can be seen that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the fixed point corresponds to an NE.
+In particular Eqn.
+(26) in the supplementary materal corresponds to the NE condition when $w^{\mu \mu} = 0$.
+This leads to the next result.
 %

### 2021-05-26 Documents/FP in NAGs/neurips_2021.tex
Updated Section 4

@@
 This significantly relaxes the communication load on each agent and
-lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
+lifts the need for a central coordinator. Recent work on NA games has shown that it is possible
 for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}.
@@
 
-The NA game is a recent introduction \cite{Parise2015} which presents
+NA games are a recent introduction \cite{Parise2015} which presents
 a variant of aggregative games by adding an underlying structure to
@@
 matrices $A^\mu$ in place of the utility functions
-$\utility{\mu}$. Hence, the NA game allows for the reduction of a
+$\utility{\mu}$. Hence, NA Games allow for the reduction of a
 multi-player game into a series of two-player games. The agent's goal
@@
 	The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is a {\em
-		Nash equilibrium} if, for all $\mu$,
+		Nash equilibrium} if, for all agents $\mu$,
 	\begin{equation*}
@@
 	%It can be seen that
-	The notion of Nash equilibrium in the NA game is a natural
+	The notion of Nash equilibrium in NA Games is a natural
 	extension of the NE in a bimatrix game.
@@
   Using this, we follow in the footsteps of  \cite{Ewerhart2020} and \cite{Harris1998} to define
-  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
+  Fictitious Play in continuous time, but with a slight adaptation for NA Games.
 %
-  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)] \label{def::NACTFP}
-    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
-    and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
-    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
+  \begin{definition}[Fictitious Play on Network Aggregative Games] \label{def::NACTFP}
+    We define Continuous Time Fictitious Play on Network Aggregative Games as a measurable map $m$ with components $m^\mu$ such that for all agents $\mu$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
+    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all time $t \geq 1$. Henceforth, $m$ will be called an \emph{NA-CTFP}.
   \end{definition}
@@
   $t = 1$, but beyond this it must play a best response to the time average of its reference
-  signal.
+  signal. We also refer to this measurable map as a `path'. In Section \ref{sec::CTFPAnalysis}, we prove that a path $m$ which satisfies this definition exists.
 
   \begin{remark}
-    As an illustration, consider the NA game with two players, in which $\edgeset = \{(1, 2),
+    As an illustration, consider NA Games with two players, in which $\edgeset = \{(1, 2),
     (2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
@@
 
-    \begin{align}
-      \alpha^\mu(t; x) = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
+    \begin{align*}
+      \alpha^\mu(t; x) = \frac{1}{t} \int_0^t \xmu(s) \, ds & \text{ for $\mu \in \{1, 2\}$}
   %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
-    \end{align}
+    \end{align*}
 
@@
   existence of a Nash equilibrium in NA games, as defined in
-  Def.~\ref{def::NE}. Then we show that the Fictitious Play
-  dynamic on NA games admits solutions \fb{doesn't this follows from the existence of NE?} \ah{So the existence of the NE and the FP dynamic are independent of one another.
-The NE is a property of the game only, whereas FP is a separate differential equation (12 in the supplementary material).
-Whilst it is intuitive that the solutions to (S12) exists, on a technical sense we still have to prove it.}.
-Finally, we show that NA-CTFP reaches a fixed point when
-  the NA game is zero-sum and that, when the network has no self-loops
+  Def.~\ref{def::NE}. Then we show that an NA-CTFP (i.e. a path $m$ which satisfies Def.~\ref{def::NACTFP}) exists. Finally, we show that NA-CTFP reaches a fixed point when
+  NA Games are zero-sum and that, when the network has no self-loops
   (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
@@
 %
-  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other $\xnu$ in the second argument. We can find $\bar{u}_i$ through the following argument
+  where we have introduced the surrogate function $\bar{u}$ which keeps $x$ in the first argument and all other agent states $\xnu$ in the second argument.
+We can find $\bar{u}_i$ through the following argument
 %  
@@
     There exists a path $m(t)$ which satisfies the property that, for all agents $\mu$, $m^\mu(t) \in
-    BR^\mu(\alpha_\sigma^\mu(t))$ for almost all $t \geq 1$.
+    BR^\mu(\alpha_\sigma^\mu(t))$ for almost all times $t \geq 1$.
   \end{lemma}
@@
 
-  In the proof of Theorem \ref{thm::NACTFPtoFixed} it can be seen that, if we choose $w^{\mu \mu}$ to be zero for all $\mu$, then the fixed point corresponds to an NE.
+  In the proof of Theorem \ref{thm::NACTFPtoFixed} it can be seen that, if we choose $w^{\mu \mu}$ to be zero for all agents $\mu$, then the fixed point corresponds to an NE.
 In particular Eqn.
@@
   In this section we aim to understand the long term behaviour of NA-CTFP for the
-  case in which the NA game is not necessarily zero-sum. In
-  particular, we show that the NA-CTFP process converges to the set of
-  coarse correlated equilibria \cite{Nisan2007}.
+  case in which NA games are not necessarily zero-sum.
+To do this, we first introduce the coarse correlated equilibria (CCE) \cite{Nisan2007} in the context of NA games as a natural extension to the two-player case.
+Then, we show that the NA-CTFP process converges to the set of
+  CCE
   %
-  \begin{definition}[CCE]
+  \begin{definition}[CCE] \label{def::CCE}
     A distribution $\mathcal{D}$ over the joint action set $S =
     \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
-     if, for all $\mu$
-    \begin{equation}
+     if, for all agents $\mu$, $
       \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
-      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
-          \mu})] \hspace{1cm} \forall j \in S^\mu.
-    \end{equation}
+      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, s^{-
+          \mu})]$ $ \forall j \in S^\mu.$
   \end{definition}
@@
   probability distribution with which they can play their actions, then
-  the expected payoff, for all agents is greater than or equal to the
+  the expected payoff, for all agents, is greater than or equal to the
   payoff that they would get by playing any of their other available
@@
 
-  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is
-  drawn from a joint probability distribution $\mathcal{D}$, then
-  there is a corresponding set of reference vectors $\sigma =
+  For an NA game, a set of actions $s = (s^1, \ldots, s^N)$ which is
+  drawn from a joint probability distribution $\mathcal{D}$, also generates
+  a corresponding set of reference vectors $\sigma =
   (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
-    N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
-  distribution over both the actions and the references.  Consider, then, a
-  vector of joint distributions over actions and references which is
-  generated by NA-CTFP. In particular, if by playing with NA-CTFP, the
+    N^\mu} \wmunu s^\nu$. In other words, if we draw $s$ from $\mathcal{D}$, then we have also drawn $\sigma$, which means our CCE condition, Def.~\ref{def::CCE}, can be written as $
+\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] \geq
+\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, \refmu)]$ $ \forall j \in S^\mu$ and all agents $\mu$.
+
+  Now, if by playing with NA-CTFP, the
   agents reach state $(\xmu)_{i = 1}^N$ with references
-  $(\refmu)_{i = 1}^N$, $\mathcal{D} =
-  (\mathcal{D}^1, ..., \mathcal{D}^N)$ is such that
+  $(\refmu)_{i = 1}^N$, then we can define a distribution $\mathcal{D} =
+  (\mathcal{D}^1, ..., \mathcal{D}^N)$ so that
   $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
@@
   \begin{align*}
-    u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
+    \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] = u^\mu (\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
   \end{align*}
@@
 %  \begin{equation}
-  $u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu)$
+  $u^\mu (\xmu, \refmu) \geq u^\mu(j, \refmu)$
   %\hspace{1cm} \
-  for all $i' \in S^\mu$.
+  for all actions $j \in S^\mu$.
 %  \end{equation}
@@
     The notion of the CCE set is related to the idea of \emph{average regret}  \cite{Nisan2007}. Here, we
-    will present what is meant by average regret and state that if at some time $T$ all agents'
+    will present what is meant by average regret and state that if at some time $t$ all agents'
     average regret is non-positive, then the game is said to have reached the CCE set. The
@@
     link between the CCE set and average regret in two player games which, of course, extends
-    naturally to the NA game.
+    naturally to NA Games.
 
@@
 %
-    \begin{equation}
-      R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(\pure{\mu}{i'}, \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\},
-    \end{equation}
+    \begin{equation*}
+      R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{t} \int_{0}^{t} u^{\mu}(\pure{\mu}{i'}, \sigma(s)) - u^{\mu}(m^\mu(s), \sigma(s)) \, ds \Big\},
+    \end{equation*}
 
@@
 %    
-    \begin{equation}
+    \begin{equation*}
       u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
-    \end{equation}
+    \end{equation*}
 
@@
 
-    \begin{equation}
+    \begin{equation*}
       u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
-    \end{equation}
+    \end{equation*}
 
@@
     \begin{equation}
-      \lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
+      \lim_{t \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{t} \int_{0}^{t} u^{\mu}(x_{i'}^\mu(s), \sigma(s)) - u^{\mu}(m^\mu(s), \sigma(s)) \, ds \Big\} = 0
     \end{equation}
@@
 %
-  \begin{equation}
+  \begin{equation*}
     W = \begin{bmatrix}
@@
     \end{bmatrix}, \; w \in (0, 1).
-  \end{equation}
+  \end{equation*}
 

### 2021-05-26 Documents/FP in NAGs/neurips_2021.tex
Update neurips_2021.tex
Updated Section 4

@@
 
+	We note at this point that a related result was found in \cite{Ewerhart2020}.
+In particular, the authors showed that, when playing on a zero-sum network game, agents learning through Fictitious Play achieve non-positive regret, regardless of the behaviour of the other agents.
+This is a slightly stronger condition than the CCE, in which agents achieve non-positive regret if all other agents do not deviate from the distribution $\mathcal{D}$.
+However, the result in \cite{Ewerhart2020} applies only under the zero-sum condition, whereas Theorem \ref{thm::NACTFPtoCCE} applies in all NA games.
+
 \section{Numerical Experiments}

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
various edits

@@
 
-\subsection{Contributions}
-
+\paragraph{Contributions.}
+%
   The main contribution of this work is to introduce learning on the Network Aggregative Game
@@
 
-\subsection{Related Work}
+\paragraph{Related Work.}
 
-\paragraph{Network Aggregative Games}
-
-NA games are a recent introduction \cite{Parise2015} which presents
+\textbf{Network Aggregative Games}
+%NA games
+are a recent introduction \cite{Parise2015} which presents
 a variant of aggregative games by adding an underlying structure to
@@
 
-\paragraph{Fictitious Play}
-
-Fictitious Play was introduced in 1951 \cite{Brown1949} as a 'natural'
+\textbf{Fictitious Play}
+%Fictitious Play
+was introduced in 1951 \cite{Brown1949} as a 'natural'
 way in which to approximate the Nash Equilibrium in zero sum games.
@@
 
-\section{Convergence of Fictitious Play}
+\section{Convergence of Fictitious Play  in Network Aggregative Games}
 \label{sec::CTFPAnalysis}
@@
 
-\section{NA-CTFP achieves no regret}
+\section{Fictitious Play  in Network Aggregative Games Achieves No Regret}
   \label{sec::CCEConvergence}
 
-  In this section we aim to understand the long term behaviour of NA-CTFP for the
-  case in which NA games are not necessarily zero-sum.
-To do this, we first introduce the coarse correlated equilibria (CCE) \cite{Nisan2007} in the context of NA games as a natural extension to the two-player case.
-Then, we show that the NA-CTFP process converges to the set of
-  CCE
+  In this section we aim to understand the long term behaviour of
+  NA-CTFP for the case in which NA games are not necessarily
+  zero-sum. To do this, we first introduce the coarse correlated
+  equilibria (CCE) \cite{Nisan2007} in the context of NA games as a
+  natural extension to \fb{of} the two-player case. Then, we show that
+  the NA-CTFP process converges to the set of CCE.
   %
   \begin{definition}[CCE] \label{def::CCE}
-    A distribution $\mathcal{D}$ over the joint action set $S =
-    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
-     if, for all agents $\mu$, $
-      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
-      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, s^{-
-          \mu})]$ $ \forall j \in S^\mu.$
+    A distribution $\mathcal{D}$ over the set $S = \times_\mu S^\mu$
+    of joint actions is called a \emph{coarse correlated equilibrium}
+    if, for all agents $\mu$ and actions $j \in S^\mu$, we have
+    $\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
+    \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, s^{- \mu})]$.
   \end{definition}
@@
   For an NA game, a set of actions $s = (s^1, \ldots, s^N)$ which is
-  drawn from a joint probability distribution $\mathcal{D}$, also generates
-  a corresponding set of reference vectors $\sigma =
+  drawn from a joint probability distribution $\mathcal{D}$, also
+  generates a corresponding set of reference vectors $\sigma =
   (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
-    N^\mu} \wmunu s^\nu$. In other words, if we draw $s$ from $\mathcal{D}$, then we have also drawn $\sigma$, which means our CCE condition, Def.~\ref{def::CCE}, can be written as $
-\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] \geq
-\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, \refmu)]$ $ \forall j \in S^\mu$ and all agents $\mu$.
+    N^\mu} \wmunu s^\nu$. That is, if we draw action $s$ from
+  $\mathcal{D}$, then we have also drawn $\sigma$, which means our CCE
+  condition, Def.~\ref{def::CCE}, can be written as $ \mathbb{E}_{s
+    \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] \geq \mathbb{E}_{s \sim
+    \mathcal{D}}[u^\mu (j, \refmu)]$, for all agents $\mu$ and actions $j \in S^\mu$.
 
@@
 %    
-    \begin{equation*}
+    \begin{equation} \label{eq1}
       u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
-    \end{equation*}
+    \end{equation}
 
@@
 
-    \begin{equation*}
+    \begin{equation}  \label{eq2}
       u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
-    \end{equation*}
+    \end{equation}
 
-    By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change.
+    By comparing equations~(\ref{eq1}) and (\ref{eq2}),
+    %the two expanded expressions,
+    we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change.
 As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time.
@@
 
-	We note at this point that a related result was found in \cite{Ewerhart2020}.
-In particular, the authors showed that, when playing on a zero-sum network game, agents learning through Fictitious Play achieve non-positive regret, regardless of the behaviour of the other agents.
-This is a slightly stronger condition than the CCE, in which agents achieve non-positive regret if all other agents do not deviate from the distribution $\mathcal{D}$.
-However, the result in \cite{Ewerhart2020} applies only under the zero-sum condition, whereas Theorem \ref{thm::NACTFPtoCCE} applies in all NA games.
+	We note at this point that a related result was found in
+        \cite{Ewerhart2020}. In particular, the authors showed that,
+        when playing on a zero-sum network game, agents learning
+        through Fictitious Play achieve non-positive regret,
+        regardless of the behaviour of the other agents. This is a
+        slightly stronger condition than the CCE, in which agents
+        achieve non-positive regret if all other agents do not deviate
+        from the distribution $\mathcal{D}$. However, the result in
+        \cite{Ewerhart2020} applies only under the zero-sum condition,
+        whereas Theorem \ref{thm::NACTFPtoCCE} applies in all NA
+        games.
 
-\section{Numerical Experiments}
+\section{Experimental Evaluation}
 
-  \subsection{Non-convergent examples} \label{sec::NonConv}
+  \subsection{Non-convergence of General Two-player Games under NA-CTFP} \label{sec::NonConv}
 

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Updated Contributions

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-%     \usepackage[final]{neurips_2021}
+%     \usepackage[final]{ne urips_2021}
 
@@
 \usepackage{enumerate}
+\usepackage{enumitem}
 \usepackage{graphicx}
@@
 %
-  The main contribution of this work is to introduce learning on the Network Aggregative Game
+  The main contribution of this work is to introduce and study learning on the Network Aggregative Game
   through the action of Fictitious Play (FP).
+In particular, we aim to establish guarantees of convergence for learning under certain classes of games.
+This allows for games to be designed so that the long term behaviour of learning is predictable, regardless of how many agents are engaged in the game.
+As such, we are able to avoid the pitfalls of chaotic dynamics in games with many players as in \cite{Sanders2018}.
 
@@
   Equilibrium. This presents an interesting avenue for future research.
+
+  To the best of our knowledge, this paper is the first time that a learning algorithm, which stems from game theoretic literature, has been studied on the network aggregative game, typically considered in the context of control and optimisation.
 
@@
 	\weightset))$ is such that
-	\begin{itemize}
+	\begin{itemize}[leftmargin=0.5cm]
 
@@
 
-Given Def.~\ref{interactiongraph} of interaction graph,
+%Given Def.~\ref{interactiongraph} of interaction graph,
 %With the above definition,
-we introduce network aggregative (NA) games:
+%we introduce network aggregative (NA) games:
 %
@@
 reference vector $\sigma^{\mu}$. Thus, instead of considering
-the actions of the entire population, or play individual games
+the actions of the entire population, or playing individual games
 against each of their neighbours, the agent only considers
@@
 against the reference vector so that
-%
-\begin{equation}
+$
 	u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
-	\cdot A^\mu \weightedsum.
-\end{equation}
+	\cdot A^\mu \weightedsum,
+$
 %
@@
 matrices $A^\mu$ in place of the utility functions
-$\utility{\mu}$. Hence, NA Games allow for the reduction of a
-multi-player game into a series of two-player games. The agent's goal
-is to maximise their payoff with respect to the reference vector. As
+$\utility{\mu}$.
+
+The agent's goal
+is to maximise their payoff $u^\mu$ with respect to their reference vector $\refmu$. As
 such, we define the best response correspondence $BR^\mu$, which maps
@@
 
-Finally, a central concept of game theory is that of the Nash
-Equilibrium, in which no rational agent has the incentive to deviate
-from their current state. This can be formalised by saying that all
+Through the best response function, we can define the Nash Equilibrium (NE), a central concept of game theory. The NE condition requires that no rational agent has the incentive to deviate
+from their current state, as long as the other agents continue to play the NE strategy. This can be formalised by saying that all
 agents are playing their best response to each other.
@@
 
-Finally, we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally,
+%Finally, we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally,
 %
 %  \begin{equation}
-$\sum_\mu u^\mu(\xmu, \weightedsum) = 0$.
+% $\sum_\mu u^\mu(\xmu, \weightedsum) = 0$.
 %  \end{equation}
@@
   be their opponent. As such, each agent $\mu$ must update their state
-  according to the time-average of $\refmu$. To formalise this we
+  according to the time-average of the reference vector $\refmu$. To formalise this we
   define $\avgref{\mu}$ as the time average of agent $\mu$'s reference
   $\refmu$ up until time $t$.
-
   \begin{equation}
@@
   \begin{definition}[Fictitious Play on Network Aggregative Games] \label{def::NACTFP}
-    We define Continuous Time Fictitious Play on Network Aggregative Games as a measurable map $m$ with components $m^\mu$ such that for all agents $\mu$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
+    We define Continuous Time Fictitious Play (CTFP) on NA Games as a measurable map $m$ with components $m^\mu$ such that for all agents $\mu$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
     BR^\mu(\alpha_{\sigma}^\mu)$ for almost all time $t \geq 1$. Henceforth, $m$ will be called an \emph{NA-CTFP}.
@@
     the off diagonal. We write the time-average of both agents' state as
-
     \begin{align*}
@@
     \end{align*}
-
     In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
@@
   \begin{theorem} \label{thm::NACTFPtoFixed}
-    Any zero-sum NA game has the property that, for any NA-CTFP path $m$, $\alpha(t; m)$ (i.e. the time-averaged state) converges to a set of fixed points.
+    Any zero-sum NA game (Assumption \ref{ass::zerosum}) has the property that, for any NA-CTFP path $m$, $\alpha(t; m)$ (i.e. the time-averaged state) converges to a set of fixed points.
   \end{theorem}
@@
   equilibria (CCE) \cite{Nisan2007} in the context of NA games as a
-  natural extension to \fb{of} the two-player case. Then, we show that
+  natural extension to of the two-player case. Then, we show that
   the NA-CTFP process converges to the set of CCE.
@@
 
-  We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected. Note that the zero-sum condition given for the three player chain is given as
+  We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected.
+Note that the zero-sum condition (Assumption \ref{ass::zerosum}) given for the three player chain is given as
 %
@@
 
-  \subsection{Addition of Noise}
+  \subsection{Convergence under the Addition of Noise}
 
@@
 
-\section{Concluding remarks}
+\section{Concluding Remarks}
 	In this work, we have considered the action of the Fictitious Play learning algorithm in Network Aggregative Games and investigated its long term behaviour through a continuous time analysis.

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Updated Experiments

@@
   existence of a Nash equilibrium in NA games, as defined in
-  Def.~\ref{def::NE}. Then we show that an NA-CTFP (i.e. a path $m$ which satisfies Def.~\ref{def::NACTFP}) exists. Finally, we show that NA-CTFP reaches a fixed point when
+  Def.~\ref{def::NE}. Then we show that an NA-CTFP (i.e. a path $m$ which satisfies Def.~\ref{def::NACTFP}) exists. Finally, we show that any NA-CTFP reaches a fixed point when
   NA Games are zero-sum and that, when the network has no self-loops
-  (i.e., is simple), NA-CTFP reaches a Nash Equilibrium. For the sake
+  (i.e., $w^{\mu \mu} = 0$ for all agents $\mu$), NA-CTFP reaches a Nash Equilibrium. For the sake
   of brevity, we defer the proofs of our statements, as well as the
@@
 \section{Experimental Evaluation}
+
+	In this section, we investigate NA-CTFP through numerical experiments.
+In particular, we look beyond zero-sum NA games and show that learning on an NA game can lead to periodic behaviour, rather than convergence to a fixed point.
+In addition, we aim to understand the behaviour of agents learning through NA-CTFP, when the measurements on their reference signal $\refmu$ is corrupted with noise.
 

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Updated Experiment Figures

@@
     \end{subfigure}
-    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain (c.f.
-    Figure \ref{fig::ThreePlayerNetwork}) with payoff matrices given by (a)
-    (\ref{eq::zeroSumShapley}) showing convergence to the interior NE (b)
-    (\ref{eq::nonzeroSumShapley}) showing cycles around the interior NE.}
+    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain for which the NE lies at the centre of the simplex. (a) Payoffs are given by
+    (\ref{eq::zeroSumShapley}). The plot shows NA-CTFP yields convergence to the NE (b)
+	NA-CTFP showing cycles around the NE when payoffs are modified slightly (c.f. Sec.~\ref{sec::NonConv}).}
   \end{figure}

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Minor updates

@@
 Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.In this study, we contribute towards the study of learning with multiple agents.
-We do this through the introduction of learning on network aggregative games, in which each player's reward depends only on its own strategy and a convex combination of its neighbours.
+We do this through the introduction of learning on Network Aggregative games, in which each player's reward depends only on its own strategy and a convex combination of its neighbours.
 In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game.
@@
 Multi-Agent Learning \cite{Schwartz2014} requires a number of agents to adapt in an environment where
-each agent must adapt in response to the behaviour of the other agents. This leads to a
+each agent responds to the behaviour of the other agents. This leads to a
 fundamentally non-stationary problem, which presents a challenge to designing effective learning
 policies. Even when there are a small number of agents in the game, learning has been shown to lead
-to non-stationary, and even chaotic behaviour \cite{Sato2002}, and this problem becomes even more
+to non-stationary, and even chaotic behaviour \cite{Sato2002}, a problem which becomes even more
 pronounced as the number of agents increase \cite{Sanders2018}.
-In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi-agent learning \cite{Chotibut2021}.
+In this light, it would seem that, when there is a large population of agents, it is almost difficult to understand the long term behaviour of multi-agent learning \cite{Chotibut2021}.
 This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
@@
 number of agents, so that the population can be represented through a distribution over players'
-states \cite{Huang2006} . Every agent then updates their action profiles depending on this
+states \cite{Huang2006}. Every agent then updates their action profiles depending on this
 distribution. In the latter each agent considers a real valued function which is a convex
@@
 In particular, we analyse the Fictitious Play Learning
-Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the previous behaviour of the others.
+Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the past behaviour of the others.
 
@@
   solutions in this setting. In particular, we study zero-sum games and show that
-  FP converges to a fixed point, which for a network without any
-  self-loops corresponds to a Nash Equilibrium. In addition, we find that, for games
+  FP converges to a fixed point which, for a network without any
+  self-loops (i.e. agents are not `connected' to themselves), corresponds to a Nash Equilibrium. In addition, we find that, for games
   which are not zero-sum, agents following FP are able to
@@
 
-  To the best of our knowledge, this paper is the first time that a learning algorithm, which stems from game theoretic literature, has been studied on the network aggregative game, typically considered in the context of control and optimisation.
+  To the best of our knowledge, this paper is the first time that a learning algorithm, which stems from game theoretic literature, has been studied on the Network Aggregative game, typically considered in the context of control and optimisation.
 
@@
 given by Lipschitz functions with unique minimisers and apply standard
-topological fixed point towards designing algorithms which will
+topological fixed point arguments towards designing algorithms which will
 converge to the NE. Another approach for distributed NE seeking is the
@@
 unique minimiser. In fact this is a common assumption in works
-concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due
+concerning NA Games \cite{Zhu2021, Lei2020} which, we believe, is due
 to its ubiquity in control settings. We have not yet come across works
@@
 \textbf{Fictitious Play}
-%Fictitious Play
-was introduced in 1951 \cite{Brown1949} as a 'natural'
-way in which to approximate the Nash Equilibrium in zero sum games.
+
+was introduced in 1951 \cite{Brown1949} as a `natural'
+way in which to approximate the Nash Equilibrium in zero-sum games.
 Since then, a number of proofs of convergence have been determined for 2 player games \cite{Robinson1951, Miyasawa1961, Metrick1994,Berger2007, Monderer1997, Monderer1996}.
@@
 the opponent. Their payoff is given by the sum of payoffs in all of
-these subgames. It was found that, if this game is zero sum, then FP
+these subgames. It was found that, if this game is zero-sum, then FP
 will converge. Similar results for more than two players were found
@@
 \cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
-considered in a Mean Field Game, with convergence in zero sum
+considered in a Mean Field Game, with convergence in zero-sum
 games. The most general result, and the one most similar to our own,
@@
 game against the aggregate of their neighbours. We also
-extend a result for two player games found by Ostrovski and van Strien
+go beyond the zero-sum requirement by exteding a result for two player games found in
 \cite{Ostrovski2014} which showed that FP achieves no-regret to the
@@
 \section{Preliminaries}
-In this section we introduce the network aggregative game framework,
+In this section we introduce the Network Aggregative game framework,
 as well as defining FP on such a game.
@@
 \begin{definition}[Interaction Graph] \label{interactiongraph}
-	Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
+	Given a set of agents $\agentset$, an {\em interaction graph} $I = (\agentset, (\edgeset,
 	\weightset))$ is such that
@@
 
-		\item $\weightset \in M_N(\mathbb{R})$ is the weight adjacency matrix, whose elements $w^{\mu
+		\item $\weightset \in M_N([0, 1])$ is the weight adjacency matrix, whose elements $w^{\mu
 			\nu} \in [0, 1]$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
@@
 \begin{definition}[NA Game]
-	A {\em network aggregative game} is
+	A {\em Network Aggregative game} is
 	%defined as the
@@
 as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
-\xmuaction{i} = 1\}$. Also associated with each agent is a utility
-function
+\xmuaction{i} = 1\}$.
 
-The utility, for each agent $\mu$ and action profile
-$(\xmu, \xnotmu)$, is given as $u^\mu(\xmu, \xnotmu)$ in which we
+Also associated with each agent is a utility
+function. For each agent $\mu$ and action profile
+$(\xmu, \xnotmu)$, this is given as $u^\mu(\xmu, \xnotmu)$ in which we
 use the standard notation $-\mu$ to refer to all agents other than
 $\mu$. Notice that this requires that each agent plays the same
-strategy against all of their neighbours. What is unique about 
+strategy against all of their neighbours.
+
+What is unique about 
 NA games is the structure of the payoffs themselves. In this format,
-each agent $\mu$ receives a reference $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a weighted sum
-of each of their neighbours state.
-%Formally
-%
-%  \begin{equation}
-%    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
-%  \end{equation}
-
-Then, the agent must optimise their payoff with respect to the
-reference vector $\sigma^{\mu}$. Thus, instead of considering
+each agent $\mu$ receives a reference $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a convex combination
+of each of their neighbours' state. Agents must optimise their payoff with respect to this
+reference vector. Thus, instead of considering
 the actions of the entire population, or playing individual games
@@
 every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
-	\refmu)}$.
-
-Through the best response function, we can define the Nash Equilibrium (NE), a central concept of game theory. The NE condition requires that no rational agent has the incentive to deviate
+	\refmu)}$ \cite{Ostrovski2014}.
+Through the best response function, we can define the Nash Equilibrium (NE), a central concept of game theory.
+The NE condition requires that no rational agent has the incentive to deviate
 from their current state, as long as the other agents continue to play the NE strategy. This can be formalised by saying that all
@@
   respond optimally (i.e. play a best response) to this state. In the
-  case of an NA game, each agent considers their reference vector to
-  be their opponent. As such, each agent $\mu$ must update their state
-  according to the time-average of the reference vector $\refmu$. To formalise this we
+  case of an NA game, each agent considers their reference vector $\refmu$ to
+  be their `opponent'. As such, each agent $\mu$ must update their state
+  according to the time-average of $\refmu$. To formalise this we
   define $\avgref{\mu}$ as the time average of agent $\mu$'s reference
@@
     theoretic analysis is starting to consider various other forms of utility functions,
-    including monotone \cite{Tatarenko2020} and convex \cite{Parise2020}. We believe that the analysis of
+    including monotone and convex \cite{Parise2020}. We believe that the analysis of
     Fictitious Play should follow in these developments and we consider it as an important area
@@
     of joint actions is called a \emph{coarse correlated equilibrium}
-    if, for all agents $\mu$ and actions $j \in S^\mu$, we have
+    if, for all agents $\mu$ and all actions $j \in S^\mu$, we have
     $\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
@@
   As such, we would say that NA-CTFP has converged to the set of CCE if, in the limit of $t
-  \rightarrow \infty$, we have that for all agents $\mu$,
+  \rightarrow \infty$, we have that, for all agents $\mu$ and all actions $j \in S^\mu$,
 %  \begin{equation}
@@
   %\hspace{1cm} \
-  for all actions $j \in S^\mu$.
 %  \end{equation}

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Included Paper Checklist

@@
 In addition, we aim to understand the behaviour of agents learning through NA-CTFP, when the measurements on their reference signal $\refmu$ is corrupted with noise.
+The code required to reproduce these simulations is provided in the Supplementary Material.
 
@@
   with the choice $\beta \approx 0.576$ and set $A$ and $C$ according to the above with the choice $w \approx 0.288$.
+These choices are arbitrary and, as we discuss below, the results of this Section were found to hold for a range of choices of $\beta$ and $w$.
 The orbits that these payoff matrices generate can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which, for each player, lies in the centre of the simplex.
@@
     \centering
-    \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
+    \includegraphics[width = 0.9 \columnwidth]{Figures/Noise20Player.png}
     \caption{\label{fig::Noise20Player} Trajectories of NA-CTFP in a 20 player game with additive noise (Left) No noise is introduced and learning converges directly to an NE.
@@
     \centering
-    \includegraphics[width = \columnwidth]{Figures/3PlayerChainNoise.png}
+    \includegraphics[width = 0.9 \columnwidth]{Figures/3PlayerChainNoise.png}
     \caption{\label{fig::3PlayerChainNoise} Trajectories of NA-CTFP on the Three Player Chain of Section \ref{sec::NonConv} with additive noise.
@@
 %	
-	We also investigate the influence of noise on the algorithm and find that even with the introduction of additive noise, FP converges to a fixed point, though not necessarily the NE.
+	We also investigate the influence of noise on the algorithm and find that even with the introduction of additive noise, FP converges to a fixed point.
 In fact, for our cyclic family of games, we find that the introduction of noise can actually remove the periodicity, resulting in FP converging to a fixed point.
@@
 
-\begin{ack}
-Use unnumbered first level headings for the acknowledgments. All acknowledgments
-go at the end of the paper before the list of references. Moreover, you are required to declare 
-funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work). 
-More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2020/PaperInformation/FundingDisclosure}.
-
-Do {\bf not} include this section in the anonymized submission, only in the final paper.
-You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
-\end{ack}
-
 \bibliographystyle{named}
@@
 
+\section*{Checklist}
+
+\begin{enumerate}
+
+	\item For all authors...
+	\begin{enumerate}
+		\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
+		\answerYes{All contributions stated in the abstract are included in Sections 3-5 of the paper.}
+		\item Did you describe the limitations of your work?
+		\answerYes{Sec.
+2.3 discusses the assumptions placed on the theoretical results, as well as their implications.
+We provide numerical simulations to provide insight into the behaviour when some of these assumptions are lifted}
+		\item Did you discuss any potential negative societal impacts of your work?
+		\answerYes{In Sec. 5, we caution against the over-reliance of convergence in learning algorithms and provide experiments to show that this will not always be the case.}
+		\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
+		\answerYes{}
+	\end{enumerate}
+
+	\item If you are including theoretical results...
+	\begin{enumerate}
+		\item Did you state the full set of assumptions of all theoretical results?
+		\answerYes{}
+		\item Did you include complete proofs of all theoretical results?
+		\answerYes{Full Proofs, as well as the arguments used to derive them, are provided in the Supplementary Material}
+	\end{enumerate}
+
+	\item If you ran experiments...
+	\begin{enumerate}
+		\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
+		\answerYes{Code is provided in the supplementary material}
+		\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
+		\answerYes{We provide explanations as to the choice for our range of strength of noise in Sec 5.2.}
+		\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
+		\answerNA{Our experiments do not concern statistical results but are rather illustrative of the behaviour of a deterministic algorithm}
+		\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
+		\answerNA{}
+	\end{enumerate}
+
+	\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
+	\begin{enumerate}
+		\item If your work uses existing assets, did you cite the creators?
+		\answerNA{}
+		\item Did you mention the license of the assets?
+		\answerNA{}
+		\item Did you include any new assets either in the supplemental material or as a URL?
+		\answerNA{}
+		\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
+		\answerNA{}
+		\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
+		\answerNA{}
+	\end{enumerate}
+
+	\item If you used crowdsourcing or conducted research with human subjects...
+	\begin{enumerate}
+		\item Did you include the full text of instructions given to participants and screenshots, if applicable?
+		\answerNA{}
+		\item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
+		\answerNA{}
+		\item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
+		\answerNA{}
+	\end{enumerate}
+
+\end{enumerate}
+
 \end{document}

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Update neurips_2021.tex

@@
 These choices are arbitrary and, as we discuss below, the results of this Section were found to hold for a range of choices of $\beta$ and $w$.
-The orbits that these payoff matrices generate can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which, for each player, lies in the centre of the simplex.
+The resulting orbits can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which lies in the centre of the simplex.
 

### 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
various edits

@@
 
-\title{Equilibria and Convergence of Fictitious Play on Network Aggregative Games}
+\title{Equilibria and Convergence of Fictitious Play\\ on Network Aggregative Games}
 
@@
 
-\author{%
- Aamal Hussain  \\
-  Department of Computing\\
-  Imperial College London\\
-  South Kensington, London \\
-  \texttt{aamal.hussain15@imperial.ac.uk} \\
+%\author{%
+% Aamal Hussain  \\
+%  Department of Computing\\
+%  Imperial College London\\
+%  South Kensington, London \\
+%  \texttt{aamal.hussain15@imperial.ac.uk} \\
   % examples of more authors
-  \And
-  Francesco Belardinelli
+%  \And
+%  Francesco Belardinelli
   % Coauthor \\
@@
   % \texttt{email} \\
-}
+%}
 
@@
 \begin{abstract}
-Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.In this study, we contribute towards the study of learning with multiple agents.
-We do this through the introduction of learning on Network Aggregative games, in which each player's reward depends only on its own strategy and a convex combination of its neighbours.
-In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game.
-We show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium.
-In addition, we show that agents learning through Fictitious Play achieve no-regret, regardless of the choice of game.
-Finally, we present experimental evidence of a family of games for which Fictitious Play reaches a limit cycle and evidence that the introduction of noise has the potential to break this cyclic behaviour and allow agents to reach the Nash Equilibrium.
+Understanding the long term behaviour of learning algorithms is an
+important object of study if we are to design AI systems that are
+%can be considered
+safe. In this work, we contribute towards the study of
+learning with multiple agents. We do this through the introduction of
+learning on Network Aggregative (NA) games, in which each player's reward
+depends only on its own strategy and a convex combination of its
+neighbours. In particular, we present a continuous time analysis of
+the Fictitious Play learning dynamic on NA games. We show that
+Fictitious Play reaches a fixed point when the game is zero-sum, and
+provide conditions under which this fixed point corresponds to a Nash
+equilibrium. In addition, we show that agents learning through
+Fictitious Play achieve no-regret, regardless of the choice of
+game. Finally, we present experimental evidence of a family of games
+for which Fictitious Play reaches a limit cycle and evidence that the
+introduction of noise has the potential to break this cyclic behaviour
+and allow agents to reach the Nash equilibrium.
 \end{abstract}
@@
 
-Multi-Agent Learning \cite{Schwartz2014} requires a number of agents to adapt in an environment where
-each agent responds to the behaviour of the other agents. This leads to a
-fundamentally non-stationary problem, which presents a challenge to designing effective learning
-policies. Even when there are a small number of agents in the game, learning has been shown to lead
-to non-stationary, and even chaotic behaviour \cite{Sato2002}, a problem which becomes even more
-pronounced as the number of agents increase \cite{Sanders2018}.
-In this light, it would seem that, when there is a large population of agents, it is almost difficult to understand the long term behaviour of multi-agent learning \cite{Chotibut2021}.
-This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.
+Multi-agent learning \cite{Schwartz2014} requires a number of agents
+to adapt in an environment, where each agent responds to the behaviour
+of the other agents. This feature leads to a fundamentally non-stationary
+problem, which presents a challenge to designing effective learning
+policies. Even for a small number of agents in the game,
+learning has been shown to lead to non-stationary, and even chaotic
+behaviour \cite{Sato2002}, a problem that becomes even more
+pronounced as the number of agents increases \cite{Sanders2018}. In
+this light, it would seem that, when there is a large population of
+agents, it is extremely difficult to understand the long-term behaviour
+of multi-agent learning \cite{Chotibut2021}. This difficulty, of course, poses a
+problem for AI safety, for which it is desirable that learning systems
+are designed so that their ultimate behaviour is guaranteed to satisfy
+some predetermined goals.
 
-To deal with this problem, one must attempt to reduce the many player game to something which is
-tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
-and \emph{Aggregative} Games. The former makes the assumption of an infinite
-number of agents, so that the population can be represented through a distribution over players'
-states \cite{Huang2006}. Every agent then updates their action profiles depending on this
-distribution. In the latter each agent considers a real valued function which is a convex
-combination of the states of the other agents. Both formulation allows for a many player game to be reduced to a set of two-player games.
+To solve this problem, a promising approach is to reduce the
+many-player game to something that is tractable. A number of
+reductions have been proposed, most notably \emph{Mean Field} games
+and \emph{Aggregative} games. The former make the assumption of an
+infinite number of agents, so that the population can be represented
+through a distribution over players' states \cite{Huang2006}. Every
+agent then updates their action profiles depending on this
+distribution. In the latter, each agent considers a real valued
+function which is a convex combination of the states of the other
+agents. Both approaches allow for a many-player game to be reduced
+to a set of two-player games.
+%
+Further, both approaches have been the object of rigorous study, which has
+ shown that agents reach an equilibrium when learning on such
+games (cf.~\cite{Perrin2020} for Mean Field Games and
+\cite{Jensen2010, DePersis2020, Parise2020} for Aggregative
+Games). However, both also present a fundamental limitation.  Namely,
+they both require that agents have access to the action profiles of
+the entire population.  This could be through communication with all
+other agents, or through the intervention of a central coordinator who
+is able access the entire population. Whilst recent work aims to relax
+this assumption through the introduction of noise \cite{Perrin2020} or
+partial observability \cite{Elie2020}, the requirement that each agent
+updates their actions based on the entire population is rather strong
+and not always supported by empirical evidence.
 
-Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{Perrin2020} for Mean Field Games and
-\cite{Jensen2010, DePersis2020, Parise2020} for Aggregative Games). However, both also present a fundamental limitation.
-Namely, they both require that agents have access to the action profiles of the entire population.
-This could be through communication with all other agents, or through the intervention of a central
-coordinator who is able view the entire population. Whilst recent work aims to relax this assumption
-through the introduction of noise \cite{Perrin2020} or partial observability \cite{Elie2020}, the
-requirement that each agent updates their actions based on the entire population is rather strong and not always supported by empirical evidence.
-
-In this study, we investigate a variant of the aggregative game known as the \emph{Network
-Aggregative} (NA) Game.
-This format assumes that each agent updates their actions according only to those agents with whom they are connected on an underlying network.
-This significantly relaxes the communication load on each agent and
-lifts the need for a central coordinator. Recent work on NA games has shown that it is possible
-for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}.
-We contribute in this direction by analysing the long term behaviour of learning on an NA game.
-In particular, we analyse the Fictitious Play Learning
-Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely to the past behaviour of the others.
+In this study, we investigate a variant of aggregative games:
+%known as the
+\emph{Network Aggregative} (NA) games. This framework assumes that
+each agent updates their actions according only to those agents with
+whom they are connected on an underlying network. This assumption
+significantly relaxes the communication load on each agent and lifts
+the need for a central coordinator. Recent work on NA games has shown
+that it is possible for agents to reach an equilibrium strategy in an
+entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021,
+  Parise2015}. We contribute in this direction by analysing the
+long-term behaviour of multi-agent learning on NA games. In
+particular, we analyse the Fictitious Play learning algorithm
+\cite{Brown1949,Harris1998}, in which agents are assumed to be
+myopic, in that they react solely to the past behaviour of the others.
 
@@
 %
-  The main contribution of this work is to introduce and study learning on the Network Aggregative Game
-  through the action of Fictitious Play (FP).
-In particular, we aim to establish guarantees of convergence for learning under certain classes of games.
-This allows for games to be designed so that the long term behaviour of learning is predictable, regardless of how many agents are engaged in the game.
-As such, we are able to avoid the pitfalls of chaotic dynamics in games with many players as in \cite{Sanders2018}.
+  The main contribution of this work is to introduce and study convergence of
+  learning on Network Aggregative games through the action of
+  Fictitious Play (FP). In particular, we aim to establish guarantees
+  of convergence for learning under certain classes of games. Such guarantees
+  allow for games to be designed so that the long-term behaviour of
+  learning is predictable, regardless of how many agents are engaged
+  in the game. As such, we are able to avoid the pitfalls of chaotic
+  dynamics in games with many players, as shownin \cite{Sanders2018}.
 
-  We first show that, in aggregative games played with FP, a Nash Equilibrium exists and that FP admits
-  solutions in this setting. In particular, we study zero-sum games and show that
-  FP converges to a fixed point which, for a network without any
-  self-loops (i.e. agents are not `connected' to themselves), corresponds to a Nash Equilibrium. In addition, we find that, for games
-  which are not zero-sum, agents following FP are able to
-  achieve no regret.
+  We first show that, in NA games played with FP, a Nash equilibrium
+  exists and that FP admits solutions in this setting. Specifically,
+  we study zero-sum games and show that FP converges to a fixed point
+  which, for a network without any self-loops (i.e., agents are not
+  `connected' to themselves), corresponds to a Nash equilibrium. In
+  addition, we find that, for games which are not zero-sum, agents
+  following FP are able to achieve no regret.
 
-  Finally, we explore FP through numerical simulations to consider the
-  question of whether it always converges. We answer this in the negative by finding a family of
-  games in which action profiles cycle around the Nash Equilibrium. Finally, our experiments
-  document how noise affects the convergence of FP. Our experiments suggest that, under
-  the presence of noise, the algorithm still reaches a fixed point, but perhaps not the Nash
-  Equilibrium. This presents an interesting avenue for future research.
+  Further, we explore FP through numerical simulations to check
+  %consider the
+  %question of
+  whether it always converges. We answer this question
+  negatively, by finding a family of games in which action profiles cycle
+  around the Nash equilibrium. Finally, our experiments document how
+  noise affects the convergence of FP, suggesting that,
+  under the presence of noise, the algorithm still reaches a fixed
+  point, but perhaps not the Nash equilibrium. This presents an
+  interesting avenue for future research.
 
-  To the best of our knowledge, this paper is the first time that a learning algorithm, which stems from game theoretic literature, has been studied on the Network Aggregative game, typically considered in the context of control and optimisation.
+  To the best of our knowledge, this contribution is the first time that a
+  learning algorithm, which stems from game-theoretic literature, has
+  been studied on Network Aggregative games, typically considered
+  in the context of control and optimisation.
 
@@
 %NA games
-are a recent introduction \cite{Parise2015} which presents
-a variant of aggregative games by adding an underlying structure to
+are a recent extension \cite{Parise2015}
+%which presents a variant of
+of aggregative games, obtained by adding an underlying structure to
 the population. Since its introduction, distributed algorithms have
-been built with the aim of finding NE. In particular,
+been built with the aim of finding NE in NA games. In particular,
 \cite{Parise2015, Parise2020} consider the case in which payoffs are
 given by Lipschitz functions with unique minimisers and apply standard
-topological fixed point arguments towards designing algorithms which will
-converge to the NE. Another approach for distributed NE seeking is the
-projected gradient (resp. subgradient) dynamics which is explored in
-\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
-works, the cost function is assumed to be convex, and therefore have a
-unique minimiser. In fact this is a common assumption in works
-concerning NA Games \cite{Zhu2021, Lei2020} which, we believe, is due
+topological fixed-point arguments towards designing algorithms that
+converge to the NE. Another approach for searching for distributed NE the
+projected gradient (resp. subgradient) dynamics, which is explored in
+\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all these
+works, the cost function is assumed to be convex, and therefore has a
+unique minimiser. In fact, this is a common assumption in works
+about NA games \cite{Zhu2021, Lei2020} which, we believe, is due
 to its ubiquity in control settings. We have not yet come across works
@@
 to the best of our knowledge, this is the first work which introduces
-the application of a learning algorithm in the NA setting.
+the application of a learning algorithm in NA games.
 
-\textbf{Fictitious Play}
-
-was introduced in 1951 \cite{Brown1949} as a `natural'
-way in which to approximate the Nash Equilibrium in zero-sum games.
-Since then, a number of proofs of convergence have been determined for 2 player games \cite{Robinson1951, Miyasawa1961, Metrick1994,Berger2007, Monderer1997, Monderer1996}.
-However, the work looking
-at FP where there are more than two agents is sparse. \cite{Sela1999}
-considers a game in which a multi-player game is decomposed by
-requiring that each agent engage in a two person game against each of
-the opponent. Their payoff is given by the sum of payoffs in all of
-these subgames. It was found that, if this game is zero-sum, then FP
-will converge. Similar results for more than two players were found
-for games where all agents share the same payoff in
+\textbf{Fictitious Play} was introduced
+%in 1951
+as a `natural' way to approximate Nash equilibria in zero-sum games
+\cite{Brown1949}. Since then, a number of results on convergence have
+been proved for two-player games \cite{Robinson1951, Miyasawa1961,
+  Metrick1994,Berger2007, Monderer1997, Monderer1996}. However, 
+works looking at FP with more than two agents is
+sparse. In \cite{Sela1999}
+%considers
+%a game in which a
+multi-player games
+are decomposed
+%by requiring that each agent engage
+in two-plpayer games between each pair of players in the game.
+%against each of the opponent.
+Each agent's payoff is given by the sum of
+payoffs in all of these subgames. It was found that, if this game is
+zero-sum, then FP converges. Similar results for more than two
+players were found for games where all agents share the same payoff in
 \cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
-considered in a Mean Field Game, with convergence in zero-sum
+considered in a Mean Field game, with convergence in zero-sum
 games. The most general result, and the one most similar to our own,
-was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020}. It was found that FP converges in network games, where each
-agent is engaged in a two-player game with each of their neighbours
-Our work adapts this model to consider NA Games, so that the agents do not play
-individual games against each of their neighbours but rather a single
-game against the aggregate of their neighbours. We also
-go beyond the zero-sum requirement by exteding a result for two player games found in
-\cite{Ostrovski2014} which showed that FP achieves no-regret to the
+appears in
+%was found by Ewerhart and Valkanova in 2020
+\cite{Ewerhart2020}, in which the authors show
+%. It
+%was found
+that FP converges in network games, where each agent is
+engaged in a two-player game with each of their neighbours
+Our work extends the analysis
+of FP in multi-player games by considering its action in NA games,
+%Our work
+%adapts this model to consider NA Games,
+so that the agents do not play
+individual games against each of their neighbours, but rather a single
+game against the aggregate of their neighbours. We also go beyond the
+zero-sum requirement by exteding a result for two-player games
+in \cite{Ostrovski2014} which showed that FP achieves no-regret in the
 multi-player setting.

### 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
Updated according to comments

@@
   in the game. As such, we are able to avoid the pitfalls of chaotic
-  dynamics in games with many players, as shownin \cite{Sanders2018}.
+  dynamics in games with many players (also called `agents'), as shownin \cite{Sanders2018}.
 
@@
 	%
-	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
+	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two-player game \cite{}.
 \end{remark}
@@
     In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
-    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
+    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, Fictitious Play requires that the agents update their
     strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
@@
   \begin{remark}
-    As usual, the notion of CCE in an NA game is a natural extension of the CCE for two player
-    games. In fact, if we consider the NA game to be a two player game with no self-loops, then
-    we recover exactly the definition of the CCE set in two player games \cite{Ostrovski2014}.
+    As usual, the notion of CCE in an NA game is a natural extension of the CCE for two-player
+    games. In fact, if we consider the NA game to be a two-player game with no self-loops, then
+    we recover exactly the definition of the CCE set in two-player games \cite{Ostrovski2014}.
   \end{remark}
@@
     reader should consult \cite{Ostrovski2014} for an excellent exposition regarding the
-    link between the CCE set and average regret in two player games which, of course, extends
+    link between the CCE set and average regret in two-player games which, of course, extends
     naturally to NA Games.
@@
     and, of course, can be related to the \emph{cumulative regret} which is used for analysis
-    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
+    in \cite{Cesa-Bianchi2021}.  To illustrate the average regret, let us
     consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
@@
 
-  As an adaptation, we take the example of a three player chain, in which player $2$ is connected to $1$ and $3$. The aggregation matrix can be given as
+  As an adaptation, we take the example of a three-player chain, in which player $2$ is connected to $1$ and $3$. The aggregation matrix can be given as
 %
@@
   We first consider the zero-sum case to show that it does indeed converge to an equilibrium as expected.
-Note that the zero-sum condition (Assumption \ref{ass::zerosum}) given for the three player chain is given as
+Note that the zero-sum condition (Assumption \ref{ass::zerosum}) given for the three-player chain is given as
 %
@@
     \end{subfigure}
-    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain for which the NE lies at the centre of the simplex. (a) Payoffs are given by
+    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three-Player Chain for which the NE lies at the centre of the simplex. (a) Payoffs are given by
     (\ref{eq::zeroSumShapley}). The plot shows NA-CTFP yields convergence to the NE (b)
@@
     \includegraphics[width = 0.9 \columnwidth]{Figures/Noise20Player.png}
-    \caption{\label{fig::Noise20Player} Trajectories of NA-CTFP in a 20 player game with additive noise (Left) No noise is introduced and learning converges directly to an NE.
+    \caption{\label{fig::Noise20Player} Trajectories of NA-CTFP in a 20-player game with additive noise (Left) No noise is introduced and learning converges directly to an NE.
 (Middle) $\gamma = 0.05$, the trajectories converge to a fixed point but removed from the NE.
@@
 
-  The fictitious play process in NA games requires that, at each time step, an agent takes a
+  The Fictitious Play process in NA games requires that, at each time step, an agent takes a
   `measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
@@
 
-  In Figure \ref{fig::3PlayerChainNoise} we revisit the Three Player Chain of Section
+  In Figure \ref{fig::3PlayerChainNoise} we revisit the Three-Player Chain of Section
   \ref{sec::NonConv}, now under the influence of additive noise. For the sake of brevity, we only
@@
 %	
-	Finally, we note that in recent years FP in two player games has shown a remarkable variety of dynamical behaviours, including periodicity and chaos.
+	Finally, we note that in recent years FP in two-player games has shown a remarkable variety of dynamical behaviours, including periodicity and chaos.
 In our work we have shown convergence to a fixed point and, through experiments, periodicity.

### 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
various edits

--- 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
@@
 In this section we introduce the Network Aggregative game framework,
-as well as defining FP on such a game.
+as well as defining Fictitious Play on such games.
 
@@
 \begin{definition}[Interaction Graph] \label{interactiongraph}
-	Given a set of agents $\agentset$, an {\em interaction graph} $I = (\agentset, (\edgeset,
+	Given a set  $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
 	\weightset))$ is such that
@@
 is defined
-as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
+as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \mid \sum_i
 \xmuaction{i} = 1\}$.
@@
 function. For each agent $\mu$ and action profile
-$(\xmu, \xnotmu)$, this is given as $u^\mu(\xmu, \xnotmu)$ in which we
+$(\xmu, \xnotmu)$, the utility is given as $u^\mu(\xmu, \xnotmu)$ in which we
 use the standard notation $-\mu$ to refer to all agents other than
@@
 What is unique about 
-NA games is the structure of the payoffs themselves. In this format,
-each agent $\mu$ receives a reference $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a convex combination
+NA games is the structure of the payoffs themselves.
+%In this format,
+Each agent $\mu$ receives a {\em reference} $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a convex combination
 of each of their neighbours' state. Agents must optimise their payoff with respect to this
@@
 %
-where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can write the game $\Gamma$ with the payoff
+where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can rewrite the game $\Gamma$ with the payoff
 matrices $A^\mu$ in place of the utility functions
@@
 
-The agent's goal
-is to maximise their payoff $u^\mu$ with respect to their reference vector $\refmu$. As
-such, we define the best response correspondence $BR^\mu$, which maps
-every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
-	\refmu)}$ \cite{Ostrovski2014}.
-Through the best response function, we can define the Nash Equilibrium (NE), a central concept of game theory.
-The NE condition requires that no rational agent has the incentive to deviate
-from their current state, as long as the other agents continue to play the NE strategy. This can be formalised by saying that all
-agents are playing their best response to each other.
+The agent's goal is to maximise their payoff $u^\mu$ with respect to
+their reference vector $\refmu$. As such, we define the best response
+correspondence $BR^\mu$, which maps every $\refmu$ to the set $\arg
+\max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$
+\cite{Ostrovski2014}. Through the best response function, we can
+define the Nash equilibrium (NE), a central concept of game
+theory. The NE condition requires that no rational agent has an
+incentive to deviate from their current state, as long as the other
+agents continue to play the NE strategy. This can be formalised by
+saying that all agents are playing their best response to each other.
 %
-This leads naturally to the definition of a Nash Equilibrium in an NA game as
+This leads naturally to the definition of a Nash equilibrium in an NA game as
 %
@@
 	%It can be seen that
-	The notion of Nash equilibrium in NA Games is a natural
-	extension of the NE in a bimatrix game.
+	The notion of Nash equilibrium in NA games is a natural
+	extension of the NE in bimatrix games.
 	%$(A, B)$.
 	In particular, if we consider an NA game with only two players and no
-	self-loops then the above definition yields that $ \NE{1}$ is an NE iff
+	self-loops, then Def.~\ref{def::NE} yields that $ \NE{1}$ is an NE iff
 	%
 	%    \begin{equation*}
-	$     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2})$,
+	$     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x \in \Delta_1} u^1 (x, \NE{2})$,
 	%    \end{equation*}
 	%
-	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
+	and similarly for $\NE{2}$. This is precisely the definition of NE in a two-player game \cite{}.
 \end{remark}
 
-We will show that the NE exists for an NA game in Section \ref{sec::CTFPAnalysis}.
+In Section \ref{sec::CTFPAnalysis} we show that NE exist for NA games.
 
@@
   considers the average state of their opponent in the past, and
-  respond optimally (i.e. play a best response) to this state. In the
+  responds optimally (i.e., play a best response) to this state. In the
   case of an NA game, each agent considers their reference vector $\refmu$ to
@@
   $\refmu$ up until time $t$.
-  \begin{equation}
+  \begin{equation*}
     \avgref{\mu} = \frac{1}{t} \int_0^t \refmu(s) \; ds.
-  \end{equation}
+  \end{equation*}
 
-  Using this, we follow in the footsteps of  \cite{Ewerhart2020} and \cite{Harris1998} to define
-  Fictitious Play in continuous time, but with a slight adaptation for NA Games.
+  Using this idea, we follow in the footsteps of  \cite{Ewerhart2020} and \cite{Harris1998} to define
+  Fictitious Play in continuous time, but with a slight adaptation for NA games.
 %
   \begin{definition}[Fictitious Play on Network Aggregative Games] \label{def::NACTFP}
-    We define Continuous Time Fictitious Play (CTFP) on NA Games as a measurable map $m$ with components $m^\mu$ such that for all agents $\mu$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
+    We define Continuous Time Fictitious Play (CTFP) on NA games as a measurable map $m$ with components $m^\mu$ such that for all agents $\mu$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
     BR^\mu(\alpha_{\sigma}^\mu)$ for almost all time $t \geq 1$. Henceforth, $m$ will be called an \emph{NA-CTFP}.
@@
 
-  We can think of this definition as saying that the player plays some arbitrary strategy before
-  $t = 1$, but beyond this it must play a best response to the time average of its reference
-  signal. We also refer to this measurable map as a `path'. In Section \ref{sec::CTFPAnalysis}, we prove that a path $m$ which satisfies this definition exists.
+  We can think of Def.~\ref{def::NACTFP} as saying that the player plays some arbitrary strategy before
+  $t = 1$, but beyond this they must play a best response to the time average of its reference
+  signal. We also refer to this measurable map as a `path'. In Section \ref{sec::CTFPAnalysis}, we prove that a path $m$ which satisfies Def.~\ref{def::NACTFP} exists.
 
   \begin{remark}
-    As an illustration, consider NA Games with two players, in which $\edgeset = \{(1, 2),
-    (2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
+    As an illustration, consider NA games with two players, in which $\edgeset = \{(1, 2),
+    (2, 1)\}$ and $\weightset$ is a $2\times 2$ matrix with zeros on its leading diagonal and ones on
     the off diagonal. We write the time-average of both agents' state as
@@
     \end{align*}
-    In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
+    In this manner, $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
     agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
     strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
-    seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
+    seen, therefore, that NA-CTFP is a natural extension of CTFP in the classic
     two-player setting \cite{Hofbauer2006}.
@@
     The weighted adjacency matrix $\weightset$ is constant and
-    \emph{row stochastic} meaning that the sum elements in each row of
+    \emph{row stochastic} meaning that the sum \fb{of} elements in each row of
     $\weightset$ is equal to one. This assumption is made to ensure
     that the analysis of NA games can be derived as a natural
-    extension to the classical setting of two-player games. We can
+    extension of the classic setting of two-player games. We can
     think of the row stochastic condition as the ability of each agent
     to prioritise the state information it receives from each of its
-    neighbours. It is also a classical assumption made in the analysis
+    neighbours. It is also a standard assumption made in the analysis
     of networks and is straightforward to implement \cite{Mai2019}.
@@
   \begin{assumption}\label{ass::matrixgame}
-    The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
-    have a rich history in game theory and allow for the design of multi-agent systems in
-    computational settings, particularly in the case of task and resource allocation \cite{Nisan2007}. It should be noted, however, that game
-    theoretic analysis is starting to consider various other forms of utility functions,
-    including monotone and convex \cite{Parise2020}. We believe that the analysis of
-    Fictitious Play should follow in these developments and we consider it as an important area
-    of future work.
+    The payoffs are given through matrix games and, therefore, are
+    bilinear. Payoff matrices have a rich history in game theory and
+    allow for the design of multi-agent systems in computational
+    settings, particularly in the case of task and resource allocation
+    \cite{Nisan2007}. It should be noted, however, that game-theoretic
+    analysis is starting to consider various other forms of utility
+    functions, including monotone and convex \cite{Parise2020}. We
+    believe that the analysis of Fictitious Play should follow in
+    these developments and we consider it as an important area of
+    future work.
   \end{assumption}
@@
   \begin{assumption}\label{ass::sameactions}
-    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
-    a classical assumption which is made in most game theoretic settings and includes, as a
-    special case. However, it should be noted that,
-    in \cite{Ewerhart2020}, CTFP was analysed without this requirement.  
+    The cardinality of each action set $|\actionset{\mu}|$ is equal
+    for all agents. This is another standard assumption that is made in
+    most game0theoretic settings and includes \fb{?}, as a special
+    case. However, it should be noted that, in \cite{Ewerhart2020},
+    CTFP is analysed without this assumption.
   \end{assumption}
@@
   \begin{assumption}\label{ass::zerosum}
-    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum) = 0$ for any set
-    of states $(x^\mu)_{\mu \in N^\mu}$. This is, perhaps, one of the stronger assumptions in
-    our analysis, and is required for the fixed point analysis. However, in Section
-    \ref{sec::CCEConvergence}, we perform a regret analysis that considers the long term
-    behaviour of NA-CTFP without this assumption.
+    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu,
+    \weightedsum) = 0$ for any set $(x^\mu)_{\mu \in N^\mu}$ of
+    states. This is, perhaps, one of the strongest assumptions in our
+    analysis, which is required for the fixed-point analysis. However,
+    in Sec.~\ref{sec::CCEConvergence}, we perform a regret analysis
+    that considers the long-term behaviour of NA-CTFP without this
+    assumption.
   \end{assumption}

### 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
various edits
Final Updates

@@
     The weighted adjacency matrix $\weightset$ is constant and
-    \emph{row stochastic} meaning that the sum \fb{of} elements in each row of
+    \emph{row stochastic} meaning that the sum of elements in each row of
     $\weightset$ is equal to one. This assumption is made to ensure
@@
     for all agents. This is another standard assumption that is made in
-    most game0theoretic settings and includes \fb{?}, as a special
-    case. However, it should be noted that, in \cite{Ewerhart2020},
+    most game-theoretic settings. However, it should be noted that, in \cite{Ewerhart2020},
     CTFP is analysed without this assumption.

### 2021-08-02 Code/Q-Learning/StabilityandChaos/StabilityinPolymatrixGames/StabiltyChaosNQL.tex
Added AAAI 2022 Folder

\documentclass[preprint,12pt]{article}

\usepackage{amsmath, amsfonts, amsthm}
\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{csquotes}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\theoremstyle{example}
\newtheorem{example}{Example}

\newcommand{\agentset}{\mathcal{N}}
\newcommand{\actionset}[1]{S^{#1}}
\newcommand{\utility}[1]{u^{#1}}
\newcommand{\NEX}{\mathbf{\bar{p}}}
\newcommand{\NEY}{\mathbf{\bar{q}}}
\newcommand{\NE}{\mathbf{\bar{x}}}

\newcommand{\A}{\mathbf{A}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\pure}[1]{\mathbf{e}_{#1}}

\newcommand{\R}{\mathbb{R}}

\newcommand{\X}{\mathcal{X}}

\newcommand{\xmu}{x^\mu}
\newcommand{\xnu}{x^\nu}

\usepackage{changepage}
\usepackage{bbm}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[toc,page]{appendix}
\usepackage[font={small,it}]{caption}
\usepackage{verbatim}
\usepackage{subfiles}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=1in,letterpaper]{geometry}
\usepackage{xcolor}
\usepackage{listings}
\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\renewcommand{\labelenumi}{\Roman{enumi}}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}

\newcommand{\ah}[1]{\textcolor{blue}{\textit{#1}}}

\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{\leftmark}

\title{Stability and Chaos in Q-Learning}

\begin{document}

	\maketitle

	The dynamics we're dealing with are

	\begin{equation}
		\frac{\dot{x}^\mu_i}{x^\mu_i} = \left( \sum_{\nu \in N_\mu} (A \xmu)_i - \xmu A \xnu \right) - T (ln \xmu_i - \langle \xmu, ln \xmu \rangle)
	\end{equation}

	Now we take the specific case of a two-player game. We can define this in two ways. Either, we choose

	\begin{equation}
		A = \begin{pmatrix}
			0 & r \\ s & 0
		\end{pmatrix}
	\end{equation}

	or

	\begin{equation}
		A = \begin{pmatrix}
			1 & S \\ T & 0
		\end{pmatrix}
	\end{equation}

	Both work, but I will start analysing the first case. In this format, if we abuse notation and write $\x^\mu = (\xmu, 1 - \xmu)$, the dynamics can be written as

	\begin{equation}
		\dot{x}^\mu = x^\mu_i (1 - x^\mu) \left( \sum_{\nu \in N_\mu} r - (r + s) \xnu(t)  - T ln \frac{x^\mu}{1 - x^\mu} \right)
	\end{equation}

	This tells us that a fixed point can only occur where, for each $\mu$, either $\xmu = 0$, $\xmu = 1$ or

	\begin{align} \label{eq::fixedpointcondition}
		& \left( \sum_{\nu \in N_\mu} r - (r + s) \xnu(t)  - T ln \frac{x^\mu}{1 - x^\mu} \right) = 0 \nonumber \\
		& \implies \frac{1}{|N_\mu|} \sum_{\nu \in N_\mu} x^\nu(t) = \frac{r}{r + s} - \frac{T}{r + s} ln \frac{x^\mu}{1 - x^\mu} 
	\end{align}

	\subsection*{Interpretation: Allowable Fixed Points at Extreme Temperatures}

	This immediately tells us something about what fixed points occur at the extremes $T \rightarrow 0$ and $T \rightarrow \infty$. For (\ref{eq::fixedpointcondition}) to make sense, the right hand side must lie in the range $[0, 1]$. The reason for this is that the left hand side must be an average over values in $[0, 1]$. For this to make sense, then we must have

	\begin{equation}
		0 \leq \frac{r}{r + s} - \frac{T}{r + s} ln \frac{x^\mu}{1 - x^\mu} \leq 1
	\end{equation}

	which translates to

	\begin{equation}
	\frac{exp(r/T)}{1 + exp(r/T)} \geq \xmu \geq \frac{exp(-s/T)}{1 + exp(-s/T)}
	\end{equation}

	We will start by trying to understand the behaviour of Q-Learning close to the fixed point. This can be done by finding the eigenvalues of the Jacobian of the dynamics. Specifically, the Jacobian $J$ is given by

	\subsection*{Linear Stability of Network QL dynamics}

	\begin{align}
		\left( J \right)_{\mu \mu} = \frac{\partial f_\mu}{\partial x^\mu} =  &(1 - 2 \xmu)\left[ \sum_{\nu \in N_\mu} r - (r + s) \xnu \right] -  T \left( (1 - 2\xmu) \, ln \frac{\xmu}{1 - \xmu} + 1 \right)
	\end{align}

	\begin{align}
		\left( J \right)_{\mu \nu} = \frac{\partial f_\mu}{\partial x^\nu}  = \begin{cases}
			-(r + s)\xmu(1 - \xmu) \hspace*{1cm} & \nu \in N_\mu \\ 
			0 & \text{otherwise}
		\end{cases}
	\end{align}

	Our job now is to determine the eigenvalues of this Jacobian so that we can assess, on a local scale, the nature of these fixed points. This was done for the case $T = 0$ in the original reference. We now try to understand the effect that T plays on our dynamics. In particular, our goal is to determine whether it is correct to say that chaotic dynamics do not occur in two player games, for any choice of $T$. This was shown to be true for the $T = 0$ case, so we will focus our attention on the $T > 0$ problem. Along the way, we may wish to understand the stability of the fixed points themselves.

	\subsubsection*{Boundary Fixed Points}

	For the case $\xmu = 0$ or $\xmu = 1$ we have that

	\begin{equation}
		\left( J \right)_{\mu \nu} = -(r + s)\xmu(1 - \xmu) = 0 \hspace{1cm}  \forall \nu,
	\end{equation}

	which means that all of the off-diagonal elements are zero. The eigenvalues are then determined by

	\begin{equation}
		\lambda_\mu = (1 - 2 \xmu)\left[ \sum_{\nu \in N_\mu} r - (r + s) \xnu \right] -  T \left( (1 - 2\xmu) \, ln \frac{\xmu}{1 - \xmu} + 1 \right)
	\end{equation}

	which is entirely real-valued.

	\subsection{Interior Fixed Points}

	As we increase $T$, the fixed points move off the boundary and towards the centre of the simplex. In this case, $(J)_{\mu \nu} \neq$. However, as we remain close to the boundary, its contribution is small. Rather, the eigenvalues are dominated by the diagonal term, which is still negative. Therefore, we would expect that fixed points close to the boundary are similarly

	\subsection*{Dissipative Dynamics}

	\begin{theorem}
		Network Q-Learning is a dissipative system for any choice of $T > 0$. 
	\end{theorem}

	\begin{proof}
		WRITE PROOF
	\end{proof}

\end{document}

### 2021-08-02 Documents/ChaoticDynamics/AAAI 2022/Formatting-Instructions-LaTeX-2022.tex
Added AAAI 2022 Folder

\def\year{2022}\relax
%File: formatting-instructions-latex-2022.tex
%release 2022.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai22}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{xcolor} % REMOVE THIS AT THE END
\newcommand\fb[1]{\textcolor{red}{\textit{FB: #1}}}
\newcommand\ah[1]{\textcolor{blue}{\textit{AH: #1}}}

%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%
%\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (Stability and Chaos in Multi Agent Reinforcement Learning)
/Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen, Francisco Cruz, Marc Pujol-Gonzalez)
/TemplateVersion (2022.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai22.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\title{Stability and Chaos in Multi-Agent Reinforcement Learning}
\author{
    %Authors
    % All authors must be in the same font size and format.
    Anonymous Submission
}
\affiliations{

}

%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse
\title{My Publication Title --- Single Author}
\author {
    Author Name
}
\affiliations{
    Affiliation\\
    Affiliation Line 2\\
    name@example.com
}
\fi

\iffalse
%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\title{My Publication Title --- Multiple Authors}
\author {
    % Authors
    First Author Name,\textsuperscript{\rm 1}
    Second Author Name, \textsuperscript{\rm 2}
    Third Author Name \textsuperscript{\rm 1}
}
\affiliations {
    % Affiliations
    \textsuperscript{\rm 1} Affiliation 1\\
    \textsuperscript{\rm 2} Affiliation 2\\
    firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
}
\fi

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
\usepackage{bibentry}
% END REMOVE bibentry

\begin{document}

\maketitle

\begin{abstract}
AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors. To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions.
\end{abstract}

\section{Draft Outline}

\begin{enumerate}
	\item Introduction - Contributions \begin{itemize}
		\item Analysis of Network Q-Learning with varying parameters and number of players
		\item Show that the prevalence of chaotic dynamics remains unaffected by the number of players in the game
		\item Show that QL cannot give chaos in 2 action matrix games
		\item As an example: QL can stabilise the rock-paper-scissors game, for which RD is chaotic
		\item Numerical Simulations to find the convergent behaviour in Network QL Games
		\item Numerical Simulations to determine Lyapunov Exponents in Network QL Games
	\end{itemize}

	\item Preliminaries \begin{itemize}
		\item Network Q-Learning Dynamics
		\item Maximum Entropy Argument for Gaussian Payoffs
	\end{itemize}

	\item Stability of Q-Learning \begin{itemize}
		\item \ah{For the sake of space it may actually be best to not present the equations themselves, but rather their visualisation}
		\item Present numerical simulations of theory
	\end{itemize}

	\item Analysis of Q-Learning in 2 action games \begin{itemize}
		\item Present discussion of results and what it means for the eigenvalues to have no imaginary component (\ah{Need to find a reference for this}) (cite original paper which looked at this problem for RD)
	\end{itemize}

	\item Experimental Evaluation \begin{itemize}
		\item Construction of Numerical Experiments: Convergence and Lyapunov
		\item Discussion: Correspondence with theory and implications for RL. Comparison with Sanders' result
	\end{itemize}

	\item Conclusion

\section{Outline for Supplementary Material}

\begin{enumerate}
	\item Introduction
	\item Dynamics of Q-Learning
	\item Generating Functional Analysis (same as what we already have)
	\item Stability of Q-Learning in 2x2 games \begin{itemize}
		\item Proof that Q-Learning is invariant under linear transformations of the payoff matrix
		\item Derivation of the Jacobian for Q-L (cite Piliouras for the diagonal elements)
		\item Eigenvalue for non-zero fixed points, explaining why fixed points do not occur on the boundary. Show that they are real valued (cite result of eigenvalue of sum being sum of eigenvalues)
	\end{itemize}
	\item Further Numerical Experiments \begin{itemize}
		\item Lyapunov 
		\item Convergence
	\end{itemize}
\end{enumerate}

\end{enumerate}

\end{document}

### 2021-08-02 Documents/FP in NAGs/Convex FP/ConvexFP.tex
Added AAAI 2022 Folder

\documentclass[preprint,12pt]{article}

\usepackage{amsmath, amsfonts, amsthm}
\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{csquotes}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\theoremstyle{example}
\newtheorem{example}{Example}

\newcommand{\agentset}{\mathcal{N}}
\newcommand{\actionset}[1]{S^{#1}}
\newcommand{\utility}[1]{u^{#1}}
\newcommand{\NEX}{\mathbf{\bar{p}}}
\newcommand{\NEY}{\mathbf{\bar{q}}}
\newcommand{\NE}{\mathbf{\bar{x}}}

\newcommand{\A}{\mathbf{A}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\pure}[1]{\mathbf{e}_{#1}}

\newcommand{\R}{\mathbb{R}}

\newcommand{\X}{\mathcal{X}}

\newcommand{\xmu}{x^\mu}

\usepackage{changepage}
\usepackage{bbm}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[toc,page]{appendix}
\usepackage[font={small,it}]{caption}
\usepackage{verbatim}
\usepackage{subfiles}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=1in,letterpaper]{geometry}
\usepackage{xcolor}
\usepackage{listings}
\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\renewcommand{\labelenumi}{\Roman{enumi}}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}

\newcommand{\ah}[1]{\textcolor{blue}{\textit{#1}}}

\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{\leftmark}

\title{Convex NA-FP}

\begin{document}
	\maketitle

	\section{Setup}

	The setup for this problem is the same as it was for the original previous paper. The major difference comes in the definition of the cost function. Let us define, for each agent, a convex $\mathcal{C}^1$ function

	\begin{equation}
			u^\mu: \times_{\mu} \Delta_\mu \rightarrow \Delta_\mu
	\end{equation}

	The goal of the agent is to choose its action $x^\mu$ so as to minimise its cost function with respect to the time average of its reference vector $\sigma^\mu (t)$. More formally, we define the best response function $BR^\mu$ as

	\begin{equation}
		BR^\mu(\alpha_\sigma^\mu(t) )= \arg \min_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu (t)), 
	\end{equation}

	in which

	\begin{equation}
		\alpha_\sigma^\mu(t) = \frac{1}{t} \int_0^t \sigma^\mu(s) ds.
	\end{equation}

	\begin{remark}
		Just as a quick note, we defined the function $u^\mu$ to be convex so that its argmin (i.e. the best response function) would be singular valued. This may not be entirely required, as we have dealt with set-valued functions in the previous paper, but it is a useful start. Secondly, we enforced that the function is $\mathcal{C}^1$ so that we can ensure it is differentiable and that the differential is continuous in both of its arguments. 
	\end{remark}

	Other than the above, the setup is exactly the same as was the case for the previous paper.

	\section{Existence of the Convex CTFP}

	This proof follows a similar structure to the one that we did for the original NA-CTFP paper. The major difference comes in the definition of the utility (or in this case the cost) function.

	\begin{theorem}
		The convex NA-CTFP exists
	\end{theorem}

	\begin{proof}[Proof Sketch]
		Start with the definition of $\alpha^\mu(t)$

		\begin{equation}
			\alpha^\mu(t) = \frac{1}{t} \int_0^t x^\mu(s) ds 
		\end{equation}

		Then,

		\begin{equation}
			\dot{\alpha}^\mu(t) = \frac{1}{t} \left( BR^\mu(\alpha_\sigma^\mu(t) ) - \alpha^\mu(t)  \right)
		\end{equation}

		In the same way as last time, we can concatenate into

		\begin{equation}
			\alpha(t) = \begin{bmatrix}
				\alpha^1(t)^T, \ldots, \alpha^N(t)^T
			\end{bmatrix}^T \subset \mathbb{R}^{Nn}
		\end{equation}

	Next, we rewrite the aggregation as

 	\begin{equation}
		\sum_{\nu \in N^\mu} w^{\mu \nu} \alpha^\nu = (w_{-\mu}^T \otimes I_n) \begin{bmatrix}
			\alpha^1 \\ . \\ . \\ . \\ \alpha^N
		\end{bmatrix} = (w_{-\mu}^T \otimes I_n) \alpha(t)
	\end{equation}

	So now our dynamic is

	\begin{equation}
		\dot{\alpha}(t) = \frac{1}{t} \left( \begin{bmatrix}
			\arg\min_{y \in \Delta_1} u^1(y, (w_{-1}^T \otimes I_n) ( \alpha (t) ) ) \\ . \\ . \\ . \\ \arg\min_{y \in \Delta_N} u^N(y, (w_{-N}^T \otimes I_n)( \alpha (t) ))
		\end{bmatrix}  - \alpha(t)  \right)
	\end{equation}

	Now, since we enforced that the function $u^\mu$ is to be $\mathcal{C}^1$ for all agents $\mu$, we can (\ah{I'm quite sure?}) assert that the function

	\begin{equation}
		f(x) = \begin{bmatrix}
			\arg\min_{y \in \Delta_1} u^1(y, (w_{-1}^T \otimes I_n) ( x ) ) \\ . \\ . \\ . \\ \arg\min_{y \in \Delta_N} u^N(y, (w_{-N}^T \otimes I_n)( x ))
		\end{bmatrix} 
	\end{equation}

	is continuous. Furthermore, due to the continuity of the cost function and compactness of $\Delta$, we know that the argmin is non-empty. Since it is also convex, the argmin is singular valued and so is compact and convex-valued. It is clearly bounded, since $\Delta$ is bounded. All of these conditions together ensure that there exist solutions to the convex NA-CTFP dynamic.
	\end{proof}

	\section{Stability of convex NA-CTFP}

	Firstly, it should be said that, thanks to the work of Grammatico, we know that a Nash Equilibrium exists for the NA-Game when the cost is given by a convex function. Since the NE correspond exactly to the fixed points of Fictitious Play, we know that our dynamic admits fixed points.

	This is where the analysis becomes a bit more tricky. To make it a little easier, we should first introduce the NA-CTFP with convex costs on two-player games. We will also focus on a particular sub-family of convex functions, namely quadratic costs. \ah{I chose this mostly because it satisfies our assumptions and they are the ones most often used in control problems}.

	Consider the costs given by

	\begin{align}
		u^A(x, q) = || x - x_d ||^2_{A_1} + || x - q ||^2_{A_2} \nonumber \\
		u^B(y, p) = || y - y_d ||^2_{B_1} + || y - p ||^2_{B_2}
	\end{align}

	in which

	\begin{equation}
		p(t) = \frac{1}{t} \int_0^t x(s) ds, \hspace{0.5cm} 	q(t) = \frac{1}{t} \int_0^t y(s) ds.
	\end{equation}

	Then we have

	\begin{align}
		BR^A(q(t)) = (A_1^T + A_2^T)^{-1} (A_1^T x_d + A_2^T q(t)) =: \bar{A}_1 x_d + \bar{A}_2 q(t) \nonumber \\
		BR^B(p(t)) = (B_1^T + B_2^T)^{-1} (B_1^T y_d + B_2^T p(t)) =: \bar{B}_1 x_d + \bar{B}_2 p(t)
	\end{align}

	The important thing to notice is that the best response function is linear in $q(t)$ and $p(t)$. This means, we can define our convex NA-CTFP dynamic as

	\begin{align}
		\dot{p}(t) = \bar{A}_1 x_d + \bar{A}_2 q(t) - p(t) \nonumber \\
		\dot{q}(t) = \bar{B}_1 y_d + \bar{B}_2 p(t) - q(t).
	\end{align}

	Which itself is a linear dynamical system. This means that we can apply the techniques of linear dynamical systems to determine its stability. First we transform our variables $p \rightarrow p - \bar{A}_1 x_d$ (and same for $q(t)$). I will also call $\bar{A}_2$ as $\bar{A}$, and same for $\bar{B}$ to make the notation a little easier

	\begin{equation}
		\frac{d}{dt} \begin{pmatrix}
			p(t) \\ q(t)
		\end{pmatrix} = \begin{pmatrix}
		-I_n & \bar{A} \\ - I_n & \bar{B}
		\end{pmatrix} \begin{pmatrix}
		p(t) \\ q(t)
	\end{pmatrix}
	\end{equation}

	Now, the stability of our fictitious play dynamic is determined entirely by the eigenvalues of

		\begin{equation}
		\begin{pmatrix}
			-I_n & \bar{A} \\ - I_n & \bar{B}
		\end{pmatrix} 
	\end{equation}

	If they are all negative, then the system is stable. If any eigenvalue is positive, then the system is unstable. The eigenvalues are determined from the characteristic function

	\begin{equation}
		det \left\{ (-1 - \lambda)(\bar{B} - \lambda I_n) + \bar{A} \right\} = 0
	\end{equation}

	Our job now is to determine conditions on $\bar{A}$ and $\bar{B}$ so that $\lambda$ comes out negative. To begin with we have that, if $\bar{A}$ and $\bar{B}$ commute (i.e. $\bar{A}\bar{B} = \bar{B}\bar{A}$), then our eigenvalues satisfy (\ah{Need to find the reference for this, but I am using the following result: As a direct consequence of simultaneous triangulizability, the eigenvalues of two commuting complex matrices A, B with their algebraic multiplicities (the multisets of roots of their characteristic polynomials) can be matched up})

	\begin{equation}
		\prod_{i = 1}^{n} (-1 - \lambda_i) (\beta_i - \lambda_i) + \alpha_i = 0, 
	\end{equation}

	in which $(\beta_i,  )$. Now, our goal is to ensure that the resulting

\end{document}

### 2021-08-02 Code/Q-Learning/StabilityandChaos/StabilityinPolymatrixGames/theory.py

@@ -8,6 +8,43 @@ import numpy as np
 import matplotlib.pyplot as plt
 from tqdm import tqdm
 import seaborn as sns
+from Agent import generateGames
+
+
+F = lambda xi, z, Xs, q, n, chi, rho, b, a: (b**2)*G * chi * Xs[xi] - a * np.log(Xs[xi]) + b * np.sqrt(q) * z - rho
+
+def getOrderParams(Xs, dz, Zs):
+    q = np.sum(((Xs) ** 2) * Dz)
+    dx = np.array([(Xs[i + 1] - Xs[i]) for i in range(len(Xs[:-1]))])
+    dxdz = dx / np.array([(Zs[i + 1] - Zs[i]) for i in range(len(Zs[:-1]))])
+    X = (1 / np.sqrt(q)) * np.sum(dxdz * Dz[:-1])
+
+    return q, X
+
+def normaliseX(Xs):
+    return Xs / np.sum(Xs * Dz)
+
+def getF(Xs, rho, b, a):
+    qs, chis = getOrderParams(Xs, dz, Zs)
+    return np.array([F(i, Zs[i], Xs, qs, nPlayers - 1, chis, rho, b, a) for i in range(len(Xs))])
+
+def lineSearch(xs, b, a, step = 1e-5, R=np.linspace(-0.5, 0.5, num=100)):
+    allYs = np.zeros(np.shape(R))
+    diff = 1e-7
+
+    for i in range(len(R)):
+        xd = xs + diff
+        xdm = xs - diff
+
+        fs = getF(xs, rho + R[i], b, a)
+        fd = getF(xd, rho + R[i], b, a)
+        fdm = getF(xdm, rho + R[i], b, a)
+
+        df = 0.5 * (((fd - fs) / (xd - xs)) + ((fs - fdm) / (xs - xdm)))
+
+        allYs[i] = abs(1 - np.sum((xs - step * fs/df) * Dz))
+
+    return rho + R[np.argmin(allYs)]
 
 nPlayers = 2
 p = nPlayers
@@ -22,62 +59,51 @@ allOrders = []
 allA = np.zeros(400)
 
 cL = 0
-for a in tqdm(np.linspace(1e-2, 3e-2, num=1)):
+for a in np.linspace(1e-2, 3e-2, num=1):
     for G in np.linspace(-1, 0, num=1):
         a = a
         b = 5e-2 * np.sqrt(nActions)
[…]

### 2021-08-02 Code/Q-Learning/StabilityandChaos/StabilityinPolymatrixGames/theorySecondAttempt.py

@@ -1,0 +1,84 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+
+def getOrderParams(Xs, dz, Dz):
+    q = np.sum(((Xs) ** 2) * Dz)
+    dx = np.array([(Xs[i + 1] - Xs[i]) for i in range(len(Xs[:-1]))])
+    dxdz = dx / dz
+    X = (1 / np.sqrt(q)) * np.sum(dxdz * Dz[:-1])
+
+    return q, X
+
+
+def lineSearch(xs, rho, b, a, step = 1e-5, R=np.linspace(-0.5, 0.5, num=100)):
+    allYs = np.zeros(np.shape(R))
+    diff = 1e-7
+
+    for i in range(len(R)):
+        xd = xs + diff
+        xdm = xs - diff
+
+        fs = getF(xs, rho + R[i], b, a)
+        fd = getF(xd, rho + R[i], b, a)
+        fdm = getF(xdm, rho + R[i], b, a)
+
+        df = (fd - fdm) / (xd - xdm)
+
+        allYs[i] = abs(1 - np.sum((xs - step * fs/df) * Dz))
+
+    return rho + R[np.argmin(allYs)]
+
+
+def getF(Xs, rho, b, a):
+    q, chi = getOrderParams(Xs, dz, Dz)
+    return np.array([getFi(i, zs[i], Xs, rho, b, a, q, chi) for i in range(len(Xs))])
+
+
+def getFi(xi, z, Xs, rho, b, a, q, chi):
+    return (b**2)*G * chi * Xs[xi] - a * np.log(Xs[xi]) + b * np.sqrt(q) * z - rho
+
+
+def findrho(Xs, zs, b, a):
+    q, chi = getOrderParams(Xs, dz, Dz)
+    allrho = np.zeros(len(Xs))
+    for xi in range(len(Xs)):
+        allrho[xi] = (b ** 2) * G * chi * Xs[xi] - a * np.log(Xs[xi]) + b * np.sqrt(q) * zs[xi]
+
+    return np.mean(allrho)
+
+if __name__ == "__main__":
+
+    nAct = 10
+
+    G = -1
+    a = 0.1
+    b = 0.1 / np.sqrt(nAct)
+
+    allA = np.zeros(10)
+
+    for cI, a in tqdm(enumerate(np.linspace(0, 0.05, num=10))):
+
+        Xs = abs(np.random.rand(100))
[…]

### 2021-08-02 Code/Q-Learning/ThreeBodyQL/ChakrabortyExpt.py

@@ -8,7 +8,7 @@ from tqdm import tqdm
 
 def TuylsChakraborty(X, t, C, agentParams):
 
-    alpha, tau, gamma = agentParams
+    T = agentParams
 
     x = X[0:2]
     y = X[2:4]
@@ -18,14 +18,14 @@ def TuylsChakraborty(X, t, C, agentParams):
     ydot = np.zeros(2)
     zdot = np.zeros(2)
 
-    xdot[0] = alpha * x[0] * tau * ((C @ z)[0] - np.dot(x, (C @ z))) + alpha * x[0] * (x[1] * np.log(x[1]/x[0]))
-    xdot[1] = alpha * x[1] * tau * ((C @ z)[1] - np.dot(x, (C @ z))) + alpha * x[1] * (x[0] * np.log(x[0]/x[1]))
+    xdot[0] = x[0] * ((C @ z)[0] - np.dot(x, (C @ z))) + T * x[0] * (x[1] * np.log(x[1]/x[0]))
+    xdot[1] = x[1] * ((C @ z)[1] - np.dot(x, (C @ z))) + T * x[1] * (x[0] * np.log(x[0]/x[1]))
 
-    ydot[0] = alpha * y[0] * tau * ((C @ x)[0] - np.dot(y, (C @ x))) + alpha * y[0] * (y[1] * np.log(y[1]/y[0]))
-    ydot[1] = alpha * y[1] * tau * ((C @ x)[1] - np.dot(y, (C @ x))) + alpha * y[1] * (y[0] * np.log(y[0]/y[1]))
+    ydot[0] = y[0] * ((C @ x)[0] - np.dot(y, (C @ x))) + T * y[0] * (y[1] * np.log(y[1]/y[0]))
+    ydot[1] = y[1] * ((C @ x)[1] - np.dot(y, (C @ x))) + T * y[1] * (y[0] * np.log(y[0]/y[1]))
 
-    zdot[0] = alpha * z[0] * tau * ((C @ y)[0] - np.dot(z, (C @ y))) + alpha * z[0] * (z[1] * np.log(z[1]/z[0]))
-    zdot[1] = alpha * z[1] * tau * ((C @ y)[1] - np.dot(z, (C @ y))) + alpha * z[1] * (z[0] * np.log(z[0]/z[1]))
[…]

### 2021-08-02 Code/Q-Learning/ThreeBodyQL/ThreeBodyFunctions.py

@@ -202,6 +202,15 @@ def TuylsCCZ(X, t, G, agentParams):
 
     return np.hstack((xdot, ydot, zdot))
 
+def averageDynamics(traj):
+    averageTraj = np.zeros(traj.shape)
+    nIter = traj.shape[0]
+    curr = np.zeros(shape=traj.shape[1])
+    for cIter, n in enumerate(range(1, nIter + 1)):
+        curr = (n * curr + traj[cIter]) / (n + 1)
+        averageTraj[cIter] = curr
+    return averageTraj
+
 if __name__ == '__main__':
 
 
@@ -215,7 +224,7 @@ if __name__ == '__main__':
     
 
     initConds = [np.array([0.41030259, 0.58969741, 0.56361327, 0.43638673, 0.53308779,
-       0.46691221]), np.array([8.00418146e-01, 1.99581854e-01, 2.93321817e-04, 9.99706678e-01,
+       0.46691221]) , np.array([8.00418146e-01, 1.99581854e-01, 2.93321817e-04, 9.99706678e-01,
        1.12708184e-01, 8.87291816e-01]), np.array([0.50203898, 0.49796102, 0.88428137, 0.11571863, 0.03295509,
        0.96704491]), np.array([0.44888546, 0.55111454, 0.34212499, 0.65787501, 0.33387894,
        0.66612106]), np.array([0.92317559, 0.07682441, 0.89499898, 0.10500102, 0.04261427,
@@ -236,26 +245,39 @@ if __name__ == '__main__':
     ax.set_xlim([0, 1])
     ax.set_ylim([0, 1])
     ax.set_zlim([0, 1])                       
-                           
-    for x0 in initConds:
 
-      # x0 = np.random.rand(3)
-      # x0 = (np.vstack((x0, 1 - x0)).T).reshape(6)
-      # alpha, tau, gamma = np.random.rand(), np.random.randint(1, 11), 0.1
-      alpha, tau, gamma = 0.1, 0.001, 0.1
-      agentParams = alpha, tau, gamma
 
-      t = np.linspace(0, int(1e6), int(1e8) + 1)
+    allFinal = np.zeros((3, 15))
 
-      sol = odeint(TuylsCCZ, x0, t, args=(G, agentParams))
-      # sol = odeint(TuylsZZC, x0, t, args=(G, agentParams))
+    for cI, tau in enumerate(np.linspace(1, 50, num=15)):
+        final = np.zeros(3)
[…]

### 2021-08-06 Documents/FP in NAGs/Reviews.tex
Added Response to Reviews

\documentclass{article}

\usepackage[margin=2cm]{geometry}

\title{Responses to Reviews}

\begin{document}
	\maketitle

	\section{Reviewer 8S4j}

	Main Review:
	Overall comments: The paper investigates the convergence of fictitious play to the Nash equilibrium of a network aggregative game. This framework rests on many simplifying assumptions that are not justified properly. The paper presentation could be greatly improved: there are many typos and sentences that are not clear or misleading. Also, the reviewer thinks that the work will greatly benefit by the identification of practical applications of such a framework.

	Detailed comments:

	The first sentence in the abstract is too vague and misleading. The link between future AI systems safety and the current work is not obvious and should either be expanded upon or removed entirely. The same goes for the last sentence in the first paragraph of the introduction.
	Also in the abstract, what does the dependence of the utility of one player on "a convex combination of its neighbours" mean? Maybe this should be rephrased.

	The following statement
	"Such guarantees allow for games to be designed so that long-term behaviour of learning is predictable regardless of how many agents are in the game."

	gives rise to the following question:

	What does this mean in real world applications in which interactions between agents occur that, more often than not, fall beyond the specific games pre-designed such that learning algorithms converge nicely to the Nash solutions?

	The authors claim an impossible task "we explore FP through numerical simulations to check whether it always converges." Such a task can only be achieved by rigurous and theoretical proof that is valid irrespective from the system parameters. Given the infinite possibilities for system parameters such a task is not possible via numerical experiments.
	Moreover, the authors provide a counter example. So the above phrasing definitely needs to be reformulated.

	In the beginning of section 2, the network aggregative game is introduced. It is not clear at this point whether this framework is original or whether it is an existing framework. If it is an original framework, the difference with the aggregative games mentioned in Sec. 1 should be made explicit.
	Also, some examples of applications which could highlight the relevance of this framework should be provided here.

	5.The set of graph nodes N and set of edges $\epsilon$ should be named when defined in Definition 1.

	Regarding the users reference $\sigma^{\mu}$, some discussion on how this information can be acquired should be provided. Some examples should be provided. This aggregation is possible only assuming that all players have the exact number of possible actions. How restrictive is this assumption? Also, some discussions should be provided about this.
	The sentence "each agent plays the same strategy against all of their neighbours" requires some explanation. Is the game performed sequencially, in pairs of players, or simultaneously?
	The sentence "In Section 3 we show that NE exist for NA games." can be a bit misleading and should be rephrased. Indeed, only under specific assumption 2 the NE exists.
	Minor comments

	Typos : "works looking at ... is sparse", "two-plpayer", "a natural extension to of"

	The reference to an assumption (II) in Lemma 1 has not been defined.

	Limitations And Societal Impact:
	Some discussions are made at the end of the paper (before the reference section). This paper is theoretical and no immediate applications are identified aside from learning in multi-agent systems.

	\subsection{Response}

	We thank the reviewer for their detailed review and their insightful comments. Regarding the link between the present work and the safety of AI systems concerns the fact that multi agent learning has been shown to lead to chaotic dynamics, a problem which becomes more prevalent as the number of agents increase. As such, it is important to find models which allow us to place guarantees (stability or regret) on the long term behaviour of learning regardless of the number of players. Our work presents a contribution towards this direction in the form of learning on the NA Game model. Under this assumption, it is possible to place theoretical guarantees which is independent of the number of players. We will be sure to make this motivation clear in our revision.

	Regarding the point of numerical simulations, our aim was indeed to provide an example for which Fictitious Play does not converge to an NE. We will be sure to state this explicitly in the revision.

	The network aggregative game is a model which was introduced in 2015 for control problems of load balancing and robotic swarms. We will clarify this point as well as the applications of such a model which have in the literature (e.g. Parise et al 2015).

	Regarding the reviewer's question on the behaviour of FP in games for which the learning algorithm does not necessarily converge to an NE, this is an important point for ongoing research. One of the empirical results which we present in our study suggests that the inclusion of noise in the reference measurement may allow for the learning dynamics to become stable. This is a point that we are currently exploring.

	We thank the reviewer for pointing out that further clarification is required in how the reference $\sigma^\mu$ is obtained. Ineed we aimed for this to generalise as much as possible, so that $\sigma^\mu$ can be calculated by each individual agent, or can be supplied from a central coordinator. We will expand on this, as well as noting some examples in our revision.

	\section{Reviewer CBzS}

	Main Review:
	This work studies convergence properties of continuous time Fictitious Play dynamics for Network Aggregative (NA) games. NA games are games where there is an underlying weighted directed network and every player plays a bimatrix game with a convex combination (according to the network’s weights) of her neighbors.

	The authors start their study by focusing on zero sum NA games. After proving existence of Nash equilibria (NE) and that indeed fictitious play creates dynamics, they observe that a technique that works for the setting where for every edge there is a different bimatrix game [Ewerhart and Valkanova 2020] works also for NA games, as long as the game is zero sum. Going along its lines, they prove that the dynamics converge to fixed points, which if we forbid self-loops coincide with NE. Next they talk about general (possibly non zero sum) NA games and prove that if we forbid self loops then the players achieve no regret. To conclude their work, the authors give an example of a non zero sum game for which the fictitious play dynamics do not converge to equilibria. Going a bit off course, they also show that the presence of noise may result in non convergence to equilibria.

	Pros: First and rich enough study of continuous time fictitious play dynamics on NA games.

	Cons: Unclear how big/important the set of NA games is, Assumption 4 is a bit peculiar. Simulates previous techniques without many new ideas.

	How does the set of zero sum NA games compares to the set of zero sum network games of [Ewerhart and Valkanova 2020] or the set of zero-sum network coordination games. Any strict inclusions? (I am trying to understand implications of Assumption 4).

	Line 87: “player” 123: you talk about a convex combination (without assuming Assumption 1), so you may want to skip it or write it in Definition 1 (or deal with this somehow).

	\subsection{Response}

	We thank the reviewer for their detailed analysis of our work. We particularly appreciate the point regarding the significance of the NA game. We will be sure to include examples and applications in our revision. To respond to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova). Such a transformation is required so that self-loops can be allowed, and it can be shown that Fictitious Play still converges to an equilibrium (though not always Nash). This point was not considered in Ewerhart and Valkanova's analysis. In addition, we aimed to extend beyond the zero-sum case (Assumption 4) with our regret analysis in Sec. 4. The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated.

	\section{Reviewer xcy8}

	The methods are based off a [Ewerhart/Walkanova 2020] in fictitious play in networks a natural extension of the continuous-time fictitious play [Haofbauer 2006], and the standard results on CCE regret. It is not clear how much novelty there is in relation to these works, besides from extending it to network aggressive maybe the author could elaborate? The contributions are to show that NA games have Nash and they are stable for networks without self-loops. Since the games are zero-sum, is it not already known that the Nash equilibria of zero-sum games are stable? What properties of NA are being employed to ensure any stronger set of results?

	The methods used are appropriate and the submission is clearly written. However, the significance of the results may be limited as similar results have been shown for zero sum network games in general, which NA games are a subset of, if I am understanding correctly. The authors can provide more unique data or conclusions about existing theoretical approach and why theirs are significant contribution.

	\subsection{Response}

	We thank the reviewer for their review and their insightful comments. Regarding the contributions, our work begins by showing that  Fictitious Play converges to an equilibrium in zero-sum NA games regardless of whether or not the network has self-loops. Convergence to a Nash Equilibrium thus becomes a special case for when there are no self-loops. To show convergence, we explicitly show how the NA game can be transformed into an equivalent network game, and how the analysis extends regardless of the existence of such self-loops. Each agent can, therefore, account for their own state as well as that of their neighbours when playing the game.

	In addition, we aimed for our analysis to extend beyond the zero-sum case. It was with this in mind that we analyse the regret properties of Fictitious Play in arbitrary NA games. Specifically, Theorem 2 shows that, regardless of the number of players in the game, or the nature of the game itself, Fictitious Play will still achieve no regret. This generalises the result of van Strien and Ostrovski, which only looked at games of two players.

	\section{Reviewer geyC}

	Originality: The work uncovers promising results about learning dynamics in a natural class of games. Although not a major concern of mine, I do think that connections between this work and prior work on learning in network games could have been more clearly highlighted.

	Quality: I did not have a chance to carefully read the full proofs in the appendix, but the results seemed reasonable and sound. The only issue I had with the paper is that the results should have been presented more formally. Throughout the paper it is a bit unclear which of the assumptions (from section 2.3) are being used for which result. From context it often became clear, but the formal results would have more impact if this was clarified in the statements. Similarly, in several places the phrase "for almost all time" is used but never explained (e.g., definition 4). Clarifying what these sorts of details are refering to in formal statements would be very helpful (even if just intuitively in the main paper).

	Clarity: Overall the paper is well written and clear. There are a few formatting issues that should be fixed. Most notably:

	The citation style should be fixed throughout paper (e.g. Line 15 Schwartz [2015] should be a citep command) since it can greatly disrupt the flow of the writing.
	On line 263 there is a reference to Remark 4, but remarks are not numbered throughout the paper.
	The plots in Figure 1 are a bit squished and it is hard to see details in them. For the cyclic dynamics it is easy to see the point that is being made, but for the convergent dynamics it is pretty difficult to distinguish from more complex dynamics.
	In addition, there are some technical details that seem to have small errors in them:

	Mixed strategies are defined as being on the unit simplex, but should they not be on the unit simplex? Either adding a non-negative constraint to the set or restricting to the non-negative reals would fix this.
	For the example given in the remark at the end of section 2.2, according to the definition given earlier in that section shouldn't alpha be the average of the other player's strategy to keep consistent with the definition given earlier in that section?
	The definition of zero-sum NA games given in assumption 4 is confusing due to the set of states given at the start of line 188.
	On line 201, is the utility defined there missing a weighted sum over neighbors' states?
	The labels in the supplementary materials do not match the labels in the main paper. For example, the proof of Lemma 1 in the main paper (existence of Nash) appears in the supplementary materials under the label "Proof of Theorem 2".
	Finally, although the presentation of assumptions is not a problem, I wanted to suggest introducing assumptions alongside their related concept. I believe this would help clarify things throughout the paper. For example, having assumption 1 (row stochastic weights) given along with the definition of NA games might help readers familiar with game theory gain intuition about NA games early on. Also, doing this might help clarify which sections/results use certain assumption or not.

	-- Small Typos: --- Line 55 "shownin" -> "show in" --- Line 87 "in two-plpayer games" -> "into two-player games" --- Line 365 "As such we Furthermore" -> "Furthermore"

	Significance: I believe the results would be of interest to many researchers studying learning in games. This work gives positive results for a classic learning dynamic while also highlighting a well-motivated class of games where studying learning dynamics could be (relatively) "easier" than other common multi-agent settings.

	\subsection{Response}

	We thank the reviewer for the detail and rigour in their review. Particularly the point regarding stating assumptions within the formal statements of the results is a good one and we will be sure to make this adjustment within our review. We will also be sure to make the suggested minor adjustments and we thank the reviewer for listing these.

	To respond to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova). Such a transformation is required so that self-loops can be allowed, and it can be shown that Fictitious Play still converges to an equilibrium (though not always Nash). This point was not considered in Ewerhart and Valkanova's analysis. In addition, we aimed to extend beyond the zero-sum case (Assumption 4) with our regret analysis in Sec. 4. The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated.

	In addition, the reviewer raises a fascinating question regarding the relationship between the strength of the self-loop component and the distance from the NE. This is certainly an interesting direction for future research and one that we will consider.

	\section{Reviewer k5tG}

	Firstly, it was unpleasant to read this paper because it is very badly written. There are typos and imprecisions in almost every sentence, many references are just cosmetic and has nothing to do here while several papers that must be cited are not (for example the best response dynamics was introduced by Gilboa and Matsui (not cited), Coarse Equilibria was introduced by Moulin and Vial (not cited), etc), some researchers are cited in the main text with their name and surname (Joseph Hofbauer), others not...

	A the scientific level, the model is not precisely and formally defined, it looks me a while to understand what's going on and how network aggregative games are to be defined... It's only after reading another paper: "Fictitious Play in Networks" by Ewerhart and Valkanova (GEB, 2020) that I understood the model of this paper and that there is nothing new in the paper compared to Ewerhart and Valkanova.

	The unique innovation is the addition of weights instead of summing the payoffs of the neighbours, but I am sure that with some imagination we can show that the models are equivalent. In any case, the proof is exactly the same, no additional idea of difficulty. The fact that the best response dynamics has no regret (in continuous time) has nothing surprising as, in a standard game, this holds by construction at every moment in time with a zero regret even. The problem is in the discretisation (and we know that FP does not have the no-regret property in discrete time).

	The biblio contains many many typos and is not in alphabetical order with respect to the names (in the same reference), many references are cited in a very incomplete way for example without the journal name, or a book with a volume number, etc (see lines 442, 426, 452, 472, etc).

	Regarding the appendix, half of it are trivialities: that an equilibrium exists in a game where the payoff function is continuous and linear wrt to each player's strategy is well known.

	\subsection{Response}

	We thank the reviewer for their insightful comments and detailed review. We are also grateful for pointing out some of the original references for concepts of Coarse Equilibria and Best Response Dynamics. Our references were chosen with the aim to keep the notation and ideas as similar to our own work, but we will be sure to include the references you have suggested in our revision.

	It is indeed true that the NA game can be shown to be equivalent to the network game, and the proof of Theorem 1 is in showing the nature of this transformation. However, in making this transformation, an additional result can be found - namely that networks even with self loops can be considered and that, in this case, the techniques of Ewerhart and Valkanova can be applied to show convergence to a fixed point. This component was not realised in Ewerhart and Valkanova's work. In addition, existing results on the no regret property of Continuous Time Fictitious Play exist only in the two-player case or in specific classes of games (e.g. zero sum). The most recent contribution in this direction was that of van Strien and Ostrovski (2014) who showed the no-regret property holds in all two-player games. Our contribution generalises this result towards all NA games, regardless of the number of players or the type of game being played. The reviewer also makes an interesting suggestion to look at the discrete variant of Fictitious Play. This is indeed an interesting avenue for future research and one which we are currently exploring.

\end{document}

### 2021-08-09 Documents/FP in NAGs/Reviews.tex
Updated Responses

@@
 We particularly appreciate the point regarding the significance of the NA game.
-We will be sure to include examples and applications in our revision.
-To respond to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova).
-Such a transformation is required so that self-loops can be allowed, and it can be shown that Fictitious Play still converges to an equilibrium (though not always Nash).
+We will be sure to include examples and applications from the literature (e.g.
+Parise et al.
+2015) in our revision.
+In response to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova).
+This turns out to be true even if the NA game possesses self-loops.
+In such a case, it is shown that Fictitious Play still converges to a fixed point, though not always Nash.
 This point was not considered in Ewerhart and Valkanova's analysis.
@@
 4.
-The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated.
+The regret result allows for an understanding of Fictitious Play in all multi-player NA games, even if Assumption 4 is not satisfied.
 
@@
 	We thank the reviewer for their review and their insightful comments.
-Regarding the contributions, our work begins by showing that  Fictitious Play converges to an equilibrium in zero-sum NA games regardless of whether or not the network has self-loops.
+Regarding the contributions, our work begins by showing that Fictitious Play converges to a fixed point in zero-sum NA games regardless of whether or not the network has self-loops.
 Convergence to a Nash Equilibrium thus becomes a special case for when there are no self-loops.
+Each agent can, therefore, account for their own history as well as that of their neighbours when playing the game.
+In a sense, the agent is able to consider itself as an opponent also.
 To show convergence, we explicitly show how the NA game can be transformed into an equivalent network game, and how the analysis extends regardless of the existence of such self-loops.
-Each agent can, therefore, account for their own state as well as that of their neighbours when playing the game.
 
@@
 This generalises the result of van Strien and Ostrovski, which only looked at games of two players.
+Similarly, Ewerhart and Valkanova were able to show a no-regret property for Fictitious Play which only applies in the zero-sum case, whereas Theorem 2 applies to any game.
+
+	Finally, we conclude with some experiments which highlight an additional property of Fictitious Play.
+One of the more surprising results is that the presence of noise seems to lead to fixed behaviour, even in cases where the original system did not converge.
+The implication is that Fictitious Play in NA games may be a robust process by which multiple agents can coordinate, a topic which we suggest for future theoretical exploration.
 
@@
 
-	To respond to your query, any NA game can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova).
-Such a transformation is required so that self-loops can be allowed, and it can be shown that Fictitious Play still converges to an equilibrium (though not always Nash).
+	To respond to your query, any NA game (whether or not there are self-loops) can be shown to be equivalent to a network game (as defined by Ewerhart and Valkanova).
+Once this transformation has been applied, it is possible to show that Fictitious Play will converge to an equilibrium.
+Convergence to Nash thus becomes a special case for when there are no self-loops.
 This point was not considered in Ewerhart and Valkanova's analysis.
@@
 The regret result allows for an understanding of Fictitious Play even if the zero-sum requirement is violated.
+For the case of zero-sum network games, Ewerhart and Valkanova were able to show that the no regret property holds.
+Theorem 2 aims to extend this analysis towards all multi-player NA games, regardless of whether Assumption 4 is satisfied.
 
@@
 This is certainly an interesting direction for future research and one that we will consider.
+
+	Finally, we are grateful that the reviewer listed some of the formatting issues within the paper. We will ensure that each of these are resolved in the final submission.
 
@@
 	It is indeed true that the NA game can be shown to be equivalent to the network game, and the proof of Theorem 1 is in showing the nature of this transformation.
-However, in making this transformation, an additional result can be found - namely that networks even with self loops can be considered and that, in this case, the techniques of Ewerhart and Valkanova can be applied to show convergence to a fixed point.
-This component was not realised in Ewerhart and Valkanova's work.
+However, in making this transformation, an additional result can be found - namely that networks even with self loops share this equivalency and that, in this case, the techniques of Ewerhart and Valkanova can be adapted to show convergence to a fixed point.
+Convergence to Nash thus becomes a special case for when there are no self-loops.
+This point was not considered in Ewerhart and Valkanova's analysis.
 In addition, existing results on the no regret property of Continuous Time Fictitious Play exist only in the two-player case or in specific classes of games (e.g.
@@
 The most recent contribution in this direction was that of van Strien and Ostrovski (2014) who showed the no-regret property holds in all two-player games.
-Our contribution generalises this result towards all NA games, regardless of the number of players or the type of game being played.
+Similarly, Ewerhart and Valkanova were able to prove a no-regret property in the specific case that the game is zero-sum.
+Our contribution in Theorem 2 generalises these results towards all NA games, regardless of the number of players or the type of game being played.
+
+	Finally, we conclude with some experiments which highlight an additional property of Fictitious Play.
+One of the more surprising results is that the presence of noise seems to lead to fixed behaviour, even in cases where the original system did not converge.
+The implication is that Fictitious Play in NA games may be a robust process by which multiple agents can coordinate, a topic which we suggest for future theoretical exploration.
+
 	The reviewer also makes an interesting suggestion to look at the discrete variant of Fictitious Play.

### 2021-08-09 Documents/FP in NAGs/neurips_2021.tex
Updated Responses

@@
 is defined
-as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \mid \sum_i
+as $\Delta_\mu := \{\xmu \in \mathbb{R}^n_+ \mid \sum_i
 \xmuaction{i} = 1\}$.
@@
     The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu,
-    \weightedsum) = 0$ for any set $(x^\mu)_{\mu \in N^\mu}$ of
+    \weightedsum) = 0$ for any set $(x^\mu)_{\mu \in \agentset}$ of
     states. This is, perhaps, one of the strongest assumptions in our
@@
   \begin{align}
-    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w_{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
+    u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\nu} w^{\mu \nu} \NE{\nu}) & = x \cdot A^\mu (w^{\mu \mu} x + \sum_{\nu \in N^\mu} w_{\mu \nu} \NE{\nu}) \label{eq::bilinear1}\\
      & = x \cdot (w^{\mu \mu} A^\mu)  x + \sum_{\nu \in N^\mu} u^{\mu \nu}(x, \NE{\nu}) \label{eq::bilinear2} \\
@@
 %  
-  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot A^\mu x^\nu$.
+  where $u^{\mu \nu}(\xmu, x^\nu) = \xmu \cdot (w^{\mu \nu}A^\mu) x^\nu$.
 

### 2021-08-09 Code/Q-Learning/StabilityandChaos/StabilityinPolymatrixGames/LCE.py
Added LCE Code

@@ -1,0 +1,124 @@
+import numpy as np
+from scipy.linalg import block_diag
+from tqdm import tqdm
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+def generateGames(gamma, nSim, nAct):
+    """
+    Draw a random payoff matrix from a multivariate Gaussian, currently the unscaled version.
+
+    gamma: Choice of co-operation parameter
+    nAct: Number of actions in the game
+
+    [reward1s, reward2s]: list of payoff matrices
+    """
+
+    nElements = nAct ** 2  # number of payoff elements in the matrix
+
+    cov = np.eye(2 * nElements)  # <a_ij^2> = <b_ji^2> = 1
+    cov[:nElements, nElements:] = np.eye(nElements) * gamma  # <a_ij b_ji> = Gamma
+    cov[nElements:, :nElements] = np.eye(nElements) * gamma
+
+    rewardAs, rewardBs = np.eye(nAct), np.eye(nAct)
+
+    for i in range(nSim):
+        rewards = np.random.multivariate_normal(np.zeros(2 * nElements), cov=cov)
+
+        rewardAs = np.dstack((rewardAs, rewards[0:nElements].reshape((nAct, nAct))))
+        # rewardAs = np.dstack((rewardAs, np.array([[1, 5], [0, 3]])))
+        rewardBs = np.dstack((rewardBs, rewards[nElements:].reshape((nAct, nAct)).T))
+        # rewardBs = np.dstack((rewardBs, np.array([[1, 0], [5, 3]])))
+    return [rewardAs[:, :, 1:], rewardBs[:, :, 1:]]
+
+def checkVar(checkWindow, windowSize, tol):
+    C = checkWindow.reshape((nAct * nAgents, nInit, windowSize))
+    return np.mean(np.var(C, axis=2), axis=0) < tol
+
+def checkMinMax(checkWindow, windowSize, tol):
+    C = np.transpose(checkWindow, (0, 3, 1, 2, 4))
+    C = C.reshape((nAct * nAgents, nInit, nSim, windowSize))
+    return np.all(((np.max(C, axis=3) - np.min(C, axis=3))/np.min(C, axis=3)) < tol, axis=0)
+
+def pLCE(data):
+    data = np.reshape(data.transpose(1, 3, 0, 2, 4), (nAgents * nAct, nInit, nSim, nIter))
[…]

### 2021-08-12 Documents/FP in NAGs/Convex FP/ConvexFP.tex
Added Convex Stuff

@@
 		\end{pmatrix} = \begin{pmatrix}
-		-I_n & \bar{A} \\ - I_n & \bar{B}
+		-I_n & \bar{A} \\ \bar{B} & -I_n
 		\end{pmatrix} \begin{pmatrix}
@@
 		\begin{pmatrix}
-			-I_n & \bar{A} \\ - I_n & \bar{B}
+			-I_n & \bar{A} \\ \bar{B} & -I_n
+		\end{pmatrix} = \begin{pmatrix}
+		0 & \bar{A} \\ \bar{B} & 0
+	\end{pmatrix} - I_{2n}
+	\end{equation}
+
+	If they are all negative, then the system is stable.
+If any eigenvalue is positive, then the system is unstable.
+To begin with we have that since every matrix commutes with the identity (\ah{Need to find the reference for this, but I am using the following result: As a direct consequence of simultaneous triangulizability, the eigenvalues of two commuting complex matrices A, B with their algebraic multiplicities (the multisets of roots of their characteristic polynomials) can be matched up}), our eigenvalues take the form
+
+	\begin{equation}
+		\lambda_i = \xi_i - 1		
+	\end{equation}
+
+	in which $\xi_i$ is an eigenvalue of the matrix
+
+	 \begin{equation}
+	 	\Lambda := \begin{pmatrix}
+	 		0 & \bar{A} \\ \bar{B} & 0
 	 	\end{pmatrix}
@@
 
-	If they are all negative, then the system is stable. If any eigenvalue is positive, then the system is unstable. The eigenvalues are determined from the characteristic function
+	Now, we need that $\lambda_i \leq 0$, so that $\xi_i \leq 1$. From Gershgorin's disk theorem, we have that any $\xi_i$ must lie in one of the disks
 
 	\begin{equation}
-		det \left\{ (-1 - \lambda)(\bar{B} - \lambda I_n) + \bar{A} \right\} = 0
+		\{ z \in \mathbb{C} : |z| \leq \sum_{j \neq i} |\Lambda_{ij}| \}
 	\end{equation}
 
-	Our job now is to determine conditions on $\bar{A}$ and $\bar{B}$ so that $\lambda$ comes out negative.
-To begin with we have that, if $\bar{A}$ and $\bar{B}$ commute (i.e.
-$\bar{A}\bar{B} = \bar{B}\bar{A}$), then our eigenvalues satisfy (\ah{Need to find the reference for this, but I am using the following result: As a direct consequence of simultaneous triangulizability, the eigenvalues of two commuting complex matrices A, B with their algebraic multiplicities (the multisets of roots of their characteristic polynomials) can be matched up})
+	We can, of course, separate these disks out into the individual components given by $\bar{A}$ and $\bar{B}$
 
 	\begin{equation}
-		\prod_{i = 1}^{n} (-1 - \lambda_i) (\beta_i - \lambda_i) + \alpha_i = 0, 
+		\{ z \in \mathbb{C} : |z| \leq \sum_{j = 1}^{n} |\bar{A}_{ij}| \} \hspace*{1cm} \{ z \in \mathbb{C} : |z| \leq \sum_{j = 1}^{n} |\bar{B}_{ij}| \}
 	\end{equation}
 
-	in which $(\beta_i,  )$. Now, our goal is to ensure that the resulting
+	A sufficient condition for stability, therefore, is that
+
+	\begin{equation}
+		\sum_{j = 1}^{n} |\bar{A}_{ij}| \leq 1 \hspace*{1cm} \sum_{j = 1}^{n} |\bar{B}_{ij}| \leq 1
+	\end{equation}
+
+	for all $i$. In words, this condition means that all of the rows of both $|\bar{A}|$ and $|\bar{B}|$ sum to at most one.
+
+	 \section{Extension to $p$-player games}
+
+	In this case, we have a cost function given by
+
+	\begin{equation}
+		u^\mu(x^\mu, \alpha_\sigma^\mu) = ||\xmu - \xmu_d||_{A^\mu_1} + ||\xmu - \alpha_\sigma^\mu||_{A^\mu_2}
+	\end{equation}
+
+	So that
+
+	\begin{equation}
+		BR^\mu(\alpha_\sigma^\mu) = \bar{A}^\mu_1 x_d + \bar{A}^\mu_2 \alpha_\sigma^\mu(t)
+	\end{equation}
+
+	In this case the Fictitious Play Dynamic (after making the appropriate transformation) is given by
+
+	\begin{align*}
+		& \dot{\alpha}^\mu(t) = \frac{1}{t} \left( \bar{A}^\mu \alpha_\sigma^\mu(t) - \alpha^\mu(t) \right) \\
+		\implies & \alpha(t) = \frac{1}{t} \left( \begin{pmatrix}
+			A^1 & & \\
+			& \ddots & \\
+			 & & A^N \\
+		\end{pmatrix} (W \otimes I_n ) - I_{Nn} \right) \alpha(t)
+	\end{align*}
+
+	Again, our eigenvalues are given by
+
+	\begin{align*}
+		\lambda_i = \xi_i - 1
+	\end{align*}
+
+	where now $\xi_i$ are the eigenvalues of
+
+	\begin{equation}
+		 \begin{pmatrix}
+			A^1 & & \\
+			& \ddots & \\
+			& & A^N \\
+		\end{pmatrix} (W \otimes I_n )
+	\end{equation}
+
+	We require that $\xi_i \leq 1$ for stability.
 
